### 2015-01-07 Papers/Prototype_1_Method/article.tex
adding Papers to the repo

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later c.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,authoryear,1p,times]{elsarticle}
%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,3p,times]{elsarticle}
%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,5p,times]{elsarticle}
%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

\usepackage{comment}

\usepackage{epstopdf}

\usepackage{bm}
\usepackage{hyperref,url}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}

\usepackage[obeyFinal]{todonotes}

\newcommand{\jrp}[1]{\todo[color=blue!30, size=\small]{JRP: #1}}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb,amsmath,array}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}

\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG: #1}}}
%\journal{Computer Methods in Applied Mechanics and Engineering}
\journal{Comput Meth Appl Mech Eng}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Overlapping Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling \\
Part I: Formulation}

%% use optional labels to link authors explicitly to addresses:
\author[UoA]{J.L.M.A. Gomes}\corref{cor1}\ead{jefferson.gomes@abdn.ac.uk} \author[IC]{D. Pavlidis} 
\author[IC]{J.R. Percival} \author[NSW]{P. Mostaghimi} \author[IC,NORMS]{P. Salinas} \author[IC]{Z. Xie} 
\author[IC]{C.C. Pain} \author[NORMS]{M.D. Jackson}
%\author[IC]{M. Blunt}

\cortext[cor1]{Corresponding author.}
\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
\address[IC]{Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK}
\address[NSW]{School of Petroleum Engineering, University of New South Wales, Australia}
\address[NORMS]{Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK}

\begin{abstract} 
This is the first of two papers devoted to a novel finite element method formulation to solve subsurface multi-fluid flows. The overlapping control volume finite element method (OCVFEM) has two major strengths, firstly it uses a dual consistent pressure-velocity representation in control volume and finite element spaces which ensures local mass conservation. Secondly, it uses a family of finite element types that ensures Darcy equations for multiphase flows can be exactly enforced. The underlying mass conservation equations are solved in control volume space and finite elements are used to obtain high-order fluxes on control volume boundaries. The novelty of the method lies in (a) permitting both continuous and discontinuous description of pressures and saturations between elements; (b) the use of arbitarily high-order polynomial representation for pressure and velocity within the mixed formulation; (c) the use of high-order flux-limited methods to avoid introducing non-physical oscillations as well as achieving high-order time accuracy where and when possible.   In this paper, the new model is described and test cases are introduced to show the numerical accuracy in one- and two-dimensional simulations. More extensive applications are introduced in the second part of this two part paper. 
\end{abstract}

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Multi-fluid flows \sep Darcy equations \sep Porous media \sep Finite element methods \sep Mixing formulation \sep Discontinuous Galerkin.

\end{keyword}

\end{frontmatter}

%\tableofcontents
%\linenumbers

\clearpage
%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Introduction}
Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines from hydrocarbon and groundwater exploration and safety assessment of deep geological disposal of radioactive waste to CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{chen_2006, aiea_1999, pruess_1990c, jiang_2011}. Complex geometries with irregular (and often internal) boundaries and heterogeneous geological formations are some of the main challenges to accurately simulate such flows.

Finite difference methods (FDM) have been extensively used in modelling and simulation of fluid flows in porous media~\citep{aziz_1986, chen_1997, chen_2005} however, they are strongly dependent on mesh quality and orientation and cannot easily represent complex geometries. In addition, FDM produce excessive numerical dispersion in heterogeneous media \citep{chavent_1986}. The geometrical flexibility of finite element methods (FEM) has proven to overcome these deficiencies. Among FEM-based formulations for porous media, the control volume finite element method (CVFEM) has become increasingly popular as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, cordazzo_2004, fung_1992, geiger_2004, cumming_2011, hurtado_2007}.  \citet{huber_2000} demonstrated that the vertex-centred finite volume - finite element method (or Box scheme) can achieve similar goals~\citep[see also][]{helmig_1997}.

For porous media flows, CVFEM discretisations with Galerkin-FEM formulation for the pressure equation has been used to solve Darcy and Richard equations as described by \citet{fung_1992} and \citet{cumming_2011}. \citet{durlofsky_1993,durlofsky_1994} investigated a mixed FEM formulation (i.e., piecewise constant in pressure and piecewise linear in velocity) and classical CVFEM for single phase Darcy flow. He concluded that the latter is more computationally efficient and numerically accurate than the former for simple problems involving a (relatively) small number of degrees of freedom. Moreover, for complex discontinuous and heterogeneous problems, mixed FEM formulations lead to physically realistic solutions.

\medskip

CVFEM often requires high resolution meshes in regions where material properties vary abruptly, such as permeability contrasts at fracture-matrix interfaces. Since the structural geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties. Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CV's at these interface. This often leads to excessive numerical dispersion, especially in highly heterogeneous media.

In order to overcome this deficiency, \citet{nick_2011b, nick_2011a} developed a new discretisation scheme -- discontinuous hybrid finite element finite volume method (DFEFVM), where CV's split along the interfaces of different material properties. This scheme was designed to simulate single and multiphase flows through discrete fractured rocks. \citet{cumming_2011} demonstrated that CVFEM-based discretisation could be used to solve Richards' equations (coupled mass conservation and Darcy equations) in heterogeneous porous media with relatively small computational overhead, compared with traditional coupled velocity-pressure based formulations. Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}~\citep[see also][]{forsyth_1990,cumming_phd2012}.

Discontinuity-capturing schemes~\citep[e.g., shock waves, contact surface or material discontinuity -- see][]{brooks_1982,tezduyar_1986,toro_1997} were originally developed to resolve sharp changing of field variables. Related discontinuity-capturing schemes include the discontinuous-Galerkin FEM (DGFEM) scheme in which continuity of the solution is not explicitly enforced, allowing sharp gradients in the solution fluxes to be captured. The DG formulation is a stabilised finite element method that is (a) locally conservative, (b) designed to achieve high-order accuracy, and (c) used in a wide range of Reynolds numbers applications. DGFEM solution fields are allowed to be discontinuous at the element faces, thus the flow solution is able to naturally handle discontinuities at material interfaces. In addition, DGFEM is well-suited to deal with interface problems by incorporating specially-designed interface fluxes. These properties have attracted the attention of subsurface flow research communities in the last 15 years \citep[see][]{riviere_2000,riviere_2002,bastian_2002}.

\medskip

In this paper, we describe a novel overlapping CVFEM (or OCVFEM) discretisation which is conservative and consistent \citep{jackson_2013}. The continuity equations are embedded into the pressure equation to enforce mass conservation and exact force balance. This is possible by using dual CV and FEM discretisations for the pressure equation, while saturation is discretised using a CV formulation. We employ an implicit algorithm with respect to time. The implicit method is unconditionally stable for pure advection, with no restriction on the time step size.

The formulation has two key developments. Firstly, it uses a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a  family of triangular and tetrahedral finite element pairs, P$_{n}$DG-P$_{n+1}$ \citep[see][]{cotter_2009b}. In this element type, the dual velocity and pressure fields are represented by $n^{\rm th}$ order (discontinuous) and $({n+1})^{\rm th}$ order (continuous) polynomials, respectively. This allows the velocity to exactly represent pressure gradients in the flow solution for homogeneous material properties. 
The P$_{n+1}$DG-P$_{n}$DG element pair, which has similar properties to the P$_n$DG-P$_{n+1}$ element pair, allows a representation in which pressure, \jrp{Saturation is on the control volume space and thus always discontinuous} saturation and other solution variables are all fully discontinuous across finite element boundaries. The second key development is that this formulation uses an overlapping finite element representation of velocity within each element. This approach can achieve an exact representation of the Darcy force balance equations.

\medskip
This is the first of two papers on the proposed methodology. Here we focus on model description and initial validation, whereas in the second part~\citep{pavlidis_2013} we employ the numerical formulation for a number of multiphase porous media flow simulations to demonstrate numerical accuracy and convergence rates. The remainder of this paper is organised as follows. New element types and the overlapping formulation are introduced in Sections~\ref{element_types_section}-\ref{overlapping_method_section}.  A detailed description of the new porous media methods is given in Section~\ref{transport_methods_section}. Scalar field equations, upwinding schemes and solution methods are introduced in Sections~\ref{Section:Saturation_Global}-\ref{Section:SolvingLinearEqns}. Initial model validation is presented in Section~\ref{Section:Results} and final remarks are drawn in Section~\ref{conc}.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Continuous and Discontinuous Finite Element Types and Control Volumes} \label{element_types_section}
The family of P$_{n}$DG-P$_{n+1}$ element pairs was originally introduced by \citet{cotter_2009a} for geophysical fluid dynamics applications \citep[see also][]{cotter_2012}. In particular, the P$_{1}$DG-P$_{2}$ element pair was originally developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes. This element pair uses element-wise linear polynomial FE basis functions, discontinuous across element interfaces, for velocity $\left(\text{P}_{1}\text{DG}\right)$ and quadratic polynomial finite element basis functions for pressure which maintain $C_{\text{0}}$ continuity across element boundaries $\left(\text{P}_{2}\right)$. %This is analogous to the exact balance also achieved with this element between the frictional and pressure gradient terms in Darcy's equations.

Figure~\ref{fem_cv_represent_a} displays three element types of the P$_{n}$DG-P$_{n+1}$ family that are used in this set of papers. P$_{\text{0}}$DGP$_{\text{1}}$ (a)  and P$_{1}$DG-P$_{2}$ are shown in Fig.~\ref{fem_cv_represent_a}(a) and (b), respectively, where pressure nodes are stored in the vertices and edges (in P$_{\text{2}}$ elements) of triangular/tetrahedral elements and control volumes are constructed around them based on a Voronoi decomposition.  One can realise that due to the continuous finite element node structure, control volumes span more than one element. Having CV's spanning to multiple elements may create artificial diffusion in cases where there is a large variations in physical properties across elements, such as at the boundary between materials with different absolute permeabilities . As an alternative, two families of fully discontinuous element pairs are also considered: P$_{n}$DG-P$_{n}$DG and P$_{n+1}$DG-P$_{n}$DG, Fig.~\ref{fem_cv_represent_a}(c) along with control volumes from their dual Voronoi decompositions. These families of elements are LBB stable and free from chequerboard pressure modes, as demonstrated by~\citet{cotter_2009b}~\citep[see also][]{cotter_2011}.

%\begin{center}
%\JGnote{Most of the simulations in this paper (and the next) were performed using P$_{1}$DGP$_{2}$ elements. However it seems that the sketch of this element pair was deleted/replaced by P$_{0}$DGP$_{1}$ and by the double-discontinuous element (fig.1 left/right) -- was this replacement on purpose or was it a mistake?} 
%\end{center}

\section{Overlapping-CVFEM Formulation -- An Accurate Representation of Multiphase Darcy Flows}
\label{overlapping_method_section}
Darcy's law for immiscible multiphase flow may be written \citep{chen_2006} in the form:%,bear_1972}:
\begin{equation}\label{e:darcy_eqn}
  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
\end{equation}
where $\mathbf{q}_{\alpha}=\left(q_\alpha^{(1)},q_\alpha^{(2)},q_\alpha^{(3)}\right)^{\text{T}}$ (for 3D flow) is the $\alpha$-th phase Darcy flow rate, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, and $\mu_{\alpha}$, $p_{\alpha}$ and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure and a source term, respectively.

If we define the interstitial or advective phase velocity, averaged over the entire medium as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then we may rewrite Eqn.~\ref{e:darcy_eqn} as:
\begin{equation}
  \bm{v}_\alpha:= {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
  \label{force-bal}
\end{equation}
where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces and $\bm{v}_\alpha$ is a saturation averaged vector of the force density of the phase, related to the advective velocity through $\bm{u}_\alpha={\underline {\underline \sigma}}_{\alpha}^{-1}\bm{v}_\alpha$.% arising in the derivation of extended Darcy's law.

In order to discretise Eqn.~\ref{force-bal}, we assume a finite element representation for the force and pressure fields and a control volume representation for phase saturation fields. The representations for force density and pressure in terms of their FE basis functions $Q_{j}$ and $P_{j}$  may be expressed, respectively, as:
\begin{displaymath}
  \bm{v}_\alpha(\bm{r},t) = \sum\limits_{j=1}^{\mathcal{N}_u} Q_{j}(\bm{r})\bm{v}_{\alpha,j}(t) \;\;\;\;\text{ and } \;\;\;\; p(\bm{r},t)  = \sum\limits_{j=1}^{\mathcal{N}_p} P_{j}(\bm{r})p_{j}(t).
\end{displaymath} 
Here $\mathcal{N}_{u}$ and $\mathcal{N}_{p}$ are the total number of degrees of freedom for the FE force and pressure representations. Each component of the weak form of the force balance (Eqn.~\ref{force-bal}) is tested with the force density basis function space to obtain:
\begin{eqnarray}
  \sum\limits_{E} \left. \int\limits_{\Omega_E} { {Q}}_i
   \left ( {\mathbf v}_\alpha + \nabla p
  -{\mathbf s}_{u_\alpha} \right) dV \right. + \displaystyle
  \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma
  + \nonumber \\ 
  \oint_{\Gamma_{\Omega}} { Q}_i {\mathbf n} \left(p -
  p_{bc}\right) d\Gamma = \bm{0},
  \label{force-semi-disc} 
\end{eqnarray} 
where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain. The numerical pressure appearing in the jump condition, $\tilde{p}$, is an average of the potentially discontinuous pressure across the element $E$,
\[\tilde{p}=\lim_{a\rightarrow 0} 
   \frac{1}{2}\left(p(\bm{r}+a\bm{n})+p(\bm{r}-a\bm{n})\right).\] This term therefore vanishes when pressure is continuous. Equation ~\ref{force-semi-disc} can be represented, in matrix form, as:
\begin{equation}
  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline {\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
\end{equation}
where the velocity $\left(\underline{\bf v}\right)$ and pressure $\left(\underline{\bf p}\right)$ solution-vectors are defined as,
\begin{eqnarray}
  &&\underline{{\bf v}} = \left({v_x}_{1,1},\ldots,{v_x}_{\mathcal{N}_\alpha,
    \mathcal{N}_u}, {v_y}_{1,1},\ldots,{v_y}_{\mathcal{N}_\alpha,
    \mathcal{N}_u},{v_z}_{1,1},\ldots,{v_z}_{\mathcal{N}_\alpha,
    \mathcal{N}_u}\right)^{T} \;\;\;\;\text{and} \nonumber \\ &&
  \underline{{\bf p}} = \left(p_1, p_2, p_3, ...,
  p_{\mathcal{N}_p}\right)^T, \nonumber \nonumber
\end{eqnarray}
respectively. $\mathcal{N}_{\alpha}$ is the number of phases and 
$v_x$, $v_y$, $v_z$ are the the velocity components 
associated with the $x-$ and $y-$ and $z-$ coordinates respectively.

Finally, the mass matrix ${\mathbf M}$, gradient matrix
${\mathbf C}$ and discretised source term ${\mathbf s}_{u}$ are:
\[\mathbf{M}=\left(
\begin{array}{ccc}
  \bm{M}^{(1,1)} &\bm{0} &\bm{0} \\
  \bm{0}   &\bm{M}^{(2,2)} &\bm{0} \\
  \bm{0} &\bm{0}  &\bm{M}^{(3,3)}   
\end{array}\right),\]
\[
\bm{C}=\left(
\begin{array}{ccc}
  \bm{C}^{(1,1)}&\bm{0}&\bm{0}\\
  \bm{0}&\bm{C}^{(2,2)}&\bm{0}\\
  \bm{0}&\bm{0}&\bm{C}^{(3,3)}\\
\end{array}\right)\quad \text{ and } \;\;
\bm{s}_u=\left(
\begin{array}{ccc}
  \bm{s}^{(1,1)}&\bm{0}&\bm{0}\\
  \bm{0}&\bm{s}^{(2,2)}&\bm{0}\\
  \bm{0}&\bm{0}&\bm{s}^{(3,3)}\\
\end{array}\right),\quad
\]
with blocks defined by:
\begin{eqnarray}
  && \left[{\mathbf M}^{(i,j)}\right]_{p,q} = \int_{\Omega}  Q_{p} \delta_{ij}
{Q}_{q}  dV, \\
  && {\left[\bm{C}^{(i,i)}\right]_{p,q} = \int_{\Omega} Q_{p} \frac{\partial P_{q}}{\partial r_i} dV - \oint_{\Gamma_{E}} \displaystyle\frac{1}{2} Q_{p} n_i^{(E,q)} P_{q} d\Gamma -  \oint_{\Gamma_{\Omega}} \displaystyle Q_{p} n_i P_{q} d\Gamma} \\
  && {\left[\bm{s}_{u}^{(i,i)}\right]_{p} = \int_{\Omega} Q_p} \left[{\mathbf s}_{u}\right]_i dV - \oint_{\Gamma_{\Omega}}\displaystyle Q_{p} n_i p_{bc} d\Gamma.
\end{eqnarray}
Here $\bm{n}=\left(n_{1},n_{2},n_{3}\right)^{T}$ is the outward-pointing normal vector of the domain $\Omega$. $\bm{n}^{(E,q)}$ is the normal to the boundary of element $E$ and is outward-pointing if $P_{q}$ takes support on $E$, and inward-pointing otherwise.

\medskip

This formulation ensures that for uniform \jrp{This tensor needs a good name} ${\underline{\underline \sigma}}_{\alpha}$ within each element the balance in the \jrp{is this only true in 1D} 1D extended Darcy flow equations is strictly enforced. The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piecewise constant in FE space to allow efficient representation of surface parametrised geometries. Thus the tensor %${\underline{\underline \sigma}}_{\alpha}$:
\begin{eqnarray}
  {\underline {\underline \sigma}}_{\alpha} &=& {\underline {\underline \sigma}}_{\alpha} \left[S_{\alpha}\left(\mathbf{r},t\right), \mu_{\alpha}, \mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right), \mathbf{K}\right] \nonumber \\
&=& \frac{S_{\alpha}\mu_{\alpha}}{\mathcal{K}_{{r}_\alpha}}\mathbf{K}^{-1},
\end{eqnarray}
is piecewise constant within the sub-volumes defined through the non-empty intersections between the elements and control volumes (in the pressure discontinuous formulation, these are precisely the control volumes themselves, see Fig.~\ref{fem_cv_represent_a}(c)). The velocity, formed by the action of ${\underline{\underline \sigma}}_{\alpha}^{-1}$ upon the force density $\bm{v}_\alpha$, has an exact polynomial representation on the sub-volumes of one degree lower that of $p$. For example, for a quadratic pressure variation there will be a piecewise linear velocity field, with discontinuities at element and control volume boundaries (Fig.~\ref{fig:darcys_law}). Thus, in 1D there are $2\times 3$ velocity nodal values per element associated with each phase.

This approach is computationally demanding in multi-dimension calculations with complex geometries. In order to overcome this major issue, overlapping (or hybrid) basis functions are introduced (Fig.~\ref{fig:overlapping2d}), in which the local velocity field within a given sub-volume is extrapolated across the entire element, allowing the existing FEM basis functions and nodal data structures to be reused.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Transport Methods}\label{transport_methods_section}
\subsection{CVFEM Formulation}
\jrp{ I think we need to justify why this section is here, or combine it with the saturation section, at the moment everything is a bit disjointed.}
Given a partitioning of a domain $\Omega$ into a set of CV's, we seek a numerical solution of the transport equation,
\begin{equation}
  \displaystyle\frac{\partial \text{T}(\mathbf{r},t) }{\partial t} +  \nabla\cdot \textbf{a} \text{T}(\mathbf{r},t) - s = 0,
  \label{traneq}
\end{equation}
where $\mathbf{a}$ is the advection velocity vector, $\textit{t}$ and $\textit{s}$ are time and a source term, respectively. The problem is discretised by testing the weak form of the equation over each CV $i$ using a set of test functions, $M_{i}$, which are unity over control volume $i$ and zero otherwise. This gives constraints,
\begin{equation}
  \int_{\Omega} M_{i} \left( \frac{\partial T }{\partial t} + \nabla\cdot \textbf{a} T - s \right)\,d V = 0, \quad \forall i \in \{1,2,..., \mathcal{M}\},
  \label{CV1}
\end {equation}
in which $\mathcal{M}$ is the number of CV's \citep[which is not necessarily equal to the $\mathcal{N}$ nodes of the underlying FEM mesh,][]{cordazzo_2004, eymard_1994}. To obtain a unique solution, this is combined with an expansion of the approximate solution {\it T} to $\text{T}$ in terms of the control volume basis functions $M_{j}$ with,
\begin{equation}  
  T\left(\mathbf{r},t\right)=\sum\limits_{i=1}^{\mathcal{M}} M_{i}\left(\mathbf{r}\right) T_{i}(t) \approx \text{T}.
  \label{transpeqn_approxfield}
\end{equation}
By applying Green's theorem, the discretised form of the advection term becomes:
\begin{equation}
  \int_{\Omega} M_{i} \nabla \cdot \mathbf{a} T \,d V =
  \oint_{\Gamma_{CV_{i}}} \mathbf{a}\cdot \mathbf{n} T \,d \Gamma
  \approx \sum_{l} \mathbf{a}\cdot \mathbf{n}\widetilde{T} \,\Delta
  \Gamma_l,
  \label{transpeqn_green}
\end{equation}
\noindent
where $\mathbf{n}$ is the outward pointing unit normal vector to the surface of the control volume \textit{i} $\left(\text{CV}_{i}\right)$. We use Gaussian quadrature to approximate the surface integral over each face of the control volume \textit{i}. To close the system, the value $\widetilde{T}$ at the quadrature integration points on the surface of the control volume must be calculated from the CV solution, \textit{T}.

\medskip
The value of $\widetilde{T}$ is calculated based on a high-order FEM interpolation $T_{\mbox{FEM}}$ of the CV solution $T$. These high-order fluxes are subject to limiting in order to obtain the final fluxes used at the Gaussian quadrature points on the control volume faces at element boundaries \citep{voller_2009,gomes_book_2012}.  Suppose that each element {\it i} has control volumes and a solution variable \jrp{is this used anywhere?} $\hat T_{i}$. Then the FEM solution, $T_{\mbox{FEM}}$, is related to the CV solution, {\it T}, by:
\begin{equation}
  \int_{\Omega} N_{i} \left({T_{\mbox{FEM}}} - T\right) \,d V = 0, \quad \forall i\in \{1,2,...,{\mathcal N}\},
\end{equation}
where $N_{i}$ is the FE basis function associated with the {\it i}-th degree of freedom. The FEM representation of \textit{T} is given by:
\begin{equation}
  T_{\mbox{FEM}} = \sum\limits_{j=1}^{\mathcal{N}} N_{j} {T_{\mbox{FEM}}}_{j}.
\end{equation}
For finite volumes, the basis function $M_{j}$ (top hat function) is used, obtaining that:
\begin{equation}
  \mathbf{B} \underline{\mathbf{T}}_{\mbox{FEM}} = \mathbf{Q} \underline{\mathbf{T}},
\end{equation} 
with
\begin{displaymath}
  \mathbf{B} = \int_{\Omega} N_{i}N_{j} \,dV \;\;\;\;\text{and}\;\;\;\; \mathbf{Q} = \int_{\Omega} N_{i} M_{j} \,  dV,
\end{displaymath} 
and
\begin{displaymath}
\underline{\mathbf{T}}_{\mbox{FEM}} = \left({T_{\mbox{FEM}}}_{1}, \ldots, {T_{\mbox{FEM}}}_{\mathcal{N}} \right)^{T} \text{ and } \underline{\mathbf{T}} =\left(T_{1}, T_{2}, \ldots, T_\mathcal{M} \right)^{T},
\end{displaymath}
contain the FE and CV values of {\it T}, respectively. Since we are using high-order approximations, extrema must be detected in order to determine where to apply first order fluxes instead of high-order. This is achieved using the normal variable diagram approach, NVD as described by~\citet{darwish_1993}~\citep[see also][]{jasak_1999,darwish_2003}.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\subsection{Time-Discretisation Scheme} \label{time_discretisation}
There are numerous time-discretisation methods to deal with parabolic system of equations, such as backward-Euler, forward-Euler, Crank-Nicolson and Runge-Kutta methods \citep{weng_2012}. An adaptive time-stepping method based on the Crank-Nicolson scheme is chosen, because it is unconditionally stable and second-order accurate.

Using Eqns.~\ref{CV1} and \ref{transpeqn_green}, the time stepping for Eqn.~\ref{traneq} takes the form:
\begin{eqnarray}
  \int_{\Omega} M_{i} \left( \displaystyle\frac{T_{i}^{n+1}
    -T_{i}^{n}}{\Delta t} - s \right) \,dV &=& \int_{\Gamma_{CV_{i}}}
  \left[\theta\left(\mathbf{a}^{n+1}\cdot \mathbf{n}
    \widetilde{T}^{n+1} +\mathbf{n}\cdot k^{n+1}\nabla
    \widetilde{T}^{n+1} \right) + \right.\nonumber
    \\ &&\left. \left(1-\theta\right)\left(\mathbf{a}^{n}\cdot
    \mathbf{n} \widetilde{T}^{n} +\mathbf{n}\cdot k^{n}\nabla
    \widetilde{T}^{n} \right) \right]d\Gamma.
  \label{theta}
\end{eqnarray} 
For each time step a value of $\theta$ between 0.5 (for Crank-Nicolson) and 1.0 (for backward-Euler) is calculated at each CV face based on the satisfaction of a TVD criterion \citep{szabo_2009,kuzmin_2004}. Assuming $L_{i}$ is the volume of the  $i^{th}$-CV then the following expression for $\theta_f^{n+\frac{1}{2}}$ of face \textit{f} is obtained \citep[see][]{gomes_book_2012},
\begin{equation}
  \theta_f^{n+\frac{1}{2}}=\max \left\{ \frac{1}{2}, 1 - \displaystyle\frac{1}{2}  \min\left\{\left|\frac{1}{p_{f}^{n+\frac{1}{2}}}\right|, \left|\frac{1}{q_{f}^{n+\frac{1}{2}}} \right| \right\} \right\}
  \label{thet1}
\end{equation}
with
\begin{displaymath}
  p_{f}^{n+\frac{1}{2}} = \displaystyle\frac{g_{f}^{n+\frac{1}{2}}\Delta t}{(T^{n+1}_{c} - T_{c}^{n}) L_{c}} , \quad q_{f}^{n+\frac{1}{2}} = \displaystyle\frac{g_{f}^{n+\frac{1}{2}}\Delta t}{(T^{n+1}_{d} - T_{d}^{n}) L_{d}}
  \label{thet2}
\end{displaymath}
and
\begin{displaymath}
  g_f^{n+\frac{1}{2}}= \int_{\Gamma_f}\left(\bm{a} \cdot \mathbf{n} T\right)^{n} \partial\Gamma - \int_{\Gamma_f}\left(\bm{a} \cdot \mathbf{n} T\right)^{n+1}
  \partial\Gamma,
\end{displaymath}
where \textit{c} and \textit{d} refer to the two CV's that are adjacent to face \textit{f}. This method can be extended \citep[as demonstrated in][]{gomes_2008,pain_2001b} to deal with composite time-dependent terms such as $\frac{\partial \left(\rho T\right)}{\partial t}$ by replacing $T_j^n$ and $T_j^{n+1}$ by $T_{j}^{n} \rho_{j}^{n}$ and $T_{j}^{n+1} \rho_j^{n+1}$, respectively, for $j = \{c,d\}$.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Saturation and Global Mass Conservative Equations}\label{Section:Saturation_Global}
This section outlines the discrete saturation equations and derives the global mass balance equations from the saturation equations assuming incompressibility. The saturation equation \citep{chavent_1986} can be written as follows,
\begin{equation}
  \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  s_{cty,\alpha},
  \label{saturation_equation}
\end{equation}
where $\phi$ represents the porosity of the rock matrix. It can be discretised in space by testing with CV basis functions $M_{i}$ and with the $\theta$-method in time, \jrp{the cross reference doesn't explicitly used the term theta method.} as described in Section~\ref{time_discretisation}:
\begin{eqnarray}
  \int_{\Omega} M_{i} \displaystyle\frac{\phi \left({S_{\alpha}}_{i}^{n+1}-{S_{\alpha}}_{i}^{n}\right)}{\Delta t} dV + \nonumber \\ 
  \oint_{\Gamma_{CV_{i}}} \left[\theta^{n+\frac{1}{2}} {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n+1} S_{\alpha}^{n+1} +  \left(1-\theta^{n+\frac{1}{2}}\right) {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n} S_{\alpha}^{n} \right]d\Gamma =  \int_{\Omega} M_{i} {s_{cty,\alpha}^{n+\theta}} dV.
  \label{detail-sat-eqn-k}
\end{eqnarray}
Summing over all $\mathcal{N}_\alpha$ phases one obtains the global continuity equation,
\begin{eqnarray}
  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} \left\lbrace \int_{\Omega} M_{i} \displaystyle\frac{\phi\left({S_{\alpha}}_{i}^{n+1}-{S_{\alpha}}_{i}^{n}\right) } {\Delta t} dV + \right. \nonumber \\ 
  \left. \displaystyle\oint_{{\Gamma_{CV}}_{i}} \left[\theta^{n+\frac{1}{2}} {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n+1} S_{\alpha}^{n+1} +  \left(1-\theta^{n+\frac{1}{2}}\right) {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n} S_{\alpha}^{n} \right] \,d\Gamma - \right. \nonumber \\
  \left. \displaystyle\int_{\Omega} M_{i} s_{cty,\alpha}^{n+\theta}\, dV \right\rbrace = 0,
           \label{detail-sat-eqn-k-sum}
\end{eqnarray}
in which $\theta^{n+\frac{1}{2}}$ is obtained as described in Section~\ref{time_discretisation} with $S_\alpha$ replacing $T$. Assuming the natural incompressible mass conservation constraint,
\begin{equation}
  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}}_{i}^{n} = 1, \quad \forall n,
\end{equation}
in matrix form Eqn.~\ref{detail-sat-eqn-k-sum} becomes,
\begin{equation}
  {\mathbf B}^T \underline{\bf v}^{n+1} = \underline{\bf s}_{p},
  \label{glob-cty-matrix}
\end{equation}
where it remains to relate the phase force density $\bm{v}_\alpha$ to the phase velocity on the control volume facets.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Upwind Velocity and Relative Permeability} \label{opt-up} 
We still need to determine the velocity to be used at the interface between CV's in the saturation (Eqn.~\ref{detail-sat-eqn-k}) and global continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations. On the CV faces, there is no information about the flow direction as the velocity is discontinuous at the CV boundaries. The discontinuities occur between (a) elements for the discontinuous formulation and (b) control volumes within each FE. An average velocity is defined by:
\begin{equation}
  {\bf v}_\alpha = \frac{1}{2} \left[ {{\bf v}_\alpha}_i + {{\bf v}_\alpha}_j \right].
\end{equation} 
Then, the interface velocities at either side of the interface can be obtained from,
\begin{equation}
  {\tilde{\bf u}}_{\alpha i}=   \underline{\underline\sigma_\alpha}_i^{-1}  {{\bf v}}_\alpha  , \;\;\;\;  {\tilde{\bf u}}_{\alpha j} =  \underline{\underline\sigma_\alpha}_j^{-1}  {{\bf v}}_\alpha    . 
  \label{two-vels}
\end{equation} 
Notice that these velocities point in the same direction and are only different in magnitude \jrp{What constraints on the permeability tensor?}. Thus, using them to define an upwind direction is not ambiguous. The vector:
\begin{equation}
  {\bf a}_\alpha= \displaystyle\frac{1}{2} \left[ \frac{  \underline{\underline \sigma_\alpha}_i^{-1} {{\bf v}_\alpha}_i +  \underline{\underline \sigma_\alpha}_j^{-1} {{\bf v}_\alpha}_j }  { {\sigma_\alpha}_i (S_\alpha)+{\sigma_\alpha}_j (S_\alpha)} \right],
\end{equation} 
\jrp{need to fix for tensor} is used to determine if information is leaving or entering a CV.

The two velocity values in Eqn.~\ref{two-vels} provide the two extremes within which the final interface velocity is obtained. Notice that if the saturation and density are equal in CV's $i$ and $j$ then these velocities will be identical. This is important in order to solve the elliptic nature of the resulting pressure equation.

If we are to apply an upwind method for calculating the interface velocity then the interface velocity becomes, % ${\tilde{\bf u}}_\alpha = {\tilde{\bf u}}_{\alpha i}$ for ${\bf n}\cdot {\bf a}_\alpha>0$ (CV $i$ outgoing information) and ${\tilde{\bf u}}_\alpha = {\tilde{\bf u}}_{\alpha j}$ for ${\bf n}\cdot {\bf a}_\alpha<0$ (CV $i$ incoming information).
\begin{displaymath}
{\tilde{\bf u}}_{\alpha} =
\begin{cases}
\tilde{\bf u}_{\alpha i}, & \text{for } {\bf n}\cdot{\bf a}_{\alpha}>0 \text{ (CV {\it i} outgoing information);} \\
\tilde{\bf u}_{\alpha j}, & \text{for } {\bf n}\cdot{\bf a}_{\alpha}<0 \text{ (CV {\it i} incoming information).} 
\end{cases}
\end{displaymath}
However, this upwind method will result in dissipative solutions. Out of numerous heuristics for obtaining this interface velocity ${\tilde{\bf u}}_\alpha$, we choose a method based on a limited high-order saturation $\tilde S_\alpha$, obtained using a DGFEM upwind approximation. The sign of ${\bf n}\cdot {\bf a}_\alpha$ is used to determine the upwind direction. From this high-order flux limited saturation, we can obtain $\tilde{\sigma}_{\alpha} = \sigma_{\alpha}\left(\tilde{S}_{\alpha}\right)$. Knowing $\tilde S_\alpha$ we can estimate the corresponding interface value of $\sigma_\alpha$, that is $\tilde\sigma_\alpha,$ from the second-order Taylor series. For ${\bf n}\cdot {\bf a}_\alpha>0$ (CV $i$ outgoing information):
\begin{equation}
  \tilde\sigma_\alpha = {\sigma_\alpha}_i + \left(\tilde S_\alpha - {S_\alpha}_i\right) \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i + \frac{1}{2}  \left(\tilde S_\alpha - {S_\alpha}_i\right)^2 \left[ \frac{\left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i - \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j } {{S_\alpha}_i -  {S_\alpha}_j} \right]
  \label{sigma-out}
\end{equation} 
and for ${\bf n}\cdot {\bf a}_\alpha<0$ (CV $i$ incoming information):
\begin{equation}
  \tilde\sigma_\alpha = {\sigma_\alpha}_j + \left(\tilde S_\alpha - {S_\alpha}_j\right) \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j +\frac{1}{2} \left(\tilde S_\alpha - {S_\alpha}_j\right)^2 \left[ \frac{\left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i - \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j } {{S_\alpha}_i - {S_\alpha}_j} \right]
  \label{sigma-in}
\end{equation} 
where $\tilde{\sigma_{\alpha}}$ is also adjusted to ensure that it lies between ${\sigma_\alpha}_i$ and ${\sigma_\alpha}_j$. Since $\tilde{\sigma_{\alpha}}$ is often a tensor on the boundaries of the CV's, we only require its normal component -- ${\bf n}^T\tilde\sigma_\alpha {\bf n}$, to be subject to this boundedness constraint. It should be noted that for high-order elements it may be advantageous to use $\tilde\sigma_\alpha = \sigma_\alpha \left(\tilde S_\alpha\right)$ directly so as to maintain the high-order convergence. In addition, for robustness, one can choose to only add the second-order terms in Eqs.~\ref{sigma-out} and \ref{sigma-in} if the resulting $\tilde{\sigma_{\alpha}}$ is closer to the upwind value of $\sigma_\alpha$.

The final interface velocity is obtained from:
\begin{equation}
  {\tilde{\bf u}_{\alpha}} = {\tilde{\sigma}_{\alpha}}^{-1} \left[\displaystyle\frac{1}{2} \left(    {{\bf v}_\alpha}_i +  {{\bf v}_\alpha}_j \right)\right],
  \label{mean_int_vel}  
\end{equation} 
which is, in addition, bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{ki}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$. The result of this is also bounded between the velocities ${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf n}$. Notice that inside an element without discontinuous sources (i.e., in Eqn.~\ref{force-bal}) ${\tilde{\bf u}_{\alpha i}}={{\bf u}_{\alpha i}}$, ${\tilde{\bf u}_{kj}}={{\bf u}_{\alpha j}}$ and ${\sigma_\alpha}_i {{\bf u}_\alpha}_i = {\sigma_\alpha}_j {{\bf u}_\alpha}_j$ and Eqn.~\ref{mean_int_vel} simply takes on the upwind value of velocity if we choose the upwind value of $\sigma_\alpha$ for interface value $\tilde\sigma_\alpha$.

In practice we have found that for CV boundaries inside an element, Eqn.~\ref{mean_int_vel} can be used to obtain the interface velocities. The upwind approach now becomes,
\begin{equation}
{\tilde{\bf u}_{\alpha}} =
\begin{cases}
{{\bf u}_{\alpha}}_{i} & \text{for }{\bf n}\cdot {\bf a}_{\alpha} > 0 \\
{{\bf u}_{\alpha}}_{j} & \text{for }{\bf n}\cdot {\bf a}_{\alpha} < 0 
\end{cases}
\end{equation}
%${\tilde{\bf u}_\alpha} ={{\bf u}_\alpha}_i $ for ${\bf n}\cdot {\bf a}_\alpha>0$ and ${\tilde{\bf u}_\alpha} ={{\bf u}_\alpha}_j$ for ${\bf n}\cdot {\bf a}_\alpha<0$.
In regions of the domain where the saturation has no spacial variation an average of the velocity is obtained in a similar approach to the harmonic averaging procedure, commonly used to obtain interface absolute permeabilities.\jrp{add a reference?}

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Determining Velocities across Discontinuous Element Interfaces}
In order to advect saturations and other scalar variables across elements with discontinuous velocity and pressure we first need to calculate the velocity between these contiguous elements. It is also necessary to obtain the discretised non-symmetric pressure equation which has elliptic-like properties. These properties mean it is necessary to propagate information in all directions across the domain. Thus, taking the upwind velocity, as commonly done within an element, is not the best strategy.

For two neighbouring CV's $i$ and $j$ which have a common FE interface, ${\bf u}_{\alpha}$ can be calculated by using a volume weighting. However, the volume {\it V} of the control volume and $\sigma_{\alpha}$ act on the velocity ${\bf u}_{\alpha}$ in a very similar way. Hence, the velocity at the interface can be expressed as,
\begin{equation} 
  {\tilde{\bf u}_\alpha} = \frac{ V_j  {{\bf v}_\alpha}_i + V_i  {{\bf v}_\alpha}_j } { V_i {\sigma_\alpha}_i + V_j {\sigma_\alpha}_j }.
\end{equation} 
\jrp{This equation needs to be fixed for tensor permeabilities.}

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Boundary Conditions for Saturation, Pressure and Relative Permeability}\label{bcs-rel-perm}

\jrp{ The notation here is rather dense for continuous text, but I'm not really sure how to improve it.}

Suitable boundary conditions can be guided by the discontinuous formulations above as well as the upwinding in the continuous formulations. In fact, exactly the same boundary condition implementations can be applied as used in the discontinuous formulations but across the boundaries of the domain and taking information from just outside the domain rather than in the neighbouring elements.

Saturation boundary conditions are relatively straightforward. One typically takes the saturation from just outside the domain (i.e., the saturation boundary condition, ${S_\alpha}_{bc}$) as part of the incoming flux (i.e., when ${\bf n}\cdot {\bf u}_\alpha<0$) for phase $\alpha$: $\left({\bf n}\cdot {\bf u}_\alpha\right){S_\alpha}_{bc}$.  When in addition the velocity ${\bf n}\cdot {{\bf u}_\alpha}_{bc}$ is specified then this also must be part of the incoming flux $\left(\right.$i.e., when ${\bf n}\cdot {{\bf u}_\alpha}_{bc}<0\left.\right)$: $\left({\bf n}\cdot {{\bf u}_\alpha}_{bc}\right){S_\alpha}_{bc}$.

Similarly, boundary conditions can be applied using Riemann variables to determine if information is travelling into or out of the domain (although most flow simulation models do not follow this more rigorous approach). Specified pressure boundary conditions for outlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ are: ${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf u}_\alpha$ nor ${S_\alpha}$ are specified.

Specified pressure boundary conditions for the inlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ are defined as: ${\bf n}\cdot {{\bf u}_\alpha}_{rel} {S_\alpha}_{bc}$, in which the relative permeability is upwinded and thus taken from outside the domain resulting in a value of ${\underline {\underline \sigma}}_\alpha$ from ${{\underline {\underline \sigma}}_\alpha}_{\text{outside}}$. The latter is calculated from the saturation boundary condition value ${S_\alpha}_{bc}$. This means that the solution velocity ${{\bf u}_\alpha}$ needs to be adjusted to apply this upwind permeability, i.e., 
\begin{equation}
  {{\bf u}_\alpha}_{rel}= \displaystyle\frac{{{\underline {\underline \sigma}}_\alpha}_\text{inside} } {{{\underline {\underline \sigma}}_\alpha}_\text{outside}}{{\bf u}_\alpha}.
\end{equation}
Another approach for upwinding the relative permeability on incoming specified pressure boundaries is to simply adjust the value of ${{\underline {\underline \sigma}}_\alpha}_\text{inside}$ just inside the domain by setting it to the value just outside the domain, 
\begin{displaymath}
{{\underline {\underline \sigma}}_\alpha}_\text{inside}={{\underline {\underline \sigma}}_\alpha}_\text{outside},
\end{displaymath}
and the flux condition then becomes
\begin{displaymath}
{\bf n}\cdot{{\bf u}_\alpha} {S_\alpha}_{bc}.
\end{displaymath}

It should be noted that these flux conditions must be used in both the discretised saturation and global continuity equations, since the latter is a summation of the former. The specified pressure condition becomes a surface flux condition in the force balance equation (Eqn.~\ref{force-semi-disc}), which effectively relaxes the pressure $p$ to its face value counterpart $p_{bc}$ at the boundaries.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Solving the Linear Equations}\label{Section:SolvingLinearEqns}
The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and force balance equations (Eqn.~\ref{force-balance-matrix-form}) are solved by substituting out the force density term and solving the system of equations for pressure. At time level $n+1$, Eqns.~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can be rewritten as:
\begin{displaymath}
%\label{glob-cty-matrix2},\label{force-balance-matrix-form2}
%\begin{eqnarray}
 % &&
\begin{cases}
 \mathbf{M} \underline{\bf v}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\ %&&
 \mathbf{B}_\sigma^{T} \underline{\bf v}^{n+1} = \underline{\bf s}_{p}^{n+1},%\label{glob-cty-matrix2}
\end{cases}
%\end{eqnarray}
\end{displaymath}
respectively. Application of a discontinuous FEM for the force density leads to a block-diagonal $\mathbf{M}_{\sigma}$ matrix that can be readily inverted, each block being local to an element. Multiplying Eqn.~\ref{force-balance-matrix-form} by $\mathbf{B}^{T}\mathbf{M}_{\sigma}^{-1}$ and summing up with Eqn.~\ref{glob-cty-matrix}, the force density $\left(\underline{\mathbf v}^{n+1}\right)$ vanishes and the pressure equation is obtained:
\begin{equation}
  \mathbf{B}_\sigma^{T}\mathbf{M}^{-1} \mathbf{C} \underline{\bf p}^{n+1} = \underline{\bf s}_{p}^{n+1} - \mathbf{B}_\sigma^{T} \mathbf{M}^{-1} \underline{\bf s}_{u}^{n+1}.
  \label{final_projection}
\end{equation}
Eqn.~\ref{final_projection} is solved for pressure and then the velocity is obtained via Eqn.~\ref{force-balance-matrix-form}. The computationally demanding effort to solve the pressure matrix equation arising from the fully discontinuous FEM formulation is achieved using a multigrid-like approach. In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating from the discontinuous system a continuous one by collapsing the pressure nodes. As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the present approximation.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Model Validation}\label{Section:Results}%
\subsection{Advection Test-Cases}
The aim of this section is to demonstrate the performance of the CVFEM approach to solve the advection equation. The control volumes are interpolated using FEM basis functions and the FEM provides the high-order flux which is limited as previously described. The 1D advection equation:
\begin{displaymath}
  \displaystyle\frac{\partial}{\partial t} T + \frac{\partial}{\partial x} \left( {\bf u}\;T \right) = 0, 
\end{displaymath}
is solved within a domain $x\in \left[0,1\right]$, with $T=1$ on the left boundary and advection velocity of $u=1$. Initial conditions at time $t=0$,
\begin{displaymath}
  T\left( x,0\right)= \begin{cases} 1, \;\; &  0.2 \le  x \le 0.4 \\
    0, & \mbox{ otherwise,}
  \end{cases}
\end{displaymath}
are specified. Figure~\ref{compar-dg} (top) shows the spatial accuracy of the schemes introduced in this work with a small (converged) time step size. The solution shown here was obtained at $t=0.2$ and the domain was divided into 5 elements. The accuracy can be gauged by comparing solutions obtained from 5 and 50 elements. CV solutions and the corresponding FE interpolation of these solutions are also shown. The FEM interpolation was used to obtain the high-order fluxes (both between and within each element).

The Courant number $\left(=u\Delta t / \Delta x\right)$ was increased based on the element size of $\Delta x = 0.5$. Courant number is equal to 2 based on the smallest control volume (representing a large time step size). Two time steps were performed, and this is a hard test for the non-linear $\theta$ time-stepping method (Section~\ref{time_discretisation}). Note that due to the large time step size the solution is more dissipative, however, the discontinuous element solution is clearly more accurate.

Figure~\ref{compar-dg-bdt-diff} demonstrates the advection capturing capability of our method. In Fig.~\ref{theta-bdt}, solutions obtained from (a) continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element pair}\right)$ and (b) discontinuous $\left(\text{either P}_{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements pairs}\right)$ formulations are compared in a problem with large time step size. The value of $\theta$ on the faces of the CV's is shown at the end of two time steps; it is important to notice that $\theta$ is smaller and closer to $0.5$ when using the continuous approach than the discontinuous method. This is due to the larger CV's, i.e. smaller Courant numbers based on the control volume size.

For the advection of an initial Gaussian profile,
\begin{displaymath}
T\left( x,0\right)= \exp{\left( \displaystyle\frac{x-0.6}{0.2} \right)^2}
\end{displaymath} 
with a left boundary condition of $T=1$ a convergence study was performed using the pressure discontinuous approach. Both CV and interpolated FEM solutions are shown in Fig.~\ref{converg} for several mesh resolutions. The method rapidly converges to the exact solution. However, it tends to round off the top of the Gaussian curve due to the limiting detecting (extrema) scheme which results in a dissipative first-order upwind scheme in this region.

The FEM interpolations for the three schemes (with 5 and 20 elements) are shown in Fig.~\ref{converg-compare-fem}. \jrp{It's a bit unclear what the difference is between the pressure discontinuous schemes. Is one upwinded and the other central? } The first two schemes are the continuous and discontinuous  approaches. The third scheme uses a central difference method (i.e., mean of the solutions either side of an element boundary) to calculate the flux between the elements and has a discontinuous solution between the elements. This figure provides a gauge of the accuracy between the methods and shows that although all methods perform similarly, the central difference approach with discontinuity between elements is best able to represent the discontinuous analytical solution.

\medskip

Further convergence analysis were performed for a 2D step function,
\begin{displaymath}
T\left(x, y,0\right) =\begin{cases}
1, & \left(x,y\right)\in \left[0.25,0.50\right] \\%  0.25\leq x \leq 0.50 \text{ and } 0.25\leq y \leq 0.50\\
0, & \text{otherwise,}
\end{cases}
\end{displaymath}
and a Gaussian profile,
\begin{displaymath}
T\left(x, y,0\right) = \exp{\left[-30\left(x-2\right)^{2}-32\left(y-0.5\right)^{2}\right]},
\end{displaymath}
using both continuous $\left(\text{P}_{2}\right)$ and discontinuous $\left(\text{between elements, P}_{1}\text{DG}\right)$ element formulations. The domain has dimension of $2.5\times 1$ length-units; time-step and element sizes were chosen to ensure a constant Courant number of 0.1667.  Simulations were performed with 5 mesh resolutions as described in Table~\ref{table:meshplume}. Figure~\ref{2D_Sanpshot_Adv2D} shows the advected scalar field after 350 (step function) 100 (plume function) time-steps (high-resolution  mesh as reference case for time-step size) and the associated analytical solution. $L_{1}$- and $L_{2}$-norms,
\begin{displaymath}
L_{1}=\displaystyle\frac{\sum\limits_{i=1}^{N}\left|T_{i}^{\text{(analytic)}}-T_{i}^{\text{(numeric)}}\right|}{N}\;\;\;\text{and}\;\;\;L_{2}=\displaystyle\frac{\sum\limits_{i=1}^{N}\left[T_{i}^{\text{(analytic)}}-T_{i}^{\text{(numeric)}}\right]^{2}}{N}
\end{displaymath} 
were calculated for both element type formulations (continuous and discontinuous) and test cases for several mesh grids and plotted on log-log scale, Fig.~\ref{L1_L2norm_Adv2D}. First- and second-order slopes are also shown in this figure. $L_{1}$ norms drop linearly for the discontinuous formulation $\left(\text{P}_{1}\text{DG}\right)$ and in a second-order manner for the continuous formulation $\left(\text{P}_{2}\right)$ as the grid resolution increases. This figure demonstrates that the accuracy of these schemes are very similar, however elements with discontinuity perform slightly better with significantly smaller degrees-of-freedom.

\subsection{Buckley-Leverett Test Case}
The Buckley-Leverett (B-L) equation is a nonlinear advection equation for the relative saturation of fluid phases representing two-phase immiscible flows in porous media. Here, water $\left(S_{l}=1\right)$ is injected at a velocity $u_{g}\phi=1$. On the outlet boundary condition, the pressure level is set to zero and all remaining boundary conditions are naturally applied. A converged time step of $1\times 10^{-3}$ is used for all simulations and applications with the continuous and discontinuous between element formulations. All simulations used the overlapping mixed FEM with a piecewise linear variation of the velocity within each element and quadratic pressure $\left(\text{P}_{1}\text{DG-P}_{2}\right)$. Saturation is colocated at the pressure nodes and although it is calculated using a CV formulation, a FEM interpolation is used to form the high-order fluxes.

In Fig.~\ref{bl-exact-meth-upwind} the CV solution of the water saturation and equivalent quadratic FEM interpolation are presented $\left(\text{P}_{1}\text{DG-P}_{2}\right)$. As it can be seen the solution converges with increased resolution. Notice that the corners of the CV's are very close to the converged solution. This can be explained as the velocities are upwinded (and also the relative permeabilities -- see Section~\ref{opt-up}), and at these corners the equations reach the balance necessary to match the analytical solution. Despite the one-dimensional nature of the problem, 2- and 3-D simulations were performed using structured and unstructured meshes and reported in the second part of this two-part paper.

\section{Final Remarks}\label{conc}
This article is the first in a two-part papers describing the new overlapping control volume finite element method (OCVFEM) for multi-fluid flows. The new formulation is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of element types $\left(\text{P}_{n}\text{DG-P}_{n+1}\right.$, P$_{n}$DG-P$_{n}$ and $\left.\text{P}_{n}\text{DG-P}_{n}\text{DG}\right)$, and has been applied to hybrid multi-component interface-tracking models~\citep{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular flows~\citep{percival_2014} and to reservoir simulation~ \citep{jackson_2013}. The aim of this paper is to describe the formulation of this approach embodied in the \href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity} software framework for multiphase flows in porous media, and the initial model validation.

\jrp{ Again, is this the limit of what we can claim?} The OCVFEM was specially tailored to ensure that in the limit of uniform permeability -- ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$, the balance in 1D Darcy multiphase flow equations is strictly enforced. Saturations are \jrp{what?} collocated (piecewise constant) in control volume space whereas the material absolute permeability tensor is piecewise constant in FE space to ensure the correct representation of the surface. Moreover, the velocity field (for each phase) is described as a function of $\underline{\underline{\sigma}}$ and pressure. \jrp{We may want to rethink this sentence} For a quadratic pressure variation there will be a piecewise linear velocity field, with discontinuities at element and control volume boundaries.

In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the DGFEM formulation and control volumes within finite elements.  \jrp{Pure advection doesn't really test the whole method though?} The resulting method was initially validated for advection problems showing good accuracy and convergence for the continuous and discontinuous (between elements) formulations. We also demonstrated the accuracy of the upwind formulation.  In the second part of this two part paper we explore the computational model framework for 2- and 3-D dimensions and focus on heterogeneous multiphase porous media flows.

\ack Dr D. Pavlidis would like to acknowledge the support from the following research grants: EPSRC ($\lq$Computational Modelling for Advanced Nuclear Power Plants') and EU/FP7 THINS. Funding for Dr P. Salinas from the Qatar Carbonates and Carbon Storage Research Centre (QCCSRC), provided jointly by Qatar Petroleum, Shell and the Qatar Science and Technology Park, is gratefully acknowledged. Dr Z. Xie is supported by EPSRC ($\lq$Multi-Scale Exploration of Multiphase Physics in Flows' -- MEMPHIS). Part funding for Prof Jackson under the TOTAL Chairs programme at Imperial College is also acknowledged.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv}
\bibliography{references}

\pagebreak
\clearpage

%\listoffigures
\pagebreak
\clearpage
\input{article_table}
\input{article_figure1}

\end{document}

%%
%% End of tex file.

%%  LocalWords:  checkboard

### 2015-01-07 Papers/Prototype_1_Method/article_figure1.tex
adding Papers to the repo

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
%\vspace{-1.cm}
%\vbox{

%\begin{center}
%\includegraphics[width=0.6\textwidth]{1D_Sketch_b.eps}
%\vspace{-1.cm}
%\end{center}
%\hbox{\hspace{6.5cm}(a)}
%\vspace{.1cm}
%
%\begin{center}
%\includegraphics[width=1.\textwidth]{1D_Sketch.eps}
%\vspace{-1.cm}
%\end{center}
%\hbox{\hspace{6.5cm}(b)}
%\vspace{-.1cm}

\vbox{
\hbox{ \hspace{4.cm}
\includegraphics[width=.55\textwidth]{diagrams/p0dgp1-cont-sat} \hspace{0.cm} (a)}
\vspace{-0.2cm}
\hbox{ \hspace{4.cm}
\includegraphics[width=.55\textwidth]{diagrams/p1dgp2-cont-sat} \hspace{0.cm} (b)}
\vspace{-0.2cm}
\hbox{ \hspace{4.cm}
\includegraphics[width=.55\textwidth]{diagrams/p2dgp1-dg-sat} \hspace{0.cm} (c)}
\vspace{-0.2cm}

%\vspace{.1cm}
}

  \caption{2D representation of the element pairs (a) P0DGP1, (b) P1DGP2  and (c) P2DGP1DG. Shaded areas denote a control volumes (in which saturation is stored), black points represent the pressure nodes and the white points the velocity.}
  \label{fem_cv_represent_a}
\end{figure}

%%%
%%% Overlapping Figure 1
%%%

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-2.cm}
\includegraphics[width=1.3\textwidth,height=1.3\textwidth]{diagrams/overlapping_cartoon}}
\vspace{-1.4cm}
\caption{Diagram showing the exact representation of Darcy's law in 1D. From top to bottom, the plots show i) a P2 continuous pressure field, $p$, across three elements, ii) the P1DG gradient of that  pressure field, iii) a P0DG absolute permeability field, ${\bf K}$, iv) a CV mobility field, $\lambda_{k}=\frac{\mathcal{K}_{rk}\left(S_{k}\right)}{\mu_{k}}$, and finally v) the resultant CV0DG velocity field arising from Darcy's law. Here dashed lines denote the boundaries of the P2 finite element mesh, dotted lines denote boundaries between the control volumes dual to the P2 mesh and solid dots indicate the natural locations of degrees of freedom in a non-overlapping formulation. }
\label{fig:darcys_law}
\end{center}
\end{figure}

%%%
%%% Overapping Figure 2
%%%

\begin{figure}[htp]
\begin{center}
\hbox{\hspace{-2.5cm}
\includegraphics[width=1.2\textwidth]{diagrams/overlapping}}
\caption{An isometric schematic of the 2D overlapping velocity
  elements. In this example we show a triangular element, ABD in the
  $x$-$y$ plane. We also indicate the contol volume boundaries lying
  within this element. Under the overlapping methodology presented
  here, each facet formed from the union of control volume and element
  possesses its own polynomial representation for velocity, indicated
  by height in the isometric projection. By extrapolating this
  representation across the rest of this element, we negate the need
  to implement a special data structure to store or evaluate this
  field, instead leveraging the standard finite element basis for ABD,
  and storing the FEM nodal values E, F, G. }
\label{fig:overlapping2d}
\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
%\begin{figure}[H]
%\vbox{
%\begin{center}
%\includegraphics[width=10.0cm,height=7.5cm]{FEM_elem2}
%\end{center}
%\vspace{-3.cm}}
%\caption{Positioning of variables in and on the boundary of CV {\it i}.}
%\label{fem_cv_represent_c}
%\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]

  \begin{center}
\vbox{\hbox{\hspace{1cm}
    \includegraphics[width=0.8\textwidth]{compar-dg.eps}}
   \hbox{ \hspace{1cm} \includegraphics[width=0.8\textwidth]{compar-dg-bdt.eps}}}
    \caption{Advection problem test-cases: control volume solution (5
      finite elements with constant width of 0.2 are used) with
      Courant number of 0.005 (top) and 0.5 (bottom).  The solution
      has been advected a distance of 0.2 with 200 (top) and 2
      (bottom) time steps. The 50 elements solution is shown to give
      an indication of the accuracy of the solutions and has a Courant
      number (based on the element width) of 0.005.\label{compar-dg}}
  \end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.2\textwidth]{compar-dg-bdt-diff}
\end{center}
\caption{Advection problem test-cases: discontinuous (between
  elements) control volume formulation within 5 finite elements (width
  of 0.2). Courant number is of 0.5 (or 2 if based on the minimum
  width of a control volume). The solution has been advected a
  distance of 0.2 with 2 time steps. The 50 element solution is for
  pure advection and is shown to give an indication of the accuracy of
  the solutions and has a Courant number (based on the element width)
  of 0.005.\label{compar-dg-bdt-diff}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{-1.3cm}
\includegraphics[width=17.5cm,height=12.5cm]{theta-bdt}}
\vspace{0.cm}}
\caption{Advection problem test-cases: value of $\theta$-time stepping
  parameter on the faces of the control volumes at the end of the
  simulation -- 5 FE are used and the Courant number (based on the
  element width of 0.2) is 0.5 (or 2 if based on the minimum width of
  a control volume). The solution has been advected a distance of 0.2
  length units with 2 time steps.}
\label{theta-bdt}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\vspace{-2cm}
\hbox{\hspace{-.5cm}
\includegraphics[width=14.0cm,height=10.cm]{converg-cv}}
\vspace{-.5cm}
\hbox{\hspace{-.5cm}
\includegraphics[width=14.0cm,height=10.cm]{converg-fem}}
}\vspace{-.3cm}
\caption{Advection problem test-cases: convergence of the solutions
  with discontinuity between elements and with increased resolution. A
  pure advection problem (from left to right) - the Courant number is
  0.005. The solution has been advected a distance of 0.2. Control
  volume solutions (top) and FEM interpolation (bottom) of the control
  volume solutions are shown. \label{converg}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\hbox{\hspace{-1cm}
\includegraphics[width=17.5cm,height=12.5cm]{converg-compare-fem}}
\caption{Advection problem test-cases: comparison of convergence of
  the solutions with and without discontinuity between elements and
  with an upwind and central difference flux between the elements and
  with increased resolution (dashed line: 5 elements, full line: 20
  elements). A pure advection problem (from left to right) - the
  Courant number is 0.005. The solution has been advected a distance
  of 0.2. The FEM interpolation of the control volume solutions are
  shown. \label{converg-compare-fem}}
\end{figure}

\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
%\vbox{
\includegraphics[width=15.5cm,height=12.cm]{./diagrams/Fields_Plume.pdf}
%\includegraphics[width=15.5cm,height=12.cm]{./diagrams/AllHighRes.pdf}
%\vspace{-1.5cm}
%\includegraphics[width=12.5cm,height=9.cm]{./diagrams/AllHighRes.pdf}}
%\vspace{1.cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 100 time-steps using continuous and discontinuous (between elements) formulations, in which (2): element size of 0.05 ($\sim$46 elements) and (3): element size: 0.10 ($\sim$ 11 elements).\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}
\end{comment}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\vbox{\vspace{-1.5cm}\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Step_P1DG-P2Cont}}
\vspace{-.5cm}
\hbox{
\includegraphics[width=15.5cm,height=10.cm]{./diagrams/Plume_P1DG-P2Cont}}}\vspace{-1cm}
\caption{Advection problem test-cases: Comparison of the resulting 2D advected field after 350 (top: step function) and 100 (bottom: Gaussian plume function) time-steps (high-resolution mesh as reference case for time-step size) using continuous and discontinuous (between elements) formulations. Mesh grids used in these simulations are described in Table~\ref{table:meshplume}.\label{2D_Sanpshot_Adv2D}}
%P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
%\caption{Advection problem test-cases: Comparison of the resulting 2D advected field at $t = 0.5$ (500 time-steps) for P$_{1}$DG-P$_{2}$, P$_{2}$DG-P$_{2}$ and P$_{1}$DG-P$_{1}$DG finite elements. There are 11.5k nodes within 22.5k elements. \label{2D_Sanpshot_Adv2D}}
\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\vspace{-2.4cm}
\hbox{
\includegraphics[width=12.5cm,height=10.5cm]{./diagrams/AllNorms_Step.png}}
\vspace{-.4cm}
\hbox{
\includegraphics[width=12.5cm,height=10.5cm]{./diagrams/AllNorms2.png}}}
\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ and $L_{2}$ norms for 2D solutions obtained from continuous and discontinuous (between elements) formulations -- top: step funtion; bottom: Gaussian plume function. First- and second-order slopes are also shown in here.\label{L1_L2norm_Adv2D}}
%\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ (top) and $L_{2}$ norms for 2D solutions obtained with $\left(\text{P}_{1}\text{DG-P}_{2}\right.$ and $\left.\text{P}_{2}\text{DG-P}_{2}\right)$ and without $\left(\text{P}_{1}\text{DG-P}_{1}\text{DG}\right)$ discontinuity between elements. \label{L1_L2norm_Adv2D}}
\end{figure}

\begin{comment}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=14.5cm,height=13.5cm]{./diagrams/AllNorms.png}
%\begin{center}
%\vbox{
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L1_PlumeConvergence.png}
%\vspace{-3.cm}
%\includegraphics[width=12.5cm,height=9.5cm]{./diagrams/All_L2_PlumeConvergence.png}}
%\vspace{2.cm}
\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ and $L_{2}$ norms for 2D solutions obtained from continuous and discontinuous (between elements) formulations. \label{L1_L2norm_Adv2D}}
%\caption{Advection problem test-cases: comparison of convergence, $L_{1}$ (top) and $L_{2}$ norms for 2D solutions obtained with $\left(\text{P}_{1}\text{DG-P}_{2}\right.$ and $\left.\text{P}_{2}\text{DG-P}_{2}\right)$ and without $\left(\text{P}_{1}\text{DG-P}_{1}\text{DG}\right)$ discontinuity between elements. \label{L1_L2norm_Adv2D}}
\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{bl-exact-meth-upwind.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Saturation solutions for the
  continuous upwind method for different 1D P$_{1}$DG-P$_{2}$ mesh
  resolutions and comparison against standard analytical solution.
\label{bl-exact-meth-upwind}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
  %\begin{center}
\vbox{\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{BL_1d_P0DGP1_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{BL_1d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{BL_1d_P2DGP3_convergence.eps}}}
   % \includegraphics[width=0.45\textwidth]{BL_2d_P1DGP2_convergence}
    \caption{Buckley--Leverett test-cases: Saturation profiles for a
      number of element pairs and numerical resolutions in 1D --
      P$_{0}$DG-P$_{1}$ (top), P$_{1}$DG-P$_{2}$ and P$_{2}$DG-P$_{3}$
      (bottom).\label{fig:BL_profiles}}
  %\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{L1_convergence_rate.eps}}
\vspace{.0cm}\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{L2_convergence_rate.eps}}}
    \caption{Buckley--Leverett test-cases: L1 (top) and L2 (bottom)
      error convergence rates for a number of element
      pairs. \label{fig:BL_converg-rates}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{bl-upwind-v-up-and-down.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Comparison of the optimal
  upwind formulation when using upwinding (OU) and coupled
  upwind/downwind (OU-D). The finite element interpolation of the
  saturation field $\left(S_{1}\right)$ is shown at different mesh
  resolutions. Downwind seems to detract from the accuracy of the
  solution. \label{bl-upwind-v-up-and-down}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\begin{center}
\includegraphics[width=1.\textwidth]{bl-exact-meth-cv-0-8-ele50.eps}
\end{center}
\vspace{0.cm}}
\caption{Buckley--Leverett test-cases: Comparison of control volume
  solutions using 80$\%$ upwinding and with optimal upwinding and
  using 50 continuous P$_{1}$DG-P$_{2}$
  elements. \label{bl-exact-meth-cv-0-8-ele50}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{bl-dg-2eles.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Two element solution using the
  discontinuous formulation. Saturation field from both CV solution
  and FEM interpolation are shown.  \label{bl-dg-2eles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-20.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-cent-4-10-20.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  the discontinuous and continuous formulation with different mesh
  resolutions. Solutions with (top) and without (bottom) upwinding
  scheme. Notice that oscillations are suppressed with the upwinding
  scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-vers-cty.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-p1-2-4-5-10-20-40.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  (top) continuous and discontinuous (between elements) formulations
  (solution with 50 elements may be considered as a converged
  result). Solution obtained (bottom) from linear pressure (P1)
  formulation with different mesh resolution with comparison against
  P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
\end{figure}

\begin{figure}[H]
\vbox{
\begin{center}
\includegraphics[width=17.5cm,height=12.5cm]{./doc_figures/bl-dg-4-10-vers-cty}
\end{center}
\vspace{0.cm}}
\caption{Gas saturations shown comparing the accuracy of the
  discontinuous between elements and continuous formulation. The 50
  element continuous solution may be viewed as a converged result.  }
\label{bl-dg-4-10-vers-cty}
\end{figure}

\end{comment}

%%%
%%%  FIGURE 
%%%

%%%
%%%  FIGURE 
%%%

### 2015-01-07 Papers/Prototype_1_Method/article_table.tex
adding Papers to the repo

\begin{table}
\begin{center}
\begin{tabular}{||c|| c c c c ||}
\hline\hline
{\bf Mesh} & {\bf Number of}        & {\bf Number of} & {\bf Element}  & {\bf Time-Step}    \\
           & {\bf Elements}$^{\star}$&{\bf Nodes}      & {\bf Size}     & {\bf Size}  \\
\hline
1          & 68 / 3 / 3                & 47              & 0.30           & 5.0$\times$10$^{-2}$ \\
2          & 538 / 12  / 28             & 304             & 0.10           & 1.667$\times$10$^{-2}$ \\
3          & 2316 / 46  / 115            & 1229            & 0.05           & 8.333$\times$10$^{-3}$ \\
4          & 6410 / 130  / 320           & 3324            & 0.03           & 5.0$\times$10$^{-3}$ \\
5          & 57650 / 1170 / 2886          & 29176           & 0.01           & 1.667$\times$10$^{-3}$ \\
\hline\hline
\end{tabular}
\caption{Advection problem test-cases: Meshes used in the simulations. $\left(^{\star}\right)$ refers to the number of elements in the domain and within the Gaussian plume and step-function. \label{table:meshplume}}
\end{center}
\end{table}

### 2015-01-07 Papers/Prototype_1_Method/diagrams/overlapping.py

@@ -1,0 +1,79 @@
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+fig = plt.figure()
+ax = fig.add_subplot(111, projection='3d')
+import numpy as n
+import pylab as p
+
+
+X1=[-0.5,0.5,0.0]
+Y1=[0,0,n.sqrt(2)]
+
+ax.plot3D((X1[0],X1[1],X1[2],X1[0]),(Y1[0],Y1[1],Y1[2],Y1[0]),c='k')
+
+for k in range(3):
+    avY=(Y1[k%3]+Y1[(k+1)%3])/2.0
+    avX=(X1[k%3]+X1[(k+1)%3])/2.0
+    CX=sum(X1)/3.0
+    CY=sum(Y1)/3.0
+
+    ax.plot3D((avX,CX),(avY,CY),c='k',ls=':')
+
+k=0
+av0Y=(Y1[k%3]+Y1[(k+1)%3])/2.0
+av0X=(X1[k%3]+X1[(k+1)%3])/2.0
+k=1
+av1Y=(Y1[k%3]+Y1[(k+1)%3])/2.0
+av1X=(X1[k%3]+X1[(k+1)%3])/2.0
+
+MX=n.array([[av0X,CX],
+    [X1[1],av1X]])
+MY=n.array([[av0Y,CY],
+    [Y1[1],av1Y]])
+
+def f(x,y):
+    return 0.4-0.1*x+0.2*y
+
+Z=f(MX,MY)
+
+ax.plot_surface(MX,MY,Z)
+
+
+
+X=n.array((X1[1],X1[2]))
+Y=n.array((Y1[1],Y1[2]))
+Z=f(X,Y)
+ax.plot3D(X,Y,zs=Z,c='k',ls='--')
+X=n.array((X1[1],X1[0]))
+Y=n.array((Y1[1],Y1[0]))
+Z=f(X,Y)
+ax.plot3D(X,Y,zs=Z,c='k',ls='--')
+
+ax.plot((av0X,av0X),(av0Y,av0Y),zs=(0,f(av0X,av0Y)),c='k')
+ax.plot((av1X,av1X),(av1Y,av1Y),zs=(0,f(av1X,av1Y)),c='k')
+
+for k in range(3):
+    ax.plot((X1[k],X1[k]),(Y1[k],Y1[k]),zs=(0,f(X1[k],Y1[k])),c='k')
+
+
[…]

### 2015-01-07 Papers/Prototype_1_Method/diagrams/overlapping_cartoon.py

@@ -1,0 +1,249 @@
+import pylab as p
+import matplotlib
+
+matplotlib.ticker.rcParams['xtick.minor.size']=0
+
+
+def p2(X,f):
+
+    p.vlines(X,0,f(X),linestyles='dashed')
+
+    XM=[f(X[0])]
+
+    for k in range(len(X)-1):
+        x0=X[k]
+        x1=0.5*(X[k]+X[k+1])
+        x2=X[k+1]
+
+        xa=0.25*(3*X[k]+X[k+1])
+        xb=0.25*(X[k]+3*X[k+1])
+
+        XM.append(X[k+1])
+
+        def g(x):
+            return (f(x0)*(x1-x)*(x2-x)/((x1-x0)*(x2-x0))
+                    +f(x1)*(x-x0)*(x2-x)/((x1-x0)*(x2-x1))
+                    +f(x2)*(x-x0)*(x-x1)/((x2-x0)*(x2-x1)))
+         
+
+        x=p.linspace(x0,x2,101)
+        p.plot(x,g(x),c="b",ls='-')
+        p.scatter(x0,f(x0),c='k')
+        p.scatter(x1,f(x1),c='k')
+        p.scatter(x2,f(x2),c='k')
+
+        p.vlines(xa,0,g(xa),linestyles='dotted')
+        p.vlines(xb,0,g(xb),linestyles='dotted')
+
+
+    p.vlines(X,0,XM,linestyles='dashed')
+    p.axis((X[0],X[-1],0,1.7))
+    p.xticks([])
+    p.yticks([0,1])
+
+def p1dg(X,f):
+
+    XM=[0]
+    Xm=[0]
+    p.hlines(0,X[0],X[-1])
+    for k in range(len(X)-1):
+        x0=X[k]
+        x1=0.5*(X[k]+X[k+1])
+        x2=X[k+1]
+
+        xa=0.25*(3*X[k]+X[k+1])
+        xb=0.25*(X[k]+3*X[k+1])
+
+
+        def g(x):
+            return (f(x0)*(-x1-x2+2.0*x)/((x1-x0)*(x2-x0))
+                    +f(x1)*(-2.0*x+x0+x2)/((x1-x0)*(x2-x1))
+                    +f(x2)*(2.0*x-x0-x1)/((x2-x0)*(x2-x1)))
+
+        XM[-1]=max(XM[-1],g(x0))
[…]

### 2015-01-07 Papers/Prototype_1_Method/article.tex
updates

@@
 
-\usepackage[obeyFinal]{todonotes}
+%\usepackage[obeyFinal]{todonotes}
+\usepackage{todonotes}
 
@@
 \title{The Overlapping Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling \\
-Part I: Formulation}
+Part I: Numerical Formulation}
 
@@
 The overlapping control volume finite element method (OCVFEM) has two major strengths, firstly it uses a dual consistent pressure-velocity representation in control volume and finite element spaces which ensures local mass conservation.
-Secondly, it uses a family of finite element types that ensures Darcy equations for multiphase flows can be exactly enforced.
+Secondly, it uses a family of finite element types that ensures multiphase Darcy equations can be exactly enforced.
 The underlying mass conservation equations are solved in control volume space and finite elements are used to obtain high-order fluxes on control volume boundaries.
@@
 Finite difference methods (FDM) have been extensively used in modelling and simulation of fluid flows in porous media~\citep{aziz_1986, chen_1997, chen_2005} however, they are strongly dependent on mesh quality and orientation and cannot easily represent complex geometries.
-In addition, FDM produce excessive numerical dispersion in heterogeneous media \citep{chavent_1986}.
+In addition, FDM produce excessive numerical dispersion in heterogeneous porous matrix \citep{chavent_1986}.
 The geometrical flexibility of finite element methods (FEM) has proven to overcome these deficiencies.
-Among FEM-based formulations for porous media, the control volume finite element method (CVFEM) has become increasingly popular as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, cordazzo_2004, fung_1992, geiger_2004, cumming_2011, hurtado_2007}.
+Among FEM-based formulations for porous media, the control volume finite element method (CVFEM) has become increasingly popular as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, cordazzo_2004, geiger_2004, hurtado_2007}.
 \citet{huber_2000} demonstrated that the vertex-centred finite volume - finite element method (or Box scheme) can achieve similar goals~\citep[see also][]{helmig_1997}.
 
-For porous media flows, CVFEM discretisations with Galerkin-FEM formulation for the pressure equation has been used to solve Darcy and Richard equations as described by \citet{fung_1992} and \citet{cumming_2011}.
-\citet{durlofsky_1993,durlofsky_1994} investigated a mixed FEM formulation (i.e., piecewise constant in pressure and piecewise linear in velocity) and classical CVFEM for single phase Darcy flow.
+%For porous media flows, CVFEM discretisations with Galerkin-FEM formulation for the pressure equation has been used to solve Darcy and Richard equations as described by \citet{fung_1992} and \citet{cumming_2011}.
+\citet{durlofsky_1993,durlofsky_1994} compared the performance of a mixed FEM formulation (i.e., piecewise constant in pressure and piecewise linear in velocity) and the classical CVFEM for single phase Darcy flow.
 He concluded that the latter is more computationally efficient and numerically accurate than the former for simple problems involving a (relatively) small number of degrees of freedom.
-Moreover, for complex discontinuous and heterogeneous problems, mixed FEM formulations lead to physically realistic solutions.
+In addition, for complex discontinuous and heterogeneous problems, mixed FEM formulations often lead to physically realistic solutions.
 

### 2015-01-07 Papers/Prototype_1_Method/article_figure1.tex
updates

@@
 \vbox{\hbox{\hspace{1cm}
-    \includegraphics[width=0.8\textwidth]{compar-dg.eps}}
-   \hbox{ \hspace{1cm} \includegraphics[width=0.8\textwidth]{compar-dg-bdt.eps}}}
+    \includegraphics[width=0.8\textwidth]{diagrams/compar-dg.eps}}
+   \hbox{ \hspace{1cm} \includegraphics[width=0.8\textwidth]{diagrams/compar-dg-bdt.eps}}}
     \caption{Advection problem test-cases: control volume solution (5
@@
 \begin{center}
-\includegraphics[width=1.2\textwidth]{compar-dg-bdt-diff}
+\includegraphics[width=1.2\textwidth]{diagrams/compar-dg-bdt-diff}
 \end{center}
@@
 \vbox{\hbox{\hspace{-1.3cm}
-\includegraphics[width=17.5cm,height=12.5cm]{theta-bdt}}
+\includegraphics[width=17.5cm,height=12.5cm]{diagrams/theta-bdt}}
 \vspace{0.cm}}
@@
 \hbox{\hspace{-.5cm}
-\includegraphics[width=14.0cm,height=10.cm]{converg-cv}}
+\includegraphics[width=14.0cm,height=10.cm]{diagrams/converg-cv}}
 \vspace{-.5cm}
 \hbox{\hspace{-.5cm}
-\includegraphics[width=14.0cm,height=10.cm]{converg-fem}}
+\includegraphics[width=14.0cm,height=10.cm]{diagrams/converg-fem}}
 }\vspace{-.3cm}
@@
 \hbox{\hspace{-1cm}
-\includegraphics[width=17.5cm,height=12.5cm]{converg-compare-fem}}
+\includegraphics[width=17.5cm,height=12.5cm]{diagrams/converg-compare-fem}}
 \caption{Advection problem test-cases: comparison of convergence of
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{bl-exact-meth-upwind.eps}
+\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-upwind.eps}
 \end{center}
@@
 \vbox{\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{BL_1d_P0DGP1_convergence.eps}}
+    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P0DGP1_convergence.eps}}
 \vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{BL_1d_P1DGP2_convergence.eps}}
+    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P1DGP2_convergence.eps}}
 \vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{BL_1d_P2DGP3_convergence.eps}}}
+    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P2DGP3_convergence.eps}}}
    % \includegraphics[width=0.45\textwidth]{BL_2d_P1DGP2_convergence}
@@
 \vbox{\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{L1_convergence_rate.eps}}
+    \includegraphics[width=0.8\textwidth]{diagrams/L1_convergence_rate.eps}}
 \vspace{.0cm}\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{L2_convergence_rate.eps}}}
+    \includegraphics[width=0.8\textwidth]{diagrams/L2_convergence_rate.eps}}}
     \caption{Buckley--Leverett test-cases: L1 (top) and L2 (bottom)
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{bl-upwind-v-up-and-down.eps}
+\includegraphics[width=1.\textwidth]{diagrams/bl-upwind-v-up-and-down.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{bl-exact-meth-cv-0-8-ele50.eps}
+\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-cv-0-8-ele50.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{bl-dg-2eles.eps}
+\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
 \end{center}
@@
 \vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-20.eps}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
 \vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-cent-4-10-20.eps}}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
 \caption{Buckley--Leverett test-cases: Saturation field obtained from
@@
 \vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-vers-cty.eps}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
 \vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-p1-2-4-5-10-20-40.eps}}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
 \caption{Buckley--Leverett test-cases: Saturation field obtained from
@@
 \begin{center}
-\includegraphics[width=17.5cm,height=12.5cm]{./doc_figures/bl-dg-4-10-vers-cty}
+\includegraphics[width=17.5cm,height=12.5cm]{diagrams/bl-dg-4-10-vers-cty}
 \end{center}

### 2015-01-08 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Updating Tunde's paper

% First of two papers based on the SPE Comparative Solution Project

%\documentclass{elsarticle}
\documentclass{article}
% package to allow adding affiliation into the title
\usepackage[affil-it]{authblk}
% todonotes allow adding notes into the text as comments
\usepackage{todonotes,amsmath,color}
\newcommand{\JG}[1]{\todo[color=blue!30, size=\small]{JG: #1}}
\newcommand{\red}{\textcolor{red}}

\begin{document}

\title{Upscaling with the Overlapping Control Volume Finite Element Method Multiphase Porous Media Flow Modelling Technique}

\author{B. Lashore\thanks{Electronic address: \texttt{r01bol14@abdn.ac.uk} (Corresponding author)} , J.L.M.A. Gomes}
\affil{School of Engineering, University of Aberdeen, UK}

\author{P. Salinas, C.C. Pain}\affil{Department of Earth Science and Engineering, Imperial College London, UK}
%\author[UoA]{B. Lashore}\corref{cor1}\ead{r01bol14@abdn.ac.uk}
%\author[IC]{P. Salinas} \author[IC]{C.C. Pain} \author[UoA]{J.L.M.A. Gomes}

%\cortext[cor1]{Corresponding author.}
%\address[UoA]{School of Engineering, University of Aberdeen, UK}
%\address[IC]{Department of Earth Science and Engineering, Imperial College London, UK}

\date \today
\maketitle
%\section*{Abstract}
\begin{abstract}
%% Comment:
\JG{For non-scientific conferences is always better to keep the title shorter and/or more $\lq$direct'/punchy and/or with key terms that are more familiar to the audience. A few key-words that you may consider for the title: upscaling (although we are not doing upscaling at the moment), benchmark, heterogeneity} \JG{As a rule of thumb, always start an {\it Abstract} with the motivation for the work (thus why is this relevant?)}
The 10$^{\text{th}}$ SPE Comparative Solution Project on upscaling involved two problems. The first problem which involves upscaling and pseudoization methods for an easily computed 2D gas-injection problem\JG{too many $\lq$problem' in  a single sentence ...}, is used in this paper to discuss another approach to upscaling. The approach removes the upscaling computation performed prior to the main flow calculation and instead makes use of an effective flux calculation within the computation \red{(what do you mean?)}.\JG{1. too many $\lq$computation' in the same sentence? 2. and what is the second problem?}

In the overlapping control volume finite element method (OCVFEM) formulation, static properties are represented in unstructured tethrahedral mesh grid in which \red{{\it describe in a few words the approach used ...}} on which the static properties are represented. The underlying mass conservation equations are solved in control volume space while high-order fluxes across control volume boundaries are obtained from FEM interpolation. A P0DG meshing scheme is used in this simulation therefore permeability, porosity, pressure and density are represented as discontinous data points in the centre of the tethrahedral elements while velocity is represented as continuous data points at the edges of the tethrahedral elements \red{(this sentence need to be modified according to your simulation set up)}. \red{(try to summarise these sentences as the main focus of this abstract is to describe the main objective of the paper (work) and how (in a few words/sentences) you are going to tackle the problems ahead)}

The paper begins with an introduction to heterogeneity and the challenges created by heterogenity. It then discusses the benefits of upscaling and the various methods of upscaling. It also discusses the P0DG meshing scheme implementation of the OCVFEM and also briefly introduces higher order meshing schemes. Finally, it presents the OCVFEM simulation results for the first problem of the 10th SPE Comparative Solution Project and compares it to the results obtained from the original participants of the project. In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM and higher order meshing schemes would be used. The paper would also make use of stochastic methods for data representation.\JG{You do not need the summary of the work/sections in the {\it Abstract}, just in the {\it Introduction} section.} \red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}
\end{abstract}

\end{document}

### 2015-01-08 Papers/Prototype_1_Method/article.tex
updates

@@
 %For porous media flows, CVFEM discretisations with Galerkin-FEM formulation for the pressure equation has been used to solve Darcy and Richard equations as described by \citet{fung_1992} and \citet{cumming_2011}.
-\citet{durlofsky_1993,durlofsky_1994} compared the performance of a mixed FEM formulation (i.e., piecewise constant in pressure and piecewise linear in velocity) and the classical CVFEM for single phase Darcy flow.
-He concluded that the latter is more computationally efficient and numerically accurate than the former for simple problems involving a (relatively) small number of degrees of freedom.
-In addition, for complex discontinuous and heterogeneous problems, mixed FEM formulations often lead to physically realistic solutions.
+\citet{durlofsky_1993,durlofsky_1994} compared the performance of a mixed FEM formulation (i.e., piecewise constant in pressure and piecewise linear in velocity) and the classical CVFEM for single phase Darcy flows.
+He concluded that the latter is more computationally efficient and numerically accurate than the former for problems involving a (relatively) small number of degrees of freedom.
+For complex discontinuous and heterogeneous problems, mixed FEM formulations often lead to physically realistic solutions.
 
@@
 CVFEM often requires high resolution meshes in regions where material properties vary abruptly, such as permeability contrasts at fracture-matrix interfaces.
-Since the structural geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
+Since the structural geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may present different properties.
 Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CV's at these interface.
 This often leads to excessive numerical dispersion, especially in highly heterogeneous media.
-
 In order to overcome this deficiency, \citet{nick_2011b, nick_2011a} developed a new discretisation scheme -- discontinuous hybrid finite element finite volume method (DFEFVM), where CV's split along the interfaces of different material properties.
 This scheme was designed to simulate single and multiphase flows through discrete fractured rocks.
+
 \citet{cumming_2011} demonstrated that CVFEM-based discretisation could be used to solve Richards' equations (coupled mass conservation and Darcy equations) in heterogeneous porous media with relatively small computational overhead, compared with traditional coupled velocity-pressure based formulations.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}~\citep[see also][]{forsyth_1990,cumming_phd2012}.
+Fluxes over CV's were calculated based upon material properties, whereas saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}~\citep[see also][]{forsyth_1990,cumming_phd2012}.
 
-Discontinuity-capturing schemes~\citep[e.g., shock waves, contact surface or material discontinuity -- see][]{brooks_1982,tezduyar_1986,toro_1997} were originally developed to resolve sharp changing of field variables.
+\medskip
+
+Discontinuity-capturing schemes~\citep[e.g., shock waves, contact surface or material discontinuity -- see][]{brooks_1982,tezduyar_1986} were originally developed to resolve sharp changing of field variables.
 Related discontinuity-capturing schemes include the discontinuous-Galerkin FEM (DGFEM) scheme in which continuity of the solution is not explicitly enforced, allowing sharp gradients in the solution fluxes to be captured.
@@
 In addition, DGFEM is well-suited to deal with interface problems by incorporating specially-designed interface fluxes.
-These properties have attracted the attention of subsurface flow research communities in the last 15 years \citep[see][]{riviere_2000,riviere_2002,bastian_2002}.
+These properties have attracted the attention of subsurface flow research communities in the past 15 years \citep[see][]{riviere_2000,riviere_2002,bastian_2002}.
 
@@
 The continuity equations are embedded into the pressure equation to enforce mass conservation and exact force balance.
-This is possible by using dual CV and FEM discretisations for the pressure equation, while saturation is discretised using a CV formulation.
-We employ an implicit algorithm with respect to time.
-The implicit method is unconditionally stable for pure advection, with no restriction on the time step size.
+This is possible by using dual CV and FEM discretisations for the pressure equation, while saturation is discretised in CV space.
+The overall formulation employs an implicit algorithm with respect to time that is unconditionally stable for pure advection and with no restriction on the time-step size.
 
 The formulation has two key developments.
-Firstly, it uses a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a  family of triangular and tetrahedral finite element pairs, P$_{n}$DG-P$_{n+1}$ \citep[see][]{cotter_2009b}.
-In this element type, the dual velocity and pressure fields are represented by $n^{\rm th}$ order (discontinuous) and $({n+1})^{\rm th}$ order (continuous) polynomials, respectively.
+Firstly, it uses a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a  family of triangular and tetrahedral finite element-pairs, P$_{n}$DG-P$_{m}$[DG] \citep[see][]{cotter_2009b}.
+In this element type, the dual velocity and pressure fields are represented by $n^{\rm th}$ order (discontinuous) and $m^{\rm th}$ order (continuous/discontinuous) polynomials, respectively.
 This allows the velocity to exactly represent pressure gradients in the flow solution for homogeneous material properties.
-The P$_{n+1}$DG-P$_{n}$DG element pair, which has similar properties to the P$_n$DG-P$_{n+1}$ element pair, allows a representation in which pressure, \jrp{Saturation is on the control volume space and thus always discontinuous} saturation and other solution variables are all fully discontinuous across finite element boundaries.
+The P$_{n+1}$DG-P$_{n}$DG element-pair, which has similar properties to the P$_n$DG-P$_{n+1}$ element-pair, allows a representation in which pressure, %\jrp{Saturation is on the control volume space and thus always discontinuous}
+saturation and other solution variables are all fully discontinuous across finite element boundaries.
 The second key development is that this formulation uses an overlapping finite element representation of velocity within each element.
@@
 The remainder of this paper is organised as follows.
-New element types and the overlapping formulation are introduced in Sections~\ref{element_types_section}-\ref{overlapping_method_section}.
+New element types and the overlapping formulation are introduced in Sections~\ref{element_types_section} and~\ref{overlapping_method_section}.
 A detailed description of the new porous media methods is given in Section~\ref{transport_methods_section}.
@@
 \section{Continuous and Discontinuous Finite Element Types and Control Volumes} \label{element_types_section}
-The family of P$_{n}$DG-P$_{n+1}$ element pairs was originally introduced by \citet{cotter_2009a} for geophysical fluid dynamics applications \citep[see also][]{cotter_2012}.
-In particular, the P$_{1}$DG-P$_{2}$ element pair was originally developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes.
-This element pair uses element-wise linear polynomial FE basis functions, discontinuous across element interfaces, for velocity $\left(\text{P}_{1}\text{DG}\right)$ and quadratic polynomial finite element basis functions for pressure which maintain $C_{\text{0}}$ continuity across element boundaries $\left(\text{P}_{2}\right)$.
+The family of P$_{n}$DG-P$_{n+1}$ element-pairs was originally introduced by \citet{cotter_2009a} for geophysical fluid dynamics applications \citep[see also][]{cotter_2012}.
+In particular, the P$_{1}$DG-P$_{2}$ element-pair was originally developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes.
+This element-pair uses element-wise linear polynomial FE basis functions, discontinuous across element interfaces for velocity $\left(\text{P}_{1}\text{DG}\right)$, and quadratic polynomial finite element basis functions for pressure which maintain $C_{\text{0}}$ continuity across element boundaries $\left(\text{P}_{2}\right)$.
 %This is analogous to the exact balance also achieved with this element between the frictional and pressure gradient terms in Darcy's equations.
@@
 Figure~\ref{fem_cv_represent_a} displays three element types of the P$_{n}$DG-P$_{n+1}$ family that are used in this set of papers.
-P$_{\text{0}}$DGP$_{\text{1}}$ (a)  and P$_{1}$DG-P$_{2}$ are shown in Fig.~\ref{fem_cv_represent_a}(a) and (b), respectively, where pressure nodes are stored in the vertices and edges (in P$_{\text{2}}$ elements) of triangular/tetrahedral elements and control volumes are constructed around them based on a Voronoi decomposition.
+P$_{\text{0}}$DGP$_{\text{1}}$ and P$_{1}$DG-P$_{2}$ are shown in Fig.~\ref{fem_cv_represent_a}(a) and (b), respectively, where pressure nodes are stored in the vertices and edges (in P$_{\text{2}}$ elements) of triangular/tetrahedral elements and control volumes are constructed around them based on a Voronoi decomposition.
 One can realise that due to the continuous finite element node structure, control volumes span more than one element.
-Having CV's spanning to multiple elements may create artificial diffusion in cases where there is a large variations in physical properties across elements, such as at the boundary between materials with different absolute permeabilities .
-As an alternative, two families of fully discontinuous element pairs are also considered: P$_{n}$DG-P$_{n}$DG and P$_{n+1}$DG-P$_{n}$DG, Fig.~\ref{fem_cv_represent_a}(c) along with control volumes from their dual Voronoi decompositions.
-These families of elements are LBB stable and free from chequerboard pressure modes, as demonstrated by~\citet{cotter_2009b}~\citep[see also][]{cotter_2011}.
+Having CV's spanning to multiple elements may create artificial diffusion in cases where there are large variations in physical properties across elements, such as at the boundary between materials with different absolute permeabilities.
+As an alternative, two families of fully discontinuous element-pairs are also considered: P$_{n}$DG-P$_{n}$DG and P$_{n+1}$DG-P$_{n}$DG~\citep[Fig.~\ref{fem_cv_represent_a}(c), applications using these element-pairs are exploited in][]{pavlidis_2015} along with control volumes from their dual Voronoi decompositions.
+These families of element-pairs are LBB stable and free from chequerboard pressure modes, as previously demonstrated by~\citet{cotter_2009b}~\citep[see also][]{cotter_2011}.
 
@@
 %\JGnote{Most of the simulations in this paper (and the next) were performed using P$_{1}$DGP$_{2}$ elements.
-However it seems that the sketch of this element pair was deleted/replaced by P$_{0}$DGP$_{1}$ and by the double-discontinuous element (fig.1 left/right) -- was this replacement on purpose or was it a mistake?}
+However it seems that the sketch of this element-pair was deleted/replaced by P$_{0}$DGP$_{1}$ and by the double-discontinuous element (fig.1 left/right) -- was this replacement on purpose or was it a mistake?}
 %\end{center}
@@
 \begin{equation}\label{e:darcy_eqn}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
 \end{equation}
-where $\mathbf{q}_{\alpha}=\left(q_\alpha^{(1)},q_\alpha^{(2)},q_\alpha^{(3)}\right)^{\text{T}}$ (for 3D flow) is the $\alpha$-th phase Darcy flow rate, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, and $\mu_{\alpha}$, $p_{\alpha}$ and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure and a source term, respectively.
+where $\mathbf{q}_{\alpha}=\left(q_\alpha^{(1)},q_\alpha^{(2)},q_\alpha^{(3)}\right)^{\text{T}}$ is the $\alpha$-th phase Darcy flow rate for 3D flows, $\mathbf{K}$ is the absolute permeability tensor of the porous matrix, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$ and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure and a source term, respectively.
 
-If we define the interstitial or advective phase velocity, averaged over the entire medium as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then we may rewrite Eqn.~\ref{e:darcy_eqn} as:
+If we define the interstitial or advective phase velocity, averaged over the entire medium, as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then we may rewrite Eqn.~\ref{e:darcy_eqn} as:
 \begin{equation}
@@
 \[\tilde{p}=\lim_{a\rightarrow 0} 
-   \frac{1}{2}\left(p(\bm{r}+a\bm{n})+p(\bm{r}-a\bm{n})\right).\] This term therefore vanishes when pressure is continuous. Equation ~\ref{force-semi-disc} can be represented, in matrix form, as:
+   \frac{1}{2}\left[p(\bm{r}+a\bm{n})+p(\bm{r}-a\bm{n})\right].\] This term therefore vanishes when pressure is continuous. Equation ~\ref{force-semi-disc} can be represented, in matrix form, as:
 \begin{equation}
@@
   \underline{{\bf p}} = \left(p_1, p_2, p_3, ...,
-  p_{\mathcal{N}_p}\right)^T, \nonumber \nonumber
+  p_{\mathcal{N}_p}\right)^T. \nonumber \nonumber
 \end{eqnarray}
-respectively. $\mathcal{N}_{\alpha}$ is the number of phases and 
-$v_x$, $v_y$, $v_z$ are the the velocity components 
-associated with the $x-$ and $y-$ and $z-$ coordinates respectively.
+$\mathcal{N}_{\alpha}$ is the number of phases and $v_x$, $v_y$, $v_z$ are the the velocity components associated with the $x-$ and $y-$ and $z-$ coordinates, respectively.
 
@@
 Figure~\ref{compar-dg-bdt-diff} demonstrates the advection capturing capability of our method.
-In Fig.~\ref{theta-bdt}, solutions obtained from (a) continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element pair}\right)$ and (b) discontinuous $\left(\text{either P}_{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements pairs}\right)$ formulations are compared in a problem with large time step size.
+In Fig.~\ref{theta-bdt}, solutions obtained from (a) continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element-pair}\right)$ and (b) discontinuous $\left(\text{either P}_{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements pairs}\right)$ formulations are compared in a problem with large time step size.
 The value of $\theta$ on the faces of the CV's is shown at the end of two time steps; it is important to notice that $\theta$ is smaller and closer to $0.5$ when using the continuous approach than the discontinuous method.

### 2015-01-08 Papers/Prototype_1_Method/article_figure1.tex
updates

@@
 \begin{figure}[h]
-%\vspace{-1.cm}
-%\vbox{
-
-%\begin{center}
-%\includegraphics[width=0.6\textwidth]{1D_Sketch_b.eps}
-%\vspace{-1.cm}
-%\end{center}
-%\hbox{\hspace{6.5cm}(a)}
-%\vspace{.1cm}
-%
-%\begin{center}
-%\includegraphics[width=1.\textwidth]{1D_Sketch.eps}
-%\vspace{-1.cm}
-%\end{center}
-%\hbox{\hspace{6.5cm}(b)}
-%\vspace{-.1cm}
-
 \vbox{
-\hbox{ \hspace{4.cm}
-\includegraphics[width=.55\textwidth]{diagrams/p0dgp1-cont-sat} \hspace{0.cm} (a)}
-\vspace{-0.2cm}
-\hbox{ \hspace{4.cm}
-\includegraphics[width=.55\textwidth]{diagrams/p1dgp2-cont-sat} \hspace{0.cm} (b)}
-\vspace{-0.2cm}
-\hbox{ \hspace{4.cm}
-\includegraphics[width=.55\textwidth]{diagrams/p2dgp1-dg-sat} \hspace{0.cm} (c)}
-\vspace{-0.2cm}
-
-%\vspace{.1cm}
+\hbox{\hspace{-0.5cm}\includegraphics[width=.6\textwidth]{diagrams/p0dgp1-cont-sat} 
+\hspace{-.9cm}\includegraphics[width=.6\textwidth]{diagrams/p1dgp2-cont-sat} }
+\hbox{\hspace{4cm}(a) \hspace{6.5cm}(b)}
+\vspace{0.cm}
+\hbox{\hspace{2.5cm}\includegraphics[width=.8\textwidth]{diagrams/p2dgp1-dg-sat} }
+\vspace{-0.3cm}
+\hbox{\hspace{6cm}(c) }
 }
-
-  \caption{2D representation of the element pairs (a) P0DGP1, (b) P1DGP2  and (c) P2DGP1DG.
+\caption{2D representation of the element-pairs (a) P0DGP1, (b) P1DGP2  and (c) P2DGP1DG.
 Shaded areas denote a control volumes (in which saturation is stored), black points represent the pressure nodes and the white points the velocity.}
@@
 \end{figure}
+
+\clearpage
 
@@
     \caption{Buckley--Leverett test-cases: Saturation profiles for a
-      number of element pairs and numerical resolutions in 1D --
+      number of element-pairs and numerical resolutions in 1D --
       P$_{0}$DG-P$_{1}$ (top), P$_{1}$DG-P$_{2}$ and P$_{2}$DG-P$_{3}$

### 2015-01-09 Papers/Prototype_1_Method/article.tex
updates

@@
 \end{eqnarray}
-Here $\bm{n}=\left(n_{1},n_{2},n_{3}\right)^{T}$ is the outward-pointing normal vector of the domain $\Omega$.
+Here $\delta_{i,j} = \left[\underline{\underline{\sigma}}_{\alpha}\right]_{i,j}$,  $\bm{n}=\left(n_{1},n_{2},n_{3}\right)^{T}$ is the outward-pointing normal vector of the domain $\Omega$.
 $\bm{n}^{(E,q)}$ is the normal to the boundary of element $E$ and is outward-pointing if $P_{q}$ takes support on $E$, and inward-pointing otherwise.
@@
 
-This formulation ensures that for uniform \jrp{This tensor needs a good name} ${\underline{\underline \sigma}}_{\alpha}$ within each element the balance in the \jrp{is this only true in 1D} 1D extended Darcy flow equations is strictly enforced.
+%This formulation ensures that for uniform \jrp{This tensor needs a good name -- JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
+Maybe solid-fluid homogeneisation factor/ parameter/ coeff} ${\underline{\underline \sigma}}_{\alpha}$ within each element the balance in the \jrp{is this only true in 1D} 1D extended Darcy flow equations is strictly enforced.
 The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-Thus the tensor %${\underline{\underline \sigma}}_{\alpha}$:
+Thus the viscous-friction damping tensor \jrp{This tensor needs a good name JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
+Maybe solid-fluid homogeneisation factor/ parameter/ coeff or viscous-friction damping ...}, %${\underline{\underline \sigma}}_{\alpha}$:
 \begin{eqnarray}
@@
 \end{eqnarray}
-is piecewise constant within the sub-volumes defined through the non-empty intersections between the elements and control volumes (in the pressure discontinuous formulation, these are precisely the control volumes themselves, see Fig.~\ref{fem_cv_represent_a}(c)).
+is piecewise constant within the sub-volumes defined through the non-empty intersections between the elements and control volumes; in the pressure discontinuous formulation, these are precisely the control volumes themselves, Fig.~\ref{fem_cv_represent_a}(c).
 The velocity, formed by the action of ${\underline{\underline \sigma}}_{\alpha}^{-1}$ upon the force density $\bm{v}_\alpha$, has an exact polynomial representation on the sub-volumes of one degree lower that of $p$.

### 2015-01-09 Papers/Prototype_1_Method/article.tex
updates

@@
 
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
 \section{Overlapping-CVFEM Formulation -- An Accurate Representation of Multiphase Darcy Flows}
@@
 The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-Thus the viscous-friction damping tensor \jrp{This tensor needs a good name JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
-Maybe solid-fluid homogeneisation factor/ parameter/ coeff or viscous-friction damping ...}, %${\underline{\underline \sigma}}_{\alpha}$:
+Thus the viscous-friction damping tensor, \jrp{This tensor needs a good name JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
+Maybe solid-fluid homogeneisation factor/ parameter/ coeff or viscous-friction damping ...} %${\underline{\underline \sigma}}_{\alpha}$:
 \begin{eqnarray}
@@
 %%%         %%%
-\section{Transport Methods}\label{transport_methods_section}
-\subsection{CVFEM Formulation}
-\jrp{ I think we need to justify why this section is here, or combine it with the saturation section, at the moment everything is a bit disjointed.}
+\section{Scalar Transport Formulation}\label{transport_methods_section}
+
+%%%            %%%
+%%% SUBSECTION %%%
+%%%            %%%
+\subsection{CVFEM Spatial Discretisation}\label{Section:CVFEMDiscretisation}
 Given a partitioning of a domain $\Omega$ into a set of CV's, we seek a numerical solution of the transport equation,
@@
 \end{equation}
-where $\mathbf{a}$ is the advection velocity vector, $\textit{t}$ and $\textit{s}$ are time and a source term, respectively.
+where \text{T} is a scalar field, $\mathbf{a}$ is the advection velocity vector, $\textit{t}$ and $\textit{s}$ are time and a source term, respectively.
 The problem is discretised by testing the weak form of the equation over each CV $i$ using a set of test functions, $M_{i}$, which are unity over control volume $i$ and zero otherwise.
@@
 in which $\mathcal{M}$ is the number of CV's \citep[which is not necessarily equal to the $\mathcal{N}$ nodes of the underlying FEM mesh,][]{cordazzo_2004, eymard_1994}.
-To obtain a unique solution, this is combined with an expansion of the approximate solution {\it T} to $\text{T}$ in terms of the control volume basis functions $M_{j}$ with,
+To obtain a unique solution, this is combined with an expansion of the approximate solution {\it T} to $\text{T}$ in terms of the CV basis functions $M_{i}$ with,
 \begin{equation}  
@@
 \noindent
-where $\mathbf{n}$ is the outward pointing unit normal vector to the surface of the control volume \textit{i} $\left(\text{CV}_{i}\right)$.
-We use Gaussian quadrature to approximate the surface integral over each face of the control volume \textit{i}.
+where $\mathbf{n}$ is the outward pointing unit normal vector to the surface of CV$_{i}$.
+Gaussian quadrature are used to approximate the surface integral over each face of CV$_{i}$.
 To close the system, the value $\widetilde{T}$ at the quadrature integration points on the surface of the control volume must be calculated from the CV solution, \textit{T}.
 
-\medskip
-The value of $\widetilde{T}$ is calculated based on a high-order FEM interpolation $T_{\mbox{FEM}}$ of the CV solution $T$.
-These high-order fluxes are subject to limiting in order to obtain the final fluxes used at the Gaussian quadrature points on the control volume faces at element boundaries \citep{voller_2009,gomes_book_2012}.
-Suppose that each element {\it i} has control volumes and a solution variable \jrp{is this used anywhere?} $\hat T_{i}$.
-Then the FEM solution, $T_{\mbox{FEM}}$, is related to the CV solution, {\it T}, by:
+$\widetilde{T}$ is calculated based on a high-order FEM interpolation $T_{\text{FEM}}$ of the CV solution {\it T}.
+These high-order fluxes are subject to limiting to obtain the final fluxes used at the Gaussian quadrature points on the control volume faces at element boundaries \citep{voller_2009,gomes_book_2012}.
+Thus, for each element {\it j} (containing a number of CVs) the FEM solution, $T_{\text{FEM}}$, is related to the CV solution, {\it T}, by:
 \begin{equation}
-  \int_{\Omega} N_{i} \left({T_{\mbox{FEM}}} - T\right) \,d V = 0, \quad \forall i\in \{1,2,...,{\mathcal N}\},
+  \int_{\Omega} N_{j} \left({T_{\text{FEM}}} - T\right) \,d V = 0, \quad \forall j\in \{1,2,...,{\mathcal N}\},
 \end{equation}
-where $N_{i}$ is the FE basis function associated with the {\it i}-th degree of freedom. The FEM representation of \textit{T} is given by:
+where $N_{j}$ is the FE basis function associated with the {\it j}-th degree of freedom. The FEM representation of {\it T} is given by:
 \begin{equation}
-  T_{\mbox{FEM}} = \sum\limits_{j=1}^{\mathcal{N}} N_{j} {T_{\mbox{FEM}}}_{j}.
+  T_{\text{FEM}} = \sum\limits_{j=1}^{\mathcal{N}} N_{j} {T_{\text{FEM}}}_{j}.
 \end{equation}
@@
 \begin{equation}
-  \mathbf{B} \underline{\mathbf{T}}_{\mbox{FEM}} = \mathbf{Q} \underline{\mathbf{T}},
+  \mathbf{B} \underline{\mathbf{T}}_{\text{FEM}} = \mathbf{Q} \underline{\mathbf{T}},
 \end{equation} 
@@
 \begin{displaymath}
-\underline{\mathbf{T}}_{\mbox{FEM}} = \left({T_{\mbox{FEM}}}_{1}, \ldots, {T_{\mbox{FEM}}}_{\mathcal{N}} \right)^{T} \text{ and } \underline{\mathbf{T}} =\left(T_{1}, T_{2}, \ldots, T_\mathcal{M} \right)^{T},
+\underline{\mathbf{T}}_{\text{FEM}} = \left({T_{\text{FEM}}}_{1}, \ldots, {T_{\text{FEM}}}_{\mathcal{N}} \right)^{T} \text{ and } \underline{\mathbf{T}} =\left(T_{1}, T_{2}, \ldots, T_\mathcal{M} \right)^{T},
 \end{displaymath}
@@
 %%%            %%%
-%%% SECTION %%%
+%%% SUBSECTION %%%
 %%%            %%%
 \subsection{Time-Discretisation Scheme} \label{time_discretisation}
-There are numerous time-discretisation methods to deal with parabolic system of equations, such as backward-Euler, forward-Euler, Crank-Nicolson and Runge-Kutta methods \citep{weng_2012}.
-An adaptive time-stepping method based on the Crank-Nicolson scheme is chosen, because it is unconditionally stable and second-order accurate.
-
+The $\theta$-method, as described by \citet{gomes_book_2012}, was used to discretise the transport equation in the time-domain.
+The method is unconditionally stable and second-order accurate.
 Using Eqns.~\ref{CV1} and \ref{transpeqn_green}, the time stepping for Eqn.~\ref{traneq} takes the form:
@@
 For each time step a value of $\theta$ between 0.5 (for Crank-Nicolson) and 1.0 (for backward-Euler) is calculated at each CV face based on the satisfaction of a TVD criterion \citep{szabo_2009,kuzmin_2004}.
-Assuming $L_{i}$ is the volume of the  $i^{th}$-CV then the following expression for $\theta_f^{n+\frac{1}{2}}$ of face \textit{f} is obtained \citep[see][]{gomes_book_2012},
+Assuming $L_{i}$ is the volume of the  $i^{th}$-CV then the following expression for $\theta_f^{n+\frac{1}{2}}$ of face \textit{f} is obtained,
 \begin{equation}
@@
 where \textit{c} and \textit{d} refer to the two CV's that are adjacent to face \textit{f}.
-This method can be extended \citep[as demonstrated in][]{gomes_2008,pain_2001b} to deal with composite time-dependent terms such as $\frac{\partial \left(\rho T\right)}{\partial t}$ by replacing $T_j^n$ and $T_j^{n+1}$ by $T_{j}^{n} \rho_{j}^{n}$ and $T_{j}^{n+1} \rho_j^{n+1}$, respectively, for $j = \{c,d\}$.
+This method can be extended \citep[as demonstrated by][]{gomes_2008,pain_2001b} to deal with composite time-dependent terms such as $\displaystyle\frac{\partial \left(\rho T\right)}{\partial t}$ by replacing $T_j^n$ and $T_j^{n+1}$ by $T_{j}^{n} \rho_{j}^{n}$ and $T_{j}^{n+1} \rho_j^{n+1}$, respectively, for $j = \{c,d\}$.
 
 %%%            %%%
-%%% SECTION %%%
+%%% SUBSECTION %%%
 %%%            %%%
-\section{Saturation and Global Mass Conservative Equations}\label{Section:Saturation_Global}
-This section outlines the discrete saturation equations and derives the global mass balance equations from the saturation equations assuming incompressibility.
-The saturation equation \citep{chavent_1986} can be written as follows,
+\subsection{Saturation and Global Mass Conservative Equations}\label{Section:Saturation_Global}
+Here, the formulation described in Section~\ref{Section:CVFEMDiscretisation} is extended to discretise the saturation conservation equations and to help deriving the global mass balance equations.
+In this work, the fluids are assumed incompressible.
+The saturation equation can be written as,
 \begin{equation}
@@
 \end{equation}
-where $\phi$ represents the porosity of the rock matrix.
-It can be discretised in space by testing with CV basis functions $M_{i}$ and with the $\theta$-method in time, \jrp{the cross reference doesn't explicitly used the term theta method.} as described in Section~\ref{time_discretisation}:
+where $\phi$ represents the porosity of the rock matrix. Equation~\ref{saturation_equation} can be discretised in space by testing with CV basis functions $M_{i}$ and with the $\theta$-method in time:
 \begin{eqnarray}
-  \int_{\Omega} M_{i} \displaystyle\frac{\phi \left({S_{\alpha}}_{i}^{n+1}-{S_{\alpha}}_{i}^{n}\right)}{\Delta t} dV + \nonumber \\ 
+  \int_{\Omega} M_{i} \displaystyle\frac{\phi \left({S_{\alpha i}^{n+1}}-{S_{\alpha i}^{n}}\right)}{\Delta t} dV + \nonumber \\ 
   \oint_{\Gamma_{CV_{i}}} \left[\theta^{n+\frac{1}{2}} {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n+1} S_{\alpha}^{n+1} +  \left(1-\theta^{n+\frac{1}{2}}\right) {\mathbf n} \cdot {\mathbf u}_{\alpha}^{n} S_{\alpha}^{n} \right]d\Gamma =  \int_{\Omega} M_{i} {s_{cty,\alpha}^{n+\theta}} dV.
@@
 \begin{eqnarray}
-  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} \left\lbrace \int_{\Omega} M_{i} \displaystyle\frac{\phi\left({S_{\alpha}}_{i}^{n+1}-{S_{\alpha}}_{i}^{n}\right) } {\Delta t} dV + \right. \nonumber \\ 
+  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} \left\lbrace \int_{\Omega} M_{i} \displaystyle\frac{\phi\left({S_{\alpha i}^{n+1}}-{S_{\alpha i}^{n}}\right) } {\Delta t} dV + \right. \nonumber \\ 
   \left.
@@
 \end{eqnarray}
-in which $\theta^{n+\frac{1}{2}}$ is obtained as described in Section~\ref{time_discretisation} with $S_\alpha$ replacing $T$. Assuming the natural incompressible mass conservation constraint,
+in which $\theta^{n+\frac{1}{2}}$ is obtained (as described in Section~\ref{time_discretisation}) with $S_\alpha$ replacing T. Assuming the natural incompressible mass conservation constraint,
 \begin{equation}
-  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}}_{i}^{n} = 1, \quad \forall n,
+  %\sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}}_{i}^{n} = 1, \quad \forall n,
+  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}^{n}}_{i} = 1, \quad \forall n,
 \end{equation}
@@
 \begin{equation}
-  {\mathbf B}^T \underline{\bf v}^{n+1} = \underline{\bf s}_{p},
+  {\mathbf B}^T \underline{\bf v}^{n+1} = \underline{\bf s}_{p}.
   \label{glob-cty-matrix}
 \end{equation}
-where it remains to relate the phase force density $\bm{v}_\alpha$ to the phase velocity on the control volume facets.
+Relationship between phase force density $\bm{v}_\alpha$ and  phase velocity on the control volume facets are addressed in the next sections.
 

### 2015-01-09 Papers/Prototype_1_Method/article.tex
updates

@@
 \usepackage{todonotes}
-
 \newcommand{\jrp}[1]{\todo[color=blue!30, size=\small]{JRP: #1}}
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG: #1}}}
 
@@
 
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG: #1}}}
 %\journal{Computer Methods in Applied Mechanics and Engineering}
 \journal{Comput Meth Appl Mech Eng}
+\newcommand{\frc}{\displaystyle\frac}
 
@@
 \end{equation}
-Relationship between phase force density $\bm{v}_\alpha$ and  phase velocity on the control volume facets are addressed in the next sections.
+%Relationship between phase force density $\bm{v}_\alpha$ and phase velocity on the control volume facets is addressed in the next section.
 
 %%%            %%%
-%%% SECTION %%%
+%%% SUBSECTION %%%
 %%%            %%%
-\section{Upwind Velocity and Relative Permeability} \label{opt-up} 
-We still need to determine the velocity to be used at the interface between CV's in the saturation (Eqn.~\ref{detail-sat-eqn-k}) and global continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations.
+\subsection{Upwind Velocity and Relative Permeability} \label{opt-up} 
+We still need to determine the velocity to be used at the interface between CV's in the saturation conservation (Eqn.~\ref{detail-sat-eqn-k}) and global continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations.
 On the CV faces, there is no information about the flow direction as the velocity is discontinuous at the CV boundaries.
-The discontinuities occur between (a) elements for the discontinuous formulation and (b) control volumes within each FE.
-An average velocity is defined by:
+The discontinuities occur between (a) elements in the discontinuous formulation and (b) control volumes within each FE.
+An average velocity is defined as,
 \begin{equation}
@@
 \end{equation} 
-Then, the interface velocities at either side of the interface can be obtained from,
+The interface velocities at either side of the interface can be obtained from,
 \begin{equation}
-  {\tilde{\bf u}}_{\alpha i}=   \underline{\underline\sigma_\alpha}_i^{-1}  {{\bf v}}_\alpha  , \;\;\;\;  {\tilde{\bf u}}_{\alpha j} =  \underline{\underline\sigma_\alpha}_j^{-1}  {{\bf v}}_\alpha    .
+  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha k}^{-1}{{\bf v}}_{\alpha}, \;\;\;\; k=\{i,j\}. 
   \label{two-vels}
 \end{equation} 
-Notice that these velocities point in the same direction and are only different in magnitude \jrp{What constraints on the permeability tensor?}.
-Thus, using them to define an upwind direction is not ambiguous.
-The vector:
+Notice that these velocities point to the same direction and are only different in magnitude therefore, using them to define an upwind direction is not ambiguous. The vector ${\bf a}_{\alpha}$,
 \begin{equation}
-  {\bf a}_\alpha= \displaystyle\frac{1}{2} \left[ \frac{  \underline{\underline \sigma_\alpha}_i^{-1} {{\bf v}_\alpha}_i +  \underline{\underline \sigma_\alpha}_j^{-1} {{\bf v}_\alpha}_j }  { {\sigma_\alpha}_i (S_\alpha)+{\sigma_\alpha}_j (S_\alpha)} \right],
+  {\bf a}_{\alpha} = \frc{1}{2} \left[\frc{ \underline{\underline{\sigma}}_{\alpha i}^{-1}{{\bf v}}_{\alpha i} +  \underline{\underline{\sigma}}_{\alpha j}^{-1}{{\bf v}}_{\alpha j} } { \underline{\underline{\sigma}}_{\alpha i} + \underline{\underline{\sigma}}_{\alpha j} }\right],
 \end{equation} 
-\jrp{need to fix for tensor} is used to determine if information is leaving or entering a CV.
-
+is used to determine if information is leaving or entering a CV.
 The two velocity values in Eqn.~\ref{two-vels} provide the two extremes within which the final interface velocity is obtained.
@@
 However, this upwind method will result in dissipative solutions.
-Out of numerous heuristics for obtaining this interface velocity ${\tilde{\bf u}}_\alpha$, we choose a method based on a limited high-order saturation $\tilde S_\alpha$, obtained using a DGFEM upwind approximation.
+Out of numerous heuristics for obtaining this interface velocity ${\tilde{\bf u}}_\alpha$, a method based on a limited high-order saturation, $\tilde S_\alpha$ (obtained from DGFEM upwind approximation), was chosen.
 The sign of ${\bf n}\cdot {\bf a}_\alpha$ is used to determine the upwind direction.
-From this high-order flux limited saturation, we can obtain $\tilde{\sigma}_{\alpha} = \sigma_{\alpha}\left(\tilde{S}_{\alpha}\right)$.
-Knowing $\tilde S_\alpha$ we can estimate the corresponding interface value of $\sigma_\alpha$, that is $\tilde\sigma_\alpha,$ from the second-order Taylor series.
+From this high-order flux limited saturation, $\tilde{\sigma}_{\alpha} = \sigma_{\alpha}\left(\tilde{S}_{\alpha}\right)$ can be obtained.
+Knowing $\tilde S_\alpha$ the corresponding interface value of $\sigma_\alpha$ can be estimated, $\tilde\sigma_\alpha$, from the second-order Taylor series.
 For ${\bf n}\cdot {\bf a}_\alpha>0$ (CV $i$ outgoing information):
 \begin{equation}
-  \tilde\sigma_\alpha = {\sigma_\alpha}_i + \left(\tilde S_\alpha - {S_\alpha}_i\right) \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i + \frac{1}{2}  \left(\tilde S_\alpha - {S_\alpha}_i\right)^2 \left[ \frac{\left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i - \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j } {{S_\alpha}_i -  {S_\alpha}_j} \right]
+  \underline{\underline{\tilde{\sigma}}}_{\alpha} = \underline{\underline{\sigma}}_{\alpha i} + \left(\tilde{S}_{\alpha}-S_{\alpha i}\right) \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{i} + \frc{1}{2}\left(\tilde{S}_{\alpha}-S_{\alpha i}\right)^{2} \left[ \frc{ \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{i} - \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{j} } { \left(S_{\alpha i}-S_{\alpha j}\right) } \right],
   \label{sigma-out}
@@
 \begin{equation}
-  \tilde\sigma_\alpha = {\sigma_\alpha}_j + \left(\tilde S_\alpha - {S_\alpha}_j\right) \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j +\frac{1}{2} \left(\tilde S_\alpha - {S_\alpha}_j\right)^2 \left[ \frac{\left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_i - \left(\frac{\partial\sigma_\alpha}{\partial S_\alpha}\right)_j } {{S_\alpha}_i - {S_\alpha}_j} \right]
+  \underline{\underline{\tilde{\sigma}}}_{\alpha} = \underline{\underline{\sigma}}_{\alpha j} + \left(\tilde{S}_{\alpha}-S_{\alpha j}\right) \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{j} + \frc{1}{2}\left(\tilde{S}_{\alpha}-S_{\alpha j}\right)^{2} \left[ \frc{ \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{i} - \left(\frc{\partial \underline{\underline{\sigma}}_{\alpha}}{\partial S_{\alpha}}\right)_{j} } { \left(S_{\alpha i}-S_{\alpha j}\right) } \right].
   \label{sigma-in}
 \end{equation}
-where $\tilde{\sigma_{\alpha}}$ is also adjusted to ensure that it lies between ${\sigma_\alpha}_i$ and ${\sigma_\alpha}_j$.
-Since $\tilde{\sigma_{\alpha}}$ is often a tensor on the boundaries of the CV's, we only require its normal component -- ${\bf n}^T\tilde\sigma_\alpha {\bf n}$, to be subject to this boundedness constraint.
-It should be noted that for high-order elements it may be advantageous to use $\tilde\sigma_\alpha = \sigma_\alpha \left(\tilde S_\alpha\right)$ directly so as to maintain the high-order convergence.
-In addition, for robustness, one can choose to only add the second-order terms in Eqs.~\ref{sigma-out} and \ref{sigma-in} if the resulting $\tilde{\sigma_{\alpha}}$ is closer to the upwind value of $\sigma_\alpha$.
+$\underline{\underline{\tilde{\sigma}}}_{\alpha}$ is adjusted to ensure that it lies between $\underline{\underline{\sigma}}_{\alpha i}$ and $\underline{\underline{\sigma}}_{\alpha j}$.
+Since $\underline{\underline{\tilde{\sigma}}}_{\alpha}$ is often a tensor on the boundaries of the CV's, we only require its normal component, ${\bf n}^{T}\underline{\underline{\tilde{\sigma}}}_{\alpha}{\bf n}$, to be subject to this boundedness constraint.
+It should be noted that for high-order elements it may be advantageous to use $\underline{\underline{\tilde{\sigma}}}_{\alpha} = \underline{\underline{\sigma}}_{\alpha}\left(\tilde{S}_{\alpha}\right)$ directly in order to maintain high-order convergence.
+In addition, for robustness, one can choose to only add the second-order terms in Eqs.~\ref{sigma-out} and \ref{sigma-in} if the resulting $\underline{\underline{\tilde{\sigma}}}_{\alpha}$ is closer to the upwind value of $\underline{\underline{\sigma}}_{\alpha}$.
 
@@
 \begin{equation}
-  {\tilde{\bf u}_{\alpha}} = {\tilde{\sigma}_{\alpha}}^{-1} \left[\displaystyle\frac{1}{2} \left(    {{\bf v}_\alpha}_i +  {{\bf v}_\alpha}_j \right)\right],
+  {\tilde{\bf u}_{\alpha}} = \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1} \left[\displaystyle\frac{1}{2} \left(    {{\bf v}_\alpha}_i +  {{\bf v}_\alpha}_j \right)\right],
   \label{mean_int_vel}  
 \end{equation} 
-which is, in addition, bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{ki}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
+which is bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
 The result of this is also bounded between the velocities ${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf n}$.
-Notice that inside an element without discontinuous sources (i.e., in Eqn.~\ref{force-bal}) ${\tilde{\bf u}_{\alpha i}}={{\bf u}_{\alpha i}}$, ${\tilde{\bf u}_{kj}}={{\bf u}_{\alpha j}}$ and ${\sigma_\alpha}_i {{\bf u}_\alpha}_i = {\sigma_\alpha}_j {{\bf u}_\alpha}_j$ and Eqn.~\ref{mean_int_vel} simply takes on the upwind value of velocity if we choose the upwind value of $\sigma_\alpha$ for interface value $\tilde\sigma_\alpha$.
+Notice that inside an element without discontinuous sources,
+\begin{displaymath}
+\tilde{\bf u}_{\alpha i} = {\bf u}_{\alpha i}, \;\; \tilde{\bf u}_{\alpha j} = {\bf u}_{\alpha j} \;\;\text{and}\;\; \underline{\underline{\sigma}}_{\alpha i} {\bf u}_{\alpha i} = \underline{\underline{\sigma}}_{\alpha j} {\bf u}_{\alpha j},
+\end{displaymath}
+and Eqn.~\ref{mean_int_vel} simply takes on the upwind value of velocity if we choose the upwind value of $\underline{\underline{\sigma}}_{\alpha}$ for interface value $\underline{\underline{\tilde{\sigma}}}_{\alpha}$.
 
@@
 \end{equation}
-%${\tilde{\bf u}_\alpha} ={{\bf u}_\alpha}_i $ for ${\bf n}\cdot {\bf a}_\alpha>0$ and ${\tilde{\bf u}_\alpha} ={{\bf u}_\alpha}_j$ for ${\bf n}\cdot {\bf a}_\alpha<0$.
-In regions of the domain where the saturation has no spacial variation an average of the velocity is obtained in a similar approach to the harmonic averaging procedure, commonly used to obtain interface absolute permeabilities.\jrp{add a reference?}
+In regions of the domain where the saturation has no spacial variation an average of the velocity is obtained in a similar approach to the harmonic averaging procedure, commonly used to obtain interface absolute permeabilities \citep{dake_1998,agelas_2009}.
 
 %%%            %%%
-%%% SECTION %%%
+%%% SUBSECTION %%%
 %%%            %%%
-\section{Determining Velocities across Discontinuous Element Interfaces}
-In order to advect saturations and other scalar variables across elements with discontinuous velocity and pressure we first need to calculate the velocity between these contiguous elements.
+\subsection{Determining Velocities across Discontinuous Element Interfaces}
+In order to advect saturation and other scalar variables across elements with discontinuous velocity and pressure, the velocity between these contiguous elements need to be calculated.
 It is also necessary to obtain the discretised non-symmetric pressure equation which has elliptic-like properties.
-These properties mean it is necessary to propagate information in all directions across the domain.
-Thus, taking the upwind velocity, as commonly done within an element, is not the best strategy.
+These properties mean it is necessary to propagate information in all directions across the domain, therefore taking the upwind velocity, as commonly done within an element, is not the best strategy.
 
 For two neighbouring CV's $i$ and $j$ which have a common FE interface, ${\bf u}_{\alpha}$ can be calculated by using a volume weighting.
-However, the volume {\it V} of the control volume and $\sigma_{\alpha}$ act on the velocity ${\bf u}_{\alpha}$ in a very similar way.
+However, the volume $\mathcal{V}$ of the control volume and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity ${\bf u}_{\alpha}$ in a very similar way.
 Hence, the velocity at the interface can be expressed as,
 \begin{equation} 
-  {\tilde{\bf u}_\alpha} = \frac{ V_j  {{\bf v}_\alpha}_i + V_i  {{\bf v}_\alpha}_j } { V_i {\sigma_\alpha}_i + V_j {\sigma_\alpha}_j }.
+  {\tilde{\bf u}_\alpha} = \frc{ \mathcal{V}_{j} {\bf v}_{\alpha i} + \mathcal{V}_{i} {\bf v}_{\alpha j}} { \mathcal{V}_{i} \underline{\underline{\sigma}}_{\alpha i} + \mathcal{V}_{j} \underline{\underline{\sigma}}_{\alpha j} }.
 \end{equation}
-\jrp{This equation needs to be fixed for tensor permeabilities.}
 
@@
 
-\jrp{ The notation here is rather dense for continuous text, but I'm not really sure how to improve it.}
+Suitable boundary conditions can be guided by the discontinuous formulation above as well as by the upwinding in the continuous formulation.
+In fact, exactly the same boundary condition implementations, as used in the discontinuous formulation, can be applied across the boundaries of the domain and taking information from just outside the domain rather than from the neighbouring elements.
 
-Suitable boundary conditions can be guided by the discontinuous formulations above as well as the upwinding in the continuous formulations.
-In fact, exactly the same boundary condition implementations can be applied as used in the discontinuous formulations but across the boundaries of the domain and taking information from just outside the domain rather than in the neighbouring elements.
+Saturation boundary conditions are relatively straightforward. One typically takes the saturation from just outside the domain (i.e., the saturation boundary condition, ${S_{\alpha, \text{bc}}}$),
+\begin{displaymath}
+\left({\bf n}\cdot {\bf u}_\alpha\right)S_{\alpha,\text{bc}}\;\;\;\;\;\text{ when } {\bf n}\cdot {\bf u}_{\alpha} < 0\;\;\text{(incoming flux)}.
+\end{displaymath}
+If the velocity, ${\bf n}\cdot {{\bf u}_\alpha}_{bc}$, is also specified then this must be part of the incoming flux $\left(\right.$i.e., when ${\bf n}\cdot {\bf u}_{\alpha,\text{bc}} < 0\left.\right)$ and therefore $\left({\bf n}\cdot {{\bf u}_\alpha}_{bc}\right)S_{\alpha,\text{bc}}$.
 
-Saturation boundary conditions are relatively straightforward.
-One typically takes the saturation from just outside the domain (i.e., the saturation boundary condition, ${S_\alpha}_{bc}$) as part of the incoming flux (i.e., when ${\bf n}\cdot {\bf u}_\alpha<0$) for phase $\alpha$: $\left({\bf n}\cdot {\bf u}_\alpha\right){S_\alpha}_{bc}$.
-When in addition the velocity ${\bf n}\cdot {{\bf u}_\alpha}_{bc}$ is specified then this also must be part of the incoming flux $\left(\right.$i.e., when ${\bf n}\cdot {{\bf u}_\alpha}_{bc}<0\left.\right)$: $\left({\bf n}\cdot {{\bf u}_\alpha}_{bc}\right){S_\alpha}_{bc}$.
+\medskip
+Similarly, boundary conditions can be applied using Riemann variables to determine if information is travelling into or out of the domain (although most flow simulation models do not follow this more rigorous approach).
+Specified pressure boundary conditions for outlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ are ${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf u}_\alpha$ nor ${S_\alpha}$ are specified.
 
-Similarly, boundary conditions can be applied using Riemann variables to determine if information is travelling into or out of the domain (although most flow simulation models do not follow this more rigorous approach).
-Specified pressure boundary conditions for outlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ are: ${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf u}_\alpha$ nor ${S_\alpha}$ are specified.
-
-Specified pressure boundary conditions for the inlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ are defined as: ${\bf n}\cdot {{\bf u}_\alpha}_{rel} {S_\alpha}_{bc}$, in which the relative permeability is upwinded and thus taken from outside the domain resulting in a value of ${\underline {\underline \sigma}}_\alpha$ from ${{\underline {\underline \sigma}}_\alpha}_{\text{outside}}$.
-The latter is calculated from the saturation boundary condition value ${S_\alpha}_{bc}$.
-This means that the solution velocity ${{\bf u}_\alpha}$ needs to be adjusted to apply this upwind permeability, i.e.,
+\medskip
+Specified pressure boundary conditions for the inlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ are defined as,
+\begin{displaymath}
+{\bf n}\cdot {\bf u}_{\alpha,\text{rel}} S_{\alpha,\text{bc}},
+\end{displaymath}
+in which the relative permeability, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$, is upwinded and thus taken from outside the domain resulting in a value of $\underline{\underline{\sigma}}_{\alpha}$ from $\underline{\underline{\sigma}}_{\alpha,\text{outside}}$.
+The latter is calculated from the saturation boundary condition value, $S_{\alpha,\text{bc}}$.
+This means that the solution velocity ${{\bf u}_\alpha}$ needs to be adjusted to apply this upwinding permeability, i.e.,
 \begin{equation}
-  {{\bf u}_\alpha}_{rel}= \displaystyle\frac{{{\underline {\underline \sigma}}_\alpha}_\text{inside} } {{{\underline {\underline \sigma}}_\alpha}_\text{outside}}{{\bf u}_\alpha}.
+  {\bf u}_{\alpha,\text{rel}} = \displaystyle\frac{ \underline{\underline{\sigma}}_{\alpha,\text{inside}}} { \underline{\underline{\sigma}}_{\alpha,\text{outside}}} {\bf u}_{\alpha}.
 \end{equation}
-Another approach for upwinding the relative permeability on incoming specified pressure boundaries is to simply adjust the value of ${{\underline {\underline \sigma}}_\alpha}_\text{inside}$ just inside the domain by setting it to the value just outside the domain,
+Another approach for upwinding the relative permeability on incoming specified pressure boundaries is to adjust the value of $\underline{\underline{\sigma}}_{\alpha,\text{inside}}$,
 \begin{displaymath}
-{{\underline {\underline \sigma}}_\alpha}_\text{inside}={{\underline {\underline \sigma}}_\alpha}_\text{outside},
+\underline{\underline{\sigma}}_{\alpha,\text{inside}} = \underline{\underline{\sigma}}_{\alpha,\text{outside}},
 \end{displaymath}
-and the flux condition then becomes
+and the flux condition becomes
 \begin{displaymath}
-{\bf n}\cdot{{\bf u}_\alpha} {S_\alpha}_{bc}.
+{\bf n}\cdot{\bf u}_{\alpha} S_{\alpha,\text{bc}}.
 \end{displaymath}

### 2015-01-09 Papers/Prototype_1_Method/article.tex
updates

@@
 The computationally demanding effort to solve the pressure matrix equation arising from the fully discontinuous FEM formulation is achieved using a multigrid-like approach.
-In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating from the discontinuous system a continuous one by collapsing the pressure nodes.
-As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the present approximation.
+In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating, from the discontinuous system, a continuous system by collapsing the pressure nodes.
+As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the current approximation.
 

### 2015-01-16 Papers/SPE_OffshoreEurope/MainPaper.tex
Changed_Paper_Title
Rewrote_Abstract_according_to_Objective_Method_Result_Novelty_format

--- 2015-01-08 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
@@
 
-\title{Upscaling with the Overlapping Control Volume Finite Element Method Multiphase Porous Media Flow Modelling Technique}
+\title{Reservoir Simulation using a Deterministic Heterogeneity Permeability Data}
 
@@
 \begin{abstract}
-%% Comment:
-\JG{For non-scientific conferences is always better to keep the title shorter and/or more $\lq$direct'/punchy and/or with key terms that are more familiar to the audience.
-A few key-words that you may consider for the title: upscaling (although we are not doing upscaling at the moment), benchmark, heterogeneity} \JG{As a rule of thumb, always start an {\it Abstract} with the motivation for the work (thus why is this relevant?)}
-The 10$^{\text{th}}$ SPE Comparative Solution Project on upscaling involved two problems.
-The first problem which involves upscaling and pseudoization methods for an easily computed 2D gas-injection problem\JG{too many $\lq$problem' in  a single sentence ...}, is used in this paper to discuss another approach to upscaling.
+This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
+The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
+Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.
+
 The approach removes the upscaling computation performed prior to the main flow calculation and instead makes use of an effective flux calculation within the computation \red{(what do you mean?)}.\JG{1.

### 2015-01-16 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Changed_Paper_Title
Rewrote_Abstract_according_to_Objective_Method_Result_Novelty_format

@@
 \usepackage{todonotes,amsmath,color}
+\usepackage[normalem]{ulem}
 \newcommand{\JG}[1]{\todo[color=blue!30, size=\small]{JG: #1}}
@@
 \begin{abstract}
-%% Comment:
-\JG{For non-scientific conferences is always better to keep the title shorter and/or more $\lq$direct'/punchy and/or with key terms that are more familiar to the audience.
-A few key-words that you may consider for the title: upscaling (although we are not doing upscaling at the moment), benchmark, heterogeneity} \JG{As a rule of thumb, always start an {\it Abstract} with the motivation for the work (thus why is this relevant?)}
-The 10$^{\text{th}}$ SPE Comparative Solution Project on upscaling involved two problems.
-The first problem which involves upscaling and pseudoization methods for an easily computed 2D gas-injection problem\JG{too many $\lq$problem' in  a single sentence ...}, is used in this paper to discuss another approach to upscaling.
-The approach removes the upscaling computation performed prior to the main flow calculation and instead makes use of an effective flux calculation within the computation \red{(what do you mean?)}.\JG{1.
-too many $\lq$computation' in the same sentence?
-2.
-and what is the second problem?}
+This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
+The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
+Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.
 
-In the overlapping control volume finite element method (OCVFEM) formulation, static properties are represented in unstructured tethrahedral mesh grid in which \red{{\it describe in a few words the approach used ...}} on which the static properties are represented.
-The underlying mass conservation equations are solved in control volume space while high-order fluxes across control volume boundaries are obtained from FEM interpolation.
-A P0DG meshing scheme is used in this simulation therefore permeability, porosity, pressure and density are represented as discontinous data points in the centre of the tethrahedral elements while velocity is represented as continuous data points at the edges of the tethrahedral elements \red{(this sentence need to be modified according to your simulation set up)}.
-\red{(try to summarise these sentences as the main focus of this abstract is to describe the main objective of the paper (work) and how (in a few words/sentences) you are going to tackle the problems ahead)}
+The overlapping control volume finite element method (OCVFEM) formulation, makes use of triangular and tetrahedral finite element pairs to represent the model properties.
+A P0DG meshing scheme is used for permeability in this simulation therefore the nodal data point for permeability are defined as discontinous data points at the centre of each tethrahedral element.
+The permeability data for the deterministic heterogeneity is spatially assigned within the simulation domain.
+And using the deterministic data, 3D interpolation is performed to determine the nodal data for the P0DG meshing scheme.
 
-The paper begins with an introduction to heterogeneity and the challenges created by heterogenity.
-It then discusses the benefits of upscaling and the various methods of upscaling.
-It also discusses the P0DG meshing scheme implementation of the OCVFEM and also briefly introduces higher order meshing schemes.
-Finally, it presents the OCVFEM simulation results for the first problem of the 10th SPE Comparative Solution Project and compares it to the results obtained from the original participants of the project.
+\red{Yet to obtain any information on the simulation}\\
+\red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}
+
+\sout{Currently available reservoir simulators require a homogeneous data input for a property such as permeability.
+Hence, upscaling is performed to determine a suitable equivalent value to be used in the simulation.} This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain.
+This has two advantages.
+First, it removes the need for a computation for upscaling.
+Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.
+
 In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM and higher order meshing schemes would be used.
-The paper would also make use of stochastic methods for data representation.\JG{You do not need the summary of the work/sections in the {\it Abstract}, just in the {\it Introduction} section.} \red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}
+The paper would also make use of stochastic methods for data representation.
 \end{abstract}

### 2015-01-16 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
updating

@@
 \begin{abstract}
+discrete or deterministic?
 This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.

### 2015-01-18 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Update in the main tex file. A few notes for Tunde's initial draft.

--- 2015-01-16 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
@@
 
-\title{Reservoir Simulation using a Deterministic Heterogeneity Permeability Data}
+\title{Reservoir Simulation using a Deterministic Heterogeneity Permeability Data \red{(heterogeneity permeability?)}}
 
@@
 \begin{abstract}
-This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
+\JG{discrete or deterministic? I guess some of the entries you may meant discrete instead of deterministic.}
+\red{What is the motivation for the work? What is the novelty you are bringing.}
+This paper demonstrates\JG{Usually, a paper reports or describes not demonstrates.} that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
 The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
 Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.
+\JG{Think about the objetive(s) of the paper (not of your whole PhD project).
+First, list it/them out using the keywords that better represent the work you are planning.
+Then start writing 1-3 cross-linked sentences using these keywords.}
 
@@
 And using the deterministic data, 3D interpolation is performed to determine the nodal data for the P0DG meshing scheme.
+\red{After stating the objectives, you can briefly explain the methods you are using tp achieve these objectives.
+A few key-words that you should consider having here, CVFEM, element-pairs, heterogeneity/permeability, discontinuous.
+You do not need to explain all details of methods etc, but just make these 2-4 sentences strong and compelling.}
 
@@
 First, it removes the need for a computation for upscaling.
-Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.
+Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.\red{Results, Conclusions.
+As we do not have them yet, you could briefly describe the preliminary results and the aim of validating the methods against the SPE10}.
 
@@
 
+\red{\begin{center}\large{SPE Instructions}\end{center}
+\begin{enumerate}
+  \item Objectives/Scope: Please list the objectives and/or scope of the proposed paper. (25-75 words)
+  \item Methods, Procedures, Process: Briefly explain your overall approach, including your methods, procedures and process. (75-100 words)
+  \item Results, Observations, Conclusions: Please describe the results, observations and conclusions of the proposed paper. (100-200 words)
+  \item Novel/Additive Information: Please explain how this paper will present novel (new) or additive information to the existing body of literature that can be of benefit to and/or add to the state of knowledge in the petroleum industry.
+(25-75 words)
+\end{enumerate}}
+
 \end{document}

### 2015-01-18 Papers/Prototype_2_Method/article.tex
Adding Paper 2

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either versixon 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later c.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,authoryear,1p,times]{elsarticle}
%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,3p,times]{elsarticle}
%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,5p,times]{elsarticle}
%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

\usepackage{comment}
\usepackage{epstopdf}
\usepackage{bm}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb,amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}

\journal{Computer Methods in Applied Mechanics and Engineering}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Overlapping Control Volume Finite Element Method for Multi-Phase Porous Media Flow Modelling \\
Part II: Applications}

\author[IC]{D. Pavlidis}\corref{cor1}\ead{dimitrios.pavlidis@imperial.ac.uk} \author[UoA]{J.L.M.A. Gomes}  \author[IC]{J.R. Percival} \author[IC]{P. Mostaghimi} \author[IC]{P. Salinas} \author[IC]{Z. Xie} \author[IC]{C.C. Pain} \author[IC]{M. D. Jackson}
\author[IC]{M. Blunt} 
\cortext[cor1]{Corresponding author.}

\address[IC]{Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK}
\address[UoA]{Environmental $\&$ Industrial Fluids Mechanics Group, School of Engineering, University of Aberdeen, UK}

\begin{abstract} 
This paper is the second part of a two-part paper on a novel finite
element method FEM-based formulation for simulating multi-phase flows
through porous media. In the first paper, the formulation, based upon
the overlapping control volume finite element method, was developed
and, simple validation test-cases were presented. In this second
paper, the OCVFEM formulation is applied to a set of multi-phase
porous media flows test-cases to assess the performance and numerical
accuracy of continuous and discontinuous (between elements) element
pairs.  The test cases include structured and unstructured (triangular
/ tetrahedral) meshes, as well as heterogeneous problems with large
permeability ratios. Numerical solutions are in good agreement with
(semi-)analytically obtained data.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Multi-phase porous media flow \sep overlapping control volume finite element method. 
\end{keyword}

\end{frontmatter}

%\tableofcontents
% \linenumbers
%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\section{Introduction}

This is the second part of a two part paper developing and applying
novel computational methods for multi-phase flow in porous media. The
new overlapping control volume finite element method was introduced in
the first part of this paper \citep{gomes_2013}.

This paper focuses on exploring, by numerical simulations of
multi-phase flow in porous media, the fidelity of the results yielded
by the continuous pressure (\PN[n]{n+1}) and discontinuous pressure
(P$_n$DG-P$_n$DG and P$_{n+1}$DG-P$_n$DG) families of finite element
(FE) types introduced in the first paper. By presenting numerical
experiments in 1-, 2- and 3-D, we shall study the accuracy, reliability
and convergence rates yielded from the proposed FE
families for modelling multi-phase displacements in porous media. In this
way, quadratic and linear elements are tested for different
geometries, meshes and permeability fields. The methods show in all
cases good behaviour and a veracious representation of the fluid flow.

The remainder of this paper is organised as follows. A brief
description of the model is given in
Section~\ref{Section:SummaryPaper1} followed by the model validation
against analytical solutions of the classical Buckley-Levrett
problem. In Section~\ref{res2}, water-flood problems (i.e., immiscible
fluids displacement) are simulated in 2-D to assess the flow
behaviour in heterogeneous porous media. The impact of
large permeability ratios (i.e., highly heterogeneous porous matrix)
in the model is investigated in Sections~\ref{res3}, \ref{res4}
and~\ref{res5}. Additionally, in Section~\ref{res4} the model
performance when elements are skewed due to large domain aspect ratio
is investigated. A brief summary of the results are presented in
Section~\ref{conc} followed by many conclusions drawn from the two
inter-linked papers.

%\setlength\parindent{0pt}

%\section{Model Validation}\label{Section:Results}
\section{Summary of the Model Formulation}\label{Section:SummaryPaper1}
The extended Darcy's law and phase saturation equations for $N_{p}$
immiscible fluid phases can be expressed as:
\begin{equation}
  \underline{\underline{\sigma}}_{\alpha} \mathbf{u}_{\alpha} :=
  S_{\alpha}\left(\displaystyle\frac{\mathbf{K}
    \mathcal{K}_{r_\alpha}}{\mu_{\alpha}}\right)^{-1}\mathbf{u}_{\alpha}=
  -\nabla p + \mathbf{s}_{u_\alpha},
  \label{Darcy}
\end{equation}
\begin{equation}\label{Eqn:Saturation}
  \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} + \nabla
  \cdot \left( {\mathbf u}_{\alpha} S_{\alpha}\right) =
  s_{\mbox{cty}_\alpha},
\end{equation}
where $\alpha\in\left[1,N_{p}\right]$ is the phase index, $S_\alpha$,
$\mathcal{K}_{r_\alpha}$ and $\mu_\alpha$ are phase saturation,
relative permeability and viscosity, respectively. The quantity
$\underline{\underline{\sigma}}_{\alpha}$ represents the
transmissibility of the phase. The vector $\mathbf{u_\alpha}$ is the
saturation-weighted Darcy velocity and the vector
$\mathbf{s}_{u_\alpha}$ is a source, containing terms such as gravity
forces and capillary pressure, associated with the force balance. Here
$\mathbf{K}$ is the medium absolute permeability tensor, $\phi$ is the
rock porosity and $p$ is the pressure, assumed independent of
phase. The mass source term $s_{\mbox{cty}_\alpha}$ may for example be
used to model the exchange of saturation between phases.

The overlapping control volume finite element method discretisation
was introduced in part I of this paper \citep{gomes_2013}. Pressure
is represented by finite element basis functions on a given FE mesh
partition, with the absolute permeability tensor assumed element-wise
constant on the same mesh. Saturation is represented by flat functions
on the node-centred CV space dual to the finite element
mesh. Velocities are represented by finite element basis functions
with support on the spaces formed by the intersection between the
saturation CV's and pressure FE's.

The weak form discretised force balance equations for time level $n$
and phase $\alpha$ are thus of the form:
\begin{eqnarray} 
  %\sum\limits_{E}\int_{\Omega_E} { {Q}}_i \left({\underline {\underline \sigma}}_k^{n+1} \cdot  {\mathbf u}^{n+1} + \nabla p^{n+1} -{\mathbf s}_u^{n+1} \right) dV +  \displaystyle\frac{1}{2} \oint_{\Gamma_{E}}  {Q}_i {\mathbf n} \left(p^{n+1} - p_{nab^{n+1}}\right) d\Gamma + \nonumber \\
  \left. \int\limits_{\Omega} { {Q}}_i \left({\underline {\underline \sigma}}_\alpha^{n}  {\mathbf u}^{n}_\alpha + \nabla p^{n} -{\mathbf s}_{u_\alpha}^{n} \right) dV \right. +  \oint_{\Gamma_{E}}  {Q}_i {\mathbf n} \left(p^{n} - \tilde{p}^{n}\right) d\Gamma  \nonumber \\
  + \oint_{\Gamma_{\Omega p}} { Q}_i {\mathbf n} \left(p^{n} - p_{bc}^{n}\right) d\Gamma &=& \bm{0},
  \label{force-semi-disc} 
\end{eqnarray} 
where the finite element pressure and velocity fields are given by:
\begin{displaymath}
p^{n}:=p(\bm{r},t)=\sum\limits_{j=1}^{\mathcal{N}_p} P_{j}(\bm{r}) p_{j}^{n} \;\;\text{  and  }\;\; {\bf u}_\alpha^{n}:=\bm{u} (\bm{r},t) =\sum\limits_{j=1}^{\mathcal{N}_u} Q_{j}(\bm{r}){\bf u}_{\alpha,j}^{n},
\end{displaymath} 
in which $\bf {n}$ is the normal to the element, $\mathcal{N}_{p}$ and
$\mathcal{N}_{u}$ are the number of degrees of freedom for the FE
pressure and velocity representations, respectively. Here $\Omega$
is the volume domain with $\Omega_E$ the subspace associated with
velocity element $E$, $\Gamma_{E}$ is the interior surface boundary of
the element $E$ and $\Gamma_{\Omega p}$ is the boundary of the domain
on which pressure is set weakly to $p_{bc}$. The inter-element
pressure, defined by:
\[\tilde{p}=\lim_{\delta\rightarrow 0}(p(\bm{r}+\delta \mathbf{n})+p(\bm{r}-\delta \mathbf{n}))/2\] is the average of the finite element pressures on either side of the boundary of element $E$.

The saturation equations (Eqn.~\ref{Eqn:Saturation}) are discretised
in space by testing them with CV basis functions and in
time with the $\theta$-method, in which $\theta=0.5$ is used as much
as possible as discussed in part I of this paper. The resulting
equations for time step size $\Delta t$ and phase $\alpha$ are given
by:
\begin{eqnarray}
  \displaystyle \int_{\Omega} M_{i}
  \left(\frac{S_{\alpha,i}^{n+1}-S_{\alpha,i}^{n}}{\Delta t}\right) dV +  \nonumber \\
  \displaystyle \oint_{ {\Gamma_{CV}}_{i}} \left ( \theta \mathbf{n}
  \cdot \mathbf{u}_{\alpha}^{n+1} S_{\alpha}^{n+1} + (1-\theta)
  \mathbf{n} \cdot \mathbf{u}_{\alpha}^{n} S_{\alpha}^{n} \right)
  d\Gamma -\displaystyle \int_{\Omega} M_{i}
  s_{cty,\alpha}^{n+\theta} dV &=& 0,
  \label{detail-global-cty}
\end{eqnarray}
where $S^{n}_{\alpha,j}:=S(\bm{r},t)=
\sum_{j=1}^{\mathcal{N}_p} M_j(\bm{r}) S^n_{\alpha,j}$. The system is
closed by the conservation constraint, $\sum_\alpha S_\alpha=1$.  A
set of coupled equations for pressure and velocity are obtained from
the overlapping CVFEM-based discretised Darcy equations
(Eqn.~\ref{force-semi-disc}) and by the sum, over all phases, of the CV-based
saturation equations (Eqn.~\ref{detail-global-cty}).

%At time level $n+1$, the coupled multiphase Darcy and global mass conservation are represented, in matricial form, as
%\begin{equation}
%\begin{cases}
%\mathbf{M}_{\sigma} \underline{\bf u}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\
%\mathbf{M}_{p} \underline{\bf p}^{n+1} + \mathbf{B}^{T} \underline{\bf u}^{n+1} = \underline{\bf s}_{p}^{n+1}
%\end{cases}
%\end{equation}

\section{Classical Buckley-Leverett Test-Cases}\label{classical_BL}

In this section, the Buckley-Leverett \citep{buckley1942} 
problem is modelled with phase 1 $\left(S_{l}=1\right)$ being injected 
at a constant velocity $u_{1}=1$ into a porous medium saturated by 
phase 2 $(S_{2}=1,$ $\phi=0.5)$.

Relative permeability in this paper is calculated as a quadratic 
function of saturation with residual saturation of phase 1 and 2  $S_{1}=0.1$ 
and $S_{2}=0.3$ ,respectively.  The endpoint of the relative permeabilities
 of phases 1 and 2 are 0.8 and 0.3, respectively (see Table 1).

The length of the domain is 4
non-dimensional units. On the outlet boundary condition, the pressure
level is set to zero and all remaining boundary conditions are weakly
applied.

Despite the one-dimensional nature of the problem, 2- and 3-D
simulations were performed using structured and unstructured meshes to
evaluate the multi-dimensional capabilities of the model.

 All simulations used the overlapping mixed-DGFEM with \PN[0]{1},
 \PN[1]{2} and/or \PN[2]{3} element-pairs with continuous /
 discontinuous (between elements) formulations with saturation
 collocated at pressure nodes. Although saturation is calculated using
 a CV formulation, a FEM interpolation is used to form the high-order
 fluxes and these are also used for most of the plots. In all 1-D
 simulations, mesh grids were designed with equi-sized elements,
 whilst 2-D meshes were regular, structured and one-element wide with
 unity aspect ratio. The width of the 2-D numerical domain is
 inversely proportional to the number of elements. The time-step size
 varied linearly within 0.125-3.125$\times$10$^{-3}$ seconds range for
 1-D simulations, and a fixed time-step of 1.0$\times$10$^{-4}$ for
 all 2- and 3-D simulations.

%\begin{comment}
%\subsection{Continuous Formulation}
%\paragraph{Upwind Solution} 
%In Fig.~\ref{bl-exact-meth-upwind} the CV solution of the water-phase saturation and equivalent quadratic FEM interpolation are presented (\PN[1]{2}). As it can be seen, the solution converges with increased resolution. Notice that the corners of the CVs are very close to the converged solution. This can be explained as the velocities are upwinded (and also the relative permeabilities), and at these corners the equations reach the balance necessary to match the analytical solution.
%\end{comment}

\paragraph{Convergence Analysis}
Convergence analyses were performed for the 1- and 2-D problems with a
number of (regular) mesh resolution and element pairs. The time-step
size was linearly varied from 1.25$\times$10$^{-4}$ to
3.25$\times$10$^{-3}$ seconds. Figure~\ref{fig:BL_profiles} shows
phase 1 saturation profiles at time $t=0.5$ for mesh grids varying
from 5 to 500 elements, and for different element types -- \PN[0]{1},
\PN[1]{2} and \PN[2]{3} (the geometry symmetry line is used to extract
data from the 2-D simulations).  In general, results are in good
agreement with the analytic solution for all resolutions and
element-pairs however, for coarser meshes, high-order elements-pairs
(\PN[2]{3} for 1-D using 5 elements and \PN[1]{2} for 2-D using 20
elements) perform significantly better and are able to capture the
sharp-front more accurately. As far as the 2-D simulations are
concerned, the coarse mesh simulation performs slightly worse than its
1-D counterpart but for higher resolutions, results are identical.

These conclusions become clearer in Fig.~\ref{fig:BL_converg-rates},
where convergence rates are shown. The L1 and L2 errors are defined
as,
\begin{displaymath}
  \displaystyle\frac{\sum\limits_{i=1}^{N}\left|S_{i}^{\text{simulated}}
    - S_{i}^{\text{analytical}}\right|}{N}\;\;\text{ and }\;\;
  \displaystyle\frac{\sqrt{
      \sum\limits_{i=1}^{N}{\left(S_{i}^{\text{simulated}} -
        S_{i}^{\text{analytical}}\right)^{2}}}}{N},
\end{displaymath}
respectively, where $S_i$ is the saturation of phase 1 at the $i$-th
node point. In addition, convergence rates for simulations performed
with full upwinding scheme are shown.

%\paragraph{Optimal Upwinding} 
%In order to optimise the upwind formulation (Section~\ref{FluxLimitingSection}), we investigated a 80/20$\%$ up/downwinding ratio -- Fig.~\ref{bl-exact-meth-cv-0-8-ele50}, with good agreement with the converged solution. 
%The optimal solution for 50 elements using optimal upwinding, as described in 
%part I, is shown in Fig.~\ref{bl-exact-meth-cv-0-8-ele50}, with a rapid convergence. For these simulations there are no oscillations in the corresponding CV solutions -- the FEM interpolation (using Galerkin projection) of the CV solution, however it does show, as expected, oscillatory behaviour near the shock-fronts.

\subsection{Discontinuous Formulation}
In this section, results for the fully discontinuous formulation are
presented. Discontinuity of the pressure field between elements allows
the use of coarse meshes to represent abrupt changes in the
solution. Figure~\ref{bl-dg-2eles} shows converged CV phase 1
saturation solutions and the corresponding FEM interpolated
solutions. This solution was obtained with upwinding within and
between the elements.  Convergence rates for the test-cases performed
with the fully discontinuous formulation (between elements) are shown
in Fig.~\ref{fig:BL_converg-rates_DG}.

Solutions obtained with upwinding and central difference schemes are
shown in Fig.~\ref{bl-dg-cent-4-10-20} for different resolutions, and
compared against the continuous (converged) solution with good
agreement. In this plot, one can also note the suppression of
oscillations resulting from the upwinding scheme.

In Figure~\ref{bl-dg-4-10-vers-cty}, saturation solutions obtained
using first (P$_{1}$) and second-order (P$_{2}$) functions in the FE
representation of pressure are shown both for continuous and
discontinuous representations. At coarse resolution the discontinuous
solution is more accurate. By comparing P$_{1}$ and P$_{2}$ solutions
in pressure, we demonstrate that near the shock-front there is little
benefit in using high-order discontinuous elements, thus linear
elements perform well compared to quadratic elements.

\subsection{2- and 3-D Simulations}
Following the convergence analysis, a number of numerical experiments
were performed to assess the robustness of the method in fully
unstructured meshes. Phase 1 saturation surface maps (and the
corresponding meshes) for 2- and 3-D simulations at time $t=0.5$ are
shown in Fig.~\ref{fig:maps2d_3d}. The simulations presented in this
section were performed using the \PN[1]{2} element-pair in fully
unstructured mesh-grid.

Saturation profiles for the phase 1 at time $t=0.5$ are shown in
Fig.~\ref{fig:BL_2d_profiles}. Results are not spatially averaged and
the geometry symmetry line is used to extract data for all
simulations. The structured coarse mesh uses $1 \times 19$ layers in
the lateral and flow directions, respectively. The structured medium
mesh uses $3 \times 40$ layers. The solution field converged towards
the analytical solution with the increase of the mesh resolution;
additionally, no substantial improvement was observed when structured
and unstructured \PN[1]{2} mesh were used. However, the use of
unstructured mesh (and potentially higher-order triangle and
tetrahedra elements) is advantageous for flow simulation in complex
geometries as demonstrated by \cite{jackson_2013}.

\section{Immiscible Displacement in Heterogeneous Porous Media}\label{res2}
%\section{A 4-region modified Buckley-Leverett test case}
This test case was designed to demonstrate the numerical robustness of
the method when solving multi-fluid flow problems involving
heterogeneous porous media.  Here, phase 1 is injected in a fully
saturated $\left(S_{2}=1\right)$ 2-D square porous matrix domain of
side length one and uniform porosity $\left(\phi=0.5\right)$ --
Fig. \ref{fig:4reg_BL_schematic}. However, unlike the test-cases in
Section \ref{classical_BL}, the permeability field is not uniform and
four equally sized $\lq$regions' are designed.  Permeability fields in
regions R1 and R4 are 4 times larger than that of regions R2 and R3,
i.e.,
\begin{displaymath}
  \mathbf{K}^{\text(1)}=\mathbf{K}^{\text(4)} =
  4\mathbf{K}^{\text(2)}=4\mathbf{K}^{\text{(3)}}.
\end{displaymath}
Phase 1 is uniformly injected at a velocity of $u_{l}=1$ on the left
boundary to displace the oil in the porous domain. On the outflow
boundary the pressure level is set to zero. Free-slip boundary
conditions are applied on the sides of the domain for the two velocity
fields. All boundary conditions are applied weakly. For relative
permeability calculations $\left(\mathcal{K}_{rk}\right)$, the
irreducible phase 1 and residual phase 2 saturations are set to 0.1
and 0.2, respectively; the endpoint of phase 2 and phase 1 relative
permeabilities are 0.3 and 0.8, while the Corey exponent is assumed as
2.

Two sets of simulations are performed using coarse (402 elements with
2412 nodes) and fine (3714 elements with 22284 nodes) meshes; in the
first set (A) the overlapping mixed DGFEM and the \PN[1]{2}
element-pairs are used, with time-step sizes of 1$\times$10$^{-3}$ and
5$\times$10$^{-4}$ seconds for simulations performed with coarse and
fine meshes, respectively. In the second set of experiments (B)
\PN[2]{2}DG element-pairs are used, with time-step sizes of
5$\times$10$^{-4}$ and 1$\times$10$^{-4}$ seconds for coarse and fine
meshes.

Figure~\ref{fig:4reg_maps} shows the phase 1 saturation profile maps
(at time $t=0.08$ seconds) for all four simulations. The results
yielded by the experiment (A) are depicted in the top left, coarse
mesh, and top right, fine mesh. The results obtained from experiment
(B) located on the bottom left, coarse mesh, and bottom right, fine
mesh. A laboratory experiment with similar setup was performed by
\citet{dawe_2008} to investigate miscible and immiscible displacement
in heterogeneous permeability and wettability cases.

For the immiscible displacement, phase 1 was uniformly injected from
the left-hand side boundary (injection rate of $\sim$1 ml/min in a
domain of 20$\times$10$\times$0.6 cm, glass ballotini beads produced
porosity of 0.4, and permeability ratio of 2.5). Snapshots in
Fig.~\ref{fig:4reg_maps} show the phase 1 flood $\lq$fingering' across
the central regions (R1 $\Rightarrow$ R4) demonstrating the
preferential flow through highly permeable matrix. This is in good
qualitative agreement with the laboratory experiments \citep[see
  Figs. 5 and 6 in][]{dawe_2008}.

Figure~\ref{fig:4reg_plots} shows phase 1 saturation profiles (at time
$t=0.08$ seconds) for all simulations. Comparing the results obtained
by both sets of experiments, a better agreement between the results
yielded by the simulations (B) -- i.e., with \PN[2]{2}DG
element-pairs, can also be observed.

\section{Underground Caisson}\label{res3}
Numerical models may fail when a high permeability gradient is in the
domain by introducing fluid in the low-permeability region not due to
a physical phenomena, but because of numerical dispersion. Thus, the
purpose of this numerical experiment is to test the fluid flow
behaviour across two distinct porous media characterised by high
different permeabilities.

The considered domain is characterised by a low-permeability square
region, with dimensions of 0.5 $\times$ 0.5 unit-area, which is
embedded in a high-permeability region with dimension 1 $\times$
1. The porosity of the whole domain and the permeability of the
high-permeability region are of 0.5 and 10$^{4}$ respectively. The
necessary parameters to obtain the relative permeability
$\left(\mathcal{K}_{rk}\right)$ are the following: the irreducible
phase 1 and residual phase 2 saturations are $S_{wi} = 0.1$ and
$S_{orw}=0.3$, respectively; Corey exponent is $N=2$; the endpoint of
phase 2 and phase 1 relative permeabilities are 0.3 and 0.8.

Regarding the initial state and the boundary conditions of the
experiment, at rest state the domain is fully saturated of phase 2
($S_o=1$). Next, phase 1 is injected with a constant velocity of
$(1,0)$ through the left boundary that can exit only through the right
boundary, which have a constant pressure of zero.

Two sets of numerical experiments are performed, one uses the
\PN[0]{1} element pair and a time step of 5$\times$10$^{-3}$ and the
second experiment the \PN[1]{1}DG element-pair and a time step of
1$\times$10$^{-4}$. Both use the same mesh and the same permeability
map, see Fig.~\ref{fig:square_permeability} (top).

Figure~\ref{fig:square_permeability} displays snapshots of phase 1
saturation profile at $t = 0.15$ and $t = 0.5$ for both
simulations. The simulation performed with \PN[0]{1} elements presents
a small dispersion of phase 1 into the low-permeability region,
whereas the saturation profile in the \PN[1]{1}DG simulation presents
a defined frontier between the low-permeability region and the
high-permeability area. Despite this small difference, both
experiments are in good agreement and provide satisfactory results by
making the fluid to go around the low-permeability region.

\section{High-Permeability Wedge-Shaped Region}\label{res4}
Fractures and cracks in porous media are ubiquitous, however, they are
not easy to model due to they small size. However, cracks may have a
dramatic impact in the behaviour of the flow since they can act as
conducts with a very high permeability. Usually, they are
characterised by thin tip and a high permeability. In order to test
the behaviour of the model presented in this paper, in the present
numerical experiment consists in a wedge-shaped high-permeability
region embedded in a rectangular low-permeability (permeability ratio
of 100) domain. The permeability map is shown in
Fig.~\ref{fig:wedge_permeability}.

Three different experiments were performed, two using the \PN[0]{1}
element-pair and one using the \PN[2]{1}DG element-pair. For the first
experiment using the \PN[0]{1} element-pair, the mesh is composed of
56902 elements, whereas for the second experiment the mesh is composed
of 672 elements. For the \PN[2]{1}DG element-pair example this latter
mesh is considered as well. The non-dimensional rectangular domain is
1 $\times$ 0.1 and the wedge is defined by a high of 0.025 and a slope
of $1/30$. The porosity is uniform and equal to 0.5. The irreducible
water and residual oil saturations are set to zero. Initially, the
porous media is fully saturated with an incompressible fluid
$\left(S_{2}=1\right)$. An immiscible fluid is injected from the left
boundary with a constant pressure of 1 and a saturation of
$S_{1}=1$. On the outflow boundary, the pressure level is set to zero.

Free-slip boundary conditions are applied on the sides of the domain
for the two velocity fields. All remaining boundary conditions are
applied weakly. The irreducible water and residual oil saturation are
both set to zero. The time steps considered are $1\times$10$^{-3}$ and
1$\times$10$^{-5}$ for the \PN[0]{1} and \PN[2]{1}DG element-pair
experiments, respectively.

The saturation pictures displayed in Fig.~\ref{fig:wedge_permeability}
shows the water-phase saturation maps at times $t=0.011$ and
$t=0.014.$ The three test-cases handle this benchmark adequately by
introducing the majority of the input flow through the high
permeability area. However, as in the previous section, the
\PN[0]{1}-based numerical experiment presents a dispersion of the
water-phase in the vicinity of the wedge. Moreover, in the experiment
with fewer elements the effect of the dispersion affects the behaviour
of the fluid dramatically.  It can be seen how the front of the water
phase is delayed compared with the other two experiments. On the other
hand, the \PN[2]{1}DG simulation presents a well-defined boundary of
the water-phase within the wedge.

\section{High-permeability canals}\label{res5}
In this section we deal with a hexahedral domain with two canals
inside that are characterised by a higher permeability. Thus, three
regions with different permeabilities are considered. The domain, the
permeability map and the mesh (composed of 201892 tetrahedra) are
displayed in Fig.~\ref{fig:3d_perm}. For the numerical experiment we
have considered a homogeneous porosity $\phi=0.25$; the irreducible
water and residual oil saturations are set to 0.2 and 0.2.

Initially, the domain is filled with a mixture of movable oil and
immovable water, $S_o=0.8$ and $S_w=0.2$ respectively. Next, water is
injected into the domain through one face at constant pressure. All
boundaries are considered as barriers to flow except one inlet face
and one outlet face with an input pressure of $10^6$ and an outlet
pressure of $0$ respectively. These pressure boundary conditions are
applied weakly.

The simulations were performed using the \PN[0]{1} element-pair. The
results for $7.9$ years and an internal slice in 2-D are depicted in
Fig.~\ref{fig:3d_perm}. As expected the majority of the flow goes
through the high permeability canals.

\section{Conclusions}\label{conc}
This article is the second in a series of papers describing a new
CVFEM formulation for multi-fluid flows in porous media. In the first
paper, we described the new model which is based upon two
computational building blocks: (a) consistent pressure-velocity
formulation in a dual mesh-spaces that led to the new overlapping
control volume, continuous and discontinuous between finite elements
(OCVFEM), and (b) a new family of triangular/tetrahedral element
types. The novel formulation, although generic in nature \citep[thus
  not restricted to porous media applications as demonstrated by][for
  interface tracking problems]{pavlidis_2013b,pavlidis_2013c}, has
demonstrated numerical robustness and accuracy in multi-fluid
subsurface flow problems.

The focus of this paper is two-fold: to demonstrate the model accuracy
in multi-fluids subsurface flows and, to exploit the new formulation
to solve problems involving highly heterogeneous porous media.

The classical Buckley-Leverett problem was used to assess model
convergence, accuracy and performance of the upwind formulation. We
demonstrated that the solutions obtained from the model summarised
here \citep[see][for a full description]{gomes_2013} are in good
agreement with analytical solutions even if a (relatively) coarse
resolution and low-order accuracy element-pairs are used.  Saturation
profiles obtained from the fully discontinuous formulation was
successfully compared against the continuous-based solutions with a
lower grid resolution.

In order to assess the performance of the formulation for
heterogeneities in permeability field across the porous matrix, we
successfully compared the flood behaviour of the numerical solution
against laboratory experiments. Additional tests involving
high-permeability ratios, skewed elements, low- and high-order
element-pairs and unstructured mesh were performed to assess the
accuracy and performance of the upwind velocity / permeability
formulation.

Overall, in these two initial papers we demonstrated the flexibility
and numerical accuracy of the new multi-phase flow model
formulation. The model was successfully validated against: (a)
analytical solutions for advection-diffusion equations and (b)
classical Buckley-Leverett problem. The flow behaviour in subsurface
water-flood conditions was qualitatively validated against lab-scale
experiments. Further validation tests will need to be performed to
rigorously assess the permeability and wettability effects in
gravity-driven subsurface flows.

\ack Dr D. Pavlidis would like to acknowledge the support from the
following research grants: EPSRC ($\lq$Computational Modelling for
Advanced Nuclear Power Plants') and EU/FP7 ($\lq$Thermo-Hydraulics for
Innovative Nuclear Systems' -- THINS). Funding for Dr P. Salinas from
the Qatar Carbonates and Carbon Storage Research Centre (QCCSRC),
provided jointly by Qatar Petroleum, Shell and the Qatar Science and
Technology Park, is gratefully acknowledged. Dr Z. Xie is supported by
EPSRC ($\lq$Multi-Scale Exploration of Multi-phase Physics in Flows' --
MEMPHIS). Part funding for Profs. Jackson and Muggeridge under the
TOTAL Chairs programme at Imperial College is also acknowledged.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv}
\bibliography{references}

\pagebreak
\clearpage

\listoffigures
\pagebreak
\clearpage

\input{article_figure1}
%\input{article_figure2}

\end{document}

%%
%% End of tex file.

### 2015-01-18 Papers/Prototype_2_Method/diagrams/article_P2.tex
Adding Paper 2

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later c.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,authoryear,1p,times]{elsarticle}
%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,3p,times]{elsarticle}
%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,5p,times]{elsarticle}
%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

\usepackage{epstopdf}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb,amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}

\journal{Computer Methods in Applied Mechanics and Engineering}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Overlapping Control Volume Finite Element Method for Porous Media Multiphase Flow Modelling: Part II 
Discontinuous Formulation}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}
\author{D. Pavlidis} 
\author{J.L.M.A. Gomes}\corref{cor1}\ead{j.gomes@imperial.ac.uk}
\author{J. Percavil} 
\author{P. Mostaghimi} 
\author{P. Salinas} \author{C.C. Pain} \author{M. D. Jackson} 
\author{M. Blunt} \author{A. Muggaridge} 
\cortext[cor1]{Corresponding author.}

\address{Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London}

\begin{abstract} 
This is the second part of a two part paper on the overlapping finite 
element method applied to porous media multiphase flows. 
In the first part we delt with the continuous formulation of 
pressure and other associated variabes like saturation between elements. 
I this second part we develop the  overlapping control volume - discontinuous 
Galerkin finite element method (OCV-DGFEM). The formulation is general
and can be applied to simulate problems ranging from multi-component
porous media to dispersed bubbly flows. The method is based on
twofolds, an overlapping CV-DGFEM mixing formulation and the 
P$_{n}$DG-P$_{n}$DG family of FE types, which ensures that
force balance equations are exactly enforced in situations when 
pressure is continuous between elements which is the physically realistic situation. 
This siuation is close to being observed in numerical simulations. 
The underlying mass
balance equations (e.g. volume fraction, saturation, mass fraction of
components, etc.) are solved through a control volume method in which
finite element methods are used to obtain the high order fluxes on the
control volume boundaries which are limited to achieve bounded
mass-based fields (e.g. volume fractions and densities).
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Multiphase Darcy Equations \sep Discontinuous Galerkin method \sep Overlapping mixing formulation

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\tableofcontents
% \linenumbers
%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\section{Introduction}

- why flow in PM: Generic applications 4 porous media: reservoir, contaminants, mineral recovery, nuclear disposal etc

- Current state-of-the-art on flow simulators (academic + industrial) -- potential computational gaps

- LitRev on FEM and CVFEM
- LitRev on DG methods
- LitRev on IMPES and fully implicit methods
- The remaining of the paper bla bla bla ...

%\begin{itemize}
%\item {\bf Couple of paragraphs on multiphase porous media flow -- applications and current methods used in commercial and academic CFD/simulators (check how OpenFoam deals with this class of problems)} ;
%\item {\bf A couple of paragraphs on FEM and CV-FEM (describe the original mansucript from early 80's) and their latest developments};
%\item {\bf A couple of paragraphs on the general methods for multiphase porous media flow -- refers to the developments on GigaPower from Saudi Aramco}
%\item {\bf A paragraph summarising the new approach and overview of the manuscript}
%\end{itemize}

The remainder of this paper is organised as follows. A detailed
description of the model is given in Sec.~\ref{transport_methods}. The
model evaluation is presented in Sec.~\ref{res1}. The model
application is presented in Sec.~\ref{res2}. Finally, some concluding
remarks and future work are given in Sec.~\ref{conc}.

\setlength\parindent{0pt}

%%%                   %%%

\section{Discontinuous Discretisation Scheme for Multiphase Flows}
%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\subsection{Continuous / Discontinuous Finite Element Types} \label{element_types_section}
The family of P$_{n}$DG-P$_{n+1}$ element pair was originally
introduced by \citet{cotter_2009b} \citep[see
  also][]{cotter_2009a,cotter_2011} for geophysical fluid dynamics
(GFD) applications. In particular, the P$_{1}$DG-P$_{2}$ element pair
-- linear discontinuous polynomial FE basis function for velocity
$\left(\text{P}_{1}\text{DG}\right)$ and quadratic polynomial FE basis
function for pressure $\left(\text{P}_{2}\right)$, was developed to
represent the balance of geostrophic pressure and velocity without
introducing spurious pressure modes.

The flux limiting across CV boundaries and non-linear time stepping proceeds 
as described in part I.

{{\bf Add a summary of PnDG-Pn+1 element types.}

\subsection{Upwind velocity/relative permeability} 
\label{opt-up}

It remains to us to dertmine the velocity to be used 
at the interface between control volumes in the 
saturation \ref{detail-sat-eqn-k} and therefore 
the global continuity equations \ref{detail-global-cty}.

The problem is that the on a CV boundary it is unclear 
which side of the control volume boundary the velocity 
should be taken from as there is a discontinuity 
of velocity at the CV boundary. The discontinuity 
is due to the differing relative permeabilities of 
$\sigma_k$'s in each CV and is the only way that 
equation \ref{force-semi-disc} can be strongly enforced. 
This discontinuity happens between elements for the DG 
formulation and as well as between CV's within each element.

One way to dertmine dertmine the value of the velocity 
$({{\mathbf n}\cdot{\mathbf u}_k})_{int}$ 
on the interface between two control volumes 
is to dermine the value of ${\sigma_k}_{int}$ on this boundary 
and then one can obtain the value of 
$({{\mathbf n}\cdot{\mathbf u}_k})_{int}$ that 
corresponds to this from equation \ref{force-semi-disc}.

When $({{\mathbf n}\cdot{\mathbf u}_k})_{int}$ 
is determined one can turn this 
into the proportion of each of the surrounding control 
volumes goes up to make 
$({{\mathbf n}\cdot{\mathbf u}_k})_{int}$. Here we any downwind 
biased averages are simply set to a central difference 
(which may not just be a simple average if we have 
unequal CV sizes or are using the FEM saturation 
on the control volume boundary) and in the case 
when there is an upwind bias then this is accepted. 
This choice is used in order to maintain consistency 
with the characteristics of the BL equations say.

\subsubsection{Upwind fraction $w_k$} 
The upwind parameter $w_k$ is 
determined from the velocity 
$({{\mathbf n}\cdot{\mathbf u}_k})_{int}$ using:

\begin{equation}
w_k= \frac{({{\mathbf n}\cdot{\mathbf u}_k})_{int} - {{\mathbf n}\cdot{\mathbf u}_k}_{right}}{{{\mathbf n}\cdot{\mathbf u}_k}_{left} - {{\mathbf n}\cdot{\mathbf u}_k}_{right}}
\label{w_k} 
\end{equation}
for example:

\begin{equation}
({{\mathbf n}\cdot{\mathbf u}_k})_{int}= \frac{{a_k}_{left} {\sigma_k}_{left} {{\mathbf n}\cdot{\mathbf u}_k}_{left} + {a_k}_{right} {\sigma_k}_{right} {{\mathbf n}\cdot{\mathbf u}_k}_{right}}{\sigma_{int}}
\end{equation}
with ${a_k}_{left}+{a_k}_{right}=1$. 
Notice that internal to an element and with a uniform 
source in each element then

\begin{equation}
{\sigma_k}_{left} {{\mathbf n}\cdot{\mathbf u}_k}_{left} =  {\sigma_k}_{right} {{\mathbf n}\cdot{\mathbf u}_k}_{right}
\label{u_int} 
\end{equation}
or for the case when equal sized CV's then a simple mean may be used:

\begin{equation}
({{\mathbf n}\cdot{\mathbf u}_k})_{int}= \frac{\frac{1}{2} {\sigma_k}_{left}{{\mathbf n}\cdot{\mathbf u}_k}_{left}  
+ \frac{1}{2}{\sigma_k}_{right} {{\mathbf n}\cdot{\mathbf u}_k}_{right}}{{\sigma_k}_{int}}
\end{equation}
Using equation \ref{u_int} then equation \ref{w_k} becomes:

\begin{equation}
w_k=\left( \frac{{\sigma_k}_{left}}{{\sigma_k}_{int}} \right) 
\frac{ {\sigma_k}_{int} - {\sigma_k}_{right}} 
{ {\sigma_k}_{left} - {\sigma_k}_{right}} 
\label{w-eqn}. 
\end{equation}

In equation \ref{w-eqn} we assume the velocity goes from $left$ to $right$ 
control volumes at the surface quadatruee point 
where we are evaluating the velocity. Now limiting 
$w_k$ so we have not down-winding using the 
geometrically centered value of $w_k$ that is ${w_k}_{geom}$ 
(${w_k}_{geom}$ may equal $\frac{1}{2}$ for same sized CV's) 
then

\begin{equation}
\tilde w_k=\beta (max\{ w_k, {w_k}_{geom} \}-{w_k}_{geom}) + {w_k}_{geom}
\end{equation}

The relaxation coefficient $\beta$ allows one to 
exadurate the upwinding. We generally use $\beta=1$ apart 
from with the approach outlined in section 
the section '{Determining interface saturations  }' 
and approach 3 of that section in which case $\beta=2$ is 
used to exadurate the unwinding.

\subsubsection{Determining the interface absorption ${\sigma_k}_{int}$ }

First of all the value of that saturations ${S_k}_{int}$ 
are dertmined on the intefrcae between the CV's. 
From these we can then dertmine the values of ${\sigma_k}_{int}$ 
using the relative permeability equations. However, 
this may be expensive and thus we store 
in each CV the values of $\sigma_k$ as well 
as the derivatives $\frac{\partial \sigma_k}{\partial S_k}$. We then 
can use a first order tailer series to dertmine 
(by projecting the gradient 
to the CV quadrature point. In fact this is done for 
both CV's surrounding the interface to give the 
two values of predicted interface ${\sigma_k}$. 
We then choose the value in a conservative way that 
is associated with the most unwinding.

Thus using a Taylor series about the $left$ CV:

\begin{equation}
{{\sigma_k}_{left}}_{int}
=
\left( 
\frac{\partial \sigma_k}{\partial {S_k}}
\right)_{left}
\left( 
\frac{ 
 {S_k}_{int} - {S_k}_{right} } 
{{\sigma_k}_{left} - {\sigma_k}_{right} }
\right) 
\end{equation}
and about the $right$ CV:

\begin{equation}
{{\sigma_k}_{right}}_{int}
=
\left( \frac{\partial \sigma_k}{\partial {S_k}}
\right)_{right}
\left( 
\frac{ 
 {S_k}_{int} - {S_k}_{left} } 
{{\sigma_k}_{right} - {\sigma_k}_{left} }
\right) 
\end{equation}
then ${{\sigma_k}}_{int}$ is chosen to be the one 
of ${{\sigma_k}_{left}}_{int}$ and ${{\sigma_k}_{right}}_{int}$
that is associated with the most unwinding as described above.

For multi-dimensional problems ${\underline {\underline \sigma}}_k$ as well 
as the gradients $\frac{\partial {\underline {\underline \sigma}}_k}{\partial S_k}$ 
are tensors. We thus project their values 
onto the normal of the CV interface:
\begin{equation}
{\sigma_k}_{left} = {\mathbf n}^T {{\underline {\underline \sigma}}_k}_{left} {\mathbf n},
\end{equation}

\begin{equation}
{\sigma_k}_{right} = {\mathbf n}^T {{\underline {\underline \sigma}}_k}_{right} {\mathbf n}, 
\end{equation}

\begin{equation}
\left({\frac{\partial \sigma_k}{\partial S_k}}\right)_{left} = 
{\mathbf n}^T \left( {\frac{\partial {\underline {\underline \sigma}}_k}{\partial S_k}}\right)_{left} {\mathbf n}, 
\end{equation}

\begin{equation}
\left({\frac{\partial \sigma_k}{\partial S_k}}\right)_{right} = {\mathbf n}^T 
\left( \frac{\partial {\underline {\underline \sigma}}_k}{\partial S_k}\right)_{right} {\mathbf n}, 
\end{equation}

(where ${\mathbf n}$ is the normal to the boundary) 
before determining ${\sigma_k}_{int}$.

\subsubsection{Determining interface saturation  }
The interface saturations ${S_k}_{int}$ that are used to determine 
${\sigma_k}_{int}$ are either determined from:
\par\noindent
1) the finite element interpolation of the CV solution;
\par\noindent
2) the flux limited finite element interpolation of the CV solution; 
\par\noindent
3) a simple linear interpolations of saturation 
e.g.
\begin{equation}
{S_k}_{int} = 
\frac{
{V_{CV}}_{left} {S_k}_{right} +{V_{CV}}_{right} {S_k}_{left}
} { {V_{CV}}_{left} + {V_{CV}}_{right} }  
\end{equation}
where ${V_{CV}}_{left}$, 
and $ {V_{CV}}_{right}$ are the volumes of CV's $left$ and $right$. 
The flux limited value is by far the most dissipative although 
it does produce good results. For simplicity we use 1 above.

In addition,

\begin{equation}
{w_k}_{geom} = \frac{ {S_k}_{int} - {S_k}_{right} }
{ {S_k}_{left} - {S_k}_{right} }
\end{equation}
for follow going from $left$ to $right$ CV's and 
\begin{equation}
{w_k}_{geom} = \frac{ {S_k}_{int} - {S_k}_{left} }
{ {S_k}_{right} - {S_k}_{left} }
\end{equation}
for flow going from $right$ to $left$.

\subsubsection{Flux limiting the interface velocity  }

Since the integral around the control volume is of the form:

\begin{equation}
\int_{CV_i} \rho_k^n S_k^n {\bf n} \cdot{\bf u}_k^n  d\Gamma
\end{equation}
one needs to limit this convolution $\rho_k^n S_k^n {\bf n} \cdot{\bf u}_k^n$. 
The velocity goes with the inverse of the $\sigma_k$ for phase $k$ 
which is dominated by relative permeability. The saturation $S_k$ 
is a reasonably accurate surrogate to this and thus we choose 
the upwind velocity based on the above for accuracy, but 
limited according to the variation of $(S_k^n)^2$ using the NVD 
limiting approach applied to $(S_k^n)^2$ with a limited  
value of  $({S_k^n}_{int})^2$, that is  $({S_k^n}_{int-lim})^2$ on the control volume boundary. Then 
\begin{equation}
{w_k}_{geom} = \frac{ {S_k}_{int-lim} - {S_k}_{right} }
{ {S_k}_{left} - {S_k}_{right} }
\end{equation}
for follow going from $left$ to $right$ CV's and 
\begin{equation}
{w_k}_{geom} = \frac{ {S_k}_{int-lim} - {S_k}_{left} }
{ {S_k}_{right} - {S_k}_{left} }
\end{equation}
for flow going from $right$ to $left$.

%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\subsection{Saturation and Global Mass Conservative Equations}
This section outlines the discrete saturation equations and derives
the global mass balance equations from the saturation equations. The
resulting equation can then be solved simultaneously with
Eqn.~\ref{force-balance-matrix-form}. The classical saturation
equation \citep{chavent_1986},
\begin{equation}
  \phi\displaystyle\frac{\partial \rho_{k} S_{k} }{\partial t}  + \nabla \cdot \left( {\mathbf u}_{k} \rho_{k} S_{k}\right) = s_{cty,k} 
\end{equation}
can be discretised in space by testing with control-volume basis functions, $M_{i}$, and with the $\theta$-method in time, as described in part I. 
%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\subsection{Overlapping-FEM Formulation for Multiphase Darcy Flow} \label{overlapping_method_section}

In the previous sections, we outlined the CV-DGFEM formulation for
multiphase fluid flows in which for uniform ${\underline{\underline
    \sigma}}_{k}$ (within each P$_{1}$DG-P$_{2}$ element,
Fig. \ref{fem_cv_represent_a} b) the balance in 1D extended Darcy flow
equations is strictly enforced. The absorption-like term
${\underline{\underline \sigma}}_{k}$,
\begin{displaymath}
{\underline {\underline \sigma}}_{k} = {\underline {\underline
    \sigma}}_{k}
\left(S_{k}\left(\mathbf{r},t\right),\mu_{k},\mathcal{K}_{rk}\left(S_{k}\right),\mathbf{K}\right)
= S_{k}\left(\lambda_{k}\mathbf{K}\right)^{-1}
\end{displaymath}
and the saturation are computed in CV space whereas the permeability
tensor $\left(\mathbf{K}\right)$ is calculated in FE
space. ${\underline {\underline \sigma}}_{k}$ is piecewise constant
within each element and is obtained via basis functions local to each
CV within each element, e.g., for a quadratic pressure variation there
will be a piecewise linear velocity field with discontinuity between
elements and linear basis and test functions within each control
volume can be used.

Thus in 1D there are $2\times 3$ velocity nodal values associated with
each phase. This approach however can become very computationally
demanding specially in both multi-dimension calculations and complex
geometries.  In order to overcome this major issue, overlapping (or
hybrid) basis functions are introduced assuming that there is a
(non-linear) functional $\left({\underline {\underline
    \sigma}}_k^{-1}\right)$, that correlates velocity within a FE and
the corresponding CV's velocity components. Thus, the discretised form
of Eqn.~\ref{force-semi-disc} within each element and its inner CV's
can be rewritten as,
\begin{equation} 
  \int_{\Omega_E} {\mathbf Q}_i \left({\underline {\underline \sigma}}_k
      {\mathbf u}_k - \nabla p -{\mathbf s}_u \right) dV +
     \frac{1}{2} \oint_{\Gamma_{E}}\gamma^n  {\mathbf Q}_i {\mathbf n} \left(p -
      p_{nab}\right) d\Gamma +
      \oint_{\Gamma_{\Omega}} \gamma^n {\mathbf Q}_i {\mathbf n} \left(p -
      p_{bc}\right) d\Gamma = 0
\label{force-semi-disc} 
\end{equation} 
in which $\Omega_E$ is the volume domain of element $E$, $\Gamma_{E}$ is the 
boundary of element $E$ and $\Gamma_{\Omega}$ is the boundary of the domain. 
Also the pressure $p_{nab}$ is the pressure value on the other side of the element 
boundary neighbouring element $E$. Also ${\mathbf Q}_{i}^{\eta}$ are both weighting and velocity basis
functions that span over the whole element that they belong to and,
\begin{displaymath}
{\mathbf Q}_{i}^{\eta} = {\mathbf Q}_{i}^{1} \;\;\;\; \forall
\eta\in\left\{1,2,\cdot\cdot\cdot,\mathcal{N}_{CV}\right\}
\end{displaymath}
where $\mathcal{N}_{CV}$ is the number of local CV's within each FE
and,
\begin{displaymath}
\mathbf{u}_{k} = \sum\limits_{\eta} \sum\limits_{j} H^{\eta}
       {\mathbf{u}_{k}}_{j}^{\eta}
\end{displaymath}
with
\begin{displaymath}
H^{\eta} =
\begin{cases}
1, \;\;\;\; & \text{in local control volume }\zeta, \\ 0, \;\;\;\; &
\text{otherwise}.
\end{cases}
\end{displaymath}
This approach allows the use of relatively low order quadrature rules
to be used across each FE.  For 2D P$_{1}$DG-P$_{2}$ elements,
Fig.~\ref{fem_cv_represent_a}(c), there are $3\times6=18$ velocity
basis functions for each of the two directions and each phase.  For
the corresponding tetrahedra elements there are $4\times 10=40$
velocity basis functions for each of the three directions and each
phase.  The aspect ratio $\left(\gamma^{\eta}\right)$ between CV
$\eta$ and the parent element $e$,
\begin{displaymath}
\gamma^{\eta} =
\displaystyle\frac{\mathcal{V}_{e}^{\eta}}{\mathcal{V}_{e}}
\displaystyle\frac{\mathcal{S}^{\eta}_{e}}{\mathcal{S}_{e}}
\end{displaymath}
where $\mathcal{V}_{e}$ and $\mathcal{S}_{e}$ are the volume and
surface area of the element $e$, whereas $\mathcal{V}_{e}^{\eta}$ and
$\mathcal{S}_{e}^{\eta}$ are the volume and surface area of control
volume $\eta$ within element $e$, respectively.

%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\subsection{Pressure matrix equation} 
Similar to part I the global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and
force balance equations (Eqn.~\ref{force-balance-matrix-form}) are
solved by vanishing thet velocity term and solving the system of
equations for pressure. At time level $n+1$,
Eqns. ~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can
be rewritten as,
\begin{eqnarray}
&& \mathbf{M}_{\sigma} \underline{\bf u}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1},\label{force-balance-matrix-form2} \\
&& \mathbf{M}_{p} \underline{\bf p}^{n+1} + \mathbf{B}^{T} \underline{\bf u}^{n+1} = \underline{\bf s}_{p}^{n+1}\label{glob-cty-matrix2}
\end{eqnarray}
and these equations are solved as described in part I by forming a pressure 
matrix equation by eliminating out the velocities then obtaining the velocities. 
The computationally more difficult to solve for discontinuous FEM resulting pressure 
matrix equation is solved here using a multi-grid approach with two grids the 
continuous and the discontinuous pressure grids. 
A continuous pressure matrix is formed by adding rows and columns of the discontinuous 
matrix this matri is then used to help precondition the discontinuous matrix 
equation. The smoother is 5 SSOR steps in the multi-grid method.

\section{1D CV advection-diffusion test}
The aim of this section is to demonstrate the performance of the
control volume FEM approach to solving advection diffusion equations.
Three control volumes are within each finite element and these are
interpolated using a quadratic finite element method basis
function. The FEM provides the high order flux which is limited as
described previously. To this end the 1D advection diffusion equation
is solved with a domain $x\in \left[0,1\right]$, boundary condition of
$T=1$ on the left boundary, $k \nabla T =0$ on the right boundary and
$u=1$. The diffusivity $k$ is set to zero unless otherwise stated. An
initial $T$ of $T=1 \forall x\in \left[ 0.2, 0.4 \right]$ and $T=0$
otherwise is used.

The results shown in Fig.~\ref{compar-dg} show the spatial accuracy
with a small (converged) time step size. The advection results at the
end of the simulation ($t=0.2$) in which a profile has been advected a
distance of 0.2 are shown in this figure for a 5 element mesh. The
accuracy can be gauged by comparing with a 50 between element
solution. The control volume solutions are shown as well as the
consistent finite element interpolation of this solution which is used
to obtain the high order fluxes - between the elements and within each
element.

In Fig.~\ref{compar-dg} we have increased the Courant number
(defined as $u \Delta t / \Delta x$) based on the element size to
${\Delta x}=0.5$. The Courant number based on the smallest control
volume is $2$. Thus this represents and large time step. And we
perform two time steps which is a difficult test of the non-linear
$\theta$ time stepping method.  Note that due to the large time
steps the solution is more dissipative, but again the discontinuous
between element solution is more accurate.

Results from a simulation with diffusion ($k=0.01$) are shown in
Fig.~\ref{compar-dg-bdt-diff}.  The result without diffusion is also
shown on the same plot.  As one might expect this result is more
dissipative.

\section{The Buckley-Leverett test case}
\label{res1}
The one-dimensional incompressible Buckley-Leverett equations with gas
injection along a fully saturated ($S_f=1$) bore hole of uniform
porosity ($\phi=0.5$) are modelled using Porosity. The gas is injected
at a velocity of $u_g=1$ and a saturation of $S_g=1$. On the outflow
boundary the pressure level is set to zero. The length of the bore
hole is 4 non-dimensional units. All boundary conditions are applied
weakly. The Corey model defined as: $k_g = S_g^{-2}$ is used to
calculate the relative permeability.

All simulations use the overlapping mixed finite element method and a
number of element pairs (for velocity and pressure) are
evaluated. Saturation is collocated at the pressure nodes. Although
saturation is calculated using a control volume formulation a FEM
interpolation is used to form the high order fluxes and this is also
used here for most of the saturation plots.
Fig.~\ref{bl-exact-meth-upwind} shows the CV saturation of gas (with
horizontal and vertical lines) and the quadratic finite element
interpolation (FEM interpolation). The solution converges with
increased resolution. Note that the right corners of the control
volumes agree best with the analytical solution. This is because
upwinding of the velocities is used (or equivalently the relative
permeabilities) and it is at these points that the equations reach the
balance necessary to match closely the analytic solution.

Despite the one-dimensional nature of the problem, it is reproduced in
two and three dimensions using structured and unstructured meshes to
evaluate the multi-dimensional capabilities of the model. In two- and
three-dimensional simulations, free-slip boundary conditions are
applied on the sides of the domain for the two velocity fields.

\subsection{Convergence analysis}
A convergence analysis is undertaken for one and two dimensions. A
number of meshes and element pairs are assessed with respect to the
gas phase saturation field.

All one-dimensional meshes have equi-sized elements. Two-dimensional
meshes are structured and one-element wide. Their elements are also
equi-sized and have unity aspect ratio. Thus the width of the
two-dimensional domains is inversely proportional to the number of
elements. The time step size is linearly varied between 1.25 10$^{-4}$
and 3.125 10$^{-3}$ for the one-dimensional simulations, while it is
10$^{-4}$ for all two-dimensional simulations.

Saturation profiles for the gas phase at time $t=0.5$ are shown in
Fig.~\ref{fig:BL_profiles}. One dimension P0DG-P1 profiles for meshes
having between 5 and 100 elements are shown on the top left. One
dimension P1DG-P2 and P2DG-P3 profiles for meshes having between 5 and
500 elements are shown on the top right and bottom left, respectively.
Finally, two dimension P1DG-P2 profiles for meshes having between 5
and 100 elements are shown on the bottom right. The geometry symmetry
line is used to extract data for the two-dimensional simulation.

Results are in good agreement with the analytic solution even for the
coarse meshes and in all four cases the results converge to the
analytical solution with increasing resolution.

Note that for the coarse meshes (5 and 20 elements) high-order
elements perform better and are able to capture the front more
accurately. Consequently, P1DG-P2 performs better than P0DG-P1 and
P2DG-P3 performs better than P1DG-P2. As far as the two-dimensional
simulations are concerned, the coarse mesh simulation performs
slightly worse than its one-dimensional counterpart but for higher
resolutions results are identical.

These conclusions become clearer in Fig.~\ref{fig:BL_converg-rates},
where convergence rates are shown. The L1 error defined as $N^{-1}
\Sigma_{i=1}^N|y_i-E_i| $ is shown on the left, while the L2 error
defined as $N^{-1} (\Sigma_{i=1}^N(y_i-E_i)^2)^{0.5}$ is shown on the
right ($y$ represents modelled gas phase saturations and $E$
represents analytic gas phase saturations). In addition to the
simulations discussed so far, convergence rates for another set
simulations that use full upwinding is also shown in
Fig.~\ref{fig:BL_converg-rates}. *** ADD DISCUSSION HERE ***

\subsection{Numerical experiments}
Following the convergence analysis a number of numerical experiments
are performed to evaluate the robustness of the method in fully
unstructured meshes.

Gas phase saturation surface maps for a two- and a three-dimensional
simulation at time $t=0.5$ are shown in Fig.~\ref{fig:}. The mesh and
surface mesh for the two- and three-dimensional simulations,
respectively, are also shown in Fig.~\ref{fig:}. These simulations use
unstructured meshes and the P1DGP2 element pair.

Saturation profiles for the gas phase at time $t=0.5$ are shown in
Fig.~\ref{fig:BL_profiles}. Results are not spatially averaged and the
geometry symmetry line is used to extract data for all simulations.
The structured coarse mesh uses $1 \times 19$ layers in the lateral
and flow directions, respectively. The structured medium mesh uses $3
\times 40$ layers.

\section{A 4-region modified Buckley-Levrett test case}
\label{res2}
A four-region modified Buckley-Levrett test case is used to
demonstrate the capabilities of the suggested method.  In this test
case gas is injected in a fully saturated ($S_f=1$) two-dimensional
square domain of side length one and uniform porosity
($\phi=0.5$). However, unlike the original Buckley-Levrett test case,
the permeability of the domain is not uniform and four `regions'
exist. A schematic of the geometry along with the four regions and
boundary conditions is shown in Fig.~\ref{fig:4reg_BL_schematic}.  The
four regions are square and equi-sized. The permeability in regions R1
and R4 is 4 times bigger than that of regions R2 and R3.

The gas is injected at a
velocity of $u_g=1$ and a saturation of $S_g=1$. On the outflow
boundary the pressure level is set to zero.
Free-slip boundary conditions are
applied on the sides of the domain for the two velocity fields.
All boundary conditions
are applied weakly.
The Corey model defined as:
$k_g = S_g^{-2}$ is used to calculate the relative permeability.

All simulations use the overlapping mixed finite element method and the
P1DG-P2 element pair. The time step sizes are 10$^{-3}$ and 5 10$^{-4}$
for the coarse and fine meshes, respectively.

Four simulations are performed in total with the only difference
between them being the mesh. All meshes are unstructured, however two
of them resolve the boundaries between the four regions and two of
them don't. For each of the two cases (resolving and non-resolving), a
coarse and fine mesh simulation is performed.

Fig.~\ref{fig:4reg_maps} shows the gas phase saturation maps at time
$t=0.1$ along with the meshes used for all four simulations. Coarse
meshes are located on the top, while fine meshes are located on the
bottom. Non-resolving meshes are on the left, while region resolving
meshes are located on the right. All four simulations are in good
agreement and gas phase saturations follow similar patterns. Note
that the differences between the region boundary resolving and
non-resolving meshes are negligible.

Fig.~\ref{fig:4reg_plots} shows four gas phase saturation profiles at
time $t=0.1$ for all four simulations.

\section{Conclusions}
\label{conc}

\ack 
This work was supported by the...

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv}
\bibliography{references}

\pagebreak
\clearpage

\listoffigures
\pagebreak
\clearpage

\input{article_figure1}

\end{document}

%%
%% End of tex file.

### 2015-01-18 Papers/Prototype_1_Method/article_figure1.tex
updates
updates in paper 1: trasnfering content on the BL test case from paper 2 to paper 1

@@
 \begin{center}
-\hbox{\hspace{-2.5cm}
-\includegraphics[width=1.2\textwidth]{diagrams/overlapping}}
+\hbox{\hspace{-3.7cm}
+\includegraphics[width=1.4\textwidth]{diagrams/overlapping}}
 \caption{An isometric schematic of the 2D overlapping velocity
@@
 
+%%%            %%%
+%%%  COMMENTS  %%%
+%%%            %%%
 \begin{comment}
@@
 \end{comment}
+%%%            %%%
+%%%  COMMENTS  %%%
+%%%            %%%
 
@@
 \begin{center}
-\vbox{\vspace{-1.5cm}\hbox{
+\vbox{\vspace{-2.cm}\hbox{
 \includegraphics[width=15.5cm,height=10.cm]{./diagrams/Step_P1DG-P2Cont}}
@@
 
+%%%            %%%
+%%%  COMMENTS  %%%
+%%%            %%%
 \begin{comment}
-
 %%%
@@
 
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-upwind.eps}
-\end{center}
-\caption{Buckley--Leverett test-cases: Saturation solutions for the
-  continuous upwind method for different 1D P$_{1}$DG-P$_{2}$ mesh
-  resolutions and comparison against standard analytical solution.
-\label{bl-exact-meth-upwind}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-  %\begin{center}
-\vbox{\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P0DGP1_convergence.eps}}
-\vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P1DGP2_convergence.eps}}
-\vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P2DGP3_convergence.eps}}}
-   % \includegraphics[width=0.45\textwidth]{BL_2d_P1DGP2_convergence}
-    \caption{Buckley--Leverett test-cases: Saturation profiles for a
-      number of element-pairs and numerical resolutions in 1D --
-      P$_{0}$DG-P$_{1}$ (top), P$_{1}$DG-P$_{2}$ and P$_{2}$DG-P$_{3}$
-      (bottom).\label{fig:BL_profiles}}
-  %\end{center}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{diagrams/L1_convergence_rate.eps}}
-\vspace{.0cm}\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{diagrams/L2_convergence_rate.eps}}}
-    \caption{Buckley--Leverett test-cases: L1 (top) and L2 (bottom)
-      error convergence rates for a number of element
-      pairs. \label{fig:BL_converg-rates}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1.\textwidth]{diagrams/bl-upwind-v-up-and-down.eps}
-\end{center}
-\caption{Buckley--Leverett test-cases: Comparison of the optimal
-  upwind formulation when using upwinding (OU) and coupled
-  upwind/downwind (OU-D). The finite element interpolation of the
-  saturation field $\left(S_{1}\right)$ is shown at different mesh
-  resolutions. Downwind seems to detract from the accuracy of the
-  solution. \label{bl-upwind-v-up-and-down}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\begin{center}
-\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-cv-0-8-ele50.eps}
-\end{center}
-\vspace{0.cm}}
-\caption{Buckley--Leverett test-cases: Comparison of control volume
-  solutions using 80$\%$ upwinding and with optimal upwinding and
-  using 50 continuous P$_{1}$DG-P$_{2}$
-  elements. \label{bl-exact-meth-cv-0-8-ele50}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
-\end{center}
-\caption{Buckley--Leverett test-cases: Two element solution using the
-  discontinuous formulation. Saturation field from both CV solution
-  and FEM interpolation are shown.  \label{bl-dg-2eles}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
-\vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
-\caption{Buckley--Leverett test-cases: Saturation field obtained from
-  the discontinuous and continuous formulation with different mesh
-  resolutions. Solutions with (top) and without (bottom) upwinding
-  scheme. Notice that oscillations are suppressed with the upwinding
-  scheme.\label{bl-dg-cent-4-10-20}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
-\vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
-\caption{Buckley--Leverett test-cases: Saturation field obtained from
-  (top) continuous and discontinuous (between elements) formulations
-  (solution with 50 elements may be considered as a converged
-  result). Solution obtained (bottom) from linear pressure (P1)
-  formulation with different mesh resolution with comparison against
-  P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
-\end{figure}
-
-\begin{figure}[H]
-\vbox{
-\begin{center}
-\includegraphics[width=17.5cm,height=12.5cm]{diagrams/bl-dg-4-10-vers-cty}
-\end{center}
-\vspace{0.cm}}
-\caption{Gas saturations shown comparing the accuracy of the
-  discontinuous between elements and continuous formulation. The 50
-  element continuous solution may be viewed as a converged result.  }
-\label{bl-dg-4-10-vers-cty}
-\end{figure}
-
 \end{comment}
-
-%%%
-%%%  FIGURE 
-%%%
-
-%%%
-%%%  FIGURE 
-%%%
+%%%            %%%
+%%%  COMMENTS  %%%
+%%%            %%%

### 2015-01-18 Papers/Prototype_1_Method/article_figure2.tex
updates in paper 1: trasnfering content on the BL test case from paper 2 to paper 1

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-upwind.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Saturation solutions for the continuous upwind method for different 1D P$_{1}$DG-P$_{2}$ mesh  resolutions and comparison against standard analytical solution.
\label{bl-exact-meth-upwind}}
\end{figure}

%%%
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
  %\begin{center}
\vbox{\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P0DGP1_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{diagrams/BL_1d_P2DGP3_convergence.eps}}}
   % \includegraphics[width=0.45\textwidth]{BL_2d_P1DGP2_convergence}
    \caption{Buckley--Leverett test-cases: Saturation profiles for a number of element-pairs and numerical resolutions in 1D -- P$_{0}$DG-P$_{1}$ (top), P$_{1}$DG-P$_{2}$ and P$_{2}$DG-P$_{3}$ (bottom).\label{fig:BL_profiles}}
  %\end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{diagrams/L1_convergence_rate.eps}}
\vspace{.0cm}\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{diagrams/L2_convergence_rate.eps}}}
    \caption{Buckley--Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of element pairs. \label{fig:BL_converg-rates}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-upwind-v-up-and-down.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Comparison of the optimal upwind formulation when using upwinding (OU) and coupled upwind/downwind (OU-D). The finite element interpolation of the saturation field $\left(S_{1}\right)$ is shown at different mesh resolutions. Downwind seems to detract from the accuracy of the solution. \label{bl-upwind-v-up-and-down}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-exact-meth-cv-0-8-ele50.eps}
\end{center}
\vspace{0.cm}}
\caption{Buckley--Leverett test-cases: Comparison of control volume
  solutions using 80$\%$ upwinding and with optimal upwinding and
  using 50 continuous P$_{1}$DG-P$_{2}$
  elements. \label{bl-exact-meth-cv-0-8-ele50}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
\end{center}
\caption{Buckley--Leverett test-cases: Two element solution using the
  discontinuous formulation. Saturation field from both CV solution
  and FEM interpolation are shown.  \label{bl-dg-2eles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  the discontinuous and continuous formulation with different mesh
  resolutions. Solutions with (top) and without (bottom) upwinding
  scheme. Notice that oscillations are suppressed with the upwinding
  scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
\caption{Buckley--Leverett test-cases: Saturation field obtained from
  (top) continuous and discontinuous (between elements) formulations
  (solution with 50 elements may be considered as a converged
  result). Solution obtained (bottom) from linear pressure (P1)
  formulation with different mesh resolution with comparison against
  P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[H]
\vbox{
\begin{center}
\includegraphics[width=17.5cm,height=12.5cm]{diagrams/bl-dg-4-10-vers-cty}
\end{center}
\vspace{0.cm}}
\caption{Gas saturations shown comparing the accuracy of the
  discontinuous between elements and continuous formulation. The 50
  element continuous solution may be viewed as a converged result.  }
\label{bl-dg-4-10-vers-cty}
\end{figure}

\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.2cm}
    \includegraphics[width=1.\textwidth]{diagrams/map_2d.png}}
\vspace{1.cm}
\hbox{\hspace{0.2cm}
    \includegraphics[width=1.\textwidth]{./diagrams/map_3d.png}}}
    \caption{Buckley-Leverett test-cases: phase 1 saturation surface maps for a 2- (770 triangles) and 3-D (1207 tetrahedra) simulations (\PN[1]{2} unstructured mesh grids) at time $t=0.5$. \label{fig:maps2d_3d}}
\end{figure}

%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{.3cm}
    \includegraphics[width=0.9\textwidth]{diagrams/BL_2d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{.3cm}
    \includegraphics[width=0.9\textwidth]{./diagrams/simulations_2d_3d.eps}}}
    \caption{Buckley-Leverett test-cases: 2- and 3-D phase 1 saturation profiles with \PN[1]{2} elements. Sensitivity analysis for (top) grid resolution using structured \PN[1]{2} mesh, and (bottom) mesh type.\label{fig:BL_2d_profiles}}
\end{figure}

\end{comment}

### 2015-01-19 Papers/Prototype_1_Method/article.tex

@@
 Here, the formulation described in Section~\ref{Section:CVFEMDiscretisation} is extended to discretise the saturation conservation equations and to help deriving the global mass balance equations.
-In this work, the fluids are assumed incompressible.
-The saturation equation can be written as,
+In this work, fluids are assumed incompressible, and the saturation equation can be written as,
 \begin{equation}
@@
 \subsection{Advection Test-Cases}
-The aim of this section is to demonstrate the performance of the CVFEM approach to solve the advection equation.
-The control volumes are interpolated using FEM basis functions and the FEM provides the high-order flux which is limited as previously described.
+The aim of this section is to demonstrate the performance of the CVFEM approach to solve the advection equation, %.
+As described in Section~\ref{transport_methods_section}, control volumes are interpolated using FEM basis functions and the FEM provides the high-order flux which is limited.
 The 1D advection equation:
 \begin{displaymath}
-  \displaystyle\frac{\partial}{\partial t} T + \frac{\partial}{\partial x} \left( {\bf u}\;T \right) = 0, 
+  \displaystyle\frac{\partial T}{\partial t} + \frac{\partial}{\partial x} \left( {\bf u}\;T \right) = 0, 
 \end{displaymath}
-is solved within a domain $x\in \left[0,1\right]$, with $T=1$ on the left boundary and advection velocity of $u=1$. Initial conditions at time $t=0$,
+within a domain $x\in \left[0,1\right]$, with $T=1$ on the left boundary and advection velocity of $u=1$. Initial conditions are defined as,
 \begin{displaymath}
-  T\left( x,0\right)= \begin{cases} 1, \;\; &  0.2 \le  x \le 0.4 \\
+  T\left( x,0\right)= \begin{cases} 1, \;\; &  0.2 \le  x \le 0.4, \\
     0, & \mbox{ otherwise,}
@@
 are specified.
+Control volumes are interpolated using FEM basis functions.
 Figure~\ref{compar-dg} (top) shows the spatial accuracy of the schemes introduced in this work with a small (converged) time step size.
-The solution shown here was obtained at $t=0.2$ and the domain was divided into 5 elements.
+The solution was obtained at $t=0.2$ and the domain was divided into 5 elements.
 The accuracy can be gauged by comparing solutions obtained from 5 and 50 elements.
@@
 
-Figure~\ref{compar-dg-bdt-diff} demonstrates the advection capturing capability of our method.
-In Fig.~\ref{theta-bdt}, solutions obtained from (a) continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element-pair}\right)$ and (b) discontinuous $\left(\text{either P}_{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements pairs}\right)$ formulations are compared in a problem with large time step size.
+Figures~\ref{compar-dg-bdt-diff} and~\ref{theta-bdt} demonstrate the advection capturing capability of our method with continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element-pairs}\right)$ and discontinuous $\left(\text{either}\right.$ P$\left._{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements-pairs}\right)$ formulations.
+In Fig.~\ref{theta-bdt}, these formulations are compared in a problem with large time step size.
 The value of $\theta$ on the faces of the CV's is shown at the end of two time steps; it is important to notice that $\theta$ is smaller and closer to $0.5$ when using the continuous approach than the discontinuous method.
@@
 
+\medskip
 For the advection of an initial Gaussian profile,
@@
 The FEM interpolations for the three schemes (with 5 and 20 elements) are shown in Fig.~\ref{converg-compare-fem}.
-\jrp{It's a bit unclear what the difference is between the pressure discontinuous schemes.
-Is one upwinded and the other central?
-} The first two schemes are the continuous and discontinuous  approaches.
+The first two schemes are the continuous and discontinuous  approaches.
 The third scheme uses a central difference method (i.e., mean of the solutions either side of an element boundary) to calculate the flux between the elements and has a discontinuous solution between the elements.
@@
 T\left(x, y,0\right) =\begin{cases}
-1, & \left(x,y\right)\in \left[0.25,0.50\right] \\%  0.25\leq x \leq 0.50 \text{ and } 0.25\leq y \leq 0.50\\
+1, & \left(x,y\right)\in \left[0.25,0.50\right], \\%  0.25\leq x \leq 0.50 \text{ and } 0.25\leq y \leq 0.50\\
 0, & \text{otherwise,}
@@
 \end{displaymath}
-and a Gaussian profile,
+and a Gaussian plume profile,
 \begin{displaymath}
@@
 \end{displaymath} 
-were calculated for both element type formulations (continuous and discontinuous) and test cases for several mesh grids and plotted on log-log scale, Fig.~\ref{L1_L2norm_Adv2D}.
+were calculated for both formulations (continuous and discontinuous) and test cases for several mesh grids and plotted on log-log scale, Fig.~\ref{L1_L2norm_Adv2D}.
 First- and second-order slopes are also shown in this figure.
@@
 
-\subsection{Buckley-Leverett Test Case}
-The Buckley-Leverett (B-L) equation is a nonlinear advection equation for the relative saturation of fluid phases representing two-phase immiscible flows in porous media.
+\subsection{Buckley-Leverett Test Cases}
+The Buckley-Leverett (B-L) equation is a nonlinear advection equation for the relative saturation of fluid phases representing immiscible two-phase flows in porous media.
 Here, water $\left(S_{l}=1\right)$ is injected at a velocity $u_{g}\phi=1$.
@@
 
-In Fig.~\ref{bl-exact-meth-upwind} the CV solution of the water saturation and equivalent quadratic FEM interpolation are presented $\left(\text{P}_{1}\text{DG-P}_{2}\right)$.
-As it can be seen the solution converges with increased resolution.
+Control volume solution of water saturation and equivalent quadratic FEM interpolation are shown in Fig.~\ref{bl-exact-meth-upwind}, where solution converges with increased resolution.
 Notice that the corners of the CV's are very close to the converged solution.
@@
 \input{article_figure1}
+\input{article_figure2}
 

### 2015-01-19 Papers/Prototype_2_Method/article_figure1.tex

%\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{./diagrams/bl-exact-meth-upwind}
\end{center}
\caption{Buckley-Leverett test-cases: Saturation solutions for the continuous upwind method for different 1D P$_{1}$DG-P$_{2}$ mesh resolutions and comparison against standard analytical solution.
\label{bl-exact-meth-upwind}}
\end{figure}

%\end{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P0DGP1_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{2.5cm}
    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P2DGP3_convergence.eps}}}
    \caption{Buckley-Leverett test-cases: 1-D Saturation profiles for a number of element pairs and grid resolutions -- \PN[0]{1} (top), \PN[1]{2}, \PN[2]{3} (bottom).\label{fig:BL_profiles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{./diagrams/L1_convergence_rate}}
\vspace{.0cm}\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{./diagrams/L2_convergence_rate}}}
    \caption{Buckley-Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of (continuous) element pairs. \label{fig:BL_converg-rates}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{./diagrams/bl-upwind-v-up-and-down}
\end{center}
\caption{Buckley-Leverett test-cases: Comparison of the optimal upwind formulation when using upwinding (OU) and coupled upwind/downwind (OU-D). The finite element interpolation of the saturation field $\left(S_{1}\right)$ is shown at different mesh resolutions. Downwind seems to detract from the accuracy of the solution. \label{bl-upwind-v-up-and-down}}
\end{figure}

\begin{comment}
%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\begin{center}
\includegraphics[width=1.\textwidth]{./diagrams/bl-exact-meth-cv-0-8-ele50}
\end{center}
\vspace{0.cm}}
\caption{Buckley-Leverett test-cases: Comparison of control volume solutions using 80$\%$ upwinding and with optimal upwinding and using 50 continuous P$_{1}$DG-P$_{2}$ elements. \label{bl-exact-meth-cv-0-8-ele50}}
\end{figure}

\end{comment}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1.\textwidth]{./diagrams/bl-dg-2eles}
\end{center}
\caption{Buckley-Leverett test-cases: Two element solution using the discontinuous formulation. Saturation field from both CV solution and FEM interpolation are shown.  \label{bl-dg-2eles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{./diagrams/L1_convergence_rate_DG.eps}}
\vspace{.0cm}\hbox{\hspace{1.cm}
    \includegraphics[width=0.8\textwidth]{./diagrams/L2_convergence_rate_DG.eps}}}
    \caption{Buckley-Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of fully discontinuous (between elements) element pairs. \label{fig:BL_converg-rates_DG}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-4-10-20}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-cent-4-10-20}}}
\caption{Buckley-Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulation with different mesh resolutions. Solutions with (top) and without (bottom) upwinding scheme. Notice that oscillations are suppressed with the upwinding scheme.\label{bl-dg-cent-4-10-20}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-4-10-vers-cty}}
\vspace{-0.cm}
\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-p1-2-4-5-10-20-40}}}
\caption{Buckley-Leverett test-cases: Saturation field obtained from (top) continuous and discontinuous (between elements) formulations (solution with 50 elements may be considered as a converged result). Solution obtained (bottom) from linear pressure (P1) formulation with different mesh resolution with comparison against P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{.2cm}
    \includegraphics[width=1.\textwidth]{./diagrams/map_2d.png}}
\vspace{1.cm}
\hbox{\hspace{0.2cm}
    \includegraphics[width=1.\textwidth]{./diagrams/map_3d.png}}}
    \caption{Buckley-Leverett test-cases: phase 1 saturation surface maps for a 2- (770 triangles) and 3-D (1207 tetrahedra) simulations (\PN[1]{2} unstructured mesh grids) at time $t=0.5$. \label{fig:maps2d_3d}}
\end{figure}

%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{\hspace{.3cm}
    \includegraphics[width=0.9\textwidth]{./diagrams/BL_2d_P1DGP2_convergence.eps}}
\vspace{-.0cm}\hbox{\hspace{.3cm}
    \includegraphics[width=0.9\textwidth]{./diagrams/simulations_2d_3d.eps}}}
    \caption{Buckley-Leverett test-cases: 2- and 3-D phase 1 saturation profiles with \PN[1]{2} elements. Sensitivity analysis for (top) grid resolution using structured \PN[1]{2} mesh, and (bottom) mesh type.\label{fig:BL_2d_profiles}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.65\textwidth]{./diagrams/4Rregion_BL}
    \caption{Heterogeneous permeability test-cases: schematic including boundary conditions. Darker areas (R1 and R4) represent regions with high permeability.\label{fig:4reg_BL_schematic}}
  \end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{\hbox{
\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{./diagrams/CG_coarse083.png}
\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{./diagrams/CG_fine083.png}}
\vspace{1.cm}\hbox{
\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{./diagrams/DG_coarse083.png}
\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{./diagrams/DG_fine083.png}}}
 \caption{Heterogeneous permeability test-cases: phase 1 saturation maps at time $t=0.08$ seconds. Upper- and lower-rows show saturation fronts (superimposed with unstructured mesh) calculated with \PN[1]{2} and \PN[2]{2}DG elements, respectively. Left/Right columns: 402 triangles (2412 nodes) and 3714 triangles (22284 nodes) meshes.\label{fig:4reg_maps}}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.475\textwidth]{./diagrams/down_left_top_right083}
    \includegraphics[width=0.475\textwidth]{./diagrams/Top_left-Down_right083}
    \includegraphics[width=0.475\textwidth]{./diagrams/X04_083}
    \includegraphics[width=0.475\textwidth]{./diagrams/y04_083}
    \caption{Heterogeneous permeability test-cases: phase 1 saturation profiles at time $t=0.08$ seconds. Top left: profiles at the diagonal starting at the bottom left corner of the domain. Top right: profiles at the diagonal starting at the top left corner of the domain. Bottom left: profiles at $x=0.4$. Bottom right: profiles at $y=0.4$.\label{fig:4reg_plots}}
  \end{center}
\end{figure}

%%%
%%%  FIGURE 
%%%
\begin{figure}[h]
\vbox{
\hbox{
\hspace{3.5cm} \includegraphics[width=0.5\textwidth]{./diagrams/square_permeability_low}}
\vspace{0.5cm}
\hbox{
\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/cg_square_015_low}
\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/cg_square_05_low}}
\vspace{0.5cm}
\hbox{
\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/dg_square_015_low}
\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/dg_square_05_low}}}
 \caption{Underground Caisson: Initial configuration of porous matrix consisting of a low-permeability square embedded in a high-permeability region (top). Phase 1 saturation profile at 0.15 (left) and 0.5 seconds (right) within the transient for simulation performed using \PN[0]{1} (middle) and \PN[1]{1}DG (bottom) element-pairs.\label{fig:square_permeability}}
\end{figure}

%%%
%%%  FIGURE 
%%%

\begin{figure}[h]
\vbox{
\hbox{
\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_permeability}}
\vspace{-1.cm}\hbox{\hspace{4cm}(a) Permeability map}
\vspace{.5cm}
\hbox{
\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_0011}}
\vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 0.011$ seconds }
\vspace{.5cm}
\hbox{
\hspace{-.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_0014}}
\vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 0.014$ seconds }
}
\caption{Wedged-shaped region: (a) two phase flow in a rectangular domain with an internal wedge-shaped region with high-permeability. Snapshots of water-phase saturation profiles of simulations performed with a fine mesh \PN[0]{1} simulation (top) 
and course mesh \PN[0]{1} simulation (middle)  and course mesh \PN[2]{1}DG simulation (bottom) at (b) 0.011 and (c) 0.0014 seconds.\label{fig:wedge_permeability}}
\end{figure}

%%%
%%%  FIGURE 
%%%

\begin{figure}[h]
\vbox{
\hbox{
\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_perm}}
\vspace{-0.cm}\hbox{\hspace{4cm}(a) Permeability map}
\vspace{.5cm}
\hbox{
\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_first}}
\vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 7.9$ years }
\vspace{.5cm}
\hbox{
\hspace{-.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_second}}
\vspace{-0.cm}\hbox{\hspace{4cm}(c) Internal section }
}
\caption{Hexahedron domain: (a) Permeability map and mesh used. Snapshots of water-phase saturation profiles of simulations performed with \PN[0]{1} (b) 3-D solution and (c) 2-D internal slice.\label{fig:3d_perm}}
\end{figure}

### 2015-01-19 Papers/Prototype_2_Method/diagrams/article222.tex

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later c.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,authoryear,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,authoryear,1p,times]{elsarticle}
%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,3p,times]{elsarticle}
%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,5p,times]{elsarticle}
%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

\usepackage{comment}
\usepackage{epstopdf}
\usepackage{bm}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb,amsmath}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}

\journal{Computer Methods in Applied Mechanics and Engineering}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{The Overlapping Control Volume Finite Element Method for Multi-Fluids Porous Media Flow Modelling. Part II: Simulation Results}

\author[IC]{D. Pavlidis}\corref{cor1}\ead{dimitrios.pavlidis@imperial.ac.uk} \author[UoA]{J.L.M.A. Gomes}  \author[IC]{J.R. Percival} \author[IC]{P. Mostaghimi} \author[IC]{P. Salinas} \author[IC]{Z. Xie} \author[IC]{C.C. Pain} \author[IC]{M. D. Jackson} \author[HW]{A.H. ElSheikh} \author[IC]{M. Blunt} \author[IC]{A. Muggeridge}  
\cortext[cor1]{Corresponding author.}

\address[IC]{Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK}
\address[UoA]{Environmental $\&$ Industrial Fluids Mechanics Group, School of Engineering, University of Aberdeen, UK}
\address[HW]{Institute of Petroleum Engineering, Heriot-Watt University, Edinburgh, UK}

\begin{abstract} 
This paper is the second in a series of manuscripts on novel FEM-based formulations for multi-scale compositional multi-fluid porous media flows. In the first paper, the multiphase formulation, based upon the overlapping control volume discontinuous-Galerkin finite element method (OCV-DGFEM), was fully described and, advection-diffusion validation test-cases were used to demonstrate the accuracy and convergence of the formulation. In this second paper, the OCV-DGFEM-based formulation is applied to a set of multi-fluids porous media flows test-cases to assess the performance and numerical accuracy of (a) element-pairs (\PN[n]{n+1}, \PN[n]{n+1}DG, \PN[n]{n} and \PN[n]{n}DG), (b) continuous / discontinuous (between elements) formulations, (c) structured and unstructured (triangle / tetrahedron) meshes, (d) upwind schemes and (e) domain heterogeneities imposed by large permeability ratios. Numerical solutions are in good agreement with (semi-)analytically and experimentally obtained data.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Multiphase porous media flow \sep DG methods \sep Mixed FEM formulation \sep Permeability discretisation \sep Computational multi-fluids dynamics. 
\end{keyword}

\end{frontmatter}

%\tableofcontents
% \linenumbers
%%%                   %%%
%%%      SECTION      %%%
%%%                   %%%
\section{Introduction}

\begin{itemize}
\item \textcolor{red}{One relatively short paragraph on main motivation for the work.}
\end{itemize}

In recent years, advances in numerical simulation techniques have played an increasing role in solving complex engineering problems. Most of these problems can be represented as fully coupled systems of nonlinear partial differential equations in a multitude of spatial- and temporal-scales. Novel mathematical methods have been continuously introduced to improve both numerical accuracy and convergence of equations' solutions while also aiming for optimum computational performance.

Finite difference methods (FDM) still are the preferred numerical tool for subsurface flows in industrial-standard models due to the inherent simplicity and ease of implementation. However FDM-based models often lack geometry flexibility and numerical accuracy and therefore have been mostly restricted to aged software packages.  Due to the simple physical interpretation, numerical accuracy $\&$ robustness and elegant mathematical formulation, finite element and volume methods (FEM and FVM) have attracted the attention of scientists and engineers interested in multi-physics applications in complex geometries \citep{cordazzo_2006, geiger_2004,nick_2011}.

Among the different families of finite element methods, mixed FEM gained great attention due to (a) high accuracy of field solutions and associated fluxes, (b) boundedness of solution (essential to physical realism) and (c) local mass conservation \citep[within an element,][]{fung_1992,durlofsky_1993,durlofsky_1994}. However, they are often plagued by very expensive computational overhead in shock-dominated conditions, e.g., large permeability ratios in fractured porous media interfaces. Discontinuous Galerkin (DG) method is another family of FEM that utilises discontinuous piecewise polynomial spaces and specialised bi-linear forms to weakly impose boundary conditions and inter-element connectivities.  DGFEM methods became popular in scientific computing communities as they are able to ensure local mass conservation with relatively small numerical diffusion and solution's oscillations whilst support nonconforming unstructured tetrahedral meshes and {\it h-p} adaptive methods \citep{merton_2012,brooks_1982}.

This is the second of a series of papers exploiting novel computational methods for multi-fluids flow in porous media. The new overlapping control volume finite element method was introduced in the first part of this series followed by an advection test-case validation \citep{gomes_2013}. The formulation lies in two-folds development, it uses a dual consistent pressure-velocity representation in CV and DGFEM spaces (through a mixing formulation) and a recently developed \PN[n]{n+1} family of FE types. Additionally a novel family of fully discontinuous element types -- the \PN[n]{n+1}DG and \PN[n]{n}DG, was introduced to represent discontinuity across neighbour elements able to represent highly heterogeneous porous media domain, typical of some geological formations.

The remainder of this paper is organised as follows. A brief description of the model is given in Section~\ref{Section:SummaryPaper1} followed by the model validation against analytical solutions of the classical Buckley-Levrett problem. In Section~\ref{res2}, water-flood problems (i.e., immiscible fluids displacement) were simulated in 2-D geometry to assess the flow behaviour in prescribed heterogeneous porous media. The impact of large permeability ratios (i.e., highly heterogeneous porous matrix) in the model was investigated in Sections~\ref{res3} and~\ref{res4}. Additionally, in the later we also investigated the model performance when elements are skewed due to large domain aspect ratio. A brief summary of the results are presented in Section~\ref{conc} followed by many conclusions drawn from the two inter-linked papers.

%\setlength\parindent{0pt}

%\section{Model Validation}\label{Section:Results}
\section{Summary of the Model Formulation}\label{Section:SummaryPaper1}
This section summarises the model formulation to solve multiphase porous media equations.  The novel overlapping control volume - discontinuous Galerkin finite element method (OCV-DGFEM) is based on two-fold numerical development, a FEM-based mixed formulation and a new family of element-pairs (\PN[n]{n+1}).  The underlying mass balance equations (e.g., saturation, density, mass fraction, etc.) are solved in control volume (CV) space whereas a Petrov-Galerkin FEM is used to obtain the high-order fluxes on the CV boundaries which are limited to achieve bounded mass-based fields (e.g., positiveness of densities and saturations ranging from zero to one).

The family of \PN[n]{n+1} element-pairs was introduced by \citet{cotter_2009b} \citep[see also][]{cotter_2011} for geophysical fluid dynamics (GFD) applications. In particular, \PN[1]{2} elements -- linear discontinuous polynomial FE basis function for velocity $\left(\text{P}_{1}\text{DG}\right)$ and quadratic polynomial FE basis function for pressure $\left(\text{P}_{2}\right)$, was developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes. Any numerical discretisation that is not based upon quadrilaterals and hexahedra mesh grids very often results in spurious pressure modes due to the unbalancing number of velocity and pressure degrees-of-freedom \citep{sollie_phd_2010}.  However, tests on the \PN[1]{2} element-pair proved that this element is LBB stable \citep{cotter_2009a} and does not present spurious pressure modes on arbitrary unstructured meshes.

The extended Darcy's law for $N_{p}$ immiscible fluid phases can be expressed as
\begin{equation}
S_{k}\left(\displaystyle\frac{\mathbf{K} \mathcal{K}_{rk}}{\mu_{k}}\right)^{-1}\mathbf{u}_{k}=\underline{\underline{\sigma}}_{k} \mathbf{u}_{k} = -\nabla p + \mathbf{s}_{u} 
\end{equation}
where $k\in\left[1,N_{p}\right]$ represents the phase, $S$, $\mathbf{K}$, $\mathcal{K}_{r}$ and $\mu$ are saturation, permeability tensor, relative permeability and viscosity, respectively. $\mathbf{u}$, $\mathbf{s}_{u}$ and $p$ are the saturation-weighted Darcy velocity, a source-like term (e.g., gravity forces) associated with the force balance and the pressure.

$\underline{\underline{\sigma}}_{k}$ is an absorption-like term with coupled FE and CV representation of the nonlinear convolution of saturation, relative permeabilities, porosity and permeability tensor fields. This term, representing the viscous frictional forces, is piecewise constant within each FE and is obtained via basis functions local to each CV within each element. An overlapping (or hybrid) basis functions formulation were introduced in \citet{gomes_2013} assuming that there is a (nonlinear) functional that correlates velocity with a FE and the corresponding CVs velocity components basis functions,
\begin{eqnarray} 
 %\sum\limits_{E}\int_{\Omega_E} { {Q}}_i \left({\underline {\underline \sigma}}_k \cdot  {\mathbf u} + \nabla p -{\mathbf s}_u \right) dV +  \displaystyle\frac{1}{2} \oint_{\Gamma_{E}}  {Q}_i {\mathbf n} \left(p - p_{nab}\right) d\Gamma + \nonumber \\
 \sum\limits_{E} \left. \int\limits_{\Omega_E} { {Q}}_i \left({\underline {\underline \sigma}}_k  {\mathbf u} + \nabla p -{\mathbf s}_u \right) dV \right. +  \displaystyle\frac{1}{2} \oint_{\Gamma_{E}}  {Q}_i {\mathbf n} \left(p - p_{nab}\right) d\Gamma + \nonumber \\
 \oint_{\Gamma_{\Omega}} { Q}_i {\mathbf n} \left(p - p_{bc}\right) d\Gamma = \bm{0}
\label{force-semi-disc} 
\end{eqnarray} 
with
\begin{displaymath}
p = \sum\limits_{j=1}^{\mathcal{N}_p} P_{j}p_{j} \;\;\;\;\text{  and  }\;\;\;\; u_k=\sum\limits_{j=1}^{\mathcal{N}_u} Q_{j}u_{k,j}.
\end{displaymath} 
in which $\mathcal{N}_{p}$ and $\mathcal{N}_{u}$ are the number of degrees of freedom for the FE pressure and velocity representations, respectively. $\Omega_E$ is the volume domain of element $E$ associated with the FE velocity, $\Gamma_{E}$ is the surface boundary of $E$ and $\Gamma_{\Omega}$ is the boundary of the entire domain. $p_{nab}$ is the pressure value on the other side of the element boundary neighbouring element $E$.
Phase-saturation equations,
\begin{equation}\label{Eqn:Saturation}
  \phi\displaystyle\frac{\partial \rho_{k} S_{k} }{\partial t}  + \nabla \cdot \left( {\mathbf u}_{k} \rho_{k} S_{k}\right) = s_{cty,k} 
\end{equation}
are discretised in space by testing with CV basis functions and in time with the $\theta$-method,
\begin{eqnarray}
&&
\sum\limits_{k}^{\mathcal{N}_{p}} 
\left\{  
\int_{\Omega} M_{i} \left[  
\displaystyle\frac{ {S_{k}}_{i}^{n} {\nu_{k,i}^{n+1}} \left( {p_{CV}}_{i}^{n+1} - \tilde{p_{CV}}_i^{n+1} \right)} { {\rho_{k}}_{i}^{n} \Delta t } + \displaystyle\frac{ {S_{k}}_{i}^{n} \left( \tilde{ {\rho}_{k}}_{i}^{n+1} - {\rho_{k}}_{i}^{n} \right) } { { \rho_{k}}_{i}^{n} \Delta t }
\right] dV \right. \nonumber \\
&&
\left. 
 + \displaystyle\frac{1}{ {\rho_{k}}_{i}^{n} } \oint_{ {\Gamma_{CV}}_{i}} \mathbf{n} \cdot \mathbf{u}_{k}^{n+\theta} \rho_{k}^{n+\theta} S_{k}^{n+\theta} d\Gamma -\displaystyle\frac{1}{ {\rho_{k}}_{i}^{n} } \int_{\Omega} M_{i} s_{cty,k}^{n+\theta} dV
\right\} = 0,
  \label{detail-global-cty}
\end{eqnarray}
In Eqn. \ref{Eqn:Saturation}, $\phi$, $\rho$ and $s_{cty}$ are the rock-matrix porosity, fluid density and source-like term associated with the global continuity equation. $\nu$ represents the CV-based projection fluids compressibility. Pressure matrix equation is produced by summing the CV-based discretised global mass balance and the overlapping CV-DGFEM-based discretised Darcy equations. At time level $n+1$, the coupled multiphase Darcy and global mass conservation are represented, in matricial form, as
\begin{equation}
\begin{cases}
\mathbf{M}_{\sigma} \underline{\bf u}^{n+1} = \mathbf{C}\underline{\bf p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\
\mathbf{M}_{p} \underline{\bf p}^{n+1} + \mathbf{B}^{T} \underline{\bf u}^{n+1} = \underline{\bf s}_{p}^{n+1}
\end{cases}
\end{equation}

\section{Classical Buckley-Leverett Test-Cases}\label{classical_BL}
The Buckley-Leverett equation \citep[B-L,][]{doster_2011,proskurowski_1981} is commonly used in petroleum industry to represent the displacement of fluids in porous media for oil recovery. When oil is initially produced, the pressure is sufficiently high to force the flow of the oil and gas through the producing wells. However, the rate in which oil is produced drops with time as the pressure naturally decreases. In order to keep the production rate, fluids $\left(\text{e.g., supercritical CO}_{2}\text{ and/or water}\right)$ are injected to drive the oil towards production wells. The B-L equation is a nonlinear advection equation for the relative saturation of fluid phases representing two-phase immiscible flows in porous matrix.

In this section, incompressible two-phase displacements is simulated with water $\left(S_{l}=1\right)$ being injected at a velocity $u_{1}=1$ into a fully saturated porous matrix containing non-wetting and immobile oil $\left(S_{2}=1,\;\phi=0.5\right)$. For relative permeability calculations $\left(\mathcal{K}_{rk}\right)$, the irreducible and residual water saturations are set to 0.2 and 0.1, respectively. The length of the domain is 4 non-dimensional units, the endpoint of oil and water relative permeabilities are 0.3 and 0.8, while Corey exponent is assumed as 2. On the outlet boundary condition, the pressure level is set to zero and all remaining boundary conditions are weakly applied.

Despite the one-dimensional nature of the problem, 2- and 3-D simulations were performed using structured and unstructured meshes to evaluate the multi-dimensional capabilities of the model. In 2- and 3-D simulations, free-slip boundary conditions are applied on the sides of the domain for the two velocity fields.

 All simulations used the overlapping mixed-DGFEM with \PN[0]{1}, \PN[1]{2} and/or \PN[2]{3} element-pairs with continuous / discontinuous (between elements) formulations with saturation collocated at pressure nodes. Although saturation is calculated using a CV formulation, a FEM interpolation is used to form the high-order fluxes and these are also used for most of the plots. In all 1-D simulations, mesh grids were designed with equi-sized elements, whilst 2-D meshes were regular, structured and one-element wide with unity aspect ratio. The width of the 2-D numerical domain is inversely proportional to the number of elements. The time-step size varied linearly within 0.125-3.125$\times$10$^{-3}$ seconds range for 1-D simulations, and 1.0$\times$10$^{-4}$ for all 2- and 3-D simulations.

\subsection{Continuous Formulation}
\paragraph{Upwind Solution} 
In Fig.~\ref{bl-exact-meth-upwind} the CV solution of the water-phase saturation and equivalent quadratic FEM interpolation are presented (\PN[1]{2}). As it can be seen, the solution converges with increased resolution. Notice that the corners of the CVs are very close to the converged solution. This can be explained as the velocities are upwinded (and also the relative permeabilities), and at these corners the equations reach the balance necessary to match the analytical solution.

\paragraph{Convergence Analysis}
Convergence analysis were performed for the 1- and 2-D problems with a number of (regular) mesh resolution and element pairs. The time-step size was linearly varied from 1.25$\times$10$^{-4}$ to 3.25$\times$10$^{-3}$ seconds. Figure~\ref{fig:BL_profiles} shows water-phase saturation profiles at time $t=0.5$ for mesh grids varying from 5 to 500 elements, and for different element types -- \PN[0]{1}, \PN[1]{2} and \PN[2]{3} (the geometry symmetry line is used to extract data from the 2-D simulations).  In general, results are in good agreement with the analytic solution for all resolutions and element-pairs however, for coarser meshes, high-order elements-pairs (\PN[2]{3} for 1-D using 5 elements and \PN[1]{2} for 2-D using 20 elements) perform significantly better and are able to capture the sharp-front more accurately. As far as the 2-D simulations are concerned, the coarse mesh simulation performs slightly worse than its 1-D counterpart but for higher resolutions, results are identical.

These conclusions become clearer in Fig.~\ref{fig:BL_converg-rates}, where convergence rates are shown. The L1 and L2 errors are defined as,
\begin{displaymath}
\displaystyle\frac{\sum\limits_{i=1}^{N}\left|S_{i}^{\text{simulated}}-S_{i}^{\text{analytical}}\right|}{N}\;\;\text{ and }\;\; \displaystyle\frac{\sum\limits_{i=1}^{N}\sqrt{\left(S_{i}^{\text{simulated}}-S_{i}^{\text{analytical}}\right)^{2}}}{N},
\end{displaymath}
respectively, where $S$ is the water-phase saturation. In addition, convergence rates for simulations performed with full upwinding scheme are also shown.

\paragraph{Optimal Upwinding} 
%In order to optimise the upwind formulation (Section~\ref{FluxLimitingSection}), we investigated a 80/20$\%$ up/downwinding ratio -- Fig.~\ref{bl-exact-meth-cv-0-8-ele50}, with good agreement with the converged solution. 
An appropriate upwind fraction may lead to the  increase of accuracy of the formulation -- here the fraction was varied from 1 (full upwinding -- typically applied near shock-fronts) to $\frac{1}{2}$ (i.e., central differencing scheme).  However, even though downwind scheme (for the velocity field) may also help increasing the accuracy we limit the current scheme to central difference. If however, a coupled up/downwind scheme (80/20$\%$ ratio) is chosen then the resulting solution is shown in Fig.~\ref{bl-upwind-v-up-and-down}. Downwind schemes may not be fully consistent with the characteristics of the differential equation, detracting from the accurate solution. Figure~\ref{bl-upwind-v-up-and-down} shows the FEM interpolated solution for the water-phase saturation field using a full optimal upwind (OU) and coupled up/downwind (OU-D: 80/20$\%$) and different mesh resolution. Solutions obtained from OU-D scheme match the converged solution with increasing resolution. The optimal solution for 50 elements using OU and OU-D schemes is shown in Fig.~\ref{bl-exact-meth-cv-0-8-ele50}, with a rapid convergence. For these simulations, there are no oscillations in the corresponding CV solutions -- the FEM interpolation (using Galerkin projection) of the CV solution, however it does show, as expected, oscillatory behaviour near the shock-fronts.

\subsection{Discontinuous Formulation}
In this section, results for the discontinuous formulation between elements are presented. Discontinuity between elements allows the use of coarse meshes to represent abruptly changing of solution fields. Figure~\ref{bl-dg-2eles} shows converged CV water-phase saturation solutions and the corresponding FEM interpolated solutions. This solution was obtained with upwinding within and between the elements.  Convergence rates for the test-cases performed with the fully discontinuous formulation (between elements) are shown in Fig.~\ref{fig:BL_converg-rates_DG}.

Solutions obtained with upwinding and central difference schemes are shown in Fig.~\ref{bl-dg-cent-4-10-20} for different resolutions, and compared against the continuous (converged) solution with good agreement. In this plot, one can also note the suppressed oscillations resulted with the upwinding scheme.

In Figure~\ref{bl-dg-4-10-vers-cty}, saturation solutions obtained from first (P$_{1}$) and second-order (P$_{2}$) in pressure and continuous/discontinuous between elements are shown -- at the coarser resolution, the discontinuous solution is more accurate despite the outstanding accuracy of the continuous formulation. By comparing P$_{1}$ and P$_{2}$ solutions in pressure, we demonstrated that near the shock-front there is little benefit in using high-order discontinuous elements, thus linear elements perform well compared to quadratic elements.

\subsection{2- and 3-D Simulations}
Following the convergence analysis a number of numerical experiments were performed to assess the robustness of the method in fully unstructured meshes. Water-phase saturation surface maps (and the corresponding meshes) for 2- and 3-D simulations at time $t=0.5$ are shown in Fig.~\ref{fig:maps2d_3d}. The simulations presented in this section were performed using the \PN[1]{2} element-pair in fully unstructured mesh-grid.

Saturation profiles for the water phase at time $t=0.5$ are shown in Fig.~\ref{fig:BL_2d_profiles}. Results are not spatially averaged and the geometry symmetry line is used to extract data for all simulations. The structured coarse mesh uses $1 \times 19$ layers in the lateral and flow directions, respectively. The structured medium mesh uses $3 \times 40$ layers. \textcolor{red}{The unstructured mesh grid used XXXX elements.}  The solution field converged towards the analytical solution with the increase of the mesh resolution; additionally, no substantial improvement was observed when structured and unstructured \PN[1]{2} mesh were used. However, the use of unstructured mesh (and potentially higher-order triangle and tetrahedra elements) is advantageous for flow simulation in complex geometries as demonstrated by \cite{jackson_2013}.

\section{Immiscible Displacement in Heterogeneous Porous Matrix}\label{res2}
%\section{A 4-region modified Buckley-Leverett test case}
This test case was designed to demonstrate the numerical robustness of the method when solving multi-fluid flow problems involving heterogeneous porous matrix.  Here, water is injected in a fully saturated $\left(S_{2}=1\right)$ 2-D square porous matrix domain of side length one and uniform porosity $\left(\phi=0.5\right)$ -- Fig. \ref{fig:4reg_BL_schematic}. However, unlike the test-cases in Section \ref{classical_BL}, the permeability field is not uniform and four equally sized $\lq$regions' are designed.  Permeability fields in regions R1 and R4 is 4 times lager than that of regions R2 and R3, i.e.,
\begin{displaymath}
\mathbf{K}^{\text(1)}=\mathbf{K}^{\text(4)}=4\mathbf{K}^{\text(2)}\left(=\mathbf{K}^{\text{(3)}}\right)
\end{displaymath}
Water is uniformly injected at a velocity of $u_{l}=1$ on the left boundary to displace the oil in the porous domain. On the outflow boundary the pressure level is set to zero. Free-slip boundary conditions are applied on the sides of the domain for the two velocity fields. All boundary conditions are applied weakly. For relative permeability calculations $\left(\mathcal{K}_{rk}\right)$, the irreducible and residual water saturations are set to 0.2 and 0.1, respectively; the endpoint of oil and water relative permeabilities are 0.3 and 0.8, while Corey exponent is assumed as 2.

Two sets of simulations are performed using coarse (402 elements with 2412 nodes) and fine (3714 elements with 22284 nodes) meshes; in the first set (A) the overlapping mixed DGFEM and the \PN[1]{2} element-pairs are used, with time-step sizes of 1$\times$10$^{-3}$ and 5$\times$10$^{-4}$ seconds for simulations performed with coarse and fine meshes, respectively. In the second set of experiments (B) \PN[2]{2}DG element-pairs are used, with time-step sizes of 5$\times$10$^{-4}$ and 1$\times$10$^{-4}$ seconds for coarse and fine meshes. \textcolor{red}{(Is there any reason/motivation to use \PN[2]{2}DG??)}

Figure~\ref{fig:4reg_maps} shows the water-phase saturation profile maps (at time $t=0.08$ seconds) for all four simulations. The results yielded by the experiment (A) are depicted in the top left, coarse mesh, and top right, fine mesh. The results obtained from experiment (B) located on the bottom left, coarse mesh, and bottom right, fine mesh. A laboratory experiment with similar setup was performed by \citet{dawe_2008} to investigate miscible and immiscible displacement in heterogeneous permeability and wettability cases.

For the immiscible displacement, water was uniformly injected from the left-hand side boundary (injection rate of $\sim$1 ml/min in a domain of 20$\times$10$\times$0.6 cm, glass ballotini beads produced porosity of 0.4, and permeability ratio of 2.5). Snapshots in Fig.~\ref{fig:4reg_maps} show the water-flood $\lq$fingering' across the central regions (R1 $\Rightarrow$ R4) demonstrating the preferential flow through highly permeable matrix. This is in good qualitative agreement with the lab-experiment \citep[see Figs. 5 and 6 in][]{dawe_2008}.

Figure~\ref{fig:4reg_plots} shows water-phase saturation profiles (at time $t=0.08$ seconds) for all performed  simulations. Comparing the results obtained by both sets of experiments, a better agreement between the results yielded by the simulations (B) -- i.e., with \PN[2]{2}DG element-pairs, can also be observed.

\section{Underground Caisson}\label{res3}
%\section{An embedded-region modified Buckley-Leverett test case}
\label{res3}
In this test-case, we investigated the fluid flow behaviour across two distinct porous matrix characterised by different permeabilities. A low-permeability square region, with dimensions of 0.5 $\times$ 0.5 unit-area, is embedded in a high-permeability region with dimension  1 $\times$ 1. Porosity and permeability ratio are of 0.5 and 10$^{4}$.  Physical properties, initial and boundary conditions used in Section~\ref{res2} are considered for this problem.

Numerical experiments were performed with: (a) \PN[0]{1} and (b) \PN[1]{1}DG element-pairs. The used time-steps size are of 5$\times$10$^{-3}$ and 1$\times$10$^{-4}$ seconds, respectively. Figure~\ref{fig:square_permeability} shows snapshots of water-phase saturation profile at $t = 0.15$ and $t = 0.5$ for both simulations.

Both simulations yield similar results however, the simulation performed with \PN[0]{1} elements shows a dispersion of phase 1 into the low-permeability region, whereas the saturation profile in the \PN[1]{1}DG simulation presents a defined frontier between the low-permeability region and the high-permeability area.

\section{High-Permeability Wedge-Shaped Region}\label{res4}
In this numerical experiment, a wedge-shaped high-permeability region embedded in a rectangular low-permeability (permeability ratio of 100) domain is considered. The permeability map and associated unstructured mesh is shown in Fig.~\ref{fig:wedge_permeability}. The non-dimensional rectangular domain is 1 $\times$ 0.1 and the wedge is defined by a high of 0.025 and a slope of $1/30$. The porosity is uniform and equal to 0.5. Initially, the porous media is fully saturated with an incompressible fluid $\left(S_{2}=1\right)$. An immiscible fluid is injected from the left boundary with a constant pressure of 1 and a saturation of $S_{1}=0.5$. On the outflow boundary, the pressure level is set to zero.

Free-slip boundary conditions were applied on the sides of the domain for the two velocity fields. All remaining boundary conditions were applied weakly and relative permeability relationship are defined as in Section~\ref{classical_BL}. Simulations were performed with \PN[0]{1} and \PN[1]{1}DG element-pairs with time-step sizes of 1$\times$10$^{-3}$ and 1$\times$10$^{-5}$ seconds, respectively.

Figure~\ref{fig:wedge_permeability} shows the water-phase saturation maps at times $t=0.08$ and $t=0.12$ seconds. In the \PN[0]{1}-based numerical experiment, we can see a dispersion of the water-phase in the vicinity of the wedge due to the use of continuous FEM formulation used for the saturation. On the other hand, for the \PN[1]{1}DG simulation, a well-defined boundary of the water-phase within the wedge can be observed. %It can be observed that for this problem the results obtained by both type of elements differs substantially.

\section{Conclusions}\label{conc}
This article is the second in a series of papers describing a new mixed DGFEM formulation model for multi-fluid flows. In the first paper, we described the new model which is based upon two computational building blocks: (a) consistent pressure-velocity formulation in a dual mesh-spaces that led to the new overlapping control volume discontinuous Galerkin finite element method (OCV-DGFEM), and (b) a new family of triangle / tetrahedron element types -- \PN[n]{n+1} originally designed for geo-fluid dynamics problems. The novel formulation, although generic in nature \citep[thus not restricted to porous media applications as demonstrated by][for interface tracking problems]{pavlidis_2013b,pavlidis_2013c}, has demonstrated numerical robustness and accuracy in multi-fluid subsurface flow problems.

The focus of this paper is two-fold: to demonstrate the model accuracy in multi-fluids subsurface flows and, to exploit the new formulation to solve problems involving highly heterogeneous porous media.

The classical Buckley-Leverett problem was used to assess model's convergence, accuracy and performance of the upwind formulation. We demonstrated that the solutions obtained from the model summarised here \citep[see][for a full description]{gomes_2013} are in good agreement with analytical solutions even if a (relatively) coarse resolution and low-order accuracy element-pairs are used.  Water-phase saturation profiles obtained from the fully discontinuous formulation was successfully compared against the continuous-based solutions with half of the grid resolution.

In order to assess the performance of the formulation for heterogeneities in permeability field across the porous matrix, we successfully compared the water-flood behaviour of the numerical solution against laboratory experiments. Additional tests involving high-permeability ratios, skewed elements, low- and high-order element-pairs and unstructured mesh were performed to assess the accuracy and performance of the upwind velocity / permeability formulation.

Overall, in these two initial papers we demonstrated the flexibiity and numerical accuracy of the new multi-fluids flow model formulation. The model (i.e., \PN[0]{1}, \PN[1]{2}, \PN[2]{3}, \PN[1]{1}DG, \PN[1]{2}DG and \PN[2]{2}DG element-pairs, continuous/discontinuous formulation between elements, dual velocity-pressure balance -- overlapping CV-DGFEM formulation, hybrid CV-FEM representation for heterogeneous derived-based material properties -- e.g.,  permeability fields and mesh-based weighted up/downwind schemes for velocity and permeability fields) was successfully validated against: (a) analytical solutions for advection-diffusion equations and (b) classical Buckley-Leverett problem. The flow behavior in subsurface water-flood conditions was qualitatively validated against lab-scale experiments. Further validation tests will need to be performed to rigorously assess the permeability and wettability effects in gravity-driven subsurface flows.

%The second part of this series of papers explores the computational model framework for 2- and 3-D dimensions and focuses on heterogeneous multiphase porous media flow validation test-cases.

\ack 
Dr D. Pavlidis would like to acknowledge the support from the following research grants: EPSRC ($\lq$Computational Modelling for Advanced Nuclear Power Plants') and EU/FP7 ($\lq$Thermo-Hydraulics for Innovative Nuclear Systems' -- THINS). Funding for Dr P. Salinas from the Qatar Carbonates and Carbon Storage Research Centre (QCCSRC), provided jointly by Qatar Petroleum, Shell and the Qatar Science and Technology Park, is gratefully acknowledged. Dr Z. Xie is supported by EPSRC ($\lq$Multi-Scale Exploration of Multiphase Physics in Flows' -- MEMPHIS). Part funding for Profs. Jackson and Muggeridge under the TOTAL Chairs programme at Imperial College is also acknowledged.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv}
\bibliography{references}

\pagebreak
\clearpage

\listoffigures
\pagebreak
\clearpage

\input{article_figure1}
%\input{article_figure2}

\end{document}

%%
%% End of tex file.

### 2015-01-19 Papers/Prototype_2_Method/diagrams/article_figure1.tex

--- 2015-01-19 Papers/Prototype_2_Method/article_figure1.tex
@@
-%\begin{comment}
+\begin{comment}
 %%%
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{./diagrams/bl-exact-meth-upwind}
+\includegraphics[width=1.\textwidth]{bl-exact-meth-upwind}
 \end{center}
@@
 
-%\end{comment}
+\end{comment}
 %%%
@@
 \vbox{\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P0DGP1_convergence.eps}}
+    \includegraphics[width=0.62\textwidth]{BL_1d_P0DGP1_convergence.eps}}
 \vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P1DGP2_convergence.eps}}
+    \includegraphics[width=0.62\textwidth]{BL_1d_P1DGP2_convergence.eps}}
 \vspace{-.0cm}\hbox{\hspace{2.5cm}
-    \includegraphics[width=0.62\textwidth]{./diagrams/BL_1d_P2DGP3_convergence.eps}}}
+    \includegraphics[width=0.62\textwidth]{BL_1d_P2DGP3_convergence.eps}}}
     \caption{Buckley-Leverett test-cases: 1-D Saturation profiles for a number of element pairs and grid resolutions -- \PN[0]{1} (top), \PN[1]{2}, \PN[2]{3} (bottom).\label{fig:BL_profiles}}
@@
 \vbox{\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{./diagrams/L1_convergence_rate}}
+    \includegraphics[width=0.8\textwidth]{L1_convergence_rate}}
 \vspace{.0cm}\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{./diagrams/L2_convergence_rate}}}
+    \includegraphics[width=0.8\textwidth]{L2_convergence_rate}}}
     \caption{Buckley-Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of (continuous) element pairs. \label{fig:BL_converg-rates}}
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{./diagrams/bl-upwind-v-up-and-down}
+\includegraphics[width=1.\textwidth]{bl-upwind-v-up-and-down}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{./diagrams/bl-exact-meth-cv-0-8-ele50}
+\includegraphics[width=1.\textwidth]{bl-exact-meth-cv-0-8-ele50}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.\textwidth]{./diagrams/bl-dg-2eles}
+\includegraphics[width=1.\textwidth]{bl-dg-2eles}
 \end{center}
@@
 \vbox{\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{./diagrams/L1_convergence_rate_DG.eps}}
+    \includegraphics[width=0.8\textwidth]{L1_convergence_rate_DG.eps}}
 \vspace{.0cm}\hbox{\hspace{1.cm}
-    \includegraphics[width=0.8\textwidth]{./diagrams/L2_convergence_rate_DG.eps}}}
+    \includegraphics[width=0.8\textwidth]{L2_convergence_rate_DG.eps}}}
     \caption{Buckley-Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of fully discontinuous (between elements) element pairs. \label{fig:BL_converg-rates_DG}}
@@
 \vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-4-10-20}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-20}}
 \vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-cent-4-10-20}}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-cent-4-10-20}}}
 \caption{Buckley-Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulation with different mesh resolutions.
@@
 \vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-4-10-vers-cty}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-4-10-vers-cty}}
 \vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{./diagrams/bl-dg-p1-2-4-5-10-20-40}}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{bl-dg-p1-2-4-5-10-20-40}}}
 \caption{Buckley-Leverett test-cases: Saturation field obtained from (top) continuous and discontinuous (between elements) formulations (solution with 50 elements may be considered as a converged result).
@@
 \hbox{\hspace{.2cm}
-    \includegraphics[width=1.\textwidth]{./diagrams/map_2d.png}}
+    \includegraphics[width=1.\textwidth]{map_2d.png}}
 \vspace{1.cm}
 \hbox{\hspace{0.2cm}
-    \includegraphics[width=1.\textwidth]{./diagrams/map_3d.png}}}
+    \includegraphics[width=1.\textwidth]{map_3d.png}}}
     \caption{Buckley-Leverett test-cases: phase 1 saturation surface maps for a 2- (770 triangles) and 3-D (1207 tetrahedra) simulations (\PN[1]{2} unstructured mesh grids) at time $t=0.5$.
@@
 \vbox{\hbox{\hspace{.3cm}
-    \includegraphics[width=0.9\textwidth]{./diagrams/BL_2d_P1DGP2_convergence.eps}}
+    \includegraphics[width=0.9\textwidth]{BL_2d_P1DGP2_convergence.eps}}
 \vspace{-.0cm}\hbox{\hspace{.3cm}
-    \includegraphics[width=0.9\textwidth]{./diagrams/simulations_2d_3d.eps}}}
+    \includegraphics[width=0.9\textwidth]{simulations_2d_3d.eps}}}
     \caption{Buckley-Leverett test-cases: 2- and 3-D phase 1 saturation profiles with \PN[1]{2} elements.
@@
   \begin{center}
-    \includegraphics[width=0.65\textwidth]{./diagrams/4Rregion_BL}
+    \includegraphics[width=0.65\textwidth]{4Rregion_BL}
     \caption{Heterogeneous permeability test-cases: schematic including boundary conditions. Darker areas (R1 and R4) represent regions with high permeability.\label{fig:4reg_BL_schematic}}
@@
 \vbox{\hbox{
-\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{./diagrams/CG_coarse083.png}
-\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{./diagrams/CG_fine083.png}}
+\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{CG_coarse083.png}
+\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{CG_fine083.png}}
 \vspace{1.cm}\hbox{
-\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{./diagrams/DG_coarse083.png}
-\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{./diagrams/DG_fine083.png}}}
+\hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{DG_coarse083.png}
+\hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{DG_fine083.png}}}
  \caption{Heterogeneous permeability test-cases: phase 1 saturation maps at time $t=0.08$ seconds.
@@
   \begin{center}
-    \includegraphics[width=0.475\textwidth]{./diagrams/down_left_top_right083}
-    \includegraphics[width=0.475\textwidth]{./diagrams/Top_left-Down_right083}
-    \includegraphics[width=0.475\textwidth]{./diagrams/X04_083}
-    \includegraphics[width=0.475\textwidth]{./diagrams/y04_083}
+    \includegraphics[width=0.475\textwidth]{down_left_top_right083}
+    \includegraphics[width=0.475\textwidth]{Top_left-Down_right083}
+    \includegraphics[width=0.475\textwidth]{X04_083}
+    \includegraphics[width=0.475\textwidth]{y04_083}
     \caption{Heterogeneous permeability test-cases: phase 1 saturation profiles at time $t=0.08$ seconds.
@@
 \hbox{
-\hspace{3.5cm} \includegraphics[width=0.5\textwidth]{./diagrams/square_permeability_low}}
+\hspace{3.5cm} \includegraphics[width=0.5\textwidth]{square_permeability_low}}
 \vspace{0.5cm}
 \hbox{
-\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/cg_square_015_low}
-\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/cg_square_05_low}}
+\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{cg_square_015_low}
+\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{cg_square_05_low}}
 \vspace{0.5cm}
 \hbox{
-\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/dg_square_015_low}
-\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{./diagrams/dg_square_05_low}}}
+\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{dg_square_015_low}
+\hspace{-0.cm}\includegraphics[width=0.5\textwidth]{dg_square_05_low}}}
  \caption{Underground Caisson: Initial configuration of porous matrix consisting of a low-permeability square embedded in a high-permeability region (top).
@@
 \hbox{
-\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_permeability}}
+\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{wedge_permeability}}
 \vspace{-1.cm}\hbox{\hspace{4cm}(a) Permeability map}
@@
 \hbox{
-\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_0011}}
+\hspace{-0.cm}\includegraphics[width=1.05\textwidth]{wedge_0011}}
 \vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 0.011$ seconds }
@@
 \hbox{
-\hspace{-.cm}\includegraphics[width=1.05\textwidth]{./diagrams/wedge_0014}}
+\hspace{-.cm}\includegraphics[width=1.05\textwidth]{wedge_0014}}
 \vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 0.014$ seconds }
@@
 \hbox{
-\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_perm}}
+\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{3d_perm}}
 \vspace{-0.cm}\hbox{\hspace{4cm}(a) Permeability map}
@@
 \hbox{
-\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_first}}
+\hspace{-0.cm}\includegraphics[width=0.85\textwidth]{3d_first}}
 \vspace{-0.cm}\hbox{\hspace{4cm}(b) $t= 7.9$ years }
@@
 \hbox{
-\hspace{-.cm}\includegraphics[width=0.85\textwidth]{./diagrams/3d_second}}
+\hspace{-.cm}\includegraphics[width=0.85\textwidth]{3d_second}}
 \vspace{-0.cm}\hbox{\hspace{4cm}(c) Internal section }

### 2015-01-19 Papers/Prototype_1_Method/article.tex
Updates in Paper 1, one step towards finishing BL description and analysis.

@@
 \newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
 
@@
 The Buckley-Leverett (B-L) equation is a nonlinear advection equation for the relative saturation of fluid phases representing immiscible two-phase flows in porous media.
-Here, water $\left(S_{l}=1\right)$ is injected at a velocity $u_{g}\phi=1$.
-On the outlet boundary condition, the pressure level is set to zero and all remaining boundary conditions are naturally applied.
-A converged time step of $1\times 10^{-3}$ is used for all simulations and applications with the continuous and discontinuous between element formulations.
-All simulations used the overlapping mixed FEM with a piecewise linear variation of the velocity within each element and quadratic pressure $\left(\text{P}_{1}\text{DG-P}_{2}\right)$.
-Saturation is colocated at the pressure nodes and although it is calculated using a CV formulation, a FEM interpolation is used to form the high-order fluxes.
+Here, a fluid (phase 1) $\left(S_{1}=1\right)$ is injected at constant velocity $u_{1}=1$ into a rock matrix ($\phi=0.5$) fully saturated with a second fluid (phase 2), $S_{2}=1$.
+Relative permeability $\left(\mathcal{K}_{r\alpha}\right)$ is calculated as a quadratic function of saturation with residual saturation of phases 1 and 2  of $S_{1}=0.1$ and $S_{2}=0.3$, respectively.
+The endpoint of the relative permeabilities  of phases 1 and 2 are 0.8 and 0.3, respectively.
 
+The length of the domain is 4 non-dimensional units.
+On the outlet boundary condition, the pressure level is set to zero and all remaining boundary conditions are weakly applied.
+Despite the one-dimensional nature of the problem, 2- and 3-D simulations were performed using structured and unstructured meshes to evaluate the multi-dimensional capabilities of the model.
+
+All simulations used the overlapping mixed-DGFEM with \PN[0]{1}, \PN[1]{2} and/or \PN[2]{3} element-pairs with continuous /  discontinuous (between elements) formulations with saturation collocated at pressure nodes.
+Although saturation is calculated using  a CV formulation, a FEM interpolation is used to form the high-order fluxes and these are also used for most of the plots.
+
+In all 1-D simulations, mesh grids were designed with equi-sized elements, whilst 2-D meshes were regular, structured and one-element wide with unity aspect ratio.
+The width of the 2-D numerical domain is inversely proportional to the number of elements.
+The time-step size varied linearly within 0.125-3.125$\times$10$^{-3}$ seconds range for 1-D simulations, and a fixed time-step of 1.0$\times$10$^{-4}$ for all 2- and 3-D simulations.
+
+\medskip
 Control volume solution of water saturation and equivalent quadratic FEM interpolation are shown in Fig.~\ref{bl-exact-meth-upwind}, where solution converges with increased resolution.

### 2015-01-20 Papers/Prototype_1_Method/article.tex
Updating Prototype Paper 1. Just need a final read and send to partners.

@@
 \newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
 
@@
 The time-step size varied linearly within 0.125-3.125$\times$10$^{-3}$ seconds range for 1-D simulations, and a fixed time-step of 1.0$\times$10$^{-4}$ for all 2- and 3-D simulations.
+In the simulations shown here the fluids are considered incompressible.
 
 \medskip
-Control volume solution of water saturation and equivalent quadratic FEM interpolation are shown in Fig.~\ref{bl-exact-meth-upwind}, where solution converges with increased resolution.
+Control volume saturation profile of phase 1 and equivalent quadratic FEM interpolation are shown in Fig.~\ref{bl-exact-meth-upwind}, where solution converges with increased resolution.
 Notice that the corners of the CV's are very close to the converged solution.
 This can be explained as the velocities are upwinded (and also the relative permeabilities -- see Section~\ref{opt-up}), and at these corners the equations reach the balance necessary to match the analytical solution.
-Despite the one-dimensional nature of the problem, 2- and 3-D simulations were performed using structured and unstructured meshes and reported in the second part of this two-part paper.
+
+\subsubsection{Convergence Analysis}
+Convergence analyses were performed for the 1- and 2-D problems with a number of (regular) mesh resolution and element pairs.
+The time-step size was linearly varied from 1.25$\times$10$^{-4}$ to 3.25$\times$10$^{-3}$ seconds.
+Figure~\ref{fig:BL_profiles} shows phase 1 saturation profiles at time $t=0.5$ for mesh grids varying from 5 to 500 elements, and for different element types -- \PN[0]{1}, \PN[1]{2} and \PN[2]{3} (the geometry symmetry line is used to extract data from the 2-D simulations).
+
+In general, results are in good agreement with the analytic solution for all resolutions and element-pairs however, for coarser meshes, high-order elements-pairs (\PN[2]{3} for 1-D using 5 elements and \PN[1]{2} for 2-D using 20 elements) perform significantly better and are able to capture the sharp-front more accurately.
+
+As far as the 2-D simulations are concerned (Fig.~\ref{fig:BL_2d_profiles}), the coarse mesh simulation performs slightly worse than its 1-D counterpart but for higher resolutions, results are identical.
+These conclusions become clearer in Fig.~\ref{fig:BL_converg-rates}, where convergence rates are shown.
+In addition, convergence rates for simulations performed with full upwinding scheme are shown.
+
+\subsubsection{Discontinuous Formulation}
+Discontinuity of the pressure field between elements allows the use of coarse meshes to represent abrupt changes in the solution.
+Figure~\ref{bl-dg-2eles} shows converged CV phase 1 saturation solutions and the corresponding FEM interpolated solutions.
+This solution was obtained with upwinding within and between the elements.
+Convergence rates for the test-cases performed with the fully discontinuous formulation (between elements) are shown in Fig.~\ref{fig:BL_converg-rates_DG}.
+
+Solutions obtained with upwinding and central difference schemes are shown in Fig.~\ref{bl-dg-cent-4-10-20} for different resolutions, and compared against the continuous (converged) solution with good agreement.
+In this plot, one can also note the suppression of oscillations resulting from the upwinding scheme.
+
+In Figure~\ref{bl-dg-4-10-vers-cty}, saturation solutions obtained using first (P$_{1}$) and second-order (P$_{2}$) functions in the FE representation of pressure are shown both for continuous and discontinuous representations.
+At coarse resolution the discontinuous solution is more accurate.
+By comparing P$_{1}$ and P$_{2}$ solutions in pressure, we demonstrate that near the shock-front there is little benefit in using high-order discontinuous elements, thus linear elements perform well compared to quadratic elements.
+
+\subsubsection{2- and 3-D Simulations}
+Following the convergence analysis, a number of numerical experiments were performed to assess the robustness of the method in fully unstructured meshes.
+Phase 1 saturation surface maps (and the corresponding meshes) for 2- and 3-D simulations at time $t=0.5$ are shown in Fig.~\ref{fig:maps2d_3d}.
+The simulations presented in this section were performed using the \PN[1]{2} element-pair in fully unstructured mesh-grid.
+
+Saturation profiles for the phase 1 at time $t=0.5$ are shown in Fig.~\ref{fig:BL_2d_profiles}.
+Results are not spatially averaged and the geometry symmetry line is used to extract data for all simulations.
+The structured coarse mesh uses $1 \times 19$ layers in the lateral and flow directions, respectively.
+The structured medium mesh uses $3 \times 40$ layers.
+The solution field converged towards the analytical solution with the increase of the mesh resolution.
+Additionally, no substantial improvement was observed when structured and unstructured \PN[1]{2} mesh were used.
+However, the use of unstructured mesh (and potentially higher-order triangle and tetrahedra elements) is advantageous for flow simulation in complex geometries as demonstrated by \citet{jackson_2013} \citep[also in][]{mostaghimi_2015}.
 
 \section{Final Remarks}\label{conc}
-This article is the first in a two-part papers describing the new overlapping control volume finite element method (OCVFEM) for multi-fluid flows.
-The new formulation is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of element types $\left(\text{P}_{n}\text{DG-P}_{n+1}\right.$, P$_{n}$DG-P$_{n}$ and $\left.\text{P}_{n}\text{DG-P}_{n}\text{DG}\right)$, and has been applied to hybrid multi-component interface-tracking models~\citep{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular flows~\citep{percival_2014} and to reservoir simulation~ \citep{jackson_2013}.
+This article is the first in a two-part papers describing the new overlapping control volume finite element method (OCVFEM) for multi-fluid flows in porous media.
+The new formulation is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of element types, \PN[n]{n+1}, \PN[n]{n} and \PNDG[n]{n}.
+Saturation and other scalar fields (e.g., density, temperature etc) are discretised in CV space and may be fully discontinuous across finite element boundaries $\left(\text{in \PNDG[n]{n} elements}\right)$.
+Material absolute permeability tensor is piecewise constant in FE space to ensure the correct representation of the surface.
+For a quadratic pressure variation there is a piecewise linear velocity field, with discontinuities at element and control volume boundaries.
+
+The formulation has been extended to hybrid multi-component interface-tracking models~\citep{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular flows~\citep{percival_2014} and to reservoir simulation~\citep{jackson_2013,mostaghimi_2015}.
 The aim of this paper is to describe the formulation of this approach embodied in the \href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity} software framework for multiphase flows in porous media, and the initial model validation.
 
-\jrp{ Again, is this the limit of what we can claim?} The OCVFEM was specially tailored to ensure that in the limit of uniform permeability -- ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$, the balance in 1D Darcy multiphase flow equations is strictly enforced.
-Saturations are \jrp{what?} collocated (piecewise constant) in control volume space whereas the material absolute permeability tensor is piecewise constant in FE space to ensure the correct representation of the surface.
-Moreover, the velocity field (for each phase) is described as a function of $\underline{\underline{\sigma}}$ and pressure.
-\jrp{We may want to rethink this sentence} For a quadratic pressure variation there will be a piecewise linear velocity field, with discontinuities at element and control volume boundaries.
+In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the DGFEM formulation and control volumes within finite elements.
+The resulting method was initially validated for advection problems showing good accuracy and convergence for the continuous and discontinuous (between elements) formulations.
+We also demonstrated the accuracy of the upwind formulation.
+The classical Buckley-Leverett problem was used to assess model convergence, accuracy and performance of the upwind formulation.
+The solutions obtained from the current formulation are in good agreement with analytical solutions even when a (relatively) coarse mesh resolution and low-order accuracy element-pairs are used.
+Saturation profiles obtained from the fully discontinuous formulation were successfully compared against the continuous-based solutions with lower grid resolution.
 
-In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the DGFEM formulation and control volumes within finite elements.
-\jrp{Pure advection doesn't really test the whole method though?} The resulting method was initially validated for advection problems showing good accuracy and convergence for the continuous and discontinuous (between elements) formulations.
-We also demonstrated the accuracy of the upwind formulation.
-In the second part of this two part paper we explore the computational model framework for 2- and 3-D dimensions and focus on heterogeneous multiphase porous media flows.
+In the second part of this paper~\citep{pavlidis_2015}, the formulation and methods are further validated against experimental solutions in more complex geometries and flows.
+In particular, the formulation is used to solve problems involving highly heterogeneous regions.
 

### 2015-01-20 Papers/Prototype_1_Method/article_figure2.tex
Updating Prototype Paper 1. Just need a final read and send to partners.

@@
 \begin{center}
+\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
+\end{center}
+\caption{Buckley--Leverett test-cases: Two element solution using the discontinuous formulation. Saturation field from both CV solution and FEM interpolation are shown.  \label{bl-dg-2eles}}
+\end{figure}
+
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\vbox{\hbox{\hspace{1.cm}
+    \includegraphics[width=0.8\textwidth]{diagrams/L1_convergence_rate_DG.eps}}
+\vspace{.0cm}\hbox{\hspace{1.cm}
+    \includegraphics[width=0.8\textwidth]{diagrams/L2_convergence_rate_DG.eps}}}
+    \caption{Buckley-Leverett test-cases: L1 (top) and L2 (bottom) error convergence rates for a number of fully discontinuous (between elements) element pairs. \label{fig:BL_converg-rates_DG}}
+\end{figure}
+
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
+\vspace{-0.cm}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
+\caption{Buckley--Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulations with different mesh resolutions.
+Solutions with (top) and without (bottom) upwinding scheme.
+Notice that oscillations are suppressed with the upwinding scheme.\label{bl-dg-cent-4-10-20}}
+\end{figure}
+
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
+\vspace{-0.cm}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
+\caption{Buckley--Leverett test-cases: Saturation field obtained from (top) continuous and discontinuous (between elements) formulations (solution with 50 elements may be considered as a converged result).
+Solution obtained (bottom) from linear pressure $\left(\text{P}_{1}\right)$ formulation with different mesh resolution with comparison against P$_{2}$-pressure formulation (continuous).
+\label{bl-dg-4-10-vers-cty}}
+\end{figure}
+
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{.2cm}
+    \includegraphics[width=1.\textwidth]{diagrams/map_2d.png}}
+\vspace{1.cm}
+\hbox{\hspace{0.2cm}
+    \includegraphics[width=1.\textwidth]{./diagrams/map_3d.png}}}
+    \caption{Buckley-Leverett test-cases: phase 1 saturation surface maps for a 2- (770 triangles) and 3-D (1207 tetrahedra) simulations (\PN[1]{2} unstructured mesh grids) at time $t=0.5$.
+\label{fig:maps2d_3d}}
+\end{figure}
+
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\vbox{\hbox{\hspace{.3cm}
+    \includegraphics[width=0.9\textwidth]{diagrams/BL_2d_P1DGP2_convergence.eps}}
+\vspace{-.0cm}\hbox{\hspace{.3cm}
+    \includegraphics[width=0.9\textwidth]{./diagrams/simulations_2d_3d.eps}}}
+    \caption{Buckley-Leverett test-cases: 2- and 3-D phase 1 saturation profiles with \PN[1]{2} elements.
+Sensitivity analysis for (top) grid resolution using structured \PN[1]{2} mesh, and (bottom) mesh type.\label{fig:BL_2d_profiles}}
+\end{figure}
+
+\begin{comment}
+%%%
+%%%  FIGURE 
+%%%
+\begin{figure}[h]
+\begin{center}
 \includegraphics[width=1.\textwidth]{diagrams/bl-upwind-v-up-and-down.eps}
@@
 %%%
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=1.\textwidth]{diagrams/bl-dg-2eles.eps}
-\end{center}
-\caption{Buckley--Leverett test-cases: Two element solution using the
-  discontinuous formulation. Saturation field from both CV solution
-  and FEM interpolation are shown.  \label{bl-dg-2eles}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
-\vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
-\caption{Buckley--Leverett test-cases: Saturation field obtained from
-  the discontinuous and continuous formulation with different mesh
-  resolutions. Solutions with (top) and without (bottom) upwinding
-  scheme. Notice that oscillations are suppressed with the upwinding
-  scheme.\label{bl-dg-cent-4-10-20}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-vers-cty.eps}}
-\vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-p1-2-4-5-10-20-40.eps}}}
-\caption{Buckley--Leverett test-cases: Saturation field obtained from
-  (top) continuous and discontinuous (between elements) formulations
-  (solution with 50 elements may be considered as a converged
-  result). Solution obtained (bottom) from linear pressure (P1)
-  formulation with different mesh resolution with comparison against
-  P2-pressure formulation (continuous). \label{bl-dg-4-10-vers-cty}}
-\end{figure}
-
-%%%
-%%%  FIGURE 
-%%%
 \begin{figure}[H]
@@
 
-\begin{comment}
-%%%
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{.2cm}
-    \includegraphics[width=1.\textwidth]{diagrams/map_2d.png}}
-\vspace{1.cm}
-\hbox{\hspace{0.2cm}
-    \includegraphics[width=1.\textwidth]{./diagrams/map_3d.png}}}
-    \caption{Buckley-Leverett test-cases: phase 1 saturation surface maps for a 2- (770 triangles) and 3-D (1207 tetrahedra) simulations (\PN[1]{2} unstructured mesh grids) at time $t=0.5$.
-\label{fig:maps2d_3d}}
-\end{figure}
-
-%%%  FIGURE 
-%%%
-\begin{figure}[h]
-\vbox{\hbox{\hspace{.3cm}
-    \includegraphics[width=0.9\textwidth]{diagrams/BL_2d_P1DGP2_convergence.eps}}
-\vspace{-.0cm}\hbox{\hspace{.3cm}
-    \includegraphics[width=0.9\textwidth]{./diagrams/simulations_2d_3d.eps}}}
-    \caption{Buckley-Leverett test-cases: 2- and 3-D phase 1 saturation profiles with \PN[1]{2} elements.
-Sensitivity analysis for (top) grid resolution using structured \PN[1]{2} mesh, and (bottom) mesh type.\label{fig:BL_2d_profiles}}
-\end{figure}
+%\begin{comment}
 
 \end{comment}
+
+%\end{comment}

### 2015-01-20 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Updated paragraph on Objective (Para1) and Method (Para2)

--- 2015-01-16 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
@@
 
-\title{Reservoir Simulation using a Deterministic Heterogeneity Permeability Data}
+\title{Reservoir Simulation using a Deterministic Heterogeneity generated from a discrete Permeability Data}
 
@@
 \begin{abstract}
-This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
-The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
-Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.
 
-The overlapping control volume finite element method (OCVFEM) formulation, makes use of triangular and tetrahedral finite element pairs to represent the model properties.
-A P0DG meshing scheme is used for permeability in this simulation therefore the nodal data point for permeability are defined as discontinous data points at the centre of each tethrahedral element.
-The permeability data for the deterministic heterogeneity is spatially assigned within the simulation domain.
-And using the deterministic data, 3D interpolation is performed to determine the nodal data for the P0DG meshing scheme.
+This paper presents an arguement for using a deterministic heterogeneous data for reservoir simulation, instead of the homogeneous data in use currently, within the Oil and Gas industry.
+It then goes on to describe a method of creating a deterministic heterogeneity from a set of discrete data for permeability.
+Finally, the paper discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
+Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection was simulated and benchmarked, for this paper.
 
-\red{Yet to obtain any information on the simulation}\\
+The overlapping control volume finite element method (OCVFEM) formulation is capable of using a deterministic heterogeneous data for reservoir simulation.
+It employes triangular and tetrahedral finite element pairs in representing the model properties.
+Permeability is the property used to carry out the analysis discussed in this report.
+And, a P0DG meshing scheme is used for it in the simulation carried out.
+This means the nodal data point for permeability are defined as discontinous data points at the centre of each tethrahedral element.
+The permeability data for the deterministic heterogeneity is spatially assigned within the simulation domain through a two stage process.
+First, a suitable mesh size is selected which would allow the available discrete data, to be optimized for the second stage of the process.
+And the second stage is the determination of each nodal data value for the P0DG meshing scheme using 3D interpolation technique.
+
+\red{Yet to obtain any information on the simulation}
+
 \red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}
 
-\sout{Currently available reservoir simulators require a homogeneous data input for a property such as permeability.
-Hence, upscaling is performed to determine a suitable equivalent value to be used in the simulation.} This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain.
+\red{Results, Conclusions. As we do not have them yet, you could briefly describe the preliminary results and the aim of validating the methods against the SPE10}.
+
+This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain.
 This has two advantages.
@@
 
-In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM and higher order meshing schemes would be used.
+In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM, and higher order meshing schemes would be used.
 The paper would also make use of stochastic methods for data representation.

### 2015-01-21 Papers/Prototype_1_Method/article.tex
Paper 1 is updated taking into account comments from Pain, Percival and Jackson. Different from the previous version of the paper (under SVN), results of the Buckley-Leverett problems in 1-3D were introduced (based on existing plots and comments of Prototype Paper 2

@@
 Secondly, it uses a family of finite element types that ensures multiphase Darcy equations can be exactly enforced.
-The underlying mass conservation equations are solved in control volume space and finite elements are used to obtain high-order fluxes on control volume boundaries.
-The novelty of the method lies in (a) permitting both continuous and discontinuous description of pressures and saturations between elements; (b) the use of arbitarily high-order polynomial representation for pressure and velocity within the mixed formulation; (c) the use of high-order flux-limited methods to avoid introducing non-physical oscillations as well as achieving high-order time accuracy where and when possible.
+The underlying mass conservation equations are solved in control volume space whereas finite elements are used to obtain high-order fluxes on control volume boundaries.
+The novelty of the method lies in (a) permitting both continuous and discontinuous description of pressures and saturations between elements; (b) the use of arbitarily high-order polynomial representation for pressure and velocity within the mixed formulation and; (c) the use of high-order flux-limited methods to avoid introducing non-physical oscillations as well as achieving high-order time accuracy where and when possible.
 In this paper, the new model is described and test cases are introduced to show the numerical accuracy in one- and two-dimensional simulations.
-More extensive applications are introduced in the second part of this two part paper.
+More extensive applications are introduced in the second part of this two-part paper.
 \end{abstract}
@@
 Among FEM-based formulations for porous media, the control volume finite element method (CVFEM) has become increasingly popular as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, cordazzo_2004, geiger_2004, hurtado_2007}.
-\citet{huber_2000} demonstrated that the vertex-centred finite volume - finite element method (or Box scheme) can achieve similar goals~\citep[see also][]{helmig_1997}.
+\citet{huber_2000} demonstrated that the vertex-centred finite volume -- finite element method (or Box scheme) can achieve similar goals~\citep[see also][]{helmig_1997}.
 
@@
 
-In this paper, we describe a novel overlapping CVFEM (or OCVFEM) discretisation which is conservative and consistent \citep{jackson_2013}.
+In this paper, we describe a novel overlapping CVFEM (or OCVFEM) formulation which is conservative and consistent.
 The continuity equations are embedded into the pressure equation to enforce mass conservation and exact force balance.
@@
 The formulation has two key developments.
-Firstly, it uses a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a family of triangular and tetrahedral finite element-pairs, P$_{n}$DG-P$_{m}$[DG] \citep[see][]{cotter_2009b}.
+Firstly, it uses a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a family of triangular and tetrahedral finite element-pairs, \PN[n]{m}[DG]~\citep[see][]{cotter_2009b}.
 In this element type, the dual velocity and pressure fields are represented by $n^{\rm th}$ order (discontinuous) and $m^{\rm th}$ order (continuous/discontinuous) polynomials, respectively.
-This allows the velocity to exactly represent pressure gradients in the flow solution for homogeneous material properties.
-The P$_{n+1}$DG-P$_{n}$DG element-pair, which has similar properties to the P$_n$DG-P$_{n+1}$ element-pair, allows a representation in which pressure, %\jrp{Saturation is on the control volume space and thus always discontinuous}
-saturation and other solution variables are all fully discontinuous across finite element boundaries.
+Such flexibility allows the velocity to exactly represent pressure gradients in the flow solution for homogeneous material properties (e.g., \PN[1]{2}).
+The \PNDG[n+1]{n} element-pair, which has similar properties to the \PN[n]{n+1} element-pair, allows a representation in which pressure, saturation and other solution variables are all fully discontinuous across finite element boundaries.
 The second key development is that this formulation uses an overlapping finite element representation of velocity within each element.
@@
 This is the first of two papers on the proposed methodology.
-Here we focus on model description and initial validation, whereas in the second part~\citep{pavlidis_2013} we employ the numerical formulation for a number of multiphase porous media flow simulations to demonstrate numerical accuracy and convergence rates.
+Here we focus on model description and initial validation, whereas in the second part, \citet{pavlidis_2015} apply the numerical formulation to a number of multiphase porous media flow problems to demonstrate numerical accuracy and convergence rates.
 The remainder of this paper is organised as follows.
 New element types and the overlapping formulation are introduced in Sections~\ref{element_types_section} and~\ref{overlapping_method_section}.
-A detailed description of the new porous media methods is given in Section~\ref{transport_methods_section}.
-Scalar field equations, upwinding schemes and solution methods are introduced in Sections~\ref{Section:Saturation_Global}-\ref{Section:SolvingLinearEqns}.
+Detailed description of the new methods is given in Section~\ref{transport_methods_section}-\ref{Section:SolvingLinearEqns}.
 Initial model validation is presented in Section~\ref{Section:Results} and final remarks are drawn in Section~\ref{conc}.
@@
 The family of P$_{n}$DG-P$_{n+1}$ element-pairs was originally introduced by \citet{cotter_2009a} for geophysical fluid dynamics applications \citep[see also][]{cotter_2012}.
-In particular, the P$_{1}$DG-P$_{2}$ element-pair was originally developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes.
+In particular, the P$_{1}$DG-P$_{2}$ element-pair was developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes.
 This element-pair uses element-wise linear polynomial FE basis functions, discontinuous across element interfaces for velocity $\left(\text{P}_{1}\text{DG}\right)$, and quadratic polynomial finite element basis functions for pressure which maintain $C_{\text{0}}$ continuity across element boundaries $\left(\text{P}_{2}\right)$.
@@
 Figure~\ref{fem_cv_represent_a} displays three element types of the P$_{n}$DG-P$_{n+1}$ family that are used in this set of papers.
-P$_{\text{0}}$DGP$_{\text{1}}$ and P$_{1}$DG-P$_{2}$ are shown in Fig.~\ref{fem_cv_represent_a}(a) and (b), respectively, where pressure nodes are stored in the vertices and edges (in P$_{\text{2}}$ elements) of triangular/tetrahedral elements and control volumes are constructed around them based on a Voronoi decomposition.
+P$_{\text{0}}$DGP$_{\text{1}}$ and P$_{1}$DG-P$_{2}$ are shown in Fig.~\ref{fem_cv_represent_a}(a) and (b), respectively, where pressure nodes are stored in the vertices and edges (in P$_{\text{2}}$ elements) of triangular/tetrahedral elements.
+Control volumes are constructed around them based on a Voronoi decomposition.
 One can realise that due to the continuous finite element node structure, control volumes span more than one element.
 Having CV's spanning to multiple elements may create artificial diffusion in cases where there are large variations in physical properties across elements, such as at the boundary between materials with different absolute permeabilities.
-As an alternative, two families of fully discontinuous element-pairs are also considered: P$_{n}$DG-P$_{n}$DG and P$_{n+1}$DG-P$_{n}$DG~\citep[Fig.~\ref{fem_cv_represent_a}(c), applications using these element-pairs are exploited in][]{pavlidis_2015} along with control volumes from their dual Voronoi decompositions.
+As an alternative, two families of fully discontinuous element-pairs are also considered: \PNDG[n]{n} and \PNDG[n+1]{n}~\citep[Fig.~\ref{fem_cv_represent_a}(c), applications using these element-pairs are exploited in][]{pavlidis_2015} along with control volumes from their dual Voronoi decompositions.
 These families of element-pairs are LBB stable and free from chequerboard pressure modes, as previously demonstrated by~\citet{cotter_2009b}~\citep[see also][]{cotter_2011}.
@@
 where $\mathbf{q}_{\alpha}=\left(q_\alpha^{(1)},q_\alpha^{(2)},q_\alpha^{(3)}\right)^{\text{T}}$ is the $\alpha$-th phase Darcy flow rate for 3D flows, $\mathbf{K}$ is the absolute permeability tensor of the porous matrix, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$ and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure and a source term, respectively.
+$\mu_{\alpha}$, $p_{\alpha}$ and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure and source term, respectively.
 
@@
 \begin{equation}
-  \bm{v}_\alpha:= {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+  \mathbf{v}_{\alpha}:= {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
   \label{force-bal}
 \end{equation}
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces and $\bm{v}_\alpha$ is a saturation averaged vector of the force density of the phase, related to the advective velocity through $\bm{u}_\alpha={\underline {\underline \sigma}}_{\alpha}^{-1}\bm{v}_\alpha$.% arising in the derivation of extended Darcy's law.
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces and $\mathbf{v}_\alpha$ is a saturation averaged vector of the force density of the phase, related to the advective velocity through $\mathbf{u}_\alpha={\underline {\underline \sigma}}_{\alpha}^{-1}\mathbf{v}_\alpha$.% arising in the derivation of extended Darcy's law.
 
@@
 \begin{displaymath}
-  \bm{v}_\alpha(\bm{r},t) = \sum\limits_{j=1}^{\mathcal{N}_u} Q_{j}(\bm{r})\bm{v}_{\alpha,j}(t) \;\;\;\;\text{ and } \;\;\;\; p(\bm{r},t)  = \sum\limits_{j=1}^{\mathcal{N}_p} P_{j}(\bm{r})p_{j}(t).
+  \mathbf{v}_\alpha(\bm{r},t) = \sum\limits_{j=1}^{\mathcal{N}_u} Q_{j}(\bm{r})\mathbf{v}_{\alpha,j}(t) \;\;\;\;\text{ and } \;\;\;\; p(\bm{r},t)  = \sum\limits_{j=1}^{\mathcal{N}_p} P_{j}(\bm{r})p_{j}(t).
 \end{displaymath} 
@@
 \end{equation}
-where the velocity $\left(\underline{\bf v}\right)$ and pressure $\left(\underline{\bf p}\right)$ solution-vectors are defined as,
+where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are defined as,
 \begin{eqnarray}
@@
 \end{eqnarray}
-$\mathcal{N}_{\alpha}$ is the number of phases and $v_x$, $v_y$, $v_z$ are the the velocity components associated with the $x-$ and $y-$ and $z-$ coordinates, respectively.
+$\mathcal{N}_{\alpha}$ is the number of phases and $v_x$, $v_y$, $v_z$ are the components associated with the $x-$ and $y-$ and $z-$ coordinates, respectively.
 
@@
   && \left[{\mathbf M}^{(i,j)}\right]_{p,q} = \int_{\Omega}  Q_{p} \delta_{ij}
-{Q}_{q}  dV, \\
-  && {\left[\bm{C}^{(i,i)}\right]_{p,q} = \int_{\Omega} Q_{p} \frac{\partial P_{q}}{\partial r_i} dV - \oint_{\Gamma_{E}} \displaystyle\frac{1}{2} Q_{p} n_i^{(E,q)} P_{q} d\Gamma -  \oint_{\Gamma_{\Omega}} \displaystyle Q_{p} n_i P_{q} d\Gamma} \\
-  && {\left[\bm{s}_{u}^{(i,i)}\right]_{p} = \int_{\Omega} Q_p} \left[{\mathbf s}_{u}\right]_i dV - \oint_{\Gamma_{\Omega}}\displaystyle Q_{p} n_i p_{bc} d\Gamma.
+{Q}_{q}  dV, \nonumber \\
+  && {\left[\bm{C}^{(i,i)}\right]_{p,q} = \int_{\Omega} Q_{p} \frac{\partial P_{q}}{\partial r_i} dV - \oint_{\Gamma_{E}} \displaystyle\frac{1}{2} Q_{p} n_i^{(E,q)} P_{q} d\Gamma -  \oint_{\Gamma_{\Omega}} \displaystyle Q_{p} n_i P_{q} d\Gamma}, \nonumber \\
+  && {\left[\bm{s}_{u}^{(i,i)}\right]_{p} = \int_{\Omega} Q_p} \left[{\mathbf s}_{u}\right]_i dV - \oint_{\Gamma_{\Omega}}\displaystyle Q_{p} n_i p_{bc} d\Gamma. \nonumber
 \end{eqnarray}
@@
 The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-Thus the viscous-friction damping tensor, \jrp{This tensor needs a good name JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
+Thus the viscous-friction damping tensor, %\jrp{This tensor needs a good name JG: I can't think on a good name for this -- it's too non-linear to hold any physical meaning.
 Maybe solid-fluid homogeneisation factor/ parameter/ coeff or viscous-friction damping ...} %${\underline{\underline \sigma}}_{\alpha}$:
@@
 is piecewise constant within the sub-volumes defined through the non-empty intersections between the elements and control volumes; in the pressure discontinuous formulation, these are precisely the control volumes themselves, Fig.~\ref{fem_cv_represent_a}(c).
-The velocity, formed by the action of ${\underline{\underline \sigma}}_{\alpha}^{-1}$ upon the force density $\bm{v}_\alpha$, has an exact polynomial representation on the sub-volumes of one degree lower that of $p$.
+The velocity, formed by the action of ${\underline{\underline \sigma}}_{\alpha}^{-1}$ upon the force density $\mathbf{v}_\alpha$, has an exact polynomial representation on the sub-volumes of one degree lower that of $p$.
 For example, for a quadratic pressure variation there will be a piecewise linear velocity field, with discontinuities at element and control volume boundaries (Fig.~\ref{fig:darcys_law}).
@@
 \end{equation}
-where \text{T} is a scalar field, $\mathbf{a}$ is the advection velocity vector, $\textit{t}$ and $\textit{s}$ are time and a source term, respectively.
+where \text{T} is a scalar field, $\mathbf{a}$ is the advection velocity vector, $\textit{t}$ and $\textit{s}$ are time and source term, respectively.
 The problem is discretised by testing the weak form of the equation over each CV $i$ using a set of test functions, $M_{i}$, which are unity over control volume $i$ and zero otherwise.
@@
 where $\mathbf{n}$ is the outward pointing unit normal vector to the surface of CV$_{i}$.
-Gaussian quadrature are used to approximate the surface integral over each face of CV$_{i}$.
+Gaussian quadratures are used to approximate the surface integral over each face of CV$_{i}$.
 To close the system, the value $\widetilde{T}$ at the quadrature integration points on the surface of the control volume must be calculated from the CV solution, \textit{T}.
@@
 \begin{displaymath}
-  \mathbf{B} = \int_{\Omega} N_{i}N_{j} \,dV \;\;\;\;\text{and}\;\;\;\; \mathbf{Q} = \int_{\Omega} N_{i} M_{j} \,  dV,
+  \mathbf{B} = \int_{\Omega} N_{i}N_{j} \,dV \;\;\;\;\text{and}\;\;\;\; \mathbf{Q} = \int_{\Omega} N_{i} M_{j} \,  dV.
 \end{displaymath} 
-and
-\begin{displaymath}
-\underline{\mathbf{T}}_{\text{FEM}} = \left({T_{\text{FEM}}}_{1}, \ldots, {T_{\text{FEM}}}_{\mathcal{N}} \right)^{T} \text{ and } \underline{\mathbf{T}} =\left(T_{1}, T_{2}, \ldots, T_\mathcal{M} \right)^{T},
-\end{displaymath}
-contain the FE and CV values of {\it T}, respectively.
+$\underline{\mathbf{T}}_{\text{FEM}} = \left({T_{\text{FEM}}}_{1}, \ldots, {T_{\text{FEM}}}_{\mathcal{N}} \right)^{T}$ and $ \underline{\mathbf{T}} =\left(T_{1}, T_{2}, \ldots, T_\mathcal{M} \right)^{T}$ contain the FE and CV values of {\it T}, respectively.
 Since we are using high-order approximations, extrema must be detected in order to determine where to apply first order fluxes instead of high-order.
@@
 \end{eqnarray}
-in which $\theta^{n+\frac{1}{2}}$ is obtained (as described in Section~\ref{time_discretisation}) with $S_\alpha$ replacing T. Assuming the natural incompressible mass conservation constraint,
+in which $\theta^{n+\frac{1}{2}}$ is obtained with $S_\alpha$ replacing T in Eqn.~\ref{theta}. Assuming the natural incompressible mass conservation constraint,
 \begin{equation}
@@
 The discontinuities occur between (a) elements in the discontinuous formulation and (b) control volumes within each FE.
-An average velocity is defined as,
+An average velocity at the interface of control volumes {\it i} and {\it j} is defined as,
 \begin{equation}
@@
 \tilde{\bf u}_{\alpha i}, & \text{for } {\bf n}\cdot{\bf a}_{\alpha}>0 \text{ (CV {\it i} outgoing information);} \\
+                        &                                                                                      \\
 \tilde{\bf u}_{\alpha j}, & \text{for } {\bf n}\cdot{\bf a}_{\alpha}<0 \text{ (CV {\it i} incoming information).} 
@@
 The sign of ${\bf n}\cdot {\bf a}_\alpha$ is used to determine the upwind direction.
-From this high-order flux limited saturation, $\tilde{\sigma}_{\alpha} = \sigma_{\alpha}\left(\tilde{S}_{\alpha}\right)$ can be obtained.
-Knowing $\tilde S_\alpha$ the corresponding interface value of $\sigma_\alpha$ can be estimated, $\tilde\sigma_\alpha$, from the second-order Taylor series.
+From this high-order flux limited saturation $\tilde{\sigma}_{\alpha} = \sigma_{\alpha}\left(\tilde{S}_{\alpha}\right)$ can be obtained.
+Knowing $\tilde{S}_{\alpha}$, the corresponding interface value of $\sigma_\alpha$ $\left(\text{i.e., }\tilde{\sigma}_{\alpha}\right)$ can be estimated from second-order Taylor series.
+
 For ${\bf n}\cdot {\bf a}_\alpha>0$ (CV $i$ outgoing information):
@@
 
-For two neighbouring CV's $i$ and $j$ which have a common FE interface, ${\bf u}_{\alpha}$ can be calculated by using a volume weighting.
+For two neighbouring CV's $i$ and $j$ with common FE interface, ${\bf u}_{\alpha}$ can be calculated by using a volume weighting.
 However, the volume $\mathcal{V}$ of the control volume and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity ${\bf u}_{\alpha}$ in a very similar way.
@@
 
-\medskip
 Similarly, boundary conditions can be applied using Riemann variables to determine if information is travelling into or out of the domain (although most flow simulation models do not follow this more rigorous approach).
-Specified pressure boundary conditions for outlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ are ${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf u}_\alpha$ nor ${S_\alpha}$ are specified.
 
 \medskip
-Specified pressure boundary conditions for the inlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ are defined as,
+Specified pressure boundary conditions for outlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ are ${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf u}_\alpha$ nor ${S_\alpha}$ are specified.
+For the inlet flux $\left(\right.$when ${\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ are defined as,
 \begin{displaymath}
@@
 \section{Solving the Linear Equations}\label{Section:SolvingLinearEqns}
-The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and force balance equations (Eqn.~\ref{force-balance-matrix-form}) are solved by substituting out the force density term and solving the system of equations for pressure.
+The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and force balance equations (Eqn.~\ref{force-balance-matrix-form}) are solved by substituting the force density term and solving the system of equations for pressure.
 At time level $n+1$, Eqns.~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can be rewritten as:
@@
 The computationally demanding effort to solve the pressure matrix equation arising from the fully discontinuous FEM formulation is achieved using a multigrid-like approach.
-In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating, from the discontinuous system, a continuous system by collapsing the pressure nodes.
+In this case the $\lq$fine' mesh is the one obtained by the discontinuous system, whereas the $\lq$coarse' mesh is obtained by creating a continuous system (from the discontinuous system) by collapsing the pressure nodes.
 As in multigrid, the coarse mesh solution is used to accelerate the convergence of the fine mesh solution by calculating the error of the current approximation.
@@
   T\left( x,0\right)= \begin{cases} 1, \;\; &  0.2 \le  x \le 0.4, \\
-    0, & \mbox{ otherwise,}
+    0, & \mbox{ otherwise.}
   \end{cases}
 \end{displaymath}
-are specified.
 Control volumes are interpolated using FEM basis functions.
@@
 
-Figures~\ref{compar-dg-bdt-diff} and~\ref{theta-bdt} demonstrate the advection capturing capability of our method with continuous $\left(\text{P}_{n}\text{DG-P}_{n+1}\text{ element-pairs}\right)$ and discontinuous $\left(\text{either}\right.$ P$\left._{n}\text{DG-P}_{n}\text{DG  or P}_{n+1}\text{DG-P}_{n}\text{DG elements-pairs}\right)$ formulations.
+Figures~\ref{compar-dg-bdt-diff} and~\ref{theta-bdt} demonstrate the advection capturing capability of our method with continuous (\PN[n]{n+1} element-pairs) and discontinuous (either \PNDG[n]{n} or \PNDG[n+1]{n} element-pairs) formulations.
 In Fig.~\ref{theta-bdt}, these formulations are compared in a problem with large time step size.
@@
 The Buckley-Leverett (B-L) equation is a nonlinear advection equation for the relative saturation of fluid phases representing immiscible two-phase flows in porous media.
-Here, a fluid (phase 1) $\left(S_{1}=1\right)$ is injected at constant velocity $u_{1}=1$ into a rock matrix ($\phi=0.5$) fully saturated with a second fluid (phase 2), $S_{2}=1$.
+Here, a fluid $\left(\text{phase 1, S}_{1}=1\right)$ is injected at constant velocity $u_{1}=1$ into a rock matrix ($\phi=0.5$) fully saturated with a second fluid (phase 2), $S_{2}=1$.
 Relative permeability $\left(\mathcal{K}_{r\alpha}\right)$ is calculated as a quadratic function of saturation with residual saturation of phases 1 and 2  of $S_{1}=0.1$ and $S_{2}=0.3$, respectively.
@@
 Notice that the corners of the CV's are very close to the converged solution.
-This can be explained as the velocities are upwinded (and also the relative permeabilities -- see Section~\ref{opt-up}), and at these corners the equations reach the balance necessary to match the analytical solution.
+This can be explained as the velocities are upwinded (and also the relative permeabilities -- see Section~\ref{opt-up}) and at these corners the equations reach the balance necessary to match the analytical solution.
 
@@
 In Figure~\ref{bl-dg-4-10-vers-cty}, saturation solutions obtained using first (P$_{1}$) and second-order (P$_{2}$) functions in the FE representation of pressure are shown both for continuous and discontinuous representations.
-At coarse resolution the discontinuous solution is more accurate.
+At coarse resolution, the discontinuous solution is more accurate.
 By comparing P$_{1}$ and P$_{2}$ solutions in pressure, we demonstrate that near the shock-front there is little benefit in using high-order discontinuous elements, thus linear elements perform well compared to quadratic elements.
@@
 The formulation has been extended to hybrid multi-component interface-tracking models~\citep{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular flows~\citep{percival_2014} and to reservoir simulation~\citep{jackson_2013,mostaghimi_2015}.
-The aim of this paper is to describe the formulation of this approach embodied in the \href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity} software framework for multiphase flows in porous media, and the initial model validation.
+The aim of this paper is to describe the formulation of this approach embodied in the open-source \href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity} software framework for multiphase flows in porous media, and the initial model validation.
 
@@
 
-In the second part of this paper~\citep{pavlidis_2015}, the formulation and methods are further validated against experimental solutions in more complex geometries and flows.
+In the second part of this paper~\citep{pavlidis_2015}, the formulation and methods are further validated against experimental solutions in complex geometries, composite materials (i.e., highly heterogeneous regions) and flow regimes.
 In particular, the formulation is used to solve problems involving highly heterogeneous regions.

### 2015-01-21 Papers/Prototype_1_Method/article_figure1.tex
Paper 1 is updated taking into account comments from Pain, Percival and Jackson. Different from the previous version of the paper (under SVN), results of the Buckley-Leverett problems in 1-3D were introduced (based on existing plots and comments of Prototype Paper 2

@@
 }
-\caption{2D representation of the element-pairs (a) P0DGP1, (b) P1DGP2  and (c) P2DGP1DG.
+\caption{2D representation of the element-pairs (a) \PN[0]{1}, (b) \PN[1]{2} and (c) \PNDG[2]{1}.
 Shaded areas denote a control volumes (in which saturation is stored), black points represent the pressure nodes and the white points the velocity.}
@@
 \caption{Diagram showing the exact representation of Darcy's law in 1D.
-From top to bottom, the plots show i) a P2 continuous pressure field, $p$, across three elements, ii) the P1DG gradient of that  pressure field, iii) a P0DG absolute permeability field, ${\bf K}$, iv) a CV mobility field, $\lambda_{k}=\frac{\mathcal{K}_{rk}\left(S_{k}\right)}{\mu_{k}}$, and finally v) the resultant CV0DG velocity field arising from Darcy's law.
-Here dashed lines denote the boundaries of the P2 finite element mesh, dotted lines denote boundaries between the control volumes dual to the P2 mesh and solid dots indicate the natural locations of degrees of freedom in a non-overlapping formulation.
+From top to bottom, the plots show i) a P$_{2}$ continuous pressure field, $p$, across three elements, ii) the P$_{1}$DG gradient of that  pressure field, iii) a P$_{0}$DG absolute permeability field, ${\bf K}$, iv) a CV mobility field, $\lambda_{k}=\frac{\mathcal{K}_{rk}\left(S_{k}\right)}{\mu_{k}}$, and finally v) the resultant CV$_{0}$DG velocity field arising from Darcy's law.
+Here dashed lines denote the boundaries of the P$_{2}$ finite element mesh, dotted lines denote boundaries between the control volumes dual to the P$_{2}$ mesh and solid dots indicate the natural locations of degrees of freedom in a non-overlapping formulation.
 }

### 2015-01-21 Papers/Prototype_1_Method/article_figure2.tex
Paper 1 is updated taking into account comments from Pain, Percival and Jackson. Different from the previous version of the paper (under SVN), results of the Buckley-Leverett problems in 1-3D were introduced (based on existing plots and comments of Prototype Paper 2

@@
 \vbox{
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}
 \vspace{-0.cm}
-\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-cent-4-10-20.eps}}}
+\hbox{\hspace{.3cm}\includegraphics[width=.9\textwidth]{diagrams/bl-dg-4-10-20.eps}}}
 \caption{Buckley--Leverett test-cases: Saturation field obtained from the discontinuous and continuous formulations with different mesh resolutions.
-Solutions with (top) and without (bottom) upwinding scheme.
+Solutions without (top) and with (bottom) upwinding scheme.
 Notice that oscillations are suppressed with the upwinding scheme.\label{bl-dg-cent-4-10-20}}

### 2015-01-23 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
Updated result paragraph and amended section word lenght

--- 2015-01-16 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
@@
 \maketitle
-%\section*{Abstract}
+
 \begin{abstract}
-discrete or deterministic?
-This paper demonstrates that the Overlapping Control Volume Finite Element Method (OCVFEM) for Reservoir Simulation can make full use of the deterministic heterogeneity data provided without resorting to upscaling.
-The results from this simulation would be benchmarked against the results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE 10 project).
-Although, only the first case from the SPE 10 project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection, would be simulated for this paper.
 
-The overlapping control volume finite element method (OCVFEM) formulation, makes use of triangular and tetrahedral finite element pairs to represent the model properties.
-A P0DG meshing scheme is used for permeability in this simulation therefore the nodal data point for permeability are defined as discontinous data points at the centre of each tethrahedral element.
-The permeability data for the deterministic heterogeneity is spatially assigned within the simulation domain.
-And using the deterministic data, 3D interpolation is performed to determine the nodal data for the P0DG meshing scheme.
+This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a homogeneous data.
+Then it describes a method of creating a deterministic heterogeneity.
+Finally, it discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project).
+Albeit, only the first case from the SPE10 Project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection.
 
-\red{Yet to obtain any information on the simulation}\\
-\red{Try to highlight the preliminary results and what you expect to obtain 'till June/July.}
+The overlapping control volume finite element method (OCVFEM) formulation is capable of using deterministic heterogeneity for reservoir simulation.
+It employes triangular and tetrahedral finite element pairs in representing the model properties.
+A P0DG meshing scheme is used for permeability, to perform this analysis.
+This means the nodal data points are defined as discontinous, at the centre of each tetrahedral element.
+The deterministic heterogeneity is spatially assigned within the domain in two stages.
+First, a suitable mesh size is selected to optimize the use of the discrete data.
+Then, each nodal data value is determined using a 3D interpolation technique.
 
-\sout{Currently available reservoir simulators require a homogeneous data input for a property such as permeability.
-Hence, upscaling is performed to determine a suitable equivalent value to be used in the simulation.} This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain.
+The tetrahedral meshing produced more elements (cells) than the given fine grid (100 x 1 x 20) in an effort to optimized the discrete data available.
+The interpolation scheme used allowed the permeability profile to change gradually between discrete data points.
+Three different mesh sizes were used to explain the relevance of optimizing the mesh size.
+And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator.
+For the preliminary simulation result, as expected, the flow profile shows a high velocity in the high permeability region and a low velocity in the low permeability region.
+Therefore, the simulation gives a better understanding of the displacement front and helps to give a realistic view of the movement of the fluids in the reservoir.
+
+This novel method of reservoir simulation does not require upscaling but instead makes use of the heterogeneous data available within the simulation domain.
 This has two advantages.
@@
 
-In a future paper, the second problem of the 10th SPE Comparative Solution Project would be simulated with the OCVFEM and higher order meshing schemes would be used.
-The paper would also make use of stochastic methods for data representation.
 \end{abstract}

### 2015-01-23 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
A few modifications into the paper ...

@@
 
-This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a homogeneous data.
-Then it describes a method of creating a deterministic heterogeneity.
-Finally, it discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project).
-Albeit, only the first case from the SPE10 Project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection.
+This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a homogeneous data\JG{I don't understand this sentence.
+Homogenous data $\times$ heterogeneous data?}.
+Then it describes a method of creating a deterministic heterogeneity\JG{what do you mean w deterministic heterogeneity?}.
+Finally, it discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project)\JG{Suggestion: Finally, the XXX (what sort of solution) solution is benchmarked against the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project).}.
+Albeit, only the first case from the SPE10 Project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection\JG{I guess you missed the second part of the sentence}.
 
-The overlapping control volume finite element method (OCVFEM) formulation is capable of using deterministic heterogeneity for reservoir simulation.
-It employes triangular and tetrahedral finite element pairs in representing the model properties.
-A P0DG meshing scheme is used for permeability, to perform this analysis.
-This means the nodal data points are defined as discontinous, at the centre of each tetrahedral element.
+The overlapping control volume finite element method (OCVFEM) formulation is capable of using deterministic heterogeneity \red{?} for reservoir simulation.
+It employes \red{a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a novel family of} \sout{triangular and} tetrahedral finite element-pairs \sout{in representing the model properties}.
+A P0DG \red{(you haven't defined this symbol ...)} meshing scheme is used \red{to represent the} \sout{for} absolute permeability tensor field \sout{, to perform this analysis}.
+This means the nodal data points are \red{discontinuously} defined \sout{as discontinous,} at the centre of each tetrahedral element.
 The deterministic heterogeneity is spatially assigned within the domain in two stages.
-First, a suitable mesh size is selected to optimize the use of the discrete data.
+First, a suitable mesh size is selected to optimize the use of the discrete data \red{you are being too vague ...}.
 Then, each nodal data value is determined using a 3D interpolation technique.
 
-The tetrahedral meshing produced more elements (cells) than the given fine grid (100 x 1 x 20) in an effort to optimized the discrete data available.
+The tetrahedral meshing produced more elements \sout{(cells)} than the given fine \red{hexahedral grid of SPE10 test} (100 x 1 x 20) in an effort to optimize the discrete data available.
 The interpolation scheme used allowed the permeability profile to change gradually between discrete data points.
-Three different mesh sizes were used to explain the relevance of optimizing the mesh size.
-And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator.
+Three different mesh sizes were used to explain the relevance of optimizing the mesh size\red{(what do you mean?)}.
+And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator \red{(?)}.
 For the preliminary simulation result, as expected, the flow profile shows a high velocity in the high permeability region and a low velocity in the low permeability region.
@@
 First, it removes the need for a computation for upscaling.
-Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.
+Second, flow simulation within the domain is similar to that of a real-life heterogeneous reservoir.\JG{(a) Try to first explain what you mean with deterministic heterogeneity!
+(b) You need to be more concise (i.e., less vague).}
 

### 2015-05-10 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex

--- 2015-01-23 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex
@@
 \newcommand{\JG}[1]{\todo[color=blue!30, size=\small]{JG: #1}}
+\newcommand{\TL}[1]{\todo[color=green!20, size=\small]{TL: #1}}
 \newcommand{\red}{\textcolor{red}}
@@
 %\address[UoA]{School of Engineering, University of Aberdeen, UK}
-%\address[IC]{Department of Earth Science and Engineering, Imperial College London, UK}
+%\address[IC]{Department of Earth Science and Engineering, Imperial College Londdefineon, UK}
 
@@
 
-This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a homogeneous data.
-Then it describes a method of creating a deterministic heterogeneity.
-Finally, it discusses the outcome of a benchmark performed against other simulation results from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project).
-Albeit, only the first case from the SPE10 Project, which involves upscaling and pseudoization methods for an easily computed 2D gas-injection.
+ Deterministic heterogeniety for permeability means that the value of permeability is known exactly everywhere within the reservoir.
+This paper discusses the benefits of using a deterministic heterogeneous data for reservoir simulation, instead of a single equivalent (upscaled)/ homogeneous value.
+Then it describes a method of creating deterministic heterogeneity.
+Finally, the solution for Cumulative Oil Produced is benchmarked against that of other participants of the first case from the 10$^{\text{th}}$ SPE Comparative Solution Project (SPE10 project).
 
-The overlapping control volume finite element method (OCVFEM) formulation is capable of using deterministic heterogeneity for reservoir simulation.
-It employes triangular and tetrahedral finite element pairs in representing the model properties.
-A P0DG meshing scheme is used for permeability, to perform this analysis.
-This means the nodal data points are defined as discontinous, at the centre of each tetrahedral element.
+The overlapping control volume finite element method (OCVFEM) formulation is capable of using properties with deterministic heterogeneity.
+It employes a dual consistent pressure-velocity representation in CV and FEM spaces embedded in a novel family of tetrahedral finite element-pairs.
+The absolute permeability tensor field is represented as discontinuous nodal data points defined at the centre of each tetrahedral element; henceforth denoted as P0DG.
 The deterministic heterogeneity is spatially assigned within the domain in two stages.
 First, a suitable mesh size is selected to optimize the use of the discrete data.
-Then, each nodal data value is determined using a 3D interpolation technique.
+Then, each nodal data value is determined using 3D interpolation.
 
-The tetrahedral meshing produced more elements (cells) than the given fine grid (100 x 1 x 20) in an effort to optimized the discrete data available.
+The tetrahedral meshing produced more elements than the given fine hexahedral grid of SPE10 test (100 x 1 x 20), in an effort to optimize the discrete data available.
 The interpolation scheme used allowed the permeability profile to change gradually between discrete data points.
-Three different mesh sizes were used to explain the relevance of optimizing the mesh size.
-And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator.
-For the preliminary simulation result, as expected, the flow profile shows a high velocity in the high permeability region and a low velocity in the low permeability region.
+Three different mesh sizes were used to explain the relevance of optimizing the mesh size with respect to the distance between the nearest discrete data points.
+And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator \red{(?)} \TL{Just to explain that the mesh size selected was not arbitrary}.
+The simulation was for an easily computed 2D gas-injection.
+For he preliminary simulation result, as expected, the flow profile shows a high velocity in the high permeability region and a low velocity in the low permeability region.
 Therefore, the simulation gives a better understanding of the displacement front and helps to give a realistic view of the movement of the fluids in the reservoir.

### 2015-08-12 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
renaming directory

%\documentclass[11pts,a4paper,amsmath,amssymb,floatfix]{article}%{report}%{book}
\documentclass[12pts,a4paper,amsmath,amssymb,floatfix]{article}%{report}%{book}
\usepackage{graphicx,wrapfig}% Include figure files
%\usepackage{dcolumn,enumerate}% Align table columns on decimal point
\usepackage{bm,dpfloat}% bold math
\usepackage[pdftex,bookmarks,colorlinks=true,urlcolor=rltblue,citecolor=blue]{hyperref}
\usepackage{amsfonts,amsmath,amssymb,stmaryrd,indentfirst}
%\usepackage{chemist}
\usepackage{times,psfrag}
\usepackage{natbib}
\usepackage{color}
\usepackage{units}
\usepackage{rotating}
\usepackage{multirow}
\usepackage{gantt}
\usepackage{pdflscape}

\usepackage{enumerate}%,enumitem}% Align table columns on decimal point

%\usepackage{pifont}
%\usepackage{subfigure}
%\usepackage{subeqnarray}
%\usepackage{ifthen}

\usepackage{supertabular}
\usepackage{moreverb}
\usepackage{listings}
\usepackage{palatino}
%\usepackage{doi}
\usepackage{longtable}
\usepackage{float}
\usepackage{perpage}
\MakeSorted{figure}
%\usepackage{pdflscape}

\definecolor{rltblue}{rgb}{0,0,0.75}

%\usepackage{natbib}
\usepackage{fancyhdr} %%%%
\pagestyle{fancy}%%%%
% with this we ensure that the chapter and section
% headings are in lowercase
%%%%\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\fancyhf{} %delete the current section for header and footer
\fancyhead[LE,RO]{\bfseries\thepage}
\fancyhead[LO]{\bfseries\rightmark}
\fancyhead[RE]{\bfseries\leftmark}
\renewcommand{\headrulewidth}{0.5pt}
% make space for the rule
\fancypagestyle{plain}{%
\fancyhead{} %get rid of the headers on plain pages
\renewcommand{\headrulewidth}{0pt} % and the line
}

\def\newblock{\hskip .11em plus .33em minus .07em}
\usepackage{color}

%\usepackage{makeidx}
%\makeindex

%\setlength\textwidth      {17.cm}
%\setlength\textheight     {21.6cm}
%\setlength\oddsidemargin  {0.0cm}
%\setlength\evensidemargin {0.0cm}

%\setlength\headheight{14.49998pt} 
%\setlength\topmargin{0.0cm}
%\setlength\headsep{1.cm}
%\setlength\footskip{1.cm}
%\setlength\parskip{0pt}
%\setlength\parindent{0pt}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=20mm,
 top=30mm,
 bottom=25mm,
 }

%%%
%%% Headers and Footers
\lhead[] {\text{\small{iCO$_{2}$-EGS}}} 
%\rhead[]{{\text{\small{CoMaELa}}}}
\rhead[]{\text{\small{Reducing Uncertainty in the Integrity of Potential CCS Sites}}}
%\rhead[] {{\text{\small{Reducing Uncertainty in the Integrity of Potential CCS Sites}}}}
%\chead[] {\text{\small{Session 2012/13}}} 
\lfoot[]{{\today}}
%\cfoot[\thepage]{\thepage}
\rfoot[\text{\small{\thepage}}]{\thepage}
\renewcommand{\headrulewidth}{0.8pt}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[version=3]{mhchem}

\makeatletter
\newcounter{reaction}
%%% >> for article <<
\renewcommand\thereaction{C\,\arabic{reaction}}
%%% << for article <<
%%% >> for report and book >>
%\renewcommand\thereaction{C\,\thechapter.\arabic{reaction}}
%\@addtoreset{reaction}{chapter}
%%% << for report and book <<
\newcommand\reactiontag{\refstepcounter{reaction}\tag{\thereaction}}
\newcommand\reaction@[2][]{\begin{equation}\ce{#2}%
\ifx\@empty#1\@empty\else\label{#1}\fi%
\reactiontag\end{equation}}
\newcommand\reaction@nonumber[1]{\begin{equation*}\ce{#1}%
\end{equation*}}
\newcommand\reaction{\@ifstar{\reaction@nonumber}{\reaction@}}
\makeatother

%%%
%%% Notes
%%%
\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{\color{blue} JG: #1}}}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}{\textcolor{green}}

%%%
%%% space between lines
%%%
\renewcommand{\baselinestretch}{1.}

\newenvironment{VarDescription}[1]%
  {\begin{list}{}{\renewcommand{\makelabel}[1]{\textbf{##1:}\hfil}%
    \settowidth{\labelwidth}{\textbf{#1:}}%
    \setlength{\leftmargin}{\labelwidth}\addtolength{\leftmargin}{\labelsep}}}%
  {\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%%      NOTATION SECTION        %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Text abbreviations.
\newcommand{\ie}{{\em{i.e., }}}
\newcommand{\eg}{{\em{e.g., }}}
%XS\newcommand{\cf}{{\em{cf., }}}
\newcommand{\wrt}{with respect to}
\newcommand{\lhs}{left hand side}
\newcommand{\rhs}{right hand side}
% Commands definining mathematical notation.

% This is for quantities which are physically vectors.
\renewcommand{\vec}[1]{{\mbox{\boldmath$#1$}}}
% Physical rank 2 tensors
\newcommand{\tensor}[1]{\overline{\overline{#1}}}
% This is for vectors formed of the value of a quantity at each node.
\newcommand{\dvec}[1]{\underline{#1}}
% This is for matrices in the discrete system.
\newcommand{\mat}[1]{\mathrm{#1}}

\DeclareMathOperator{\sgn}{sgn}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lemma}[thm]{Lemma}

%\newcommand\qed{\hfill\mbox{$\Box$}}
\newcommand{\re}{{\mathrm{I}\hspace{-0.2em}\mathrm{R}}}
\newcommand{\inner}[2]{\langle#1,#2\rangle}
\renewcommand\leq{\leqslant}
\renewcommand\geq{\geqslant}
\renewcommand\le{\leqslant}
\renewcommand\ge{\geqslant}
\renewcommand\epsilon{\varepsilon}
\newcommand\eps{\varepsilon}
\renewcommand\phi{\varphi}
\newcommand{\bmF}{\vec{F}}
\newcommand{\bmphi}{\vec{\phi}}
\newcommand{\bmn}{\vec{n}}
\newcommand{\bmns}{{\textrm{\scriptsize{\boldmath $n$}}}}
\newcommand{\bmi}{\vec{i}}
\newcommand{\bmj}{\vec{j}}
\newcommand{\bmk}{\vec{k}}
\newcommand{\bmx}{\vec{x}}
\newcommand{\bmu}{\vec{u}}
\newcommand{\bmv}{\vec{v}}
\newcommand{\bmr}{\vec{r}}
\newcommand{\bma}{\vec{a}}
\newcommand{\bmg}{\vec{g}}
\newcommand{\bmU}{\vec{U}}
\newcommand{\bmI}{\vec{I}}
\newcommand{\bmq}{\vec{q}}
\newcommand{\bmT}{\vec{T}}
\newcommand{\bmM}{\vec{M}}
\newcommand{\bmtau}{\vec{\tau}}
\newcommand{\bmOmega}{\vec{\Omega}}
\newcommand{\pp}{\partial}
\newcommand{\kaptens}{\tensor{\kappa}}
\newcommand{\tautens}{\tensor{\tau}}
\newcommand{\sigtens}{\tensor{\sigma}}
\newcommand{\etens}{\tensor{\dot\epsilon}}
\newcommand{\ktens}{\tensor{k}}
\newcommand{\half}{{\textstyle \frac{1}{2}}}
\newcommand{\tote}{E}
\newcommand{\inte}{e}
\newcommand{\strt}{\dot\epsilon}
\newcommand{\modu}{|\bmu|}
% Derivatives
\renewcommand{\d}{\mathrm{d}}
\newcommand{\D}{\mathrm{D}}
\newcommand{\ddx}[2][x]{\frac{\d#2}{\d#1}}
\newcommand{\ddxx}[2][x]{\frac{\d^2#2}{\d#1^2}}
\newcommand{\ddt}[2][t]{\frac{\d#2}{\d#1}}
\newcommand{\ddtt}[2][t]{\frac{\d^2#2}{\d#1^2}}
\newcommand{\ppx}[2][x]{\frac{\partial#2}{\partial#1}}
\newcommand{\ppxx}[2][x]{\frac{\partial^2#2}{\partial#1^2}}
\newcommand{\ppt}[2][t]{\frac{\partial#2}{\partial#1}}
\newcommand{\pptt}[2][t]{\frac{\partial^2#2}{\partial#1^2}}
\newcommand{\DDx}[2][x]{\frac{\D#2}{\D#1}}
\newcommand{\DDxx}[2][x]{\frac{\D^2#2}{\D#1^2}}
\newcommand{\DDt}[2][t]{\frac{\D#2}{\D#1}}
\newcommand{\DDtt}[2][t]{\frac{\D^2#2}{\D#1^2}}
% Norms
\newcommand{\Ltwo}{\ensuremath{L_2} }
% Basis functions
\newcommand{\Qone}{\ensuremath{Q_1} }
\newcommand{\Qtwo}{\ensuremath{Q_2} }
\newcommand{\Qthree}{\ensuremath{Q_3} }
\newcommand{\QN}{\ensuremath{Q_N} }
\newcommand{\Pzero}{\ensuremath{P_0} }
\newcommand{\Pone}{\ensuremath{P_1} }
\newcommand{\Ptwo}{\ensuremath{P_2} }
\newcommand{\Pthree}{\ensuremath{P_3} }
\newcommand{\PN}{\ensuremath{P_N} }
\newcommand{\Poo}{\ensuremath{P_1P_1} }
\newcommand{\PoDGPt}{\ensuremath{P_{-1}P_2} }

\newcommand{\metric}{\tensor{M}}
\newcommand{\configureflag}[1]{\texttt{#1}}

% Units
\newcommand{\m}[1][]{\unit[#1]{m}}
\newcommand{\km}[1][]{\unit[#1]{km}}
\newcommand{\s}[1][]{\unit[#1]{s}}
\newcommand{\invs}[1][]{\unit[#1]{s}\ensuremath{^{-1}}}
\newcommand{\ms}[1][]{\unit[#1]{m\ensuremath{\,}s\ensuremath{^{-1}}}}
\newcommand{\mss}[1][]{\unit[#1]{m\ensuremath{\,}s\ensuremath{^{-2}}}}
\newcommand{\K}[1][]{\unit[#1]{K}}
\newcommand{\PSU}[1][]{\unit[#1]{PSU}}
\newcommand{\Pa}[1][]{\unit[#1]{Pa}}
\newcommand{\kg}[1][]{\unit[#1]{kg}}
\newcommand{\rads}[1][]{\unit[#1]{rad\ensuremath{\,}s\ensuremath{^{-1}}}}
\newcommand{\kgmm}[1][]{\unit[#1]{kg\ensuremath{\,}m\ensuremath{^{-2}}}}
\newcommand{\kgmmm}[1][]{\unit[#1]{kg\ensuremath{\,}m\ensuremath{^{-3}}}}
\newcommand{\Nmm}[1][]{\unit[#1]{N\ensuremath{\,}m\ensuremath{^{-2}}}}

% Dimensionless numbers
\newcommand{\dimensionless}[1]{\mathrm{#1}}
\renewcommand{\Re}{\dimensionless{Re}}
\newcommand{\Ro}{\dimensionless{Ro}}
\newcommand{\Fr}{\dimensionless{Fr}}
\newcommand{\Bu}{\dimensionless{Bu}}
\newcommand{\Ri}{\dimensionless{Ri}}
\renewcommand{\Pr}{\dimensionless{Pr}}
\newcommand{\Pe}{\dimensionless{Pe}}
\newcommand{\Ek}{\dimensionless{Ek}}
\newcommand{\Gr}{\dimensionless{Gr}}
\newcommand{\Ra}{\dimensionless{Ra}}
\newcommand{\Sh}{\dimensionless{Sh}}
\newcommand{\Sc}{\dimensionless{Sc}}

% Journals
\newcommand{\IJHMT}{{\it International Journal of Heat and Mass Transfer}}
\newcommand{\NED}{{\it Nuclear Engineering and Design}}
\newcommand{\ICHMT}{{\it International Communications in Heat and Mass Transfer}}
\newcommand{\NET}{{\it Nuclear Engineering and Technology}}
\newcommand{\HT}{{\it Heat Transfer}}   
\newcommand{\IJHT}{{\it International Journal for Heat Transfer}}

\newcommand{\frc}{\displaystyle\frac}
\newcommand{\CO}{CO\ensuremath{_{2}}}
\newenvironment{frcseries}{\fontfamily{frc}\selectfont}{}
\newcommand{\textfrc}[1]{{\frcseries#1}}

%\usepackage{enumitem}%
%\newlist{ExList}{enumerate}{1}
%\setlist[ExList,1]{label={\bf Example 1.} {\bf \arabic*}}

%\newlist{ProbList}{enumerate}{1}
%\setlist[ProbList,1]{label={\bf Problem 1.} {\bf \arabic*}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%% END OF THE NOTATION SECTION  %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Cause numbering of subsubsections. 
%\setcounter{secnumdepth}{8}
%\setcounter{tocdepth}{8}

\setcounter{secnumdepth}{4}%
\setcounter{tocdepth}{4}%

\begin{document}

\begin{center}
  {\Large {\bf Progress Towards Sustainable Geothermal Energy:}} \\
  {\Large {\bf Integrated Prediction Tool for Migration and Leakage in CO$_{2}$ Geological Storage using New Generation Modelling}}
%{\Large{\bf Integrated Model Framework for CO$_{2}$-Brine Fractured Enhanced Geothermal System $\left(\text{iCO}_{2}\text{-EGS}\right)$}}
\end{center}
\begin{flushright}
\end{flushright}

%%%
%%% TRACK RECORD (3 pages) 
%%%
\section{Track Record (3 pages)}

\begin{enumerate}[(a)]
%
\item {\bf University of Aberdeen (UoA), School of Engineering - Environmental and Industrial Fluid Mechanics Group (EnIFluG)\footnote{\href{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}}:} The Group specialises in combined computational methods, laboratory experimentation, and field work on permeable/porous media flows, sediment transport, coastal monitoring, turbulent buoyant jets and large-scale environmental flows. The Group has outstanding experimental facilities, including a range of large water. The latest addition is the petroleum engineering laboratory which represents a \pounds 200k investment in new equipment. The laboratory comprises four independent core-flood rigs with custom-made Hassler cells, an Anton Paar density meter and glass capillary viscometers with thermal bath. In May, UoA was awarded a further \pounds 950k (under the framework of Oil $\&$ Gas Academy of Scotland) for the purchase of equipment related to O$\&$G training. Among the equipment that will be purchased is an X-ray micro-computed tomography (microCT) system for in-situ imaging of fluids in rock samples. \red{make it more general}. \\
{\bf Dr Jefferson Gomes (JG)} leads the development of the computational multi-physics models within Fluidity. He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.

%
\item {\bf Imperial College London (IC), Department of Earth Science and Engineering – Applied Modelling and Computation Group (AMCG)\footnote{\href{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}}:} The Group is is a multi-disciplinary team of 60 scientists and engineers with backgrounds in engineering, mathematics, physics, earth and computational sciences. It specialises in the development of world-class numerical methods for modelling multi-scale multi-physical processes, with application to fracture and fragmentation, porous media and turbulent flows, nuclear criticality safety, industrial and environmental flows, ocean modelling, impact cratering and air pollution. \\
{\bf Prof. Christopher C. Pain (CCP)} is head of AMCG. He has a diverse range of modelling/physics interests including: general CFD (which comprises multiphase flow and geophysical fluid dynamics), nuclear safety, optimisation, numerical research (including parallel solution techniques, error measures and mesh adaptivity) and discretisation techniques10-14. He is the original author of the general-purpose parallel CFD model Fluidity, with mesh adaptivity, multiphase and ocean modelling features and has published 125 journal papers and graduated 33 PhD students. 
%
\end{enumerate}

\clearpage

\abstract{In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO\; is captured from energy-intensive point sources, mitigated by either chemical conversion or injection into geological formations. Each CCUS process is at very different stages of development and optimisation. In this project, research into developing an integrated dynamic prediction tool model will yield a capability to monitor migration of \CO\; plumes in geological storage sites. The generic mathematical model (High-order accurate Control Volume Finite Element Methods / HPC Computational Multi-Fluid Dynamics) will enable detailed investigation of: (a) \CO\; transport in heterogeneous media, (b) \CO-brine-rock interactions (dissolution, precipitation and exsolution due to thermal gradients and brine dissolution in supercritical \CO) and impact on permeability / porosity spatial- and time-variability.  The integrated model will be validated against

 We have assembled a team which we believe can successfully carry out the proposed work, combining a wide range of skills encompassing physics, mathematics, earth science and chemical engineering.
}

%%%
%%% CASE FOR SUPPORT (16 pages) 
%%%
\section{Case for Support (16 pages)}
\subsection{Introduction}

In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO\; is captured from energy-intensive point sources, mitigated by either chemical conversion or injection into geological formations for either indefinite storage (CCS) or to improve hydrocarbon productivity as part of enhanced oil recovery (\CO-EOR) technologies. Each CCUS process is at very different stages of development and optimisation.

Since the publication of the Intergovernmental Panel on Climate Change Report (IPCC, 2005) the injection of \CO\; in geological formations, became a viable option to mitigate GHG emissions. The European Council's directive 2009/31/EC outlines key conditions that must be met to obtain a geological storage site permit including detailed plans to mitigate \CO\; leakage events and continuous monitoring of the site conditions (e.g., amount and quality of injected \CO, temperature and pressure for assessment of phase behaviour, \CO\; migration paths).

Although storage technologies have been heavily utilised in \CO-EOR processes since the 70's, detailed and systematic studies on \CO\; transport and interactions with surrounding rock under reservoir conditions are still incipient. The impact of supercritical \CO\; injection (or any fluid at high- or fracking-pressure conditions) on the geo-environment -- including ground-fluid flow within overburden strata and injection/production wells under dynamic stress conditions, has also received increasing attention from the energy and safety communities.

This project aims to study \CO\; plume migration dynamics under reservoir conditions. This and time-dependent supercritical \CO-brine phase change in dedicated geothermal storage sites.
Groundwater flow within overburden strata under dynamic stress conditions

Since the publication of the Intergovernmental Panel on Climate Change Report (IPCC, 2005) the injection of \CO in geological formations, became a viable option to mitigate GHG emissions. Depleted oil and gas reservoirs, saline aquifers and unminable coal beds are examples of potential geological formations for injection sites. Such geological repositories could provide storage for at least 2000Gt of \CO. The European Council's directive 2009/31/EC outlines key conditions that must be met to obtain a storage site permit including detailed plans to mitigate \CO leakage events and continuous monitoring of the site conditions (e.g., amount and quality of injected \CO, temperature and pressure for assessment of phase behaviour, \CO migration paths).

In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO is captured from energy-intensive point sources, mitigated by either chemical conversion or injected in geological formations for either indefinite storage (CCS) or to improve hydrocarbon productivity as part of enhanced oil recovery (\CO-EOR) technologies. Each CCUS process is at very different stages of development and optimisation. Although technologies for \CO capture and chemical conversion are well-established technologies, one of the major R$\&$D focus is on retrofitting existing power plants that are in continuous development need to be optimised have benefited of years

%%%
%%% SCHEDULING CHART (2 pages) 
%%%
\section{Scheduling Chart (2 pages)}

%%%
%%% JUSTIFICATION OF RESOURCES (4 pages) 
%%%
\section{Justification of Resources (4 pages)}

%%%
%%% PATHWAYS TO IMPACT (2 pages)
%%%
\section{Pathways to Impact (2 pages)}

The high cost of collecting geological and well information means that it is difficult to develop mathematical models to predict key quantities such as maximum rate at which fluids can safely be injected or produced.  Traditional modelling methods are unable to represent complex geological structures and may cost hundreds of millions of pounds on unreliable data.  It is the purpose of this research to develop new tools that will allow for an improved understanding of CO2 geological-based storage. This project will be collaborative primarily with an existing industrially funded project on ”Integrated Simulation for Carbonate Reservoirs“ funded by Shell and Qatar Petroleum through QCCSRC. This programme currently funds two PDRAs dedicated to the development of the new reservoir simulator. In addition the MEMPHIS Program Grant supports development on predictive modelling. Researchers funded by these initiatives represent substantial leveraged funding for this proposal.  It is envisioned that the three projects will have common project meetings, seminars and presentations to industrial sponsors from the energy sector.
The proposed research will fit into the recently-established ICL-based Grantham Institute for Climate Change that funds research in all aspects of climate science, climate change mitigation and policy.   The Grantham Institute will provide a forum for linking the results of this research into policy, allowing the concepts to be disseminated to a much wider audience beyond the specialist scientific community. Additionally, this proposed project also fits into a number of R$\&$D Programmes under the UoA Energy Theme. Drs Tanino and Gomes were recently hired to further enhance research activities in the field of oil and gas engineering at UoA.  The outcome from this project will be integrated into policy making research and further foster collaboration with the energy sector in UK through academics in the UoA’s Schools of Law whose expertise are in the regulatory aspects of CCS.

%%%
%%% DISSEMINATION 
%%%
\section{Dissemination}

Academic dissemination will be done via publications in international refereed literature and presentations at leading international conferences in the areas of multiphase flows, petroleum engineering, computational fluids dynamics and porous media.
Dissemination will also be extended via the learned groups of which the academics are involved, including the SPE. We will organize annual themed workshop to disseminate the results to the beneficiaries and to establish new collaborations within Norway and the UK. We will also organize yearly induction courses on reservoir simulator for new researchers and users providing tutorial problems for training. Towards the end of the project, we will organize an international workshop dissemination event to showcase the results of this project and present our new modelling framework. The entire team, including the PDRAs, will be involved with organizing a series of outreach events to inform the wider general public. Activities will include public lectures, an interactive website, and general science/engineering activities. 
All software functionalities developed under this project will be licensed under open-source LGP licences, so that they are available for use and external code development by anyone wishing to utilise it for non-commercial purposes.  This will allow academics and research labs around the world to use and edit our code for uses in their own reservoir simulators or any other CFD applications.

\begin{comment}

%%%
%%% ABSTRACT (100 words)
%%%
\section{Abstract}

{\it Abstract: A 100 word synopsis of the proposed research project suitable for the lay reader.}

Motivation:

Objective:

Brief Description:

Expected Outcome:

%%%
%%% Why the Levehulme Trust (250 words)
%%%
\section{Why the Levehulme Trust}

Why the Leverhulme Trust?: It is in the Principal Applicant's interests to ensure that a full clear justification for applying to the Trust is provided, based on their understanding of the character of the Trust. Peer reviewers and Trust Board members place considerable weight on your reply, so give very careful thought to what you write and take note of the following six tips:
• Consult “Our approach to grant making” on the Trust’s website to determine if your project fits the type of research we are seeking to fund.
• Do not simply cut and paste text from our website – we know what our own website says!
• Do not just repeat what you have said elsewhere on the application form – duplicating information is not a good use of the space.
• Do answer the question. Don’t use the space to say something not relevant to the question.
• Avoid writing purely descriptive text about the research project or about the skills of the research team. You can address these points elsewhere in the application.
• Consider carefully whether the Trust really is the best recipient for your application – it may be that other funders are more suitable for the type of research you wish to undertake.

%%%
%%% Other Research Commitments (50 words)
%%%
\section{Other Research Commitments}

Other Research Commitments: This information is required to enable assessors to judge whether the Principal Applicant will have sufficient time available to devote to the proposed project.

\clearpage

%%%
%%% Summary of the Proposal (1000 words)
%%%
\section{Summary of the Proposal}

Proposal Summary: The summary should be written in a style suitable for a reader with good knowledge of the subject area. It should include hypotheses to be tested, objectives, significance, methods to be used, and details of how results will be published.
The upload limit is two pages (ARIAL 11). You can include figures but may need to add these in a table for formatting reasons. The system does not suppport PDFs. The word limit for text entry is 1000.

%%%
%%% References (500 words)
%%%
\section{References}

References: If applicable please provide a bibliography for the proposal summary.
Please note that the maximum file size for an uploaded document is 2MB.

%%%
%%% Co-Applicants
%%%
\section{Co-Applicants}
A maximum of 3 co-applicants can be added.
Co-applicants can be from a non-UK institution - and will be asked to confirm their participation in the project before it can be submitted to the Trust. It is the Principal Applicant's responsibilty to ensure that any co-applicants are aware of their role in the application process. Should the application proceed to the Detailed Application stage,they should complete their CV details within their own account and approve the application before it can be submitted - applicant's are responsible for making the necessary arrangements with their co-applicants.
Please note co-applicants may not claim a salary from the Trust, therefore they can not be the named researcher/ student on the proposal. Replacement teaching costs can be added for the Co-Applicants. To be eligible for these, they must be currently employed on a continuing basis by their eligible institution. A maximum of one year’s (33$\%$) staff replacement per grant over the course of a three year grant may be awarded – and pro rata for grants of different lengths or for those with contracts less than full time, e.g up to 8 months for a two year grant, up to 16 months for a four year grant, and so on. The replacement should not be someone currently studying for a research degree. The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned. Replacement teaching is not allowable for co-applicants outside of the UK.

%%%
%%% Referees
%%%
\section{Referees}

The individuals should be able to provide the Trust with an independent opinion on the proposed project at the detailed application stage. They must not themselves be closely allied with the project, and must be located in institutions other than that of the Principal/ Co Applicant(s).
Referees are not allowed to come from the same institution as each other. Referees based overseas are acceptable. You will need to enter complete details, including a department. Enter N/A if not applicable.
It is the responsibility of the Principal Applicant to ensure that these individuals will be in a position to respond promptly to the Trust should the proposal progress to the Full Application stage.

%%%
%%% RESEARCH GRANTS
%%%
\section{Previous and Current Research Grants}

RESEARCH PROJECT GRANTS $\&$ INTERNATIONAL NETWORKS
Previous/current application to the Leverhulme Trust: Please provide details of the Principal Applicant’s applications to the Leverhulme Trust.  If none, please enter None or N/A in the title box.
Previous/current application to other funding bodies: Please provide details of current or recent applications of Principal Applicant to other bodies for identical or closely related projects with dates and results. Please comment on reasons for rejection if known.  If none, please enter None or N/A in the title box.
INTERNATIONAL NETWORKS ONLY
Abstract: Please provide a summary of current or recent applications to other funding bodies in other subject areas. Please comment on reasons for rejection if known.
Title: character limit of 50
Ref No: character limit of 10

%%%
%%% FINANCE
%%%
\section{Finance}
Salary budget:  It is recommended that you liaise with your institution regarding the budget to minimise any delays. 
One Research Assistant, Local Researcher or PhD Student must spend at least 50% of their time on the project - of all of the time.
When entering the ‘Percentage of time spent on the project’ please ensure that you enter the percentage of time over the entire project duration, not for each year – for research assistants, PhD students and local researchers.
Personal details such as First name, Surname, Title and Current employment only need to be entered if known at time of application. However, if you do tick Name Known, personal details will become mandatory.

The Trust does not make awards on a full economic costing basis.
The budget should be entered in £ sterling.
Every field should be completed using zeros where necessary. Do not include pence.

A local researcher is where the research is taking place outside the UK and it is more appropriate to employ personnel local to the area than a UK based person paid to travel to the region.
A consultant is for use when someone is required for a limited number of hours across the duration of the project. This is not for the provision of a salary for a consultant.
Replacement teaching can be added for the Principal/Co-Applicants. To be eligible for these, applicants must be currently employed on a continuing basis by their eligible institution. A maximum of one year’s replacement per grant over the course of a three year grant – and pro rata for grants of different lengths or for those with contracts less than full time – may be awarded. The replacement should not be someone currently studying for a research degree. The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned.
Explicit and clear justification should be provided for why replacement teaching costs are sought/required. Do not simply provide a breakdown of how this is calculated, but why this is required for the project.
Associated costs: Please be reminded that the total Associated Costs cannot exceed 25$\%$ of the total amount requested.  Select type from drop down list.  Please choose only ONE of each type, and total specific items within the type, fully detailing and justifying the cost within the justification box.
Open Access costs are permissible and should be included within the 25$\%$ associated costs allowable However, open access charges should only be incurred during the period of a Leverhulme award (rather than being built into a budget but with anticipated expenditure after the research and award has concluded).  If these costs are not incurred during the life of the grant, the funds cannot be switched to any other budget heading, and must be returned to the Trust.

%%%
%%% SECTION
%%%
\section{Track Record}

\clearpage

%%% 
%%% SECTION
%%%
\section{Case for Support}

%%%
%%% Sub-Section
%%%
\subsection{Motivation and Objectives}
\begin{itemize}
\item \red{1-2 Paragraphs on general motivation for the proposed project}
\item \red{1-2 Paragraph on applications or how the project will benefit power generation via geothermal energy developments and  hydrocarbon production in HPHT reservoirs} 
\end{itemize}

Furthermore, because of the high pressures involved, the injection of cold fluids into the geothermal reservoir (at high temperature and pressure conditions) may lead to the formation of further stress- and thermal-induced fractures. \blue{Text linking injection to isenthalpic flash}.

 Within this context, the research proposed here is aimed at developing an integrated model framework to investigate CO$_{2}$-brine-contaminants flows in thermal energy recovery systems in geological formations at high temperature and pressure conditions. The ultimate goal is to be able to improve our understanding of density- and viscous-driven fluid instabilities in liquid-vapour fronts.

 experimentally validating comprehensive predictive models for both dense phase pneumatic conveying and fluidized bed gasifiers, which fully represent the physics of particulate behaviour (in its production, transport and interaction at a surface). The ultimate objective is to be able to design coal gasifiers in which these aspects can be controlled in such a way as to deliver a further increase in thermal efficiency of around 5%, leading to a further decrease in CO2 emissions of 10% per kWh. Modelling is essential as real scale, actual pressure/temperature experiments are inordinately expensive. This will require both experimental and computational elements. The former will provide information at a level of detail and at conditions hitherto not available. The objectives of this 48 month project are:

%%%
%%% Sub-Section
%%%
\subsection{Technical Background -- Coupled Non-Equilibrium Vapour-Liquid Equilibria and Transport of Volatile Organic Geochemicals }

%%%
%%% Sub-Section
%%%
\subsection{Methodology and Work Programme}

%%%
%%% Sub-Section
%%%
\subsection{Impact Summary}

%%%
%%% Sub-Section
%%%
\subsection{Academic Beneficiaries}

\clearpage

%%%
%%% SECTION
%%%
\section{Justification of Resources}

\clearpage

%%%
%%% SECTION
%%%
\section{Pathways for Impact}

\clearpage

%%%
%%% SECTION
%%%
\section{Workplan}

\clearpage

\end{comment}

\end{document}

### 2015-08-12 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

@@
 %%%
-\renewcommand{\baselinestretch}{1.}
+\renewcommand{\baselinestretch}{1.3}
 
@@
 
+\abstract{Environmental and industrial porous media flow is key to a wide range of traditional and emerging applications, including hydrocarbon exploration, geothermal reservoir engineering, nuclear waste repository, groundwater contamination, protection and remediation and \CO\; capture and storage.
+In this project, research into developing an integrated dynamic prediction tool model will yield a capability to monitor migration of \CO\; plumes in geological storage sites.
+The generic mathematical model (High-order accurate Control Volume Finite Element Methods / Computational Multi-Fluid Dynamics) will enable detailed investigation of: (a) \CO\; transport in heterogeneous media, (b) \CO-brine-rock interactions (dissolution, precipitation and exsolution due to thermal gradients and brine dissolution in supercritical \CO) and impact on permeability / porosity spatial- and time-variability.
+The integrated model will be validated against (a) standard SPE reservoir simulation benchmarks and (b) field data obtained from existing experiments (e.g., Frio Brine Pilot Experiment and XXXX).
+We have assembled a team which we believe can successfully carry out the proposed work, combining a wide range of skills encompassing physics, mathematics, earth science and engineering.
+}
+
 %%%
@@
 
-\abstract{In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO\; is captured from energy-intensive point sources, mitigated by either chemical conversion or injection into geological formations.
-Each CCUS process is at very different stages of development and optimisation.
-In this project, research into developing an integrated dynamic prediction tool model will yield a capability to monitor migration of \CO\; plumes in geological storage sites.
-The generic mathematical model (High-order accurate Control Volume Finite Element Methods / HPC Computational Multi-Fluid Dynamics) will enable detailed investigation of: (a) \CO\; transport in heterogeneous media, (b) \CO-brine-rock interactions (dissolution, precipitation and exsolution due to thermal gradients and brine dissolution in supercritical \CO) and impact on permeability / porosity spatial- and time-variability.
-The integrated model will be validated against
-
- We have assembled a team which we believe can successfully carry out the proposed work, combining a wide range of skills encompassing physics, mathematics, earth science and chemical engineering.
-}
-
 %%%
@@
 Although technologies for \CO capture and chemical conversion are well-established technologies, one of the major R$\&$D focus is on retrofitting existing power plants that are in continuous development need to be optimised have benefited of years
+
+\begin{comment}
+This proposal comes at a time when the UK nuclear sector is resurgent.
+It is now widely accepted that one of the ways in which the UK can meet its commitments to reducing CO2 emissions, as well as dealing with its over-reliance on imported fuel supplies, is to replace the current fleet of ageing nuclear reactors.
+
+Natural and industrial porous media is key to a wide variety of traditional and emerging engineering applications, including but not limited to oil and gas extraction from geological reservoirs, carbon capture and storage, geothermal reservoir engineering, soil sciences, groundwater remediation and protection, biological engineering, food processing, fuel cells, nano-technology, construction engineering, wood processing and printing.
+
+Global warming due to the accumulating concentration of atmospheric CO2 is being accepted by the scientific and broader community.
+Amongst a number of CO2 atmospheric emission management considerations is carbon dioxide capture and storage, CCS, related to major coal burning power generation.
+The operation of CCS requires a close synergy of CO2 capture and CO2 storage.
+Clearly the most effective capture technology is of no value unless the captured CO2 can be stored.
+Carbon dioxide is a very soluble gas which makes storing CO2 in large volumes of liquids in porous subsurface reservoirs a serious consideration for captured CO2.
+Subsurface brine aquifers have a large potential for CO2 storage.
+Computer based reservoir simulation has been used increasingly by oil companies to predict flow and oil recovery behaviour of reservoirs and help in decision making of project viability.
+The quality of the simulation process depends on the ability of the simulator to represent the physics and chemistry of the various phenomena occurring in the reservoir and the quality of the various properties characterising the reservoir structure and fluids.
+The Institute of Petroleum Engineering at Heriot-Watt University will use its oil related reservoir simulation experience and existing commercial simulation software to predict the behaviour of injecting carbon dioxide into brine containing structures in the near vicinity of power generation stations.
+Predicting the behaviour of CO2 injected into subsurface rocks containing brine requires an understanding of the impact of a wide range of issues; the geology of the formation, the properties of the porous rocks and the fluids, and the change in these properties resulting from interaction with CO2.
+Reservoir simulation provides an effective platform to evaluate these issues and generate forecasts of CO2 storage potential and distribution.
+Integrating with and using data from BGS and UoE, the Heriot-Watt team will construct reservoir simulation models, using different levels of characterisation, detail, to simulate specific potential storage sites.
+The team will examine the impact of a wide range of characterising parameters.
+Injecting CO2 into brine containing rocks is likely to change rock properties affecting flow behaviour.
+For example the dissolution of acidic CO2 saturated brine could change the mechanical strength of the rock as well as dissolve minerals, again impacting on flow behaviour.
+As well as predicting this impact in the reservoir simulation process, the Heriot-Watt team will carry out laboratory based evaluations on rocks, representative of the potential sites, on mechanical strength changes as a result of CO2 brine interaction.
+Using reservoir condition experimental facilities evaluation of chemical interactions using static soaking and dynamic flow of fluids through rocks (core flooding) and measuring effluent ion concentrations and permeability changes, the HWU team will examine the impact of chemical interaction of carbonated brine with the various rock types provided by BGS.
+The output from these reservoir simulation based evaluations will be integrated with the other partner outputs and use will be made of 3D visualisation to enable project partners to examine the impact of various issues on the short and long term storage capacity and distribution of the considered subsurface storage sites.
+The output and 3D simulation will also be used to communicate to other interested stake holders, eg.
+Scottish Government, DTI, Local Government, EC, other power generators, environmental agencies, and not least the general public, the process and potential of subsurface CO2 storage.
+
+\end{comment}
 

### 2015-08-12 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

@@
 \section{Case for Support (16 pages)}
-\subsection{Introduction}
+
+\subsection{Background}
 
@@
 
+The proposed project is focused on predicting \CO\; lateral migration and leakage in complex geological heterogeneity.
+For the simulation of \CO\; migration it is critically important to accurately represent geological structural characteristics (e.g., facies of the same material property, faults and fractures).
+Fully unstructured tetrahedral finite elements have unrivalled geometrical flexibility and are by far the best choice to represent these complex geometries and internal boundaries.
+Such geological-conforming geometry representation is used with the next generation of models based upon a new family of discontinuous finite element methods.
+This approach promises a step-change in accuracy from conventional corner-point grids methods in industry-standard flow simulators and represents a novel contribution to CCUS technology.
+The new model is able to optimally adapt the mesh to represent physics of particular interest, e.g., to focus resolution in the pathways of \CO\; migration.
+This model will help quantifying time-scales for supercritical \CO\; migration and potential leakage in geological repositories.
+
 This project aims to study \CO\; plume migration dynamics under reservoir conditions. This and time-dependent supercritical \CO-brine phase change in dedicated geothermal storage sites.
 Groundwater flow within overburden strata under dynamic stress conditions
-
-Since the publication of the Intergovernmental Panel on Climate Change Report (IPCC, 2005) the injection of \CO in geological formations, became a viable option to mitigate GHG emissions.
-Depleted oil and gas reservoirs, saline aquifers and unminable coal beds are examples of potential geological formations for injection sites.
-Such geological repositories could provide storage for at least 2000Gt of \CO.
-The European Council's directive 2009/31/EC outlines key conditions that must be met to obtain a storage site permit including detailed plans to mitigate \CO leakage events and continuous monitoring of the site conditions (e.g., amount and quality of injected \CO, temperature and pressure for assessment of phase behaviour, \CO migration paths).
-
-In Carbon Capture, Utilisation, and Storage (CCUS) integrated processes, \CO is captured from energy-intensive point sources, mitigated by either chemical conversion or injected in geological formations for either indefinite storage (CCS) or to improve hydrocarbon productivity as part of enhanced oil recovery (\CO-EOR) technologies.
-Each CCUS process is at very different stages of development and optimisation.
-Although technologies for \CO capture and chemical conversion are well-established technologies, one of the major R$\&$D focus is on retrofitting existing power plants that are in continuous development need to be optimised have benefited of years
 

### 2015-08-12 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

@@
 
+%%%
+%%% SUBSECTION
+%%%
 \subsection{Background}
@@
 
-The proposed project is focused on predicting \CO\; lateral migration and leakage in complex geological heterogeneity.
+The proposed project is focused on predicting \CO\; plume migration dynamics under reservoir conditions in complex geological heterogeneity.
 For the simulation of \CO\; migration it is critically important to accurately represent geological structural characteristics (e.g., facies of the same material property, faults and fractures).
@@
 
-This project aims to study \CO\; plume migration dynamics under reservoir conditions. This and time-dependent supercritical \CO-brine phase change in dedicated geothermal storage sites.
-Groundwater flow within overburden strata under dynamic stress conditions
+%%%
+%%% SUBSECTION
+%%%
+\subsection{Motivation and Objectives}
+\CO\; has been injected and stored in underground geological formations to dispose of acidic gasses (mainly H$_{2}$S and \CO) from industrial plants.
+This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions.
+However, geological CO2 storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
+\begin{enumerate}[(a)]
+   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
+   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
+   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
+   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
+   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e}
+\end{enumerate}
+
+Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{options:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{options:b},~\ref{options:c}).
+Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended CO2 migration.
+Our model framework may also be used during the continuous site monitoring stage (\ref{options:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.
 

### 2015-08-13 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
updated text

@@
 \subsection{Motivation and Objectives}
-\CO\; has been injected and stored in underground geological formations to dispose of acidic gasses (mainly H$_{2}$S and \CO) from industrial plants.
+\CO\; has been injected in underground geological formations to enhance hydrocarbon productivity (e.g.
+\CO-EOR) whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants.
 This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions.
-However, geological CO2 storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
+However, geological \CO\; storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
 \begin{enumerate}[(a)]
@@
 
-\begin{comment}
-
-%%%
-%%% ABSTRACT (100 words)
-%%%
-\section{Abstract}
-
-{\it Abstract: A 100 word synopsis of the proposed research project suitable for the lay reader.}
-
-Motivation:
-
-Objective:
-
-Brief Description:
-
-Expected Outcome:
-
-%%%
-%%% Why the Levehulme Trust (250 words)
-%%%
-\section{Why the Levehulme Trust}
-
-Why the Leverhulme Trust?: It is in the Principal Applicant's interests to ensure that a full clear justification for applying to the Trust is provided, based on their understanding of the character of the Trust.
-Peer reviewers and Trust Board members place considerable weight on your reply, so give very careful thought to what you write and take note of the following six tips:
-• Consult “Our approach to grant making” on the Trust’s website to determine if your project fits the type of research we are seeking to fund.
-• Do not simply cut and paste text from our website – we know what our own website says!
-• Do not just repeat what you have said elsewhere on the application form – duplicating information is not a good use of the space.
-• Do answer the question. Don’t use the space to say something not relevant to the question.
-• Avoid writing purely descriptive text about the research project or about the skills of the research team. You can address these points elsewhere in the application.
-• Consider carefully whether the Trust really is the best recipient for your application – it may be that other funders are more suitable for the type of research you wish to undertake.
-
-%%%
-%%% Other Research Commitments (50 words)
-%%%
-\section{Other Research Commitments}
-
-Other Research Commitments: This information is required to enable assessors to judge whether the Principal Applicant will have sufficient time available to devote to the proposed project.
-
-\clearpage
-
-%%%
-%%% Summary of the Proposal (1000 words)
-%%%
-\section{Summary of the Proposal}
-
-Proposal Summary: The summary should be written in a style suitable for a reader with good knowledge of the subject area.
-It should include hypotheses to be tested, objectives, significance, methods to be used, and details of how results will be published.
-The upload limit is two pages (ARIAL 11). You can include figures but may need to add these in a table for formatting reasons. The system does not suppport PDFs. The word limit for text entry is 1000.
-
-%%%
-%%% References (500 words)
-%%%
-\section{References}
-
-References: If applicable please provide a bibliography for the proposal summary.
-Please note that the maximum file size for an uploaded document is 2MB.
-
-%%%
-%%% Co-Applicants
-%%%
-\section{Co-Applicants}
-A maximum of 3 co-applicants can be added.
-Co-applicants can be from a non-UK institution - and will be asked to confirm their participation in the project before it can be submitted to the Trust.
-It is the Principal Applicant's responsibilty to ensure that any co-applicants are aware of their role in the application process.
-Should the application proceed to the Detailed Application stage,they should complete their CV details within their own account and approve the application before it can be submitted - applicant's are responsible for making the necessary arrangements with their co-applicants.
-Please note co-applicants may not claim a salary from the Trust, therefore they can not be the named researcher/ student on the proposal.
-Replacement teaching costs can be added for the Co-Applicants.
-To be eligible for these, they must be currently employed on a continuing basis by their eligible institution.
-A maximum of one year’s (33$\%$) staff replacement per grant over the course of a three year grant may be awarded – and pro rata for grants of different lengths or for those with contracts less than full time, e.g up to 8 months for a two year grant, up to 16 months for a four year grant, and so on.
-The replacement should not be someone currently studying for a research degree.
-The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned.
-Replacement teaching is not allowable for co-applicants outside of the UK.
-
-%%%
-%%% Referees
-%%%
-\section{Referees}
-
-The individuals should be able to provide the Trust with an independent opinion on the proposed project at the detailed application stage.
-They must not themselves be closely allied with the project, and must be located in institutions other than that of the Principal/ Co Applicant(s).
-Referees are not allowed to come from the same institution as each other.
-Referees based overseas are acceptable.
-You will need to enter complete details, including a department.
-Enter N/A if not applicable.
-It is the responsibility of the Principal Applicant to ensure that these individuals will be in a position to respond promptly to the Trust should the proposal progress to the Full Application stage.
-
-%%%
-%%% RESEARCH GRANTS
-%%%
-\section{Previous and Current Research Grants}
-
-RESEARCH PROJECT GRANTS $\&$ INTERNATIONAL NETWORKS
-Previous/current application to the Leverhulme Trust: Please provide details of the Principal Applicant’s applications to the Leverhulme Trust.  If none, please enter None or N/A in the title box.
-Previous/current application to other funding bodies: Please provide details of current or recent applications of Principal Applicant to other bodies for identical or closely related projects with dates and results.
-Please comment on reasons for rejection if known.
-If none, please enter None or N/A in the title box.
-INTERNATIONAL NETWORKS ONLY
-Abstract: Please provide a summary of current or recent applications to other funding bodies in other subject areas. Please comment on reasons for rejection if known.
-Title: character limit of 50
-Ref No: character limit of 10
-
-%%%
-%%% FINANCE
-%%%
-\section{Finance}
-Salary budget:  It is recommended that you liaise with your institution regarding the budget to minimise any delays. 
-One Research Assistant, Local Researcher or PhD Student must spend at least 50% of their time on the project - of all of the time.
-When entering the ‘Percentage of time spent on the project’ please ensure that you enter the percentage of time over the entire project duration, not for each year – for research assistants, PhD students and local researchers.
-Personal details such as First name, Surname, Title and Current employment only need to be entered if known at time of application.
-However, if you do tick Name Known, personal details will become mandatory.
-
-The Trust does not make awards on a full economic costing basis.
-The budget should be entered in £ sterling.
-Every field should be completed using zeros where necessary. Do not include pence.
-
-A local researcher is where the research is taking place outside the UK and it is more appropriate to employ personnel local to the area than a UK based person paid to travel to the region.
-A consultant is for use when someone is required for a limited number of hours across the duration of the project. This is not for the provision of a salary for a consultant.
-Replacement teaching can be added for the Principal/Co-Applicants.
-To be eligible for these, applicants must be currently employed on a continuing basis by their eligible institution.
-A maximum of one year’s replacement per grant over the course of a three year grant – and pro rata for grants of different lengths or for those with contracts less than full time – may be awarded.
-The replacement should not be someone currently studying for a research degree.
-The staff replacement should normally start at the most junior point of the lecturer scale of the institution concerned.
-Explicit and clear justification should be provided for why replacement teaching costs are sought/required.
-Do not simply provide a breakdown of how this is calculated, but why this is required for the project.
-Associated costs: Please be reminded that the total Associated Costs cannot exceed 25$\%$ of the total amount requested.
-Select type from drop down list.
-Please choose only ONE of each type, and total specific items within the type, fully detailing and justifying the cost within the justification box.
-Open Access costs are permissible and should be included within the 25$\%$ associated costs allowable However, open access charges should only be incurred during the period of a Leverhulme award (rather than being built into a budget but with anticipated expenditure after the research and award has concluded).
-If these costs are not incurred during the life of the grant, the funds cannot be switched to any other budget heading, and must be returned to the Trust.
-
-%%%
-%%% SECTION
-%%%
-\section{Track Record}
-
-\clearpage
-
-%%% 
-%%% SECTION
-%%%
-\section{Case for Support}
-
-%%%
-%%% Sub-Section
-%%%
-\subsection{Motivation and Objectives}
-\begin{itemize}
-\item \red{1-2 Paragraphs on general motivation for the proposed project}
-\item \red{1-2 Paragraph on applications or how the project will benefit power generation via geothermal energy developments and  hydrocarbon production in HPHT reservoirs} 
-\end{itemize}
-
-Furthermore, because of the high pressures involved, the injection of cold fluids into the geothermal reservoir (at high temperature and pressure conditions) may lead to the formation of further stress- and thermal-induced fractures.
-\blue{Text linking injection to isenthalpic flash}.
-
- Within this context, the research proposed here is aimed at developing an integrated model framework to investigate CO$_{2}$-brine-contaminants flows in thermal energy recovery systems in geological formations at high temperature and pressure conditions.
-The ultimate goal is to be able to improve our understanding of density- and viscous-driven fluid instabilities in liquid-vapour fronts.
-
- experimentally validating comprehensive predictive models for both dense phase pneumatic conveying and fluidized bed gasifiers, which fully represent the physics of particulate behaviour (in its production, transport and interaction at a surface).
-The ultimate objective is to be able to design coal gasifiers in which these aspects can be controlled in such a way as to deliver a further increase in thermal efficiency of around 5%, leading to a further decrease in CO2 emissions of 10% per kWh.
-Modelling is essential as real scale, actual pressure/temperature experiments are inordinately expensive.
-This will require both experimental and computational elements.
-The former will provide information at a level of detail and at conditions hitherto not available.
-The objectives of this 48 month project are:
-
-%%%
-%%% Sub-Section
-%%%
-\subsection{Technical Background -- Coupled Non-Equilibrium Vapour-Liquid Equilibria and Transport of Volatile Organic Geochemicals }
-
-%%%
-%%% Sub-Section
-%%%
-\subsection{Methodology and Work Programme}
-
-%%%
-%%% Sub-Section
-%%%
-\subsection{Impact Summary}
-
-%%%
-%%% Sub-Section
-%%%
-\subsection{Academic Beneficiaries}
-
-\clearpage
-
-%%%
-%%% SECTION
-%%%
-\section{Justification of Resources}
-
-\clearpage
-
-%%%
-%%% SECTION
-%%%
-\section{Pathways for Impact}
-
-\clearpage
-
-%%%
-%%% SECTION
-%%%
-\section{Workplan}
-
-\clearpage
-
-\end{comment}
-
 \end{document}

### 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
updated text

@@
 \CO\; has been injected in underground geological formations to enhance hydrocarbon productivity (e.g.
-\CO-EOR) whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants.
+\CO-EOR).
+%whilst disposing acidic gasses (mainly H$_{2}$S and \CO) from natural occurance or captured from industrial plants.
 This has helped to prove that geological \CO\; storage is a viable engineering and economic strategy for reducing GHG emissions.
-However, geological \CO\; storage schemes must comply with requirements (European Council's directive 2009/31/EC) for:
+However, geological \CO\; storage schemes must comply with UK/EUrequirements (European Council's directive 2009/31/EC) for:
 \begin{enumerate}[(a)]
+%
    \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
+%
    \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
+%
    \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
+%
    \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
+%
    \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e}
+%
 \end{enumerate}
@@
 Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{options:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{options:b},~\ref{options:c}).
-Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended CO2 migration.
+Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended \CO\; migration.
 Our model framework may also be used during the continuous site monitoring stage (\ref{options:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.
+
+The main objectives of this proposal are:
+\begin{enumerate}[(i)]
+%
+   \item Investigation of \CO\; plume dynamics (migration and leakage);
+%
+   \item Assessment of fluid flow through zones of potential rheological weakness in the overburden (e.g., faults and chimneys);
+%
+   \item    
+%
+\end{enumerate}
 

### 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

@@
 %%%
-\section{Case for Support (16 pages)}
+\section{Case for Support (max 16 pages)}
 
@@
 The European Council's directive 2009/31/EC outlines key conditions that must be met to obtain a geological storage site permit including detailed plans to mitigate \CO\; leakage events and continuous monitoring of the site conditions (e.g., amount and quality of injected \CO, temperature and pressure for assessment of phase behaviour, \CO\; migration paths).
+Although storage technologies have been heavily utilised in \CO-EOR processes since the 70's, detailed and systematic studies on \CO\; transport and interactions with surrounding rock under reservoir conditions are still incipient.
+The impact of supercritical \CO\; injection (or any fluid at high- or fracking-pressure conditions) on the geo-environment (including ground-fluid flow within overburden strata and injection/production wells under dynamic stress conditions) has received increasing attention from energy and safety communities.
 
-Although storage technologies have been heavily utilised in \CO-EOR processes since the 70's, detailed and systematic studies on \CO\; transport and interactions with surrounding rock under reservoir conditions are still incipient.
-The impact of supercritical \CO\; injection (or any fluid at high- or fracking-pressure conditions) on the geo-environment -- including ground-fluid flow within overburden strata and injection/production wells under dynamic stress conditions, has also received increasing attention from the energy and safety communities.
+\CO\; storage requires detailed understanding of the behaviour of fluids in the subsurface.
+Plume-scale/long-time fate of the injected \CO\; is determined primarily by large-scale features, most notably spatial heterogeneity in permeability and the presence and distribution of fractures or other high permeability pathways.
+Yet the structure of geological formations is highly uncertain even with the most advanced seismic imaging and well logging.
+Moreover, exposure to acidic \CO-rich brine is expected to modify the porosity, permeability, and the wettability through dissolution, precipitation and exsolution.
+Consequently, the petrophysical properties of a storage site will evolve both during injection and post-operation, possibly over many thousands of years.
 
-The proposed project is focused on predicting \CO\; plume migration dynamics under reservoir conditions in complex geological heterogeneity.
+Injected supercritical \CO\; migrates from the injection well to far field regions.
+With rock and fluid properties changing over the life-cycle of the geological storage, assessing the risk of leakage and quantifying the sensitivity of petrophysical properties of overburden strata (e.g., permeability, porosity, stress etc) to \CO\; time-dependent conditions is crucial for geological site screening and selection.
+
+A wide array of monitoring technologies originally developed for the oil and gas industry to track fluids movement in the subsurface are now being deployed to monitor underground \CO\; migration and leakage into the cap rock and around the wellbore casing: (a) seismic surveying resulting in reconstructed images of the subsurface allowing \CO\; plumes to be mapped and predicted, (b) grid of smart sensors placed in the borehole (injection, production and monitoring wells) to monitor key parameters (temperature, pressure, salinity, pH), and (c) surface \CO\; sensors.
+
+%Flow Simulator: In existing academic- and industry-standard flow simulators, the geological volumetric domain is bounded by prescribed surfaces (top and bottom), and faults are represented by an extra set of surfaces.
+The geological volume is then subdivided in geologically-defined zones (bounded by surfaces).
+Each zone is finally subdivided into grid cells where rock and fluids properties are assigned.
+In conventional flow simulators, a fixed (and usually coarse) grid resolution is applied to each geological-defined zone due to limited computational resources.
+However, in many scenarios, a high-resolution grid is required in specific regions to predict strong flow gradients (e.g., saturation, CO2 concentration), and a lower resolution is acceptable elsewhere.
+For example, during water flooding, high-resolution is required close to the migrating waterfront where the saturation gradient is large but, behind the front, the saturation changes gradually and high resolution is not required.
+A more efficient use of computational effort is to dynamically adapt the computational mesh in space and time (Figure ).
+This is achieved in our novel reservoir simulator, built on top of the state-of-the-art open-source Fluidity software, under development as part of a collaborative programme between AMCG and the PERM groups at Imperial College (ICL) and the E&IFM group at the University of Aberdeen (UoA).
+Fluidity is an open-source (LGPL) adaptive finite element model with capabilities in a wide variety of CFD applications1  and has demonstrated impressive parallel scaling2.
+
+%The proposed project is focused on predicting \CO\; plume migration dynamics under reservoir conditions in complex geological heterogeneity.
 For the simulation of \CO\; migration it is critically important to accurately represent geological structural characteristics (e.g., facies of the same material property, faults and fractures).
@@
 %
-   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{options:a}
+   \item Site screening and selection to identify potential geological locations for \CO\; storage;\label{Motivation:a}
 %
-   \item Site characterisation to assess the engineering and economic feasibility;\label{options:b}
+   \item Site characterisation to assess the engineering and economic feasibility;\label{Motivation:b}
 %
-   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{options:c}
+   \item Simulation of potential injection strategies to assess (i) pressure and stress distribution and their evolution in time, (ii) plume migration, (iii) oil recovery, (iv) storage capacity and (v) flow rate of injection;\label{Motivation:c}
 %
-   \item Risk assessment to identify risks of leakage via pathways identified in (~\ref{options:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{options:d}
+   \item Risk assessment to identify risks of leakage via pathways identified in (\ref{Motivation:c}), to design a monitoring scheme for continuous assessment of these risks, and to develop contingency plans in case of  leakage scenarios;\label{Motivation:d}
 %
-   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{options:e}
+   \item Site management and operation to ensure that the site is operated in compliance with regulations and to continuously assess the risks associated with the storage site during operation, closure and post-closure stages.\label{Motivation:e}
 %
@@
 
-Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{options:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{options:b},~\ref{options:c}).
+Although the main focus of this proposal is to assess potential \CO\; leakage (\ref{Motivation:d}), the technology developed here can also be applied to assess the storage feasibility of new and existing geological sites (\ref{Motivation:b},~\ref{Motivation:c}).
 Risk assessment based on detailed numerical simulations can identify specific risk features and processes (e.g., leaky faults and wellbores, unexpected injection pressure rise, residual saturation trapping) which may help prevent unintended \CO\; migration.
-Our model framework may also be used during the continuous site monitoring stage (\ref{options:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.
+Our model framework may also be used during the continuous site monitoring stage (\ref{Motivation:e}) to assess potential risks during injection and storage as the model can use data from field sensors (data assimilation) to help predict the likelihood of \CO\; leakage.
 
@@
 %
-   \item Assessment of fluid flow through zones of potential rheological weakness in the overburden (e.g., faults and chimneys);
+   \item \red{Investigation of multi-fluid flows through zones of potential rheological weakness in the overburden (e.g., faults and chimneys): solid-fluid interactions and stress-induced fractures formation;}
 %
-   \item    
+   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
+%
+   \item Model quality assurance
 %

### 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal

@@
 %
-   \item Model quality assurance
+   \item Model quality assurance (monitoring $\&$ verification for risk assessment and environmental impact).
 %
 \end{enumerate}
+
+{\bf The novelty of this project is in addressing in an integrated way detailed modelling of \CO\; flows under reservoir conditions (plume migration $\&$ leakage), changes on petrophysical properties (permeability/porosity spatial- and time-variability), solid-fluid interactions (integrity of repositories) and monitoring $\&$ verification technologies.} We shall consider multi-scale and multi-physics aspects of CCUS problem: two length-scales:
+
+both the polydispersity and the closure problems by resorting to a self-consistent multiscale modelling approach.
+We shall consider two (length) scales: a microscopic scale, comparable with the characteristic size of the discrete particles, and a macroscopic scale, comparable with the characteristic length of the gradients that the modeller wishes to capture in the system analysed.
+We shall employ Lagrangian modelling at the microscale and Eulerian modelling at the macroscale.
+With the information provided by the Lagrangian simulations, we shall develop constitutive equations that we shall implement in the Eulerian model, experimentally validated for different types of flow by means of advanced imaging techniques (Fig.1).
+The ultimate goal is to develop a self-standing Eulerian (that is, continuum) model for dense fluid-particle flows, able to correctly describe polydispersity and solvable by means of CFD codes.
 

### 2015-08-25 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
Updates in the proposal
updates

@@
 {\bf Dr Jefferson Gomes (JG)} leads the development of the computational multi-physics models within Fluidity.
-He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.
+He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.\\
+{\bf Dr Yukie Tanino (YT)} research combines theory and laboratory experiment to model flow and mass transport in obstructed and/or confined systems, including geological reservoirs, inclined pipes, and artificial wetlands for wastewater treatment.
+She manages the recently established petroleum engineering laboratory in the School.
 
@@
 However, geological \CO\; storage schemes must comply with UK/EUrequirements (European Council's directive 2009/31/EC) for:
-\begin{enumerate}[(a)]
+\begin{enumerate}[(i)]
 %
@@
 The main objectives of this proposal are: 
-\begin{enumerate}[(i)]
+\begin{enumerate}[(a)]
 %
@@
 
-{\bf The novelty of this project is in addressing in an integrated way detailed modelling of \CO\; flows under reservoir conditions (plume migration $\&$ leakage), changes on petrophysical properties (permeability/porosity spatial- and time-variability), solid-fluid interactions (integrity of repositories) and monitoring $\&$ verification technologies.} We shall consider multi-scale and multi-physics aspects of CCUS problem: two length-scales:
+{\bf The novelty of this project is in addressing in an integrated way: detailed modelling of \CO\; flows under reservoir conditions (plume migration $\&$ leakage); changes on petrophysical properties (permeability/porosity spatial- and time-variability); solid-fluid interactions (integrity of repositories); and monitoring $\&$ verification technologies.}
+
+\medskip
+We shall consider two integrated length-scales in the CCUS problem: 
+\begin{enumerate}[(a)]
+  \item \red{flow mechanisms and structures in pore-scale} -- {\bf YT};
+  \item flow detachment in field scale \blue{(develop this as a backbone for phase change and flow instability)} -- {\bf JG}.
+\end{enumerate}
 

### 2015-08-27 Papers/Prototype_Merged/Manuscript_IJNMF.tex
Updates. Initial file design (cls style) for IJNMF

% flddoc.tex V2.0, 13 May 2010

\documentclass[times]{fldauth}

\usepackage{moreverb}

\usepackage[dvips,colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2015}

\begin{document}

\runningheads{J.L.M.A.~ Gomes {\it et al.}}{A Force-Balanced CVFEM for Multiphase Porous Media Flow Modelling}

\title{A Force-Balanced Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling}

%% use optional labels to link authors explicitly to addresses:
\author{J. L. M. A. Gomes\corrauth$^{1,4}$, D. Pavlidis$^{2,4}$, P. Salinas$^{2,4}$, Z. Xie$^{2,4}$, J. R. Percival$^{2}$, P. Mostaghimi$^{3}$, C. C. Pain$^{2,4}$, M. D. Jackson$^{4}$}

%\cortext[cor1]{Corresponding author.}
\address{$^{1}$Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK \\
         $^{2}$Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK \\
         $^{3}$School of Petroleum Engineering, University of New South Wales, Australia \\
         $^{4}$Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK\\}

\corraddr{University of Aberdeen, AB24~3UE, UK.}

\begin{abstract}
  A novel control volume finite element method for simulating subsurface multiphase flows is presented here. The approach has two major strengths. First, it uses a dual consistent pressure-velocity representation in control volume and finite element spaces which ensures local mass conservation. Second, it uses a family of finite element types that ensure the multiphase Darcy equations can be exactly enforced. The underlying mass conservation equations are solved in control volume space whereas finite elements are used to obtain high-order fluxes on control volume boundaries. The novelty of the method lies in (a) permitting both continuous and discontinuous description of pressures and saturations between elements; (b) the use of arbitrarily high-order polynomial representation for pressure and velocity within the mixed formulation and (c) the use of high-order flux-limited methods to avoid introducing non-physical oscillations while achieving high-order time accuracy where and when possible. The model is initially evaluated and then applied to a series of test cases using structured and unstructured (triangular/ tetrahedral) meshes, as well as heterogeneous problems with large permeability ratios. Numerical results are in good agreement with analytically obtained solutions.
\end{abstract}

\keywords{CVFEM mixed formulation; Discontinuous Galerkin; Multiphase flows; Porous media}

\maketitle

\vspace{-6pt}

\section{Introduction}
\vspace{-2pt}
Many authors submitting to research journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{\journalclass} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in the \emph{\journalnamelc}.

The \textsf{\journalclass} class file preserves much of the
standard \LaTeXe\ interface so that any document which was
produced using the standard \LaTeXe\ \textsf{article} style can
easily be converted to work with the \textsf{\journalclassshort}
style. However, the width of text and typesize will vary from that
of \textsf{article.cls}; therefore, \emph{line breaks will change}
and it is likely that displayed mathematics and tabular material
will need re-setting.

In the following sections we describe how to lay out your code to
use \textsf{\journalclass} to reproduce the typographical look of
the \emph{\journalnamelc}. However, this paper is not a guide to
using \LaTeXe\ and we would refer you to any of the many books
available (see, for example, \cite{R1,R2,R3}).

\vspace{-6pt}

\section{The Three Golden Rules}
\vspace{-2pt}

Before we proceed, we would like to stress \emph{three golden
rules} that need to be followed to enable the most efficient use
of your code at the typesetting stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{\journalnamelc} reference style.
\end{enumerate}

\pagebreak

\section{Getting Started} The \textsf{\journalclassshort} class file should run
on any standard \LaTeXe\ installation. If any of the fonts, style
files or packages it requires are missing from your installation,
they can be found on the \emph{\TeX\ Collection} DVDs or from
CTAN.

\emph{\journalnamelc} is published using Times fonts and this is
achieved by using the \verb"times"
option as\\
\verb"\documentclass[times]{fldauth}".

\noindent If for any reason you have a problem using Times you can
easily resort to Computer Modern fonts by removing the
\verb"times" option.

\begin{figure}
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\documentclass[times]{fldauth}
%\documentclass[times,doublespace]{fldauth}%For paper submission

\begin{document}

\runningheads{<Initials and Surnames>}{<Short title>}

\title{<Initial cap, lower case>}

\author{<An Author\affil{1},
Someone Else\affil{2}\corrauth\ and Perhaps Another\affil{1}>}

\address{<\affilnum{1}First author's address
(in this example it is the same as the third author)\break
\affilnum{2}Second author's address>}

\corraddr{<Corresponding author's address (the second author in
this example)>. E-mail: <corresponding author's email address>}

%\cgs{<Contract/grant sponsor name (no number)>}
%\cgsn{<Contract/grant sponsor name>}{<number>}

\begin{abstract}
<Text>
\end{abstract}

\keywords{<List keywords>}

\maketitle

\section{Introduction}
.
.
.
\end{boxedverbatim}
\end{center}
%\vspace{-12pt}
\caption{Example header text.\label{F1}}
\end{figure}

\section{The Article Header Information}
The heading for any file using \textsf{\journalclass} is shown in
Figure~\ref{F1}.

\subsection{Remarks}
\begin{enumerate}
\item[(i)] In \verb"\runningheads" use `\emph{et~al.}' if there
are three or more authors.

\item[(ii)] Note the use of \verb"\affil" and \verb"\affilnum" to
link names and addresses. The author for correspondence is marked
by \verb"\corrauth" and \verb"\corraddr" is used to give that
author's address, which will be printed as a footnote, prefaced by
`Correspondence to:'.

\item[(iii)] For submitting a double-spaced manuscript, add
\verb"doublespace" as an option to the documentclass line.

\item[(iv)] Use \verb"\cgs" for giving details of financial
sponsors; alternatively use \verb"\cgsn" if the grant number is
also to be included. These details will be printed as a footnote,
with `Contract/grant sponsor:' and `contract/grant number:'
inserted in the appropriate places.

\item[(v)] The abstract should be capable of standing by itself,
in the absence of the body of the article and of the bibliography.
Therefore, it must not contain any reference citations.

\item[(vi)] Keywords are separated by semicolons.
\end{enumerate}

\begin{figure}
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\begin{table}
\caption{<Table caption>}
\centering
\tabsize
\begin{tabular}{<table alignment>}
\toprule
<column headings>\\
\midrule
<table entries
(separated by & as usual)>\\
<table entries>\\
.
.
.\\
\bottomrule
\end{tabular}
\end{table}
\end{boxedverbatim}
\end{center}
\vspace{-6pt}
\caption{Example table layout.\label{F2}}
\vspace{-6pt}
\end{figure}

\section{The Body of the Article}

\subsection{Mathematics} \textsf{\journalclass} makes the full
functionality of \AmS\/\TeX\ available. We encourage the use of
the \verb"align", \verb"gather" and \verb"multline" environments
for displayed mathematics. \textsf{amsthm} is used for setting
theorem-like and proof environments. The usual \verb"\newtheorem"
command needs to be used to set up the environments for your
particular document.

\subsection{Figures and Tables} \textsf{\journalclass} includes the
\textsf{graphicx} package for handling figures.

Figures are called in as follows:
\begin{verbatim}
\begin{figure}
\centering
\includegraphics{<figure name>}
\caption{<Figure caption>}
\end{figure}
\end{verbatim}

For further details on how to size figures, etc., with the
\textsf{graphicx} package see, for example, \cite{R1}
or \cite{R3}. If figures are available in an
acceptable format (for example, .eps, .ps) they will be used but a
printed version should always be provided. \medbreak

The standard coding for a table is shown in Figure~\ref{F2}.

\subsection{Cross-referencing}
The use of the \LaTeX\ cross-reference system
for figures, tables, equations, etc., is encouraged
(using \verb"\ref{<name>}" and \verb"\label{<name>}").

\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
\verb"\acks" for \textit{Acknowledgement} or
\textit{Acknowledgements}, respectively. It must be placed just
before the References.

\subsection{Bibliography}
The normal commands for producing the reference list are:
\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{<x-ref label>}
         <Reference details>
.
.
.
\end{thebibliography}
\end{verbatim}
where \verb"\bibitem{x-ref label}"
corresponds to \verb"\cite{x-ref label}" in the body of the article
and \verb"{99}" is the widest such number expected and determines
the width of the number column in the reference list.

Please note that the file \textsf{wileyj.bst} is available from
the same download page for those authors using \BibTeX.

\subsection{Double Spacing}
If you need to double space your document for submission please
use the \verb+doublespace+ option as shown in the sample layout in
Figure~\ref{F1}.

\section{Support for \textsf{\journalclass}}
We offer on-line support to participating authors. Please contact
us via e-mail at\\
\href{mailto:fldauth-cls@wiley.co.uk}{\texttt{fldauth-cls@wiley.co.uk}}.

We would welcome any feedback, positive or otherwise, on your
experiences of using \textsf{\journalclass}.

\section{Copyright Statement}
Please  be  aware that the use of  this \LaTeXe\ class file is
governed by the following conditions.

\subsection{Copyright}
Copyright \copyright\ \volumeyear\ John Wiley \& Sons, Ltd, The
Atrium, Southern Gate, Chichester, West Sussex, PO19~8SQ, UK. All
rights reserved.

\subsection{Rules of Use}
This class file is made available for use by authors who wish to
prepare an article for publication in the \emph{\journalnamelc}
published by John Wiley \& Sons, Ltd. The user may not exploit any
part of the class file commercially.

This class file is provided on an \emph{as is}  basis, without
warranties of any kind, either express or implied, including but
not limited to warranties of title, or implied  warranties of
merchantablility or fitness for a particular purpose. There will
be no duty on the author[s] of the software or  John Wiley \&
Sons, Ltd to correct any errors or defects in the software. Any
statutory  rights you may have remain unaffected by your
acceptance of these rules of use.

\ack This class file was developed by Sunrise Setting Ltd,
Torquay, Devon, UK. Website:\\
\href{http://www.sunrise-setting.co.uk}{\texttt{www.sunrise-setting.co.uk}}

\begin{thebibliography}{9}

\bibitem{R1} Kopka~H, Daly~PW. 2003. \emph{A Guide to \LaTeX} (4th~edn).
Addison-Wesley.

\bibitem{R2} Lamport~L. 1994. \emph{\LaTeX: a Document Preparation System} (2nd~edn).
Addison-Wesley.

\bibitem{R3} Mittelbach~F, Goossens~M. 2004. \emph{The \LaTeX\ Companion}
(2nd~edn). Addison-Wesley.
\end{thebibliography}
\end{document}

### 2015-10-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Initial design of Kostas paper

% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later c.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with harvard style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%
%
\documentclass[preprint,authoryear,12pt]{elsarticle}

% Use the option review to obtain double line spacing
%\documentclass[authoryear,preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
%\documentclass[final,authoryear,1p,times]{elsarticle}
%\documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%\documentclass[final,authoryear,3p,times]{elsarticle}
%\documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%\documentclass[final,authoryear,5p,times]{elsarticle}
%\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

\usepackage{comment}

\usepackage{epstopdf}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{hyperref,url}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb,amsmath,array}
%The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subfigure}  
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

\usepackage{lscape}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%% \biboptions{longnamesfirst,comma}

% \biboptions{}

\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG Note $\Rightarrow$ #1}}}
\journal{Advances in Water Resources}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media}

%% use optional labels to link authors explicitly to addresses:
\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} 
\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}

\cortext[cor1]{Corresponding author.}
\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}

\begin{abstract}

\textcolor{blue}{Accurate simulation of multiphase flows in porous media remains a challenge. While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability. This paper introduce a multi-fluid porous media flow model which is the basis of a reservoir simulator, as implemented in Fluidity, a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics. The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
%The element type described above has a discontinuous $n^{th}$ order polynomial representation of velocity and a continuous $(n+1)^{th}$ representation for pressure. This method includes the Darcy force balance equation, pressure, velocity and saturation fields throughout the domain while there is automatic mesh adaptivity in space and time and the computational cost is reduced.} 
Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this. The impact of fingers formation in our simulations is also investigated.  
%This paper describes a  In particular, the \PNDG[1]{1} element (i.e., discontinuous and piecewise linear shape functions to discretise velocity and pressure fields) is introduced as the basis of the discretisation and also as the CVFEM counterpart. In addition to the unstructured grid used for the simulations, uniform and random permeability distribution are introduced. The formulation is applied to saturated porous media systems.
We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects. }

\end{abstract}

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods.

\end{keyword}

\end{frontmatter}

%\tableofcontents
%\linenumbers

\clearpage
%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Introduction}\label{section:Intro}
Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years. This is mainly due to applications on oil and gas recovery, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011} as well as in groundwater operations.

For reservoir engineers and hydrogeologists, mapping the behaviour of multiphase flows and predict the response of the system is a major challenge followed by complex geometries with irregular boundaries and heterogeneous geological formations. These are some of the main challenges for accurately forecasting the behaviour of flows into porous media. Both Permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media. %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales. 
At the microscopic level, the continuum approach can be applied to a representative elementary Volume (REV) to define these parameters~\citep{bastian_phd1999}. This is well suited for analysis of small scales such as core samples.

Although parallel processing is available nowadays, a fine-scale geological model is far too detailed to be accumulated by common reservoir simulators, mainly because of the processing time.

Therefore larger scales can be approached by upscaling techniques. This technique which is usually employed to solve the problem fails for certain types of heterogeneity. These cases are normally resolved by stochastic representation of permeability and porosity fields. 
%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
There are several approaches to upscale the solutions, while three common types are herein discussed. The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space renormalization methods. The $2^{nd}$ approach is called pseudoization. It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations. The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.

The first approach is limited to low flow rates and very small heterogeneity. The second approach overcomes these limitation but also posses drawbacks which include; availability of fine-grid simulation with suitable level of accuracy, dependence of the psuedo functions on rate, direction and grid specification. The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}. While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.

%\medskip
Under certain conditions the displacement of fluids in porous media is unstable and results in the formation of strange patterns in the form of \textit{fingers}. This phenomenon is referred to as \textit{viscous fingering}. The flow of an injected fluid into a geological formation (porous medium) generates many instabilities due to the heterogeneities of the porous medium. Even though the mechanism of the instabilities may vary (in \textcolor{blue}{immiscible fluids} the most important factor is the surface tension while in the \textcolor{blue}{miscible fluids} it is the diffusion) however it is still a function of many variables such as, relative mobility, gravity, dispersion, permeability differences. Moreover,in most of the cases interfacial tension is directly linked with the mobility ratio -or viscosity ratio- between the displaced and the displacing fluid.

Both the evolution of the computers and the advances in modelling and simulation of flows in porous media may help to visualise and address the importance of this phenomenon which can be found in many petroleum, chemical and environmental related applications.

%\medskip
Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc). However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}. Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}. The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.

Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}. In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.

Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces. Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties. Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface. This often leads to excessive numerical dispersion especially in highly heterogeneous media. In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}. This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.

\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.

%\medskip 
%\begin{center}
%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
%\end{center}

\textcolor{blue}{In this paper, the overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media. In the OCVFEM, a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}. In these element types, the dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations.\textcolor{red}{The main objective of this paper is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}. 
In addition, the study focused in flow instabilities determined by the viscosity ratio. In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space. Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space. High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions. Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation. Finally, conclusions are drawn in the final section.}

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Numerical Formulation}\label{section:NumericalFormulation}
In the OCVFEM formulation, a consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces is used with a recently developed family of $P_{m}DG-P_{n}$ tetrahedral element pairs.The new family of $PN_{n}{m}$ element pair was originally introduced. These element-pairs have a discontinuous $m^{th}$-order polynomial representation for velocity and a continuous representation for pressure of order {\it n}.  The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries, which are limited to yield bounded fields. 
This family of element pairs was originally introduced for geophysical fluid dynamics applications. In particular, the $P_{1}DG-P_{2}$ element pair was developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes. This element pair (Fig.~\ref{fig:2}) has a linear discontinuous basis function for velocity $\left(\text{P}_{1}\text{DG}\right)$ and a quadratic polynomial basis function for pressure $\left(\text{P}_{2}\right)$ which maintains $C_{\text{0}}$ continuity across element boundaries. Pressure nodes are located at the element corners and mid-points of the element-edges and control volumes are built around them. Scalar fields, such as saturation, density, temperature, species concentration are stored in control volume space. This family of finite element pairs, when used with the OCVFEM method presented here, is mass conservative and also exactly enforces the force balance represented by the multiphase Darcy equation.

Let's assume a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions). Darcy's law for single phase flow can be extended for immiscible multiphase flow as,
\begin{equation}
  \mathbf{q}_{k} = -\frac{\mathcal{K}_{{r}_k}\left(S_{k}\right)\mathbf{K}}{\mu_{k}}\left( \nabla p_{k} - {\mathbf{s}_{u}}_{k} \right),
%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{k} = \underline{\underline{\sigma}}_{k} {\bf u}_{k} = -\nabla p + \mathcal{S}_{u},
\label{Eqn:DarcyEq}
\end{equation}
where $\mathbf{q}_{k}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate. $S$, $\mathbf{K}$, $\mathcal{K}_{rk}\left(S_{k}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively. $s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.

 Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{k}= \mathbf{q}_{k}/S_{k}$, then we may rewrite Eq.(\ref{Eqn:DarcyExt0}),
\begin{equation}
  {\underline {\underline \sigma}}_{k} \mathbf{u}_{k} = - \nabla p + {\mathbf{s}_{u}}_{k},
  \label{Eqn:DarcyExt}
\end{equation}
$\underline{\underline{\sigma}}_{k}=\mu_{k}S_{k}\left(\mathcal{K}_{rk}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.

The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,

\begin{eqnarray}
\left(\displaystyle\frac{\mu_{k}S_{k}}{{\mathbf K}\mathcal{K}_{rk}}\right) {\mathbf u}_{k} = \underline{\underline{\sigma}}_{k} {\mathbf u}_{k} = -\nabla p + \mathcal{S}_{u,k},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
\phi\displaystyle\frac{\partial S_{k} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{k}  S_{k}\right) =  \mathcal{S}_{cty,k},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
\end{eqnarray}

where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively. ${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,k}$ is the relative permeability. $\mathcal{S}$ is the source term associated with the Darcy and continuity equations. $S_{k}$ is saturation of the $k$-phase with the constraint of $\sum\limits_{k=1}^{\mathcal{N}_{p}} S_{k} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.

Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}. Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element. $\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces. Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries. The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}. Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
%\textcolor{red}{KC: could you add 1-2 short paragraphs on viscous instabilities ... focus on the phenomena rather than a literature review, that may take place in the Intro Section}
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions. Under this assumption, viscous fingering is no exception. It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity. This type of instability can be found across many research areas, disciplines and scales. Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.

However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows. Those three mechanisms are shielding, spreading and tip-splitting. Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches. It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR). Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.

Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers. The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR). This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.

%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.

Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$. The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$. Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.

\begin{equation}
 U = \frac{b^2}{12 \mu} \nabla p
\end{equation}

and the above equation can be re-arranged for 1D steady flow as,

\begin{equation}
 \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g 
\end{equation}

where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.

Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly. Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is

\begin{equation}
\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
\end{equation}

If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\

\begin{equation}
U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
\end{equation}

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Model Validation}\label{section:ModelValidation}

%%%         %%%
%%% SECTION %%%
%%%         %%%
\subsection{Bucklet-Leverett Equation}\label{section:BuckletLeverettEquation}
\textcolor{red}{JG: text and simulation of P1DGP2, P1DGP1DG fixed and adaptive mesh -- quantitative analysis}\\
\textcolor{blue}{KC: do i have to mention something here?\\}

Models of water and another fluid, such as air, flowing through a
porous material, are used throughout science and
engineering.  Furthermore, individual chemical and biological
substances being transported in the fluids are often fundamentally
important. The mathematical models for these processes take several forms: scalar nonlinear parabolic equations (Richards' equation), scalar hyperbolic equations (Buckley-Leverett equation), systems of degenerate nonlinear parabolic systems (two-phase and compositional flow), and free boundary problems (Muskat's model). These are macroscopic continuum models that govern the distribution and evolution of quantities that are {\em averages} of the densities, pressures, and velocities arising in classical fluid mechanics. The basis of porous media models in microscopic physics is, however, incomplete: many observed phenomena such as history-dependent behavior and various other scale effects have not been satisfactorily modeled, particularly for multiphase,
multicomponent systems at the scale required for environmental
studies.

Modeling of two-phase immiscible flows in porous media is
important for many industrial applications, such as oil recovery and carbon sequestration. Mathematical conceptualizations for such flows include the Buckley–Leverett model, which, in its simplest form, is represented by a nonlinear advection equation for the relative saturation of fluid phases.This equation models the two phase flows that arise oil-recovery problems and physically
represents a mixture of oil and water through the porous medium.
In conservative form the flux function for this
problem is given by:
\begin{equation}
f(u) = \frac{u^2}{u^2 + \nu(1-u)^2}. \label{buckley}
\end{equation}
Here $\nu$ is viscosity ratio and $u$ represents the saturation of water and
lies between $0$ and $1$.

\subsection{Four Regions}\label{section:4Regions}
\textcolor{blue}{KC \textcolor{red}{WR}: text and simulations -- qualitative analysis}\\

Starting from the simplest case of simulations as describe in fig. \ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities. We inject fluid 1 across the left hand side of the formation and we are trying to displace the existing fluid 2. The front start to collapse and one main finger starts to appear.

The behaviour as well as the prediction of the two different phase volume fractions can be qualitatively compared with bibliographic results. The two phase volume volume fractions have the same but opposite behaviour across the length of the formation. As we inject fluid 1, at the first half of the formation the velocity magnitude is increasing while pressure drops gradually. This behaviour changes at the middle of the formation where there is the transition from one permeability zone to the other and the front has already collapsed forming the finger.

From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced. There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig. \ref{fig:1} the phase volume fraction is constant. (\textcolor{blue}{KC: i think we can rephrase it better here.})

Later, we introduce two versions of a second set of simulations consisted of the same number of regions (4) but with different formations and phase ratios as can be described in fig. \ref{fig:2} to fig. \ref{fig:subim7}.

The initial and boundary condition regarding the inlet and outlet are the same. The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems.

The main body of the formation (blue area) is where fluid 2 exists fig. \ref{fig:3}. Above the blue area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio. All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.

Fluid 1 is again injected across the left hand side of the formation. In this case the value of mobility or \textit{viscosity ratio} is 10. Later on mobility ratios of different values will be introduced and compared. As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow. The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development. In fig.\ref{fig:2} and fig.\ref{fig:3}) the mesh deforms on time and on space and that allows the user to have an initial good qualitative approach regarding the development of the multiphase flow. In fig. \ref{fig:subim6} and fig. \ref{fig:subim7} the patterns of the multiphase flows for the phase 1 and phase 2 are described respectively.

Based on the graph/plots for the second set of simulations we can get a initial approach and relation between the quantitative and qualitative outcome of our simulations. It is experimentally validated and is happening in this case that fingers will develop faster in areas where permeabilities are higher. This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid 1. Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists. After flowing through this area there is a balance (plateau) among the two faces on time fig.\ref{fig:subim8 middle}. Going higher in the formation, fig.\ref{fig:subim9 up} in the next zone just above the main body (blue area), there is an initial fluctuating decrease  of the velocity of the injected fluid which is driven by the different permeability value. At the top layer ref.\ref{fig:subim10 upper} of the formation there is a smooth increase of the injected fluid velocity magnitude which basically describes an overall and study development of the flow while just before the end collapses.

Comparing the three plots we can see three different velocities to be developed which means that numerically the initial uniform front collapses. This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Viscous Instabilities}\label{section:ViscousInstabilities}

An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous 
instabilities. An unfavourable - mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time. Although numerical investigations 
in the last few years have remarkably improved the physical 
understanding of viscous fingering, some questions still remain 
unanswered.\\

First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance? Second, how 
is a viscous instability affected by parameters including mobility 
ratio and/or permeability variance. \textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}

\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}

The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure. At the $n+1$ step those two equations mentioned above can be rewritten as,

\begin{equation}
M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
\label{mass balance eq}
\end{equation}

\begin{equation}
B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
\label{force balance eq}
\end{equation}

\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element. This system of equations can be rewritten to produce the pressure equation,

\begin{equation}
B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
\label{pressure eq}
\end{equation}

The computationally demanding effort to solve the pressure matrix equation (arising from the discontinuous FEM formulation) is achieved using a multigrid-like approach.

The original geometry of the system is an orthogonal 2D domain where the  heterogeneity is imposed by introducing 4 distinct regions of four regions of different absolute permeabilities (K) as can being seen in fig.\ref{fig:1} and fig. \ref{fig:subim6}.

The Richard equation (non-linear advection equation) for relative saturation fluid phases representing two phases immiscible flows in porous media has been simulated. The fluid $1$ or \textit{injected fluid} is injected a a velocity of $u_1 \phi = 1$. On the outlet, or right hand side boundary, the pressure level is set to zero and all the remaining boundary are naturally applied. All the simulations discussed in this section used the overlapping control volume FEM with a piecewise linear variation of the velocity with each element and quadratic pressure ($P_1 DG-P_2$). Saturation is collocated at the  pressure nodes and although it is calculated using a CV formulation, a FEM interpolation is used to form the higher order fluxes. There is no flow across the lower and upper boundaries (no-slip conditions) and the initial velocity of the fluid 2 or displaced fluid is set to zero, while the gravity is assumed negligible.

%%%         %%%
%%% SECTION %%%
%%%         %%%
\subsection{Impact of Permeability Field}\label{section:PermeabilityAnalysis}

The higher the permeability of a medium, the easier it is for flow to propagate through it. Therefore, fluid will flow faster through the higher permeability region. Hence, in Case 1, it is expected that the injected fluid will flow fastest in the top layer which has the highest permeability. The second layer's permeability is higher than that of the bottom layer, so also, its front should be expected to move ahead of that of the bottom layer. The high permeability zone within the lower layer may result in some interesting flow characteristics at the horizontal flow boundary (the top and bottom boundary) depending on the difference between the two permeabilities. If this difference is sufficiently large enough, the fluid from the low permeability region will tend to cross into the high permeability region and flow forward from there. This will result in a region of reduced flow at these boundaries just beyond the deviation from normal flow and may also cause a stationary point at these boundaries within the flow.

\medskip
\textcolor{red}{WR: results }

%%%         %%%
%%% SECTION %%%
%%%         %%%
\subsection{Investigation of Viscosity (Mobility? I think its better if i keep as Mobility Ratio) Ratio}\label{section:MobilityAnalysis}
\textcolor{red}{KC: would you like to add a paragraph on the expected impact of MR in the flow?}\\
\medskip
\textcolor{red}{WR and KC: results}\\
%------------------------KC------------------------------------------

During the simulations performed in this paper the Viscous fingering phenomenon has been observed. Viscous fingering  is highly related with the mobility, which describes how easily a fluid moves into a porous media and can be expressed through the mobility ratio (\textit{MR}). The ratio between the mobility of the displacing phase to the mobility of the displaced.

It generally accepted \textcolor{red}{can we say that...?} ( Saffman and Taylor, $1958$, Chouke et al., $1959$, Peters,$1979$ and Homsy,$1987$) that the higher the mobility ratio the easier is for viscous fingering to appear and more specific, for fingers to start to develop and grow. In the simulations above an $MR=10$ is used. This ration combined with the use of unstructured adaptive mesh makes the fingers more visible, easier to detect them. For cases where the is less than 5, ($MR \le 5$) we expect no difference as there is no significant impact. In the extreme case of $MR=1$ we can clearly see the relation between finger development and the zones of different porosity.      
%------------------------KC------------------------------------------

\pagebreak

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Final Remarks}\label{section:conclusions}
%\textcolor{red}{KC and WR: do you want to have a bash on this ?}\\ 
%------------------------KC------------------------------------------
\textcolor{blue}{KC - i will try to have something on it as well}

In the first set of simulations, saturation phase 2 is set to one throughout the whole domain ($S_2 = 1$) whereas fluid 1 is injected in the left boundary. Starting from fig.\ref{fig:1st} and ending to fig.\ref{fig:4th} the total transition from setting the simulations and using the elements mentioned in previous section, as well as the intermediate results and the final stage of simulations are described.

The number of elements used under the fixed coarse mesh approach is almost $5000$ elements and it is less than the instructed and adaptive mesh  grids which is around $20500$ elements while the max number has reached up to $24000$. The later mesh can focus the resolution inthe saturation front. In fig.\ref{fig:4} it can be seen that the high permeability square-region, where most of the fingers are formed are most noticeable.

In the case of both saturated/unsaturated porous media the square region is initially saturated with the fluid 1. The pattern of the initial inlet front is almost similar with the case mentioned above. The behaviour in the two top layers interface is initially inverse exponential followed by a direct decrease in the saturation front due to fingering.

We proposed a surface-based approach to reservoir modelling. The new overlapping control volume finite element method for multi-fluid flows is based upon an dual consistent velocity-pressure representation in CV and FEM spaces introducing the element type family of $P_n DG P_{n+1}$.  
The aim of the paper is to extend apply the formulation to to multiphase flows in heterogeneous porous media. The above method is beneficial for two reasons. Firstly, numerical dispersion is reduced by adaptively refining the grid on time and space as the displacement front is evolving. Secondly the multi-scale heterogeneity can be better captured using the above mesh formation that can be adjusted to complex reservoir geometries over a wide variety of length-scales, without required the petrophysical properties to be rescaled each time that the mesh is changed.\\

\textcolor{blue}{The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution. So far, the results illustrate that the displacing fluid tends to flow easier towards the zones with higher values of permeability (spatial acceleration / deceleration of flow – fingers formation). It can also be seen that finger like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability. This behaviour is triggered by the permeability contrast among layers.
As can be seen from Fig........ the higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content. Also, the higher the viscosity ratio, more to the right the breakpoint is shifted, in the time axis. The increased viscosity ratio increases the computational cost and requires the decrease of the solution's time-step.
Both the geometrical domain and the development of the flow, as can be seen in Fig........ follow the linear tip-splitting finger behaviour. In addition properties such as porosity and saturation can be readily up-scaled using statistical methods.%, like the python function that was introduced in the second case of the simulations, that provides fast and reasonable values.
To conclude, up-scaling or averaging the geological model can assist in running reservoir models faster and as close as possible to fine geological model.}\\

In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages:

\begin{enumerate}
\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\

\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability.
\item[3.] Finger-like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability. This behaviour is triggered by the permeability contrast among layers.
\item[4.] The higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
\item[5.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes. At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
\item[6.] Both the geometrical domain and the development of the flow follow the linear tip-splitting finger behaviour.
\item[7.] Properties such as porosity and saturation can be readily up-scaled using statistical methods while production simulations run directly on the geological model without the need to upscale.

\end{enumerate}

\noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.

%------------------------KC------------------------------------------

\section{Achknowledgements}
Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}. Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}). Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.

%\textcolor{blue}{KC - Is it valid to include that part of this work has been published in international conferences and being awarded.}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References with bibTeX database:
\bibliographystyle{elsarticle-harv}
\bibliography{references}

\pagebreak
\clearpage

%\listoftables
%\pagebreak
%\input{Manuscript_Table}

\pagebreak
\clearpage

\listoffigures

\begin{figure}[h]
\makebox[\textwidth]{%
\includegraphics[width=0.49\textwidth]{2b2_P1DGP2_perm}%
\hfill    
\includegraphics[width=0.49\textwidth]{2b2_P1DGP2_mesh}%
}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\includegraphics[width=0.75\textwidth]{2b2_P1DGP2_plot}%
}%
\caption{ Caption 1}
\label{fig:1}
\end{figure}

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\centering
%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
%\caption{Caption 3}
%\label{fig:subim3}
%\end{center}

%\caption{Caption for this figure with two images}
%\label{fig:image1}
%\end{figure}
%\pagebreak
%\clearpage

\begin{figure}[h]

\begin{center}
\centering
\includegraphics[width=0.75\linewidth, height=5cm]{P1DG-P2_element_type} 
\caption{Caption 2}
\label{fig:2}
\end{center}

\begin{center}
\centering
\includegraphics[width=0.8\linewidth, height=7cm]{4r_po_adapt_fine_125_mesh} 
\caption{Caption 3}
\label{fig:3}
\end{center}

\begin{center}
\centering
\includegraphics[width=0.8\linewidth, height=7cm]{4r_po_adapt_fine_100_mesh}
\caption{Caption 4}
\label{fig:4}
\end{center}

%\caption{Caption for this figure with two images}
\label{fig:image2}
\end{figure}
\pagebreak
\clearpage

\begin{landscape}
\begin{figure}[ht!]
\begin{center}
\subfigure[MR100, at the beginning of the simulations]{%
\label{fig:1st}
\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_100}
}%
\subfigure[MR100, at the middle of the simulation]{%
\label{fig:2nd}
\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
}\\
\subfigure[MR100, Phase 1 Volume fraction]{%
\label{fig:3rd}
\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase1_vol_frac}
}%
\subfigure[MR100, Phase 2 Volume fraction]{%
\label{fig:4th}
\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase2_vol_fraction}
}\\
\caption{Comparison of different MR's and their recovery rates}
\label{fig:5}
\end{center}
\end{figure}
\end{landscape}

\pagebreak
\clearpage
%\input{article_figure1}
%\input{Manuscript_Figure1}

\begin{figure}[ht!]
\begin{center}
\subfigure[MR1]{%
\label{fig:first}
\includegraphics[width=0.7\textwidth]{MR1.png}
}%
\subfigure[Recovery for MR1]{%
\label{fig:second}
\includegraphics[width=0.52\textwidth]{Recovery_MR1_1.png}
}\\
\subfigure[MR10]{%
\label{fig:first}
\includegraphics[width=0.7\textwidth]{MR10.png}
}%
\subfigure[Recovery for MR10]{%
\label{fig:second}
\includegraphics[width=0.52\textwidth]{Recovery_MR10_10.png}
}\\
\subfigure[MR100]{%
\label{fig:first}
\includegraphics[width=0.7\textwidth]{MR100_100_start.png}
}%
\subfigure[Recovery for MR100]{%
\label{fig:second}
\includegraphics[width=0.52\textwidth]{Recovery_MR100_100.png}
}\\ 
\end{center}
\caption{Comparison of different MR's and their recovery rates}
\label{fig:6}
\end{figure}

\end{document}
%% End of tex file.

%%  LocalWords:  checkboard

### 2015-10-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in the Abstract and first paragraphs of Introd.

@@
 \newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG Note $\Rightarrow$ #1}}}
+\newcommand{\red}{\textcolor{red}}
 \journal{Advances in Water Resources}
@@
 
-\textcolor{blue}{Accurate simulation of multiphase flows in porous media remains a challenge.
+Accurate simulation of multiphase flows in porous media remains a challenge \red{(Why?
+Sentencing is hanging ...
+word `accurate' is vague here!
+The second sentence is not gramatically correct and too simplistic -- see notes below.)}.
 While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability.
-This paper introduce a multi-fluid porous media flow model which is the basis of a reservoir simulator, as implemented in Fluidity, a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics.
+This paper introduces a multi-fluid porous media flow model which is the basis of a reservoir simulator, as implemented in Fluidity, a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics.
 The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
@@
 We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.
-}
+
+\JGnote{ Abstracts for journal papers have very `squared-structure': (a) Motivation (why would anyone bother to read the paper?
+Why is it (the paper and/or the subject) relevant?
+This needs to be covered in 1-3 punchy sentences.); (b) (Main) Objective(s) of the manuscript with particular focus on the \underline{novelty(ies)} the paper may bring (this should be covered in 2-6 (very dry) sentences); (c) Summary of the main technologies that you are using or introducing (and, in some cases, how this/these link(s) with (a), 2-6 sentences); (d) Summary of the main findings (linkage with (b), 2-3 sentences).}
 
@@
 Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-This is mainly due to applications on oil and gas recovery, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011} as well as in groundwater operations.
+This is mainly due to applications on oil and gas recovery, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
-For reservoir engineers and hydrogeologists, mapping the behaviour of multiphase flows and predict the response of the system is a major challenge followed by complex geometries with irregular boundaries and heterogeneous geological formations.
-These are some of the main challenges for accurately forecasting the behaviour of flows into porous media.
-Both Permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.
-%Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
+For reservoir engineers and hydrogeologists, mapping \red{(you don't map a behaviour)} the behaviour of multiphase flows and predict the response of the system are major challenges followed by complex geometries with irregular boundaries and heterogeneous geological formations \red{(sentence needs to be improved)}.
+These are some of the main challenges \red{(too many challenges in the same paragraph ...)} for accurately forecasting the behaviour of flows into porous media.
+Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
 At the microscopic level, the continuum approach can be applied to a representative elementary Volume (REV) to define these parameters~\citep{bastian_phd1999}.
-This is well suited for analysis of small scales such as core samples.
+This is well suited for analysis of small scales such as core samples \red{(These sentences are not linked with the previous sentences, also what is the objective of them?
+)}.
 
 Although parallel processing is available nowadays, a fine-scale geological model is far too detailed to be accumulated by common reservoir simulators, mainly because of the processing time.
+\red{(Same comment as above!)}
 
@@
 While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
+\red{From `At the microscopic level ...' to `...reservoir simulations' --try to rewrite these sentences/paragraphs ...
+they are very confusing and not really connected'}
+
+\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage w previous paragraphs or linkage w the main subject(s).}
 
@@
 \makebox[\textwidth]{%
-\includegraphics[width=0.49\textwidth]{2b2_P1DGP2_perm}%
+\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_perm}%
 \hfill    
-\includegraphics[width=0.49\textwidth]{2b2_P1DGP2_mesh}%
+\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_mesh}%
 }\\[0.5cm]% If you want some vertical space
 \makebox[\textwidth]{%
-\includegraphics[width=0.75\textwidth]{2b2_P1DGP2_plot}%
+\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2_plot}%
 }%
@@
 \centering
-\includegraphics[width=0.75\linewidth, height=5cm]{P1DG-P2_element_type} 
+\includegraphics[width=0.75\linewidth, height=5cm]{./Pics/P1DG-P2_element_type} 
 \caption{Caption 2}
@@
 \centering
-\includegraphics[width=0.8\linewidth, height=7cm]{4r_po_adapt_fine_125_mesh} 
+\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_125_mesh} 
 \caption{Caption 3}
@@
 \centering
-\includegraphics[width=0.8\linewidth, height=7cm]{4r_po_adapt_fine_100_mesh}
+\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_100_mesh}
 \caption{Caption 4}
@@
 \label{fig:1st}
-\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_100}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
 }%
@@
 \label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
 }\\
@@
 \label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase1_vol_frac}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
 }%
@@
 \label{fig:4th}
-\includegraphics[width=0.75\textwidth]{4r_po_adapt_fine_125_phase2_vol_fraction}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
 }\\
@@
 \label{fig:first}
-\includegraphics[width=0.7\textwidth]{MR1.png}
+\includegraphics[width=0.7\textwidth]{./Pics/MR1.png}
 }%
@@
 \label{fig:second}
-\includegraphics[width=0.52\textwidth]{Recovery_MR1_1.png}
+\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
 }\\
@@
 \label{fig:first}
-\includegraphics[width=0.7\textwidth]{MR10.png}
+\includegraphics[width=0.7\textwidth]{./Pics/MR10.png}
 }%
@@
 \label{fig:second}
-\includegraphics[width=0.52\textwidth]{Recovery_MR10_10.png}
+\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
 }\\
@@
 \label{fig:first}
-\includegraphics[width=0.7\textwidth]{MR100_100_start.png}
+\includegraphics[width=0.7\textwidth]{./Pics/MR100_100_start.png}
 }%
@@
 \label{fig:second}
-\includegraphics[width=0.52\textwidth]{Recovery_MR100_100.png}
+\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
 }\\ 

### 2015-10-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %\medskip
-Under certain conditions the displacement of fluids in porous media is unstable and results in the formation of strange patterns in the form of \textit{fingers}.
+Under certain conditions the displacement of fluids in porous media is unstable \red{(what sort of conditions?)} and results in the formation of strange patterns \red{(sentence is not very technical} in the form of \textit{fingers}.
 This phenomenon is referred to as \textit{viscous fingering}.
-The flow of an injected fluid into a geological formation (porous medium) generates many instabilities due to the heterogeneities of the porous medium.
-Even though the mechanism of the instabilities may vary (in \textcolor{blue}{immiscible fluids} the most important factor is the surface tension while in the \textcolor{blue}{miscible fluids} it is the diffusion) however it is still a function of many variables such as, relative mobility, gravity, dispersion, permeability differences.
-Moreover,in most of the cases interfacial tension is directly linked with the mobility ratio -or viscosity ratio- between the displaced and the displacing fluid.
+The flow of an injected fluid into a geological formation (porous medium) generates instabilities due to the heterogeneities of the porous medium \red{(Is this correct?
+Is it your opnion?
+If so built up the facts to substantiate your conclusions.
+If it is not your opinion then give reference(s))}.
+Even though the mechanism of the instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
+Moreover, in most cases interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid.
 
 Both the evolution of the computers and the advances in modelling and simulation of flows in porous media may help to visualise and address the importance of this phenomenon which can be found in many petroleum, chemical and environmental related applications.
+\red{(sentence is not written in a technical format, also what is its objective?)}
 
 %\medskip
+\begin{comment}
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
@@
 Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+\end{comment}
 
@@
 
-\textcolor{blue}{In this paper, the overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.
+In this paper, the overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media \red{(what is the objective of this paper?
+To study multiphase porous media flows?
+Or to study a particular physical aspect of multiphase flows in porous media?
+You need to be precise here!
+)}.
 In the OCVFEM, a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
@@
 Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
-Finally, conclusions are drawn in the final section.}
+Finally, conclusions are drawn in the final section.
 

### 2015-11-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex

@@
 
-For reservoir engineers and hydrogeologists, mapping \red{(you don't map a behaviour)} the behaviour of multiphase flows and predict the response of the system are major challenges followed by complex geometries with irregular boundaries and heterogeneous geological formations \red{(sentence needs to be improved)}.
-These are some of the main challenges \red{(too many challenges in the same paragraph ...)} for accurately forecasting the behaviour of flows into porous media.
-Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-At the microscopic level, the continuum approach can be applied to a representative elementary Volume (REV) to define these parameters~\citep{bastian_phd1999}.
-This is well suited for analysis of small scales such as core samples \red{(These sentences are not linked with the previous sentences, also what is the objective of them?
+Reservoir engineers and hydrogeologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
+To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
+%This is well suited for analysis of small scales such as core samples.
+\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
 )}.
 
-Although parallel processing is available nowadays, a fine-scale geological model is far too detailed to be accumulated by common reservoir simulators, mainly because of the processing time.
-\red{(Same comment as above!)}
-
-Therefore larger scales can be approached by upscaling techniques.
+Larger scale problems can be approached by upscaling techniques.
 This technique which is usually employed to solve the problem fails for certain types of heterogeneity.
@@
 While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
-\red{From `At the microscopic level ...' to `...reservoir simulations' --try to rewrite these sentences/paragraphs ...
-they are very confusing and not really connected'}
 
@@
 %\medskip
-Under certain conditions the displacement of fluids in porous media is unstable \red{(what sort of conditions?)} and results in the formation of strange patterns \red{(sentence is not very technical} in the form of \textit{fingers}.
-This phenomenon is referred to as \textit{viscous fingering}.
-The flow of an injected fluid into a geological formation (porous medium) generates instabilities due to the heterogeneities of the porous medium \red{(Is this correct?
-Is it your opnion?
-If so built up the facts to substantiate your conclusions.
-If it is not your opinion then give reference(s))}.
+Under certain \red{(spatial or geological, which is the best word?)} conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of \textit{fingers}.
+This phenomenon, that describes these flow instabilities mentioned above is referred to as \textit{viscous fingering}.
 Even though the mechanism of the instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
@@
 
-Both the evolution of the computers and the advances in modelling and simulation of flows in porous media may help to visualise and address the importance of this phenomenon which can be found in many petroleum, chemical and environmental related applications.
-\red{(sentence is not written in a technical format, also what is its objective?)}
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of flows in porous media may help to represent and address the importance of this phenomenon which can be found in petroleum, chemical and environmental related applications.
 
 %\medskip
-\begin{comment}
+%\begin{comment}
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
@@
 Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-\end{comment}
+%\end{comment}
 
@@
 
-In this paper, the overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media \red{(what is the objective of this paper?
-To study multiphase porous media flows?
-Or to study a particular physical aspect of multiphase flows in porous media?
-You need to be precise here!
-)}.
-In the OCVFEM, a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
-In these element types, the dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-Moreover, velocity field has dual mapping in FEM and CV spaces.
-This approach can achieve an exact representation of the Darcy force balance equations.\textcolor{red}{The main objective of this paper is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
+The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
+Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
 In addition, the study focused in flow instabilities determined by the viscosity ratio.
@@
 
-During the simulations performed in this paper the Viscous fingering phenomenon has been observed.
+During the simulations performed the Viscous fingering phenomenon has been observed.
 Viscous fingering  is highly related with the mobility, which describes how easily a fluid moves into a porous media and can be expressed through the mobility ratio (\textit{MR}).

### 2015-11-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex

@@
 \begin{abstract} 
-
-Accurate simulation of multiphase flows in porous media remains a challenge \red{(Why?
-Sentencing is hanging ...
-word `accurate' is vague here!
-The second sentence is not gramatically correct and too simplistic -- see notes below.)}.
+Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines Accurate prediction of multiphase flows in porous media remains one of the problems.
 While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability.
-This paper introduces a multi-fluid porous media flow model which is the basis of a reservoir simulator, as implemented in Fluidity, a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics.
+This paper introduces a multi-fluid porous media flow model which is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics.
 The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.

### 2015-11-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
initial update and comments of the paper ...

@@
 \journal{Advances in Water Resources}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
 
@@
 %\medskip
-Under certain \red{(spatial or geological, which is the best word?)} conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of \textit{fingers}.
-This phenomenon, that describes these flow instabilities mentioned above is referred to as \textit{viscous fingering}.
-Even though the mechanism of the instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
+Under specfic spatial conditions the displacement of fluids in porous media is unstable {\bf(why?)} and results in the formation of irregular flow patterns in the form of fingers.
+This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??)}.
+Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
 Moreover, in most cases interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid.
+\medskip
+%Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of flows in porous media may help to represent and address the importance of this phenomenon which can be found in petroleum, chemical and environmental related applications.
+{\bf (does the paper address any aspect of parallel computation or computational/data visualization?)}
 
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of flows in porous media may help to represent and address the importance of this phenomenon which can be found in petroleum, chemical and environmental related applications.
+In this paper, the overlapping control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
+In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
+Scalar fields (e.g., saturation, concentration, density, etc) are represented in the CV space.
+High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
+This formulation can achieve an exact representation of the Darcy force balance equations.
 
-%\medskip
-%\begin{comment}
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+\medskip
 
-Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
-In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
-
-Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
-Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-%\end{comment}
-
-%\medskip 
-%\begin{center}
-%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
-%\end{center}
-
-In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
-The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
-The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
-In addition, the study focused in flow instabilities determined by the viscosity ratio.
-In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
-High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
+Here, the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
+{\bf (try to develop it further; be more specific.
+Write this objective sentence/paragraph based on the paper's conclusions!)}.
+This study focuses on flow instabilities determined {\bf(determined or controlled?)} by the viscosity ratio.
 Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
 Finally, conclusions are drawn in the final section.
+{\bf (Needs better description of the remaining of teh paper.)}
 

### 2016-05-08 Papers/Prototype_Accepted/KickAssIJNMF/CommentsForReviewers.tex
updates

\documentclass[12pts,a4paper,amsmath,amssymb,floatfix]{article}
\usepackage{graphicx,pdfpages}% Include figure files
\usepackage{enumerate}% Align table columns on decimal point
\usepackage{bm,dpfloat}% bold math
\usepackage[pdftex,bookmarks,colorlinks=true,urlcolor=rltblue,citecolor=blue]{hyperref}
\usepackage{amsfonts,amsmath,amssymb,stmaryrd,indentfirst}
\usepackage{times,psfrag,comment}
\usepackage{color}
\usepackage{float}

%%%
%%% Page Format
%%%
\setlength\textwidth      {16.cm}
\setlength\textheight     {22.6cm}
\setlength\oddsidemargin  {-0.3cm}
\setlength\evensidemargin {0.3cm}
\setlength\headheight{14.49998pt} 
\setlength\topmargin{0.0cm}
\setlength\headsep{1.cm}
\setlength\footskip{1.cm}
\setlength\parskip{0pt}
\setlength\parindent{0pt}

%%%
%%% Space between lines
%%%
\renewcommand{\baselinestretch}{1.5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%%      NOTATION SECTION        %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Text abbreviations.
\newcommand{\ie}{{\em{i.e., }}}
\newcommand{\eg}{{\em{e.g., }}}
\newcommand{\wrt}{with respect to}
\newcommand{\lhs}{left hand side}
\newcommand{\rhs}{right hand side}
\newcommand{\frc}{\displaystyle\frac}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%% END OF THE NOTATION SECTION  %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{description}
%%%
\item[\blue{Comment 1:}] \blue{``In Section 2.5 I found the interchange of the symbol {\bf v} (force per unit volume) with {\bf u} (saturation-weighted Darcy velocity) to be confusing: in the notation of eqn. 2, I would have expected to find $\mathbf{\tilde{v}_{\alpha}}$ instead of $\mathbf{\tilde{u}_{\alpha}}$. The same goes for eqn. 15. Moreover, it is not clear how eqn. 12 is derived and whether eqn. 15 replaces eqn. 13 or not. The two final paragraphs in the section are rather obscure and should be expanded more.''}\\
 bal bal
%%%
\item[\blue{Comment 2:}] \blue{``The matrix $\mathbf{B}$ and the source term $s_{p}$ in eqn. 10 are not explicitly defined as the terms of eqn. 5 are.''}\\
%%%
\item[\blue{Comment 3:}] \blue{``(...) a statement in the {\it Conclusions} that 'control volumes do not span elements' apparently contradicts the sentence that 'Control volume (CV) boundaries span finite elements where material properties	are defined' (...) ''}\\
%%%
\item[\blue{Comment 4:}] \blue{``(...) the demonstration case `3d fluvial channel' is not sufficiently developed. It is not clear what are the specific challenges that a similar problem poses, compared to similar efforts found in the literature; and it is not specified what is the representative computational time for its solution (...) ''}\\
%%%
\item[\blue{Comment 5:}] \blue{``
''}\\
%%%

%%%
\end{description}

\end{document}

### 2016-05-08 Papers/Prototype_Accepted/KickAssIJNMF/article_bak.tex
updates

\documentclass[times]{fldauth}

\usepackage{moreverb}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage{graphicx}

\usepackage{epsfig}

\usepackage{comment}

\usepackage{epstopdf}

\usepackage{subfig}

\usepackage{bm}
\usepackage{hyperref,url}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}

%\usepackage[obeyFinal]{todonotes}
\usepackage{todonotes}
\newcommand{\jrp}[1]{\todo[color=blue!30, size=\small]{JRP: #1}}
\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG: #1}}}

\usepackage{amssymb,amsmath,array}

\newcommand{\frc}{\displaystyle\frac}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}

\begin{document}

\address{\affilnum{1} Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK. \\ \affilnum{2}Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK. \\ \affilnum{3} Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK.}
\corraddr{Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK. E-mail: dimitrios.pavlidis@imperial.ac.uk}

\runningheads{J. L. M. A. Gomes \textit{et al.}}{A Force-Balanced CVFEM for Multi-phase Porous Media Flow Modelling}

\title{A Force-Balanced Control Volume Finite Element Method for Multi-phase Porous Media Flow Modelling}

\author{J. L. M. A. Gomes\affil{3,1}, D. Pavlidis\corrauth\affil{1,2}, P. Salinas\affil{1,2}, Z. Xie\affil{1,2}, J. R. Percival\affil{2}, \\Y. Melnikova\affil{1,2}, C. C. Pain\affil{1,2}, M. D. Jackson\affil{1}}

\begin{abstract}
  A novel method for simulating multi-phase flow in porous media is
  presented. The approach is based on a control volume finite element
  mixed formulation and new force-balanced finite element pairs. The
  novelty of the method lies in: (a) permitting both continuous and
  discontinuous description of pressure and saturation between
  elements; (b) the use of arbitrarily high-order polynomial
  representation for pressure and velocity and (c) the use of
  high-order flux-limited methods in space and time to avoid
  introducing non-physical oscillations while achieving high-order
  accuracy where and when possible. The model is initially validated
  for two-phase flow. Results are in good agreement with analytically
  obtained solutions and experimental results. The potential of this
  method is demonstrated by simulating flow in a realistic geometry
  composed of highly permeable meandering channels.
\end{abstract}

\keywords{CVFEM mixed formulation; Discontinuous Galerkin; Flux-limiting; High-order method; Multi-phase flows; Porous media flows}

\maketitle

\section{Introduction}

Numerical modelling of multi-phase flows in porous media has
applications in a wide range of disciplines, including hydrocarbon and
groundwater production, safety assessment of deep geological disposal
of radioactive waste, and carbon capture and storage \cite{chen_2006,
  aiea_1999, pruess_1990c, jiang_2011}. Such applications often
include complex geometries with irregular (and often internal)
boundaries between rock types with contrasting porosity and
permeability. Accurately capturing these complex geometries is a key
challenge when simulating such flows.

Finite difference methods (FDM) have been extensively used for
modelling fluid flows in porous media
\cite{aziz_1986, chen_1997, chen_2005}. However, they are strongly
dependent on mesh quality and orientation, and cannot easily represent
complex geometries. In addition, FDM can produce excessive numerical
dispersion in heterogeneous porous media \cite{chavent_1986}.

The geometrical flexibility of finite element methods (FEM) has been
shown to overcome these deficiencies. Among FEM-based formulations for
porous media, the control volume finite element method (CVFEM) is
increasingly popular as it can guarantee local mass conservation, it
has the potential to be high-order accurate, and is able to use
tetrahedral, geometry-conforming elements \cite{forsyth_1990,
  cordazzo_2004, geiger_2004, hurtado_2007}. Huber and Helmig \cite{huber_2000}
demonstrated that the vertex-centred, finite volume-finite element
method (or Box scheme) can achieve similar goals (see also \cite{helmig_1997}).

Durlofsky \cite{durlofsky_1993,durlofsky_1994} compared the performance of a
mixed FEM formulation (piece-wise linear in velocity and piece-wise
constant in pressure) and the classical CVFEM for single phase Darcy
flows. It was concluded that the latter is computationally more
efficient and numerically more accurate than the former for problems
involving a (relatively) small number of degrees of freedom. Moreover,
for complex heterogeneous problems with sharp changes in material
properties, the mixed FEM formulation often led to physically
unrealistic solutions.  Cumming et al. \cite{cumming_2011} demonstrated that a
CVFEM-based discretisation could be used to solve the Richards
equation (coupled mass conservation and Darcy equations) in
heterogeneous porous media with relatively small computational
overhead, compared with traditional, coupled velocity-pressure based
formulations.  Mass balance was enforced as described by Kirkland et al.
\cite{kirkland_1992} (see also \cite{forsyth_1990,cumming_phd2012}). However, CVFEM often requires
high resolution meshes in regions where material properties vary
abruptly, such as permeability contrasts at (for example)
fracture-matrix interfaces, or boundaries between different rock
types. Control volume (CV) boundaries span finite elements where
material properties are defined; therefore, some average value of the
permeability must be calculated across CV interfaces. This often leads
to excessive numerical dispersion, especially in highly heterogeneous
media \cite{nick_2011b, nick_2011a}.

Discontinuity-capturing schemes (e.g. shock waves, contact
  surface or material discontinuities --
  see \cite{brooks_1982,tezduyar_1986}) were originally developed to
resolve sharp changes in solution fields such as velocity or
saturation. Related discontinuity-capturing schemes include the
discontinuous-Galerkin FEM (DGFEM) scheme in which continuity of the
solution is not explicitly enforced, allowing sharp changes in the
solution fields to be captured. The DGFEM scheme is stabilised,
locally conservative and designed to achieve high-order
accuracy. DGFEM solution fields are allowed to be discontinuous at the
element faces; thus, the solution is able to handle discontinuities in
material properties at internal boundaries. In addition, DGFEM is
well-suited to deal with interface problems by incorporating
specially-designed interface fluxes. These properties have attracted
the attention of the porous media flow community over the past 15
years (see \cite{riviere_2000,riviere_2002,bastian_2002}) and are
utilised here.

In this paper, a novel CVFEM formulation which is conservative and
consistent is presented. The continuity equations are embedded into
the pressure equation to enforce mass conservation and the exact force
balance. The \PN[n]{m}[DG] family of triangular and tetrahedral finite
element pairs is used to discretise velocity and pressure in
space. For this element type, the velocity field is represented by
$n^{\rm th}$-order polynomials that are discontinuous across elements,
while the pressure field is represented by $m^{\rm th}$-order
polynomials that may be continuous (termed P$_n$DG-P$_m$) or
discontinuous (termed P$_n$DG-P$_m$DG) across elements. Control
volumes are dual to the pressure mesh. The formulation employs an
implicit algorithm with respect to time that is less restrictive than
the implicit-pressure-explicit-saturation (IMPES) scheme often adopted
in porous media flow problems (e.g. see \cite{aziz_1986, geiger_2004}).

The method is demonstrated using two families of element pairs: the
\PN[n]{m} pair which can allow the velocity to exactly represent the
pressure gradients in the flow solution for homogeneous material
properties; and the \PNDG[n+1]{n} pair, which has similar properties
to the \PN[n]{n+1} element pair, but allows a representation in which
pressure, saturation and other solution variables are discontinuous
across finite element boundaries. This solves the long-standing
problem described above with respect to the use of traditional CVFEM
to capture sharp changes in material properties.

Results using this method in simple geometries have been previously
reported in the literature
(e.g. see \cite{jackson_2015,kaisu}). However, the method has not
been described in detail or thoroughly validated, and its potential has not been
explored. The remainder of this paper is organised as follows. The
governing equations and numerical methods employed to solve them are
presented in Section~\ref{overlapping_method_section}. Model set-up
and results including comparison against reference data are given in
Sections~\ref{setup} and \ref{res}, respectively. Finally, some
concluding remarks are presented in Section~\ref{conc}.

\section{Governing equations and numerical method}
\label{overlapping_method_section}

\subsection{A novel representation of multi-phase Darcy flows}
Darcy's law for immiscible multi-phase flow may be written in the form:
\begin{equation}\label{e:darcy_eqn}
  \mathbf{q}_{\alpha} =
  -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(
  \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
\end{equation}
where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity,
$\mathbf{K}$ is the absolute permeability tensor of the porous medium,
$\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase
relative permeability, which is a function of the phase saturation
$S_{\alpha}\left(\mathbf{r},t\right)$. $\mu_{\alpha}$, $p_{\alpha}$,
$\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic
viscosity, pressure, density and source term, which may include gravity and/or
capillarity, respectively.

Introducing a saturation-weighted Darcy velocity defined as
$\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then
Eqn.~\ref{e:darcy_eqn} may be rewritten as:
\begin{equation}
  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha}
  \mathbf{u}_{\alpha} = - \nabla p_{\alpha} +
         {\mathbf{s}_{u}}_{\alpha},
  \label{force-bal}
\end{equation}
where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha
\left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the
implicit linearisation of the viscous frictional forces. The force per
unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline
    \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic
variable in this approach, as explained in
Section~\ref{Section:Force_density}.

In order to discretise Eqn.~\ref{force-bal}, a finite element
representation for $\mathbf{v}_\alpha$ and $p$ is assumed, expressed
in terms of their FE basis functions $Q_{j}$ and $P_{j}$,
respectively, as:
\begin{equation}
  \mathbf{v}_\alpha(\bm{r},t) = \sum\limits_{j=1}^{\mathcal{N}_u}
  Q_{j}(\bm{r})\mathbf{v}_{\alpha,j}(t) \;\;\;\;\text{ and } \;\;\;\;
  p(\bm{r},t) = \sum\limits_{j=1}^{\mathcal{N}_p}
  P_{j}(\bm{r})p_{j}(t).
\end{equation} 
Here $\mathcal{N}_{u}$ and $\mathcal{N}_{p}$ are the total number of
degrees of freedom for the FE force and pressure representations. Each
component of the weak form of the force balance (Eqn.~\ref{force-bal})
is tested with the $\mathbf{v}_\alpha$ basis function space to obtain:
\begin{eqnarray}
  \sum\limits_{E} \left. \int\limits_{\Omega_E} { {Q}}_i \left (
             {\mathbf v}_\alpha + \nabla p  -\rho_\alpha g \mathbf{d} -{\mathbf s}_{u_\alpha}
             \right) dV \right. + \displaystyle \oint_{\Gamma_{E}}
                   {Q}_i {\mathbf n} \left(p - \tilde{p}\right)
                   d\Gamma + \nonumber \\ \oint_{\Gamma_{\Omega}} {
                     Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma
                   = \bm{0},
                   \label{force-semi-disc} 
\end{eqnarray} 
where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of
element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of
the computational domain. The numerical pressure $\tilde{p}$ appearing
in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is
the arithmetic mean of the potentially discontinuous pressure across
the element $E$. This term vanishes when a continuous formulation is
used to discretise the pressure field. The last term in
Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure
level to $p_\text{bc}$ on a computational domain boundary.

In matrix form, Eqn.~\ref{force-semi-disc} is:
\begin{equation}
  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline
  {\mathbf p} + \underline {\mathbf
    s}_{u}, \label{force-balance-matrix-form}
\end{equation}
where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are
defined as:
\begin{eqnarray}
  &&\underline{{\bf v}} = \left( 
  \left( {v_x},{v_y},{v_z} \right)  _{1,1},
  \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots,
  \left( {v_x},{v_y},{v_z} \right)  _{\mathcal{N}_\alpha,\mathcal{N}_u}
  \right)^{T}
  \;\text{and} \nonumber \\ &&
  \underline{{\bf p}} = \left(p_1, p_2, p_3, ...,
  p_{\mathcal{N}_p}\right)^T. \nonumber \nonumber
\end{eqnarray}
$\mathcal{N}_{\alpha}$ is the number of phases and $v_x$, $v_y$ and
$v_z$ are the components associated with the $x$, $y$ and $z$
dimensions, respectively. Finally, the mass matrix ${\mathbf M}$,
gradient matrix ${\mathbf C}$ and source vector $\underline {\mathbf
  s}_{u}$ are defined as:
\begin{eqnarray}
  && \left[{\mathbf M}^{(i,j)}\right]_{k,l} = \int_{\Omega} Q_{k}
  \left[\underline{\underline{\sigma}}_{\alpha}\right]_{i,j} {Q}_{l}
  dV, \nonumber \\ && {\left[\bm{C}^{(i,i)}\right]_{k,l} =
    \int_{\Omega} Q_{k} \frac{\partial P_{l}}{\partial r_i} dV -
    \oint_{\Gamma_{E}} \displaystyle\frac{1}{2} Q_{k} n_i^{(E,l)}
    P_{l} d\Gamma - \oint_{\Gamma_{\Omega}} \displaystyle Q_{k} n_i
    P_{l} d\Gamma}, \nonumber \\ &&
  {\left[\bm{s}_{u}^{(i,i)}\right]_{k} = \int_{\Omega} Q_k}
  \left[{\mathbf s}_{u_\alpha} \right]_i dV -
  \oint_{\Gamma_{\Omega}}\displaystyle Q_{k} n_i p_\text{bc} d\Gamma,
  \nonumber
\end{eqnarray}
where $i$ and $j$ are dimensions and $k$ and $l$ are the degrees of
freedom of element $E$. Here, $\bm{n} = \left(n_{1}, n_{2},
n_{3}\right)^{T}$ is the outward-pointing normal vector of the domain
$\Omega$. $\bm{n}^{(E,l)}$ is the normal to the boundary of element
$E$ and is outward-pointing if $P_{l}$ takes support on $E$, and
inward-pointing otherwise.

The saturations are computed in CV space, whereas the permeability
tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE
space. Thus the viscous-friction damping tensor $ {\underline
  {\underline \sigma}}_{\alpha}$ is piece-wise constant within the
sub-control volumes defined through intersections between the elements
and control volumes (see Fig.~\ref{fem_cv_represent_a}).

\subsection{Control volume finite element types}
In the formulation presented here, pressure, velocity, permeability
and porosity are represented FE-wise, but saturation, relative
permeability and fluid properties such as viscosity and density are
represented CV-wise. Fig.~\ref{fem_cv_represent_a} displays the two
families of element types presented in this
paper. Fig.~\ref{fem_cv_represent_a} (a) shows the P$_{n}$DG-P$_{n+1}$
element type, with $n = 1$, in two dimensions (2D). Here, the velocity
field is linear, discontinuous (between elements), the pressure field
has a quadratic, continuous (between elements), representation and the
CV's span various elements. Fig.~\ref{fem_cv_represent_a} (b) shows
the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$, also in 2D. Here,
the velocity field is quadratic, discontinuous (between elements), the
pressure field has a linear, discontinuous (between elements),
representation and the CV's do not span elements.

\begin{figure}[h!]
\subfloat[P$_1$DG-P$_2$]{\includegraphics[width=.5\textwidth]{p1dgp2-cont-sat.pdf}}
\subfloat[P$_2$DG-P$_1$DG]{\includegraphics[width=.5\textwidth]{p2dgp1-dg-sat.pdf}}
\caption{2D representation of the element pairs presented in this
  work. Shaded areas denote control volumes (in which saturation is
  stored), black points represent the pressure nodes and white points
  the velocity nodes.}
    \label{fem_cv_represent_a}
\end{figure}

\subsection{Finite element representation of velocity} \label{Section:Force_density}
From Eqn.~\ref{e:darcy_eqn}, it can be seen that the velocity field
depends, among other fields, on the absolute permeability, which is
FE-wise, and the relative permeability, which is CV-wise. This means
that the velocity representation is different in each CV. However, the
quantity $\mathbf{v}_\alpha$ is homogeneous within an element and this
is what is stored using FE. To obtain the velocity
$\mathbf{u}_{\alpha}$ in a particular CV within a FE,
Eqn.~\ref{force-bal} is used.

\subsection{Saturation and global mass conservative equations} \label{Section:Saturation_Global}
Here, the saturation conservation equations are discretised and the
global mass balance equation is derived. In this work, fluids are
assumed incompressible. The saturation equation can be written as:
\begin{equation}
  \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} + \nabla
  \cdot \left( {\mathbf u}_{\alpha} S_{\alpha}\right) =
  s_{cty,\alpha},
  \label{saturation_equation}
\end{equation}
where $\phi$ is the porosity and $s_{cty}$ is a source
term. Eqn.~\ref{saturation_equation} is discretised in space by
testing with CV basis functions $M_{i}$ and with the $\theta$-method
in time:
\begin{eqnarray}
  \int_{\Omega} M_{i} \displaystyle\frac{\phi \left({S_{\alpha
        i}^{n+1}}-{S_{\alpha i}^{n}}\right)}{\Delta t} dV + \nonumber
  \\ \oint_{\Gamma_{CV_{i}}} \left[\theta^{n+\frac{1}{2}} {\mathbf n}
    \cdot {\mathbf u}_{\alpha}^{n+1} S_{\alpha}^{n+1} +
    \left(1-\theta^{n+\frac{1}{2}}\right) {\mathbf n} \cdot {\mathbf
      u}_{\alpha}^{n} S_{\alpha}^{n} \right]d\Gamma = \int_{\Omega}
  M_{i} {s_{cty,\alpha}^{n+\theta}} dV,
  \label{detail-sat-eqn-k}
\end{eqnarray}
where $\mathbf{n}$ is the outward-pointing unit normal vector to the
surface ($\Gamma_{CV_{i}}$) of the control volume $i$ and $n$ is the
current time level. More details on the numerical methods used to
solve Eqn.~\ref{detail-sat-eqn-k} can be found in
\cite{pavlidis_2013b}.

The global continuity equation is obtained by summing
Eqn.~\ref{detail-sat-eqn-k} over all phases:
\begin{eqnarray}
  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} \left\lbrace
  \int_{\Omega} M_{i} \displaystyle\frac{\phi\left({S_{\alpha
        i}^{n+1}}-{S_{\alpha i}^{n}}\right) } {\Delta t} dV +
  \right. \nonumber \\ \left. \displaystyle\oint_{{\Gamma_{CV}}_{i}}
  \left[\theta^{n+\frac{1}{2}} {\mathbf n} \cdot {\mathbf
      u}_{\alpha}^{n+1} S_{\alpha}^{n+1} +
    \left(1-\theta^{n+\frac{1}{2}}\right) {\mathbf n} \cdot {\mathbf
      u}_{\alpha}^{n} S_{\alpha}^{n} \right] \,d\Gamma -
  \right. \nonumber \\ \left. \displaystyle\int_{\Omega} M_{i}
  s_{cty,\alpha}^{n+\theta}\, dV \right\rbrace = 0.
           \label{detail-sat-eqn-k-sum}
\end{eqnarray}
Eq.~\ref{detail-sat-eqn-k-sum} is also bounded by the constraint:
\begin{equation}
  \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}^{n}}_{i} =
  1, \quad \forall n.
\end{equation}
Solving for ${\mathbf u}^{n+1}$ in matrix form,
Eqn.~\ref{detail-sat-eqn-k-sum} becomes:
\begin{equation}
  {\mathbf B}^T \underline{\bf v}^{n+1} = \underline{\bf s}_{p}.
  \label{glob-cty-matrix}
\end{equation}

\subsection{Velocity at control volume interfaces} \label{opt-up} 
The velocity to be used at the interface between CV's in the
saturation conservation (Eqn.~\ref{detail-sat-eqn-k}) and global
continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations needs to be
determined. On the CV faces, there is no information about the flow
direction as the velocity is discontinuous at the CV boundaries. The
discontinuities occur between (a) control volumes within each FE and
(b) between elements when using the P$_{n+1}$DG-P$_{n}$DG pair.

To calculate the velocity across CV's within a FE, an average velocity
at the interface of control volumes {\it i} and {\it j} is defined as:
\begin{equation}
  {\tilde{\bf u}}_\alpha = \frac{1}{2} \left[ {{\bf u}_\alpha}_i +
    {{\bf u}_\alpha}_j \right].
\end{equation} 
From this, the interface velocities at either side of the interface
can be obtained from:
\begin{equation}
  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha
    k}^{-1}{\tilde{{\bf u}}}_{\alpha}, \;\;\;\; k=\{i,j\}.
  \label{two-vels}
\end{equation} 
These velocities have the same direction and 
differ only in magnitude, so using them to define an upwind
direction is not ambiguous.

If an upwind method for calculating the interface velocity is applied
then the interface velocity becomes:
\begin{equation}
  {\tilde{\bf u}}_{\alpha} = \tilde{\bf u}_{\alpha k},
\end{equation}
where $k=i$, if ${\bf n}\cdot{\bf u}_{\alpha}>0$ (CV {\it i} outgoing
information) and $k=j$, if ${\bf n}\cdot{\bf u}_{\alpha}<0$ (CV {\it
  i} incoming information). However, upwind methods yield dissipative
solutions. In order to obtain a high-order approximation of the
velocity at the interface, the saturation at the interface
$\tilde{S}_{\alpha}$ is calculated using a finite element
representation of the saturation following the upwind direction.
$\tilde \sigma_{\alpha}$ can then be calculated using second-order
Taylor series:
\begin{small}
\begin{equation}
  \underline{\underline{\tilde{\sigma}}}_{\alpha} =
  \underline{\underline{\sigma}}_{\alpha k} +
  \left(\tilde{S}_{\alpha}-S_{\alpha k}\right) \left(\frc{\partial
    \underline{\underline{\sigma}}_{\alpha}}{\partial
    S_{\alpha}}\right)_{k} +
  \frc{1}{2}\left(\tilde{S}_{\alpha}-S_{\alpha k}\right)^{2} \left[
    \frc{ \left(\frc{\partial
        \underline{\underline{\sigma}}_{\alpha}}{\partial
        S_{\alpha}}\right)_{k} - \left(\frc{\partial
        \underline{\underline{\sigma}}_{\alpha}}{\partial
        S_{\alpha}}\right)_{l} } { \left(S_{\alpha k}-S_{\alpha
        l}\right) } \right],
  \label{sigma-out}
\end{equation}
\end{small}
where $k=i$ and $l=j$, if ${\bf n}\cdot{\bf u}_{\alpha}>0$ and $k=j$
and $l=i$, if ${\bf n}\cdot{\bf u}_{\alpha}<0$. The final interface
velocity is obtained from:
\begin{equation}
  {\tilde{\bf u}_{\alpha}} =
  \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1}
  \left[\displaystyle\frac{1}{2} \left( {{\bf u}_\alpha}_i + {{\bf
        u}_\alpha}_j \right)\right],
  \label{mean_int_vel}  
\end{equation} 
which is bounded to ensure that its normal component ${\tilde{\bf
    u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha
    i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf
  n}$. The result of this is also bounded between the velocities
${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf
  n}$.

In order to calculate the velocity between elements (when using
P$_{n+1}$DG-P$_{n}$DG elements) one first needs to consider that it is
also necessary to obtain the discretised non-symmetric pressure
equation which has elliptic-like properties. These properties mean it
is necessary to propagate information in all directions across the
domain, therefore taking the upwind velocity, as commonly done within
an element, is not the best strategy.

For two neighbouring CV's $i$ and $j$ with common FE interface,
$\tilde{\bf u}_\alpha$ can be calculated by using a volume-weighted
harmonic mean. However, the volume $\mathcal{V}$ of the control volume
and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity in a
very similar way. Hence, the velocity at the interface is expressed
as:
\begin{equation} 
  {\tilde{\bf u}_\alpha} =  \left(\mathcal{V}_{j}  
    \underline{\underline{\sigma}}_{\alpha j} \, {\bf
      u}_{\alpha i} + \mathcal{V}_{i} \underline{\underline{\sigma}}_{\alpha i}\, {\bf
      u}_{\alpha j} \right) \left(  \mathcal{V}_{i} 
    \underline{\underline{\sigma}}_{\alpha i} +
    \mathcal{V}_{j} 
    \underline{\underline{\sigma}}_{\alpha j} \right)^{-1}.
\end{equation}

\subsection{Weak enforcement of boundary conditions}\label{bcs-rel-perm} 
Suitable boundary conditions for velocity can be applied by the
discontinuous formulation above as well as by the upwinding in the
continuous formulation. In fact, exactly the same boundary condition
implementations, as used in the discontinuous formulation, can be
applied across the boundaries of the domain by taking information from
`just outside' the domain rather than from the neighbouring elements.

Saturation boundary conditions are relatively straightforward. One
typically takes the saturation from `just outside' the domain
($S_{\alpha, \text{bc}}$) and the flux becomes $\left({\bf n}\cdot
{\bf u}_{\alpha}\right)S_{\alpha,\text{bc}}$, if ${\bf n}\cdot {\bf
  u}_{\alpha} < 0$. If the velocity is also specified (${\bf
  u}_{\alpha,\text{bc}}$) then this becomes part of the incoming flux
$\left({\bf n}\cdot {\bf
  u}_{\alpha,\text{bc}}\right)S_{\alpha,\text{bc}}$.

In case of specified pressure for outflow boundaries
$\left(\right.{\bf n}\cdot {\bf u}_\alpha>0\left.\right)$ the flux is
${\bf n}\cdot {\bf u}_\alpha {S_\alpha}$, in which neither ${\bf
  u}_\alpha$ nor ${S_\alpha}$ are specified.

However, for inflow boundaries with specified pressure
$\left(\right.{\bf n}\cdot {\bf u}_\alpha<0\left.\right)$ the flux is
${\bf n}\cdot {\bf u}_{\alpha,\text{bc}} S_{\alpha,\text{bc}}$, in
which ${\bf u}_{\alpha,\text{bc}}$ is calculated using:
\begin{equation}
  {\bf u}_{\alpha,\text{bc}} = 
    \underline{\underline{\sigma}}_{\alpha,\text{bc}} ^{-1}
    \underline{\underline{\sigma}}_{\alpha}  
              {\bf u}_{\alpha},
\end{equation}
where $\underline{\underline{\sigma}}_{\alpha,\text{bc}}$ is
calculated using $S_{\alpha,\text{bc}}$.

It should be noted that this flux condition must be used in both the
discretised saturation and global continuity equations, since the
latter is a summation of the former. The specified pressure condition
becomes a surface flux condition in the force balance equation
(Eqn.~\ref{force-semi-disc}), which effectively relaxes the pressure
$p$ to its face value counterpart $p_\text{bc}$ at the boundaries.

\subsection{Solving the linear equations}\label{Section:SolvingLinearEqns}
The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and
force balance equations (Eqn.~\ref{force-balance-matrix-form}) are
solved by substituting $\underline{\mathbf v}$ and solving the system
of equations for pressure. At time level $n+1$,
Eqns.~\ref{force-balance-matrix-form} and ~\ref{glob-cty-matrix} can
be rewritten as:
\begin{displaymath}
  \begin{cases}
    \mathbf{M} \underline{\bf v}^{n+1} = \mathbf{C}\underline{\bf
      p}^{n+1} + \underline{\bf s}_{u}^{n+1} \\ \mathbf{B}^{T}
    \underline{\bf v}^{n+1} = \underline{\bf s}_{p}^{n+1},
  \end{cases}
\end{displaymath}
respectively. Application of a discontinuous FEM for
$\mathbf{v}$ leads to a block-diagonal $\mathbf{M}$ matrix that
can be readily inverted, each block being local to an
element. Multiplying Eqn.~\ref{force-balance-matrix-form} by
$\mathbf{B}^{T}\mathbf{M}^{-1}$ and summing up with
Eqn.~\ref{glob-cty-matrix}, $\underline{\mathbf v}^{n+1}$
vanishes and the pressure equation is obtained:
\begin{equation}
  \mathbf{B}^{T}\mathbf{M}^{-1} \mathbf{C} \underline{\bf p}^{n+1} =
  \underline{\bf s}_{p}^{n+1} - \mathbf{B}^{T} \mathbf{M}^{-1}
  \underline{\bf s}_{u}^{n+1}.
  \label{final_projection}
\end{equation}
Eqn.~\ref{final_projection} is solved for pressure and then the
velocity is obtained via Eqn.~\ref{force-balance-matrix-form}. The
computationally demanding effort to solve the pressure matrix equation
arising from the fully discontinuous FEM formulation is achieved using
a multigrid-like approach (see \cite{Brandt}). In this case the
`fine' mesh is the one obtained by the discontinuous system, whereas
the `coarse' mesh is obtained by creating a continuous system (from
the discontinuous system) by collapsing the pressure nodes. As in
multigrid, the coarse mesh solution is used to accelerate the
convergence of the fine mesh solution by calculating the error of the
current approximation.

\section{Model set-up}\label{setup}
The numerical method is evaluated using four test cases (\ref{classical_BL} --
\ref{res5}). All test cases simulate two-phase flow. The Brooks-Corey model
\cite{brooks_1964}: 
\begin{eqnarray}
k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
\end{eqnarray}
where $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume
fractions, respectively, is used to calculate the relative
permeabilities for all test cases. The exponents $n_w$ and $n_{nw}$
are both set to 2 for all test cases.

The length of all computational domains is 1 non-dimensional length
unit. Computational domain height, boundary conditions, exponents for
the wetting $n_w$ and non-wetting $n_{nw}$ phases in the Brooks-Corey
model, along with the irreducible wetting phase saturation $S_{wirr}$,
residual non-wetting phase saturation $S_{nwr}$ and mobility $M^0$ for
each test case are shown in Table~\ref{tab:1}.

\begin{table}[h!]
  \centering
  \small{
    \caption{Model set-up for test cases \ref{classical_BL} --
      \ref{res5}.\label{tab:1}}
    \begin{tabular}{c c c c c c c c c c c c c c c} 
      \hline
      & $M^0$ & $\phi$ & $\mathbf{K}_\text{1}$ & $\mathbf{K}_\text{2}$ & $\mathbf{K}_\text{3}$ & $S_{wirr}$ & $S_{nwr}$ & $u_{\mathrm{in}}$ & $\Delta p$ & height \\ \hline
      \ref{classical_BL} & 10 & 0.2 & 1.0 & N/A    & N/A & 0.2   & 0.3 & 0.2 & N/A & N/A\\
      \ref{res2}         & 10 & 0.4 & 1.0 & 2.5    & N/A & 0.1   & 0.2 & 1.0 & N/A & 1.0\\ 
      \ref{res4}         & 10 & 0.5 & 1.0 & 10$^2$ & N/A & 0.0   & 0.0 & N/A & 1.0 & 0.1\\
      \ref{res5}         & 4  & 0.2 & 1.0 & 2.0    & 10  & 0.2   & 0.2 & N/A & 1.0 & 0.1\\ \hline
    \end{tabular}
  }
\end{table}

In all test cases, the domain is initially saturated with the
non-wetting phase at $(1- S_{wirr}).$ The wetting phase is then
injected through the left boundary, displacing the non-wetting phase
towards the opposite boundary. The wetting phase is injected at a
uniform, constant velocity ($u_{\mathrm{in}}$) from the left boundary
for test cases  \ref{classical_BL} and  \ref{res2}. In test case \ref{res2} the
inlet velocity is weighted by the permeability. For test cases  \ref{res4} and  \ref{res5},
the flow is driven by a pressure difference ($\Delta p$)
between the inflow (left) and outflow (right) boundaries of the
computational domain. The pressure level at the outflow boundary is
set to 0 for all test cases.

For the test cases considered here, the porosity $\phi$ is assumed
uniform and for case \ref{classical_BL}, $\mathbf{K}$ is also
uniform. However, for cases \ref{res2} -- \ref{res5}, $\mathbf{K}$ is
non-uniform and regions of constant $\mathbf{K}$ are used. For all
cases, $\mathbf{K}$ is isotropic. The subscript in $\mathbf{K}$
denotes region identities (see Figs.~\ref{fig:4reg_BL_schematic} and
\ref{fig:wedge_permeability}).

\section{Results}\label{res}

\subsection{The Buckley-Leverett test case}\label{classical_BL}

The Buckley-Leverett problem \cite[non-wetting phase displaced by a
  wetting phase]{buckley1942} is simulated here.  Despite the
one-dimensional (1D) nature of the problem, 2D and three-dimensional
(3D) simulations are performed to evaluate the multi-dimensional
capabilities of the model (see Fig.~\ref{fig:maps2d_3d}). The
\PN[1]{1}, \PN[1]{2} and \PN[2]{1}DG element pairs are used for these
simulations.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{BL_3D_merged}
    \caption{Wetting phase volume fraction for the Buckley-Leverett
      test case using the \PN[1]{2} element pair in 2D (a) and 3D
      (b). \label{fig:maps2d_3d}}
  \end{center}
\end{figure}

Fig.~\ref{fig:BL_tests} (a), (b) and (c) shows phase volume fraction
profiles of the wetting phase for four meshes in 2D at
non-dimensional time $t=0.2$. All meshes are structured and have 4
elements perpendicular to the flow and 60, 120, 240 or 480 elements
parallel to the flow (see Fig.~\ref{fig:maps2d_3d}, a). The geometry
centre-line is used to plot these profiles. All element pairs
satisfactorily capture the discontinuity in the phase volume fraction
and as the number of elements is increased the error is reduced.
Fig.~\ref{fig:BL_tests} (d) shows results obtained for a
Buckley-Leverett test case in 3D. A 1207-element fully unstructured
mesh is used for these simulations. The geometry centre-line is used
to plot these profiles. All the element pairs are again capable of
accurately capturing the discontinuity in the phase volume fraction.

\begin{figure}[h!]
  \begin{center}
    \vbox{\hbox{
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P1DGP1.eps} 
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P1DGP2.eps}}
      \hbox{
        \vspace{-0.cm}\hbox{\hspace{3.0cm}(a)} 
        \vspace{-0.cm}\hbox{\hspace{6.0cm}(b)}}
      \vspace{0.0cm}\hbox{
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P2DGP1DG.eps}
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_3D.eps}}
      \hbox{
        \vspace{-0.cm}\hbox{\hspace{3.0cm}(c)} 
        \vspace{-0.cm}\hbox{\hspace{6.0cm}(d)}}}
    \caption{Wetting phase volume fraction along the geometry
      centre-line at non-dimensional time $t=0.2$ for the
      Buckley-Leverett test case. 2D results with the \PN[1]{1},
      \PN[1]{2} and \PN[2]{1}DG element pairs are shown in (a), (b)
      and (c), respectively. 3D results for an unstructured mesh are
      shown in (d). The 1D analytic solution is shown for comparison
      in all plots.\label{fig:BL_tests}}
  \end{center}
\end{figure}

Fig.~\ref{fig:errors_BL_2D} (a) shows convergence rates for the
results presented in Fig.~\ref{fig:BL_tests} (a), (b) and (c). The
L$_2$ error norm of the wetting phase volume fraction is used
here. Due to the discontinuity in the solution variable, a
first-order convergence rate is achieved even when the high-order
element pair is used (Fig.~\ref{fig:BL_tests}, b). This is because
high-order methods switch to simple upwinding at the discontinuity.
Fig.~\ref{fig:errors_BL_2D} (b) shows the convergence rate of the same
high-order element pair simulation (Fig.~\ref{fig:BL_tests}, b) at
non-dimensional time $t=0.3$. At this time level the phase volume
fraction field is smooth since the discontinuity has been advected out
of the computational domain and for this reason a second-order
convergence rate is achieved.

\begin{figure}[h!]
  \begin{center}
    \vbox{\hbox{
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{Conv1.eps} 
        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{Conv2.eps}}
      \hbox{
        \vspace{-0.cm}\hbox{\hspace{3.0cm}(a)} 
        \vspace{-0.cm}\hbox{\hspace{6.0cm}(b)}}}
    \caption{Error metrics versus number of elements for the
      Buckley-Leverett test case for element pairs \PN[1]{1},
      \PN[1]{2} and \PN[2]{1}DG in 2D. \label{fig:errors_BL_2D}}
  \end{center}
\end{figure}

\subsection{Immiscible displacement in heterogeneous porous media}\label{res2}

This test case is designed to demonstrate the numerical robustness of
the method for modelling heterogeneous porous media and it is based on
the physical experiment presented in Dawe and Grattoni \cite{dawe_2008}. As shown in
Fig.~\ref{fig:4reg_BL_schematic} the permeability field is
non-uniform.

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{4Rregion_BLv2}
    \caption{Schematic of the computational domain along with the
      material properties and boundary conditions for the
      heterogeneous permeability test case. Darker areas
      ($\mathbf{K}_\text{1}$) represent regions with high
      permeability. \label{fig:4reg_BL_schematic}}
  \end{center}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.45\textwidth]{CG_coarse083.png}
  \includegraphics[width=0.45\textwidth]{CG_fine083.png}
  \includegraphics[width=0.45\textwidth]{DG_coarse083.png}
  \includegraphics[width=0.45\textwidth]{DG_fine083.png}
  \caption{Wetting phase volume fraction maps at time $t=0.16$ for the
    heterogeneous permeability test case. Top row: \PN[1]{2}
    elements. Bottom row: \PN[2]{1}DG elements. Left column: coarse
    mesh. Right column: fine mesh. The meshes used for these
    simulations are also shown here.\label{fig:4reg_maps}}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=0.6\textwidth]{Real_quadrant}
    \caption{Wetting phase volume fraction maps from the experiments
      of \cite{dawe_2008}. \label{fig:dawe_real}}
  \end{center}
\end{figure}

Two sets of simulations are performed using coarse (402 elements) and
fine (3714 elements) meshes; in the first set the \PN[1]{2} element
pair is used, while in the second one the \PN[2]{1}DG element pair is
used. The time step sizes for the coarse and fine mesh simulations are
5$\times$10$^{-3}$ and 10$^{-3}$ non-dimensional time units,
respectively.

Fig.~\ref{fig:4reg_maps} shows the wetting phase volume fraction maps
at time $t=0.16$ for all four simulations. Results for the
\PN[1]{2} element pair set of simulations is shown in the top row.
Results for the \PN[2]{1}DG element pair set of simulations is shown
in the bottom row.

A physical experiment with similar set-up was performed by Dawe and Grattoni
\cite{dawe_2008} to investigate miscible and immiscible displacement
in heterogeneous permeability and wettability cases. For immiscible
displacement, the wetting phase was uniformly injected at rate of
$\approx 1$ml/min in a domain of 20cm$\times$10cm$\times$0.6cm. Glass
ballotini beads produced porosity of 0.4. The permeability ratio was
2.5.

Snapshots in Fig.~\ref{fig:4reg_maps} show the wetting phase flood
`fingering' across the four region intersection, demonstrating the
preferential flow through high permeability regions. This is in good
qualitative agreement with the experimental results
(see Fig.~\ref{fig:dawe_real}, taken from Dawe and Grattoni \cite{dawe_2008}).

\subsection{High permeability high aspect ratio region}\label{res4}

Fractures and cracks in porous media are ubiquitous, however, they are
not easy to model due to their high aspect ratio and small size
compared to the reservoir domain. Nonetheless, cracks may have a
dramatic impact in the overall behaviour of the flow as they can
channelise the flow through them. Usually, they are characterised by a
thin tip and a high permeability. A simplified 2D wedge-shaped
high permeability region embedded in a rectangular low-permeability
domain is considered here. The permeability map is shown in
Fig.~\ref{fig:wedge_permeability}. The wedge aspect ratio is $1/30$
and its maximum height is 0.025.

\begin{figure}[h!]
  \vbox{
    \hbox{
      \hspace{-0.cm}\includegraphics[width=1.0\textwidth]{wedge_permeabilityv2}}
    \vspace{-1.cm}\hbox{\hspace{4cm}(a)}
    \vspace{.5cm}
    \hbox{
      \hspace{-0.cm}\includegraphics[width=1.0\textwidth]{wedge_0011}}
    \vspace{-0.cm}\hbox{\hspace{4cm}(b)}
    \vspace{.5cm}
    \hbox{
      \hspace{-.cm}\includegraphics[width=1.0\textwidth]{wedge_0014}}
    \vspace{-0.cm}\hbox{\hspace{4cm}(c)}
  }
  \caption{Schematic of the computational domain along with the
    permeability map for the high permeability wedge-shaped region
    test case (a). Snapshots of the wetting phase volume fraction
    field for a fine mesh \PN[1]{2} simulation (top), coarse mesh
    \PN[1]{2} simulation (middle) and coarse mesh \PN[2]{1}DG
    simulation (bottom) at non-dimensional times $t = 0.011$ (b) and
    $t=0.0014$ (c). The meshes used for these simulations are also
    shown in (b) and (c).
    \label{fig:wedge_permeability}}
\end{figure}

Three numerical simulations are performed in total. Two use the
\PN[1]{2} element pair and one uses the \PN[2]{1}DG element pair.
\PN[1]{2} element pair simulations are performed using a coarse (672
elements) and a fine (56902 elements) mesh. The coarse mesh is used
for the \PN[2]{1}DG element pair simulation.

Fig.~\ref{fig:wedge_permeability} shows wetting phase volume fraction
maps at non-dimensional times $t=0.011$ and 0.014. The \PN[1]{2}-based
solutions disperse the wetting phase into the low-permeability
matrix. This is more pronounced for the coarse mesh simulation. It can
be seen how the front of the wetting phase is considerably delayed
compared with the other two simulations. On the other hand, the
\PN[2]{1}DG solution does not disperse the wetting phase into the
matrix and even a very coarse mesh is sufficient to accurately capture
the flow.

\subsection{3D fluvial channel model}\label{res5}

\begin{figure}[h!]
  \vbox{
    \hbox{
      \hspace{3.5cm} \includegraphics[width=0.45\textwidth]{permeability_map}}
    \vspace{0.1cm}
    \hbox{
      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_vtu10}
      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_vtu20}}
    \vspace{0.1cm}
    \hbox{
      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_DGvtu10}
      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_DGvtu20}}}
  \caption{Schematic of the computational domain along with the
    permeability map and mesh used for the 3D fluvial channel case
    (top). Wetting phase volume fraction maps at two time levels
    (left and right). \PN[1]{1} element pair results are shown in the
    middle row. \PN[2]{1}DG element pair results are shown in the
    bottom row.
    \label{fig:fluvial_model}}
\end{figure}

The method is finally applied to a subsurface example of high
permeability fluvial sandstone channels embedded in a low permeability
mudstone background. Such features are often observed in aquifers and
petroleum reservoirs. Due to the importance of these channels to the
flow behaviour, their correct representation and resolution is key to
obtaining reliable solutions. In this model three different sets of
highly permeable channels are considered. The mesh and permeability
map for these simulations is shown in Fig.~\ref{fig:fluvial_model}
(top). The thin channels have a permeability of $\mathbf{K}_\text{3}$,
the medium size channels $\mathbf{K}_\text{2}$ and the wide channels
$\mathbf{K}_\text{1}$.

Two numerical simulations are performed using an 8000-element fully
unstructured mesh. Wetting phase volume fraction maps at two time
levels are shown in Fig.~\ref{fig:fluvial_model}. Results for
the \PN[1]{1}DG element pair are shown in the middle, while results
for the \PN[2]{1}DG element pair are shown in the bottom row. Results
are in reasonable agreement. It is worth noting that the \PN[1]{1}
element pair (closest to traditional CVFEM formulation) is numerically
more dispersive. Nevertheless, these results demonstrate the potential
of the methods presented here to simulating real-world geometries.

\section{Conclusions}\label{conc}

A novel CVFEM based on the \PN[n]{m}(DG) element pairs with $n^{\rm
  th}$-order representation for velocity and $m^{\rm th}$-order for
pressure has been presented. The main advantages of this method over
existing ones is that arbitrarily high-order polynomial representation
for pressure and velocity can be used and it is high-order accurate in
space and time. In addition, for \PN[n]{m}DG element pairs control
volumes do not span elements, which resolves a long-standing problem
associated with the use of traditional CVFEM formulations in
heterogeneous porous media.

The new formulation was evaluated using the Buckley-Leverett benchmark
and first-order convergence rates were achieved for solutions with
discontinuities, which is not common in the literature
(see \cite{Schmid,Hoteit}). Second-order convergence rates were
achieved for solutions without a discontinuity. More numerical
simulations were performed to demonstrate the capabilities of the
methods presented under heterogeneous and high aspect ratio
computational domains. It was shown that the method is able to resolve
successfully multi-phase flows under those circumstances. Furthermore,
the \PN[n+1]{n}DG element pair was shown to completely remove
numerical dispersion induced by heterogeneous permeabilities.

The formulation presented here was implemented in the open-source
software framework
\href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity}
for multi-phase flows (IC-Ferst) and it has been extended to
include/model multi-component/interface-capturing flows
\cite{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular
flows \cite{percival_2014} and oil reservoir flows
\cite{jackson_2015,mostaghimi_2015, Salinas}.

\ack Dr D. Pavlidis would like to acknowledge the support from the
following research grants: Innovate UK `Octopus', EPSRC `Reactor
Core-Structure Re-location Modelling for Severe Nuclear Accidents')
and Horizon 2020 `In-Vessel Melt Retention'. Funding for Dr P. Salinas
from ExxonMobil is gratefully acknowledged. Dr Z. Xie is supported by
EPSRC `Multi-Scale Exploration of Multiphase Physics in Flows'. Part
funding for Prof Jackson under the TOTAL Chairs programme at Imperial
College is also acknowledged. The authors would also like to acknowledge
Mr Y. Debbabi for supplying analytic solutions.

\bibliographystyle{wileyj}
\bibliography{references}

\end{document}

%%
%% End of tex file.

### 2016-07-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates in the text

@@
 
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG Note $\Rightarrow$ #1}}}
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
 \newcommand{\red}{\textcolor{red}}
@@
 %% use optional labels to link authors explicitly to addresses:
-\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} 
+\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
 \author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
@@
 \address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
+\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
 
 \begin{abstract} 
-Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines Accurate prediction of multiphase flows in porous media remains one of the problems.
+%Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines Accurate prediction of multiphase flows in porous media remains one of the problems.
 While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability.
@@
 The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
-The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
+%The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
 %The element type described above has a discontinuous $n^{th}$ order polynomial representation of velocity and a continuous $(n+1)^{th}$ representation for pressure.
 This method includes the Darcy force balance equation, pressure, velocity and saturation fields throughout the domain while there is automatic mesh adaptivity in space and time and the computational cost is reduced.}
-Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this.
+%Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this.
 The impact of fingers formation in our simulations is also investigated.
@@
 The formulation is applied to saturated porous media systems.
-We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.
+%We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.
 
@@
 \section{Introduction}\label{section:Intro}
-Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-This is mainly due to applications on oil and gas recovery, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Detailed numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community for the past 50 years.
+This is mainly due to applications in oil and gas exploration and recovery, groundwater resources, underground coal gasification, geothermal power systems and, more recently, in carbon capture and storage (CCS) processes~\citep{spycher_2003, chen_2006,self_2012,pruess_1990c, white_1981,jiang_2011}.
+Complex geometries with irregular boundaries and strong heterogeneity in geological formations are the main issues addressed by developers of industry- and academic-standard flow simulators.
 
-Reservoir engineers and hydrogeologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+Accurate prediction of multiphase flow behaviour through realistic porous media domains is one of the the main research challenges as \red{write about the main issues related to heterogeneity and link it with flow behaviour (2-4 sentences)}.
+
+%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account. 
 %Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
+%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
 %This is well suited for analysis of small scales such as core samples.

### 2016-07-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Finished notes and edition of Introduction ... more to come on Section 2

@@
 \newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
 \journal{Advances in Water Resources}
@@
 
-\title{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media}
+\title{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media \blue{(You may want to change the title to something close to the main topic of the manuscript ...
+something with viscous flow instability or viscous fingering)}}
 
@@
 
-\JGnote{ Abstracts for journal papers have very `squared-structure': (a) Motivation (why would anyone bother to read the paper?
-Why is it (the paper and/or the subject) relevant?
-This needs to be covered in 1-3 punchy sentences.); (b) (Main) Objective(s) of the manuscript with particular focus on the \underline{novelty(ies)} the paper may bring (this should be covered in 2-6 (very dry) sentences); (c) Summary of the main technologies that you are using or introducing (and, in some cases, how this/these link(s) with (a), 2-6 sentences); (d) Summary of the main findings (linkage with (b), 2-3 sentences).}
+\blue{Abstracts for journal papers have very `squared-structure', and should contain: (a) Motivation (why would anyone bother to read the paper?
+Why is the paper and/or the subject relevant?
+This needs to be covered in 1-3 punchy sentences); (b) Main objective(s) of the manuscript with particular focus on the \underline{novelty(ies)} (this should be covered in 2-6 (very dry) sentences); (c) Summary of the main technologies that you are using or introducing (and, in some cases, how this/these link(s) with (a), 2-6 sentences); (d) Summary of the main findings (linkage with (b), 2-3 sentences).}
 
@@
   Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods.
+\blue{(choose key-words that do represent the contents of the paper.
+State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}
 
@@
 \section{Introduction}\label{section:Intro}
+
+\blue{The Introduction Section of a manuscript is often divided into 4 parts:
+   \begin{enumerate}[(a)]
+       \item Motivation for the work undertaken.
+What are the environmental, industrial and/or lab problems that this work will help tackling and/or solving (first and \underline{only one} paragraph)?
+       \item Literature review: this should focus on the main topics directly related to the manuscript (as a rule-of-thumb, you should choose up to 5 key-words that can better represent the work and write \underline{concisely} about recent development on them, i.e., state-of-the-art).
+Length of literature review should be 3-10 paragraphs and focus on `recent' developments in the topics including strengths and weakness.
+This `list' of topics (with associated references and range of strengths and weakness) may lead to {\it an explicit statement of the current gap of knowledge on the field that the manuscript will address}.
+This last key sentence will naturally lead to the;
+       \item Main aim and (list of) objective(s) of the work and how you intend to tackle the science problem (1 paragraph);
+       \item Summary of the work (last paragraph). 
+   \end{enumerate}
+}
+
 Detailed numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community for the past 50 years.
-This is mainly due to applications in oil and gas exploration and recovery, groundwater resources, underground coal gasification, geothermal power systems and, more recently, in carbon capture and storage (CCS) processes~\citep{spycher_2003, chen_2006,self_2012,pruess_1990c, white_1981,jiang_2011}.
-Complex geometries with irregular boundaries and strong heterogeneity in geological formations are the main issues addressed by developers of industry- and academic-standard flow simulators.
+This is mainly due to applications in oil and gas exploration, groundwater resources, underground coal gasification, geothermal power systems and, more recently, in carbon capture and storage (CCS) processes~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981, jiang_2011}.
+However, current porous media multiphase flow models are plagued with uncertainties associated with subsurface topology, lithostratigraphic heterogeneity and chemical and physical properties of subsurface fluids.
+Viscous fingering, a flow instability phenomenon that occurs at the interface of fluids with distinct viscosities, has a strong impact on the efficiency of both oil recovery and CO$_{2}$ trapping under reservoir conditions.
 
-Accurate prediction of multiphase flow behaviour through realistic porous media domains is one of the the main research challenges as \red{write about the main issues related to heterogeneity and link it with flow behaviour (2-4 sentences)}.
+Accurate prediction of multiphase flow behaviour through realistic porous media domains is one of the main research challenges as \red{write about the main issues related to heterogeneity and link it with flow behaviour (2-5 sentences with references)}.
+
+\red{\bf Write here \underline{3-6 literature review paragraphs based on} the chosen \underline{key-words} with the associated references. \underline{Be concise}!}
 
@@
 
-Larger scale problems can be approached by upscaling techniques.
+%Larger scale problems can be approached by upscaling techniques.
 This technique which is usually employed to solve the problem fails for certain types of heterogeneity.
@@
 The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-
-The first approach is limited to low flow rates and very small heterogeneity.
+\red{Try to rewrite this paragraph bearing in mind: (a) Is upscaling relevant for this manuscript?
+(b) If positive how are they related ?
+As we haven't introduced the main aim (and objectives) of the manuscript, such relationship must be added clearly and smoothly here.}
+ %The first approach is limited to low flow rates and very small heterogeneity.
 The second approach overcomes these limitation but also posses drawbacks which include; availability of fine-grid simulation with suitable level of accuracy, dependence of the psuedo functions on rate, direction and grid specification.
@@
 
-\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage w previous paragraphs or linkage w the main subject(s).}
+%\medskip
+Under specfic spatial conditions the displacement of fluids in porous media is unstable \red{{\bf(why?)}} and results in the formation of irregular flow patterns in the form of fingers \red{\bf why?}.
+This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??
+you are repeating the previous sentence ...)}.
+Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ??
+be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences\red{(Is this true ??
+if so give references.
+why is gravity or relperm relevant?
+dispersion...
+why?
+perm grad??)}.
+Moreover, in most cases \red{(refs?)} interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid \red{(How and why?)}.
+\medskip
 
-%\medskip
-Under specfic spatial conditions the displacement of fluids in porous media is unstable {\bf(why?)} and results in the formation of irregular flow patterns in the form of fingers.
-This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??)}.
-Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
-Moreover, in most cases interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid.
-\medskip
-%Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of flows in porous media may help to represent and address the importance of this phenomenon which can be found in petroleum, chemical and environmental related applications.
-{\bf (does the paper address any aspect of parallel computation or computational/data visualization?)}
+\blue{This last paragraph before aims and objectives (next paragraph) should be gentle transition from current state-of-the-art and this work.
+As a suggestion, the last paragraph should focus on a particular aspect of viscous fingering that may not be well-understood by the scientific community and that is addressed in the paper.
+For example, (a) impact of heterogeneity in the onset of fingering, (b) qualitative sensitivity study of viscosity ratio impact in the finger formation (based on analytical assessment studies), etc.}
 
-In this paper, the overlapping control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
+The main aim of this work is to numerically investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
+\red{\bf (try to develop it further; be more specific.
+Write this objective sentence/paragraph based on the paper's conclusions!)}.
+This study focuses on flow instabilities due to relatively large viscosity ratios.
+
+In this paper, a control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
 In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
@@
 
-\medskip
-
-Here, the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
-{\bf (try to develop it further; be more specific.
-Write this objective sentence/paragraph based on the paper's conclusions!)}.
-This study focuses on flow instabilities determined {\bf(determined or controlled?)} by the viscosity ratio.
-Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
-Finally, conclusions are drawn in the final section.
-{\bf (Needs better description of the remaining of teh paper.)}
+Section~\ref{section:NumericalFormulation} summarises the numerical formulation used in this work.
+The model is validated against Bucklet-Leverett (incompressible fluid displacement in homogeneous domain) and traditional four-regions (cross-flow assessment due to permeability gradient) test-cases (Section~\ref{section:ModelValidation}).
+Viscous flow instabilities in heterogeneous porous media is numerically investigated in Section~\ref{section:ViscousInstabilities} following by final remarks.
 

### 2016-10-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
latest changes

--- 2015-11-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \journal{Advances in Water Resources}
-\newcommand{\frc}{\displaystyle\frac}
-\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
-\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
 
@@
 \begin{abstract} 
-Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines Accurate prediction of multiphase flows in porous media remains one of the problems.
-While the governing equations are the conservation of mass and Darcy's law, there are also the primary variables, such us pressure, velocity, saturation and permeability.
-This paper introduces a multi-fluid porous media flow model which is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to control the local solution errors and  increase the computational accuracy in the research on the development of numerical methods in geophysical fluid mechanics.
-The governing multiphase porous media flow equations are solved using the adaptive and unstructured mesh.
+Numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
+Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow.
+A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics.
+The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
 The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
-%The element type described above has a discontinuous $n^{th}$ order polynomial representation of velocity and a continuous $(n+1)^{th}$ representation for pressure.
-This method includes the Darcy force balance equation, pressure, velocity and saturation fields throughout the domain while there is automatic mesh adaptivity in space and time and the computational cost is reduced.}
-Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this.
+Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena. 
+%The advantages of mesh adaptivity and the capability of the scheme are demonstrated for simulation of flow in several challenging computational domains.
+The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
+%Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this.
 The impact of fingers formation in our simulations is also investigated.
@@
 The formulation is applied to saturated porous media systems.
-We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage projects.
+We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
 
@@
 %%% SECTION %%%
+
 %%%         %%%
 \section{Introduction}\label{section:Intro}
+
 Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-This is mainly due to applications on oil and gas recovery, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
-Reservoir engineers and hydrogeologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+The conservation of mass along with Darcy's law are the governing equations while quantities such pressure, velocity,saturation and permeability define the  behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
+Considering the limitations of finite differences formulations the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model
+able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
+Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+
+Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
 Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
@@
 Larger scale problems can be approached by upscaling techniques.
-This technique which is usually employed to solve the problem fails for certain types of heterogeneity.
+These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
 These cases are normally resolved by stochastic representation of permeability and porosity fields.
 %Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
-There are several approaches to upscale the solutions, while three common types are herein discussed.
-The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space renormalization methods.
+There are several approaches to upscale solutions, while three common types are discussed.
+The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
 The $2^{nd}$ approach is called pseudoization.
@@
 
-The first approach is limited to low flow rates and very small heterogeneity.
-The second approach overcomes these limitation but also posses drawbacks which include; availability of fine-grid simulation with suitable level of accuracy, dependence of the psuedo functions on rate, direction and grid specification.
+The first approach is limited to low flow rates and very small heterogeneities.
+The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
 The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
@@
 
-\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage w previous paragraphs or linkage w the main subject(s).}
+\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage with previous paragraphs or linkage with the main subject(s).}
 
 %\medskip
-Under specfic spatial conditions the displacement of fluids in porous media is unstable {\bf(why?)} and results in the formation of irregular flow patterns in the form of fingers.
-This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??)}.
-Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences.
-Moreover, in most cases interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid.
-\medskip
-%Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of flows in porous media may help to represent and address the importance of this phenomenon which can be found in petroleum, chemical and environmental related applications.
-{\bf (does the paper address any aspect of parallel computation or computational/data visualization?)}
+Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
+The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
+%(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
+however it is still a function of relative mobility, gravity, dispersion, permeability differences.
+Moreover, in most cases interfacial tension is directly linked with the mobility ratio between the displaced and the displacing fluid.
 
-In this paper, the overlapping control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
-In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the CV space.
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
+
+%\medskip
+%\begin{comment}
+Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+
+Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
+In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
+
+Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
+Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+%\end{comment}
+
+%\medskip 
+%\begin{center}
+%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
+%\end{center}
+
+In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
+The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
+Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
+In addition, the study focused in flow instabilities determined by the viscosity ratio.
+In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
+Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
 High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
-This formulation can achieve an exact representation of the Darcy force balance equations.
-
-\medskip
-
-Here, the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
-{\bf (try to develop it further; be more specific.
-Write this objective sentence/paragraph based on the paper's conclusions!)}.
-This study focuses on flow instabilities determined {\bf(determined or controlled?)} by the viscosity ratio.
 Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
 Finally, conclusions are drawn in the final section.
-{\bf (Needs better description of the remaining of teh paper.)}
 
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
 %%%         %%%
@@
 
-During the simulations performed the Viscous fingering phenomenon has been observed.
+During the simulations performed in this paper the Viscous fingering phenomenon has been observed.
 Viscous fingering  is highly related with the mobility, which describes how easily a fluid moves into a porous media and can be expressed through the mobility ratio (\textit{MR}).

### 2016-10-03 Papers/Prototype_Accepted/KickAssIJNMF/CommentsForReviewers.tex

@@
 
+%%%
+%%% Numbering the equation in this file
+%%%
+\newcounter{defcounter}
+\setcounter{defcounter}{10}
+\usepackage{amsthm}
+\newenvironment{myequation}{%
+\addtocounter{equation}{-1}
+\refstepcounter{defcounter}
+\renewcommand\theequation{\thedefcounter}
+\begin{equation}}
+{\end{equation}}
+
 \begin{document}
+We thanks the reviewers for blablabla
+
+As such, the required modifications were performed as described below
 
@@
 %%%
-\item[\blue{Comment 1:}] \blue{``In Section 2.5 I found the interchange of the symbol {\bf v} (force per unit volume) with {\bf u} (saturation-weighted Darcy velocity) to be confusing: in the notation of eqn.
-2, I would have expected to find $\mathbf{\tilde{v}_{\alpha}}$ instead of $\mathbf{\tilde{u}_{\alpha}}$.
+\item[\blue{Comment 1:}] ``In Section 2.5 I found the interchange of the symbol {\bf v} (force per unit volume) with {\bf u} (saturation-weighted Darcy velocity) to be confusing: in the notation of eqn.
+12, I would have expected to find $\mathbf{\tilde{v}_{\alpha}}$ instead of $\mathbf{\tilde{u}_{\alpha}}$.
 The same goes for eqn.
@@
 13 or not.
-The two final paragraphs in the section are rather obscure and should be expanded more.''}\\
- bal bal
+The two final paragraphs in the section are rather obscure and should be expanded more.''\\
+ {\it We thank the reviewers for the comment and modified Section 2.5 to improve its readibility, clarify a few arguments and correct a few typos. This section should read as:}\\
+
+`{\it 2.5. Velocity at control volume interfaces}
+
+The velocity to be used at the interface between CV's in the saturation conservation (Eqn.
+7) and global continuity (Eqn.
+8) equations needs to be determined.
+On the CV faces, there is no information about the flow direction as the velocity is discontinuous at the CV boundaries.
+The discontinuities occur between (a) control volumes within each FE and (b) between elements when using the \PNDG[n+1]{n} element pair.
+
+In order to calculate the velocity across CV's within a FE, an average velocity at the interface of control volumes {\it i} and {\it j} is defined as:
+\begin{myequation}
+  {\tilde{\bf u}}_\alpha = \frac{1}{2} \left[ {{\bf u}_\alpha}_i + {{\bf u}_\alpha}_j \right].
+\end{myequation} 
+From this, the interface velocities at either side of the interface can be obtained from:
+%\begin{equation}
+%  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha
+%    k}^{-1}{\tilde{{\bf u}}}_{\alpha}, \;\;\;\; k=\{i,j\}.
+%  \label{two-vels}
+%\end{equation} 
+\begin{myequation}
+  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha k}^{-1}{{\bf \tilde{v}}}_{\alpha}, \;\;\;\; k=\{i,j\}. 
+  \label{two-vels}
+\end{myequation}
+
+These velocities have the same direction and differ only in magnitude, so using them to define an upwind direction is not ambiguous.
+If an upwind method for calculating the interface velocity is applied then,
+\begin{myequation}
+  {\tilde{\bf u}}_{\alpha} = \tilde{\bf u}_{\alpha k},\label{interface_velocity_upwind}
+\end{myequation}
+where $k=i$ if ${\bf n}\cdot{\bf u}_{\alpha}>0$ (CV {\it i} outgoing information), and $k=j$ if ${\bf n}\cdot{\bf u}_{\alpha}<0$ (CV {\it i} incoming information).
+
+However, upwind methods yield dissipative solutions therefore, in order to obtain a high-order approximation of the velocity at the interface, the saturation at the interface $\tilde{S}_{\alpha}$ is calculated using a finite element representation of the saturation following the upwind direction.
+$\tilde \sigma_{\alpha}$ can then be calculated using second-order Taylor series:
+%\begin{small}
+\begin{myequation}
+  \underline{\underline{\tilde{\sigma}}}_{\alpha} =
+  \underline{\underline{\sigma}}_{\alpha k} +
+  \left(\tilde{S}_{\alpha}-S_{\alpha k}\right) \left(\frc{\partial
+    \underline{\underline{\sigma}}_{\alpha}}{\partial
+    S_{\alpha}}\right)_{k} +
+  \frc{1}{2}\left(\tilde{S}_{\alpha}-S_{\alpha k}\right)^{2} \left[
+    \frc{ \left(\frc{\partial
+        \underline{\underline{\sigma}}_{\alpha}}{\partial
+        S_{\alpha}}\right)_{k} - \left(\frc{\partial
+        \underline{\underline{\sigma}}_{\alpha}}{\partial
+        S_{\alpha}}\right)_{l} } { \left(S_{\alpha k}-S_{\alpha
+        l}\right) } \right],
+  \label{sigma-out}
+\end{myequation}
+%\end{small}
+where $k=i$ and $l=j$ if ${\bf n}\cdot{\bf u}_{\alpha}>0$ and, $k=j$ and $l=i$ if ${\bf n}\cdot{\bf u}_{\alpha}<0$. Therefore, the final interface velocity (Eqn. 13) can be obtained from:
+%\begin{equation}
+%  {\tilde{\bf u}_{\alpha}} = \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1} \left[\displaystyle\frac{1}{2} \left( {{\bf u}_\alpha}_i + {{\bf u}_\alpha}_j \right)\right], \label{mean_int_vel}  
+%\end{equation} 
+\begin{myequation}
+  {\tilde{\bf u}_{\alpha}} = \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1} \left[\displaystyle\frac{1}{2} \left( {{\bf v}_\alpha}_i + {{\bf v}_\alpha}_j \right)\right], \label{mean_int_vel}  
+\end{myequation} 
+%The interface velocity obtained from Eqn.~\ref{mean_int_vel} is bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
+The result of this is also bounded between the velocities ${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf n}$.
+The interface velocity obtained from Eqn.
+15 is bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
+The result of this is also bounded between the velocities ${{\bf v}_\alpha}_i\cdot {\bf n}$ and ${{\bf v}_\alpha}_j\cdot {\bf n}$.
+
+\medskip
+
+In a fully discontinuous formulation with \PNDG[n+1]{n} element pairs, the interface velocity (now between neighbour elements) can not be calculated using Eqn.
+15 due the elliptic nature of the discretised non-symmetric pressure equation, Eqn.
+5.
+This means that information is propagated in all directions across the (discontinuous) domain and hence, taking the upwind velocity as commonly done within an element is not an adequate strategy.
+
+For two neighbouring CV's $i$ and $j$ with common FE interface ({\it e.g.}, see Fig.
+1b for \PNDG[2]{1} element pair), $\tilde{\bf u}_\alpha$ can be calculated by using a volume-weighted harmonic mean.
+However, the volume $\mathcal{V}$ of the control volume and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity in a very similar way.
+Hence, the velocity at the interface is expressed as,
+\begin{myequation} 
+  {\tilde{\bf u}_\alpha} =  \left(\mathcal{V}_{j}  
+    \underline{\underline{\sigma}}_{\alpha j} \, {\bf
+      u}_{\alpha i} + \mathcal{V}_{i} \underline{\underline{\sigma}}_{\alpha i}\, {\bf
+      u}_{\alpha j} \right) \left(  \mathcal{V}_{i} 
+    \underline{\underline{\sigma}}_{\alpha i} +
+    \mathcal{V}_{j} 
+    \underline{\underline{\sigma}}_{\alpha j} \right)^{-1}.
+\end{myequation}
+
 %%%
@@
 %%%
-\item[\blue{Comment 3:}] \blue{``(...) a statement in the {\it Conclusions} that 'control volumes do not span elements' apparently contradicts the sentence that 'Control volume (CV) boundaries span finite elements where material properties	are defined' (...) ''}\\
+\item[\blue{Comment 3:}] ``(...) a statement in the {\it Conclusions} that 'control volumes do not span elements' apparently contradicts the sentence that 'Control volume (CV) boundaries span finite elements where material properties	are defined' (...) ''\\
+{\it The first paragraph of the Conclusion was modify to take into account the suggestion of the reviewer, and not it reads as,} `A novel CVFEM formulation based on \PN[n]{m}(DG) element pairs with $n^{\rm th}$-order representation for velocity and $m^{\rm th}$-order for pressure has been presented.
+The main advantages of this formulation over existing ones is that arbitrarily high-order polynomial representation for pressure and velocity can be used and it is high-order accurate in space and time.
+In \PN[n]{n+1} element pairs, velocity is discontinuously defined by polynomials of order $n$ whereas pressure is continuously represented by polynomials of order $n+1$ with CVs spanning various neighbours elements, as exemplified by Fig.
+1a.
+However, in the novel \PNDG[n+1]{n} element pair, introduced in this paper, both pressure and velocity have discontinuous representation with polynomials of order $n$ and $n+1$, respectively.
+In this family of element pairs, CVs do not span elements (see Fig.
+1b), which resolves a long-standing problem associated with the use of traditional CVFEM formulations in heterogeneous porous media flows.'
+
 %%%
@@
 %%%
-\item[\blue{Comment 5:}] \blue{``
-''}\\
+\item[\blue{Comment 5:}] ``Finally, I think it would be useful to recap in the {\it Conclusions} what are the main differences in the use of \PN[1]{2} elements compared to \PNDG[2]{1} or other combinations.
+In my opinion, a systematic evaluation of the trade-off between higher order polynomials, grid refinement and computational cost is crucial to appreciate the results provided in the manuscript; however, the choice of elements pairs in the test cases appears to be made almost without rationale.
+Moreover, it would appear that the choice of the discontinuous formulation is always preferable for discontinuous materials: is there a counter-example that the authors can provide where the discontinuous formulation should not be used?''\\
+{\it Summary of the difference between the element-pairs are now included in the `Conclusion' section as described in {\bf Comment 3} above.
+In this paper, the family of \PNDG[n+1]{n} element-pair was introduced and we demonstrated that its use along with the novel numerical formulation -- Sections 2.3-6, can lead to advances on the study of numerical accuracy and stability of multiphase flows in heterogeneous porous matrices.
+The aim of this paper was not to either numerically explore this family of element-pairs in different conditions or, to assess the computational capability of the overall method.
+These were already performed by the authors elsewhere -- see refs.
+[27-29, 37-41].
+The overall aim of this paper is to describe the numerical formulation, and to demonstrate some of its functionality in multiphase porous media flow problems.
+However, we took the reviewer's comment on board and summarised, in a more structured manner, the formulation's functionalities.
+The following was included in the end of Section 3:}
+
+`For the test-cases considered here, porosity $\phi$ is assumed uniform and, for 4.1 $\mathbf{K}$ is also uniform.
+However, for test-cases~4.2-4.4, $\mathbf{K}$ is non-uniform and regions of constant $\mathbf{K}$ are used (subscript denotes region identities -- Figs.
+5 and 8).
+For all cases $\mathbf{K}$ is assumed isotropic.
+
+In Section 4, four sets of numerical simulations are performed using the formulation introduced in Section 2.
+The main aims of these simulations (Table II) are: a) to assess numerical convergence and accuracy; b) to validate the model against analytical (quantitative) and lab-experiments (qualitative) solutions; c) to numerically investigate the performance of \PN[1]{2} and \PNDG[2]{1} element-pairs in multiphase flows behaviour in highly heterogeneous media ({\it i.e.}, large permeability gradient) and; d) \red{any comment on test 4?}
+
+\begin{center}
+%\begin{table}[h]
+\centering{Table II. Summary of the test-cases performed in Section 4}
+\begin{tabular}{c|l c l}
+{\bf Test-Case} & {\bf Element-pairs}     & {\bf Dimensionality}   &   {\bf Main Features} \\
+                &                         & {\bf and mesh}         &                  \\ 
+\hline
+4.1 (Buckley-   & \PN[1]{1},              &  2D and 3D             & Assessment of model  \\
+Leverett)       & \PN[1]{2} and           &(structured/            & accuracy against analytical \\ 
+                & \PNDG[2]{1}             & unstructured)          & solutions \\
+\hline
+4.2 (Immiscible &\PN[1]{2} and            &  2D                    &  Qualitative analysis of the \\
+displacement)   &\PNDG[2]{1}              &(coarse and fine)       & model against lab-experiments\\
+\hline
+4.3 (Permeability &\PN[1]{2} and          & 2D                    & Numerical dispersion in \\
+constrast and aspect ratio) &\PNDG[2]{1}  &(coarse and fine)      & high-permeability contrast. \\
+\hline 
+4.4 (Channelisation)& \PNDG[1]{1}          & 3D                    &  \red{?}            \\
+                    & and \PNDG[2]{1}      &                       &                     \\
+\hline 
+\end{tabular}
+%\end{table}
+\end{center}
+
+%%%
+\item[\blue{Comment 6:}] ``(...) I have some grammatical preferences that are not significant.
+e.g., [Page 13, line 9: 'simulating' should be 'simulate'.], [Page 13, line 17: 'is' should be 'are'.], [Page 13, line 26: 'resolve successfully' should be 'successfully resolve'.] ''\\
+   {\it These changes were performed.}
+%%%
+\item[\blue{Comment 7:}] ``Page 3, line 16 (and Page 4, line 54): Why does this warrant a separate (sub)section.''\\
+   {\it We believe that the reviewer refers to the contents of Sections 2, and in particular the `rationale' behind  Sections 2.1-3.
+These subsections describe: a) explicit format of the extended Darcy equation used throughout this work; b) novel CVFEM formulation; c) new set of element-pairs; d) dual representation of the velocity field.
+The authors believe that by splitting these topics into 3 separated sections we have easied the reading and improved the understanding of the more complex parts of the introduced formulation described in Sections 2.5-7.}
+%%%
+\item[\blue{Comment 8:}] ``Page 4, line 27: This paragraph is not very clear; use of commas is a bit confusing. [e.g., linear and continuous]''\\
+{\it The authors agree with the reviewer and have modified the whole paragraph, which now reads as:} `In the formulation presented here, pressure, velocity, permeability and porosity are represented FE-wise, however saturation, relative permeability and fluid properties such as viscosity and density are represented CV-wise.
+Figure 1 displays the two families of element types presented in this paper: Fig.
+1(a) shows the P$_{n}$DG-P$_{n+1}$ element type, with $n = 1$, in two dimensions (2D).
+Here, the velocity field is linear and discontinuous (between elements) whilst pressure has a quadratic and continuous (between elements) representation with the CV's span various elements.
+Figure 1(b) shows the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$ (also in 2D).
+Here, the velocity field is quadratic and discontinuous (between elements) whereas pressure has a linear and discontinuous (between elements) representation and the CV's do not span elements.'
+
+%%%
+\item[\blue{Comment 9:}] ``Page 4, Figure 1: The two symbols overlaid (on the right panel) look somewhat like a third symbol, but this is probably OK.''\\
+{\it The authors agree with the reviewer that the overlaping of symbols may be confusing for readers as it does represent pressure and velocity nodes in the vertices of the triagles, therefore the caption of the figure now reads as:} `2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.'
+
+%%%
+\item[\blue{Comment 10:}]``Page 7, line 30: I believe the Brooks Corey model contains errors.''\\
+{\it The authors corrected the equations and associated text:} `The numerical model is evaluated using four two-phase flow test cases (Sections 4.1-4.4). The modified Brooks-Corey model [31,32]: 
+%\begin{eqnarray}
+%k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
+%k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
+%\end{eqnarray}
+\begin{eqnarray}
+   k_{rw}\left ( S_{w} \right ) &=& k_{rw}^{\circ} \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
+   k_{rnw}\left ( S_{w} \right ) &=& k_{rnw}^{\circ} \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
+\end{eqnarray}
+where subscripts {\it w} and {\it nw} indicate wetting and non-wetting phase.
+$k_{rw}^{\circ}$ and $k_{rnw}^{\circ}$ are end-point relative permeability to wetting and non-weting phases, $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume fractions, respectively.
+The exponents $n_w$ and $n_{nw}$ are both set to 2 for all test cases.'
+
+%%%
+\item[\blue{Comment 11:}] ``Page 7, line 40: The exponents are not in the table. Double-check this.''\\
+{\it Exponents for the modified Brooks-Corey, $n_w$ and $n_{nw}$, are set to 2 as described in the end of the paragraph that follows the equation:} `(...) $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume fractions, respectively.
+The exponents $n_w$ and $n_{nw}$ are both set to 2 for all test cases.'
+%%%
+\item[\blue{Comment 12:}] ``Page 8, line 40: Redundant description of the centre-line sentence (not necessary).''\\
+{\it The authors agree with the reviewer and have the second reference to center-line plot,} `(...) The geometry centre-line is used to plot these profiles (...)'{\it, removed.}
+%%%
+\item[\blue{Comment 13:}] ``Page 10, Figures 6 and 7: Is it possible to use similar color scale and/or do a quantitative comparison?''\\
+{\it Unfortunately the authors are not able to match the colour scale of the numerical simuations (Fig.
+6) with the one used by the physical experiments by Dawe and Grattoni.
+However, we improve the caption of Fig.
+7 to make it clearer, now it reads as,} `Figure 7.
+Wetting phase volume fraction map obtained from the experiment performed by Dawe and Grattoni (extracted from [34]).
+Red contour indicates the injected fluid breakthrough.
+Permeability distribution used in this experiment is the same as shown in Fig.
+5.'
+%%%
+\item[\blue{Comment 14:}] \blue{``Page 12, Figure 9: Is it possible to use a colorbar/colorscale to clarify the top panel?''}\\
+\red{DP, can you add a legend for Fig. 9?} 
 %%%

### 2016-10-03 Papers/Prototype_Accepted/KickAssIJNMF/article.tex

--- 2016-05-08 Papers/Prototype_Accepted/KickAssIJNMF/article_bak.tex
@@
 
+% Adding line numbers ... and colours for comments
+\usepackage{lineno}
+\linenumbers
+\pagewiselinenumbers
+\usepackage{color}
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+
 \begin{document}
@@
 
-\title{A Force-Balanced Control Volume Finite Element Method for Multi-phase Porous Media Flow Modelling}
+\title{A Force-Balanced Control Volume Finite Element Method for Multi-Phase Porous Media Flow Modelling}
 
@@
 of radioactive waste, and carbon capture and storage \cite{chen_2006,
-  aiea_1999, pruess_1990c, jiang_2011}. Such applications often
+ aiea_1999,pruess_1990c,jiang_2011}. Such applications often
 include complex geometries with irregular (and often internal)
@@
 complex geometries. In addition, FDM can produce excessive numerical
-dispersion in heterogeneous porous media \cite{chavent_1986}.
+dispersion in heterogeneous porous media flows \cite{chavent_1986}.
 
@@
 properties, the mixed FEM formulation often led to physically
-unrealistic solutions.  Cumming et al. \cite{cumming_2011} demonstrated that a
+unrealistic solutions.  Cumming {\it et al.} \cite{cumming_2011} demonstrated that a
 CVFEM-based discretisation could be used to solve the Richards
@@
 overhead, compared with traditional, coupled velocity-pressure based
-formulations.  Mass balance was enforced as described by Kirkland et al.
+formulations.  Mass balance was enforced as described by Kirkland {\it et al.}
 \cite{kirkland_1992} (see also \cite{forsyth_1990,cumming_phd2012}). However, CVFEM often requires
@@
   surface or material discontinuities --
-  see \cite{brooks_1982,tezduyar_1986}) were originally developed to
+  see \cite{brooks_1982,tezduyar_1986}), were originally developed to
 resolve sharp changes in solution fields such as velocity or
@@
 governing equations and numerical methods employed to solve them are
-presented in Section~\ref{overlapping_method_section}. Model set-up
+introduced in Section~\ref{overlapping_method_section}. Model set-up
 and results including comparison against reference data are given in
-Sections~\ref{setup} and \ref{res}, respectively. Finally, some
+Sections~\ref{setup} and~\ref{res}, respectively. Finally, 
 concluding remarks are presented in Section~\ref{conc}.
 
-\section{Governing equations and numerical method}
+\section{Governing Equations and Numerical Formulation}
 \label{overlapping_method_section}
@@
 \end{eqnarray} 
+\red{DP, shouldn't this equation be 
+\begin{eqnarray}
+  \sum\limits_{E} \left. \int\limits_{\Omega_E} { {Q}}_i \left (
+             {\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha}
+             \right) dV \right. + \displaystyle \oint_{\Gamma_{E}}
+                   {Q}_i {\mathbf n} \left(p - \tilde{p}\right)
+                   d\Gamma + \nonumber \\ \oint_{\Gamma_{\Omega}} {
+                     Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma
+                   = \bm{0},\nonumber
+                   \label{force-semi-disc} 
+\end{eqnarray} 
+instead (to be consistent w Eqn. 3)? }
+
 where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of
@@
 \subsection{Control volume finite element types}
-In the formulation presented here, pressure, velocity, permeability
-and porosity are represented FE-wise, but saturation, relative
-permeability and fluid properties such as viscosity and density are
-represented CV-wise. Fig.~\ref{fem_cv_represent_a} displays the two
-families of element types presented in this
-paper. Fig.~\ref{fem_cv_represent_a} (a) shows the P$_{n}$DG-P$_{n+1}$
-element type, with $n = 1$, in two dimensions (2D). Here, the velocity
-field is linear, discontinuous (between elements), the pressure field
-has a quadratic, continuous (between elements), representation and the
-CV's span various elements. Fig.~\ref{fem_cv_represent_a} (b) shows
-the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$, also in 2D. Here,
-the velocity field is quadratic, discontinuous (between elements), the
-pressure field has a linear, discontinuous (between elements),
-representation and the CV's do not span elements.
+In the formulation presented here, pressure, velocity, permeability and porosity are represented FE-wise, however saturation, relative permeability and fluid properties such as viscosity and density are represented CV-wise.
+Figure~\ref{fem_cv_represent_a} displays the two families of element types presented in this paper: Fig.~\ref{fem_cv_represent_a} (a) shows the P$_{n}$DG-P$_{n+1}$ element type, with $n = 1$, in two dimensions (2D).
+Here, the velocity field is linear and discontinuous (between elements) whilst pressure has a quadratic and continuous (between elements) representation with the CV's span various elements.
+Figure~\ref{fem_cv_represent_a} (b) shows the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$ (also in 2D).
+Here, the velocity field is quadratic and discontinuous (between elements) whereas pressure has a linear and discontinuous (between elements) representation and the CV's do not span elements.
 
@@
 \subfloat[P$_2$DG-P$_1$DG]{\includegraphics[width=.5\textwidth]{p2dgp1-dg-sat.pdf}}
-\caption{2D representation of the element pairs presented in this
-  work. Shaded areas denote control volumes (in which saturation is
-  stored), black points represent the pressure nodes and white points
-  the velocity nodes.}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
     \label{fem_cv_represent_a}
@@
 \subsection{Finite element representation of velocity} \label{Section:Force_density}
-From Eqn.~\ref{e:darcy_eqn}, it can be seen that the velocity field
-depends, among other fields, on the absolute permeability, which is
-FE-wise, and the relative permeability, which is CV-wise. This means
-that the velocity representation is different in each CV. However, the
-quantity $\mathbf{v}_\alpha$ is homogeneous within an element and this
-is what is stored using FE. To obtain the velocity
-$\mathbf{u}_{\alpha}$ in a particular CV within a FE,
-Eqn.~\ref{force-bal} is used.
+From Eqn.~\ref{e:darcy_eqn}, it can be seen that the velocity field depends, among other fields, on the absolute permeability which is FE-wise, and the relative permeability which is CV-wise.
+This means that the velocity representation is different in each CV.
+However, the quantity $\mathbf{v}_\alpha$ is homogeneous within an element and this is stored using FE representation.
+To obtain the velocity $\mathbf{u}_{\alpha}$ in a particular CV within a FE, Eqn.~\ref{force-bal} is used.
 
@@
 \subsection{Velocity at control volume interfaces} \label{opt-up} 
-The velocity to be used at the interface between CV's in the
-saturation conservation (Eqn.~\ref{detail-sat-eqn-k}) and global
-continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations needs to be
-determined. On the CV faces, there is no information about the flow
-direction as the velocity is discontinuous at the CV boundaries. The
-discontinuities occur between (a) control volumes within each FE and
-(b) between elements when using the P$_{n+1}$DG-P$_{n}$DG pair.
+The velocity to be used at the interface between CV's in the saturation conservation (Eqn.~\ref{detail-sat-eqn-k}) and global continuity (Eqn.~\ref{detail-sat-eqn-k-sum}) equations needs to be determined.
+On the CV faces, there is no information about the flow direction as the velocity is discontinuous at the CV boundaries.
+The discontinuities occur between (a) control volumes within each FE and (b) between elements when using the \PNDG[n+1]{n} element pair.
 
-To calculate the velocity across CV's within a FE, an average velocity
-at the interface of control volumes {\it i} and {\it j} is defined as:
+In order to calculate the velocity across CV's within a FE, an average velocity at the interface of control volumes {\it i} and {\it j} is defined as:
 \begin{equation}
-  {\tilde{\bf u}}_\alpha = \frac{1}{2} \left[ {{\bf u}_\alpha}_i +
-    {{\bf u}_\alpha}_j \right].
+  {\tilde{\bf u}}_\alpha = \frac{1}{2} \left[ {{\bf u}_\alpha}_i + {{\bf u}_\alpha}_j \right].
 \end{equation} 
-From this, the interface velocities at either side of the interface
-can be obtained from:
+From this, the interface velocities at either side of the interface can be obtained from:
+%\begin{equation}
+%  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha
+%    k}^{-1}{\tilde{{\bf u}}}_{\alpha}, \;\;\;\; k=\{i,j\}.
+%  \label{two-vels}
+%\end{equation} 
 \begin{equation}
-  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha
-    k}^{-1}{\tilde{{\bf u}}}_{\alpha}, \;\;\;\; k=\{i,j\}.
+  {\tilde{\bf u}}_{\alpha k} = \underline{\underline{\sigma}}_{\alpha k}^{-1}{{\bf \tilde{v}}}_{\alpha}, \;\;\;\; k=\{i,j\}. 
   \label{two-vels}
 \end{equation}
-These velocities have the same direction and 
-differ only in magnitude, so using them to define an upwind
-direction is not ambiguous.
 
-If an upwind method for calculating the interface velocity is applied
-then the interface velocity becomes:
+These velocities have the same direction and differ only in magnitude, so using them to define an upwind direction is not ambiguous.
+If an upwind method for calculating the interface velocity is applied then,
 \begin{equation}
-  {\tilde{\bf u}}_{\alpha} = \tilde{\bf u}_{\alpha k},
+  {\tilde{\bf u}}_{\alpha} = \tilde{\bf u}_{\alpha k},\label{interface_velocity_upwind}
 \end{equation}
-where $k=i$, if ${\bf n}\cdot{\bf u}_{\alpha}>0$ (CV {\it i} outgoing
-information) and $k=j$, if ${\bf n}\cdot{\bf u}_{\alpha}<0$ (CV {\it
-  i} incoming information). However, upwind methods yield dissipative
-solutions. In order to obtain a high-order approximation of the
-velocity at the interface, the saturation at the interface
-$\tilde{S}_{\alpha}$ is calculated using a finite element
-representation of the saturation following the upwind direction.
-$\tilde \sigma_{\alpha}$ can then be calculated using second-order
-Taylor series:
-\begin{small}
+where $k=i$ if ${\bf n}\cdot{\bf u}_{\alpha}>0$ (CV {\it i} outgoing information), and $k=j$ if ${\bf n}\cdot{\bf u}_{\alpha}<0$ (CV {\it i} incoming information).
+
+However, upwind methods yield dissipative solutions therefore, in order to obtain a high-order approximation of the velocity at the interface, the saturation at the interface $\tilde{S}_{\alpha}$ is calculated using a finite element representation of the saturation following the upwind direction.
+$\tilde \sigma_{\alpha}$ can then be calculated using second-order Taylor series:
+%\begin{small}
 \begin{equation}
@@
 \end{equation}
-\end{small}
-where $k=i$ and $l=j$, if ${\bf n}\cdot{\bf u}_{\alpha}>0$ and $k=j$
-and $l=i$, if ${\bf n}\cdot{\bf u}_{\alpha}<0$. The final interface
-velocity is obtained from:
+%\end{small}
+where $k=i$ and $l=j$ if ${\bf n}\cdot{\bf u}_{\alpha}>0$ and, $k=j$ and $l=i$ if ${\bf n}\cdot{\bf u}_{\alpha}<0$.
+Therefore, the final interface velocity (Eqn.~\ref{interface_velocity_upwind}) can be obtained from:
+%\begin{equation}
+%  {\tilde{\bf u}_{\alpha}} = \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1} \left[\displaystyle\frac{1}{2} \left( {{\bf u}_\alpha}_i + {{\bf u}_\alpha}_j \right)\right], \label{mean_int_vel}  
+%\end{equation} 
 \begin{equation}
-  {\tilde{\bf u}_{\alpha}} =
-  \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1}
-  \left[\displaystyle\frac{1}{2} \left( {{\bf u}_\alpha}_i + {{\bf
-        u}_\alpha}_j \right)\right],
-  \label{mean_int_vel}  
+  {\tilde{\bf u}_{\alpha}} = \underline{\underline{\tilde{\sigma}}}_{\alpha}^{-1} \left[\displaystyle\frac{1}{2} \left( {{\bf v}_\alpha}_i + {{\bf v}_\alpha}_j \right)\right], \label{mean_int_vel}  
 \end{equation} 
-which is bounded to ensure that its normal component ${\tilde{\bf
-    u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha
-    i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf
-  n}$. The result of this is also bounded between the velocities
-${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf
-  n}$.
+%The interface velocity obtained from Eqn.~\ref{mean_int_vel} is bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
+The result of this is also bounded between the velocities ${{\bf u}_\alpha}_i\cdot {\bf n}$ and ${{\bf u}_\alpha}_j\cdot {\bf n}$.
+The interface velocity obtained from Eqn.~\ref{mean_int_vel} is bounded to ensure that its normal component ${\tilde{\bf u}_\alpha}\cdot {\bf n}$ lies between ${\tilde{\bf u}_{\alpha i}}\cdot {\bf n}$ and ${\tilde{\bf u}_{\alpha j}}\cdot {\bf n}$.
+The result of this is also bounded between the velocities ${{\bf v}_\alpha}_i\cdot {\bf n}$ and ${{\bf v}_\alpha}_j\cdot {\bf n}$.
 
-In order to calculate the velocity between elements (when using
-P$_{n+1}$DG-P$_{n}$DG elements) one first needs to consider that it is
-also necessary to obtain the discretised non-symmetric pressure
-equation which has elliptic-like properties. These properties mean it
-is necessary to propagate information in all directions across the
-domain, therefore taking the upwind velocity, as commonly done within
-an element, is not the best strategy.
+\medskip
 
-For two neighbouring CV's $i$ and $j$ with common FE interface,
-$\tilde{\bf u}_\alpha$ can be calculated by using a volume-weighted
-harmonic mean. However, the volume $\mathcal{V}$ of the control volume
-and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity in a
-very similar way. Hence, the velocity at the interface is expressed
-as:
+In a fully discontinuous formulation with \PNDG[n+1]{n} element pairs, the interface velocity (now between neighbour elements) can not be calculated using Eqn.~\ref{mean_int_vel} due the elliptic nature of the discretised non-symmetric pressure equation, Eqn.~\ref{force-balance-matrix-form}.
+This means that information is propagated in all directions across the (discontinuous) domain and hence, taking the upwind velocity as commonly done within an element is not an adequate strategy.
+
+For two neighbouring CV's $i$ and $j$ with common FE interface ({\it e.g.}, see Fig.~\ref{fem_cv_represent_a}b for \PNDG[2]{1} element pair), $\tilde{\bf u}_\alpha$ can be calculated by using a volume-weighted harmonic mean.
+However, the volume $\mathcal{V}$ of the control volume and $\underline{\underline{\sigma}}_{\alpha}$ act on the velocity in a very similar way.
+Hence, the velocity at the interface is expressed as,
 \begin{equation} 
@@
 \section{Model set-up}\label{setup}
-The numerical method is evaluated using four test cases (\ref{classical_BL} --
-\ref{res5}). All test cases simulate two-phase flow. The Brooks-Corey model
-\cite{brooks_1964}: 
+The numerical model is evaluated using four two-phase flow test-cases (Sections~\ref{classical_BL}-~\ref{res5}). The modified Brooks-Corey model \cite{Alpak_1999,brooks_1964}: 
+%\begin{eqnarray}
+%k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
+%k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
+%\end{eqnarray}
 \begin{eqnarray}
-k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
-k_{rw}\left ( S_{w} \right ) &=& \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
+   k_{rw}\left ( S_{w} \right ) &=& k_{rw}^{\circ} \left ( \frac{S_w-S_{wirr}}{1-S_{wirr}-S_{nwr}} \right )^{n_w}, \\
+   k_{rnw}\left ( S_{w} \right ) &=& k_{rnw}^{\circ} \left ( \frac{S_{nw}-S_{nwr}}{1-S_{wirr}-S_{nwr}} \right)^{n_{nw}}, 
 \end{eqnarray}
-where $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume
-fractions, respectively, is used to calculate the relative
-permeabilities for all test cases. The exponents $n_w$ and $n_{nw}$
-are both set to 2 for all test cases.
+where subscripts {\it w} and {\it nw} indicate wetting and non-wetting phase.
+$k_{rw}^{\circ}$ and $k_{rnw}^{\circ}$ are end-point relative permeability to wetting and non-weting phases, $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume fractions, respectively.
+The exponents $n_w$ and $n_{nw}$ are both set to 2 for all test cases.
 
@@
 
-For the test cases considered here, the porosity $\phi$ is assumed
-uniform and for case \ref{classical_BL}, $\mathbf{K}$ is also
-uniform. However, for cases \ref{res2} -- \ref{res5}, $\mathbf{K}$ is
-non-uniform and regions of constant $\mathbf{K}$ are used. For all
-cases, $\mathbf{K}$ is isotropic. The subscript in $\mathbf{K}$
-denotes region identities (see Figs.~\ref{fig:4reg_BL_schematic} and
-\ref{fig:wedge_permeability}).
+For the test-cases considered here, porosity $\phi$ is assumed uniform and, for \ref{classical_BL} $\mathbf{K}$ is also uniform.
+However, for test-cases~\ref{res2}-~\ref{res5}, $\mathbf{K}$ is non-uniform and regions of constant $\mathbf{K}$ are used (subscript denotes region identities -- Figs.~\ref{fig:4reg_BL_schematic} and~\ref{fig:wedge_permeability}).
+For all cases $\mathbf{K}$ is assumed isotropic.
 
+In Section~\ref{res}, four sets of numerical simulations are performed using the formulation introduced in Section~\ref{overlapping_method_section}.
+The main aims of these simulations (Table~\ref{Table:SummaryTestCases}) are: a) to assess numerical convergence and accuracy; b) to validate the model against analytical (quantitative) and lab-experiments (qualitative) solutions; c) to numerically investigate the performance of \PN[1]{2} and \PNDG[2]{1} element-pairs in multiphase flows behaviour in highly heterogeneous media ({\it i.e.}, large permeability gradient) and; d) \red{any comment on test 4?}
+\begin{center}
+\begin{table}[h]
+    \caption{Summary of the test-cases performed in Section~\ref{res}}\label{Table:SummaryTestCases}
+\begin{tabular}{c|l c l}
+{\bf Test-Case} & {\bf Element-pairs}     & {\bf Dimensionality}   &   {\bf Main Features} \\
+                &                         & {\bf and mesh}         &                  \\ 
+\hline
+4.1 (Buckley-   & \PN[1]{1},              &  2D and 3D             & Assessment of model  \\
+Leverett)       & \PN[1]{2} and           &(structured/            & accuracy against analytical \\ 
+                & \PNDG[2]{1}             & unstructured)          & solutions \\
+\hline
+4.2 (Immiscible &\PN[1]{2} and            &  2D                    &  Qualitative analysis of the \\
+displacement)   &\PNDG[2]{1}              &(coarse and fine)       & model against lab-experiments\\
+\hline
+4.3 (Permeability &\PN[1]{2} and          & 2D                    & Numerical dispersion in \\
+constrast and aspect ratio) &\PNDG[2]{1}  &(coarse and fine)      & high-permeability contrast. \\
+\hline 
+4.4 (Channelisation)& \PNDG[1]{1}          & 3D                    &  \red{?}            \\
+                    & and \PNDG[2]{1}      &                       &                     \\
+\hline 
+\end{tabular}
+\end{table}
+\end{center}
+
+%%%
+%%%
+%%%
 \section{Results}\label{res}
@@
 
-The Buckley-Leverett problem \cite[non-wetting phase displaced by a
-  wetting phase]{buckley1942} is simulated here.  Despite the
-one-dimensional (1D) nature of the problem, 2D and three-dimensional
-(3D) simulations are performed to evaluate the multi-dimensional
-capabilities of the model (see Fig.~\ref{fig:maps2d_3d}). The
-\PN[1]{1}, \PN[1]{2} and \PN[2]{1}DG element pairs are used for these
-simulations.
+The Buckley-Leverett problem (non-wetting phase displaced by a wetting phase~\cite{buckley1942}) is simulated here.
+Despite the 1D nature of the problem, 2D and 3D simulations are performed to evaluate the multi-dimensional capabilities of the model (see Fig.~\ref{fig:maps2d_3d}).
+The \PN[1]{1}, \PN[1]{2} and \PN[2]{1}DG element pairs are used for these simulations.
 
@@
 
-Fig.~\ref{fig:BL_tests} (a), (b) and (c) shows phase volume fraction
-profiles of the wetting phase for four meshes in 2D at
-non-dimensional time $t=0.2$. All meshes are structured and have 4
-elements perpendicular to the flow and 60, 120, 240 or 480 elements
-parallel to the flow (see Fig.~\ref{fig:maps2d_3d}, a). The geometry
-centre-line is used to plot these profiles. All element pairs
-satisfactorily capture the discontinuity in the phase volume fraction
-and as the number of elements is increased the error is reduced.
-Fig.~\ref{fig:BL_tests} (d) shows results obtained for a
-Buckley-Leverett test case in 3D. A 1207-element fully unstructured
-mesh is used for these simulations. The geometry centre-line is used
-to plot these profiles. All the element pairs are again capable of
-accurately capturing the discontinuity in the phase volume fraction.
+Figures~\ref{fig:BL_tests} (a-c) show phase volume fraction profiles of the wetting phase for four meshes in 2D at non-dimensional time $t=0.2$.
+All meshes are structured and have 4 elements perpendicular to the flow and 60, 120, 240 or 480 elements parallel to the flow (see Fig.~\ref{fig:maps2d_3d}, a).
+The geometry centre-line is used to plot these profiles.
+All element pairs satisfactorily capture the discontinuity in the phase volume fraction and as the number of elements is increased the error is reduced.
+Figure~\ref{fig:BL_tests} (d) shows results obtained for a Buckley-Leverett test case in 3D.
+A 1207-element fully unstructured mesh is used for these simulations.% The geometry centre-line is used to plot these profiles.
+All the element pairs are again capable of accurately capturing the discontinuity in the phase volume fraction.
 
@@
 
-Fig.~\ref{fig:errors_BL_2D} (a) shows convergence rates for the
-results presented in Fig.~\ref{fig:BL_tests} (a), (b) and (c). The
+Figure~\ref{fig:errors_BL_2D} (a) shows convergence rates for the
+results presented in Fig.~\ref{fig:BL_tests} (a-c). The
 L$_2$ error norm of the wetting phase volume fraction is used
@@
 high-order methods switch to simple upwinding at the discontinuity.
-Fig.~\ref{fig:errors_BL_2D} (b) shows the convergence rate of the same
+Figure~\ref{fig:errors_BL_2D} (b) shows the convergence rate of the same
 high-order element pair simulation (Fig.~\ref{fig:BL_tests}, b) at
@@
       Buckley-Leverett test case for element pairs \PN[1]{1},
-      \PN[1]{2} and \PN[2]{1}DG in 2D. \label{fig:errors_BL_2D}}
+      \PN[1]{2} and \PN[2]{1}DG in 2D. \red{DP, can we have the number of elements in Fig a?}\label{fig:errors_BL_2D}}
   \end{center}
@@
 
-This test case is designed to demonstrate the numerical robustness of
-the method for modelling heterogeneous porous media and it is based on
-the physical experiment presented in Dawe and Grattoni \cite{dawe_2008}. As shown in
-Fig.~\ref{fig:4reg_BL_schematic} the permeability field is
-non-uniform.
+This test case is designed to demonstrate the numerical robustness of the method for modelling heterogeneous porous media and it is based on the physical experiment presented by Dawe and Grattoni \cite{dawe_2008}.
+As shown in Fig.~\ref{fig:4reg_BL_schematic} the permeability field is non-uniform.
 
@@
     elements. Bottom row: \PN[2]{1}DG elements. Left column: coarse
-    mesh. Right column: fine mesh. The meshes used for these
-    simulations are also shown here.\label{fig:4reg_maps}}
+    mesh. Right column: fine mesh. \label{fig:4reg_maps}}%The meshes used for these simulations are also shown here.\label{fig:4reg_maps}}
 \end{figure}
@@
     \includegraphics[width=0.6\textwidth]{Real_quadrant}
-    \caption{Wetting phase volume fraction maps from the experiments
-      of \cite{dawe_2008}. \label{fig:dawe_real}}
+    \caption{Wetting phase volume fraction map obtained from the experiment performed by Dawe and Grattoni (extracted from \cite{dawe_2008}).
+Red contour indicates the injected fluid breakthrough.
+Geometry and permeability distribution used in this experiment is the same as shown in Fig.~\ref{fig:4reg_BL_schematic}.
+\label{fig:dawe_real}}
   \end{center}
@@
 
-Fig.~\ref{fig:4reg_maps} shows the wetting phase volume fraction maps
+Figure~\ref{fig:4reg_maps} shows the wetting phase volume fraction maps
 at time $t=0.16$ for all four simulations. Results for the
@@
 flow behaviour, their correct representation and resolution is key to
-obtaining reliable solutions. In this model three different sets of
+obtain reliable productivity solutions. In this model three different sets of
 highly permeable channels are considered. The mesh and permeability
-map for these simulations is shown in Fig.~\ref{fig:fluvial_model}
+map for these simulations are shown in Fig.~\ref{fig:fluvial_model}
 (top). The thin channels have a permeability of $\mathbf{K}_\text{3}$,
@@
 $\mathbf{K}_\text{1}$.
+\red{Maybe it is worth commenting either $\mathbf{K}$ ratio or which one is the more or less permeable, i.e., $\mathbf{K}_{1} < \mathbf{K}_{2} < \mathbf{K}_{3}$ -- See reviewers' comments 4, 14 and 3.}
 
@@
 element pair (closest to traditional CVFEM formulation) is numerically
-more dispersive. Nevertheless, these results demonstrate the potential
-of the methods presented here to simulating real-world geometries.
+more dispersive \red{(do we have any proof of this? either for this paper or other published paper)}. Nevertheless, these results demonstrate the potential
+of the methods presented here to simulate real-world geometries.
 
@@
 
-A novel CVFEM based on the \PN[n]{m}(DG) element pairs with $n^{\rm
-  th}$-order representation for velocity and $m^{\rm th}$-order for
-pressure has been presented. The main advantages of this method over
-existing ones is that arbitrarily high-order polynomial representation
-for pressure and velocity can be used and it is high-order accurate in
-space and time. In addition, for \PN[n]{m}DG element pairs control
-volumes do not span elements, which resolves a long-standing problem
-associated with the use of traditional CVFEM formulations in
-heterogeneous porous media.
+A novel CVFEM formulation based on \PN[n]{m}(DG) element pairs with $n^{\rm th}$-order representation for velocity and $m^{\rm th}$-order for pressure has been presented.
+The main advantages of this formulation over existing ones is that arbitrarily high-order polynomial representation for pressure and velocity can be used and it is high-order accurate in space and time.
+In \PN[n]{n+1} element pairs, velocity is discontinuously defined by polynomials of order $n$ whereas pressure is continuously represented by polynomials of order $n+1$ with CVs spanning various neighbours elements, as exemplified by Fig.~\ref{fem_cv_represent_a}a.
+However, in the novel \PNDG[n+1]{n} element pair, introduced in this paper, both pressure and velocity have discontinuous representation with polynomials of order $n$ and $n+1$, respectively.
+In this family of element pairs, CVs do not span elements (see Fig.~\ref{fem_cv_represent_a}b), which resolves a long-standing problem associated with the use of traditional CVFEM formulations in heterogeneous porous media flows.
 
@@
 and first-order convergence rates were achieved for solutions with
-discontinuities, which is not common in the literature
+discontinuities, which are not common in the literature
 (see \cite{Schmid,Hoteit}). Second-order convergence rates were
@@
 methods presented under heterogeneous and high aspect ratio
-computational domains. It was shown that the method is able to resolve
-successfully multi-phase flows under those circumstances. Furthermore,
+computational domains. It was shown that the method is able to 
+successfully resolve multi-phase flows under those circumstances. Furthermore,
 the \PN[n+1]{n}DG element pair was shown to completely remove

### 2017-01-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{blue} JG Note $\Rightarrow$ #1}}}
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
 \newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
 \journal{Advances in Water Resources}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
 
@@
 
-\title{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media}
+\title{ \blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ...
+something with viscous flow instability or viscous fingering)}}
 
 %% use optional labels to link authors explicitly to addresses:
-\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} 
+\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
 \author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
@@
 \address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
+\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
 
@@
 Numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
+Viscous fingering, a fluid instability can be a major concern regarding enhanced oil-recovery methods (EOR).
 Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow.
 A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
-The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics.
+The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics and tackle the difficulties that commercial resevoir simulators may rise when using low order finite volume/differences methods based on structured grids.
 The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
@@
 Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena.
-%The advantages of mesh adaptivity and the capability of the scheme are demonstrated for simulation of flow in several challenging computational domains.
 The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
-%Numerical modelling of multiphase flows in porous media has application in a wide range of disciplines, from hydrocarbons exploration and extraction to groundwater operations.Viscous fingering, member of the flow instabilities family, is a major concern for the oil \& gas industry, but not only to this.
-The impact of fingers formation in our simulations is also investigated.
-%This paper describes a  In particular, the \PNDG[1]{1} element (i.e., discontinuous and piecewise linear shape functions to discretise velocity and pressure fields) is introduced as the basis of the discretisation and also as the CVFEM counterpart.
-In addition to the unstructured grid used for the simulations, uniform and random permeability distribution are introduced.
-The formulation is applied to saturated porous media systems.
 We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
 
-\JGnote{ Abstracts for journal papers have very `squared-structure': (a) Motivation (why would anyone bother to read the paper?
+%\JGnote{ Abstracts for journal papers have very `squared-structure': (a) Motivation (why would anyone bother to read the paper?
 Why is it (the paper and/or the subject) relevant?
@@
 %%% SECTION %%%
-
-%%%         %%%
+%%%         %%%
+
+\KCnote{Please reorganise the structure like the papers you read, and reference them!}
+
 \section{Introduction}\label{section:Intro}
@@
 Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-
-The conservation of mass along with Darcy's law are the governing equations while quantities such pressure, velocity,saturation and permeability define the  behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
-Considering the limitations of finite differences formulations the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model
-able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
-
+Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies.
 Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
 Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
-%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
-%This is well suited for analysis of small scales such as core samples.
-\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
-)}.
+This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+\medskip
+
+The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
+Particle methods, front-tracking methods \citep{univerdi_1992} but in particular volume of fluid (VOF) methods \citep{hirt_1981,rider_1998} are used to describe the afformentioned proeprties.
+In addition, finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
+
+The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
+Considering the limitations of finite differences formulations the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
+Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
 
@@
 These cases are normally resolved by stochastic representation of permeability and porosity fields.
-%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
 There are several approaches to upscale solutions, while three common types are discussed.
@@
 The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-
-The first approach is limited to low flow rates and very small heterogeneities.
+Problems start to rise when complex flow patterns will appear during the recovery of hydrocarbons triggered by heterogeneities.
+%The first approach is limited to low flow rates and very small heterogeneities.
 The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
@@
 
-\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage with previous paragraphs or linkage with the main subject(s).}
-
-%\medskip
+%\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage with previous paragraphs or linkage with the main subject(s).}
+
+\medskip
 Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
-The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
+These patterns are also described as flow instabilities or \textit{viscous fingering},  or most widely known as Saffman-Taylor instabilitises.
+This phenomenon will occur during an unfavorable -mobility-ration displacement, when a more viscous fluid is displaced by a less viscous (Saffman and Taylor $1958$).
+The mechanism of the instabilities may vary,
 %(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
-however it is still a function of relative mobility, gravity, dispersion, permeability differences.
-Moreover, in most cases interfacial tension is directly linked with the mobility ratio between the displaced and the displacing fluid.
+however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
+As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
+After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
+As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
+Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+Important parameter is the mobility (or viscosity) ratio.
+This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+\begin{equation}
+\lambda = \frac{K\;k_{\alpha}}{\mu}
+\label{eq:mobility-of-fluid}
+\end{equation}
 
@@
 
+% are based on domains that require high resolution static meshes to capture the development of the fingers 
+Even though some commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
+In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+
+The remainder of the paper is orgranised as follows.
+
+\KCnote{ this needs to be rephrased later -- Next section \citet{math-model} illustrates the model and the governing equations of immiscible and incompressible flow in porous media.
+The method and numerical formulations that describes the CVFEM follows, along with cases that demonstrate how the mesh adaptivity for simulation of viscous fingering is implemented.
+In the end, conclusions and final remarks of the work are discussed.--}
+
+\section{Mathematical Formulation}\label{section:math-model}
 %\medskip
 %\begin{comment}
+The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+\begin{equation}\label{e:darcy_eqn}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eqn} may be rewritten as:
+\begin{equation}
+  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+  \label{force-bal}
+\end{equation}
+
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+\label{E:darcy_eqn}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+ Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+\begin{equation}
+  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+  \label{E:darcy_ext}
+\end{equation}
+$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+
+The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\end{eqnarray}
+
+where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
+\medskip
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
+Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
+Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
+The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fig:fem_cv}
+\end{figure}
+
+\section{The Overlapping CVFEM formulation}
+
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
+However, FDM are often limited to relatively simple geometries
+%(with low grid quality and orientation) 
+representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
@@
 In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
+
+In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (Eq.\ref{cvfe_pressure}) while saturation is represented in node centered CV basis (Eq.\ref{cvfe_saturation}) control volume basis functions respectevely:
+
+\begin{equation}
+ p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+\label{cvfe_pressure}
+\end{equation}
+
+\begin{equation}
+ S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+\label{cvfe_saturation}
+\end{equation}
+
+where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
+The saturation equation is solved explicitly after solving for pressure at each time.
 
@@
 %\end{center}
+
+%\textcolor{red}{The impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
+The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
+%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
+%In addition, the study focused in flow instabilities determined by the viscosity ratio.
+In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
+Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
+High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
+Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
+Finally, conclusions are drawn in the final section.
+
+%Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
+Most commercial reservoir simulators use low-order finite-volume/differences methods based on structured grids.
+Considering the limitations of finite differences formulations, the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
+Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+
+%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
+%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
+%This is well suited for analysis of small scales such as core samples.
+\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
+)}.
+
+%Larger scale problems can be approached by upscaling techniques.
+These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
+These cases are normally resolved by stochastic representation of permeability and porosity fields.
+%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
+%There are several approaches to upscale solutions, while three common types are discussed.
+The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
+The $2^{nd}$ approach is called pseudoization.
+It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
+The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
+
+%The first approach is limited to low flow rates and very small heterogeneities.
+The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
+The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
+While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
+
+%\medskip
+\begin{comment}
+Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+%=======
+%\blue{The Introduction Section of a manuscript is often divided into 4 parts:
+%   \begin{enumerate}[(a)]
+%       \item Motivation for the work undertaken.
+What are the environmental, industrial and/or lab problems that this work will help tackling and/or solving (first and \underline{only one} paragraph)?
+%       \item Literature review: this should focus on the main topics directly related to the manuscript (as a rule-of-thumb, you should choose up to 5 key-words that can better represent the work and write \underline{concisely} about recent development on them, i.e., state-of-the-art).
+Length of literature review should be 3-10 paragraphs and focus on `recent' developments in the topics including strengths and weakness.
+This `list' of topics (with associated references and range of strengths and weakness) may lead to {\it an explicit statement of the current gap of knowledge on the field that the manuscript will address}.
+This last key sentence will naturally lead to the;
+%       \item Main aim and (list of) objective(s) of the work and how you intend to tackle the science problem (1 paragraph);
+%       \item Summary of the work (last paragraph). 
+%   \end{enumerate}
+%}
+
+%Detailed numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community for the past 50 years.
+This is mainly due to applications in oil and gas exploration, groundwater resources, underground coal gasification, geothermal power systems and, more recently, in carbon capture and storage (CCS) processes~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981, jiang_2011}.
+However, current porous media multiphase flow models are plagued with uncertainties associated with subsurface topology, lithostratigraphic heterogeneity and chemical and physical properties of subsurface fluids.
+Viscous fingering, a flow instability phenomenon that occurs at the interface of fluids with distinct viscosities, has a strong impact on the efficiency of both oil recovery and CO$_{2}$ trapping under reservoir conditions.
+
+%Accurate prediction of multiphase flow behaviour through realistic porous media domains is one of the main research challenges as \red{write about the main issues related to heterogeneity and link it with flow behaviour (2-5 sentences with references)}.
+
+%\red{\bf Write here \underline{3-6 literature review paragraphs based on} the chosen \underline{key-words} with the associated references. \underline{Be concise}!}
+
+%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account. 
+%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
+%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
+%This is well suited for analysis of small scales such as core samples.
+\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
+)}.
+
+%Larger scale problems can be approached by upscaling techniques.
+This technique which is usually employed to solve the problem fails for certain types of heterogeneity.
+These cases are normally resolved by stochastic representation of permeability and porosity fields.
+%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
+There are several approaches to upscale the solutions, while three common types are herein discussed.
+The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space renormalization methods.
+The $2^{nd}$ approach is called pseudoization.
+It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
+The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
+\red{Try to rewrite this paragraph bearing in mind: (a) Is upscaling relevant for this manuscript?
+(b) If positive how are they related ?
+As we haven't introduced the main aim (and objectives) of the manuscript, such relationship must be added clearly and smoothly here.}
+ %The first approach is limited to low flow rates and very small heterogeneity.
+The second approach overcomes these limitation but also posses drawbacks which include; availability of fine-grid simulation with suitable level of accuracy, dependence of the psuedo functions on rate, direction and grid specification.
+The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
+While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
+
+%\medskip
+Under specfic spatial conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers.
+This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??
+you are repeating the previous sentence ...)}.
+Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ??
+be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences\red{(Is this true ??
+if so give references.
+why is gravity or relperm relevant?
+dispersion...
+why?
+perm grad??)}.
+Moreover, in most cases \red{(refs?)} interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid \red{(How and why?)}.
+\medskip
+
+\blue{This last paragraph before aims and objectives (next paragraph) should be gentle transition from current state-of-the-art and this work.
+As a suggestion, the last paragraph should focus on a particular aspect of viscous fingering that may not be well-understood by the scientific community and that is addressed in the paper.
+For example, (a) impact of heterogeneity in the onset of fingering, (b) qualitative sensitivity study of viscosity ratio impact in the finger formation (based on analytical assessment studies), etc.}
+
+The main aim of this work is to numerically investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
+\red{\bf (try to develop it further; be more specific.
+Write this objective sentence/paragraph based on the paper's conclusions!)}.
+This study focuses on flow instabilities due to relatively large viscosity ratios.
+
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+\end{comment}
+
+\begin{comment}
+Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
+The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
+%(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
+however it is still a function of relative mobility, gravity, dispersion, permeability differences.
+Moreover, in most cases interfacial tension is directly linked with the mobility ratio between the displaced and the displacing fluid.
+
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
+
+In this paper, a control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
+In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
+Scalar fields (e.g., saturation, concentration, density, etc) are represented in the CV space.
+High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
+This formulation can achieve an exact representation of the Darcy force balance equations.
 
@@
 Finally, conclusions are drawn in the final section.
+\end{comment}
+
+\medskip
+\KCnote{Section~\ref{section:NumericalFormulation} summarises the numerical formulation used in this work.
+The model is validated against Bucklet-Leverett (incompressible fluid displacement in homogeneous domain) and traditional four-regions (cross-flow assessment due to permeability gradient) test-cases (Section~\ref{section:ModelValidation}).
+Viscous flow instabilities in heterogeneous porous media is numerically investigated in Section~\ref{section:ViscousInstabilities} following by final remarks.
 
@@
 %%%         %%%
+\section{Numerical Formulation}\label{section:NumericalFormulation}
+The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation.
+The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
+These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure.
+The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2_ele.png}
+\caption{Porosity $\phi$, and permeability K are associated to the elements.
+The velocity nodes are associated to the element corners and the mid-points of the element edges as described in fig.\ref{fig:fem_cv}; pressure nodes are associated to the corners of the elements.
+The three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.}
+\label{fig:fem_elem}
+\end{figure}
+
+Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
+The pressure, a key difference to other CVFE methods reported previously, allows the use of CVs that do not span multiple FEs.
+Hence each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+
+As we have to be consistent with \citet{jackson_2015} we assume that rick and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
+
+\begin{equation}
+\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (v_{\alpha}S_{\alpha})= q_{\alpha}
+\label{mass_balance}
+\end{equation}
+
+where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
+
+\begin{equation}
+\sum  S_{p}-1
+\label{saturation_constrain}
+\end{equation}
+
+The Eq.\ref{saturation_constrain}, is discretized in time and space following the approach of \citet{Jackson_2013} in which the time discretization is obtained using the $\theta$-method as implemented by %\citet{gomes_2013}.
+Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation, Eq.\ref{global_mass_balance},
+
+\begin{equation}
+\begin{aligned}
+\sum_{\alpha=1}^{N_{p}} {\int_{\Omega_{CVi}}} \! M_{i} \, \frac{\phi(S_{\alpha i}^{n+1})-(S_{\alpha i}^{n})}{\Delta t} dv + \\
+& \cap \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \\
+& \cap \;\int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; }=0
+\end{aligned}
+\label{global_mass_balance}
+\end{equation}
+
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, n is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to CN) and $1$ (corresponding to BE) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
+
 %%%         %%%
@@
 %%%         %%%
-\section{Numerical Formulation}\label{section:NumericalFormulation}
-In the OCVFEM formulation, a consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces is used with a recently developed family of $P_{m}DG-P_{n}$ tetrahedral element pairs.The new family of $PN_{n}{m}$ element pair was originally introduced.
-These element-pairs have a discontinuous $m^{th}$-order polynomial representation for velocity and a continuous representation for pressure of order {\it n}.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-This family of element pairs was originally introduced for geophysical fluid dynamics applications.
-In particular, the $P_{1}DG-P_{2}$ element pair was developed to represent the balance of geostrophic pressure and velocity without introducing spurious pressure modes.
-This element pair (Fig.~\ref{fig:2}) has a linear discontinuous basis function for velocity $\left(\text{P}_{1}\text{DG}\right)$ and a quadratic polynomial basis function for pressure $\left(\text{P}_{2}\right)$ which maintains $C_{\text{0}}$ continuity across element boundaries.
-Pressure nodes are located at the element corners and mid-points of the element-edges and control volumes are built around them.
-Scalar fields, such as saturation, density, temperature, species concentration are stored in control volume space.
-This family of finite element pairs, when used with the OCVFEM method presented here, is mass conservative and also exactly enforces the force balance represented by the multiphase Darcy equation.
-
-Let's assume a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions). Darcy's law for single phase flow can be extended for immiscible multiphase flow as,
-\begin{equation}
-  \mathbf{q}_{k} = -\frac{\mathcal{K}_{{r}_k}\left(S_{k}\right)\mathbf{K}}{\mu_{k}}\left( \nabla p_{k} - {\mathbf{s}_{u}}_{k} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{k} = \underline{\underline{\sigma}}_{k} {\bf u}_{k} = -\nabla p + \mathcal{S}_{u},
-\label{Eqn:DarcyEq}
-\end{equation}
-where $\mathbf{q}_{k}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{rk}\left(S_{k}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
- Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{k}= \mathbf{q}_{k}/S_{k}$, then we may rewrite Eq.(\ref{Eqn:DarcyExt0}),
-\begin{equation}
-  {\underline {\underline \sigma}}_{k} \mathbf{u}_{k} = - \nabla p + {\mathbf{s}_{u}}_{k},
-  \label{Eqn:DarcyExt}
-\end{equation}
-$\underline{\underline{\sigma}}_{k}=\mu_{k}S_{k}\left(\mathcal{K}_{rk}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-
-The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{k}S_{k}}{{\mathbf K}\mathcal{K}_{rk}}\right) {\mathbf u}_{k} = \underline{\underline{\sigma}}_{k} {\mathbf u}_{k} = -\nabla p + \mathcal{S}_{u,k},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{k} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{k}  S_{k}\right) =  \mathcal{S}_{cty,k},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,k}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{k}$ is saturation of the $k$-phase with the constraint of $\sum\limits_{k=1}^{\mathcal{N}_{p}} S_{k} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
-Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
+
 \section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
@@
 problem is given by:
+
 \begin{equation}
@@
 
+-------------------------------------------------------------------------------------------
+
+\begin{equation}
+B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+\label{force balance eq}
+\end{equation}
+
+\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+This system of equations can be rewritten to produce the pressure equation,
+
+\begin{equation}
+B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+\label{pressure eq}
+\end{equation}
+-------------------------------------------------------------------------------------------
+
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
+\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
+%\textcolor{red}{KC: could you add 1-2 short paragraphs on viscous instabilities ... focus on the phenomena rather than a literature review, that may take place in the Intro Section}
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
+Under this assumption, viscous fingering is no exception.
+It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
+This type of instability can be found across many research areas, disciplines and scales.
+Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.
+
+However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows.
+Those three mechanisms are shielding, spreading and tip-splitting.
+Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches.
+It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR).
+Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.
+
+Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
+The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
+This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
+
+%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.
+
+Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
+Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
+
+\begin{equation}
+ U = \frac{b^2}{12 \mu} \nabla p
+\end{equation}
+
+and the above equation can be re-arranged for 1D steady flow as,
+
+\begin{equation}
+ \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g 
+\end{equation}
+
+where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
+
+Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
+Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
+
+\begin{equation}
+\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
+\end{equation}
+
+If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\
+
+\begin{equation}
+U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
+\end{equation}
+
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
+\section{Model Validation}\label{section:ModelValidation}
+
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
+\subsection{Bucklet-Leverett Equation}\label{section:BuckletLeverettEquation}
+\textcolor{red}{JG: text and simulation of P1DGP2, P1DGP1DG fixed and adaptive mesh -- quantitative analysis}\\
+\textcolor{blue}{KC: do i have to mention something here?\\}
+
+Models of water and another fluid, such as air, flowing through a
+porous material, are used throughout science and
+engineering.  Furthermore, individual chemical and biological
+substances being transported in the fluids are often fundamentally
+important.
+The mathematical models for these processes take several forms: scalar nonlinear parabolic equations (Richards' equation), scalar hyperbolic equations (Buckley-Leverett equation), systems of degenerate nonlinear parabolic systems (two-phase and compositional flow), and free boundary problems (Muskat's model).
+These are macroscopic continuum models that govern the distribution and evolution of quantities that are {\em averages} of the densities, pressures, and velocities arising in classical fluid mechanics.
+The basis of porous media models in microscopic physics is, however, incomplete: many observed phenomena such as history-dependent behavior and various other scale effects have not been satisfactorily modeled, particularly for multiphase,
+multicomponent systems at the scale required for environmental
+studies.
+
+Modeling of two-phase immiscible flows in porous media is
+important for many industrial applications, such as oil recovery and carbon sequestration.
+Mathematical conceptualizations for such flows include the Buckley–Leverett model, which, in its simplest form, is represented by a nonlinear advection equation for the relative saturation of fluid phases.This equation models the two phase flows that arise oil-recovery problems and physically
+represents a mixture of oil and water through the porous medium.
+In conservative form the flux function for this
+problem is given by:
+
+\begin{equation}
+f(u) = \frac{u^2}{u^2 + \nu(1-u)^2}. \label{buckley}
+\end{equation}
+Here $\nu$ is viscosity ratio and $u$ represents the saturation of water and
+lies between $0$ and $1$.
+
+\subsection{Four Regions}\label{section:4Regions}
+\textcolor{blue}{KC \textcolor{red}{WR}: text and simulations -- qualitative analysis}\\
+
+Starting from the simplest case of simulations as describe in fig.
+\ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities.
+We inject fluid 1 across the left hand side of the formation and we are trying to displace the existing fluid 2.
+The front start to collapse and one main finger starts to appear.
+
+The behaviour as well as the prediction of the two different phase volume fractions can be qualitatively compared with bibliographic results.
+The two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
+As we inject fluid 1, at the first half of the formation the velocity magnitude is increasing while pressure drops gradually.
+This behaviour changes at the middle of the formation where there is the transition from one permeability zone to the other and the front has already collapsed forming the finger.
+
+From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced.
+There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig.
+\ref{fig:1} the phase volume fraction is constant.
+(\textcolor{blue}{KC: i think we can rephrase it better here.})
+
+Later, we introduce two versions of a second set of simulations consisted of the same number of regions (4) but with different formations and phase ratios as can be described in fig.
+\ref{fig:2} to fig.
+\ref{fig:subim7}.
+
+The initial and boundary condition regarding the inlet and outlet are the same.
+The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems.
+
+The main body of the formation (blue area) is where fluid 2 exists fig.
+\ref{fig:3}.
+Above the blue area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio.
+All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.
+
+Fluid 1 is again injected across the left hand side of the formation.
+In this case the value of mobility or \textit{viscosity ratio} is 10.
+Later on mobility ratios of different values will be introduced and compared.
+As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow.
+The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development.
+In fig.\ref{fig:2} and fig.\ref{fig:3}) the mesh deforms on time and on space and that allows the user to have an initial good qualitative approach regarding the development of the multiphase flow.
+In fig.
+\ref{fig:subim6} and fig.
+\ref{fig:subim7} the patterns of the multiphase flows for the phase 1 and phase 2 are described respectively.
+
+Based on the graph/plots for the second set of simulations we can get a initial approach and relation between the quantitative and qualitative outcome of our simulations.
+It is experimentally validated and is happening in this case that fingers will develop faster in areas where permeabilities are higher.
+This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid 1.
+Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists.
+After flowing through this area there is a balance (plateau) among the two faces on time fig.\ref{fig:subim8 middle}.
+Going higher in the formation, fig.\ref{fig:subim9 up} in the next zone just above the main body (blue area), there is an initial fluctuating decrease  of the velocity of the injected fluid which is driven by the different permeability value.
+At the top layer ref.\ref{fig:subim10 upper} of the formation there is a smooth increase of the injected fluid velocity magnitude which basically describes an overall and study development of the flow while just before the end collapses.
+
+Comparing the three plots we can see three different velocities to be developed which means that numerically the initial uniform front collapses.
+This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
+
+%%%         %%%
+%%% SECTION %%%
+%%%         %%%
+\section{Viscous Instabilities}\label{section:ViscousInstabilities}
+
+An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous 
+instabilities.
+An unfavourable - mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
+Although numerical investigations
+in the last few years have remarkably improved the physical 
+understanding of viscous fingering, some questions still remain 
+unanswered.\\
+
+First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance? Second, how 
+is a viscous instability affected by parameters including mobility 
+ratio and/or permeability variance. \textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
+
+\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
+\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}
+
+The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
+At the $n+1$ step those two equations mentioned above can be rewritten as,
+
+\begin{equation}
+M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+\label{mass balance eq}
+\end{equation}
+
 \begin{equation}
@@
 %------------------------KC------------------------------------------
-\textcolor{blue}{KC - i will try to have something on it as well}
-
-In the first set of simulations, saturation phase 2 is set to one throughout the whole domain ($S_2 = 1$) whereas fluid 1 is injected in the left boundary.
+
+\KCnote{In the first set of simulations, saturation phase 2 is set to one throughout the whole domain ($S_2 = 1$) whereas fluid 1 is injected in the left boundary.
 Starting from fig.\ref{fig:1st} and ending to fig.\ref{fig:4th} the total transition from setting the simulations and using the elements mentioned in previous section, as well as the intermediate results and the final stage of simulations are described.
@@
 \end{enumerate} 
+}
 
 \noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.
-
-%------------------------KC------------------------------------------
-
-\section{Achknowledgements}
-Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
-Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).
-Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.
 
@@
 
-\begin{figure}[ht!]
+\section{Results}\label{section:results}
+
+The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively.
+The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible.
+Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
+The domain is fully saturated with fluid $2$.
+At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
+Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is 5.
+The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
+Saturation is located at the pressure nodes.
+Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
+The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
+
+Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or mutliple fingers will be observed.
+
+This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
+Viscocity is a measure of resistance, therefore a frictional property.
+In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
+For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
+Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
+Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
+In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
+In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
+This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
+The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./Pics1/mr1_fixed/permeability.png}
+\caption{2D domain that consist of five regions with 5 different absolute permeabilities as these are represented with different colors.}
+\label{fig:5regions_domain}
+\end{center}
+\end{figure}
+
+\begin{figure}[H]
+\begin{center}
+\subfigure[MR1 fixed mesh start]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.png}
+}%
+\subfigure[MR10 fixed mesh start]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.png}
+}\\
+\subfigure[MR1 fixed mesh middle]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.png}
+}%
+\subfigure[MR10 fixed mesh middle]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.png}
+}\\
+\subfigure[MR1 fixed mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.png}
+}\\
+\subfigure[MR10 fixed mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.png}
+}\\
+\end{center}
+\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
+\label{fig:1testcase}
+\end{figure}
+
+Having already observed the significant growth of fingers comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}), the next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh test case (Fig.\ref{fig:2testcase}).
+
+\begin{figure}[H]
+\begin{center}
+\subfigure[MR10 fixed mesh start]{%
+\label{fig:first}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.png}
+}%
+\subfigure[MR10 adapt mesh start]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.png}
+}\\
+\subfigure[MR10 fixed mesh]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.png}
+}%
+\subfigure[MR10 adapt mesh]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.png}
+}\\
+\subfigure[MR10 fixed mesh]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.png}
+}%
+\subfigure[MR10 adapt mesh]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.png}
+}\\ 
+\subfigure[MR10 fixed mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.png}
+}\\
+\subfigure[MR10 adapt mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.png}
+}\\
+\end{center}
+\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.
+}
+\label{fig:2testcase}
+\end{figure}
+
+In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation.
+This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
+The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
+The major difference is located in the velocity fields as the presence of this extra inlet increases the flow at the top layers.
+
+\begin{figure}[H]
+\begin{center}
+\subfigure[MR10 fixed mesh start]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.png}
+}%
+\subfigure[MR10 fixed adapt start]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.png}
+}\\
+\subfigure[MR10 fixed mesh t=1500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.png}
+}%
+\subfigure[MR10 fixed adapt t=1500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.png}
+}\\
+\subfigure[MR10 fixed mesh t=7500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.png}
+}%
+\subfigure[MR10 fixed adapt t=7500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.png}
+}\\ 
+\subfigure[MR10 fixed mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.png}
+}\\
+\subfigure[MR10 fixed adapt end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.png}
+}\\
+\end{center}
+\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
+\label{fig:3testcase}
+\end{figure}
+
+At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
+Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
+
+\begin{figure}[H]
+%\begin{center}
+\centering
+\subfigure[MR100 fixed mesh t=500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
+}%
+\subfigure[MR100 fixed mesh t=1500]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
+}%
+\subfigure[MR100 fixed mesh t=3000]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
+}\\ 
+\subfigure[MR100 fixed mesh end]{%
+\label{fig:}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
+}\\
+%\end{center}
+\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase}
+\end{figure}
+
+\begin{figure}[H]
 \begin{center}
 \subfigure[MR1]{%
-\label{fig:first}
-\includegraphics[width=0.7\textwidth]{./Pics/MR1.png}
+\label{fig:}
+\includegraphics[width=0.6\textwidth]{./Pics/MR1.png}
 }%
 \subfigure[Recovery for MR1]{%
-\label{fig:second}
+\label{fig:}
 \includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
@@
 \subfigure[MR10]{%
-\label{fig:first}
-\includegraphics[width=0.7\textwidth]{./Pics/MR10.png}
+\label{fig:}
+\includegraphics[width=0.6\textwidth]{./Pics/MR10.png}
 }%
 \subfigure[Recovery for MR10]{%
-\label{fig:second}
+\label{fig:}
 \includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
@@
 \subfigure[MR100]{%
-\label{fig:first}
-\includegraphics[width=0.7\textwidth]{./Pics/MR100_100_start.png}
+\label{fig:}
+\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.png}
 }%
 \subfigure[Recovery for MR100]{%
-\label{fig:second}
+\label{fig:}
 \includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
@@
 \end{center}
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:6}
+\caption{Comparison of different MR's and their recovery rates.
+The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}.
+}
+\label{fig:recoveryrates}
 \end{figure}
+
+The macroscopic sweep efficiency is principally affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
+The permeability depends on the number, size and connectivity of the pores.
+This set of parameters is described by the $\sigma$ in the global mass balance equation (eq.\ref{global_mass_balance}).
+Including higher permeability zones also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
+As can been seen so far in all the test-case illustrated, main differences can be found on the way the shape of fingering is developed.
+Adaptive meshes tend to display fingering easier because of the enhcanced and stronger resolution in the interface.
+Inside the high permeability square region there is an acceleration of the flow with the maximum value of it at the interface as this starts to develops at the back of this region and onwards.
+At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
+The breaking point, also known as the point the two curves meet where beyond that water production will occur, is shifted towards the right as MR is increased.
+
+\KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
+
+\section{Achknowledgements}
+Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
+Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).
+Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.
 

### 2017-02-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\KCnote{Please reorganise the structure like the papers you read, and reference them!}
+%\KCnote{Please reorganise the structure like the papers you read, and reference them!}
 
@@
 Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Out of this mixed and complex formations, viscous flow instabilities can occur both within a single phase or when multiple phases flow through porous media.
 Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+Injections of low-viscosity, high-density fluid $1$ (e.g.
+water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow.
 This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.

### 2017-02-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow.
-This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+These phenomena have great importance during the oil and gas recovery operations in both mature and new fields.
+Starting from oil and gas migration of contaminants through groundwater is the opposite problem governed by the same principles.
+The most complicated of processes include fingering that wil loccur in multiphase and compositional flow.
+Underground coal gasification is another potential application but more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
 \medskip
-
 The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
-Particle methods, front-tracking methods \citep{univerdi_1992} but in particular volume of fluid (VOF) methods \citep{hirt_1981,rider_1998} are used to describe the afformentioned proeprties.
-In addition, finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-
-The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
-Considering the limitations of finite differences formulations the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
+Particle methods, front-tracking methods \citep{univerdi_1992} but in particular volume of fluid (VOF) methods \citep{hirt_1981,rider_1998} are used to describe the afformentioned properties.
+In addition, finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008}.
+This work will mainly focus on macroscale flow instabilities or \textit{viscous fingering} in heterogeneous resevoirs -or computational domains- and will compare the development of fingers using an alternative finite element method.
+In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+All these parameters are represented under one term in the global mass balance equation.
+
+\medskip
+The objective of this study is to investigate and accurately describe the behaviour of fingering in multiphase ($2$-phase) flows using a control volume finite element method (CVFEM).
+Considering the limitations of finite differences formulations the CVFE the model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
 Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
 
-Larger scale problems can be approached by upscaling techniques.
-These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
+\medskip
+The sections that follow include a summary of the main governing equations for multiphase compositional flow.
+The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of simulations results and the key conclusions.
+The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
+
+%These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
 These cases are normally resolved by stochastic representation of permeability and porosity fields.
@@
 
-\medskip
-Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
-These patterns are also described as flow instabilities or \textit{viscous fingering},  or most widely known as Saffman-Taylor instabilitises.
+%\medskip
+%Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
+%These patterns are also described as flow instabilities or \textit{viscous fingering},  or most widely known as Saffman-Taylor instabilitises.
 This phenomenon will occur during an unfavorable -mobility-ration displacement, when a more viscous fluid is displaced by a less viscous (Saffman and Taylor $1958$).
@@
 %(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
-however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+%however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
 In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+
+\KCnote{ - - to be putted in the mathematical formulation as intro - - 
 Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
@@
 
- Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
-
-% are based on domains that require high resolution static meshes to capture the development of the fingers 
-Even though some commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
-In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-
-The remainder of the paper is orgranised as follows.
-
-\KCnote{ this needs to be rephrased later -- Next section \citet{math-model} illustrates the model and the governing equations of immiscible and incompressible flow in porous media.
-The method and numerical formulations that describes the CVFEM follows, along with cases that demonstrate how the mesh adaptivity for simulation of viscous fingering is implemented.
-In the end, conclusions and final remarks of the work are discussed.--}
+}
 
@@
 
+\KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
+\KCnote{ -to be placed in results-
+ Even though some commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
+In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.}
+
 \begin{figure}[H]
@@
 
-\KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
-
 \section{Achknowledgements}

### 2017-02-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}
-
 \end{keyword}
@@
 \clearpage
+
 %%%         %%%
@@
 %%%         %%%
-
-%\KCnote{Please reorganise the structure like the papers you read, and reference them!}
-
 \section{Introduction}\label{section:Intro}
@@
 
-\KCnote{ - - to be putted in the mathematical formulation as intro - - 
-Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
-As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
-After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
-In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
-Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
-Important parameter is the mobility (or viscosity) ratio.
-This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-\begin{equation}
-\lambda = \frac{K\;k_{\alpha}}{\mu}
-\label{eq:mobility-of-fluid}
-\end{equation}
-
-}
-
-\section{Mathematical Formulation}\label{section:math-model}
-%\medskip
-%\begin{comment}
-The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-\begin{equation}\label{e:darcy_eqn}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eqn} may be rewritten as:
-\begin{equation}
-  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-  \label{force-bal}
-\end{equation}
-
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
-
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-\label{E:darcy_eqn}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
- Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-\begin{equation}
-  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-  \label{E:darcy_ext}
-\end{equation}
-$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-
-The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
-Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fig:fem_cv}
-\end{figure}
-
-\section{The Overlapping CVFEM formulation}
-
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
-However, FDM are often limited to relatively simple geometries
-%(with low grid quality and orientation) 
-representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
-
-Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
-In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
-
-In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (Eq.\ref{cvfe_pressure}) while saturation is represented in node centered CV basis (Eq.\ref{cvfe_saturation}) control volume basis functions respectevely:
-
-\begin{equation}
- p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-\label{cvfe_pressure}
-\end{equation}
-
-\begin{equation}
- S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-\label{cvfe_saturation}
-\end{equation}
-
-where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
-The saturation equation is solved explicitly after solving for pressure at each time.
-
-Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
-Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-%\end{comment}
-
-%\medskip 
-%\begin{center}
-%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
-%\end{center}
-
-%\textcolor{red}{The impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
-The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
-The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
-%In addition, the study focused in flow instabilities determined by the viscosity ratio.
-In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
-High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
-Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
-Finally, conclusions are drawn in the final section.
-
-%Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
-This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-
-The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
-Most commercial reservoir simulators use low-order finite-volume/differences methods based on structured grids.
-Considering the limitations of finite differences formulations, the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
-
-%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
-%This is well suited for analysis of small scales such as core samples.
-\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
-)}.
-
-%Larger scale problems can be approached by upscaling techniques.
-These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
-These cases are normally resolved by stochastic representation of permeability and porosity fields.
-%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
-%There are several approaches to upscale solutions, while three common types are discussed.
-The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
-The $2^{nd}$ approach is called pseudoization.
-It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
-The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-
-%The first approach is limited to low flow rates and very small heterogeneities.
-The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
-The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
-While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
-
-%\medskip
-\begin{comment}
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
-%=======
 %\blue{The Introduction Section of a manuscript is often divided into 4 parts:
@@
 %}
+
+\section{Problem set-up}\label{problem_set_up}
+
+Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
+Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities.
+This will change the mobility contrast between two phases for a given \textit{viscosity} ratio.
+Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities.
+
+\subsection{Mathematical Formulation}\label{section:math-model}
+%\medskip
+
+\KCnote{ - - to be putted in the mathematical formulation as intro - - 
+Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
+As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
+After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
+As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
+Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+Important parameter is the mobility (or viscosity) ratio.
+This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+\begin{equation}
+\lambda = \frac{K\;k_{\alpha}}{\mu}
+\label{eq:mobility-of-fluid}
+\end{equation}
+
+}
+
+The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+\begin{equation}\label{e:darcy_eqn}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eqn} may be rewritten as:
+\begin{equation}
+  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+  \label{force-bal}
+\end{equation}
+
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+\label{E:darcy_eqn}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+ Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+\begin{equation}
+  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+  \label{E:darcy_ext}
+\end{equation}
+$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+
+The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\end{eqnarray}
+
+where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
+\medskip
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
+Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
+Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
+The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fig:fem_cv}
+\end{figure}
+
+\section{The Overlapping CVFEM formulation}
+
+Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
+However, FDM are often limited to relatively simple geometries
+%(with low grid quality and orientation) 
+representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+
+Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
+In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
+
+In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (Eq.\ref{cvfe_pressure}) while saturation is represented in node centered CV basis (Eq.\ref{cvfe_saturation}) control volume basis functions respectevely:
+
+\begin{equation}
+ p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+\label{cvfe_pressure}
+\end{equation}
+
+\begin{equation}
+ S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+\label{cvfe_saturation}
+\end{equation}
+
+where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
+The saturation equation is solved explicitly after solving for pressure at each time.
+
+Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
+Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+%\medskip 
+%\begin{center}
+%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
+%\end{center}
+
+%\textcolor{red}{The impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
+The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
+%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
+%In addition, the study focused in flow instabilities determined by the viscosity ratio.
+In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
+Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
+High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
+Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
+Finally, conclusions are drawn in the final section.
+
+%Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
+Most commercial reservoir simulators use low-order finite-volume/differences methods based on structured grids.
+Considering the limitations of finite differences formulations, the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
+Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+
+%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
+%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
+%This is well suited for analysis of small scales such as core samples.
+\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
+)}.
+
+%Larger scale problems can be approached by upscaling techniques.
+These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
+These cases are normally resolved by stochastic representation of permeability and porosity fields.
+%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
+%There are several approaches to upscale solutions, while three common types are discussed.
+The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
+The $2^{nd}$ approach is called pseudoization.
+It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
+The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
+
+%The first approach is limited to low flow rates and very small heterogeneities.
+The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
+The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
+While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
+
+%\medskip
+\begin{comment}
+Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
 

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities.
+In this paper, the test-cases are also based on the discontinuous Galerkin (DG) method to simulate viscous fingering.
+Roughly speaking, DG-method combines advantages of classical finite volume and finite element methods.
+
+\subsection{Numerical Formulation}
+
+Flows in porous media are expressed by the Darcy's law and the saturation equation.
+At this stage the control volume finite element method is used (CVFEM).
+Darcy's law for immiscible multi-phase flow may be written in the form:
+\begin{equation}\label{e:darcy_eq}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+\begin{equation}
+  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+  \label{force-bal}
+\end{equation}
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
+
+In matrix form, Eqn.~\ref{force-bal} is: %~\ref{force-semi-disc} is: 
+\begin{equation}
+  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
+\end{equation}
+where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are defined as:
+\begin{eqnarray}
+    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
+    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+\end{eqnarray}
+
+The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
+
+Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+\begin{equation}
+  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+  \label{e:force_balance}
+\end{equation}
+
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
+
+The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\label{e:darcy_eq}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+\label{E:darcy_eqn}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+ Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+\begin{equation}
+  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+  \label{E:darcy_ext}
+\end{equation}
+$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+
+The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\end{eqnarray}
+
+where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
+\medskip
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
+Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
+Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
+The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fig:fem_cv}
+\end{figure}
 
@@
 }
-
-The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-\begin{equation}\label{e:darcy_eqn}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eqn} may be rewritten as:
-\begin{equation}
-  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-  \label{force-bal}
-\end{equation}
-
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
-
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-\label{E:darcy_eqn}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
- Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-\begin{equation}
-  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-  \label{E:darcy_ext}
-\end{equation}
-$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-
-The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
-Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fig:fem_cv}
-\end{figure}
 

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \section{Introduction}\label{section:Intro}
-
+\medskip
 Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
@@
 
-%These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
-These cases are normally resolved by stochastic representation of permeability and porosity fields.
-There are several approaches to upscale solutions, while three common types are discussed.
-The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
-The $2^{nd}$ approach is called pseudoization.
-It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
-The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-Problems start to rise when complex flow patterns will appear during the recovery of hydrocarbons triggered by heterogeneities.
-%The first approach is limited to low flow rates and very small heterogeneities.
-The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
-The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
-While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
-
-%\JGnote{As a rule of thumb, when you are introducing a paragraph, the very first sentence needs to give the reader a clue of either linkage with previous paragraphs or linkage with the main subject(s).}
-
-%\medskip
-%Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
-%These patterns are also described as flow instabilities or \textit{viscous fingering},  or most widely known as Saffman-Taylor instabilitises.
-This phenomenon will occur during an unfavorable -mobility-ration displacement, when a more viscous fluid is displaced by a less viscous (Saffman and Taylor $1958$).
-The mechanism of the instabilities may vary,
-%(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
-%however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-
-%\blue{The Introduction Section of a manuscript is often divided into 4 parts:
-%   \begin{enumerate}[(a)]
-%       \item Motivation for the work undertaken.
-What are the environmental, industrial and/or lab problems that this work will help tackling and/or solving (first and \underline{only one} paragraph)?
-%       \item Literature review: this should focus on the main topics directly related to the manuscript (as a rule-of-thumb, you should choose up to 5 key-words that can better represent the work and write \underline{concisely} about recent development on them, i.e., state-of-the-art).
-Length of literature review should be 3-10 paragraphs and focus on `recent' developments in the topics including strengths and weakness.
-This `list' of topics (with associated references and range of strengths and weakness) may lead to {\it an explicit statement of the current gap of knowledge on the field that the manuscript will address}.
-This last key sentence will naturally lead to the;
-%       \item Main aim and (list of) objective(s) of the work and how you intend to tackle the science problem (1 paragraph);
-%       \item Summary of the work (last paragraph). 
-%   \end{enumerate}
-%}
-
 \section{Problem set-up}\label{problem_set_up}      
-
 Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
@@
 
-\subsection{Numerical Formulation}
-
-Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-\begin{equation}\label{e:darcy_eq}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-\begin{equation}
-  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-  \label{force-bal}
-\end{equation}
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-In matrix form, Eqn.~\ref{force-bal} is: %~\ref{force-semi-disc} is: 
-\begin{equation}
-  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-\end{equation}
-where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are defined as:
-\begin{eqnarray}
-    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-\end{eqnarray}
-
-The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-
-Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-\begin{equation}
-  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-  \label{e:force_balance}
-\end{equation}
-
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-Darcy's law for single phase flow can be extended (from Eq.\ref{e:darcy_eqn}) for immiscible multiphase flow to Eq.\ref{E:darcy_eqn} below,
-
-The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\label{e:darcy_eq}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-\label{E:darcy_eqn}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
- Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-\begin{equation}
-  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-  \label{E:darcy_ext}
-\end{equation}
-$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-
-The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
+\subsection{Mathematical Formulation}\label{section:math-model}
 \medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation -- Eqn.~\ref{eqn:darcy_eqn}.
-Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fig:fem_cv}
-\end{figure}
-
-\subsection{Mathematical Formulation}\label{section:math-model}
-%\medskip
-
 \KCnote{ - - to be putted in the mathematical formulation as intro - - 
@@
 
-\section{The Overlapping CVFEM formulation}
+\subsection{Numerical Formulation}
+\medskip
+Flows in porous media are expressed by the Darcy's law and the saturation equation.
+At this stage the control volume finite element method is used (CVFEM).
+Darcy's law for immiscible multi-phase flow may be written in the form:
+\begin{equation}\label{e:darcy_eq}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+\begin{equation}
+  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+  \label{e:force_bal}
+\end{equation}
+where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
+
+In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
+\begin{equation}
+  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
+\end{equation}
+where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are defined as:
+\begin{eqnarray}
+    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
+    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+\end{eqnarray}
+
+The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
+%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_balance}
+%\end{equation}
+
+\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+
+%%%%%%%%%%%%%%%
+\begin{comment}
+The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\label{e:darcy_eq}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+\begin{equation}
+  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+\label{E:darcy_eqn}
+\end{equation}
+where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+ Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+\begin{equation}
+  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+  \label{E:darcy_ext}
+\end{equation}
+$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+\end{comment}
+
+\noindent The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\end{eqnarray}
+where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
+\subsection{The Overlapping CVFEM formulation}
+\medskip
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (eq.~\ref{e:darcy_eq}).
+Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
+Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
+The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fig:fem_cv}
+\end{figure}
 
@@
 
-%\medskip 
-%\begin{center}
-%\JGnote{WR: small summary of the paper -- 3 or 4 punchy sentences %followed by description of the remaining of the paper}
-%\end{center}
-
-%\textcolor{red}{The impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
-The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
-The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
-%In addition, the study focused in flow instabilities determined by the viscosity ratio.
-In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
-High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
-Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
-Finally, conclusions are drawn in the final section.
-
-%Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
-This is mainly due to the importance of the oil and gas recovery operations, groundwater exploration, underground coal gasification, and more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-
 The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
@@
 
-%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
-%This is well suited for analysis of small scales such as core samples.
-\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
-)}.
-
-%Larger scale problems can be approached by upscaling techniques.
-These are techniques which are usually employed to solve problems that fail because of certain types of heterogeneities.
-These cases are normally resolved by stochastic representation of permeability and porosity fields.
-%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
-%There are several approaches to upscale solutions, while three common types are discussed.
-The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space re-normalization methods.
-The $2^{nd}$ approach is called pseudoization.
-It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
-The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-
-%The first approach is limited to low flow rates and very small heterogeneities.
-The second approach overcomes these limitations but also posses drawbacks such us, unavailability of fine-grid simulation with suitable level of accuracy, dependence of the pseudo functions on rate, direction and grid specification.
-The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
-While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
-
-%\medskip
 \begin{comment}
@@
 
-%Detailed numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community for the past 50 years.
-This is mainly due to applications in oil and gas exploration, groundwater resources, underground coal gasification, geothermal power systems and, more recently, in carbon capture and storage (CCS) processes~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981, jiang_2011}.
-However, current porous media multiphase flow models are plagued with uncertainties associated with subsurface topology, lithostratigraphic heterogeneity and chemical and physical properties of subsurface fluids.
-Viscous fingering, a flow instability phenomenon that occurs at the interface of fluids with distinct viscosities, has a strong impact on the efficiency of both oil recovery and CO$_{2}$ trapping under reservoir conditions.
-
-%Accurate prediction of multiphase flow behaviour through realistic porous media domains is one of the main research challenges as \red{write about the main issues related to heterogeneity and link it with flow behaviour (2-5 sentences with references)}.
-
-%\red{\bf Write here \underline{3-6 literature review paragraphs based on} the chosen \underline{key-words} with the associated references. \underline{Be concise}!}
-
-%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account. 
-%Both permeability and porosity are important parameters in the equations used for numerical simulation of multiphase flow in porous media.\red{(what was the objective of this sentence?)}  %Heterogeniety of permeability and porosity is a product of the medium's formation process %-- deposition and diagenesis -- and exists at different scales.
-%To tackle these problems the continuum approach, in a microscopic level, can be applied to a representative elementary Volume (REV) to describe the spatial variation in parameters such as the porosity and permeability~\citep{bastian_phd1999}.
-%This is well suited for analysis of small scales such as core samples.
-\red{(These sentences are not linked with the previous sentences, also what is the objective of them?
-)}.
-
-%Larger scale problems can be approached by upscaling techniques.
-This technique which is usually employed to solve the problem fails for certain types of heterogeneity.
-These cases are normally resolved by stochastic representation of permeability and porosity fields.
-%Various upscaling techniques, including analytical and numerical, have been introduced in the literature to calculate upscaled flow properties.
-There are several approaches to upscale the solutions, while three common types are herein discussed.
-The $1^{st}$ assumes capillary equilibrium and calculates effective relative permeability using a suitable technique, such as numerical methods, percolation methods and space renormalization methods.
-The $2^{nd}$ approach is called pseudoization.
-It generates a psuedo relative permeability by matching immiscible displacement simulation of a coarse-grid to the output of fine-grid simulations.
-The $3^{rd}$ approach involves direct calculation of relative permeability from displacement experiments.~\citep{johnson_1959, jones_1978}.
-\red{Try to rewrite this paragraph bearing in mind: (a) Is upscaling relevant for this manuscript?
-(b) If positive how are they related ?
-As we haven't introduced the main aim (and objectives) of the manuscript, such relationship must be added clearly and smoothly here.}
- %The first approach is limited to low flow rates and very small heterogeneity.
-The second approach overcomes these limitation but also posses drawbacks which include; availability of fine-grid simulation with suitable level of accuracy, dependence of the psuedo functions on rate, direction and grid specification.
-The experimental data from the third approach is only suitable for a small class of scenarios.~\citep{Chang_1994}.
-While  non-uniform permeability and porosity may be easy to deal with at a microscopic scale for porous media flow equations, it presents a lot of challenges at a meso/field scale, which is required for reservoir simulations.
-
-%\medskip
 Under specfic spatial conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers.
@@
 
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
 \section{Viscous Instabilities}\label{section:ViscousInstabilities}
 
-An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous 
-instabilities.
-An unfavourable - mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
-Although numerical investigations
-in the last few years have remarkably improved the physical 
-understanding of viscous fingering, some questions still remain 
-unanswered.\\
-
-First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance? Second, how 
-is a viscous instability affected by parameters including mobility 
-ratio and/or permeability variance. \textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
+An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
+An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
+Although numerical investigations in the last few years have remarkably improved the physical understanding of viscous fingering, some questions still remain unanswered.
+
+First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance?
+Second, how is a viscous instability affected by parameters including mobility ratio and/or permeability variance.
+\textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
 

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}\label{section:Intro}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Problem set-up}\label{problem_set_up}      
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Numerical Formulation}
@@
 \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .The objective of this work is to investigate and accurately describe the behaviour of fluid instabilities in compositional flows using a control volume finite element method (CVFEM).
-Most commercial reservoir simulators use low-order finite-volume/differences methods based on structured grids.
-Considering the limitations of finite differences formulations, the CVFE The model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
 
@@
 
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Numerical Formulation}\label{section:NumericalFormulation}
@@
 The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  
 \section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
@@
 
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\section{Model Validation}\label{section:ModelValidation}
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\subsection{Bucklet-Leverett Equation}\label{section:BuckletLeverettEquation}
-\textcolor{red}{JG: text and simulation of P1DGP2, P1DGP1DG fixed and adaptive mesh -- quantitative analysis}\\
-\textcolor{blue}{KC: do i have to mention something here?\\}
-
-Models of water and another fluid, such as air, flowing through a
-porous material, are used throughout science and
-engineering.  Furthermore, individual chemical and biological
-substances being transported in the fluids are often fundamentally
-important.
-The mathematical models for these processes take several forms: scalar nonlinear parabolic equations (Richards' equation), scalar hyperbolic equations (Buckley-Leverett equation), systems of degenerate nonlinear parabolic systems (two-phase and compositional flow), and free boundary problems (Muskat's model).
-These are macroscopic continuum models that govern the distribution and evolution of quantities that are {\em averages} of the densities, pressures, and velocities arising in classical fluid mechanics.
-The basis of porous media models in microscopic physics is, however, incomplete: many observed phenomena such as history-dependent behavior and various other scale effects have not been satisfactorily modeled, particularly for multiphase,
-multicomponent systems at the scale required for environmental
-studies.
-
-Modeling of two-phase immiscible flows in porous media is
-important for many industrial applications, such as oil recovery and carbon sequestration.
-Mathematical conceptualizations for such flows include the Buckley–Leverett model, which, in its simplest form, is represented by a nonlinear advection equation for the relative saturation of fluid phases.This equation models the two phase flows that arise oil-recovery problems and physically
-represents a mixture of oil and water through the porous medium.
-In conservative form the flux function for this
-problem is given by:
-
-\begin{equation}
-f(u) = \frac{u^2}{u^2 + \nu(1-u)^2}. \label{buckley}
-\end{equation}
-Here $\nu$ is viscosity ratio and $u$ represents the saturation of water and
-lies between $0$ and $1$.
-
-\subsection{Four Regions}\label{section:4Regions}
-\textcolor{blue}{KC \textcolor{red}{WR}: text and simulations -- qualitative analysis}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Viscous Instabilities}\label{section:ViscousInstabilities}
+
+An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
+An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
+Although numerical investigations in the last few years have remarkably improved the physical understanding of viscous fingering, some questions still remain unanswered.
+
+First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance?
+Second, how is a viscous instability affected by parameters including mobility ratio and/or permeability variance.
+\textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
+
+\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
+\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}
+
+The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
+At the $n+1$ step those two equations mentioned above can be rewritten as,
+
+\begin{equation}
+M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+\label{mass balance eq}
+\end{equation}
+
+-------------------------------------------------------------------------------------------
+
+\begin{equation}
+B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+\label{force balance eq}
+\end{equation}
+
+\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+This system of equations can be rewritten to produce the pressure equation,
+
+\begin{equation}
+B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+\label{pressure eq}
+\end{equation}
+-------------------------------------------------------------------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
+\medskip
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
+Under this assumption, viscous fingering is no exception.
+It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
+This type of instability can be found across many research areas, disciplines and scales.
+Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.
+
+However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows.
+Those three mechanisms are shielding, spreading and tip-splitting.
+Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches.
+It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR).
+Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.
+
+Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
+The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
+This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
+
+%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.
+
+Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
+Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
+
+\begin{equation}
+ U = \frac{b^2}{12 \mu} \nabla p
+\end{equation}
+
+and the above equation can be re-arranged for 1D steady flow as,
+
+\begin{equation}
+ \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g 
+\end{equation}
+
+where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
+
+Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
+Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
+
+\begin{equation}
+\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
+\end{equation}
+
+If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\
+
+\begin{equation}
+U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
-
-\section{Viscous Instabilities}\label{section:ViscousInstabilities}
-
-An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
-An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
-Although numerical investigations in the last few years have remarkably improved the physical understanding of viscous fingering, some questions still remain unanswered.
-
-First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance?
-Second, how is a viscous instability affected by parameters including mobility ratio and/or permeability variance.
-\textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
-
-\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
-\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}
-
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-\begin{equation}
-M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{mass balance eq}
-\end{equation}
-
--------------------------------------------------------------------------------------------
-
-\begin{equation}
-B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-\label{force balance eq}
-\end{equation}
-
-\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-\begin{equation}
-B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-\label{pressure eq}
-\end{equation}
--------------------------------------------------------------------------------------------
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-%\textcolor{red}{KC: could you add 1-2 short paragraphs on viscous instabilities ... focus on the phenomena rather than a literature review, that may take place in the Intro Section}
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
-Under this assumption, viscous fingering is no exception.
-It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
-This type of instability can be found across many research areas, disciplines and scales.
-Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.
-
-However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows.
-Those three mechanisms are shielding, spreading and tip-splitting.
-Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches.
-It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR).
-Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.
-
-Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
-The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
-This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
-
-%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.
-
-Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-\begin{equation}
- U = \frac{b^2}{12 \mu} \nabla p
-\end{equation}
-
-and the above equation can be re-arranged for 1D steady flow as,
-
-\begin{equation}
- \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g 
-\end{equation}
-
-where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-\begin{equation}
-\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-\end{equation}
-
-If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\
-
-\begin{equation}
-U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-\end{equation}
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\section{Model Validation}\label{section:ModelValidation}
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\subsection{Bucklet-Leverett Equation}\label{section:BuckletLeverettEquation}
-\textcolor{red}{JG: text and simulation of P1DGP2, P1DGP1DG fixed and adaptive mesh -- quantitative analysis}\\
-\textcolor{blue}{KC: do i have to mention something here?\\}
-
-Models of water and another fluid, such as air, flowing through a
-porous material, are used throughout science and
-engineering.  Furthermore, individual chemical and biological
-substances being transported in the fluids are often fundamentally
-important.
-The mathematical models for these processes take several forms: scalar nonlinear parabolic equations (Richards' equation), scalar hyperbolic equations (Buckley-Leverett equation), systems of degenerate nonlinear parabolic systems (two-phase and compositional flow), and free boundary problems (Muskat's model).
-These are macroscopic continuum models that govern the distribution and evolution of quantities that are {\em averages} of the densities, pressures, and velocities arising in classical fluid mechanics.
-The basis of porous media models in microscopic physics is, however, incomplete: many observed phenomena such as history-dependent behavior and various other scale effects have not been satisfactorily modeled, particularly for multiphase,
-multicomponent systems at the scale required for environmental
-studies.
-
-Modeling of two-phase immiscible flows in porous media is
-important for many industrial applications, such as oil recovery and carbon sequestration.
-Mathematical conceptualizations for such flows include the Buckley–Leverett model, which, in its simplest form, is represented by a nonlinear advection equation for the relative saturation of fluid phases.This equation models the two phase flows that arise oil-recovery problems and physically
-represents a mixture of oil and water through the porous medium.
-In conservative form the flux function for this
-problem is given by:
-
-\begin{equation}
-f(u) = \frac{u^2}{u^2 + \nu(1-u)^2}. \label{buckley}
-\end{equation}
-Here $\nu$ is viscosity ratio and $u$ represents the saturation of water and
-lies between $0$ and $1$.
-
-\subsection{Four Regions}\label{section:4Regions}
-\textcolor{blue}{KC \textcolor{red}{WR}: text and simulations -- qualitative analysis}\\
-
-Starting from the simplest case of simulations as describe in fig.
-\ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities.
-We inject fluid 1 across the left hand side of the formation and we are trying to displace the existing fluid 2.
-The front start to collapse and one main finger starts to appear.
-
-The behaviour as well as the prediction of the two different phase volume fractions can be qualitatively compared with bibliographic results.
-The two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
-As we inject fluid 1, at the first half of the formation the velocity magnitude is increasing while pressure drops gradually.
-This behaviour changes at the middle of the formation where there is the transition from one permeability zone to the other and the front has already collapsed forming the finger.
-
-From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced.
-There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig.
-\ref{fig:1} the phase volume fraction is constant.
-(\textcolor{blue}{KC: i think we can rephrase it better here.})
-
-Later, we introduce two versions of a second set of simulations consisted of the same number of regions (4) but with different formations and phase ratios as can be described in fig.
-\ref{fig:2} to fig.
-\ref{fig:subim7}.
-
-The initial and boundary condition regarding the inlet and outlet are the same.
-The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems.
-
-The main body of the formation (blue area) is where fluid 2 exists fig.
-\ref{fig:3}.
-Above the blue area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio.
-All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.
-
-Fluid 1 is again injected across the left hand side of the formation.
-In this case the value of mobility or \textit{viscosity ratio} is 10.
-Later on mobility ratios of different values will be introduced and compared.
-As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow.
-The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development.
-In fig.\ref{fig:2} and fig.\ref{fig:3}) the mesh deforms on time and on space and that allows the user to have an initial good qualitative approach regarding the development of the multiphase flow.
-In fig.
-\ref{fig:subim6} and fig.
-\ref{fig:subim7} the patterns of the multiphase flows for the phase 1 and phase 2 are described respectively.
-
-Based on the graph/plots for the second set of simulations we can get a initial approach and relation between the quantitative and qualitative outcome of our simulations.
-It is experimentally validated and is happening in this case that fingers will develop faster in areas where permeabilities are higher.
-This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid 1.
-Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists.
-After flowing through this area there is a balance (plateau) among the two faces on time fig.\ref{fig:subim8 middle}.
-Going higher in the formation, fig.\ref{fig:subim9 up} in the next zone just above the main body (blue area), there is an initial fluctuating decrease  of the velocity of the injected fluid which is driven by the different permeability value.
-At the top layer ref.\ref{fig:subim10 upper} of the formation there is a smooth increase of the injected fluid velocity magnitude which basically describes an overall and study development of the flow while just before the end collapses.
-
-Comparing the three plots we can see three different velocities to be developed which means that numerically the initial uniform front collapses.
-This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\section{Viscous Instabilities}\label{section:ViscousInstabilities}
-
-An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous 
-instabilities.
-An unfavourable - mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
-Although numerical investigations
-in the last few years have remarkably improved the physical 
-understanding of viscous fingering, some questions still remain 
-unanswered.\\
-
-First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance? Second, how 
-is a viscous instability affected by parameters including mobility 
-ratio and/or permeability variance. \textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
-
-\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
-\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}
-
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-\begin{equation}
-M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{mass balance eq}
-\end{equation}
-
-\begin{equation}
-B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-\label{force balance eq}
-\end{equation}
-
-\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-\begin{equation}
-B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-\label{pressure eq}
-\end{equation}
-
-The computationally demanding effort to solve the pressure matrix equation (arising from the discontinuous FEM formulation) is achieved using a multigrid-like approach.
-
-The original geometry of the system is an orthogonal 2D domain where the  heterogeneity is imposed by introducing 4 distinct regions of four regions of different absolute permeabilities (K) as can being seen in fig.\ref{fig:1} and fig.
-\ref{fig:subim6}.
-
-The Richard equation (non-linear advection equation) for relative saturation fluid phases representing two phases immiscible flows in porous media has been simulated.
-The fluid $1$ or \textit{injected fluid} is injected a a velocity of $u_1 \phi = 1$.
-On the outlet, or right hand side boundary, the pressure level is set to zero and all the remaining boundary are naturally applied.
-All the simulations discussed in this section used the overlapping control volume FEM with a piecewise linear variation of the velocity with each element and quadratic pressure ($P_1 DG-P_2$).
-Saturation is collocated at the  pressure nodes and although it is calculated using a CV formulation, a FEM interpolation is used to form the higher order fluxes.
-There is no flow across the lower and upper boundaries (no-slip conditions) and the initial velocity of the fluid 2 or displaced fluid is set to zero, while the gravity is assumed negligible.
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\subsection{Impact of Permeability Field}\label{section:PermeabilityAnalysis}
-
-The higher the permeability of a medium, the easier it is for flow to propagate through it.
-Therefore, fluid will flow faster through the higher permeability region.
-Hence, in Case 1, it is expected that the injected fluid will flow fastest in the top layer which has the highest permeability.
-The second layer's permeability is higher than that of the bottom layer, so also, its front should be expected to move ahead of that of the bottom layer.
-The high permeability zone within the lower layer may result in some interesting flow characteristics at the horizontal flow boundary (the top and bottom boundary) depending on the difference between the two permeabilities.
-If this difference is sufficiently large enough, the fluid from the low permeability region will tend to cross into the high permeability region and flow forward from there.
-This will result in a region of reduced flow at these boundaries just beyond the deviation from normal flow and may also cause a stationary point at these boundaries within the flow.
-
-\medskip
-\textcolor{red}{WR: results }
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\subsection{Investigation of Viscosity (Mobility? I think its better if i keep as Mobility Ratio) Ratio}\label{section:MobilityAnalysis}
-\textcolor{red}{KC: would you like to add a paragraph on the expected impact of MR in the flow?}\\
-\medskip
-\textcolor{red}{WR and KC: results}\\
-%------------------------KC------------------------------------------
-
-During the simulations performed the Viscous fingering phenomenon has been observed.
-Viscous fingering  is highly related with the mobility, which describes how easily a fluid moves into a porous media and can be expressed through the mobility ratio (\textit{MR}).
-The ratio between the mobility of the displacing phase to the mobility of the displaced.
-
-It generally accepted \textcolor{red}{can we say that...?} ( Saffman and Taylor, $1958$, Chouke et al., $1959$, Peters,$1979$ and Homsy,$1987$) that the higher the mobility ratio the easier is for viscous fingering to appear and more specific, for fingers to start to develop and grow.
-In the simulations above an $MR=10$ is used.
-This ration combined with the use of unstructured adaptive mesh makes the fingers more visible, easier to detect them.
-For cases where the is less than 5, ($MR \le 5$) we expect no difference as there is no significant impact.
-In the extreme case of $MR=1$ we can clearly see the relation between finger development and the zones of different porosity.
-%------------------------KC------------------------------------------
-
-\pagebreak
-
-%%%         %%%
-%%% SECTION %%%
-%%%         %%%
-\section{Final Remarks}\label{section:conclusions}
-%\textcolor{red}{KC and WR: do you want to have a bash on this ?}\\ 
-%------------------------KC------------------------------------------
 

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \section{Introduction}\label{section:Intro}
@@
 
-\subsection{Mathematical Formulation}\label{section:math-model}
-\medskip
-\KCnote{ - - to be putted in the mathematical formulation as intro - - 
-Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
-As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
-After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
-In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
-Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
-Important parameter is the mobility (or viscosity) ratio.
-This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-\begin{equation}
-\lambda = \frac{K\;k_{\alpha}}{\mu}
-\label{eq:mobility-of-fluid}
-\end{equation}
-
-}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 $S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
+The main equations that will be used along with the following OCVFEM techique can be summarised below:
+
+\begin{equation}
+M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+\label{e:mas_bal}
+\end{equation}
+
+\begin{equation}
+B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+\label{e:force_bal}
+\end{equation}
+
+\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+This system of equations can be rewritten to produce the pressure equation,
+
+\begin{equation}
+B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+\label{e:pressure_eq}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \subsection{The Overlapping CVFEM formulation}
@@
 The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-%\textcolor{red}{KC: could you add 1-2 short paragraphs on viscous instabilities ... focus on the phenomena rather than a literature review, that may take place in the Intro Section}
+
+\KCnote{ - - to be putted in the mathematical formulation as intro - - 
+Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
+As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
+After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
+As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
+Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+Important parameter is the mobility (or viscosity) ratio.
+This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+\begin{equation}
+\lambda = \frac{K\;k_{\alpha}}{\mu}
+\label{eq:mobility-of-fluid}
+\end{equation}
+
+}
+
 As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
@@
 
-First, how satisfactory are the effects of modelled-observed viscous fingering on displacement performance?
-Second, how is a viscous instability affected by parameters including mobility ratio and/or permeability variance.
-\textcolor{red}{ KC: something came to me right now, And third, can the viscous fingering be scaled?}
-
-\subsection{Designing the Numerical Experiment}\label{section:NumericalExperiment}
-\textcolor{red}{WR: could add here a paragraph describing the original geometry and simulation set up (initial and boundary conditions)and maybe a table with the differences between the diff numerical experiments.}
-
 The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
@@
 M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{mass balance eq}
+\label{mas_bal}
 \end{equation}

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
+\KCnote{In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations}.
+\KCnote{The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
+So far, the results illustrate that the displacing fluid tends to flow easier towards the zones with higher values of permeability (spatial acceleration / deceleration of flow – fingers formation).
+It can also be seen that finger like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
+This behaviour is triggered by the permeability contrast among layers.
+As can be seen from Fig........
+the higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
+Also, the higher the viscosity ratio, more to the right the breakpoint is shifted, in the time axis.
+The increased viscosity ratio increases the computational cost and requires the decrease of the solution's time-step.
+Both the geometrical domain and the development of the flow, as can be seen in Fig........
+follow the linear tip-splitting finger behaviour.
+In addition properties such as porosity and saturation can be readily up-scaled using statistical methods.%, like the python function that was introduced in the second case of the simulations, that provides fast and reasonable values.
+To conclude, up-scaling or averaging the geological model can assist in running reservoir models faster and as close as possible to fine geological model.}
 
@@
 $S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-The main equations that will be used along with the following OCVFEM techique can be summarised below:
+The main equations that will be used along with the following OCVFEM techique can be summarised below.
+The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
+At the $n+1$ step those two equations mentioned above can be rewritten as,
 
@@
 M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{e:mas_bal}
+\label{e:mass_bal}
 \end{equation}
@@
 \begin{comment}
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+%Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
 However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
@@
 
-Under specfic spatial conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers.
+%Under specfic spatial conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers.
 This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??
@@
 Moreover, in most cases \red{(refs?)} interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid \red{(How and why?)}.
-\medskip
-
-\blue{This last paragraph before aims and objectives (next paragraph) should be gentle transition from current state-of-the-art and this work.
+%\medskip
+%\blue{This last paragraph before aims and objectives (next paragraph) should be gentle transition from current state-of-the-art and this work.
 As a suggestion, the last paragraph should focus on a particular aspect of viscous fingering that may not be well-understood by the scientific community and that is addressed in the paper.
@@
 
-The main aim of this work is to numerically investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
+%The main aim of this work is to numerically investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
 \red{\bf (try to develop it further; be more specific.
@@
 
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+%\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
 Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-\end{comment}
-
-\begin{comment}
-Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
-The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
+
+%Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
+%The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
 %(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
-however it is still a function of relative mobility, gravity, dispersion, permeability differences.
+%however it is still a function of relative mobility, gravity, dispersion, permeability differences.
 Moreover, in most cases interfacial tension is directly linked with the mobility ratio between the displaced and the displacing fluid.
 
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
-
-In this paper, a control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
+%Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
+
+%In this paper, a control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
 In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
@@
 
-In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
+%In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
 The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
 The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
-In addition, the study focused in flow instabilities determined by the viscosity ratio.
+%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
+%In addition, the study focused in flow instabilities determined by the viscosity ratio.
 In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
@@
 
-\medskip
-\KCnote{Section~\ref{section:NumericalFormulation} summarises the numerical formulation used in this work.
-The model is validated against Bucklet-Leverett (incompressible fluid displacement in homogeneous domain) and traditional four-regions (cross-flow assessment due to permeability gradient) test-cases (Section~\ref{section:ModelValidation}).
-Viscous flow instabilities in heterogeneous porous media is numerically investigated in Section~\ref{section:ViscousInstabilities} following by final remarks.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Formulation}\label{section:NumericalFormulation}
+\KCnote{\section{Numerical Formulation}\label{section:NumericalFormulation}
 The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation.
@@
 The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
-
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-
-\KCnote{ - - to be putted in the mathematical formulation as intro - - 
+\medskip
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
+Under this assumption, viscous fingering is no exception.
+It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
+This type of instability can be found across many research areas, disciplines and scales.
+Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems,  such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
+The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
+This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
+
+An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
+An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
 Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
@@
 
-}
-
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
-Under this assumption, viscous fingering is no exception.
-It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
-This type of instability can be found across many research areas, disciplines and scales.
-Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.
-
-However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows.
-Those three mechanisms are shielding, spreading and tip-splitting.
-Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches.
-It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR).
-Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.
-
-Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
-The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
-This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
-
-%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.
-
-Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
 The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
@@
 where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-
 Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
@@
 
-If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\
+If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Viscous Instabilities}\label{section:ViscousInstabilities}
-
-An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
-An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
-Although numerical investigations in the last few years have remarkably improved the physical understanding of viscous fingering, some questions still remain unanswered.
-
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-\begin{equation}
-M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{mas_bal}
-\end{equation}
-
--------------------------------------------------------------------------------------------
-
-\begin{equation}
-B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-\label{force balance eq}
-\end{equation}
-
-\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-\begin{equation}
-B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-\label{pressure eq}
-\end{equation}
--------------------------------------------------------------------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-\medskip
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
-Under this assumption, viscous fingering is no exception.
-It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
-This type of instability can be found across many research areas, disciplines and scales.
-Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems.
-
-However, one feature is common in the examples mentioned above and this is related with the mechanisms that govern these flows.
-Those three mechanisms are shielding, spreading and tip-splitting.
-Tip-splitting, Fig.~\ref{fig:shielding}(a), happens when a finger becomes unstable and splits into two branches.
-It is a function of Peclet number \textit{Pe}, which depends on the mobility ratio (MR).
-Spreading can be found mainly in porous medium when the flow velocity is not large and finally shielding, Fig.~\ref{fig:shielding}(b), occurs when one finger grows much faster than other fingers.
-
-Viscous fingering has been found to influence industrial processes such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
-The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
-This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
-
-%(Oil \& Gas fields and pollutant dispersion in aquifers) the main %principle as well as mechanism has the same pattern.The difference in %large systems or Oil \& Gas fields, in particular for the Oil Industry %lies in the fact that the extraction and production of Hydrocarbons is %initially energy and financially crucial as well as computationally %expensive regarding the numerical modelling and simulation methods.
-
-Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-\begin{equation}
- U = \frac{b^2}{12 \mu} \nabla p
-\end{equation}
-
-and the above equation can be re-arranged for 1D steady flow as,
-
-\begin{equation}
- \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g 
-\end{equation}
-
-where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-\begin{equation}
-\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-\end{equation}
-
-If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.\\
-
-\begin{equation}
-U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-\end{equation}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv}
+\bibliography{references}
+
+\pagebreak
+\clearpage
+
+%\listoftables
+%\pagebreak
+%\input{Manuscript_Table}
+
+\pagebreak
+\clearpage
+
+\listoffigures
+
+\begin{figure}[h]
+\makebox[\textwidth]{%
+\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_perm}%
+\hfill    
+\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_mesh}%
+}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2_plot}%
+}%
+\caption{ Caption 1}
+\label{fig:1}
+\end{figure}
+
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
+%\caption{Caption 1}
+%\label{fig:subim1}
+%\end{center}
+
+%\begin{center}
+%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
+%\caption{Caption 1}
+%\label{fig:subim1}
+%\end{center}
+
+%\begin{center}
+%\centering
+%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
+%\caption{Caption 3}
+%\label{fig:subim3}
+%\end{center}
+
+%\caption{Caption for this figure with two images}
+%\label{fig:image1}
+%\end{figure}
+%\pagebreak
+%\clearpage
+
+\begin{figure}[h]
+
+\begin{center}
+\centering
+\includegraphics[width=0.75\linewidth, height=5cm]{./Pics/P1DG-P2_element_type} 
+\caption{Caption 2}
+\label{fig:2}
+\end{center}
+
+\begin{center}
+\centering
+\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_125_mesh} 
+\caption{Caption 3}
+\label{fig:3}
+\end{center}
+
+\begin{center}
+\centering
+\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_100_mesh}
+\caption{Caption 4}
+\label{fig:4}
+\end{center}
+
+%\caption{Caption for this figure with two images}
+\label{fig:image2}
+\end{figure}
+\pagebreak
+\clearpage
+
+\begin{landscape}
+\begin{figure}[ht!]
+\begin{center}
+\subfigure[MR100, at the beginning of the simulations]{%
+\label{fig:1st}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
+}%
+\subfigure[MR100, at the middle of the simulation]{%
+\label{fig:2nd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
+}\\
+\subfigure[MR100, Phase 1 Volume fraction]{%
+\label{fig:3rd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
+}%
+\subfigure[MR100, Phase 2 Volume fraction]{%
+\label{fig:4th}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
+}\\
+\caption{Comparison of different MR's and their recovery rates}
+\label{fig:5}
+\end{center}
+\end{figure}
+\end{landscape}
+
+\pagebreak
+\clearpage
+%\input{article_figure1}
+%\input{Manuscript_Figure1}
+
+\section{Results}\label{section:results}
 
@@
 This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
-
-\KCnote{In the first set of simulations, saturation phase 2 is set to one throughout the whole domain ($S_2 = 1$) whereas fluid 1 is injected in the left boundary.
-Starting from fig.\ref{fig:1st} and ending to fig.\ref{fig:4th} the total transition from setting the simulations and using the elements mentioned in previous section, as well as the intermediate results and the final stage of simulations are described.
-
-The number of elements used under the fixed coarse mesh approach is almost $5000$ elements and it is less than the instructed and adaptive mesh  grids which is around $20500$ elements while the max number has reached up to $24000$.
-The later mesh can focus the resolution inthe saturation front.
-In fig.\ref{fig:4} it can be seen that the high permeability square-region, where most of the fingers are formed are most noticeable.
-
-In the case of both saturated/unsaturated porous media the square region is initially saturated with the fluid 1.
-The pattern of the initial inlet front is almost similar with the case mentioned above.
-The behaviour in the two top layers interface is initially inverse exponential followed by a direct decrease in the saturation front due to fingering.
-
-We proposed a surface-based approach to reservoir modelling.
-The new overlapping control volume finite element method for multi-fluid flows is based upon an dual consistent velocity-pressure representation in CV and FEM spaces introducing the element type family of $P_n DG P_{n+1}$.
-The aim of the paper is to extend apply the formulation to to multiphase flows in heterogeneous porous media.
-The above method is beneficial for two reasons.
-Firstly, numerical dispersion is reduced by adaptively refining the grid on time and space as the displacement front is evolving.
-Secondly the multi-scale heterogeneity can be better captured using the above mesh formation that can be adjusted to complex reservoir geometries over a wide variety of length-scales, without required the petrophysical properties to be rescaled each time that the mesh is changed.\\
-
-\textcolor{blue}{The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
-So far, the results illustrate that the displacing fluid tends to flow easier towards the zones with higher values of permeability (spatial acceleration / deceleration of flow – fingers formation).
-It can also be seen that finger like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
-This behaviour is triggered by the permeability contrast among layers.
-As can be seen from Fig........
-the higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
-Also, the higher the viscosity ratio, more to the right the breakpoint is shifted, in the time axis.
-The increased viscosity ratio increases the computational cost and requires the decrease of the solution's time-step.
-Both the geometrical domain and the development of the flow, as can be seen in Fig........
-follow the linear tip-splitting finger behaviour.
-In addition properties such as porosity and saturation can be readily up-scaled using statistical methods.%, like the python function that was introduced in the second case of the simulations, that provides fast and reasonable values.
-To conclude, up-scaling or averaging the geological model can assist in running reservoir models faster and as close as possible to fine geological model.}\\
-
-In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages:
-
-\begin{enumerate}
-\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
-%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
-
-\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability.
-\item[3.] Finger-like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
-This behaviour is triggered by the permeability contrast among layers.
-\item[4.] The higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
-\item[5.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
-At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
-\item[6.] Both the geometrical domain and the development of the flow follow the linear tip-splitting finger behaviour.
-\item[7.] Properties such as porosity and saturation can be readily up-scaled using statistical methods while production simulations run directly on the geological model without the need to upscale.
-
-\end{enumerate} 
-}
-
-\noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.
-
-%\textcolor{blue}{KC - Is it valid to include that part of this work has been published in international conferences and being awarded.}
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% References with bibTeX database:
-\bibliographystyle{elsarticle-harv}
-\bibliography{references}
-
-\pagebreak
-\clearpage
-
-%\listoftables
-%\pagebreak
-%\input{Manuscript_Table}
-
-\pagebreak
-\clearpage
-
-\listoffigures
-
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_perm}%
-\hfill    
-\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_mesh}%
-}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2_plot}%
-}%
-\caption{ Caption 1}
-\label{fig:1}
-\end{figure}
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\centering
-%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
-%\caption{Caption 3}
-%\label{fig:subim3}
-%\end{center}
-
-%\caption{Caption for this figure with two images}
-%\label{fig:image1}
-%\end{figure}
-%\pagebreak
-%\clearpage
-
-\begin{figure}[h]
-
-\begin{center}
-\centering
-\includegraphics[width=0.75\linewidth, height=5cm]{./Pics/P1DG-P2_element_type} 
-\caption{Caption 2}
-\label{fig:2}
-\end{center}
-
-\begin{center}
-\centering
-\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_125_mesh} 
-\caption{Caption 3}
-\label{fig:3}
-\end{center}
-
-\begin{center}
-\centering
-\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_100_mesh}
-\caption{Caption 4}
-\label{fig:4}
-\end{center}
-
-%\caption{Caption for this figure with two images}
-\label{fig:image2}
-\end{figure}
-\pagebreak
-\clearpage
-
-\begin{landscape}
-\begin{figure}[ht!]
-\begin{center}
-\subfigure[MR100, at the beginning of the simulations]{%
-\label{fig:1st}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
-}%
-\subfigure[MR100, at the middle of the simulation]{%
-\label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
-}\\
-\subfigure[MR100, Phase 1 Volume fraction]{%
-\label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
-}%
-\subfigure[MR100, Phase 2 Volume fraction]{%
-\label{fig:4th}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
-}\\
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:5}
-\end{center}
-\end{figure}
-\end{landscape}
-
-\pagebreak
-\clearpage
-%\input{article_figure1}
-%\input{Manuscript_Figure1}
-
-\section{Results}\label{section:results}
 
@@
 Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.}
+\KCnote{In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
+\begin{enumerate}
+\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
+%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
+%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
+%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
+
+\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability.
+\item[3.] Finger-like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
+This behaviour is triggered by the permeability contrast among layers.
+\item[4.] The higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
+\item[5.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
+At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
+\item[6.] Both the geometrical domain and the development of the flow follow the linear tip-splitting finger behaviour.
+\item[7.] Properties such as porosity and saturation can be readily up-scaled using statistical methods while production simulations run directly on the geological model without the need to upscale.
+
+\end{enumerate} 
+}
+}
+
+\noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.
 

### 2017-02-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\KCnote{\section{Numerical Formulation}\label{section:NumericalFormulation}
+\section{Numerical Formulation}\label{section:NumericalFormulation}
 The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation.
@@
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2_ele.png}
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
 \caption{Porosity $\phi$, and permeability K are associated to the elements.
@@
 
-\begin{equation}
-\begin{aligned}
-\sum_{\alpha=1}^{N_{p}} {\int_{\Omega_{CVi}}} \! M_{i} \, \frac{\phi(S_{\alpha i}^{n+1})-(S_{\alpha i}^{n})}{\Delta t} dv + \\
-& \cap \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \\
-& \cap \;\int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; }=0
-\end{aligned}
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \, \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \nonumber\\
+ &&  \int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; =0
 \label{global_mass_balance}
-\end{equation}
+\end{eqnarray}
 
@@
 The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
-}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
 }
-}
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \begin{center}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 %\begin{center}
@@
 
-\begin{figure}[H]
+\begin{figure}[h] 
 \begin{center}

### 2017-02-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_perm}%
-\hfill    
-\includegraphics[width=0.49\textwidth]{./Pics/2b2_P1DGP2_mesh}%
-}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2_plot}%
-}%
-\caption{ Caption 1}
-\label{fig:1}
-\end{figure}
-
 %\begin{figure}[h]
@@
 
-\begin{figure}[h]
-
-\begin{center}
-\centering
-\includegraphics[width=0.75\linewidth, height=5cm]{./Pics/P1DG-P2_element_type} 
-\caption{Caption 2}
-\label{fig:2}
-\end{center}
-
-\begin{center}
-\centering
-\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_125_mesh} 
-\caption{Caption 3}
-\label{fig:3}
-\end{center}
-
-\begin{center}
-\centering
-\includegraphics[width=0.8\linewidth, height=7cm]{./Pics/4r_po_adapt_fine_100_mesh}
-\caption{Caption 4}
-\label{fig:4}
-\end{center}
-
-%\caption{Caption for this figure with two images}
-\label{fig:image2}
-\end{figure}
 \pagebreak
@@
 
-Starting from the simplest case of simulations as describe in fig.
+Starting from a simple case as this is described in fig.
 \ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities.
-We inject fluid 1 across the left hand side of the formation and we are trying to displace the existing fluid 2.
-The front start to collapse and one main finger starts to appear.
+The domain is fully saturated with fluid $2$.
+We inject fluid $1$ across the left hand side of the formation and we are trying to displace the existing fluid $2$.
+The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ and a main finger starts to appear.
 
-The behaviour as well as the prediction of the two different phase volume fractions can be qualitatively compared with bibliographic results.
-The two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
-As we inject fluid 1, at the first half of the formation the velocity magnitude is increasing while pressure drops gradually.
-This behaviour changes at the middle of the formation where there is the transition from one permeability zone to the other and the front has already collapsed forming the finger.
+\begin{figure}[h]
+\makebox[\textwidth]{%
+\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm}%
+\hfill    
+\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh}%
+}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot}%
+}%
+\caption{A simple test-case of a square region with four subregions.
+The permeability contrast is constant.
+The mesh is unstructured but fixed.
+After the injection of fluid $1$ at a velocity of u = 1, the velocity magnitude drops to zero.
+The main finger starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.
+The mechanism that still drives the phenomenon is the pressure difference and the tip-splitting pattern can be more profound.
+}
+\label{fig:square}
+\end{figure}
 
+In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
 From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced.
 There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig.
-\ref{fig:1} the phase volume fraction is constant.
-(\textcolor{blue}{KC: i think we can rephrase it better here.})
-
-Later, we introduce two versions of a second set of simulations consisted of the same number of regions (4) but with different formations and phase ratios as can be described in fig.
-\ref{fig:2} to fig.
-\ref{fig:subim7}.
+\ref{fig:square}, the phase volume fraction is constant.
 
 The initial and boundary condition regarding the inlet and outlet are the same.
+One more test-case (fig.\ref{fig:testcase}), to verify the finger formation in a simple but same set-up is also illustrated.
+
+\begin{figure}[h]
+\begin{center}
+\subfigure[MR1 fixed mesh start aspect ratio 2]{%
+\label{fig:}
+\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.png}
+}%
+\subfigure[MR1 fixed mesh end aspect ratio 2]{%
+\label{fig:}
+\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.png}
+}\\
+\end{center}
+\caption{In this tes-case fixed and unstructured mesh is used.
+The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious.
+Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
+\label{fig:testcase}
+\end{figure}
+
  The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems.
+A more detailed description of the element type and the formation that will be used in the next set of test cases follows.
 
-The main body of the formation (blue area) is where fluid 2 exists fig.
-\ref{fig:3}.
-Above the blue area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio.
+%{./Pics/P1DG-P2_element_type} 
+%{./Pics/4r_po_adapt_fine_125_mesh} 
+%{./Pics/4r_po_adapt_fine_100_mesh}
+
+\begin{figure}[h]
+\begin{center}
+\subfigure[The $P_{1}DGP_{2}$ element type]{%
+\label{fig:}
+\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type}
+}%
+\subfigure[The map of permeabilities]{%
+\label{fig:}
+\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh}
+}\\
+\end{center}
+\caption{(a) represents the element type of $P_{1}DGP_{2}$ as well as where each of the parameters is located and calculated on the element type.
+(b) describes the permeability map as this is introduced throught a python script during the set-up of simulations.
+In general, the main body of the formation is the blue area that is fully saturated with fluid $2$.
+Above the main (blue colored) area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio.
 All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.
+}
+\label{fig:elem_type_perm_map}
+\end{figure}
 
 Fluid 1 is again injected across the left hand side of the formation.
-In this case the value of mobility or \textit{viscosity ratio} is 10.
-Later on mobility ratios of different values will be introduced and compared.
+Mobility ratios of different values will be introduced and compared.
 As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow.
 The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development.
-In fig.\ref{fig:2} and fig.\ref{fig:3}) the mesh deforms on time and on space and that allows the user to have an initial good qualitative approach regarding the development of the multiphase flow.
 In fig.
-\ref{fig:subim6} and fig.
-\ref{fig:subim7} the patterns of the multiphase flows for the phase 1 and phase 2 are described respectively.
+\ref{fig:simple_case} the simple case of a domain with uniform permeability is displayed.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.6\textwidth]{./Pics1/phase_vol_frac_unif_perm.pdf}
+\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
+\label{fig:simple_case}
+\end{center}
+\end{figure}
 
@@
 This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively.
@@
 \noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.5\textwidth]{./Pics1/mr1_fixed/permeability.png}
-\caption{2D domain that consist of five regions with 5 different absolute permeabilities as these are represented with different colors.}
-\label{fig:5regions_domain}
-\end{center}
-\end{figure}
 

### 2017-02-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\begin{landscape}
-\begin{figure}[ht!]
-\begin{center}
-\subfigure[MR100, at the beginning of the simulations]{%
-\label{fig:1st}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
-}%
-\subfigure[MR100, at the middle of the simulation]{%
-\label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
-}\\
-\subfigure[MR100, Phase 1 Volume fraction]{%
-\label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
-}%
-\subfigure[MR100, Phase 2 Volume fraction]{%
-\label{fig:4th}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
-}\\
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:5}
-\end{center}
-\end{figure}
-\end{landscape}
-
 \pagebreak
@@
 
-Fluid 1 is again injected across the left hand side of the formation.
+Fluid $1$ is again injected across the left hand side of the formation.
 Mobility ratios of different values will be introduced and compared.
@@
 
-Based on the graph/plots for the second set of simulations we can get a initial approach and relation between the quantitative and qualitative outcome of our simulations.
-It is experimentally validated and is happening in this case that fingers will develop faster in areas where permeabilities are higher.
-This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid 1.
-Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists.
+Based on these two case so far an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
+Fingers will develop faster in areas where permeabilities are higher.
+This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
+
+%Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists.
 After flowing through this area there is a balance (plateau) among the two faces on time fig.\ref{fig:subim8 middle}.
@@
 
-Comparing the three plots we can see three different velocities to be developed which means that numerically the initial uniform front collapses.
-This behaviour can be described on the following chapter, where the explanation of viscous instabilities is given.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{comment}
+\begin{landscape}
+\begin{figure}[ht!]
+\begin{center}
+\subfigure[MR100, at the beginning of the simulations]{%
+\label{fig:1st}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
+}%
+\subfigure[MR100, at the middle of the simulation]{%
+\label{fig:2nd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
+}\\
+\subfigure[MR100, Phase 1 Volume fraction]{%
+\label{fig:3rd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
+}%
+\subfigure[MR100, Phase 2 Volume fraction]{%
+\label{fig:4th}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
+}\\
+\caption{Comparison of different MR's and their recovery rates}
+\label{fig:5}
+\end{center}
+\end{figure}
+\end{landscape}
+\end{comment}
+
 \section{Achknowledgements}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
...

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Problem set-up}\label{problem_set_up}      
+\section{Governing equations and numerical scheme}\label{equations_scheme}      
 Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
...

@@
 \end{equation}
-where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors are defined as:
+where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
 \begin{eqnarray}
@@
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
-\caption{Porosity $\phi$, and permeability K are associated to the elements.
-The velocity nodes are associated to the element corners and the mid-points of the element edges as described in fig.\ref{fig:fem_cv}; pressure nodes are associated to the corners of the elements.
-The three CVs fit into a $2$D element.
+\includegraphics[width=.5\textwidth]{./Pics/element_n.png}
+\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
+The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
 Saturation and saturation-dependent variables are stored CV-wise.}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
...

@@
 
-In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
+\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
 \begin{equation}
@@
     && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+\label{v_and_p}
 \end{eqnarray}
 
-The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+\noindent The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
 Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
@@
 
-In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (Eq.\ref{cvfe_pressure}) while saturation is represented in node centered CV basis (Eq.\ref{cvfe_saturation}) control volume basis functions respectevely:
+In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (see Eq.\ref{v_and_p}, also known as shape functions, $\underline{\bf v}$ and $\underline{\bf p}$) while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
 
+\begin{comment}
 \begin{equation}
@@
 \end{equation}
+\end{comment}
 
-where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
-The saturation equation is solved explicitly after solving for pressure at each time.
+%where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
 

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning up

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Numerical Formulation}\label{section:NumericalFormulation}
-The method presented here builds on that reported by \citet{jackson_2015} is known as OCVFEM formulation.
+%\section{Numerical Formulation}\label{section:NumericalFormulation}
+The method presented here builds on that reported by \citet{jackson_2015, salinas2015} is known as OCVFEM formulation.
 The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
@@
 Starting from a simple case as this is described in fig.
-\ref{fig:1}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities.
+\ref{fig:square}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities (blue and red shaded square areas).
 The domain is fully saturated with fluid $2$.

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning up

@@
 An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
+This scheme ha already been describe in detail by \citet{pavlidis2016}.
 An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
@@
 Important parameter is the mobility (or viscosity) ratio.
-This is given by Eqn.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
 

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning up

@@
 \begin{abstract} 
-Numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
+\KCnote{Numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
 Viscous fingering, a fluid instability can be a major concern regarding enhanced oil-recovery methods (EOR).
@@
 The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
-We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
+We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.}
 \KCnote{In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
@@
 \KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
-\KCnote{ -to be placed in results-
- Even though some commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
-In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.}
-\KCnote{In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
-\begin{enumerate}
-\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
-%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
-
-\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability.
-\item[3.] Finger-like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
-This behaviour is triggered by the permeability contrast among layers.
-\item[4.] The higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
-\item[5.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
-At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
-\item[6.] Both the geometrical domain and the development of the flow follow the linear tip-splitting finger behaviour.
-\item[7.] Properties such as porosity and saturation can be readily up-scaled using statistical methods while production simulations run directly on the geological model without the need to upscale.
-
-\end{enumerate} 
-}
-
-\noindent Even thought this model is promising there is still work to be done since it is not yet a complete product. Further work is required to develop the surface-based modelling algorithms.
 
@@
 
+Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
+In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced byt the use of OCVFEM and families of elements.
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in both upstream and downstream operations.
+Even thought this model is promising there is still work to be done since it is not yet a complete product.
+Further work is required to develop the surface-based modelling algorithms.
+
+In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
+\begin{enumerate}
+\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
+%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
+%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
+%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
+
+\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domain.
+The higher the mobility ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
+\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
+At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
+The domain used in these test-cases the development of the flow follow the linear tip-splitting finger behaviour.
+\item[4.] Properties such as porosity and saturation can be readily up-scaled using statistical methods, can be included in the element boundaries,  while production simulations run directly on the geological model without the need to upscale.
+\end{enumerate}
+
 \begin{comment}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
new pics vel magn

@@
 The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields as the presence of this extra inlet increases the flow at the top layers.
+The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers.
 
@@
 
+\begin{figure}
+\centering 
+%\begin{minipage}{1.0\textwidth}%
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.png}%
+%\end{minipage}%
+\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+Reading from top to bottom, the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
+for adaptive mesh (middle) and finally the velocity magnitude for adaptive mesh with double inlet (bottom) is compard.
+The main difference between the top plot and the middle one is the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
+While there is a significant difference between the top and middle plot, at the bottom one, the impact of a second injection interval can be seen from the slope and the rate that the velocity magnitude is changing.
+}
+\label{fig:vel_magn}
+\end{figure}
+
 \section{Achknowledgements}

### 2017-02-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
new pics vel magn

@@
 \caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-Reading from top to bottom, the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh (middle) and finally the velocity magnitude for adaptive mesh with double inlet (bottom) is compard.
-The main difference between the top plot and the middle one is the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
-While there is a significant difference between the top and middle plot, at the bottom one, the impact of a second injection interval can be seen from the slope and the rate that the velocity magnitude is changing.
-}
+Reading from top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
+for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom).
+The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
+While there
+is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
 \label{fig:vel_magn}

### 2017-02-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates in .tex and .bib

@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-  Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods.
-\blue{(choose key-words that do represent the contents of the paper.
-State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}
+ Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods.
 \end{keyword}
@@
 At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
-Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is 5.
+Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
 The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
@@
 The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers.
+At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
+Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
+Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of ﬁngers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
+A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
+No ﬁngers could be observed due to mesh coarseness (ﬁngers were ob-served in ﬁner uniform and adaptive meshes).
 
@@
 \end{figure}
-
-At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
-Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
 

### 2017-02-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates in .tex and .bib

@@
 
-\begin{figure}[h]
+\begin{figure}
+\centering 
+%\begin{minipage}{1.0\textwidth}%
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.png}%
+%\end{minipage}%
+\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
+for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
+The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
+While there
+is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
+\label{fig:vel_magn}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}%
+\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase}
+\end{figure}
+
+%\begin{figure}[h]
 %\begin{center}
-\centering
-\subfigure[MR100 fixed mesh t=500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
-}%
-\subfigure[MR100 fixed mesh t=1500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
-}%
-\subfigure[MR100 fixed mesh t=3000]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
-}\\ 
-\subfigure[MR100 fixed mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
-}\\
+%\centering
+%\subfigure[MR100 fixed mesh t=500]{%
+%\label{fig:}
+%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
+%}%
+%\subfigure[MR100 fixed mesh t=1500]{%
+%\label{fig:}
+%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
+%}%
+%\subfigure[MR100 fixed mesh t=3000]{%
+%\label{fig:}
+%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
+%}\\ 
+%\subfigure[MR100 fixed mesh end]{%
+%\label{fig:}
+%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
+%}\\
 %\end{center}
-\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-\label{fig:4testcase}
-\end{figure}
+%\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+%\label{fig:4testcase}
+%\end{figure}
 
@@
 
-\begin{figure}
-\centering 
-%\begin{minipage}{1.0\textwidth}%
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.png}%
-%\end{minipage}%
-\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-Reading from top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom).
-The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
-While there
-is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn}
-\end{figure}
-
 \section{Achknowledgements}

### 2017-02-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates in .tex and .bib
cleaning up

@@
 
-%% References with bibTeX database:
-\bibliographystyle{elsarticle-harv}
-\bibliography{references}
-
 \pagebreak
@@
 \clearpage
-
-\listoffigures
 
@@
 
+\begin{figure}
+\centering 
+%\begin{minipage}{1.0\textwidth}%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.png}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.png}%
+%\end{minipage}%
+\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+From top to bottom,these graphs describe the velocity magnitude for single inlet with adaptive mesh coarse (top), adaptive and fine (middle) and adaptive and refined as these simulations are shown in fig.\ref{fig:2testcase}.
+The main difference between the top, middle and bottom graph lies in the first part and how the vleocity magnitude is builded up as a relation of phase $1$ volume fraction and lower.}
+\label{fig:vel_magn1}
+\end{figure}
+
 In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation.
@@
 The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn}) as the presence of this extra inlet increases the flow at the top layers.
+The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
 At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
@@
 is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn}
+\label{fig:vel_magn2}
 \end{figure}
@@
 
+\clearpage
+\listoffigures
+
+\clearpage 
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv}
+\bibliography{references}
+
 \end{document}

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Out of this mixed and complex formations, viscous flow instabilities can occur both within a single phase or when multiple phases flow through porous media.
-Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
-Injections of low-viscosity, high-density fluid $1$ (e.g.
+Oil and gas migration, transport of contaminants through groundwater are some of important physical problem that porous media flows play a crucial role.
+Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, research focus on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+\medskip
+Out of this mixed and complex various geological formations, multiphase flows through porous media.
+play the most important role in understanding the afformentioned operations.
+These often involves the displacement of a non-wetting invading fluid from a porous medium by a wetting fluid.
+Modeling of multiphase flow, on the other hand is still an enormous technical and computational challenge.
+In all branches of fluid mechanics, there are the instabilities, also know as flow instabilities.
+The first distinction should be made between microscopic and macroscopic instabilities.
+The term microscopic instabilities is used for the phenomena occurring locally; for example, the Helmholtz and Taylor instabilities or bubble collapse.
+On the other hand the macroscopic instabilities involve, e.g.the entire two-phase flow system.
+In this paper, the main focus is kept on macroscopic phenomena.
+Part of flow instabilities is the viscous flow instabilities also know as \textit{viscous fingering}.
+In large scale field operations it is the condition whereby the interface of two fluids, such as oil and water, bypasses sections of reservoir as it moves along, creating an uneven, or fingered, profile.
+Fingering is a relatively common condition in reservoirs with water-injection wells.
+The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
+It can occur both within a single phase or when multiple phases flow through porous media.
+
+%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
+Injections of low-viscosity, high-density fluid (e.g.
 water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow.
 These phenomena have great importance during the oil and gas recovery operations in both mature and new fields.
-Starting from oil and gas migration of contaminants through groundwater is the opposite problem governed by the same principles.
-The most complicated of processes include fingering that wil loccur in multiphase and compositional flow.
-Underground coal gasification is another potential application but more recently on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture and storage (CCS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
-Particle methods, front-tracking methods \citep{univerdi_1992} but in particular volume of fluid (VOF) methods \citep{hirt_1981,rider_1998} are used to describe the afformentioned properties.
-In addition, finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008}.
-This work will mainly focus on macroscale flow instabilities or \textit{viscous fingering} in heterogeneous resevoirs -or computational domains- and will compare the development of fingers using an alternative finite element method.
-In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Finding an exact solution to some differential  equations is whether impossible or very time consuming.
+This is where people employ numerical analysis schemes to address the issue by creating a sequence  of approximations.
+This is done through discretization of the continuous differential equations.
+Therefore there are several methods that offer a means to obtain the approximate solutions, there appears that the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM), the Finite DVolume Methods (FVM) and the Finite Element Methods.
+The latter is the one that will be used in this paper and more precisely a member of the FEM family, the COntrol-Volume-FEM method.
+
+\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
 Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.
+All these parameters are represented under one term in the global mass balance equation.}
 

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 Therefore there are several methods that offer a means to obtain the approximate solutions, there appears that the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM), the Finite DVolume Methods (FVM) and the Finite Element Methods.
-The latter is the one that will be used in this paper and more precisely a member of the FEM family, the COntrol-Volume-FEM method.
-
-\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+The latter is the one that will be used in this paper and more precisely a member of the FEM family, the Control-Volume FEM method (CVFEM).
+
+%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
 Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
@@
 \medskip
-The sections that follow include a summary of the main governing equations for multiphase compositional flow.
+\KCnote{ \blue{as soon as we finish the paper}, the sections that follow include a summary of the main governing equations for multiphase compositional flow.
 The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of simulations results and the key conclusions.
-The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
+The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.}
 

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 In this paper, the main focus is kept on macroscopic phenomena.
-Part of flow instabilities is the viscous flow instabilities also know as \textit{viscous fingering}.
+Part of flow instabilities is the viscous flow instabilities, also know as \textit{viscous fingering}.
 In large scale field operations it is the condition whereby the interface of two fluids, such as oil and water, bypasses sections of reservoir as it moves along, creating an uneven, or fingered, profile.
@@
 It can occur both within a single phase or when multiple phases flow through porous media.
+This instability is essentially governed by the mobility-ratio, MR, which is defined as the ratio of the mobility of the displacing fluid over that of the displaced fluid.
+In a water-oil system the MR is given by eq.\ref{eq:MR}    However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravity, anisotropic dispersion, velocity dependence of dispersion, nonmonotonic viscosity profiles, etc.
+High mobility-ratio displacement processes present very  complex  fingering  patterns.
+
+\begin{equation}
+ MR  = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+\label{eq:MR}
+\end{equation}
 
@@
 Considering the limitations of finite differences formulations the CVFE the model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the model above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
 
@@
 \section{Governing equations and numerical scheme}\label{equations_scheme}      
-Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
+Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
 Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities.

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 \begin{equation}
- MR  = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+ MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
 \label{eq:MR}
@@
 Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities.
-This will change the mobility contrast between two phases for a given \textit{viscosity} ratio.
-Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities.
-In this paper, the test-cases are also based on the discontinuous Galerkin (DG) method to simulate viscous fingering.
-Roughly speaking, DG-method combines advantages of classical finite volume and finite element methods.
+Different domains will produce different flow instabilities.
+In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
+DG-methods combine advantages of classical finite volume and finite element methods.
 

### 2017-02-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
-We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.}
-\KCnote{In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations}.
-\KCnote{The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
+We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
+In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
+The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
 So far, the results illustrate that the displacing fluid tends to flow easier towards the zones with higher values of permeability (spatial acceleration / deceleration of flow – fingers formation).

### 2017-02-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections

@@
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.PNG}
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
 \caption{2D representation of the element pairs presented in this work.
@@
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/element_n.png}
+\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
 \caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
@@
 \makebox[\textwidth]{%
-\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm}%
+\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm.pdf}%
 \hfill    
-\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh}%
+\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh.pdf}%
 }\\[0.5cm]% If you want some vertical space
 \makebox[\textwidth]{%
-\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot}%
+\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}%
 }%
@@
 \label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.png}
+\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.png}
+\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type}
+\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh}
+\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}
 }\\
@@
 \label{fig:first}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
 }\\ 
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
 }\\

### 2017-02-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections changing into pdf reviewing the text

@@
 %\begin{minipage}{1.0\textwidth}%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.png}%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.pdf}%
 %\end{minipage}%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}
 }\\ 
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.png}
+\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}
 }\\
@@
 %\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.png}%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
 %\end{minipage}%

### 2017-02-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
making corrections changing into pdf reviewing the text

@@
 \centering
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
 \caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
@@
 \label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR1.png}
+\includegraphics[width=0.6\textwidth]{./Pics/MR1.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR10.png}
+\includegraphics[width=0.6\textwidth]{./Pics/MR10.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.png}
+\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.pdf}
 }\\
@@
 \label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.png}
+\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.pdf}
 }%
@@
 \label{fig:}
-\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.png}
+\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.pdf}
 }\\ 

### 2017-02-18 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 The first distinction should be made between microscopic and macroscopic instabilities.
-The term microscopic instabilities is used for the phenomena occurring locally; for example, the Helmholtz and Taylor instabilities or bubble collapse.
+The term microscopic instabilities is used for the phenomena occurring locally; for example, the Helmholtz and Saffman-Taylor instabilities.
 On the other hand the macroscopic instabilities involve, e.g.the entire two-phase flow system.
@@
 
+\KCnote{ \blue{need to move it in a later section}
 \begin{equation}
@@
 \end{equation}
+}
 
@@
 This is done through discretization of the continuous differential equations.
-Therefore there are several methods that offer a means to obtain the approximate solutions, there appears that the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM), the Finite DVolume Methods (FVM) and the Finite Element Methods.
+Therefore there are several methods that offer a means to obtain the approximate solutions.
+
+\medskip 
+Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
+Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
+However, FDM are often limited to relatively simple geometries
+%(with low grid quality and orientation) 
+representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+Even though the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM) there are also the Finite Volume Methods (FVM) and the Finite Element Methods.
 The latter is the one that will be used in this paper and more precisely a member of the FEM family, the Control-Volume FEM method (CVFEM).
+
+\medskip
+Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
+In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+\label{fig:fem_cv}
+\end{figure}
+
+\medskip
+In the CVFE method pressure is interpollated using piecewise linear finite element basis functions, also known as shape functions, $\underline{\bf v}$ and $\underline{\bf p}$) while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
+%%%%%%%%%%%%%%%
+\begin{comment}
+\begin{equation}
+ p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+\label{cvfe_pressure}
+\end{equation}
+
+\begin{equation}
+ S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+\label{cvfe_saturation}
+\end{equation}
+\end{comment}
+%%%%%%%%%%%%%%%
+Control volume finite element methods require high resolution meshes, as these are represented in fig.\ref{fig:fem_cv}, in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
+Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
 
@@
 \medskip
+
+%%%%%%%%%%%%%%%
+\begin{comment}
 Flows in porous media are expressed by the Darcy's law and the saturation equation.
@@
 
-\noindent The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
 Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
@@
 Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-
+\end{comment}
 %%%%%%%%%%%%%%%
@@
 
-\noindent The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
 \begin{eqnarray}
@@
 $S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
+%%%%%%%%%%%%%%%
+\begin{comment}
 The main equations that will be used along with the following OCVFEM techique can be summarised below.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\subsection{The Overlapping CVFEM formulation}
+\end{comment}
+%%%%%%%%%%%%%%%
+
 \medskip
 Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (eq.~\ref{e:darcy_eq}).
-Hybrid (i.e., overlapping) basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
 $\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
@@
 The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2013}~\citep[see also][]{jackson_2013}.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fig:fem_cv}
-\end{figure}
-
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
-However, FDM are often limited to relatively simple geometries
-%(with low grid quality and orientation) 
-representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
-
-Among FEM-based formulations for porous media, the control volume finite element methods (CVFEM) ~\citep[CVFEM,][]{fung_1992,cordazzo_2004} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
-In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
-
-In the CVFE method pressure is interpollated using piecewise linear finite element basis functions (see Eq.\ref{v_and_p}, also known as shape functions, $\underline{\bf v}$ and $\underline{\bf p}$) while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
-
-\begin{comment}
-\begin{equation}
- p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-\label{cvfe_pressure}
-\end{equation}
-
-\begin{equation}
- S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-\label{cvfe_saturation}
-\end{equation}
-\end{comment}
-
-%where $N_{\alpha}$ is first order finite element basis function and $M_{b}$ is the control volume basis function that is equal to unity over the control volume constructed around node j and is equal to zero everywhere else.
-
-Control volume finite element methods require high resolution meshes in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
-Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-
-\begin{comment}
-%Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
-
-%Under specfic spatial conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers.
-This phenomenon, viscous fingering, describes flow instabilities {\bf (and ...??
-you are repeating the previous sentence ...)}.
-Even though the mechanism of instabilities may vary (in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ??
-be specific)}), however it is still a function of several variables such as, relative mobility, gravity, dispersion, permeability differences\red{(Is this true ??
-if so give references.
-why is gravity or relperm relevant?
-dispersion...
-why?
-perm grad??)}.
-Moreover, in most cases \red{(refs?)} interfacial tension is directly linked with the mobility ratio (or viscosity ratio) between the displaced and the displacing fluid \red{(How and why?)}.
-%\medskip
-%\blue{This last paragraph before aims and objectives (next paragraph) should be gentle transition from current state-of-the-art and this work.
-As a suggestion, the last paragraph should focus on a particular aspect of viscous fingering that may not be well-understood by the scientific community and that is addressed in the paper.
-For example, (a) impact of heterogeneity in the onset of fingering, (b) qualitative sensitivity study of viscosity ratio impact in the finger formation (based on analytical assessment studies), etc.}
-
-%The main aim of this work is to numerically investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media.
-\red{\bf (try to develop it further; be more specific.
-Write this objective sentence/paragraph based on the paper's conclusions!)}.
-This study focuses on flow instabilities due to relatively large viscosity ratios.
-
-%\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%Under certain geological conditions the displacement of fluids in porous media is unstable and results in the formation of irregular flow patterns in the form of fingers %\textit{fingers}. 
-%The flow instabilities mentioned above are described as \textit{viscous fingering}. Even though the mechanism of the instabilities may vary, 
-%(in immiscible fluids the most important factor is the surface tension while in miscible fluids, it is the diffusion \red{(thermal or mass diffusion ...be specific)})
-%however it is still a function of relative mobility, gravity, dispersion, permeability differences.
-Moreover, in most cases interfacial tension is directly linked with the mobility ratio between the displaced and the displacing fluid.
-
-%Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
-
-%In this paper, a control volume finite element method (CVFEM) formulation, recently introduced by~\citet{jackson_2015}~\citep[see also][]{radunz_2014}, is used to investigate the development of multiphase flows through heterogeneous porous media.
-In this formulation, the dual pressure-velocity representation in CV and FEM spaces are embedded into a family of triangular/tetrahedral element-pairs, \PN[n]{m} and \PNDG[n]{m} \citep[][]{cotter_2009b,xie_2014} -- basis function with $n^{\rm th}$- (discontinuous) and $m^{\rm th}$-order (continuous/discontinuous) polynomials for velocity and pressure fileds, respectively.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the CV space.
-High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
-This formulation can achieve an exact representation of the Darcy force balance equations.
-
-%In this paper, \textcolor{red}{the main objective is to investigate the impact of heterogeneous porous media in fingers formation using a FEM-based unstructured fixed mesh multi-fluid model with uniform permeability distribution under both saturated and unsaturated porous media}.
-The overlapping control volume finite element method (OCVFEM), formulation recently introduced by~\citet{jackson_2013}~\citep[see also][]{gomes_2013,pavlidis_2013} is used to investigate the development of multiphase flows through heterogeneous porous media.This finite element based method has a dual pressure-velocity representation in CV and FEM spaces  are embedded into a family of triangular/tetrahedral element pairs, P$_{m}$DG-P$_{n}$~\citep{cotter_2009b} and P$_{m}$DG-P$_{n}DG$~\citep{xie_2014}.
-The dual velocity and pressure fields are represented by $m^{\rm th}$- (discontinuous) and $({n})^{\rm th}$-order (continuous/discontinuous) polynomials, respectively.
-%Moreover, velocity field has dual mapping in FEM and CV spaces. This approach can achieve an exact representation of the Darcy force balance equations. 
-%In addition, the study focused in flow instabilities determined by the viscosity ratio.
-In the simulations presented in this paper the element pairs as described above and the overlapping control volume finite element method (CVFEM) model were used, in which the dual velocity-pressure fields are embedded in FEM space with simultaneous projection into CV space.
-Scalar fields (e.g., saturation, concentration, density, etc) are represented in the control volume space.
-High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions.
-Section $2$ summarises the numerical formulation used in this work, followed by description of the flow instabilities  and a description of model validation.
-Finally, conclusions are drawn in the final section.
-\end{comment}
+Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 

### 2017-02-18 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 %\section{Numerical Formulation}\label{section:NumericalFormulation}
-The method presented here builds on that reported by \citet{jackson_2015, salinas2015} is known as OCVFEM formulation.
-The method developed is applicable to $N_{p}$ fluid phases and to the general family of $P_{n+1}(DG)-P_{n}(DG)$ element pair consistent dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
-These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a continuous representation of pressure.
+ The method developed is applicable to $N_{p}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
+These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order of pressure.
+Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
 The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.

### 2017-02-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 \end{comment}
+
 %%%%%%%%%%%%%%%
@@
 \end{comment}
+%%%%%%%%%%%%%%%
 
@@
 
-As we have to be consistent with \citet{jackson_2015} we assume that rick and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
-
-\begin{equation}
-\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (v_{\alpha}S_{\alpha})= q_{\alpha}
+In this model we assume that rock and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
+
+\begin{equation}
+\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha}
 \label{mass_balance}
@@
 
-where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
-
-\begin{equation}
-\sum  S_{p}-1
-\label{saturation_constrain}
-\end{equation}
-
-The Eq.\ref{saturation_constrain}, is discretized in time and space following the approach of \citet{Jackson_2013} in which the time discretization is obtained using the $\theta$-method as implemented by %\citet{gomes_2013}.
-Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation, Eq.\ref{global_mass_balance},
+%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
+
+%\begin{equation}
+%\sum  S_{p}-1
+%\label{saturation_constrain}
+%\end{equation}
+
+Equation \ref{mass_balance}, is discretize in time and space following the $\theta$-method.
+Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation %\ref{global_mass_balance},
+
+\medskip
+The discretised global mass and force balance equations are solved using a multigrid-like approach ,see \citet{pavlidis2016}.
 

### 2017-02-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Introduction}\label{section:Intro}
+\section{Introduction}\label{section:intro}
 \medskip
@@
 This instability is essentially governed by the mobility-ratio, MR, which is defined as the ratio of the mobility of the displacing fluid over that of the displaced fluid.
-In a water-oil system the MR is given by eq.\ref{eq:MR}    However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravity, anisotropic dispersion, velocity dependence of dispersion, nonmonotonic viscosity profiles, etc.
+%In a water-oil system the MR is given by eq.\ref{eq:MR}.
+However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravity, anisotropic dispersion, velocity dependence of dispersion, nonmonotonic viscosity profiles, etc.
 High mobility-ratio displacement processes present very  complex  fingering  patterns.
-
-\KCnote{ \blue{need to move it in a later section}
-\begin{equation}
- MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
-\label{eq:MR}
-\end{equation}
-}
 
@@
 
-\medskip
-The discretised global mass and force balance equations are solved using a multigrid-like approach ,see \citet{pavlidis2016}.
-
 \begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \, \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} [\theta^{n+1/2}\; n\dot\;v_{p}^{n+1}S_{p}^{n+1}\;+\;(1-)\theta^{n+1/2}\;v_{p}^{n}S_{p}^{n}] d\Gamma \;- \nonumber\\
- &&  \int_{\Omega_{CVi}} M_{i}q_{\alpha}^{n+\theta}dV\; =0
+ && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; n\dot \; v_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; v_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
+ &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0
 \label{global_mass_balance}
@@
 
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, n is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to CN) and $1$ (corresponding to BE) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-The Eq.\ref{global_mass_balance} can be expressed in amtrix form at time level $n+1$ as
+\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to Backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
 
@@
 \medskip
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits, are those that occur under highly critical conditions.
-Under this assumption, viscous fingering is no exception.
-It is a viscous driven hydrodynamic instability that results the collapse of the uniform interface between the fluids of different viscosity.
-This type of instability can be found across many research areas, disciplines and scales.
-Starting from small scale flow instabilities in Hele-Shaw cells that can provide the basic mathematical model, to coupled chromatographic separation systems for chemical and medical applications and reaching up to large scale reservoir systems,  such as the removal of oil from reservoirs, the potential use of CO$_2$ sequestration and the re-mediation of spills, or the transport of pollutants in aquifers.
-The primary removal of oil from reservoirs leaves the porous reservoirs with remaining oil that can only be removed by the use of enhanced oil-recovery (EOR).
-This secondary and tertiary removal of oil from porous beds is required to be as efficient and economically viable as possible.
-
-An accurate finite-element simulator with an adaptive and unstructured 2D grid was used in this study of viscous instabilities.
-This scheme ha already been describe in detail by \citet{pavlidis2016}.
-An unfavourable mobility-ratio displacement coupled with the heterogeneity of the porous medium results in viscous instability (fingering),which in turn affects the displacement efficiency of im/miscible processes as well as sweep efficiency and breakthrough time.
-Fingering will occur in miscible displacments when the viscocity ratio is greater than unity.
-As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system.
+The flow of a fluid over or next to another heavier fluid, can produce a flow instability.
+Under this assumption when a fluid is injected in a porous domain saturated with an other fluid trying to displace it, viscous fingering will occur.
+
+\medskip
+This viscous driven hydrodynamic instability results the collapse of the uniform interface between the fluids of different viscosity.
+This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.
+Starting from the work of \citet{saffman_1959} and \citet{homsy_1987}, and the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, a basic mathematical model has been initially developed to describe the physics of this phenomenon.
+
+\medskip
+In viscous fingering, a less viscous fluid (i.e.
+water) pushes a more viscous fluid (i.e.
+oil), in a thin rectangular cells (known as Hele-Shaw cells).
+Under the assumption that fluids remaining completely separated (or immiscible) along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
+For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
+In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.
+The higher the velocity of the injected fluid, the less wide (a tip-splitting behaviour) the finger will be.
+In addition, pressure differences acting on the interface will produce a net pressure force $\frac{dP}{dx}$ which is a function of the viscosities of the fluids, permeability value and whether gravitational effects are included or not.
+
+As mentioned in section \ref{section:intro}, an unfavourable mobility-ratio (i.e.
+in a water-oil system, see eq.\ref{eq:MR}, displacement coupled with the heterogeneity of the porous medium results in viscous instability, which in turn affects the displacement efficiency of im/miscible processes.
+
+\begin{equation}
+ MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+\label{eq:MR}
+\end{equation}
+
+Fingering will occur in miscible displacements when the viscocity ratio is greater than unity.
+%As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
 After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As a result of \textit{shielding}, one of these lobes will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+\noindent As a result of \textit{shielding}, one of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
 In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.

### 2017-02-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 The higher the velocity of the injected fluid, the less wide (a tip-splitting behaviour) the finger will be.
-In addition, pressure differences acting on the interface will produce a net pressure force $\frac{dP}{dx}$ which is a function of the viscosities of the fluids, permeability value and whether gravitational effects are included or not.
-
+In addition, pressure differences (eq.\ref{eq:pressure_dif}) acting on the interface will produce a net pressure force.
+
+\begin{equation}
+\Delta P= - \gamma \nabla \; \dot \; \hat{n} 
+\label{eq:pressure_dif} 
+\end{equation}
+
+\noindent This is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference,$\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
 As mentioned in section \ref{section:intro}, an unfavourable mobility-ratio (i.e.
@@
 
-Fingering will occur in miscible displacements when the viscocity ratio is greater than unity.
+\noindent Fingering will occur in miscible displacements when the viscocity ratio is greater than unity.
 %As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
 After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-\noindent As a result of \textit{shielding}, one of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+As a result of \textit{shielding}, one of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
 In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
 Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
-Important parameter is the mobility (or viscosity) ratio.
-This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+In  this paper, viscous instabilities for different test-cases will be investigated.
+Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
+Initially cases that verify
+
+%%%%%%%%%%%%%%%
+\begin{comment}
+Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
 
@@
 \frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
+\label{eq:pressure_dif} 
 \end{equation}
@@
 \end{equation}
+\end{comment}
+%%%%%%%%%%%%%%%
 

### 2017-02-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 
-\title{ \blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ...
+\title{ \blue{Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
 something with viscous flow instability or viscous fingering)}}
@@
 \begin{abstract} 
-\KCnote{Numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
+\KCnote{ \blue{......numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
 Viscous fingering, a fluid instability can be a major concern regarding enhanced oil-recovery methods (EOR).
@@
 The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
-Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena.
+%Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena.
 The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
@@
 Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
-The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
-So far, the results illustrate that the displacing fluid tends to flow easier towards the zones with higher values of permeability (spatial acceleration / deceleration of flow – fingers formation).
-It can also be seen that finger like structure will remain connected as it travels towards the outlet while it will grow faster in zones with higher permeability.
-This behaviour is triggered by the permeability contrast among layers.
-As can be seen from Fig........
-the higher the viscosity ratio the easier it is for the uniform front of the injected fluid to break into fingers that will decrease the recovery of hydrocarbon content.
-Also, the higher the viscosity ratio, more to the right the breakpoint is shifted, in the time axis.
-The increased viscosity ratio increases the computational cost and requires the decrease of the solution's time-step.
-Both the geometrical domain and the development of the flow, as can be seen in Fig........
-follow the linear tip-splitting finger behaviour.
-In addition properties such as porosity and saturation can be readily up-scaled using statistical methods.%, like the python function that was introduced in the second case of the simulations, that provides fast and reasonable values.
-To conclude, up-scaling or averaging the geological model can assist in running reservoir models faster and as close as possible to fine geological model.}
+The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution...}}
 
@@
 Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
-Initially cases that verify
+Initially test-cases that verify the existence of fingers in plain domain will illustrated follow by more complicated computational domains and finger patterns.
 
@@
 \section{Results}\label{section:results}
+
+\subsection{Model Validation}
 

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Results}\label{section:results}
@@
 \subsection{Model Validation}
-
-Starting from a simple case as this is described in fig.
-\ref{fig:square}, there is a simple square shape formation consisted of 2 values of different (K) permeabilities (blue and red shaded square areas).
-The domain is fully saturated with fluid $2$.
-We inject fluid $1$ across the left hand side of the formation and we are trying to displace the existing fluid $2$.
-The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ and a main finger starts to appear.
+Initially a case to demonstrate the model validation against experiments is described in fig.
+\ref{fig:square}.
+A simple square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
+The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
+At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain.
+The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$.
+Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$.
+What can been seen here is a cross flow case as the flow passes through different regions and develops.
+The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
 
@@
 
+\section{Conclusions}
+
 In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_perm.pdf}%
-\hfill    
-\includegraphics[width=0.39\textwidth]{./Pics/2b2_P1DGP2_mesh.pdf}%
-}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\includegraphics[width=0.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}%
-}%
-\caption{A simple test-case of a square region with four subregions.
-The permeability contrast is constant.
-The mesh is unstructured but fixed.
-After the injection of fluid $1$ at a velocity of u = 1, the velocity magnitude drops to zero.
-The main finger starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.
-The mechanism that still drives the phenomenon is the pressure difference and the tip-splitting pattern can be more profound.
-}
+\begin{figure}
+\begin{center}
+\subfigure[Initial and boundary conditions]{\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
+\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
+\caption{This is the first test-case of a square region with four subregions of constant permeabilities K.
+The mesh is unstructured but fixed and on average there are 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet.
+This is a cross flow example based on the experimental work of \citet{evans_1994}.
+The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
 \label{fig:square}
+\end{center}
 \end{figure}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 \subsection{Model Validation}
-Initially a case to demonstrate the model validation against experiments is described in fig.
+
+The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain.
+The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones.
+But one step before that, is to verify the existence of cross flow in the following domain as this is defined in fig.
+\ref{fig:simple_case}.
+Fluid $1$ is introduced on the  across the left hand side of the formation.
+Later different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
+\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
+\label{fig:simple_case}
+\end{center}
+\end{figure}
+
+One more case to demonstrate the model validation against experiments is described in fig.
 \ref{fig:square}.
-A simple square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
+A square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
 The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
@@
 \begin{center}
-\subfigure[Initial and boundary conditions]{\includegraphics[width=0.75\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
+\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
 \subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
@@
 \label{fig:elem_type_perm_map}
-\end{figure}
-
-Fluid $1$ is again injected across the left hand side of the formation.
-Mobility ratios of different values will be introduced and compared.
-As the flow is developed the initial uniform front collapses start forming fingers, areas where the flow is developed faster than the rest of the main body of the flow.
-The new unstructured and adaptive mesh with the $P_{n}DG-P_{n+1}$ element type is used in order to capture the flow development.
-In fig.
-\ref{fig:simple_case} the simple case of a domain with uniform permeability is displayed.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.6\textwidth]{./Pics1/phase_vol_frac_unif_perm.pdf}
-\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
-\label{fig:simple_case}
-\end{center}
 \end{figure}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones.
-But one step before that, is to verify the existence of cross flow in the following domain as this is defined in fig.
+One step before it is important to verify the existence of cross flow in the following domain as this is defined in fig.
 \ref{fig:simple_case}.
@@
 \includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
-\caption{This is the simple case where the initially piston shape front is collapsing and starts forming fingers, in a domain with uniform permeability.}
+\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (on average 3000 elements).}
 \label{fig:simple_case}
@@
 \ref{fig:square}.
-A square shape formation consisted of$4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
+A square shape formation consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
 The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
-At the upper and lower sides of the domain no-slip boundary condition is applied, meaning there is no mass transport in and out of the domain.
+At the upper and lower sides of the domain no-slip boundary condition is applied, that at a solid boundary, the fluid will have zero velocity relative to the boundary.
+The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary..
 The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$.
@@
 
-\begin{figure}
+\begin{figure}[h]
 \begin{center}
@@
 In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
-From that point till the end of the formation, the velocity magnitute of the injected fluid remains the same having the minimum value since there is no more fluid 2 to be displaced.
-There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further since at the same time, as can been seen from the graph plot at fig.
-\ref{fig:square}, the phase volume fraction is constant.
-
-The initial and boundary condition regarding the inlet and outlet are the same.
-One more test-case (fig.\ref{fig:testcase}), to verify the finger formation in a simple but same set-up is also illustrated.
+The velocity magnitute is builded up starting from the inlet all the way to the middle of the square.
+There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant.
+An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.
 
@@
 \begin{center}
-\subfigure[MR1 fixed mesh start aspect ratio 2]{%
-\label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_1.pdf}
-}%
-\subfigure[MR1 fixed mesh end aspect ratio 2]{%
-\label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-}\\
-\end{center}
-\caption{In this tes-case fixed and unstructured mesh is used.
+\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
+\subfigure[flow at t=250]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
+\subfigure[flow at t=3000]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
+\caption{In this test-case fixed and unstructured mesh is used.
 The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious.
@@
 \label{fig:testcase}
-\end{figure}
-
- The purpose is to expand this technique and introduce it into more complex formations so as to test it and develop a more stable and solid approach in real time and scale problems.
+\end{center}
+\end{figure}
+
+ The purpose of these case was to verify that our model is working for cases that experimentally are proven.
+This will allow to proceed further and expand this technique into more complex formations.
 A more detailed description of the element type and the formation that will be used in the next set of test cases follows.
+
+\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
 

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 
+%%%%%%%%%%%%
 \subsection{Model Validation}
@@
 
-One more case to demonstrate the model validation against experiments is described in fig.
+\noindent One more case to demonstrate the model validation against experiments is described in fig.
 \ref{fig:square}.
@@
 
-In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
+\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
 The velocity magnitute is builded up starting from the inlet all the way to the middle of the square.
@@
 \subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
-\subfigure[flow at t=250]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
-\subfigure[flow at t=3000]{\includegraphics[width=0.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
+\subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
+\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
+\caption{In this test-case fixed and unstructured mesh is used.
+The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious.
+Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
+\label{fig:testcase}
+\end{center}
+\end{figure}
+
+ The purpose of these cases was to verify that our model is working for cases that experimentally are proven.
+This will allow to proceed further and expand this technique into more complex formations.
+A more detailed description of the element type and the formation that will be used in the next set of test cases follows.
+
+%%%%%%%%%%%%
+\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
+
+%{./Pics/P1DG-P2_element_type} 
+%{./Pics/4r_po_adapt_fine_125_mesh} 
+%{./Pics/4r_po_adapt_fine_100_mesh}
+
+Having already verified that model is working for the test-cases illustrated in previous section, its to introduce a more complicated case where we have regions of different geometrical domains and different permeabilities.
+The time, the domain that we will use is defined in fig.\ref{fig:testcase_heter_domain}.
+
+\begin{figure}[h]
+\begin{center}
+
+\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{a}}
+
 \caption{In this test-case fixed and unstructured mesh is used.
@@
 Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
-\label{fig:testcase}
+\label{fig:testcase_heter_domain}
 \end{center}
-\end{figure}
-
- The purpose of these case was to verify that our model is working for cases that experimentally are proven.
-This will allow to proceed further and expand this technique into more complex formations.
-A more detailed description of the element type and the formation that will be used in the next set of test cases follows.
-
-\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
-
-%{./Pics/P1DG-P2_element_type} 
-%{./Pics/4r_po_adapt_fine_125_mesh} 
-%{./Pics/4r_po_adapt_fine_100_mesh}
-
-\begin{figure}[h]
-\begin{center}
-\subfigure[The $P_{1}DGP_{2}$ element type]{%
-\label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics/P1DG-P2_element_type.pdf}
-}%
-\subfigure[The map of permeabilities]{%
-\label{fig:}
-\includegraphics[width=0.45\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
-}\\
-\end{center}
-\caption{(a) represents the element type of $P_{1}DGP_{2}$ as well as where each of the parameters is located and calculated on the element type.
-(b) describes the permeability map as this is introduced throught a python script during the set-up of simulations.
-In general, the main body of the formation is the blue area that is fully saturated with fluid $2$.
-Above the main (blue colored) area there are two layers - formations of different absolute permeabilities while in the main body there is a also a square shaped red coloured area where the two fluids exist in 50-50 phase ratio.
-All those ratios as well as the values of the permeabilities can be changes any time according to the data that are provided.
-}
-\label{fig:elem_type_perm_map}
 \end{figure}

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant.
-An slightly modified test-case follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.
+An slightly modified test-case (see fig.\ref{fig:testcase}) follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.
+The last set of simulations as this is described in fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
 
@@
 \subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
-\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{b}}
+\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{c}}
 \caption{In this test-case fixed and unstructured mesh is used.
-The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious.
+The aspect ratio is 2 (a), which allows the flow to develop for longer.
 Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
@@
 
+\begin{figure}[h]
+\makebox[\textwidth]{%
+\subfigure[MR1]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
+}%
+\hfill    
+\subfigure[MR10]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\subfigure[MR1]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
+}%
+\hfill    
+\subfigure[MR10]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\subfigure[MR1]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
+}%
+\hfill    
+\subfigure[MR10]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
+}}%
+\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from (a) t=100(start) to (c) t=3000(end).}
+\label{fig:1testcase}
+\end{figure}
+
 %%%%%%%%%%%%
@@
 
-Having already verified that model is working for the test-cases illustrated in previous section, its to introduce a more complicated case where we have regions of different geometrical domains and different permeabilities.
-The time, the domain that we will use is defined in fig.\ref{fig:testcase_heter_domain}.
+\KCnote{\blue{need to put screenshots from pseudo hele-shaw case - log on to Jeff's station and then include the following cases}}
+
+Having already verified that model is working for the test-cases illustrated in previous section, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
+Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
 
@@
 \begin{center}
-
-\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{a}}
-
-\caption{In this test-case fixed and unstructured mesh is used.
-The aspect ratio is 2, which allows the finger to develop faster and make the tip-splitting stage more obvious.
-Simulation time step increases from left (a) to right (b) and from t=250(start) to t=3000(end).}
+\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/map_of_boundaries.pdf}\label{a}}
+\subfigure[permeabilities using an unstructured and fixed computational domain]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{b}}
+\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
+Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
 \label{fig:testcase_heter_domain}
@@
 \KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
-
-\begin{figure}[h]
-\begin{center}
-\subfigure[MR1 fixed mesh start]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-}%
-\subfigure[MR10 fixed mesh start]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}\\
-\subfigure[MR1 fixed mesh middle]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}
-}%
-\subfigure[MR10 fixed mesh middle]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}\\
-\subfigure[MR1 fixed mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}
-}\\
-\subfigure[MR10 fixed mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}
-}\\
-\end{center}
-\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from t=100(start) to t=3000(end).}
-\label{fig:1testcase}
-\end{figure}
 

### 2017-02-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 \begin{figure}[h]
-\begin{center}
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh start]{%
-\label{fig:first}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}
-}%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
+}%
+\hfill    
 \subfigure[MR10 adapt mesh start]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
-}\\
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}
-}%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
+}%
+\hfill    
 \subfigure[MR10 adapt mesh]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
-}\\
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}
-}%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
+}%
+\hfill    
 \subfigure[MR10 adapt mesh]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
-}\\ 
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}
-}\\
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
+}%
+\hfill    
 \subfigure[MR10 adapt mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
-}\\
-\end{center}
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
+}}%
 \caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
@@
 \begin{figure}[h]
-\begin{center}
-\subfigure[MR10 fixed mesh start]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}
-}%
-\subfigure[MR10 fixed adapt start]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
-}\\
+\makebox[\textwidth]{%
+\subfigure[[MR10 fixed mesh start]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh start]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh t=1500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
-}%
-\subfigure[MR10 fixed adapt t=1500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
-}\\
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh t=1500]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh t=7500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}
-}%
-\subfigure[MR10 fixed adapt t=7500]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}
-}\\ 
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh t=7500]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
 \subfigure[MR10 fixed mesh end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
-}\\
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}%
+}%
+\hfill    
 \subfigure[MR10 fixed adapt end]{%
-\label{fig:}
-\includegraphics[width=0.35\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}
-}\\
-\end{center}
-\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}%
+}}%
+\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
+%\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
 \label{fig:3testcase}

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
keep on updating

@@
 %%%%%%%%%%%%
-\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
+\subsection{\blue{title for the $3$ hell shaw cases}}
+
+%\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
+
+At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}.
+The Hele-shaw cell geometrical domain as this is defined by experimental studies and is presented in figures \ref{{fig:1a_homoheleshaw_3},{fig:1b_homoheleshaw_3}} and fig.
+\ref{fig:1c_homoheleshaw_3} is used.
+In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 (i.e., sqrt(2*0.25)).
+The sink (represented by 0 pressure BC) is allocated in the top right hand side corner of the domain.
+Newmann BC (i.e., no flux) was imposed to all borders of the domain except at the top righ hand side corner.
+The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter homogeneous and heterogeneous domain is used.
+
+\begin{figure}
+\centering
+\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}}\\[2mm]%
+\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}}%
+\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+More screenshot follow that describe the progression of the flow in fig.\ref{fig:1b_homoheleshaw_3} and fig.\ref{fig:1c_homoheleshaw_3}}
+\label{fig:1a_homoheleshaw_3}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
+\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
+\caption{As the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
+\label{fig:1b_homoheleshaw_3}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=3500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf}}\\[2mm]%
+\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}%
+\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:1c_homoheleshaw_3}
+\end{figure}
+
+%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}}\\[2mm]%
+\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}}%
+\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_3}}
+\label{fig:2a_homoheleshaw_10}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}\\[2mm]%
+\subfigure[flow at t=4000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}}%
+\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
+\label{fig:2b_homoheleshaw_10}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}}\\[2mm]%
+\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}%
+\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:2c_homoheleshaw_10}
+\end{figure}
+
+%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}}\\[2mm]%
+\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}}%
+\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_3}}
+\label{fig:3a_heteheleshaw_10}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=2000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf}}\\[2mm]%
+\subfigure[flow at t=3000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}}%
+\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
+Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
+\label{fig:3b_heteheleshaw_10}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}}\\[2mm]%
+\subfigure[flow at t=24000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}}%
+\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
+At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
+\label{fig:3c_heteheleshaw_10}
+\end{figure}
 
@@
 
-\KCnote{\blue{need to put screenshots from pseudo hele-shaw case - log on to Jeff's station and then include the following cases}}
+\begin{figure}[h]
+\makebox[\textwidth]{%
+\subfigure[MR10 fixed mesh start]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh start]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\subfigure[MR10 fixed mesh]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\subfigure[MR10 fixed mesh]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
+}}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\subfigure[MR10 fixed mesh end]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
+}%
+\hfill    
+\subfigure[MR10 adapt mesh end]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
+}}%
+\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.
+}
+\label{fig:2testcase}
+\end{figure}
 
@@
 \begin{figure}
-\centering
+%\centering
 \includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\centering
-%\subfigure[MR100 fixed mesh t=500]{%
-%\label{fig:}
-%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.png}
-%}%
-%\subfigure[MR100 fixed mesh t=1500]{%
-%\label{fig:}
-%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.png}
-%}%
-%\subfigure[MR100 fixed mesh t=3000]{%
-%\label{fig:}
-%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.png}
-%}\\ 
-%\subfigure[MR100 fixed mesh end]{%
-%\label{fig:}
-%\includegraphics[width=0.35\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.png}
-%}\\
-%\end{center}
-%\caption{snapshots when the MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-%\label{fig:4testcase}
-%\end{figure}
-
+\begin{comment}
 \begin{figure}[h] 
@@
 \end{figure}
+\end{comment}
 

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updating everything

@@
 
-\begin{figure}
-%\centering
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
-\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-\label{fig:4testcase}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
+%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
+%\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
+%\label{fig:4testcase}
+%\end{center}
+%\end{figure}
 

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updating everything

@@
 %%%%%%%%%%%%
-\subsection{\blue{title for the $3$ hell shaw cases}}
-
-%\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
-
+\subsection{Hele-Shaw verification cases for homogeneous and heterogeneous domains under two different mobility ratios}
+
+\medskip
 At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}.
-The Hele-shaw cell geometrical domain as this is defined by experimental studies and is presented in figures \ref{{fig:1a_homoheleshaw_3},{fig:1b_homoheleshaw_3}} and fig.
+The Hele-shaw cell geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
 \ref{fig:1c_homoheleshaw_3} is used.
@@
 \caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_3}}
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
 \label{fig:2a_homoheleshaw_10}
@@
 \caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_3}}
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
 \label{fig:3a_heteheleshaw_10}
@@
 
-Having already verified that model is working for the test-cases illustrated in previous section, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
+\noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
 Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
+
+\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
+
+\medskip
+\KCnote{mpla mplam mpla the case with 4regions and permeabilities}
 

### 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updating everything

@@
 
-\begin{figure}[h]
+%%%%%%%%%%%%%%%%
+\begin{figure}
 \makebox[\textwidth]{%
@@
 \includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
+}}%
+\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d).,followed by the t=1500(a,b), t=3000(c,d) in fig.\ref{fig:2btestcase}.}
+\label{fig:2atestcase}
+\end{figure}
+
+\begin{figure}
 \makebox[\textwidth]{%
@@
 }}%
-\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.
-}
-\label{fig:2testcase}
+\caption{When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time. }
+\label{fig:2btestcase}
 \end{figure}
@@
 \begin{figure}
-\centering 
+%\center
 %\begin{minipage}{1.0\textwidth}%

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

--- 2017-02-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
-}}%
-\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.
-}
-\label{fig:2testcase}
-\end{figure}
-
+%%%%%%%%%%%%%
+\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases for MR10 fixed vs. adaptive mesh}}
+
+\medskip
+\KCnote{ 4regions and 4 permeabilities}
 \noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
+There is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}) so the next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh test case.
 Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
-
-\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases}}
-
-\medskip
-\KCnote{mpla mplam mpla the case with 4regions and permeabilities}
+Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of th esimulation for different time-steps as these are desrcibed.
+In this set the interfacial instability is becoming more profound.
+Based on these two case so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
+Fingers will develop faster in areas where permeabilities are higher.
+This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
 
@@
 
- Based on these two case so far an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
-Fingers will develop faster in areas where permeabilities are higher.
-This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
-
-%Starting from the middle of the formation there is an increase in the velocity of the injected fluid but then it 'crashes' on the red square shape region where it slows down from the existence of both the fluid 1 \& fluid 2 that coexists.
-After flowing through this area there is a balance (plateau) among the two faces on time fig.\ref{fig:subim8 middle}.
-Going higher in the formation, fig.\ref{fig:subim9 up} in the next zone just above the main body (blue area), there is an initial fluctuating decrease  of the velocity of the injected fluid which is driven by the different permeability value.
-At the top layer ref.\ref{fig:subim10 upper} of the formation there is a smooth increase of the injected fluid velocity magnitude which basically describes an overall and study development of the flow while just before the end collapses.
-
+\begin{figure}
+\centering
+\subfigure[flow at t=250 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}}\\[2mm]%
+\subfigure[flow at t=250 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}}%
+\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
+There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
+\label{fig:2testcase_a}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}}\\[2mm]%
+\subfigure[flow at t=500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}}%
+\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\label{fig:2testcase_b}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t=1500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}}\\[2mm]%
+\subfigure[flow at t=1500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}}%
+\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
+\label{fig:2testcase_c}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[flow at t= end (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}}\\[2mm]%
+\subfigure[flow at t= end (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}}%
+\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
+\label{fig:2testcase_d}
+\end{figure}
+
+%%%%%%%%%%%%%
+\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases for MR10 adaptive double inlet}}
+
+\medskip
+\KCnote{velocity magnituted comparison under the adaptive vs. adaptive and refined mesh - NOT sure if we can include that}
+
+%\begin{figure}
+%\centering
+%\subfigure[flow at t=1000  (adaptive coarse mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.pdf}}\\[2mm]%
+%\subfigure[flow at t=1000  (adaptive and fine mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.pdf}}\\[2mm]%
+%\subfigure[flow at t=1000  (adaptive and refined mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.pdf}}%
+%\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+From top to bottom These graphs describe the velocity magnitude for single inlet with adaptive and fine mesh (a) and adaptive and refined mesh (b).
+The main difference between the (a) and (b) lies in the first part and how the velocity magnitude is builded up as a relation of phase $1$ volume fraction.}
+%\label{fig:vel_magn1}
+%\end{figure}
+
+In fig.\ref{fig:3testcase_a} there is a set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
+This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
+The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
+The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
+At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
+Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
+Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of ﬁngers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
+A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
+No ﬁngers could be observed due to mesh coarseness (ﬁngers were observed in ﬁner uniform and adaptive meshes).
+
+%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[map of permeabilities]{\includegraphics[width=0.5\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
+\subfigure[flow at start]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
+\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
+\label{fig:3testcase_a}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
+\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
+\label{fig:3testcase_b}
+\end{figure
+
+%%%%%%%%%%%%%
+\begin{comment}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\KCnote{need to include some figures and analysis of the velocities, magnitude etc.}
-
-Having already observed the significant growth of fingers comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}), the next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh test case (Fig.\ref{fig:2testcase}).
-
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}%
-}}%
-\caption{Comparing test-cases of fixed and adaptive mesh, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.
-}
-\label{fig:2testcase}
-\end{figure}
-
-\begin{figure}
-\centering 
-%\begin{minipage}{1.0\textwidth}%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.pdf}%
-%\end{minipage}%
-\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-From top to bottom,these graphs describe the velocity magnitude for single inlet with adaptive mesh coarse (top), adaptive and fine (middle) and adaptive and refined as these simulations are shown in fig.\ref{fig:2testcase}.
-The main difference between the top, middle and bottom graph lies in the first part and how the vleocity magnitude is builded up as a relation of phase $1$ volume fraction and lower.}
-\label{fig:vel_magn1}
-\end{figure}
-
-In fig.\ref{fig:3testcase} there is a comparison between a single and double injection of fluid $1$ into the formation.
-This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
-The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
-Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
-Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of ﬁngers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
-A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
-No ﬁngers could be observed due to mesh coarseness (ﬁngers were ob-served in ﬁner uniform and adaptive meshes).
-
+%%%%%%%%%%%%%%%%
 \begin{figure}[h]
@@
 \begin{figure}
-\centering 
-%\begin{minipage}{1.0\textwidth}%
+\begin{center}
 %\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
-%\end{minipage}%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
+\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
 \caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
@@
 \label{fig:vel_magn2}
+\end{center}
 \end{figure}

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

@@
 \centering
-\subfigure[map of permeabilities]{\includegraphics[width=0.5\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
-\subfigure[flow at start]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
+\subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
+\subfigure[flow at start]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
 \caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
@@
 \centering
-\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
-\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
-\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
+\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
+\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+\caption{In fig.(a)  fig.(b) .}
 \label{fig:3testcase_b}
-\end{figure
+\end{figure}
 

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

@@
 \centering
-\subfigure[dual inlet flow, fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
-\subfigure[dual inlet flow, adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
 \caption{In fig.(a)  fig.(b) .}
@@
 
-%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[fixed mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}}%
+\caption{In fig.(a)  fig.(b) .}
+\label{fig:3testcase_c}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[fixed mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}}%
+\caption{In fig.(a)  fig.(b) .}
+\label{fig:3testcase_d}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
+\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
+\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
+\label{fig:4testcase}
+\end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%
 \begin{comment}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively.
-The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible.
-Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
-The domain is fully saturated with fluid $2$.
-At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
-Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
-The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
-Saturation is located at the pressure nodes.
-Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
-The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
-
-Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or mutliple fingers will be observed.
-
-This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
-Viscocity is a measure of resistance, therefore a frictional property.
-In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
-For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
-Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
-Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
-In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
-In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
-This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
-The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
-
-%%%%%%%%%%%%%%%%
 \begin{figure}[h]
@@
 \end{figure}
-
+\end{comment}
+
+\medskip
+The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively.
+The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible.
+Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
+The domain is fully saturated with fluid $2$.
+At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
+Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
+The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
+Saturation is located at the pressure nodes.
+Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
+The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
+
+Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or mutliple fingers will be observed.
+
+This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
+Viscocity is a measure of resistance, therefore a frictional property.
+In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
+For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
+Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
+Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
+In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
+In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
+This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
+The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
+
+%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
-%\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
-%\label{fig:4testcase}
-%\end{center}
-%\end{figure}
-
+%%%%%%%%%%%%%%%
 \begin{comment}
@@
 
+\medskip
 The macroscopic sweep efficiency is principally affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
@@
 Including higher permeability zones also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
+
+\medskip 
 As can been seen so far in all the test-case illustrated, main differences can be found on the way the shape of fingering is developed.
@@
 
+\medskip
 Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
@@
 
-\section{Conclusions}
+\section{Conclusions }
+
+\KCnote{need to work that section again}
 

### 2017-02-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)

@@
 \begin{abstract} 
-\KCnote{ \blue{......numerical modelling of multiphase flow in porous media has a wide range of applications in science and engineering.
-Viscous fingering, a fluid instability can be a major concern regarding enhanced oil-recovery methods (EOR).
+\KCnote{ \blue{ Multiphase flows in porous media is an interesting and important subject in fields ranging from oil recovery to medicine.
+From physics standpoint, the complex structures observed in multiphase flows, also know as fingers, are especially interesting.
+Much work both experimental and numerical has been done on invasion systems where one fluid is injected into a system filled with another fluid.
+These patterns are causing an instability known as Safmman-Taylor or Viscous fingering.
 Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow.
@@
 \KCnote{velocity magnituted comparison under the adaptive vs. adaptive and refined mesh - NOT sure if we can include that}
-
-%\begin{figure}
-%\centering
-%\subfigure[flow at t=1000  (adaptive coarse mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_coarse_vel_magn.pdf}}\\[2mm]%
-%\subfigure[flow at t=1000  (adaptive and fine mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_vel_magn.pdf}}\\[2mm]%
-%\subfigure[flow at t=1000  (adaptive and refined mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_4regions_python_only_adapt/4regions_python_only_adapt_refine_vel_mag.pdf}}%
-%\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-From top to bottom These graphs describe the velocity magnitude for single inlet with adaptive and fine mesh (a) and adaptive and refined mesh (b).
-The main difference between the (a) and (b) lies in the first part and how the velocity magnitude is builded up as a relation of phase $1$ volume fraction.}
-%\label{fig:vel_magn1}
-%\end{figure}
 

### 2017-02-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
correct the \center L801 703(?)
few more comments on the results, waiting feedback from Jeff
Update Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \usepackage{epsfig}
-
+%\usepackage{subfig}
 \usepackage{comment}
@@
 The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain.
-The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from the basic ones.
+The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from some basic model set-ups.
 One step before it is important to verify the existence of cross flow in the following domain as this is defined in fig.
 \ref{fig:simple_case}.
-Fluid $1$ is introduced on the  across the left hand side of the formation.
-Later different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
+Fluid $1$ is introduced in the domain across the left hand side of the formation.
+Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
 
@@
 \ref{fig:square}.
-A square shape formation consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
-The aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
-At the upper and lower sides of the domain no-slip boundary condition is applied, that at a solid boundary, the fluid will have zero velocity relative to the boundary.
-The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary..
-The left hand side of the domain is defined as the inlet for fluid $1$ with a velocity of $u=1$ while the right hand side is the outlet and pressure is set to $0$.
+A square domain consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
+The geometrical aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
+At the upper and lower sides of the domain no-slip boundary condition is applied (fluid will have zero velocity relative to the boundary).
+The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary.
+The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$.
+The right hand side is the outlet and pressure is set to $0$.
 Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$.
-What can been seen here is a cross flow case as the flow passes through different regions and develops.
+What can been seen here is a cross flow case as the flow passes through different regions and evolves.
 The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
@@
 \caption{This is the first test-case of a square region with four subregions of constant permeabilities K.
-The mesh is unstructured but fixed and on average there are 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = 1, while as the flow progress the velocity magnitude drops to zero close to the outlet.
+The mesh is unstructured and fixed and on average there are 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, while as the flow progress the velocity magnitude drops to zero close to the outlet.
 This is a cross flow example based on the experimental work of \citet{evans_1994}.
@@
 
-\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviour across the length of the formation.
+\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
 The velocity magnitute is builded up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid 2 cannot be pushed any further (see fig.\ref{fig:square}) while the phase volume fraction is constant.
+There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see fig.\ref{fig:square}) while the phase volume fraction is constant.
 An slightly modified test-case (see fig.\ref{fig:testcase}) follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.
@@
 
- The purpose of these cases was to verify that our model is working for cases that experimentally are proven.
+\noindent The purpose of these two cases was to verify that our model is working for cases that experimentally are proven.
 This will allow to proceed further and expand this technique into more complex formations.
@@
 At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}.
-The Hele-shaw cell geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
+The Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
 \ref{fig:1c_homoheleshaw_3} is used.
-In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 (i.e., sqrt(2*0.25)).
-The sink (represented by 0 pressure BC) is allocated in the top right hand side corner of the domain.
-Newmann BC (i.e., no flux) was imposed to all borders of the domain except at the top righ hand side corner.
-The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter homogeneous and heterogeneous domain is used.
+In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
+. The sink (pressure is set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
+was imposed to all borders of the domain except at the top righ hand side corner.
+The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
 
@@
 
-\KCnote{need to work that section again}
+\KCnote{need to work that section again, try to maintain the flow on the description of the results starting from the basics to the hele shaw to heterogeneities to more complicated MR10 flows to double inlet to MR1,10,100 compasiron}
 

### 2017-02-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex

@@
 %%%%%%%%%%%%%
-\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases for MR10 fixed vs. adaptive mesh}}
+\subsection{\blue{need to find a name for this heterogeneous region/set of test-cases for MR10 fixed vs. adaptive mesh}}
 
@@
 \noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-There is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}) so the next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh test case.
-Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
-Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of th esimulation for different time-steps as these are desrcibed.
-In this set the interfacial instability is becoming more profound.
-Based on these two case so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
+Initial and boundary conditions are described in fig.
+\ref{fig:testcase_heter_domain}.
+What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}).
+The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
+%Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
+Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
+In this set the interfacial instability is becoming more profound as the flow develops.
+Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
 Fingers will develop faster in areas where permeabilities are higher.

### 2017-02-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex
latest updates - I think now I corrected the missing file. 
Thank you Jeff

@@
 \end{figure}
+
+The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
+Screenshots of the phase volume fraction and the development of fingers will are shown in fig.
+\red{fig:4testcase}.
 
@@
 Inside the high permeability square region there is an acceleration of the flow with the maximum value of it at the interface as this starts to develops at the back of this region and onwards.
-At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
+%At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
 The breaking point, also known as the point the two curves meet where beyond that water production will occur, is shifted towards the right as MR is increased.
 
-\medskip
+\section{Conclusions}
+
+\KCnote{need to work that section again, try to maintain the flow on the description of the results starting from the basics to the hele shaw to heterogeneities to more complicated MR10 flows to double inlet to MR1,10,100 compasiron}
+
+\medskip
+A number of different cases have been illustrated in section \ref{section:results}.
+Starting from tested experimental cases and geomtrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
+Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows.
+For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
+In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number (N_{c}) but mainly on mobility ratio (MR).
+If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
+On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
+Therefore for an i.e., water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
+Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
+
+\medskip
+We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
 Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
-In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced byt the use of OCVFEM and families of elements.
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in both upstream and downstream operations.
-Even thought this model is promising there is still work to be done since it is not yet a complete product.
-Further work is required to develop the surface-based modelling algorithms.
-
-\section{Conclusions }
-
-\KCnote{need to work that section again, try to maintain the flow on the description of the results starting from the basics to the hele shaw to heterogeneities to more complicated MR10 flows to double inlet to MR1,10,100 compasiron}
-
-In conclusion the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
+In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
+
+\medskip
+As usually seen for high viscosity contrast, the leading finger screens out the trailing by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
+At long times the large finger advances approximately at
+constant velocity. Results which question the evolution of fingers and the finger competition are those referring to the dynamic role of viscosity contrast.
+
+\medskip
+In summary, the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
 \begin{enumerate}
@@
 \end{enumerate}
+
+\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
+Keeping both the thickness and the injection rate constant, it was observed that increasing the mobility ratio decreases the finger width, which subsequently leads to more fingers and subsequently more complexity at a given distance away from the injection point.
+Tip-splitting, a phenomenon in which the initial stage of fingers split into two or more new fingers, can also be observed at higher mobility ratios.}
 

### 2017-02-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
line 700

@@
 The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see fig.{\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
+At this point is proper to mentioned the extreme case, see fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
 Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
@@
 \subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
-\caption{In fig.(a)  fig.(b) .}
+\caption{In fig.(a)  fig.(b).}
 \label{fig:3testcase_b}
@@
 \subfigure[adaptive mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}}%
-\caption{In fig.(a)  fig.(b) .}
+\caption{In fig.(a)  fig.(b).}
 \label{fig:3testcase_c}
@@
 \subfigure[adaptive mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}}%
-\caption{In fig.(a)  fig.(b) .}
+\caption{In fig.(a)  fig.(b).}
 \label{fig:3testcase_d}
@@
 The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers will are shown in fig.
-\red{fig:4testcase}.
+Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}\\[2mm]%
-\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
 \caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
@@
 
+\begin{comment}
 \section{Achknowledgements}
@@
 Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.
+\end{comment}
 

### 2017-02-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
line 700

@@
 
-\begin{figure}
-\begin{center}
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
-\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
-\label{fig:4testcase}
-\end{center}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
+%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
+%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
+%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
+%\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
+%\label{fig:4testcase}
+%\end{center}
+%\end{figure}
 

### 2017-03-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
lets try now

--- 2017-02-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \usepackage{subfigure}
+
 %% The lineno packages adds line numbers. Start line numbering with
@@
 \medskip
-Numerical investigation and modelling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Numerical investigation and modeling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
 Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies.
+Oil and gas migration, transport of contaminants through groundwater are some of important physical problem that porous media flows play a crucial role.
 Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Oil and gas migration, transport of contaminants through groundwater are some of important physical problem that porous media flows play a crucial role.
 Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, research focus on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
@@
 \medskip
-Out of this mixed and complex various geological formations, multiphase flows through porous media.
-play the most important role in understanding the afformentioned operations.
-These often involves the displacement of a non-wetting invading fluid from a porous medium by a wetting fluid.
-Modeling of multiphase flow, on the other hand is still an enormous technical and computational challenge.
-In all branches of fluid mechanics, there are the instabilities, also know as flow instabilities.
+Due to complex and/or heterogeneous geological formations, multiphase flows through porous media play an important role in understanding the afformentioned operations.
+Modeling of multiphase flow, is an enormous technical and computational challenge.
+Starting from important contributions on the field of multiphase flows from \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}, in all branches of fluid mechanics, there are the instabilities, also know as flow instabilities as these, first described by \citet{saffman_1958}.
 The first distinction should be made between microscopic and macroscopic instabilities.
-The term microscopic instabilities is used for the phenomena occurring locally; for example, the Helmholtz and Saffman-Taylor instabilities.
-On the other hand the macroscopic instabilities involve, e.g.the entire two-phase flow system.
+Microscopic instabilities are used for phenomena occurring locally, for example, the Helmholtz and Saffman-Taylor instabilities (\citep{saffman_1959}).
+On the other hand the macroscopic instabilities involves two-phase flow system (\citep{bottoni_1992}).
 In this paper, the main focus is kept on macroscopic phenomena.
-Part of flow instabilities is the viscous flow instabilities, also know as \textit{viscous fingering}.
-In large scale field operations it is the condition whereby the interface of two fluids, such as oil and water, bypasses sections of reservoir as it moves along, creating an uneven, or fingered, profile.
-Fingering is a relatively common condition in reservoirs with water-injection wells.
+A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.
+
+\medskip
+In large scale field operations, fingering is a relatively common condition in reservoirs with water-injection wells.
+As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile.
 The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-It can occur both within a single phase or when multiple phases flow through porous media.
-This instability is essentially governed by the mobility-ratio, MR, which is defined as the ratio of the mobility of the displacing fluid over that of the displaced fluid.
+This instability is mainly governed by the ratio of the mobility of the displacing fluid over that of the displaced fluid (Mobility-ratio, MR).
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.
 However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravity, anisotropic dispersion, velocity dependence of dispersion, nonmonotonic viscosity profiles, etc.
-High mobility-ratio displacement processes present very  complex  fingering  patterns.
+High mobility-ratio displacement processes introduces very complex fingering patterns.
 
@@
 
-\medskip
-The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
+% Good for thesis not for paper
+%\medskip
+%The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
 Finding an exact solution to some differential  equations is whether impossible or very time consuming.
@@
 \medskip 
+The conservation of mass along with the Darcy's law are the governing equations that describe the flow dynamics in porous media.
+Several computational methods have been developed to accurately represent force balanceand mass conservation in darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
-However, FDM are often limited to relatively simple geometries
-%(with low grid quality and orientation) 
-representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+A finite difference method (FDM) discretization is based upon the differential form of the PDE to be solved.
+%Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
+However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
-Even though the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM) there are also the Finite Volume Methods (FVM) and the Finite Element Methods.
+A finite element method (FEM) discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided up into smaller domains (finite elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM are the better description of the geometry and complex shapes, better treatment of fluid flow and saccurate more accurate stress calculations using a smaller number of nodes, less memory space and shorter run times.
+At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
+%Even though the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM) there are also the Finite Volume Methods (FVM) and the Finite Element Methods.
 The latter is the one that will be used in this paper and more precisely a member of the FEM family, the Control-Volume FEM method (CVFEM).
@@
 \medskip
-Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements~\citep{forsyth_1990, geiger_2004, hurtado_2007}.
-In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
+Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+
+%~\citep{forsyth_1990, geiger_2004, hurtado_2007}. 
+%In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
 
@@
 \medskip
-In the CVFE method pressure is interpollated using piecewise linear finite element basis functions, also known as shape functions, $\underline{\bf v}$ and $\underline{\bf p}$) while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
+In the CVFE method pressure is interpollated using piecewise linear finite element basis functions, also known as shape functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
+while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
+
 %%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%
-Control volume finite element methods require high resolution meshes, as these are represented in fig.\ref{fig:fem_cv}, in regions where material properties vary abruptly, such as permeability and/or porosity contrasts at fracture-matrix interfaces.
+
+Material properties in control volume finite element methods (Fig.\ref{fig:fem_cv}) may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
 Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
@@
 \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
 Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-
 %\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
@@
 \medskip
-The objective of this study is to investigate and accurately describe the behaviour of fingering in multiphase ($2$-phase) flows using a control volume finite element method (CVFEM).
-Considering the limitations of finite differences formulations the CVFE the model formulation will use a conservative computational multi-fluid porous media flow model able to exploit mesh adaptivity methods on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and pressure fields at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
-
-\medskip
-\KCnote{ \blue{as soon as we finish the paper}, the sections that follow include a summary of the main governing equations for multiphase compositional flow.
-The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of simulations results and the key conclusions.
-The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.}
+The objective of this study is to investigate and describe the behaviour of viscous fingering in multiphase flows using a control volume finite element method (CVFEM).
+Taking into account the limitations of finite differences, the CVFE method  will use a conservative computational multi-fluid porous media approach able to exploit the mesh adaptivity on a fully-unstructured tetrahedral grid.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
+
+\medskip
+In the sections following the introduction, numerical fomrulation and a summary of the main governing equations for multiphase compositional flows will follow.
+The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.
+The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
 
@@
 \section{Governing equations and numerical scheme}\label{equations_scheme}      
-Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
+%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
 Different domains will produce different flow instabilities.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Numerical Formulation}
-\medskip
-
+%\subsection{Numerical Formulation}
 %%%%%%%%%%%%%%%
@@
 
+\medskip
 The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
@@
 \end{eqnarray}
-where $S$, $\mu$, ${\bf K}$, $p$ and $\phi$ are the saturation, viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{k}$ is the saturation-weighted Darcy velocity of the $k$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
 $\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
@@
 \medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (eq.~\ref{e:darcy_eq}).
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{e:darcy_eq}).
 Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
@@
  The method developed is applicable to $N_{p}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
-These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order of pressure.
+These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial pressure.
 Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
@@
 \includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
-The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.}
+\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{2}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
 \label{fig:fem_elem}
@@
 
-In this model we assume that rock and fluids are incopressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
+In this model we assume that rock and fluids are incompressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
 
@@
 
-Equation \ref{mass_balance}, is discretize in time and space following the $\theta$-method.
-Summing over all phases and discretizing in time using the $\theta$-method yields the global mass balance equation %\ref{global_mass_balance},
+Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method (\citep{saramito_1994}) .
+Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
 
@@
  && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; n\dot \; v_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; v_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
  &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0
@@
 
-\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is normal vector of the CV and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to Backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
+\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach (see \citet{pavlidis2016}).
 
@@
 \end{figure}
+
+\begin{comment}
 
@@
 %%%%%%%%%%%%%%%%
-\begin{figure}
-\begin{center}
+\begin{comment}
+\begin{figure}[h!]
 %\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}\\[2mm]%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}%
+\subfigure[single inlet velocity magnitude]{\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}}\\[2mm]%
+\subfigure[double inlet velocity magnitude]{\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}}%
 \caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
@@
 for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
-The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happen during the finger development and their velocity patterns.
+The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
 While there
@@
 \label{fig:vel_magn2}
-\end{center}
-\end{figure}
+\end{figure}
+\end{comment}
 
@@
 For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
-In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number (N_{c}) but mainly on mobility ratio (MR).
+In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR).
 If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.

### 2017-03-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem})  , which are limited to yield bounded fields.
+The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
 
@@
 \medskip
-This viscous driven hydrodynamic instability results the collapse of the uniform interface between the fluids of different viscosity.
+This viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
 This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.
-Starting from the work of \citet{saffman_1959} and \citet{homsy_1987}, and the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, a basic mathematical model has been initially developed to describe the physics of this phenomenon.
-
-\medskip
-In viscous fingering, a less viscous fluid (i.e.
-water) pushes a more viscous fluid (i.e.
-oil), in a thin rectangular cells (known as Hele-Shaw cells).
-Under the assumption that fluids remaining completely separated (or immiscible) along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
+Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon.
+The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap.
+The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law).
+More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
+
+\medskip
+In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell).
+\citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
 For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
 In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.
-The higher the velocity of the injected fluid, the less wide (a tip-splitting behaviour) the finger will be.
-In addition, pressure differences (eq.\ref{eq:pressure_dif}) acting on the interface will produce a net pressure force.
-
-\begin{equation}
-\Delta P= - \gamma \nabla \; \dot \; \hat{n} 
+The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be.
+In addition, pressure differences %(eq.\ref{eq:pressure_dif})
+acting on the interface will produce a net pressure force,
+
+\begin{equation}
+\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
 \label{eq:pressure_dif} 
@@
 
-\noindent This is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference,$\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
-As mentioned in section \ref{section:intro}, an unfavourable mobility-ratio (i.e.
-in a water-oil system, see eq.\ref{eq:MR}, displacement coupled with the heterogeneity of the porous medium results in viscous instability, which in turn affects the displacement efficiency of im/miscible processes.
+\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
+As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.
 
@@
 
-\noindent Fingering will occur in miscible displacements when the viscocity ratio is greater than unity.
+\noindent Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
 %As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 
-Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method (\citep{saramito_1994}) .
+Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method \citep{saramito_1994}.
 Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
@@
 The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law).
-More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
+More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
 
@@
 After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As a result of \textit{shielding}, one of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+As surface tension becomes weak, the front is stressed and goes under a viscous-fingering instability.
+The front will collapse and will start splitting into new lobes of fingers.
+One of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
 In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
@@
 Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
-Initially test-cases that verify the existence of fingers in plain domain will illustrated follow by more complicated computational domains and finger patterns.
+Initially test-cases that verify the existence of fingers in experimental domains will illustrated follow by more complicated computational domains and finger patterns.
 
@@
 
-The set of test-cases that we are going to illustrate starts with an elementary case in an homogeneous domain.
-The aim of this test-case is to verify that the numerical model is actually working in different simulation/scenarios starting from some basic model set-ups.
-One step before it is important to verify the existence of cross flow in the following domain as this is defined in fig.
-\ref{fig:simple_case}.
-Fluid $1$ is introduced in the domain across the left hand side of the formation.
+The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
+The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+
+Fig.\ref{fig:simple_case} describes the starting point of the simulations that will follow.
+Fluid $1$ is from the left hand side of the formation.
 Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
+Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on th right hand side of the domain.
+Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively.
+Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).
 
@@
 \includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
-\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (on average 3000 elements).}
+\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
 \label{fig:simple_case}
@@
 
-\noindent One more case to demonstrate the model validation against experiments is described in fig.
-\ref{fig:square}.
-A square domain consisted of $4$ square regions that each one has $2$ values of different permeabilities (K is represented by the blue and red shaded square areas).
-The geometrical aspect ratio of the domain is $1$ and is fully saturated with fluid $2$.
-At the upper and lower sides of the domain no-slip boundary condition is applied (fluid will have zero velocity relative to the boundary).
-The fluid velocity at all fluid–solid boundaries is equal to that of the solid boundary.
+%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
+\noindent A square domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
+At the upper and lower sides of the domain no-slip boundary condition is applied.
 The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$.
 The right hand side is the outlet and pressure is set to $0$.
-Fluid $1$ across the left hand side of the formation is trying to displace the existing fluid $2$.
+Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$.
 What can been seen here is a cross flow case as the flow passes through different regions and evolves.
-The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
+The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ (Fig.\ref{fig:square}b).
 
@@
 \subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
-\caption{This is the first test-case of a square region with four subregions of constant permeabilities K.
-The mesh is unstructured and fixed and on average there are 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, while as the flow progress the velocity magnitude drops to zero close to the outlet.
-This is a cross flow example based on the experimental work of \citet{evans_1994}.
-The main finger desrcibes the cross flow and starts to dies out during the transition from one permeability zone to another and as it approaches closer to the right boundary.}
+\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+The mesh is unstructured and fixed with 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
 \label{fig:square}
@@
 \noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
-The velocity magnitute is builded up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see fig.\ref{fig:square}) while the phase volume fraction is constant.
-An slightly modified test-case (see fig.\ref{fig:testcase}) follows with the initial and boundary condition to remain the same, but in this set of simulations the geometrical aspect ration is $2$.
-The last set of simulations as this is described in fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
+The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
+There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see Fig.\ref{fig:square}) while the phase volume fraction is constant.
+
+\medskip
+A slightly modified test-case (see Fig.\ref{fig:testcase}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$.
+The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
+The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
 
@@
 \subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{c}}
-\caption{In this test-case fixed and unstructured mesh is used.
+\caption{In this test-case an unstructured mesh is used.
+Permeability $K=1$ at the blue region and $K=2.5$ at the red region.
 The aspect ratio is 2 (a), which allows the flow to develop for longer.
@@
 %%%%%%%%%%%%
-\subsection{Hele-Shaw verification cases for homogeneous and heterogeneous domains under two different mobility ratios}
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}
 

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 
-\noindent The purpose of these two cases was to verify that our model is working for cases that experimentally are proven.
-This will allow to proceed further and expand this technique into more complex formations.
-A more detailed description of the element type and the formation that will be used in the next set of test cases follows.
+\medskip
+In this section three different sets of simulations were explained.
+Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio.
+The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop.
+The third test-case is based in the initial and boundary condition of the second set of simulations.
+Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:1testcase}) and how the cross-flow as well as the simulation will progress on time.
+The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
 
@@
 }}%
-\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from (a) t=100(start) to (c) t=3000(end).}
+\caption{Comparing MR1 and MR10 cases using fixed mesh using the same map of permeabilities as test-case in Fig.\ref{fig:testcase}.
+Simulation time step increases from top to bottom and from (a,b) t=100(start) to (e,f) t=3000(end).}
 \label{fig:1testcase}
@@
 \medskip
-At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}.
-The Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
-\ref{fig:1c_homoheleshaw_3} is used.
-In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
+Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
+\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
+In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
 . The sink (pressure is set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 \medskip
-Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig.
+Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and Fig.
 \ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
 In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
-. The sink (pressure is set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
+. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
 was imposed to all borders of the domain except at the top righ hand side corner.
 The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
+
+\medskip
+In Fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
+Three different cases with different set-ups will follow.
+The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
+For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
 
@@
 \caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in fig.\ref{fig:1b_homoheleshaw_3} and fig.\ref{fig:1c_homoheleshaw_3}}
+More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
 \label{fig:1a_homoheleshaw_3}

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 \subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
-\caption{As the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
+\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
 \label{fig:1b_homoheleshaw_3}
@@
 \end{figure}
+
+As can been seen from the Fig.\ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$.
+As the set-up of the simulation remained the same, fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
 

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

--- 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \medskip
-Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and Fig.
-\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
+Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
 In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
@@
 
+\medskip
+As can been seen from the Fig.\ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
+Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} give a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in Figures \ref{fig:3a_heteheleshaw_10},\ref{fig:3b_heteheleshaw_10},\ref{fig:3c_heteheleshaw_10}.
+Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
+In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation.
+The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.
+
 %%%%%%%%%%%%%
-\subsection{\blue{need to find a name for this heterogeneous region/set of test-cases for MR10 fixed vs. adaptive mesh}}
-
-\medskip
-\KCnote{ 4regions and 4 permeabilities}
-\noindent Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-Initial and boundary conditions are described in fig.
-\ref{fig:testcase_heter_domain}.
+\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
+
+\medskip
+Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
+Initial and boundary conditions are described in Fig.
+\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
+A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.
 What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}).
 The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
+For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$.
 %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
-Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c}, \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
+Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c} and \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
 In this set the interfacial instability is becoming more profound as the flow develops.
@@
 %%%%%%%%%%%%%
-\subsection{\blue{need to find a name for this heterogeneus region/set of test-cases for MR10 adaptive double inlet}}
-
-\medskip
-\KCnote{velocity magnituted comparison under the adaptive vs. adaptive and refined mesh - NOT sure if we can include that}
-
-In fig.\ref{fig:3testcase_a} there is a set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
+\subsection{Comparison of flow pattern under the same simulation set-up with an additional inlet}
+
+\medskip
+Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
 This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields (see fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
+The major difference is located in the velocity fields (see Fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
+At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
 Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
-Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of ﬁngers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
+Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
 A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
-No ﬁngers could be observed due to mesh coarseness (ﬁngers were observed in ﬁner uniform and adaptive meshes).
-
-%%%%%%%%%%%%%
-\begin{figure}
-\centering
+No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).
+
+\begin{figure}
+\begin{center}
 \subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
@@
 \label{fig:3testcase_a}
+\end{center}
 \end{figure}
@@
 \begin{comment}
-
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
-\caption{In fig.(a)  fig.(b).}
-\label{fig:3testcase_b}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}}%
-\caption{In fig.(a)  fig.(b).}
-\label{fig:3testcase_c}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}}%
-\caption{In fig.(a)  fig.(b).}
-\label{fig:3testcase_d}
-\end{figure}
-
-The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
-
-\begin{figure}
-\begin{center}
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
-\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
-\label{fig:4testcase}
-\end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}[h]
+\begin{figure}
 \makebox[\textwidth]{%
@@
 
+\begin{comment}
+\begin{figure}
+\centering
+\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_b}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[fixed mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}}%
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_c}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure[fixed mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf}}\\[2mm]%
+\subfigure[adaptive mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}}%
+\caption{for t=end of simulation, there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_d}
+\end{figure}
+\end{comment}
+
+The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
+Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
+
+\begin{figure}
+\begin{center}
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
+\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
+\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
+\label{fig:4testcase}
+\end{center}
+\end{figure}
+
 \medskip
@@
 
-\KCnote{need to work that section again, try to maintain the flow on the description of the results starting from the basics to the hele shaw to heterogeneities to more complicated MR10 flows to double inlet to MR1,10,100 compasiron}
-
 \medskip

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 %%%%%%%%%%%%%
-\subsection{Comparison of flow pattern under the same simulation set-up with an additional inlet}
+\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}
 
@@
 \begin{figure}
-\begin{center}
+\centering
 \subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
@@
 \label{fig:3testcase_a}
-\end{center}
 \end{figure}
@@
 \begin{figure}
-\begin{center}
+\centering
 \subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
@@
 \label{fig:4testcase}
-\end{center}
 \end{figure}
@@
 The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. 
-The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible.
+%The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. 
 Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
@@
 
-Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or mutliple fingers will be observed.
+Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.
 
@@
 
-%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}[h] 
-\begin{center}
-\subfigure[MR1]{%
-\label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR1.pdf}
-}%
-\subfigure[Recovery for MR1]{%
-\label{fig:}
-\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR1_1.png}
-}\\
-\subfigure[MR10]{%
-\label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR10.pdf}
-}%
-\subfigure[Recovery for MR10]{%
-\label{fig:}
-\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR10_10.pdf}
-}\\
-\subfigure[MR100]{%
-\label{fig:}
-\includegraphics[width=0.6\textwidth]{./Pics/MR100_100_start.pdf}
-}%
-\subfigure[Recovery for MR100]{%
-\label{fig:}
-\includegraphics[width=0.52\textwidth]{./Pics/Recovery_MR100_100.pdf}
-}\\ 
-\end{center}
-\caption{Comparison of different MR's and their recovery rates.
-The comparison among the MR = $1$,MR = $10$ and MR = $100$ has been done using the boundary conditions and set upt as this has already been describe in the beginning of the section \ref{section:results}.
-}
-\label{fig:recoveryrates}
-\end{figure}
-\end{comment}
-
 \medskip
@@
 \medskip
-A number of different cases have been illustrated in section \ref{section:results}.
-Starting from tested experimental cases and geomtrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
+A number of different cases have been illustrated in Section \ref{section:results}.
+Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
 Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows.
@@
 
-\medskip
-We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
+%\medskip
+%We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
 Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
@@
 
-\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
+%\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
 Keeping both the thickness and the injection rate constant, it was observed that increasing the mobility ratio decreases the finger width, which subsequently leads to more fingers and subsequently more complexity at a given distance away from the injection point.

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
final 1

@@
 \begin{abstract} 
-\KCnote{ \blue{ Multiphase flows in porous media is an interesting and important subject in fields ranging from oil recovery to medicine.
+A set of simulations is presented so as to model the viscous fingering-flow instability using a novel method for modeling multi-phase flows in porous media.
+Starting from the Hele-Shaw experimental which is mathematically analogous to the two-dimensional flow in porous medium, test-cases of both homogenous and heterogeneous computational domains, under different conditions are listed.
+The development of finger structures is explained by taking into account different maps of permeabilities, mobility ratios and surface tension.
+A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
+In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+It was found that the initial state is the decisive factor in the development of the process up to large times
+% Multiphase flows in porous media is an interesting and important subject in fields ranging from oil recovery to medicine.
 From physics standpoint, the complex structures observed in multiphase flows, also know as fingers, are especially interesting.
@@
 Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow.
-A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
 The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics and tackle the difficulties that commercial resevoir simulators may rise when using low order finite volume/differences methods based on structured grids.
@@
 We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
-In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+%In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
 Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
-The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution...}}
+The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
 
@@
 Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
-Also by focusing the grid resolution in the saturation front, \citet{christou2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
+Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
 A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
@@
 
-\begin{comment}
+%\begin{comment}
 \begin{figure}
@@
 \end{figure}
-\end{comment}
+%\end{comment}
 

### 2017-03-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1

@@
 Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies.
-Oil and gas migration, transport of contaminants through groundwater are some of important physical problem that porous media flows play a crucial role.
-Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, research focus on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Oil and gas migration and transport of contaminants in groundwater are some of important physical problems that porous media flows play a crucial role.
+%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, most research focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
@@
 Modeling of multiphase flow, is an enormous technical and computational challenge.
-Starting from important contributions on the field of multiphase flows from \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}, in all branches of fluid mechanics, there are the instabilities, also know as flow instabilities as these, first described by \citet{saffman_1958}.
+Starting from important contributions on the field of multiphase flows from \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}, in the research area of fluid mechanics, there are the instabilities, also know as flow instabilities as these, first described by \citet{saffman_1958}.
 The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities are used for phenomena occurring locally, for example, the Helmholtz and Saffman-Taylor instabilities (\citep{saffman_1959}).
-On the other hand the macroscopic instabilities involves two-phase flow system (\citep{bottoni_1992}).
-In this paper, the main focus is kept on macroscopic phenomena.
+Microscopic instabilities are used for phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+On the other hand the macroscopic instabilities involves two-phase flow system \citep{bottoni_1992}.
+In this paper, the test-cases taht will follow focus on macroscopic instabilities and phenomena.
 A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.
@@
 The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of the mobility of the displacing fluid over that of the displaced fluid (Mobility-ratio, MR).
+This instability is mainly governed by the ratio of mobility of the displacing fluid over that of the displaced fluid (Mobility-ratio, MR).
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.

### 2017-03-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1

@@
 The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of mobility of the displacing fluid over that of the displaced fluid (Mobility-ratio, MR).
+This instability is mainly governed by the ratio of mobility of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.
-However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravity, anisotropic dispersion, velocity dependence of dispersion, nonmonotonic viscosity profiles, etc.
-High mobility-ratio displacement processes introduces very complex fingering patterns.
+However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
 
@@
 The conservation of mass along with the Darcy's law are the governing equations that describe the flow dynamics in porous media.
-Several computational methods have been developed to accurately represent force balanceand mass conservation in darcean flows.
+Several computational methods have been developed to accurately represent force balanceand mass conservation in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-A finite difference method (FDM) discretization is based upon the differential form of the PDE to be solved.
+%The FDM discretization is based upon the differential form of the PDE to be solved. 
 %Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
@@
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometries.
 A finite element method (FEM) discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
@@
 Advantages of FEM are the better description of the geometry and complex shapes, better treatment of fluid flow and saccurate more accurate stress calculations using a smaller number of nodes, less memory space and shorter run times.
-At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
+%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
 %Even though the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM) there are also the Finite Volume Methods (FVM) and the Finite Element Methods.
@@
 Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-
-%~\citep{forsyth_1990, geiger_2004, hurtado_2007}. 
-%In this formulation, standard Galerkin-FEM method is used to discretise the pressure equation (FEM representation of pressure and velocity fields) whereas a control volume-based formulation is used to discretise all remaining scalar fields~\citep[e.g., saturation, density, species concentration etc, see][]{gomes_book_2012}.
 
@@
 
-\medskip
-In the CVFE method pressure is interpollated using piecewise linear finite element basis functions, also known as shape functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
+In the CVFEM pressure is interpollated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
 while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.

### 2017-03-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1

@@
 
-In the CVFEM pressure is interpollated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
-while saturation is represented in node centered CV basis functions respectevely, and the saturation equation is solved explicitly after solving for pressure at each time.
+In the CVFEM pressure is interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
+while saturation is represented in node centered CV basis functions respectively, and the saturation equation is solved explicitly after solving for pressure at each time.
 
@@
 
-Material properties in control volume finite element methods (Fig.\ref{fig:fem_cv}) may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
+Material properties in control volume finite element methods (Fig.\ref{fig:fem_cv}, describes the $P_{1}DGP_{2}$ element type) may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
 Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
@@
 \medskip
-The objective of this study is to investigate and describe the behaviour of viscous fingering in multiphase flows using a control volume finite element method (CVFEM).
-Taking into account the limitations of finite differences, the CVFE method  will use a conservative computational multi-fluid porous media approach able to exploit the mesh adaptivity on a fully-unstructured tetrahedral grid.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{n+1}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) the overlapping control volume finite element method (CVFEM)formulation.
-
-\medskip
-In the sections following the introduction, numerical fomrulation and a summary of the main governing equations for multiphase compositional flows will follow.
+The objective of this study is to investigate and describe the behaviour of viscous fingering.
+The CVFE method  will use a conservative computational multi-fluid porous media formulation able to exploit the mesh adaptivity on fully-unstructured tetrahedral grids.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) the overlapping control volume finite element method formulation.
+
+\medskip
+In the sections following the introduction, numerical formulation and a summary of the main governing equations for multiphase compositional flows will follow.
 The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.
@@
   {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-  \label{E:darcy_ext}
+  \label{e:darcy_ext}
 \end{equation}
@@
 \medskip
-The two-phase flow through the porous media $\Omega$ may be described by the coupled extended Darcy and global mass conservation equations,
+The two-phase flow through the porous media domain $\Omega$, may be described by the coupled extended Darcy and global mass conservation equations,
 \begin{eqnarray}
@@
 \medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{e:darcy_eq}).
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation %(Eqn.~\ref{e:darcy_eq}). 
 Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
@@
 The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 
@@
 %\section{Numerical Formulation}\label{section:NumericalFormulation}
- The method developed is applicable to $N_{p}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
-These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial pressure.
+ The method developed is applicable to $\mathcal{N_{p}}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
+These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial for pressure.
 Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
+The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (Fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
 
@@
 \caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{2}$.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
 Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
@@
 
-Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method \citep{saramito_1994}.
+Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method %\citep{saramito_1994}. 
 Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
@@
 \noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach (see \citet{pavlidis2016}).
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
 
@@
 As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system.
-The flow of a fluid over or next to another heavier fluid, can produce a flow instability.
-Under this assumption when a fluid is injected in a porous domain saturated with an other fluid trying to displace it, viscous fingering will occur.
-
-\medskip
-This viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
+Under this assumption when a fluid is injected in a porous domain saturated with another fluid trying to displace it, viscous fingering will occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
 This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.

### 2017-03-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Update Manuscript_ViscousInstabilities_KC.tex
Section 1 and VFinger

@@
 On the other hand the macroscopic instabilities involves two-phase flow system \citep{bottoni_1992}.
-In this paper, the test-cases taht will follow focus on macroscopic instabilities and phenomena.
-A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.
+In this paper, the test-cases will focus on macroscopic flow instabilities due to viscous and stress forces also often named as viscous instabilities or \textit{viscous fingering}.
 
@@
 \medskip
-In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell).
+The physics as well as the main ide of the viscous fingering is the described experimentaly by the Hele-Shaw cell.
+Two layers really close to each other they they form an infinite lenght while a less viscous fluid pushes a more viscous one in between this rectangular cell.
 \citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
@@
 In addition, pressure differences %(eq.\ref{eq:pressure_dif})
-acting on the interface will produce a net pressure force,
+acting on the interface will produce a net pressure force, expressed by the Young-Laplace equation,
 
@@
 
-\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
-As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.
-
-\begin{equation}
- MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+\noindent a relation describing the capillary pressure difference across the interface between two fluids.
+In Eq.
+\ref{eq:pressure_dif} $\Delta P$ denotes the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ the surface tension.
+As mentioned in Section \ref{section:intro}, the mobility-ratio in a water-oil system can be defined as
+
+\begin{equation}
+ MR \; = \frac{K_{rw} \; \mu_{w}}{K_{ro} \; \mu_{o}} 
 \label{eq:MR}
@@
 
-\noindent Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
+\noindent Fingering occurs in immiscible displacements when the viscocity ratio is greater than unity.
 %As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
 After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As surface tension becomes weak, the front is stressed and goes under a viscous-fingering instability.
-The front will collapse and will start splitting into new lobes of fingers.
-One of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
-In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
-Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+As surface tension becomes weak, the front is stressed and undergoes a viscous-fingering instability.
+The front collapses and starts splitting into new lobes of fingers.
+One of these fingers eventually outgrows the others and then spreads to occupy the appropriate width.
+In the process, it reaches a width that is again unstable resulting in splitting, and the cycle repeats.
+Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuring repeated branching.
 

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 & vfingering
section 1 updated

--- 2017-03-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies.
-Oil and gas migration and transport of contaminants in groundwater are some of important physical problems that porous media flows play a crucial role.
+Oil and gas migration and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to the global environmental problems, most research focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to global environmental problems, most research has focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
@@
 Due to complex and/or heterogeneous geological formations, multiphase flows through porous media play an important role in understanding the afformentioned operations.
-Modeling of multiphase flow, is an enormous technical and computational challenge.
-Starting from important contributions on the field of multiphase flows from \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}, in the research area of fluid mechanics, there are the instabilities, also know as flow instabilities as these, first described by \citet{saffman_1958}.
+Modeling of multiphase flow is an enormous technical and computational challenge.
+Important contributions regarding the description of physics and mechanisms related with multiphase flows have been made by \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}.
+Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}.
 The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities are used for phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
 On the other hand the macroscopic instabilities involves two-phase flow system \citep{bottoni_1992}.
-In this paper, the test-cases taht will follow focus on macroscopic instabilities and phenomena.
+This paper will focus on microscopic instabilities and phenomena for a two-phase system.
 A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.
@@
 \medskip
-In large scale field operations, fingering is a relatively common condition in reservoirs with water-injection wells.
-As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile.
+In large scale field O$\&$G operations, viscous or density fingering is a relatively common condition in reservoirs with water-injection wells.
+As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
 The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of mobility of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
+This instability is mainly governed by the ratio of mobility (MR) of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.
-However, other important factors also influence the severity of viscous fingering: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+However, other important factors that also influence the severity of viscous fingering are: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
 
@@
 \medskip 
-The conservation of mass along with the Darcy's law are the governing equations that describe the flow dynamics in porous media.
-Several computational methods have been developed to accurately represent force balanceand mass conservation in Darcean flows.
+Conservation of mass along with the Darcy's law are the governing equations that describe the flow dynamics in porous media.
+Several computational methods have been developed to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
@@
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometries.
-A finite element method (FEM) discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided up into smaller domains (finite elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM are the better description of the geometry and complex shapes, better treatment of fluid flow and saccurate more accurate stress calculations using a smaller number of nodes, less memory space and shorter run times.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
 %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
@@
 Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In the CVFEM pressure is interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while saturation is represented in node centered CV basis functions respectively, and the saturation equations are solved explicitly after solving for pressure at each non-linear iteration.
 
@@
 \end{figure}
-
-In the CVFEM pressure is interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$) 
-while saturation is represented in node centered CV basis functions respectively, and the saturation equation is solved explicitly after solving for pressure at each time.
 

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated

@@
 
-Material properties in control volume finite element methods (Fig.\ref{fig:fem_cv}, describes the $P_{1}DGP_{2}$ element type) may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements (FE), constructed control volumes (CV) typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interface.
+Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
+%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
+Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
 This often leads to excessive numerical dispersion especially in highly heterogeneous media.

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated

@@
 This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was developed by \citet{nick_2011b, nick_2011a}.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated

@@
 \medskip
-The objective of this study is to investigate and describe the behaviour of viscous fingering.
-The CVFE method  will use a conservative computational multi-fluid porous media formulation able to exploit the mesh adaptivity on fully-unstructured tetrahedral grids.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) the overlapping control volume finite element method formulation.
-
-\medskip
-In the sections following the introduction, numerical formulation and a summary of the main governing equations for multiphase compositional flows will follow.
+The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
+
+\medskip
+In the next sections the numerical formulation and a summary of the main governing equations for multiphase compositional flows will discussed.
 The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.

### 2017-03-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated
section 1 updates

@@
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification, for the mining industry is an important area of interest, but more recently, also due to global environmental problems, most research has focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Underground coal gasification for the mining industry is an important area of interest, but more recently, also due to global environmental problems, most research has focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
@@
 \medskip
-In large scale field O$\&$G operations, viscous or density fingering is a relatively common condition in reservoirs with water-injection wells.
-As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
-The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of mobility (MR) of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
+In large scale field oil and gas operations, viscous or density fingers are relatively common in reservoirs with water-injection wells.
+As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
+The result of fingering is an inefficient sweeping efficiency that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
+This instability is mainly governed by the ratio of mobility (MR) of the displacing and the displaced fluids (mobility-ratio, MR).
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.
@@
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geological domains.
+FEM discretization is based upon a piecewise representation of the solution space  and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from the basis functions.
 Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
@@
 %%%%%%%%%%%%%%%
-
-Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
+\medskip
+%Through the $P_{1}DGP_{2}$ element type, 
+Material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
 %describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
 Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
@@
 \medskip
-The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
+The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFEM formulation that exploits adaptive mesh of fully-unstructured triangle and tetrahedron grids.
+Also two key characteristics that describe the research concept are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) dual representation of pressure and velocity fields in the FE and CV spaces.
 

### 2017-03-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \usepackage{epsfig}
-%\usepackage{subfig}
+\usepackage{subfig}
 \usepackage{comment}
@@
 It was found that the initial state is the decisive factor in the development of the process up to large times
-% Multiphase flows in porous media is an interesting and important subject in fields ranging from oil recovery to medicine.
-From physics standpoint, the complex structures observed in multiphase flows, also know as fingers, are especially interesting.
-Much work both experimental and numerical has been done on invasion systems where one fluid is injected into a system filled with another fluid.
-These patterns are causing an instability known as Safmman-Taylor or Viscous fingering.
-Continuity equation and the Darcy's law govern the processes, while pressure, velocity, saturation and permeability are quantities that define the behaviour of the flow.
-The current model is the basis of a general purpose flow simulator that is equipped with anisotropic mesh adaptivity techniques to increase the computational accuracy of numerical methods used in geophysical fluid mechanics and tackle the difficulties that commercial resevoir simulators may rise when using low order finite volume/differences methods based on structured grids.
-The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
-The model is based upon two key numerical characteristics: (a) the family of $P_{n}DG-P_{n+1}$ finite element pairs and (b) a consistent overlapping control volume finite element method (CVFEM) formulation.
-%Moreover, the mesh adaptivity algorithm employs multi-constraints on element size in different regions of the porous medium to resolve multi-scale transport phenomena.
-The scheme captures the key characteristics of the flow while its applicable to heterogeneous porous media and geological formations.
-We conclude that understanding the multiphase flow properties will allow us to efficiently facilitate more efficient oil \& gas recovery, efficient contaminant removal and better planning of carbon capture and storage (CCS) projects.
-%In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-Both the evolution of visualisation techniques through the extensive use of parallel computing as well as the advances in modelling and simulation of porous media flows may help to address the importance of this phenomenon which can be found in petroleum, chemical and environmental operations.
 The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
-
-%\JGnote{ Abstracts for journal papers have very `squared-structure': (a) Motivation (why would anyone bother to read the paper?
-Why is it (the paper and/or the subject) relevant?
-This needs to be covered in 1-3 punchy sentences.); (b) (Main) Objective(s) of the manuscript with particular focus on the \underline{novelty(ies)} the paper may bring (this should be covered in 2-6 (very dry) sentences); (c) Summary of the main technologies that you are using or introducing (and, in some cases, how this/these link(s) with (a), 2-6 sentences); (d) Summary of the main findings (linkage with (b), 2-3 sentences).}
-
 \end{abstract}
@@
 Underground coal gasification for the mining industry is an important area of interest, but more recently, also due to global environmental problems, most research has focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Underground coal gasification, for the mining industry is an important area of interest, but more recently, due to global environmental problems, most research has focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
@@
 Modeling of multiphase flow is an enormous technical and computational challenge.
-Important contributions regarding the description of physics and mechanisms related with multiphase flows have been made by \citet{wooding_1976}, \citet{homsy_1987} and \citet{adler_1988}.
+Important contributions regarding the description of physics and mechanisms related with multiphase flows have been made by \citet{wooding_1976} as far as the importance of capillary pressure and the flow regimes in capillary media.
+From \citet{homsy_1987} we have an extensive desrciption of the mechanisms of fingering and how these are related with the forces acting on the interface between two immiscible fluids, and from \citet{adler_1988} there is an extensive description of both microscopic and macroscopic scale darcy-equations.
 Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}.
@@
 %In a water-oil system the MR is given by eq.\ref{eq:MR}.
+
+\medskip
+In large scale field O$\&$G operations, viscous or density fingering is a relatively common condition in reservoirs with water-injection wells.
+As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
+The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
+This instability is mainly governed by the ratio of mobility (MR) of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
+%In a water-oil system the MR is given by eq.\ref{eq:MR}.
 However, other important factors that also influence the severity of viscous fingering are: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
-
-%Forecasting the behaviour of multiphase flows or the future response of the system are major challenges that need to be taken into account.
-Injections of low-viscosity, high-density fluid (e.g.
-water) into a reservoir saturated with lighter but more viscous oil is an example where both viscous and gravitational instabilities may occur for two-phase immiscible and incompressible flow.
-These phenomena have great importance during the oil and gas recovery operations in both mature and new fields.
-
-% Good for thesis not for paper
-%\medskip
-%The conservation of mass along with Darcy's law are the governing equations that describe the flow pattern.
-Finding an exact solution to some differential  equations is whether impossible or very time consuming.
-This is where people employ numerical analysis schemes to address the issue by creating a sequence  of approximations.
-This is done through discretization of the continuous differential equations.
-Therefore there are several methods that offer a means to obtain the approximate solutions.
 
@@
 %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%Even though the most popular ones for the fluid flow equations are the Finite Difference Methods (FDM) there are also the Finite Volume Methods (FVM) and the Finite Element Methods.
-The latter is the one that will be used in this paper and more precisely a member of the FEM family, the Control-Volume FEM method (CVFEM).
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
 
@@
 
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
+%\label{fig:fem_cv}
+%\end{figure}
+
+%\begin{figure}[h]
+%   \vbox{
+%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
+%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
+%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
+%\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+%    \label{fem_cv_represent_a}
+%\end{figure}
+
 \begin{figure}[h]
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
 \caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
@@
 %%%%%%%%%%%%%%%
-\begin{comment}
-\begin{equation}
- p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-\label{cvfe_pressure}
-\end{equation}
-
-\begin{equation}
- S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-\label{cvfe_saturation}
-\end{equation}
-\end{comment}
+%\begin{comment}
+%\begin{equation}
+% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+%\label{cvfe_pressure}
+%\end{equation}
+
+%\begin{equation}
+% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+%\label{cvfe_saturation}
+%\end{equation}
+%\end{comment}
 %%%%%%%%%%%%%%%
+
 \medskip
@@
 
+Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
+%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
+Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
 %The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
@@
 Also two key characteristics that describe the research concept are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) dual representation of pressure and velocity fields in the FE and CV spaces.
+The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
 
@@
 %%%%%%%%%%%%%%%
-\begin{comment}
-Flows in porous media are expressed by the Darcy's law and the saturation equation.
+%\begin{comment}
+%Flows in porous media are expressed by the Darcy's law and the saturation equation.
 At this stage the control volume finite element method is used (CVFEM).
 Darcy's law for immiscible multi-phase flow may be written in the form:
-\begin{equation}\label{e:darcy_eq}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+%\begin{equation}\label{e:darcy_eq}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
 $\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
 
-Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-\begin{equation}
-  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-  \label{e:force_bal}
-\end{equation}
-where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_bal}
+%\end{equation}
+%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
 The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
 
-\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-\begin{equation}
-  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-\end{equation}
-where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-\begin{eqnarray}
-    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-\label{v_and_p}
-\end{eqnarray}
-
-The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
+%\begin{equation}
+%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
+%\end{equation}
+%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
+%\begin{eqnarray}
+%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
+%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+%\label{v_and_p}
+%\end{eqnarray}
+
+%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
 Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
@@
 
-\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
 Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-\end{comment}
+%\end{comment}
 
 %%%%%%%%%%%%%%%
-\begin{comment}
-The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+%\begin{comment}
+%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
 In addition, we neglect the effects of capillarity and gravity in our simulations.
@@
 
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-\label{e:darcy_eq}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\label{e:darcy_eq}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
 $\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
 
-\begin{equation}
-  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
 %S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-\label{E:darcy_eqn}
-\end{equation}
-where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+%\label{E:darcy_eqn}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
 $S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
@@
 
- Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-\begin{equation}
-  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-  \label{e:darcy_ext}
-\end{equation}
-$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-\end{comment}
+% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+%\begin{equation}
+%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:darcy_ext}
+%\end{equation}
+%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+%\end{comment}
 %%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%
-\begin{comment}
-The main equations that will be used along with the following OCVFEM techique can be summarised below.
+%\begin{comment}
+%The main equations that will be used along with the following OCVFEM techique can be summarised below.
 The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
@@
 
-\begin{equation}
-M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-\label{e:mass_bal}
-\end{equation}
-
-\begin{equation}
-B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-\label{e:force_bal}
-\end{equation}
-
-\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+%\begin{equation}
+%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+%\label{e:mass_bal}
+%\end{equation}
+
+%\begin{equation}
+%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+%\label{e:force_bal}
+%\end{equation}
+
+%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
 This system of equations can be rewritten to produce the pressure equation,
 
-\begin{equation}
-B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-\label{e:pressure_eq}
-\end{equation}
-
-\end{comment}
+%\begin{equation}
+%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+%\label{e:pressure_eq}
+%\end{equation}
+
+%\end{comment}
 %%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Numerical Formulation}\label{section:NumericalFormulation}
+\medskip
 The method developed is applicable to $\mathcal{N_{p}}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
@@
 
+%\begin{figure}[h] 
+%\centering
+%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+%\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
+%\label{fig:fem_elem}
+%\end{figure}
+
 \begin{figure}[h]
 \centering
-\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
 \caption{This is a description of two different element types.
@@
 %%%%%%%%%%%%%%%
-\begin{comment}
-Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-\begin{equation}
-\lambda = \frac{K\;k_{\alpha}}{\mu}
-\label{eq:mobility-of-fluid}
-\end{equation}
-
-\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+%\begin{comment}
+%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+%\begin{equation}
+%\lambda = \frac{K\;k_{\alpha}}{\mu}
+%\label{eq:mobility-of-fluid}
+%\end{equation}
+
+%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
 The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
@@
 
-\begin{equation}
- U = \frac{b^2}{12 \mu} \nabla p
-\end{equation}
-
-and the above equation can be re-arranged for 1D steady flow as,
-
-\begin{equation}
-\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
-\label{eq:pressure_dif} 
-\end{equation}
-
-where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
+%\begin{equation}
+%U = \frac{b^2}{12 \mu} \nabla p
+%\end{equation}
+
+%and the above equation can be re-arranged for 1D steady flow as,
+
+%\begin{equation}
+%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
+%\label{eq:pressure_dif} 
+%\end{equation}
+
+%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
 Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
@@
 
-\begin{equation}
-\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-\end{equation}
-
-If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
-
-\begin{equation}
-U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-\end{equation}
-\end{comment}
+%\begin{equation}
+%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
+%\end{equation}
+
+%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
+
+%\begin{equation}
+%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
+%\end{equation}
+%\end{comment}
 %%%%%%%%%%%%%%%
@@
 
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
+%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
+%\label{fig:simple_case}
+%\end{center}
+%\end{figure}
+
 \begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
+\centering
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
 \caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
 \label{fig:simple_case}
-\end{center}
 \end{figure}
@@
 
-\begin{figure}[h]
-\begin{center}
-\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
-\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
-\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+%\begin{figure}[h]
+%\begin{center}
+%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
+%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
+%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
 The mesh is unstructured and fixed with 5000 elements.
 Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
-\label{fig:square}
-\end{center}
-\end{figure}
+%\label{fig:square}
+%\end{center}
+%\end{figure}
+
+\begin{figure}[h]
+   \vbox{
+       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
+             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
+       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+    \label{fem_cv_represent_a}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/2b2_P1DGP2.pdf}
+      \vspace{1.0cm} (a)
+      %\hspace{0.0cm} (a)
+      %\vspace{0.0cm} (a)
+      \includegraphics[width=.75\textwidth]{./Pics/2b2_P1DGP2.pdf}
+      \vspace{0.0cm} (b)
+      %\hspace{0.0cm} (b)
+      %\vspace{0.0cm} (b)  
+}     
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fem_cv_represent_a}
+\end{figure}
+
+\begin{comment}
 
@@
 
+\begin{figure}[htbp]                
+\centering
+\includegraphics{./Pics1/5reg_dinlet_fixed_500.pdf}
+\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_b}
+\end{figure}
+
 %\begin{comment}
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+%\begin{figure}
+%\centering
+%\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
+%\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+%\label{fig:3testcase_b}
+%\end{figure}
+
+\begin{figure}[h]
+\makebox[\textwidth]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+\hfill    
+\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+}\\[0.5cm]% If you want some vertical space
+\makebox[\textwidth]{%
+\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+\hfill    
+\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+}%
 \caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
@@
 
+\end{comment}
+
 \end{document}

### 2017-04-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
updated

@@
 
+%\begin{figure}[h]
+%   \vbox{
+%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
+%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
+%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
+%\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+%    \label{fem_cv_represent_a}
+%\end{figure}
+
 \begin{figure}[h]
 \vbox{
-       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
-             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
-       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a)  
+}
+\vspace{0.5cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
+}
+\vspace{1.0cm}
+\hbox{\hspace{5.0cm} (b)  
+}}     
 \caption{2D representation of the element pairs presented in this work.
@@
 
+\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
+The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
+There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see Fig.\ref{fig:square}) while the phase volume fraction is constant.
+
+\medskip
+A slightly modified test-case (see Fig.\ref{fig:testcase}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$.
+The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
+The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
+
 \begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/2b2_P1DGP2.pdf}
-      \vspace{1.0cm} (a)
-      %\hspace{0.0cm} (a)
-      %\vspace{0.0cm} (a)
-      \includegraphics[width=.75\textwidth]{./Pics/2b2_P1DGP2.pdf}
-      \vspace{0.0cm} (b)
-      %\hspace{0.0cm} (b)
-      %\vspace{0.0cm} (b)  
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilties K  
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000  
+}
 }     
@@
 
-\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
-The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see Fig.\ref{fig:square}) while the phase volume fraction is constant.
-
-\medskip
-A slightly modified test-case (see Fig.\ref{fig:testcase}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$.
-The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
-The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
-
 \begin{figure}[h]
@@
 \subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{c}}
-\caption{In this test-case an unstructured mesh is used.
-Permeability $K=1$ at the blue region and $K=2.5$ at the red region.
-The aspect ratio is 2 (a), which allows the flow to develop for longer.
-Simulation time step increases from (b) to (c) and from t=250(start) to t=3000(end).}
-\label{fig:testcase}
+
 \end{center}
@@
 \end{figure}
-\end{comment}
+
+%\end{comment}
 

### 2017-04-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 \vbox{
-\hbox{\hspace{2.5cm}
+\hbox{\hspace{1.5cm}
 \includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
@@
 \vspace{0.25cm}
-\hbox{\hspace{2.5cm}
+\hbox{\hspace{1.5cm}
 \includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
@@
 \vspace{0.25cm}
-\hbox{\hspace{2.5cm}
+\hbox{\hspace{1.5cm}
 \includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
@@
 }     
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\caption{........}
 \label{fem_cv_represent_a}
-\end{figure}
-
-\begin{comment}
-
-\begin{figure}[h]
-\begin{center}
-\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf}\label{a}}
-\subfigure[flow at t=250]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}\label{b}}
-\subfigure[flow at t=3000]{\includegraphics[width=0.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}\label{c}}
-
-\end{center}
 \end{figure}
@@
 The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
+
+\begin{comment}
 

### 2017-05-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 \usepackage{epsfig}
-\usepackage{subfig}
+%\usepackage{subfig}
 \usepackage{comment}
@@
 }     
-\caption{........}
+\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
 \label{fem_cv_represent_a}
@@
 The third test-case is based in the initial and boundary condition of the second set of simulations.
-Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:1testcase}) and how the cross-flow as well as the simulation will progress on time.
+Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a},\ref{fig:6b},\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
 The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
 
-\begin{comment}
-
 \begin{figure}[h]
-\makebox[\textwidth]{%
-\subfigure[MR1]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
-}%
-\hfill    
-\subfigure[MR10]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR1]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
-}%
-\hfill    
-\subfigure[MR10]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR1]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
-}%
-\hfill    
-\subfigure[MR10]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
-}}%
-\caption{Comparing MR1 and MR10 cases using fixed mesh using the same map of permeabilities as test-case in Fig.\ref{fig:testcase}.
-Simulation time step increases from top to bottom and from (a,b) t=100(start) to (e,f) t=3000(end).}
-\label{fig:1testcase}
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
+\label{fig:6a}
+\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
+\label{fig:6b}
+\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
+\label{fig:6c}
 \end{figure}
@@
 For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
+
+\begin{comment}
 

### 2017-05-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 
-\begin{comment}
-
-\begin{figure}
-\centering
-\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}}\\[2mm]%
-\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
 \caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}\\[2mm]%
-\subfigure[flow at t=2500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=2500  
+}
+}     
 \caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=3500]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf}}\\[2mm]%
-\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=3500   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end  
+}
+}     
 \caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
@@
 %%%%%%%%%%%%%
-\begin{figure}
-\centering
-\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}}\\[2mm]%
-\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
 \caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=1000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}\\[2mm]%
-\subfigure[flow at t=4000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=4000  
+}
+}     
 \caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}}\\[2mm]%
-\subfigure[flow at t=end]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end   
+}
+}     
 \caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
@@
 %%%%%%%%%%%%%
-\begin{figure}
-\centering
-\subfigure[Hell-Shaw cell domain]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}}\\[2mm]%
-\subfigure[flow at t=250]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
 \caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=2000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf}}\\[2mm]%
-\subfigure[flow at t=3000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=2000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000     
+}
+}     
 \caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=6000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}}\\[2mm]%
-\subfigure[flow at t=24000]{\includegraphics[width=0.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000    
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=24000     
+}
+}     
 \caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
@@
 \begin{figure}[h]
-\begin{center}
-\subfigure[map of permeabilties K]{\includegraphics[width=0.75\textwidth]{./Pics/map_of_boundaries.pdf}\label{a}}
-\subfigure[permeabilities using an unstructured and fixed computational domain]{\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}\label{b}}
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilties K   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b)      
+}
+}     
 \caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
@@
 \label{fig:testcase_heter_domain}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[flow at t=250 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf}}\\[2mm]%
-\subfigure[flow at t=250 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}}%
+\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=250   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
 \caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf}}\\[2mm]%
-\subfigure[flow at t=500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
+}
+}     
 \caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
@@
 
-\begin{figure}
-\centering
-\subfigure[flow at t=1500 (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf}}\\[2mm]%
-\subfigure[flow at t=1500 (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
+}
+}     
 \caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
@@
 \begin{figure}
-\centering
-\subfigure[flow at t= end (fixed mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf}}\\[2mm]%
-\subfigure[flow at t= end (adaptive mesh)]{\includegraphics[width=0.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}}%
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
+}
+}     
 \caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
@@
 
-\begin{figure}
-\centering
-\subfigure[map of permeabilities]{\includegraphics[width=0.75\textwidth]{./Pics1/map_of_perm_1.pdf}}\\[2mm]%
-\subfigure[flow at start]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}}%
+%\begin{figure}[h]
+%\vbox{
+%\hbox{\hspace{3.5cm}
+%\includegraphics[width=.5\textwidth]{} 
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{5.0cm} (a)    
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{3.5cm}
+%\includegraphics[width=.5\textwidth]{}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{5.0cm} (b)      
+%}
+%}     
+%\caption{}
+%\label{}
+%\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/map_of_perm_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilities   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at start      
+}
+}     
 \caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
@@
 
-\begin{comment}
-\begin{figure}
-\makebox[\textwidth]{%
-\subfigure[[MR10 fixed mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh start]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh t=1500]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh t=1500]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh t=7500]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_2000.pdf}%
-}%
-\hfill    
-\subfigure[MR10 adapt mesh t=7500]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_2000.pdf}%
-}}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\subfigure[MR10 fixed mesh end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}%
-}%
-\hfill    
-\subfigure[MR10 fixed adapt end]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_end.pdf}%
-}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) MR10 fixed mesh start    
+}
+\vspace{0.25cm}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) MR10 adapt mesh start     
+}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (c) MR10 fixed mesh t=1500      
+}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (d) MR10 adapt mesh t=1500     
+}
+}     
+\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
+\label{fig:3testcase_a}
+\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (e) MR10 fixed mesh t=7500    
+}
+\vspace{0.25cm}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (f) MR10 adapt mesh t=7500      
+}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (g) MR10 fixed mesh end      
+}
+
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end]     
+}
+}     
 \caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
 When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
-%\caption{Comparing the MR=$10$, between single and double injection of fluid $1$ under the adaptive and unstructured mesh for the same time steps, t=100(a,b), t=1500(c,d), t=7500(e,f), t=10000(g,h) }
-\label{fig:3testcase}
-\end{figure}
-
-%\end{comment}
-
-\begin{figure}[htbp]                
+\label{fig:3testcase_b}
+\end{figure}
+
+\begin{figure}                
 \centering
@@
 %\end{figure}
+
+\begin{comment}
 

### 2017-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 %% if you use PostScript figures in your article
-%% use the graphics package for simple commands
+%% use the gra
+
+%%graphis package for simple commands
 %% \usepackage{graphics}
@@
 }     
-\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
+\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
 \label{fig:2testcase_c}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \vbox{
@@
 \vspace{0.25cm}
-
 \hbox{\hspace{3.5cm}
@@
 }
-
 \hbox{\hspace{3.5cm}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{} 
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_1500.pdf} 
 }
@@
 \vspace{0.25cm}
-
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_1500.pdf}
 }
@@
 }
-
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
 }
@@
 }
-
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end]     
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end     
 }
@@
 
-\begin{figure}                
-\centering
-\includegraphics{./Pics1/5reg_dinlet_fixed_500.pdf}
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
 \caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
@@
 
-%\begin{comment}
-%\begin{figure}
-%\centering
-%\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
-%\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
+%\begin{figure}[h]
+%\makebox[\textwidth]{%
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+%\hfill    
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+%}\\[0.5cm]% If you want some vertical space
+%\makebox[\textwidth]{%
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+%\hfill    
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+%}%
 %\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
@@
 %\end{figure}
-
-\begin{comment}
-
-\begin{figure}[h]
-\makebox[\textwidth]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-\hfill    
-\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-}\\[0.5cm]% If you want some vertical space
-\makebox[\textwidth]{%
-\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-\hfill    
-\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-}%
-\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_b}
-\end{figure}
 

### 2017-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/map_of_perm_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilities   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/5reg_dinlet_adapt_100.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at start      
-}
-}     
-\caption{In fig.(a) there is the map of permeabilities as this will be implemented in this case while in fig.(b) there is an illustration of the adaptive mesh just in the beggining of the simulation.}
-\label{fig:3testcase_a}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR10 fixed mesh start    
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 adapt mesh start     
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (c) MR10 fixed mesh t=1500      
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (d) MR10 adapt mesh t=1500     
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_start.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
 }
@@
 \label{fig:3testcase_a}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (e) MR10 fixed mesh t=7500    
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (f) MR10 adapt mesh t=7500      
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (g) MR10 fixed mesh end      
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end     
-}
-}     
-\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h).
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
-\label{fig:3testcase_b}
 \end{figure}
@@
 
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=1500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
 \caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
@@
 
-\begin{figure}
-\centering
-\subfigure[fixed mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf}}\\[2mm]%
-\subfigure[adaptive mesh, t=end]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}}%
-\caption{for t=end of simulation, there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
 \label{fig:3testcase_d}
 \end{figure}
-%\end{comment}
 
@@
 Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_d}
+\end{figure}
 

### 2017-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated with vbox some errors l.964

@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_d}
-\end{figure}
-
-\begin{figure}
-\centering
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
-\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
-\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
-\label{fig:4testcase}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase_a}
+\end{figure}
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
+\label{fig:4testcase_b}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{figure}[h!]
-%\includegraphics[width=0.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_vel_magn.png}\\[2mm]%
-\subfigure[single inlet velocity magnitude]{\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf}}\\[2mm]%
-\subfigure[double inlet velocity magnitude]{\includegraphics[width=0.49\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}}%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
+}
+}     
 \caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
@@
 is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn2}
-\end{figure}
-\end{comment}
+\label{fig:vel_magn}
+\end{figure}
 

### 2017-05-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
Updates: Removing errors with figures and citations. Still missing figures references

@@
 
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_100.pdf} 
+%%%%
+%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
+%%%%
+
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_start.pdf}
+  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
 }
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{comment}
 \section{Achknowledgements}
@@
 Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).
-Last but not least credit should be given to both Dr Jefferson Gomes \& Dr Marcus Campell Bannerman, both lecturers at the University of Aberdeen, at the School of Engineering.
-\end{comment}
 
@@
 
-\end{comment}
-
 \end{document}

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 \medskip
-Numerical investigation and modeling of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterization of the flow of fluids through porous media serves as the foundation of reservoir engineering studies.
-Oil and gas migration and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
+Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Characterisation of fluid flow through porous media serves as the foundation of reservoir engineering and groundwater studies.
+%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification for the mining industry is an important area of interest, but more recently, also due to global environmental problems, most research has focused on the CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-Underground coal gasification, for the mining industry is an important area of interest, but more recently, due to global environmental problems, most research has focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilization and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-
-\medskip
-Due to complex and/or heterogeneous geological formations, multiphase flows through porous media play an important role in understanding the afformentioned operations.
-Modeling of multiphase flow is an enormous technical and computational challenge.
-Important contributions regarding the description of physics and mechanisms related with multiphase flows have been made by \citet{wooding_1976} as far as the importance of capillary pressure and the flow regimes in capillary media.
-From \citet{homsy_1987} we have an extensive desrciption of the mechanisms of fingering and how these are related with the forces acting on the interface between two immiscible fluids, and from \citet{adler_1988} there is an extensive description of both microscopic and macroscopic scale darcy-equations.
+Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes.
+Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media.
+A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(COULD YOU BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD???)}.
 Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}.

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(COULD YOU BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD???)}.
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.
 Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}.

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.
-Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958}.
+Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
 The first distinction should be made between microscopic and macroscopic instabilities.
 Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand the macroscopic instabilities involves two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena for a two-phase system.
-A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering}.
-
-\medskip
-In large scale field oil and gas operations, viscous or density fingers are relatively common in reservoirs with water-injection wells.
+On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
+This paper will focus on microscopic instabilities and phenomena in two-phase systems.
+A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
+
+\medskip
+In oil and gas reservoir exploration, viscous and density fingers are relatively common in reservoirs with water-injection wells.
 As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
-
-\medskip
-In oil and gas reservoir exploration, viscous and density fingers are relatively common in reservoirs with water-injection wells.
-As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
-The result of fingering is an inefficient sweeping efficiency that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of mobility (MR) of the displacing and the displaced fluids (mobility-ratio, MR).
-%In a water-oil system the MR is given by eq.\ref{eq:MR}.
-
-\medskip
-In large scale field O$\&$G operations, viscous or density fingering is a relatively common condition in reservoirs with water-injection wells.
-As water and oil interacts, the interface between those two fluids moves along the geological formation, creating an uneven, or fingered, profile (see Fig.\ref{fig:simple_case}.
-The result of fingering is an inefficient sweeping action that can bypass significant volumes of recoverable oil and, in severe cases, an early breakthrough of water into adjacent production wellbores.
-This instability is mainly governed by the ratio of mobility (MR) of the displacing fluid and the of the displaced fluid (mobility-ratio, MR).
-%In a water-oil system the MR is given by eq.\ref{eq:MR}.
-However, other important factors that also influence the severity of viscous fingering are: heterogeneous permeability fields, gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
+As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
 
@@
 
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
-%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
-%\label{fig:fem_cv}
-%\end{figure}
-
-%\begin{figure}[h]
-%   \vbox{
-%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
-%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
-%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
-%\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-%    \label{fem_cv_represent_a}
-%\end{figure}
-
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
-\label{fig:fem_cv}
-\end{figure}
-
 %%%%%%%%%%%%%%%
@@
 
-%\begin{figure}[h] 
-%\centering
-%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-%\caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
-%\label{fig:fem_elem}
-%\end{figure}
-
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
-\caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
-\label{fig:fem_elem}
-\end{figure}
-
 Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\centering
-%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
-%\caption{Caption 3}
-%\label{fig:subim3}
-%\end{center}
-
-%\caption{Caption for this figure with two images}
-%\label{fig:image1}
-%\end{figure}
-%\pagebreak
-%\clearpage
-
-\pagebreak
-\clearpage
-
-\pagebreak
-\clearpage
-%\input{article_figure1}
-%\input{Manuscript_Figure1}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
-%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
-%\label{fig:simple_case}
-%\end{center}
-%\end{figure}
-
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
-\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
-\label{fig:simple_case}
-\end{figure}
 
@@
 
-%\begin{figure}[h]
-%\begin{center}
-%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
-%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
-%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
-The mesh is unstructured and fixed with 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
-%\label{fig:square}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[h]
-%   \vbox{
-%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
-%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
-%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
-%\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-%    \label{fem_cv_represent_a}
-%\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a)  
-}
-\vspace{0.5cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
-}
-\vspace{1.0cm}
-\hbox{\hspace{5.0cm} (b)  
-}}     
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fem_cv_represent_a}
-\end{figure}
-
 \noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
@@
 The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000  
-}
-}     
-\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
-\label{fem_cv_represent_a}
-\end{figure}
 
@@
 
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
-\label{fig:6a}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
-\label{fig:6b}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
-\label{fig:6c}
-\end{figure}
-
 %%%%%%%%%%%%
@@
 For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
-\label{fig:1a_homoheleshaw_3}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=2500  
-}
-}     
-\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
-\label{fig:1b_homoheleshaw_3}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=3500   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end  
-}
-}     
-\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:1c_homoheleshaw_3}
-\end{figure}
-
-%%%%%%%%%%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
-\label{fig:2a_homoheleshaw_10}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
-}
-}     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end   
-}
-}     
-\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:2c_homoheleshaw_10}
-\end{figure}
-
-%%%%%%%%%%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
-\label{fig:3a_heteheleshaw_10}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=2000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000     
-}
-}     
-\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
-Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
-\label{fig:3b_heteheleshaw_10}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000    
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=24000     
-}
-}     
-\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
-At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
-\label{fig:3c_heteheleshaw_10}
-\end{figure}
-
-%{./Pics/P1DG-P2_element_type} 
-%{./Pics/4r_po_adapt_fine_125_mesh} 
-%{./Pics/4r_po_adapt_fine_100_mesh}
 
@@
 
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b)      
-}
-}     
-\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
-Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
-\label{fig:testcase_heter_domain}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=250   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
-There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
-\label{fig:2testcase_a}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
-}
-}     
-\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
-\label{fig:2testcase_b}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
-}
-}     
-\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
-\label{fig:2testcase_c}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
-}
-}     
-\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
-\label{fig:2testcase_d}
-\end{figure}
-
-%%%%%%%%%%%%%
 \subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}
@@
 
-%\begin{figure}[h]
-%\vbox{
-%\hbox{\hspace{3.5cm}
-%\includegraphics[width=.5\textwidth]{} 
-%}
-%\vspace{0.0cm}
-%\hbox{\hspace{5.0cm} (a)    
-%}
-%\vspace{0.25cm}
-%\hbox{\hspace{3.5cm}
-%\includegraphics[width=.5\textwidth]{}
-%}
-%\vspace{0.0cm}
-%\hbox{\hspace{5.0cm} (b)      
-%}
-%}     
-%\caption{}
-%\label{}
-%\end{figure}
-
-%%%%
-%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
-%%%%
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
-\label{fig:3testcase_a}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_b}
-\end{figure}
-
-%\begin{figure}[h]
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}\\[0.5cm]% If you want some vertical space
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}%
-%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-%\label{fig:3testcase_b}
-%\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_c}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_d}
-\end{figure}
-
 The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
 Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-\label{fig:4testcase_a}
-\end{figure}
-
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
-\label{fig:4testcase_b}
-\end{figure}
 
@@
 
-%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
-}
-}     
-\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
-The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
-While there
-is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn}
-\end{figure}
-
 \medskip
@@
 
-\begin{comment}
-\begin{landscape}
-\begin{figure}[ht!]
-\begin{center}
-\subfigure[MR100, at the beginning of the simulations]{%
-\label{fig:1st}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
-}%
-\subfigure[MR100, at the middle of the simulation]{%
-\label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
-}\\
-\subfigure[MR100, Phase 1 Volume fraction]{%
-\label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
-}%
-\subfigure[MR100, Phase 2 Volume fraction]{%
-\label{fig:4th}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
-}\\
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:5}
-\end{center}
-\end{figure}
-\end{landscape}
-\end{comment}
-
 \section{Achknowledgements}
@@
 Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).
-
-\clearpage
-\listoffigures
 
@@
 
+\clearpage
+\listoffigures
+\clearpage
+
+\input{article_figure1}
+%\input{article_figure2}
+
 \end{document}

### 2017-05-07 Papers/ViscousInstabilities/article_figure1.tex
Updates: starting revising Introduction

%\begin{figure}[h]
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
%\label{fig:fem_cv}
%\end{figure}

%\begin{figure}[h]
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

%%%%
%%%%  FIGURE 1
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue). The ratio of viscosity between the two fluids is 5. In this case, the initially piston shape front collapses leading to the formation of several fingers.}
\label{fig:simple_case}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work. Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
\label{fig:fem_cv}
\end{figure}

%\begin{figure}[h] 
%\centering
%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
%\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
%\label{fig:fem_elem}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
\caption{This is a description of two different element types. Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$. Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$. The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element. Saturation and saturation-dependent variables are stored CV-wise. }
\label{fig:fem_elem}
\end{figure}

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\centering
%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
%\caption{Caption 3}
%\label{fig:subim3}
%\end{center}

%\caption{Caption for this figure with two images}
%\label{fig:image1}
%\end{figure}
%\pagebreak
%\clearpage

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
%\label{fig:simple_case}
%\end{center}
%\end{figure}

%\begin{figure}[h]
%\begin{center}
%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region. The mesh is unstructured and fixed with 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
%\label{fig:square}
%\end{center}
%\end{figure}

%\begin{figure}[h]
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{5.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end   
}
}     
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}
%{./Pics/P1DG-P2_element_type} 
%{./Pics/4r_po_adapt_fine_125_mesh} 
%{./Pics/4r_po_adapt_fine_100_mesh}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=250   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
%%%%
%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

%\begin{figure}[h]
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}\\[0.5cm]% If you want some vertical space
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}%
%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
%\label{fig:3testcase_b}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_d}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
\label{fig:4testcase_b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
}
}     
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}. The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns. While there 
is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
\label{fig:vel_magn}
\end{figure}

%%%%
%%%%  FIGURE
%%%%

\begin{comment}
\begin{landscape}
\begin{figure}[ht!]
\begin{center}
\subfigure[MR100, at the beginning of the simulations]{%
\label{fig:1st}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
}%
\subfigure[MR100, at the middle of the simulation]{%
\label{fig:2nd}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
}\\
\subfigure[MR100, Phase 1 Volume fraction]{%
\label{fig:3rd}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
}%
\subfigure[MR100, Phase 2 Volume fraction]{%
\label{fig:4th}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
}\\
\caption{Comparison of different MR's and their recovery rates}
\label{fig:5}
\end{center}
\end{figure}
\end{landscape}
\end{comment}

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
+
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
@@
 \medskip 
-Conservation of mass along with the Darcy's law are the governing equations that describe the flow dynamics in porous media.
+Conservation of mass and Darcy's law are the governing equations that describe the flow dynamics in porous media.
 Several computational methods have been developed to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc).
-%The FDM discretization is based upon the differential form of the PDE to be solved. 
-%Analytic models can be used to analyze reservoir performance as long as the reservoir is not highly heterogeneous.
-However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications.
+However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geological domains.
-FEM discretization is based upon a piecewise representation of the solution space  and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
+FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
+%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
 %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
 FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
@@
 
-\medskip
 Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In the CVFEM pressure is interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while saturation is represented in node centered CV basis functions respectively, and the saturation equations are solved explicitly after solving for pressure at each non-linear iteration.
+In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while saturation is represented in node centered CV basis functions.
+Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{lux_2012,chen_2006}.
 

### 2017-05-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction

@@
 while saturation is represented in node centered CV basis functions.
-Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{lux_2012,chen_2006}.
+Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
 

### 2017-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: starting revising Introduction
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 \usepackage{graphicx}
-\usepackage{subfigure}
+%\usepackage{subfigure}
 
@@
 
-Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while saturation is represented in node centered CV basis functions.
-Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+\medskip
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
 
@@
 
-\medskip
-%Through the $P_{1}DGP_{2}$ element type, 
-Material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
-%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
-%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
+These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
 In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
@@
 \medskip 
-The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFEM formulation that exploits adaptive mesh of fully-unstructured triangle and tetrahedron grids.
-Also two key characteristics that describe the research concept are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) dual representation of pressure and velocity fields in the FE and CV spaces.
-The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
+Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
+The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
 
 \medskip
-In the next sections the numerical formulation and a summary of the main governing equations for multiphase compositional flows will discussed.
-The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.
-The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
+A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
+Impact of mobility ratio on the fingers formation is also included in this section.
+The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
+Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
 
@@
 \medskip
-The two-phase flow through the porous media domain $\Omega$, may be described by the coupled extended Darcy and global mass conservation equations,
+The two-phase flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
 \begin{eqnarray}
@@
 \end{eqnarray}
-where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+respectively, where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
 $\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-
+$S_{\alpha}$ represents the saturation of the $\alpha$-phase with constraints of
+\begin{displaymath}
+\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
+\end{displaymath}
+where $\mathcal{N}_{p}$ denotes the number of phases.
 %%%%%%%%%%%%%%%
@@
 
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation %(Eqn.~\ref{e:darcy_eq}). 
-Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
+\begin{displaymath}
+   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
+\end{displaymath}
+Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2017}.
 
-\medskip
-The method developed is applicable to $\mathcal{N_{p}}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
-These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial for pressure.
-Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (Fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
-
+This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on the novel family of \PNDG[n]{m} element-pairs~\citep{cotter_2009a} consistent with the dual pressure-velocity representation in control volume (CV).
+In this family of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either discontinuous or continuous (thus the notation \PNDG[n]{m}) across elements.
+The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain the high-order fluxes on CV boundaries, which are limited to yield bounded fields~\citep{jackson_2013}.
+Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
 Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
-The pressure, a key difference to other CVFE methods reported previously, allows the use of CVs that do not span multiple FEs.
-Hence each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
 
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{Section:Conclusion}
 
@@
 
-\section{Achknowledgements}
+\section{Acknowledgements}
 Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.

### 2017-05-08 Papers/ViscousInstabilities/article_figure1.tex
Updates: starting revising Introduction
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
-%\begin{figure}[h]
+%\begin{figure}[ht]
 %\centering
@@
 
-%\begin{figure}[h]
+%\begin{figure}[ht]
 %   \vbox{
@@
 %%%%
-\begin{figure}[h]
+\begin{figure}[ht]
 \centering
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
-\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
+\vbox{\includegraphics[width=\textwidth]{./Pics/phase_vol_frac_uni_perm_1}}
+\caption{Schematics of flow instabilities during injection of a pure low viscosity fluid (left-hand side in red) into a domain saturated with a second fluid (dark blue).
 The ratio of viscosity between the two fluids is 5.
@@
 %%%%
-%%%%  FIGURE
+%%%%  FIGURE 2
 %%%%
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/P1DGP2}}
+\hbox{\hspace{6cm}(a)}
+\vspace{.5cm}
+\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/element_n}}
+\hbox{\hspace{6cm}(b)}}
+\caption{Sketches of FE-pairs: (a) 2D representation of the \PN[1]{2} element-pair used in this work.
+Shaded areas denote control volumes (in which scalar fields such as phase saturation, temperature, density etc are stored); blue and white circles represent pressure and velocity nodes, respectively.
+(b) Simplified representation of field storage in a \PN[1]{1} element-pair: permeability $\left(K_{i}\right)$ and porosity $\left(\phi_{i}\right)$ are stored in $P_{0}DG$ space ($A$), whereas all other scalar fields (e.g., saturation, density, viscosity, relative permeability etc) are stored in CV space ($B$).
+\red{(KOSTAS, COULD YOU: (a) REPLACE 1 BY i (top quad of ELEMENT B) AND (b) REMOVE THE WHITE CIRCLES IN ELEMENT A)}.}
 \label{fig:fem_cv}
 \end{figure}
-
-%\begin{figure}[h] 
-%\centering
-%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-%\caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
-%\label{fig:fem_elem}
-%\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
-\caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
-\label{fig:fem_elem}
-\end{figure}
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\centering
-%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
-%\caption{Caption 3}
-%\label{fig:subim3}
-%\end{center}
-
-%\caption{Caption for this figure with two images}
-%\label{fig:image1}
-%\end{figure}
-%\pagebreak
-%\clearpage
-
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
-%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
-%\label{fig:simple_case}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[h]
-%\begin{center}
-%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
-%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
-%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
-The mesh is unstructured and fixed with 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
-%\label{fig:square}
-%\end{center}
-%\end{figure}
-
-%\begin{figure}[h]
-%   \vbox{
-%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
-%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
-%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
-%\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-%    \label{fem_cv_represent_a}
-%\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a)  
-}
-\vspace{0.5cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
-}
-\vspace{1.0cm}
-\hbox{\hspace{5.0cm} (b)  
-}}     
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fem_cv_represent_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000  
-}
-}     
-\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
-\label{fem_cv_represent_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
-\label{fig:6a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
-\label{fig:6b}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
-\label{fig:6c}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
-\label{fig:1a_homoheleshaw_3}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=2500  
-}
-}     
-\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
-\label{fig:1b_homoheleshaw_3}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=3500   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end  
-}
-}     
-\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:1c_homoheleshaw_3}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
-\label{fig:2a_homoheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
-}
-}     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
-}
-}     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end   
-}
-}     
-\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:2c_homoheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
-\label{fig:3a_heteheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=2000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000     
-}
-}     
-\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
-Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
-\label{fig:3b_heteheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000    
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=24000     
-}
-}     
-\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
-At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
-\label{fig:3c_heteheleshaw_10}
-\end{figure}
-%{./Pics/P1DG-P2_element_type} 
-%{./Pics/4r_po_adapt_fine_125_mesh} 
-%{./Pics/4r_po_adapt_fine_100_mesh}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b)      
-}
-}     
-\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
-Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
-\label{fig:testcase_heter_domain}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=250   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
-There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
-\label{fig:2testcase_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
-}
-}     
-\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
-\label{fig:2testcase_b}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
-}
-}     
-\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
-\label{fig:2testcase_c}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
-}
-}     
-\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
-\label{fig:2testcase_d}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-%%%%
-%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
-\label{fig:3testcase_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_b}
-\end{figure}
-
-%\begin{figure}[h]
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}\\[0.5cm]% If you want some vertical space
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}%
-%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-%\label{fig:3testcase_b}
-%\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_c}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_d}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-\label{fig:4testcase_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
-\label{fig:4testcase_b}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
-}
-}     
-\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
-The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
-While there
-is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-
-\begin{comment}
-\begin{landscape}
-\begin{figure}[ht!]
-\begin{center}
-\subfigure[MR100, at the beginning of the simulations]{%
-\label{fig:1st}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
-}%
-\subfigure[MR100, at the middle of the simulation]{%
-\label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
-}\\
-\subfigure[MR100, Phase 1 Volume fraction]{%
-\label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
-}%
-\subfigure[MR100, Phase 2 Volume fraction]{%
-\label{fig:4th}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
-}\\
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:5}
-\end{center}
-\end{figure}
-\end{landscape}
-\end{comment}

### 2017-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 
-In this model we assume that rock and fluids are incompressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
-
-\begin{equation}
-\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
-\label{mass_balance}
-\end{equation}
+%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
+%\begin{equation}
+%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
+%\label{mass_balance}
+%\end{equation}
 
@@
 
-Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method %\citep{saramito_1994}. 
-Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
+Equation~\ref{eqn:saturation_eqn} is discretized in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
 
@@
  &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
- &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0
+ &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0,
 \label{global_mass_balance}
 \end{eqnarray}
-
-\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
+This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
 

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{gomes_2017}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 
-This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on the novel family of \PNDG[n]{m} element-pairs~\citep{cotter_2009a} consistent with the dual pressure-velocity representation in control volume (CV).
-In this family of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either discontinuous or continuous (thus the notation \PNDG[n]{m}) across elements.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain the high-order fluxes on CV boundaries, which are limited to yield bounded fields~\citep{jackson_2013}.
+This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
 Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
+Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
 %Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
@@
 
-Equation~\ref{eqn:saturation_eqn} is discretized in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
-
+Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
 \begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
- &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0,
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
 \label{global_mass_balance}
 \end{eqnarray}
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
-Under this assumption when a fluid is injected in a porous domain saturated with another fluid trying to displace it, viscous fingering will occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+
 This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 
-This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.
-Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon.
-The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap.
-The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law).
-More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
+Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
+Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ...
+WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.
 
 \medskip
-In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell).
-\citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
-For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
+In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
+The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ...
+SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN?
+...
+TRY TO REWRITE THE SENTENCE)}.
+More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
+
+\medskip
+ During the displacement of a fluid by a less viscous one, the expected uniform front is broken \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long extensions of the fluids (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+In such viscous fluid instabilities, a less viscous fluid displaces a more viscous fluid For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
 In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
-Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
 
 \medskip
- During the displacement of a fluid by a less viscous one, the expected uniform front is broken \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long extensions of the fluids (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
-In such viscous fluid instabilities, a less viscous fluid displaces a more viscous fluid For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
-In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.
+ Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+The interface becomes unstable and collapses, taking a curved shape.
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX.
 The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
 The interface becomes unstable and collapses, taking a curved shape.
+
 In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX.
-The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger will be.
 In addition, pressure differences %(eq.\ref{eq:pressure_dif})

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

@@
 
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger will be.
-In addition, pressure differences %(eq.\ref{eq:pressure_dif})
-acting on the interface will produce a net pressure force,
-
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section \red{XXX}.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+In addition, pressure differences acting on the interface produces a net pressure force,
 \begin{equation}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section \red{XXX}.
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-In addition, pressure differences acting on the interface produces a net pressure force,
+Pressure differences acting on the interface produces a net pressure force,
 \begin{equation}
-\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
+\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
 \label{eq:pressure_dif} 
 \end{equation}
+This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
 
-\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
-As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.
-
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$)to that of the displaced fluid ($j$),
 \begin{equation}
- MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
 \label{eq:MR}
 \end{equation}
+MR is a function not only of fluid viscosities and saturations, but also the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 ...
-TRY TO REWRITE THE SENTENCE)}.
+TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}.
 More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
@@
 
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$)to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement, and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 \end{equation}
-MR is a function not only of fluid viscosities and saturations, but also the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{buckley_1942,sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
@@
 \end{equation}
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
 
-\noindent Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
+Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
 %As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
@@
 
-\pagebreak
-\clearpage
+%\pagebreak
+%\clearpage
 

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \\
+  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks}
+\end{eqnarray}
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
 

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 \begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \\
-  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
 \end{eqnarray}
@@
 
-Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
-%As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
-After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As surface tension becomes weak, the front is stressed and goes under a viscous-fingering instability.
-The front will collapse and will start splitting into new lobes of fingers.
-One of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
-In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
+From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the parameterised MR can be reduced to
+\begin{displaymath}
+    \text{MR} = \frc{\mu_{i}}{\mu_{j}},
+\end{displaymath}
+ i.e., the viscosity ratio.
+Fingering will occur in immiscible displacements when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+The interface collapses and starts splitting into new lobes of fingers.
+One of the fingers may eventually outgrow the others and then spread to occupy an increasingly larger width.
+In the process, the finger reaches a width that is again unstable and splits again, and the pattern repeats itself.
 Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the parameterised MR can be reduced to
+Therefore, with no lack of generality, the MR can be reduced to
 \begin{displaymath}
@@
  i.e., the viscosity ratio.
-Fingering will occur in immiscible displacements when the viscosity ratio is greater than unity.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
+\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
+
+Viscous fingering occurs in immiscible displacements when the viscosity ratio is greater than unity.
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 
-Viscous fingering occurs in immiscible displacements when the viscosity ratio is greater than unity.
+In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
 The interface collapses and starts splitting into new lobes of fingers.
-One of the fingers may eventually outgrow the others and then spread to occupy an increasingly larger width.
-In the process, the finger reaches a width that is again unstable and splits again, and the pattern repeats itself.
-Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
+Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
 
-In  this paper, viscous instabilities for different test-cases will be investigated.
-Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
-Initially test-cases that verify the existence of fingers in experimental domains will illustrated follow by more complicated computational domains and finger patterns.
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities \red{(Section XXX)}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid \red{(Section XXX)}; (c) the impact of viscosity ratios on the formation and progress of fingers \red{(Section XXX)}.
 

### 2017-05-09 Papers/ViscousInstabilities/article_figure1.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 \end{figure}
+
+%%%%
+%%%%  FIGURE 3
+%%%%
+\begin{figure}[ht]
+\vbox{
+\hbox{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2}}
+\vspace{-0.cm}
+\hbox{\hspace{5cm}(a)}
+\vspace{-0.cm}
+\hbox{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot}}
+\vspace{-0.cm}
+\hbox{\hspace{5cm}(b)}
+}\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+The mesh is unstructured and fixed with 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}\label{fig:square}
+\end{figure}
+
+%\begin{center}
+%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}%}
+%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{%./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
+%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+The mesh is unstructured and fixed with 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
+%\label{fig:square}
+%\end{center}
+%\end{figure}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 3 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing equations and numerical scheme}\label{equations_scheme}      
+\section{Model Formulation}\label{equations_scheme}      
 %Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Model Validation}\label{section:validation:results}
 
-%%%%%%%%%%%%
-\subsection{Model Validation}
+Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}}.
+A full description of the model can be found in \citet{gomes_2017,jackson_2015,pavlidis2016} \citep[see also][]{porosity_documentation,fluidity_manual}
 
@@
 The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+\citet{salinas_2016}
 
@@
 The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{section:results}
 

### 2017-05-10 Papers/ViscousInstabilities/article_figure1.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

--- 2017-05-08 Papers/ViscousInstabilities/article_figure1.tex
@@
 \end{figure}
+
+%%%%
+%%%%  FIGURE 3
+%%%%
+\begin{figure}[ht]
+\vbox{
+\hbox{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2}}
+\vspace{-0.cm}
+\hbox{\hspace{5cm}(a)}
+\vspace{-0.cm}
+\hbox{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot}}
+\vspace{-0.cm}
+\hbox{\hspace{5cm}(b)}
+}\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+The mesh is unstructured and fixed with 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}\label{fig:square}
+\end{figure}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

--- 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Model Validation}\label{section:validation:results}
 
-%%%%%%%%%%%%
-\subsection{Model Validation}
+Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,porosity_documentation,fluidity_manual}
+
+%,jackson_2015,pavlidis2016
 

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

--- 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Model Validation}\label{section:validation:results}
 
-%%%%%%%%%%%%
-\subsection{Model Validation}
+Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displecement, viscous crossflow etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+Two test-cases
 

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

--- 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to
+Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
 \begin{displaymath}
-    \text{MR} = \frc{\mu_{i}}{\mu_{j}},
+    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
 \end{displaymath}
- i.e., the viscosity ratio.
+ that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
 Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Model Validation}\label{section:validation:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{section:results}
 
-Numerical simulations performed for this work were conducted with the next generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,porosity_documentation,fluidity_manual}
+%%%%%%%%%%%% 
+\subsection{Model Set-up}\label{section:results:setup}
 
-%,jackson_2015,pavlidis2016
+Numerical simulations performed in this section were conducted with the next-generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+
+%%%%%%%%%%%% 
+\subsection{Model Validation}\label{section:results:validation}
+
+This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media
 
@@
 The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
-\citet{salinas_2016}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
-
 %%%%%%%%%%%%  
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}
 
@@
 \clearpage
+
+\listoftables
+\clearpage
+\input{article_table}
+\clearpage  
 \listoffigures
 \clearpage
-
 \input{article_figure1}

### 2017-05-10 Papers/ViscousInstabilities/article_table.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

\begin{table}
  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
    \hline
      {\bf Section} & $\phi$ & MR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
    \hline
      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
      \hline
   \end{tabular}
   \caption{Sumary of model set-up used in the numerical simulations. Superscript $0$ denotes initial condition. \red{(KOSTAS, PLEASE: DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES AND REPLACE ALL XX; $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}
\end{table}

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 
-Numerical simulations performed in this section were conducted with the next-generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+
+All test-cases were performed in an idealised geometry discretised with unstructured triangular \PN[1]{2} and \PN[1]{1} FE mesh.
+In most simulations, the domain was initially fully saturated with the non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity ($u$).
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$
 

### 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
 
-All test-cases were performed in an idealised geometry discretised with unstructured triangular \PN[1]{2} and \PN[1]{1} FE mesh.
-In most simulations, the domain was initially fully saturated with the non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity ($u$).
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$
+All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+Fluids are assumed incompressible and gravity was neglected.
+The set-up for the numerical simulations are summarised in Table \ref{table:setup}.
 

### 2017-05-10 Papers/ViscousInstabilities/article_table.tex
Updates: working on section 4 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic until find the problem. Edting section on fluid instabilities

@@
     \hline
-      {\bf Section} & $\phi$ & MR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
+      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
     \hline
@@
 Superscript $0$ denotes initial condition.
-\red{(KOSTAS, PLEASE: DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES AND REPLACE ALL XX; $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}
+\red{(KOSTAS, PLEASE: 1.
+DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2.
+REPLACE ALL XX; 3.
+COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.
+$S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
 \end{table}

### 2017-05-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-05-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.
-Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
+For a porous medium that is statistically homogenous two immiscible fluids are asumed to coexist together within a solid matrix.
+In a microscopic level fluids are newtonian and incompressible and gravity is the only external force acting on the system.
+An interfacial tension $\sigma$ is assumed to exist at the interfaces separating the two fluids.
+The main difference between microscopic and macroscopic level is the concept of capillary pressure.
+%\red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
@@
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena in two-phase systems.
-A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
+This paper will focus on microscopic instabilities and phenomena in two-phase systems while a this work will focus on a local flow instability due to viscous and stress forces, often referred as viscous instability or \textit{viscous fingering}.
 
@@
 
-\medskip
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+Among FEM-based formulations for porous media, the control volume finite element methods, ~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear finite element basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while saturation is represented in node centered CV basis functions.
+Saturation equations are solved explicitly after solving for pressure at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
 
@@
 
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
+\medskip
+%Through the $P_{1}DGP_{2}$ element type, 
+Material properties and flow conditions (e.g., density, temperature, species concentration etc) can be allocated in control volume space as shown in Fig.~\ref{fig:fem_cv}.
+%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
+%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
+Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
+Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
 In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
@@
 \medskip
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
-Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
-The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFEM formulation that exploits adaptive mesh of fully-unstructured triangle and tetrahedron grids.
+Also two key characteristics that describe the research concept are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) dual representation of pressure and velocity fields in the FE and CV spaces.
+The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
+Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
 
 \medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
-Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
-The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
-Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+In the next sections the numerical formulation and a summary of the main governing equations for multiphase compositional flows will discussed.
+The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.
+The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Formulation}\label{equations_scheme}      
+\section{Governing equations and numerical scheme}\label{equations_scheme}      
 %Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
@@
 \medskip
-The two-phase flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
+The two-phase flow through the porous media domain $\Omega$, may be described by the coupled extended Darcy and global mass conservation equations,
 \begin{eqnarray}
@@
 \end{eqnarray}
-respectively, where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
 $\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with constraints of
-\begin{displaymath}
-\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
-\end{displaymath}
-where $\mathcal{N}_{p}$ denotes the number of phases.
+$S_{\alpha}$ is saturation of the $\alpha$-phase with the constraint of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+
 %%%%%%%%%%%%%%%
@@
 
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
-\begin{displaymath}
-   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
-\end{displaymath}
-Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+\medskip
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation %(Eqn.~\ref{e:darcy_eq}). 
+Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
+Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
+The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 
-This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
-%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+\medskip
+The method developed is applicable to $\mathcal{N_{p}}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
+These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial for pressure.
+Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
+The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (Fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
 
-%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
-%\begin{equation}
-%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
-%\label{mass_balance}
-%\end{equation}
+Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
+The pressure, a key difference to other CVFE methods reported previously, allows the use of CVs that do not span multiple FEs.
+Hence each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+
+In this model we assume that rock and fluids are incompressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
+
+\begin{equation}
+\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha}
+\label{mass_balance}
+\end{equation}
 
@@
 
-Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
+Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method %\citep{saramito_1994}. 
+Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
+
 \begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+ && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
+ &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0
 \label{global_mass_balance}
 \end{eqnarray}
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
-$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+
+\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
-This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
 
@@
 The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
-Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
-
-Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ...
-WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.
+Under this assumption when a fluid is injected in a porous domain saturated with another fluid trying to displace it, viscous fingering will occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.
+Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon.
+The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap.
+The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law).
+More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
 
 \medskip
-In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ...
-SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN?
-...
-TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell).
+\citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
+For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
+In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.
+The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be.
+In addition, pressure differences %(eq.\ref{eq:pressure_dif})
+acting on the interface will produce a net pressure force,
 
-\medskip
- Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{buckley_1942,sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape.
-
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
 \begin{equation}
-\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
+\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
 \label{eq:pressure_dif} 
 \end{equation}
-This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
 
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
+As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.
+
 \begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
+ MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
 \label{eq:MR}
 \end{equation}
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
 
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
-\begin{displaymath}
-    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
-\end{displaymath}
- that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
-\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
+\noindent Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
+%As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
+After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
+As surface tension becomes weak, the front is stressed and goes under a viscous-fingering instability.
+The front will collapse and will start splitting into new lobes of fingers.
+One of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
+In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
+Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
 
-In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-The interface collapses and starts splitting into new lobes of fingers.
-One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
-Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
-
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities \red{(Section XXX)}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid \red{(Section XXX)}; (c) the impact of viscosity ratios on the formation and progress of fingers \red{(Section XXX)}.
+In  this paper, viscous instabilities for different test-cases will be investigated.
+Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
+Initially test-cases that verify the existence of fingers in experimental domains will illustrated follow by more complicated computational domains and finger patterns.
 
@@
 
-%\pagebreak
-%\clearpage
+\pagebreak
+\clearpage
 
@@
 %%%%%%%%%%%%
-\subsection{Model Set-up}\label{section:results:setup}
-
-Numerical simulations performed in this section were conducted with the next-generation reservoir simulator IC-FERST model\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
-
-%%%%%%%%%%%% 
-\subsection{Model Validation}\label{section:results:validation}
-
-This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media
+\subsection{Model Validation}
 
@@
 %%%%%%%%%%%%
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}
 
@@
 
-\section{Conclusions}\label{Section:Conclusion}
+\section{Conclusions}
 
@@
 
-\section{Acknowledgements}
+\section{Achknowledgements}
 Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
@@
 \clearpage
-
-\listoftables
-\clearpage
-\input{article_table}
-\clearpage  
 \listoffigures
 \clearpage
-\input{article_figure1}
+
+%\input{article_figure1}
 %\input{article_figure2}

### 2017-05-14 Papers/ViscousInstabilities/article_figure1.tex
updates

--- 2017-05-08 Papers/ViscousInstabilities/article_figure1.tex
@@
-%\begin{figure}[ht]
+%%%%%%%%%%%%%%%%
+%%% Figure 1 %%%
+%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+   \begin{center}
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+\label{fig:fem_cv}
+\end{center}
+\end{figure}
+
+\clearpage
+%%%%%%%%%%%%%%%%
+%%% Figure 2 %%%
+%%%%%%%%%%%%%%%%
+\begin{figure}[h] 
+   \begin{center}
+\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
+The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.}
+\label{fig:fem_elem}
+\end{center}
+\end{figure}
+
+\clearpage
+
+\begin{comment}
+%%%%%%%%%%%%%%%%%%%
+%%% Figure test %%%
+%%%%%%%%%%%%%%%%%%%
+\begin{figure} 
+   \vbox{
+      \hbox{\hspace{3cm}
+           \includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
+          \vspace{.1cm}
+             \hbox{\hspace{4cm}(a) flow at t=1000}
+           \vspace{1.cm}
+      \hbox{\hspace{3cm}
+           \includegraphics[width=0.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}}
+          \vspace{.1cm}
+             \hbox{\hspace{4cm}(a) flow at t=2500}}
+      \caption{As the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}\label{fig:1b_homoheleshaw_3}
+\end{figure}
+
+\clearpage
+\end{comment}
+
+%\begin{figure}[h]
 %\centering
@@
 
-%\begin{figure}[ht]
+%\begin{figure}[h]
 %   \vbox{
@@
 %%%%
-\begin{figure}[ht]
+\begin{figure}[h]
 \centering
-\vbox{\includegraphics[width=\textwidth]{./Pics/phase_vol_frac_uni_perm_1}}
-\caption{Schematics of flow instabilities during injection of a pure low viscosity fluid (left-hand side in red) into a domain saturated with a second fluid (dark blue).
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
+\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
 The ratio of viscosity between the two fluids is 5.
@@
 %%%%
-%%%%  FIGURE 2
+%%%%  FIGURE 
 %%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/P1DGP2}}
-\hbox{\hspace{6cm}(a)}
-\vspace{.5cm}
-\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/element_n}}
-\hbox{\hspace{6cm}(b)}}
-\caption{Sketches of FE-pairs: (a) 2D representation of the \PN[1]{2} element-pair used in this work.
-Shaded areas denote control volumes (in which scalar fields such as phase saturation, temperature, density etc are stored); blue and white circles represent pressure and velocity nodes, respectively.
-(b) Simplified representation of field storage in a \PN[1]{1} element-pair: permeability $\left(K_{i}\right)$ and porosity $\left(\phi_{i}\right)$ are stored in $P_{0}DG$ space ($A$), whereas all other scalar fields (e.g., saturation, density, viscosity, relative permeability etc) are stored in CV space ($B$).
-\red{(KOSTAS, COULD YOU: (a) REPLACE 1 BY i (top quad of ELEMENT B) AND (b) REMOVE THE WHITE CIRCLES IN ELEMENT A)}.}
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
+\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
 \label{fig:fem_cv}
 \end{figure}
+
+%\begin{figure}[h] 
+%\centering
+%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+%\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
+%\label{fig:fem_elem}
+%\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
+\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
+\label{fig:fem_elem}
+\end{figure}
+
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
+%\caption{Caption 1}
+%\label{fig:subim1}
+%\end{center}
+
+%\begin{center}
+%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
+%\caption{Caption 1}
+%\label{fig:subim1}
+%\end{center}
+
+%\begin{center}
+%\centering
+%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
+%\caption{Caption 3}
+%\label{fig:subim3}
+%\end{center}
+
+%\caption{Caption for this figure with two images}
+%\label{fig:image1}
+%\end{figure}
+%\pagebreak
+%\clearpage
+
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
+%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
+%\label{fig:simple_case}
+%\end{center}
+%\end{figure}
+
+%\begin{figure}[h]
+%\begin{center}
+%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
+%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
+%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
+The mesh is unstructured and fixed with 5000 elements.
+Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
+%\label{fig:square}
+%\end{center}
+%\end{figure}
+
+%\begin{figure}[h]
+%   \vbox{
+%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
+%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
+%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
+%\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+%    \label{fem_cv_represent_a}
+%\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.0cm} (a)  
+}
+\vspace{0.5cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
+}
+\vspace{1.0cm}
+\hbox{\hspace{6.0cm} (b)  
+}}     
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fem_cv_represent_a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilties K  
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000  
+}
+}     
+\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
+\label{fem_cv_represent_a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
+\label{fig:6a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
+\label{fig:6b}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
+\label{fig:6c}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.5cm} (a) Hele-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
+\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
+\label{fig:1a_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=2500  
+}
+}     
+\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
+\label{fig:1b_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=3500   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end  
+}
+}     
+\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:1c_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) Hele-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
+\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
+\label{fig:2a_homoheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=4000  
+}
+}     
+\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
+\label{fig:2b_homoheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{figure}[h]
+%\vbox{
+%\hbox{\hspace{3.5cm}
+%\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{5.0cm} (a) flow at t=1000   
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{3.5cm}
+%\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{5.0cm} (b) flow at t=4000  
+%}
+%}     
+%\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
+%\label{fig:2b_homoheleshaw_10}
+%\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end   
+}
+}     
+\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:2c_homoheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
+\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
+Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
+\label{fig:3a_heteheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=2000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000     
+}
+}     
+\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
+Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
+\label{fig:3b_heteheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000    
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=24000     
+}
+}     
+\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
+At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
+\label{fig:3c_heteheleshaw_10}
+\end{figure}
+%{./Pics/P1DG-P2_element_type} 
+%{./Pics/4r_po_adapt_fine_125_mesh} 
+%{./Pics/4r_po_adapt_fine_100_mesh}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilties K   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b)      
+}
+}     
+\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
+Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
+\label{fig:testcase_heter_domain}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=250   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
+\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
+There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
+\label{fig:2testcase_a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=500   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=500     
+}
+}     
+\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\label{fig:2testcase_b}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
+}
+}     
+\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\label{fig:2testcase_c}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
+}
+}     
+\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
+\label{fig:2testcase_d}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+%%%%
+%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
+\label{fig:3testcase_a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_b}
+\end{figure}
+
+%\begin{figure}[h]
+%\makebox[\textwidth]{%
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+%\hfill    
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+%}\\[0.5cm]% If you want some vertical space
+%\makebox[\textwidth]{%
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
+%\hfill    
+%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
+%}%
+%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+%\label{fig:3testcase_b}
+%\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_c}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_d}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase_a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
+\label{fig:4testcase_b}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
+}
+}     
+\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
+for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
+The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
+While there
+is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
+\label{fig:vel_magn}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht!]
+\begin{center}
+\subfigure[MR100, at the beginning of the simulations]{%
+\label{fig:1st}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
+}%
+\subfigure[MR100, at the middle of the simulation]{%
+\label{fig:2nd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
+}\\
+\subfigure[MR100, Phase 1 Volume fraction]{%
+\label{fig:3rd}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
+}%
+\subfigure[MR100, Phase 2 Volume fraction]{%
+\label{fig:4th}
+\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
+}\\
+\caption{Comparison of different MR's and their recovery rates}
+\label{fig:5}
+\end{center}
+\end{figure}
+\end{landscape}

### 2017-05-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

@@
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Underground coal gasification is another important area of interest.
+More recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
 
@@
 \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
-For a porous medium that is statistically homogenous two immiscible fluids are asumed to coexist together within a solid matrix.
+Immiscible displacements in porous media with both capillary and viscous effects can be characterized by two dimensionless numbers, the
+capillary number $C$ (macroscopic level), which is the ratio of viscous forces to capillary forces, and the ratio $M$ (or MR for both microscopic and macroscopic level) of the two viscosities.
+For certain values of these numbers, either viscous or capillary forces dominate leading to the following basic concepts, (a) viscous fingering (this will be described in the following sections), (b) capillary fingering or (c) stable displacement (cross flow with piston shape front characteristics).
+%In a porous medium that is statistically homogenous two immiscible fluids are asumed to coexist together within a solid matrix.
 In a microscopic level fluids are newtonian and incompressible and gravity is the only external force acting on the system.
@@
 The main difference between microscopic and macroscopic level is the concept of capillary pressure.
-%\red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} %\red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+A distinction should also be made between microscopic and macroscopic instabilities.
+The first describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.

### 2017-05-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated
Updated (saved in .txt just in case)

@@
+%  LocalWords:  checkboard
 % Copyright 2007, 2008, 2009 Elsevier Ltd
@@
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-A distinction should also be made between microscopic and macroscopic instabilities.
-The first describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+ A distinction should be made between microscopic and macroscopic instabilities.
+Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.

### 2017-05-16 Papers/PapersConferences/Abstract_SFMM2017.tex

\documentclass[12pts,a4paper,amsmath,amssymb,floatfix]{article}
\usepackage{graphicx,wrapfig}% Include figure files
%\usepackage{dcolumn,enumerate}% Align table columns on decimal point
\usepackage{bm,dpfloat}% bold math
\usepackage[pdftex,bookmarks,colorlinks=true,urlcolor=rltblue,citecolor=blue]{hyperref}
\usepackage{amsfonts,amsmath,amssymb,stmaryrd,indentfirst}
%\usepackage{chemist}
\usepackage{times,psfrag,subfigure}  
\usepackage{color}
\usepackage{gantt}
\usepackage{pdflscape}

\makeatletter

\newcommand{\cmd}[1]{\texttt{\textbackslash #1}}
\setlength{\parindent}{0pt}

\usepackage{enumerate}%,enumitem}% Align table columns on decimal point

\usepackage{supertabular}
\usepackage{moreverb}
\usepackage{listings}
\usepackage{palatino}
%\usepackage{doi}
\usepackage{longtable}
\usepackage{float}
%\MakeSorted{figure}
\usepackage{pdflscape}

\definecolor{rltblue}{rgb}{0,0,0.75}
\usepackage[round]{natbib}
\usepackage{color}

\setlength\textwidth      {16.cm}
\setlength\textheight     {21.6cm}
\setlength\oddsidemargin  {-0.3cm}
\setlength\evensidemargin {0.3cm}

\setlength\headheight{14.49998pt} 
\setlength\topmargin{0.0cm}
\setlength\headsep{1.cm}
\setlength\footskip{1.cm}
\setlength\parskip{0pt}
\setlength\parindent{0pt}

\makeatletter

%%%
%%% Notes
%%%
\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{\color{blue} JG: #1}}}

%%%
%%% space between lines
%%%
\renewcommand{\baselinestretch}{1.5}

\newenvironment{VarDescription}[1]%
  {\begin{list}{}{\renewcommand{\makelabel}[1]{\textbf{##1:}\hfil}%
    \settowidth{\labelwidth}{\textbf{#1:}}%
    \setlength{\leftmargin}{\labelwidth}\addtolength{\leftmargin}{\labelsep}}}%
  {\end{list}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%%      NOTATION SECTION        %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Text abbreviations.
\newcommand{\ie}{{\em{i.e., }}}
\newcommand{\eg}{{\em{e.g., }}}
%XS\newcommand{\cf}{{\em{cf., }}}
\newcommand{\wrt}{with respect to}
\newcommand{\lhs}{left hand side}
\newcommand{\rhs}{right hand side}
\newcommand{\frc}{\displaystyle\frac}
\newenvironment{frcseries}{\fontfamily{frc}\selectfont}{}
\newcommand{\textfrc}[1]{{\frcseries#1}}
\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                              %%%%%%%
%%%%%% END OF THE NOTATION SECTION  %%%%%%%
%%%%%%                              %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Cause numbering of subsubsections. 
%\setcounter{secnumdepth}{8}
%\setcounter{tocdepth}{8}

\setcounter{secnumdepth}{4}%
\setcounter{tocdepth}{4}%
%\pagestyle{empty}
\pagenumbering{gobble}

%\author{CoMaELa/CoPhyMs}
\usepackage{authblk}

\begin{document}
\begin{center}
{\Large{ \bf Multi-Fluid Dynamics Model for Heterogenoeus Porous Media Flows}}

J. Gomes$^{\text{a}}$, K. Christou$^{\text{a}}$, B. Lashore$^{\text{a}}$

$^{\text{a}}$Fluids and Structures Group, School of Engineering, \\
University of Aberdeen, AB24 3UE, UK

\end{center}

\noindent
{\large{\bf Abstract}}

\noindent
Current porous media flow models are often based on outdated computational methods (e.g. structured or block structured hexahedral FEM- and FDM-based discretisation). Since these methods are often at the heart of transport in porous media, it is vital that they are updated in light of recent advances in computational methods and able to exploit the current state-of-the-art mesh-adaptive methods.

\noindent
Here, we introduce a conservative computational multi-fluid porous media flows model able to exploit the latest mesh adaptivity methods on fully-unstructured tetrahedral grids. The model is based on two key numerical characteristics: (a) novel families of P$_{\text{m}}$DG-P$_{\text{n}}$ and P$_{\text{m}}$DG-P$_{\text{n}}$DG finite element-pairs and (b) a consistent control volume finite element method (CVFEM) formulation. In particular, the P$_{\text{1}}$DG-P$_{\text{2}}$ and P$_{\text{1}}$DG-P$_{\text{1}}$DG element-pairs are introduced as the basis of the discretisation. This is necessary, as it is very difficult to use FE representation of scalar fields (e.g., saturation and density) and simultaneously ensure physical realism in these solution variables (i.e., positivity and suppression of numerical oscillations provided by high-order or limiting methods).

\noindent
The main aim of this work is to report the latest development of a generic FEM-based unstructured and adaptive-mesh multi-fluid porous media flow model. In the simulations performed in this paper, scalar fields (e.g., phase saturation, concentration, density etc) are represented in the CV space and the velocity-pressure dual fields are embedded in FEM space with simultaneous projection into the CV space. High-order accurate downwind schemes on element boundaries on discontinuous scalar fields are flux-limited (based on NVD approach) to obtain bounded and compressive (capturing the interfaces) solutions. We focus on benchmark simulations of dual saturated-unsaturated flows in heterogeneous porous media, where a fluid is injected in a porous matrix and the resulting fluid content during the drainage is qualitively analysed.

\medskip
\noindent
{\it{\bf Keywords:}}

\noindent
Multi-fluid Darcy flows, Finite element methods, Flow instabilities.

\end{document}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
updated

--- 2017-05-10 Papers/ViscousInstabilities/article_figure1.tex
@@
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
-%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored)blue points represent the pressure nodes and white points the velocity nodes.}
-%\label{fig:fem_cv}
-%\end{figure}
+%%%%%%%%%%%%%%%%
+%%% Figure 1 %%%
+%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+   \begin{center}
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+\label{fig:fem_cv}
+\end{center}
+\end{figure}
 
-%\begin{figure}[ht]
-%   \vbox{
-%       \hbox{\includegraphics[width=.5\textwidth]{./Figs/p1dgp2-cont-sat.pdf}
-%             \includegraphics[width=.5\textwidth]{./Figs/p2dgp1-dg-sat.pdf}}
-%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{5.cm} (b)\PNDG[2]{1}}}
-%\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is   stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-%    \label{fem_cv_represent_a}
-%\end{figure}
+\clearpage
+%%%%%%%%%%%%%%%%
+%%% Figure 2 %%%
+%%%%%%%%%%%%%%%%
+\begin{figure}[h] 
+   \begin{center}
+\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
+The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.}
+\label{fig:fem_elem}
+\end{center}
+\end{figure}
+
+\clearpage
 
@@
 %%%%
-%%%%  FIGURE 2
+%%%%  FIGURE 
 %%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/P1DGP2}}
-\hbox{\hspace{6cm}(a)}
-\vspace{.5cm}
-\hbox{\hspace{1cm}\includegraphics[width=.7\textwidth]{./Pics/element_n}}
-\hbox{\hspace{6cm}(b)}}
-\caption{Sketches of FE-pairs: (a) 2D representation of the \PN[1]{2} element-pair used in this work.
-Shaded areas denote control volumes (in which scalar fields such as phase saturation, temperature, density etc are stored); blue and white circles represent pressure and velocity nodes, respectively.
-(b) Simplified representation of field storage in a \PN[1]{1} element-pair: permeability $\left(K_{i}\right)$ and porosity $\left(\phi_{i}\right)$ are stored in $P_{0}DG$ space ($A$), whereas all other scalar fields (e.g., saturation, density, viscosity, relative permeability etc) are stored in CV space ($B$).
-\red{(KOSTAS, COULD YOU: (a) REPLACE 1 BY i (top quad of ELEMENT B) AND (b) REMOVE THE WHITE CIRCLES IN ELEMENT A)}.}
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
+\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
 \label{fig:fem_cv}
@@
 
+%\begin{figure}[h] 
+%\centering
+%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+%\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
+%\label{fig:fem_elem}
+%\end{figure}
+
 %%%%
-%%%%  FIGURE 3
+%%%%  FIGURE
 %%%%
-\begin{figure}[ht]
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
+\caption{This is a description of two different element types.
+Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
+Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
+The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.
+}
+\label{fig:fem_elem}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
 \vbox{
-\hbox{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2}}
-\vspace{-0.cm}
-\hbox{\hspace{5cm}(a)}
-\vspace{-0.cm}
-\hbox{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot}}
-\vspace{-0.cm}
-\hbox{\hspace{5cm}(b)}
-}\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
-The mesh is unstructured and fixed with 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}\label{fig:square}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.0cm} (a)  
+}
+\vspace{0.5cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
+}
+\vspace{1.0cm}
+\hbox{\hspace{6.0cm} (b)  
+}}     
+\caption{2D representation of the element pairs presented in this work.
+Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
+Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
+\label{fem_cv_represent_a}
 \end{figure}

### 2017-05-16 Papers/ViscousInstabilities/article_figure2.tex

%\begin{figure}[ht] 
%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
%\caption{Caption 1}
%\label{fig:subim1}
%\end{center}

%\begin{center}
%\centering
%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
%\caption{Caption 3}
%\label{fig:subim3}
%\end{center}

%\caption{Caption for this figure with two images}
%\label{fig:image1}
%\end{figure}
%\pagebreak
%\clearpage

%\begin{figure}[ht] 
%\begin{center}
%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
%\label{fig:simple_case}
%\end{center}
%\end{figure}

%\begin{figure}[ht] 
%\begin{center}
%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region. The mesh is unstructured and fixed with 5000 elements. Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
%\label{fig:square}
%\end{center}
%\end{figure}

%\begin{figure}[ht] 
%   \vbox{
%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
%\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
%    \label{fem_cv_represent_a}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a)  
}
\vspace{0.5cm}
\hbox{\hspace{2.5cm}
\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
}
\vspace{1.0cm}
\hbox{\hspace{5.0cm} (b)  
}}     
\caption{2D representation of the element pairs presented in this work. Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes. Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000  
}
}     
\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
\label{fem_cv_represent_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
\label{fig:6a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
\label{fig:6b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
}
}     
\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
\label{fig:6c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
\label{fig:1a_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=2500  
}
}     
\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
\label{fig:1b_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=3500   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end  
}
}     
\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:1c_homoheleshaw_3}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250  
}
}     
\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
\label{fig:2a_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=4000  
}
}     
\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
\label{fig:2b_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end   
}
}     
\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
\label{fig:2c_homoheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b). Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
\label{fig:3a_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=2000   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=3000     
}
}     
\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations. Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
\label{fig:3b_heteheleshaw_10}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=6000    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=24000     
}
}     
\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers. At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
\label{fig:3c_heteheleshaw_10}
\end{figure}
%{./Pics/P1DG-P2_element_type} 
%{./Pics/4r_po_adapt_fine_125_mesh} 
%{./Pics/4r_po_adapt_fine_100_mesh}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=250   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=250     
}
}     
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
%%%%
%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

%\begin{figure}[ht] 
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}\\[0.5cm]% If you want some vertical space
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}%
%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
%\label{fig:3testcase_b}
%\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_c}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_d}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
\label{fig:4testcase_a}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
}
}     
\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
\label{fig:4testcase_b}
\end{figure}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
}
}     
\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions. From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude 
for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}. The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns. While there 
is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
\label{fig:vel_magn}
\end{figure}

%%%%
%%%%  FIGURE
%%%%

\begin{comment}
\begin{landscape}
\begin{figure}[ht!]
\begin{center}
\subfigure[MR100, at the beginning of the simulations]{%
\label{fig:1st}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
}%
\subfigure[MR100, at the middle of the simulation]{%
\label{fig:2nd}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
}\\
\subfigure[MR100, Phase 1 Volume fraction]{%
\label{fig:3rd}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
}%
\subfigure[MR100, Phase 2 Volume fraction]{%
\label{fig:4th}
\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
}\\
\caption{Comparison of different MR's and their recovery rates}
\label{fig:5}
\end{center}
\end{figure}
\end{landscape}
\end{comment}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 \end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{0.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) map of permeabilties K  
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000  
+}
+}     
+\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
+\label{fem_cv_represent_a}
+\end{figure}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 %%%%%%%%%%%%%%%%
-\begin{figure}[h]
-   \begin{center}
-\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
-\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+%\begin{figure}[h]
+%\begin{center}
+%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
 Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
-\label{fig:fem_cv}
-\end{center}
-\end{figure}
+%\label{fig:fem_cv}
+%\end{center}
+%\end{figure}
+%\clearpage
 
-\clearpage
 %%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%
-\begin{figure}[h] 
-   \begin{center}
-\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
+%\begin{figure}[h] 
+%\begin{center}
+%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+%\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
 The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
 Saturation and saturation-dependent variables are stored CV-wise.}
-\label{fig:fem_elem}
-\end{center}
-\end{figure}
-
-\clearpage
-
-%%%%
-%%%%  FIGURE 1
-%%%%
-\begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
-\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
-The ratio of viscosity between the two fluids is 5.
-In this case, the initially piston shape front collapses leading to the formation of several fingers.}
-\label{fig:simple_case}
-\end{figure}
-\clearpage
+%\label{fig:fem_elem}
+%\end{center}
+%\end{figure}
+%\clearpage
 
@@
 \end{figure}
-
-%\begin{figure}[h] 
-%\centering
-%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-%\caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
-%\label{fig:fem_elem}
-%\end{figure}
 
@@
 \end{figure}
+
+%%%%
+%%%%  FIGURE 1
+%%%%
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
+\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
+The ratio of viscosity between the two fluids is 5.
+In this case, the initially piston shape front collapses leading to the formation of several fingers.}
+\label{fig:simple_case}
+\end{figure}
+\clearpage
 

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000  
+\hbox{\hspace{5.0cm} (c) flow at t=3000  
 }
@@
 \end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
+\label{fig:6a}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
+\label{fig:6b}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
+\label{fig:6c}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
+\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
+\label{fig:1a_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=2500  
+}
+}     
+\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
+\label{fig:1b_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=3500   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end  
+}
+}     
+\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:1c_homoheleshaw_3}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
+\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
+\label{fig:2a_homoheleshaw_10}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=4000  
+}
+}     
+\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
+\label{fig:2b_homoheleshaw_10}
+\end{figure}

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 \end{figure}
+\clearpage
 
@@
 \end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht]
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=end   
+}
+}     
+\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:2c_homoheleshaw_10}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
+\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
+Screenshot will follow that describe the progression of the flow in figure \ref{fig:3b_heteheleshaw_10} and figure \ref{fig:3c_heteheleshaw_10}.}
+\label{fig:3a_heteheleshaw_10}
+\end{figure}
+\clearpage

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=2000   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=3000     
+}
+}     
+\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
+Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
+\label{fig:3b_heteheleshaw_10}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) flow at t=6000    
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.75cm} (b) flow at t=24000     
+}
+}     
+\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
+At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
+\label{fig:3c_heteheleshaw_10}
+\end{figure}
+\clearpage

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{4.0cm}
+\includegraphics[width=.8\textwidth]{./Pics/map_of_boundaries.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) map of permeabilties K   
+}
+\vspace{0.25cm}
+\hbox{\hspace{4.0cm}
+\includegraphics[width=.8\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{7.5cm} (b)      
+}
+}     
+\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
+Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
+\label{fig:testcase_heter_domain}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) flow at t=250   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) flow at t=250     
+}
+}     
+\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
+There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
+\label{fig:2testcase_a}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
+}
+}     
+\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\label{fig:2testcase_b}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
+}
+}     
+\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\label{fig:2testcase_c}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
+}
+}     
+\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
+When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
+\label{fig:2testcase_d}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+  \includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
+\label{fig:3testcase_a}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_b}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_c}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_d}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase_a}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
+\label{fig:4testcase_b}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-05-16 Papers/ViscousInstabilities/article_figure1.tex
working-updated

@@
 %%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
+}
+}     
+\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
+From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
+for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase_a}.
+The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
+While there
+is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
+\label{fig:vel_magn}
+\end{figure}
+
+%%%%
+%%%%  FIGURE
+%%%%
 \begin{landscape}

### 2017-05-18 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
small changes
updated the text as 10 days ago, remove the pics and start corrections

--- 2017-05-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
-For a porous medium that is statistically homogenous two immiscible fluids are asumed to coexist together within a solid matrix.
-In a microscopic level fluids are newtonian and incompressible and gravity is the only external force acting on the system.
-An interfacial tension $\sigma$ is assumed to exist at the interfaces separating the two fluids.
-The main difference between microscopic and macroscopic level is the concept of capillary pressure.
-%\red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.
+Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
@@
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena in two-phase systems while a this work will focus on a local flow instability due to viscous and stress forces, often referred as viscous instability or \textit{viscous fingering}.
+This paper will focus on microscopic instabilities and phenomena in two-phase systems.
+A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
 
@@
 
-\medskip
-%Through the $P_{1}DGP_{2}$ element type, 
-Material properties and flow conditions (e.g., density, temperature, species concentration etc) can be allocated in control volume space as shown in Fig.~\ref{fig:fem_cv}.
-%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-Through the $P_{1}DGP_{2}$ element type, material properties can be described using the control volume finite element methods (Fig.\ref{fig:fem_cv}.
-%describes the $P_{1}DGP_{2}$ element type may vary abruptly (permeability and/or porosity contrasts at fracture-matrix interfaces).
-Since geometries are captured by finite elements, constructed control volumes typically extend over the interfaces which may have different properties.
-Therefore, some average value of the permeability (defined in the FE space but projected into the CV space) is applied across the CVs at these interfaces.
-This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
+These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
 In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
@@
 \medskip 
-The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFEM formulation that exploits adaptive mesh of fully-unstructured triangle and tetrahedron grids.
-Also two key characteristics that describe the research concept are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) dual representation of pressure and velocity fields in the FE and CV spaces.
-The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids.
-Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
+Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
+The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
 
 \medskip
-In the next sections the numerical formulation and a summary of the main governing equations for multiphase compositional flows will discussed.
-The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions.
-The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
+A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
+Impact of mobility ratio on the fingers formation is also included in this section.
+The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
+Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Governing equations and numerical scheme}\label{equations_scheme}      
+\section{Model Formulation}\label{equations_scheme}      
 %Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
@@
 
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation %(Eqn.~\ref{e:darcy_eq}). 
-Hybrid basis functions are also developed to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{k}=\underline{\underline{\sigma}}_{k}\left({\mathbf K}, \mathcal{K}_{rk}, S_{K}, \mu_{k}\right)$ is an absorption-like term that lies in both CV and FEM spaces.
-Though, whilst the saturation field is calculated in CV space, permeability $\left({\mathbf K}\right)$ is piecewise constant in FE space to allow efficient representation of surface parametrised geometries.
-The global saturation equation (Eqn.~\ref{eqn:saturation_eqn}) is discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv} below) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
+\begin{displaymath}
+   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
+\end{displaymath}
+Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 
-\medskip
-The method developed is applicable to $\mathcal{N_{p}}$ fluid phases and is based on the novel family of $P_{n}(DG)-P_{m}(DG)$ element-pair consistent with the dual pressure-velocity representation in control volume (CV) and finite element (FE) spaces.
-These element-pairs have a discontinuous $n^{th}$-order polynomial representation for velocity and a discontinuous $m^{th}$-order polynomial for pressure.
-Another element pair, that can be used is the $P_{n}DGP_{m}$ with an $m^{th}$-order continuous representation for pressure.
-The mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin finite element (FE) method is used to obtain the high-order fluxes on CV boundaries (Fig.\ref{fig:fem_elem}), which are limited to yield bounded fields.
+This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
+Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
+Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
 
-Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented CV-wise.
-The pressure, a key difference to other CVFE methods reported previously, allows the use of CVs that do not span multiple FEs.
-Hence each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
-
-In this model we assume that rock and fluids are incompressible thus the mass ballance for phase $\alpha$ can be written as (Eq.\ref{mass_balance})
-
-\begin{equation}
-\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha}
-\label{mass_balance}
-\end{equation}
+%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
+%\begin{equation}
+%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
+%\label{mass_balance}
+%\end{equation}
 
@@
 
-Equation \ref{mass_balance} is discretized in time and space using the $\theta$-method %\citep{saramito_1994}. 
-Summing over all phases yields the global mass balance equation %\ref{global_mass_balance},
-
+Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
 \begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}\right)-\left(S_{\alpha i}^{n}\right)}{\Delta t} dV  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} [\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; (1-\theta^{n+1/2}) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}] d\Gamma \;- \nonumber\\
- &&  \int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\; =0
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
 \label{global_mass_balance}
 \end{eqnarray}
-
-\noindent where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
+This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
 
@@
 The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
-Under this assumption when a fluid is injected in a porous domain saturated with another fluid trying to displace it, viscous fingering will occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
-This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems.
-Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon.
-The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap.
-The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law).
-More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
+Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+
+Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
+Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ...
+WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.
 
 \medskip
-In viscous fingering, a less viscous fluid pushes a more viscous fluid, in a thin rectangular cell (known as Hele-Shaw cell).
-\citet{howison_2000}  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers.
-For homogeneous domains fingers will start to develop when surface tension acting on the interface, is opposing towards the change of shape of the interface thus the interface becomes unstable and will collapse, taking a curved shape.
-In heterogeneous environments this process may also be triggered by permeability differences between smaller regions.
-The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be.
-In addition, pressure differences %(eq.\ref{eq:pressure_dif})
-acting on the interface will produce a net pressure force,
+In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
+The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ...
+SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN?
+...
+TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}.
+More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
 
+\medskip
+ Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{buckley_1942,sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+The interface becomes unstable and collapses, taking a curved shape.
+
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+Pressure differences acting on the interface produces a net pressure force,
 \begin{equation}
-\Delta P= - \gamma \; \nabla \; \dot \; \hat{n} 
+\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
 \label{eq:pressure_dif} 
 \end{equation}
+This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
 
-\noindent this is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ the unit normal vector out of the surface, and $\gamma$ the surface tension.
-As mentioned in Section \ref{section:intro}, an unfavourable mobility-ratio in a water-oil system will have the following definition, see eqn.\ref{eq:MR}.
-
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
- MR \; = \frac{k_{rw} \; \mu_{w}}{k_{ro} \; \mu_{o}} 
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
 \label{eq:MR}
 \end{equation}
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
 
-\noindent Fingering will occur in immiscible displacements when the viscocity ratio is greater than unity.
-%As surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability by the basic mechanism associated with a less viscous fluid displacing a more viscous one.
-After a split, each of the new lobes of the finger is stable as a result of their being thinner than the finger from which they split.
-As surface tension becomes weak, the front is stressed and goes under a viscous-fingering instability.
-The front will collapse and will start splitting into new lobes of fingers.
-One of these fingers will eventually outgrow the others and will then spread to occupy the appropriate width of the cell.
-In the process, it reaches a width that is again unstable to splitting, and the pattern repeats.
-Thus, surface tension plays an essential dual role; it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
+\begin{displaymath}
+    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
+\end{displaymath}
+ that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
+\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
 
-In  this paper, viscous instabilities for different test-cases will be investigated.
-Adaptive and unstructured mesh will be used to capture the collapse of the interface and the development of the fingers in relation to different values of mobility ratios and different maps of permeabilities.
-Initially test-cases that verify the existence of fingers in experimental domains will illustrated follow by more complicated computational domains and finger patterns.
+In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+The interface collapses and starts splitting into new lobes of fingers.
+One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
+Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities \red{(Section XXX)}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid \red{(Section XXX)}; (c) the impact of viscosity ratios on the formation and progress of fingers \red{(Section XXX)}.
 
@@
 %%%%%%%%%%%% 
-\subsection{Model Validation}
+\subsection{Model Set-up}\label{section:results:setup}
+
+Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+
+All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+Fluids are assumed incompressible and gravity was neglected.
+The set-up for the numerical simulations are summarised in Table \ref{table:setup}.
+
+%%%%%%%%%%%% 
+\subsection{Model Validation}\label{section:results:validation}
+
+This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media
 
@@
 %%%%%%%%%%%%  
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}
 
@@
 \clearpage
+
+\listoftables
+\clearpage
+\input{article_table}
+\clearpage  
 \listoffigures
@@
 
-%\input{article_figure1}
+\input{article_figure1}
 %\input{article_figure2}

### 2017-05-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
testing/changes
reviewing correcting and uploading

@@
 A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations \red{(BE MORE SPECIFIC ON THEIR CONTRIBUTION TO THE STATE-OF-THE-ART OF THE FIELD!!)}.
-Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
+% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
@@
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena in two-phase systems.
-A local flow instability that is the focus of this work is due to viscous and stress forces and often named as viscous instabilities or \textit{viscous fingering} \red{(TRY TO MERGE THESE 2 SENTENCES!)}.
+This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.
 

### 2017-05-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
reviewing correcting and uploading

@@
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon\red{(SENTENCE SEEMS INCOMPLETE ...
-WHAT WERE THE CONTRIBUTION OF THESE AUTHORS ???)}.
+\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
+T is the surface tension and U is a velocity characteristic of the moving interface.
+
+\begin{equation}
+Ca = \frac{\mu U}{T}
+\label{eq:capillary_number}
+\end{equation}
+
+For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
+If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
 
@@
 TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave an extensive \red{(DO YOU MEAN EXTENSIVE OR COMPREHENSIVE?)} description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
 
@@
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{buckley_1942,sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}}
+leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
reviewing correcting and uploading

@@
 \section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
+
 \medskip
@@
 
+\medskip
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
@@
 In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) \red{(THIS SENTENCE IS A BIT CONFUSING ...
+The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% keep drafting it %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\red{(THIS SENTENCE IS A BIT CONFUSING ...
 SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN?

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
reviewing correcting and uploading

@@
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
+\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
 T is the surface tension and U is a velocity characteristic of the moving interface.
@@
 In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% keep drafting it %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\red{(THIS SENTENCE IS A BIT CONFUSING ...
-SO THE EQNS THAT DESCRIBE FLOWS IN H-S CELLS ARE THE POTENTIAL EQUATION FOR INVISCID FLUIDS AND THE DARCY EQN?
-...
-TRY TO REWRITE THE SENTENCE AND EXPLAIN THE IMPORTANCE OF THE H-S CELLS IN THE UNDERSTANDING OF VISCOUS FLOW INSTABILITIES)}.
+This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
+%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
 More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
@@
 Pressure differences acting on the interface produces a net pressure force,
+
 \begin{equation}
@@
 \end{equation}
+
 This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
@@
 As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+
 \begin{equation}
@@
 \end{equation}
+
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+
 \begin{eqnarray}
@@
 \end{eqnarray}
+
 where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in \red{Section XXX}.
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in Section \ref{section:results_homo_hete}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
@@
 %%%%%%%%%%%% 
-\subsection{Model Validation}\label{section:results:validation}
+\subsection{Model Validation}\label{section:results_validation}
 
@@
 %%%%%%%%%%%%  
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results:heleshaw}
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results_homo_hete}
 

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities \red{(Section XXX)}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid \red{(Section XXX)}; (c) the impact of viscosity ratios on the formation and progress of fingers \red{(Section XXX)}.
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{}.
 
@@
 %%%%%%%%%%%%%
-\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
+\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}
 
@@
 
-\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}
+\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{Section:results_dinlet}
 

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
-Fig.\ref{fig:simple_case} describes the starting point of the simulations that will follow.
+Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
 Fluid $1$ is from the left hand side of the formation.
@@
 \medskip
-In Fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
+In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
 Three different cases with different set-ups will follow.

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{}.
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
 
@@
 
-Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,jackson_2013,porosity_documentation,fluidity_manual}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{jackson_2015,pavlidis2016,salinas2015,salinas_2016,adam_2016b,su_2015,radunz_2014}.
+Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
 
@@
 
-\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{Section:results_dinlet}
+\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{section:results_dinlet}
 

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
 
-Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
-Fluid $1$ is from the left hand side of the formation.
+\medskip
+Fluid $1$ is introduced from the left hand side of the formation.
 Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
-Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on th right hand side of the domain.
+Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain.
 Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively.
-Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).
-
+Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used).
 %\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
-\noindent A square domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
+A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
 At the upper and lower sides of the domain no-slip boundary condition is applied.
@@
 The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see Fig.\ref{fig:square}) while the phase volume fraction is constant.
+There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further %\ref{fig:square})
+while the phase volume fraction is constant.
 
 \medskip
-A slightly modified test-case (see Fig.\ref{fig:testcase}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$.
+A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) 
+with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
 The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
-This The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media
-
-The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
+\medskip
+The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
 The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
@@
 What can been seen here is a cross flow case as the flow passes through different regions and evolves.
-The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ (Fig.\ref{fig:square}b).
+The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
+%\ref{fig:square}b).
 
@@
 \medskip
-A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) 
-with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
+A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
 The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
-The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
+The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
 
@@
 \medskip
-As can been seen from the Fig.\ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
-Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3} give a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in Figures \ref{fig:3a_heteheleshaw_10},\ref{fig:3b_heteheleshaw_10},\ref{fig:3c_heteheleshaw_10}.
+As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
+%Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
+They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figures \ref{fig:3a_heteheleshaw_10} %\ref{fig:3b_heteheleshaw_10}
+-\ref{fig:3c_heteheleshaw_10}.
 Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
@@
 Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-Initial and boundary conditions are described in Fig.
-\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
+Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
 A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 
+\medskip
 Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes.
@@
 
+\medskip
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
@@
 
+\medskip
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
@@
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
+\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
 T is the surface tension and U is a velocity characteristic of the moving interface.
@@
 \begin{equation}
-Ca = \frac{\mu U}{T}
+N_{C} = \frac{\mu U}{T}
 \label{eq:capillary_number}
@@
 %\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
-A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
+A domain consisting of $4$ square regions in which each quarter is represented by a permeability value %(Fig.\ref{fig:square}a) 
+and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
 At the upper and lower sides of the domain no-slip boundary condition is applied.
@@
 The third test-case is based in the initial and boundary condition of the second set of simulations.
-Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a},\ref{fig:6b},\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
+Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
+\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
 The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
@@
 \medskip
-Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3},\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
+Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3}
+\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
 In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
@@
 A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.
-What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude (Fig.\ref{fig:1testcase}).
+What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude.
+%(fig.\ref{fig:1testcase})
 The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
@@
 %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
-Figures \ref{fig:2testcase_a}, \ref{fig:2testcase_b}, \ref{fig:2testcase_c} and \ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
+Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
+-\ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
 In this set the interfacial instability is becoming more profound as the flow develops.
@@
 The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields (see Fig.\ref{fig:vel_magn2}) as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$.
-Even though a this case is unlikely to happen as the mobility ration of the existing fluids in the industry, it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
+The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2})
+as the presence of this extra inlet increases the flow at the top layers.
+At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$,
+%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
+it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
 Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
@@
 No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).
-
 The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase}.
+Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.
 
@@
 
+\medskip
 Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.
 
+\medskip
 This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.

### 2017-05-25 Papers/ViscousInstabilities/article_table.tex
cleaning the paper adding some extra info

@@
       \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
-      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
+      \ref{section:results_homo_hete}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
                                        & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\

### 2017-05-25 Papers/ViscousInstabilities/article_table.tex
cleaning the paper adding some extra info

--- 2017-05-10 Papers/ViscousInstabilities/article_table.tex
@@
+\begin{landscape}
 \begin{table}
@@
     \hline
-      \ref{section:results:validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
-      \ref{section:results:heleshaw}   & 0.2  & 1.0  & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
-                                       & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
+      \ref{section:results_validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
+      \ref{section:results_homo_hete}  & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
+      \ref{section:results_hete_fix_adapt}  & 0.2  & 1.0  & 0.0  & 1.0  &  3.0  & 2.0  & 5.0  & 1.0  & N/A & 0.2  & 0.3 & XX  \\
       \hline
@@
 \end{table}
+\end{landscape}
+\clearpage

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 \medskip
-As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-\ref{fig:1c_homoheleshaw_3} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
+As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
+\ref{fig:2c_homoheleshaw_10} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
 %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}

### 2017-05-25 Papers/ViscousInstabilities/article_figure1.tex
updated the text as 10 days ago, remove the pics and start corrections
cleaning the paper adding some extra info

@@
 
+\begin{comment}
 %%%%
@@
 \clearpage
+\end{comment}
 
 %%%%
-%%%%  FIGURE
+%%%%  FIGURE 4
 %%%%
@@
 }     
-\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\caption{Fingers are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
 \label{fig:2c_homoheleshaw_10}
@@
 \vspace{0.0cm}
-\hbox{\hspace{7.5cm} (b)      
+\hbox{\hspace{9cm} (b)      
 }

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

@@
 Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
-Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES}).
+Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
 

### 2017-05-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info
updates

@@
 Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of fluid flow through porous media serves as the foundation of reservoir engineering and groundwater studies.
+Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies~\citep{white_1981}.
 %Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, self_2012, jiang_2011}.
 
 \medskip
-Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes.
-Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media.
-A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
+Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
+Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of mechanisms of fluid instabilities (i.e., fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations \red{(COULD YOU EXPLAIN WHAT YOU MEANT WITH THIS SENTENCE?
+ALSO LINK THIS SENTENCE WITH THE FOLLOWING!)}.
 % Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
@@
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.
+This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces and is often referred as viscous instabilities or viscous fingering.
 
@@
 The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.
+Screenshots of the phase volume fraction and the development of fingers are shown in figures \ref{fig:4testcase_a}-\ref{fig:4testcase_b}.
 

### 2017-06-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-\title{ \blue{Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
-something with viscous flow instability or viscous fingering)}}
+\title{ \blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
+something with viscous flow instability or viscous fingering...}}
 

### 2017-06-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
+%%  LocalWords:  checkboard % Copyright 2007, 2008, 2009 Elsevier Ltd
+%
+% This file is part of the 'Elsarticle Bundle'.
+% ---------------------------------------------
+%
+% It may be distributed under the conditions of the LaTeX Project Public
+% License, either version 1.2 of this license or (at your option) any
+% later version.  The latest version of this license is in
+%    http://www.latex-project.org/lppl.txt
+% and version 1.2 or later is part of all distributions of LaTeX
+% version 1999/12/01 or later c.
+%
+% The list of all files belonging to the 'Elsarticle Bundle' is
+% given in the file `manifest.txt'.
+%
+
+% Template article for Elsevier's document class `elsarticle'
+% with harvard style bibliographic references
+% SP 2008/03/01
+%
+%
+%
+% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
+%
+%
+\documentclass[preprint,authoryear,12pt]{elsarticle}
+
+% Use the option review to obtain double line spacing
+%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+% for a journal layout:
+%\documentclass[final,authoryear,1p,times]{elsarticle}
+%\documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
+%\documentclass[final,authoryear,3p,times]{elsarticle}
+%\documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
+%\documentclass[final,authoryear,5p,times]{elsarticle}
+%\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the gra
+
+%%graphis package for simple commands
+%% \usepackage{graphics}
+%\usepackage{cases}
+%% or use the graphicx package for more complicated commands
+\usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+\usepackage{epsfig}
+%\usepackage{subfig}
+\usepackage{comment}
+
+\usepackage{epstopdf}
+\usepackage{pdflscape}
+\usepackage{bm}
+\usepackage{hyperref,url}
+\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb,amsmath,array}
+%The amsthm package provides extended theorem environments
+\usepackage{amsthm}
+\usepackage{graphicx}
+%\usepackage{subfigure}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+\usepackage{lscape}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon (default)
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   authoryear - selects author-year citations (default)
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%   longnamesfirst  -  makes first citation full author list
+%%
+%% \biboptions{longnamesfirst,comma}
+
+% \biboptions{}
+
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
+\journal{Advances in Water Resources}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
+
+\begin{document}
+
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+\title{ \blue{Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
+something with viscous flow instability or viscous fingering)}}
+
+%% use optional labels to link authors explicitly to addresses:
+\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
+\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
+
+\cortext[cor1]{Corresponding author.}
+\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
+\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
+\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
+
+\begin{abstract} 
+A set of simulations is presented so as to model the viscous fingering-flow instability using a novel method for modeling multi-phase flows in porous media.
+Starting from the Hele-Shaw experimental which is mathematically analogous to the two-dimensional flow in porous medium, test-cases of both homogenous and heterogeneous computational domains, under different conditions are listed.
+The development of finger structures is explained by taking into account different maps of permeabilities, mobility ratios and surface tension.
+A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
+In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+It was found that the initial state is the decisive factor in the development of the process up to large times
+The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
+\end{abstract}
+
+\begin{keyword} %% keywords here, in the form: keyword \sep keyword
+ Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods.
+\end{keyword}
+
+\end{frontmatter}
+
+%\tableofcontents
+%\linenumbers
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Introduction}\label{section:intro}
+\medskip
+Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Characterisation of fluid flow through porous media serves as the foundation of reservoir engineering and groundwater studies.
+%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
+%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
+
+\medskip
+Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes.
+Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media.
+A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
+% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
+The first distinction should be made between microscopic and macroscopic instabilities.
+Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
+This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.
+
+\medskip
+In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
+As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+
+\medskip 
+Conservation of mass and Darcy's law are the governing equations that describe the flow dynamics in porous media.
+Several computational methods have been developed to accurately represent force balances in Darcean flows.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications.
+However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+
+\medskip
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
+FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
+%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
+%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+
+\medskip
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%\begin{equation}
+% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+%\label{cvfe_pressure} 
+%\end{equation}
+
+%\begin{equation}
+% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+%\label{cvfe_saturation}
+%\end{equation}
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
+These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
+In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
+%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+All these parameters are represented under one term in the global mass balance equation.}
+
+\medskip 
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
+Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
+The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+
+\medskip
+A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
+Impact of mobility ratio on the fingers formation is also included in this section.
+The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
+Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Model Formulation}\label{equations_scheme}      
+%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
+Different domains will produce different flow instabilities.
+In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
+DG-methods combine advantages of classical finite volume and finite element methods.
+
+%\subsection{Numerical Formulation}
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%Flows in porous media are expressed by the Darcy's law and the saturation equation.
+At this stage the control volume finite element method is used (CVFEM).
+Darcy's law for immiscible multi-phase flow may be written in the form:
+%\begin{equation}\label{e:darcy_eq}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_bal}
+%\end{equation}
+%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
+
+%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
+%\begin{equation}
+%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
+%\end{equation}
+%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
+%\begin{eqnarray}
+%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
+%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+%\label{v_and_p}
+%\end{eqnarray}
+
+%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
+%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_balance}
+%\end{equation}
+
+%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+%\end{comment}
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\label{e:darcy_eq}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+%\label{E:darcy_eqn}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+%\begin{equation}
+%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:darcy_ext}
+%\end{equation}
+%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+\medskip
+The two-phase flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\end{eqnarray}
+respectively, where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ represents the saturation of the $\alpha$-phase with constraints of
+\begin{displaymath}
+\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
+\end{displaymath}
+where $\mathcal{N}_{p}$ denotes the number of phases.
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%The main equations that will be used along with the following OCVFEM techique can be summarised below.
+The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
+At the $n+1$ step those two equations mentioned above can be rewritten as,
+
+%\begin{equation}
+%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+%\label{e:mass_bal}
+%\end{equation}
+
+%\begin{equation}
+%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+%\label{e:force_bal}
+%\end{equation}
+
+%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+This system of equations can be rewritten to produce the pressure equation,
+
+%\begin{equation}
+%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+%\label{e:pressure_eq}
+%\end{equation}
+
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
+\begin{displaymath}
+   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
+\end{displaymath}
+Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+
+This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
+Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
+Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+
+%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
+%\begin{equation}
+%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
+%\label{mass_balance}
+%\end{equation}
+
+%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
+
+%\begin{equation}
+%\sum  S_{p}-1
+%\label{saturation_constrain}
+%\end{equation}
+
+Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+\label{global_mass_balance}
+\end{eqnarray}
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
+This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
+
+\medskip
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system.
+The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
+Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+
+\medskip
+Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
+\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
+T is the surface tension and U is a velocity characteristic of the moving interface.
+
+\begin{equation}
+N_{C} = \frac{\mu U}{T}
+\label{eq:capillary_number}
+\end{equation}
+
+For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
+If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
+
+\medskip
+In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
+This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
+%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
+More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+
+\medskip
+ Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
+During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}}
+leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+The interface becomes unstable and collapses, taking a curved shape.
+
+In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in Section \ref{section:results_homo_hete}.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+Pressure differences acting on the interface produces a net pressure force,
+
+\begin{equation}
+\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
+\label{eq:pressure_dif} 
+\end{equation}
+
+This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
+
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+
+\begin{equation}
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
+\label{eq:MR}
+\end{equation}
+
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+
+From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
+\begin{displaymath}
+    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
+\end{displaymath}
+ that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
+\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
+
+In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+The interface collapses and starts splitting into new lobes of fingers.
+One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
+Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+%\begin{equation}
+%\lambda = \frac{K\;k_{\alpha}}{\mu}
+%\label{eq:mobility-of-fluid}
+%\end{equation}
+
+%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
+Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
+
+%\begin{equation}
+%U = \frac{b^2}{12 \mu} \nabla p
+%\end{equation}
+
+%and the above equation can be re-arranged for 1D steady flow as,
+
+%\begin{equation}
+%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
+%\label{eq:pressure_dif} 
+%\end{equation}
+
+%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
+Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
+Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
+
+%\begin{equation}
+%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
+%\end{equation}
+
+%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
+
+%\begin{equation}
+%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
+%\end{equation}
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%\pagebreak
+%\clearpage
+
+%\listoftables
+%\pagebreak
+%\input{Manuscript_Table}
+
+%\pagebreak
+%\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{section:results}
+
+%%%%%%%%%%%% 
+\subsection{Model Set-up}\label{section:results:setup}
+
+Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
+
+All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+Fluids are assumed incompressible and gravity was neglected.
+The set-up for the numerical simulations are summarised in Table \ref{table:setup}.
+
+%%%%%%%%%%%% 
+\subsection{Model Validation}\label{section:results_validation}
+
+\medskip
+The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
+The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
+
+\medskip
+Fluid $1$ is introduced from the left hand side of the formation.
+Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
+Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain.
+Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively.
+Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used).
+%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
+A domain consisting of $4$ square regions in which each quarter is represented by a permeability value %(Fig.\ref{fig:square}a) 
+and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
+At the upper and lower sides of the domain no-slip boundary condition is applied.
+The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$.
+The right hand side is the outlet and pressure is set to $0$.
+Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$.
+What can been seen here is a cross flow case as the flow passes through different regions and evolves.
+The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
+%\ref{fig:square}b).
+
+\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
+The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
+There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further %\ref{fig:square})
+while the phase volume fraction is constant.
+
+\medskip
+A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
+The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
+The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
+
+\medskip
+In this section three different sets of simulations were explained.
+Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio.
+The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop.
+The third test-case is based in the initial and boundary condition of the second set of simulations.
+Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
+\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
+The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
+
+%%%%%%%%%%%%  
+\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results_homo_hete}
+
+\medskip
+Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3}
+\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
+In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
+. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
+was imposed to all borders of the domain except at the top righ hand side corner.
+The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
+
+\medskip
+In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
+Three different cases with different set-ups will follow.
+The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
+For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
+
+\medskip
+As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
+\ref{fig:2c_homoheleshaw_10} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
+%Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
+They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figures \ref{fig:3a_heteheleshaw_10} %\ref{fig:3b_heteheleshaw_10}
+-\ref{fig:3c_heteheleshaw_10}.
+Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
+In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation.
+The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.
+
+%%%%%%%%%%%%%
+\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}
+
+\medskip
+Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
+Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
+A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.
+What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude.
+%(fig.\ref{fig:1testcase})
+The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
+For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$.
+%Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
+Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
+-\ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
+In this set the interfacial instability is becoming more profound as the flow develops.
+Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
+Fingers will develop faster in areas where permeabilities are higher.
+This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
+
+\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{section:results_dinlet}
+
+\medskip
+Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
+This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
+The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
+The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2})
+as the presence of this extra inlet increases the flow at the top layers.
+At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$,
+%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
+it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
+Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
+A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
+No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).
+The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
+Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.
+
+\medskip
+The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. 
+%The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. 
+Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
+The domain is fully saturated with fluid $2$.
+At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
+Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
+The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
+Saturation is located at the pressure nodes.
+Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
+The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
+
+\medskip
+Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.
+
+\medskip
+This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
+Viscocity is a measure of resistance, therefore a frictional property.
+In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
+For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
+Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
+Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
+In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
+In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
+This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
+The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
+
+\medskip
+The macroscopic sweep efficiency is principally affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
+The permeability depends on the number, size and connectivity of the pores.
+This set of parameters is described by the $\sigma$ in the global mass balance equation (eq.\ref{global_mass_balance}).
+Including higher permeability zones also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
+
+\medskip 
+As can been seen so far in all the test-case illustrated, main differences can be found on the way the shape of fingering is developed.
+Adaptive meshes tend to display fingering easier because of the enhcanced and stronger resolution in the interface.
+Inside the high permeability square region there is an acceleration of the flow with the maximum value of it at the interface as this starts to develops at the back of this region and onwards.
+%At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
+The breaking point, also known as the point the two curves meet where beyond that water production will occur, is shifted towards the right as MR is increased.
+
+\section{Conclusions}\label{Section:Conclusion}
+
+\medskip
+A number of different cases have been illustrated in Section \ref{section:results}.
+Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
+Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows.
+For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
+In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR).
+If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
+On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
+Therefore for an i.e., water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
+Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
+
+%\medskip
+%We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
+Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
+In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
+
+\medskip
+As usually seen for high viscosity contrast, the leading finger screens out the trailing by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
+At long times the large finger advances approximately at
+constant velocity. Results which question the evolution of fingers and the finger competition are those referring to the dynamic role of viscosity contrast.
+
+\medskip
+In summary, the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
+\begin{enumerate}
+\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
+%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
+%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
+%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
+
+\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domain.
+The higher the mobility ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
+\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
+At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
+The domain used in these test-cases the development of the flow follow the linear tip-splitting finger behaviour.
+\item[4.] Properties such as porosity and saturation can be readily up-scaled using statistical methods, can be included in the element boundaries,  while production simulations run directly on the geological model without the need to upscale.
+\end{enumerate}
+
+%\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
+Keeping both the thickness and the injection rate constant, it was observed that increasing the mobility ratio decreases the finger width, which subsequently leads to more fingers and subsequently more complexity at a given distance away from the injection point.
+Tip-splitting, a phenomenon in which the initial stage of fingers split into two or more new fingers, can also be observed at higher mobility ratios.}
+
+\section{Acknowledgements}
+Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
+Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
+
+\clearpage
+
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv} 
+\bibliography{references}
+\clearpage
+
+\listoftables
+\clearpage
+
+\input{article_table}
+\clearpage
+
+\listoffigures
+\clearpage
+
+\input{article_figure1}
+%\input{article_figure2}
+
+\end{document}
+%% End of tex file.
+
 %%  LocalWords:  checkboard

### 2017-06-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies~\citep{white_1981}.
+Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
 %Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, self_2012, jiang_2011}.
+Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
 
@@
 A comprehensive review of mechanisms of fluid instabilities (i.e., fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations \red{(COULD YOU EXPLAIN WHAT YOU MEANT WITH THIS SENTENCE?
-ALSO LINK THIS SENTENCE WITH THE FOLLOWING!)}.
+\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
 % Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated
Starting updates in the paper ... Intro

@@
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., wide spatial permeability distribution), gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
 

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

--- 2017-06-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
 

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

@@
 \medskip 
-Conservation of mass and Darcy's law are the governing equations that describe the flow dynamics in porous media.
-Several computational methods have been developed to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications.
+Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media.
+A number of computational methods have been developed to accurately represent force balances in Darcean flows.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
 However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

@@
 Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media.
-A number of computational methods have been developed to accurately represent force balances in Darcean flows.
+Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
 Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

@@
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
-FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
+%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
 %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
@@
 Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-
-\medskip
 Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
 while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
@@
 
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
 Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
 These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
 \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
 
@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
-Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical investigation of formation and evolution of viscous fingers in heterogeneous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
 A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.

### 2017-06-16 Papers/ViscousInstabilities/article_figure1.tex
cleaning the paper adding some extra info
Starting updates in the paper ... Intro

@@
 \vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+\caption{2D representation of $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue and white circles represent pressure and velocity nodes, respectively.}
 \label{fig:fem_cv}

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

@@
 A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
+A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
 The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
@@
 Impact of mobility ratio on the fingers formation is also included in this section.
-The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
@@
 \end{eqnarray}
-respectively, where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.

### 2017-06-16 Papers/ViscousInstabilities/article_figure1.tex
Starting updates in the paper ... Intro

@@
 \vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored), blue and white circles represent pressure and velocity nodes, respectively.}
+\caption{2D representation of \PN[1]{2} element pairs used in this work.
+Shaded areas denote control volumes across two contiguous elements.
+Blue and white circles represent pressure and velocity nodes, respectively.}
 \label{fig:fem_cv}
 \end{figure}
+
+\clearpage
 
@@
 \caption{This is a description of two different element types.
-Element A is the $P_{1}DGP_{2}$, while element B is the $P_{1}DGP_{1}$.
-Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements $P_{o}DG$.
-The velocity and pressure are associated to the element nodes and the mid-points as described in Fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.
-}
+Element A is the \PN[1]{2}, while element B is the \PN[1]{1} \red{(THIS IS NOT CORRECT!!)}.
+Porosity $\phi_{i}$ \red{(THIS DOES NOT APPEAR IN THE FIGURE ...
+AT LEAST NOT WITH THIS SYMBOL)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
+Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
 \label{fig:fem_elem}
 \end{figure}
+
+\clearpage
 

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Editing Section 2

@@
 \medskip
-The two-phase flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
+The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
 \begin{eqnarray}
@@
 \end{eqnarray} 
-respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
+respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
 $\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with constraints of
+$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of
 \begin{displaymath}
@@
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
-\begin{displaymath}
-   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
-\end{displaymath}
-Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
+%\begin{displaymath}
+%   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
+%\end{displaymath}
+Though, whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 
@@
 Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
 %Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.

### 2017-06-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Editing Section 2

@@
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
-This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
+This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-
-\medskip
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system.
-The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
-Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
-
-\medskip
+\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
+
+\medskip
+The behaviour of the fluid under conditions \red{(what sort of conditions?
+thermophysical, rheological ...???)} that exceed critical limits may cause flow instabilities.
+For example, the flow of a fluid over or next to a heavier fluid can produce flow instabilities.
+Thus, when a fluid is injected into a porous domain saturated with a second and more viscous fluid, viscous fingering may occur as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
-T is the surface tension and U is a velocity characteristic of the moving interface.
-
+\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates, and the impact of capillary number ($N_{c}$),
 \begin{equation}
-N_{C} = \frac{\mu U}{T}
+N_{C} = \frac{\mu U}{\gamma},
 \label{eq:capillary_number}
 \end{equation}
-
-For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
+on the interface pressure and pressure.
+\citet{muskat_1934} also derived the perturbation solution of this axisymmetric problem.
+In Eqn.~\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
 
@@
 More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
+Thus if \textit{Ca} \red{(What is Ca?)} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
 
@@
 
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in Section \ref{section:results_homo_hete}.
+In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section \ref{section:results_homo_hete}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
 Pressure differences acting on the interface produces a net pressure force,
-
 \begin{equation}
@@
 \end{equation}
-
-This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
-
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
-
+This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference \red{(capillary pressure or pressure ??)} across the interface between two fluids.
+With $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
+
+As demonstrated by \citet{habermann_1960}, mobility ratio (MR) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 \end{equation}
-
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-
 where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
@@
 From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio,
 \begin{displaymath}

### 2017-06-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Editing Section 2

@@
  that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
-\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
-
-In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field which is calculated along with pressure and velocity.
+
+In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
@@
 
-Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
 This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

### 2017-06-17 Papers/ViscousInstabilities/article_table.tex
cleaning the paper adding some extra info
Editing Section 2

@@
      \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 1.0 & 2.5 & N/A & N/A & N/A & 0.2 & 0.3 & 1.0 \\
-      \ref{section:results_homo_hete}  & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
+     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.0 & N/A & N/A & N/A & N/A & 0.2 & 0.3 & XX  \\
+     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 - & 1.e-12 - & 1.e-12 - & 1.e-10 & N/A & 0.2  & 0.3 & 1.0 \\
+      &   &  &  &  & 5.e-10$^a$ & 5.e-10$^b$ & 1.e-10$^b$  &  &  &  & & \\
      \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & N/A & 0.2 & 0.3 & XX  \\
+     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & N/A & 0.2  & 0.3 & XX  \\
      \hline
@@
 Superscript $0$ denotes initial condition.
-\red{(KOSTAS, PLEASE: 1.
+a: random.gauss, b: random.uniform \red{(thus give the range of distribution of K!)} \blue{(PLEASE: 1.
 DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2.

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Editing Section 2

--- 2017-06-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
+\newcommand{\eg}{{\it e.g.,}} 
+\newcommand{\ie}{{\it i.e.,}}
 
@@
 Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of mechanisms of fluid instabilities (i.e., fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
 \citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
@@
 Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
 
@@
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
 Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
@@
 
-Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
+Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
 
@@
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, i.e., $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
 Fluids are assumed incompressible and gravity was neglected.
@@
 \medskip
-The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
-The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.
+The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
 Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
@@
 On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
-Therefore for an i.e., water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
+Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
 Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
@@
 Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media.
-A comprehensive review of mechanisms of fingering (i.e., fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+A comprehensive review of mechanisms of fingering (\ie fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
 \citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
@@
 Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (i.e., large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
 
@@
 In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
 Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
@@
 Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (e.g., advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
 
@@
 The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
-The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
+The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
 Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Editing Section 2

@@
 Element A is the \PN[1]{2}, while element B is the \PN[1]{1} \red{(THIS IS NOT CORRECT!!)}.
-Porosity $\phi_{i}$ \red{(THIS DOES NOT APPEAR IN THE FIGURE ...
-AT LEAST NOT WITH THIS SYMBOL)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
+Porosity $\phi_{i}$ \red{(THIS SYMBOL DOES NOT APPEAR IN THE FIGURE !!)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
 Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
@@
 \clearpage
-
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[h]
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.0cm} (a)  
-}
-\vspace{0.5cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
-}
-\vspace{1.0cm}
-\hbox{\hspace{6.0cm} (b)  
-}}     
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fem_cv_represent_a}
-\end{figure}
-\clearpage
-\end{comment}
 
@@
 \clearpage
+
+%%%
+%%% FIGURE
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+    \vbox{ 
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
+      \hbox{\hspace{10cm} (a) VR = 1}
+      \vspace{1cm}
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf} }
+      \hbox{\hspace{10cm} (b) VR = 10  }}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).}
+\label{fem_cv_represent_a}
+\end{figure}
+\end{landscape}
+\clearpage
+%%%
+%%%
+%%%
 

### 2017-06-19 Papers/ViscousInstabilities/article_table.tex
Editing Section 2

--- 2017-05-25 Papers/ViscousInstabilities/article_table.tex
@@
 \begin{table}
-  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c  c   c}
+  \begin{tabular}{c | c c  c  c  c  c  c  c  c  c   c}
     \hline
-      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $K_{5}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
+      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
     \hline
-      \ref{section:results_validation} & 0.2  & 1.0  & 0.0  & 1.0  & 1.0  & 2.5  & N/A  & N/A  & N/A & 0.2  & 0.3 & 1.0 \\
-      \ref{section:results_homo_hete}  & 0.2  & 10.0 & 0.0  & 1.0  &  XX  & N/A  & N/A  & N/A  & N/A & 0.2  & 0.3 & XX  \\
-      \ref{section:results_hete_fix_adapt}  & 0.2  & 1.0  & 0.0  & 1.0  &  3.0  & 2.0  & 5.0  & 1.0  & N/A & 0.2  & 0.3 & XX  \\
+     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 1.0 & 2.5 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
+     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.0 & N/A & N/A & N/A & 0.2 & 0.3 & XX  \\
+     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
+      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
+     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & XX  \\
+     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & XX  \\
      \hline
@@
 Superscript $0$ denotes initial condition.
-\red{(KOSTAS, PLEASE: 1.
+\blue{(PLEASE: 1.
 DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2.
-REPLACE ALL XX; 3.
+\underline{REPLACE ALL \red{XX}}; 3.
 COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 \newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
-\newcommand{\eg}{{\it e.g.,}} 
-\newcommand{\ie}{{\it i.e.,}}
+\newcommand{\eg}{{\it e.g., }} 
+\newcommand{\ie}{{\it i.e., }}
 
@@
  && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
  &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
@@
 $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
 This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
@@
 
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete}; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet}.
 
@@
  && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\dot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n} \cdot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
  &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
@@
 
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt} ; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete} ; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete}; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
 
@@
 \medskip
-The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
+The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in homogeneous porous media.
+The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
 The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 \medskip
-The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in homogeneous porous media.
+The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in heterogeneous porous media.
+The numerical experiment is similar to the lab set up by \citet{evans_1994} and \citet{dawe_2008}
+
 The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 \medskip
-The test-case shown in this section demonstrates the model capability to capture viscous crossflow in immiscible displacement in homogeneous porous media.
+Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is \red{XX} $\times$ \red{XX} unit-length and fully saturated with fluid 2 ({\it VR}=1).
+Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
+Boundary conditions also includes no-flux across upper and lower boundaries.
+The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
+
+Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
+They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions.
+Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{evans_1994} \citep[see also][]{dawe_2008}.
+
 The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
 \vbox{
-\hbox{\hspace{0.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+\hbox{\hspace{-0.3cm}
+\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K  
+\hbox{\hspace{5.0cm} (a) map of permeabilities ($\mathbf{K}$)
 }
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
+\hbox{\hspace{5.0cm} (b) flow at t=250  \red{(Is this time or the vtu number ??)}
 }
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
 }
@@
 }     
-\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
+\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{t=XX} and \red{t=XX}.
+The domain is discretised in \red{XX} \PN[1]{2} elements.
+\red{(ALSO YOU MUST ADD SATURATION LEGENDS IN ALL FIGURES.)}}
 \label{fem_cv_represent_a}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 
+\medskip
+Two further numerical simulations were performed in slightly modified test-cases (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under distinct viscosity ratio conditions.
+In both simulations initial and boundary conditions remain the same, but V, but in this set of simulations the geometrical aspect ration is $2$ is following.
+The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
+The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
+
 The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
       \hbox{\hspace{10cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).
+\red{(It is clear that figures are not correct ...
+as they seem wrong.)}}
 \label{fem_cv_represent_a}

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

--- 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 %%%%%%%%%%%% 
-\subsection{Model Validation}\label{section:results_validation}
+\subsection{Initial Model Validation}\label{section:results_validation}
 
@@
 They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions.
-Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{evans_1994} \citep[see also][]{dawe_2008}.
-
-The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
-Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
-
-\medskip
-Fluid $1$ is introduced from the left hand side of the formation.
-Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
-Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain.
-Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively.
-Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used).
-%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
-A domain consisting of $4$ square regions in which each quarter is represented by a permeability value %(Fig.\ref{fig:square}a) 
-and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
-At the upper and lower sides of the domain no-slip boundary condition is applied.
-The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$.
-The right hand side is the outlet and pressure is set to $0$.
-Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$.
-What can been seen here is a cross flow case as the flow passes through different regions and evolves.
-The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
-%\ref{fig:square}b).
-
-\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
-The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further %\ref{fig:square})
-while the phase volume fraction is constant.
-
-\medskip
-A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
-The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
-The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
-
-\medskip
-In this section three different sets of simulations were explained.
+Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+
+\medskip
+Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994} (\red{ ....
+COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})
+
+\red{KOSTAS ... HAVE A LOOK IN FIG.~\ref{fem_cv_represent_abc} ... SATURATION PROFILES DO NOT SEEM TO MATCH ...}
+
+\medskip
+In this section three \red{(??)} different sets of simulations were explained.
 Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio.
@@
 
+\medskip
+\noindent
+\red{QUICK QUESTIONS ... \\
+\noindent
+A) FOR THE FIRST TEST-CASE, WAS THE SIMULATION PERFORMED IN A SQUARED DOMAIN (FROM THE PICS, IT SEEMS TO BE RECTANGULAR)?
+\\ B) THUS ASSUMING THAT THE FIRST DOMAIN WAS RECTANGULAR, THUS IT IS THE SAME AS THE SECOND SIMULATION!
+THUS WHY THE SATURATION PROFILE IS DIFF (FOR VR=1) FROM SIMULATION 1???
+\\
+\noindent
+C) ALSO: DO NOT USE 'WE' IN TECHNICAL TEXT ... IT DOES REALLY DOWNGRADE IT !!! }
+
 %%%%%%%%%%%%  
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results_homo_hete}
-
-\medskip
+\subsection{Flow Simulations in Hele-Shaw Cells at Several Viscosity Ratio Conditions}\label{section:results_homo_hete}
+
+In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work.
+In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem formulation and solution.
+
+Here, 2D simulations are conducted in 5$\times$5 domain, Fig.~\ref{fig:homoheleshaw}(a) fully saturated with a fluid.
+Wetting phase fluid is injected from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
+A zero-flux condition was applied to all boundaries, except the top right-hand corner (named as sink).
+XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
+ of the problem. formation and stability of viscous flow instaseminal work of \citet{saffman_1986}
 Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3}

### 2017-06-19 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
       \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
+      \vspace{0.cm}
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
+\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
+\label{fem_cv_represent_abc}
+\end{figure}
+\end{landscape}
+\clearpage
+%%%
+%%%
+%%%
+
+%%%
+%%% FIGURE
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+    \vbox{ 
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
             \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
@@
 \end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{1.0cm} (a) Hell-Shaw cell domain \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{3.0cm} (e) t=1000\red{(???)}   \hspace{4.cm} (f) t=XXX\red{(???)}}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell: (a) source and sink regions are explicitly shown along with prescribed dimensions; (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains \red{XX} \PN[1]{2} elements and {\it VR}=1.}
+\label{fig:homoheleshaw}
+\end{figure}
+\end{landscape}
 \clearpage

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

@@
 In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work.
-In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem formulation and solution.
-
-Here, 2D simulations are conducted in 5$\times$5 domain, Fig.~\ref{fig:homoheleshaw}(a) fully saturated with a fluid.
-Wetting phase fluid is injected from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
-A zero-flux condition was applied to all boundaries, except the top right-hand corner (named as sink).
-XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
- of the problem. formation and stability of viscous flow instaseminal work of \citet{saffman_1986}
-Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3}
-\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
-In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
-. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
-was imposed to all borders of the domain except at the top righ hand side corner.
-The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
+In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.
+
+Here, 2D simulations were conducted in a 5$\times$5 unit-length domain (Fig.~\ref{fig:homoheleshaw}a) fully saturated with a fluid.
+Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
+Newmann boundary condition (\ie, no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink).
+Viscosity ratios for this set of simulations are 3 and 10.
 

### 2017-06-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

@@
 
-In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following \citet{saffman_1986} work.
-In this work, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.
+In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following work by \citet{saffman_1986}.
+In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.
 
@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
-Newmann boundary condition (\ie, no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink).
+Newmann boundary condition (\ie no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink).
 Viscosity ratios for this set of simulations are 3 and 10.

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

@@
 
-In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following work by \citet{saffman_1986}.
-In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem mathematical formulation and solutions.
+In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
+In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem's mathematical formulation and solutions.
 

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 
-Here, 2D simulations were conducted in a 5$\times$5 unit-length domain (Fig.~\ref{fig:homoheleshaw}a) fully saturated with a fluid.
+Here, 2D simulations were conducted in a 5$\times$5 unit-length Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN1}a) fully saturated with a fluid.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
-Newmann boundary condition (\ie no flux) was imposed to all borders of the domain except at the top right-hand corner (named as sink).
-Viscosity ratios for this set of simulations are 3 and 10.
-
+Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.
+Viscosity ratios for this set of simulations were 1, 3 and 10.
+
+Figures~\ref{fig:homoheleshaw_VN1} (b-f) show continuous fluid displacement in a simulation conducted with {\it VR}=1.
+As expected (in a similar way as the Buckley-Leverett solution), saturation evolves in tie with a smooth front throughout most of the domain
 \medskip
@@
 The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
-For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
+For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.
 

### 2017-06-20 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
 \begin{figure}[ht] 
-\vbox{
+\vbox{\vspace{-1cm}
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}
@@
 \vspace{0.cm}
-\hbox{\hspace{1.0cm} (a) Hell-Shaw cell domain \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
+\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
 \vspace{0.5cm}
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell: (a) source and sink regions are explicitly shown along with prescribed dimensions; (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains \red{XX} \PN[1]{2} elements and {\it VR}=1.}
-\label{fig:homoheleshaw}
+\caption{Simulated flow in a Hele-Shaw cell: (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains \red{XX} \PN[1]{2} triangular elements and {\it VR}=1.
+\red{(ADD SATURATION AND PRESSURE LEGENDS !!)}}
+\label{fig:homoheleshaw_VN1}
 \end{figure}

### 2017-06-20 Papers/ViscousInstabilities/article_table.tex
Start updating Results Section 4.2

@@
     \hline
-      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $K_{1}$ & $K_{2}$ & $K_{3}$ & $K_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{0}_{w}$ \\ 
+      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $\mathbf{K}_{1}$ & $\mathbf{K}_{2}$ & $\mathbf{K}_{3}$ & $\mathbf{K}_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{\circ}_{w}$ \\ 
     \hline
-     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 1.0 & 2.5 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
-     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.0 & N/A & N/A & N/A & 0.2 & 0.3 & XX  \\
+     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
+     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & \red{XX}  \\
      \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
       &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
-     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & XX  \\
-     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & XX  \\
+     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & \red{XX}  \\
+     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & \red{XX}  \\
      \hline
@@
    \caption{Sumary of model set-up used in the numerical simulations.
-Superscript $0$ denotes initial condition.
-\blue{(PLEASE: 1.
+Superscript $\circ$ denotes initial condition.
+$\mathbf{K}_{i}$ is in \red{XX} (units) and $u^{\circ}_{w}$ is in \red{XX} (units).
+\red{(PLEASE: 1.
 DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2.
 \underline{REPLACE ALL \red{XX}}; 3.
-COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS.
-$S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.) }}\label{table:setup}
+COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS; 4.
+UNITS FOR K AND U.)}  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.
+}\label{table:setup}
 \end{table}

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 
-Here, 2D simulations were conducted in a 5$\times$5 unit-length Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN1}a) fully saturated with a fluid.
+Here, 2D simulations were conducted in a 5$\times$5 unit-length Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
 Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.
-Viscosity ratios for this set of simulations were 1, 3 and 10.
-
-Figures~\ref{fig:homoheleshaw_VN1} (b-f) show continuous fluid displacement in a simulation conducted with {\it VR}=1.
-As expected (in a similar way as the Buckley-Leverett solution), saturation evolves in tie with a smooth front throughout most of the domain
+Viscosity ratios for this set of simulations were 3 and 10.
+
+Figures~\ref{fig:homoheleshaw_VN3} (b-f) show continuous fluid displacement in a simulation conducted with {\it VR}=3.
+At such relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
 \medskip

### 2017-06-20 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell: (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains \red{XX} \PN[1]{2} triangular elements and {\it VR}=1.
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains \red{XX} \PN[1]{2} triangular elements.
 \red{(ADD SATURATION AND PRESSURE LEGENDS !!)}}
-\label{fig:homoheleshaw_VN1}
+\label{fig:homoheleshaw_VN3}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=4000\red{(???)}}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{4.cm} (e) t=XXX\red{(???)}}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains \red{XX} \PN[1]{2} triangular elements.
+\red{(ADD SATURATION AND PRESSURE LEGENDS !!
+...
+IF THE LEGENDS ARE THE SAME AS IN THE PREVIOUS PIC, THEN JUST EXPLICITLY REFER TO THEM)}}
+\label{fig:homoheleshaw_VN10}
 \end{figure}

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.
-Viscosity ratios for this set of simulations were 3 and 10.
-
-Figures~\ref{fig:homoheleshaw_VN3} (b-f) show continuous fluid displacement in a simulation conducted with {\it VR}=3.
-At such relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
+
+Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10} show continuous fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
+At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
+Elongated saturation profile is due to pressure gradient near the sink region.
+However, in the simulation conducted with {\it VR}=10
 \medskip

### 2017-06-20 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains \red{XX} \PN[1]{2} triangular elements.

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Start updating Results Section 4.2

@@
 
-Here, 2D simulations were conducted in a 5$\times$5 unit-length Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
-Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of $\frac{\sqrt{2}}{2}$.
+Here, 2D simulations were conducted in a 5$\times$5 cm Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
+Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
 Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.
 
-Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10} show continuous fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
+Figures~\ref{fig:homoheleshaw_VN3} and\ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
 At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
-Elongated saturation profile is due to pressure gradient near the sink region.
+Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
 However, in the simulation conducted with {\it VR}=10

### 2017-06-20 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: Revision of Section 4.3

@@
 
-In order to investigate the impact of viscosity ratio on flow behaviour, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
+In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
 In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem's mathematical formulation and solutions.
@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary condition was imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions were initially imposed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
 

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-If \textit{Ca} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
+If \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
 

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 
+\medskip
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
@@
 
+\medskip
 Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
@@
 
+\medskip
 This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 
+\medskip
 Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation, 
@@
 \medskip
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system.
+As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits (unstable interface because of viscocity differences, density differences,the existance of gravitational forces or not, and/or opposite stress tensors) may cause instabilities in the system.
 The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell,
-T is the surface tension and U is a velocity characteristic of the moving interface.
+\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $ \alpha \beta \gamma $ is the surface tension and U is a velocity characteristic of the moving interface.
 

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Section 4.3

@@
 
-Figures~\ref{fig:homoheleshaw_VN3} and\ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
-At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
+Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
+At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.

### 2017-06-23 Papers/ViscousInstabilities/article_figure1.tex
Start updating Results Section 4.2
updates on progress

@@
 \vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
-\caption{This is a description of two different element types.
-Element A is the \PN[1]{2}, while element B is the \PN[1]{1} \red{(THIS IS NOT CORRECT!!)}.
-Porosity $\phi_{i}$ \red{(THIS SYMBOL DOES NOT APPEAR IN THE FIGURE !!)} and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
+\caption{This is a graphical representation of two different element types.
+Element A is the \PN[1]{2}, while element B is the \PN[1]{1}.
+Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
 Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
+}
 \label{fig:fem_elem}
@@
 \vspace{0.cm}
-\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=4000\red{(???)}}
+\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
 \vspace{0.5cm}

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Section 4.3
updates on progress

--- 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
+\medskip
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
@@
 $\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
+
 \begin{displaymath}
@@
 \end{displaymath}
+
 Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
@@
 \end{eqnarray}
+
 where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex

@@
 
-Figures~\ref{fig:homoheleshaw_VN3} and\ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
-At relatively low viscosity ratio, saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
+Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
+At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, in the simulation conducted with {\it VR}=10
+However, in the simulation conducted with {\it VR}=10, the formation of fingers can be noticed at early stages of the simulation.
 \medskip

### 2017-06-23 Papers/ViscousInstabilities/article_figure1.tex
updates on progress

@@
 \centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}}
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
 \caption{This is a graphical representation of two different element types.
@@
 Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
-}
 \label{fig:fem_elem}
 \end{figure}
-
 \clearpage
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  \red{(Is this time or the vtu number ??)}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
 }
@@
 }     
-\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{t=XX} and \red{t=XX}.
-The domain is discretised in \red{XX} \PN[1]{2} elements.
-\red{(ALSO YOU MUST ADD SATURATION LEGENDS IN ALL FIGURES.)}}
+\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec.
+The domain is discretised in $5960$ \PN[1]{2} elements.
+}
 \label{fem_cv_represent_a}

### 2017-06-23 Papers/ViscousInstabilities/article_figure1.tex
updates on progress

@@
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilities ($\mathbf{K}$)
+\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
+\hbox{\hspace{4.5cm} (b) flow at t=250  
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (c) flow at t=3000  
+\hbox{\hspace{4.0cm} (c) flow at t=3000  
 }
@@
 
+\begin{comment}
 %%%
@@
 %%%
+\end{comment}
 
@@
     \vbox{ 
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
-      \hbox{\hspace{10cm} (a) VR = 1}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
+      \hbox{\hspace{8.0cm} (a) VR = 1}
       \vspace{1cm}
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf} }
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
       \hbox{\hspace{10cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10 (the domain contains \red{XX} elements).
-\red{(It is clear that figures are not correct ...
-as they seem wrong.)}}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
 \label{fem_cv_represent_a}

### 2017-06-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 \medskip
-The behaviour of the fluid under conditions \red{(what sort of conditions?
-thermophysical, rheological ...???)} that exceed critical limits may cause flow instabilities.
+The behaviour of the fluid under conditions caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits can cause flow instabilities.
 For example, the flow of a fluid over or next to a heavier fluid can produce flow instabilities.
@@
 For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-Thus if \textit{Ca} \red{(What is Ca?)} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
+Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
 
@@
 
+\medskip 
 In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section \ref{section:results_homo_hete}.
@@
 \end{equation}
-This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference \red{(capillary pressure or pressure ??)} across the interface between two fluids.
+
+This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids.
 With $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
 
+\medskip
 As demonstrated by \citet{habermann_1960}, mobility ratio (MR) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
@@
 \end{equation}
+
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
@@
 
+\medskip
 From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
@@
 
+\medskip
 In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
@@
 
+\medskip
 In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete}; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet}.
@@
 
+\medskip
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.

### 2017-06-23 Papers/ViscousInstabilities/article_figure1.tex
updates on progress

@@
             \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
-      \hbox{\hspace{10cm} (b) VR = 10  }}
+      \hbox{\hspace{8.0cm} (b) VR = 10  }}
 \caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
@@
 \clearpage
+\end{comment}
 
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
+\hbox{\includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
+      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
 \vspace{0.cm}
-\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
+\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{4.cm} (b) t=250\red{(???)} \hspace{2.5cm} (c) t=1000\red{(???)}}
 \vspace{0.5cm}
 \hbox{
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
+      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
 \vspace{0.cm}

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, in the simulation conducted with {\it VR}=10, the formation of fingers can be noticed at early stages of the simulation.
-\medskip
+However, formation of fingers can be noticed at early stages of the simulation conducted with {\it VR}=10.
+
 In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.

### 2017-06-25 Papers/ViscousInstabilities/article_figure1.tex
updates on progress
updates

@@
       \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
+      \includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{3.0cm} (e) t=1000\red{(???)}   \hspace{4.cm} (f) t=XXX\red{(???)}}
+\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{4.0cm} (e) t=1000\red{(???)}   \hspace{2.5cm} (f) t=XXX\red{(???)}}
 \vspace{0.cm}
@@
 \end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-1cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
+      \hbox{\hspace{1.0cm} (a) t=0\red{??} \hspace{3.cm} (b) t=500\red{(???)} \hspace{3.0cm} (c) t=2000\red{(???)}}
+      \vspace{0.5cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
+      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{3.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
+\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
+The domain contains \red{XXXX} elements.}
+\label{HeleShawHeter_VR10}
+\end{figure}
+\end{landscape}
 \clearpage

### 2017-06-25 Papers/ViscousInstabilities/article_figure1.tex
changes on progress

@@
-%%%%%%%%%%%%%%%%
-%%% Figure 1 %%%
-%%%%%%%%%%%%%%%%
-%\begin{figure}[h]
-%\begin{center}
-%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
-%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
-Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
-%\label{fig:fem_cv}
-%\end{center}
-%\end{figure}
-%\clearpage
-
-%%%%%%%%%%%%%%%%
-%%% Figure 2 %%%
-%%%%%%%%%%%%%%%%
-%\begin{figure}[h] 
-%\begin{center}
-%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
-%\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
-The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
-Saturation and saturation-dependent variables are stored CV-wise.}
-%\label{fig:fem_elem}
-%\end{center}
-%\end{figure}
-%\clearpage
-
 %%%%
@@
 %%%%
-%%%%  FIGURE 1
+%%%%  FIGURE 
 %%%%
@@
 %%%%
-%%%%  FIGURE 4
+%%%%  FIGURE 
 %%%%
@@
 
-\begin{comment}
-%%%
-%%% FIGURE
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-    \vbox{ 
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
-      \vspace{0.cm}
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
-\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
-\label{fem_cv_represent_abc}
-\end{figure}
-\end{landscape}
-\clearpage
-%%%
-%%%
-%%%
-\end{comment}
-
 %%%
@@
 
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
-\label{fig:6a}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
-\label{fig:6b}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
-\label{fig:6c}
-\end{figure}
-\clearpage
-\end{comment}
-
 %%%%
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
-      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
+\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
+      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
 \vspace{0.cm}
-\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{4.cm} (b) t=250\red{(???)} \hspace{2.5cm} (c) t=1000\red{(???)}}
+\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{5.cm} (b) t=250\red{(???)} \hspace{2.75cm} (c) t=1000\red{(???)}}
 \vspace{0.5cm}
 \hbox{
-      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-      \includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
+      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{4.0cm} (e) t=1000\red{(???)}   \hspace{2.5cm} (f) t=XXX\red{(???)}}
+\hbox{ \hspace{1.cm} (d) t=2500\red{(???)} \hspace{2.0cm} (e) t=1000\red{(???)}   \hspace{3.0cm} (f) t=XXX\red{(???)}}
 \vspace{0.cm}
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains \red{XX} \PN[1]{2} triangular elements.
-\red{(ADD SATURATION AND PRESSURE LEGENDS !!)}}
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $47500$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN3}
@@
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{4.cm} (e) t=XXX\red{(???)}}
+\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
 \vspace{0.cm}
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains \red{XX} \PN[1]{2} triangular elements.
-\red{(ADD SATURATION AND PRESSURE LEGENDS !!
-...
-IF THE LEGENDS ARE THE SAME AS IN THE PREVIOUS PIC, THEN JUST EXPLICITLY REFER TO THEM)}}
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $47000$ \PN[1]{2} triangular elements.
+The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
 \label{fig:homoheleshaw_VN10}
@@
 \end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
-\label{fig:1a_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=2500  
-}
-}     
-\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
-\label{fig:1b_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=3500   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end  
-}
-}     
-\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:1c_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
-\label{fig:2a_homoheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
-}
-}     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht]
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end   
-}
-}     
-\caption{Fingers are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:2c_homoheleshaw_10}
-\end{figure}
 \clearpage
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{1.0cm} (a) t=0\red{??} \hspace{3.cm} (b) t=500\red{(???)} \hspace{3.0cm} (c) t=2000\red{(???)}}
+      \hbox{\hspace{2.0cm} (a) t=0\red{??} \hspace{5.cm} (b) t=500\red{(???)} \hspace{4.0cm} (c) t=2000\red{(???)}}
       \vspace{0.5cm}
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
-      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{3.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
+      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{5.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
 \caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
@@
 \end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in figure \ref{fig:3b_heteheleshaw_10} and figure \ref{fig:3c_heteheleshaw_10}.}
-\label{fig:3a_heteheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=2000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000     
-}
-}     
-\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
-Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
-\label{fig:3b_heteheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000    
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.75cm} (b) flow at t=24000     
-}
-}     
-\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
-At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
-\label{fig:3c_heteheleshaw_10}
-\end{figure}
 \clearpage

### 2017-06-25 Papers/ViscousInstabilities/article_figure2.tex
working-updated
changes on progress

@@
-%\begin{figure}[ht] 
+%%%%%%%%%%%%%%%%
+%%% Figure 1 %%%
+%%%%%%%%%%%%%%%%
+%\begin{figure}[h]
 %\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_perm} 
-%\caption{Caption 1}
-%\label{fig:subim1}
+%\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}
+%\caption{2D representation of the $P_{1}DGP_{2}$ element pairs used in this work.
+Shaded areas denote control volumes (in which saturation field is stored), blue points represent the pressure nodes and white points the velocity nodes.}
+%\label{fig:fem_cv}
 %\end{center}
-
-%\begin{center}
-%\includegraphics[width=0.75\linewidth, height=7cm]{2b2_P1DGP2_mesh} 
-%\caption{Caption 1}
-%\label{fig:subim1}
-%\end{center}
-
-%\begin{center}
-%\centering
-%\includegraphics[width=0.75\linewidth, height=6cm]{2b2_P1DGP2_plot}
-%\caption{Caption 3}
-%\label{fig:subim3}
-%\end{center}
-
-%\caption{Caption for this figure with two images}
-%\label{fig:image1}
 %\end{figure}
-%\pagebreak
 %\clearpage
 
-%\begin{figure}[ht] 
+%%%%%%%%%%%%%%%%
+%%% Figure 2 %%%
+%%%%%%%%%%%%%%%%
+%\begin{figure}[h] 
 %\begin{center}
-%\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}
-%\caption{This is the case where the initially piston shape front is collapsing and starts forming fingers in an unstructured domain with uniform permeability (3000 elements, K=1, MR=5).}
-%\label{fig:simple_case}
+%\includegraphics[width=.5\textwidth]{./Pics/element_n.pdf}
+%\caption{Porosity $\phi_{i}$, and permeability $K_{i}$ are associated to the elements.
+The velocity and pressure are associated to the element corners and the mid-points as described in fig.\ref{fig:fem_cv}; three CVs fit into a $2$D element.
+Saturation and saturation-dependent variables are stored CV-wise.}
+%\label{fig:fem_elem}
 %\end{center}
 %\end{figure}
+%\clearpage
 
-%\begin{figure}[ht] 
-%\begin{center}
-%\subfigure[Initial and boundary conditions]{\includegraphics[width=0.65\textwidth]{./Pics/2b2_P1DGP2.pdf}\label{a}}
-%\subfigure[Plots of velocity magnitude, pressure and phase volume fraction]{\includegraphics[width=0.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}\label{b}}
-%\caption{This is the first test-case of a region with four squares of constant permeabilities K of $1$ at the the blue region and $2.5$ at the red region.
-The mesh is unstructured and fixed with 5000 elements.
-Fluid $1$ is introduced from the right hand side at a constant velocity of u = $1$, This test-case is based on the experimental work of \citet{evans_1994}.}
-%\label{fig:square}
-%\end{center}
-%\end{figure}
+%%%%
+%%%%  FIGURE 
+%%%%
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
+\caption{2D representation of \PN[1]{2} element pairs used in this work.
+Shaded areas denote control volumes across two contiguous elements.
+Blue and white circles represent pressure and velocity nodes, respectively.}
+\label{fig:fem_cv}
+\end{figure}
 
-%\begin{figure}[ht] 
-%   \vbox{
-%       \hbox{\includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2.pdf}
-%             \includegraphics[width=.5\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}}
-%       \hbox{\hspace{3cm}(a) \PN[1]{2} \hspace{4.cm} (b)\PNDG[2]{1}}}
-%\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is   stored), black points% represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-%    \label{fem_cv_represent_a}
-%\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
+\caption{This is a graphical representation of two different element types.
+Element A is the \PN[1]{2}, while element B is the \PN[1]{1}.
+Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
+Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
+\label{fig:fem_elem}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE 1
+%%%%
+\begin{figure}[h]
+\centering
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
+\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
+The ratio of viscosity between the two fluids is 5.
+In this case, the initially piston shape front collapses leading to the formation of several fingers.}
+\label{fig:simple_case}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE 4
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{-0.3cm}
+\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.5cm} (b) flow at t=250  
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (c) flow at t=3000  
+}
+}     
+\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec.
+The domain is discretised in $5960$ \PN[1]{2} elements.
+}
+\label{fem_cv_represent_a}
+\end{figure}
+\clearpage
+
+\begin{comment}
+%%%
+%%% FIGURE
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+    \vbox{ 
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
+      \vspace{0.cm}
+      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
+\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
+\label{fem_cv_represent_abc}
+\end{figure}
+\end{landscape}
+\clearpage
+%%%
+%%%
+%%%
+\end{comment}
+
+%%%
+%%% FIGURE
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+    \vbox{ 
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
+      \hbox{\hspace{8.0cm} (a) VR = 1}
+      \vspace{1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
+      \hbox{\hspace{8.0cm} (b) VR = 10  }}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
+\label{fem_cv_represent_a}
+\end{figure}
+\end{landscape}
+\clearpage
+%%%
+%%%
+%%%
+
+\begin{comment}
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
+\label{fig:6a}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
+\label{fig:6b}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
+}
+\vspace{0.25cm}
+\hbox{\hspace{1.5cm}
+\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
+}
+}     
+\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
+\label{fig:6c}
+\end{figure}
+\clearpage
+\end{comment}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
+      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+      \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{5.cm} (b) t=250\red{(???)} \hspace{2.75cm} (c) t=1000\red{(???)}}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
+\vspace{0.cm}
+\hbox{ \hspace{1.cm} (d) t=2500\red{(???)} \hspace{2.0cm} (e) t=1000\red{(???)}   \hspace{3.0cm} (f) t=XXX\red{(???)}}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $47500$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN3}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $47000$ \PN[1]{2} triangular elements.
+The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
+\label{fig:homoheleshaw_VN10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+\begin{comment}
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250  
+}
+}     
+\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
+More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
+\label{fig:1a_homoheleshaw_3}
+\end{figure}
+\clearpage
 
@@
 \hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2.pdf} 
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a)  
+\hbox{\hspace{5.0cm} (a) flow at t=1000   
 }
-\vspace{0.5cm}
+\vspace{0.25cm}
 \hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics/2b2_P1DGP2_plot.pdf}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
 }
-\vspace{1.0cm}
-\hbox{\hspace{5.0cm} (b)  
-}}     
-\caption{2D representation of the element pairs presented in this work.
-Shaded areas denote control volumes (in which saturation is stored), black points represent the pressure nodes and white points the velocity nodes.
-Note that in (b) velocity and pressure nodes overlap in the triangles' vertices.}
-\label{fem_cv_represent_a}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=2500  
+}
+}     
+\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
+\label{fig:1b_homoheleshaw_3}
 \end{figure}
+\clearpage
 
@@
 \vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000  
-}
-}     
-\caption{Using unstructured but fixed mesh the domain is devide into $4$ different regions of different permeabilities as these are represented in the figures above}
-\label{fem_cv_represent_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 100 (start)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 100 (start)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
-\label{fig:6a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 1500 (middle)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 1500 (middle)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
-\label{fig:6b}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) MR1 at t = 3000 (end)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.75\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) MR10 at t = 3000 (end)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
-\label{fig:6c}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in Fig.\ref{fig:1b_homoheleshaw_3} and Fig.\ref{fig:1c_homoheleshaw_3}}
-\label{fig:1a_homoheleshaw_3}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=2500  
-}
-}     
-\caption{Following Fig.\ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b)}
-\label{fig:1b_homoheleshaw_3}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
 }
@@
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
 }
@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
+\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
 }
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
 }
@@
 \caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:2b_homoheleshaw_10} and fig.\ref{fig:2c_homoheleshaw_10}}
+Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
 \label{fig:2a_homoheleshaw_10}
 \end{figure}
+\clearpage
 
@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
 }
@@
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
 }
@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
+\hbox{\hspace{5.0cm} (a) flow at t=6000   
 }
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
+\hbox{\hspace{5.0cm} (b) flow at t=end   
 }
 }     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
+\caption{Fingers are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
+\label{fig:2c_homoheleshaw_10}
 \end{figure}
+\clearpage
+\end{comment}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-1cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
+      \hbox{\hspace{2.0cm} (a) t=0\red{??} \hspace{5.cm} (b) t=500\red{(???)} \hspace{4.0cm} (c) t=2000\red{(???)}}
+      \vspace{0.5cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
+      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{5.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
+\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
+The domain contains \red{XXXX} elements.}
+\label{HeleShawHeter_VR10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+\begin{comment}
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
+}
+\vspace{0.25cm}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{5.0cm} (b) flow at t=250     
+}
+}     
+\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
+Screenshot will follow that describe the progression of the flow in figure \ref{fig:3b_heteheleshaw_10} and figure \ref{fig:3c_heteheleshaw_10}.}
+\label{fig:3a_heteheleshaw_10}
+\end{figure}
+\clearpage
 
@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end   
-}
-}     
-\caption{Finger are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:2c_homoheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in fig.\ref{fig:3b_heteheleshaw_10} and fig.\ref{fig:3c_heteheleshaw_10}}
-\label{fig:3a_heteheleshaw_10}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
 }
@@
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
 }
@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
 }
@@
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=24000     
+\hbox{\hspace{4.75cm} (b) flow at t=24000     
 }
@@
 \end{figure}
-%{./Pics/P1DG-P2_element_type} 
-%{./Pics/4r_po_adapt_fine_125_mesh} 
-%{./Pics/4r_po_adapt_fine_100_mesh}
+\clearpage
+\end{comment}
 
@@
 %%%%
+\begin{landscape}
 \begin{figure}[ht] 
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/map_of_boundaries.pdf} 
+\hbox{\hspace{4.0cm}
+\includegraphics[width=.8\textwidth]{./Pics/map_of_boundaries.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) map of permeabilties K   
+\hbox{\hspace{6.5cm} (a) map of permeabilties K   
 }
 \vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
+\hbox{\hspace{4.0cm}
+\includegraphics[width=.8\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b)      
+\hbox{\hspace{9cm} (b)      
 }
@@
 \end{figure}
+\end{landscape}
+\clearpage
 
@@
 %%%%
+\begin{landscape}
 \begin{figure}[ht] 
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=250   
+\hbox{\hspace{6.5cm} (a) flow at t=250   
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
+\hbox{\hspace{6.5cm} (b) flow at t=250     
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=500 (fixed mesh)   
+\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=500 (adaptive mesh)     
+\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
+\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
+\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
+\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
+\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
 }
@@
 %%%%
-%%%%
-%%%%  CHECK THIS BLOCK IF THE FILES ARE CORRECT ... CHANGED ON MAY 5TH
-%%%%
+\begin{landscape}
 \begin{figure}[ht] 
@@
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
+\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
 }
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
+  \includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
 }
 \vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
 }
@@
 \end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_b}
-\end{figure}
-
-%\begin{figure}[ht] 
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}\\[0.5cm]% If you want some vertical space
-%\makebox[\textwidth]{%
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
-%\hfill    
-%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
-%}%
-%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-%\label{fig:3testcase_b}
-%\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_c}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_d}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
-\label{fig:4testcase_a}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
-}
-}     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
-\label{fig:4testcase_b}
-\end{figure}
+\end{landscape}
+\clearpage
 
@@
 From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase}.
+for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase_a}.
 The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
@@
 %%%%
-
-\begin{comment}
 \begin{landscape}
-\begin{figure}[ht!]
-\begin{center}
-\subfigure[MR100, at the beginning of the simulations]{%
-\label{fig:1st}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_100}
-}%
-\subfigure[MR100, at the middle of the simulation]{%
-\label{fig:2nd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_fraction_mesh}
-}\\
-\subfigure[MR100, Phase 1 Volume fraction]{%
-\label{fig:3rd}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase1_vol_frac}
-}%
-\subfigure[MR100, Phase 2 Volume fraction]{%
-\label{fig:4th}
-\includegraphics[width=0.75\textwidth]{./Pics/4r_po_adapt_fine_125_phase2_vol_fraction}
-}\\
-\caption{Comparison of different MR's and their recovery rates}
-\label{fig:5}
-\end{center}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_b}
 \end{figure}
 \end{landscape}
-\end{comment}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_c}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
+}
+}     
+\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\label{fig:3testcase_d}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\label{fig:4testcase_a}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
+}
+}     
+\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
+\label{fig:4testcase_b}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
changes on progress
updates on progress

@@
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is \red{XX} $\times$ \red{XX} unit-length and fully saturated with fluid 2 ({\it VR}=1).
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1).
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
@@
 
-Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
+\medskip
+Figures~\ref{fem_cv_represent_a}(a) and (b) show the continuous displacement of fluid 2 due to the injection of fluid 1.
 They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions.
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type.
+This, in large scale, is a problem that can be found in petroleum production.
 
@@
 Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
-Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994} (\red{ ....
-COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})
+Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
+
+\medskip
+Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system.
+The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}.
+In both cases the flow will not follow the standar source-sink behaviour.
+The mobility ratio (or VR) is playing a crucial role for these flows but the cross-flow pattern always occurs.
+The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
+In the current case the map of permeabilities is the same but reversed sto the main cross-flow is heading downwards instead of upwards.
+
+ (\red{ .... COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})
 

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1).
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length (aspect ratio of $2$) and fully saturated with fluid 2 ({\it VR}=1).
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
+
+\medskip
+Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
 
@@
 The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type.
-This, in large scale, is a problem that can be found in petroleum production.
-
-\medskip
-Another numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
-Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
+This, in large scale, is a problem that can be found in petroleum production operations.
 
@@
 
- (\red{ .... COMMENT THE RESULTS OBTAINED AND COMPARE IT WITH EVANS WORK ...})
-
-\red{KOSTAS ... HAVE A LOOK IN FIG.~\ref{fem_cv_represent_abc} ... SATURATION PROFILES DO NOT SEEM TO MATCH ...}
-
-\medskip
-In this section three \red{(??)} different sets of simulations were explained.
-Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio.
-The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop.
-The third test-case is based in the initial and boundary condition of the second set of simulations.
-Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
-\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
-The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
-
-\medskip
-\noindent
-\red{QUICK QUESTIONS ... \\
-\noindent
-A) FOR THE FIRST TEST-CASE, WAS THE SIMULATION PERFORMED IN A SQUARED DOMAIN (FROM THE PICS, IT SEEMS TO BE RECTANGULAR)?
-\\ B) THUS ASSUMING THAT THE FIRST DOMAIN WAS RECTANGULAR, THUS IT IS THE SAME AS THE SECOND SIMULATION!
-THUS WHY THE SATURATION PROFILE IS DIFF (FOR VR=1) FROM SIMULATION 1???
-\\
-\noindent 
-C) ALSO: DO NOT USE 'WE' IN TECHNICAL TEXT ... IT DOES REALLY DOWNGRADE IT !!! }
+\medskip
+In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulationsd.
+Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was under the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
+The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
 

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 %%%%%%%%%%%%  
-\subsection{Flow Simulations in Hele-Shaw Cells at Several Viscosity Ratio Conditions}\label{section:results_homo_hete}
+\subsection{Flow Simulations in Hele-Shaw Cells at different Viscosity Ratio Conditions}\label{section:results_homo_hete}
 
@@
 
+\medskip 
 Here, 2D simulations were conducted in a 5$\times$5 cm Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
@@
 
+\medskip
 Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
@@
 
+\medskip
 In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on progress

@@
 \medskip
-In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
+In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain.
 Three different cases with different set-ups will follow.
 The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
-For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.
-
-\medskip
-As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
-\ref{fig:2c_homoheleshaw_10} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
+For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.
+
+\medskip
+As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
+%\ref{fig:2c_homoheleshaw_10} there is 
+a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
 %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
-They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figures \ref{fig:3a_heteheleshaw_10} %\ref{fig:3b_heteheleshaw_10}
--\ref{fig:3c_heteheleshaw_10}.
+They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}.
+%\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.
  Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
small corrections

@@
 The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
+
 \begin{eqnarray}
@@
 where $\mathcal{N}_{p}$ denotes the number of phases.
+
 %%%%%%%%%%%%%%%
@@
 %\end{displaymath}
+
+\medskip
 Though, whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
@@
 
+\medskip
 Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
 \citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates, and the impact of capillary number ($N_{c}$),
+
 \begin{equation}
@@
 \end{equation}
+
 on the interface pressure and pressure.
@@
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+
 \begin{eqnarray}
@@
 \medskip
-Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system.
+%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
 The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}.
-In both cases the flow will not follow the standar source-sink behaviour.
-The mobility ratio (or VR) is playing a crucial role for these flows but the cross-flow pattern always occurs.
+In both cases the flow will not follow the standar source-sink behaviour while the mobility ratio (or VR) is playing a crucial role for these flows.
 The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
-In the current case the map of permeabilities is the same but reversed sto the main cross-flow is heading downwards instead of upwards.
-
-\medskip
-In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulationsd.
-Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was under the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
+
+\medskip
+In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
+Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
 The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
small corrections

@@
 In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
-In this manuscript, he investigated the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} and the impact of boundary conditions in the problem's mathematical formulation and solutions.
+In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.
 
@@
 %Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
-They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}.
+The third case is of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}.
 %\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.
@@
 In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation.
-The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.
+The importance of this set-up is to understand how the simulation works and whether the flow pattern of the fingers follows the experimental results.
+Also how the fingers will be developed under different permeability schemes as these has already been experimentaly tested.
 

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length (aspect ratio of $2$) and fully saturated with fluid 2 ({\it VR}=1).
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1).
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-Boundary conditions also includes no-flux across upper and lower boundaries.
+Boundary conditions also include no-flux across upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-Figures~\ref{fem_cv_represent_a}(a) and (b) show the continuous displacement of fluid 2 due to the injection of fluid 1.
+Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
 They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions.
@@
 This, in large scale, is a problem that can be found in petroleum production operations.
+\red{(PLEASE REVISE THE PARAGRAPH ...
+AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
 

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-The idea was to to study the effects of heterogeneity of a quadrant model geometry using the current element type.
-This, in large scale, is a problem that can be found in petroleum production operations.
-\red{(PLEASE REVISE THE PARAGRAPH ...
-AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
 
@@
 %Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
+\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
 The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}.

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\medskip
 Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
@@
 
-\medskip
 Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-
-\medskip
+The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
+\red{(????
+THE TWO PAPERS ARE EXPERIMENTAL ...
+THIS SENTENCE DOES NOT MAKE ANY SENSE ...
+PLEASE READ IT THROUGH !!)}
+
 %Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
 \red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
-The flow profile follows the same behaviour with the experimental work of \citet{evans_1994}.
-In both cases the flow will not follow the standar source-sink behaviour while the mobility ratio (or VR) is playing a crucial role for these flows.
-The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
-
-\medskip
 In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \red{(????
-THE TWO PAPERS ARE EXPERIMENTAL ...
-THIS SENTENCE DOES NOT MAKE ANY SENSE ...
-PLEASE READ IT THROUGH !!)}
+THESE TWO PAPERS ARE EXPERIMENTAL ...
+THIS LAST SENTENCE DOES NOT MAKE ANY SENSE ...
+PLEASE READ IT THROUGH AND ADDRESS MY PREVIOUS COMMENT ...!!)}
 
 %Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system. 
-\red{(PLEASE REVISE THE PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS ....)}
+\red{(PLEASE REVISE THIS PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS WRT FIG 5 AND FIG 4 !!!! ....)}
 In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.

### 2017-06-26 Papers/ViscousInstabilities/article_figure1.tex
updates on progress
updates

@@
 Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
-Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
+Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.\red{(TRIANGLE A IS NOT CORRECT ...
+MID POINTS SHOULD BE BLUE -- QUADRATIC PRESSURE NODES!!)} }
 \label{fig:fem_elem}
@@
 \caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec.
-The domain is discretised in $5960$ \PN[1]{2} elements.
+The domain is discretised with $5960$ \PN[1]{2} elements.
 }
@@
 \caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
-\label{fem_cv_represent_a}
+\label{fem_cv_represent_vr1_vr10}
 \end{figure}
@@
 The domain contains \red{XXXX} elements.}
-\label{HeleShawHeter_VR10}
+\label{fig:HeleShawHeter_VR10}
 \end{figure}

### 2017-06-26 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $47500$ \PN[1]{2} triangular elements.}

### 2017-06-26 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip 
-Here, 2D simulations were conducted in a 5$\times$5 cm Hele-shaw cells (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top r ight-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
 

### 2017-06-26 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.8\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
+\vspace{0.cm}
+\hbox{\hspace{3.5cm} (a) t=0.66s \hspace{7.cm} (b) t=3.43s }
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{4.5cm} (e)t=10.00s}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+\begin{comment}
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}

### 2017-06-26 Papers/ViscousInstabilities/article_figure1.tex
updating times

@@
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=250   
+\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=250     
+\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
 }
 }     
-\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
+\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for $time=0.125$ sec ($t=250$, timestemp).
 There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
@@
 }     
-\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\caption{At $time=0.25sec$ ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
 \label{fig:2testcase_b}
@@
 }     
-\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\caption{At $time=0.75$ ($t=1500$, timestemp) cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
 \label{fig:2testcase_c}
@@
 }     
-\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
+\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
+The end of simulation happens at $time=5$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
 When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}

### 2017-06-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\medskip 
 Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
@@
 
-\medskip
 Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be noticed at early stages of the simulation conducted with {\it VR}=10.
+However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=10.
+
+Viscous finger morphologies \citet{guan_2003} investigated the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells.
+Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
 

### 2017-06-27 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \vspace{0.cm}
-\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{5.cm} (b) t=250\red{(???)} \hspace{2.75cm} (c) t=1000\red{(???)}}
+\hbox{\hspace{2.5cm} (a) pressure at t=0s \hspace{5.cm} (b) t=0.87s \hspace{2.75cm} (c) t=3.54s}
 \vspace{0.5cm}
@@
 \vspace{0.cm}
-\hbox{ \hspace{1.cm} (d) t=2500\red{(???)} \hspace{2.0cm} (e) t=1000\red{(???)}   \hspace{3.0cm} (f) t=XXX\red{(???)}}
+\hbox{ \hspace{1.cm} (d) t=8.86s \hspace{3.0cm} (e) t=12.41s   \hspace{4.0cm} (f) t=17.95s}
 \vspace{0.cm}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.8\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
 \vspace{0.cm}
-\hbox{\hspace{3.5cm} (a) t=0.66s \hspace{7.cm} (b) t=3.43s }
+\hbox{\hspace{3.5cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
 \vspace{0.5cm}
@@
 }     
-\caption{At $time=0.75$ ($t=1500$, timestemp) cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\caption{At $time=0.75 sec$ ($t=1500$, timestemp) cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
 \label{fig:2testcase_c}
@@
 \caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
-The end of simulation happens at $time=5$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
+The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
 When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
@@
 }     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\caption{For the case of MR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
 \label{fig:4testcase_a}
@@
 \vspace{0.0cm}
-\hbox{\hspace{3.75cm} (a) fixed and unstructured mesh for MR = 100 (t = 3000)   
+\hbox{\hspace{3.75cm} (c) fixed and unstructured mesh for MR = 100    
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = end)   
+\hbox{\hspace{7.cm} (d) end of simulations     
 }
 }     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=3000(a), t=end(b) }
+\caption{screenshot (c) is for t=$1.5$ sec or t=$3000$ and screenshot (d) is for t=$3.175$ sec, at the end of the simulations. }
 \label{fig:4testcase_b}

### 2017-06-27 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
-Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.\red{(TRIANGLE A IS NOT CORRECT ...
-MID POINTS SHOULD BE BLUE -- QUADRATIC PRESSURE NODES!!)} }
+Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
 \label{fig:fem_elem}
@@
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+      \includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
 \vspace{0.cm}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-on the interface pressure and pressure.
+\noindent on the interface pressure and pressure.
 \citet{muskat_1934} also derived the perturbation solution of this axisymmetric problem.
@@
 \subsection{Model Set-up}\label{section:results:setup}
-
 Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
@@
 
-\medskip
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
@@
 \subsection{Initial Model Validation}\label{section:results_validation}
-
-\medskip
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
@@
 
-Viscous finger morphologies \citet{guan_2003} investigated the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells.
-Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
+Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
+A sensitivity study of capillary forces and viscosity ratios were conducted to assess the impact on fingers' formation, branchiness and dimensions.
+the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
 

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-A sensitivity study of capillary forces and viscosity ratios were conducted to assess the impact on fingers' formation, branchiness and dimensions.
-the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
+A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width
+
+%and viscosity ratios 10$^{2}\le${\it VR}$\le$10$^{4}$ and 632$\leN_{C}^{'}\le$6.32$\times$10$^{7}$. 
+%the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
 

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width
+A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
+\begin{equation} 
+   \mathcal{Q} = U b \lambda_{f}.\label{eqn:guaneqn} 
+\end{equation} 
+Numerical simulation performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.\blue{XX}), respectively, which are close match to the expected from equation
 

### 2017-06-28 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
+\hspace{0.5cm}      
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
 \vspace{0.cm}
-\hbox{\hspace{3.5cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
+\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
 \vspace{0.5cm}
@@
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
-      \includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
 \vspace{0.cm}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+ \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
+\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}).
+\blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10_VN250}
+\end{figure}
 
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{2.0cm} (a) t=0\red{??} \hspace{5.cm} (b) t=500\red{(???)} \hspace{4.0cm} (c) t=2000\red{(???)}}
+      \hbox{\hspace{1.0cm} (a) map of permeabilities \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
       \vspace{0.5cm}
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
-      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{5.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
+      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
 \caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \end{equation} 
-Numerical simulation performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.\blue{XX}), respectively, which are close match to the expected from equation
-
-%and viscosity ratios 10$^{2}\le${\it VR}$\le$10$^{4}$ and 632$\leN_{C}^{'}\le$6.32$\times$10$^{7}$. 
-%the impact of fluids' interfacial tension on formation and growth of fingers in Hele-Shaw Cells. Their calculations were based on \citet{mclean_1981} semi-analytical solution that correlate
+Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively.
+This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).
 

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
+In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy).
+
 In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain.

### 2017-06-28 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
       \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
-\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
+\caption{Simulated flow in a modified Hele-Shaw cell with (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
+Saturation map is the same as used in Fig.\red{XX ...
+is it true??}.
 The domain contains \red{XXXX} elements.}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \medskip
+In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) and viscosity ratio of 10.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulation, which was conducted with the same mesh resolution, boundary and initial conditions as in the previous homogeneous cases.
+Figure~\ref{fig:HeleShawHeter_VR10} shows formation of fingers with continuous growth and coalescence of  dendritic fingers
+
 In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain.

### 2017-06-28 Papers/ViscousInstabilities/article_figure1.tex
updates

--- 2017-06-28 Papers/ViscousInstabilities/article_figure1.tex
@@
       \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
-\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
+Saturation map is the same as used in Fig.\red{XX ...
+is it true??}.
 The domain contains \red{XXXX} elements.}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Finishing Section 4.3 ... now justwaiting for the simulations finishing to extract the relavant data and pics

@@
 Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulation, which was conducted with the same mesh resolution, boundary and initial conditions as in the previous homogeneous cases.
-Figure~\ref{fig:HeleShawHeter_VR10} shows formation of fingers with continuous growth and coalescence of  dendritic fingers
-
-In figure \ref{fig:HeleShawHeter_VR10}(a), there is the description of the domain.
-Three different cases with different set-ups will follow.
-The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
-For the homogeneous case there are  two different mobility ratios of $3$ and $10$ while for the heterogeneous case only the case of  mobility ratio of $10$ will be investigated.
-
-\medskip
-As can been seen so far there is %from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
-%\ref{fig:2c_homoheleshaw_10} there is 
-a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
-%Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
-The third case is of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for a heterogeneous formation as this is described in figure \ref{fig:HeleShawHeter_VR10}.
-%\ref{fig:3b_heteheleshaw_10}-\ref{fig:3c_heteheleshaw_10}.
- Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
-In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation.
-The importance of this set-up is to understand how the simulation works and whether the flow pattern of the fingers follows the experimental results.
-Also how the fingers will be developed under different permeability schemes as these has already been experimentaly tested.
+Figure~\ref{fig:HeleShawHeter_VR10} shows formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
+Finger width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
 

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Finishing Section 4.3 ... now justwaiting for the simulations finishing to extract the relavant data and pics

@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
 Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
 \begin{equation} 
-   \mathcal{Q} = U b \lambda_{f}.\label{eqn:guaneqn} 
+   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
 \end{equation} 

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush

@@
 %% End of tex file.
-
-%%  LocalWords:  checkboard % Copyright 2007, 2008, 2009 Elsevier Ltd
-%
-% This file is part of the 'Elsarticle Bundle'.
-% ---------------------------------------------
-%
-% It may be distributed under the conditions of the LaTeX Project Public
-% License, either version 1.2 of this license or (at your option) any
-% later version.  The latest version of this license is in
-%    http://www.latex-project.org/lppl.txt
-% and version 1.2 or later is part of all distributions of LaTeX
-% version 1999/12/01 or later c.
-%
-% The list of all files belonging to the 'Elsarticle Bundle' is
-% given in the file `manifest.txt'.
-%
-
-% Template article for Elsevier's document class `elsarticle'
-% with harvard style bibliographic references
-% SP 2008/03/01
-%
-%
-%
-% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
-%
-%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
-
-% Use the option review to obtain double line spacing
-%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-% for a journal layout:
-%\documentclass[final,authoryear,1p,times]{elsarticle}
-%\documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
-%\documentclass[final,authoryear,3p,times]{elsarticle}
-%\documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
-%\documentclass[final,authoryear,5p,times]{elsarticle}
-%\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
-
-%% if you use PostScript figures in your article
-%% use the gra
-
-%%graphis package for simple commands
-%% \usepackage{graphics}
-%\usepackage{cases}
-%% or use the graphicx package for more complicated commands
-\usepackage{graphicx}
-%% or use the epsfig package if you prefer to use the old commands
-\usepackage{epsfig}
-%\usepackage{subfig}
-\usepackage{comment}
-
-\usepackage{epstopdf}
-\usepackage{pdflscape}
-\usepackage{bm}
-\usepackage{hyperref,url}
-\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb,amsmath,array}
-%The amsthm package provides extended theorem environments
-\usepackage{amsthm}
-\usepackage{graphicx}
-%\usepackage{subfigure}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-\usepackage{lscape}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon (default)
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   authoryear - selects author-year citations (default)
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%   longnamesfirst  -  makes first citation full author list
-%%
-%% \biboptions{longnamesfirst,comma}
-
-% \biboptions{}
-
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
-\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
-\newcommand{\red}{\textcolor{red}}
-\newcommand{\blue}{\textcolor{blue}}
-\newcommand{\green}{\textcolor{green}}
-\journal{Advances in Water Resources}
-\newcommand{\frc}{\displaystyle\frac}
-\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
-\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
-
-\begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{ \blue{Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
-something with viscous flow instability or viscous fingering)}}
-
-%% use optional labels to link authors explicitly to addresses:
-\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
-\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
-
-\cortext[cor1]{Corresponding author.}
-\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
-\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
-\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
-
-\begin{abstract} 
-A set of simulations is presented so as to model the viscous fingering-flow instability using a novel method for modeling multi-phase flows in porous media.
-Starting from the Hele-Shaw experimental which is mathematically analogous to the two-dimensional flow in porous medium, test-cases of both homogenous and heterogeneous computational domains, under different conditions are listed.
-The development of finger structures is explained by taking into account different maps of permeabilities, mobility ratios and surface tension.
-A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
-The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
-In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-It was found that the initial state is the decisive factor in the development of the process up to large times
-The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
-\end{abstract}
-
-\begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods.
-\end{keyword}
-
-\end{frontmatter}
-
-%\tableofcontents
-%\linenumbers
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Introduction}\label{section:intro}
-\medskip
-Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of fluid flow through porous media serves as the foundation of reservoir engineering and groundwater studies.
-%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
-%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important area of interest and, more recently due to global environmental problems several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations~\citep{spycher_2003, chen_2006, self_2012, pruess_1990c, white_1981,jiang_2011}.
-
-\medskip
-Due to complex and/or heterogeneous geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial to understand the aforementioned processes.
-Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and the flow regimes in capillary media.
-A comprehensive review of mechanisms of fingering (\ie fluid instability) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale darcy-equations.
-% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
-SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper will focus on microscopic instabilities and phenomena in two-phase systems that mainly occur due to viscous and stress forces and often referred as viscous instabilities or \textit{viscous fingering}.
-
-\medskip
-In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly governed by the ratio of mobility (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie large spatial permeability gradient) , gravitational forces, anisotropic dispersion, velocity dependence of dispersion, non-monotonic viscosity profiles, etc.
-
-\medskip 
-Conservation of mass and Darcy's law are the governing equations that describe the flow dynamics in porous media.
-Several computational methods have been developed to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications.
-However, FDM are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
-FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
-%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-
-\medskip
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In standard CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
-
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation}
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties (Fig.~\ref{fig:fem_cv}a).
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CV's were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical simulations to investigate formation and evolution of viscous fingers in heterogeneous media.
-Continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b).
-The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
-
-\medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
-Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
-The analysis considers: heterogeneity due to space-dependent permeability field, capture the development of the interface and the evolution of fingers and test-case comparisons.
-Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Formulation}\label{equations_scheme}      
-%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Different domains will produce different flow instabilities.
-In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
-DG-methods combine advantages of classical finite volume and finite element methods.
-
-%\subsection{Numerical Formulation}
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-%\begin{equation}\label{e:darcy_eq}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_bal}
-%\end{equation}
-%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-%\begin{equation}
-%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-%\end{equation}
-%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-%\begin{eqnarray}
-%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-%\label{v_and_p}
-%\end{eqnarray}
-
-%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_balance}
-%\end{equation}
-
-%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-%\end{comment}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\label{e:darcy_eq}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-%\label{E:darcy_eqn}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
-% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-%\begin{equation}
-%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:darcy_ext}
-%\end{equation}
-%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
-The two-phase flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
-\end{eqnarray}
-respectively, where, $\mu$, ${\bf K}$, $p$ and $\phi$ are the viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with constraints of
-\begin{displaymath}
-\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
-\end{displaymath}
-where $\mathcal{N}_{p}$ denotes the number of phases.
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The main equations that will be used along with the following OCVFEM techique can be summarised below.
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-%\begin{equation}
-%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-%\label{e:mass_bal}
-%\end{equation}
-
-%\begin{equation}
-%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-%\label{e:force_bal}
-%\end{equation}
-
-%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-%\begin{equation}
-%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-%\label{e:pressure_eq}
-%\end{equation}
-
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces,
-
-\begin{displaymath}
- \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
-\end{displaymath}
-
-Though, whilst saturation is calculated in CV space, permeability is piecewise constant in FE space to allow efficient representation of surface parameterised geometries (element $A$ in Fig.~\ref{fig:fem_cv}b).
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements, see Fig.\ref{fig:fem_cv}a) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
-
-\medskip
-This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
-%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
-
-%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
-%\begin{equation}
-%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
-%\label{mass_balance}
-%\end{equation}
-
-%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
-
-%\begin{equation}
-%\sum  S_{p}-1
-%\label{saturation_constrain}
-%\end{equation}
-
-\medskip
-Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation, 
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n} \cdot \; {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
-
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
-$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach, see \citet{pavlidis2016}.
-This numerical formulation is fully described in \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
-
-\medskip
-As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits (unstable interface because of viscocity differences, density differences,the existance of gravitational forces or not, and/or opposite stress tensors) may cause instabilities in the system.
-The flow of a fluid over or next to another heavier fluid, can produce flow instabilities.
-Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
-
-\medskip
-Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} initially derives a perturbation solution of an axisymmetric problem (injected fluid between two infinite parallel plates) assuming a circle shaped front of the interface while his main interest is on the interface pressure shape and pressure for different values of capillary number ($N_{c}$) as this is defined below in eq.~\ref{eq:capillarry_number} where $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $ \alpha \beta \gamma $ is the surface tension and U is a velocity characteristic of the moving interface.
-
-\begin{equation}
-N_{C} = \frac{\mu U}{T}
-\label{eq:capillary_number}
-\end{equation}
-
-For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-If \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and other agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity U.
-
-\medskip
-In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
-%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
-
-\medskip
- Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}}
-leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape.
-
-In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is demonstrated in Section \ref{section:results_homo_hete}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
-
-\begin{equation}
-\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
-\label{eq:pressure_dif} 
-\end{equation}
-
-This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure difference across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference, $\hat{n}$ is the unit normal vector out of the surface, and $\gamma$ is the surface tension.
-
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR, see Section~\ref{section:intro}) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
-
-\begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
-\label{eq:MR}
-\end{equation}
-
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
-
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to a viscosity ratio,
-\begin{displaymath}
-    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
-\end{displaymath}
- that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field that is calculated along with pressure and velocity.
-\red{(PARAGRAPH NEEDS TO BE IMPROVED)}
-
-In immiscible displacements , viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-The interface collapses and starts splitting into new lobes of fingers.
-One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
-Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
-
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete}; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet} .
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-%\begin{equation}
-%\lambda = \frac{K\;k_{\alpha}}{\mu}
-%\label{eq:mobility-of-fluid}
-%\end{equation}
-
-%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-%\begin{equation}
-%U = \frac{b^2}{12 \mu} \nabla p
-%\end{equation}
-
-%and the above equation can be re-arranged for 1D steady flow as,
-
-%\begin{equation}
-%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
-%\label{eq:pressure_dif} 
-%\end{equation}
-
-%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-%\begin{equation}
-%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-%\end{equation}
-
-%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
-
-%\begin{equation}
-%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-%\end{equation}
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%\pagebreak
-%\clearpage
-
-%\listoftables
-%\pagebreak
-%\input{Manuscript_Table}
-
-%\pagebreak
-%\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
-
-%%%%%%%%%%%% 
-\subsection{Model Set-up}\label{section:results:setup}
-
-Numerical simulations were conducted with model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
-
-\medskip
-All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
-Fluids are assumed incompressible and gravity was neglected.
-The set-up for the numerical simulations are summarised in Table \ref{table:setup}.
-
-%%%%%%%%%%%% 
-\subsection{Model Validation}\label{section:results_validation}
-
-\medskip
-The test-case shown in this section demonstrates the model capability to capture crossflow in immiscible displacement in heterogeneous porous media.
-The numerical experiment is similar to the lab set up by \citet{evans_1994} and \citet{dawe_2008}
-
-The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain.
-The aim of this test-case is to validate the different simulation/scenarios \ie cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.
-Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.
-
-\medskip
-Fluid $1$ is introduced from the left hand side of the formation.
-Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied.
-Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain.
-Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively.
-Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used).
-%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
-A domain consisting of $4$ square regions in which each quarter is represented by a permeability value %(Fig.\ref{fig:square}a) 
-and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$.
-At the upper and lower sides of the domain no-slip boundary condition is applied.
-The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$.
-The right hand side is the outlet and pressure is set to $0$.
-Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$.
-What can been seen here is a cross flow case as the flow passes through different regions and evolves.
-The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$.
-%\ref{fig:square}b).
-
-\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation.
-The velocity magnitute is built up starting from the inlet all the way to the middle of the square.
-There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further %\ref{fig:square})
-while the phase volume fraction is constant.
-
-\medskip
-A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following.
-The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}.
-The last set of simulations as this is described in fig.\ref{fem_cv_represent_a}c is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
-
-\medskip
-In this section three different sets of simulations were explained.
-Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio.
-The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop.
-The third test-case is based in the initial and boundary condition of the second set of simulations.
-Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:6a}-%\ref{fig:6b},
-\ref{fig:6c}) and how the cross-flow as well as the simulation will progress on time.
-The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
-
-%%%%%%%%%%%%  
-\subsection{Hele-Shaw validation cases for homogeneous and heterogeneous domains under two different mobility ratios}\label{section:results_homo_hete}
-
-\medskip
-Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}-%,\ref{fig:1b_homoheleshaw_3}
-\ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations.
-In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
-. The sink (pressure set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
-was imposed to all borders of the domain except at the top righ hand side corner.
-The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
-
-\medskip
-In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain.
-Three different cases with different set-ups will follow.
-The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$.
-For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogenous case using a mobility ratio of $10$.
-
-\medskip
-As can been seen from the fig.\ref{fig:1a_homoheleshaw_3}-%\ref{fig:1c_homoheleshaw_3}
-\ref{fig:2c_homoheleshaw_10} there is a significant difference on the flow pattern when the mobility ratio is $3$ and when it is $10$ under the same number of elements.
-%Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3}, \ref{fig:1c_homoheleshaw_3}
-They also provide the reader with a description of the Hele-Shaw cell simulation when $MR=10$ followed by the same initial and boundary conditions set-up, but now for the Hele-Shaw case of a heterogeneous formation as this is described in figures \ref{fig:3a_heteheleshaw_10} %\ref{fig:3b_heteheleshaw_10}
--\ref{fig:3c_heteheleshaw_10}.
-Fingers will be more profound and will start develop faster when the $MR=10$ compared to the uniform front that is developing when the $MR=3$ for the same time steps.
-In addition the flow patter of the fingers will be sharper and more intense when different regions with different permeabilities are introduced in the formation.
-The importance of this set-up is to understand how the simulation works and if the result that will produced reagarding the development and pattern of the fingers, actually follow the experimental results  and how this is developed under different permeability schemes as these has already been experimentaly tested.
-
-%%%%%%%%%%%%%
-\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}
-
-\medskip
-Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
-A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.
-What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude.
-%(fig.\ref{fig:1testcase})
-The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
-For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$.
-%Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
-Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
--\ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
-In this set the interfacial instability is becoming more profound as the flow develops.
-Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
-Fingers will develop faster in areas where permeabilities are higher.
-This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
-
-\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{section:results_dinlet}
-
-\medskip
-Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
-This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
-The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2})
-as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$,
-%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
-it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
-Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
-A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
-No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).
-The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers will are shown in fig.\ref{fig:4testcase_a}.
-
-\medskip
-The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. 
-%The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. 
-Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
-The domain is fully saturated with fluid $2$.
-At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
-Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
-The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
-Saturation is located at the pressure nodes.
-Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
-The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
-
-\medskip
-Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.
-
-\medskip
-This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
-Viscocity is a measure of resistance, therefore a frictional property.
-In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
-For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
-Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
-Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
-In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
-In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
-This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
-The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
-
-\medskip
-The macroscopic sweep efficiency is principally affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
-The permeability depends on the number, size and connectivity of the pores.
-This set of parameters is described by the $\sigma$ in the global mass balance equation (eq.\ref{global_mass_balance}).
-Including higher permeability zones also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
-
-\medskip 
-As can been seen so far in all the test-case illustrated, main differences can be found on the way the shape of fingering is developed.
-Adaptive meshes tend to display fingering easier because of the enhcanced and stronger resolution in the interface.
-Inside the high permeability square region there is an acceleration of the flow with the maximum value of it at the interface as this starts to develops at the back of this region and onwards.
-%At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
-The breaking point, also known as the point the two curves meet where beyond that water production will occur, is shifted towards the right as MR is increased.
-
-\section{Conclusions}\label{Section:Conclusion}
-
-\medskip
-A number of different cases have been illustrated in Section \ref{section:results}.
-Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
-Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows.
-For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
-In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR).
-If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
-On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
-Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
-Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
-
-%\medskip
-%We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
-Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
-In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
-
-\medskip
-As usually seen for high viscosity contrast, the leading finger screens out the trailing by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
-At long times the large finger advances approximately at
-constant velocity. Results which question the evolution of fingers and the finger competition are those referring to the dynamic role of viscosity contrast.
-
-\medskip
-In summary, the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
-\begin{enumerate}
-\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
-%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
-
-\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domain.
-The higher the mobility ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
-\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
-At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
-The domain used in these test-cases the development of the flow follow the linear tip-splitting finger behaviour.
-\item[4.] Properties such as porosity and saturation can be readily up-scaled using statistical methods, can be included in the element boundaries,  while production simulations run directly on the geological model without the need to upscale.
-\end{enumerate}
-
-%\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
-Keeping both the thickness and the injection rate constant, it was observed that increasing the mobility ratio decreases the finger width, which subsequently leads to more fingers and subsequently more complexity at a given distance away from the injection point.
-Tip-splitting, a phenomenon in which the initial stage of fingers split into two or more new fingers, can also be observed at higher mobility ratios.}
-
-\section{Acknowledgements}
-Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
-Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
-
-\clearpage
-
-%% References with bibTeX database:
-\bibliographystyle{elsarticle-harv} 
-\bibliography{references}
-\clearpage
-
-\listoftables
-\clearpage
-
-\input{article_table}
-\clearpage
-
-\listoffigures
-\clearpage
-
-\input{article_figure1}
-%\input{article_figure2}
-
-\end{document}
-%% End of tex file.
-
-%%  LocalWords:  checkboard

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
do not rush

@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
 \hspace{0.5cm}      
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
 \vspace{0.cm}

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
Updates in Figs

@@
 \caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b}
+\hspace{0.5cm}      
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b}}
+\vspace{0.cm}
+\hbox{\hspace{5.cm} (a) t=0.27s \hspace{8.cm} (b) t=0.94s }
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{4.5cm} (e)t=2.31s}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=150): snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Figs

@@
 \end{equation} 
-Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively.
+Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
 This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
Updates in Figs

@@
  \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
-\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}).
-\blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
-\label{fig:homoheleshaw_VN10_VN250}
+       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
+\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s).
+Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.
+Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10_VN150}
 \end{figure}

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Figs

@@
 \end{equation} 
-Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
-This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).
+Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on the tip velocity).
 

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

--- 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 The behaviour of the fluid under conditions caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits can cause flow instabilities.
-For example, the flow of a fluid over or next to a heavier fluid can produce flow instabilities.
-Thus, when a fluid is injected into a porous domain saturated with a second and more viscous fluid, viscous fingering may occur as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.
+For example, during water flooding displacement, efficiency is related with capillary number.
+The higher the capillary number the higher the recovery.
+The driving force induced by the injected fluid should overcome the capillary force thus leading to a hydrodynamic instability that will cause the collapse of the uniform interface between fluids and start forming finger.
+Fingering problems can become more intense from the heterogeity (i.e.
+natural fractures) of the porous medium so sweep efficiency may reduce further or early breakthrough may result.
+During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature.
+The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil.
+The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result in $CO_{2}$.
+The outcome of the above operations is the that when a fluid is injected into a porous domain saturated with a second and more viscous fluid, viscous fingering may occur.
 
 \medskip
-Viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
+As mentioned above viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
 \citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates, and the impact of capillary number ($N_{c}$),
@@
 
-This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids.
+\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids.
 With $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
@@
 
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
@@
 
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
 $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
@@
 \medskip
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+\noindent From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
 Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio,
@@
 
+\medskip
 Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
-
 Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-The main difference between these two works is that by introducing an unstructured mesh the flow patterns are not only verified but also there is a more accurate descriptions during the development of the flow.
-\red{(????
-THESE TWO PAPERS ARE EXPERIMENTAL ...
-THIS LAST SENTENCE DOES NOT MAKE ANY SENSE ...
-PLEASE READ IT THROUGH AND ADDRESS MY PREVIOUS COMMENT ...!!)}
+The main difference between the current works and the afformentioned is that by introducing an unstructured mesh the flow patterns are not only verified in greater detail but also there is a more accurate descriptions during the development of the flow.
 

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

--- 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
@@
 %%%%
+\begin{landscape}
 \begin{figure}[ht] 
- \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
+ \hbox{\includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
+       \includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
 \caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}).
@@
 \end{figure}
+\end{landscape}
 

### 2017-06-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

@@
 \end{equation} 
-Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.~\ref{fig:homoheleshaw_VN10_VN250}), respectively.
-This is a close match with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.125 to 0.750 (depending on the tip velocity).
+Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on the tip velocity).
 

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex

--- 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
@@
 %%%%
+\begin{landscape}
 \begin{figure}[ht] 
+\hbox{\includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
+       \includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
+\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}).
+\blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10_VN250}
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
@@
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
-Saturation map is the same as used in Fig.\red{XX ...
-is it true??}.
-The domain contains \red{XXXX} elements.}
+The domain contains elements.}
 \label{fig:HeleShawHeter_VR10}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100_1.pdf}
 }
@@
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
+  \includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start_1.pdf}
 }
@@
 }     
-\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
+\caption{Comparing test-cases of fixed and adaptive mesh while a second region/inlet is introduced.
+For $t=0.101$s, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps.
+For this simulation there are $13226$ elements for the fixed messh and $43716$ for the adaptive.}
 \label{fig:3testcase_a}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_500_1.pdf}
 }
@@
 }     
-\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{For $t=5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
 \label{fig:3testcase_b}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_1500.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_1500_1.pdf}
 }
@@
 }     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{For $t=7.5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
 \label{fig:3testcase_c}
@@
 }     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.}
 \label{fig:3testcase_d}

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
 }     
-\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations.
-Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
+\caption{Figure (a) describes the initial and boundary conditions as these are applied in this set of simulations.
+Below (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh.
+During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids.
+}
 \label{fig:testcase_heter_domain}
@@
 }     
-\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for $time=0.125$ sec ($t=250$, timestemp).
+\caption{For $t=0.125$s, $2$ test-cases under the MR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared.
 There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500_1.pdf}
 }
@@
 }     
-\caption{At $time=0.25sec$ ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\caption{At $t=0.25$s ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound as can been seen at the bottom.}
 \label{fig:2testcase_b}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500_1.pdf}
 }
@@
 }     
-\caption{At $time=0.75 sec$ ($t=1500$, timestemp) cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\caption{At $t=0.75 sec$ ($t=1500$, timestemp) the initial cross flow is now fully developed and has travel all the way towards the outlet (right-hand side).
+and the finger below start forming a front that is also travelling towards the left-hand side.}
 \label{fig:2testcase_c}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
 }

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
 }

### 2017-06-30 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates in Section 4.3

@@
 Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on the tip velocity).
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity).
 
 \medskip
-In order to investigate the impact of medium heterogeneity on formation and growth of viscous fingers, a numerical simulation was conducted using a distribution of permeability ({\bf K}) and viscosity ratio of 10.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulation, which was conducted with the same mesh resolution, boundary and initial conditions as in the previous homogeneous cases.
-Figure~\ref{fig:HeleShawHeter_VR10} shows formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
+In order to investigate the impact of porous media heterogeneity on formation and growth of viscous fingers, numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) were used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+Figures~\ref{fig:HeleShawHeter_VR10} and \red{XXX(to be added)} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
 Finger width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.

### 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
Updates in Section 4.3

@@
 \begin{figure}[ht] 
-\hbox{\includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
-       \includegraphics[width=.75\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
-\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}).
-\blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
-\label{fig:homoheleshaw_VN10_VN250}
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
@@
 Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.
-Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.}
+Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.\red{(More pics to be added!!)}}
 \label{fig:homoheleshaw_VN10_VN150}
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{1.0cm} (a) map of permeabilities \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
+      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
       \vspace{0.5cm}
@@
       \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
-\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) distribution of permeability ({\bf K}) field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
 The domain contains elements.}
@@
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start_1.pdf}
+  \includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
 }

### 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

--- 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
@@
 }     
-\caption{For $t=7.5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{For $t=7.5$s this is a comparison between fixed mesh(a) and adaptive mesh(b).}
 \label{fig:3testcase_c}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/5reg_dinlet_adapt_end.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_end_1.pdf}
 }
@@
 }     
-\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.}
+\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.
+For the fixed mesh at this point the maximum number of point is $13226$ while for the adaptive mesh is $7582$ and most of them are located where is needed in the domain.}
 \label{fig:3testcase_d}

### 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
Updates in Section 4.3

--- 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
@@
 \caption{This is a graphical representation of two different element types.
-Element A is the \PN[1]{2}, while element B is the \PN[1]{1}.
-Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
-Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
+Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.\red{(AS MENTIONED IN PREVIOUS VERSIONS ...
+THIS IS STILL NOT RIGHT ...
+IN TRIANG A, MID-LINE CIRCLES ARE BLUE AS THEY ARE PRESSURE NODES!!)}
 \label{fig:fem_elem}

### 2017-06-30 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas
Updates in Section 4.3

@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-The main difference between the current works and the afformentioned is that by introducing an unstructured mesh the flow patterns are not only verified in greater detail but also there is a more accurate descriptions during the development of the flow.
+\red{The main difference between the current works and the afformentioned is that by introducing an unstructured mesh the flow patterns are not only verified in greater detail but also there is a more accurate descriptions during the development of the flow.}
 

### 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
Updates in Section 4.3

@@
 THIS IS STILL NOT RIGHT ...
-IN TRIANG A, MID-LINE CIRCLES ARE BLUE AS THEY ARE PRESSURE NODES!!)}
+IN TRIANG A, MID-LINE CIRCLES ARE BLUE AS THEY ARE PRESSURE NODES!!)}}
 \label{fig:fem_elem}
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=250  
+\hbox{\hspace{4.5cm} (b) flow at t=250 \red{(XXX)} 
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.0cm} (c) flow at t=3000  
+\hbox{\hspace{4.0cm} (c) flow at t=3000  \red{(XXX)} 
 }
 }     
-\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec.
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{$t=XXX$} and \red{$t=XXX$} sec.
 The domain is discretised with $5960$ \PN[1]{2} elements.
@@
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
-The domain contains elements.}
+The domain contains \red{XX} \PN[1]{2} element-pairs.}
 \label{fig:HeleShawHeter_VR10}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

@@
 
-\title{ \blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios - change the title to something close to the main topic of the manuscript ...
-something with viscous flow instability or viscous fingering...}}
+\title{ \blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}}
 
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods.
+ Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods \sep Capillary number.
 \end{keyword}
@@
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work have focused on CO$_{\text{2}}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work has been focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
 
 \medskip
-Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
+%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
 Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
@@
 On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces and is often referred as viscous instabilities or viscous fingering.
+This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
 
@@
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these two fluids moves along the geological formation, creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+As water and oil interacts, the interface between these two fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
@@
 \end{eqnarray}
-respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
+
+\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
@@
 \medskip
-Though, whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
@@
 
-Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
+\noindent Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
 \begin{eqnarray}
@@
 \medskip
-The behaviour of the fluid under conditions caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits can cause flow instabilities.
+Flow instabilities may be caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits and heterogeneities of the domain.
 For example, during water flooding displacement, efficiency is related with capillary number.
-The higher the capillary number the higher the recovery.
-The driving force induced by the injected fluid should overcome the capillary force thus leading to a hydrodynamic instability that will cause the collapse of the uniform interface between fluids and start forming finger.
-Fingering problems can become more intense from the heterogeity (i.e.
-natural fractures) of the porous medium so sweep efficiency may reduce further or early breakthrough may result.
+The higher the capillary number the higher the recovery of hydrocarbons.
+When the driving force of the injected fluid overcomes the capillary force, a hydrodynamic instability will occur that will cause the collapse of the interface between fluids and start forming fingers.
+
+\medskip
+Fingering problems can become more intense from the heterogeneities (i.e.
+natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}.
 During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature.
 The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil.
-The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result in $CO_{2}$.
-The outcome of the above operations is the that when a fluid is injected into a porous domain saturated with a second and more viscous fluid, viscous fingering may occur.
+The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result.
+The outcome of the above operations \textit{viscous fingering}.
 
@@
 As mentioned above viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates, and the impact of capillary number ($N_{c}$),
+\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates and the impact of capillary number ($N_{c}$),
 
@@
 
-\noindent on the interface pressure and pressure.
-\citet{muskat_1934} also derived the perturbation solution of this axisymmetric problem.
-In Eqn.~\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
+\noindent In Eqn.
+\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
 
@@
 During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}}
-leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'.
+leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
@@
 \medskip
-As demonstrated by \citet{habermann_1960}, mobility ratio (MR) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

@@
 \medskip
-As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) (also known as \textit{viscocity ratio} (VR), is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 
-\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+\noindent VR  is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-\red{The main difference between the current works and the afformentioned is that by introducing an unstructured mesh the flow patterns are not only verified in greater detail but also there is a more accurate descriptions during the development of the flow.}
 
-%Permeability values have been prescribed in the formation following a simple quadrant heterogenous model that will give the cross-flow that is expected in such a system.   
-\red{(PLEASE REVISE THIS PARAGRAPH ... AND YOU HAVEN'T ADDRESSED MY PREVIOUS COMMENTS WRT FIG 5 AND FIG 4 !!!! ....)}
-In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
-Following a different set-up the idea is to validate the existance of cross flow and along with another region of different permeability.There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
-The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
+\red{In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
+There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
+The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.}
 
@@
 as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when MR=$100$,
+At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when VR=$100$,
 %this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
@@
 For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
-In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR).
+In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR or VR).
 If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=250 \red{(XXX)} 
+\hbox{\hspace{4.5cm} (b) flow at t=250 
 }
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{4.0cm} (c) flow at t=3000  \red{(XXX)} 
+\hbox{\hspace{4.0cm} (c) flow at t=3000   
 }
 }     
-\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at \red{$t=XXX$} and \red{$t=XXX$} sec.
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec.
 The domain is discretised with $5960$ \PN[1]{2} elements.

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-Flow instabilities may be caused from pressure differences along the interface of two fluids, stresses acting in different directions, mobility differences that may exceed critical limits and heterogeneities of the domain.
-For example, during water flooding displacement, efficiency is related with capillary number.
-The higher the capillary number the higher the recovery of hydrocarbons.
-When the driving force of the injected fluid overcomes the capillary force, a hydrodynamic instability will occur that will cause the collapse of the interface between fluids and start forming fingers.
+Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain.
+\red{For example, during water flooding, efficiency is related with capillary number.
+The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES !
+HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ...
+of the domain' ...
+AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}.
+When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
 
 \medskip
-Fingering problems can become more intense from the heterogeneities (i.e.
-natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}.
+Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}.
 During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature.

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
 Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.\red{(AS MENTIONED IN PREVIOUS VERSIONS ...
-THIS IS STILL NOT RIGHT ...
-IN TRIANG A, MID-LINE CIRCLES ARE BLUE AS THEY ARE PRESSURE NODES!!)}}
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \hbox{\hspace{4.0cm} (c) flow at t=3000   
-}
-}     
+}}     
 \caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec.
@@
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
+  \includegraphics[width=.67\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
 }

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore, sweep efficiency may reduce further or early breakthrough may result \citep{riaz_2004, tavassoli_2015}.
-During immiscible $CO_{2}$ flooding, $CO_{2}$ turns into supercritical phase under under high pressure and temperature.
-The density of supercritical $CO_{2}$ is usually lower than the \textit{in-situ} hydrocarbons therefore it may override oil.
-The viscocity of supercritical $CO_{2}$ is much smaller than that of the oil thus viscous fingering and/or channeling may result.
-The outcome of the above operations \textit{viscous fingering}.
+Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, \red{therefore it may override oil (?)}.
+Viscosity of supercritical CO$_{2}$ is also significantly smaller than that of the oil thus viscous fingering and/or channelling may occur.
+The outcome of the above operations \textit{viscous fingering} \red{(Merge these 2 sentences ...
+remember sentences often need to be long than a single line and shorter than 3-4 lines!!)}.
 

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
             \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
             \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
       \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4678$ elements.}
 \label{fem_cv_represent_vr1_vr10}

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

--- 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-\red{In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
+\red{ NEEDS TO BE MOVED LATER In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
 There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
@@
 
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
+\medskip
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid (\textit{in-situ} hydrocarbons).
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
       \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4678$ elements.}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
+The domain contains $4678$ elements.(\blue{this is a different set of simulation, we might have to change it and bring between the  })}
 \label{fem_cv_represent_vr1_vr10}
@@
 }     
-\caption{For $t=0.125$s, $2$ test-cases under the MR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared.
+\caption{For $t=0.125$s, $2$ test-cases under the VR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared.
 There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
@@
 }     
-\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
+\caption{Using the $P_{1}DGP_{2}$ element type for VR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
 The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
@@
 }     
-\caption{For the case of MR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
+\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
 \label{fig:4testcase_a}

### 2017-07-03 Papers/ViscousInstabilities/article_figure2.tex
do not rush Kostas

@@
 \caption{This is a graphical representation of two different element types.
-Element A is the \PN[1]{2}, while element B is the \PN[1]{1}.
-Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space.
-Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
+Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
 }
@@
 \hbox{\hspace{1.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
+\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
 }
@@
 \hbox{\hspace{4.0cm} (c) flow at t=3000   
-}
-}     
-\caption{Model validation of fluid displacement in heterogeneous porous media: (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at $t=250$ and $t=3000$ sec.
-The domain is discretised in $5960$ \PN[1]{2} elements.
+}}     
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec.
+The domain is discretised with $5960$ \PN[1]{2} elements.
 }
@@
 \clearpage
-
-\begin{comment}
-%%%
-%%% FIGURE
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-    \vbox{ 
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} }
-      \vspace{0.cm}
-      \hbox{\includegraphics[width=.55\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_1.pdf}
-            \includegraphics[width=.55\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}}}
-\caption{\red{THIS IS JUST FOR OUR OWN COMPARISON ... IT DOESN'T SEEM TO MATCH ... }}
-\label{fem_cv_represent_abc}
-\end{figure}
-\end{landscape}
-\clearpage
-%%%
-%%%
-%%%
-\end{comment}
 
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
             \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
       \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10. The domain contains $4700$ elements.}
-\label{fem_cv_represent_a}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
+The domain contains $4678$ elements.(\blue{this is a different set of simulation, we might have to change it and bring between the  })}
+\label{fem_cv_represent_vr1_vr10}
 \end{figure}
@@
 %%%
-
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 100 (start)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 100 (start)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the beggining of the simulation.}
-\label{fig:6a}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 1500 (middle)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 1500 (middle)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the middle of the simulation.}
-\label{fig:6b}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) MR1 at t = 3000 (end)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) MR10 at t = 3000 (end)  
-}
-}     
-\caption{Comparing the the MR1 and MR10 cases using fixed mesh in the end of the simulation.}
-\label{fig:6c}
-\end{figure}
-\clearpage
-\end{comment}
 
@@
 \vspace{0.cm}
-\hbox{ \hspace{1.cm} (d) t=2500\red{(???)} \hspace{2.0cm} (e) t=1000\red{(???)}   \hspace{3.0cm} (f) t=XXX\red{(???)}}
+\hbox{ \hspace{1.cm} (d) t=8.86s \hspace{3.0cm} (e) t=12.41s   \hspace{4.0cm} (f) t=17.95s}
 \vspace{0.cm}
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $47500$ \PN[1]{2} triangular elements.}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
+\hspace{0.5cm}      
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{4.5cm} (e)t=10.00s}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b}
+\hspace{0.5cm}      
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b}}
+\vspace{0.cm}
+\hbox{\hspace{5.cm} (a) t=0.27s \hspace{8.cm} (b) t=0.94s }
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
+\vspace{0.cm}
+\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{4.5cm} (e)t=2.31s}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=150): snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
+       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
+\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s).
+Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.
+Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.\red{(More pics to be added!!)}}
+\label{fig:homoheleshaw_VN10_VN150}
+\end{figure}
+\end{landscape}
+
+\begin{comment}
 
@@
 \clearpage
-
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-More screenshot follow that describe the progression of the flow in figure \ref{fig:1b_homoheleshaw_3} and figure \ref{fig:1c_homoheleshaw_3}.}
-\label{fig:1a_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=2500  
-}
-}     
-\caption{Following figure \ref{fig:1a_homoheleshaw_3} as the flow progress, t=1000(a), a tip start to appears, at t=2500(b).}
-\label{fig:1b_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=3500   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end  
-}
-}     
-\caption{This tip will become sharper at t=3500(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:1c_homoheleshaw_3}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250  
-}
-}     
-\caption{This is a description of a Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=250(b).
-Screenshot will follow that describe the progression of the flow in figure \ref{fig:2b_homoheleshaw_10} and figure \ref{fig:2c_homoheleshaw_10}.}
-\label{fig:2a_homoheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=1000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_4000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=4000  
-}
-}     
-\caption{As the flow progress at t=1000(a) the front still remains uniform. The first break down of the front is happening at t=4000(b) where $3$ tips start to come out of the main flow.}
-\label{fig:2b_homoheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht]
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=end   
-}
-}     
-\caption{Fingers are now more obvious as the flow progress and the tip-splitting mechanism becomes stronger at t=6000(a) as it approaches the area where sink term exist and finally at t=end(b) it will be absorbed.}
-\label{fig:2c_homoheleshaw_10}
-\end{figure}
-\clearpage
 \end{comment}
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{2.0cm} (a) t=0\red{??} \hspace{5.cm} (b) t=500\red{(???)} \hspace{4.0cm} (c) t=2000\red{(???)}}
+      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
       \vspace{0.5cm}
@@
             \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
-      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{5.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
-\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$.
-The domain contains \red{XXXX} elements.}
-\label{HeleShawHeter_VR10}
+      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
+The domain contains \red{XX} \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR10}
 \end{figure}
@@
 \clearpage
-
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.5cm} (a) Hell-Shaw cell domain   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=250     
-}
-}     
-\caption{This is a description of a heterogeneous Hele-Shaw experimental domain, when MR=$10$ showing the source and sink term as this is implied in this test-case followed by a screenshot of the flow at time, t=500(b).
-Screenshot will follow that describe the progression of the flow in figure \ref{fig:3b_heteheleshaw_10} and figure \ref{fig:3c_heteheleshaw_10}.}
-\label{fig:3a_heteheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=2000   
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) flow at t=3000     
-}
-}     
-\caption{As the flow progress at t=2000(a) but now the front is completely unstable as it has already collapsed forming many finger formations.
-Finger formations are more aggressive as the simulations progress, t=3000(b) where many tips have already start to develop out of the main flow.}
-\label{fig:3b_heteheleshaw_10}
-\end{figure}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) flow at t=6000    
-}
-\vspace{0.25cm}
-\hbox{\hspace{2.5cm}
-\includegraphics[width=.6\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.75cm} (b) flow at t=24000     
-}
-}     
-\caption{At t=6000(a), one main finger have already reached the area where sink exists as they have develop much faster than the rest of the fingers.
-At t=24000(b) there are two main fingers that now have developed and drive the flow forwards.}
-\label{fig:3c_heteheleshaw_10}
-\end{figure}
-\clearpage
-\end{comment}
 
@@
 \clearpage
+
+%%%
+%%% FIGURE
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+    \vbox{ 
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
+            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
+      \hbox{\hspace{8.0cm} (a) VR = 1}
+      \vspace{1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
+            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
+      \hbox{\hspace{8.0cm} (b) VR = 10  }}
+\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
+The domain contains $4678$ elements.(\blue{ Jeff this is a different set of simulation, I have moved it just after the \textit{map of permeabilities} above as a first comparison between $VR1$ and $VR10$})}
+\label{fem_cv_represent_vr1_vr10}
+\end{figure}
+\end{landscape}
+\clearpage
+%%%
+%%%
+%%%
 
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
+\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=250   
+\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
+\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=250     
+\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
 }
 }     
-\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for t=250.
+\caption{For $t=0.125$s, $2$ test-cases under the VR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared.
 There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
@@
 }     
-\caption{Cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
+\caption{At $t=0.25$s ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound as can been seen at the bottom.}
 \label{fig:2testcase_b}
@@
 }     
-\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
+\caption{At $t=0.75 sec$ ($t=1500$, timestemp) the initial cross flow is now fully developed and has travel all the way towards the outlet (right-hand side).
+and the finger below start forming a front that is also travelling towards the left-hand side.}
 \label{fig:2testcase_c}
@@
 }     
-\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh.
+\caption{Using the $P_{1}DGP_{2}$ element type for VR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
+The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
 When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
@@
 \hbox{\hspace{3.5cm}
-  \includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start}
+  \includegraphics[width=.67\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
 }
@@
 }     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{For $t=7.5$s this is a comparison between fixed mesh(a) and adaptive mesh(b).}
 \label{fig:3testcase_c}
@@
 }     
-\caption{for t=$1500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
+\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.
+For the fixed mesh at this point the maximum number of point is $13226$ while for the adaptive mesh is $7582$ and most of them are located where is needed in the domain.}
 \label{fig:3testcase_d}
@@
 }     
-\caption{for the case of MR=$100$ from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d) }
+\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
 \label{fig:4testcase_a}

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

@@
 \clearpage
-
-%%%
-%%% FIGURE
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-    \vbox{ 
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
-            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (a) VR = 1}
-      \vspace{1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
-            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
-The domain contains $4678$ elements.(\blue{this is a different set of simulation, we might have to change it and bring between the  })}
-\label{fem_cv_represent_vr1_vr10}
-\end{figure}
-\end{landscape}
-\clearpage
-%%%
-%%%
-%%%
 
@@
 \hbox{\hspace{4.0cm}
-\includegraphics[width=.8\textwidth]{./Pics/map_of_boundaries.pdf} 
+\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
 }
@@
 \hbox{\hspace{4.0cm}
-\includegraphics[width=.8\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
+\includegraphics[width=.9\textwidth]{./Pics/map_of_boundaries_1.pdf}
 }

### 2017-07-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush Kostas

@@
 
+\medskip
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.

### 2017-07-03 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \clearpage
-\end{comment}
 
@@
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
-The domain contains \red{XX} \PN[1]{2} element-pairs.}
+The domain contains 26313 \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR10}
+\end{figure}
+\end{landscape}
+\clearpage
+\end{comment}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1}
+            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb} 
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb} }
+      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.19s \hspace{4.0cm} (c) t=0.63s}
+      \vspace{0.5cm}
+      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb.pdf}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb.pdf}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb.pdf} }
+      \hbox{\hspace{2.5cm} (d) t=3.41ss \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation.
+The domain contains 26313 \PN[1]{2} element-pairs.}
 \label{fig:HeleShawHeter_VR10}

### 2017-07-04 Papers/ViscousInstabilities/article_figure1.tex
updating mesh and perm mapping pic for 3D channel flow ... updating pics of HS cell w VR=150 heter

@@
       \vspace{0.5cm}
-      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb.pdf}
-            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb.pdf}
-            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb.pdf} }
-      \hbox{\hspace{2.5cm} (d) t=3.41ss \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
+      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb} }
+      \hbox{\hspace{2.5cm} (d) t=3.41s \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation.
@@
 \label{fig:HeleShawHeter_VR10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D500Hb}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb} }
+      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{4.cm} (b) t=0.24ss \hspace{4.0cm} (c) t=0.37s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D1500Hb}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D5000Hb}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D8000Hb} }
+      \hbox{\hspace{2.5cm} (d) t=0.59s \hspace{4.cm} (e) t= 1.61s\hspace{3.0cm} (f) t=2.50s }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=150: snapshots of saturation profile during 2.50 seconds of simulation.
+Permeability distribution used in this simulation was the same as shown in Fig.~\ref{fig:HeleShawHeter_VR10}a.
+The domain contains 26313 \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR150}
 \end{figure}

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
updating mesh and perm mapping pic for 3D channel flow ... updating pics of HS cell w VR=150 heter

@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top r ight-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
 
@@
 \subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}    
-
 \medskip

### 2017-07-04 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $47500$ \PN[1]{2} triangular elements.}
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=150): snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=150, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
@@
 \clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
-       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
-\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s).
-Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.
-Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.\red{(More pics to be added!!)}}
-\label{fig:homoheleshaw_VN10_VN150}
-\end{figure}
-\end{landscape}
 
@@
 \end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\vbox{
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b}}
+\hbox{\hspace{0.5cm} (a) {\it VR}=10 (homogeneous) \hspace{2.cm} (b) {\it VR}=150 (homogeneous) }
+\vspace{0.5cm}
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b}}
+\hbox{\hspace{0.5cm} (c) {\it VR}=10 (heterogeneous) \hspace{2.cm} (d) {\it VR}=150 (heterogeneous) }
+}
+\caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
+Top and bottom rows describe simulations performed with constant $\left(\text{\ie homogeneous with {\bf K}= 10}^{-10}\text{cm}^{2}\right)$ and randomly distributed (\ie heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Width of largest fingers for homogeneous cases are approximately 0.70 and 0.90cm ({\it VR}=10 and {\it VR}=150, respectively), whereas for heterogeneous cases are 0.56 and 0.40cm.
+Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}
+\label{fig:homoheleshaw_VN10_VN150}
+\end{figure}
+
 \clearpage

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively.
+Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
 At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.

### 2017-07-04 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $47500$ \PN[1]{2} triangular elements.}
+The domain contains $26313$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN3}
@@
 The domain contains $26313$ \PN[1]{2} triangular elements.}
-\label{fig:homoheleshaw_VN10}
+\label{fig:homoheleshaw_VN150}
 \end{figure}
@@
 \clearpage
-
-\begin{comment}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
-\vspace{0.cm}
-\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
-\vspace{0.5cm}
-\hbox{
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
-\vspace{0.cm}
-\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
-\vspace{0.cm}
-}   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $47000$ \PN[1]{2} triangular elements.
-The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
-\label{fig:homoheleshaw_VN10}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%
-%%% FIGURE XXXXXX
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-  \vbox{\vspace{-1cm}
-      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
-      \vspace{0.5cm}
-      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
-      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
-\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
-The domain contains 26313 \PN[1]{2} element-pairs.}
-\label{fig:HeleShawHeter_VR10}
-\end{figure}
-\end{landscape}
-\clearpage
-\end{comment}
 
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability} }
+      \hbox{\hspace{1.0cm} (a) permeability map }}
+\caption{3D channel flow \red{FIGS AND COMMENTS TO BE ADDED AS SOON AS THE SIMULATION FINISHES}. The domain contains 243056 \PN[1]{1} element-pairs.}
+\label{fig:3DChannel_PermMesh}
+\end{figure}
+\clearpage

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \end{equation}  
-Numerical simulations performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150}), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity).
+Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
 

### 2017-07-04 Papers/ViscousInstabilities/article_table.tex
updates

@@
+%%%
+%%%   TABLE 1
+%%%
 \begin{landscape}
@@
 \clearpage
+
+%%%
+%%%   TABLE 2
+%%%
+\begin{table}
+  \begin{tabular}{c | c c c c}
+    \hline\hline
+                                  & {\bf K}                                  & {\it VR}  & $\lambda_{f}^{\text{(calc)}}$ (cm) & $\lambda_{f}^{\text{(simul)}}$ (cm) \\
+                                  & $\left(\text{cm}^{2}\right)$              &           &  (Eqn.~\ref{eqn:guaneqn})  &                    \\
+    \hline\hline
+    {\bf Case 1} (homogeneous)    &  1$\times$10$^{-10}$                      &    10      &  0.13-0.75                 &   0.45-0.70       \\
+    {\bf Case 2} (homogeneous)    &  1$\times$10$^{-10}$                      &    150     &  0.30-0.75                 &   0.50-0.90       \\
+    {\bf Case 3} (heterogeneous)  &  1$\times$10$^{-12}$-5$\times$10$^{-10}$   &    10      &  0.25-4.50                 &   0.44-0.56       \\
+    {\bf Case 4} (heterogeneous)  &  1$\times$10$^{-12}$-5$\times$10$^{-10}$   &    150     &  0.88-3.00                 &   0.24-0.40       
+  \end{tabular}
+   \caption{Flow simulations in Heleshaw cells (Section~\ref{section:results_homo_hete}): summary of finger width calculations using Eqn.~\ref{eqn:guaneqn} and obtained through numerical simualtions.
+$\lambda_{f}^{\text{calc}}$ was calculated based on fingers' tip velocities and outflow rate.
+Calculations were based on simulation data obtained from snapshots shown in Fig.~\ref{fig:homoheleshaw_VN10_VN150}.}\label{table:Heleshaw}
+\end{table}

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{Flow Simulations in Hele-Shaw Cells at different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
-
 In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
@@
 
-\medskip
 Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid (\textit{in-situ} hydrocarbons).
@@
 
-\medskip
 Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
@@
 \medskip
+Porous media heterogeneity does play a significant role in formation and growth of fingers as it triggers fluid instabilities  
 In order to investigate the impact of porous media heterogeneity on formation and growth of viscous fingers, numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) were used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
-Figures~\ref{fig:HeleShawHeter_VR10} and \red{XXX(to be added)} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
+
 Finger width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
@@
 \medskip
+
+\red{Blablabla ...
+improve text ...} ...
+{\it The mesh adaptive algorithm embedded in the Fluidity/ICFERST model utilises a metric tensor field dependent on solution interpolation error-estimates \red{(talk about a posteriori errors and a short description of the mesh adaptivity algorithm)}\blue{(ref mesh adaptivity paper of 1995)} which locally control size and shape of elements in the metric.
+Mesh optimisation, based on XXX simulated annealing, is able to generate unstructured finer mesh grid in regions where flow properties change faster and coarser mesh grid in regions  where properties does not change so quickly.
+}
+
 Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-Porous media heterogeneity does play a significant role in formation and growth of fingers as it triggers fluid instabilities  
-In order to investigate the impact of porous media heterogeneity on formation and growth of viscous fingers, numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
+Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
+Spatial variation in geological formations occurs in all length-scales, where characteristics of heterogeneities in small (pore) length-scales are statistically embedded into permeability (absolute and relative) and porosity parameters.
+Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep{ewing_1989,tchelepi_1994}.
+
+In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
 Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
-Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers.
+Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers in simulations performed with viscosity ratio of 10 and 150, respectively.
 

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \end{equation}  
-Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
+Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
 
@@
 Spatial variation in geological formations occurs in all length-scales, where characteristics of heterogeneities in small (pore) length-scales are statistically embedded into permeability (absolute and relative) and porosity parameters.
-Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep{ewing_1989,tchelepi_1994}.
+Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
 
@@
 Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
-Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multiscale elongations with continuous growth and coalescence of dendritic fingers in simulations performed with viscosity ratio of 10 and 150, respectively.
-
-Finger width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
+Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
+In both simulations, fingers width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
 

### 2017-07-04 Papers/ViscousInstabilities/article_table.tex
updates

@@
     \hline\hline
-                                  & {\bf K}                                  & {\it VR}  & $\lambda_{f}^{\text{(calc)}}$ (cm) & $\lambda_{f}^{\text{(simul)}}$ (cm) \\
+                                  & {\bf K}                                  & {\it VR}  & $\lambda_{f}^{\text{(calc,max)}}$ (cm) & $\lambda_{f}^{\text{(simul,max)}}$ (cm) \\
                                   & $\left(\text{cm}^{2}\right)$              &           &  (Eqn.~\ref{eqn:guaneqn})  &                    \\

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, fingers width of approximately \red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Table~\ref{table:Heleshaw}).
+Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
+
+\red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
 

### 2017-07-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Table~\ref{table:Heleshaw}).
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
 Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
-
-\red{XXX-XX} cm were obtained \red{(JG: COMPARE IT W THEORETICAL VALUE)}.
 

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+
 Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
 In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
-Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
+Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981}  clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
 

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
-Spatial variation in geological formations occurs in all length-scales, where characteristics of heterogeneities in small (pore) length-scales are statistically embedded into permeability (absolute and relative) and porosity parameters.
+Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
 Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
@@
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases.
 
@@
 In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
-Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981}  clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
+Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
 

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\medskip
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varies in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
 Fluids are assumed incompressible and gravity was neglected.

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
do not rush kostas

--- 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
-Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
+Spatial variation in geological formations occurs in all length-scales, where characteristics of heterogeneities in small (pore) length-scales are statistically embedded into permeability (absolute and relative) and porosity parameters.
 Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
@@
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases.
-
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same mesh resolution, boundary and initial conditions as in previous homogeneous cases.
 Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
 In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
-Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
+Such calculated \citep[\ie theoretical based on simplified mathematical formulation due to][]{mclean_1981} ranges clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) does not take into account spatial variability of heterogeneity.
 

### 2017-07-05 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D500Hb}
-            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb} }
+      \hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D500Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb.pdf} }
       \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{4.cm} (b) t=0.24ss \hspace{4.0cm} (c) t=0.37s}
       \vspace{0.5cm}
-      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D1500Hb}
-            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D5000Hb}
-            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D8000Hb} }
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D1500Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D5000Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D8000Hb.pdf} }
       \hbox{\hspace{2.5cm} (d) t=0.59s \hspace{4.cm} (e) t= 1.61s\hspace{3.0cm} (f) t=2.50s }}
@@
 \vbox{
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b}}
-\hbox{\hspace{0.5cm} (a) {\it VR}=10 (homogeneous) \hspace{2.cm} (b) {\it VR}=150 (homogeneous) }
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b.pdf}}
+\hbox{\hspace{0.25cm} (a) {\it VR}=10 (homogeneous) \hspace{1.5cm} (b) {\it VR}=150 (homogeneous) }
 \vspace{0.5cm}
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b}}
-\hbox{\hspace{0.5cm} (c) {\it VR}=10 (heterogeneous) \hspace{2.cm} (d) {\it VR}=150 (heterogeneous) }
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b.pdf}}
+\hbox{\hspace{0.25cm} (c) {\it VR}=10 (heterogeneous) \hspace{1.5cm} (d) {\it VR}=150 (heterogeneous) }
 }
 \caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
-Top and bottom rows describe simulations performed with constant $\left(\text{\ie homogeneous with {\bf K}= 10}^{-10}\text{cm}^{2}\right)$ and randomly distributed (\ie heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
-Width of largest fingers for homogeneous cases are approximately 0.70 and 0.90cm ({\it VR}=10 and {\it VR}=150, respectively), whereas for heterogeneous cases are 0.56 and 0.40cm.
+Top and bottom rows describe simulations performed with constant \textit{\ie homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (\ie heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm ({\textit VR}=$10$ and {\textit VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
 Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}

### 2017-07-05 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
-Top and bottom rows describe simulations performed with constant \textit{\ie homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (\ie heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
-Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm ({\textit VR}=$10$ and {\textit VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
+Top and bottom rows describe simulations performed with constant \textit{i.e.
+homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (i.e.
+heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm (\textit{VR}=$10$ and \textit{VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
 Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}
@@
 \end{figure}
-
 \clearpage

### 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas
updates

--- 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 %%%%%%%%%%%%%
-\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}    
-\medskip
+\subsection{Capturing Fingering Formation with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
+%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
+In most geofluid numerical simulations, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably assimilate the information
 

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 %%%%%%%%%%%%%
-\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}    
-\medskip
+\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
+%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
+In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+Self-adaptive mesh refinement methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) as the simulation evolves in time and space focusing resolution where is necessary.
 

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
-Self-adaptive mesh refinement methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
-In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) as the simulation evolves in time and space focusing resolution where is necessary.
+Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
+These lead to a mesh that conforms to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
 
+Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
+There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
+Detailed description and analysis of these methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book,plewa_book,frey_book}.
+
+The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model
 \red{Blablabla ...

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model
-\red{Blablabla ...
-improve text ...} ...
-{\it The mesh adaptive algorithm embedded in the Fluidity/ICFERST model utilises a metric tensor field dependent on solution interpolation error-estimates \red{(talk about a posteriori errors and a short description of the mesh adaptivity algorithm)}\blue{(ref mesh adaptivity paper of 1995)} which locally control size and shape of elements in the metric.
-Mesh optimisation, based on XXX simulated annealing, is able to generate unstructured finer mesh grid in regions where flow properties change faster and coarser mesh grid in regions  where properties does not change so quickly.
-}
+The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
 

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
-Detailed description and analysis of these methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book,plewa_book,frey_book}.
+Detailed description and analysis of these methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
 

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
-Detailed description and analysis of these methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
+Detailed description and analysis of these mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
 

### 2017-07-07 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability} }
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
       \hbox{\hspace{1.0cm} (a) permeability map }}
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+\begin{figure}[ht]
+\vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
+      \hbox{\hspace{5.0cm} }}
+\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
+\label{fig:3DChannel_elem_planes}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-07-07 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
       \hbox{\hspace{1.0cm} (a) permeability map }}
-\caption{3D channel flow \red{FIGS AND COMMENTS TO BE ADDED AS SOON AS THE SIMULATION FINISHES}. The domain contains 243056 \PN[1]{1} element-pairs.}
+\caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
 \label{fig:3DChannel_PermMesh}
@@
 %%%
-\begin{landscape}
+%\begin{landscape}
 \begin{figure}[ht]
@@
 \end{figure}
+%\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.0cm} (a)     
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.cm} (b)      
+}
+}     
+\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$$s and (b)t=$$s.}
+\label{fig:3DChannel_darcy_vel}
+\end{figure}
 \end{landscape}
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.0cm} (a)     
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.cm} (b)      
+}
+}     
+\caption{For the same time steps as in Figure \ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$$s and (b)t=$$s.}
+\label{fig:3DChannel_sat}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-07-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
do not rush kostas

@@
 Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain.
-\red{For example, during water flooding, efficiency is related with capillary number.
+%\red{For example, during water flooding, efficiency is related with capillary number.
 The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES !
@@
 Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, \red{therefore it may override oil (?)}.
-Viscosity of supercritical CO$_{2}$ is also significantly smaller than that of the oil thus viscous fingering and/or channelling may occur.
-The outcome of the above operations \textit{viscous fingering} \red{(Merge these 2 sentences ...
-remember sentences often need to be long than a single line and shorter than 3-4 lines!!)}.
+During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
 

### 2017-07-07 Papers/ViscousInstabilities/article_table.tex
do not rush kostas

@@
      \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
-     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & \red{XX}  \\
+     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & 0.5  \\
      \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
       &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
-     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & \red{XX}  \\
-     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & \red{XX}  \\
+     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & 0.5  \\
+     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & 0.5  \\
      \hline
@@
 Superscript $\circ$ denotes initial condition.
-$\mathbf{K}_{i}$ is in \red{XX} (units) and $u^{\circ}_{w}$ is in \red{XX} (units).
-\red{(PLEASE: 1.
-DOUBLE CHECK THE K, u and S0 VALUES FROM THE MPML FILES; 2.
-\underline{REPLACE ALL \red{XX}}; 3.
-COMPLETE THE TABLE FOR ALL SECTIONS/SIMULATIONS; 4.
-UNITS FOR K AND U.)}  $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.
-}\label{table:setup}
+$\mathbf{K}_{i}$ is in $m^{2}$ and $u^{\circ}_{w}$ is in m/sec (units).
+$S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.
+}
+\label{table:setup}
 \end{table}

### 2017-07-07 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 }     
-\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$$s and (b)t=$$s.}
+\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_darcy_vel}
@@
 }     
-\caption{For the same time steps as in Figure \ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$$s and (b)t=$$s.}
+\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_sat}

### 2017-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

@@
 An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+In most simulations, the domain was initially fully saturated (\ie in-situ hydrocarbons) with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
@@
 Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
-They also show the wetting phase 'fingering' through the four subdomains, demonstrating the preferential flow through high-permeability regions.
+They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions.
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
 
-\red{ NEEDS TO BE MOVED LATER In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
+%%%%%%    
+%\red{ NEEDS TO BE MOVED LATER In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
 There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
 The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.}
+%%%%%%
 
 %%%%%%%%%%%%    
-\subsection{Flow Simulations in Hele-Shaw Cells at different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
+\subsection{Flow simulations in Hele-Shaw cells at different Viscosity Ratio conditions}\label{section:results_homo_hete} 
 In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
@@
 
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid (\textit{in-situ} hydrocarbons).
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid \ie in-situ hydrocarbons.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
@@
 
+\medskip
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.

### 2017-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

@@
 
+\medskip
 Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid \ie in-situ hydrocarbons.
@@
 
+\medskip
 Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=10.
+However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=$10$.
 
@@
 \end{equation}
-Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+
+\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
 This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).

### 2017-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

@@
 
-%%%%%%    
-%\red{ NEEDS TO BE MOVED LATER In Figures \ref{fem_cv_represent_vr1_vr10} there is a different set of simulations.
-There is a comparison between the $VR=1$ and $VR=10$ case and the reason was to imply the same domain, boundary and initial conditions and number of elements to underastand how the cross-flow will develop.
-The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.}
-%%%%%%
-
 %%%%%%%%%%%%    
@@
 
+\medskip
 Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
@@
 
+\medskip
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
@@
 
+\medskip
 The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
@@
 
+\medskip
 Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $u=1$ on the left hand side and the pressure set to $0$ on the outlet.
-A quick reminder at this point is that the simulator we are testing has also options to introduce gravity and/or corriolis, but for this current set of simulations these are neglected.
+Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $1$ on the left hand side, and the pressure is set to $0$ on the outlet.
 What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude.
 %(fig.\ref{fig:1testcase})
+Figure \ref{fem_cv_represent_vr1_vr10} describes an initial comparison between the $VR=1$ and $VR=10$ case under the same domain, boundary and initial conditions and number of elements so as to underastand how the cross-flow in the upper layers can be developed compared with the fingers that will appear below.
+The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
 The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
@@
 %Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
+
+\medskip
 Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
--\ref{fig:2testcase_d} will give a description of the simulation for different time-steps as these are described.
-In this set the interfacial instability is becoming more profound as the flow develops.
+-\ref{fig:2testcase_d} give a summary of the simulation for different time-steps as these are described.
+In this set, the interfacial instability is becoming more profound as the flow develops.
 Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.

### 2017-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

@@
 \medskip
-Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation.
+Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ has introduced into the formation.
 This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.

### 2017-07-10 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
-The ratio of viscosity between the two fluids is 5.
+The viscocity ratio of the two fluids is VR=$5$.
 In this case, the initially piston shape front collapses leading to the formation of several fingers.}
@@
 %%%%
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_vel_magn.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (a) single inlet velocity magnitude   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_vel_magn.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{5.0cm} (b) double inlet velocity magnitude   
-}
-}     
-\caption{For the same time step, t=1000, these plots describe the velocity magnitudes of the phase $1$ (injected fluid) under the same boundary and initiall conditions.
-From top to bottom,these graphs describe the velocity magnitude %for fixed mesh is plotted(top), the velocity magnitude
-for adaptive mesh-single inlet (top) and the velocity magnitude for adaptive mesh with double inlet (bottom) as these are also presented in fig.\ref{fig:3testcase_a}.
-The main difference between the upper and lower plot %is not just the ability to capture in greater detail, the fluid instabilities as they happenduring the finger development and their velocity patterns.
-While there
-is the impact of the second injection interval as this can be seen from the slope and the rate that the velocity magnitude is changing.}
-\label{fig:vel_magn}
-\end{figure}
-
-%%%%
-%%%%  FIGURE
-%%%%
 \begin{landscape}
@@
       \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
-      \hbox{\hspace{1.0cm} (a) permeability map }}
+      \hbox{\hspace{5.0cm} (a) permeability map }}
 \caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
@@
 \end{figure}
-\clearpage
-
-%%%
-%%% FIGURE XXXXXX
-%%%
-%\begin{landscape}
-\begin{figure}[ht]
-\vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
-      \hbox{\hspace{5.0cm} }}
-\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
-\label{fig:3DChannel_elem_planes}
-\end{figure}
-%\end{landscape}
 \clearpage

### 2017-07-10 Papers/ViscousInstabilities/article_figure2.tex
do not rush kostas

@@
 
-%%%
-%%% FIGURE
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-    \vbox{ 
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
-            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (a) VR = 1}
-      \vspace{1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
-            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
-The domain contains $4678$ elements.(\blue{this is a different set of simulation, we might have to change it and bring between the  })}
-\label{fem_cv_represent_vr1_vr10}
-\end{figure}
-\end{landscape}
-\clearpage
-%%%
-%%%
-%%%
-
 %%%%
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $47500$ \PN[1]{2} triangular elements.}
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN3}
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=150): snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=150, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
-\label{fig:homoheleshaw_VN10}
+\label{fig:homoheleshaw_VN150}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1}
+            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb} 
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb} }
+      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.19s \hspace{4.0cm} (c) t=0.63s}
+      \vspace{0.5cm}
+      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb}
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb} }
+      \hbox{\hspace{2.5cm} (d) t=3.41s \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation.
+The domain contains 26313 \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR10}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D500Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb.pdf} }
+      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{4.cm} (b) t=0.24ss \hspace{4.0cm} (c) t=0.37s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D1500Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D5000Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D8000Hb.pdf} }
+      \hbox{\hspace{2.5cm} (d) t=0.59s \hspace{4.cm} (e) t= 1.61s\hspace{3.0cm} (f) t=2.50s }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=150: snapshots of saturation profile during 2.50 seconds of simulation.
+Permeability distribution used in this simulation was the same as shown in Fig.~\ref{fig:HeleShawHeter_VR10}a.
+The domain contains 26313 \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR150}
 \end{figure}
@@
 %%%%
-\begin{landscape}
 \begin{figure}[ht]
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
-       \includegraphics[width=.49\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_k2b}}
-\caption{Simulated flow in Hele-Shaw cells performed with viscosity ratios of 10 (left, t=7.61s) and 150 (t=1.94s).
-Width of largest fingers are approximetely 0.70 and 0.90cm, which are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.
-Domains of both simulations contain $26313$ \PN[1]{2} triangular elements.\red{(More pics to be added!!)}}
+\vbox{
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b.pdf}}
+\hbox{\hspace{0.25cm} (a) {\it VR}=10 (homogeneous) \hspace{1.5cm} (b) {\it VR}=150 (homogeneous) }
+\vspace{0.5cm}
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b.pdf}}
+\hbox{\hspace{0.25cm} (c) {\it VR}=10 (heterogeneous) \hspace{1.5cm} (d) {\it VR}=150 (heterogeneous) }
+}
+\caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
+Top and bottom rows describe simulations performed with constant \textit{i.e.
+homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (i.e.
+heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm (\textit{VR}=$10$ and \textit{VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
+Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}
 \label{fig:homoheleshaw_VN10_VN150}
 \end{figure}
-\end{landscape}
-
-\begin{comment}
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_250_1.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_1000.pdf}}
-\vspace{0.cm}
-\hbox{\hspace{1.0cm} (a) pressure at t=0 \hspace{3.cm} (b) t=250\red{(???)} \hspace{3.0cm} (c) t=1000\red{(???)}}
-\vspace{0.5cm}
-\hbox{
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_6000.pdf}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous/saffman_homo_fixed_end_1.pdf}}
-\vspace{0.cm}
-\hbox{ \hspace{2.cm} (d) t=6000\red{(???)} \hspace{3.cm} (e) t=XXX\red{(???)}}
-\vspace{0.cm}
-}   
-\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): (a) pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-e) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $47000$ \PN[1]{2} triangular elements.
-The pressure and saturation range of values are the same like the  case in fig.\ref{fig:homoheleshaw_VN3}.}
-\label{fig:homoheleshaw_VN10}
-\end{figure}
-\end{landscape}
-\clearpage
-\end{comment}
-
-%%%
-%%% FIGURE XXXXXX
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-  \vbox{\vspace{-1cm}
-      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
-      \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
-      \vspace{0.5cm}
-      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
-      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
-\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during \red{XX} seconds of simulation.
-The domain contains \red{XX} \PN[1]{2} element-pairs.}
-\label{fig:HeleShawHeter_VR10}
-\end{figure}
-\end{landscape}
 \clearpage
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{figure}[ht]
+\vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
+      \hbox{\hspace{5.0cm} (a) permeability map }}
+\caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
+\label{fig:3DChannel_PermMesh}
+\end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+%\begin{landscape}
+\begin{figure}[ht]
+\vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
+      \hbox{\hspace{5.0cm} }}
+\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
+\label{fig:3DChannel_elem_planes}
+\end{figure}
+%\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.0cm} (a)     
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.cm} (b)      
+}
+}     
+\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
+\label{fig:3DChannel_darcy_vel}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.0cm} (a)     
+}
+\hbox{\hspace{3.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{10.cm} (b)      
+}
+}     
+\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
+\label{fig:3DChannel_sat}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-07-10 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
+\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for MR = 100 (start)   
+\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for VR = 100 (start)   
 }
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
+\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
 }
 \vspace{0.0cm}
-\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for MR = 100 (t = 1500)   
+\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for VR = 100 (t = 1500)   
 }
 }     
-\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh for the same time steps, t=$0.25$ or t=500(a), t=$0.75$ or t=1500(b). }
+\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh was used for the same time steps, t=$0.25$s or t=500(a), t=$0.75$s or t=1500(b).
+}
 \label{fig:4testcase_a}
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
+\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{3.75cm} (c) fixed and unstructured mesh for MR = 100    
+\hbox{\hspace{3.75cm} (c) fixed and unstructured mesh for VR = 100    
 }
 \hbox{\hspace{3.5cm}
-\includegraphics[width=.8\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
+\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
 }
@@
 }     
-\caption{screenshot (c) is for t=$1.5$ sec or t=$3000$ and screenshot (d) is for t=$3.175$ sec, at the end of the simulations. }
+\caption{screenshot (c) is for t=$1.5$s or t=$3000$ and screenshot (d) is for t=$3.175$s, at the end of the simulations. }
 \label{fig:4testcase_b}

### 2017-07-10 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
+\hbox{\includegraphics[width=.71\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
       \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
@@
 \hbox{
-      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
-      \includegraphics[width=.375\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-      \includegraphics[width=.65\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
+      \includegraphics[width=.38\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
+      \includegraphics[width=.38\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
+      \includegraphics[width=.66\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
 \vspace{0.cm}
@@
 \hbox{
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{4.5cm} (e)t=10.00s}
+\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{5.cm} (e)t=10.00s}
 \vspace{0.cm}
@@
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{4.5cm} (e)t=2.31s}
+\hbox{ \hspace{2.cm} (c) t=1.32s \hspace{4.5cm} (d) t=1.70s \hspace{5.cm} (e)t=2.31s}
 \vspace{0.cm}
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1}
-            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb} 
-            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb} }
+      \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
+            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb.pdf} 
+            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb.pdf} }
       \hbox{\hspace{1.0cm} (a) permeability map \hspace{3.cm} (b) t=0.19s \hspace{4.0cm} (c) t=0.63s}
       \vspace{0.5cm}
-      \hbox{\includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb}
-            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb}
-            \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb} }
-      \hbox{\hspace{2.5cm} (d) t=3.41s \hspace{5.cm} (e) t= 5.54s\hspace{3.0cm} (f) t=9.77s }}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D5000Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D8000Hb.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D13800Hb.pdf} }
+      \hbox{\hspace{2.cm} (d) t=3.41s \hspace{3.5cm} (e) t= 5.54s\hspace{4.5cm} (f) t=9.77s }}
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation.
@@
             \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb.pdf} }
-      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{4.cm} (b) t=0.24ss \hspace{4.0cm} (c) t=0.37s}
+      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{6.cm} (b) t=0.24ss \hspace{4.cm} (c) t=0.37s}
       \vspace{0.5cm}
@@
             \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D8000Hb.pdf} }
-      \hbox{\hspace{2.5cm} (d) t=0.59s \hspace{4.cm} (e) t= 1.61s\hspace{3.0cm} (f) t=2.50s }}
+      \hbox{\hspace{3.cm} (d) t=0.59s \hspace{3.cm} (e) t= 1.61s\hspace{4.cm} (f) t=2.50s }}
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=150: snapshots of saturation profile during 2.50 seconds of simulation.

### 2017-07-10 Papers/ViscousInstabilities/article_figure1.tex
do not rush kostas

@@
 \caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
-The domain contains $4678$ elements.(\blue{ Jeff this is a different set of simulation, I have moved it just after the \textit{map of permeabilities} above as a first comparison between $VR1$ and $VR10$})}
+The domain contains $4678$ elements.
+\red{need to put his footnote here?
+"At this poing it is proper to mention that the white grid lines of the domain, as they appear in this set of figures and the rest are for visual purposes only and they are not related with mesh itslef"}}
 \label{fem_cv_represent_vr1_vr10}
@@
 }     
-\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
+\caption{Contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_darcy_vel}

### 2017-07-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas
update
updates

@@
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-These lead to a mesh that conforms to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
+This leads to mesh grid that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
 
@@
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
-In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
+In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
 There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 The domain is discretised with $5960$ \PN[1]{2} elements.
-}
+\red{(ARE YOU SURE TIME IS CORRECT ??)} }
 \label{fem_cv_represent_a}
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
+      \hbox{\hspace{2.0cm} (a) t=XXXs \hspace{6.cm} (b) t=XXXs \hspace{4.cm} (c) t=XXXs}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D300c} }
+      \hbox{\hspace{3.cm} (d) t=XXXs \hspace{3.cm} (e) t= XXXs\hspace{4.cm} (f) t=XXXs }}
+\caption{XXX.}
+\label{fig:3DChannel_Isosurf}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
+\red{(KOSTAS: YOU HAVE REMOVED 1 SIMULATION HERE ... THEREFORE YOU NEED TO MAKE SURE THAT THE TEXT REFLECT THE NEW FIGURE'S CONFIGURATION!!)}
+
 %%%%%%%%%%%%    
@@
 %%%%%%%%%%%%%
-\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
+\subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}    
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
 This leads to mesh grid that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
+
+In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the nucleation of fingers was demonstrated in homogeneous porous media
 

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the nucleation of fingers was demonstrated in homogeneous porous media
+In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability nucleation were demonstrated in modified simulated Hele-Shaw cells.
 

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 
-In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the nucleation of fingers was demonstrated in homogeneous porous media
+In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
+In order to capture the continuous development of such viscous instabilities, mesh grids  with sufficient resolution need to be applied over the interface between fluids.
 

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \vspace{0.0cm}
-\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
+\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) map of permeabilties K   
+\hbox{\hspace{6.5cm} (a) Schematics of the domain
 }
@@
 }     
-\caption{Figure (a) describes the initial and boundary conditions as these are applied in this set of simulations.
-Below (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh.
+\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the domain depicting four regions with prescribed synthetic permeabilities; (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh.
 During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids.

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
-In order to capture the continuous development of such viscous instabilities, mesh grids  with sufficient resolution need to be applied over the interface between fluids.
+In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
+In this section, numerical simulations were conducted with distinct mesh resolutions to qualitatively assess model capability to capture fingers growth.
+In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain}a).
 

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
update

@@
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
-      \hbox{\hspace{2.0cm} (a) t=XXXs \hspace{6.cm} (b) t=XXXs \hspace{4.cm} (c) t=XXXs}
+      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
       \vspace{0.5cm}
@@
             \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
-            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D300c} }
-      \hbox{\hspace{3.cm} (d) t=XXXs \hspace{3.cm} (e) t= XXXs\hspace{4.cm} (f) t=XXXs }}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c} }
+      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
 \caption{XXX.}

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \hbox{\hspace{4.0cm}
-\includegraphics[width=.9\textwidth]{./Pics/map_of_boundaries_1.pdf}
+\includegraphics[width=.9\textwidth]{./Pics/Four_regions_coarse_MeshPermeability}
 }
@@
 }     
-\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the domain depicting four regions with prescribed synthetic permeabilities; (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh.
-During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids.
-}
+\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the simulated domain; (b) permeability distribution with grid resolution in the simulation performed with a coarse mesh (there are 1292 \PN[1]{2} element-pairs in the domain).}
 \label{fig:testcase_heter_domain}

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-This leads to mesh grid that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
+This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
 
@@
 In this section, numerical simulations were conducted with distinct mesh resolutions to qualitatively assess model capability to capture fingers growth.
-In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain}a).
+In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain}).
 

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 %%%%
-\begin{landscape}
 \begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{4.0cm}
-\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) Schematics of the domain
-}
-\vspace{0.25cm}
-\hbox{\hspace{4.0cm}
-\includegraphics[width=.9\textwidth]{./Pics/Four_regions_coarse_MeshPermeability}
-}
-\vspace{0.0cm}
-\hbox{\hspace{9cm} (b)      
-}
-}     
-\caption{Impact of mesh resolution on flow instabilities: (a) schematics of the simulated domain; (b) permeability distribution with grid resolution in the simulation performed with a coarse mesh (there are 1292 \PN[1]{2} element-pairs in the domain).}
+%\vbox{
+%\hbox{\hspace{4.0cm}
+%\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{6.5cm} (a) Schematics of the domain
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{4.0cm}
+%\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
+\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshPerm}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{4cm} (b) Permeability distribution for coarse mesh simulation     
+%}
+%}     
+\caption{Impact of mesh resolution on flow instabilities: permeability distribution with initial grid resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+There are 13068 \PN[1]{2} element-pairs in the domain.}
 \label{fig:testcase_heter_domain}
 \end{figure}
-\end{landscape}
 \clearpage
 
+\begin{comment}
 %%%

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \begin{figure}[ht] 
-%\vbox{
+\vbox{
 %\hbox{\hspace{4.0cm}
@@
 %\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
-\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshPerm}
+\hbox{\hspace{1cm}
+\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshPerm}}
+\vspace{-1.0cm}
+\hbox{\hspace{3.5cm} (a) Permeability mapping ({\bf K})}
+\vspace{0.0cm}
+\hbox{\hspace{1cm}
+\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshSat1}}
+\vspace{-1.0cm}
+\hbox{\hspace{3.5cm} (b) Initial saturation distribution}}
 %}
@@
 %}     
-\caption{Impact of mesh resolution on flow instabilities: permeability distribution with initial grid resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on flow instabilities: (a) permeability and (b) initial saturation with initial grid resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshPerm}}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm}}
 \vspace{-1.0cm}
@@
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Five_regions_adapt_MeshSat1}}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1}}
 \vspace{-1.0cm}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements}
+\caption{Impact of mesh resolution on flow instabilities: mesh resolution \red{JG: add here some comments ... this pic needs to be placed after the sat plots for the adaptivity case ...}}
+\end{figure}
 

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \label{fig:testcase_heter_domain}
+\end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-1.cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on flow instabilities:}
+\label{fig:5regions_fixedmesh}
+\end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-1.cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on flow instabilities:}
+\label{fig:5regions_fixedmesh}
+\end{figure}
+\clearpage
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-1.cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350velb}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100velb} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700velb}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150velb} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000velb}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200velb} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500velb}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250velb}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on flow instabilities:}
+\label{fig:5regions_fixedmesh}
 \end{figure}

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
-Detailed description and analysis of these mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
+Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
 

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \caption{Impact of mesh resolution on flow instabilities:}
-\label{fig:5regions_fixedmesh}
+\label{fig:5regions_adaptmesh}
 \end{figure}
@@
 \caption{Impact of mesh resolution on flow instabilities:}
-\label{fig:5regions_fixedmesh}
+\label{fig:5regions_adaptmeshvels}
 \end{figure}
@@
 \caption{Impact of mesh resolution on flow instabilities: mesh resolution \red{JG: add here some comments ... this pic needs to be placed after the sat plots for the adaptivity case ...}}
+\label{fig:5regions_plottimenodeselements}
 \end{figure}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{
+            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_nomeshb}
+            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251b} }
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b}
+            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}}
+\caption{Impact of mesh resolution on flow instabilities: }
+\label{fig:5regions_AdaptZoom}
+\end{figure}
+\end{landscape}
+\clearpage
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-In this section, numerical simulations were conducted with distinct mesh resolutions to qualitatively assess model capability to capture fingers growth.
-In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain}).
+Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
 
-\medskip
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
@@
 
-\medskip
 The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
 Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+
+\medskip
+In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers growth.
+In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain} a).
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
@@
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
-In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
+In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the whole domain but in particular at the interface between fluids.
 Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the whole domain but in particular at the interface between fluids.
-Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and/or highly heterogeneous properties.
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
+\medskip
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
-There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
+There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes in order of element basis function (p-adaptivity).
 Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+The mesh adapts within thee stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
+In the simulations shown in this work, mesh will adapt as a response to oscillations in phase saturation field with prescribed interpolation error estimate.
 
 \medskip
-In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers growth.
-In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain} a).
+In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
+In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
+The computational domain is shown Fig.~\ref{fig:testcase_heter_domain} (a),
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex

@@
 \begin{abstract} 
-A set of simulations is presented so as to model the viscous fingering-flow instability using a novel method for modeling multi-phase flows in porous media.
-Starting from the Hele-Shaw experimental which is mathematically analogous to the two-dimensional flow in porous medium, test-cases of both homogenous and heterogeneous computational domains, under different conditions are listed.
-The development of finger structures is explained by taking into account different maps of permeabilities, mobility ratios and surface tension.
+The aim of this paper is to model flow instabilities \ie{viscous fingering} using a novel method for modeling multi-phase flows in heterogeneous porous with either uniform or random generated permeability distribution.
+Starting from modelling the Hele-Shaw experimental apparatus, which is mathematically analogous to the two-dimensional flow in porous media problem.
+The development of finger structures is investigated by taking into account different conditions such as, different domains under uniform or different permeabilities regions, mobility ratios, mesh types.
 A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
-The governing multiphase porous media flow equations are solved using an adaptive and unstructured mesh.
-In this paper the use of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows is introduced, as one of the methods that will allow the user to focus the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-It was found that the initial state is the decisive factor in the development of the process up to large times
-The aim of this paper is to extend and further apply the formulation (embedded in the Fluidity software framework) to multiphase flows in heterogeneous porous media combined with either uniform or random generated permeability distribution.
+The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
+Dynamic mesh adaptivity will not only help to better capture the development of finger but also allow the system to focus the computational effort where is needed, minimizing both the CPU time and the numerical diffusion.
+It was found that mobility ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an ustructured mesh allow the user to better describe and visualise the phenomenon.
 \end{abstract}
@@
 \medskip
-As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) (also known as \textit{viscocity ratio} (VR), is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) also known as \textit{viscocity ratio} (VR), is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 \medskip
-Numerical simulation was performed in slightly modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
@@
 
-\red{(KOSTAS: YOU HAVE REMOVED 1 SIMULATION HERE ... THEREFORE YOU NEED TO MAKE SURE THAT THE TEXT REFLECT THE NEW FIGURE'S CONFIGURATION!!)}
+\red{(KOSTAS: YOU HAVE REMOVED 1 SIMULATION HERE ... THEREFORE YOU NEED TO MAKE SURE THAT THE TEXT REFLECT THE NEW FIGURE'S CONFIGURATION!!) \blue{will work on it ASAP this evening}}
 
@@
 Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
+
 \begin{equation}   
@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
@@
 
+\medskip
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
-In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the whole domain but in particular at the interface between fluids.
-Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and/or highly heterogeneous properties.
+In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
+Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
 
@@
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
-There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes in order of element basis function (p-adaptivity).
+There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
 Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
-The mesh adapts within thee stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
-In the simulations shown in this work, mesh will adapt as a response to oscillations in phase saturation field with prescribed interpolation error estimate.
+The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
+In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate.
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
+During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
 
@@
 An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
-In most simulations, the domain was initially fully saturated (\ie in-situ hydrocarbons) with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+In most simulations, the domain was initially fully saturated (\ie {\it in situ} hydrocarbons) with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
@@
 \medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid \ie in-situ hydrocarbons.
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid, \ie {\it in situ} hydrocarbons.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
@@
 \medskip
-In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
+In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics (\ie formation and growth).
 In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
-The computational domain is shown Fig.~\ref{fig:testcase_heter_domain} (a),
+The computational domain, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain dully saturated with five regions with prescribed permeabilities, and
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain dully saturated with five regions with prescribed permeabilities, and
+The computational space, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase) and divided into 5 regions with prescribed permeabilities.
+No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at $u_{1}=1$.
 

### 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2017-07-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain} (a), consists of a rectangular domain dully saturated with five regions with prescribed permeabilities, and
+The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities.
+No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+Pressure gradient between inlet and outlet (right-hand) faces was initially prescribed to the system.
 

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 %}     
-\caption{Impact of mesh resolution on flow instabilities: (a) permeability and (b) initial saturation with initial grid resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 %}     
-\caption{Impact of mesh resolution on flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on flow instabilities:}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
 \label{fig:5regions_fixedmesh}

### 2017-07-12 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
   \begin{figure}[ht]
-  \vbox{\vspace{-1.cm}
+  \vbox{\vspace{-2.cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b} 
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on flow instabilities:}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
 \label{fig:5regions_adaptmesh}
@@
   \begin{figure}[ht]
-  \vbox{\vspace{-1.cm}
+  \vbox{\vspace{-2.5cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb} 
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on flow instabilities:}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field overlapped with Darcy velocity (in cm/s) through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.
+Colour scheme for saturation is the same as used in Fig.~\ref{fig:5regions_adaptmesh}.}
 \label{fig:5regions_adaptmeshvels}

### 2017-07-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
update

@@
 \medskip
-In this section, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics (\ie formation and growth).
+Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
 In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
@@
 No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
-Pressure gradient between inlet and outlet (right-hand) faces was initially prescribed to the system.
 

### 2017-07-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities.
-No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+
+Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive mesh grids over 1.50 seconds.
+Both simulations started with a mesh of 13068 triangular elements (\PN[1]{2} element-pairs), however as flow dynamics evolves the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements})
 

### 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements}
-\caption{Impact of mesh resolution on flow instabilities: mesh resolution \red{JG: add here some comments ... this pic needs to be placed after the sat plots for the adaptivity case ...}}
+\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
 \label{fig:5regions_plottimenodeselements}

### 2017-07-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive mesh grids over 1.50 seconds.
-Both simulations started with a mesh of 13068 triangular elements (\PN[1]{2} element-pairs), however as flow dynamics evolves the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements})
+Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
+Sharp permeability gradient triggered the onset of fingers' formation
 

### 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 %%%
-\begin{landscape}
+%\begin{landscape}
   \begin{figure}[ht]
   \vbox{\vspace{-.5cm}
-      \hbox{
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_nomeshb}
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251b} }
-      \vspace{0.5cm}
-      \hbox{\hspace{.5cm} \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b}
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}}
+      \hbox{\hspace{4cm}\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb} }
+      \vspace{-0.cm}\hbox{\hspace{5cm}(a) saturation (phase 1) }\vspace{-0.cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel1b.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel2b.pdf} }
+      \vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b}
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}
+      \vspace{-0.cm}\hbox{\hspace{1cm}(d) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm} }
 \caption{Impact of mesh resolution on flow instabilities: }
@@
 \end{figure}
-\end{landscape}
+%\end{landscape}
 \clearpage

### 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
update

--- 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
@@
 %%%
-\begin{landscape}
+%\begin{landscape}
   \begin{figure}[ht]
   \vbox{\vspace{-.5cm}
-      \hbox{
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_nomeshb}
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251b} }
-      \vspace{0.5cm}
-      \hbox{\hspace{.5cm} \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b}
-            \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}}
-\caption{Impact of mesh resolution on flow instabilities: }
+      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb}
+            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb} }
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(a) fixed and adaptive mesh  }\vspace{-0.cm}
+      %\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel1b.pdf}
+      %      \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel2b.pdf} }
+      %\vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b} }
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(b) Zoom on region {\it A}  }\vspace{-0.cm}
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b} }
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
+\caption{Impact of mesh resolution on flow instabilities: Capture of flow instabilities at interfaces in two regions of the computational domain, {\it A} and {\it B}, in simulations conducted with fixed and adaptive mesh.
+}
 \label{fig:5regions_AdaptZoom}
 \end{figure}
-\end{landscape}
+%\end{landscape}
 \clearpage

### 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
update

@@
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
-\caption{Impact of mesh resolution on flow instabilities: Capture of flow instabilities at interfaces in two regions of the computational domain, {\it A} and {\it B}, in simulations conducted with fixed and adaptive mesh.
+\caption{Impact of mesh resolution on flow instabilities: Capture of flow instabilities at interfaces (t = 0.20 s) in two regions of the computational domain, {\it A} and {\it B}, in simulations conducted with fixed and adaptive mesh.
 }

### 2017-07-14 Papers/ViscousInstabilities/article_figure1.tex
update

--- 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
@@
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
-\caption{Impact of mesh resolution on flow instabilities: Capture of flow instabilities at interfaces in two regions of the computational domain, {\it A} and {\it B}, in simulations conducted with fixed and adaptive mesh.
+\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20 s) in two regions of the computational domain, {\it A} and {\it B}.
+Simulations were conducted with fixed (left-hand side) and adaptive meshes.
 }

### 2017-07-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 
-The mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
+The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
 Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
@@
 A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+Viscosity ratio is set to 10.
 
-Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive mesh grids over 1.50 seconds.
+Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes 1.50 seconds.
 Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
-Sharp permeability gradient triggered the onset of fingers' formation
+The simulation performed with a fixed and relatively fine mesh
+Sharp permeability gradient triggered the onset of fingers' formation, as shown in
 

### 2017-07-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
-In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate.
+In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
 
@@
 A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
-Viscosity ratio is set to 10.
+Viscosity ratio of the two fluids is set to 10.
 

### 2017-07-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes 1.50 seconds.
+Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.
 Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
+In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeability at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
 The simulation performed with a fixed and relatively fine mesh

### 2017-07-14 Papers/ViscousInstabilities/article_figure1.tex
some updates

@@
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm}}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
 \vspace{-1.0cm}
@@
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1}}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
 \vspace{-1.0cm}
@@
   \vbox{\vspace{-1.cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
@@
   \vbox{\vspace{-2.cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
@@
   \vbox{\vspace{-2.5cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350velb}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350velb.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100velb} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700velb}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700velb.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150velb} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000velb}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000velb.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200velb} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500velb}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500velb.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250velb}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250velb.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
@@
 \begin{figure}[ht] 
-\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements.pdf}
 \caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb}
-            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb} }
+      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb.pdf}
+            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb.pdf} }
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(a) fixed and adaptive mesh  }\vspace{-0.cm}
@@
       %\vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
-      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b}
-             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b} }
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b.pdf}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b.pdf} }
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(b) Zoom on region {\it A}  }\vspace{-0.cm}
-      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b}
-             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b} }
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b.pdf}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}

### 2017-07-14 Papers/ViscousInstabilities/article_figure1.tex
some updates

@@
 
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
-}
-}     
-\caption{For $t=0.125$s, $2$ test-cases under the VR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared.
-There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
-\label{fig:2testcase_a}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
-}
-}     
-\caption{At $t=0.25$s ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound as can been seen at the bottom.}
-\label{fig:2testcase_b}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
-}
-}     
-\caption{At $t=0.75 sec$ ($t=1500$, timestemp) the initial cross flow is now fully developed and has travel all the way towards the outlet (right-hand side).
-and the finger below start forming a front that is also travelling towards the left-hand side.}
-\label{fig:2testcase_c}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
-}
-\vspace{0.25cm}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
-}
-}     
-\caption{Using the $P_{1}DGP_{2}$ element type for VR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe.
-The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$.
-When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
-\label{fig:2testcase_d}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-  \includegraphics[width=.67\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{Comparing test-cases of fixed and adaptive mesh while a second region/inlet is introduced.
-For $t=0.101$s, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps.
-For this simulation there are $13226$ elements for the fixed messh and $43716$ for the adaptive.}
-\label{fig:3testcase_a}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_500_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{For $t=5$s there is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_b}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_1500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_1500_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{For $t=7.5$s this is a comparison between fixed mesh(a) and adaptive mesh(b).}
-\label{fig:3testcase_c}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/5reg_dinlet_fixed_end.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) double inlet - fixed mesh   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.9\textwidth]{./Pics1/5reg_dinlet_adapt_end_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{6.5cm} (b) double inlet adaptive mesh   
-}
-}     
-\caption{This is a comparison between fixed mesh(a) and adaptive mesh(b) at the end of the simulation.
-For the fixed mesh at this point the maximum number of point is $13226$ while for the adaptive mesh is $7582$ and most of them are located where is needed in the domain.}
-\label{fig:3testcase_d}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (a) fixed and unstructured mesh for VR = 100 (start)   
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{3.75cm} (b) fixed and unstructured mesh for VR = 100 (t = 1500)   
-}
-}     
-\caption{For the case of VR=$100$ from top to bottom, the number of elements is $4680$ and fixed and unstructured mesh was used for the same time steps, t=$0.25$s or t=500(a), t=$0.75$s or t=1500(b).
-}
-\label{fig:4testcase_a}
-\end{figure}
-\end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.7\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{3.75cm} (c) fixed and unstructured mesh for VR = 100    
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=.93\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{7.cm} (d) end of simulations     
-}
-}     
-\caption{screenshot (c) is for t=$1.5$s or t=$3000$ and screenshot (d) is for t=$3.175$s, at the end of the simulations. }
-\label{fig:4testcase_b}
-\end{figure}
-\end{landscape}
-\clearpage
-
 %%%
@@
 %%%%
-\begin{landscape}
+%\begin{landscape}
 \begin{figure}[ht] 
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
+\hbox{\hspace{0.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100_1.pdf} 
 }
-\vspace{0.0cm}
-\hbox{\hspace{10.0cm} (a)     
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (a)     
 }
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
+\hbox{\hspace{0.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
 }
-\vspace{0.0cm}
-\hbox{\hspace{10.cm} (b)      
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (b)      
 }
 }     
-\caption{Contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
-\label{fig:3DChannel_darcy_vel}
+\caption{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.91$s and (b)t=$4.3$s.}
+\label{fig:3DChannel_planes}
 \end{figure}
-\end{landscape}
+%\end{landscape}
 \clearpage
 
+\begin{comment}
 %%%%
@@
 %%%%
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\vspace{-5.0cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
+}
+\hspace{-5.0cm}
+\hbox{\hspace{6.0cm} (a) \hspace{6.cm} (b)    
+}
+\hbox{\vspace{0.0cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
+}
+\hspace{-5.0cm}
+\hbox{\hspace{6.0cm} (c) \hspace{6.cm} (d)     
+}
+}     
+\caption{The figures (a) t=$0.91$s and (b)t=$4.3$s give a description of the saturation front. }
+\label{fig:3DChannel_sat}
+\end{figure}
+%\end{landscape}
+\clearpage
+\end{comment}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
 \begin{landscape}
   \begin{figure}[ht]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{10.0cm} (a)     
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{10.cm} (b)      
-}
-}     
-\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
-\label{fig:3DChannel_sat}
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} }
+      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
+      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
+\caption{$368513$ elements.}
+\label{fig:3DChannel_Isosurf}
 \end{figure}
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
+      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c.pdf} }
       \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
       \vspace{0.5cm}
-      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
-            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
-            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c} }
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c.pdf} }
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{XXX.}
+\caption{$368513$ elements.}
 \label{fig:3DChannel_Isosurf}

### 2017-07-14 Papers/ViscousInstabilities/article_figure2.tex
some updates

@@
 %%%%
-\begin{landscape}
 \begin{figure}[ht] 
 \vbox{
-\hbox{\hspace{4.0cm}
-\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
-}
+%\hbox{\hspace{4.0cm}
+%\includegraphics[width=.75\textwidth]{./Pics/map_of_boundaries.pdf} 
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{6.5cm} (a) Schematics of the domain
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{4.0cm}
+%\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
+\hbox{\hspace{1cm}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
+\vspace{-1.0cm}
+\hbox{\hspace{3.5cm} (a) Permeability mapping ({\bf K})}
 \vspace{0.0cm}
-\hbox{\hspace{6.5cm} (a) map of permeabilties K   
-}
-\vspace{0.25cm}
-\hbox{\hspace{4.0cm}
-\includegraphics[width=.9\textwidth]{./Pics/map_of_boundaries_1.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{9cm} (b)      
-}
-}     
-\caption{Figure (a) describes the initial and boundary conditions as these are applied in this set of simulations.
-Below (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh.
-During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids.
-}
+\hbox{\hspace{1cm}
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
+\vspace{-1.0cm}
+\hbox{\hspace{3.5cm} (b) Initial saturation distribution}}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{4cm} (b) Permeability distribution for coarse mesh simulation     
+%}
+%}     
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+There are 13068 \PN[1]{2} element-pairs in the domain.}
 \label{fig:testcase_heter_domain}
 \end{figure}
-\end{landscape}
 \clearpage
 
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-1.cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
+\label{fig:5regions_fixedmesh}
+\end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-2.cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
+\label{fig:5regions_adaptmesh}
+\end{figure}
+\clearpage
+%%%
+%%% FIGURE XXXXXX
+%%%
+  \begin{figure}[ht]
+  \vbox{\vspace{-2.5cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350velb.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700velb.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000velb.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200velb.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500velb.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250velb.pdf}}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field overlapped with Darcy velocity (in cm/s) through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.
+Colour scheme for saturation is the same as used in Fig.~\ref{fig:5regions_adaptmesh}.}
+\label{fig:5regions_adaptmeshvels}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht] 
+\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements.pdf}
+\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
+\label{fig:5regions_plottimenodeselements}
+\end{figure}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+%\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D250_meshb.pdf}
+            \includegraphics[width=.5\textwidth, height=0.33\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250_edb.pdf} }
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(a) fixed and adaptive mesh  }\vspace{-0.cm}
+      %\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel1b.pdf}
+      %      \includegraphics[width=.5\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_vel2b.pdf} }
+      %\vspace{-0.cm}\hbox{\hspace{1cm}(b) Darcy velocity (phase 1) \hspace{1cm}(c) Darcy velocity (phase 2) }\vspace{0.cm}
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom1b.pdf}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom1b.pdf} }
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(b) Zoom on region {\it A}  }\vspace{-0.cm}
+      \hbox{ \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_D251_Zoom2b.pdf}
+             \includegraphics[width=.5\textwidth, height=0.3\textwidth,clip]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D251_Zoom2b.pdf}}
+      \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
+\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20 s) in two regions of the computational domain, {\it A} and {\it B}.
+Simulations were conducted with fixed (left-hand side) and adaptive meshes.
+}
+\label{fig:5regions_AdaptZoom}
+\end{figure}
+%\end{landscape}
+\clearpage
+
+\begin{comment}
 %%%
@@
 
-%%%
-%%% FIGURE XXXXXX
-%%%
-%\begin{landscape}
-\begin{figure}[ht]
-\vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/3D_channel_elem_planes_1.pdf} }
-      \hbox{\hspace{5.0cm} }}
-\caption{ XY and YZ planes in the middle of the domain at the end of simulation \red{t=$4.3$sec, but am I reading something wrong?} }
-\label{fig:3DChannel_elem_planes}
-\end{figure}
-%\end{landscape}
-\clearpage
-
 %%%%
@@
 %%%%
-\begin{landscape}
+%\begin{landscape}
 \begin{figure}[ht] 
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100.pdf} 
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100_1.pdf} 
 }
@@
 \hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490.pdf}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
 }
@@
 }     
-\caption{ contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
+\caption{Contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_darcy_vel}
 \end{figure}
-\end{landscape}
+%\end{landscape}
 \clearpage
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
+      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c} }
+      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
+\caption{XXX.}
+\label{fig:3DChannel_Isosurf}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-07-16 Papers/ViscousInstabilities/article_figure1.tex
working on the 3D

@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
+      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} } 
-      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
       \vspace{0.5cm}
       \hbox{\hspace{.5cm} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
-      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} }
+      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s } }
 \caption{$368513$ elements.}
-\label{fig:3DChannel_Isosurf}
+\label{fig:3DChannel_sat}
 \end{figure}

### 2017-07-16 Papers/ViscousInstabilities/article_figure1.tex
working on the 3D

@@
       \hbox{\hspace{.5cm} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} }
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_110.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
       \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }

### 2017-07-16 Papers/ViscousInstabilities/article_figure1.tex
working on the 3D

@@
 \hbox{\hspace{0.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100_1.pdf} 
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1.pdf} 
 }
@@
 }     
-\caption{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.91$s and (b)t=$4.3$s.}
+\caption{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.29$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_planes}

### 2017-07-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
working on the 3D

@@
 
-\subsection{Comparison of flow pattern with a different simulation set-up with and an additional inlet region.}\label{section:results_dinlet}
+\subsection{ \blue{The concept of the preferential flow path. A 3D case demonstration} }\label{section:results_dinlet}
 
 \medskip
-Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ has introduced into the formation.
-This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied.
-The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$.
-The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2})
-as the presence of this extra inlet increases the flow at the top layers.
-At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when VR=$100$,
-%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
-it is a test-case that can illustrate the higher, faster and more profound development of instabilities.
-Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio.
-A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$.
-No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes).
-The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$.
-Screenshots of the phase volume fraction and the development of fingers are shown in figures \ref{fig:4testcase_a}-\ref{fig:4testcase_b}.
+Figure \ref{fig:3DChannel_PermMesh} describes the permeability pattern as this is implied in a $3D$ domain.
+The surface on the left hand side of the domain is the area where fluid $1$ is injected with a velovity $ u=2.5 cm/sec $.
+The areas around the domain have a no-slip condition is implied (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
+The domain is constructed in such a way so as to be able tos capture the preferencial path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
 \medskip
-The first example is a simple comparison between two cases using fixed mesh and mobility ratios of $1$ and $10$ respectively. 
-%The aspect ratio of the $2D$ domain is 2 and it favors viscous fingering effects while temperature is not taken into account (assume isothermal environment) and gravity effects are negligible. 
-Fluid $1$ is initially injected from the left hand side with velocity $u_{inj}=1$.
-The domain is fully saturated with fluid $2$.
-At the outlet (right hand side) boundary pressure levels are set to zero while no slip boundary conditions are implied at the upper and lower part of the formation.
-Fixed time step sizes of $1 \times 10^{-3}$ for both the fixed meshes and the CFL number for this set of simulations is $0.5$.
-The $P_{1}DGP_{2}$ element type with piecewise linear description of veleocity within each element and quadratic pressure representation as part of the OCVFEM method along with the discontinuous Galerkin method are implied and composing the mesh.
-Saturation is located at the pressure nodes.
-Five different regions of 5 distinct absolute permeabilities (K) are introduced (fig.\ref{fig:5regions_domain}).
-The red square region is saturated with a $50\%-50\%$ mixture of both phase $1$ and $2$.
+Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
+While the saturation levels for phase $1$, as this is progress over time, remain between the values of $0.25-0.75$ there the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow.
+A comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
+Along with the individual steps as the also shown in figures \ref{fig:3DChannel_sat}(a)-(f), the evolution of the saturation front becomes more obvious.
+Based on the boundary conditions that implemented in this domain, the preferencial path of the flow can been seen.
+In a large scale enhanced oil-recovery operation this might have direct impact on the in-sity hydrocarbons located in lower permeability areas.
 
 \medskip
-Two general behaviors for the interface may occur: (i) If a more viscous fluid displaces a less viscous one or a less viscous displaces a more viscous with a low average velocity, the interface is flat; (ii) if a less viscous fluid displaces a more viscous one with intermediate values of the average velocity, single or multiple fingers will be observed.
+Thus macroscopic sweep efficiency is affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
+The permeability depends on the number, size and connectivity of the pores.
+An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
 
 \medskip 
-This test-case serves as a base case for comparison between mobility (or viscocity) ratios that differ by an order of magnitude.
-Viscocity is a measure of resistance, therefore a frictional property.
-In these test-cases the $\sigma$ term as this is described above contains the individual parameters related with wettability and contact angle while the porous surface is a fluid $2$ wetted surface.
-For mobility ratios below $5$ the injection front will uniformly develop as time progress (piston shape front) and no fingers are expexted.
-Instabilities will start to occur and will be more obvious for mobility ratios higher than $5$.
-Between two layers or two regions with different permeabilities, but both saturated with fluid $2$, fingers will be triggered because of the permeability differences on the interface of these layers.
-In between the porous cappilary pressure difference with curve the interface and will lead to the formation of fingers.
-In macroscopic scale the interface between the two fluid will become unstable, an uneven or fingered profile will be controlled by capilary pressure -acting in the scale of the pores- and therefore due to the overall surface tension difference between the two immiscible fluids the front will collapse.
-This is of major practical importance in the petroleum industry, environmental waste remediation, and subsurface hydrology and it is key to understanding the movement of large volumes of injection fluids into subsurface reservoirs.
-The relationships between the capillarity of a geologic system, and the saturation and permeability of the fluids has a direct bearing on the migration speed and reservoir sweep of hydrocarbons affected the productivity of an oil field.
-
-\medskip
-The macroscopic sweep efficiency is principally affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
-The permeability depends on the number, size and connectivity of the pores.
-This set of parameters is described by the $\sigma$ in the global mass balance equation (eq.\ref{global_mass_balance}).
-Including higher permeability zones also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
-
-\medskip 
-As can been seen so far in all the test-case illustrated, main differences can be found on the way the shape of fingering is developed.
-Adaptive meshes tend to display fingering easier because of the enhcanced and stronger resolution in the interface.
-Inside the high permeability square region there is an acceleration of the flow with the maximum value of it at the interface as this starts to develops at the back of this region and onwards.
-%At this point attention should be given to the recovery rates as they can be illustrated from fig.{\ref{fig:recoveryrates}}.
-The breaking point, also known as the point the two curves meet where beyond that water production will occur, is shifted towards the right as MR is increased.
+The evolution and results of the saturation front and the idea of preferential flow path in the domain is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
+For the same timesteps of the saturation front evolution an inside look on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
 

### 2017-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
-In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced.
-The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities.
+In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
+The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
 A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
-Viscosity ratio of the two fluids is set to 10.
+Viscosity ratio was set to 10.
 
@@
 Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
-In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeability at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
-The simulation performed with a fixed and relatively fine mesh
-Sharp permeability gradient triggered the onset of fingers' formation, as shown in
+In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
+The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$.
+In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh.
+In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead.
 
-\medskip
-Having already verified that model is working for the hele-shaw experimental test-cases, now a more complicated case will be introduced with regions of different geometrical domains and different permeabilities.
-Initial and boundary conditions are described in fig.\ref{fig:testcase_heter_domain}, while inlet velocity is $1$ on the left hand side, and the pressure is set to $0$ on the outlet.
-What is expected is a significant growth of fingers when comparing mobility ratios that differ an order of magnitude.
-%(fig.\ref{fig:1testcase})
-Figure \ref{fem_cv_represent_vr1_vr10} describes an initial comparison between the $VR=1$ and $VR=10$ case under the same domain, boundary and initial conditions and number of elements so as to underastand how the cross-flow in the upper layers can be developed compared with the fingers that will appear below.
-The purpose of these two cases was to verify that the model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.
-The next step is a comparison under the same mobility ratio of $10$, using the fixed and the adaptive mesh.
-For the fixed mesh we have $4600$ elements, but for the adaptive mesh we start with $400$ up to $600$, depends how fine we would like the mesh to be, and we reach up to $24000$.
-%Figure \ref{fig:testcase_heter_domain} gives a description of the domain that will be used.
+\subsection{3-D Channel Flows: Investigation of Preferential Flow Path and Formation of Fingers} \label{section:results_dinlet}
 
-\medskip
-Figures \ref{fig:2testcase_a}%\ref{fig:2testcase_b}, \ref{fig:2testcase_c} 
--\ref{fig:2testcase_d} give a summary of the simulation for different time-steps as these are described.
-In this set, the interfacial instability is becoming more profound as the flow develops.
-Based on these two cases so far, an initial relation between the quantitative and qualitative outcome of our simulations can be derived.
-Fingers will develop faster in areas where permeabilities are higher.
-This can be seen from the overall sharp increase of velocity magnitude during the injection of the fluid $1$.
-
-\subsection{ \blue{The concept of the preferential flow path. A 3D case demonstration} }\label{section:results_dinlet}
+\blue{(a) Little intro of the case; (b) set up what are the main issues (theory) of the simulations you are showing in this section; (c) then briefly describe what are the strategies to tackle these issues; (d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
 

### 2017-07-21 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
+The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
+This fact will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
 
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-
-\red{(KOSTAS: YOU HAVE REMOVED 1 SIMULATION HERE ... THEREFORE YOU NEED TO MAKE SURE THAT THE TEXT REFLECT THE NEW FIGURE'S CONFIGURATION!!) \blue{will work on it ASAP this evening}}
 

### 2017-07-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas
3D case updates

@@
 The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-This fact will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
+This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
 
@@
 
-\blue{(a) Little intro of the case; (b) set up what are the main issues (theory) of the simulations you are showing in this section; (c) then briefly describe what are the strategies to tackle these issues; (d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
+\blue{(a) Little intro of the case;} 
+The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions as these are decribed by figure \ref{fig:3DChannel_PermMesh}.
+
+\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section;}
+\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called
+viscous fingers. The geometrical evolution of these patterns provides good indications about the evolution of the penetration into a zone with a less viscous fluid.
+
+\blue{(c) then briefly describe what are the strategies to tackle these issues; }
+Capturing and tracking the  evolution of viscous fingers is important for the understanding the penetration process and fluid patterns that will be created.
+
+\blue{(d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
 

### 2017-07-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
3D case updates

@@
 
-\blue{(a) Little intro of the case;} 
+\blue{(a) Little intro of the case; }\\
 The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions as these are decribed by figure \ref{fig:3DChannel_PermMesh}.
 
-\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section;}
+\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
 \textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called
@@
 
-\blue{(c) then briefly describe what are the strategies to tackle these issues; }
-Capturing and tracking the  evolution of viscous fingers is important for the understanding the penetration process and fluid patterns that will be created.
+\blue{(c) then briefly describe what are the strategies to tackle these issues; }\\
+Capturing and tracking the evolution of fluid patterns is important for the understanding the penetration process.
 
-\blue{(d) then describe the numerical experiment w all BC and IC; (e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
-
-\medskip
+\blue{(d) then describe the numerical experiment w all BC and IC;}\\
 Figure \ref{fig:3DChannel_PermMesh} describes the permeability pattern as this is implied in a $3D$ domain.
@@
 
-\medskip
+\blue{(e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
 Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 

### 2017-07-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
3D case minor updates / description

@@
 \blue{(a) Little intro of the case; }\\
-The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions as these are decribed by figure \ref{fig:3DChannel_PermMesh}.
+The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
 
 \blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
-\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called
-viscous fingers. The geometrical evolution of these patterns provides good indications about the evolution of the penetration into a zone with a less viscous fluid.
-
-\blue{(c) then briefly describe what are the strategies to tackle these issues; }\\
-Capturing and tracking the evolution of fluid patterns is important for the understanding the penetration process.
+\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
+The geometrical evolution of these patterns provides good indications on capturing and tracking the fluid patterns.
 
@@
 Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
-While the saturation levels for phase $1$, as this is progress over time, remain between the values of $0.25-0.75$ there the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow.
-A comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
-Along with the individual steps as the also shown in figures \ref{fig:3DChannel_sat}(a)-(f), the evolution of the saturation front becomes more obvious.
+While the saturation levels for phase $1$, remain between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can been seen by the darcy velocity contours.
+Initially most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region.
+At this point a comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
+As the flow progress, in a $2D$ domain a finger formation will start to appear.
+This is triggerded initially cause of the permeability differences in the domain.
+In a $3D$ domain though, the same finger fomration does not look the same, as it is more a description of the preferential flow path that includes smaller fingers that will break out of the flow path.
+Two characteristic time steps are shown in figures \ref{fig:3DChannel_sat}(a)-(f), along with the evolution of the saturation front that now becomes more obvious.
 Based on the boundary conditions that implemented in this domain, the preferencial path of the flow can been seen.

### 2017-07-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
3D case updates and rewrite the conclusions

@@
 \blue{(a) Little intro of the case; }\\
-The last of the simulations is related with the effort to describe the finger evolution and the idea of the prefereable path using 3D domain with different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
+The last of the simulations is a $3$D domain that will help in the description of the finger evolution and the idea of the preferential path using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
 
 \blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
-\textit{Viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
-The geometrical evolution of these patterns provides good indications on capturing and tracking the fluid patterns.
+As already mentioned \textit{viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
+The geometrical evolution of these patterns provides good indications on capturing and tracking any discontinuities or instabilities in the flow front.
 
@@
 The surface on the left hand side of the domain is the area where fluid $1$ is injected with a velovity $ u=2.5 cm/sec $.
-The areas around the domain have a no-slip condition is implied (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
-The domain is constructed in such a way so as to be able tos capture the preferencial path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+In the areas around the domain a no-slip condition is implied (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
+The domain is constructed in such a way so as to be able to capture the preferencial path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
 \blue{(e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
-Figure \ref{fig:3DChannel_planes} give a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
-While the saturation levels for phase $1$, remain between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can been seen by the darcy velocity contours.
+Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
+While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can been seen by the darcy velocity contours.
 Initially most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region.
 At this point a comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
-As the flow progress, in a $2D$ domain a finger formation will start to appear.
+
+\medskip
+As the flow progress, in the $2D$ domain a finger formation will start to appear.
 This is triggerded initially cause of the permeability differences in the domain.
-In a $3D$ domain though, the same finger fomration does not look the same, as it is more a description of the preferential flow path that includes smaller fingers that will break out of the flow path.
-Two characteristic time steps are shown in figures \ref{fig:3DChannel_sat}(a)-(f), along with the evolution of the saturation front that now becomes more obvious.
-Based on the boundary conditions that implemented in this domain, the preferencial path of the flow can been seen.
-In a large scale enhanced oil-recovery operation this might have direct impact on the in-sity hydrocarbons located in lower permeability areas.
+In the $3D$ domain though, the same finger formation does not look the same, as it is more a description of the preferential flow path that may include smaller fingers which will break out of the flow.
+Figures \ref{fig:3DChannel_sat}(a)-(f) give a description of the preferable flow path in various time-steps alongside with the evolution of the saturation front that now becomes more obvious.
+Based on the boundary conditions that implemented, the preferencial path of the flow can been seen.
+In a large scale enhanced oil-recovery operation this might have direct impact on the in-situ hydrocarbons located in lower permeability areas.
 
@@
 
+\medskip
+At this point it is proper to review the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}).
+In all the previous cases, as surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
+As a result of shielding, one of these fingers will eventually outgrow the other and, will then spread to occupy the appropriate width of the domain ahead of it.
+Following this process, it reaches a width that is again unstable and the pattern repeats.
+So far shielding and spreading were dominating the flow but using this this domain and conditions the mechanics of tip-splitting along a front can be understood at least qualitatively.
+
 \section{Conclusions}\label{Section:Conclusion}
@@
 A number of different cases have been illustrated in Section \ref{section:results}.
-Starting from tested experimental cases and geometrical domains to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
-Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces on the developement of the flows.
-For immiscible displacements upon which only viscous and capillary forces are acting (being horizontal flow, gravity can be ignored), the expected displacement patterns are either stable front displacement or unstable front displacement.
-In the latter case the instability arises due to either capillary or viscous fingering depending on capillary number ($N_{c}$) but mainly on mobility ratio (MR or VR).
-If the mobility ratio is significantly less than $5$ (MR=$3$ has been used) , it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
+Starting from testing experimental cases and geometrical domains (Hele-shaw domain) to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
+Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces and fingering mechanisms on the developement of the flows.
+
+\medskip
+For immiscible displacements upon which only viscous and capillary forces are acting, the expected displacement patterns are either fully developed cross flow displacement or unstable front displacement.
+In the latter case the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but mainly is a fuction of viscocity ratio (\ie VR).
+If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
 On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
 Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
-Hence, the displacement form could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
-
-%\medskip
-%We have numerically computed the evolution of the initial condition and for various values of the viscosity contrast under the same initial conditions and surface tension.
-Even though the commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
-In this paper the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
+Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
 
 \medskip
-As usually seen for high viscosity contrast, the leading finger screens out the trailing by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
-At long times the large finger advances approximately at
-constant velocity. Results which question the evolution of fingers and the finger competition are those referring to the dynamic role of viscosity contrast.
+As usually seen for high viscosity contrast, there is a leading finger (tip splitting mechanism) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
+At long times the large finger advances approximately at in a constant flow rate.
+In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
+Commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
 
@@
 \item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-%\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-%\item[3.] The basis of the below argument is the flexibility and variance of the unstructured grid in time and space.
-%\item[4.] Production simulations run directly on the geological model without the need to upscale.\\
-
-\item[2.] The displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domain.
-The higher the mobility ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
-\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes.
-At the same time the basis of the argument above is the flexibility and variance of the unstructured grid in time and space.
-The domain used in these test-cases the development of the flow follow the linear tip-splitting finger behaviour.
-\item[4.] Properties such as porosity and saturation can be readily up-scaled using statistical methods, can be included in the element boundaries,  while production simulations run directly on the geological model without the need to upscale.
+\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
+The basis of the this argument is the flexibility and variance of the unstructured grid in time and space.
+\item[3.] Production simulations run directly on the geological model without the need to upscale.\\
 \end{enumerate}
 
-%\KCnote{Having confirmed that equal viscosity fluids do not finger into each other, a set of experiments were completed at different mobility ratios.
-Keeping both the thickness and the injection rate constant, it was observed that increasing the mobility ratio decreases the finger width, which subsequently leads to more fingers and subsequently more complexity at a given distance away from the injection point.
-Tip-splitting, a phenomenon in which the initial stage of fingers split into two or more new fingers, can also be observed at higher mobility ratios.}
+\medskip
+Regarding the flow characteristics and the mechanics of fingering formations,
+
+\begin{enumerate}
+\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from cross-section (\red{i want to say that in hele-shaw cells this can be seen from above, longitudinal section?
+or frame plan}) througout the Hele-shaw domains.
+\item[2.] Even though different permeability patterns will initially make the uniform front to collapse, it is the \textit{viscocity ratio} the key parameter and the capillary forces as these are related with surface tension that will eventually lead the flow instabilities.
+The higher the viscocity ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
+\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes. 
+\item[4.] Properties such as porosity and saturation can be readily up-scaled as they can be included in the element boundaries.
+The domains used in these test-cases have the ability to describe the fingering mechanism and the development of the flow \ie the latter case clearly describes the linear tip-splitting finger behaviour inside the domain.
+\end{enumerate}
 

### 2017-07-28 Papers/ViscousInstabilities/article_figure1.tex
working on the 3D
update
3D case updates and rewrite the conclusions

@@
 The domain is discretised with $5960$ \PN[1]{2} elements.
-\red{(ARE YOU SURE TIME IS CORRECT ??)} }
+}
 \label{fem_cv_represent_a}
@@
 \clearpage
+
+\begin{comment}
 %%%
@@
       \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
-\caption{$368513$ elements.}
+\caption{Evolution of saturation front and description of the preferable flow path in different times steps.
+The domain currently has $368513$ elements.
+In figure (a) an initial tip of the flow front can been seen, while as the time progress, in figure (f) the flow path has become more obvious.}
 \label{fig:3DChannel_sat}
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{$368513$ elements.}
+\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a partial visual isolation of the preferential path of the flow inside the domain.
+The aim was to manage and describe the individual finger patterns, as the flow develops, inside the domain.
+In particular, figures (c)-(f) give a detailed description of the finger that starts to break out of the front.}
 \label{fig:3DChannel_Isosurf}

### 2017-07-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
3D case updates and rewrite the conclusions

@@
 
-\subsection{3-D Channel Flows: Investigation of Preferential Flow Path and Formation of Fingers} \label{section:results_dinlet}
+\subsection{3-D channel flows} \label{section:results_3D}
 
-\blue{(a) Little intro of the case; }\\
-The last of the simulations is a $3$D domain that will help in the description of the finger evolution and the idea of the preferential path using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
+The last of the simulations introduces a $3$D domain that will showcase the idea of the preferential flow path and finger growth using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
+In large scale geological formations preferential flow allows much faster contaminant transport and creates significant consequences for ground-water quality.
 
-\blue{(b) set up what are the main issues (theory) of the simulations you are showing in this section; }\\
-As already mentioned \textit{viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
+\medskip
+As already mentioned in section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
 The geometrical evolution of these patterns provides good indications on capturing and tracking any discontinuities or instabilities in the flow front.
-
-\blue{(d) then describe the numerical experiment w all BC and IC;}\\
 Figure \ref{fig:3DChannel_PermMesh} describes the permeability pattern as this is implied in a $3D$ domain.
@@
 In the areas around the domain a no-slip condition is implied (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
-The domain is constructed in such a way so as to be able to capture the preferencial path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+The domain is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
-\blue{(e) then finally describe the results with a clear conclusion based on observation but backed by theory and/or physics!!}
-Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, in the beggining and just before the end of the simulation. 
-While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can been seen by the darcy velocity contours.
-Initially most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region.
+\medskip
+Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, during the beggining and just before the end of the simulation.
+While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can be given by the darcy velocity contours.
+In the beginning of the simulation most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region.
 At this point a comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
@@
 \medskip
-As the flow progress, in the $2D$ domain a finger formation will start to appear.
-This is triggerded initially cause of the permeability differences in the domain.
-In the $3D$ domain though, the same finger formation does not look the same, as it is more a description of the preferential flow path that may include smaller fingers which will break out of the flow.
-Figures \ref{fig:3DChannel_sat}(a)-(f) give a description of the preferable flow path in various time-steps alongside with the evolution of the saturation front that now becomes more obvious.
+In previous sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
+These flow instabilities were triggerded because of the permeability differences in the domain.
+Using the $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious.
+Figures \ref{fig:3DChannel_sat}(a)-(f) give a description of the preferable flow path in various time-steps alongside with the progression of the saturation front that now becomes more obvious.
 Based on the boundary conditions that implemented, the preferencial path of the flow can been seen.
-In a large scale enhanced oil-recovery operation this might have direct impact on the in-situ hydrocarbons located in lower permeability areas.
+Heterogeneity in the reservoir controls the spatial distribution of porosity and permeability.
+The permeability depends on the number, size and connectivity of the pores.
+An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows our test-cases to give a good approximation of the so called "thief zones".
 
 \medskip 
-Thus macroscopic sweep efficiency is affected by the heterogeneity in the reservoir which controls the spatial distribution of porosity and permeability.
-The permeability depends on the number, size and connectivity of the pores.
-An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels or layers in the set up of the model, allows our test-cases to give a good approximation of the so called "thief zones", something that is common in heterogeneous geological formations.
+The saturation front progress and the idea of preferential flow path is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
+For the same time-steps an inside view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
 
 \medskip
-The evolution and results of the saturation front and the idea of preferential flow path in the domain is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
-For the same timesteps of the saturation front evolution an inside look on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
-
-\medskip
-At this point it is proper to review the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}).
-In all the previous cases, as surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
-As a result of shielding, one of these fingers will eventually outgrow the other and, will then spread to occupy the appropriate width of the domain ahead of it.
+A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
+In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
+Through \textit{shielding} mechanism, one of these fingers will eventually outgrow the other and, will then spread (\textit{spreading}) to occupy the appropriate width of the domain ahead of it.
 Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but using this this domain and conditions the mechanics of tip-splitting along a front can be understood at least qualitatively.
+So far shielding and spreading were dominating the flow but using the current $3$D domain and because of the lack of high resolution, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
 
@@
 \begin{enumerate}
-\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from cross-section (\red{i want to say that in hele-shaw cells this can be seen from above, longitudinal section?
-or frame plan}) througout the Hele-shaw domains.
+\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from longitudinal section througout the Hele-shaw domains.
 \item[2.] Even though different permeability patterns will initially make the uniform front to collapse, it is the \textit{viscocity ratio} the key parameter and the capillary forces as these are related with surface tension that will eventually lead the flow instabilities.

### 2017-07-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-As already mentioned in section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of a characteristic pattern, called viscous fingers.
+As already mentioned in section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
 The geometrical evolution of these patterns provides good indications on capturing and tracking any discontinuities or instabilities in the flow front.
@@
 The surface on the left hand side of the domain is the area where fluid $1$ is injected with a velovity $ u=2.5 cm/sec $.
-In the areas around the domain a no-slip condition is implied (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
-The domain is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+No-slip conditions are implied around the domain (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
+The control volume is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
@@
 The permeability depends on the number, size and connectivity of the pores.
-An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows our test-cases to give a good approximation of the so called "thief zones".
+An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows the domain to give a good approximation of the so called "thief zones".
 
@@
 The saturation front progress and the idea of preferential flow path is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
-For the same time-steps an inside view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
 At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
@@
 A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
-In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as surface tension becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
+In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as interfacial surface tension (IFT) becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
 Through \textit{shielding} mechanism, one of these fingers will eventually outgrow the other and, will then spread (\textit{spreading}) to occupy the appropriate width of the domain ahead of it.
 Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but using the current $3$D domain and because of the lack of high resolution, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
+So far shielding and spreading were dominating the flow but, using the current $3$D domain, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
 

### 2017-08-07 Papers/ViscousInstabilities/article_figure1.tex
rerun the 5regions for 700 elements
3D updates and working on it kostas

@@
 %%%
+%\begin{figure}[ht]
+%\vbox{\vspace{-1.cm}
+%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
+%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
+%      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
+%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
+%      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
+%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
+%      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
+%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
+%      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
+%      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
+%\caption{\red{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 586 elements)} and {\it VR}=10.}
+%\label{fig:5regions_fixedmesh_coarse}
+%\end{figure}
+%\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
   \begin{figure}[ht]
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+\begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} } 
+      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
+      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
+\caption{Evolution of saturation front and description of the preferable flow path in different times steps.
+The domain at t=$0.29$s currently has $327253$ elements while the maximum number of elements as the adaptive mesh develops is $1242202$.
+In figure (a) an initial tip of the flow front can been seen, while as the time progress, in figure (f) the flow path has become more obvious.
+The advantage of adaptivity is that computational times has decreased significantly as less files have been created for the same solution time.}
+\label{fig:3DChannel_sat}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-08-08 Papers/ViscousInstabilities/article_figure1.tex
need to re-size the pics and put comments number of elements

@@
 
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\hspace{0.5cm}
+\includegraphics[width=0.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_end.pdf} 
+}
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (a)     
+}
+\hbox{\hspace{0.5cm}
+\includegraphics[width=0.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_end.pdf}
+}
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (b)      
+}
+}     
+\caption{\red{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.29$s and (b)t=$4.3$s.}
+\label{fig:3DChannel_planes}.}
+\end{figure}
+%\end{landscape}
+\clearpage
+
 %%%
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
+      \hbox{\includegraphics[width=.45\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
-      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
-      \vspace{0.5cm}
-      \hbox{\hspace{.5cm} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
-      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
-\caption{Evolution of saturation front and description of the preferable flow path in different times steps.
-The domain at t=$0.29$s currently has $327253$ elements while the maximum number of elements as the adaptive mesh develops is $1242202$.
-In figure (a) an initial tip of the flow front can been seen, while as the time progress, in figure (f) the flow path has become more obvious.
-The advantage of adaptivity is that computational times has decreased significantly as less files have been created for the same solution time.}
-\label{fig:3DChannel_sat}
+      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{-0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
+      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
+\caption{\red{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a partial visual isolation of the preferential path of the flow inside the domain.
+The aim was to manage and describe the individual finger patterns, as the flow develops, inside the domain.
+In particular, figures (c)-(f) give a detailed description of the finger that starts to break out of the front}.}
+\label{fig:3DChannel_sat_adapt}
 \end{figure}

### 2017-08-10 Papers/ViscousInstabilities/article_figure1.tex
I find these 3D figs really nice! working on the text to cite them

@@
 
-%%%%
-%%%%  FIGURE
-%%%%
-%\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\hspace{0.5cm}
-\includegraphics[width=0.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_end.pdf} 
-}
-\vspace{-12.0cm}
-\hbox{\hspace{6.0cm} (a)     
-}
-\hbox{\hspace{0.5cm}
-\includegraphics[width=0.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_end.pdf}
-}
-\vspace{-12.0cm}
-\hbox{\hspace{6.0cm} (b)      
-}
-}     
-\caption{\red{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.29$s and (b)t=$4.3$s.}
-\label{fig:3DChannel_planes}.}
-\end{figure}
-%\end{landscape}
-\clearpage
-
 %%%
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.45\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
+      \hbox{\includegraphics[width=.5\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
             \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
-      \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
-      \vspace{-0.5cm}
+      \hbox{\hspace{3.0cm} (a) t=0.29s \hspace{4.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{1.5cm}
       \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{\red{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a partial visual isolation of the preferential path of the flow inside the domain.
-The aim was to manage and describe the individual finger patterns, as the flow develops, inside the domain.
-In particular, figures (c)-(f) give a detailed description of the finger that starts to break out of the front}.}
+\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a description of the same flow path but now using an adaptive and unstructured mesh.
+The aim was to describe in greater detail the finger patterns, as the flow develops but also address the importance of a resolution, in this case the type of mesh that is used to capture these phenomena.}
 \label{fig:3DChannel_sat_adapt}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-4.cm}
+\vbox{\hspace{2.5cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{2.0cm} (a) fixed unstructured mesh of 322493 elements    
+}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{-2.0cm} (b) adaptive and unstructured mesh with a maximum of 1242202 elements at the end of the simulation    
+}
+}     
+\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.}
+\end{figure}
+%\end{landscape}
+\clearpage

### 2017-08-10 Papers/ViscousInstabilities/article_figure1.tex
I find these 3D figs really nice! working on the text to cite them

@@
 }     
-\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.}
+\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain. \red{perhaps we need to change the order?}}
 \end{figure}

### 2017-08-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
latest updates

@@
 
+%%%%%%%%%%%%%
 \subsection{3-D channel flows} \label{section:results_3D}
 
-The last of the simulations introduces a $3$D domain that will showcase the idea of the preferential flow path and finger growth using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
+The last of the simulations introduced is a $3$D domain that will showcase the idea of the preferential flow path and finger growth using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
 In large scale geological formations preferential flow allows much faster contaminant transport and creates significant consequences for ground-water quality.
@@
 As already mentioned in section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
-The geometrical evolution of these patterns provides good indications on capturing and tracking any discontinuities or instabilities in the flow front.
+The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.
 Figure \ref{fig:3DChannel_PermMesh} describes the permeability pattern as this is implied in a $3D$ domain.
 The surface on the left hand side of the domain is the area where fluid $1$ is injected with a velovity $ u=2.5 cm/sec $.
-No-slip conditions are implied around the domain (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain is the outlet.
+No-slip conditions are implied everywhere else (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain there is the outlet.
 The control volume is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
@@
 \medskip
-Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, during the beggining and just before the end of the simulation.
+Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, in times related to the beginning and just before the end of simulation.
 While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can be given by the darcy velocity contours.
@@
 \medskip
-In previous sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
-These flow instabilities were triggerded because of the permeability differences in the domain.
+In sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
+These flow instabilities were triggerded from the permeability differences in the domain.
 Using the $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious.
-Figures \ref{fig:3DChannel_sat}(a)-(f) give a description of the preferable flow path in various time-steps alongside with the progression of the saturation front that now becomes more obvious.
-Based on the boundary conditions that implemented, the preferencial path of the flow can been seen.
-Heterogeneity in the reservoir controls the spatial distribution of porosity and permeability.
+Figures \ref{fig:3DChannel_sat}(a)-(f) describe the flow path in various time-steps alongside with the progression of the saturation front that now becomes more obvious.
+Heterogeneity in the reservoir controls the spatial distribution of porosity ($\phi =0.2$ in the current case) and permeability.
 The permeability depends on the number, size and connectivity of the pores.
@@
 The saturation front progress and the idea of preferential flow path is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
+In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
 For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
@@
 Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but, using the current $3$D domain, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
+So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
 
+%%%%%%%%%%%%%
 \section{Conclusions}\label{Section:Conclusion}
@@
 \medskip
-As usually seen for high viscosity contrast, there is a leading finger (tip splitting mechanism) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
+As seen for high viscosity contrast, there is a leading finger (\textit{tip splitting mechanism}) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
 At long times the large finger advances approximately at in a constant flow rate.
-In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced.
-Commercial simulators provide the user with option of an unstructured type of mesh still they are not able to dynamically adapt the mesh as the simulation develops and they increase the computational cost as the saturation front changes slowly.
+In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced for all the $2D$ and $3D$ cases.
+Commercial simulators provide the user with option of an unstructured type of mesh, still they are not able to dynamically adapt the mesh where is needed and manage the computational cost more efficient.
 
@@
 \item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-\item[2.] Computational cost can be reduced because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-The basis of the this argument is the flexibility and variance of the unstructured grid in time and space.
+\item[2.] Computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
+The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
 \item[3.] Production simulations run directly on the geological model without the need to upscale.\\

### 2017-08-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
latest updates

@@
 
-\title{ \blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}}
+\title{ Numerical investigation of viscous flow instabilities through heterogeneous porous media.
+Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
 
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Viscous Instabilities \sep Mobility Ratio \sep Porous media \sep Finite Element Methods \sep Capillary number.
+ Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio \sep Preferential flowpath \sep Finite Element Methods \sep Capillary number \sep Unstructured domain \sep Mesh adaptivity.
 \end{keyword}

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 
-The last of the simulations introduced is a $3$D domain that will showcase the idea of the preferential flow path and finger growth using different permeability regions, as these are decribed in figure \ref{fig:3DChannel_PermMesh}.
-In large scale geological formations preferential flow allows much faster contaminant transport and creates significant consequences for ground-water quality.
+In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers, as decribed in Figure \ref{fig:3DChannel_PermMesh}.
+In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon production fields.
 
 \medskip
-As already mentioned in section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
+As mentioned in Section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
 The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.
-Figure \ref{fig:3DChannel_PermMesh} describes the permeability pattern as this is implied in a $3D$ domain.
-The surface on the left hand side of the domain is the area where fluid $1$ is injected with a velovity $ u=2.5 cm/sec $.
-No-slip conditions are implied everywhere else (\ie insulation, no exchange of material or Neumann boundary condition for mass transfer) while at the right hand side of the domain there is the outlet.
-The control volume is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section.
+The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velovity of 2.5 cm.s$^{-1}$.
+No-slip conditions are implied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
+The control volume is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from Figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
-In most simulations, the domain was initially fully saturated (\ie {\it in situ} hydrocarbons) with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
@@
 The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velovity of 2.5 cm.s$^{-1}$.
-No-slip conditions are implied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
-The control volume is constructed in such a way so as to be able to focus and capture the preferential path of flow as this can be seen from Figures \ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
+Initially, the domain was partially saturated with with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
+The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
 \medskip
-Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ darcy velocity, in times related to the beginning and just before the end of simulation.
+Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ Darcy velocity, in times related to the beginning and just before the end of simulation.
 While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can be given by the darcy velocity contours.

### 2017-08-11 Papers/ViscousInstabilities/article_figure1.tex
latest updates
Updates on Section 4.5

@@
 \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }
-      \hbox{\hspace{5.0cm} (a) permeability map }}
-\caption{3D channel flow. The domain contains 243056 \PN[1]{1} element-pairs.}
+      \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
+\caption{3D channel flow: permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
 \label{fig:3DChannel_PermMesh}
@@
 }     
-\caption{The XY and YZ plabes, this is a description of the Darcy velocity vectors for (a) t=$0.29$s and (b)t=$4.3$s.}
+\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.
+\red{(AS I MENTIONED BEFORE THE FIGURE SHOULD SHOW OVERLAPPING VELOCITY VECTORS ON FLUID SATURATION FIELD INSTEAD OF OVERLAPPING VELOCITY VECTORS ON VELOCITY FIELD!!!!
+PLEASE CHANGE IT!!
+}}
 \label{fig:3DChannel_planes}
@@
 \begin{figure}[ht] 
-\vbox{\vspace{-4.cm}
+\vbox{\vspace{-3.5cm}
 \vbox{\hspace{2.5cm}
@@
 }     
-\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain. \red{perhaps we need to change the order?}}
+\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.
+\red{perhaps we need to change the order between this figure and the \ref{fig:3DChannel_sat_adapt}?
+} }
 \end{figure}

### 2017-08-11 Papers/ViscousInstabilities/article_figure1.tex
Updates on Section 4.5

@@
       \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
-\caption{Evolution of saturation front and description of the preferable flow path in different times steps.
-The domain currently has $368513$ elements.
-In figure (a) an initial tip of the flow front can been seen, while as the time progress, in figure (f) the flow path has become more obvious.}
+\caption{3D channel flow: saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
+Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
+The domain contains 368513 \PN[1]{1} elements.}
 \label{fig:3DChannel_sat}
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a partial visual isolation of the preferential path of the flow inside the domain.
-The aim was to manage and describe the individual finger patterns, as the flow develops, inside the domain.
-In particular, figures (c)-(f) give a detailed description of the finger that starts to break out of the front.}
+\caption{3D channel flow: Isosurfaces for wetted phase saturatioh ranging from 0.45 and 0.60 at the same instants of time of Fig.~\ref{fig:3DChannel_sat}.
+Preferential flow pathway can be readily noticed in (b) and (f).
+Fingers' formation and growth can be clearly noticed in (b)-(e).
+The domain contains 368513 \PN[1]{1} elements.}
 \label{fig:3DChannel_Isosurf}

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section.
-The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velovity of 2.5 cm.s$^{-1}$.
+The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
 No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
-Initially, the domain was partially saturated with with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
+Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
 The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
@@
 \medskip
-Figure \ref{fig:3DChannel_planes} gives a comprehensive description of the contours of phase $1$ Darcy velocity, in times related to the beginning and just before the end of simulation.
-While the saturation level for phase $1$, remains between the values of $0.25-0.75$ the main difference between the figures \ref{fig:3DChannel_planes} (a) and (b) is the intensity of the flow as this can be given by the darcy velocity contours.
-In the beginning of the simulation most of the contours for phase $1$ are populated and achieve their higher values closer to the inlet region.
-At this point a comparison between the figures \ref{fig:3DChannel_planes}(a)-\ref{fig:3DChannel_sat}(a) and \ref{fig:3DChannel_planes}(b)-\ref{fig:3DChannel_sat}(f) as they both describe the darcy velocity contours and the saturation front for the same timesteps, is necesserary.
+Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown.
+Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not displaced.
 
 \medskip
-In sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
+In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
 These flow instabilities were triggerded from the permeability differences in the domain.

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown.
-Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not displaced.
+Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.
 
@@
 These flow instabilities were triggerded from the permeability differences in the domain.
-Using the $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious.
-Figures \ref{fig:3DChannel_sat}(a)-(f) describe the flow path in various time-steps alongside with the progression of the saturation front that now becomes more obvious.
-Heterogeneity in the reservoir controls the spatial distribution of porosity ($\phi =0.2$ in the current case) and permeability.
-The permeability depends on the number, size and connectivity of the pores.
+In $3D$ domain, difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious \red{(I AM NOT SURE IF I UNDERSTAND THIS SENTENCE ...
+YOU MAY WANT TO IMPROVE IT !!)}.
+Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more obvious \red{(TRY TO AVOID AS MUCH AS YOU CAN THE USE OF STRONG WORDS IN TECHNICAL WRITING ...
+SUCH AS 'OBVIOUS', 'GREAT', ' POWERFUL' ETC)}.
+Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.
+Permeability depends on the number, size and connectivity of the pores.
 An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows the domain to give a good approximation of the so called "thief zones".
+\red{(THIS LAST SENTENCE ('Permeability depends on ...') IS QUITE CONFUSING AND I AM NOT SURE WHAT YOU WANT TO SAY  OR ITS AIM/OBJECTIVE ...
+TRY TO REWRITE IT ...
+IS THIS A COMMON NAME -- 'THIEF ZONE', IN THE LITERATURE ?
+IF SO, GIVE REFERENCE).}
 
 \medskip 
-The saturation front progress and the idea of preferential flow path is followed by a more detail representation as this can be found in figure \ref{fig:3DChannel_Isosurf}.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in the isosurface shown in Fig.~\ref{fig:3DChannel_Isosurf}.
+However due to the relatively low mesh resolution, in particular above and below the central channel region,
+
 In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Figure XXX shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
+As it can be seen \red{(COMPLETE THESE PARAGRAPH WITH BRIEF COMMENTS ON THE ONGOING SIMULATION WRT LOW MESH RESOLUTION AND ITS IMPACT ON CAPTURING FLOW DYNAMICS AND FINGER FORMATION AND GROWTH IN PARTICULAR)}.
 
 \medskip
+Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
@@
 \medskip 
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in the isosurface shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-However due to the relatively low mesh resolution, in particular above and below the central channel region,
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
+However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was quite limited
 

### 2017-08-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates on Section 4.5

@@
 The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was quite limited
+However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
 

### 2017-08-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
kostas speed up do not rush

@@
 %% The amssymb package provides various useful mathematical symbols
+
 \usepackage{amssymb,amsmath,array}
 %The amsthm package provides extended theorem environments
+
 \usepackage{amsthm}
@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure XXX shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
-As it can be seen \red{(COMPLETE THESE PARAGRAPH WITH BRIEF COMMENTS ON THE ONGOING SIMULATION WRT LOW MESH RESOLUTION AND ITS IMPACT ON CAPTURING FLOW DYNAMICS AND FINGER FORMATION AND GROWTH IN PARTICULAR)}.
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
+As can been seen, the lower the resolution the more difficult is to capture the fingers formations.
+(\red{I think I did something here with the order of figures})
 
@@
 
+\medskip
 The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
@@
 These flow instabilities were triggerded from the permeability differences in the domain.
-In $3D$ domain, difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious \red{(I AM NOT SURE IF I UNDERSTAND THIS SENTENCE ...
-YOU MAY WANT TO IMPROVE IT !!)}.
-Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more obvious \red{(TRY TO AVOID AS MUCH AS YOU CAN THE USE OF STRONG WORDS IN TECHNICAL WRITING ...
-SUCH AS 'OBVIOUS', 'GREAT', ' POWERFUL' ETC)}.
+Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations.
+Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct.
 Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.
-Permeability depends on the number, size and connectivity of the pores.
-An on purpose implementation of significant high permeability zones (compared with the lower ones) also know as higher permeability channels, allows the domain to give a good approximation of the so called "thief zones".
-\red{(THIS LAST SENTENCE ('Permeability depends on ...') IS QUITE CONFUSING AND I AM NOT SURE WHAT YOU WANT TO SAY  OR ITS AIM/OBJECTIVE ...
-TRY TO REWRITE IT ...
-IS THIS A COMMON NAME -- 'THIEF ZONE', IN THE LITERATURE ?
-IF SO, GIVE REFERENCE).}
 
@@
 However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
-
 In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.

### 2017-08-22 Papers/ViscousInstabilities/article_figure1.tex
kostas speed up do not rush

@@
 \hbox{
-      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
-      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c.pdf}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c.pdf}}
 \vspace{0.cm}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b}
+\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b.pdf}
 \hspace{0.5cm}      
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b}}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D1600b.pdf}}
 \vspace{0.cm}
@@
 \hbox{
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b}
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b}
-      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b}}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D2700b.pdf}
+      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D4000b.pdf}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D7000b.pdf}}
 \vspace{0.cm}
@@
             \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D800Hb.pdf} }
-      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{6.cm} (b) t=0.24ss \hspace{4.cm} (c) t=0.37s}
+      \hbox{\hspace{2.0cm} (a) t=0.10s \hspace{6.cm} (b) t=0.24s \hspace{4.cm} (c) t=0.37s}
       \vspace{0.5cm}
@@
 \label{fig:HeleShawHeter_VR150}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX 
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.65\textwidth, height=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_50.pdf} 
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_500.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_1000.pdf} }
+      \hbox{\hspace{2.0cm} (a) t=0.07s \hspace{6.cm} (b) t=0.96s \hspace{4.cm} (c) t=2.0s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_1500.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_1800.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_2180.pdf} }
+      \hbox{\hspace{3.cm} (d) t=2.7s \hspace{3.cm} (e) t= 3.13s\hspace{4.cm} (f) t=3.42s }}
+\caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=150: snapshots of saturation profile.
+Permeability distribution used in this simulation was the same as shown in Fig.~\ref{fig:HeleShawHeter_VR10}a.
+The domain contains 3734 \PN[1]{2} element-pairs.}
+\label{fig:HeleShawHeter_VR150_coarse}
 \end{figure}
@@
 %%%
-%\begin{figure}[ht]
-%\vbox{\vspace{-1.cm}
-%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
-%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
-%      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
-%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
-%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
-%      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
-%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
-%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
-%      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
-%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
-%            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
-%      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-%      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
-%      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-%\caption{\red{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 586 elements)} and {\it VR}=10.}
-%\label{fig:5regions_fixedmesh_coarse}
-%\end{figure}
-%\clearpage
-
-%%%
-%%% FIGURE XXXXXX
-%%%
   \begin{figure}[ht]
@@
 
-\begin{comment}
-%%%
-%%% FIGURE XXXXXX
-%%%
-  \begin{figure}[ht]
-  \vbox{\vspace{-2.5cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D10velb.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350velb.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100velb.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700velb.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150velb.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000velb.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200velb.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500velb.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250velb.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field overlapped with Darcy velocity (in cm/s) through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.
-Colour scheme for saturation is the same as used in Fig.~\ref{fig:5regions_adaptmesh}.}
-\label{fig:5regions_adaptmeshvels}
-\end{figure}
-\clearpage
-\end{comment}
-
 %%%%
@@
 \clearpage
-
-\begin{comment}
-%%%
-%%% FIGURE
-%%%
-\begin{landscape}
-  \begin{figure}[ht]
-    \vbox{ 
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr1_fixed/mr1_fixed_2500.pdf} 
-            \includegraphics[width=.57\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (a) VR = 1}
-      \vspace{1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}
-            \includegraphics[width=.45\textwidth]{./Pics1/mr10_fixed/mr10_fixed_2500.pdf}
-            \includegraphics[width=.57\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf} }
-      \hbox{\hspace{8.0cm} (b) VR = 10  }}
-\caption{Initial model validation: snapshots of numerical simulations performed with VR=1 and VR=10.
-The domain contains $4678$ elements.
-\red{need to put his footnote here?
-"At this poing it is proper to mention that the white grid lines of the domain, as they appear in this set of figures and the rest are for visual purposes only and they are not related with mesh itslef"}}
-\label{fem_cv_represent_vr1_vr10}
-\end{figure}
-\end{landscape}
-\clearpage
-%%%
-%%%
-%%%
-\end{comment}
 
@@
 \clearpage
-
-\begin{comment}
-%%%%
-%%%%  FIGURE
-%%%%
-%\begin{landscape}
-\begin{figure}[ht] 
-\vbox{
-\hbox{\vspace{-5.0cm}
-\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf}
-\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
-}
-\hspace{-5.0cm}
-\hbox{\hspace{6.0cm} (a) \hspace{6.cm} (b)    
-}
-\hbox{\vspace{0.0cm}
-\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
-\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
-}
-\hspace{-5.0cm}
-\hbox{\hspace{6.0cm} (c) \hspace{6.cm} (d)     
-}
-}     
-\caption{The figures (a) t=$0.91$s and (b)t=$4.3$s give a description of the saturation front. }
-\label{fig:3DChannel_sat}
-\end{figure}
-%\end{landscape}
-\clearpage
-\end{comment}
 

### 2017-08-22 Papers/ViscousInstabilities/article_figure2.tex
kostas speed up do not rush

@@
 \vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_100_1.pdf} 
+\hbox{\hspace{0.5cm}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1.pdf} 
 }
-\vspace{0.0cm}
-\hbox{\hspace{10.0cm} (a)     
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (a)     
 }
-\hbox{\hspace{3.5cm}
+\hbox{\hspace{0.5cm}
 \includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
 }
-\vspace{0.0cm}
-\hbox{\hspace{10.cm} (b)      
+\vspace{-12.0cm}
+\hbox{\hspace{6.0cm} (b)      
 }
 }     
-\caption{Contours of Darcy velocity in XY and YZ planes for (a) t=$0.91$s and (b)t=$4.3$s.}
-\label{fig:3DChannel_darcy_vel}
+\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.
+\red{(AS I MENTIONED BEFORE THE FIGURE SHOULD SHOW OVERLAPPING VELOCITY VECTORS ON FLUID SATURATION FIELD INSTEAD OF OVERLAPPING VELOCITY VECTORS ON VELOCITY FIELD!!!!
+PLEASE CHANGE IT!!
+}}
+\label{fig:3DChannel_planes}
 \end{figure}
@@
 %%%%
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{
+\hbox{\vspace{-5.0cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
+}
+\hspace{-5.0cm}
+\hbox{\hspace{6.0cm} (a) \hspace{6.cm} (b)    
+}
+\hbox{\vspace{0.0cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
+}
+\hspace{-5.0cm}
+\hbox{\hspace{6.0cm} (c) \hspace{6.cm} (d)     
+}
+}     
+\caption{The figures (a) t=$0.91$s and (b)t=$4.3$s give a description of the saturation front. }
+\label{fig:3DChannel_sat}
+\end{figure}
+%\end{landscape}
+\clearpage
+\end{comment}
+
+%%%
+%%% FIGURE XXXXXX
+%%%
 \begin{landscape}
 \begin{figure}[ht]
-\vbox{
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_100.pdf} 
-}
-\vspace{0.0cm}
-\hbox{\hspace{10.0cm} (a)     
-}
-\hbox{\hspace{3.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{10.cm} (b)      
-}
-}     
-\caption{For the same time steps as in fig.\ref{fig:3DChannel_darcy_vel} there is a description of the saturation front in (a) t=$0.91$s and (b)t=$4.3$s.}
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} } 
+      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_110.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
+      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
+\caption{3D channel flow: saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
+Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
+The domain contains 368513 \PN[1]{1} elements.}
 \label{fig:3DChannel_sat}
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
+      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c.pdf} }
       \hbox{\hspace{2.0cm} (a) t=0.29s \hspace{6.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
       \vspace{0.5cm}
-      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
-            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
-            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c} }
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D400c.pdf} }
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{XXX.}
+\caption{3D channel flow: Isosurfaces for wetted phase saturatioh ranging from 0.45 and 0.60 at the same instants of time of Fig.~\ref{fig:3DChannel_sat}.
+Preferential flow pathway can be readily noticed in (b) and (f).
+Fingers' formation and growth can be clearly noticed in (b)-(e).
+The domain contains 368513 \PN[1]{1} elements.}
 \label{fig:3DChannel_Isosurf}
@@
 \clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+  \begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.5\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_30.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_60.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_90.pdf} }
+      \hbox{\hspace{3.0cm} (a) t=0.29s \hspace{4.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{1.5cm}
+      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_110.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_150.pdf}
+            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_288.pdf} }
+      \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
+\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a description of the same flow path but now using an adaptive and unstructured mesh.
+The aim was to describe in greater detail the finger patterns, as the flow develops but also address the importance of a resolution, in this case the type of mesh that is used to capture these phenomena.}
+\label{fig:3DChannel_sat_adapt}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-3.5cm}
+\vbox{\hspace{2.5cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_end.pdf} 
+}
+\vspace{0.0cm}
+\hbox{\hspace{2.0cm} (a) fixed unstructured mesh of 322493 elements    
+}
+\hbox{\hspace{2.5cm}
+\includegraphics[width=0.75\textwidth]{./Pics1/3D_Channel/3D_channel_sat_adapt_end.pdf}
+}
+\vspace{0.0cm}
+\hbox{\hspace{-2.0cm} (b) adaptive and unstructured mesh with a maximum of 1242202 elements at the end of the simulation    
+}
+}     
+\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.
+\red{perhaps we need to change the order between this figure and the \ref{fig:3DChannel_sat_adapt}?
+} }
+\end{figure}
+%\end{landscape}
+\clearpage

### 2017-09-08 Papers/ViscousInstabilities/article_figure1.tex
working on final changes

@@
 }     
-\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.
-\red{perhaps we need to change the order between this figure and the \ref{fig:3DChannel_sat_adapt}?
-} }
+\caption{This is a qualitative comparison at t=end of simulation, for bot the fixed and unstructured mesh used in the 3D domain.}
 \end{figure}

### 2017-09-08 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+        \hbox{\hspace{5.cm}
+            \includegraphics[width=\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Mesh_b} }
+      \vspace{.5cm} 
+         \hbox{\hspace{0.cm}
+             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_StreamLinesHoriz_b} 
+      \hspace{.5cm} 
+             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Isosurface_b} 
+            }}
+\caption{3D Channel: Text to come}
+\end{figure}
+\end{landscape}
+\clearpage

### 2017-09-08 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_0_ContourPlotSlice_b} \hspace{-.5cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_20_ContourPlotSlice_b}}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_60_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_120_ContourPlotSlice_b}}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_200_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_ContourPlotSlice_b}}
+}
+\caption{3D Channel: Text to come}
+\end{figure}
+%\end{landscape}
+\clearpage

### 2017-09-15 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \hbox{\hspace{0.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1.pdf} 
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1_1.pdf} 
 }
@@
 }     
-\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.
-\red{(AS I MENTIONED BEFORE THE FIGURE SHOULD SHOW OVERLAPPING VELOCITY VECTORS ON FLUID SATURATION FIELD INSTEAD OF OVERLAPPING VELOCITY VECTORS ON VELOCITY FIELD!!!!
-PLEASE CHANGE IT!!
-}}
+\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_planes}

### 2017-09-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
working on final changes
latest updates

@@
 As can been seen, the lower the resolution the more difficult is to capture the fingers formations.
-(\red{I think I did something here with the order of figures})
 
 \medskip
-Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Traditional numerical methods often rely on fixed git add manuscrip	mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.

### 2017-10-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \begin{equation}
-N_{C} = \frac{\mu U}{\gamma},
+N_{c} = \frac{\mu U}{\gamma},
 \label{eq:capillary_number}
@@
 \medskip
-As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) also known as \textit{viscocity ratio} (VR), is a key-parameter to assess the efficiency during fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 
-\noindent VR  is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
@@
 \noindent From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio,
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
 \begin{displaymath}

### 2017-10-30 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
minor changes

@@
 
+\medskip 
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
@@
 
+\medskip
 Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.

### 2017-11-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
minor updates
minor changes
minor corrections
change group name

@@
 \cortext[cor1]{Corresponding author.}
-\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
+\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
 \address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
@@
 The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
+Microscopic instabilities describe phenomena occurring locally, \eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}, whereas macroscopic instabilities involve two-phase flow systems \citep{bottoni_1992}.
+This paper focuses on microscopic instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).
 
@@
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these two fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
+As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly controlled by the mobility ratio (MR) between the displacing and the displaced fluids.
 Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.

### 2017-11-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
+Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
 

### 2017-11-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 \medskip 
-Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations with coupling mass terms (\ie density and saturation)xx.
 Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.

### 2017-12-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
+A comprehensive review of force balance at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}.
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).
+
+% \citet{adler_1988} described both microscopic- and macroscopic-scale instabilities in Darcy flows.
+Microscopic instabilities describe phenomena occurring locally \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}
 % Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-The first distinction should be made between microscopic and macroscopic instabilities.
+%The first distinction should be made between microscopic and macroscopic instabilities.
 Microscopic instabilities describe phenomena occurring locally, \eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}, whereas macroscopic instabilities involve two-phase flow systems \citep{bottoni_1992}.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
 
 \medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations with coupling mass terms (\ie density and saturation)xx.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phase) with coupling mass terms (\ie density and saturation) appearing in both sets.
 Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 \medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve flow dynamics in complex geometries.
 %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 \medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve flow dynamics in complex geometries.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
 %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
@@
 Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
@@
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
 These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
@@
 In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical investigation of formation and evolution of viscous fingers in heterogeneous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
 A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements whereas pressure is represented by $m^{\text{th}}$-order polynomials that are continuous across the elements.
+A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
@@
 
-\medskip
 The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha} \hspace{1cm} \text{ with } x_{i}\in\Omega, t>0, \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha} \hspace{1cm} \text{ with } x_{i}\in\Omega, t>0,\label{eqn:saturation_eqn}
 \end{eqnarray}
@@
 \medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations (Eqn.~\ref{eqn:darcy_eqn}).
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
@@
 \medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time \citep{gomes_book_2012}.
 Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
@@
 This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
 Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements whereas pressure is represented by $m^{\text{th}}$-order polynomials that are continuous across the elements.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.%, in which velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements whereas pressure is represented by $m^{\text{th}}$-order polynomials that are continuous across the elements.
 A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 where $\mathcal{N}_{p}$ denotes the number of phases.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both control volume (CV) and finite element (FE) spaces.
 
@@
 %%%%%%%%%%%%%%%
+\medskip
+The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
+In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
+Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
 
@@
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
+The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively.
+Each component of the weak form of the extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
+\begin{eqnarray}
+  \sum\limits_{E} \left.
+\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
++ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
+  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
+                   \label{force-semi-disc} 
+\end{eqnarray} 
+where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
+The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$.
+This term vanishes when a continuous formulation is used to discretise the pressure field.
+The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
+
 %\begin{displaymath}
@@
 Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time \citep{gomes_book_2012}.
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time \citep{gomes_book_2012}.
 Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
-
-\medskip
-This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+\label{global_mass_balance}
+\end{eqnarray}
+%\medskip %Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
 %Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
@@
 %\end{equation}
-
-\noindent Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+\noindent
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
 $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
+In addition to the numerical scheme above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
 This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 As mentioned above viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates and the impact of capillary number ($N_{c}$),
+\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
 
 \begin{equation}
-N_{c} = \frac{\mu U}{\gamma},
+N_{c} = \frac{\mu U}{\gamma}.
 \label{eq:capillary_number}
@@
 
-\noindent In Eqn.
-\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
-
-\medskip
+\noindent In Eqn.~\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
 In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
+This experimental apparatus enables instability to be qualitatively verified and simplifies the problem of flow in both porous and non-porous media.
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
 For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.

### 2017-12-02 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
+For a Hele-Shaw cell of a given size the flow development only depends on the capillary number.
 Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
@@
 \medskip 
-In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section \ref{section:results_homo_hete}.
+In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
@@
 \begin{equation} 
-\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
+\Delta P= - \gamma \nabla\cdot\hat{n}. 
 \label{eq:pressure_dif} 
@@
 \medskip
-As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 
-\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+\noindent MR is a function not only of fluids' viscosity, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
@@
   \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
 \end{eqnarray}

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical scheme above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
-This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
+The discretised global mass and force balance equations (Eqns.~\ref{force-semi-disc}-\ref{global_mass_balance}) are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
+The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
 
@@
 \medskip 
-All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
 An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
+An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.

### 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
updates
small changes
should i mention something about the last 2 sets of figures?
minor comment/ question on figures
change group name

@@
 \vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
-\caption{This is a graphical representation of two different element types.
-Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
+\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=250 
+\hbox{\hspace{4.5cm} (b) flow at t=25
 }
@@
 }}     
-\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec.
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
 The domain is discretised with $5960$ \PN[1]{2} elements.
@@
 \hbox{\hspace{0.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1_1.pdf} 
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1_1.pdf} 
 }
@@
 \hbox{\hspace{0.5cm}
-\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_490_1.pdf}
+\includegraphics[width=1.0\textwidth]{./Pics1/3D_Channel/3D_channel_darcy_vel_planes_30_1_1.pdf}
 }
@@
 }
-\caption{3D Channel: Text to come}
+\caption{3D Channel: Text to come \red{should i mention something here? something qualitative}}
 \end{figure}

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
+\red{The permeability spatial distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be led to the high permeability region.
+This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.} \green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ...
+ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}
 
 \medskip
-Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+A numerical simulation was also performed in modified conditions to assess model behaviour at {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+\red{THIS PARAGRAPH ONLY MAKE SENSE IF YOU ARE SHOWING THE RESULTS OF VR =10.
+HOWEVER, FIGS 4b-c REFER TO VR=1, WHICH, BY THE WAY, HAS NO COMMENT IN THE PREVIOUS PARAGRAPH ...
+IN THIS SECTION YOU \underline{\bf MUST} TALK ABOUT CROSS-FLOW !!}
 
@@
 \medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid, \ie {\it in situ} hydrocarbons.
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
 
@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=$10$.
+However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.
 
@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
-
+They conducted a sensitivity study to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,% \citep{guan_2003},
 \begin{equation}   
@@
 \end{equation}  
-
-\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
+Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
 
@@
 
-\medskip
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.

### 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
change group name

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b.pdf}
+\hbox{\includegraphics[width=.8\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b.pdf}
 \hspace{0.5cm}      
@@
 \end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{figure}[ht]
+\vbox{
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b.pdf}}
+\hbox{\hspace{0.25cm} (a) {\it VR}=10 (homogeneous) \hspace{1.5cm} (b) {\it VR}=150 (homogeneous) }
+\vspace{0.5cm}
+\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b.pdf}
+       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b.pdf}}
+\hbox{\hspace{0.25cm} (c) {\it VR}=10 (heterogeneous) \hspace{1.5cm} (d) {\it VR}=150 (heterogeneous) }
+}
+\caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
+Top and bottom rows describe simulations performed with constant \textit{i.e.
+homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (i.e.
+heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm (\textit{VR}=$10$ and \textit{VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
+Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}
+\label{fig:homoheleshaw_VN10_VN150}
+\end{figure}
 \clearpage
@@
 \end{landscape}
-\clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{figure}[ht]
-\vbox{
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_W2b.pdf}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D5003_W2b.pdf}}
-\hbox{\hspace{0.25cm} (a) {\it VR}=10 (homogeneous) \hspace{1.5cm} (b) {\it VR}=150 (homogeneous) }
-\vspace{0.5cm}
-\hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D11000_W2b.pdf}
-       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D6500_W2b.pdf}}
-\hbox{\hspace{0.25cm} (c) {\it VR}=10 (heterogeneous) \hspace{1.5cm} (d) {\it VR}=150 (heterogeneous) }
-}
-\caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
-Top and bottom rows describe simulations performed with constant \textit{i.e.
-homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (i.e.
-heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
-Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm (\textit{VR}=$10$ and \textit{VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
-Results for homogeneous cases are in good agreement with values obtained from \citet{guan_2003}'s analytic solution.}
-\label{fig:homoheleshaw_VN10_VN150}
-\end{figure}
 \clearpage

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases (Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
 
-\medskip
-Figures~\ref{fig:HeleShawHeter_VR10} and ~\ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
+Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
 In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150, Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}).
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

--- 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- Fig.~\ref{fig:homoheleshaw_VN10_VN150}c-d and Table~\ref{table:Heleshaw}).
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
-As can been seen, the lower the resolution the more difficult is to capture the fingers formations.
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
+As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
 
 \medskip
-Traditional numerical methods often rely on fixed git add manuscrip	mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
 Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
@@
 \medskip
-Traditional numerical methods often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Mesh adaptivity methods have been extensively used by the computational geo-fluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 \medskip
-Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
 Mesh adaptivity methods have been extensively used by the computational geo-fluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the computational geo-fluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 
-\medskip
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
@@
 
-\medskip
 The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
 The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
@@
 
-\medskip
 Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
-A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
+A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
 Viscosity ratio was set to 10.
@@
 In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers, as decribed in Figure \ref{fig:3DChannel_PermMesh}.
-In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon production fields.
+In large scale geological formations preferential flow may allow fast contaminant transport (therefore creating significant consequences for groundwater quality) and low recovery rate (in hydrocarbon production fields).
 

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 
-\medskip
-As mentioned in Section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
+As mentioned in Section \ref{section:ViscousInstabilities}, viscous instabilities is characterised by the formation of flow patterns, called viscous fingers.
 The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

@@
 
-In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers, as decribed in Figure \ref{fig:3DChannel_PermMesh}.
+In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers.
 In large scale geological formations preferential flow may allow fast contaminant transport (therefore creating significant consequences for groundwater quality) and low recovery rate (in hydrocarbon production fields).
 
-As mentioned in Section \ref{section:ViscousInstabilities}, viscous instabilities is characterised by the formation of flow patterns, called viscous fingers.
-The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.
-Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section.
-The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
-No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
-Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
-The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
+The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.
+Figure \ref{fig:3DChannel_PermMesh} shows initial permeability distribution for the simulations described in this section.
+The surface on the left-hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
+No-flux boundary conditions are applied to all borders, except the right-hand side (inlet) and the left-hand side (outflow).
+Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was displaced by a pure (wetting) fluid.
+The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to capture preferential flow pathways, \ie regions with larger permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as demonstrated in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
-\medskip
-Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown.
+Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting fluid saturation are shown.
 Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{3-D channel flows} \label{section:results_3D} 
+In large scale geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) and low hydrocarbon recovery rates (in oil/gas exploration fields).
+In this section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
 
-In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers.
-In large scale geological formations preferential flow may allow fast contaminant transport (therefore creating significant consequences for groundwater quality) and low recovery rate (in hydrocarbon production fields).
-
-As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
+%As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
 The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.
-Figure \ref{fig:3DChannel_PermMesh} shows initial permeability distribution for the simulations described in this section.
+Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
+No-flux boundary conditions are applied to all borders, except the right-hand (inlet) and the left-hand sides (outflow).
+Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
+The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+
 The surface on the left-hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
-No-flux boundary conditions are applied to all borders, except the right-hand side (inlet) and the left-hand side (outflow).
-Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was displaced by a pure (wetting) fluid.
-The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to capture preferential flow pathways, \ie regions with larger permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as demonstrated in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
-
-The surface on the left-hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
+The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{3-D channel flows} \label{section:results_3D} 
-In large scale geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) and low hydrocarbon recovery rates (in oil/gas exploration fields).
-In this section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
+In geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in oil/gas exploration fields).
+In this Section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
 
@@
 
-\medskip
-In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
-These flow instabilities were triggerded from the permeability differences in the domain.
-Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations.
+In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and braching were triggerded by domain heterogeneity represented by permeability differences.
+Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
+%In 3D simulations, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations.
 Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct.
 Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.
-
-\medskip 
 The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
-In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
+However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}.
 For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
@@
 Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
+So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.\red{WHAT IS THE LINKAGE BETWEEN THIS PARAGRAPH AND THE REMAINING OF THE SECTION?}
 

### 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
       \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
-\caption{3D channel flow: permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
+\caption{3D channel flow (fixed mesh): permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
 \label{fig:3DChannel_PermMesh}
@@
 }     
-\caption{3D channel flow: XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.}
+\caption{3D channel flow (fixed mesh): XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_planes}
@@
       \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
-\caption{3D channel flow: saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
+\caption{3D channel flow (fixed mesh): saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
 Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{3D channel flow: Isosurfaces for wetted phase saturatioh ranging from 0.45 and 0.60 at the same instants of time of Fig.~\ref{fig:3DChannel_sat}.
+\caption{3D channel flow (fixed mesh): Isosurfaces for wetted phase saturatioh ranging from 0.45 and 0.60 at the same instants of time of Fig.~\ref{fig:3DChannel_sat}.
 Preferential flow pathway can be readily noticed in (b) and (f).
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{For the same time steps as these are shown in figure \ref{fig:3DChannel_sat} there is a description of the same flow path but now using an adaptive and unstructured mesh.
-The aim was to describe in greater detail the finger patterns, as the flow develops but also address the importance of a resolution, in this case the type of mesh that is used to capture these phenomena.}
+\caption{3D channel flow (adaptive mesh): numerical simulation was performed with the smae boundary and initial conditions as in Figs.~\ref{fig:3DChannel_PermMesh}-\ref{fig:3DChannel_Isosurf} with an adaptive mesh.
+Flow pathway is very similar to the one shown in Fig.~\ref{fig:3DChannel_sat}.}
 \label{fig:3DChannel_sat_adapt}
@@
 \clearpage
+\end{comment}
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_0_ContourPlotSlice_b} \hspace{-.5cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_20_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(a)\hspace{9cm}(b)}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_60_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_120_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(c)\hspace{9cm}(d)}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_200_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(e)\hspace{9cm}(f)}
+}
+    \caption{3D Channel (adaptive mesh):  XY and YZ planes showing wetting fluid saturation overlapped with Darcy velocity vectors at  (a) 0.00, (b) 0.09, (c) 0.71, (d) 1.75, (e) 2.47 and (f) 3.78s.
+Colour scheme for saturation profile is the same as used in Fig.~\ref{fig:3DChannel_sat_adapt}.}
+\end{figure}
+%\end{landscape}
+  \clearpage
 
@@
 \clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-%\begin{landscape}
-  \begin{figure}[ht] 
-    \vbox{\vspace{0.cm}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_0_ContourPlotSlice_b} \hspace{-.5cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_20_ContourPlotSlice_b}}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_60_ContourPlotSlice_b}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_120_ContourPlotSlice_b}}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_200_ContourPlotSlice_b}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_ContourPlotSlice_b}}
-}
-\caption{3D Channel: Text to come \red{should i mention something here? something qualitative}}
-\end{figure}
-%\end{landscape}
-\clearpage

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}.
-For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from XX to XX tetrahedral \PNDG[1]{1} element-pairs.
+Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
 At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.

### 2017-12-12 Papers/ViscousInstabilities/article_figure1.tex
updates
correcting figure 2B
correcting figure 2B

--- 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
@@
 \centering
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
-\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
+\caption{This is a graphical representation of two different element types.
+Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=25
+\hbox{\hspace{4.5cm} (b) flow at t=250 
 }
@@
 }}     
-\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec.
 The domain is discretised with $5960$ \PN[1]{2} elements.

### 2017-12-12 Papers/ViscousInstabilities/article_figure1.tex
2B changed

--- 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
@@
 Colour scheme for saturation profile is the same as used in Fig.~\ref{fig:3DChannel_sat_adapt}.}
+\label{fig:3DChannel_satvel_XYplanes_adapt}
 \end{figure}
@@
 \caption{3D Channel: Text to come}
+\label{fig:3DChannel_satvel_XYplanes_adapt}
 \end{figure}

### 2017-12-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
minor corrections

--- 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \cortext[cor1]{Corresponding author.}
-\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
+\address[UoA]{Fluids \& Structures Group, School of Engineering, University of Aberdeen, UK}
 \address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
@@
 Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of force balance at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).
-
-% \citet{adler_1988} described both microscopic- and macroscopic-scale instabilities in Darcy flows.
-Microscopic instabilities describe phenomena occurring locally \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}
+A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
 % Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-%The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, \eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}, whereas macroscopic instabilities involve two-phase flow systems \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or \textit{viscous fingering}, Section \ref{section:ViscousInstabilities}).
+The first distinction should be made between microscopic and macroscopic instabilities.
+Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
+This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
 
@@
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+As water and oil interacts, the interface between these two fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
 
 \medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phase) with coupling mass terms (\ie density and saturation) appearing in both sets.
+Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media.
 Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 
 \medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
 %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
@@
 Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
@@
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
 These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
@@
 In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical investigation of formation and evolution of viscous fingers in heterogeneous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.%, in which velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements whereas pressure is represented by $m^{\text{th}}$-order polynomials that are continuous across the elements.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
@@
 
+\medskip
 The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha} \hspace{1cm} \text{ with } x_{i}\in\Omega, t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha} \hspace{1cm} \text{ with } x_{i}\in\Omega, t>0,\label{eqn:saturation_eqn}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
 \end{eqnarray}
@@
 where $\mathcal{N}_{p}$ denotes the number of phases.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both control volume (CV) and finite element (FE) spaces.
 
@@
 %%%%%%%%%%%%%%%
-\medskip
-The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
-In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
-Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
 
 \medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations (Eqn.~\ref{eqn:darcy_eqn}).
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively.
-Each component of the weak form of the extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
-\begin{eqnarray}
-  \sum\limits_{E} \left.
-\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
-+ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
-  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
-                   \label{force-semi-disc} 
-\end{eqnarray} 
-where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
-The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$.
-This term vanishes when a continuous formulation is used to discretise the pressure field.
-The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
-
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
 %\begin{displaymath}
@@
 \medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time \citep{gomes_book_2012}.
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
 Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
-Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
-%\medskip %Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+
+\medskip
+This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
+Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
+%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
 %Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
@@
 %\end{equation}
-\noindent
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+
+\noindent Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+\label{global_mass_balance}
+\end{eqnarray}
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
 $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-The discretised global mass and force balance equations (Eqns.~\ref{force-semi-disc}-\ref{global_mass_balance}) are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
-The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
+In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
+This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
 
@@
 As mentioned above viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
+\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates and the impact of capillary number ($N_{c}$),
 
 \begin{equation}
-N_{c} = \frac{\mu U}{\gamma}.
+N_{c} = \frac{\mu U}{\gamma},
 \label{eq:capillary_number}
@@
 
-\noindent In Eqn.~\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
+\noindent In Eqn.
+\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
+
+\medskip
 In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-This experimental apparatus enables instability to be qualitatively verified and simplifies the problem of flow in both porous and non-porous media.
+This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size the flow development only depends on the capillary number.
+More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
 Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
@@
 \medskip 
-In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
+In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section \ref{section:results_homo_hete}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
@@
 \begin{equation} 
-\Delta P= - \gamma \nabla\cdot\hat{n}. 
+\Delta P= - \gamma \; \nabla \; \cdot \; \hat{n}. 
 \label{eq:pressure_dif} 
@@
 \medskip
-As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
@@
 
-\noindent MR is a function not only of fluids' viscosity, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
@@
   \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
 \end{eqnarray}
@@
 \medskip 
-All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
+All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-\red{The permeability spatial distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be led to the high permeability region.
-This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.} \green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ...
-ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}
+The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
+This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
 
 \medskip
-A numerical simulation was also performed in modified conditions to assess model behaviour at {\it VR}=10.
+Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-\red{THIS PARAGRAPH ONLY MAKE SENSE IF YOU ARE SHOWING THE RESULTS OF VR =10.
-HOWEVER, FIGS 4b-c REFER TO VR=1, WHICH, BY THE WAY, HAS NO COMMENT IN THE PREVIOUS PARAGRAPH ...
-IN THIS SECTION YOU \underline{\bf MUST} TALK ABOUT CROSS-FLOW !!}
 
@@
 \medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid, \ie {\it in situ} hydrocarbons.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
 
@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.
+However, formation of fingers can be readily noticed at early stages of the simulation conducted with {\it VR}=$10$.
 
@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-They conducted a sensitivity study to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,% \citep{guan_2003},
+A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
+
 \begin{equation}   
@@
 \end{equation}
-Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
+
+\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
 
@@
 
+\medskip
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases (Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases.
 
-Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- Fig.~\ref{fig:homoheleshaw_VN10_VN150}c-d and Table~\ref{table:Heleshaw}).
+\medskip
+Figures \ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
@@
 
+\medskip
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
-As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
+As can been seen, the lower the resolution the more difficult is to capture the fingers formations.
 
 \medskip
-Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+Traditional numerical methods often rely on fixed git add manuscrip	mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
+Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
@@
 
+\medskip
 The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
 The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
@@
 
+\medskip
 Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
-A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
+The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
+A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
 Viscosity ratio was set to 10.
@@
 \subsection{3-D channel flows} \label{section:results_3D}
-In large scale geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) and low hydrocarbon recovery rates (in oil/gas exploration fields).
-In this section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
 
-%As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
-The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.
-Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
-No-flux boundary conditions are applied to all borders, except the right-hand (inlet) and the left-hand sides (outflow).
-Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers, as decribed in Figure \ref{fig:3DChannel_PermMesh}.
+In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon production fields.
 
-Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting fluid saturation are shown.
+\medskip
+As mentioned in Section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
+The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.
+Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section.
+The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
+No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
+Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
+The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+
+\medskip
+Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown.
 Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\title{ Numerical investigation of viscous flow instabilities through heterogeneous porous media.
+\title{ Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media}%.
 Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
@@
 \cortext[cor1]{Corresponding author.}
-\address[UoA]{Fluids \& Structures Group, School of Engineering, University of Aberdeen, UK}
+\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
 \address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
+  %% Tittle was too long and 'Advantages and limitations unstructured and adaptive meshes' would mean a full numerical analysis on these 2 issues ...
+we haven't fully studied flows in either  unstructured / structured or adaptive / fixed meshes ...
 
@@
 $\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of
-\begin{displaymath}
-\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
-\end{displaymath}
-where $\mathcal{N}_{p}$ denotes the number of phases.
+$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+%\begin{displaymath}
+%\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
+%\end{displaymath}
+%where $\mathcal{N}_{p}$ denotes the number of phases.
 

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
-This numerical formulation is fully described by \citet{gomes_2017}\citep[see also][]{salinas2015,adam_2016}.
+This numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
 
@@
 \medskip
-Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
+In oil exploration, viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations, therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than the \textit{in situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
 
@@
 \end{equation}
-
-\noindent In Eqn.
-\ref{eq:capillary_number}, $\mu$ is the viscosity of the fuid that initially fills the Hele-Shaw cell, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
+where $\mu$ is the viscosity of the fuid, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
 
 \medskip
-In the Hele-Shaw cell, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-This experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
+In Hele-Shaw cells, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
+The experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cell (also know as Saffman $\&$ Taylor problem).
+More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
 For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987}, \citet{tabeling_1987} and others agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
+Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
 
@@
 Pressure differences acting on the interface produces a net pressure force,
-
 \begin{equation} 
@@
 
-\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids.
-With $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
+\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
 
@@
 One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a (critical) width that is again unstable and splits again, and the pattern repeats itself.
+In the process, the finger reaches a critical width that is again unstable and splits again, and the pattern repeats itself.
 Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
@@
 \subsection{Initial Model Validation}\label{section:results_validation}
-Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrates the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
+Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
 The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1).

### 2017-12-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-This will cause difficulties for numerically solving fluid flows in heterogeneous porous media.
+\green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ...
+ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}
 
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+\red{KOSTAS ...
+COULD YOU REVIEW THIS SECTION ...
+IT INITIALLY REFERS TO VR=1 AND THEN TO VR=10 ...
+BUT IT IS NOT CLEAR IF THE PLOTS IN FIG 4 REFER TO VR1 OR VR10 ...}
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-  \title{ Numerical Investigation of Viscous Flow Instabilities in Heterogeneous Porous Media}%.
+  \title{ Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media}%.
 Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
@@
 \section{Introduction}\label{section:intro}
-\medskip
 Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
@@
 
-\medskip
 %Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
-Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}.
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
+%Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
 A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
@@
 SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-The first distinction should be made between microscopic and macroscopic instabilities.
+%The first distinction should be made between microscopic and macroscopic instabilities.
 Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
@@
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these two fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and, may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly governed by the mobility ratio (MR) between the displacing and the displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc.
+As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
 
 \medskip 
-Conservation of mass and Darcy's law are the governing equations that describe flow dynamics in porous media.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
 Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadilateral (2-D) and hexahedral (3-D) grid cells of low quality~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM schemes result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
 %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
@@
 
-\medskip
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces.
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
 These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}.
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical investigation of formation and evolution of viscous fingers in heterogeneous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
+%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\;\;\; x_{i}\in\Omega, t>0 \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\;\;\; x_{i}\in\Omega, t>0\label{eqn:saturation_eqn}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
 \end{eqnarray}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
 %\begin{displaymath}
@@
 
-\medskip
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
+In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
+Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
+
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively -- note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
+Each component of the weak form of the extended Darcy equation is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
+\begin{eqnarray}
+  \sum\limits_{E} \left.
+\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
++ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
+  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
+                   \label{force-semi-disc} 
+\end{eqnarray} 
+where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
+The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$ $\left(\text{consistent with the \PNDG[n]{m} element-pairs}\right)$.
+This term vanishes when a continuous formulation is used to discretise the pressure field $\left(\text{with \PN[n]{m} element-pairs}\right)$.
+The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
+%Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
@@
 \medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, permeability is piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function and with the $\theta$-method in time as described by \citet{gomes_book_2012}.
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
 Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+\label{global_mass_balance}
+\end{eqnarray}
 
-\medskip
-This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+%This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
 In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
@@
 %\end{equation}
-
-\noindent Equation~\ref{eqn:saturation_eqn} is discretised in time and space using the $\theta$-method. Summing over all phases yields the global mass balance equation,
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
+\noindent
 where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
 $\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-In addition to the numerical schemes above the discretised global mass and force balance equations are solved using a multigrid-like approach \citep[see][]{pavlidis2016}.
-This numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
+
+\medskip
+The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
+The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-\medskip
 Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
+The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations.
+In this application, volumetric sweep efficiency \red{(KOSTAS: MAY BE YOU SHOULD ADD ONE SENTENCE DEFINING/EXPLAINING ``SWEEP EFFICIENCY'' AND ``BREAKTHROUGH'' ...
+AND HOW THEY ARE RELATED.)} may be reduced and early breakthrough may occur \citep{riaz_2004, tavassoli_2015}, leading to low oil production.
+During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
 
-Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain.
+\medskip
+Flow instabilities may be due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain.
 %\red{For example, during water flooding, efficiency is related with capillary number.
@@
 When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
+\red{(KOSTAS: YOU STILL NEED TO REWRITE THIS PARAGRAPH AND LINK BOTH SENTENCES.
+THE SECOND SENTENCE (``When the driving'') IS A GOOD START FOR THE PARAGRAPH, ALTHOUGH YOU SHOULD DETERMINE WHAT IS THE ''DRIVING FORCE''  THAT YOU REFERRED TO.)}
 
 \medskip
-In oil exploration, viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations, therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than the \textit{in situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
-
-\medskip
-As mentioned above viscous flow instabilities can be found across many research areas, disciplines and scales, from chemical and medical separation systems to large scale geological reservoir fields.
-\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates and the impact of capillary number ($N_{c}$),
-
+Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
+\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
 \begin{equation}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \begin{equation}
-N_{c} = \frac{\mu U}{\gamma},
+N_{c} = \frac{\mu U}{\gamma}.
 \label{eq:capillary_number}
 \end{equation}
-where $\mu$ is the viscosity of the fuid, $\gamma$ is the surface tension and $U$ is a velocity characteristic of the moving interface.
-
-\medskip
+In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
 In Hele-Shaw cells, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-The experimental apparatus allows the predicted instability to be verified qualitatively and simplifies the problem of flow in both porous and non-porous media.
+This experimental apparatus enables instabilities to be qualitatively investogated by simplifying the flow problem in both porous and non-porous media.
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
-\citet{muskat_1934} investigated the flow of a fluid injected between two infinite parallel plates (Hele-Shaw cell) and the impact on capillary number ($N_{c}$),
+\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
 \begin{equation}
@@
 In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
-In Hele-Shaw cells, a fluid is introduced between two parallel flat plates separated by an infinitesimally small gap.
-This experimental apparatus enables instabilities to be qualitatively investogated by simplifying the flow problem in both porous and non-porous media.
+This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
 %The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
-%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.
-More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
+
+More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
 For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number.
-Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
+For a Hele-Shaw cell of a given size the development flow only depends on the capillary number.
+Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
 
-\medskip
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed %\citep{(described by the Buckley-Leverett theory of immiscible displacement){buckley_1942,sheldon_1959}}
-leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
+During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
 The interface becomes unstable and collapses, taking a curved shape.
+\red{(KOSTAS: IS/ARE THERE ANY REFERENCE FOR THIS FINGERING FORMATION MECHANISMS?')}
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \medskip 
-In heterogeneous domains, such instability may also be triggered by permeability differences across regions as demonstrated in Section \ref{section:results_homo_hete}.
+In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
 The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 The interface becomes unstable and collapses, taking a curved shape.
-\red{(KOSTAS: IS/ARE THERE ANY REFERENCE FOR THIS FINGERING FORMATION MECHANISMS?')}
+\red{(KOSTAS: IS/ARE THERE ANY REFERENCE FOR THIS FINGERING FORMATION MECHANISMS?)}
 
@@
 \medskip
-As demonstrated by \citet{habermann_1960}, \textit{mobility ratio} (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
 \begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \; \mu_{j}}{\mathcal{K}_{rj} \; \mu_{i}}. 
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
 \label{eq:MR}
 \end{equation}
-
-\noindent MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of the residual and maximum phase saturation prescribed in the pore rock matrix.
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
-
 \begin{eqnarray}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified Brooks-Corey model was used \citep{alpak_1999,brooks_1964},
+In the simulations conducted for this work, the modified \cite{brooks_1964} model was used \citep{alpak_1999},
 \begin{eqnarray}
   \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
 \end{eqnarray}
-
-\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
 $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
@@
 
-\medskip
-\noindent From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
 Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
@@
  that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation is a prognostic field which is calculated along with pressure and velocity.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In the process, the finger reaches a critical width that is again unstable and splits again, and the pattern repeats itself.
-Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the \textit{spreading} and ensuing repeated branching.
+Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching.
+\red{(KOSTAS: REFERENCE(S) FOR THIS FINGERING SPLITTING MECHANISM.)}
 
 \medskip
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities in Sections \ref{section:results_homo_hete} and \ref{section:results_hete_fix_adapt}; (b) the collapse of fluid interfaces through the use of adaptive mesh grid in Section \ref{section:results_homo_hete}; (c) the impact of viscosity ratios on the formation and progress of fingers in Section \ref{section:results_hete_fix_adapt} and \ref{section:results_dinlet}.
+
+In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) \red{(KOSTAS: WHAT ABOUT SECTION 4.2?)}; (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
 
@@
 
-\medskip 
 All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-All test-cases were performed in idealised geometries discretised with unstructured triangular mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs.
+\medskip
+In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
 An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
+An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL][]{courant_1941} of 2.
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

--- 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with an {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy \citep{courant_1941} number of 2.
+An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
 In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
 
@@
 Fluids are assumed incompressible and gravity was neglected.
-The set-up for the numerical simulations are summarised in Table \ref{table:setup}.
+Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-\green{PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE ...
-ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY (AS INFERRED B4) OR IN PRESSURE, JUST A LARGE K AND P DISTRO ...} \red{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}
+\red{(PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE (``The spatial discontinuities ...
+permeability region'') ...
+ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ...
+IN ADDITION ...IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?)}
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 permeability region'') ...
-ACTUALLY THIS IS NOT CORRECT AS THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ...
-IN ADDITION ...IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?)}
+ACTUALLY THIS SENTENCE IS NOT CORRECT AS (IN THIS CASE) THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ...
+IN ADDITION ...\underline{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?})}
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 ({\it VR}=1).
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
@@
 
-\medskip
-Numerical simulation was performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
@@
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-\red{KOSTAS ...
-COULD YOU REVIEW THIS SECTION ...
-IT INITIALLY REFERS TO VR=1 AND THEN TO VR=10 ...
-BUT IT IS NOT CLEAR IF THE PLOTS IN FIG 4 REFER TO VR1 OR VR10 ...}
+\red{THIS PARAGRAPH ONLY MAKE SENSE IF YOU ARE SHOWING THE RESULTS OF VR =10.
+HOWEVER, FIGS 4b-c REFER TO VR=1, WHICH, BY THE WAY, HAS NO COMMENT IN THE PREVIOUS PARAGRAPH ...
+IN THIS SECTION YOU \underline{\bf MUST} TALK ABOUT CROSS-FLOW !!}
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 %%%%%%%%%%%%    
-\subsection{Flow simulations in Hele-Shaw cells at different Viscosity Ratio conditions}\label{section:results_homo_hete} 
-In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells (\ie parallel flat plates separated by infinitesimal space) following the work by \citet{saffman_1986}.
+\subsection{Flow Simulations in Hele-Shaw Cells at Different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
+In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work by \citet{saffman_1986}.
 In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid, \ie {\it in situ} hydrocarbons.
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand corner (named as sink), and a pressure gradient between source and sink regions was initially prescribed to the system.
+Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-\medskip
 Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-Newmann (\ie no flux) boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
+No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
 

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
2B and minor updates
Correction

--- 2017-12-07 Papers/ViscousInstabilities/article_figure1.tex
@@
 \centering
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
 \caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+They conducted a sensitivity study to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
 Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
-
 \begin{equation}   

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{in cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-They conducted a sensitivity study to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003},
+They conducted a sensitivity analysis to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,
 \begin{equation}   

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 (depending on finger's tip velocity, Table~\ref{table:Heleshaw}).
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases(Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-\medskip
-Figures \ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c and d, Table~\ref{table:Heleshaw}).
+Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}).
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geofluid dynamics local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (1768 instead of 26313 \PN[1]{2} element-pairs).
-As can been seen, the lower the resolution the more difficult is to capture the fingers formations.
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
+As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
 
-\medskip
-Traditional numerical methods often rely on fixed git add manuscrip	mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow recirculation, heat and mass transfers etc), however computational resources may make it prohibitive for complex geometries and highly heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
+Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
 In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

--- 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
 The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
@@
 
-\medskip
 Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
-A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
+A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
 Viscosity ratio was set to 10.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-\medskip
 Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh.
-In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead.
+In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead, as indicated in Fig.~\ref{fig:5regions_plottimenodeselements}.
 

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

@@
 \includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements.pdf}
-\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
+\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements (red) and nodes (blue) for simulations performed with fixed (dot line) and adaptive (full line) mesh. }
 \label{fig:5regions_plottimenodeselements}

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

--- 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
@@
 \includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements.pdf}
-\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
+\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements (red) and nodes (blue) for simulations performed with fixed (dotted line) and adaptive (full line) mesh. }
 \label{fig:5regions_plottimenodeselements}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers, as decribed in Figure \ref{fig:3DChannel_PermMesh}.
+In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers.
 In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon production fields.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers.
-In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon production fields.
+In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon exploration.
 

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \subsection{3-D channel flows} \label{section:results_3D} 
+In geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in oil/gas exploration fields).
+In this Section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
 
-In this section, 3D simulations are introduced to investigate preferential flow pathways and finger growth through semi-pervious and impervious layers.
-In large scale geological formations preferential flow may allow fast contaminant transport and creates significant consequences for ground-water quality, and low recovery rate in hydrocarbon exploration.
+As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
+Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
+Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
+No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
+Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
+The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
-\medskip
-As mentioned in Section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers.
-The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front.
-Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section.
+No-flux boundary conditions are applied to all borders, except the right-hand (inlet) and the left-hand sides (outflow)..
 The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-No-flux boundary conditions are applied to all borders, except the right-hand (inlet) and the left-hand sides (outflow)..
-The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
-No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain.
-Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid.
-The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
-
 \medskip

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

@@
       \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
-\caption{3D channel flow (fixed mesh): permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
+\caption{3D channel flow (fixed mesh): permeability distribution. The domain contains 235242 \PNDG[1]{1} element-pairs.}
 \label{fig:3DChannel_PermMesh}
@@
 }     
-\caption{3D channel flow (fixed mesh): XY and YZ planes showing wetting fluid phase Darcy velocity vectors overlapped with wetting fluid saturation at (a) t=$0.29$s and (b)t=$4.3$s.}
+\caption{3D channel flow (fixed mesh): XY and YZ planes showing wetting phase saturation overlapped with Darcy velocity vectors $\left(\text{in cm.s}^{-1}\right)$  at (a) t=$0.29$s and (b)t=$4.3$s.}
 \label{fig:3DChannel_planes}

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \medskip
-Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown.
+Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
 Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.
@@
 \medskip
-In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations.
-These flow instabilities were triggerded from the permeability differences in the domain.
+In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
+Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
+
 Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 
-Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations.
-Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct.
-Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
+However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from XX to XX tetrahedral \PNDG[1]{1} element-pairs.
+Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
 
-\medskip 
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-However due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
 In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited.
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from XX to XX tetrahedral \PNDG[1]{1} element-pairs.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs.
 Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
 
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs.
 Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

@@
 \begin{abstract} 
-The aim of this paper is to model flow instabilities \ie{viscous fingering} using a novel method for modeling multi-phase flows in heterogeneous porous with either uniform or random generated permeability distribution.
+  The aim of this paper is to model flow instabilities \ie viscous fingering using a novel method for modeling multi-phase flows in heterogeneous porous media.
 Starting from modelling the Hele-Shaw experimental apparatus, which is mathematically analogous to the two-dimensional flow in porous media problem.
@@
 It was found that mobility ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an ustructured mesh allow the user to better describe and visualise the phenomenon.
+\red{KOSTAS: Abstracts are divided into 4 parts: (1) Motivation (1-2 sentences); (2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ...
+this should be implicit); (3) summary of the main technologies/methods and; (4) summary of the main findings.}
+
 \end{abstract}
@@
  Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio \sep Preferential flowpath \sep Finite Element Methods \sep Capillary number \sep Unstructured domain \sep Mesh adaptivity.
+\red{KOSTAS: choose 3-5 key-words that better represent the work done.}
 \end{keyword}
@@
 Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}.
 
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs.
-Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
+Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.
+
+%For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
 At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-
-In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
+%In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
 For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
 At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-
-\medskip
-A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
+%\medskip
+%A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
 In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as interfacial surface tension (IFT) becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
@@
 \section{Conclusions}\label{Section:Conclusion}
+\red{KOSTAS: Conclusions of numerical modelling papers are are often very short and divided into 3 parts: (1) Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by \underline{your work} in the present manuscript; (2) Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory); and (3) (optional) 1 paragraph of potential future work.
+Make sure that (1) and (2) are covered in the present Section.}
 
-\medskip
-A number of different cases have been illustrated in Section \ref{section:results}.
+%A number of different cases have been illustrated in Section \ref{section:results}.
 Starting from testing experimental cases and geometrical domains (Hele-shaw domain) to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.

### 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
Correction

@@
 Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
-The domain contains 368513 \PN[1]{1} elements.}
+The domain contains 235242 \PNDG[1]{1} elements.}
 \label{fig:3DChannel_sat}
@@
 Fingers' formation and growth can be clearly noticed in (b)-(e).
-The domain contains 368513 \PN[1]{1} elements.}
+The domain contains 235242 \PNDG[1]{1} elements.}
 \label{fig:3DChannel_Isosurf}
@@
           \includegraphics[width=\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Mesh_b} }
+        \hbox{\hspace{10cm}(a)}
       \vspace{.5cm} 
@@
              \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Isosurface_b} 
-            }}
-\caption{3D Channel: Text to come}
-\label{fig:3DChannel_satvel_XYplanes_adapt}
+         }
+        \hbox{\hspace{6cm}(b) \hspace{8cm}(c)}
+    }
+\caption{3D Channel (adaptive mesh): (a) Wetting fluid saturation overlapped with mesh; (b) streamlines and; (c) isosurfaces.
+All plots are shown at 3.78s (Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}f).
+}
+\label{fig:3DChannel_severalfields_adapt}
 \end{figure}

### 2018-01-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction
changes on progress

@@
 \red{KOSTAS: Abstracts are divided into 4 parts: (1) Motivation (1-2 sentences); (2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ...
-this should be implicit); (3) summary of the main technologies/methods and; (4) summary of the main findings.}
-
+this should be implicit, 2-6 sentences); (3) summary of the main technologies/methods (2-5 sentences) and; (4) summary of the main findings (1-3 sentences).}
 \end{abstract}
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio \sep Preferential flowpath \sep Finite Element Methods \sep Capillary number \sep Unstructured domain \sep Mesh adaptivity.
-\red{KOSTAS: choose 3-5 key-words that better represent the work done.}
+ Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio.
 \end{keyword}
@@
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
-The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations.
-In this application, volumetric sweep efficiency \red{(KOSTAS: MAY BE YOU SHOULD ADD ONE SENTENCE DEFINING/EXPLAINING ``SWEEP EFFICIENCY'' AND ``BREAKTHROUGH'' ...
-AND HOW THEY ARE RELATED.)} may be reduced and early breakthrough may occur \citep{riaz_2004, tavassoli_2015}, leading to low oil production.
+The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations that may affect the oil production.
+Important factors during flooding operations are the volumetric sweep efficiency, or the ration of volumes between the recovered and the injected fluids as well as the breakthrough of injected fluid.
+A major problem associated with water-flooding projects is the early water-breakthrough, the main causes of which are high-permeability layers and unfavorable mobility ratios.
+Water breakthrough is the main determinant of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
 During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
@@
 \medskip
-Flow instabilities may be due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain.
-%\red{For example, during water flooding, efficiency is related with capillary number.
-The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES !
-HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ...
-of the domain' ...
-AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}.
-When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
-\red{(KOSTAS: YOU STILL NEED TO REWRITE THIS PARAGRAPH AND LINK BOTH SENTENCES.
-THE SECOND SENTENCE (``When the driving'') IS A GOOD START FOR THE PARAGRAPH, ALTHOUGH YOU SHOULD DETERMINE WHAT IS THE ''DRIVING FORCE''  THAT YOU REFERRED TO.)}
+The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number. 
+%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
+When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
 
@@
 The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-\red{(PS: I AM NOT SURE WHICH INFO YOU WANT TO CONVEY IN THIS SENTENCE (``The spatial discontinuities ...
-permeability region'') ...
-ACTUALLY THIS SENTENCE IS NOT CORRECT AS (IN THIS CASE) THERE IS NO DISCONTINUITY IN EITHER PERMEABILITY OR IN PRESSURE, JUST A LARGE K AND P DISTRIBUTION ...
-IN ADDITION ...\underline{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?})}
+\red{{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}}
 

### 2018-01-15 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 It was found that mobility ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an ustructured mesh allow the user to better describe and visualise the phenomenon.
+
 \red{KOSTAS: Abstracts are divided into 4 parts: (1) Motivation (1-2 sentences); (2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ...
@@
 
+\medskip
 %Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
@@
 
+\medskip
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
@@
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape.
-\red{(KOSTAS: IS/ARE THERE ANY REFERENCE FOR THIS FINGERING FORMATION MECHANISMS?)}
+The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
 
@@
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-The interface collapses and starts splitting into new lobes of fingers.
-One of the fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width that is again unstable and splits again, and the pattern repeats itself.
-Thus, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching.
-\red{(KOSTAS: REFERENCE(S) FOR THIS FINGERING SPLITTING MECHANISM.)}
+At this point it should be mentioned that there are two parameters, the Peclet number (Pe) and mobility ratio (M), that determine the stability characteristics.
+There are always a few dominant fingers that spread and shield the growth of other fingers.
+The interface of the main finger collapses and starts splitting into new lobes of fingers.
+One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a critical width while the concentration gradient of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
+Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
 
 \medskip
-
-In the next section, multi-fluid simulations are performed to numerically investigate: (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) \red{(KOSTAS: WHAT ABOUT SECTION 4.2?)}; (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
+In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed.
+Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
 
@@
 %%%%%%%%%%%% 
-\subsection{Model Set-up}\label{section:results:setup}
+\subsection{Model Set-up}\label{section:results_setup}
 Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
@@
 %%%%%%%%%%%% 
-\subsection{Initial Model Validation}\label{section:results_validation}
+\subsection{Initial Model Validation}\label{section:results_initial_model_validation}
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
@@
 The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-\red{{IS THERE ANY COMMENT WRT FIG 4b-c AT VR=1?}}
+Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
 
-A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+\medskip
+%A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
+A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties such as porosity and permeability is initially simulated. During the displacement
+of one phase by another, fluids may crossflow between adjacent layers, due to any combination of the viscous, capillary and/or gravitational forces which drive multiphase flow.
+In this set of simulations, crossflow caused by viscous forces, which is commonly termed viscous
+crossflow is investigated.
 Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
-They also show the development of wetting phase through the four subdomains, demonstrating the preferential flow path through high-permeability regions.
+They also demonstrate the preferential flow path through high-permeability regions.
 Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-\red{THIS PARAGRAPH ONLY MAKE SENSE IF YOU ARE SHOWING THE RESULTS OF VR =10.
-HOWEVER, FIGS 4b-c REFER TO VR=1, WHICH, BY THE WAY, HAS NO COMMENT IN THE PREVIOUS PARAGRAPH ...
-IN THIS SECTION YOU \underline{\bf MUST} TALK ABOUT CROSS-FLOW !!}
 
@@
 
+\medskip
 Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
@@
 
+\medskip
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.

### 2018-01-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on abstract etc.

@@
 \begin{abstract} 
-  The aim of this paper is to model flow instabilities \ie viscous fingering using a novel method for modeling multi-phase flows in heterogeneous porous media.
-Starting from modelling the Hele-Shaw experimental apparatus, which is mathematically analogous to the two-dimensional flow in porous media problem.
-The development of finger structures is investigated by taking into account different conditions such as, different domains under uniform or different permeabilities regions, mobility ratios, mesh types.
-A novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+\red{(1) Motivation (1-2 sentences);}
+We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media.
+
+\red{(2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ... this should be implicit, 2-6 sentences);}
+Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
+Finally a 3D domain setup is displaying the difference between the preferential flow path and the fingering regimes that will occur in the domain.
+
+\red{(3) summary of the main technologies/methods (2-5 sentences)}
+For these cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
 The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
 Dynamic mesh adaptivity will not only help to better capture the development of finger but also allow the system to focus the computational effort where is needed, minimizing both the CPU time and the numerical diffusion.
-It was found that mobility ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an ustructured mesh allow the user to better describe and visualise the phenomenon.
 
-\red{KOSTAS: Abstracts are divided into 4 parts: (1) Motivation (1-2 sentences); (2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ...
-this should be implicit, 2-6 sentences); (3) summary of the main technologies/methods (2-5 sentences) and; (4) summary of the main findings (1-3 sentences).}
+\red{(4) summary of the main findings}
+It was found that viscosity ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an unstructured mesh will allow the user to directly apply and examine a geological model accurately and without the need of upscaling.
+Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
+
 \end{abstract}
@@
 A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities][]{saffman_1959}.
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface (\eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}).
 This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
@@
 \medskip
-The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number. 
+The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number ($N_{c}$, see eq.\ref{eq:capillary_number}). 
 %Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
@@
 \end{equation}
-In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
+
+\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
 This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
 
+\medskip
 More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
@@
 
+\medskip
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
@@
 
+\medskip
 Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
@@
 
+\medskip
 Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
@@
 
+\medskip
 As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
@@
 
+\medskip
 A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).

### 2018-01-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on abstract and conclusions

@@
 \section{Conclusions}\label{Section:Conclusion}
-\red{KOSTAS: Conclusions of numerical modelling papers are are often very short and divided into 3 parts: (1) Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by \underline{your work} in the present manuscript; (2) Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory); and (3) (optional) 1 paragraph of potential future work.
-Make sure that (1) and (2) are covered in the present Section.}
+\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
+The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development.
+Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.
 
-%A number of different cases have been illustrated in Section \ref{section:results}.
-Starting from testing experimental cases and geometrical domains (Hele-shaw domain) to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied.
-Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces and fingering mechanisms on the developement of the flows.
-
+\red{(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);}
 \medskip
-For immiscible displacements upon which only viscous and capillary forces are acting, the expected displacement patterns are either fully developed cross flow displacement or unstable front displacement.
-In the latter case the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but mainly is a fuction of viscocity ratio (\ie VR).
+By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR).
 If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
@@
 Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
+The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells.
+The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
 
@@
 Commercial simulators provide the user with option of an unstructured type of mesh, still they are not able to dynamically adapt the mesh where is needed and manage the computational cost more efficient.
-
-\medskip
-In summary, the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
-\begin{enumerate}
-\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
-\item[2.] Computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells.
-The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
-\item[3.] Production simulations run directly on the geological model without the need to upscale.\\
-\end{enumerate}
 
@@
 \end{enumerate}
+
+\red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
 

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
+\begin{enumerate}
+  \item \green{Try do avoid (as much as possible) the use of \underline{{\bf 'we'}} in technical/academic writing;}
+  \item \green{\underline{\bf Motivation} means:
+    \begin{itemize}
+      \item Why is the subject of study important?
+      \item What sort of applications will this study impact upon?
+    \end{itemize}}
+  \item \green{\underline{\bf Main aim} means:
+    \begin{itemize}
+      \item What is the main goal of this study?
+    \end{itemize}}
+
+\end{enumerate} 
 \end{abstract}
@@
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
-The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of geological formations that may affect the oil production.
-Important factors during flooding operations are the volumetric sweep efficiency, or the ration of volumes between the recovered and the injected fluids as well as the breakthrough of injected fluid.
-A major problem associated with water-flooding projects is the early water-breakthrough, the main causes of which are high-permeability layers and unfavorable mobility ratios.
-Water breakthrough is the main determinant of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$ flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
+The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
+A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
+Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$-flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
 

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \medskip
-The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number ($N_{c}$, see eq.\ref{eq:capillary_number}). 
+The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, see Eqn.\ref{eq:capillary_number}). 
 %Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \medskip
-The displacement efficiency depends upon the ratio of the viscous to capillary forces or capillary number ($N_{c}$, see eq.\ref{eq:capillary_number}). 
+The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
 %Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
@@
 Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
+\red{KOSTAS, please read and rewrite this paragraph!}
 

### 2018-01-19 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{Initial Model Validation}\label{section:results_initial_model_validation}
-Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow in immiscible displacement in heterogeneous porous media.
+Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
 The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).

### 2018-01-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
update abstract

@@
 \begin{abstract} 
-\red{(1) Motivation (1-2 sentences);}
 We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media.
-
-\red{(2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ... this should be implicit, 2-6 sentences);}
+Those "fingers" will multiply and develop further into complex networks that will eventually effect the efficiency of field operations.
+
 Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
-Finally a 3D domain setup is displaying the difference between the preferential flow path and the fingering regimes that will occur in the domain.
-
-\red{(3) summary of the main technologies/methods (2-5 sentences)}
-For these cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+Finally, a 3D domain setup is showcasing the difference between the preferential flow path and the fingering regimes that will occur in the domain.
+
+For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
 The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
-Dynamic mesh adaptivity will not only help to better capture the development of finger but also allow the system to focus the computational effort where is needed, minimizing both the CPU time and the numerical diffusion.
-
-\red{(4) summary of the main findings}
-It was found that viscosity ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an unstructured mesh will allow the user to directly apply and examine a geological model accurately and without the need of upscaling.
+Dynamic mesh adaptivity will not only help to better capture the development of finger but also overcome the computational limitations focusing the effort where is needed, minimizing both the CPU time and the numerical diffusion.
+
+Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.
 Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
 
-\begin{enumerate}
-  \item \green{Try do avoid (as much as possible) the use of \underline{{\bf 'we'}} in technical/academic writing;}
-  \item \green{\underline{\bf Motivation} means:
-    \begin{itemize}
-      \item Why is the subject of study important?
-      \item What sort of applications will this study impact upon?
-    \end{itemize}}
-  \item \green{\underline{\bf Main aim} means:
-    \begin{itemize}
-      \item What is the main goal of this study?
-    \end{itemize}}
-
-\end{enumerate} 
 \end{abstract}
@@
 %% End of tex file.
+
+% Copyright 2007, 2008, 2009 Elsevier Ltd 
+% 
+% This file is part of the 'Elsarticle Bundle'.
+% --------------------------------------------- 
+%
+% It may be distributed under the conditions of the LaTeX Project Public
+% License, either version 1.2 of this license or (at your option) any
+% later version.  The latest version of this license is in
+%    http://www.latex-project.org/lppl.txt
+% and version 1.2 or later is part of all distributions of LaTeX
+% version 1999/12/01 or later c.
+%
+% The list of all files belonging to the 'Elsarticle Bundle' is
+% given in the file `manifest.txt'.
+%
+
+% Template article for Elsevier's document class `elsarticle'
+% with harvard style bibliographic references
+% SP 2008/03/01
+%
+%
+%
+% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
+%
+%
+\documentclass[preprint,authoryear,12pt]{elsarticle}
+
+% Use the option review to obtain double line spacing
+%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+% for a journal layout:
+%\documentclass[final,authoryear,1p,times]{elsarticle}
+%\documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
+%\documentclass[final,authoryear,3p,times]{elsarticle}
+%\documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
+%\documentclass[final,authoryear,5p,times]{elsarticle}
+%\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the gra
+
+%%graphis package for simple commands
+%% \usepackage{graphics}
+%\usepackage{cases}
+%% or use the graphicx package for more complicated commands
+\usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+\usepackage{epsfig}
+%\usepackage{subfig}
+\usepackage{comment}
+
+\usepackage{epstopdf}
+\usepackage{pdflscape}
+\usepackage{bm}
+\usepackage{hyperref,url}
+\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
+
+%% The amssymb package provides various useful mathematical symbols
+
+\usepackage{amssymb,amsmath,array}
+%The amsthm package provides extended theorem environments
+
+\usepackage{amsthm}
+\usepackage{graphicx}
+%\usepackage{subfigure}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+\usepackage{lscape}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon (default)
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   authoryear - selects author-year citations (default)
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%   longnamesfirst  -  makes first citation full author list
+%%
+%% \biboptions{longnamesfirst,comma}
+
+% \biboptions{}
+
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
+\journal{Advances in Water Resources}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
+\newcommand{\eg}{{\it e.g., }} 
+\newcommand{\ie}{{\it i.e., }}
+
+\begin{document}
+
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+  \title{ Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media}%.
+Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
+  %% Tittle was too long and 'Advantages and limitations unstructured and adaptive meshes' would mean a full numerical analysis on these 2 issues ...
+we haven't fully studied flows in either  unstructured / structured or adaptive / fixed meshes ...
+
+%% use optional labels to link authors explicitly to addresses:
+\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
+\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
+
+\cortext[cor1]{Corresponding author.}
+\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
+\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
+\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
+
+\begin{abstract} 
+\red{(1) Motivation (1-2 sentences);}
+We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media.
+
+\red{(2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ... this should be implicit, 2-6 sentences);}
+Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
+Finally a 3D domain setup is displaying the difference between the preferential flow path and the fingering regimes that will occur in the domain.
+
+\red{(3) summary of the main technologies/methods (2-5 sentences)}
+For these cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
+Dynamic mesh adaptivity will not only help to better capture the development of finger but also allow the system to focus the computational effort where is needed, minimizing both the CPU time and the numerical diffusion.
+
+\red{(4) summary of the main findings}
+It was found that viscosity ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an unstructured mesh will allow the user to directly apply and examine a geological model accurately and without the need of upscaling.
+Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
+
+\begin{enumerate}
+  \item \green{Try do avoid (as much as possible) the use of \underline{{\bf 'we'}} in technical/academic writing;}
+  \item \green{\underline{\bf Motivation} means:
+    \begin{itemize}
+      \item Why is the subject of study important?
+      \item What sort of applications will this study impact upon?
+    \end{itemize}}
+  \item \green{\underline{\bf Main aim} means:
+    \begin{itemize}
+      \item What is the main goal of this study?
+    \end{itemize}}
+
+\end{enumerate} 
+\end{abstract}
+
+\begin{keyword} %% keywords here, in the form: keyword \sep keyword
+ Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio.
+\end{keyword}
+
+\end{frontmatter}
+
+%\tableofcontents
+%\linenumbers
+
+\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Introduction}\label{section:intro}
+Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
+%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
+%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
+Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work has been focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+
+\medskip
+%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
+Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface (\eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}).
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
+%Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
+\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
+% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
+SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
+%The first distinction should be made between microscopic and macroscopic instabilities.
+Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
+On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
+This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
+
+\medskip
+In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
+As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+
+\medskip 
+Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
+Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM schemes result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+
+\medskip
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
+%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
+%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
+%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%\begin{equation}
+% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+%\label{cvfe_pressure} 
+%\end{equation}
+
+%\begin{equation}
+% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+%\label{cvfe_saturation}
+%\end{equation} 
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+\medskip
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
+These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
+%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+All these parameters are represented under one term in the global mass balance equation.}
+
+\medskip 
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
+%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
+The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+
+\medskip
+A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
+Impact of mobility ratio on the fingers formation is also included in this section.
+Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Model Formulation}\label{equations_scheme}      
+%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
+Different domains will produce different flow instabilities.
+In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
+DG-methods combine advantages of classical finite volume and finite element methods.
+
+%\subsection{Numerical Formulation}
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%Flows in porous media are expressed by the Darcy's law and the saturation equation.
+At this stage the control volume finite element method is used (CVFEM).
+Darcy's law for immiscible multi-phase flow may be written in the form:
+%\begin{equation}\label{e:darcy_eq}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_bal}
+%\end{equation}
+%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
+
+%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
+%\begin{equation}
+%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
+%\end{equation}
+%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
+%\begin{eqnarray}
+%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
+%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
+%\label{v_and_p}
+%\end{eqnarray}
+
+%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
+Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
+%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
+%\begin{equation}
+%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:force_balance}
+%\end{equation}
+
+%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
+Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
+%\end{comment}
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
+In addition, we neglect the effects of capillarity and gravity in our simulations.
+Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
+
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%\label{e:darcy_eq}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+
+%\begin{equation}
+%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
+%\label{E:darcy_eqn}
+%\end{equation}
+%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
+$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
+$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
+
+% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
+%\begin{equation}
+%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
+%  \label{e:darcy_ext}
+%\end{equation}
+%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
+
+\begin{eqnarray}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+\end{eqnarray}
+
+\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
+${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
+%\begin{displaymath}
+%\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
+%\end{displaymath}
+%where $\mathcal{N}_{p}$ denotes the number of phases.
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%The main equations that will be used along with the following OCVFEM techique can be summarised below.
+The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
+At the $n+1$ step those two equations mentioned above can be rewritten as,
+
+%\begin{equation}
+%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
+%\label{e:mass_bal}
+%\end{equation}
+
+%\begin{equation}
+%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
+%\label{e:force_bal}
+%\end{equation}
+
+%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
+This system of equations can be rewritten to produce the pressure equation,
+
+%\begin{equation}
+%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
+%\label{e:pressure_eq}
+%\end{equation}
+
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
+In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
+Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
+
+Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively -- note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
+Each component of the weak form of the extended Darcy equation is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
+\begin{eqnarray}
+  \sum\limits_{E} \left.
+\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
++ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
+  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
+                   \label{force-semi-disc} 
+\end{eqnarray} 
+where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
+The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$ $\left(\text{consistent with the \PNDG[n]{m} element-pairs}\right)$.
+This term vanishes when a continuous formulation is used to discretise the pressure field $\left(\text{with \PN[n]{m} element-pairs}\right)$.
+The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
+%Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
+Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
+$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
+%\begin{displaymath}
+%   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
+%\end{displaymath}
+
+\medskip
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
+Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
+Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
+\begin{eqnarray}
+ && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
+ &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
+ &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
+\label{global_mass_balance}
+\end{eqnarray}
+
+%This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
+In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
+Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
+%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
+%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
+
+%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
+%\begin{equation}
+%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
+%\label{mass_balance}
+%\end{equation}
+
+%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
+
+%\begin{equation}
+%\sum  S_{p}-1
+%\label{saturation_constrain}
+%\end{equation}
+\noindent
+where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
+$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
+
+\medskip
+The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
+The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
+The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
+A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
+Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$-flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
+
+\medskip
+The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
+%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
+When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
+
+\medskip
+Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
+\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
+\begin{equation}
+N_{c} = \frac{\mu U}{\gamma}.
+\label{eq:capillary_number}
+\end{equation}
+
+\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
+This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
+
+\medskip
+More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
+For a Hele-Shaw cell of a given size the development flow only depends on the capillary number.
+Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
+
+\medskip
+ Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
+During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
+In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
+
+\medskip 
+In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+Pressure differences acting on the interface produces a net pressure force,
+\begin{equation} 
+\Delta P= - \gamma \nabla\cdot\hat{n}. 
+\label{eq:pressure_dif} 
+\end{equation}
+
+\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
+
+\medskip
+As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+\begin{equation}
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
+\label{eq:MR}
+\end{equation}
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified \cite{brooks_1964} model was used \citep{alpak_1999},
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+
+From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
+\begin{displaymath}
+    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
+\end{displaymath}
+ that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
+
+\medskip
+In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+At this point it should be mentioned that there are two parameters, the Peclet number (Pe) and mobility ratio (M), that determine the stability characteristics.
+There are always a few dominant fingers that spread and shield the growth of other fingers.
+The interface of the main finger collapses and starts splitting into new lobes of fingers.
+One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a critical width while the concentration gradient of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
+Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
+
+\medskip
+In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed.
+Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
+\red{KOSTAS, please read and rewrite this paragraph!}
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
+
+%\begin{equation}
+%\lambda = \frac{K\;k_{\alpha}}{\mu}
+%\label{eq:mobility-of-fluid}
+%\end{equation}
+
+%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
+The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
+Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
+
+%\begin{equation}
+%U = \frac{b^2}{12 \mu} \nabla p
+%\end{equation}
+
+%and the above equation can be re-arranged for 1D steady flow as,
+
+%\begin{equation}
+%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
+%\label{eq:pressure_dif} 
+%\end{equation}
+
+%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
+Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
+Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
+
+%\begin{equation}
+%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
+%\end{equation}
+
+%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
+
+%\begin{equation}
+%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
+%\end{equation}
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%\pagebreak
+%\clearpage
+
+%\listoftables 
+%\pagebreak
+%\input{Manuscript_Table}
+
+%\pagebreak
+%\clearpage
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}\label{section:results}
+
+%%%%%%%%%%%% 
+\subsection{Model Set-up}\label{section:results_setup} 
+Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
+
+\medskip
+In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
+An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
+Fluids are assumed incompressible and gravity was neglected.
+Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
+
+%%%%%%%%%%%% 
+\subsection{Initial Model Validation}\label{section:results_initial_model_validation}
+Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
+The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
+Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
+Boundary conditions also include no-flux across upper and lower borders.
+The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
+The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
+Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
+
+\medskip
+%A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
+Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
+A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties such as porosity and permeability is initially simulated. During the displacement
+of one phase by another, fluids may crossflow between adjacent layers, due to any combination of the viscous, capillary and/or gravitational forces which drive multiphase flow.
+In this set of simulations, crossflow caused by viscous forces, which is commonly termed viscous
+crossflow is investigated.
+Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
+They also demonstrate the preferential flow path through high-permeability regions.
+Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+
+%%%%%%%%%%%%    
+\subsection{Flow Simulations in Hele-Shaw Cells at Different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
+In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work by \citet{saffman_1986}.
+In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.
+
+\medskip
+Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
+Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
+No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
+
+\medskip
+Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
+At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
+Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
+However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.
+
+\medskip
+Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
+They conducted a sensitivity analysis to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,
+\begin{equation}   
+   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
+\end{equation}
+
+\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
+
+\medskip
+Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
+Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
+Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
+
+\medskip
+In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases(Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
+
+\medskip
+Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}).
+Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
+
+%%%%%%%%%%%%%
+\subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}    
+%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
+In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
+This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
+
+\medskip
+In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
+In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
+As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
+
+\medskip
+Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
+Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
+In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
+There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
+Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
+
+\medskip
+The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
+The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
+In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
+
+\medskip
+Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
+In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
+A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
+Viscosity ratio was set to 10.
+
+\medskip
+Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.
+Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
+In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
+The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$.
+In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh.
+In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead, as indicated in Fig.~\ref{fig:5regions_plottimenodeselements}.
+
+%%%%%%%%%%%%%
+\subsection{3-D channel flows} \label{section:results_3D} 
+In geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in oil/gas exploration fields).
+In this Section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
+
+\medskip
+As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
+Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
+Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
+No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
+Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
+The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+
+\medskip
+Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
+Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.
+
+\medskip
+In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
+Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}.
+
+\medskip
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
+Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.
+
+%For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
+%In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
+For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
+At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
+%\medskip
+%A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
+In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as interfacial surface tension (IFT) becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
+Through \textit{shielding} mechanism, one of these fingers will eventually outgrow the other and, will then spread (\textit{spreading}) to occupy the appropriate width of the domain ahead of it.
+Following this process, it reaches a width that is again unstable and the pattern repeats.
+So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
+
+%%%%%%%%%%%%%
+\section{Conclusions}\label{Section:Conclusion}
+\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
+The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development.
+Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.
+
+\red{(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);}
+\medskip
+By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR).
+If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
+On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
+Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
+Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
+The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells.
+The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
+
+\medskip
+As seen for high viscosity contrast, there is a leading finger (\textit{tip splitting mechanism}) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
+At long times the large finger advances approximately at in a constant flow rate.
+In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced for all the $2D$ and $3D$ cases.
+Commercial simulators provide the user with option of an unstructured type of mesh, still they are not able to dynamically adapt the mesh where is needed and manage the computational cost more efficient.
+
+\medskip
+Regarding the flow characteristics and the mechanics of fingering formations,
+
+\begin{enumerate}
+\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from longitudinal section througout the Hele-shaw domains.
+\item[2.] Even though different permeability patterns will initially make the uniform front to collapse, it is the \textit{viscocity ratio} the key parameter and the capillary forces as these are related with surface tension that will eventually lead the flow instabilities.
+The higher the viscocity ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
+\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes. 
+\item[4.] Properties such as porosity and saturation can be readily up-scaled as they can be included in the element boundaries.
+The domains used in these test-cases have the ability to describe the fingering mechanism and the development of the flow \ie the latter case clearly describes the linear tip-splitting finger behaviour inside the domain.
+\end{enumerate}
+
+\red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
+
+\section{Acknowledgements}
+Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
+Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
+
+\clearpage 
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv} 
+\bibliography{references}
+
+\clearpage
+
+\listoftables
+\clearpage
+\input{article_table}
+\clearpage  
+\listoffigures
+\clearpage
+
+\input{article_figure1}
+%\input{article_figure2}
+
+\end{document}
+%% End of tex file.

### 2018-01-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates abstract
update conclusion
updates

@@
 Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.
-Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
+Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow path can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
 
@@
 \medskip
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
-Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{3DChannel_satvel_XYplanes_adapt}a).
+Distinct preferable flow pathways can be shown (Fig.
+\ref{3DChannel_satvel_XYplanes_adapt}c)
+%(Fig.~\ref{fig:3DChannel_severalfields_adapt}c)
+, in particular through the central channel (see streamlines in 
+Fig. \ref{3DChannel_satvel_XYplanes_adapt}f)
+%Fig.~\ref{fig:3DChannel_severalfields_adapt}b) 
+and at the top of the domain.
 

### 2018-01-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
I have now upload the updated version

--- 2018-01-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 %% End of tex file.
-
-% Copyright 2007, 2008, 2009 Elsevier Ltd 
-% 
-% This file is part of the 'Elsarticle Bundle'.
-% --------------------------------------------- 
-%
-% It may be distributed under the conditions of the LaTeX Project Public
-% License, either version 1.2 of this license or (at your option) any
-% later version.  The latest version of this license is in
-%    http://www.latex-project.org/lppl.txt
-% and version 1.2 or later is part of all distributions of LaTeX
-% version 1999/12/01 or later c.
-%
-% The list of all files belonging to the 'Elsarticle Bundle' is
-% given in the file `manifest.txt'.
-%
-
-% Template article for Elsevier's document class `elsarticle'
-% with harvard style bibliographic references
-% SP 2008/03/01
-%
-%
-%
-% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
-%
-%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
-
-% Use the option review to obtain double line spacing
-%\documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-% for a journal layout:
-%\documentclass[final,authoryear,1p,times]{elsarticle}
-%\documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
-%\documentclass[final,authoryear,3p,times]{elsarticle}
-%\documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
-%\documentclass[final,authoryear,5p,times]{elsarticle}
-%\documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
-
-%% if you use PostScript figures in your article
-%% use the gra
-
-%%graphis package for simple commands
-%% \usepackage{graphics}
-%\usepackage{cases}
-%% or use the graphicx package for more complicated commands
-\usepackage{graphicx}
-%% or use the epsfig package if you prefer to use the old commands
-\usepackage{epsfig}
-%\usepackage{subfig}
-\usepackage{comment}
-
-\usepackage{epstopdf}
-\usepackage{pdflscape}
-\usepackage{bm}
-\usepackage{hyperref,url}
-\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
-
-%% The amssymb package provides various useful mathematical symbols
-
-\usepackage{amssymb,amsmath,array}
-%The amsthm package provides extended theorem environments
-
-\usepackage{amsthm}
-\usepackage{graphicx}
-%\usepackage{subfigure}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-\usepackage{lscape}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon (default)
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   authoryear - selects author-year citations (default)
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%   longnamesfirst  -  makes first citation full author list
-%%
-%% \biboptions{longnamesfirst,comma}
-
-% \biboptions{}
-
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
-\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
-\newcommand{\red}{\textcolor{red}}
-\newcommand{\blue}{\textcolor{blue}}
-\newcommand{\green}{\textcolor{green}}
-\journal{Advances in Water Resources}
-\newcommand{\frc}{\displaystyle\frac}
-\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
-\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
-\newcommand{\eg}{{\it e.g., }} 
-\newcommand{\ie}{{\it i.e., }}
-
-\begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-  \title{ Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media}%.
-Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
-  %% Tittle was too long and 'Advantages and limitations unstructured and adaptive meshes' would mean a full numerical analysis on these 2 issues ...
-we haven't fully studied flows in either  unstructured / structured or adaptive / fixed meshes ...
-
-%% use optional labels to link authors explicitly to addresses:
-\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
-\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
-
-\cortext[cor1]{Corresponding author.}
-\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
-\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
-\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
-
-\begin{abstract} 
-\red{(1) Motivation (1-2 sentences);}
-We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media.
-
-\red{(2) Main aim of the manuscript highlighting the novelty of the work (you must not use the word novelty ... this should be implicit, 2-6 sentences);}
-Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
-A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
-Finally a 3D domain setup is displaying the difference between the preferential flow path and the fingering regimes that will occur in the domain.
-
-\red{(3) summary of the main technologies/methods (2-5 sentences)}
-For these cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
-The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
-Dynamic mesh adaptivity will not only help to better capture the development of finger but also allow the system to focus the computational effort where is needed, minimizing both the CPU time and the numerical diffusion.
-
-\red{(4) summary of the main findings}
-It was found that viscosity ratio along with the initial and boundary conditions, as well as the use of adaptivity on top of an unstructured mesh will allow the user to directly apply and examine a geological model accurately and without the need of upscaling.
-Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
-
-\begin{enumerate}
-  \item \green{Try do avoid (as much as possible) the use of \underline{{\bf 'we'}} in technical/academic writing;}
-  \item \green{\underline{\bf Motivation} means:
-    \begin{itemize}
-      \item Why is the subject of study important?
-      \item What sort of applications will this study impact upon?
-    \end{itemize}}
-  \item \green{\underline{\bf Main aim} means:
-    \begin{itemize}
-      \item What is the main goal of this study?
-    \end{itemize}}
-
-\end{enumerate} 
-\end{abstract}
-
-\begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio.
-\end{keyword}
-
-\end{frontmatter}
-
-%\tableofcontents
-%\linenumbers
-
-\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Introduction}\label{section:intro}
-Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
-%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
-%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work has been focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
-
-\medskip
-%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
-Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface (\eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}).
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
-%Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
-% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
-SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-%The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
-
-\medskip
-In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
-
-\medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM schemes result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
-%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
-
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation} 
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
-%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
-
-\medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
-Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
-Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Formulation}\label{equations_scheme}      
-%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Different domains will produce different flow instabilities.
-In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
-DG-methods combine advantages of classical finite volume and finite element methods.
-
-%\subsection{Numerical Formulation}
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-%\begin{equation}\label{e:darcy_eq}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_bal}
-%\end{equation}
-%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-%\begin{equation}
-%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-%\end{equation}
-%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-%\begin{eqnarray}
-%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-%\label{v_and_p}
-%\end{eqnarray}
-
-%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_balance}
-%\end{equation}
-
-%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-%\end{comment}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\label{e:darcy_eq}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-%\label{E:darcy_eqn}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
-% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-%\begin{equation}
-%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:darcy_ext}
-%\end{equation}
-%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
-%\begin{displaymath}
-%\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
-%\end{displaymath}
-%where $\mathcal{N}_{p}$ denotes the number of phases.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The main equations that will be used along with the following OCVFEM techique can be summarised below.
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-%\begin{equation}
-%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-%\label{e:mass_bal}
-%\end{equation}
-
-%\begin{equation}
-%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-%\label{e:force_bal}
-%\end{equation}
-
-%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-%\begin{equation}
-%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-%\label{e:pressure_eq}
-%\end{equation}
-
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
-In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
-Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
-
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively -- note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
-Each component of the weak form of the extended Darcy equation is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
-\begin{eqnarray}
-  \sum\limits_{E} \left.
-\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
-+ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
-  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
-                   \label{force-semi-disc} 
-\end{eqnarray} 
-where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
-The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$ $\left(\text{consistent with the \PNDG[n]{m} element-pairs}\right)$.
-This term vanishes when a continuous formulation is used to discretise the pressure field $\left(\text{with \PN[n]{m} element-pairs}\right)$.
-The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
-%Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
-%\begin{displaymath}
-%   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
-%\end{displaymath}
-
-\medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
-Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
-
-%This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
-%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
-
-%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
-%\begin{equation}
-%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
-%\label{mass_balance}
-%\end{equation}
-
-%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
-
-%\begin{equation}
-%\sum  S_{p}-1
-%\label{saturation_constrain}
-%\end{equation}
-\noindent
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
-$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-
-\medskip
-The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
-The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
-The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
-A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
-Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$-flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
-
-\medskip
-The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
-%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
-When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
-
-\medskip
-Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
-\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
-\begin{equation}
-N_{c} = \frac{\mu U}{\gamma}.
-\label{eq:capillary_number}
-\end{equation}
-
-\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
-This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
-
-\medskip
-More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size the development flow only depends on the capillary number.
-Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
-
-\medskip
- Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
-
-\medskip 
-In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
-\begin{equation} 
-\Delta P= - \gamma \nabla\cdot\hat{n}. 
-\label{eq:pressure_dif} 
-\end{equation}
-
-\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
-
-\medskip
-As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
-\begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
-\label{eq:MR}
-\end{equation}
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \cite{brooks_1964} model was used \citep{alpak_1999},
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
-\begin{displaymath}
-    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
-\end{displaymath}
- that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
-
-\medskip
-In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-At this point it should be mentioned that there are two parameters, the Peclet number (Pe) and mobility ratio (M), that determine the stability characteristics.
-There are always a few dominant fingers that spread and shield the growth of other fingers.
-The interface of the main finger collapses and starts splitting into new lobes of fingers.
-One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width while the concentration gradient of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
-Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
-
-\medskip
-In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed.
-Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
-\red{KOSTAS, please read and rewrite this paragraph!}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-%\begin{equation}
-%\lambda = \frac{K\;k_{\alpha}}{\mu}
-%\label{eq:mobility-of-fluid}
-%\end{equation}
-
-%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-%\begin{equation}
-%U = \frac{b^2}{12 \mu} \nabla p
-%\end{equation}
-
-%and the above equation can be re-arranged for 1D steady flow as,
-
-%\begin{equation}
-%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
-%\label{eq:pressure_dif} 
-%\end{equation}
-
-%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-%\begin{equation}
-%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-%\end{equation}
-
-%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
-
-%\begin{equation}
-%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-%\end{equation}
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%\pagebreak
-%\clearpage
-
-%\listoftables 
-%\pagebreak
-%\input{Manuscript_Table}
-
-%\pagebreak
-%\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
-
-%%%%%%%%%%%% 
-\subsection{Model Set-up}\label{section:results_setup} 
-Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
-
-\medskip
-In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
-Fluids are assumed incompressible and gravity was neglected.
-Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
-
-%%%%%%%%%%%% 
-\subsection{Initial Model Validation}\label{section:results_initial_model_validation}
-Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
-Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-Boundary conditions also include no-flux across upper and lower borders.
-The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
-
-\medskip
-%A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
-Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
-A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties such as porosity and permeability is initially simulated. During the displacement
-of one phase by another, fluids may crossflow between adjacent layers, due to any combination of the viscous, capillary and/or gravitational forces which drive multiphase flow.
-In this set of simulations, crossflow caused by viscous forces, which is commonly termed viscous
-crossflow is investigated.
-Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
-They also demonstrate the preferential flow path through high-permeability regions.
-Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-
-%%%%%%%%%%%%    
-\subsection{Flow Simulations in Hele-Shaw Cells at Different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
-In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work by \citet{saffman_1986}.
-In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.
-
-\medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
-Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
-
-\medskip
-Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
-At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
-Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.
-
-\medskip
-Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-They conducted a sensitivity analysis to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,
-\begin{equation}   
-   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
-\end{equation}
-
-\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
-
-\medskip
-Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
-Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
-Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
-
-\medskip
-In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases(Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
-
-\medskip
-Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}).
-Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
-
-%%%%%%%%%%%%%
-\subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}    
-%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
-Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
-
-\medskip
-In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
-In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
-As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
-
-\medskip
-Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
-In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
-There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
-Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
-
-\medskip
-The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
-The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
-In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
-
-\medskip
-Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
-In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
-A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
-Viscosity ratio was set to 10.
-
-\medskip
-Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.
-Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
-In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
-The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$.
-In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh.
-In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead, as indicated in Fig.~\ref{fig:5regions_plottimenodeselements}.
-
-%%%%%%%%%%%%%
-\subsection{3-D channel flows} \label{section:results_3D} 
-In geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in oil/gas exploration fields).
-In this Section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
-
-\medskip
-As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
-Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
-Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
-No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
-Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
-
-\medskip
-Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
-Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.
-
-\medskip
-In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
-Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}.
-
-\medskip
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
-Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.
-
-%For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
-At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-%In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
-For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
-At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-%\medskip
-%A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
-In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as interfacial surface tension (IFT) becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
-Through \textit{shielding} mechanism, one of these fingers will eventually outgrow the other and, will then spread (\textit{spreading}) to occupy the appropriate width of the domain ahead of it.
-Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
-
-%%%%%%%%%%%%%
-\section{Conclusions}\label{Section:Conclusion}
-\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
-The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development.
-Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.
-
-\red{(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);}
-\medskip
-By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR).
-If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
-On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
-Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
-Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
-The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells.
-The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
-
-\medskip
-As seen for high viscosity contrast, there is a leading finger (\textit{tip splitting mechanism}) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
-At long times the large finger advances approximately at in a constant flow rate.
-In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced for all the $2D$ and $3D$ cases.
-Commercial simulators provide the user with option of an unstructured type of mesh, still they are not able to dynamically adapt the mesh where is needed and manage the computational cost more efficient.
-
-\medskip
-Regarding the flow characteristics and the mechanics of fingering formations,
-
-\begin{enumerate}
-\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from longitudinal section througout the Hele-shaw domains.
-\item[2.] Even though different permeability patterns will initially make the uniform front to collapse, it is the \textit{viscocity ratio} the key parameter and the capillary forces as these are related with surface tension that will eventually lead the flow instabilities.
-The higher the viscocity ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
-\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes. 
-\item[4.] Properties such as porosity and saturation can be readily up-scaled as they can be included in the element boundaries.
-The domains used in these test-cases have the ability to describe the fingering mechanism and the development of the flow \ie the latter case clearly describes the linear tip-splitting finger behaviour inside the domain.
-\end{enumerate}
-
-\red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
-
-\section{Acknowledgements}
-Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
-Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
-
-\clearpage 
-%% References with bibTeX database:
-\bibliographystyle{elsarticle-harv} 
-\bibliography{references}
-
-\clearpage
-
-\listoftables
-\clearpage
-\input{article_table}
-\clearpage  
-\listoffigures
-\clearpage
-
-\input{article_figure1}
-%\input{article_figure2}
-
-\end{document}
-%% End of tex file.

### 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \begin{abstract} 
-We examine the flow instabilities, \ie viscous fingering on the displacement of one fluid by a second, using a novel computational method for modeling multi-phase flows in heterogeneous porous media.
-Those "fingers" will multiply and develop further into complex networks that will eventually effect the efficiency of field operations.
+We examine flow instabilities that leads to formation and growth of viscous fingers during fluid displacement using a novel computational multi-phase flows model in heterogeneous porous media.
+Fingers often grow and develop into complex networks that have strong impact on the efficiency of oil and gas exploration.
 
-Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, the finger development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
@@
 Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
-\red{KOSTAS, please read and rewrite this paragraph!}
 

### 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+From initial studies of XXXStarting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.

### 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \begin{abstract} 
+CAUSE --> EFFECT --> MOTIVATION (P1)
+In immiscible two-fluid flow displacement, viscosity differences  mechanism is highly related to the viscosity ratio and capillary number
 We examine flow instabilities that leads to formation and growth of viscous fingers during fluid displacement using a novel computational multi-phase flows model in heterogeneous porous media.
@@
 
-Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
+From initial fluid flow studies in the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
@@
 
+CAUSE --> EFFECT --> FEW TECHS USED  (P3)
 For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
@@
 
+CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
 Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.

### 2018-02-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

--- 2018-02-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \begin{abstract} 
-We examine flow instabilities that leads to formation and growth of viscous fingers during fluid displacement using a novel computational multi-phase flows model in heterogeneous porous media.
-Fingers often grow and develop into complex networks that have strong impact on the efficiency of oil and gas exploration.
+%CAUSE --> EFFECT --> MOTIVATION (P1)
+A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the quantity of fluid that can be pushed by another fluid due to pressure gradient.
+Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which simulation of immiscible fluid displacement dynamics may help mitigating water resources contamination and improving hydrocarbons production.
+In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated.
+Viscous flow instabilities lead to formation and growth of fingers that have strong impact on the efficiency of oil and gas exploration.
 
-Starting from modelling the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
+From initial fluid flow studies of the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
@@
 
+%CAUSE --> EFFECT --> FEW TECHS USED  (P3)
 For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
@@
 
+%CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
 Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which simulation of immiscible fluid displacement dynamics may help mitigating water resources contamination and improving hydrocarbons production.
-In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated.
-Viscous flow instabilities lead to formation and growth of fingers that have strong impact on the efficiency of oil and gas exploration.
+Due to large fluids' viscosity ratio, flow instabilities may arise leading to formation and growth of fingers with strong impact on the efficiency of oil and gas exploration.
 
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
+The main aim of this work is to numerically investigate
+
+  In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated.
+
 From initial fluid flow studies of the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %CAUSE --> EFFECT --> MOTIVATION (P1)
-  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the quantity of fluid that can be pushed by another fluid due to pressure gradient.
-Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which simulation of immiscible fluid displacement dynamics may help mitigating water resources contamination and improving hydrocarbons production.
-Due to large fluids' viscosity ratio, flow instabilities may arise leading to formation and growth of fingers with strong impact on the efficiency of oil and gas exploration.
+  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
+Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production.
+Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers, with strong impact on the displacement efficiency.
+%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
 
-%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
 The main aim of this work is to numerically investigate

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
-
-The main aim of this work is to numerically investigate
+Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers depends mostly on mobility ratio and capillary number, however heterogeneity of the porous domain may affect the onset formation of fingers.
+Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
+The model used here is based on a novel control volume finite element method (CVFEM) formulation with a new family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-The model used here is based on a novel control volume finite element method (CVFEM) formulation with a new family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}
+The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} and \PNDG[n]{m} specially tailored for Darcean flows.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production.
-Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers, with strong impact on the displacement efficiency.
+Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
@@
 Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
+%CAUSE --> EFFECT --> FEW TECHS USED  (P3)
 The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} and \PNDG[n]{m} specially tailored for Darcean flows.
+Dynamic mesh adaptivity enables capturing fingers development whilst saving computational overheads.
+Numerical experiments were performed to investigate the impact of viscosity ratio, heterogeneity and mesh resolution in the capture of fluids instabilities.
+%CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
+Numerical simulations demonstrated that the heterogeneity of the domain triggers the early-onset formation of fingers under prescribed viscosity ratio conditions.
+Also, effective capture of growth (in particular, tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
 
-  In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated.
-
-From initial fluid flow studies of the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
+%In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated. 
+%From initial fluid flow studies of the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
 A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
@@
 %CAUSE --> EFFECT --> FEW TECHS USED  (P3)
-For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
+%For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
 The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
@@
 %CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
-Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.
+%Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.
 Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow path can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %CAUSE --> EFFECT --> MOTIVATION (P1)
-  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
-Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production.
-Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
+  A critical aspect of multiphase flow in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
+Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
+Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
-Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers depends mostly on mobility ratio and capillary number, however heterogeneity of the porous domain may affect the onset formation of fingers.
+Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers mostly depends on mobility ratio and capillary number, however heterogeneity of the porous domain may also affect the onset of instabilities.
 Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
@@
 Dynamic mesh adaptivity enables capturing fingers development whilst saving computational overheads.
-Numerical experiments were performed to investigate the impact of viscosity ratio, heterogeneity and mesh resolution in the capture of fluids instabilities.
+Numerical experiments were performed to investigate the impact of viscosity ratio and heterogeneity on Saffmann-Taylor instabilities.
 %CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
 Numerical simulations demonstrated that the heterogeneity of the domain triggers the early-onset formation of fingers under prescribed viscosity ratio conditions.
-Also, effective capture of growth (in particular, tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
+Also, effective numerical capture of growth (in particular, tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to global environmental problems, several research work has been focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+Underground coal gasification is another important field of interest and, more recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface (\eg Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}).
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
 This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
@@
 However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM schemes result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %CAUSE --> EFFECT --> FEW TECHS USED  (P3)
-The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} and \PNDG[n]{m} specially tailored for Darcean flows.
+The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} specially tailored for Darcean flows.
 Dynamic mesh adaptivity enables capturing fingers development whilst saving computational overheads.
@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous media.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
@@
 A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
-Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of the reservoir \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$-flooding $\left(\text{\eg in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, density of supercritical CO$_{2}$ is usually lower than hydrocarbons, thus viscous fingering and/or channelling may occur.
+Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of a reservoir \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$-flooding $\left(\text{\ie in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, viscosity of supercritical CO$_{2}$ is lower than crude oil, thus viscous fingering and/or channelling may occur.
 
@@
 %Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
-When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.
+When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and fingers start to form.
 
@@
 More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size the development flow only depends on the capillary number.
-Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
+For a Hele-Shaw cell of a given size, flow development depends only on the capillary number.
+Thus if \textit{$N_{c}$} is too high, \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
 
@@
  Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
+During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations at the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
 In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
@@
  that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
 
@@
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-At this point it should be mentioned that there are two parameters, the Peclet number (Pe) and mobility ratio (M), that determine the stability characteristics.
+At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the stability characteristics.
 There are always a few dominant fingers that spread and shield the growth of other fingers.
@@
 One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width while the concentration gradient of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
+In the process, the finger reaches a critical width while the saturation %concentration gradient
+of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
 Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 In the process, the finger reaches a critical width while the saturation %concentration gradient
-of its front becomes steep as a result of stretching caused by the cross-flow; thus causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
+of its front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
 Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
@@
 \medskip
-In the next section \ref{section:results_setup} is an introduction to the model that will be used followed by section \ref{section:results_initial_model_validation} will be discussed.
-Multi-fluid simulations are performed to numerically investigate (a) the impact of heterogeneity (here represented by spatially-dependent permeability) on the onset and propagation of viscous instabilities (Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}) (b) flow pathways in 3D heterogeneous systems (Section \ref{section:results_3D}).
+In the next section, the numerical formulation used to simulate multi-fluid flow in porous media is briefly validated (Section \ref{section:results_initial_model_validation}) against laboratory experiments (qualitative validation).
+The impact of VR (quantitative validation) and heterogeneity on the onset instability and growth of fingers are numerically investigated in Section \ref{section:results_homo_hete}.
+Section \ref{section:results_hete_fix_adapt} demonstrates the importance of an appropriate mesh resolution to adequately capture the initial stages of viscous fingers formation and development.
+Finally, flow pathway (channelling) is the focus of Section \ref{section:results_3D}.
 
@@
 \subsection{Model Set-up}\label{section:results_setup} 
-Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
 This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
@@
 An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{\circ}\right)$.
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial discontinuities of permeability distribution will create a rough pressure field, \ie the pressure gradient is discontinuous across the interface between different permeability zones thus the flow will be lead to the high permeability region.
-Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
+The spatial permeability distribution creates a rough pressure field, \ie pressure gradient is discontinuous across the interface between different permeability zones, thus the fluid flows to the larger permeability region.
+%Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
 
@@
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
-A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties such as porosity and permeability is initially simulated. During the displacement
-of one phase by another, fluids may crossflow between adjacent layers, due to any combination of the viscous, capillary and/or gravitational forces which drive multiphase flow.
-In this set of simulations, crossflow caused by viscous forces, which is commonly termed viscous
-crossflow is investigated.
+A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
+During the fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces that drive the flow.
+In this numerical simulation, crossflow is caused by viscous forces, which is commonly named viscous crossflow.
 Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
 They also demonstrate the preferential flow path through high-permeability regions.
-Such flow behaviour, represented by the crossflow through the four regions, is a good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+Such flow behaviour, represented by the crossflow through the four regions, is in good qualitative agreement with experiments conducted by \citet{dawe_2008}.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{Flow Simulations in Hele-Shaw Cells at Different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
-In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work by \citet{saffman_1986}.
+In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work of \citet{saffman_1986}.
 In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.
@@
 Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratio of 10 and 150.
+However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratios of 10 and 150.
 

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
-As can been seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
+As it can be seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
 
@@
 \medskip
-In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
+In Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
 Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}.
+The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}).
 
 \medskip
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
+A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 of tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
 Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \section{Conclusions}\label{Section:Conclusion}
-\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
-The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development.
+% Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
+The purpose of this paper is to numerically investigate the dynamics of viscous flow instabilities in porous media.
+Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
+The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
+Saturation and other scalar fields (e.g., density, temperature etc) are discretised in CV space and may be fully discontinuous across finite element boundaries.
+Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface .In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
+
 Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \section{Conclusions}\label{Section:Conclusion}
-% Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
+% Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;
 The purpose of this paper is to numerically investigate the dynamics of viscous flow instabilities in porous media.
@@
 Saturation and other scalar fields (e.g., density, temperature etc) are discretised in CV space and may be fully discontinuous across finite element boundaries.
-Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface .In order to strongly enforce the discretised Darcy equation in the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, the numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
+%Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface.
+In order to strongly enforce discretised Darcy equations at the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
+
+%(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
 
@@
 
-\red{(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);}
 \medskip

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the stability characteristics.
+At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
 There are always a few dominant fingers that spread and shield the growth of other fingers.
@@
 Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
+Studies by \citet{langtangen_1992} on fluid flow dynamics in heterogeneous porous media (analytical and numerical solutions) demonstrated that hyperbolic Buckley-Leverett model is inherently unstable, \ie the expected uniform interface front collapses as any perturbation in physical parameters are imposed to the problem.
+
 Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
@@
 Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
-The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and the novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
-Saturation and other scalar fields (e.g., density, temperature etc) are discretised in CV space and may be fully discontinuous across finite element boundaries.
+The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and a novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
+Saturation and other scalar fields are discretised in CV space and may be fully discontinuous across finite element boundaries.
 %Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface.
 In order to strongly enforce discretised Darcy equations at the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
+
+During immiscible multi-fluid flow displacements, the expected uniform front is perturbed if fluids have different densitites and/or viscositiesleading to an uneven front with elongations at the outside edge of the fluid interface
+
+viscous fingering occurs when the viscosity ratio is greater than unity. As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
 

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 % Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;
-The purpose of this paper is to numerically investigate the dynamics of viscous flow instabilities in porous media.
+During immiscible multi-fluid flow displacements, the expected uniform front becomes unstable due to: (a) density ratio; (b) viscosity ratio, and; (c) heterogeneity.
+If viscosity ratio is relatively large (VR$\ge$3), surface tension becomes weak and the interface between two fluids is unstable in the presence of tangential velocity discontinuities, leading to the formation of fingers \citep{saffman_1986}.
+Heterogeneity in the porous media domain  also leads to solution instabilities in the hyperbolic Buckley-Leverett problem \citep{langtangen_1992}.
+This paper aims to numerically investigate the dynamics of viscous flow instabilities in porous media triggered by permeability heterogeneity.
+
 Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
@@
 Saturation and other scalar fields are discretised in CV space and may be fully discontinuous across finite element boundaries.
-%Material absolute permeability is piecewise constant in FE space to ensure the correct representation of the surface.
 In order to strongly enforce discretised Darcy equations at the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
 
-During immiscible multi-fluid flow displacements, the expected uniform front is perturbed if fluids have different densitites and/or viscositiesleading to an uneven front with elongations at the outside edge of the fluid interface
+ is perturbed if fluids have different densitites and/or viscositiesleading to an uneven front with elongations at the outside edge of the fluid interface
 

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150 -- (Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}).
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150) -- Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}.
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
@@
 
- is perturbed if fluids have different densitites and/or viscositiesleading to an uneven front with elongations at the outside edge of the fluid interface
+%(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
+The numerical formulation was initially validated against laboratory experiments \citep{dawe_2008} to qualitatively assess model functionality to simulate crossflow (\ie preferential flow pathways) in a chequerboard permeability domain.
+Formation and development of viscous fingers in Hele-Shaw cells (homogeneous domain) were investigated to demonstrate that the onset of interface flow instability occur when VR$\ge$3.
+Maximum dendritic finger widths obtained from numerical simulations performed with VR=10 and VR=150 largely agree with expected parametric analytic solutions \citep{mclean_1981,guan_2003}.
+However, when perturbations are imposed into the domain geophysical properties, \ie spatial variability of absolute permeability, numerical solutions partially agree with analytic solutions.
+This may be due to the domain homogeneity assumption in the analytic solution (Eqns.~\ref {eqn:guaneqn}).
 
-viscous fingering occurs when the viscosity ratio is greater than unity. As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-
-%(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
-
-Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.
+analytic solution seems to overestimate maximum finger widths as theoverestimate   dendritic finger branching start to form as predicted by \citep{mclean_1981}. However
 

### 2018-02-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Maximum dendritic finger widths obtained from numerical simulations performed with VR=10 and VR=150 largely agree with expected parametric analytic solutions \citep{mclean_1981,guan_2003}.
-However, when perturbations are imposed into the domain geophysical properties, \ie spatial variability of absolute permeability, numerical solutions partially agree with analytic solutions.
+However, when perturbations are imposed into the domain's geophysical properties, \ie spatial variability of absolute permeability, numerical solutions partially agree with analytic solutions (Table~\ref{table:Heleshaw}).
 This may be due to the domain homogeneity assumption in the analytic solution (Eqns.~\ref {eqn:guaneqn}).
 
-analytic solution seems to overestimate maximum finger widths as theoverestimate   dendritic finger branching start to form as predicted by \citep{mclean_1981}. However
+Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flows.
+Mesh resolution is thus crucial to capture flow dynamics, and adaptive dynamic mesh is
 

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flows.
-Mesh resolution is thus crucial to capture flow dynamics, and adaptive dynamic mesh is
+Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
+Mesh resolution is thus crucial to investigate Saffmann-Taylor instabilities, and adaptive dynamic mesh has proved to be an efficient tool to capture initial interface perturbations.
+Numerical simulations were performed with VR=10 using fixed and adaptive \PN[1]{2} element-pairs.
+Results (Figs.~\ref{fig:5regions_plottimenodeselements} and~\ref{fig:5regions_AdaptZoom}) demonstrated that by dynamically adapting the mesh to follow saturation gradients (\ie fluids interfaces), early-onset flow instability can be readily captured with further formation of long multi-fluid fingers which have themselves split into sub-fingers (see Figs.~\ref{fig:5regions_fixedmesh}i and~\ref{fig:5regions_adaptmesh}i).
 

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \subsection{3-D channel flows} \label{section:results_3D} 
-In geological formations, preferential flow may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in oil/gas exploration fields).
-In this Section, 3D simulations are introduced to investigate preferential flow pathways through semi-pervious and impervious geological layers.
+In geological formations, preferential pathways flows may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in water-, CO$_{2}$- and/or polymer-flooding operations in oil/gas field exploration).
+In this Section, 3D simulations are conducted to investigate preferential flow pathways through semi-pervious and impervious geological layers.
 
@@
 Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
-Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$.
+
+The computational domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs, Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability $\left(\text{10}^{-4}\le\mathbf{K}\le\text{10}^{5}\text{ milidarcy}\right)$.
+Pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$ from the left-hand side face.
 No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
 Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+%The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
 
@@
 Results (Figs.~\ref{fig:5regions_plottimenodeselements} and~\ref{fig:5regions_AdaptZoom}) demonstrated that by dynamically adapting the mesh to follow saturation gradients (\ie fluids interfaces), early-onset flow instability can be readily captured with further formation of long multi-fluid fingers which have themselves split into sub-fingers (see Figs.~\ref{fig:5regions_fixedmesh}i and~\ref{fig:5regions_adaptmesh}i).
+Overall computational cost of the simulation conducted with dynamically adapting the mesh were significantly smaller than the simulation conducted with fixed mesh (Figs.~\ref{fig:5regions_plottimenodeselements}).
 

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\medskip
-As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
+%\medskip
+%As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
 Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
 
-The computational domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs, Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability $\left(\text{10}^{-4}\le\mathbf{K}\le\text{10}^{5}\text{ milidarcy}\right)$.
+The computational domain with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
 Pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$ from the left-hand side face.
 No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
-Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress.
-%The domain (with 235242 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}).% as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
+Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was continuously displaced by the wetting fluid as the simulation progress.
+
+As demonstrated in the preliminary model validation (Section~\ref{section:results_initial_model_validation}), crossflow towards the upper region of the initial part of the domain is due to boundary pressures and diffusivities (both at different vertical layers), \ie caused by large permeability gradients (Fig.~\ref{fig:3DChannel_sat}).
+As the simulation progresses, non-wetting fluid is driven from regions with lower fluid resistance (central channel), although adjacent region (with low permeability) remains stagnant (Fig.~\ref{fig:3DChannel_planes}).
 

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was continuously displaced by the wetting fluid as the simulation progress.
+The domain was discretised with 235k tetrahedral \PNDG[1]{1} element-pairs.
 
 As demonstrated in the preliminary model validation (Section~\ref{section:results_initial_model_validation}), crossflow towards the upper region of the initial part of the domain is due to boundary pressures and diffusivities (both at different vertical layers), \ie caused by large permeability gradients (Fig.~\ref{fig:3DChannel_sat}).
-As the simulation progresses, non-wetting fluid is driven from regions with lower fluid resistance (central channel), although adjacent region (with low permeability) remains stagnant (Fig.~\ref{fig:3DChannel_planes}).
+As the simulation progresses, non-wetting fluid is driven from regions with lower fluid resistance (central channel), although adjacent region (with low permeability) remains stagnant.
 
-\medskip
-Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
-Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.
+Such preferential flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
+Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) is not effectively displaced.
 
-\medskip
 In Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
-Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.
 The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}).
@@
 \medskip
-A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 of tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
-Distinct preferable flow pathways can be shown (Fig.~\ref{fig:3DChannel_severalfields_adapt}c), in particular through the central channel (see streamlines in Fig.~\ref{fig:3DChannel_severalfields_adapt}b) and at the top of the domain.
+A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh.
+During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
+Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_severalfields_adapt}b-c and~\ref{fig:3DChannel_satvel_XYplanes_adapt}.
+Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}.
+As expected, both simulations (fixed and adaptive mesh, Figs.~\ref{fig:3DChannel_sat} and~\ref{fig:3DChannel_sat_adapt}, respectively) led to similar results, \ie similar flow pathways and fingers development.
+
+However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
 

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
-Mesh resolution is thus crucial to investigate Saffmann-Taylor instabilities, and adaptive dynamic mesh has proved to be an efficient tool to capture initial interface perturbations.
+Mesh resolution is thus crucial to investigate Saffmann-Taylor instabilities, and adaptive dynamic mesh technology has proved to be an efficient tool to capture initial interface perturbations.
 Numerical simulations were performed with VR=10 using fixed and adaptive \PN[1]{2} element-pairs.

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Numerical simulations were performed with VR=10 using fixed and adaptive \PN[1]{2} element-pairs.
-Results (Figs.~\ref{fig:5regions_plottimenodeselements} and~\ref{fig:5regions_AdaptZoom}) demonstrated that by dynamically adapting the mesh to follow saturation gradients (\ie fluids interfaces), early-onset flow instability can be readily captured with further formation of long multi-fluid fingers which have themselves split into sub-fingers (see Figs.~\ref{fig:5regions_fixedmesh}i and~\ref{fig:5regions_adaptmesh}i).
-Overall computational cost of the simulation conducted with dynamically adapting the mesh were significantly smaller than the simulation conducted with fixed mesh (Figs.~\ref{fig:5regions_plottimenodeselements}).
+Results (Figs.~\ref{fig:5regions_plottimenodeselements} and~\ref{fig:5regions_AdaptZoom}) demonstrated that by dynamically adapting the mesh to follow saturation gradients (\ie fluids interfaces), early-onset flow instability and further formation of long multi-fluid fingers, which have themselves split into sub-fingers, can be readily captured (see Figs.~\ref{fig:5regions_fixedmesh}i and~\ref{fig:5regions_adaptmesh}i).
+Overall computational cost of the simulation conducted with dynamically adapting the mesh were significantly smaller than the simulation conducted with fixed mesh as indicated by the number of elements/nodes (Figs.~\ref{fig:5regions_plottimenodeselements}).
 
+Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious/impervious channelised domain were performed.
+Numerical data indicated preferential flow through regions of larger permeability leaving adjacent region (with low permeability) with nearly stagnant fluids (Figs.~\ref{fig:3DChannel_sat}-~\ref{fig:3DChannel_planes}).
+Order 0f the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
+\medskip
+
+% (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
+
+\begin{comment}
 \medskip
@@
 \red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
-
+\end{comment}
 \section{Acknowledgements}

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 % (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
+Through
 
-\begin{comment}
-\medskip
+\begin{comment}\medskip
 By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR).

### 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Final updates from Jeff

@@
 
-\clearpage
+%\clearpage
 
@@
 
-However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
+However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,salinas_2018,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
 
@@
 
-Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious/impervious channelised domain were performed.
+Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious / impervious channelised domain were performed.
 Numerical data indicated preferential flow through regions of larger permeability leaving adjacent region (with low permeability) with nearly stagnant fluids (Figs.~\ref{fig:3DChannel_sat}-~\ref{fig:3DChannel_planes}).
-Order 0f the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
+Order of accuracy of the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
 \medskip
@@
 % (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
-Through
+This work focuses on complexity associated with flow channelling and instability dynamics in heterogeneous porous media.
+Methods used to simulate such flows are based in a novel high-order CVFEM formulation that accurately preserves sharp fluid saturation gradients associated with contrasting permeability distribution.
+Future work will include numerical investigation of (a) crossover from capillary fingering (at low fluid velocity) to viscous fingering for immiscible unstable flows, and (b) coupled viscous and density fingering in miscible fluid flows.
 

### 2018-02-09 Papers/ViscousInstabilities/article_table.tex
do not rush kostas
Updates on Section 4.5
kostas speed up do not rush
Correction
updates
Final updates from Jeff

@@
     \hline
-      {\bf Section} & $\phi$ & VR  & $S^{0}_{w}$ & $S^{0}_{nw}$ & $\mathbf{K}_{1}$ & $\mathbf{K}_{2}$ & $\mathbf{K}_{3}$ & $\mathbf{K}_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{\circ}_{w}$ \\ 
+      {\bf Section} & $\phi$ & VR  & $S^{\circ}_{w}$ & $S^{\circ}_{nw}$ & $\mathbf{K}_{1}$ & $\mathbf{K}_{2}$ & $\mathbf{K}_{3}$ & $\mathbf{K}_{4}$ & $S_{w,irr}$ & $S_{nw,r}$ & $u^{\circ}_{w}$ \\ 
     \hline
-     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
+     \ref{section:results_initial_model_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
      \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & 0.5  \\
-     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
-      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
+     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.0e-11 -- & 1.0e-12 -- & 1.0e-12 -- & 1.0e-10 & 0.2  & 0.3 & 1.0 \\
+      &   &  &  &  & 5.0e-10 & 5.0e-10 & 1.0e-10  &  &  &  & \\
      \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & 0.5  \\
-     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & 0.5  \\
+     \ref{section:results_3D}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & 0.5  \\
      \hline
@@
 Superscript $\circ$ denotes initial condition.
-$\mathbf{K}_{i}$ is in $m^{2}$ and $u^{\circ}_{w}$ is in m/sec (units).
+$\mathbf{K}_{i}$ is in $cm^{2}$ and $u^{\circ}_{w}$ is in cm.s$^{-1}$.
 $S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.
-}
+\red{KOSTAS: PLEASE MAKE SURE THAT ALL DATA IS UPDATED...} }
 \label{table:setup}
@@
 %%%
+\begin{landscape}
 \begin{table}
@@
   \end{tabular}
-   \caption{Flow simulations in Heleshaw cells (Section~\ref{section:results_homo_hete}): summary of finger width calculations using Eqn.~\ref{eqn:guaneqn} and obtained through numerical simualtions.
+   \caption{Flow simulations in Heleshaw cells (Section~\ref{section:results_homo_hete}): summary of finger width calculations using Eqn.~\ref{eqn:guaneqn} and obtained through numerical simulations.
 $\lambda_{f}^{\text{calc}}$ was calculated based on fingers' tip velocities and outflow rate.

### 2018-03-07 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Starting new paper

--- 2018-02-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \newcommand{\green}{\textcolor{green}}
-\journal{Advances in Water Resources}
 \newcommand{\frc}{\displaystyle\frac}
@@
 \newcommand{\ie}{{\it i.e., }}
+
+\journal{Applied Mathematical Modelling}
 
@@
 
-  \title{ Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media}%.
-Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.}
-  %% Tittle was too long and 'Advantages and limitations unstructured and adaptive meshes' would mean a full numerical analysis on these 2 issues ...
-we haven't fully studied flows in either  unstructured / structured or adaptive / fixed meshes ...
-
-%% use optional labels to link authors explicitly to addresses:
-\author[UoA]{K. Christou} \author[UoA,UFRGS]{W.C. Rad\"unz}  \author[UoA]{B. Lashore} \author[UESC]{F.B.S. de Oliveira}
-\author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
-
+  \title{ Numerical Investigation of Stochastic and Determininstic Upscaling Methods for Permeability Fields; Using SVD}
+\author[UoA]{Babatunde Lashore} \author[UoA]{J.L.M.A. Gomes}
 \cortext[cor1]{Corresponding author.}
 \address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
-\address[UFRGS]{Engineering School, Federal University of Rio Grande do Sul, Brazil}
-\address[UESC]{Department of Exact and Technological Sciences, State University of Santa Cruz, Bahia, Brazil}
 
 \begin{abstract}
-%CAUSE --> EFFECT --> MOTIVATION (P1)
-  A critical aspect of multiphase flow in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
-Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
-Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
-%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
-Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers mostly depends on mobility ratio and capillary number, however heterogeneity of the porous domain may also affect the onset of instabilities.
-Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-%CAUSE --> EFFECT --> FEW TECHS USED  (P3)
-The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} specially tailored for Darcean flows.
-Dynamic mesh adaptivity enables capturing fingers development whilst saving computational overheads.
-Numerical experiments were performed to investigate the impact of viscosity ratio and heterogeneity on Saffmann-Taylor instabilities.
-%CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
-Numerical simulations demonstrated that the heterogeneity of the domain triggers the early-onset formation of fingers under prescribed viscosity ratio conditions.
-Also, effective numerical capture of growth (in particular, tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
-
-%In this work, flow instabilities that arise from fluids' viscosity ratio are numerically investigated. 
-%From initial fluid flow studies of the Hele-Shaw experimental apparatus, a mathematically analogous process to the two-dimensional flow in porous media problem, fingers development as a function of mobility ratio (MR), different domain set-up under uniform or different permeabilities regions and mesh types is examined.
-A series of cases are listed, showing the validation of the method against experimental setup followed by a more complex 2D domain setup under different viscosity ratios and different mesh resolutions.
-Finally, a 3D domain setup is showcasing the difference between the preferential flow path and the fingering regimes that will occur in the domain.
-
-%CAUSE --> EFFECT --> FEW TECHS USED  (P3)
-%For the cases mentioned above, a novel control finite element method (CVFEM) is used to discretize the governing equations that will solve the multi-fluid porous media flow model.
-The governing multiphase porous media flow equations are solved using an unstructured mesh by introducing adaptivity in later stages.
-Dynamic mesh adaptivity will not only help to better capture the development of finger but also overcome the computational limitations focusing the effort where is needed, minimizing both the CPU time and the numerical diffusion.
-
-%CAUSE --> EFFECT -->  MAIN FINDINGS  (P4)
-%Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling.
-Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow path can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.
-
+  BlaBlaBla
 \end{abstract}
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
- Multi-fluid flows \sep Porous media \sep Viscous Instabilities \sep Mobility Ratio.
+Singular Value Decomposition, SVD\sep Upscaling\sep Model Order Reduction, MOD \sep  Principal Component Spaces \sep Permeability field
 \end{keyword}
@@
 
-%\tableofcontents
-%\linenumbers
-
-\clearpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 \section{Introduction}\label{section:intro}
-Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
-%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
-%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+Naturally occuring rock formations are inherently heterogeneous, which means that the rock properties such as permeability, pore spaces ({\it i.e.}, porosity) and pore throat vary from point to point, and at different length scales.
+The heterogeneity of rock formations (studied under the general title of porous media) is relevant in calculations required for understanding transportation and storage of fluids in porous media.
+This is because the heterogeneous properties are important parameters in the mathematical models used for the aforementioned calculations.
+Therefore, the representation of these heterogeneous properties is of great importance to the porous media and applied mathematics community as well as the oil and gas industry, the Carbon Capture and Storage (CCS) industry, and waste management industry for whom this has direct application in reservoir management, CO$_2$ transportation and storage in subsurface rocks and remediation of contaminated soil respectively.
 
-\medskip
-%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
-Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
-%Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
-% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
-SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-%The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
+Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain \citep[\ie scale problems,][for further details]{Renard_1997} \cite{miller_1998} \citet{chen_2006}.
+This is particularly true for large geological domains which span several kilometres.
+Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems).
+It is possible to overcome these challenges by upscaling.
+Upscaling techniques solve both problems by replacing discrete geological and fluid property values of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+And upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain gives the best representation of the heterogeneous property.
 
-\medskip
-In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+There are several upscaling techniques which fall under different categories \cite{Renard_1997, Szymkiewicz_2013, Hasting_2001}, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Verwoerd_2009, Ravalec-Dupin_2010, Guilleminot_2012}.
+One of the reasons for this is because stochastic techniques are robust enough to handle multiphase flow in porous media, and they address scale and uncertainity problems which were previously mentioned.
 
-\medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+This work couples stochastic and deterministic upscaling representations of the permeability field to a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) so as to investigate statistical properties and multiphase flow behaviour in highly heterogeneous porous media.
 
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
-%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+Four upscaling techniques are investigated in this research.
+The arithmetic and harmonic mean are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
+The third is a randomly generated permeability field with a Guassian distribution, prescribed by a probability density function (PDF) which was obtained from a base case ({\it i.e.}, high-resolution mesh with known permeability distribution).
+The four upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using interpolation within the concept of principal component space to reduce the order of the permeability field.
 
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
+In section 2, the basic mathematical explanation of SVD and its associated linear algebra properties are presented.
+The the concept of spaces is explained from the engineer's perspective and also from the mathematician's perspective.
+The objective of this explanation is to assist both parties in visualizing the relevant spaces and performing the necessary transformation within those spaces.
+Finally, the section describes model order space reduction for the permeability field within the principal component space.
+Section 3, starts by describing the high resolution base case on which the four upscaling techniques are modelled.
+The the simulation run which is similar for all the cases/models is described.
+A brief summary of the pre-processing step for each of the models is also presented.
+Section 4 provides the results of for the simulations, Section 5 discusses the results of the simulations and gives further intepretation to the result obtained from the SVD upscaling techniques; and section 6 provides the conclusion.
 
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation} 
-%\end{comment}
-%%%%%%%%%%%%%%%
+\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}
 
-\medskip
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
-%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
-
-\medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
-Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
-Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Formulation}\label{equations_scheme}      
-%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Different domains will produce different flow instabilities.
-In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
-DG-methods combine advantages of classical finite volume and finite element methods.
-
-%\subsection{Numerical Formulation}
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-%\begin{equation}\label{e:darcy_eq}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_bal}
-%\end{equation}
-%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-%\begin{equation}
-%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-%\end{equation}
-%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-%\begin{eqnarray}
-%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-%\label{v_and_p}
-%\end{eqnarray}
-
-%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_balance}
-%\end{equation}
-
-%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-%\end{comment}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\label{e:darcy_eq}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-%\label{E:darcy_eqn}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
-% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-%\begin{equation}
-%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:darcy_ext}
-%\end{equation}
-%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-The two-phase immiscible and incompressible fluid flow through a porous media domain $\Omega$, may be described by the coupled extended Darcy and saturation equations,
-
-\begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
-\end{eqnarray}
-
-\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
-%\begin{displaymath}
-%\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1, 
-%\end{displaymath}
-%where $\mathcal{N}_{p}$ denotes the number of phases.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The main equations that will be used along with the following OCVFEM techique can be summarised below.
-The global mass balance equation and force balance equation are solving by vanishing the velocity term and solving the system of equations for pressure.
-At the $n+1$ step those two equations mentioned above can be rewritten as,
-
-%\begin{equation}
-%M_{\sigma} {{\underline{u}}^{n+1}} = C {\underline{p}^{n+1}} + {\underline{s}_u ^{n+1}}
-%\label{e:mass_bal}
-%\end{equation}
-
-%\begin{equation}
-%B^T {{\underline{u}}^{n+1}} = {\underline{s}_p ^{n+1}}
-%\label{e:force_bal}
-%\end{equation}
-
-%\noindent Application of a discontinuous FEM for velocity leads to a block-diagonal $M_{\sigma}$ matrix that can be readily inverted, each block being local to an element.
-This system of equations can be rewritten to produce the pressure equation,
-
-%\begin{equation}
-%B^T M_{\sigma} ^{-1} C{{\underline{p}}^{n+1}} = {\underline{s}_p ^{n+1}} - B^T M_{\sigma} ^{-1} {{\underline{s}}^{n+1}} 
-%\label{e:pressure_eq}
-%\end{equation}
-
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
-In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
-Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
-
-Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively -- note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
-Each component of the weak form of the extended Darcy equation is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:
-\begin{eqnarray}
-  \sum\limits_{E} \left.
-\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
-+ \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
-  \oint_{\Gamma_{\Omega}} {Q}_i {\mathbf n} \left(p - p_\text{bc}\right) d\Gamma = \bm{0},
-                   \label{force-semi-disc} 
-\end{eqnarray} 
-where $\Omega_E$ and $\Gamma_{E}$ are the volume and boundary of element $E$, respectively, and $\Gamma_{\Omega}$ is the boundary of the computational domain.
-The numerical pressure $\tilde{p}$ appearing in the jump condition (second term in Eqn.~\ref{force-semi-disc}) is the arithmetic mean of the potentially discontinuous pressure across the element $E$ $\left(\text{consistent with the \PNDG[n]{m} element-pairs}\right)$.
-This term vanishes when a continuous formulation is used to discretise the pressure field $\left(\text{with \PN[n]{m} element-pairs}\right)$.
-The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
-%Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
-Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-$\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces, and lies in both CV and FEM spaces.
-%\begin{displaymath}
-%   \underline{\underline{\sigma}}_{\alpha} = \displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}.
-%\end{displaymath}
-
-\medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
-Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
-Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
-\begin{eqnarray}
- && \sum_{\alpha=1}^{N_{p}} \left\{\int\limits_{\Omega_{CVi}} \; M_{i} \; \frac{\phi\left(S_{\alpha i}^{n+1}-S_{\alpha i}^{n}\right)}{\Delta t} dV\right.  + \nonumber\\
- &&  \oint_{\Gamma_{CVi}} \left[\; \theta^{n+1/2}\; {\mathbf n}\cdot {\mathbf u}_{\alpha}^{n+1}S_{\alpha}^{n+1} \; + \; \left(1-\theta^{n+1/2}\right) \; {\mathbf u}_{\alpha}^{n}S_{\alpha}^{n}\right] d\Gamma \;- \nonumber\\
- &&  \left.\int_{\Omega_{CVi}} M_{i} \; \mathcal{S}_{cty,\alpha}^{n+\theta} \; dV\;\right\} =0,
-\label{global_mass_balance}
-\end{eqnarray}
-
-%This formulation is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of  FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in control volume (CV).
-In these families of FE-pairs velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields.
-Simulations performed for this work were conducted using two types of elements: \PN[1]{2} and \PN[1]{1}.
-%Saturation, and all saturation-dependent material properties such as relative permeability and capillary pressure, are represented in CV space.
-%Hence, each CV (and FE) is associated with a unique set of petrophysical properties, in contrast to most previous methods in which CVs span multiple values of petrophysical properties described FE-wise.
-
-%For the simulations performed in this work, rock and fluids are assumed incompressible thus the mass balance for phase $\alpha$ can be written as
-%\begin{equation}
-%\phi \; \frac{\partial S_{\alpha}}{\partial t} + \nabla (u_{\alpha}S_{\alpha})= \mathcal{S}_{cty,\alpha} 
-%\label{mass_balance}
-%\end{equation}
-
-%\noindent where $\phi$ represents the porosity, S represents the saturation and v is the saturation weighted Darcy velocity (such that $v_{\alpha}S_{\alpha}$ is the traditional Darcy velocity of phase p), and q is a volume source term, subject to the contrains on the saturation
-
-%\begin{equation}
-%\sum  S_{p}-1
-%\label{saturation_constrain}
-%\end{equation}
-\noindent
-where $\Omega_{CVi}$ and $\Gamma_{CVi}$ are the volume and boundary of CV i respectively, $M_{i}$ are CV basis functions, \textbf{n} is the outward pointing unit normal vector to the surface of $CV_{i}$ and $n$ is the current time level.
-$\theta$ varies smoothly between $0.5$ (corresponding to Crank-Nicolson method) and $1$ (corresponding to backward-Euler scheme) to avoid the introduction of spurious oscillations for large grid Courant numbers.
-
-\medskip
-The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
-The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
-The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
-A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
-Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of a reservoir \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$-flooding $\left(\text{\ie in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, viscosity of supercritical CO$_{2}$ is lower than crude oil, thus viscous fingering and/or channelling may occur.
-
-\medskip
-The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
-%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
-When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and fingers start to form.
-
-\medskip
-Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
-\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
-\begin{equation}
-N_{c} = \frac{\mu U}{\gamma}.
-\label{eq:capillary_number}
-\end{equation}
-
-\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
-This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
-
-\medskip
-More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size, flow development depends only on the capillary number.
-Thus if \textit{$N_{c}$} is too high, \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
-
-\medskip
- Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations at the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
-
-\medskip 
-In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
-\begin{equation} 
-\Delta P= - \gamma \nabla\cdot\hat{n}. 
-\label{eq:pressure_dif} 
-\end{equation}
-
-\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
-
-\medskip
-As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
-\begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
-\label{eq:MR}
-\end{equation}
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \cite{brooks_1964} model was used \citep{alpak_1999},
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
-\begin{displaymath}
-    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
-\end{displaymath}
- that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
-
-\medskip
-In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
-There are always a few dominant fingers that spread and shield the growth of other fingers.
-The interface of the main finger collapses and starts splitting into new lobes of fingers.
-One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width while the saturation %concentration gradient
-of its front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
-Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
-
-\medskip
-In the next section, the numerical formulation used to simulate multi-fluid flow in porous media is briefly validated (Section \ref{section:results_initial_model_validation}) against laboratory experiments (qualitative validation).
-The impact of VR (quantitative validation) and heterogeneity on the onset instability and growth of fingers are numerically investigated in Section \ref{section:results_homo_hete}.
-Section \ref{section:results_hete_fix_adapt} demonstrates the importance of an appropriate mesh resolution to adequately capture the initial stages of viscous fingers formation and development.
-Finally, flow pathway (channelling) is the focus of Section \ref{section:results_3D}.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-%\begin{equation}
-%\lambda = \frac{K\;k_{\alpha}}{\mu}
-%\label{eq:mobility-of-fluid}
-%\end{equation}
-
-%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-%\begin{equation}
-%U = \frac{b^2}{12 \mu} \nabla p
-%\end{equation}
-
-%and the above equation can be re-arranged for 1D steady flow as,
-
-%\begin{equation}
-%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
-%\label{eq:pressure_dif} 
-%\end{equation}
-
-%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-%\begin{equation}
-%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-%\end{equation}
-
-%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
-
-%\begin{equation}
-%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-%\end{equation}
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%\pagebreak
-%\clearpage
-
-%\listoftables 
-%\pagebreak
-%\input{Manuscript_Table}
-
-%\pagebreak
-%\clearpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}\label{section:results}
-
-%%%%%%%%%%%% 
-\subsection{Model Set-up}\label{section:results_setup} 
-Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
-This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
-
-\medskip
-In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
-An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{\circ}\right)$.
-For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
-Fluids are assumed incompressible and gravity was neglected.
-Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
-
-%%%%%%%%%%%% 
-\subsection{Initial Model Validation}\label{section:results_initial_model_validation}
-Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
-Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-Boundary conditions also include no-flux across upper and lower borders.
-The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial permeability distribution creates a rough pressure field, \ie pressure gradient is discontinuous across the interface between different permeability zones, thus the fluid flows to the larger permeability region.
-%Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
-
-\medskip
-%A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
-Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
-A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
-During the fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces that drive the flow.
-In this numerical simulation, crossflow is caused by viscous forces, which is commonly named viscous crossflow.
-Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
-They also demonstrate the preferential flow path through high-permeability regions.
-Such flow behaviour, represented by the crossflow through the four regions, is in good qualitative agreement with experiments conducted by \citet{dawe_2008}.
-
-%%%%%%%%%%%%    
-\subsection{Flow Simulations in Hele-Shaw Cells at Different Viscosity Ratio Conditions}\label{section:results_homo_hete} 
-In order to investigate the impact of viscosity ratio on the flow dynamics, numerical simulations of fluid displacement were conducted in Hele-shaw cells following the work of \citet{saffman_1986}.
-In this manuscript, the onset of viscous flow instabilities \citep[following his seminal work in][]{saffman_1958} is investigated along with the impact of boundary conditions in the problem's mathematical formulation and solutions.
-
-\medskip
-Here, 2D simulations were conducted in a 5$\times$5 cm domain (Fig.~\ref{fig:homoheleshaw_VN3}a) fully saturated with a fluid.
-Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
-
-\medskip
-Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
-At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
-Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region.
-However, formation of fingers can be readily noticed at early stages of simulations conducted with viscosity ratios of 10 and 150.
-
-\medskip
-Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}.
-They conducted a sensitivity analysis to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,
-\begin{equation}   
-   \mathcal{Q} = U_{f} b \lambda_{f}.\label{eqn:guaneqn} 
-\end{equation}
-
-\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
-This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
-
-\medskip
-Fluid flow dynamics through heterogeneous porous media are sensibly more complex than in homogeneous media and strongly depend on problem properties.
-Studies by \citet{langtangen_1992} on fluid flow dynamics in heterogeneous porous media (analytical and numerical solutions) demonstrated that hyperbolic Buckley-Leverett model is inherently unstable, \ie the expected uniform interface front collapses as any perturbation in physical parameters are imposed to the problem.
-
-Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
-Such multi-scale heterogeneity induces preferential flow pathways and plays a significant role in the onset of fluid instabilities as it triggers fingers formation and their accelerated growth \citep[see][]{ewing_1989,tchelepi_1994}.
-
-\medskip
-In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases(Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
-
-\medskip
-Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150) -- Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}.
-Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
-
-%%%%%%%%%%%%%
-\subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}    
-%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
-Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
-
-\medskip
-In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
-In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
-As it can be seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.
-
-\medskip
-Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
-Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
-In these methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) to focus resolution where is necessary as the simulation evolves in time and space.
-There are four main families of mesh adaptivity methods: adaptive mesh refinement (AMR), edge and face element manipulations whereas keeping the order of the element basis function fixed (h-adaptivity), mesh deformation (r-adaptivity) and changes of element basis function order (p-adaptivity).
-Detailed description and analysis of mesh adaptivity methods are beyond the scope of this manuscript but can be readily found in \citet{lo_book} \citep[see also][]{plewa_book,frey_book}.
-
-\medskip
-The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
-The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
-In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
-
-\medskip
-Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
-In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
-A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
-Viscosity ratio was set to 10.
-
-\medskip
-Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive meshes.
-Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
-In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
-The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$.
-In regions with no permeability gradient, formation and development of fingers (Fig.~\ref{fig:5regions_AdaptZoom}c) were not captured by the simulation conducted with fixed mesh.
-In both cases, dynamic adaptive mesh based on perturbation of phase saturations with imposed interpolation error estimate proved to be able to capture the onset of instabilities and fingers' development with relatively little computational overhead, as indicated in Fig.~\ref{fig:5regions_plottimenodeselements}.
-
-%%%%%%%%%%%%%
-\subsection{3-D channel flows} \label{section:results_3D} 
-In geological formations, preferential pathways flows may result in fast polutant transport (advection-diffusion-dispersion) after industrial spillage (therefore leading to contamination of groundwater) or low hydrocarbon recovery rates (in water-, CO$_{2}$- and/or polymer-flooding operations in oil/gas field exploration).
-In this Section, 3D simulations are conducted to investigate preferential flow pathways through semi-pervious and impervious geological layers.
-
-%\medskip
-%As outlined in Section \ref{section:ViscousInstabilities}, viscous flow instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers.
-Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
-
-The computational domain with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
-Pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$ from the left-hand side face.
-No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
-Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was continuously displaced by the wetting fluid as the simulation progress.
-The domain was discretised with 235k tetrahedral \PNDG[1]{1} element-pairs.
-
-As demonstrated in the preliminary model validation (Section~\ref{section:results_initial_model_validation}), crossflow towards the upper region of the initial part of the domain is due to boundary pressures and diffusivities (both at different vertical layers), \ie caused by large permeability gradients (Fig.~\ref{fig:3DChannel_sat}).
-As the simulation progresses, non-wetting fluid is driven from regions with lower fluid resistance (central channel), although adjacent region (with low permeability) remains stagnant.
-
-Such preferential flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
-Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) is not effectively displaced.
-
-In Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
-The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces (Fig.~\ref{fig:3DChannel_Isosurf}).
-
-\medskip
-A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh.
-During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
-Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_severalfields_adapt}b-c and~\ref{fig:3DChannel_satvel_XYplanes_adapt}.
-Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}.
-As expected, both simulations (fixed and adaptive mesh, Figs.~\ref{fig:3DChannel_sat} and~\ref{fig:3DChannel_sat_adapt}, respectively) led to similar results, \ie similar flow pathways and fingers development.
-
-However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
-
-%For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
-At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-%In figures \ref{fig:3DChannel_sat_adapt}(a)-(f) an unstructured and adaptive mesh has been introduced in order to achieve higher resolution and focus the computational effort where is needed in he domain.
-For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created.
-At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
-%\medskip
-%A quick review to the mechanisms of viscous fingering (\ie shielding, spreading and tip-splitting, \citet{homsy_1987}) is required.
-In all the $2$D previous cases (sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}), as interfacial surface tension (IFT) becomes weak, the front of the steady finger is susceptible to a viscous-fingering instability.
-Through \textit{shielding} mechanism, one of these fingers will eventually outgrow the other and, will then spread (\textit{spreading}) to occupy the appropriate width of the domain ahead of it.
-Following this process, it reaches a width that is again unstable and the pattern repeats.
-So far shielding and spreading were dominating the flow but, using the current $3$D domain and by applying two types of meshes, despite the resolution restrictions, the conditions and the mechanics of tip-splitting along a front can be qualitatively understood.
-
-%%%%%%%%%%%%%
-\section{Conclusions}\label{Section:Conclusion}
-% Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;
-During immiscible multi-fluid flow displacements, the expected uniform front becomes unstable due to: (a) density ratio; (b) viscosity ratio, and; (c) heterogeneity.
-If viscosity ratio is relatively large (VR$\ge$3), surface tension becomes weak and the interface between two fluids is unstable in the presence of tangential velocity discontinuities, leading to the formation of fingers \citep{saffman_1986}.
-Heterogeneity in the porous media domain  also leads to solution instabilities in the hyperbolic Buckley-Leverett problem \citep{langtangen_1992}.
-This paper aims to numerically investigate the dynamics of viscous flow instabilities in porous media triggered by permeability heterogeneity.
-
-Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
-The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and a novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
-Saturation and other scalar fields are discretised in CV space and may be fully discontinuous across finite element boundaries.
-In order to strongly enforce discretised Darcy equations at the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
-
-%(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
-The numerical formulation was initially validated against laboratory experiments \citep{dawe_2008} to qualitatively assess model functionality to simulate crossflow (\ie preferential flow pathways) in a chequerboard permeability domain.
-Formation and development of viscous fingers in Hele-Shaw cells (homogeneous domain) were investigated to demonstrate that the onset of interface flow instability occur when VR$\ge$3.
-Maximum dendritic finger widths obtained from numerical simulations performed with VR=10 and VR=150 largely agree with expected parametric analytic solutions \citep{mclean_1981,guan_2003}.
-However, when perturbations are imposed into the domain's geophysical properties, \ie spatial variability of absolute permeability, numerical solutions partially agree with analytic solutions (Table~\ref{table:Heleshaw}).
-This may be due to the domain homogeneity assumption in the analytic solution (Eqns.~\ref {eqn:guaneqn}).
-
-Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
-Mesh resolution is thus crucial to investigate Saffmann-Taylor instabilities, and adaptive dynamic mesh technology has proved to be an efficient tool to capture initial interface perturbations.
-Numerical simulations were performed with VR=10 using fixed and adaptive \PN[1]{2} element-pairs.
-Results (Figs.~\ref{fig:5regions_plottimenodeselements} and~\ref{fig:5regions_AdaptZoom}) demonstrated that by dynamically adapting the mesh to follow saturation gradients (\ie fluids interfaces), early-onset flow instability and further formation of long multi-fluid fingers, which have themselves split into sub-fingers, can be readily captured (see Figs.~\ref{fig:5regions_fixedmesh}i and~\ref{fig:5regions_adaptmesh}i).
-Overall computational cost of the simulation conducted with dynamically adapting the mesh were significantly smaller than the simulation conducted with fixed mesh as indicated by the number of elements/nodes (Figs.~\ref{fig:5regions_plottimenodeselements}).
-
-Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious/impervious channelised domain were performed.
-Numerical data indicated preferential flow through regions of larger permeability leaving adjacent region (with low permeability) with nearly stagnant fluids (Figs.~\ref{fig:3DChannel_sat}-~\ref{fig:3DChannel_planes}).
-Order 0f the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
-\medskip
-
-% (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
-
-\begin{comment}
-\medskip
-By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR).
-If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate.
-On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate.
-Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil.
-Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.
-The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells.
-The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
-
-\medskip
-As seen for high viscosity contrast, there is a leading finger (\textit{tip splitting mechanism}) that breaks out of the front by suppressing its growth to the point that smaller fingers will break out driven by surface tension.
-At long times the large finger advances approximately at in a constant flow rate.
-In order to run all these simulations in detail, the use and benefits of dynamic mesh adaptivity to capture the viscous fingering in reservoir flows was introduced for all the $2D$ and $3D$ cases.
-Commercial simulators provide the user with option of an unstructured type of mesh, still they are not able to dynamically adapt the mesh where is needed and manage the computational cost more efficient.
-
-\medskip
-Regarding the flow characteristics and the mechanics of fingering formations,
-
-\begin{enumerate}
-\item[1.] After having separate the cross flow pattern from the viscous finger one, the findings show that the displacing fluid tends to flow easier towards the zones with higher values of permeability, as these can been seen from evolution of fingers in the upper layers of the domains or from longitudinal section througout the Hele-shaw domains.
-\item[2.] Even though different permeability patterns will initially make the uniform front to collapse, it is the \textit{viscocity ratio} the key parameter and the capillary forces as these are related with surface tension that will eventually lead the flow instabilities.
-The higher the viscocity ratio the easier it is for the uniform front of the injected fluid to break into fingers that eventually will decrease the recovery of hydrocarbon content.
-\item[3.] The increased viscosity ratio increases the computational cost and requires the use of smaller time-step sizes. 
-\item[4.] Properties such as porosity and saturation can be readily up-scaled as they can be included in the element boundaries.
-The domains used in these test-cases have the ability to describe the fingering mechanism and the development of the flow \ie the latter case clearly describes the linear tip-splitting finger behaviour inside the domain.
-\end{enumerate}
-
-\red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
-\end{comment}
-\section{Acknowledgements}
-Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
+%\section{Acknowledgements}
+%Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
 Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
@@
 \bibliographystyle{elsarticle-harv} 
+%\bibliographystyle{elsarticle-num}
+%\bibliographystyle{apacite}
 \bibliography{references}
@@
 \clearpage
-\input{article_table}
+%\input{article_table}
 \clearpage  
@@
 \clearpage
-
 \input{article_figure1}

### 2018-03-07 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Solving reference/citation issue

@@
 %
-\documentclass[preprint,authoryear,12pt]{elsarticle}
+%\documentclass[preprint,authoryear,12pt]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
@@
 
-Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain \citep[\ie scale problems,][for further details]{Renard_1997} \cite{miller_1998} \citet{chen_2006}.
+Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain (\ie scale problems) \cite{Renard_1997} \cite{miller_1998} \cite{chen_2006}.
 This is particularly true for large geological domains which span several kilometres.

### 2018-03-13 Papers/AppliedMaths2018/article_figure1.tex

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[h!]
   \vbox{
     \hbox{\includegraphics[width=\columnwidth,clip]{./Pics/PermField_Saturation.png}}
     \hbox{\hspace{4cm}(a)\hspace{7.8cm}(b)}}
        \caption{(a) Permeability distribution and (b) phase saturation showing preferential flow pathways.}
        \label{fig:PermField_Saturation}  
\end{figure}
\clearpage

### 2018-03-13 Papers/Prototype_Merged/Manuscript_IJNMF.tex

@@
 \def\volumeyear{2015}
+
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
 
@@
 \vspace{-2pt}
+
+Numerical modelling of multiphase flow in porous media has applications in a wide range of disciplines, including hydrocarbon and groundwater production, safety assessment of deep geological disposal of radioactive waste, and CO$_{\text{2}}$ migration and trapping in carbon capture and storage ~\cite{chen_2006, aiea_1999, pruess_1990c,jiang_2011}.
+Such geological and geophysical applications often include complex rock geometries with irregular (and often internal) boundaries between rock types with contrasting porosity and permeability.
+Accurately capturing these complex geometries is a key challenge when simulating such flows.
+
+Finite difference methods (FDM) have been extensively used in modelling and simulation of fluid flows in porous media~\cite{aziz_1986, chen_1997, chen_2005}.
+However, they are strongly dependent on mesh quality and orientation, and cannot easily represent complex geometries.
+In addition, FDM can produce excessive numerical dispersion in heterogeneous porous media~\cite{chavent_1986}.
+The geometrical flexibility of finite element methods (FEM) has been shown to overcome these deficiencies.
+Among FEM-based formulations for porous media, the control volume finite element method (CVFEM) has become increasingly popular as it can guarantee local mass conservation and high-order numerical accuracy, as well as being able to use tetrahedral, geometry-conforming elements~\cite{forsyth_1990,cordazzo_2004, geiger_2004, hurtado_2007}.
+\cite{huber_2000} demonstrated that the vertex-centred, finite volume-finite element method (or Box scheme) can achieve similar goals (see also \cite{helmig_1997}).
+
+\cite{durlofsky_1993,durlofsky_1994} compared the performance of a mixed FEM formulation (i.e.
+piece-wise constant in pressure and piece-wise linear in velocity) and the classical CVFEM for single phase Darcy flows.
+He concluded that the latter is more computationally efficient and numerically accurate than the former for problems involving a (relatively) small number of degrees of freedom.
+Moreover, for complex heterogeneous problems with sharp changes in material properties, mixed FEM formulations often lead to physically unrealistic solutions.
+\cite{cumming_2011} demonstrated that a CVFEM-based discretisation could be used to solve the Richards equation (coupled mass conservation and Darcy equations) in heterogeneous porous media with relatively small computational overhead, compared with traditional, coupled velocity-pressure based formulations.
+Mass balance was enforced as described by \cite{kirkland_1992} (see also \cite{forsyth_1990,cumming_phd2012}).
+The efficiency and accuracy of CVFEM for porous media flows has motivated our development of a CVFEM-based discretisation here.
+However, CVFEM often requires high resolution meshes in regions where material properties vary abruptly, such as permeability contrasts at (for example) fracture-matrix interfaces, or boundaries between different rock types.
+Control volume (CV) boundaries span finite elements where material properties are defined; therefore, some average value of the permeability must be calculated across CV interfaces.
+This often leads to excessive numerical dispersion, especially in highly heterogeneous media \cite{nick_2011b, nick_2011a}.
+
+Discontinuity-capturing schemes (e.g.
+shock waves, contact surface or material discontinuities -- see~\cite{brooks_1982,tezduyar_1986}) were originally developed to resolve sharp changes in solution fields such as velocity or saturation.
+Related discontinuity-capturing schemes include the discontinuous-Galerkin FEM (DGFEM) scheme in which continuity of the solution is not explicitly enforced, allowing sharp changes in the solution fields to be captured.
+The DG formulation is a stabilised finite element method that is locally conservative and designed to achieve high-order accuracy.
+DGFEM solution fields are allowed to be discontinuous at the element faces; thus, the solution is able to handle discontinuities in material properties at internal boundaries.
+In addition, DGFEM is well-suited to deal with interface problems by incorporating specially-designed interface fluxes.
+These properties have attracted the attention of the porous media flow community over the past 15 years~\cite{riviere_2000,riviere_2002,bastian_2002} and are utilised here.
+
+In this paper, a novel CVFEM formulation which is conservative and consistent is presented.
+The continuity equations are embedded into the pressure equation to enforce mass conservation and the exact force balance.
+The formulation employs an implicit algorithm with respect to time that is less restrictive than the implicit-pressure-explicit-saturation (IMPES) scheme often adopted in porous media flow problems (see \cite{aziz_1986,geiger_2004}).
+There are two key novel aspects in our approach.
+The first is that it uses a dual consistent CVFEM representation that is embedded in the \PN[n]{m}[DG] family of triangular and tetrahedral finite element pairs \cite{kaisu}.
+For this element type, the velocity field is represented by $n^{\rm th}$-order polynomials that are discontinuous across elements, while the pressure field is represented by $m^{\rm th}$-order polynomials that may be continuous (termed P$_n$DG-P$_m$) or discontinuous (termed P$_n$DG-P$_m$DG) across elements.
+In particular, here the P$_n$DG-P$_{n+1}$ element pair, which allows the velocity to exactly represent the pressure gradients in the flow solution for homogeneous material properties, is demonstrated.
+The \PNDG[n+1]{n} element pair, which has similar properties to the \PN[n]{n+1} element pair, but allows a representation in which pressure, saturation and other solution variables are discontinuous across finite element boundaries, is also demonstrated.
+This solves the long-standing problem described above with respect to the use of traditional CVFEM methods to capture sharp changes in material properties.
+The second key novelty is the velocity representation that is described in detail in Section~\ref{overlapping_method_section} and can achieve an exact representation of the multiphase Darcy force balance equations.
+
+The remainder of this paper is organised as follows.
+The governing equations and numerical methods employed to solve them are presented in Section~\ref{overlapping_method_section}.
+Model set-up and results including comparison against reference data for a series of benchmark problems are given in Sections~\ref{setup} and \ref{res}, respectively.
+Finally, some concluding remarks are presented in Section~\ref{conc}.
+
+\bigskip
+
 Many authors submitting to research journals use \LaTeXe\ to
@@
 \begin{thebibliography}{9}
+%
 
+\bibitem{aiea_1999}
+AIEA, 1999. Use of natural analogues to support radionuclide transport models
+  for deep geological repositories for long-lived radioactive wastes. Tech.
+  rep., AIEA, iAEA-TECDOC-1109.
+
+\bibitem{aziz_1986}
+Aziz, K., Settari, A., 1986. Fundamentals of reservoir simulation. Elsevier
+  Applied Science Publishers, New York.
+
+\bibitem{bastian_2002}
+Bastian, P., 2002. Challenges in Scientific Computing - CISC 2002. Lecture
+  Notes in Computational Science and Engineering. Springer, Ch. Higher Order
+  Discontinuous Galerkin Methods for Flow and Transport in Porous Media.
+
+\bibitem{Brandt}
+Brandt, A., 1977. Multi–level adaptive solutions to boundary-value problems.
+  Mathematics of Computation 31, 333 -- 390.
+
+\bibitem{brooks_1982}
+Brooks, A., Hughes, T., 1982. Streamline upwind {P}etrov-{G}alerkin
+  formulations for convection dominated flows with particular emphasis on the
+  incompressible {N}avier-{S}tokes equations. Comput. Methods Appl. Mech.
+  Engrg. 32, 199--259.
+
+\bibitem{brooks_1964}
+Brooks, R., Corey, A., 1964. Hydrology Papers. Vol.~3. Colorado State
+  University, Ch. Hydraulic properties of porous media.
+
+\bibitem{buckley1942}
+Buckley, S., Leverett, M., 1942. Mechanism of fluid displacements in sands.
+  Transactions of the AIME~(146), 107--116.
+
+\bibitem{chavent_1986}
+Chavent, G., Jaffr\'e, J., 1986. Mathematical Models and Finite Elements for
+  Reservoir Simulation. Vol.~17 of Studies in Mathematics and Its Applications.
+  North Holland.
+
+\bibitem{chen_1997}
+Chen, Z., Ewing, R., 1997. Comparison of various formulations of three-phase
+  flow in porous media. Journal of Computational Physics 132~(2), 362--373.
+
+\bibitem{chen_2006}
+Chen, Z., Huan, G., Ma, Y., 2006. Computational Methods for Multiphase Flows in
+  Porous Media. SIAM.
+
+\bibitem{chen_2005}
+Chen, Z., Huan, G., Wang, H., 2005. Simulation of a compositional model for
+  multiphase flow in porous media. Numerical Methods for Partial Differential
+  Equations 21~(4), 726--741.
+
+\bibitem{cordazzo_2004} 
+Cordazzo, J., Maliska, C., da~Silva, A., Hurtado, F., November 2004. The
+  negative transmissibility issue when using {CVFEM} in petroleum reservoir
+  simulation -- 1. {T}heory. In: Proceedings of the 10th Brazilian Congress of
+  Thermal Sciences and Engineering -- ENCIT 2004. Brazilian Society of
+  Mechanical Engineering -- ABCM, Rio de Janeiro, Brazil.
+
+\bibitem{cumming_phd2012}
+Cumming, B., 2012. Modelling sea water intrusion in coastal aquifers using
+  heterogeneous computing. Ph.D. thesis, Queensland University of Technology,
+  Australia.
+
+\bibitem{cumming_2011}
+Cumming, B., Moroney, T., Turner, I., 2011. A mass-conservative control
+  volume-finite element method for solving {R}ichards' equation in
+  heterogeneous porous media. BIT Numerical Mathematics 51~(4), 845--864.
+
+\bibitem{dawe_2008}
+Dawe, R.~A., Grattoni, C.~A., 2008. Experimental displacement patterns in a
+  2$\times$2 quadrant block with permeability and wettability
+  heterogeneities—problems for numerical modelling. Transport in Porous Media
+  71, 5--22.
+
+\bibitem{durlofsky_1993}
+Durlofsky, L., 1993. A triangle based mixed finite element finite volume
+  technique for modelling two-phase flow through porous media. Journal
+  Computational Physics 105, 252--266.
+
+\bibitem{durlofsky_1994}
+Durlofsky, L., 1994. Accuracy of mixed and control volume finite element
+  approximations to {D}arcy velocity and related quantities. Water Resources
+  Research 30, 965--973.
+
+\bibitem{forsyth_1990}
+Forsyth, P., 1990. A control volume, finite element method for local mesh
+  refinement in thermal reservoir simulation. SPE Resevoir Engineering 5~(4),
+  561--566.
+
+\bibitem{geiger_2004}
+Geiger, S., Roberts, S., Matth{\"a}i, S., Zoppou, C., A.~Burri, A., 2004.
+  Combining finite element and finite volume methods for efficient multiphase
+  flow simulations in highly heterogeneous and structurally complex geologic
+  media. Geofluids 4~(4), 284--299.
+
+\bibitem{helmig_1997}
+Helmig, R., 1997. Multiphase flow and transport processes in the subsurface.
+  Springer-Verlag, Berlin.
+
+\bibitem{Hoteit}
+Hoteit, H., Firoozabadi, A., 2008. Numerical modeling of two-phase flow in
+  heterogeneous permeable media with different capillarity pressures. Advances
+  in Water Resources 31~(1), 56 -- 73.
+
+\bibitem{huber_2000}
+Huber, H., Helmig, R., 2000. Node-centered finite volume discretizations for
+  the numerical simulation of multiphase flow in heterogeneous porous media.
+  Comput. Geosci. 4, 141--164.
+
+\bibitem{hurtado_2007}
+Hurtado, F., Maliska, C., Silva, A., Cordazzo, J., 2007. A quadrilateral finite
+  element-based finite-volume formulation for the simulation of complex
+  reservoirs. SPE 107444.
+
+\bibitem{jackson_2013}
+Jackson, M., Gomes, J., Mostaghimi, P., Percival, J., Tollit, B., Pavlidis, D.,
+  Pain, C., A.H. El-Sheikh, S.~P., Muggeridge, A., Blunt, M., 2013. Reservoir
+  modeling for flow simulation using surfaces, adaptive unstructured meshes,
+  and control-volume-finite-element methods. In: SPE Reservoir Simulation
+  Symposium, DOI: 10.2118/163633-PA.
+
+\bibitem{jiang_2011} 
+Jiang, X., 2011. A review of physical modelling and numerical simulation of
+  long-term geological storage of carbon dioxide. Applied Energy 88,
+  3557--3566.
+
+\bibitem{kirkland_1992}
+Kirkland, M., Hills, R., Wierenga, P., 1992. Algorithms for solving {R}ichards'
+  equation for variably-saturated soils. Water Resources Research 28,
+  2049--2058.
+
+\bibitem{mostaghimi_2015}
+Mostaghimi, P., Percival, J., Pavlidis, D., Ferrier, R., Gomes, J., Gorman, G.,
+  Jackson, M., Neethling, S., Pain, C., 2015. Anisotropic mesh adaptivity and
+  control volume finite element methods for nucmerical simulation of multiphase
+  flow in porous media. Mathematical Geoscience 347, 673--676.
+
+\bibitem{nick_2011b}
+Nick, H., Matthai, S., 2011a. Comparison of three fe-fv numerical
+  schemes for single- and tw-phase flow simulation of fractured porous media.
+  Transp. Porous Med 90, 421--444.
+
+\bibitem{nick_2011a}
+Nick, H., Matthai, S., 2011b. A hybrid finite-element
+  finite-volume method with embedded discontinuities for solute transport in
+  heterogeneous media. Vadose Zone Journal 10, 299--312.
+
+\bibitem{pavlidis_2013b}
+Pavlidis, D., Gomes, J., Xie, Z., Percival, J., Pain, C., Matar, O., 2015.
+  Compressive-advection and multi-component methods for interface-capturing.
+  International Journal for Numerical Methods in Fluids\;(Accepted).
+
+\bibitem{pavlidis_2014}
+Pavlidis, D., Xie, Z., Percival, J., Gomes, J., Pain, C., Matar, O., 2014. Two-
+  and three-phase horizontal slug flow modelling using an interface-capturing
+  compositional approach. International Journal for Multiphase Flow 67, 85--91.
+
+\bibitem{percival_2014}
+Percival, J., Pavlidis, D., Xie, Z., Gomes, J., Matar, O., Sakai, M.,
+  Takahashi, H., Pain, C., 2014. Transport and segregation of sand and granular
+  flows in fluidized beds. International Journal for Multiphase Flow 67,
+  191--199.
+
+\bibitem{pruess_1990c}
+Pruess, K., 1990. Numerical modeling of gas migration at a proposed repository
+  for low and intermediate level nuclear wastes. Tech. Rep. Report LBL-25413,
+  Lawrence Berkeley Laboratory, Berkeley, USA.
+
+\bibitem{riviere_2002}
+Rivi\`ere, B., Wheeler, M., 2002. Discontinuous {G}alerkin methods for flow and
+  transport problems in porous media. Communications in Numerical Methods in
+  Engineering 18, 63--68.
+
+\bibitem{riviere_2000}
+Rivi\`ere, B., Wheeler, M., Banas, K., 2000. Part 2: Discontinuous {G}alerkin
+  method applied to a single phase flow in porous media. Comp. Geosci. 4,
+  337--349.
+
+\bibitem{Salinas}
+Salinas, P., Percival, J.~R., Pavlidis, D., Xie, Z., Gomes, J., Pain, C.~C.,
+  Jackson, M.~D., 2015. A discontinuous overlapping control volume finite
+  element method for multi-phase porous media flow using dynamic unstructured
+  mesh optimization. In: SPE 173279.
+
+\bibitem{Schmid}
+Schmid, K., Geiger, S., Sorbie, K., 2013. Higher order fe–fv method on
+  unstructured grids for transport and two-phase flow with variable viscosity
+  in heterogeneous porous media. Journal of Computational Physics 241~(0), 416
+  -- 444.
+
+\bibitem{kaisu}
+Su, K., Latham, J.-P., Pavlidis, D., Xiang, J., Fang, F., Mostaghimi, P.,
+  Percival, J.~R., Pain, C.~C., Jackson, M.~D., 2015. Multiphase flow
+  simulation through porous media with explicitly resolved fractures.
+  Geofluids, n/a--n/a.
+% \newline\urlprefix\url{http://dx.doi.org/10.1111/gfl.12129}
+
+\bibitem{tezduyar_1986}
+Tezduyar, T., Park, Y., 1986. Discontinuity-capturing finite element
+  formulations for nonlinear convection-diffusion-reaction equations. Computer
+  Methods in Applied Mechanics and Engineering 59, 307--325.
+
+\bibitem{xie_2014}
+Xie, Z., Pavlidis, D., Percival, J., Gomes, J., Pain, C., Matar, O., 2014.
+  Adaptive unstructured mesh modelling of multiphase flows. International
+  Journal for Multiphase Flow 67, 104--110.
+%
 \bibitem{R1} Kopka~H, Daly~PW. 2003. \emph{A Guide to \LaTeX} (4th~edn).

### 2018-03-13 Papers/Prototype_Merged/article.tex

--- 2016-05-08 Papers/Prototype_Accepted/KickAssIJNMF/article_bak.tex
@@
-\documentclass[times]{fldauth}
+%%
+%% Copyright 2007, 2008, 2009 Elsevier Ltd
+%%
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%%
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later c.
+%%
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
 
-\usepackage{moreverb}
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+%% SP 2008/03/01
+%%
+%%
+%%
+%% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
+%%
+%%
+\documentclass[preprint,authoryear,12pt]{elsarticle}
 
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
 
-\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,authoryear,1p,times]{elsarticle}
+%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,authoryear,3p,times]{elsarticle}
+%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,authoryear,5p,times]{elsarticle}
+%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
 
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%\usepackage{cases}
+%% or use the graphicx package for more complicated commands
 \usepackage{graphicx}
-
+%% or use the epsfig package if you prefer to use the old commands
 \usepackage{epsfig}
@@
 
+%% The amssymb package provides various useful mathematical symbols
 \usepackage{amssymb,amsmath,array}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
 
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon (default)
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   authoryear - selects author-year citations (default)
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%   longnamesfirst  -  makes first citation full author list
+%%
+%% \biboptions{longnamesfirst,comma}
+
+% \biboptions{}
+
+%\journal{Computer Methods in Applied Mechanics and Engineering}
+\journal{Comput Meth Appl Mech Eng}
 \newcommand{\frc}{\displaystyle\frac}
@@
 
-\address{\affilnum{1} Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK.
-\\ \affilnum{2}Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK.
-\\ \affilnum{3} Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK.}
-\corraddr{Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK. E-mail: dimitrios.pavlidis@imperial.ac.uk}
+\begin{frontmatter}
 
-\runningheads{J. L. M. A. Gomes \textit{et al.}}{A Force-Balanced CVFEM for Multi-phase Porous Media Flow Modelling}
+%% Title, authors and addresses
 
-\title{A Force-Balanced Control Volume Finite Element Method for Multi-phase Porous Media Flow Modelling}
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
 
-\author{J.
-L.
-M.
-A.
-Gomes\affil{3,1}, D.
-Pavlidis\corrauth\affil{1,2}, P.
-Salinas\affil{1,2}, Z.
-Xie\affil{1,2}, J.
-R.
-Percival\affil{2}, \\Y.
-Melnikova\affil{1,2}, C.
-C.
-Pain\affil{1,2}, M.
-D.
-Jackson\affil{1}}
+\title{A Force-Balanced Control Volume Finite Element Method for Multiphase Porous Media Flow Modelling}
+
+%% use optional labels to link authors explicitly to addresses:
+\author[UoA,NORMS]{J. L. M. A. Gomes}\corref{cor1}\ead{jefferson.gomes@abdn.ac.uk} \author[IC,NORMS]{D. Pavlidis} 
+\author[IC,NORMS]{P. Salinas} \author[IC,NORMS]{Z. Xie}
+\author[IC]{J. R. Percival} \author[NSW]{P. Mostaghimi} 
+\author[IC,NORMS]{C. C. Pain} \author[NORMS]{M. D. Jackson}
+%\author[IC]{M. Blunt}
+
+\cortext[cor1]{Corresponding author.}
+\address[UoA]{Environmental and Industrial Fluid Mechanics Group, School of Engineering, University of Aberdeen, UK}
+\address[IC]{Applied Modelling and Computation Group, Department of Earth Science and Engineering, Imperial College London, UK}
+\address[NSW]{School of Petroleum Engineering, University of New South Wales, Australia}
+\address[NORMS]{Novel Reservoir Modelling and Simulation Group, Department of Earth Science and Engineering, Imperial College London, UK}
 
 \begin{abstract}
-  A novel method for simulating multi-phase flow in porous media is
-  presented. The approach is based on a control volume finite element
-  mixed formulation and new force-balanced finite element pairs. The
-  novelty of the method lies in: (a) permitting both continuous and
-  discontinuous description of pressure and saturation between
+  A novel control volume finite element method for simulating
+  subsurface multiphase flows is presented here. The approach has two
+  major strengths. First, it uses a dual consistent pressure-velocity
+  representation in control volume and finite element spaces which
+  ensures local mass conservation. Second, it uses a family of
+  finite element types that ensure the multiphase Darcy equations can be
+  exactly enforced. The underlying mass conservation equations are
+  solved in control volume space whereas finite elements are used to
+  obtain high-order fluxes on control volume boundaries. The novelty
+  of the method lies in (a) permitting both continuous and
+  discontinuous description of pressures and saturations between
   elements; (b) the use of arbitrarily high-order polynomial
-  representation for pressure and velocity and (c) the use of
-  high-order flux-limited methods in space and time to avoid
-  introducing non-physical oscillations while achieving high-order
-  accuracy where and when possible. The model is initially validated
-  for two-phase flow. Results are in good agreement with analytically
-  obtained solutions and experimental results. The potential of this
-  method is demonstrated by simulating flow in a realistic geometry
-  composed of highly permeable meandering channels.
+  representation for pressure and velocity within the mixed
+  formulation and (c) the use of high-order flux-limited methods to
+  avoid introducing non-physical oscillations while achieving
+  high-order time accuracy where and when possible. The model is
+  initially evaluated and then applied to a series of test cases using
+  structured and unstructured (triangular/ tetrahedral) meshes, as
+  well as heterogeneous problems with large permeability
+  ratios. Numerical results are in good agreement with analytically
+  obtained solutions.
 \end{abstract}
 
-\keywords{CVFEM mixed formulation; Discontinuous Galerkin; Flux-limiting; High-order method; Multi-phase flows; Porous media flows}
+\begin{keyword} %% keywords here, in the form: keyword \sep keyword
+CVFEM mixed formulation \sep Discontinuous Galerkin  \sep Multiphase flows \sep Porous media.
 
-\maketitle
+\end{keyword}
+
+\end{frontmatter}
 
 \section{Introduction}
-
-Numerical modelling of multi-phase flows in porous media has
+Numerical modelling of multiphase flow in porous media has
 applications in a wide range of disciplines, including hydrocarbon and
 groundwater production, safety assessment of deep geological disposal
-of radioactive waste, and carbon capture and storage \cite{chen_2006,
-  aiea_1999, pruess_1990c, jiang_2011}. Such applications often
-include complex geometries with irregular (and often internal)
+of radioactive waste, and CO$_{\text{2}}$ migration and trapping in
+carbon capture and storage ~\citep{chen_2006, aiea_1999, pruess_1990c,
+  jiang_2011}. Such geological and geophysical applications often
+include complex rock geometries with irregular (and often internal)
 boundaries between rock types with contrasting porosity and
@@
 
-Finite difference methods (FDM) have been extensively used for
-modelling fluid flows in porous media
-\cite{aziz_1986, chen_1997, chen_2005}. However, they are strongly
+Finite difference methods (FDM) have been extensively used in
+modelling and simulation of fluid flows in porous media
+\citep{aziz_1986, chen_1997, chen_2005}.  However, they are strongly
 dependent on mesh quality and orientation, and cannot easily represent
 complex geometries. In addition, FDM can produce excessive numerical
-dispersion in heterogeneous porous media \cite{chavent_1986}.
+dispersion in heterogeneous porous media \citep{chavent_1986}. The
+geometrical flexibility of finite element methods (FEM) has been shown
+to overcome these deficiencies. Among FEM-based formulations for
+porous media, the control volume finite element method (CVFEM) has
+become increasingly popular as it can guarantee local mass
+conservation and high-order numerical accuracy, as well as being able
+to use tetrahedral, geometry-conforming elements \citep{forsyth_1990,
+  cordazzo_2004, geiger_2004, hurtado_2007}. \citet{huber_2000}
+demonstrated that the vertex-centred, finite volume-finite element
+method (or Box scheme) can achieve similar goals \citep[see
+  also][]{helmig_1997}.
 
-The geometrical flexibility of finite element methods (FEM) has been
-shown to overcome these deficiencies. Among FEM-based formulations for
-porous media, the control volume finite element method (CVFEM) is
-increasingly popular as it can guarantee local mass conservation, it
-has the potential to be high-order accurate, and is able to use
-tetrahedral, geometry-conforming elements \cite{forsyth_1990,
-  cordazzo_2004, geiger_2004, hurtado_2007}. Huber and Helmig \cite{huber_2000}
-demonstrated that the vertex-centred, finite volume-finite element
-method (or Box scheme) can achieve similar goals (see also \cite{helmig_1997}).
-
-Durlofsky \cite{durlofsky_1993,durlofsky_1994} compared the performance of a
-mixed FEM formulation (piece-wise linear in velocity and piece-wise
-constant in pressure) and the classical CVFEM for single phase Darcy
-flows. It was concluded that the latter is computationally more
-efficient and numerically more accurate than the former for problems
-involving a (relatively) small number of degrees of freedom. Moreover,
-for complex heterogeneous problems with sharp changes in material
-properties, the mixed FEM formulation often led to physically
-unrealistic solutions.  Cumming et al. \cite{cumming_2011} demonstrated that a
-CVFEM-based discretisation could be used to solve the Richards
+\citet{durlofsky_1993,durlofsky_1994} compared the performance of a
+mixed FEM formulation (i.e. piece-wise constant in pressure and
+piece-wise linear in velocity) and the classical CVFEM for single
+phase Darcy flows. He concluded that the latter is more
+computationally efficient and numerically accurate than the former for
+problems involving a (relatively) small number of degrees of
+freedom. Moreover, for complex heterogeneous problems with sharp
+changes in material properties, mixed FEM formulations often lead to
+physically unrealistic solutions.  \citet{cumming_2011} demonstrated
+that a CVFEM-based discretisation could be used to solve the Richards
 equation (coupled mass conservation and Darcy equations) in
@@
 overhead, compared with traditional, coupled velocity-pressure based
-formulations.  Mass balance was enforced as described by Kirkland et al.
-\cite{kirkland_1992} (see also \cite{forsyth_1990,cumming_phd2012}). However, CVFEM often requires
-high resolution meshes in regions where material properties vary
-abruptly, such as permeability contrasts at (for example)
-fracture-matrix interfaces, or boundaries between different rock
-types. Control volume (CV) boundaries span finite elements where
-material properties are defined; therefore, some average value of the
-permeability must be calculated across CV interfaces. This often leads
-to excessive numerical dispersion, especially in highly heterogeneous
-media \cite{nick_2011b, nick_2011a}.
+formulations.  Mass balance was enforced as described by
+\citet{kirkland_1992}~\citep[see
+  also][]{forsyth_1990,cumming_phd2012}.  The efficiency and accuracy
+of CVFEM for porous media flows has motivated our development of a
+CVFEM-based discretisation here.  However, CVFEM often requires high
+resolution meshes in regions where material properties vary abruptly,
+such as permeability contrasts at (for example) fracture-matrix
+interfaces, or boundaries between different rock types. Control volume
+(CV) boundaries span finite elements where material properties are
+defined; therefore, some average value of the permeability must be
+calculated across CV interfaces. This often leads to excessive
+numerical dispersion, especially in highly heterogeneous media
+\citep{nick_2011b, nick_2011a}.
 
-Discontinuity-capturing schemes (e.g. shock waves, contact
+Discontinuity-capturing schemes~\citep[e.g. shock waves, contact
   surface or material discontinuities --
-  see \cite{brooks_1982,tezduyar_1986}) were originally developed to
+  see][]{brooks_1982,tezduyar_1986} were originally developed to
 resolve sharp changes in solution fields such as velocity or
@@
 solution is not explicitly enforced, allowing sharp changes in the
-solution fields to be captured. The DGFEM scheme is stabilised,
-locally conservative and designed to achieve high-order
-accuracy. DGFEM solution fields are allowed to be discontinuous at the
-element faces; thus, the solution is able to handle discontinuities in
-material properties at internal boundaries. In addition, DGFEM is
-well-suited to deal with interface problems by incorporating
-specially-designed interface fluxes. These properties have attracted
-the attention of the porous media flow community over the past 15
-years (see \cite{riviere_2000,riviere_2002,bastian_2002}) and are
-utilised here.
+solution fields to be captured. The DG formulation is a stabilised
+finite element method that is locally conservative and designed to
+achieve high-order accuracy. DGFEM solution fields are allowed to be
+discontinuous at the element faces; thus, the solution is able to
+handle discontinuities in material properties at internal
+boundaries. In addition, DGFEM is well-suited to deal with interface
+problems by incorporating specially-designed interface fluxes. These
+properties have attracted the attention of the porous media flow
+community over the past 15 years
+\citep[see][]{riviere_2000,riviere_2002,bastian_2002} and are utilised
+here.
 
@@
 the pressure equation to enforce mass conservation and the exact force
-balance. The \PN[n]{m}[DG] family of triangular and tetrahedral finite
-element pairs is used to discretise velocity and pressure in
-space. For this element type, the velocity field is represented by
-$n^{\rm th}$-order polynomials that are discontinuous across elements,
-while the pressure field is represented by $m^{\rm th}$-order
-polynomials that may be continuous (termed P$_n$DG-P$_m$) or
-discontinuous (termed P$_n$DG-P$_m$DG) across elements. Control
-volumes are dual to the pressure mesh. The formulation employs an
-implicit algorithm with respect to time that is less restrictive than
-the implicit-pressure-explicit-saturation (IMPES) scheme often adopted
-in porous media flow problems (e.g. see \cite{aziz_1986, geiger_2004}).
+balance. The formulation employs an implicit algorithm with respect to
+time that is less restrictive than the
+implicit-pressure-explicit-saturation (IMPES) scheme often adopted in
+porous media flow problems \citep[e.g. see][]{aziz_1986,
+  geiger_2004}. There are two key novel aspects in our approach. The
+first is that it uses a dual consistent CVFEM representation that is
+embedded in the \PN[n]{m}[DG] family of triangular and tetrahedral
+finite element pairs \citep[see][]{kaisu}. For this element type, the
+velocity field is represented by $n^{\rm th}$-order polynomials that
+are discontinuous across elements, while the pressure field is
+represented by $m^{\rm th}$-order polynomials that may be continuous
+(termed P$_n$DG-P$_m$) or discontinuous (termed P$_n$DG-P$_m$DG)
+across elements. In particular, here the P$_n$DG-P$_{n+1}$ element
+pair, which allows the velocity to exactly represent the pressure
+gradients in the flow solution for homogeneous material properties, is
+demonstrated. The \PNDG[n+1]{n} element pair, which has similar
+properties to the \PN[n]{n+1} element pair, but allows a
+representation in which pressure, saturation and other solution
+variables are discontinuous across finite element boundaries, is also
+demonstrated.  This solves the long-standing problem described above
+with respect to the use of traditional CVFEM methods to capture sharp
+changes in material properties. The second key novelty is the velocity
+representation that is described in detail in
+Section~\ref{overlapping_method_section} and can achieve an exact
+representation of the multiphase Darcy force balance equations.
 
-The method is demonstrated using two families of element pairs: the
-\PN[n]{m} pair which can allow the velocity to exactly represent the
-pressure gradients in the flow solution for homogeneous material
-properties; and the \PNDG[n+1]{n} pair, which has similar properties
-to the \PN[n]{n+1} element pair, but allows a representation in which
-pressure, saturation and other solution variables are discontinuous
-across finite element boundaries. This solves the long-standing
-problem described above with respect to the use of traditional CVFEM
-to capture sharp changes in material properties.
+The remainder of this paper is organised as follows. The governing
+equations and numerical methods employed to solve them are presented
+in Section~\ref{overlapping_method_section}. Model set-up and results
+including comparison against reference data for a series of benchmark
+problems are given in Sections~\ref{setup} and \ref{res},
+respectively. Finally, some concluding remarks are presented in
+Section~\ref{conc}.
 
-Results using this method in simple geometries have been previously
-reported in the literature
-(e.g. see \cite{jackson_2015,kaisu}). However, the method has not
-been described in detail or thoroughly validated, and its potential has not been
-explored. The remainder of this paper is organised as follows. The
-governing equations and numerical methods employed to solve them are
-presented in Section~\ref{overlapping_method_section}. Model set-up
-and results including comparison against reference data are given in
-Sections~\ref{setup} and \ref{res}, respectively. Finally, some
-concluding remarks are presented in Section~\ref{conc}.
-
-\section{Governing equations and numerical method}
+\section{Governing equations and Numerical Method}
 \label{overlapping_method_section}
 
-\subsection{A novel representation of multi-phase Darcy flows}
-Darcy's law for immiscible multi-phase flow may be written in the form:
+\subsection{A Novel Representation of Multiphase Darcy Flows}
+Darcy's law for immiscible multiphase flow may be written in the form:
 \begin{equation}\label{e:darcy_eqn}
@@
 relative permeability, which is a function of the phase saturation
-$S_{\alpha}\left(\mathbf{r},t\right)$. $\mu_{\alpha}$, $p_{\alpha}$,
-$\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic
-viscosity, pressure, density and source term, which may include gravity and/or
-capillarity, respectively.
+$S_{\alpha}\left(\mathbf{r},t\right)$. $\mu_{\alpha}$, $p_{\alpha}$
+and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity,
+pressure and source term, which may include gravity and capillary
+pressure, respectively.
 
@@
   \sum\limits_{E} \left. \int\limits_{\Omega_E} { {Q}}_i \left (
-             {\mathbf v}_\alpha + \nabla p  -\rho_\alpha g \mathbf{d} -{\mathbf s}_{u_\alpha}
+             {\mathbf v}_\alpha + \nabla p -{\mathbf s}_{u_\alpha}
              \right) dV \right. + \displaystyle \oint_{\Gamma_{E}}
@@
 
-\subsection{Control volume finite element types}
+\subsection{Control-Volume Finite element types}
 In the formulation presented here, pressure, velocity, permeability
@@
 paper. Fig.~\ref{fem_cv_represent_a} (a) shows the P$_{n}$DG-P$_{n+1}$
-element type, with $n = 1$, in two dimensions (2D). Here, the velocity
+element type, with $n = 1$, in two dimensions (2D). Here the velocity
 field is linear, discontinuous (between elements), the pressure field
@@
 CV's span various elements. Fig.~\ref{fem_cv_represent_a} (b) shows
-the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$, also in 2D. Here,
+the P$_{n+1}$DG-P$_{n}$DG element type, with $n = 1$, also in 2D. Here
 the velocity field is quadratic, discontinuous (between elements), the
 pressure field has a linear, discontinuous (between elements),
-representation and the CV's do not span elements.
+representation and the CV's do not span elements. Note that in the
+latter element pair, CV's have piece-wise constant permeability and
+porosity values.
 
 \begin{figure}[h!]
-\subfloat[P$_1$DG-P$_2$]{\includegraphics[width=.5\textwidth]{p1dgp2-cont-sat.pdf}}
-\subfloat[P$_2$DG-P$_1$DG]{\includegraphics[width=.5\textwidth]{p2dgp1-dg-sat.pdf}}
+\subfloat[P$_1$DG-P$_2$]{\includegraphics[width=.5\textwidth]{diagrams/p1dgp2-cont-sat}}
+\subfloat[P$_2$DG-P$_1$DG]{\includegraphics[width=.5\textwidth]{diagrams/p2dgp1-dg-sat}}
 \caption{2D representation of the element pairs presented in this
@@
 
-\subsection{Saturation and global mass conservative equations} \label{Section:Saturation_Global}
+\subsection{Saturation and Global Mass Conservative Equations} \label{Section:Saturation_Global}
 Here, the saturation conservation equations are discretised and the
@@
 solve Eqn.~\ref{detail-sat-eqn-k} can be found in
-\cite{pavlidis_2013b}.
+\citet{pavlidis_2013b}.
 
@@
   \sum\limits_{\alpha=1}^{\mathcal{N}_{\alpha}} {S_{\alpha}^{n}}_{i} =
-  1, \quad \forall n.
+  1, \quad \forall n,
 \end{equation}
@@
 
-\subsection{Velocity at control volume interfaces} \label{opt-up} 
+\subsection{Velocity at Control Volume Interfaces} \label{opt-up} 
 The velocity to be used at the interface between CV's in the
@@
 
-In order to calculate the velocity between elements (when using
-P$_{n+1}$DG-P$_{n}$DG elements) one first needs to consider that it is
+In order to calculate the velocity between elements when using
+P$_{n+1}$DG-P$_{n}$DG elements one first needs to consider that it is
 also necessary to obtain the discretised non-symmetric pressure
@@
 \begin{equation} 
-  {\tilde{\bf u}_\alpha} =  \left(\mathcal{V}_{j}  
-    \underline{\underline{\sigma}}_{\alpha j} \, {\bf
-      u}_{\alpha i} + \mathcal{V}_{i} \underline{\underline{\sigma}}_{\alpha i}\, {\bf
-      u}_{\alpha j} \right) \left(  \mathcal{V}_{i} 
-    \underline{\underline{\sigma}}_{\alpha i} +
-    \mathcal{V}_{j} 
-    \underline{\underline{\sigma}}_{\alpha j} \right)^{-1}.
+  {\tilde{\bf u}_\alpha} = \frc{ \mathcal{V}_{j} {\bf n}^T \cdot
+    \underline{\underline{\sigma}}_{\alpha j}\cdot{\bf n} \, {\bf
+      u}_{\alpha i} + \mathcal{V}_{i} {\bf n}^T
+    \cdot\underline{\underline{\sigma}}_{\alpha i}\cdot{\bf n}\, {\bf
+      u}_{\alpha j}} { \mathcal{V}_{i} {\bf n}^T
+    \cdot\underline{\underline{\sigma}}_{\alpha i}\cdot{\bf n} +
+    \mathcal{V}_{j} {\bf n}^T
+    \cdot\underline{\underline{\sigma}}_{\alpha j}\cdot{\bf n} }.
 \end{equation}
 
-\subsection{Weak enforcement of boundary conditions}\label{bcs-rel-perm} 
+\subsection{Weak Enforcement of Boundary Conditions}\label{bcs-rel-perm} 
 Suitable boundary conditions for velocity can be applied by the
@@
 applied across the boundaries of the domain by taking information from
-`just outside' the domain rather than from the neighbouring elements.
+just outside the domain rather than from the neighbouring elements.
 
 Saturation boundary conditions are relatively straightforward. One
-typically takes the saturation from `just outside' the domain
+typically takes the saturation from just outside the domain
 ($S_{\alpha, \text{bc}}$) and the flux becomes $\left({\bf n}\cdot
@@
 
-\subsection{Solving the linear equations}\label{Section:SolvingLinearEqns}
+\subsection{Solving the Linear Equations}\label{Section:SolvingLinearEqns}
 The global mass balance equation (Eqn.~\ref{glob-cty-matrix}) and
@@
 arising from the fully discontinuous FEM formulation is achieved using
-a multigrid-like approach (see \cite{Brandt}). In this case the
+a multigrid-like approach \citep[see][]{Brandt}. In this case the
 `fine' mesh is the one obtained by the discontinuous system, whereas
@@
 The numerical method is evaluated using four test cases (\ref{classical_BL} --
-\ref{res5}). All test cases simulate two-phase flow. The Brooks-Corey model
-\cite{brooks_1964}: 
+\ref{res4}). All simulate two-phase flow. The Brooks-Corey model
+\citep{brooks_1964}: 
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $S_w$ and $S_{nw}$ are the wetting and non-wetting phase volume
-fractions, respectively, is used to calculate the relative
-permeabilities for all test cases. The exponents $n_w$ and $n_{nw}$
-are both set to 2 for all test cases.
-
-The length of all computational domains is 1 non-dimensional length
-unit. Computational domain height, boundary conditions, exponents for
-the wetting $n_w$ and non-wetting $n_{nw}$ phases in the Brooks-Corey
-model, along with the irreducible wetting phase saturation $S_{wirr}$,
-residual non-wetting phase saturation $S_{nwr}$ and mobility $M^0$ for
-each test case are shown in Table~\ref{tab:1}.
+where $S_w$ and $S_{nw}$ are the wetting and non-wetting phase
+saturations, respectively, is used to calculate the relative
+permeabilities for all test cases. The length of all computational
+domains is 1 non-dimensional length unit. Computational domain height,
+boundary conditions, exponents for the wetting $n_w$ and non-wetting
+$n_{nw}$ phases in the Brooks-Corey model, along with the irreducible
+wetting phase saturation $S_{wirr}$, residual non-wetting phase
+saturation $S_{nwr}$ and mobility $M^0$ for each test case are shown
+in Table~\ref{tab:1}.
 
@@
     \caption{Model set-up for test cases \ref{classical_BL} --
-      \ref{res5}.\label{tab:1}}
-    \begin{tabular}{c c c c c c c c c c c c c c c} 
+      \ref{res4}.\label{tab:1}}
+    \begin{tabular}{c c c c c c c c c c c c c c c c } 
       \hline
-      & $M^0$ & $\phi$ & $\mathbf{K}_\text{1}$ & $\mathbf{K}_\text{2}$ & $\mathbf{K}_\text{3}$ & $S_{wirr}$ & $S_{nwr}$ & $u_{\mathrm{in}}$ & $\Delta p$ & height \\ \hline
-      \ref{classical_BL} & 10 & 0.2 & 1.0 & N/A    & N/A & 0.2   & 0.3 & 0.2 & N/A & N/A\\
-      \ref{res2}         & 10 & 0.4 & 1.0 & 2.5    & N/A & 0.1   & 0.2 & 1.0 & N/A & 1.0\\ 
-      \ref{res4}         & 10 & 0.5 & 1.0 & 10$^2$ & N/A & 0.0   & 0.0 & N/A & 1.0 & 0.1\\
-      \ref{res5}         & 4  & 0.2 & 1.0 & 2.0    & 10  & 0.2   & 0.2 & N/A & 1.0 & 0.1\\ \hline
+      & $M^0$ & $\phi$ & $\mathbf{K}_\text{1}$ & $\mathbf{K}_\text{2}$ & $S_{wirr}$ & $S_{nwr}$ & $n_{w}$ & $n_{nw}$ & $u_{\mathrm{in}}$ & $\Delta p$ & height \\ \hline
+      M1 & 10 & 0.2 & 1.0 & N/A    & 0.2 & 0.3 & 2 & 2 & 0.2 & N/A & N/A\\ 
+      M2 & 10 & 0.4 & 1.0 & 2.5    & 0.1 & 0.2 & 2 & 2 & 1.0 & N/A & 1.0\\ 
+      M3 & 10 & 0.5 & 0.5 & 10$^4$ & 0.1 & 0.3 & 2 & 2 & 1.0 & N/A & 1.0\\ 
+      M4 & 10 & 0.5 & 1.0 & 10$^2$ & 0.0 & 0.0 & 2 & 2 & N/A & 1.0 & 0.1\\ \hline
     \end{tabular}
@@
 uniform, constant velocity ($u_{\mathrm{in}}$) from the left boundary
-for test cases  \ref{classical_BL} and  \ref{res2}. In test case \ref{res2} the
-inlet velocity is weighted by the permeability. For test cases  \ref{res4} and  \ref{res5},
-the flow is driven by a pressure difference ($\Delta p$)
+for test cases \ref{res2} -- \ref{res3}. In test case \ref{res2} the
+inlet velocity is weighted by the permeability. For the last test case
+(\ref{res4}), the flow is driven by a pressure difference ($\Delta p$)
 between the inflow (left) and outflow (right) boundaries of the
@@
 uniform and for case \ref{classical_BL}, $\mathbf{K}$ is also
-uniform. However, for cases \ref{res2} -- \ref{res5}, $\mathbf{K}$ is
+uniform. However, for cases \ref{res2} -- \ref{res4}, $\mathbf{K}$ is
 non-uniform and regions of constant $\mathbf{K}$ are used. For all
 cases, $\mathbf{K}$ is isotropic. The subscript in $\mathbf{K}$
-denotes region identities (see Figs.~\ref{fig:4reg_BL_schematic} and
-\ref{fig:wedge_permeability}).
+denotes region identities (see Figs.~\ref{fig:4reg_BL_schematic},
+\ref{fig:square_permeability} and \ref{fig:wedge_permeability}).
 
 \section{Results}\label{res}
-
 \subsection{The Buckley-Leverett test case}\label{classical_BL}
 
-The Buckley-Leverett problem \cite[non-wetting phase displaced by a
-  wetting phase]{buckley1942} is simulated here.  Despite the
+The Buckley-Leverett problem \citep[non-wetting phase displaced by a
+  wetting phase,][]{buckley1942} is simulated here.  Despite the
 one-dimensional (1D) nature of the problem, 2D and three-dimensional
@@
 
-Fig.~\ref{fig:BL_tests} (a), (b) and (c) shows phase volume fraction
-profiles of the wetting phase for four meshes in 2D at
-non-dimensional time $t=0.2$. All meshes are structured and have 4
-elements perpendicular to the flow and 60, 120, 240 or 480 elements
-parallel to the flow (see Fig.~\ref{fig:maps2d_3d}, a). The geometry
-centre-line is used to plot these profiles. All element pairs
-satisfactorily capture the discontinuity in the phase volume fraction
-and as the number of elements is increased the error is reduced.
-Fig.~\ref{fig:BL_tests} (d) shows results obtained for a
-Buckley-Leverett test case in 3D. A 1207-element fully unstructured
-mesh is used for these simulations. The geometry centre-line is used
-to plot these profiles. All the element pairs are again capable of
-accurately capturing the discontinuity in the phase volume fraction.
-
 \begin{figure}[h!]
@@
     \vbox{\hbox{
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P1DGP1.eps} 
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P1DGP2.eps}}
+        \hspace{0.25cm}\includegraphics[width=0.45\textwidth]{P1DGP1_M10.eps} 
+        \hspace{0.25cm}\includegraphics[width=0.45\textwidth]{P1DGP2_M10.eps}}
       \hbox{
-        \vspace{-0.cm}\hbox{\hspace{3.0cm}(a)} 
-        \vspace{-0.cm}\hbox{\hspace{6.0cm}(b)}}
+        \vspace{-0.cm}\hbox{\hspace{2.5cm}(a)} 
+        \vspace{-0.cm}\hbox{\hspace{6.5cm}(b)}}
       \vspace{0.0cm}\hbox{
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_P2DGP1DG.eps}
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{BL_3D.eps}}
+        \hspace{0.5cm}\includegraphics[width=0.45\textwidth]{P2DGP1DG_M10.eps}
+        \hspace{0.5cm}\includegraphics[width=0.45\textwidth]{3D_three_elements.eps}}
       \hbox{
-        \vspace{-0.cm}\hbox{\hspace{3.0cm}(c)} 
-        \vspace{-0.cm}\hbox{\hspace{6.0cm}(d)}}}
-    \caption{Wetting phase volume fraction along the geometry
+        \vspace{-0.cm}\hbox{\hspace{2.5cm}(c)} 
+        \vspace{-0.cm}\hbox{\hspace{6.5cm}(d)}}}
+    \caption{Wetting phase volume fraction along at the geometry
       centre-line at non-dimensional time $t=0.2$ for the
@@
 
-Fig.~\ref{fig:errors_BL_2D} (a) shows convergence rates for the
-results presented in Fig.~\ref{fig:BL_tests} (a), (b) and (c). The
-L$_2$ error norm of the wetting phase volume fraction is used
-here. Due to the discontinuity in the solution variable, a
-first-order convergence rate is achieved even when the high-order
-element pair is used (Fig.~\ref{fig:BL_tests}, b). This is because
-high-order methods switch to simple upwinding at the discontinuity.
-Fig.~\ref{fig:errors_BL_2D} (b) shows the convergence rate of the same
-high-order element pair simulation (Fig.~\ref{fig:BL_tests}, b) at
-non-dimensional time $t=0.3$. At this time level the phase volume
-fraction field is smooth since the discontinuity has been advected out
-of the computational domain and for this reason a second-order
-convergence rate is achieved.
-
 \begin{figure}[h!]
   \begin{center}
-    \vbox{\hbox{
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{Conv1.eps} 
-        \hspace{0.0cm}\includegraphics[width=0.45\textwidth]{Conv2.eps}}
-      \hbox{
-        \vspace{-0.cm}\hbox{\hspace{3.0cm}(a)} 
-        \vspace{-0.cm}\hbox{\hspace{6.0cm}(b)}}}
+    \includegraphics[width=0.70\textwidth]{BL_2D_Errors.eps}
     \caption{Error metrics versus number of elements for the
@@
 
-\subsection{Immiscible displacement in heterogeneous porous media}\label{res2}
+Fig.~\ref{fig:BL_tests} (a), (b) and (c) shows phase volume fraction
+profiles of the wetting phase for three meshes in 2D at
+non-dimensional time $t=0.2$. All meshes are structured and have 4
+elements perpendicular to the flow and 120, 240 or 480 elements
+parallel to the flow (see Fig.~\ref{fig:maps2d_3d}, a). The geometry
+centre-line is used to plot these profiles. All element pairs
+satisfactorily capture the discontinuity in the phase volume fraction
+and as the number of elements is increased the error is reduced. Due
+to this discontinuity in the solution variables, a first-order
+convergence rate is achieved even when the high-order element pair is
+used (Fig.~\ref{fig:errors_BL_2D}). This is because high-order methods
+switch to simple upwinding at the discontinuity.
+
+Fig.~\ref{fig:BL_tests} (d) shows results obtained for a
+Buckley-Leverett test case in 3D. A 1207-element fully unstructured
+mesh is used for these simulations. The geometry centre-line is used
+to plot these profiles. All the element pairs are again capable of
+accurately capturing the discontinuity in the phase volume fraction.
+
+\subsection{Immiscible Displacement in Heterogeneous Porous Media}\label{res2}
 
 This test case is designed to demonstrate the numerical robustness of
-the method for modelling heterogeneous porous media and it is based on
-the physical experiment presented in Dawe and Grattoni \cite{dawe_2008}. As shown in
-Fig.~\ref{fig:4reg_BL_schematic} the permeability field is
+the method for modelling heterogeneous porous media and it is loosely
+based on the physical experiment presented in \cite{dawe_2008}. As
+shown in Fig.~\ref{fig:4reg_BL_schematic} the permeability field is
 non-uniform.
@@
   \begin{center}
-    \includegraphics[width=0.5\textwidth]{4Rregion_BLv2}
+    \includegraphics[width=0.6\textwidth]{4Rregion_BLv2}
     \caption{Schematic of the computational domain along with the
@@
 \begin{figure}[h!]
-  \centering
-  \includegraphics[width=0.45\textwidth]{CG_coarse083.png}
-  \includegraphics[width=0.45\textwidth]{CG_fine083.png}
-  \includegraphics[width=0.45\textwidth]{DG_coarse083.png}
-  \includegraphics[width=0.45\textwidth]{DG_fine083.png}
+  \vbox{\hbox{
+      \hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{CG_coarse083.png}
+      \hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{CG_fine083.png}}
+    \vspace{1.cm}\hbox{
+      \hspace{-1.8cm}\includegraphics[width=0.6\textwidth]{DG_coarse083.png}
+      \hspace{-0.2cm}\includegraphics[width=0.6\textwidth]{DG_fine083.png}}}
   \caption{Wetting phase volume fraction maps at time $t=0.16$ for the
@@
 
-\begin{figure}[h!]
-  \begin{center}
-    \includegraphics[width=0.6\textwidth]{Real_quadrant}
-    \caption{Wetting phase volume fraction maps from the experiments
-      of \cite{dawe_2008}. \label{fig:dawe_real}}
-  \end{center}
-\end{figure}
-
 Two sets of simulations are performed using coarse (402 elements) and
@@
 used. The time step sizes for the coarse and fine mesh simulations are
-5$\times$10$^{-3}$ and 10$^{-3}$ non-dimensional time units,
+5$\times$10$^{-3}$ and 1$\times$10$^{-3}$ non-dimensional time units,
 respectively.
 
+Fig.~\ref{fig:4reg_maps} shows the wetting phase volume fraction
+maps (at time $t=0.16$) for all four simulations. The results yielded
+by the experiment (a) are depicted in the top left, coarse mesh, and
+top right, fine mesh. The results obtained from experiment (b) located
+on the bottom left, coarse mesh, and bottom right, fine mesh.
+
 Fig.~\ref{fig:4reg_maps} shows the wetting phase volume fraction maps
-at time $t=0.16$ for all four simulations. Results for the
+(at time $t=0.16$) for all four simulations. Results from the
 \PN[1]{2} element pair set of simulations is shown in the top row.
-Results for the \PN[2]{1}DG element pair set of simulations is shown
+Results from the \PN[2]{1}DG element pair set of simulations is shown
 in the bottom row.
 
-A physical experiment with similar set-up was performed by Dawe and Grattoni
-\cite{dawe_2008} to investigate miscible and immiscible displacement
+A physical experiment with similar set-up was performed by
+\citet{dawe_2008} to investigate miscible and immiscible displacement
 in heterogeneous permeability and wettability cases. For immiscible
@@
 `fingering' across the four region intersection, demonstrating the
-preferential flow through high permeability regions. This is in good
-qualitative agreement with the experimental results
-(see Fig.~\ref{fig:dawe_real}, taken from Dawe and Grattoni \cite{dawe_2008}).
+preferential flow through highly permeable matrix. This is in good
+qualitative agreement with experimental results from \cite{dawe_2008}
+\citep[see Fig.~\ref{fig:dawe_real} taken from ][]{dawe_2008}.
 
-\subsection{High permeability high aspect ratio region}\label{res4}
+\begin{figure}[h!]
+  \begin{center}
+    \includegraphics[width=0.75\textwidth]{Real_quadrant}
+    \caption{Wetting phase volume fraction maps from the experiments
+      of \cite{dawe_2008}. \label{fig:dawe_real}}
+  \end{center}
+\end{figure}
+
+\subsection{Underground Caisson}\label{res3}
+
+This test case is similar to that in Section~\ref{res2}, however, the
+permeability ratio is considerably higher at $10^4$. The computational
+domain considered here is characterised by a low-permeability square
+region of length 0.5 non-dimensional units, which is embedded in a
+high-permeability square domain.
+
+\begin{figure}[h!]
+  \vbox{
+    \hbox{
+      \hspace{3.5cm} \includegraphics[width=0.45\textwidth]{square_permeability_lowv2}}
+    \vspace{0.25cm}
+    \hbox{
+      \hspace{0.4cm}\includegraphics[width=0.45\textwidth]{cg_square_015_low}
+      \hspace{0.4cm}\includegraphics[width=0.45\textwidth]{cg_square_05_low}}
+    \vspace{0.25cm}
+    \hbox{
+      \hspace{0.4cm}\includegraphics[width=0.45\textwidth]{dg_square_015_low}
+      \hspace{0.4cm}\includegraphics[width=0.45\textwidth]{dg_square_05_low}}}
+  \caption{Schematic of the computational domain along with the
+    permeability map and mesh used for the underground caisson test
+    case (top).  Wetting phase volume fraction maps at non-dimensional
+    times $t=0.15$ (left) and $t=0.5$ (right). \PN[1]{2} element pair
+    results are shown in the middle row. \PN[2]{1}DG element pair
+    results are shown in the bottom row.
+    \label{fig:square_permeability}}
+\end{figure}
+
+Two numerical simulations are performed. The first one uses the
+\PN[1]{2} element pair and a time step size of 5$\times$10$^{-3}$
+non-dimensional time units and the second one uses the \PN[2]{1}DG
+element pair and a time step size of 1$\times$10$^{-4}$. The mesh and
+permeability map for these simulations is shown in
+Fig.~\ref{fig:square_permeability} (top).
+
+Fig.~\ref{fig:square_permeability} shows snapshots of the wetting
+phase volume fraction field at non-dimensional times $t = 0.15$ and
+0.5 for both simulations.  Numerical dispersion can be seen in the
+solution of the \PN[1]{2} element pair simulation. This is because
+CV's span material property interfaces. However, this is not the case
+for the \PN[2]{1}DG element pair and the wetting phase here does not
+diffuse into the low-permeability region of the computational domain.
+Despite this small difference, both simulations are in good agreement
+and provide satisfactory results with respect to dispersing the
+wetting phase into the low-permeability region.
+
+\subsection{High-Permeability high-aspect ratio region}\label{res4}
 
@@
 thin tip and a high permeability. A simplified 2D wedge-shaped
-high permeability region embedded in a rectangular low-permeability
+high-permeability region embedded in a rectangular low-permeability
 domain is considered here. The permeability map is shown in
@@
   \caption{Schematic of the computational domain along with the
-    permeability map for the high permeability wedge-shaped region
+    permeability map for the high-permeability wedge-shaped region
     test case (a). Snapshots of the wetting phase volume fraction
@@
 
-\subsection{3D fluvial channel model}\label{res5}
+\section{Concluding Remarks}\label{conc}
+A novel, high-order, control-volume-finite-element (CVFE) method with
+$n^{\rm th}$-order representation for velocity and $m^{\rm th}$-order
+for pressure is presented. The method conserves mass and ensures that
+the extended Darcy equations for multiphase flow are exactly
+enforced. Moreover, for \PN[n+1]{n}DG element pairs control volumes
+do not span elements; this resolves a long-standing problem associated
+with the use of classical CVFE methods in highly heterogeneous porous
+media flow modelling. In addition, the use of force per unit volume
+instead of Darcy velocity significantly improves the computational
+cost and memory usage.
 
-\begin{figure}[h!]
-  \vbox{
-    \hbox{
-      \hspace{3.5cm} \includegraphics[width=0.45\textwidth]{permeability_map}}
-    \vspace{0.1cm}
-    \hbox{
-      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_vtu10}
-      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_vtu20}}
-    \vspace{0.1cm}
-    \hbox{
-      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_DGvtu10}
-      \hspace{0.0cm}\includegraphics[width=0.475\textwidth]{phase_vol_fraction_DGvtu20}}}
-  \caption{Schematic of the computational domain along with the
-    permeability map and mesh used for the 3D fluvial channel case
-    (top). Wetting phase volume fraction maps at two time levels
-    (left and right). \PN[1]{1} element pair results are shown in the
-    middle row. \PN[2]{1}DG element pair results are shown in the
-    bottom row.
-    \label{fig:fluvial_model}}
-\end{figure}
+The new formulation is evaluated using the classical Buckley-Leverett
+benchmark and first-order convergence rates are achieved, which is not
+common in the literature \citep[see][]{Schmid,Hoteit}. More numerical
+simulations are performed to demonstrate the capabilities of the
+methods presented under heterogeneous and high aspect ratio
+computational domains, showing that this method is able to resolve
+successfully the flow under those circumstances. Furthermore, the
+\PN[n+1]{n}DG element pair shows that it completely removes numerical
+dispersion induced by heterogeneous permeabilities.
 
-The method is finally applied to a subsurface example of high
-permeability fluvial sandstone channels embedded in a low permeability
-mudstone background. Such features are often observed in aquifers and
-petroleum reservoirs. Due to the importance of these channels to the
-flow behaviour, their correct representation and resolution is key to
-obtaining reliable solutions. In this model three different sets of
-highly permeable channels are considered. The mesh and permeability
-map for these simulations is shown in Fig.~\ref{fig:fluvial_model}
-(top). The thin channels have a permeability of $\mathbf{K}_\text{3}$,
-the medium size channels $\mathbf{K}_\text{2}$ and the wide channels
-$\mathbf{K}_\text{1}$.
-
-Two numerical simulations are performed using an 8000-element fully
-unstructured mesh. Wetting phase volume fraction maps at two time
-levels are shown in Fig.~\ref{fig:fluvial_model}. Results for
-the \PN[1]{1}DG element pair are shown in the middle, while results
-for the \PN[2]{1}DG element pair are shown in the bottom row. Results
-are in reasonable agreement. It is worth noting that the \PN[1]{1}
-element pair (closest to traditional CVFEM formulation) is numerically
-more dispersive. Nevertheless, these results demonstrate the potential
-of the methods presented here to simulating real-world geometries.
-
-\section{Conclusions}\label{conc}
-
-A novel CVFEM based on the \PN[n]{m}(DG) element pairs with $n^{\rm
-  th}$-order representation for velocity and $m^{\rm th}$-order for
-pressure has been presented. The main advantages of this method over
-existing ones is that arbitrarily high-order polynomial representation
-for pressure and velocity can be used and it is high-order accurate in
-space and time. In addition, for \PN[n]{m}DG element pairs control
-volumes do not span elements, which resolves a long-standing problem
-associated with the use of traditional CVFEM formulations in
-heterogeneous porous media.
-
-The new formulation was evaluated using the Buckley-Leverett benchmark
-and first-order convergence rates were achieved for solutions with
-discontinuities, which is not common in the literature
-(see \cite{Schmid,Hoteit}). Second-order convergence rates were
-achieved for solutions without a discontinuity. More numerical
-simulations were performed to demonstrate the capabilities of the
-methods presented under heterogeneous and high aspect ratio
-computational domains. It was shown that the method is able to resolve
-successfully multi-phase flows under those circumstances. Furthermore,
-the \PN[n+1]{n}DG element pair was shown to completely remove
-numerical dispersion induced by heterogeneous permeabilities.
-
-The formulation presented here was implemented in the open-source
+The formulation presented here is implemented in the open-source
 software framework
 \href{http://www3.imperial.ac.uk/earthscienceandengineering/research/amcg/fluidity}{Fluidity}
-for multi-phase flows (IC-Ferst) and it has been extended to
-include/model multi-component/interface-capturing flows
-\cite{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular
-flows \cite{percival_2014} and oil reservoir flows
-\cite{jackson_2015,mostaghimi_2015, Salinas}.
+for multiphase flows and it has been extended to include/model
+multi-component, interface-capturing
+\citep{pavlidis_2013b,pavlidis_2014,xie_2014}, segregation in granular
+flows~\citep{percival_2014} and oil reservoirs
+\citep{jackson_2013,mostaghimi_2015, Salinas}.
 
 \ack Dr D. Pavlidis would like to acknowledge the support from the
-following research grants: Innovate UK `Octopus', EPSRC `Reactor
-Core-Structure Re-location Modelling for Severe Nuclear Accidents')
-and Horizon 2020 `In-Vessel Melt Retention'. Funding for Dr P. Salinas
-from ExxonMobil is gratefully acknowledged. Dr Z. Xie is supported by
-EPSRC `Multi-Scale Exploration of Multiphase Physics in Flows'. Part
-funding for Prof Jackson under the TOTAL Chairs programme at Imperial
-College is also acknowledged. The authors would also like to acknowledge
-Mr Y. Debbabi for supplying analytic solutions.
+following research grants: EPSRC ($\lq$Computational Modelling for
+Advanced Nuclear Power Plants') and EU/FP7 THINS. Funding for Dr
+P. Salinas from ExxonMobil is gratefully acknowledged. Dr Z. Xie is
+supported by EPSRC ($\lq$Multi-Scale Exploration of Multiphase Physics
+in Flows' -- MEMPHIS). Part funding for Prof Jackson under the TOTAL
+Chairs programme at Imperial College is also acknowledged.
 
-\bibliographystyle{wileyj}
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv}
 \bibliography{references}

### 2018-03-13 Papers/SPE_OffshoreEurope/Upscaling_with_OCVFEM.tex

@@
 Three different mesh sizes were used to explain the relevance of optimizing the mesh size with respect to the distance between the nearest discrete data points.
-And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator \red{(?)} \TL{Just to explain that the mesh size selected was not arbitrary}.
+And, it was shown that a mesh size that is relatively small compared to the distance between the nearest discrete data points produced unnecessarily large computational load for the simulator.
 The simulation was for an easily computed 2D gas-injection.

### 2018-03-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex

@@
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \cite{brooks_1964} model was used \citep{alpak_1999},
+In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
 \begin{eqnarray}
@@
 \subsection{Model Set-up}\label{section:results_setup} 
-Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}.
+Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{jackson_2013,gomes_2017}.
 This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.

### 2018-03-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Started working on section title SVD application

@@
 
-\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}
+\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}\label{section:svd}
+\section{A Brief Introduction to SVD}\label{subsection:svd_brief}
+
+Singular Value Decomposition
 

### 2018-03-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex

@@
 
-  \title{ Numerical Investigation of Stochastic and Determininstic Upscaling Methods for Permeability Fields; Using SVD}
-\author[UoA]{Babatunde Lashore} \author[UoA]{J.L.M.A. Gomes}
+\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD, by Interpolating in the Principal Component Spaces}
+\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{J.L.M.A. Gomes} \author[UoA]{K. Christou}
 \cortext[cor1]{Corresponding author.}
@@
 A brief summary of the pre-processing step for each of the models is also presented.
-Section 4 provides the results of for the simulations, Section 5 discusses the results of the simulations and gives further intepretation to the result obtained from the SVD upscaling techniques; and section 6 provides the conclusion.
+Section 4 provides the results and some discussion on the results of the simulations.
+It als gives further intepretation to the result obtained from the SVD upscaling technique.
+Finally, section 5 provides the conclusion.
 
 \section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}\label{section:svd}
-\section{A Brief Introduction to SVD}\label{subsection:svd_brief}
+\subsection{A Brief Introduction to SVD}\label{subsection:svd_brief}
 
-Singular Value Decomposition
+Singular Value Decomposition, SVD, exists within the linear algebra branch of mathematics as one of the most exciting means of factorizing a matrix, $\mathbf{A}$, into three parts $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$.
+Where $\mathbf{U}$ and $\mathbf{V}$ are orthonormal, and $\Sigma$ is a diagonal matrix.
+If $\mathbf{A}$, is a square matrix then $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$ are square matrix and $\mathbf{U}^{\intercal}\mathbf{U} = \mathbf{V}^{\intercal}\mathbf{V} = \mathbf{I}$.
+But if $\mathbf{A}$ is an $m * n$ matrix, $\mathbf{U}$ and $\mathbf{V}$ still remain as square matrices, albeit with different matricial sizes.
+$\mathbf{U}$ is an $m * m$ while $\mathbf{V}$ is an $n * n$.
+Another interesting property of $\mathbf{U}$ and $\mathbf{V}$ since they are square (irrespective of whether A is square or rectangular) is that $\mathbf{U}^{-1} = \mathbf{U}^{\intercal}$ and $\mathbf{V}^{-1} = \mathbf{V}^{\intercal}$.
+When $\mathbf{A}$ is an $m * n$ matrix, $\Sigma$ is a diagonal $m x n$ matrix.
+The diagonal entries of $\Sigma$ (in both the case of square and rectangular matrices) are referred to as the singular values of $\mathbf{A}$, and are usually denoted by sigma ($\sigma_{1}, \sigma_{2},..., \sigma_{r}$).
+For a rectangular matrix, the singular values fill the first $r$ places on the main diagonal of $\Sigma$, where $r$ is the rank of A.
+Additionally, the $i$th singular value, $\sigma_{i}$ is ordered such that $\sigma_{1} \geq \sigma_{2} \geq ...\geq \sigma_{r}$.
+A huge benefit of the SVD is the orthogonality of the columns in $\mathbf{U}$ and $\mathbf{V}$.
+The columns of $\mathbf{U}$ are known as the left singular vectors while the columns in $\mathbf{V}$ are known as the right singular vectors.
+A simple consideration of the benefit of this, is the ease with which it allows the inverse of square matrix $\mathbf{A}$ to be calculated.
+This example is presented thus:
+
+\begin{equation}
+ \mathbf{A}x = b
+\end{equation}
+\begin{equation}
+ \mathbf{U} \Sigma \mathbf{V}^{\intercal} x = b
+\end{equation}
+\begin{equation}
+ x = \mathbf{V} \Sigma^{-1} \mathbf{U}^{\intercal} b
+\end{equation}
+
+\section{Simulation Setup}\label{section:simulation_setup}
+
+\section{Results and Discussion}\label{section:results_discussion}
+
+\section{Conclusion}\label{section:conclusion}
 

### 2018-03-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex

@@
 
+Four upscaled models were obtained from a base case which is a high-resolution permeability field with a known permeability distribution.
+The base case consists of four regions, where each region is uniformly randomly generated within a specified range.
+For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
+Newmann ({\it i.e.} no flux) boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face.
+Fig (...........)a shows the permeability field of the base case while fig
+
 \section{Results and Discussion}\label{section:results_discussion}

### 2018-03-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Draft for Section 1-3 typed out. Section 4(Results and Discussion) and Section 5 (Conclusion) outstanding

@@
 
-\section{Simulation Setup}\label{section:simulation_setup}
+\subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
+
+Blah blah visualizing the spaces blah
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\section{Model Description and Simulation Setup}\label{section:model_simulation}
+blah blah about geology
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+
+\subsection{Model Description}\label{subsection:model}
+The model for the permeabiliy field builds on the $2 * 2$ block, $4$ quadrant model used by 
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
 
@@
 The base case consists of four regions, where each region is uniformly randomly generated within a specified range.
+
+\subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
+\begin{enumerate}[1]
+  \item A function is used to randomly generate uniform ({\it i.e.} Gaussian) data for each block. The range for each block is as below:
+  \begin{enumerate}[a]
+    \item \textbf{K1} :
+    \item \textbf{K2} :
+    \item \textbf{K3} :
+    \item \textbf{K4} : 
+  \end{enumerate}                                                    
+  \item The number of data generated for each block is $1600$ and the data is randomly position within each block in a structured pattern.
+Albeit, the simulation grid ({\it i.e.} mesh) is unstructured.
+  \item Merge data from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned data in each block.
+This file will be used by the Control Volume Finite Element Method (CVFEM) simulator to prescribe the permeability field for the base case.
+\end{enumerate}
+
+\subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
+\begin{enumerate}[1]
+  \item Data from step one of the pre-processing algorithm for the base case is used to calculate the mean and standard deviation for each block of the permeability field.
+  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the base case for each of the four blocks.
+  \item The number of data generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
+As in the base case, the simulation grid ({\it i.e.} mesh) is unstructured.
+  \item Finally, the structured data from each block is combined into a single file and then provided to the CVFEM simulator.
+\end{enumerate}
+
+\subsubsection{SVDCase Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
+\begin{enumerate}[1]
+  \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
+  \item A selected number, $z$, of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
+  \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
+  \item Within each column of $\mathbf{U}$ and $\mathbf{V}$ a linear interpolation is performed to form a new column with the number of data in each column reduced to a half of the original column.
+And, these new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
+  \item The permeability field used for the SVD case is the matrix, $\mathbf{A_{new2}}$ which is defined as $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+It is a permeability field with a quater of the data in the base cased and therefore a permeability field with a reduced order.
+\end{enumerate}
+
+\subsection{Simulations}\label{subsection:simulations}
 For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
 Newmann ({\it i.e.} no flux) boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face.
-Fig (...........)a shows the permeability field of the base case while fig
+Fig (...........)a shows the permeability field of the base case while fig (.......
+- ........) shows the phase saturation field during fluid injection for time, $t = 0.15s, 0.30s, 0.50s, 1.15s, 1.75s$ and $2.95s$.
 
@@
 
+Where are them beautiful screenshots!\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+
 \section{Conclusion}\label{section:conclusion}
+
+Conclude man!\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
+\\
 

### 2018-03-16 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Section 4(Result) and Section 5(Conclusion) still uncompleted; First image placed

@@
 \begin{abstract}
-  BlaBlaBla
+  BlaBlaBlah Nice Abstract 
 \end{abstract}
@@
 
-Blah blah visualizing the spaces blah
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+\subsubsection{Visualizing the permeability space}\label{subsubsection:visualization_permspace}
+In real-life ({\it i.e.}, a 3D geometry), permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining part of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
+Furthermore, the simulator prescribes the permeability field using $P0DG$ element type, which means that permeability values are assigned in the middle node of the triangular unstructured mesh used for discretizing the 2D simulation geometry.
+And the value assigned in the middle node of the triangle represents the permeability value for the whole triangular element.
+But for simplicity, in the remaining part of this section, we will imagine or assume the $2D$ geometry is discritized by a square grid with the value for each square element assigned in the middle of the element.
+This explanation allow one to easily visualize this permeability space because it is defined by the $x,y$ co-ordinates  system which most people are already familiar with.
+The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.
+Consider for instance a small square which is discretized to contain four squares such that $4$ data values are defined in the middle of the four squares.
+The permeability space of $4$ can be reduced to a smaller value of $1$ through an averaging process such as arithmetic, harmonic or geometric mean.
+This type of reduction is the focus of this paper, albeit the main focus of this paper is achieving this reduction through singular value decomposition in the principal component spaces.
+
+\subsubsection{Visualizing the principal component spaces}\label{subsubsection:visualization_pcspaces}
+Essentially, the existing permeability space is transformed through SVD to principal component spaces where usually, traditional principal component analysis is performed before interpolation is used to implement further data reduction in the principal component spaces.
+This reduced data in the principal component space is then transformed back into the permeability space to obtain a reduced permeability space.
+
+The principal component space is a bit more challenging to visualize because it usually consists of more than $3$ dimensions.
+$3D$ ({\it i.e.}, $x, y$ and $z$ in the cartesian plane) being the natural dimension which humans exist, is easy to visualize.
+Many engineers are also able to visualize 4D with time as the fourth dimension, albeit only few scientists and engineers are able to visualize and work in the abstract dimension where the number of dimensions exceed four.
+An aid for visualizing the PC space is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or imagine the matrices written out) and consider the singular vectors ({\it i.e.},columns in $\mathbf{U}$ and rows in $\mathbf{U}$) as separate principal component spaces.
+
+\subsubsection{Model Order Reduction/Principal Component Space Reduction}\label{subsubsection:svdcase_preprocess_algorithm}
+ For the SVD model order reduction of the permeability field, all the work is done in the principal component spaces.
+This can be completed in two steps.
+The first step is optional and it is the well known principal component analysis (PCA).
+Here, the singular values are examined and based on a pre-defined criteria, z singular values are selected, starting from $\sigma_{1}$ and in a decreasing order.
+$z \leq r$, where in the case $z = r$, it can be assumed that step 1 has been ignored.
+In the case where $z < r$, the first z columns of $\mathbf{U}$ and the first z rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
+The selected z singular values also for a new diagonal matrix ({\it i.e.}, where $z < r$).
+
+The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$), to reduce the number of data in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
+The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$ $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
+
 \section{Model Description and Simulation Setup}\label{section:model_simulation}
 blah blah about geology
-\\
-\\
 \\
@@
 \input{article_figure1}
-%\input{article_figure2}
 

### 2018-03-16 Papers/AppliedMaths2018/article_figure1.tex
Section 4(Result) and Section 5(Conclusion) still uncompleted; First image placed

@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot30.png}
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot50.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{4.cm} (b) t=0.30s \hspace{3.75cm} (c) t=0.50s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot75.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_2dot95.png}}
+\vspace{0.cm}
+\hbox{ \hspace{1.cm} (d) t=1.15s \hspace{3.0cm} (e) t=1.75s   \hspace{4.0cm} (f) t=2.95s}
+\vspace{0.cm}
+}   
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+The domain contains $26313$ \PN[1]{2} triangular elements.}
+\label{fig:homoheleshaw_VN3}
+\end{figure}
+\end{landscape}
+\clearpage

### 2018-03-23 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Section 3 is an afterthought; Section 5 and 6 (Results and Conclusion) are have not been started)

@@
 \newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
-\newcommand{\KCnote}[1]{\fbox{\parbox{\textwidth}{ \color{black} KC Note $\Rightarrow$ #1}}}
+\newcommand{\BLnote}[1]{\fbox{\parbox{\textwidth}{ \color{green} BL Note $\Rightarrow$ #1}}}
 \newcommand{\red}{\textcolor{red}}
@@
 \begin{abstract}
-  BlaBlaBlah Nice Abstract 
+Nice Abstract - Short, punchy
+\\
+\\
+\\
+\\
+\\
+\\ 
 \end{abstract}
@@
 
+\section{Brief Overview of Upscaling}\label{section:overview_upscaling}
+
+The first section briefly introduced the rational behind upscaling.
+This is a subject which has interested the academic community for over $7$ decades.
+\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities.
+\citet{King1996} investigated the use of renormalization for upscaling.
+And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2 dimension hydraulic conductivity fields.
+\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling in \citeyear{Renard_1997}.
+\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
+
 \section{Model Description and Simulation Setup}\label{section:model_simulation}
-blah blah about geology
-\\
-\\
-\\
-\\
-\\
-\\
 
 \subsection{Model Description}\label{subsection:model}
-The model for the permeabiliy field builds on the $2 * 2$ block, $4$ quadrant model used by 
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+The BaseCase  ({\it i.e.} fine resolution) model for the permeabiliy field builds on the $2 * 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other se.
+So that, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
+The BaseCase permeability model used in this manuscript retains the checkerboard desgined used by the recently named authors.
+Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value ({\it i.e.} not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+Futhermore, within each block, the permeability field varies within a predefined range and consists of $1600$ permeability values.
+More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
+And Fig.~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible respectively.
+Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1, K2, K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.
 
-Four upscaled models were obtained from a base case which is a high-resolution permeability field with a known permeability distribution.
-The base case consists of four regions, where each region is uniformly randomly generated within a specified range.
+Four upscaled permeability field models were obtained from the high-resolution ({\it i.e.} the BaseCase) permeability field.
+And compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field.
+Specifically, for the simulation domain, the high resolution ({\it i.e.} BaseCase) model had 4112 triangular elements while the upscaled models had 728 triangular elements.
+The first two upscaled models are referred to as the ArithMean and the HarmMean Case, and this is because they are based on the arithmetic and the harmonic averaging methods, respectively.
+In both the ArithMean and HarmMean Cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
+This effectively homogenizes the permeability field in each block.
+The upscaled permeability field for the third and fourth cases are referred to as PDFCase and SVDCase, respectively.
+And, as can be deduced from the names, these cases are based on probability density function (PDF) and singular value decomposition (SVD).
+The description for these permeability field models are more involved and are presented in section ~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
+It is appropriate to note that although these models (PDFCase and SVDCase) are upscaled, they retain heterogeneity within the blocks.
 
@@
 
-Where are them beautiful screenshots!\\
+Talk about those beautiful screenshots!\\
 \\

### 2018-03-23 Papers/AppliedMaths2018/article_figure1.tex
Section 3 is an afterthought; Section 5 and 6 (Results and Conclusion) are have not been started)

@@
 %%%%
-\begin{figure}[h!]
-   \vbox{
-     \hbox{\includegraphics[width=\columnwidth,clip]{./Pics/PermField_Saturation.png}}
-     \hbox{\hspace{4cm}(a)\hspace{7.8cm}(b)}}
-        \caption{(a) Permeability distribution and (b) phase saturation showing preferential flow pathways.}
-        \label{fig:PermField_Saturation}  
+%\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_MeshOnly.png}
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_MeshOnly.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.25cm} (a) High Resolution Grid(BaseCase) \hspace{0.75cm} (b) Low Resolution Grid(Upscaled Cases) \hspace{3.0cm}}
+\vspace{0.5cm}
+}   
+\caption{Simulation grid for the high resolution case and the upscaled cases}
+\label{fig:HiRes_LowRes_Mesh}
 \end{figure}
+%\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
+      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_PermField_withoutMesh2.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) BaseCase(with mesh) \hspace{3.75cm} (b) BaseCase(without Mesh) \hspace{3.0cm} (c) ArithMean Case}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_PermField_withoutMesh2.png}
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_PermField_withoutMesh2.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_PermField_withoutMesh2.png}}
+\vspace{0.cm}
+\hbox{ \hspace{1.5cm} (d) HarmMean Case \hspace{4.75cm} (e) PDFCase  \hspace{5.0cm} (f) SVDCase}
+\vspace{0.cm}
+}   
+\caption{Permeability field for the base case as well as the upscaled case}
+\label{fig:PermFields}
+\end{figure}
+\end{landscape}
 \clearpage
@@
 \vspace{0.cm}
-\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{4.cm} (b) t=0.30s \hspace{3.75cm} (c) t=0.50s}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{3.75cm} (b) t=0.30s \hspace{5.0cm} (c) t=0.50s}
 \vspace{0.5cm}
@@
 \vspace{0.cm}
-\hbox{ \hspace{1.cm} (d) t=1.15s \hspace{3.0cm} (e) t=1.75s   \hspace{4.0cm} (f) t=2.95s}
+\hbox{ \hspace{2.5cm} (d) t=1.15s \hspace{5.5cm} (e) t=1.75s   \hspace{5.5cm} (f) t=2.95s}
 \vspace{0.cm}
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $26313$ \PN[1]{2} triangular elements.}
-\label{fig:homoheleshaw_VN3}
+\caption{Simulations for the BaseCase}
+\label{fig:BaseCase_Saturation}
 \end{figure}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot30.png}
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot50.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{3.75cm} (b) t=0.30s \hspace{5.0cm} (c) t=0.50s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot75.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_2dot95.png}}
+\vspace{0.cm}
+\hbox{ \hspace{2.5cm} (d) t=1.15s \hspace{5.5cm} (e) t=1.75s   \hspace{5.5cm} (f) t=2.95s}
+\vspace{0.cm}
+}   
+\caption{Simulations for the ArithMean Case}
+\label{fig:ArithMeanCase_Saturation}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot30.png}
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot50.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{3.75cm} (b) t=0.30s \hspace{5.0cm} (c) t=0.50s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_1dot75.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_2dot95.png}}
+\vspace{0.cm}
+\hbox{ \hspace{2.5cm} (d) t=1.15s \hspace{5.5cm} (e) t=1.75s   \hspace{5.5cm} (f) t=2.95s}
+\vspace{0.cm}
+}   
+\caption{Simulations for the HarmMean Case}
+\label{fig:HarmMeanCase_Saturation}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot30.png}
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot50.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{3.75cm} (b) t=0.30s \hspace{5.0cm} (c) t=0.50s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_1dot75.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_2dot95.png}}
+\vspace{0.cm}
+\hbox{ \hspace{2.5cm} (d) t=1.15s \hspace{5.5cm} (e) t=1.75s   \hspace{5.5cm} (f) t=2.95s}
+\vspace{0.cm}
+}   
+\caption{Simulations for the PDFCase}
+\label{fig:PDFCase_Saturation}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot30.png}
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot50.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) Phase 1 Saturation at t=0.15s \hspace{3.75cm} (b) t=0.30s \hspace{5.0cm} (c) t=0.50s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_1dot75.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_2dot95.png}}
+\vspace{0.cm}
+\hbox{ \hspace{2.5cm} (d) t=1.15s \hspace{5.5cm} (e) t=1.75s   \hspace{5.5cm} (f) t=2.95s}
+\vspace{0.cm}
+}   
+\caption{Simulation for the SVDCase}
+\label{fig:SVDCase_Saturation}
+\end{figure}
+\end{landscape}
+\clearpage

### 2018-03-24 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Updates

@@
 
-\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD, by Interpolating in the Principal Component Spaces}
+\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD, by Interpolating in the Principal Component Spaces \red{(Maybe you should consider a shorter and punchier title ...)}}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{J.L.M.A. Gomes} \author[UoA]{K. Christou}
 \cortext[cor1]{Corresponding author.}
-\address[UoA]{Mechanics of Fluids, Soils \& Structures Group, School of Engineering, University of Aberdeen, UK}
+\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering University of Aberdeen, UK}
 
@@
 \section{Introduction}\label{section:intro}
-Naturally occuring rock formations are inherently heterogeneous, which means that the rock properties such as permeability, pore spaces ({\it i.e.}, porosity) and pore throat vary from point to point, and at different length scales.
-The heterogeneity of rock formations (studied under the general title of porous media) is relevant in calculations required for understanding transportation and storage of fluids in porous media.
-This is because the heterogeneous properties are important parameters in the mathematical models used for the aforementioned calculations.
-Therefore, the representation of these heterogeneous properties is of great importance to the porous media and applied mathematics community as well as the oil and gas industry, the Carbon Capture and Storage (CCS) industry, and waste management industry for whom this has direct application in reservoir management, CO$_2$ transportation and storage in subsurface rocks and remediation of contaminated soil respectively.
+Naturally occuring rock formations are inherently heterogeneous, which means that rock properties such as permeability, pore spaces ({\it i.e.}, porosity) and pore throat vary spatially at different length scales.
+The heterogeneity of rock formations (\ie porous media) is relevant in calculations of transport and storage of fluids in porous media.
+Therefore, the representation of these heterogeneous properties is of great importance to oil and gas (\ie reservoir management), carbon capture and storage (CCS, \ie CO$_2$ transportation and storage in subsurface rocks) and waste management (\ie remediation of contaminated soil).
 
-Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain (\ie scale problems) \cite{Renard_1997} \cite{miller_1998} \cite{chen_2006}.
+\JGnote{You need to ensure that the paragraphs are somehow linked ... \eg how is the first sentence of the following paragraph linked with the previous paragraph? }
+
+Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all spatial coordinates of the domain (\ie scale problems) \cite{chen_2006,miller_1998,Renard_1997}.
 This is particularly true for large geological domains which span several kilometres.
-Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems).
+Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems) \red{(Isn't this sentence a repetition of the first one?)}.
 It is possible to overcome these challenges by upscaling.
-Upscaling techniques solve both problems by replacing discrete geological and fluid property values of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-And upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain gives the best representation of the heterogeneous property.
+Upscaling techniques solve both problems by replacing discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
 
-There are several upscaling techniques which fall under different categories \cite{Renard_1997, Szymkiewicz_2013, Hasting_2001}, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Verwoerd_2009, Ravalec-Dupin_2010, Guilleminot_2012}.
+Upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of the heterogeneous property.
+There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
 One of the reasons for this is because stochastic techniques are robust enough to handle multiphase flow in porous media, and they address scale and uncertainity problems which were previously mentioned.
 
+\JGnote{The technique we are using/advocating here is not stochastic, though it would be good to develop it further, \ie brief lit review.
+Maybe you should add a few sentences/paragraphs on: ROM and the use of SVD for upscalling ...
+}
+\medskip
+
 This work couples stochastic and deterministic upscaling representations of the permeability field to a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) so as to investigate statistical properties and multiphase flow behaviour in highly heterogeneous porous media.
+\red{(Try to split this really long sentence ...)}
 
-Four upscaling techniques are investigated in this research.
-The arithmetic and harmonic mean are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
-The third is a randomly generated permeability field with a Guassian distribution, prescribed by a probability density function (PDF) which was obtained from a base case ({\it i.e.}, high-resolution mesh with known permeability distribution).
-The four upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using interpolation within the concept of principal component space to reduce the order of the permeability field.
+Four upscaling techniques are investigated in this work.
+Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
+The third is a randomly generated permeability field with a Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie  base case).
+The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using interpolation within the concept of principal component space to reduce the order of the permeability field \red{(Sentence is quite confusing and does not say much ...)}.
 
-In section 2, the basic mathematical explanation of SVD and its associated linear algebra properties are presented.
-The the concept of spaces is explained from the engineer's perspective and also from the mathematician's perspective.
+In Section 2, the basic mathematical explanation of SVD and its associated properties are presented.
+Then, the concept of spaces is explained from the engineer's perspective and also from the mathematician's perspective.
 The objective of this explanation is to assist both parties in visualizing the relevant spaces and performing the necessary transformation within those spaces.
@@
 
-Singular Value Decomposition, SVD, exists within the linear algebra branch of mathematics as one of the most exciting means of factorizing a matrix, $\mathbf{A}$, into three parts $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$.
+Singular Value Decomposition, SVD, \JGnote{ioioioiok} exists within the linear algebra branch of mathematics as one of the most exciting means of factorizing a matrix, $\mathbf{A}$, into three parts $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$.
 Where $\mathbf{U}$ and $\mathbf{V}$ are orthonormal, and $\Sigma$ is a diagonal matrix.

### 2018-03-26 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Updates

@@
 \newcommand{\ie}{{\it i.e., }}
+\newcommand{\st}{{\it s.t., }}
 
@@
 In Section 2, the basic mathematical explanation of SVD and its associated properties are presented.
-Then, the concept of spaces is explained from the engineer's perspective and also from the mathematician's perspective.
-The objective of this explanation is to assist both parties in visualizing the relevant spaces and performing the necessary transformation within those spaces.
-Finally, the section describes model order space reduction for the permeability field within the principal component space.
+Then, the concept of spaces\red{(spaces ...
+could you be more specific?)} is explained from the engineer's perspective and also from the mathematician's perspective \red{(Please do rephrase this sentence ...
+engineers/mathematician perspective is not appropriate for a scientific journal ...)}.
+The objective of this explanation is to assist both parties in \green{visualizing} the relevant spaces and performing the necessary transformation within those spaces.
+Finally, the section \red{(which section?)} describes model order space reduction for the permeability field within the principal component space.
 Section 3, starts by describing the high resolution base case on which the four upscaling techniques are modelled.
@@
 \subsection{A Brief Introduction to SVD}\label{subsection:svd_brief}
-
-Singular Value Decomposition, SVD, \JGnote{ioioioiok} exists within the linear algebra branch of mathematics as one of the most exciting means of factorizing a matrix, $\mathbf{A}$, into three parts $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$.
-Where $\mathbf{U}$ and $\mathbf{V}$ are orthonormal, and $\Sigma$ is a diagonal matrix.
-If $\mathbf{A}$, is a square matrix then $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$ are square matrix and $\mathbf{U}^{\intercal}\mathbf{U} = \mathbf{V}^{\intercal}\mathbf{V} = \mathbf{I}$.
-But if $\mathbf{A}$ is an $m * n$ matrix, $\mathbf{U}$ and $\mathbf{V}$ still remain as square matrices, albeit with different matricial sizes.
-$\mathbf{U}$ is an $m * m$ while $\mathbf{V}$ is an $n * n$.
-Another interesting property of $\mathbf{U}$ and $\mathbf{V}$ since they are square (irrespective of whether A is square or rectangular) is that $\mathbf{U}^{-1} = \mathbf{U}^{\intercal}$ and $\mathbf{V}^{-1} = \mathbf{V}^{\intercal}$.
-When $\mathbf{A}$ is an $m * n$ matrix, $\Sigma$ is a diagonal $m x n$ matrix.
-The diagonal entries of $\Sigma$ (in both the case of square and rectangular matrices) are referred to as the singular values of $\mathbf{A}$, and are usually denoted by sigma ($\sigma_{1}, \sigma_{2},..., \sigma_{r}$).
-For a rectangular matrix, the singular values fill the first $r$ places on the main diagonal of $\Sigma$, where $r$ is the rank of A.
-Additionally, the $i$th singular value, $\sigma_{i}$ is ordered such that $\sigma_{1} \geq \sigma_{2} \geq ...\geq \sigma_{r}$.
-A huge benefit of the SVD is the orthogonality of the columns in $\mathbf{U}$ and $\mathbf{V}$.
+Given a matrix $\mathbf{A}\in\mathcal{R}^{m\times n}$, the singular value decomposition (SVD) is a method for factorizing $\mathbf{A}$, such that,
+\begin{equation}
+  \mathbf{A} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}^{\intercal}.
+\end{equation}
+where $\mathbf{U}=\left[\underline{u}_{1},\underline{u}_{2},\cdots,\underline{u}_{m}\right]\in\mathcal{R}^{m\times n}$ and $\mathbf{V}=\left[\underline{v}_{1},\underline{v}_{2},\cdots,\underline{v}_{n}\right]\in\mathcal{R}^{m\times n}$ are orthogonal but not necessarily the same.
+$\Sigma$ is a diagonal matrix, \ie $\Sigma=\text{diag}\left(\sigma_{1},\sigma_{2},\cdots,\sigma_{r}\right)\in\mathcal{R}^{m\times n}$ and $r=\min\left\{m,n\right\}$ is the rank of $\mathbf{A}$, with $\sigma_{1}\ge\sigma_{2}\ge\cdots\sigma_{r}\ge 0$.
+The diagonal entries of $\Sigma$ $\left(\ie \sigma_{i}, i=1,r\right)$ are called singular values of $\mathbf{A}$.
+If $\mathbf{A}$ is a square matrix then $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$ are also square matrices.
+Also, as $\mathbf{U}$ and $\mathbf{V}$ are orthogonals and unitary,
+\begin{equation}
+  \mathbf{U}^{\intercal}\mathbf{U} = \mathbf{V}^{\intercal}\mathbf{V} = \mathbf{I},
+\end{equation}
+where $\mathbf{I}$ is an identity matrix.
+However, if $\mathbf{A}$ is an $m\times n$ matrix, $\mathbf{U}$ and $\mathbf{V}$ still remain as square matrices, albeit with different matricial sizes.
+$\mathbf{U}$ is an $m\times m$ while $\mathbf{V}$ is an $n\times n$.
+Another relevant property of $\mathbf{U}$ and $\mathbf{V}$ since they are square (irrespective of whether $\mathbf{A}$ is square or rectangular) is that
+\begin{equation}
+  \mathbf{U}^{-1} = \mathbf{U}^{\intercal} \;\;\;\text{ and }\;\;\; \mathbf{V}^{-1} = \mathbf{V}^{\intercal},
+\end{equation}
+and if $\mathbf{A}$ is an $m \times n$ matrix thus $\Sigma$ is a diagonal $m \times n$ matrix.
+For a rectangular matrix, the singular values fill the first $r$ places on the main diagonal of $\Sigma$.
+A benefit of the SVD is the orthogonality of the columns in $\mathbf{U}$ and $\mathbf{V}$.
 The columns of $\mathbf{U}$ are known as the left singular vectors while the columns in $\mathbf{V}$ are known as the right singular vectors.
-A simple consideration of the benefit of this, is the ease with which it allows the inverse of square matrix $\mathbf{A}$ to be calculated.
+A simple consideration of the benefit of this is the ease with which it allows the inverse of square matrix $\mathbf{A}$ to be calculated.
 This example is presented thus:
-
 \begin{equation}
@@
 \end{equation}
+\red{(I guess we have talked about this on Friday ...
+make it clear that matrix inversion is an (useful?) example of SVD ...
+also explain step-by-step this matricial equations above ...
+remember ...
+every single equation must be explained ...)}
 
 \subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
+\JGnote{As we talked on Friday: (a)make sure you explain what permeability is before starting to operating on it; (b) $P0DG$ could be easily replaced by saying that the quantity of interest is allocated in the centre of the element/cell -- this make it more general; (c) Just reading it through, we can summarise the {\it procedure} as (i) SVD of matrix of permeability scalar quantities (\ie upscaling) and (ii) linear interpolation of the upscaled/homogeneised quantities upon a new mesh grid resolution (\ie upgriding).
+Whereas the first is the object of the interest for this study, the second gives an overall motivation for the work ...
+thus, make sure this is clear within the text, \ie upscaling $\rightarrow$ upgriding.}
 
 \subsubsection{Visualizing the permeability space}\label{subsubsection:visualization_permspace}
-In real-life ({\it i.e.}, a 3D geometry), permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining part of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
+In 3D geometry, permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining part of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
 Furthermore, the simulator prescribes the permeability field using $P0DG$ element type, which means that permeability values are assigned in the middle node of the triangular unstructured mesh used for discretizing the 2D simulation geometry.
@@
 
+\JGnote{Maybe you should consider describing the procedure above as pseudocode within a table.}
+
 \section{Brief Overview of Upscaling}\label{section:overview_upscaling}
 
-The first section briefly introduced the rational behind upscaling.
+The first section \red{(Are you referring to Section 1 -- Intro or Section 2?)} briefly introduced the rational behind upscaling.
+Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
 This is a subject which has interested the academic community for over $7$ decades.
@@
 \citet{King1996} investigated the use of renormalization for upscaling.
-And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2 dimension hydraulic conductivity fields.
-\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling in \citeyear{Renard_1997}.
+And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields.
+\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
 \citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
+\red{(And what are the main conclusions/contributions of these papers?)}
 

### 2018-04-08 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Updates
First Final Draft :)

@@
 \newcommand{\green}{\textcolor{green}}
+\newcommand{\yellow}{\textcolor{yellow}}
 \newcommand{\frc}{\displaystyle\frac}
@@
 
-\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD, by Interpolating in the Principal Component Spaces \red{(Maybe you should consider a shorter and punchier title ...)}}
-\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{J.L.M.A. Gomes} \author[UoA]{K. Christou}
+\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD}
+\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
 \cortext[cor1]{Corresponding author.}
@@
 \begin{abstract}
-Nice Abstract - Short, punchy
-\\
-\\
-\\
-\\
-\\
-\\ 
+
+In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced.
+This method was compared to arithmetic and harmonic averaging (\ie upscaling) technique as well as a stochastic probability density function (PDF) method of upscaling, to highlight its benefits.
+It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase.
+Additionally, the SVD upscaling technique did not require a priori understanding of similar permeability blocks within the existing domain (\ie the BaseCase).
+
 \end{abstract}
@@
 Naturally occuring rock formations are inherently heterogeneous, which means that rock properties such as permeability, pore spaces ({\it i.e.}, porosity) and pore throat vary spatially at different length scales.
-The heterogeneity of rock formations (\ie porous media) is relevant in calculations of transport and storage of fluids in porous media.
+The heterogeneity of rock formations (\ie porous media) is relevant in calculations of transport and storage of fluids in porous media (\ie Multiphase flow in subsurface rocks).
 Therefore, the representation of these heterogeneous properties is of great importance to oil and gas (\ie reservoir management), carbon capture and storage (CCS, \ie CO$_2$ transportation and storage in subsurface rocks) and waste management (\ie remediation of contaminated soil).
 
-\JGnote{You need to ensure that the paragraphs are somehow linked ... \eg how is the first sentence of the following paragraph linked with the previous paragraph? }
-
-Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all spatial coordinates of the domain (\ie scale problems) \cite{chen_2006,miller_1998,Renard_1997}.
+In essence, heterogeneity makes it impossible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems).
+Additionally, due to limitations in computing resources, it is neither efficient nor possible to use exact values of geological properties at all spatial coordinates of the domain for running fine-grid simulations (\ie scale problems) \cite{chen_2006,miller_1998,Renard_1997}.
 This is particularly true for large geological domains which span several kilometres.
-Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems) \red{(Isn't this sentence a repetition of the first one?)}.
 It is possible to overcome these challenges by upscaling.
@@
 Upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of the heterogeneous property.
-There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
-One of the reasons for this is because stochastic techniques are robust enough to handle multiphase flow in porous media, and they address scale and uncertainity problems which were previously mentioned.
+There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
+Traditionally, the techniques were deterministic, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
+One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media, and they address scale and uncertainity problems which were previously mentioned.
 
-\JGnote{The technique we are using/advocating here is not stochastic, though it would be good to develop it further, \ie brief lit review.
-Maybe you should add a few sentences/paragraphs on: ROM and the use of SVD for upscalling ...
-}
-\medskip
+Upscaling is a term used in a few industries, some of which were mentioned in the first paragraph.
+It is more popularly known in the larger science and engineering community as a form of Model Order Reduction (MOR), or the output (\ie Reduced Order Model, ROM).
+Depending on the context in which MOR is being used, it can simply be referred to as dimensionality reduction.
+The definition of MOR also depends on the context it is being used \cite{Schilders2008}, but it suffices to state that MOR captures the essential features of a system, structure or parameter.
+This implies that an original system, structure or parameter exists with more detailed information.
+Fig.~\ref{fig:IllustrationMOR} presents a graphical intepretation of the MOR concept.
+It shows that even with the reduced number of facets, the graphic on the right of this illustration is recognized as that of a rabbit.
 
-This work couples stochastic and deterministic upscaling representations of the permeability field to a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) so as to investigate statistical properties and multiphase flow behaviour in highly heterogeneous porous media.
-\red{(Try to split this really long sentence ...)}
+\citet{Schilders2008} provides a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric term, to the work of \citet{Odabasioglu_1998} in 1998 which introduced PRIMA - Passive Reduced-order Interconnect Marcromodeling Algorithm.
+Truncated Balanced Realization \cite{Moore_1981} is one of the MOR methods, published in 1981, it called attention to principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods published in 1984 and 1987 respectively.
+In 1990, Asymptotic Waveform Evaluation \cite{Pillage_1990} the first MOR method related to the Krylov was born, this was followed by Pade Via Lanczos \cite{Feldmann_1995} in 1995 and then PRIMA.
+In this work, upscaling is performed by SVD in the principal component spaces.
+
+The research focuses on reducing the order of the permeability field.
+Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
+The mathematical model is discretized by a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) which couples both the fine resolution and upscaled representation of the permeability field.
+Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.
 
@@
 The third is a randomly generated permeability field with a Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie  base case).
-The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using interpolation within the concept of principal component space to reduce the order of the permeability field \red{(Sentence is quite confusing and does not say much ...)}.
+The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability field.
 
-In Section 2, the basic mathematical explanation of SVD and its associated properties are presented.
-Then, the concept of spaces\red{(spaces ...
-could you be more specific?)} is explained from the engineer's perspective and also from the mathematician's perspective \red{(Please do rephrase this sentence ...
-engineers/mathematician perspective is not appropriate for a scientific journal ...)}.
-The objective of this explanation is to assist both parties in \green{visualizing} the relevant spaces and performing the necessary transformation within those spaces.
-Finally, the section \red{(which section?)} describes model order space reduction for the permeability field within the principal component space.
-Section 3, starts by describing the high resolution base case on which the four upscaling techniques are modelled.
+In Section~\ref{section:svd}, the basic mathematical explanation of SVD and its associated properties are presented.
+Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work.
+Finally, the Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space.
+Section~\ref{section:model_simulation}, starts by describing the high resolution base case on which the four upscaling techniques are modelled.
 The the simulation run which is similar for all the cases/models is described.
 A brief summary of the pre-processing step for each of the models is also presented.
-Section 4 provides the results and some discussion on the results of the simulations.
-It als gives further intepretation to the result obtained from the SVD upscaling technique.
-Finally, section 5 provides the conclusion.
+Section~\ref{section:results_discussion} provides the results and some discussion on the results of the simulations.
+It also gives further intepretation to the result obtained from the SVD upscaling technique.
+Finally, Section~\ref{section:conclusion} provides the conclusion.
+
+\section{Mathematical Model}\label{section:mathematical_model}
+
+\citet{Gomes_2017} provides details on the governing equations and numerical formulation which forms the mathematical model for the multi-flow flow in this work.
+Albeit, it suffices to introduce only the representation of Darcy's law for immiscible multi-phase flow for the following discussion.
+This is written in the form:
+\begin{equation}\label{e:darcy_eqn}
+  \mathbf{q}_{\alpha} =
+  -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(
+  \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
+\end{equation}
+where $\alpha$ designates a phase and $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+$\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is a function of the vector position $\mathbf{r}$, and time, $t$.
+Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is the absolute permeability tensor of the porous medium and it is a function of the vector position $\mathbf{r}$.
+
+In this work, $\mathbf{K}$ is prescribed in the system of governing equations used to model multi-phase flow in porous media, this means it is an input/independent variable.
+Since $\mathbf{K}$ varies with position, it is impossible to determine at every point and even if it is available at every point it would require immense computer resources to utilize all the available information in a simulation.
+This is the reason upscaling is required for the permeability field.
+Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($Km$)\cite{ECMI_2004}.
+The upscaling discussed here is from the micro scale also known as the Darcy scale.
+
+\section{Brief Overview of Upscaling}\label{section:overview_upscaling}
+
+Section~\ref{section:intro} briefly introduced the rational behind upscaling.
+Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+This is a subject which has interested the academic community for over $7$ decades.
+\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities.
+\citet{King1996} investigated the use of renormalization for upscaling.
+And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields.
+\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
+\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
+\red{(And what are the main conclusions/contributions of these papers?)}
+
+\JGnote{You should consider writing a more detailed section on upscaling as this is part of the core of your work here ...}
+
+\BLnote{I will do this before submitting, please let me know if you will be able to review again on Thursday or Friday}
 
@@
 For a rectangular matrix, the singular values fill the first $r$ places on the main diagonal of $\Sigma$.
-A benefit of the SVD is the orthogonality of the columns in $\mathbf{U}$ and $\mathbf{V}$.
+The SVD benefits from the orthogonality of the columns in $\mathbf{U}$ and $\mathbf{V}$.
 The columns of $\mathbf{U}$ are known as the left singular vectors while the columns in $\mathbf{V}$ are known as the right singular vectors.
-A simple consideration of the benefit of this is the ease with which it allows the inverse of square matrix $\mathbf{A}$ to be calculated.
-This example is presented thus:
-\begin{equation}
+A simple consideration of the benefit of the orthogonal factors, $\mathbf{U}$ and $\mathbf{V}$, is the ease with which they allow the inverse of the square matrix $\mathbf{A}$ to be calculated.
+This in turn makes it easy to solve the linear Equ.~\ref{e:Ax=b} for $x$.
+Equ.~\ref{e:SVD_factorization} show the SVD factorization already discussed, and with benefit of the orthogonal property also already discussed, the solution for $x$ is simply presented as in Equ.~\ref{e:x_solution}.
+\begin{equation}\label{e:Ax=b}
  \mathbf{A}x = b
 \end{equation}
-\begin{equation}
+\begin{equation}\label{e:SVD_factorization}
  \mathbf{U} \Sigma \mathbf{V}^{\intercal} x = b
 \end{equation}
-\begin{equation}
+\begin{equation}\label{e:x_solution}
  x = \mathbf{V} \Sigma^{-1} \mathbf{U}^{\intercal} b
@@
 
+\BLnote{The equations are now explained in the last 3 sentences of this section.}
+
 \subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
@@
 
-\subsubsection{Visualizing the permeability space}\label{subsubsection:visualization_permspace}
+\BLnote{(a)Permeability is now introduced in Section~\ref{section:mathematical_model}; (b) $P0DG$ now replaced with centre of element/cell (c) I thought we agreed that upscaling cannot be separated from upgridding.
+Actually, you convinced me that upscaling cannot be seperated from upgridding.
+Upscaling is not completed in the SVDCase until the interpolation is completed.
+Strictly speaking, interpolation only defines the level of upgridding.
+I will mention this in the results section (Section~\ref{section:results_discussion})}
+
+\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
 In 3D geometry, permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining part of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
-Furthermore, the simulator prescribes the permeability field using $P0DG$ element type, which means that permeability values are assigned in the middle node of the triangular unstructured mesh used for discretizing the 2D simulation geometry.
-And the value assigned in the middle node of the triangle represents the permeability value for the whole triangular element.
-But for simplicity, in the remaining part of this section, we will imagine or assume the $2D$ geometry is discritized by a square grid with the value for each square element assigned in the middle of the element.
-This explanation allow one to easily visualize this permeability space because it is defined by the $x,y$ co-ordinates  system which most people are already familiar with.
+Furthermore, the simulator prescribes the permeability field by assigning permeability values in the centre of the elements/cells which discretizing the 2D simulation domain.
+The permeability value assigned in the centre of the element/cell represents the permeability value for that element/cell.
+For simplicity, in the remaining part of this section, it will be assumed that the $2D$ geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
+This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates  system which most people are already familiar with.
 The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.
@@
 
-\subsubsection{Visualizing the principal component spaces}\label{subsubsection:visualization_pcspaces}
+\subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
 Essentially, the existing permeability space is transformed through SVD to principal component spaces where usually, traditional principal component analysis is performed before interpolation is used to implement further data reduction in the principal component spaces.
@@
 
-The principal component space is a bit more challenging to visualize because it usually consists of more than $3$ dimensions.
-$3D$ ({\it i.e.}, $x, y$ and $z$ in the cartesian plane) being the natural dimension which humans exist, is easy to visualize.
-Many engineers are also able to visualize 4D with time as the fourth dimension, albeit only few scientists and engineers are able to visualize and work in the abstract dimension where the number of dimensions exceed four.
+The principal component space is more challenging to visualize because it usually consists of more than $3$ dimensions.
+$3-D$ ({\it i.e.}, $x, y$ and $z$ in the cartesian plane) being the natural dimension which humans exist, is easy to visualize.
+Many individuals are also able to understand the concept of 4D with time as the fourth dimension, albeit only few scientists and engineers are able to visualize and work in the abstract dimension where the number of dimensions exceed four.
 An aid for visualizing the PC space is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or imagine the matrices written out) and consider the singular vectors ({\it i.e.},columns in $\mathbf{U}$ and rows in $\mathbf{U}$) as separate principal component spaces.
@@
 This can be completed in two steps.
-The first step is optional and it is the well known principal component analysis (PCA).
-Here, the singular values are examined and based on a pre-defined criteria, z singular values are selected, starting from $\sigma_{1}$ and in a decreasing order.
-$z \leq r$, where in the case $z = r$, it can be assumed that step 1 has been ignored.
-In the case where $z < r$, the first z columns of $\mathbf{U}$ and the first z rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
-The selected z singular values also for a new diagonal matrix ({\it i.e.}, where $z < r$).
+The first step is optional and it is the well known principal component analysis (PCA) \cite{Hotelling_1933}.
+Here, the singular values are examined and based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+In the case with $z = r$, it can be assumed that step 1 has been ignored.
+However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
+The selected $z$ singular values also form a new diagonal matrix, $\mathbf{\Sigma_{new}}$ .
 
@@
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
-The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$ $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
+The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
 
@@
 
-\section{Brief Overview of Upscaling}\label{section:overview_upscaling}
-
-The first section \red{(Are you referring to Section 1 -- Intro or Section 2?)} briefly introduced the rational behind upscaling.
-Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-This is a subject which has interested the academic community for over $7$ decades.
-\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities.
-\citet{King1996} investigated the use of renormalization for upscaling.
-And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields.
-\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
-\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
-\red{(And what are the main conclusions/contributions of these papers?)}
+\BLnote{I have an algorithm in Section~\ref{subsubsection:svdcase_preprocess_algorithm} which itemizes the procedure in a sort of psuedocode}
 
@@
 The BaseCase  ({\it i.e.} fine resolution) model for the permeabiliy field builds on the $2 * 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
-These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other se.
-So that, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
+These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
+Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
 The BaseCase permeability model used in this manuscript retains the checkerboard desgined used by the recently named authors.
 Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value ({\it i.e.} not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
-Futhermore, within each block, the permeability field varies within a predefined range and consists of $1600$ permeability values.
+Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
 More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
 And Fig.~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible respectively.
-Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1, K2, K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.
+Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.
 
-Four upscaled permeability field models were obtained from the high-resolution ({\it i.e.} the BaseCase) permeability field.
-And compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field.
-Specifically, for the simulation domain, the high resolution ({\it i.e.} BaseCase) model had 4112 triangular elements while the upscaled models had 728 triangular elements.
-The first two upscaled models are referred to as the ArithMean and the HarmMean Case, and this is because they are based on the arithmetic and the harmonic averaging methods, respectively.
+As already mentioned, four upscaled permeability field models were obtained from the high-resolution ({\it i.e.} the BaseCase) permeability field.
+When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
+The first two upscaled models are referred to as the ArithMean and the HarmMean Cases, and this is because they are based on the arithmetic and the harmonic averaging methods, respectively.
 In both the ArithMean and HarmMean Cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
@@
   \begin{enumerate}[a]
-    \item \textbf{K1} :
-    \item \textbf{K2} :
-    \item \textbf{K3} :
-    \item \textbf{K4} : 
+    \item \textbf{K1} : $700 - 900mD$
+    \item \textbf{K2} : $50 - 150mD$
+    \item \textbf{K3} : $100 - 200mD$
+    \item \textbf{K4} : $1000 - 1200mD$
   \end{enumerate}                                                    
@@
   \item Data from step one of the pre-processing algorithm for the base case is used to calculate the mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the base case for each of the four blocks.
+  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the BaseCase for each of the four blocks.
   \item The number of data generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
@@
   \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-  \item Within each column of $\mathbf{U}$ and $\mathbf{V}$ a linear interpolation is performed to form a new column with the number of data in each column reduced to a half of the original column.
+  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ a linear interpolation is performed to form a new column with the number of data in each column reduced to a half of the original column.
 And, these new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
-  \item The permeability field used for the SVD case is the matrix, $\mathbf{A_{new2}}$ which is defined as $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+  \item The permeability field used for the SVD case is the matrix, $\mathbf{A_{new2}}$ which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
 It is a permeability field with a quater of the data in the base cased and therefore a permeability field with a reduced order.
@@
 Newmann ({\it i.e.} no flux) boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face.
-Fig (...........)a shows the permeability field of the base case while fig (.......
-- ........) shows the phase saturation field during fluid injection for time, $t = 0.15s, 0.30s, 0.50s, 1.15s, 1.75s$ and $2.95s$.
+Fig.~\ref{fig:PermFields} shows the permeability field for all the cases while Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} shows the phase saturation field during fluid injection for time, $t = 0.15s,~0.30s,~0.50s,~1.15s,~1.75s$ and $2.95s$ for all the cases.
 
@@
 
-Talk about those beautiful screenshots!\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+Fig.~\ref{fig:HiRes_LowRes_Mesh}(a) shows the discretized permeability field for the BaseCase.
+It has $4112$ triangular elements.
+Fig.~\ref{fig:HiRes_LowRes_Mesh}(b) shows the discretized permeability field for the four upscaled models.
+It has $728$ triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
+
+Fig.~\ref{fig:PermFields} compares the permeability field for all the models.
+The permeability field legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
+The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f).
+This highlights the fact that the permeability field in  Fig.~\ref{fig:PermFields}(c) and (d)(\ie ArithMean and HarmMean cases, respectively) are homogeneous within each block while Fig.~\ref{fig:PermFields}(e) and (f)(\ie PDFCase and SVDCase, respectively) are heterogeneous.
+Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase.
+An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability field.
+Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.
+
+With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase.
+Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
+Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation.
+
+Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case.
+However, with the SVDCase, knowledge of blocks with similar properties is not required prior to the upscaling.
+Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation (\ie feature elimination).
+The limits of the techniques used for the SVDCase is discussed in the author's future work.
+
+Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} presents the phase 1 saturation field simulation for all the cases at $t=0.15s,~t=0.30s,~t=0.50s,~t=1.15s,~t=1.75s$ and $t=2.95$.
+Fig.~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively.
+In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
+Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}  (c) shows that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (d) and (e)).
+Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
+
+Fig.~\ref{fig:Saturationfield@t=1.15s} compares the phase 1 saturation field for all the cases at $t=1.15s$.
+Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical.
+Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
+This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean.
+However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ .
+Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
+This inconsistence is with respect to this realization of the PDFCase.
+Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
 
@@
 
-Conclude man!\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
-\\
+Upscaling is a form of model order reduction, and a method of implimenting upscaling using singular value decomposition, SVD, is introduced in this work.
+The SVD method of upscaling first factorizes the matrix of the permeability field and then performs interpolation within the principal component space.
+The interpolated data in the principal component space is then recombined to form a reduced matrix of the permeability field.
+
+Results show that the permeability field data reduction can be specifically defined for the PDFCase and the SVDCase but not for the ArithMeanCase and the HarmMeanCase.
+This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution.
+The SVDCase is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.
+
+The author's future work will provide a statistical analysis of the technique used for the SVDcase and also presents other implementations of the technique.
 
@@
 
-\listoftables
-\clearpage
+%\listoftables
+%\clearpage
 %\input{article_table}

### 2018-04-08 Papers/AppliedMaths2018/article_figure1.tex
First Final Draft :)

@@
 %\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\centering
+\includegraphics[width=.56\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
+\vspace{0.cm}
+\vspace{0.5cm}
+}   
+\caption{Graphical Illustration of model order reduction (Initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research)}
+\vspace{1.5cm}
+\label{fig:IllustrationMOR}
+\end{figure}
+
 \begin{figure}[ht] 
@@
 \end{figure}
+
 %\end{landscape}
@@
 }   
-\caption{Permeability field for the base case as well as the upscaled case}
+\caption{Permeability field for the base case as well as the upscaled cases}
 \label{fig:PermFields}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\hspace{4cm} \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15withlegend.png}
+      \hspace {1.5cm} \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot15.png}}
+\vspace{0.cm}
+\hbox{\hspace{3.75cm} (a) BaseCase: Phase 1 Saturation at t=1.15s \hspace{1cm} (b) ArithMeanCase: Phase 1 Saturation at t=1.15s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_1dot15.png}
+      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_1dot15.png} 
+      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_1dot15.png}}
+\vspace{0.cm}
+\hbox{ \hspace{0cm} (c) HarmMeanCase: Saturation (t=1.15s) \hspace{0.5cm} (d) PDFCase: Saturation (t=1.15s) \hspace{1.5cm} (e) SVDCase: Saturation (t=1.15s)}
+\vspace{0.cm}
+}   
+\caption{Comparing the phase 1 saturation field for all the models at t=1.15s}
+\label{fig:Saturationfield@t=1.15s}
+\end{figure}
+\end{landscape}
+\clearpage

### 2018-04-10 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD}
+\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
 \cortext[cor1]{Corresponding author.}
-\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering University of Aberdeen, UK}
+\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering, University of Aberdeen, UK}
 
@@
 
-In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced.
+\red{Motivation for the work?
+What is the main aim of the work?} In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced.
 This method was compared to arithmetic and harmonic averaging (\ie upscaling) technique as well as a stochastic probability density function (PDF) method of upscaling, to highlight its benefits.

### 2018-04-10 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-Singular Value Decomposition, SVD\sep Upscaling\sep Model Order Reduction, MOD \sep  Principal Component Spaces \sep Permeability field
+Singular Value Decomposition (SVD)\sep Upscaling\sep Model Order Reduction (MOR) \sep  Principal Component Spaces \sep Permeability field
 \end{keyword}

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
-\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
+\author[UoA]{B. Lashore}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
+%\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
 \cortext[cor1]{Corresponding author.}
@@
 \red{Motivation for the work?
-What is the main aim of the work?} In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced.
-This method was compared to arithmetic and harmonic averaging (\ie upscaling) technique as well as a stochastic probability density function (PDF) method of upscaling, to highlight its benefits.
-It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase.
-Additionally, the SVD upscaling technique did not require a priori understanding of similar permeability blocks within the existing domain (\ie the BaseCase).
+What is the main aim of the work?} In this paper, a SVD-based method was developed to reduce the order of porous media permeability field (\ie upscale).
+This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits \red{(performance??)}.
+It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
+Additionally, the SVD upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
 
@@
 \section{Introduction}\label{section:intro}
-Naturally occuring rock formations are inherently heterogeneous, which means that rock properties such as permeability, pore spaces ({\it i.e.}, porosity) and pore throat vary spatially at different length scales.
-The heterogeneity of rock formations (\ie porous media) is relevant in calculations of transport and storage of fluids in porous media (\ie Multiphase flow in subsurface rocks).
-Therefore, the representation of these heterogeneous properties is of great importance to oil and gas (\ie reservoir management), carbon capture and storage (CCS, \ie CO$_2$ transportation and storage in subsurface rocks) and waste management (\ie remediation of contaminated soil).
+Naturally occuring rock formations are inherently heterogeneous, which means that rock properties such as permeability, pore spaces (\ie porosity) and pore throat vary spatially at different length scales.
+Heterogeneity of rock formations is relevant in calculations of transport and storage of fluids in porous media (\ie multiphase flow in subsurface rocks).
+Therefore, the representation of such heterogeneous properties is of great importance to oil and gas (\ie reservoir management), carbon capture and storage (CCS, \ie CO$_2$ transportation and storage in subsurface rocks) and waste management (\ie remediation of contaminated soil).
 
-In essence, heterogeneity makes it impossible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems).
-Additionally, due to limitations in computing resources, it is neither efficient nor possible to use exact values of geological properties at all spatial coordinates of the domain for running fine-grid simulations (\ie scale problems) \cite{chen_2006,miller_1998,Renard_1997}.
+In essence, rock heterogeneity makes it impossible to obtain reliable and accurate spatial information about geological properties throughout the domain (\ie uncertainty problem).
+Additionally, due to limitations in computing resources, it is neither efficient nor possible to use exact values of geological properties at all spatial coordinates of the domain to perform fine-grid simulations (\ie scaling problem) \cite{chen_2006,miller_1998,Renard_1997}.
 This is particularly true for large geological domains which span several kilometres.
-It is possible to overcome these challenges by upscaling.
-Upscaling techniques solve both problems by replacing discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+It is possible to overcome these challenges by a family of techniques called {\it upscaling}.
+Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
 
-Upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of the heterogeneous property.
-There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
-Traditionally, the techniques were deterministic, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
-One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media, and they address scale and uncertainity problems which were previously mentioned.
+Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of heterogeneous properties.
+There are several upscaling techniques which \red{fall} under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
+Traditional upscaling techniques are deterministic in nature, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
+One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media and they are able to address scaling and uncertainity problems.
 
-Upscaling is a term used in a few industries, some of which were mentioned in the first paragraph.
-It is more popularly known in the larger science and engineering community as a form of Model Order Reduction (MOR), or the output (\ie Reduced Order Model, ROM).
+{\it Upscaling} is a term commonly used in a few industries, and it is often referred throughout the applied mathematics and engineering communities as a form of model order reduction (MOR), or the output (\ie Reduced Order Model, ROM).
 Depending on the context in which MOR is being used, it can simply be referred to as dimensionality reduction.

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of heterogeneous properties.
-There are several upscaling techniques which \red{fall} under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
+There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
 Traditional upscaling techniques are deterministic in nature, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
@@
 
-{\it Upscaling} is a term commonly used in a few industries, and it is often referred throughout the applied mathematics and engineering communities as a form of model order reduction (MOR), or the output (\ie Reduced Order Model, ROM).
-Depending on the context in which MOR is being used, it can simply be referred to as dimensionality reduction.
-The definition of MOR also depends on the context it is being used \cite{Schilders2008}, but it suffices to state that MOR captures the essential features of a system, structure or parameter.
-This implies that an original system, structure or parameter exists with more detailed information.
-Fig.~\ref{fig:IllustrationMOR} presents a graphical intepretation of the MOR concept.
-It shows that even with the reduced number of facets, the graphic on the right of this illustration is recognized as that of a rabbit.
+{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
+Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction.
+The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}.
+This implies that an original system exists with more detailed information.
+Figure~\ref{fig:IllustrationMOR} presents a graphical intepretation of the MOR concept in which it shows that even with the reduced number of facets, the graphic on the rhs of this illustration is recognised as that of a rabbit.
 

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 This implies that an original system exists with more detailed information.
-Figure~\ref{fig:IllustrationMOR} presents a graphical intepretation of the MOR concept in which it shows that even with the reduced number of facets, the graphic on the rhs of this illustration is recognised as that of a rabbit.
+Figure~\ref{fig:IllustrationMOR} presents an interpretation of MOR concept in which a graphical representation of a rabbit is reconstructed with a reduced number of facets (rhs of this illustration).
 

### 2018-04-12 Papers/AppliedMaths2018/article_figure1.tex
updates

@@
 }   
-\caption{Graphical Illustration of model order reduction (Initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research)}
+\caption{Graphical illustration of model order reduction (initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research.)}
 \vspace{1.5cm}

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-\citet{Schilders2008} provides a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric term, to the work of \citet{Odabasioglu_1998} in 1998 which introduced PRIMA - Passive Reduced-order Interconnect Marcromodeling Algorithm.
-Truncated Balanced Realization \cite{Moore_1981} is one of the MOR methods, published in 1981, it called attention to principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods published in 1984 and 1987 respectively.
-In 1990, Asymptotic Waveform Evaluation \cite{Pillage_1990} the first MOR method related to the Krylov was born, this was followed by Pade Via Lanczos \cite{Feldmann_1995} in 1995 and then PRIMA.
-In this work, upscaling is performed by SVD in the principal component spaces.
+\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998 which introduced Passive Reduced-order Interconnect Macromodeling Algorithm (PRIMA).
+Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods developed published in 1984 and 1987 respectively\red{(I DONT THINK THIS IS ACCURATE ...
+POD OR KARHUNEN-LOEVE DECOMPOSITION/TRANSFORM ORIGINAL PAPERS ARE FROM 1933-48!)}.
+The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
+In this work, upscaling is performed by SVD in principal component spaces.
 

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
+\medskip
 {\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
@@
 
-The research focuses on reducing the order of the permeability field.
+\bigskip
+This work focuses on reducing the order of permeability field distribution for multiphase flow simulations in porous media.
 Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
-The mathematical model is discretized by a novel high-order accurate control volume finite element method (CVFEM) (see \cite{Gomes_2017} for further details of the model formulation) which couples both the fine resolution and upscaled representation of the permeability field.
+The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) which couples both the fine resolution and upscaled representation of the permeability field.
 Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
-The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) which couples both the fine resolution and upscaled representation of the permeability field.
-Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to analyse the various upscaling techniques used.
+The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.
+Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
 

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \bigskip
-This work focuses on reducing the order of permeability field distribution for multiphase flow simulations in porous media.
-Section~\ref{section:mathematical_model} presents the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
+This work focuses on reducing the order of permeability distribution in porous media flow simulations.
+Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
 The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-Four upscaling techniques are investigated in this work.
-Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
-The third is a randomly generated permeability field with a Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie  base case).
-The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability field.
+Four upscaling techniques are investigated in this work, arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
+The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case).
+The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability distribution.
 

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-In Section~\ref{section:svd}, the basic mathematical explanation of SVD and its associated properties are presented.
+In Section~\ref{section:svd}, fundamental mathematics of SVD and associated properties are presented.
 Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work.
-Finally, the Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space.
-Section~\ref{section:model_simulation}, starts by describing the high resolution base case on which the four upscaling techniques are modelled.
-The the simulation run which is similar for all the cases/models is described.
+Finally, Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space.
+Section~\ref{section:model_simulation} starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to.
 A brief summary of the pre-processing step for each of the models is also presented.

### 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 A brief summary of the pre-processing step for each of the models is also presented.
-Section~\ref{section:results_discussion} provides the results and some discussion on the results of the simulations.
-It also gives further intepretation to the result obtained from the SVD upscaling technique.
-Finally, Section~\ref{section:conclusion} provides the conclusion.
+Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique.
+Finally, Conclusions are drawn in Section~\ref{section:conclusion}.
 

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-\section{Mathematical Model}\label{section:mathematical_model}
+\section{Multi-Fluid Flow Model}\label{section:mathematical_model}
 
-\citet{Gomes_2017} provides details on the governing equations and numerical formulation which forms the mathematical model for the multi-flow flow in this work.
+In this work, a novel control volume finite element method (CVFEM) formulation is used to discretise and solve the set of multi-fluid flow equations.
+Continuity equations are embedded into the pressure equation to enforce mass conservation and the exact force balance (extended Darcy equations).
+The numerical formulation employs an implicit algorithm with respect to time which is less restrictive than the traditional industry-standard implicit-pressure-explicit-saturation (IMPES) scheme \cite{aziz_1986,geiger_2004}.
+
+The formulation used in this work uses a dual consistent CVFEM representation which is embedded in novel families of triangular and tetrahedral finite element-pairs, \PN[n]{m} and \PNDG[n]{m}.
+In this element-pairs velocity is represented by $n^{\rm th}$-order polynomials that are discontinuous across elements, while pressure is represented by $m^{\rm th}$-order polynomials that may be either continuous (\PN[n]{m}) or discontinuous (\PNDG[n]{m}) across elements.
+Most properties of \PNDG[n]{m} element-pairs are similar to those in the \PN[n]{m} element-pairs but allows a representation in which pressure, saturation and other solution variables (\eg temperature, concentrations etc) are discontinuous across finite element boundaries \cite{salinas_2018,adam_2016}.
+
+\cite{Gomes_2017} provides details on the governing equations and numerical formulation which forms the mathematical model for the multi-flow flow in this work.
 Albeit, it suffices to introduce only the representation of Darcy's law for immiscible multi-phase flow for the following discussion.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updated upscaling (Section 3)

--- 2018-04-12 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
@@
 
-\red{Motivation for the work?
-What is the main aim of the work?} In this paper, a SVD-based method was developed to reduce the order of porous media permeability field (\ie upscale).
-This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits \red{(performance??)}.
+Representation of heterogeneous properties (\ie permeability in this case) within a large system, is a challenge that cuts across many industries that deal with flow in porous media.
+This is because it is impossible to obtain the value of permeability at every point in realistic domain.
+And, even if this was possible, it would be extremely challenging to get the computing resources to make use of all this data.
+This challenge gave birth to upscaling, a model order reduction method.
+
+In this paper, a SVD-based method was developed to reduce the order of porous media permeability field (\ie upscale).
+This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits performance.
 It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-Singular Value Decomposition (SVD)\sep Upscaling\sep Model Order Reduction (MOR) \sep  Principal Component Spaces \sep Permeability field
+Singular Value Decomposition (SVD)\sep Upscaling\sep Model Order Reduction (MOR) \sep  Principal Component Spaces \sep Permeability field \sep Heterogeneity
 \end{keyword}
@@
 Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods developed published in 1984 and 1987 respectively\red{(I DONT THINK THIS IS ACCURATE ...
-POD OR KARHUNEN-LOEVE DECOMPOSITION/TRANSFORM ORIGINAL PAPERS ARE FROM 1933-48!)}.
+Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods discussed in the referenced articles published in 1984 and 1987 respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
@@
 Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
-The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.
+The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.
 Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
@@
 Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-This is a subject which has interested the academic community for over $7$ decades.
+This subject of upscaling heterogenous properties has interested industries (\ie oil and gas, CCS and waste management) as well as the academic community for over $7$ decades.
+
+Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach to be subject.
+In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
+And in the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
+In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
+
+A lot of work has been carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
 \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities.
-\citet{King1996} investigated the use of renormalization for upscaling.
-And \citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields.
+The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
+
+\citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields for two cases.
+Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up.
+The first case had low permeablitity in all the blocks except the bottom right block which had high permeability, while the second case employed the checkboard style described in Section~\ref{subsection:model}.
+Different conductivity ratios were also investigated for the two cases.
+The conclusion drawn was that renormalization worked fairly well for the first case, but very poorly for the second case.
+
 \citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
+He found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
+\citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
+
 \citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
-\red{(And what are the main conclusions/contributions of these papers?)}
-
-\JGnote{You should consider writing a more detailed section on upscaling as this is part of the core of your work here ...}
-
-\BLnote{I will do this before submitting, please let me know if you will be able to review again on Thursday or Friday}
+The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.
 
@@
 \end{equation}
-\red{(I guess we have talked about this on Friday ...
-make it clear that matrix inversion is an (useful?) example of SVD ...
-also explain step-by-step this matricial equations above ...
-remember ...
-every single equation must be explained ...)}
-
-\BLnote{The equations are now explained in the last 3 sentences of this section.}
 
 \subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
-\JGnote{As we talked on Friday: (a)make sure you explain what permeability is before starting to operating on it; (b) $P0DG$ could be easily replaced by saying that the quantity of interest is allocated in the centre of the element/cell -- this make it more general; (c) Just reading it through, we can summarise the {\it procedure} as (i) SVD of matrix of permeability scalar quantities (\ie upscaling) and (ii) linear interpolation of the upscaled/homogeneised quantities upon a new mesh grid resolution (\ie upgriding).
-Whereas the first is the object of the interest for this study, the second gives an overall motivation for the work ...
-thus, make sure this is clear within the text, \ie upscaling $\rightarrow$ upgriding.}
-
-\BLnote{(a)Permeability is now introduced in Section~\ref{section:mathematical_model}; (b) $P0DG$ now replaced with centre of element/cell (c) I thought we agreed that upscaling cannot be separated from upgridding.
-Actually, you convinced me that upscaling cannot be seperated from upgridding.
-Upscaling is not completed in the SVDCase until the interpolation is completed.
-Strictly speaking, interpolation only defines the level of upgridding.
-I will mention this in the results section (Section~\ref{section:results_discussion})}
 
@@
 
-\JGnote{Maybe you should consider describing the procedure above as pseudocode within a table.}
-
-\BLnote{I have an algorithm in Section~\ref{subsubsection:svdcase_preprocess_algorithm} which itemizes the procedure in a sort of psuedocode}
-
 \section{Model Description and Simulation Setup}\label{section:model_simulation}
@@
 \subsection{Model Description}\label{subsection:model}
-The BaseCase  ({\it i.e.} fine resolution) model for the permeabiliy field builds on the $2 * 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+The BaseCase  ({\it i.e.} fine resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
 These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-Representation of heterogeneous properties (\ie permeability in this case) within a large system, is a challenge that cuts across many industries that deal with flow in porous media.
-This is because it is impossible to obtain the value of permeability at every point in realistic domain.
-And, even if this was possible, it would be extremely challenging to get the computing resources to make use of all this data.
+Representation of heterogeneous properties (\ie permeability in this case) within a large system, is a challenge that cuts across many industries that deal with flows in porous media.
+This is because it is impossible to obtain the value of permeability at every point in realistic domains.
+And, even if this was possible, it would be extremely challenging to get the computing resources to make use of all available data.
 This challenge gave birth to upscaling, a model order reduction method.
@@
 Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods discussed in the referenced articles published in 1984 and 1987 respectively.
+Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
@@
 
-\cite{Gomes_2017} provides details on the governing equations and numerical formulation which forms the mathematical model for the multi-flow flow in this work.
-Albeit, it suffices to introduce only the representation of Darcy's law for immiscible multi-phase flow for the following discussion.
-This is written in the form:
+Immiscible multi-fluid flows in porous media may be represented by the extended Darcy equation,
 \begin{equation}\label{e:darcy_eqn}
-  \mathbf{q}_{\alpha} =
+  \mathbf{q}_{\alpha} = \mathbf{u}_{\alpha}S_\alpha=
   -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(
@@
 \end{equation}
-where $\alpha$ designates a phase and $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity.
+where $\alpha$ designates a phase, $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity and $\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity.
 $\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
 $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is a function of the vector position $\mathbf{r}$, and time, $t$.
+
+In addition to the extended Darcy equation (Eqn.~\ref{e:darcy_eqn}), saturation conservative equations,
+\begin{equation}
+  \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} + \nabla
+  \cdot \left( {\mathbf u}_{\alpha} S_{\alpha}\right) =
+  s_{cty,\alpha},
+  \label{saturation_equation}
+\end{equation}
+are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{pavlidis_2013b}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
+
+\medskip
+The discretised saturation and Darcy equations are solved using a multigrid-like approach as described by \citeauthor{pavlidis2016}~\cite{pavlidis2016}.
+The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{salinas2015,adam_2016}).
+
+\medskip
 Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is the absolute permeability tensor of the porous medium and it is a function of the vector position $\mathbf{r}$.
-
-In this work, $\mathbf{K}$ is prescribed in the system of governing equations used to model multi-phase flow in porous media, this means it is an input/independent variable.
-Since $\mathbf{K}$ varies with position, it is impossible to determine at every point and even if it is available at every point it would require immense computer resources to utilize all the available information in a simulation.
-This is the reason upscaling is required for the permeability field.
-Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($Km$)\cite{ECMI_2004}.
+$\mathbf{K}$ is prescribed in the system of governing conservative equations, \ie it is an indepedent input variable.
+Since $\mathbf{K}$ is petrophysical rock property that varies spatially, it is not possible to determine at every spatial coordinate.
+And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations.
+This is the reason upscaling is required for processing permeability variables.
+Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($km$)\cite{ECMI_2004}.
 The upscaling discussed here is from the micro scale also known as the Darcy scale.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach to be subject.
+Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach.
 In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
-And in the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
+In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
 In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-A lot of work has been carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
-\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for an oil reservoir with varying permeabilities.
+Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
+\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
 The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
-He found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
+They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
 \citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-\section{Singular Value Decomposition, SVD, and its application for reducing the order of a permeability field}\label{section:svd}
+\section{Singular Value Decomposition (SVD) and Application for Reducing the Order of Permeability Fields}\label{section:svd}
 \subsection{A Brief Introduction to SVD}\label{subsection:svd_brief}
@@
 where $\mathbf{U}=\left[\underline{u}_{1},\underline{u}_{2},\cdots,\underline{u}_{m}\right]\in\mathcal{R}^{m\times n}$ and $\mathbf{V}=\left[\underline{v}_{1},\underline{v}_{2},\cdots,\underline{v}_{n}\right]\in\mathcal{R}^{m\times n}$ are orthogonal but not necessarily the same.
-$\Sigma$ is a diagonal matrix, \ie $\Sigma=\text{diag}\left(\sigma_{1},\sigma_{2},\cdots,\sigma_{r}\right)\in\mathcal{R}^{m\times n}$ and $r=\min\left\{m,n\right\}$ is the rank of $\mathbf{A}$, with $\sigma_{1}\ge\sigma_{2}\ge\cdots\sigma_{r}\ge 0$.
-The diagonal entries of $\Sigma$ $\left(\ie \sigma_{i}, i=1,r\right)$ are called singular values of $\mathbf{A}$.
+$\Sigma$ is a diagonal matrix, \ie
+\begin{displaymath}
+  \Sigma=\text{diag}\left(\sigma_{1},\sigma_{2},\cdots,\sigma_{r}\right)\in\mathcal{R}^{m\times n},
+\end{displaymath}
+and $r=\min\left\{m,n\right\}$ is the rank of $\mathbf{A}$, with $\sigma_{1}\ge\sigma_{2}\ge\cdots\sigma_{r}\ge 0$.
+The diagonal entries of $\Sigma$ $\left(\text{\ie} \sigma_{i}, i=1,r\right)$ are called singular values of $\mathbf{A}$.
 If $\mathbf{A}$ is a square matrix then $\mathbf{U}$, $\Sigma$ and $\mathbf{V}$ are also square matrices.
@@
 and if $\mathbf{A}$ is an $m \times n$ matrix thus $\Sigma$ is a diagonal $m \times n$ matrix.
+
+\medskip
 For a rectangular matrix, the singular values fill the first $r$ places on the main diagonal of $\Sigma$.
@@
 A simple consideration of the benefit of the orthogonal factors, $\mathbf{U}$ and $\mathbf{V}$, is the ease with which they allow the inverse of the square matrix $\mathbf{A}$ to be calculated.
-This in turn makes it easy to solve the linear Equ.~\ref{e:Ax=b} for $x$.
-Equ.~\ref{e:SVD_factorization} show the SVD factorization already discussed, and with benefit of the orthogonal property also already discussed, the solution for $x$ is simply presented as in Equ.~\ref{e:x_solution}.
-\begin{equation}\label{e:Ax=b}
- \mathbf{A}x = b
+This in turn makes it easy to solve the linear equations, $\mathbf{A}x = b$ with the SVD factorization,
+\begin{equation}\label{e:SVD_factorization}
+ \mathbf{U} \Sigma \mathbf{V}^{\intercal} x = b \;\;\Longrightarrow\;\; x = \mathbf{V} \Sigma^{-1} \mathbf{U}^{\intercal} b,
 \end{equation} 
-\begin{equation}\label{e:SVD_factorization}
- \mathbf{U} \Sigma \mathbf{V}^{\intercal} x = b
-\end{equation}
-\begin{equation}\label{e:x_solution}
- x = \mathbf{V} \Sigma^{-1} \mathbf{U}^{\intercal} b
-\end{equation}
+with benefit of the orthogonal property already discussed.
 
@@
 \subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
-In 3D geometry, permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining part of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
-Furthermore, the simulator prescribes the permeability field by assigning permeability values in the centre of the elements/cells which discretizing the 2D simulation domain.
-The permeability value assigned in the centre of the element/cell represents the permeability value for that element/cell.
+In 3D geometry, permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
+Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the 2D simulation domain.
+
+Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
 For simplicity, in the remaining part of this section, it will be assumed that the $2D$ geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
-This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates  system which most people are already familiar with.
+This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
 The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
+
 The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.
@@
 The permeability space of $4$ can be reduced to a smaller value of $1$ through an averaging process such as arithmetic, harmonic or geometric mean.
-This type of reduction is the focus of this paper, albeit the main focus of this paper is achieving this reduction through singular value decomposition in the principal component spaces.
+This type of reduction is the focus of this paper, albeit the main focus of this paper is achieving this reduction through SVD in the principal component spaces.
 

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed through SVD to principal component spaces where usually, traditional principal component analysis is performed before interpolation is used to implement further data reduction in the principal component spaces.
-This reduced data in the principal component space is then transformed back into the permeability space to obtain a reduced permeability space.
+Essentially, the existing permeability space is transformed through SVD to principal component spaces (PCS) where traditional principal component analysis is performed before interpolation is used to implement further data reduction in the principal component spaces.
+This reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
 
-The principal component space is more challenging to visualize because it usually consists of more than $3$ dimensions.
-$3-D$ ({\it i.e.}, $x, y$ and $z$ in the cartesian plane) being the natural dimension which humans exist, is easy to visualize.
-Many individuals are also able to understand the concept of 4D with time as the fourth dimension, albeit only few scientists and engineers are able to visualize and work in the abstract dimension where the number of dimensions exceed four.
-An aid for visualizing the PC space is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or imagine the matrices written out) and consider the singular vectors ({\it i.e.},columns in $\mathbf{U}$ and rows in $\mathbf{U}$) as separate principal component spaces.
+The PCS is more challenging to visualize because it usually consists of more than 3-D.
+An aid for visualizing the PCS is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{U}$) as separate PCS.
 
@@
 For the SVD model order reduction of the permeability field, all the work is done in the principal component spaces.
-This can be completed in two steps.
-The first step is optional and it is the well known principal component analysis (PCA) \cite{Hotelling_1933}.
-Here, the singular values are examined and based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+This can be completed in two steps: the first step is the principal component analysis (PCA) \cite{Hotelling_1933}, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+
 In the case with $z = r$, it can be assumed that step 1 has been ignored.
@@
 
-The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$), to reduce the number of data in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
@@
 \subsection{Model Description}\label{subsection:model}
-The BaseCase  ({\it i.e.} fine resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+The BaseCase  (\ie fine mesh resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
 These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
-The BaseCase permeability model used in this manuscript retains the checkerboard desgined used by the recently named authors.
-Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value ({\it i.e.} not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+
+The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
+Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
 Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
 More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
-And Fig.~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible respectively.
+Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
 Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
-Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right respectively.
+Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
 
-As already mentioned, four upscaled permeability field models were obtained from the high-resolution ({\it i.e.} the BaseCase) permeability field.
+As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field.
 When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
-The first two upscaled models are referred to as the ArithMean and the HarmMean Cases, and this is because they are based on the arithmetic and the harmonic averaging methods, respectively.
-In both the ArithMean and HarmMean Cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
+The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).
+
+In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
 This effectively homogenizes the permeability field in each block.

### 2018-04-13 Papers/AppliedMaths2018/article_figure1.tex
updates

@@
 \vspace{0.cm}
-\hbox{\hspace{0.25cm} (a) High Resolution Grid(BaseCase) \hspace{0.75cm} (b) Low Resolution Grid(Upscaled Cases) \hspace{3.0cm}}
+\hbox{\hspace{0.25cm} (a) High Resolution Grid (BaseCase) \hspace{0.75cm} (b) Low Resolution Grid (Upscaled Cases) \hspace{3.0cm}}
 \vspace{0.5cm}
 }   
-\caption{Simulation grid for the high resolution case and the upscaled cases}
+\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases. \red{(ADD NUMEBR OF ELEMENTS OR NODES FOR EACH CASE)}}
 \label{fig:HiRes_LowRes_Mesh}

### 2018-04-13 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{salinas2015,adam_2016}).
+These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{jackson_2013,Gomes_2017}).
 
@@
 The upscaled permeability field for the third and fourth cases are referred to as PDFCase and SVDCase, respectively.
-And, as can be deduced from the names, these cases are based on probability density function (PDF) and singular value decomposition (SVD).
-The description for these permeability field models are more involved and are presented in section ~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
+And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively.
+The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
 It is appropriate to note that although these models (PDFCase and SVDCase) are upscaled, they retain heterogeneity within the blocks.
@@
 \subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
-\begin{enumerate}[1]
-  \item A function is used to randomly generate uniform ({\it i.e.} Gaussian) data for each block. The range for each block is as below:
-  \begin{enumerate}[a]
-    \item \textbf{K1} : $700 - 900mD$
-    \item \textbf{K2} : $50 - 150mD$
-    \item \textbf{K3} : $100 - 200mD$
-    \item \textbf{K4} : $1000 - 1200mD$
+\begin{enumerate}[1.]
+  \item A function is used to randomly generate uniform (\ie Gaussian) data for each block. The range for each block is as below:
+  \begin{enumerate}[a)]
+    \item \textbf{K1} : $700 - 900$ mD
+    \item \textbf{K2} : $50 - 150$ mD
+    \item \textbf{K3} : $100 - 200$ mD
+    \item \textbf{K4} : $1000 - 1200$ mD
   \end{enumerate}                                                    
-  \item The number of data generated for each block is $1600$ and the data is randomly position within each block in a structured pattern.
+  \item The number of data generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern.
 Albeit, the simulation grid ({\it i.e.} mesh) is unstructured.
   \item Merge data from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned data in each block.
-This file will be used by the Control Volume Finite Element Method (CVFEM) simulator to prescribe the permeability field for the base case.
+This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
 \end{enumerate}
@@
 \subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
-\begin{enumerate}[1]
+\begin{enumerate}[1.]
   \item Data from step one of the pre-processing algorithm for the base case is used to calculate the mean and standard deviation for each block of the permeability field.
   \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the BaseCase for each of the four blocks.
-  \item The number of data generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
-As in the base case, the simulation grid ({\it i.e.} mesh) is unstructured.
+  \item The number of data generated for each block is $400$ and the data is randomly position within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
   \item Finally, the structured data from each block is combined into a single file and then provided to the CVFEM simulator.
@@
 \subsubsection{SVDCase Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
-\begin{enumerate}[1]
+\begin{enumerate}[1.]
   \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
@@
 For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
-Newmann ({\it i.e.} no flux) boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face.
-Fig.~\ref{fig:PermFields} shows the permeability field for all the cases while Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} shows the phase saturation field during fluid injection for time, $t = 0.15s,~0.30s,~0.50s,~1.15s,~1.75s$ and $2.95s$ for all the cases.
+No flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
+Figure~\ref{fig:PermFields} shows the permeability field for all the cases while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation field during fluid injection for time: $t = 0.15s,~0.30s,~0.50s,~1.15s,~1.75s$ and $2.95s$ for all cases.
 
@@
 
-Fig.~\ref{fig:HiRes_LowRes_Mesh}(a) shows the discretized permeability field for the BaseCase.
-It has $4112$ triangular elements.
-Fig.~\ref{fig:HiRes_LowRes_Mesh}(b) shows the discretized permeability field for the four upscaled models.
-It has $728$ triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
+Figure~\ref{fig:HiRes_LowRes_Mesh}(a) shows the discretized permeability field for the BaseCase.
+It has $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements.
+Figure~\ref{fig:HiRes_LowRes_Mesh}(b) shows the discretized permeability field for the four upscaled models.
+It has $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
 
-Fig.~\ref{fig:PermFields} compares the permeability field for all the models.
+Figure~\ref{fig:PermFields} compares the permeability field for all the models.
 The permeability field legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
   \end{enumerate}                                                    
-  \item The number of data generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern.
-Albeit, the simulation grid ({\it i.e.} mesh) is unstructured.
+  \item The number of data generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
   \item Merge data from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned data in each block.
@@
 \begin{enumerate}[1.]
-  \item Data from step one of the pre-processing algorithm for the base case is used to calculate the mean and standard deviation for each block of the permeability field.
+  \item Data from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) is used to calculate mean and standard deviation for each block of the permeability field.
   \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the BaseCase for each of the four blocks.
@@
   \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
-  \item A selected number, $z$, of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
+  \item A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
   \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ a linear interpolation is performed to form a new column with the number of data in each column reduced to a half of the original column.
-And, these new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
-  \item The permeability field used for the SVD case is the matrix, $\mathbf{A_{new2}}$ which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
-It is a permeability field with a quater of the data in the base cased and therefore a permeability field with a reduced order.
+  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data in each column reduced to half of the original column.
+These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
+  \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+It is a permeability field with a quarter of the data in the base case and therefore a permeability field with reduced order.
 \end{enumerate}
@@
 It has $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
+\red{(STOPPED HERE ...)}
 
-Figure~\ref{fig:PermFields} compares the permeability field for all the models.
+Figure~\ref{fig:PermFields} compares the permeability field for all models.
 The permeability field legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
   \item Data from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) is used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quater of the number of data in the BaseCase for each of the four blocks.
-  \item The number of data generated for each block is $400$ and the data is randomly position within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
+  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quarter of data from the BaseCase for each of the four blocks.
+  \item The amount of data \red{(PREVIOUSLY, IT WAS ``THE NUMBER OF DATA'' ...
+HOWEVER DATA IS NOT AN ACCOUNTABLE NOUM, THEREFORE YOU MAY USE EITHER ``AMOUNT OF DATA'' OR ``NUMBER OF DATA POINTS'')} generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
+As in the base case, the simulation grid is unstructured.
   \item Finally, the structured data from each block is combined into a single file and then provided to the CVFEM simulator.

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
   \end{enumerate}                                                    
-  \item The number of data generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
+  \item The number of data points generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
   \item Merge data from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned data in each block.
@@
   \item The amount of data \red{(PREVIOUSLY, IT WAS ``THE NUMBER OF DATA'' ...
-HOWEVER DATA IS NOT AN ACCOUNTABLE NOUM, THEREFORE YOU MAY USE EITHER ``AMOUNT OF DATA'' OR ``NUMBER OF DATA POINTS'')} generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
+HOWEVER DATA IS NOT AN ACCOUNTABLE NOUM, THEREFORE YOU MAY USE EITHER ``AMOUNT OF DATA'' OR ``NUMBER OF DATA POINTS'' ...
+I REPLACED MOST OF ENTRIES -RE DATA AS AN ACCOUNTABLE NOUM ...
+PLEASE REVISE THE MANUSCRIPT ACCORDINGLY.)} generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
 As in the base case, the simulation grid is unstructured.

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
   \item Data from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) is used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quarter of data from the BaseCase for each of the four blocks.
-  \item The amount of data \red{(PREVIOUSLY, IT WAS ``THE NUMBER OF DATA'' ...
+  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quarter of data points from the BaseCase for each of the four blocks.
+  \item The number of data points \red{(PREVIOUSLY, IT WAS ``THE NUMBER OF DATA'' ...
 HOWEVER DATA IS NOT AN ACCOUNTABLE NOUM, THEREFORE YOU MAY USE EITHER ``AMOUNT OF DATA'' OR ``NUMBER OF DATA POINTS'' ...
 I REPLACED MOST OF ENTRIES -RE DATA AS AN ACCOUNTABLE NOUM ...
-PLEASE REVISE THE MANUSCRIPT ACCORDINGLY.)} generated for each block is $400$ and the data is randomly position within each block in a structured pattern.
+PLEASE REVISE THE MANUSCRIPT ACCORDINGLY.)} generated for each block is $400$ and the data is randomly positioned within each block in a structured pattern.
 As in the base case, the simulation grid is unstructured.
-  \item Finally, the structured data from each block is combined into a single file and then provided to the CVFEM simulator.
+  \item Finally, the structured data from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
 \end{enumerate}

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
-No flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
-Figure~\ref{fig:PermFields} shows the permeability field for all the cases while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation field during fluid injection for time: $t = 0.15s,~0.30s,~0.50s,~1.15s,~1.75s$ and $2.95s$ for all cases.
+No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
+Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+
+Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+\begin{displaymath}
+  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
+\end{displaymath}
 

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-Figure~\ref{fig:HiRes_LowRes_Mesh}(a) shows the discretized permeability field for the BaseCase.
-It has $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements.
-Figure~\ref{fig:HiRes_LowRes_Mesh}(b) shows the discretized permeability field for the four upscaled models.
-It has $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular elements, therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
-\red{(STOPPED HERE ...)}
+Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
+Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs.
+Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
 

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 
-Figure~\ref{fig:PermFields} compares the permeability field for all models.
-The permeability field legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
+Figure~\ref{fig:PermFields} compares the permeability distribution for all models.
+\red{Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f))} \red{(THIS INFO SHOULD BE IN THE CAPTION OF THE FIGURES INSTEAD)}.
 The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f).

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f).
-This highlights the fact that the permeability field in  Fig.~\ref{fig:PermFields}(c) and (d)(\ie ArithMean and HarmMean cases, respectively) are homogeneous within each block while Fig.~\ref{fig:PermFields}(e) and (f)(\ie PDFCase and SVDCase, respectively) are heterogeneous.
+
+This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and SVDCase cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous.
 Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase.

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase.
-An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability field.
+An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution.
 Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.
@@
 Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
-Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation.
+Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation \red{(SENTENCE IS SLIGHTLY CONFUSING ...
+NOT SURE WHAT YOU WANT TO CONVEY)}.
 

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 However, with the SVDCase, knowledge of blocks with similar properties is not required prior to the upscaling.
-Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation (\ie feature elimination).
-The limits of the techniques used for the SVDCase is discussed in the author's future work.
+Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation.
+The limits of the techniques used for the SVDCase will be discussed in the author's future work.
 
-Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} presents the phase 1 saturation field simulation for all the cases at $t=0.15s,~t=0.30s,~t=0.50s,~t=1.15s,~t=1.75s$ and $t=2.95$.
-Fig.~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively.
+\medskip
+Figure~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} presents snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
+Figure~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively.
 In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 \medskip
-Figure~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} presents snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
-Figure~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively.
-In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
-Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}  (c) shows that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (d) and (e)).
-Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
+\red{(I GUESS YOU SHOULD USE ONE PARAGRAPH JUST TO DESCRIBE (TO THE READER WHO HASNT READ THE OTHER REFERENCES) THE PHYSICS ASSOCIATED WITH THE BASECASE -- FIG 4 LINKING WITH THE REFERENCES ...
+REMEMBER THIS IS YOUR WORK'S VALIDATION!!!
+THIS BENCHMARK WOULD: (A) IF THE SIMULATION WAS PERFORMED W HOMOGENEOUS MEDIA (AT EACH BLOCK) A PISTON SHAPE BEHAVIOR (AT EACH BLOCK, I.E., A BLOCK DIVIDED BUCKLEY-LEVERETT BEHAVIOR) COULD BE NOTICED HOWEVER AS THE WHOLE SYSTEM IS HETEROGENEOUS THIS MAY NOT BE CLEARLY NOTICED; (B) CROSS-FLOW, I.E., PREFERENTIAL FLOW  THROUGH REGIONS OF HIGH PERMEABILITY; (C) FLOW QUALITATIVE BEHAVIOUR MATCHES THE EXPERIMENTS  ETC ETC ETC MAKE IT STRONG !)}
 
-Fig.~\ref{fig:Saturationfield@t=1.15s} compares the phase 1 saturation field for all the cases at $t=1.15s$.
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
+In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)).
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
+
+Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
 Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical.

### 2018-04-14 Papers/AppliedMaths2018/article_figure1.tex
updates

@@
 \vspace{0.cm}
-\hbox{\hspace{0.5cm} (a) BaseCase(with mesh) \hspace{3.75cm} (b) BaseCase(without Mesh) \hspace{3.0cm} (c) ArithMean Case}
+\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{3.75cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
 \vspace{0.5cm}
@@
 \vspace{0.cm}
-\hbox{\hspace{3.75cm} (a) BaseCase: Phase 1 Saturation at t=1.15s \hspace{1cm} (b) ArithMeanCase: Phase 1 Saturation at t=1.15s}
+\hbox{\hspace{3.75cm} (a) BaseCase\hspace{1cm} (b) ArithMeanCase}
 \vspace{0.5cm}
@@
 \vspace{0.cm}
-\hbox{ \hspace{0cm} (c) HarmMeanCase: Saturation (t=1.15s) \hspace{0.5cm} (d) PDFCase: Saturation (t=1.15s) \hspace{1.5cm} (e) SVDCase: Saturation (t=1.15s)}
+\hbox{ \hspace{0cm} (c) HarmMeanCase \hspace{0.5cm} (d) PDFCase \hspace{1.5cm} (e) SVDCase}
 \vspace{0.cm}
 }   
-\caption{Comparing the phase 1 saturation field for all the models at t=1.15s}
+\caption{Comparing phase 1 saturation distribution for all the models at $t=1.15$ s}
 \label{fig:Saturationfield@t=1.15s}

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
-Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical.
-Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
+Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
+Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c)\red{(WHAT DO YOU MEAN W ``MORE INJECTION''?
+MASS FLOW RATE OF INJECTION (BC) WAS THE SAME FOR ALL CASES ...DO YOU MEAN THE DISPLACEMENT IN THE RHS QUADRANTS?)}.
 This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean.

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

@@
 MASS FLOW RATE OF INJECTION (BC) WAS THE SAME FOR ALL CASES ...DO YOU MEAN THE DISPLACEMENT IN THE RHS QUADRANTS?)}.
-This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean.
-However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ .
-Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
-This inconsistence is with respect to this realization of the PDFCase.
-Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
+This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
+However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.
+
+Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
+This inconsistency is with respect to this realization of the PDFCase.
+Hence, SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
 
@@
 
-Upscaling is a form of model order reduction, and a method of implimenting upscaling using singular value decomposition, SVD, is introduced in this work.
+Upscaling is a form of model order reduction, and a method of implementing upscaling using singular value decomposition, SVD, is introduced in this work.
 The SVD method of upscaling first factorizes the matrix of the permeability field and then performs interpolation within the principal component space.

### 2018-04-15 Papers/AppliedMaths2018/Highlights.tex
For First Submission 15th April 2018

Performed a model order reduction (i.e., upscale) of a permeability field using singular value decomposition (SVD)

Reduced order model (ROM) for SVD was implimented in the principal component space (PCS)

Benchmarked the SVD model by comparing with Arithmetic mean, Harmonic mean and probability density function (PDF) models

A novel high-order accurate control volume FEM multiphase flow simulator also compared the simulations from all the models

The SVD model presented a better representation compared to the other models

### 2018-04-15 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
For First Submission 15th April 2018

@@
 This is because it is impossible to obtain the value of permeability at every point in realistic domains.
-And, even if this was possible, it would be extremely challenging to get the computing resources to make use of all available data.
+And, even if this was possible, it would be extremely challenging to get the computing resources to make use of all available data values.
 This challenge gave birth to upscaling, a model order reduction method.
@@
 In this paper, a SVD-based method was developed to reduce the order of porous media permeability field (\ie upscale).
-This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits performance.
+This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
 It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
@@
 $\mathbf{K}$ is prescribed in the system of governing conservative equations, \ie it is an indepedent input variable.
-Since $\mathbf{K}$ is petrophysical rock property that varies spatially, it is not possible to determine at every spatial coordinate.
+Since $\mathbf{K}$ is a petrophysical rock property that varies spatially, it cannot be determined at every spatial coordinate.
 And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations.
@@
 The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.
-Consider for instance a small square which is discretized to contain four squares such that $4$ data values are defined in the middle of the four squares.
+Consider for instance a small square which is discretized to contain four squares such that $4$ data points are defined in the middle of the four squares.
 The permeability space of $4$ can be reduced to a smaller value of $1$ through an averaging process such as arithmetic, harmonic or geometric mean.
@@
 
-The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
@@
 The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
-Albeit, the permeability data for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
 Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
@@
 \begin{enumerate}[1.]
-  \item A function is used to randomly generate uniform (\ie Gaussian) data for each block. The range for each block is as below:
+  \item A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
   \begin{enumerate}[a)]
@@
   \end{enumerate}                                                    
-  \item The number of data points generated for each block is $1600$ and the data is randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
-  \item Merge data from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned data in each block.
+  \item The number of data points generated for each block is $1600$ and the data values are randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
+  \item Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned dataset for each block.
 This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
@@
 \begin{enumerate}[1.]
-  \item Data from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) is used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian data set using arithmetic mean and standard deviation is used to stochastically produce a quarter of data points from the BaseCase for each of the four blocks.
-  \item The number of data points \red{(PREVIOUSLY, IT WAS ``THE NUMBER OF DATA'' ...
-HOWEVER DATA IS NOT AN ACCOUNTABLE NOUM, THEREFORE YOU MAY USE EITHER ``AMOUNT OF DATA'' OR ``NUMBER OF DATA POINTS'' ...
-I REPLACED MOST OF ENTRIES -RE DATA AS AN ACCOUNTABLE NOUM ...
-PLEASE REVISE THE MANUSCRIPT ACCORDINGLY.)} generated for each block is $400$ and the data is randomly positioned within each block in a structured pattern.
-As in the base case, the simulation grid is unstructured.
-  \item Finally, the structured data from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
+  \item The datasets from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) are used to calculate mean and standard deviation for each block of the permeability field.
+  \item A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase for each of the four blocks  (\ie $400$ data points for each block).
+  \item The data values in the dataset for each block is randomly positioned within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
+  \item Finally, the structured/arranged dataset from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
 \end{enumerate}
@@
   \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data in each column reduced to half of the original column.
+  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
 These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
   \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
-It is a permeability field with a quarter of the data in the base case and therefore a permeability field with reduced order.
+It is a permeability field with a quarter of the data values in the base case and therefore a permeability field with reduced order.
 \end{enumerate}
@@
 Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
-Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PNDG[1]{1} \red{(IS THIS TRUE?)} triangular element-pairs.
+Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs.
 Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
 
-Figure~\ref{fig:PermFields} compares the permeability distribution for all models.
-\red{Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f))} \red{(THIS INFO SHOULD BE IN THE CAPTION OF THE FIGURES INSTEAD)}.
-The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f).
+Figure~\ref{fig:PermFields} compares the permeability distribution for all the models.
+As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
+Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.
 
@@
 Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
-Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the same point in the BaseCase but the SVDCase has this direct connection through the interpolation \red{(SENTENCE IS SLIGHTLY CONFUSING ...
-NOT SURE WHAT YOU WANT TO CONVEY)}.
+Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block.
+However, the data value at a point in the SVDCase is directly related to the nearest data values with respect to the same point in the BaseCase, throught the interpolation which takes place in the PCS.
 
@@
 
-\medskip
-\red{(I GUESS YOU SHOULD USE ONE PARAGRAPH JUST TO DESCRIBE (TO THE READER WHO HASNT READ THE OTHER REFERENCES) THE PHYSICS ASSOCIATED WITH THE BASECASE -- FIG 4 LINKING WITH THE REFERENCES ...
-REMEMBER THIS IS YOUR WORK'S VALIDATION!!!
-THIS BENCHMARK WOULD: (A) IF THE SIMULATION WAS PERFORMED W HOMOGENEOUS MEDIA (AT EACH BLOCK) A PISTON SHAPE BEHAVIOR (AT EACH BLOCK, I.E., A BLOCK DIVIDED BUCKLEY-LEVERETT BEHAVIOR) COULD BE NOTICED HOWEVER AS THE WHOLE SYSTEM IS HETEROGENEOUS THIS MAY NOT BE CLEARLY NOTICED; (B) CROSS-FLOW, I.E., PREFERENTIAL FLOW  THROUGH REGIONS OF HIGH PERMEABILITY; (C) FLOW QUALITATIVE BEHAVIOUR MATCHES THE EXPERIMENTS  ETC ETC ETC MAKE IT STRONG !)}
+Before going on to review the results of the simulations, it is beneficial to briefly consider the Buckley-Leverett and cross-flow behaviour which are be used to validate the results from this work.
+
+\citet{buckley_1942} in 1942 derived the Buckley-Leverett equation, an analytical (albeit simplified) two phase flow equation.
+The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation.
+The equation is referred to as "simplified" because of the assumptions made while deriving it, some of which were ignored in this work.
+Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities.
+Additionally, the permeability field in each block is heterogeneous.
+However, the general validation test or expectation from Buckley-Leverett's influence on this work, is that, the injected fluid saturation in $K1$ and $K2$ is expected to have a piston-shape front within those blocks, subject some inconsistency at the boundary between the two blocks, and also within the blocks due to the heterogeneity.
+
+\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were somewhat replicated here for the simulations.
+Therefore, the work of \citet{dawe_2008} can be used to validate the resulting simulations from this work.
+In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$.
+Additionally, the cross-flow from $K1$ to $K4$ is well represented in the simulations.
 
@@
 Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
-Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c)\red{(WHAT DO YOU MEAN W ``MORE INJECTION''?
-MASS FLOW RATE OF INJECTION (BC) WAS THE SAME FOR ALL CASES ...DO YOU MEAN THE DISPLACEMENT IN THE RHS QUADRANTS?)}.
+Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
 This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
@@
 Results show that the permeability field data reduction can be specifically defined for the PDFCase and the SVDCase but not for the ArithMeanCase and the HarmMeanCase.
-This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution.
+This is because the latter cases will produce the same permeabiBuckleylity field irrespective of the upgrid resolution.
 The SVDCase is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.

### 2018-04-15 Papers/AppliedMaths2018/article_figure1.tex
For First Submission 15th April 2018

@@
 }   
-\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases. \red{(ADD NUMEBR OF ELEMENTS OR NODES FOR EACH CASE)}}
+\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases with 4112 and 728 triangular elements respectively}
 \label{fig:HiRes_LowRes_Mesh}
@@
 }   
-\caption{Permeability field for the base case as well as the upscaled cases}
+\caption{Permeability field for the base case as well as the upscaled cases (Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures - \ie Fig.~\ref{fig:PermFields}(b) to (f))}
 \label{fig:PermFields}
@@
 }   
-\caption{Simulations for the BaseCase}
+\caption{Simulations for the BaseCase (Saturation legend in Fig.~\ref{fig:BaseCase_Saturation}(a) is representative for all the other figures - \ie Fig.~\ref{fig:BaseCase_Saturation}(b) to (f))}
 \label{fig:BaseCase_Saturation}
@@
 }   
-\caption{Simulations for the ArithMean Case}
+\caption{Simulations for the ArithMean Case (Saturation legend in Fig.~\ref{fig:ArithMeanCase_Saturation}(a) is representative for all the other figures - \ie Fig.~\ref{fig:ArithMeanCase_Saturation}(b) to (f))}
 \label{fig:ArithMeanCase_Saturation}
@@
 }   
-\caption{Simulations for the HarmMean Case}
+\caption{Simulations for the HarmMean Case (Saturation legend in Fig.~\ref{fig:HarmMeanCase_Saturation}(a) is representative for all the other figures - \ie Fig.~\ref{fig:HarmMeanCase_Saturation}(b) to (f))}
 \label{fig:HarmMeanCase_Saturation}
@@
 }   
-\caption{Simulations for the PDFCase}
+\caption{Simulations for the PDFCase (Saturation legend in Fig.~\ref{fig:PDFCase_Saturation}(a) is representative for all the other figures - \ie Fig.~\ref{fig:PDFCase_Saturation}(b) to (f))}
 \label{fig:PDFCase_Saturation}
@@
 }   
-\caption{Simulation for the SVDCase}
+\caption{Simulation for the SVDCase (Saturation legend in Fig.~\ref{fig:SVDCase_Saturation}(a) is representative for all the other figures - \ie Fig.~\ref{fig:SVDCase_Saturation}(b) to (f))}
 \label{fig:SVDCase_Saturation}
@@
 \vspace{0.cm}
-\hbox{\hspace{3.75cm} (a) BaseCase\hspace{1cm} (b) ArithMeanCase}
+\hbox{\hspace{7.0cm} (a) BaseCase \hspace{5.75cm} (b) ArithMeanCase}
 \vspace{0.5cm}
@@
 \vspace{0.cm}
-\hbox{ \hspace{0cm} (c) HarmMeanCase \hspace{0.5cm} (d) PDFCase \hspace{1.5cm} (e) SVDCase}
+\hbox{ \hspace{1.75cm} (c) HarmMeanCase \hspace{5.0cm} (d) PDFCase \hspace{5.0cm} (e) SVDCase}
 \vspace{0.cm}
 }   
-\caption{Comparing phase 1 saturation distribution for all the models at $t=1.15$ s}
+\caption{Comparing phase 1 saturation distribution for all the models at $t=1.15$ s (Saturation legend in Fig.~\ref{fig:Saturationfield@t=1.15s}(a) is representative for all the other figures - \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) to (e))}
 \label{fig:Saturationfield@t=1.15s}

### 2018-04-15 Papers/AppliedMaths2018/cover_letter.tex
For First Submission 15th April 2018

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{Dr Masoud Jabbari \\
CEng MIMechE PMSAMPE AMACerS MInterPore \\
Lead Guest Editor for Special Issue: \\
Applied Mathematical Modelling \\
WMG, University of Warwick \\
Coventry, CV4 7AL}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Mr. Babatunde Lashore \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
Room 207, Fraser Noble Building \\ University of Aberdeen, Aberdeen AB24 3UE. \\ email: lashorebabatunde@yahoo.com % Your address and phone number
\end{center} 
\vfill

\signature{B. Lashore} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Dr. Jabbari,}

I am submitting a manuscript to be considered for publication in the special issue of "Applied Mathematical Modelling" on "Transport in Porous Media" in relation to the $3^{rd}$ UK InterPore Conference on Porous Media and the $1^{st}$ Monash-Warwick PREFRAC Workshop on Hydraulic Fracturing. The abstract and presentation I made at that conference has progressed since then, and the title of my submission has changed from "A Numerical Investigation of Stochastic and Deterministic Upscaling Methods for Permeability Fields" to "A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)".

I hereby confirm that the research in this work has not been published elsewhere and it has not been submitted simultaneously for publication elsewhere.

The manuscript presents a model for representing an upscaled permeability field using singular value decomposition. It compares the benefits/performance of this model to well known deterministc methods such as arithmetic and harmonic averaging techniques. The model is also compared with a stochastic probability density function (PDF) model. Then a novel control volume finite element method (CVFEM) multiphase flow simulator is used to compare simulation results from the aforementioned models. The manuscript presents and discusses the results before drawing conclusions.

I hope you find the manuscript satisfactory and accept it for publication in the journal. I thank you for your time and I look forward to further correspondence from you.

\closing{Sincerely yours,}

\encl{Cover Letter, Highlight.tex, Manuscript(Makefile, Stochastic\_Upscaling\_UK\_AMM\_2018.tex, article\_/figure1.tex, Pics Folder, references.bib, elsarticle.cls, elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}

### 2018-04-15 Papers/AppliedMaths2018/Highlights.tex
Initial submission of final manuscript 15th April 2018

@@
-Performed a model order reduction (i.e., upscale) of a permeability field using singular value decomposition (SVD)
+\documentclass[a4paper,11pt]{article}
 
-Reduced order model (ROM) for SVD was implimented in the principal component space (PCS)
+\newcommand{\ie}{{\it i.e., }}
+% define the title
+\author{B.~Lashore}
+\title{Highlights}
+\begin{document}
+% generates the title
+\maketitle
+% insert the table of contents
+%\tableofcontents
+%\section{Some Interesting Words}
 
-Benchmarked the SVD model by comparing with Arithmetic mean, Harmonic mean and probability density function (PDF) models
-
-A novel high-order accurate control volume FEM multiphase flow simulator also compared the simulations from all the models
-
-The SVD model presented a better representation compared to the other models
+\begin{enumerate}
+  \item Performed a model order reduction (\it upscale) of a permeability field using singular value decomposition (SVD)
+  \item Reduced order model (ROM) for SVD was implimented in the principal component space (PCS)
+  \item Benchmarked the SVD model by comparing with Arithmetic mean, Harmonic mean and probability density function (PDF) models
+  \item A novel high-order accurate control volume FEM multiphase flow simulator also compared the simulations from all the models
+  \item The SVD model presented a better representation compared to the other models 
+\end{enumerate}
+\end{document}

### 2018-04-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
eq3 symbol update

@@
 
+\medskip
 The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
@@
 
+\medskip
 Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
@@
   \sum\limits_{E} \left.
-\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
+\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  - \mathcal{S}_{u_\alpha} \right) dV \right.
 + \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\

### 2018-04-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update Jackson et al 2015

@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.

### 2018-04-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
+\medskip
 The computational domain with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
@@
 
+\medskip
 As demonstrated in the preliminary model validation (Section~\ref{section:results_initial_model_validation}), crossflow towards the upper region of the initial part of the domain is due to boundary pressures and diffusivities (both at different vertical layers), \ie caused by large permeability gradients (Fig.~\ref{fig:3DChannel_sat}).
@@
 
+\medskip
 Such preferential flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
@@
 
+\medskip
 In Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
@@
 
+\medskip
 However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,salinas_2018,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
@@
 
+\medskip
 Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
@@
 
+\medskip
 %(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
@@
 
+\medskip
 Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
@@
 
+\medskip
 Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious / impervious channelised domain were performed.
@@
 Order of accuracy of the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
+
 \medskip
-
 % (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.

### 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
updates
update
update the no-slip condition for fig 3 and 4

--- 2017-12-29 Papers/ViscousInstabilities/article_figure1.tex
@@
 \vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
-\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
+\caption{This is a graphical representation of two different element types.
+Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \centering
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_2.pdf}}
 \caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
@@
 \hbox{\hspace{-0.3cm}
-\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
+\hbox{\hspace{0.25cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=25
+\hbox{\hspace{4.0cm} (b) flow at t=25
 }
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{in cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
@@
 \includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements.pdf}
-\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements (red) and nodes (blue) for simulations performed with fixed (dotted line) and adaptive (full line) mesh. }
+\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
 \label{fig:5regions_plottimenodeselements}

### 2018-04-18 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
-Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
+Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers, uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
@@
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+%The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
 
@@
 \left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
 \end{eqnarray}
@@
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
+$\mathcal{S_{ua})}$ is the source term associated with the Darcy and continuity equations.
 $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.

### 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
update
update fig 2
update

@@
 \centering
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
 \caption{This is a graphical representation of two different element types.
-Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair.
+Triangle on the left ({\it A}) is a representation of the \PN[1]{2} element-pair, whereas triangle on the right ({\it B}) represents the \PN[1]{1} element-pair.
 Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}

### 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
update

@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D0b.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}

### 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
 \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
@@
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S_{ua})}$ is the source term associated with the Darcy and continuity equations.
+$\mathcal{S_{u,{\alpha}}}$ is the source term %associated with the Darcy and continuity equations.
+which may include gravity and/or capillarity, respectively.
 $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-Boundary conditions also include no-flux across upper and lower borders.
+\green{No normalflux boundary conditions are implied across the upper and lower borders}.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
@@
 Studies by \citet{langtangen_1992} on fluid flow dynamics in heterogeneous porous media (analytical and numerical solutions) demonstrated that hyperbolic Buckley-Leverett model is inherently unstable, \ie the expected uniform interface front collapses as any perturbation in physical parameters are imposed to the problem.
-
 Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
@@
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed \green{synthetic permeability distribution with values between $1$ and $5$}.
 A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.

### 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-\green{No normalflux boundary conditions are implied across the upper and lower borders}.
+\red{No normal flux boundary conditions are implied across the upper and lower borders}.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
@@
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed \green{synthetic permeability distribution with values between $1$ and $5$}.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed \red{synthetic permeability distribution with values between $1$ and $5$}.
 A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.

### 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
 \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}

### 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

--- 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} ,\label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
 \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}

### 2018-04-22 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability in cm^{2} and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}

### 2018-04-22 Papers/ViscousInstabilities/article_figure1.tex
update

--- 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability in \red{cm^{2}} and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}

### 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
+
 \begin{eqnarray}
@@
 \end{eqnarray}
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+
+\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
 $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
 Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+\red{The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn})}.
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
 
-From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
 \begin{displaymath}
@@
 \end{displaymath}
- that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+
+\noindent that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
 Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.

### 2018-04-23 Papers/ViscousInstabilities/0 submission file/Manuscript_ViscousInstabilities_KC.tex

--- 2018-04-22 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
-Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers, uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
+Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers -- uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
@@
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-%The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
 
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
 \end{eqnarray}
@@
 ${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S_{u,{\alpha}}}$ is the source term %associated with the Darcy and continuity equations.
-which may include gravity and/or capillarity, respectively.
+$\mathcal{S}$ is the source term associated with the Darcy and continuity equations.
 $S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
@@
 
-\medskip
 The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
@@
   \sum\limits_{E} \left.
-\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  - \mathcal{S}_{u_\alpha} \right) dV \right.
+\int\limits_{\Omega_E} { {Q}}_{i} \left({\mathbf v}_\alpha + \nabla p  -{\mathbf s}_{u_\alpha} \right) dV \right.
 + \displaystyle \oint_{\Gamma_{E}} {Q}_i {\mathbf n} \left(p - \tilde{p}\right) d\Gamma + \nonumber \\
@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-\red{No normal flux boundary conditions are implied across the upper and lower borders}.
+Boundary conditions also include no-flux across upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
@@
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed \red{synthetic permeability distribution with values between $1$ and $5$}.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeability distribution.
 A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
@@
 Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
-
 \medskip

### 2018-04-23 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex

@@
 Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
-Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers, uneven front with elongation at the outside edge of fluids interface, with strong impact on the displacement efficiency.
+Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers therefore creating an uneven front with elongation at the outside edge of fluids interface with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
@@
 Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-\red{The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn})}.
+The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).
 Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-\red{No normal flux boundary conditions are implied across the upper and lower borders}.
+No normal flux boundary conditions are implied across the upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
@@
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed \red{synthetic permeability distribution with values between $1$ and $5$}.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed synthetic permeability distribution with values between $1$ and $5$.
 A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.

### 2018-04-23 Papers/ViscousInstabilities/article_figure1.tex
update
i have to check the last page again

--- 2018-04-18 Papers/ViscousInstabilities/article_figure1.tex
@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability in $cm^{2}$ and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}
@@
             }}
-\caption{3D Channel: Text to come}
+\caption{3D Channel: \red{Text to come}}
 \label{fig:3DChannel_satvel_XYplanes_adapt}

### 2018-04-24 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} ,\label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
 \phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
@@
 Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+%The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
+%\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
 The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).

### 2018-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 \medskip
-%Due to the heterogeneity of geological formations, detailed modelling and simulation of multiphase flows through porous media is crucial for design, control and prediction of the aforementioned processes.
 Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
@@
 Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
+%Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
@@
 \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
 

### 2018-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
-Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+%Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
 Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
@@
 
-\medskip
-The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
+%\medskip
+%The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
 The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.

### 2018-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
I have colored the 1st paragraph of the section 4.4 as i think this can be removed. That was also part of the maajor comments/feedback.

@@
 %\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
-In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+
+\blue{ - KC:I think this part can be removed from here - } 
+\red{In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
+This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.}
 

### 2018-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
so far most of the comments from the first reviewer that also mentioned by the other 2 have been corrected/altered/ removed..
update

@@
 while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+
+%Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
 
@@
 As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
-There are always a few dominant fingers that spread and shield the growth of other fingers.
+%At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
+Out of these finger shape formation there are always a few dominant fingers that spread and shield the growth of other fingers.
 The interface of the main finger collapses and starts splitting into new lobes of fingers.
@@
 \subsection{Initial Model Validation}\label{section:results_initial_model_validation}
-Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
+Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model's capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
 The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).

### 2018-05-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial permeability distribution creates a rough pressure field, \ie pressure gradient is discontinuous across the interface between different permeability zones, thus the fluid flows to the larger permeability region.
+The spatial permeability distribution creates a rough pressure field, \ie pressure gradient is discontinuous across the interface between different permeability zones, therefore the fluid flows to the larger permeability region.
 %Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.

### 2018-05-04 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh.
-During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
-Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_severalfields_adapt}b-c and~\ref{fig:3DChannel_satvel_XYplanes_adapt}.
+During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}a).
+Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}b-c and \ref{fig:3DChannel_satvel_XYplanes_adapt}.
 Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}.

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
update
alternative introduction with section 3 viscous finger. included - on progress

@@
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\blue{\subsection{Alternative Introduction}}
+\blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
+
+Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
+Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
+More recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+
+\medskip
+Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
+Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
+
+\medskip
+In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
+As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+
+\medskip 
+Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
+%Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
+However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
+Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+
+\medskip
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
+%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
+%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
+%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
+FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
+The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
+Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
+Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
+while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+
+%Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+
+%%%%%%%%%%%%%%%
+%\begin{comment}
+%\begin{equation}
+% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
+%\label{cvfe_pressure} 
+%\end{equation}
+
+%\begin{equation}
+% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
+%\label{cvfe_saturation}
+%\end{equation} 
+%\end{comment}
+%%%%%%%%%%%%%%%
+
+\medskip
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
+These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
+In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+
+%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
+Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
+%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
+Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
+All these parameters are represented under one term in the global mass balance equation.}
+
+\medskip 
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
+A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
+%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
+A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
+%The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
+
+\medskip
+A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
+Impact of mobility ratio on the fingers formation is also included in this section.
+Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+
+\medskip
+\blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
 

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
alternative introduction between in blue

@@
 Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces by neglecting gravitational effects (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
 
@@
 Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-%Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
 Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
@@
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
-%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
 Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-
-%Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
-
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation} 
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
 Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
 Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+%These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
+In order to overcome any potential numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
 This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
 \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
 
@@
 A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
-%, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
 A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-%The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
 

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
this is an alternative version/introduction. I have comment the previous section -introduction and intro to viscous instab- and I have created a new introduction that includes both of them while i tried to decrease the size.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{comment}
 \section{Introduction}\label{section:intro}
@@
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
+\end{comment}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\blue{\subsection{Alternative Introduction}}
+\blue{\section{Alternative Introduction}}
 \blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
@@
 Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces by neglecting gravitational effects (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces by neglecting gravitational effects (often referred as viscous instabilities or viscous fingering).
+%Section \ref{section:ViscousInstabilities}).
 
@@
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+This problem is associated with water-flooding processes and caused by high-permeability layers and unfavorable mobility ratios.
+Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of a reservoir \citep{riaz_2004, tavassoli_2015}.
+During immiscible CO$_{2}$-flooding $\left(\text{\ie in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, viscosity of supercritical CO$_{2}$ is lower than crude oil, thus viscous fingering and/or channelling may occur.
+
+\medskip
+Viscous instabilities can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
 Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
+
+\begin{equation}
+N_{c} = \frac{\mu U}{\gamma}.
+\label{eq:capillary_number}
+\end{equation}
+
+\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
+This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
+
+\medskip
+In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
+In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
+The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+Pressure differences acting on the interface produces a net pressure force,
+
+\begin{equation} 
+\Delta P= - \gamma \nabla\cdot\hat{n}. 
+\label{eq:pressure_dif} 
+\end{equation}
+
+\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
+
+\medskip
+As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+\begin{equation}
+ \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
+\label{eq:MR}
+\end{equation}
+MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
+
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+
+\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).
+Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
+
+\begin{displaymath}
+    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
+\end{displaymath}
+
+\noindent that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
+
+\medskip
+In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+%At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
+Out of these finger shape formation there are always a few dominant fingers that spread and shield the growth of other fingers.
+The interface of the main finger collapses and starts splitting into new lobes of fingers.
+One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a critical width while the saturation %concentration gradient
+of its front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
+Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment} 
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
@@
 %\clearpage
+\end{comment}
 

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
trying to decrease the intro and combine it with viscou fingering

@@
 Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
-More recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
-
-\medskip
+%More recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
 Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
@@
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-This problem is associated with water-flooding processes and caused by high-permeability layers and unfavorable mobility ratios.
+This problem associated with water-flooding processes is caused by high-permeability layers and unfavorable mobility ratios.
 Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of a reservoir \citep{riaz_2004, tavassoli_2015}.
@@
 \medskip
-Viscous instabilities can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+Viscous instabilities can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR)(see eq.\ref{eq:MR}) between displacing and displaced fluids.
 Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 %More recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
-Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+Description of physics and mechanisms of multiphase porous media flows were reported by %\citet{wooding_1969} 
+\citet{wooding_1976} with focus on capillary pressure and flow regimes.
 A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
@@
 In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
+As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.\ref{fig:simple_case}).
 Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
@@
 As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
+
 \begin{equation}
@@
 \end{equation}
+
 MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.

### 2018-05-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 \medskip
-Viscous instabilities can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR)(see eq.\ref{eq:MR}) between displacing and displaced fluids.
+\textit{Viscous instabilities} can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR)(see eq.\ref{eq:MR}) between displacing and displaced fluids.
 Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.

### 2018-05-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC_Feb.tex
Adding files that hopefully were used in the original submission back on Feb2018

--- 2018-04-23 Papers/ViscousInstabilities/0 submission file/Manuscript_ViscousInstabilities_KC.tex
@@
 
-\medskip
 Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equations.
@@
 
-\medskip
 From Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}, it is clear that during fluid displacement, the mobility ratio changes as phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, varies in time and space (Eqn.~\ref{eqn:saturation_eqn}).
@@
 Studies by \citet{langtangen_1992} on fluid flow dynamics in heterogeneous porous media (analytical and numerical solutions) demonstrated that hyperbolic Buckley-Leverett model is inherently unstable, \ie the expected uniform interface front collapses as any perturbation in physical parameters are imposed to the problem.
+
 Spatial variation in geological formations occurs in all length-scales, where heterogeneity characteristics in small length-scales (\ie pore) are statistically embedded into permeability (absolute and relative) and porosity parameters.
@@
 Geometrical evolution in time and space of these elongations provides good indication of instabilities at the fluid front interface.
-\medskip
+
 The computational domain with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
@@
 
-\medskip
 As demonstrated in the preliminary model validation (Section~\ref{section:results_initial_model_validation}), crossflow towards the upper region of the initial part of the domain is due to boundary pressures and diffusivities (both at different vertical layers), \ie caused by large permeability gradients (Fig.~\ref{fig:3DChannel_sat}).
@@
 
-\medskip
 Such preferential flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown.
@@
 
-\medskip
 In Sections \ref{section:results_homo_hete}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences.
@@
 
-\medskip
 However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,salinas_2018,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
@@
 
-\medskip
 Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
@@
 
-\medskip
 %(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
@@
 
-\medskip
 Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
@@
 
-\medskip
 Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious / impervious channelised domain were performed.
@@
 Order of accuracy of the element-pair and mesh resolution play key-roles to capture directional flow pathways and fingers in 3D simulations.
+\medskip
 
-\medskip
 % (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.
@@
 \bibliographystyle{elsarticle-harv} 
-\bibliography{references}
+\bibliography{references_Feb}
 
@@
 \clearpage
-\input{article_table}
+\input{article_table_Feb}
 \clearpage  
@@
 
-\input{article_figure1}
+\input{article_figure1_Feb}
 %\input{article_figure2}

### 2018-05-13 Papers/ViscousInstabilities/article_figure1_Feb.tex
Adding files that hopefully were used in the original submission back on Feb2018

--- 2018-04-22 Papers/ViscousInstabilities/article_figure1.tex
@@
 \centering
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
-\caption{This is a graphical representation of two different element types.
-Triangle on the left ({\it A}) is a representation of the \PN[1]{2} element-pair, whereas triangle on the right ({\it B}) represents the \PN[1]{1} element-pair.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
+\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
+\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \centering
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_2.pdf}}
+\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
 \caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
@@
 \hbox{\hspace{-0.3cm}
-\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
+\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
 }
 \vspace{0.0cm}
-\hbox{\hspace{0.25cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
+\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
 }
@@
 \vspace{0.0cm}
-\hbox{\hspace{4.0cm} (b) flow at t=25
+\hbox{\hspace{4.5cm} (b) flow at t=25
 }
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{in cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
 The domain contains $26313$ \PN[1]{2} triangular elements.}
@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability in cm^{2} and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D0b.pdf} 
-            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
+            \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
-      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
+      \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
@@
       \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
-\caption{3D channel flow (fixed mesh): permeability distribution. The domain contains 243056 \PN[1]{1} element-pairs.}
+\caption{3D channel flow: Permeability distribution within the computational domain, containing 235242 \PNDG[1]{1} element-pairs.}
 \label{fig:3DChannel_PermMesh}
 \end{figure}
+\clearpage
+
+%%%
+%%% FIGURE XXXXXX
+%%%
+\begin{landscape}
+\begin{figure}[ht]
+  \vbox{\vspace{-.5cm}
+      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} } 
+      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
+      \vspace{0.5cm}
+      \hbox{\hspace{.5cm} 
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_110.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
+            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
+      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
+\caption{3D channel flow (fixed mesh): saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
+Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
+The domain contains 235242 \PNDG[1]{1} elements.}
+\label{fig:3DChannel_sat}
+\end{figure}
+\end{landscape}
 \clearpage
@@
 %\end{landscape}
-\clearpage
-
-%%%
-%%% FIGURE XXXXXX
-%%%
-\begin{landscape}
-\begin{figure}[ht]
-  \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.6\textwidth]{./Pics1/3D_Channel/3D_channel_sat_30.pdf} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_60.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_90.pdf} } 
-      \hbox{\hspace{2.cm} (a) t=0.29s \hspace{5.cm} (b) t=0.56s \hspace{4.cm} (c) t=0.82s}
-      \vspace{0.5cm}
-      \hbox{\hspace{.5cm} 
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_110.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_150.pdf}
-            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_channel_sat_490.pdf} }
-      \hbox{\hspace{2.cm} (d) t=1.00s \hspace{5.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s  } }
-\caption{3D channel flow (fixed mesh): saturation front evolving in time and space with preferential flow pathways through 3.50 seconds of numerical simulations.
-Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
-The domain contains 368513 \PN[1]{1} elements.}
-\label{fig:3DChannel_sat}
-\end{figure}
-\end{landscape}
 \clearpage
@@
 \end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+        \hbox{\hspace{5.cm}
+          \includegraphics[width=\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Mesh_b} }
+        \hbox{\hspace{10cm}(a)}
+      \vspace{.5cm} 
+         \hbox{\hspace{0.cm}
+             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_StreamLinesHoriz_b} 
+      \hspace{.5cm} 
+             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Isosurface_b} 
+         }
+        \hbox{\hspace{6cm}(b) \hspace{8cm}(c)}
+    }
+\caption{3D Channel (adaptive mesh): (a) Wetting fluid saturation overlapped with mesh; (b) streamlines and; (c) isosurfaces.
+All plots are shown at 3.78s (Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}f).
+}
+\label{fig:3DChannel_severalfields_adapt}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_0_ContourPlotSlice_b} \hspace{-.5cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_20_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(a)\hspace{9cm}(b)}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_60_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_120_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(c)\hspace{9cm}(d)}
+        \hbox{\hspace{-3.cm}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_200_ContourPlotSlice_b}
+            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_ContourPlotSlice_b}}
+        \hbox{\hspace{2cm}(e)\hspace{9cm}(f)}
+}
+    \caption{3D Channel (adaptive mesh):  XY and YZ planes showing wetting fluid saturation overlapped with Darcy velocity vectors at  (a) 0.00, (b) 0.09, (c) 0.71, (d) 1.75, (e) 2.47 and (f) 3.78s.
+Colour scheme for saturation profile is the same as used in Fig.~\ref{fig:3DChannel_sat_adapt}.}
+\label{fig:3DChannel_satvel_XYplanes_adapt}
+\end{figure}
+%\end{landscape}
   \clearpage
@@
 \end{comment}
-
-%%%%
-%%%%  FIGURE
-%%%%
-%\begin{landscape}
-  \begin{figure}[ht] 
-    \vbox{\vspace{0.cm}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_0_ContourPlotSlice_b} \hspace{-.5cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_20_ContourPlotSlice_b}}
-        \hbox{\hspace{2cm}(a)\hspace{9cm}(b)}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_60_ContourPlotSlice_b}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_120_ContourPlotSlice_b}}
-        \hbox{\hspace{2cm}(c)\hspace{9cm}(d)}
-        \hbox{\hspace{-3.cm}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_200_ContourPlotSlice_b}
-            \includegraphics[width=.70\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_ContourPlotSlice_b}}
-        \hbox{\hspace{2cm}(e)\hspace{9cm}(f)}
-}
-    \caption{3D Channel (adaptive mesh):  XY and YZ planes showing wetting fluid saturation overlapped with Darcy velocity vectors at  (a) 0.00, (b) 0.09, (c) 0.71, (d) 1.75, (e) 2.47 and (f) 3.78s.
-Colour scheme for saturation profile is the same as used in Fig.~\ref{fig:3DChannel_sat_adapt}.}
-\label{fig:3DChannel_satvel_XYplanes_adapt}
-\end{figure}
-%\end{landscape}
-  \clearpage
-
-%%%%
-%%%%  FIGURE
-%%%%
-\begin{landscape}
-  \begin{figure}[ht] 
-    \vbox{\vspace{0.cm}
-        \hbox{\hspace{5.cm}
-            \includegraphics[width=\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Mesh_b} }
-      \vspace{.5cm} 
-         \hbox{\hspace{0.cm}
-             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_StreamLinesHoriz_b} 
-      \hspace{.5cm} 
-             \includegraphics[width=0.75\textwidth]{./Pics1/3D_ChannelAdaptive/Test_SlowNewAdapt_288_Isosurface_b} 
-            }}
-\caption{3D Channel: Text to come}
-\label{fig:3DChannel_satvel_XYplanes_adapt}
-\end{figure}
-\end{landscape}
-\clearpage

### 2018-05-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
+
 \section{Introduction}\label{section:intro}
@@
 Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities}).
-%Description of physics and mechanisms of multiphase flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of mechanisms of fluid instabilities (\ie fingering) and forces acting on the interface between two immiscible fluids can be found in \citet{homsy_1987}.
-\citet{adler_1988} described both microscopic and macroscopic scale Darcy-equations.
-% Nevertheless we should refer to the area of flow instabilities  as these, first described by \citet{saffman_1958} \red{(IS THIS TRUE?
-SAFFMANN MAY HAVE BEEN THE FIRST TO THROUGHLY DISCUSS VISCOUS INSTABILITIES, BUT THERE WERE OTHER SCIENTISTS THAT DESCRIBED FLUID INSTABILITIES BEFORE, E.G., RAYLEIGH(1896), TAYLOR (1955) ETC)}.
-%The first distinction should be made between microscopic and macroscopic instabilities.
-Microscopic instabilities describe phenomena occurring locally, for example, Kelvin-Helmholtz and Saffman-Taylor instabilities \citep{saffman_1959}.
-On the other hand, macroscopic instabilities involve two-phase flow system \citep{bottoni_1992}.
-This paper focuses on microscopic instabilities in two-phase systems that occurs due to viscous and stress forces, often referred as viscous instabilities or \textit{viscous fingering} (see section \ref{section:ViscousInstabilities}).
+\blue{This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities})}.
 
@@
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
-\end{comment}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \blue{\section{Alternative Introduction}}
@@
 \blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
+\end{comment}
 
@@
 \left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{u,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
 \end{eqnarray}
@@
 \noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
-${\mathbf u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S_{u,{\alpha}}}$ is the source term %associated with the Darcy and continuity equations.
-which may include gravity and/or capillarity, respectively.
-$S_{\alpha}$ represents the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
+$\mathcal{S}_{u, \alpha}$ is the source term
+which may include gravity and/or capillarity and is related with momentum while the $\mathcal{S}_{cty,\alpha}$ is the source term related with mass (continuity equation).
+$S_{u, \alpha}$ is the source term for momentum while the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
 $\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.

### 2018-06-19 Papers/ViscousInstabilities/Bank2/article_figure1_Feb.tex
keeping the original February files safe

--- 2018-05-13 Papers/ViscousInstabilities/article_figure1_Feb.tex
@@
       \hbox{\hspace{3.cm} (d) t=1.00s \hspace{3.cm} (e) t=1.35s\hspace{4.cm} (f) t=3.50s }}
-\caption{3D channel flow (adaptive mesh): numerical simulation was performed with the smae boundary and initial conditions as in Figs.~\ref{fig:3DChannel_PermMesh}-\ref{fig:3DChannel_Isosurf} with an adaptive mesh.
+\caption{3D channel flow (adaptive mesh): numerical simulation was performed with the same boundary and initial conditions as in Figs.~\ref{fig:3DChannel_PermMesh}-\ref{fig:3DChannel_Isosurf} with an adaptive mesh.
 Flow pathway is very similar to the one shown in Fig.~\ref{fig:3DChannel_sat}.}

### 2018-06-20 Papers/ViscousInstabilities/article_figure1.tex
Copied article_figure1_Feb.tex into article_figure1.tex and started renaming some figures names that were in the original article_figure1.tex file. The original article_figure1.tex file -- now article_figure1_bak.tex, was the old file -- probably from Nov/17, that contained wrong captions. Now, going line by line to check consistency between files.

--- 2018-04-22 Papers/ViscousInstabilities/article_figure1.tex
@@
 \centering
+%\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
 \vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
-\caption{This is a graphical representation of two different element types.
-Triangle on the left ({\it A}) is a representation of the \PN[1]{2} element-pair, whereas triangle on the right ({\it B}) represents the \PN[1]{1} element-pair.
-Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
+\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
+Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
 \label{fig:fem_elem}
@@
 \centering
+%\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
 \vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_2.pdf}}
@@
 \hbox{\hspace{-0.3cm}
+%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
 \includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
@@
 \vspace{0.0cm}
-\hbox{\hspace{0.25cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
+\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
 }
@@
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}} 
+            %\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
@@
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
+      %\hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}

### 2018-07-05 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC_bak.tex
updates of files

--- 2018-05-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
@@
 Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-\blue{This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities})}.
+This work focuses on flow instabilities in two-phase systems due to viscous and stress forces, often referred as viscous instabilities or viscous fingering (Section \ref{section:ViscousInstabilities}).
 
@@
 \medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-%Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators however, they are often limited to relatively simple geometries and often lead to excessive numerical dispersion when strong heterogeneity is present~\citep{chavent_1986}.
+%representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
 Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
 
-\medskip
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
@@
 Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+%Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+%while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. 
+Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
 
-%Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Therefore, average values of coupled velocity-pressure variables are applied across the CVs at the interfaces.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to reduce artificial numerical dispersion associated to the upwind weighting of the advected quantity in regions of strong heterogeneity, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+A control-volume distributed (CVD) scheme coupled with mixed FEM (MFEM) was introduced by \citet{edwards_2006}, where flow and rock variables are discretised in CV space whereas pressure and velocity are solved in FEM space.
+CVD flux-limiting scheme was coupled with high-order convection scheme to assess reduction of anisotropic numerical dispersion in flows through semi-impervious barrier (\ie a region of very low permeability).
 
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
-
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation} 
-%\end{comment}
-%%%%%%%%%%%%%%%
+% \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
+%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
 
 \medskip 
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to simulate viscous flow instabilities in porous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
+A hybrid family of \PN[n]{m} and \PNDG[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure variables.
+Thus, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media through a novel computational multi-fluid dynamics model (embedded in the next-generation flow simulator Fluidity/IC-FERST software).
+The two main aspects of this work are: (a) qualitative and quantitative validation of the model (Section~\ref{section:results_homo_hete}) for viscous flow instabilities and, (b) impact of mesh resolution on capturing the onset of viscous fingers formation.
 
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
 %, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+%A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
@@
 \medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+A brief description of the numerical formulation and viscous flow instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
 Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
+Impact of viscosity ratio on the fingers formation is also included in this section.
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
@@
 \section{Model Formulation}\label{equations_scheme}
-%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Different domains will produce different flow instabilities.
-In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
-DG-methods combine advantages of classical finite volume and finite element methods.
-
-%\subsection{Numerical Formulation}
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-%\begin{equation}\label{e:darcy_eq}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_bal}
-%\end{equation}
-%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-%\begin{equation}
-%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-%\end{equation}
-%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-%\begin{eqnarray}
-%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-%\label{v_and_p}
-%\end{eqnarray}
-
-%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_balance}
-%\end{equation}
-
-%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-%\end{comment}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\label{e:darcy_eq}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-%\label{E:darcy_eqn}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
-% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-%\begin{equation}
-%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:darcy_ext}
-%\end{equation}
-%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-%\end{comment}
-%%%%%%%%%%%%%%%
 
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+&&\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+&&\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\label{eqn:saturation_eqn}
 \end{eqnarray} 
-
-\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
-$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}_{u, \alpha}$ is the source term
-which may include gravity and/or capillarity and is related with momentum while the $\mathcal{S}_{cty,\alpha}$ is the source term related with mass (continuity equation).
-$S_{u, \alpha}$ is the source term for momentum while the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+with $x_{i}\in\Omega,\; t>0$.
+$\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
+$\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase.
+$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase related to the momentum (\eg gravity, capillarity etc) and continuity (\eg geochemical reactions etc) equations.
+Finally, $\mathcal{K}_{r,\alpha}$ is the relative permeability, and $S_{\alpha}$ is the  $\alpha$-phase saturation with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
 $\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
@@
 In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
-Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries, which are limited to yield bounded fields (\eg positive densities, saturations bounded between 0 and 1, etc).
-Simulations performed for this work were conducted using two types of elements: \PN[1]{1} and \PN[1]{2}.
+
+Mass balance (continuity) equations are solved in CV space and a Petrov-Galerkin FEM is used to obtain high-order fluxes on CV boundaries.
+Smooth transition between first- and high-order fluxes are enforced through an extrema detection scheme based on normalised variable diagram \citep[NVD,][]{jasak_1999,darwish_2003} applied across faces of neighbouring CVs.
+Resulting normalised upwind face values are used to calculate flux-limited solutions \citep[based on total variation diminishing criteria, TVD,][]{piperno_1998} to yield bounded fields \citep[\eg positive densities, saturations bounded between 0 and 1 etc.
+See][for more details on the flux-limiting scheme within the model]{gomes_book_2012}.
+Simulations performed for this work were conducted using three types of elements: \PN[1]{1}, \PN[1]{2} and \PNDG[1]{1} (Section~\ref{section:results_3D}).
 
@@
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.
-%Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\sigma$ at individual CV as described by \citet{jackson_2013}.
+Velocities across CV interfaces (within and between elements) are calculated through a directional-weighted flux-limited scheme based on upwind value of $\underline{\underline{\sigma}}$ at individual CV as described by \citet{gomes_2017}.
 Summing the discretised Eqn.~\ref{eqn:saturation_eqn} over all phases yields the global mass balance equation,
@@
 %\medskip
-%The discretised global mass and force balance equations are solved using a multigrid-like approach as described by \citet{pavlidis2016} \citep[see also][]{salinas_2016}.
+The discretised global mass and force balance equations are solved using a multigrid-like approach.
 The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment} 
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
@@
 %\clearpage
-\end{comment}
 
@@
 \medskip
-In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
+In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2}, \PN[1]{1} (Fig.~\ref{fig:fem_elem}) and \PNDG[1]{1} (Section~\ref{section:results_3D})  FE-pairs.
 An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-No normal flux boundary conditions are implied across the upper and lower borders.
+Boundary conditions also include no-flux across upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
@@
 \subsection{Capturing Flow Dynamics and Fingering Growth: Impact of Mesh Resolution}\label{section:results_hete_fix_adapt}
-%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
 
-\blue{ - KC:I think this part can be removed from here - } 
-\red{In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
+In most numerical simulations involving geo-fluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features.
 Whilst structured grids often struggle to conform to complex domain boundaries with consistent mesh connectivity, unstructured mesh techniques often relax cells' neighbourhood relationship constraints by dividing the domain into polytopes in which elements share adjacent faces.
-This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.}
+This leads to mesh grids that conform to the domain topography and can make the best use of state-of-the-art self-adaptive computational methods.
 
-\medskip
 In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells.
@@
 
-\medskip
-Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
+%Traditional computational geo-fluid dynamics (CGFD) models often rely on fixed mesh with sufficient resolution throughout the domain to capture specific flow dynamics (\eg fluid instabilities, flow re-circulation, heat and mass transfers etc), however computational overhead may be prohibitive for simulations involving complex geometries and heterogeneous properties.
 Mesh adaptivity methods have been extensively used by the CGFD community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep{pluszny_2007,pietro_2014,su_2016,melnikova_2016}.
@@
 
-\medskip
-The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006}.
-The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
+The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014}.
+%The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
 In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
@@
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed synthetic permeability distribution with values between $1$ and $5$.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a-b, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}c) and divided into 5 regions with prescribed synthetic permeability distribution with values between $1$ and $5$.
 A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
@@
 \medskip
-The computational domain with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh})  was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
+Simulations were performed in a hexahedron domain of 4 cm $\times$ 2.5 cm $\times$ 10 cm, with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh}).
+The computational domain was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
 Pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$ from the left-hand side face.
@@
 \input{article_figure1}
+%\input{article_figure1_Feb}
 %\input{article_figure2}

### 2018-07-05 Papers/ViscousInstabilities/article_figure1.tex
updates of files

@@
 \vbox{
+\vspace{-.5cm}
 %\hbox{\hspace{4.0cm}
@@
 %\includegraphics[width=\textwidth]{./Pics1/Four_regions_coarse_MeshPermeability}
+\hbox{\hspace{.8cm}
+\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Sketch_5Regions.pdf}}
+\vspace{-.5cm}
+\hbox{\hspace{3.5cm} (a) Sketch}
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
+\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshPerm.pdf}}
 \vspace{-1.0cm}
-\hbox{\hspace{3.5cm} (a) Permeability mapping ({\bf K})}
+\hbox{\hspace{3.5cm} (b) Permeability mapping ({\bf K})}
 \vspace{0.0cm}
 \hbox{\hspace{1cm}
-\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
+\includegraphics[width=\textwidth, height=0.45\textwidth]{./Pics1/Section4_4/Five_regions_adapt_MeshSat1.pdf}}
 \vspace{-1.0cm}
-\hbox{\hspace{3.5cm} (b) Initial saturation distribution}}
+\hbox{\hspace{3.5cm} (c) Initial saturation distribution}}
 %}
@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) permeability and (b) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) sketch of the computational domain (dimensions in cm); (b) permeability $\left(\text{cm}^{2}\right)$, and; (c) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}

### 2018-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
updates
Copied article_figure1_Feb.tex into article_figure1.tex and started renaming some figures names that were in the original article_figure1.tex file. The original article_figure1.tex file -- now article_figure1_bak.tex, was the old file -- probably from Nov/17, that contained wrong captions. Now, going line by line to check consistency between files.

@@
 \section{Introduction}\label{section:intro}
-Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
-%Oil and gas migration in reservoirs and transport of contaminants in groundwater are some of important physical problems in which porous media flows play a crucial role.
-%Reservoir engineers and hydro-geologists are dealing with complex geometries, irregular boundaries and heterogeneous geological formations.
-Underground coal gasification is another important field of interest and, more recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+Numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community over the past 40 years.
+Characterisation and prediction of such flows serve as the foundation of hydrocarbon reservoir and groundwater studies.% \citep{white_1981}.
+%Underground coal gasification is another important field of interest and, more recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
+
+Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
+%Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
+This work focused on flow instabilities in two-phase systems due to viscous and stress forces, often referred as viscous instabilities or viscous fingering.
+
+%Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. 
+\citet{muskat_1934} used Hele-Shaw cells (\ie parallel flat plates separated by an infinitesimal gap) to study fluid flow and the impact on the capillary number $\left(\text{N}_{c}\right)$ in the flow dynamics.
+%investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
+%\begin{equation}
+%N_{c} = \frac{\mu U}{\gamma}.\label{eq:capillary_number}
+%\end{equation}
+ %In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface. 
+This experimental apparatus enabled instabilities to be qualitatively investigated by simplifying the flow (in both porous and non-porous media) into a 2D problem.
+
+More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
+For a Hele-Shaw cell of a given size, flow development depends only on the capillary number, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity.
+%Dynamic adaptive mesh was used by \citet{mostaghimi_2016} to capture viscous flow instabilities at oil-water interfaces (waterflooding) in heavy oil reservoirs.
 
 \medskip 
-Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-\blue{This work focuses on flow instabilities in two-phase systems due to viscous and stress forces (often referred as viscous instabilities or viscous fingering, Section \ref{section:ViscousInstabilities})}.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators however, they are often limited to relatively simple geometries and often lead to excessive numerical dispersion when strong heterogeneity is present~\citep{chavent_1986}.
+
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+
+Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Therefore, average values of coupled velocity-pressure variables are applied across the CVs at the interfaces.
+This often leads to excessive numerical dispersion especially in highly heterogeneous media.
+In order to reduce artificial numerical diffusion associated to the upwind weighting of the advected quantity in regions of strong heterogeneity, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
+This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+A control-volume distributed (CVD) scheme coupled with mixed FEM (MFEM) was introduced by \citet{edwards_2006}, where flow and rock variables are discretised in CV space whereas pressure and velocity are solved in FEM space.
+CVD flux-limiting scheme was coupled with high-order convection scheme to reduce anisotropic numerical diffusion in flows through semi-impervious barrier (\ie a region of very low permeability).
 
 \medskip 
-In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.~\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to simulate viscous flow instabilities in porous media.
+The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
+A hybrid family of \PN[n]{m} and \PNDG[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure variables.
 
-\medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-%Advanced numerical methods are in continuous development to accurately represent force balances in Darcean flows.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
+Thus, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media through a novel computational multi-fluid dynamics model (embedded in the next-generation flow simulator Fluidity/IC-FERST software).
+The two main aspects of this work are: (a) qualitative and quantitative validation of the model (Section~\ref{section:results_homo_hete}) for viscous flow instabilities and, (b) impact of mesh resolution on capturing the onset of viscous fingers formation.
 
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-%FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions.
-%Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-%At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
-%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains.
-FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions.
-The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions.
-Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
-while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-
-%Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%\begin{equation}
-% p^{n} = \sum_{j} \hat{p_{j}} N_{\alpha} 
-%\label{cvfe_pressure} 
-%\end{equation}
-
-%\begin{equation}
-% S^{n} = \sum_{j} \hat{p_{j}} M_{b} 
-%\label{cvfe_saturation}
-%\end{equation} 
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-\medskip
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-%Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
-
-%The conservation of mass along with Darcy's law are the governing equations while variables such as pressure, velocity,saturation and permeability define the behaviour of the flow.
-Finite difference methods have been applied to discretise the governing equations \citep{Luo2016,Moortgat2016,Hoteit2008} .
-%\KCnote{in our case only - In conventional reservoirs the principal forces that affect fluid flow include, viscous forces, effects of gravity and permeability diffrences while in unconventional gas reservoirs flow simulation models take into account the phenomena of adsorption and diffusion \citep{abdus_2015}.
-Even though the mechanisms of the instabilities may vary, however it is still a function of relative mobility, gravity, viscous forces and permeability differences.
-All these parameters are represented under one term in the global mass balance equation.}
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
 %, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
+%A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
 Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
@@
 \medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
+A brief description of the numerical formulation and viscous flow instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
 Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
+Impact of viscosity ratio on the fingers formation is also included in this section.
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\blue{\section{Alternative Introduction}}
-\blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
-
-Numerical investigation of multiphase flows in porous media have attracted the attention of the scientific community over the past 40 years.
-Characterisation of such fluid flows serves as the foundation of reservoir engineering and groundwater studies \citep{white_1981}.
-%More recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
-Description of physics and mechanisms of multiphase porous media flows were reported by %\citet{wooding_1969} 
-\citet{wooding_1976} with focus on capillary pressure and flow regimes.
-A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
-Flow instabilities can be classified as macroscopic and microscopic, the former is due to imposed boundary conditions, whereas the later is associated to local phenomena at the fluids interface \citep[\eg Kelvin-Helmholtz and Saffman-Taylor instabilities,][]{saffman_1959}.
-This work focuses on flow instabilities in two-phase systems due to viscous and stress forces by neglecting gravitational effects (often referred as viscous instabilities or viscous fingering).
-%Section \ref{section:ViscousInstabilities}).
-
-\medskip
-In oil and gas reservoir exploration, viscous and density instabilities are relatively common during water-injection processes.
-As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (see Fig.\ref{fig:simple_case}).
-Viscous fingering results in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
-This problem associated with water-flooding processes is caused by high-permeability layers and unfavorable mobility ratios.
-Water breakthrough and volumetric sweep efficiency (ratio of volumes between the recovered and the injected fluids) are the main determinants of the productive life of a reservoir \citep{riaz_2004, tavassoli_2015}.
-During immiscible CO$_{2}$-flooding $\left(\text{\ie in CO}_{2}\text{ enhanced oil recovery, CO}_{2}\text{-EOR, processes}\right)$, viscosity of supercritical CO$_{2}$ is lower than crude oil, thus viscous fingering and/or channelling may occur.
-
-\medskip
-\textit{Viscous instabilities} can be found across several disciplines and scales and are mainly controlled by the mobility ratio (MR)(see eq.\ref{eq:MR}) between displacing and displaced fluids.
-Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
-\citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
-
-\begin{equation}
-N_{c} = \frac{\mu U}{\gamma}.
-\label{eq:capillary_number}
-\end{equation}
-
-\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
-This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
-
-\medskip
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
-The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
-In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
-
-\begin{equation} 
-\Delta P= - \gamma \nabla\cdot\hat{n}. 
-\label{eq:pressure_dif} 
-\end{equation}
-
-\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
-
-\medskip
-As demonstrated by \citet{habermann_1960} \citep[see also][]{budek_2017}, mobility ratio (MR) is a key-parameter to assess fluid displacement and is defined as the ratio of mobility of the displacing (fluid $i$) to that of the displaced fluid ($j$),
-
-\begin{equation}
- \text{MR} \; = \frac{\mathcal{K}_{ri} \mu_{j}}{\mathcal{K}_{rj} \mu_{i}}. 
-\label{eq:MR}
-\end{equation}
-
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
-
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-
-\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
-
-\begin{displaymath}
-    \text{VR} = \frc{\mu_{i}}{\mu_{j}},
-\end{displaymath}
-
-\noindent that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
-
-\medskip
-In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-%At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
-Out of these finger shape formation there are always a few dominant fingers that spread and shield the growth of other fingers.
-The interface of the main finger collapses and starts splitting into new lobes of fingers.
-One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width while the saturation %concentration gradient
-of its front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
-Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
-
-\medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum (extended Darcy's law) conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success.
-However, they are often limited to relatively simple geometries representing idealised geological formations through structured quadrilateral (2-D) and hexahedral (3-D) grid cells~\citep{mlacnik_2004, king_1999}.
-Additionally, FDM schemes often result in excessive numerical dispersion when strong heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}.
-
-\medskip
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been widely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
-Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected onto the CV space) are applied across the CVs at these interfaces.
-%These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields).
-In order to overcome any potential numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}.
-
-\medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} (see also \citet{jackson_2015,salinas2015}), is used to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure.
-A sketch of the \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions.
-Scalar fields are stored in CV space (Fig.~\ref{fig:fem_elem}).
-
-\medskip
-A brief description of the numerical formulation and viscous fluid instabilities are introduced in Sections~\ref{equations_scheme} and~\ref{section:ViscousInstabilities}, respectively.
-Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of mobility ratio on the fingers formation is also included in this section.
-Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.
-
-\medskip
-\blue{- - - - - - - - - - - - - - - - - - - - - - - - - - - -}
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%
+%%% SECTION
+%%%
 \section{Model Formulation}\label{equations_scheme}
-%Multiphase flow in porous media is described by mass conversation and Darcy equations for all the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
-Different domains will produce different flow instabilities.
-In this paper, the test-cases are based on the discontinuous Galerkin (DG) method.
-DG-methods combine advantages of classical finite volume and finite element methods.
-
-%\subsection{Numerical Formulation}
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Flows in porous media are expressed by the Darcy's law and the saturation equation.
-At this stage the control volume finite element method is used (CVFEM).
-Darcy's law for immiscible multi-phase flow may be written in the form:
-%\begin{equation}\label{e:darcy_eq}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%Substituting the saturation-weighted Darcy velocity by $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_bal}
-%\end{equation}
-%where ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-The force per unit volume $\mathbf{v}_\alpha$, defined as ${\underline {\underline \sigma}}_{\alpha} \mathbf{u}_\alpha$, is used as a prognostic variable in this approach \citep{pavlidis_2014}.
-
-%\noindent In matrix form, Eq.~\ref{e:force_bal} is: %~\ref{force-semi-disc} is: 
-%\begin{equation}
-%  {\mathbf M} \underline {\mathbf v} = -{\mathbf C} \underline{\mathbf p} + \underline {\mathbf s}_{u}, \label{force-balance-matrix-form}
-%\end{equation}
-%where $\underline{\bf v}$ and $\underline{\bf p}$ solution-vectors (also known as shape functions) are defined as:
-%\begin{eqnarray}
-%    &&\underline{{\bf v}} = \left( \left( {v_x},{v_y},{v_z} \right)_{1,1}, \left( {v_x},{v_y},{v_z} \right)  _{2,1},\ldots, \left( {v_x},{v_y},{v_z} \right)_{\mathcal{N}_\alpha,\mathcal{N}_u} \right)^{T} \;\text{and} \nonumber \\
-%    && \underline{{\bf p}} = \left(p_1, p_2, p_3, \cdots, p_{\mathcal{N}_p}\right)^T. \nonumber% \nonumber
-%\label{v_and_p}
-%\end{eqnarray}
-
-%The saturations are computed in CV space, whereas the permeability tensor $\left(\mathbf{K}\right)$ is assumed piece-wise constant in FE space.
-Thus the viscous-friction damping tensor $ {\underline {\underline \sigma}}_{\alpha}$ is piece-wise constant within the sub-control volumes defined through intersections between the elements and control volumes.
-%Introducing a saturation-weighted Darcy velocity defined as $\mathbf{u}_\alpha= \mathbf{q}_\alpha/S_\alpha$, then Eqn.~\ref{e:darcy_eq} may be rewritten as:
-%\begin{equation}
-%  \mathbf{v}_\alpha={\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p_{\alpha} + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:force_balance}
-%\end{equation}
-
-%\noindent The ${\underline {\underline \sigma}}_{\alpha}=\mu_\alpha S_\alpha \left(\mathcal{K}_{{r}_\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces.
-Assuming a porous media domain $\Omega\subset\mathcal{R}^{n}$ ($n$ is the number of dimensions).
-%\end{comment}
-
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions.
-In addition, we neglect the effects of capillarity and gravity in our simulations.
-Therefore the governing equations of conservation of mass and Darcy's law can be described below as,
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\mathbf{K}}{\mu_{\alpha}}\left(\nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%\label{e:darcy_eq}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity, $\mathbf{K}$ is the absolute permeability tensor of the porous medium, $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-
-%\begin{equation}
-%  \mathbf{q}_{\alpha} = -\frac{\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)\mathbf{K}}{\mu_{\alpha}}\left( \nabla p_{\alpha} - {\mathbf{s}_{u}}_{\alpha} \right),
-%S_{k}\left(\lambda_{k}\mathcal{K}\right)^{-1}\phi v_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\bf u}_{\alpha} = -\nabla p + \mathcal{S}_{u},
-%\label{E:darcy_eqn}
-%\end{equation}
-%where $\mathbf{q}_{\alpha}$ is the $k\left(\in\left\{1,N_{p}\right\}\right)$-phase Darcy flow rate.
-$S$, $\mathbf{K}$, $\mathcal{K}_{r\alpha}\left(S_{\alpha}\right)$ and $\mu$ are saturation, absolute permeability tensor, phase relative permeability and viscosity, respectively.
-$s_{u}$ is a source term (e.g., gravity force) associated with the force balance and $p$ is the pressure.
-
-% Defining the advective velocity averaged over the entire domain -- $\mathbf{u}_{\alpha}= \mathbf{q}_{\alpha}/S_{\alpha}$, then we may rewrite Eq.(\ref{E:darcy_ext}),
-%\begin{equation}
-%  {\underline {\underline \sigma}}_{\alpha} \mathbf{u}_{\alpha} = - \nabla p + {\mathbf{s}_{u}}_{\alpha},
-%  \label{e:darcy_ext}
-%\end{equation}
-%$\underline{\underline{\sigma}}_{\alpha}=\mu_{\alpha}S_{\alpha}\left(\mathcal{K}_{r\alpha}\mathbf{K}\right)^{-1}$ represents the implicit linearisation of the viscous frictional forces, and is piecewise constant within each FE and is obtained via basis functions local to each CV within each element \citep{Jackson13,Radunz14}.
-%\end{comment}
-%%%%%%%%%%%%%%%
 
@@
 \begin{eqnarray}
-\left(\displaystyle\frac{\mu_{\alpha}S_{\alpha}}{{\mathbf K}\mathcal{K}_{r\alpha}}\right) {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha}\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
-\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha}\hspace{1cm} \text{ with } x_{i}\in\Omega,\; t>0,\label{eqn:saturation_eqn}
+&& \mu_{\alpha}S_{\alpha}\left({\mathbf K}\mathcal{K}_{r\alpha}\right)^{-1} {\mathbf u}_{\alpha} = \underline{\underline{\sigma}}_{\alpha} {\mathbf u}_{\alpha} = -\nabla p + \mathcal{S}_{u,\alpha},\hspace{1cm} \label{eqn:darcy_eqn} \\ %\text{ with } x_{i}\in\Omega,\; t>0, \label{eqn:darcy_eqn} \\
+&&\phi\displaystyle\frac{\partial S_{\alpha} }{\partial t} +   \nabla \cdot \left( {\mathbf u}_{\alpha}  S_{\alpha}\right) =  \mathcal{S}_{cty,\alpha},\label{eqn:saturation_eqn}
 \end{eqnarray} 
-
-\noindent respectively, where $\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
-$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase and $\mathcal{K}_{r,\alpha}$ is the relative permeability.
-$\mathcal{S}_{u, \alpha}$ is the source term
-which may include gravity and/or capillarity and is related with momentum while the $\mathcal{S}_{cty,\alpha}$ is the source term related with mass (continuity equation).
-$S_{u, \alpha}$ is the source term for momentum while the saturation of the $\alpha$-phase with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
+with $x_{i}\in\Omega,\; t>0$.
+$\mu$, ${\bf K}$, $p$ and $\phi$ are viscosity, absolute permeability, pressure and porosity, respectively.
+$\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase.
+$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase related to the momentum (\eg gravity, capillarity etc) and continuity (\eg geochemical reactions etc) equations, respectively.
+Finally, $\mathcal{K}_{r,\alpha}$ is the relative permeability, and $S_{\alpha}$ is the  $\alpha$-phase saturation with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
 $\underline{\underline{\sigma}}_{\alpha}$ is an absorption-like term that represents the implicit linearisation of the viscous frictional forces.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment} 
 \section{Brief Summary of Viscous Instabilities}\label{section:ViscousInstabilities}
-The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
+%The study of viscous flow instabilities (\ie fingering) is particularly important in oil exploration due to heterogeneities (\ie natural fractures, permeability and/or porosity characteristics in different zones) of geological formations.
 A major problem associated with water-flooding processes is the early water-breakthrough caused by high-permeability layers and unfavorable mobility ratios.
@@
 
-\medskip
-The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}). 
-%Flow instabilities will occur due to: pressure gradient along the interface of fluids; stress forces acting in opposite directions; mobility differences that may exceed critical limits and; heterogeneities of the domain (layering).
+%\medskip
+%The efficiency of fluid displacement depends upon the ratio of viscous and capillary forces (or capillary number, $N_{c}$, Eqn.~\ref{eq:capillary_number}).
 When viscous force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and fingers start to form.
 
-\medskip
-Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
+%\medskip
+%Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids.
 \citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
-\begin{equation}
-N_{c} = \frac{\mu U}{\gamma}.
-\label{eq:capillary_number}
-\end{equation}
+%\begin{equation}
+%N_{c} = \frac{\mu U}{\gamma}.
+%\label{eq:capillary_number}
+%\end{equation}
 
-\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
+%\noindent In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface.
 This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.
 
-\medskip
-More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
+%\medskip
+%More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
 For a Hele-Shaw cell of a given size, flow development depends only on the capillary number.
@@
 
-\medskip
- Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}.
-During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations at the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as \textit{fingers}.
-In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
+%\medskip
+Viscous flow instabilities are relatively common in waterflooding for heavy oil reservoirs, resulting in inefficient flow sweeping which can bypass significant quantities of recoverable oil.
+This may also lead to early breakthrough of water in neighbour production wells.
+
+%, leading inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+%In hydrocarbon reservoir exploration, viscous %and density 
+%instabilities are relatively common in waterflooding processes.
+%As water and oil interacts, the interface between these fluids moves creating an uneven or fingered flow profile (\ie collapse of the interface between fluids, Fig.~\ref{fig:simple_case}).
+%Viscous instabilities result in inefficient flow sweeping which can bypass significant quantities of recoverable oil and may lead to early breakthrough of water into neighbour production wells.
+%Viscous instabilities are mainly controlled by the mobility ratio (MR) between displacing and displaced fluids.
+Other conditions that may also influence the severity of viscous fingering are: heterogeneity (\ie wide spatial porosity and/or permeability distribution), gravitational forces, anisotropic dispersion, non-monotonic viscosity profile etc \citep{budek_2017,nicolaides_2015}.
+ Under the assumption that fluids remain immiscible along the interface, surface tension plays an important role in determining shape and progress of the fingers~\citep{howison_2000}.
+During the displacement of a fluid by a less viscous one, the expected uniform front \citep{buckley_1942,sheldon_1959} is perturbed leading to an uneven front with elongations at the outside edge of the fluid interface.
+%In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface.
 The interface becomes unstable and collapses, taking a curved shape \citep{homsy_1987, jackson_2017}.
-
-\medskip 
+In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
+As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
+%At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
+Out of these finger shape formation there are always a few dominant fingers that spread and shield the growth of other fingers.
+The interface of the main finger collapses and starts splitting into new lobes of fingers.
+One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
+In the process, the finger reaches a critical width while the saturation gradient at the front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splitting again, and the pattern repeats.
+Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
 In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
-The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
-Pressure differences acting on the interface produces a net pressure force,
-\begin{equation} 
-\Delta P= - \gamma \nabla\cdot\hat{n}. 
-\label{eq:pressure_dif} 
-\end{equation}
-
-\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
+%The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.
+%Pressure differences acting on the interface produces a net pressure force,
+%\begin{equation} 
+%\Delta P= - \gamma \nabla\cdot\hat{n}. 
+%\label{eq:pressure_dif} 
+%\end{equation}
+%\noindent This expression is also know as the Young-Laplace equation, a relation describing the capillary pressure across the interface between two fluids, with $\Delta P$ denoting the pressure difference and $\hat{n}$ is the unit normal vector out of the surface.
 
@@
 \noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases.
+$S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
 Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
@@
 $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-The MR contains the phase saturation (see Eqns.~\ref{eq:MR}-\ref{Eqn:CoreyBrooks2}) while it is clear that during fluid displacement phase saturation, $S_{w}\left(x_{i},t\right)$ and $S_{nw}\left(x_{i},t\right)$, will change in time and space (Eqn.~\ref{eqn:saturation_eqn}).
-Therefore, with no lack of generality, the MR can be reduced to the viscosity ratio (VR),
 
+The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the saturation equation (Eqn.~\ref{eqn:saturation_eqn}).
+Assuming that phase viscosities remain invariant throughout the simulated fluid displacement, in this work, with no lack of generality, the MR can be replaced by the viscosity ratio (VR),
 \begin{displaymath} 
@@
 \end{displaymath}
-
-\noindent that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ fields.
-
-\medskip
-In immiscible displacements, viscous fingering occurs when the viscosity ratio is greater than unity.
-As surface tension becomes weak, the interface is stressed and becomes unstable leading to the formation of fingers.
-%At this point it should be mentioned that there are two parameters -- Peclet number (Pe) and mobility ratio (MR), that determine the flow stability characteristics.
-Out of these finger shape formation there are always a few dominant fingers that spread and shield the growth of other fingers.
-The interface of the main finger collapses and starts splitting into new lobes of fingers.
-One of these new fingers may eventually outgrow the others and then spreads to occupy an increasingly larger width.
-In the process, the finger reaches a critical width while the saturation %concentration gradient
-of its front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splits again, and the pattern repeats itself.
-Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
+that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ variables.
 
@@
 
-%%%%%%%%%%%%%%%
-%\begin{comment}
-%Important parameter is the mobility (or viscosity) ratio. This is given by Eq.~\ref{eq:mobility-of-fluid} where $K$ is absolute permeability and $k_{r}$ is relative permeability :
-
-%\begin{equation}
-%\lambda = \frac{K\;k_{\alpha}}{\mu}
-%\label{eq:mobility-of-fluid}
-%\end{equation}
-
-%\noindent Regarding the mechanics, lets assume a porous medium, characterized by a constant permeability $K$.
-The flow will typically involve the displacement of a fluid of viscosity $\mu_1$  and density $\rho_1$ by a second of viscosity $\mu_2$ and density $\rho_2$.
-Under suitable continuum assumptions, Darcy's law, is used to describe the flow through a porous medium.
-
-%\begin{equation}
-%U = \frac{b^2}{12 \mu} \nabla p
-%\end{equation}
-
-%and the above equation can be re-arranged for 1D steady flow as,
-
-%\begin{equation}
-%\frac{dp}{dx}= - \frac{\mu U}{K} + \rho g
-%\label{eq:pressure_dif} 
-%\end{equation}
-
-%where, \textit{U}, is the velocity of the more viscous fluid, \textit{b}, is the cell gap (referring to Hele-Shaw cell) and \textit{$\nabla p$} is the pressure gradient.
-Now consider a sharp interface or zone where density, viscosity, and solute concentration all change rapidly.
-Then the pressure force $(\rho_2-\rho_1)$ on the displaced fluid as a result of a virtual displacement $\delta_x$ of the interface from its simple convected location is
-
-%\begin{equation}
-%\delta\rho=(\rho_2-\rho_1)=[[\frac{(\mu_1-\mu_2)U}{\kappa}]+(\rho_2-\rho_1)g] \delta\chi
-%\end{equation}
-
-%If the net pressure force is positive, then any small displacement will amplify, leading to an instability.In this case gravity is a stabilizing force while viscosity is destabilizing leading to critical velocity $U_c$ above which there is an instability.
-
-%\begin{equation}
-%U_c = \frac{(\rho_1-\rho_2) \cdot g \cdot K}{(\mu_1-\mu_2)}
-%\end{equation}
-%\end{comment}
-%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%\pagebreak
-%\clearpage
-
-%\listoftables 
-%\pagebreak
-%\input{Manuscript_Table}
-
-%\pagebreak
-%\clearpage
-\end{comment}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%
 \section{Results}\label{section:results}
@@
 \medskip
-In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}).
+In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2}, \PN[1]{1} (Fig.~\ref{fig:fem_elem}, Sections~\ref{section:results_initial_model_validation}-\ref{section:results_hete_fix_adapt}) and \PNDG[1]{1} (Section~\ref{section:results_3D})  FE-pairs.
 An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
@@
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.
-Fluids are assumed incompressible and gravity was neglected.
+Fluids are assumed incompressible, also gravity and capillary pressure were neglected.
 Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
@@
 Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
-No normal flux boundary conditions are implied across the upper and lower borders.
+Boundary conditions also include no-flux across upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The spatial permeability distribution creates a rough pressure field, \ie pressure gradient is discontinuous across the interface between different permeability zones, therefore the fluid flows to the larger permeability region.
+The discontinuous spatial permeability distribution (across the regions) leads to preferential flow through more permeable regions $\left(\text{\ie through K}_{1}\right)$.
 %Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.

### 2018-07-06 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 }}     
-\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
 The domain is discretised with $5960$ \PN[1]{2} elements.
@@
 %}     
-\caption{Impact of mesh resolution on capturing flow instabilities: (a) sketch of the computational domain (dimensions in cm); (b) permeability $\left(\text{cm}^{2}\right)$, and; (c) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
+\caption{Impact of mesh resolution on capturing flow instabilities: (a) sketch of the computational domain (dimensions in unit-length); (b) permeability, and; (c) initial saturation and  mesh resolution used in the simulations performed in Section~\ref{section:results_hete_fix_adapt}.
 There are 13068 \PN[1]{2} element-pairs in the domain.}
@@
             %\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00 \hspace{4cm} (f) t= 0.35}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D100b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D700b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10 \hspace{4cm} (g) t= 0.70}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D150b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1000b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15 \hspace{4cm} (h) t= 1.00}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D200b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D1500b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20 \hspace{4cm} (i) t= 1.50}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D350b.pdf}}
       %\hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_D250b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
 \label{fig:5regions_fixedmesh}
@@
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D350b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00s \hspace{4cm} (f) t= 0.35s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(a) t=0.00 \hspace{4cm} (f) t= 0.35}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D100b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D700b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10s \hspace{4cm} (g) t= 0.70s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(b) t=0.10 \hspace{4cm} (g) t= 0.70}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D150b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1000b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15s \hspace{4cm} (h) t= 1.00s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(c) t=0.15 \hspace{4cm} (h) t= 1.00}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D200b.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D1500b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20s \hspace{4cm} (i) t= 1.50s}\vspace{-.1cm}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(d) t=0.20 \hspace{4cm} (i) t= 1.50}\vspace{-.1cm}
       \hbox{\includegraphics[width=.45\textwidth]{./Pics1/Section4_4/5r_po_left_inlet_adapt_D250b.pdf}}
-      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25s}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 seconds of numerical simulation performed with adaptive mesh and {\it VR}=10.}
+      \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25}\vspace{-.1cm}}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with adaptive mesh and {\it VR}=10.}
 \label{fig:5regions_adaptmesh}
@@
       \vspace{-0.cm}\hbox{\hspace{4.5cm}(c) Zoom on region {\it B}  }\vspace{-0.cm}}
-\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20 s) in two regions of the computational domain, {\it A} and {\it B}.
+\caption{Impact of mesh resolution on flow instabilities: capturing formation and growth of flow instabilities at fluid interfaces (t = 0.20) in two regions of the computational domain, {\it A} and {\it B}.
 Simulations were conducted with fixed (left-hand side) and adaptive meshes.

### 2018-07-07 Papers/ViscousInstabilities/article_figure1.tex
update

@@
 \begin{figure}[h]
-\centering
-\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of \PN[1]{2} element pairs used in this work.
-Shaded areas denote control volumes across two contiguous elements.
-Blue and white circles represent pressure and velocity nodes, respectively.}
-\label{fig:fem_cv}
+\vbox{\vspace{0.cm}
+\hbox{\hspace{2cm}
+\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{5cm}(a)}
+\vspace{0.5cm}
+\hbox{\hspace{1cm}
+\includegraphics[width=.75\textwidth]{./Pics/element_n_2b.pdf}}
+\vspace{0.cm}
+\hbox{\hspace{3.5cm}(b)\hspace{3cm}(c)}}
+%\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
+\caption{2D representation of \PN[n]{m} element-pairs used in this work: (a) set of \PN[1]{2} FE with shaded areas as control volumes across two contiguous elements (blue and white circles represent pressure and velocity nodes, respectively); Detailed (b) \PN[1]{2} and (c) \PN[1]{1} element-pairs.}
+\label{fig:fem_elem}
 \end{figure}
@@
 %%%%
-\begin{figure}[h]
-\centering
+%\begin{figure}[h]
+%\centering
 %\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
-\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
-\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
+%\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
+%\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively.
 Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
-\label{fig:fem_elem}
-\end{figure}
-\clearpage
+%\label{fig:fem_elem}
+%\end{figure}
+%\clearpage
 

### 2018-07-07 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex

--- 2015-08-14 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex
@@
 
-\begin{enumerate}[(a)]
+%\begin{enumerate}[(a)]
 %
-\item {\bf University of Aberdeen (UoA), School of Engineering - Environmental and Industrial Fluid Mechanics Group (EnIFluG)\footnote{\href{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}}:} The Group specialises in combined computational methods, laboratory experimentation, and field work on permeable/porous media flows, sediment transport, coastal monitoring, turbulent buoyant jets and large-scale environmental flows.
+%\item 
+{\bf University of Aberdeen (UoA), School of Engineering - Environmental and Industrial Fluid Mechanics Group (EnIFluG)\footnote{\href{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}}:} The Group specialises in combined computational methods, laboratory experimentation, and field work on permeable/porous media flows, sediment transport, coastal monitoring, turbulent buoyant jets and large-scale environmental flows.
 The Group has outstanding experimental facilities, including a range of large water.
@@
 \\
+
+\medskip
 {\bf Dr Jefferson Gomes (JG)} leads the development of the computational multi-physics models within Fluidity.
-He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.
+He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.\\
+
+\medskip
+{\bf Dr Yukie Tanino (YT)} research combines theory and laboratory experiment to model flow and mass transport in obstructed and/or confined systems, including geological reservoirs, inclined pipes, and artificial wetlands for wastewater treatment.
+She manages the recently established petroleum engineering laboratory in the School.\\
+
+\medskip
+{\bf Dr XXXXXX (XX)} ...
 
 %
-\item {\bf Imperial College London (IC), Department of Earth Science and Engineering – Applied Modelling and Computation Group (AMCG)\footnote{\href{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}}:} The Group is is a multi-disciplinary team of 60 scientists and engineers with backgrounds in engineering, mathematics, physics, earth and computational sciences.
+%\item {\bf Imperial College London (IC), Department of Earth Science and Engineering – Applied Modelling and Computation Group (AMCG)\footnote{\href{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}}:} The Group is is a multi-disciplinary team of 60 scientists and engineers with backgrounds in engineering, mathematics, physics, earth and computational sciences.
 It specialises in the development of world-class numerical methods for modelling multi-scale multi-physical processes, with application to fracture and fragmentation, porous media and turbulent flows, nuclear criticality safety, industrial and environmental flows, ocean modelling, impact cratering and air pollution.
 \\
-{\bf Prof.
+%{\bf Prof.
 Christopher C.
@@
 %
-\end{enumerate}
+%\end{enumerate}
 
@@
 
-The main objectives of this proposal are:
-\begin{enumerate}[(i)]
+The main objectives of this proposal are \red{(big picture here ...)}: 
+\begin{enumerate}[(a)]
 %
@@
 %
-   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
+%   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
 %
-   \item Model quality assurance
+   \item Model quality assurance (monitoring $\&$ verification for risk assessment and environmental impact).
 %
 \end{enumerate}
+
+{\bf The novelty of this project is in addressing in an integrated way: detailed multiphase flow transport modelling under reservoir conditions (\CO plume migration $\&$ leakage); changes on petrophysical properties (permeability/porosity spatial- and time-variability); solid-fluid interactions (integrity of repositories); and monitoring $\&$ verification technologies.} \red{add here science question(s) we want to address and the relevance to both applications and the call itself!.}
+
+\medskip
+We shall consider two integrated length-scales in the CCUS problem: 
+\begin{enumerate}[(a)]
+  \item \red{flow mechanisms and structures in pore-scale} -- {\bf YT};
+  \item flow detachment in field-scale \blue{(develop this as a backbone for phase change (multi-physics) and flow instability)} -- {\bf JG}.
+\end{enumerate}
+
+%%%
+%%% SUBSECTION
+%%%
+\subsection{Programme and Methodology}
+
+\begin{description}%[{WP.}1]
+%
+\item[WP-1 Investigation of \CO Plume Dynamics: Migration and in Porous Media:] \red{Topics that may be covered here - JG}
+%
+\begin{enumerate}[{WP-1.}1]
+%
+\item Extend current multi-component and multiphase model formulations for:
+\begin{enumerate}
+ \item parametrised chemical reactions and phase change to take into account `simple' precipitation, dissolution and exsolution processes;
+ \item non-isothermal process
+\end{enumerate}
+%
+\item Include time- and spatial-variability of porosity and permeability
+%
+\item Large-scale simulations (parallel)
+%
+\end{enumerate}
+
+%
+\item[WP-2 Monitoring $\&$ Verification for Risk Assessment and Environmental Impact] bla
+%
+\begin{enumerate}[{WP-2.}1]
+%
+\item Model and software quality assurance
+%
+\item \blue{anything here from lab ??}
+%
+\item \blue{Field validation?}
+%
+\end{enumerate}
+%
+\item[WP-3 YT] bla
+%
+\end{description}
 

### 2018-07-08 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update
updates

@@
 This experimental apparatus enabled instabilities to be qualitatively investigated by simplifying the flow (in both porous and non-porous media) into a 2D problem.
+\citet{mclean_1981} developed a semi-analytic solution for flows in Hele-Shaw cells which were later used by \citet{guan_2003} to investigate fingers' formation, dimensions and branchiness.
 
-More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem).
-For a Hele-Shaw cell of a given size, flow development depends only on the capillary number, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} determined that the flow develops into a single steady-state finger which moves through the cell with constant velocity.
-%Dynamic adaptive mesh was used by \citet{mostaghimi_2016} to capture viscous flow instabilities at oil-water interfaces (waterflooding) in heavy oil reservoirs.
+More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells.
+For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959} \citep[see also][]{homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
 
@@
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-A hybrid family of \PN[n]{m} and \PNDG[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure variables.
 
 Thus, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media through a novel computational multi-fluid dynamics model (embedded in the next-generation flow simulator Fluidity/IC-FERST software).
-The two main aspects of this work are: (a) qualitative and quantitative validation of the model (Section~\ref{section:results_homo_hete}) for viscous flow instabilities and, (b) impact of mesh resolution on capturing the onset of viscous fingers formation.
+The two main aspects of this work are: (a) qualitative and quantitative validation of the model (Section~\ref{section:results_homo_hete}) for viscous flow instabilities and, (b) impact of mesh resolution on capturing the onset formation and growth of viscous fingers (Section~\ref{section:results_hete_fix_adapt}).
 
@@
 Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
-In heterogeneous domains, such instability may be triggered by permeability differences across regions as demonstrated in Section~\ref{section:results_homo_hete}.
+In heterogeneous domains, such instability may be triggered by permeability differences across regions as shown in Section~\ref{section:results_homo_hete}.
 %The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger is.

### 2018-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 See][for more details on the flux-limiting scheme within the model]{gomes_book_2012}.
-Simulations performed for this work were conducted using three types of elements: \PN[1]{1}, \PN[1]{2} and \PNDG[1]{1} (Section~\ref{section:results_3D}).
+Simulations performed for this work were conducted using three types of elements: \PN[1]{1}, \PN[1]{2} (Sections~\ref{section:results_homo_hete} and~\ref{section:results_hete_fix_adapt}) and \PNDG[1]{1} (Section~\ref{section:results_3D}).
 
@@
 Wetting phase fluid is driven from the bottom left-hand corner of the domain with velocity of 1 cm.s$^{-1}$ (magnitude).
-No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and a pressure gradient between source and sink regions was initially imposed to the system.
+No-flux boundary conditions were imposed to all borders of the domain except at the top right-hand side corner (named as sink), and pressure gradient between source and sink regions was initially imposed to the system.
+Solution mesh-independence was achieved through comparison of non-wetting phase saturation profiles along a line between source and sink regions (diagonal across the domain) with several mesh resolutions.
+Mesh convergence criterion was a maximum residual of 10$^{-2}$ and it was achieved with approximately 3.5k elements (Fig.~\ref{fig:MeshDependence}).
+Thus, all simulations shown in this Section used mesh with resolution larger than 3546 \PN[1]{2} triangular elements.
 
@@
 The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001}.
-Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014}.
+Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014,mostaghimi_2016}.
 %The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}.
-In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.
+In the simulations shown in this section, mesh grid adapts as a response to oscillations of phase saturations with: (a) minimum value for length of elements of 0.05 unit-length, (b) maximum number of nodes of 5$\times$10$^{4}$, and (c) prescribed interpolation error estimate of 10$^{-2}$.
 

### 2018-07-09 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 %%%%
-\begin{figure}[h]
-\centering
+%\begin{figure}[h]
+%\centering
 %\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_1.pdf}}
-\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_2.pdf}}
-\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
+%\vbox{\includegraphics[width=0.75\textwidth]{./Pics/phase_vol_frac_uni_perm_2.pdf}}
+%\caption{Schematics of formation of flow instabilities during injection of a pure low viscosity fluid (red) into a domain saturated with a second fluid (dark blue).
 The viscocity ratio of the two fluids is VR=$5$.
 In this case, the initially piston shape front collapses leading to the formation of several fingers.}
-\label{fig:simple_case}
-\end{figure}
-\clearpage
+%\label{fig:simple_case}
+%\end{figure}
+%\clearpage
 
@@
 \label{fem_cv_represent_a}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE 
+%%%%
+\begin{figure}[h]
+\begin{center}
+  \includegraphics[width=0.75\textwidth]{./Pics1/Saffman_homogeneous/MeshIndependence.pdf}
+  \caption{Mesh convergence analysis for Hele-Shaw cells flow simulations: non-wetting phase saturation profiles through a center-line across the domain (diagonal) with grid resolution ranging from 1881 to 3546 \PN[1]{2} triangular elements.}
+\end{center}
+\label{fig:MeshDependence}
 \end{figure}

### 2018-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

@@
 More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells.
-For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959} \citep[see also][]{homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
+For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
 

### 2018-07-10 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively.
+\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively (assuming b = 0.1 cm).
 This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
-Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers mostly depends on mobility ratio and capillary number, however heterogeneity of the porous domain may also affect the onset of instabilities.
+Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers mostly depends on mobility and capillary forces, however heterogeneity of the porous domain may also affect the onset of instabilities.
 Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
 %CAUSE --> EFFECT --> FEW TECHS USED  (P3)
-The model used here is based on a novel control volume finite element method (CVFEM) formulation with a family of FE-pairs, \PN[n]{m} specially tailored for Darcean flows.
+The model used here is based on a novel control volume finite element method (CVFEM) formulation with families of FE-pairs, \PN[n]{m} and  \PNDG[n]{m}, specially tailored for Darcean flows.
 Dynamic mesh adaptivity enables capturing fingers development whilst saving computational overheads.
@@
 Numerical simulations demonstrated that the heterogeneity of the domain triggers the early-onset formation of fingers under prescribed viscosity ratio conditions.
-Also, effective numerical capture of growth (in particular, tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
+Also, effective numerical capture of growth (in particular tip-splitting) and coalescence of dendritic finger branching induced by large viscosity ratio largely depends on mesh resolution at the fluids interface.
 

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells.
-For a Hele-Shaw cell of a given size, flow development depends only on the capillary number $\left(\text{N}_{c}\right)$, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
+For a Hele-Shaw cell of a given size, flow development depends only on the capillary number, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
 

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
+Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
-In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}.
+In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are interpolated with CV basis functions~\citep{voller_2009}.
 
-Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties.
+Since geometries are captured by FE, constructed CVs typically extend on each side of the interface which may have different properties.
 Therefore, average values of coupled velocity-pressure variables are applied across the CVs at the interfaces.
@@
 A control-volume distributed (CVD) scheme coupled with mixed FEM (MFEM) was introduced by \citet{edwards_2006}, where flow and rock variables are discretised in CV space whereas pressure and velocity are solved in FEM space.
-CVD flux-limiting scheme was coupled with high-order convection scheme to reduce anisotropic numerical diffusion in flows through semi-impervious barrier (\ie a region of very low permeability).
+CVD flux-limiting scheme was coupled with high-order convection scheme to reduce anisotropic numerical diffusion in flows through semi-impervious barrier  \citep[\ie a region of very low permeability, see also][that solved this particular numerical diffusion problem with the same model used here, originally proposed by \citet{edwards_2006}]{salinas_2018}.
 

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-
 Thus, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media through a novel computational multi-fluid dynamics model (embedded in the next-generation flow simulator Fluidity/IC-FERST software).
@@
 Hybrid basis functions are also used to allow CV-based velocity to be extrapolated across the entire element.
-The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively -- note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
+The extended Darcy equation (Eqn.~\ref{eqn:darcy_eqn}) is discretrised using a FE representation of $\mathbf{v}_{\alpha}=\underline{\underline{\sigma}}_{\alpha}\mathbf{u}_{\alpha}$ and $p$ with FE basis functions $Q_{j}$ and $P_{j}$, respectively.
+Note that $\underline{\underline{\sigma}}_{\alpha}$ lies in both CV and FEM spaces.
 Each component of the weak form of the extended Darcy equation is tested with the $\mathbf{v}_\alpha$ basis function, $Q_{j}$, to obtain:

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 This term vanishes when a continuous formulation is used to discretise the pressure field $\left(\text{with \PN[n]{m} element-pairs}\right)$.
-The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on a computational domain boundary.
+The last term in Eqn.~\ref{force-semi-disc} is used to weakly enforce the pressure level to $p_\text{bc}$ on the computational domain boundary.
 %Finite element basis functions for velocity and pressure fields are introduced in the discretisation of force-balance equation (Eqn.~\ref{eqn:darcy_eqn}).
@@
 The discretised global mass and force balance equations are solved using a multigrid-like approach.
-The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,adam_2016}.
+The numerical formulation is fully described by \citet{gomes_2017} \citep[see also][]{salinas2015,salinas_2018,adam_2016}.
 

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \end{equation}
-MR is a function not only of fluids' viscosity and saturation, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+MR is a function not only of fluids' viscosity, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
 In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 MR is a function not only of fluids' viscosity, but also of the parameterised relative permeability, $\mathcal{K}_{r\alpha}$, which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
-
+In the simulations conducted in Section~\ref{section:results}, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
 \begin{eqnarray}
@@
 \end{eqnarray}
-
-\noindent where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
 $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases.

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the saturation equation (Eqn.~\ref{eqn:saturation_eqn}).
+The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the global mass balance equation.
 Assuming that phase viscosities remain invariant throughout the simulated fluid displacement, in this work, with no lack of generality, the MR can be replaced by the viscosity ratio (VR),
@@
 \end{displaymath}
-that will be used in the parametrisation of the numerical simulations conducted in Section \ref{section:results}.
+which will be used in the parametrisation of the numerical simulations conducted in Section~\ref{section:results}.
 Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ variables.
@@
 The impact of VR (quantitative validation) and heterogeneity on the onset instability and growth of fingers are numerically investigated in Section \ref{section:results_homo_hete}.
-Section \ref{section:results_hete_fix_adapt} demonstrates the importance of an appropriate mesh resolution to adequately capture the initial stages of viscous fingers formation and development.
+Section \ref{section:results_hete_fix_adapt} demonstrates the importance of appropriate mesh resolution to adequately capture the initial stages of viscous fingers formation and development.
 Finally, flow pathway (channelling) is the focus of Section \ref{section:results_3D}.
@@
 \subsection{Model Set-up}\label{section:results_setup} 
-Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{jackson_2013,gomes_2017}.
+Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{gomes_2017,salinas_2018}.
 This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.
 
-\medskip
 In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2}, \PN[1]{1} (Fig.~\ref{fig:fem_elem}, Sections~\ref{section:results_initial_model_validation}-\ref{section:results_hete_fix_adapt}) and \PNDG[1]{1} (Section~\ref{section:results_3D})  FE-pairs.
@@
 
-\medskip
 %A numerical simulation was also performed in modified conditions (see Fig.~\ref{fem_cv_represent_a}) to assess model behaviour under larger {\it VR}=10.
@@
 A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
-During the fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces that drive the flow.
+During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces that drive the flow.
 In this numerical simulation, crossflow is caused by viscous forces, which is commonly named viscous crossflow.
-Figures~\ref{fem_cv_represent_a}(b) and (c) show the continuous displacement of fluid 2 due to the injection of fluid 1.
+Figures~\ref{fem_cv_represent_a}(b) and (c) show continuous displacement of fluid 2 due to the injection of fluid 1.
 They also demonstrate the preferential flow path through high-permeability regions.

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 They also demonstrate the preferential flow path through high-permeability regions.
-Such flow behaviour, represented by the crossflow through the four regions, is in good qualitative agreement with experiments conducted by \citet{dawe_2008}.
+Such flow behaviour, represented by the crossflow through first and fourth quadrant of the domain, is in good qualitative agreement with experiments conducted by \citet{dawe_2008} (see Figs.
+5 and 6 of this reference).
 
@@
 Solution mesh-independence was achieved through comparison of non-wetting phase saturation profiles along a line between source and sink regions (diagonal across the domain) with several mesh resolutions.
-Mesh convergence criterion was a maximum residual of 10$^{-2}$ and it was achieved with approximately 3.5k elements (Fig.~\ref{fig:MeshDependence}).
+Mesh convergence criterion was a maximum residual of 10$^{-2}$ and it was achieved with approximately 3.5k elements (Fig.~\ref{fig:MeshDependenceAnalysis}).
 Thus, all simulations shown in this Section used mesh with resolution larger than 3546 \PN[1]{2} triangular elements.
@@
 \medskip
-Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively.
+Figures~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN150} show fluid displacement in simulations conducted with {\it VR} = $\left\{\text{3, 10, 150}\right\}$, respectively, with homogeneous permeability distribution $\left(\mathbf{K}=\text{10}^{-10}\text{ cm}^{2}\right)$.
 At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed.
@@
 They conducted a sensitivity analysis to investigate fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U_{f}\mu\gamma^{-1}(W/b)^{2}$, where $U_{f}$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$.
-Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through,
+Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region were correlated through,
 \begin{equation}   

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 \end{equation}  
-
-\noindent Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively (assuming b = 0.1 cm).
+Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively (assuming b = 0.1 cm).
 This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
@@
 
-\medskip
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.

### 2018-07-11 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \begin{figure}[h]
-\begin{center}
-  \includegraphics[width=0.75\textwidth]{./Pics1/Saffman_homogeneous/MeshIndependence.pdf}
+  \hbox{\hspace{2cm}
+  \includegraphics[width=0.75\textwidth]{./Pics1/Saffman_homogeneous/MeshIndependence.pdf}}
   \caption{Mesh convergence analysis for Hele-Shaw cells flow simulations: non-wetting phase saturation profiles through a center-line across the domain (diagonal) with grid resolution ranging from 1881 to 3546 \PN[1]{2} triangular elements.}
-\end{center}
-\label{fig:MeshDependence}
+\label{fig:MeshDependenceAnalysis}
 \end{figure}
@@
 \caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $26313$ \PN[1]{2} triangular elements.}
+The domain was discretised with $26313$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN3}
@@
 \caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=10, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of overlapped wetting phase saturation and velocity vectors $\left(\text{in cm.s}^{-1}\right)$ showing flow profile as the simulation evolves.
-The domain contains $26313$ \PN[1]{2} triangular elements.}
+The domain was discretised with $26313$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN10}
@@
 \caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=150, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: snapshots of wetting phase saturation showing flow profile as the simulation evolves.
-The domain contains $26313$ \PN[1]{2} triangular elements.}
+The domain was discretised with $26313$ \PN[1]{2} triangular elements.}
 \label{fig:homoheleshaw_VN150}
@@
 \caption{Simulated flow in a modified Hele-Shaw cell with {\it VR}=10: (a) permeability distribution $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$, {\bf K}$_{2}$=10$^{-10}$, 10$^{-11}\le\mathbf{K}_{3}\le$ 5$\times$10$^{-10}$ and 10$^{-12}\le\mathbf{K}_{4}\le$ 5$\times$10$\left.^{-10}\text{ cm}^{2}\right)$; (b-f) snapshots of saturation profile during 9.77 seconds of simulation.
-The domain contains 26313 \PN[1]{2} element-pairs.}
+The domain was discretised with 26313 \PN[1]{2} element-pairs.}
 \label{fig:HeleShawHeter_VR10}
@@
 Permeability distribution used in this simulation was the same as shown in Fig.~\ref{fig:HeleShawHeter_VR10}a.
-The domain contains 26313 \PN[1]{2} element-pairs.}
+The domain was discretised with 26313 \PN[1]{2} element-pairs.}
 \label{fig:HeleShawHeter_VR150}
@@
 Permeability distribution used in this simulation was the same as shown in Fig.~\ref{fig:HeleShawHeter_VR10}a.
-The domain contains 3734 \PN[1]{2} element-pairs.}
+The domain was discretised with 3734 \PN[1]{2} element-pairs.}
 \label{fig:HeleShawHeter_VR150_coarse}
@@
 Preferential flow pathway can be readily noticed in these frames, mirroring permeability distribution.
-The domain contains 235242 \PNDG[1]{1} elements.}
+The domain was discretised with 235242 \PNDG[1]{1} elements.}
 \label{fig:3DChannel_sat}
@@
 Fingers' formation and growth can be clearly noticed in (b)-(e).
-The domain contains 235242 \PNDG[1]{1} elements.}
+The domain was discretised with 235242 \PNDG[1]{1} elements.}
 \label{fig:3DChannel_Isosurf}

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 Figures~\ref{fig:HeleShawHeter_VR10} and \ref{fig:HeleShawHeter_VR150} show formation of multi-scale elongations with continuous growth and coalescence of dendritic finger branching in simulations performed with viscosity ratio of 10 and 150, respectively.
-In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150) -- Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d, Table~\ref{table:Heleshaw}.
+In both simulations, maximum fingers width of approximately 0.44-0.56 ({\it VR}=10) and 0.24-0.44 cm were found, whereas estimated values (based on Eqn.~\ref{eqn:guaneqn}) were 0.25-4.50 ({\it VR}=10) and 0.88-3.00 cm ({\it VR}=150), Fig.~\ref{fig:homoheleshaw_VN10_VN150} c-d and Table~\ref{table:Heleshaw}.
 Such calculated ranges \citep[\ie theoretical values based on analytic solutions due to][]{mclean_1981} clearly overestimate fingers dimensions as the mathematical formulation (and therefore Eqn.~\ref{eqn:guaneqn}) assumes incompressible flows in homogeneous porous medium, \ie it does not take into account any spatial variability of heterogeneity.
@@
 In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids.
-Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements).
+Figure \ref{fig:HeleShawHeter_VR150_coarse} shows a numerical simulation performed with the same geometry, boundary and initial conditions as the one shown in Fig.~\ref{fig:HeleShawHeter_VR150}, but with noticeable lower resolution (3734 instead of 26313 elements, \ie marginally above the solution mesh-independent resolution of 3.5k elements shown in Fig.~\ref{fig:MeshDependenceAnalysis}).
 As it can be seen, the lower the resolution the more difficult is to capture the fingers formations, growth and branching.

### 2018-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 
-The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001}.
+The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}.
 Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster, and coarser mesh in regions where properties change more slowly \citep{piggott_2006,hiester_2014,mostaghimi_2016}.

### 2018-07-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

@@
 This experimental apparatus enabled instabilities to be qualitatively investigated by simplifying the flow (in both porous and non-porous media) into a 2D problem.
-\citet{mclean_1981} developed a semi-analytic solution for flows in Hele-Shaw cells which were later used by \citet{guan_2003} to investigate fingers' formation, dimensions and branchiness.
+\citet{mclean_1981} developed a semi-analytic solution for flows in Hele-Shaw cells which was later used by \citet{guan_2003} to investigate fingers' formation, dimensions and branchiness.
 
@@
 For a Hele-Shaw cell of a given size, flow development depends only on the capillary number, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
+The impact of viscosity ratio and mass flow-rate on fingering development was experimentally (coreflood and micromodels) studied by \citet{Doorwar_2016}.
+Through numerical (based on pore-network model) experiments, they demonstrated that fingers' dynamics (\ie growth, splitting and coalescence) are also strongly dependent on the domain's aspect-ratio and capillary forces \citep[see][]{Doorwar_2014}, and proposed a new instability dimensionless number to assess breakthrough recovery of a number of experimental data sets.
 

### 2018-07-16 Papers/ViscousInstabilities/article_figure1.tex
updates

@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.71\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
+\hbox{\includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2b.pdf}
+%\hbox{\includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
       \includegraphics[width=.37\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
@@
 \vspace{0.cm}
-\hbox{\hspace{2.5cm} (a) pressure at t=0s \hspace{5.cm} (b) t=0.87s \hspace{2.75cm} (c) t=3.54s}
+\hbox{\hspace{2.5cm} (a) schematics \hspace{3.cm} (b) t=0.87s \hspace{2.75cm} (c) t=3.54s}
 \vspace{0.5cm}
@@
       \includegraphics[width=.38\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
-      \includegraphics[width=.66\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
+      \includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_d5803_endb.pdf}}
+      %\includegraphics[width=.66\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end.pdf}}
 \vspace{0.cm}
@@
 }   
-\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) initial pressure profile $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
+\caption{Simulated flow in a Hele-Shaw cell $\left(\text{{\it VR}=3, {\bf K}=10}^{-10}\text{cm}^{2}\right)$: (a) schematics of the HS cell indicating source and sink regions along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves.
 The domain was discretised with $26313$ \PN[1]{2} triangular elements.}

### 2018-07-16 Papers/ViscousInstabilities/article_figure1.tex
update figures ... just missing Fig2

@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
-\hspace{0.5cm}      
-      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
+%\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c.pdf}
+%\hspace{0.5cm}      
+      %\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c.pdf}}
+\hbox{\includegraphics[width=\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001cbd.pdf}
+      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}}
 \vspace{0.cm}
-\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
+\hbox{\hspace{5.cm} (a) t=3.43s  \hspace{8.cm} (b) t=6.92s}
 \vspace{0.5cm}
-\hbox{
-      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}
+\hbox{\hspace{3cm}
+      %\includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c.pdf}
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c.pdf}
-      \includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c.pdf}}
+      \hspace{4cm}\includegraphics[width=.51\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c.pdf}}
 \vspace{0.cm}
-\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{5.cm} (e)t=10.00s}
+\hbox{ \hspace{5.cm} (c) t=7.61s \hspace{8.cm} (d)t=10.00s}
 \vspace{0.cm}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.8\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300b.pdf}
+%\hbox{\includegraphics[width=.8\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300bcpdf}
+\hbox{\includegraphics[width=.7\textwidth]{./Pics1/Saffman_homogeneous_VR150/ST_Homog_VR150_D300bcd.pdf}
 \hspace{0.5cm}      
@@
       \hbox{\includegraphics[width=.4\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
-            \includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb.pdf} 
+            %\includegraphics[width=.55\textwidth, height=.4\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hb.pdf} 
+            \includegraphics[width=.57\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D200Hbcd.pdf} 
             \includegraphics[width=.42\textwidth]{./Pics1/Saffman_heterogeneous_VR10/ST_Heterog_VR10_D900Hb.pdf} }
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb.pdf} 
+      %\hbox{\includegraphics[width=.65\textwidth, height=.46\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hb.pdf} 
+      \hbox{\includegraphics[width=.65\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D200Hbcd.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Saffman_heterogeneous_VR150/ST_Heterog_VR150_D500Hb.pdf}
@@
   \vbox{\vspace{-.5cm}
-      \hbox{\includegraphics[width=.65\textwidth, height=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_50.pdf} 
+      %\hbox{\includegraphics[width=.65\textwidth, height=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_50.pdf} 
+      \hbox{\includegraphics[width=.65\textwidth]{./Pics1/Saffman_new/ST_Heterog_50bcd.pdf} 
             \includegraphics[width=.45\textwidth]{./Pics1/Saffman_new/ST_Heterog_500.pdf}

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 %CAUSE --> EFFECT --> MOTIVATION (P1)
-  A critical aspect of multiphase flow in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
+  A critical aspect of multiphase flow in porous media is the displacement efficiency, which measures the amount of fluid that can be pushed by another fluid driven by pressure gradient.
 Migration of contaminants and reservoir waterflooding are typical applications where understanding the dynamics of immiscible fluid displacement helps mitigating water resources contamination and improving hydrocarbons production, respectively.
-Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers therefore creating an uneven front with elongation at the outside edge of fluids interface with strong impact on the displacement efficiency.
+Due to large viscosity ratios, flow instabilities at fluids' interface may arise leading to the formation of fingers, \ie uneven fronts with elongation at the outside edge of fluids interface with strong impact on the displacement efficiency.
 %CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
-Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers mostly depends on mobility and capillary forces, however heterogeneity of the porous domain may also affect the onset of instabilities.
+Initial studies of viscous instabilities indicated that the development of fingers mostly depends on mobility and capillary forces, however heterogeneity of the porous domain may also affect the onset of instabilities.
 Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media.
@@
 \section{Introduction}\label{section:intro}
-Numerical investigation of multiphase flows in porous media has attracted the attention of the scientific community over the past 40 years.
-Characterisation and prediction of such flows serve as the foundation of hydrocarbon reservoir and groundwater studies.% \citep{white_1981}.
+Numerical investigation of multiphase Darcy flows has attracted the attention of the porous media community over the past 40 years.
+Characterisation and prediction of such flows are the foundation of groundwater and oil $\&$ gas reservoirs studies.% \citep{white_1981}.
 %Underground coal gasification is another important field of interest and, more recently, due to the role of green house gases (GHG) emissions in the global climate change, several research work have focused on CO$_{2}$ migration and trapping mechanisms in carbon capture utilisation and storage (CCUS) operations \citep{spycher_2003, self_2012, jiang_2011}.
 
-Description of physics and mechanisms of multiphase porous media flows were reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
+Description of physics and mechanisms of multiphase porous media flows was reported by \citet{wooding_1976} with focus on capillary pressure and flow regimes.
 A comprehensive review of force balances at the interface between immiscible fluids and resulting mechanisms for flow instabilities can be found in \citet{homsy_1987}.
@@
 %Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. 
-\citet{muskat_1934} used Hele-Shaw cells (\ie parallel flat plates separated by an infinitesimal gap) to study fluid flow and the impact on the capillary number $\left(\text{N}_{c}\right)$ in the flow dynamics.
+\citet{muskat_1934} used Hele-Shaw cells (\ie parallel flat plates separated by an infinitesimal gap) to study fluid flow and the impact of the capillary number $\left(\text{N}_{c}\right)$ on the flow dynamics.
 %investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
@@
  %In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface. 
-This experimental apparatus enabled instabilities to be qualitatively investigated by simplifying the flow (in both porous and non-porous media) into a 2D problem.
+This experimental apparatus enabled instabilities to be qualitatively investigated by simplifying the flow (in both porous and non-porous media) to a 2D problem.
 \citet{mclean_1981} developed a semi-analytic solution for flows in Hele-Shaw cells which was later used by \citet{guan_2003} to investigate fingers' formation, dimensions and branchiness.
@@
 \medskip 
-Multi-fluid flow dynamics in porous media are described by continuity and momentum conservative equations for each fluid (or phases) with coupling mass terms (\ie density and saturation) appearing in both sets of equations.
-Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators however, they are often limited to relatively simple geometries and often lead to excessive numerical dispersion when strong heterogeneity is present~\citep{chavent_1986}.
+Multi-fluid flow dynamics in porous media are described by continuity and momentum conservative equations for each fluid with coupling terms appearing in both sets of equations.
+Finite difference methods (FDM) have been extensively used in most industry-standard reservoir simulators to solve this set of equations, however they are often limited to relatively simple geometries and often lead to excessive numerical dispersion when strong heterogeneity is present~\citep{chavent_1986}.
 
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-Among FEM-based formulations for porous media flows, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+Among FEM-based formulations for porous media flows, the control volume finite element method~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are interpolated with CV basis functions~\citep{voller_2009}.

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM to solve fluid flow dynamics in complex geometries.
-Among FEM-based formulations for porous media flows, the control volume finite element method~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements.
+Among FEM-based formulations for porous media flows, the control volume finite element method~\citep[CVFEM,][]{fung_1992} was designed to guarantee local mass conservation and high-order numerical accuracy as well as being able to use geometry-conforming elements (\eg triangles, tetrahedra, pyramids etc).
 In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, while material properties and flow conditions (\eg phase saturation, density, temperature, species concentration etc) are interpolated with CV basis functions~\citep{voller_2009}.

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 In order to reduce artificial numerical diffusion associated to the upwind weighting of the advected quantity in regions of strong heterogeneity, a discontinuous hybrid finite element finite volume method (DFEFVM) formulation was introduced by \citet{nick_2011b, nick_2011a}.
-This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
-A control-volume distributed (CVD) scheme coupled with mixed FEM (MFEM) was introduced by \citet{edwards_2006}, where flow and rock variables are discretised in CV space whereas pressure and velocity are solved in FEM space.
-CVD flux-limiting scheme was coupled with high-order convection scheme to reduce anisotropic numerical diffusion in flows through semi-impervious barrier  \citep[\ie a region of very low permeability, see also][that solved this particular numerical diffusion problem with the same model used here, originally proposed by \citet{edwards_2006}]{salinas_2018}.
+This discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials.
+Coupled control-volume distributed (CVD) flux-limiting method and high-order convection schemes were introduced by \citet{edwards_2006} to reduce anisotropic numerical diffusion in flows through semi-impervious barriers (\ie flow across regions of large permeability gradient).
+Solution for such particular numerical diffusion problem was recently revisited by \citet{salinas_2018} using the model formulation outlined in Section~\ref{equations_scheme}.
 

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 For a Hele-Shaw cell of a given size, flow development depends only on the capillary number, therefore if \textit{$N_{c}$} is too high, \citet{saffman_1959b} \citep[see also][]{saffman_1959,homsy_1987,tabeling_1987} demonstrated that the flow develops to a single steady-state finger which moves throughout the cell with constant velocity.
-The impact of viscosity ratio and mass flow-rate on fingering development was experimentally (coreflood and micromodels) studied by \citet{Doorwar_2016}.
-Through numerical (based on pore-network model) experiments, they demonstrated that fingers' dynamics (\ie growth, splitting and coalescence) are also strongly dependent on the domain's aspect-ratio and capillary forces \citep[see][]{Doorwar_2014}, and proposed a new instability dimensionless number to assess breakthrough recovery of a number of experimental data sets.
 
@@
 \medskip 
-In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017} \citep[see also][]{jackson_2015,salinas2015}, is used to simulate viscous flow instabilities in porous media.
-The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring that the force balance is preserved.
-Thus, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media through a novel computational multi-fluid dynamics model (embedded in the next-generation flow simulator Fluidity/IC-FERST software).
+The impact of viscosity ratio and flow rate on fingering development was experimentally investigated (with coreflood and micromodels) by \citet{Doorwar_2016}.
+Through numerical experiments (based on pore-network model), they demonstrated that fingers' dynamics (\ie growth, splitting and coalescence) are also strongly dependent on the domain's aspect-ratio and capillary forces \citep[see][]{Doorwar_2014}, and proposed a new instability dimensionless number to assess breakthrough recovery of an extensive set of experimental data.
+
+Therefore, the main aim of this work is to numerically investigate the onset of viscous instabilities in heterogeneous porous media flows through a novel computational multi-fluid dynamics model~\citep{gomes_2017}.
 The two main aspects of this work are: (a) qualitative and quantitative validation of the model (Section~\ref{section:results_homo_hete}) for viscous flow instabilities and, (b) impact of mesh resolution on capturing the onset formation and growth of viscous fingers (Section~\ref{section:results_hete_fix_adapt}).
@@
 Model set up and results including initial model-benchmark are presented in Section~\ref{section:results}.
-Impact of viscosity ratio on the fingers formation is also included in this section.
 Finally, concluding remarks are presented in Section~\ref{Section:Conclusion}.

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 $\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity of the $\alpha$-phase.
-$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase related to the momentum (\eg gravity, capillarity etc) and continuity (\eg geochemical reactions etc) equations, respectively.
+$\mathcal{S}_{u,\alpha}$ and $\mathcal{S}_{cty,\alpha}$ are source terms of the $\alpha$-phase related to the momentum (\eg gravity, capillarity forces etc) and continuity (\eg mass transfer across fluids/phases, geochemical reactions etc) equations, respectively.
 Finally, $\mathcal{K}_{r,\alpha}$ is the relative permeability, and $S_{\alpha}$ is the  $\alpha$-phase saturation with mass conservation constraints of $\sum\limits_{\alpha=1}^{\mathcal{N}_{p}} S_{\alpha} = 1$, where $\mathcal{N}_{p}$ denotes the number of phases.
@@
 \medskip
-The formulation introduced here is applicable to $\mathcal{N}_{p}$ fluid phases and is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
+The formulation introduced here is based on two families of FE-pairs: \PNDG[n]{m} and \PN[n]{m}~\citep{cotter_2009a}, consistent with the dual pressure-velocity representation in CV space.
 In these families of FE-pairs, velocity is represented by $n^{\text{th}}$-order polynomials that are discontinuous across elements, whereas pressure is represented by $m^{\text{th}}$-order polynomials that may be either continuous or discontinuous (thus the notation \PN[n]{m} and \PNDG[n]{m}, respectively) across elements.
@@
 \medskip
-Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability is assumed piecewise constant in FE space.
+Whilst saturation (and all saturation-dependent material properties such as relative permeability and capillary pressure) is calculated in CV space, absolute permeability ($\mathbf{K}$) is assumed piecewise constant in FE space.
 Saturation equations (Eqn.~\ref{eqn:saturation_eqn}) are discretised in space with CV basis function, $M_{i}$, and with the $\theta$-method in time~\citep{gomes_book_2012}.

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 In the process, the finger reaches a critical width while the saturation gradient at the front becomes steep as a result of stretching caused by the cross-flow, causing the tip of the finger to become unstable and splitting again, and the pattern repeats.
+
 Therefore, surface tension plays an essential dual role, it must be weak enough for the tip front to be unstable, but it is also the physical force causing the spreading and ensuing repeated branching \citep{tan_1988, carvalho_2013}.
@@
 
-The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the global mass balance equation.
+The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the global mass conservation equation.
 Assuming that phase viscosities remain invariant throughout the simulated fluid displacement, in this work, with no lack of generality, the MR can be replaced by the viscosity ratio (VR),
@@
 which will be used in the parametrisation of the numerical simulations conducted in Section~\ref{section:results}.
-Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent prognostic field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$ variables.
+Analysis performed in the following sections will make use of this simplified definition as phase saturation $\left(S_{\alpha}\right)$ is a time- and spatial-dependent field which is calculated along with pressure ($p$) and velocity $\left(\mathbf{u}_{\alpha}\right)$.
 
@@
 In the next section, the numerical formulation used to simulate multi-fluid flow in porous media is briefly validated (Section \ref{section:results_initial_model_validation}) against laboratory experiments (qualitative validation).
-The impact of VR (quantitative validation) and heterogeneity on the onset instability and growth of fingers are numerically investigated in Section \ref{section:results_homo_hete}.
+The impact of VR (quantitative validation) and heterogeneity on the onset of interface instability and growth of fingers are numerically investigated in Section \ref{section:results_homo_hete}.
 Section \ref{section:results_hete_fix_adapt} demonstrates the importance of appropriate mesh resolution to adequately capture the initial stages of viscous fingers formation and development.

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2.
-In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{\circ}\right)$.
+In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(\mathbf{u}_{\alpha}^{\circ}\right)$.
 For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$.

### 2018-07-17 Papers/ViscousInstabilities/article_figure1.tex
Last Revision: small changes to improve readibility

@@
 %\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
-\caption{2D representation of \PN[n]{m} element-pairs used in this work: (a) set of \PN[1]{2} FE with shaded areas as control volumes across two contiguous elements (blue and white circles represent pressure and velocity nodes, respectively); Detailed (b) \PN[1]{2} and (c) \PN[1]{1} element-pairs.}
+\caption{2D representation of \PN[n]{m} element-pairs used in this work: (a) set of \PN[1]{2} FE with shaded areas as control volumes across two contiguous elements (blue and white circles represent pressure and velocity nodes, respectively).
+Detailed (b) \PN[1]{2} and (c) \PN[1]{1} element-pairs.}
 \label{fig:fem_elem}

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 In the simulations conducted in Section~\ref{section:results}, the modified \cite{Brooks_1964} model was used \citep{alpak_1999},
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
+\begin{equation}
+   \begin{cases}
+      \mathcal{K}_{rw}\left(S_{w}\right) = \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, & \\%\label{Eqn:CoreyBrooks1}\\
+                                                                                                                         & \\
+      \mathcal{K}_{rnw}\left(S_{nw}\right) = \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, & \label{Eqn:CoreyBrooks}%\label{Eqn:CoreyBrooks2}
+   \end{cases}
+\end{equation}
 where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
@@
 
-The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqns.~\ref{Eqn:CoreyBrooks1}-\ref{Eqn:CoreyBrooks2}), however it is clear that during fluid displacement they change in time and space according to the global mass conservation equation.
+The MR expression (Eqn.~\ref{eq:MR}) contains phase saturations, $S_{w}\left(x_{i},t\right)$ and  $S_{nw}\left(x_{i},t\right)$ (Eqn.~\ref{Eqn:CoreyBrooks}), however it is clear that during fluid displacement they change in time and space according to the global mass conservation equation.
 Assuming that phase viscosities remain invariant throughout the simulated fluid displacement, in this work, with no lack of generality, the MR can be replaced by the viscosity ratio (VR),
@@
 The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
-Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u=1$.
+Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u_{x}=1$.
 Boundary conditions also include no-flux across upper and lower borders.
 The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
-The discontinuous spatial permeability distribution (across the regions) leads to preferential flow through more permeable regions $\left(\text{\ie through K}_{1}\right)$.
-%Figure \ref{fem_cv_represent_a}(b-c)describe the saturation field at different times.
+
+A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
+During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces in discontinuous spatial permeability distribution.
+Such preferential flows are shown in Figs.~\ref{fem_cv_represent_a}(b-c).
+In this case, the crossflow dynamics through first and fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008} (see Figs.
+5 and 6 of this reference).
 
@@
 Initial and boundary conditions remain the same, and flow behaviour qualitatively agree validated against laboratory experiments conducted by \citet{evans_1994}.
-A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
+%XXXXXXXXXXXXXXXXXXXXX
+%A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
 During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces that drive the flow.

### 2018-07-17 Papers/ViscousInstabilities/article_table.tex
updated
update
update the numbers - not look like a code
updates
Last Revision: small changes to improve readibility

--- 2017-07-07 Papers/ViscousInstabilities/article_table.tex
@@
     \hline
-     \ref{section:results_validation} & 0.2 & 1.0 & 0.0 & 1.0 & 2.5 & 1.0 & N/A & N/A & 0.2 & 0.3 & 1.0 \\
-     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 10.0 & 0.0 & 1.0 & 1.e-10 & N/A & N/A & N/A & 0.2 & 0.3 & 0.5  \\
-     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 1.0 & 0.0 & 1.0 & 1.e-11 -- & 1.e-12 -- & 1.e-12 -- & 1.e-10 & 0.2  & 0.3 & 1.0 \\
-      &   &  &  &  & 5.e-10 & 5.e-10 & 1.e-10  &  &  &  & \\
-     \ref{section:results_hete_fix_adapt}  & 0.2 & 1.0 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & 0.5  \\
-     \ref{section:results_dinlet}  & 0.2 & 1.0 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & 0.5  \\
+     \ref{section:results_initial_model_validation} & 0.2 & 1 & 0.0 & 1.0 & 2.5 & 1.0 & -- & -- & 0.2 & 0.3 & 1.0 \\
+     \ref{section:results_homo_hete}(homogenous)  & 0.2 & 3/10/150 & 0.0 & 1.0 & 1$\times$10$^{-10}$ & -- & -- & -- & 0.2 & 0.3 & 1.0  \\
+     %                                             &     & 150 &     &     &                    &     &     &     &     &     &      \\
+     \ref{section:results_homo_hete}(heterogenous) & 0.2 & 10/150 & 0.0 & 1.0 & 1$\times$10$^{-11} $-- & 1$\times$10$^{-12}$ -- & 1$\times$10$^{-12}$ -- & 1$\times$10$^{-10}$ & 0.2  & 0.3 & 1.0 \\
+      &   &  &  &  & 5$\times$10$^{-10}$ & 5$\times$10$^{-10}$ & 1$\times$10$^{-10}$  &  &  &  & \\
+     \ref{section:results_hete_fix_adapt}  & 0.2 & 10 & 0.0 & 1.0  & 3.0 & 2.0 & 5.0 & 1.0 & 0.2 & 0.3 & 0.5  \\
+     \ref{section:results_3D}  & 0.2 & 150 & 0.0 & 1.0 & 3.0 & 2.0 & 5.0 & 1.0 & 0.2  & 0.3 & 0.5  \\
      \hline
@@
 Superscript $\circ$ denotes initial condition.
-$\mathbf{K}_{i}$ is in $m^{2}$ and $u^{\circ}_{w}$ is in m/sec (units).
-$S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations.
-}
+$\mathbf{K}_{i}$ is in cm$^{2}$ and $u^{\circ}_{w}$ is in cm.s$^{-1}$ (except for Sections~\ref{section:results_initial_model_validation} and \ref{section:results_hete_fix_adapt} with dimensionless units).
+$S_{w,irr}$ and $S_{nw,r}$ are the same for all simulations (Eqn.~\ref{Eqn:CoreyBrooks}).}
 \label{table:setup}

### 2018-07-17 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: small changes to improve readibility

@@
 Such preferential flows are shown in Figs.~\ref{fem_cv_represent_a}(b-c).
-In this case, the crossflow dynamics through first and fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008} (see Figs.
-5 and 6 of this reference).
+In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008} (see Figs.
+5-6 of this reference).
 
@@
 \end{equation}  
-Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively (assuming b = 0.1 cm).
+Here, numerical simulations performed with viscosity ratio of 10 and 150 indicated maximum fingers width of approximately 0.45-0.70 and 0.50-0.90 cm (Fig.~\ref{fig:homoheleshaw_VN10_VN150} a and b), respectively (assuming b = 1 mm).
 This is in close agreement with expected values obtained from Eqn.~\ref{eqn:guaneqn} which indicates maximum finger width ranging from 0.13 to 0.75 (for {\it VR}=10) and from 0.30 to 0.75 ({\it VR}=150, Table~\ref{table:Heleshaw}).
@@
 In order to qualitatively investigate the impact of heterogeneity (here represented by changing in the permeability field), numerical simulations were conducted using a prescribed permeability distribution and viscosity ratios of 10 and 150.
-Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases(Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
+Absolute permeability ranging from 1.0$\times$10$^{-12}$ to 5.0$\times$10$^{-10}$ cm$^{2}$ (\ie 0.1 $\le$ {\bf K} $\le$ 50 milidarcy) was used in the simulations, which were performed with the same geometry,  mesh resolution, boundary and initial conditions as in previous homogeneous cases (Figs.~\ref{fig:homoheleshaw_VN3}-\ref{fig:homoheleshaw_VN10_VN150}b).
 
@@
 \medskip
-Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
+Here, numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics.
 In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced.
-The computational domain, Fig.~\ref{fig:testcase_heter_domain}a-b, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}c) and divided into 5 regions with prescribed synthetic permeability distribution with values between $1$ and $5$.
-A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1}=1$.
+The computational domain, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular geometry fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}c) and divided into 5 regions with prescribed synthetic permeability distribution with values between $1$ and $5$ (Fig.~\ref{fig:testcase_heter_domain}b).
+A no-flux boundary condition was imposed across upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand side face at velocity $u_{1,x}=1$.
 Viscosity ratio was set to 10.
@@
 Both simulations started with a mesh of 13068 triangular (\PN[1]{2}) elements, however as flow dynamics evolve the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements}).
-In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of distinct permeabilities at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
+In both cases, fingers' development (formation, growth and coalescence) and fluid cross flows (through regions of sharp permeability gradient at the top of the domain, $\mathbf{K}=\left\{2,3\right\}$) can be readily noticed.
 The simulation performed with a fixed and relatively fine mesh was able to capture the progressive development of fingers (as shown in Fig.~\ref{fig:5regions_AdaptZoom}b) prompted by sharp permeability gradient at the interface of regions with $\mathbf{K}=\left\{1,5\right\}$.
@@
 
-\medskip
 Simulations were performed in a hexahedron domain of 4 cm $\times$ 2.5 cm $\times$ 10 cm, with permeability distribution of 10$^{-4}\le\mathbf{K}\le$10$^{5}$  milidarcy (Fig.~\ref{fig:3DChannel_PermMesh}).
 The computational domain was designed to naturally capture preferential flow pathways through channels of large absolute permeability.
-Pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$ from the left-hand side face.
+Pure (wetting) fluid is added into the domain with uniform velocity of 0.5 cm.s$^{-1}$ from the left-hand side face.
 No-flux boundary conditions are applied to all borders, except at the inlet (left-hand side) and outflow (right-hand side) faces.
@@
 
-\medskip
 A similar numerical simulation (\ie same geometry, initial mesh resolution, initial and boundary conditions) was also performed using dynamically adaptive mesh.
-During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}a).
-Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_satvel_XYplanes_adapt}b-c and \ref{fig:3DChannel_satvel_XYplanes_adapt}.
+During the simulation, mesh resolution ranged from 235k to 643k \PNDG[1]{1} element-pairs (Fig.~\ref{fig:3DChannel_severalfields_adapt}a).
+Distinct preferable flow pathways and fingers are shown in Fig.~\ref{fig:3DChannel_severalfields_adapt}-\ref{fig:3DChannel_sat_adapt}.
 Saturation of the wetting fluid during the course of the simulation is shown in Fig.~\ref{fig:3DChannel_sat_adapt}.
@@
 
-\medskip
-However, due to low-order accuracy of element-pairs -- \PNDG[1]{1} instead of \PN[1]{2} of previous sections \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,salinas_2018,adam_2016, gomes_2017}, and coarser mesh throughout the computational domain, simulation performed with fixed mesh showed larger smeared fluid saturation.
+Low-order accuracy of \PNDG[1]{1} element-pairs (in comparison with \PN[1]{2} used in previous sections) were used in this set of simulations due to the computational overhead \citep[for full investigation on numerical accuracy associated with these element-pairs, see][]{salinas2015,salinas_2016,salinas_2018,adam_2016, gomes_2017}.
+However, results in this section have shown larger smeared spatial saturation distribution obtained from the fixed mesh simulation indicating numerical diffusion in flows across large permeability gradient.
 
@@
 
-\medskip
+%\medskip
 Simulations involving formation and growth of viscous fingers were conducted with the CVFEM-based multi-fluid flow simulator Fluidity/IC-FERST model.
-The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and a novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
+%The model is based upon a dual consistent pressure-velocity representation in CV and FEM spaces and a novel family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}.
 Saturation and other scalar fields are discretised in CV space and may be fully discontinuous across finite element boundaries.
 In order to strongly enforce discretised Darcy equations at the boundaries between elements and control volumes, a directional-weighted flux-limited was introduced to take into account discontinuities risen from both, numerical formulation (based on discontinuous-Galerkin finite element method, DGFEM) and control volumes within finite elements.
-
-\medskip
+%\medskip
 %(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);
@@
 
-\medskip
+%\medskip
 Determining the early-onset flow instability is critical to accurately simulate formation, growth and coalescence of fingers, and therefore to: (a) predict displacement (sweep) efficiency and (b) design strategies to either mitigate or avoid fingering and preferential flow pathways.
@@
 
-\medskip
+%\medskip
 Investigation of preferential flow pathways was the focus of Section~\ref{section:results_3D}, where 3D numerical simulations of multi-fluid flow through semi-pervious / impervious channelised domain were performed.
@@
 
-\medskip
+%\medskip
 % (3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.

### 2018-07-17 Papers/ViscousInstabilities/article_figure1.tex
Last Revision: small changes to improve readibility

@@
   \includegraphics[width=0.75\textwidth]{./Pics1/Saffman_homogeneous/MeshIndependence.pdf}}
-  \caption{Mesh convergence analysis for Hele-Shaw cells flow simulations: non-wetting phase saturation profiles through a center-line across the domain (diagonal) with grid resolution ranging from 1881 to 3546 \PN[1]{2} triangular elements.}
+  \caption{Mesh convergence analysis for Hele-Shaw cells flow simulations (VR=1): non-wetting phase saturation profiles through a center-line across the domain (diagonal) with grid resolution ranging from 1881 to 3546 \PN[1]{2} triangular elements.
+}
 \label{fig:MeshDependenceAnalysis}
@@
 \caption{Isosurfaces of simulated flows in Hele-Shaw cells with viscosity ratios of 10 (a and c) and 150 (b and d).
-Top and bottom rows describe simulations performed with constant \textit{i.e.
-homogeneous with \textbf{K}}= $10^{-10}$ \textit{${cm}^{2}$} and randomly distributed (i.e.
-heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
+Top and bottom rows describe simulations performed with constant $\left(\text{\ie homogeneous with }\textbf{K}\text{ = 10}^{-10}\text{ cm}^{2}\right)$ and randomly distributed (\ie heterogeneous, Fig.~\ref{fig:HeleShawHeter_VR10}a) permeabilities.
 Width of largest fingers for homogeneous cases are approximately $0.70$ and $0.90$cm (\textit{VR}=$10$ and \textit{VR}=$150$, respectively), whereas for heterogeneous cases are $0.56$ and $0.40$cm.
@@
       \vspace{-.1cm}\hbox{\hspace{2.cm}(e) t=0.25}\vspace{-.1cm}}
-\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with fixed mesh (of 13068 elements) and {\it VR}=10.}
+\caption{Impact of mesh resolution on capturing flow instabilities: snapshots of saturation field through 1.50 unit-time of numerical simulation performed with fixed mesh (i) of 13068 elements and {\it VR}=10.}
 \label{fig:5regions_fixedmesh}
@@
       \hbox{\includegraphics[width=\textwidth]{./Pics1/3D_Channel/Test_SlowNew_MeshPermeability.pdf} }}
-\caption{3D channel flow: Permeability distribution within the computational domain, containing 235242 \PNDG[1]{1} element-pairs.}
+\caption{3D channel flow: Permeability distribution within the computational domain, containing 235242 \PNDG[1]{1} tetrahedra element-pairs.}
 \label{fig:3DChannel_PermMesh}

### 2018-07-31 Papers/ViscousInstabilities/article_figure1.tex
updates: adding figures for the qualitative validation -- Section 4.2 ... text to come ...

@@
 %%%%
+%\begin{figure}[ht] 
+%\vbox{
+%\hbox{\hspace{-0.3cm}
+%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
+%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{1.5cm}
+%\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{4.5cm} (b) flow at t=25
+%}
+%\vspace{0.25cm}
+%\hbox{\hspace{1.5cm}
+%\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
+%}
+%\vspace{0.0cm}
+%\hbox{\hspace{4.0cm} (c) flow at t=3000   
+%}}     
+%\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
+The domain is discretised with $5960$ \PN[1]{2} elements.
+}
+%\label{DaweGrattoniExperiment_a}
+%\end{figure}
+%\clearpage
+%\end{comments}
+
+%%%%
+%%%%  FIGURE
+%%%%
 \begin{figure}[ht] 
     \vbox{
-\hbox{\hspace{-0.3cm}
-%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
-\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
+       \hbox{\hspace{1.cm}\includegraphics[width=\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2}}
+       \vspace{0.cm}
+       \hbox{\hspace{7cm}(a)}
+       \vspace{0.cm}
+       \hbox{\hspace{1.cm}\includegraphics[width=\textwidth]{./Pics1/DaweGrattoni_Experiment/1pageb}}
+       \vspace{0.cm}
+       \hbox{\hspace{7cm}(b)}
     }   
-\vspace{0.0cm}
-\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) sketch of the the domain which is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b) fluid displacement with permeability ratio of 2.5, exttracted from \citet{dawe_2008}.
 }
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
+\label{DaweGrattoniExperiment_a}
+\end{figure}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+  \begin{figure}[ht] 
+    \vbox{\vspace{0.cm}
+       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d61b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d125b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d145b} }
+       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d152b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d180b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d250b} }
+       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d260b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d275b} \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/legendb} }
+       \vspace{0.cm}
     }  
-\vspace{0.0cm}
-\hbox{\hspace{4.5cm} (b) flow at t=25
+\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): Snapshots of wetting fluid saturation overlapped with Darcy velocity over t=39.70 time-units.
+The domain is divided in four subdomains with permeabilities of $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$.
+The domain is discretised with 37872 \PN[1]{2} triangular elements.
 }
-\vspace{0.25cm}
-\hbox{\hspace{1.5cm}
-\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
-}
-\vspace{0.0cm}
-\hbox{\hspace{4.0cm} (c) flow at t=3000   
-}}     
-\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$.
-The domain is discretised with $5960$ \PN[1]{2} elements.
-}
-\label{fem_cv_represent_a}
+\label{DaweGrattoniExperiment_b}
   \end{figure}
+\end{landscape}
 \clearpage

### 2018-07-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Last Revision: Last modification (by Jeff) on the paper ... now it is up to Kostas
updates: adding figures for the qualitative validation -- Section 4.2 ... text to come ...

@@
 Numerical simulations \citep[based on lab experiments due to][]{evans_1994,dawe_2008} were conducted to demonstrate the model's capability to capture viscous crossflow during immiscible displacement in heterogeneous porous media.
-The 2D domain, shown in Fig.~\ref{fem_cv_represent_a}, is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
-Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u_{x}=1$.
+The 2D domain, shown in Fig.~\ref{DaweGrattoniExperiment_a}(a), is $4$ $\times$ $2$ unit-length and fully saturated with fluid 2 (VR=1).
+Fluid 1 is injected from the left-hand side of the domain with constant velocity of $u_{x}=$8.33$\times$10$^{-3}$.
 Boundary conditions also include no-flux across upper and lower borders.
-The domain consists of four regions in which each quarter is represented by a permeability value, Fig.~\ref{fem_cv_represent_a}(a).
+The domain consists of four regions in which each quarter is represented by a permeability value.
 
-A two-phase immiscible flow along homogeneous and parallel layers of contrasting petrophysical properties (\ie permeability) is initially simulated.
+A two-phase immiscible flow along homogeneous and parallel layers of contrasting permeability is initially simulated.
 During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces in discontinuous spatial permeability distribution.
-Such preferential flows are shown in Figs.~\ref{fem_cv_represent_a}(b-c).
-In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008} (see Figs.
-5-6 of this reference).
+Such preferential flows are shown in Figs.~\ref{DaweGrattoniExperiment_b}.
+In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008}, Fig.~\ref{DaweGrattoniExperiment_a}.
 

### 2018-07-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates: adding figures for the qualitative validation -- Section 4.2 ... text to come ...

@@
 Such preferential flows are shown in Figs.~\ref{DaweGrattoniExperiment_b}.
-In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008}, Fig.~\ref{DaweGrattoniExperiment_a}.
+In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008}, Fig.~\ref{DaweGrattoniExperiment_a}(b).
 

### 2018-11-12 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Added .gitignore files and started response for re-submission

--- 2018-04-15 Papers/AppliedMaths2018/cover_letter.tex
@@
 
-\begin{letter}{Dr Masoud Jabbari \\
+\begin{letter}{Dr. Masoud Jabbari \\
 CEng MIMechE PMSAMPE AMACerS MInterPore \\

### 2018-11-14 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Finished copying first Reviewer's comments

@@
 \documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
+\usepackage{hyperref,url}
+\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
+%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
+%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
+%% The amssymb package provides various useful mathematical symbols
 
-\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
-%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
+\usepackage{amssymb,amsmath,array}
+%The amsthm package provides extended theorem environments
+
+\usepackage{amsthm}
+\usepackage{graphicx}
+%\usepackage{subfigure}
+
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\BLnote}[1]{\fbox{\parbox{\textwidth}{ \color{green} BL Note $\Rightarrow$ #1}}}
+\newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
+\newcommand{\yellow}{\textcolor{yellow}}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
+\newcommand{\eg}{{\it e.g., }} 
+\newcommand{\ie}{{\it i.e., }}
+\newcommand{\st}{{\it s.t., }}
 
@@
 
-\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
+%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
 
+%----------------------------------------------------------------------------------------
+%	YOUR NAME & ADDRESS SECTION
+%----------------------------------------------------------------------------------------
+
+%\begin{center}
+\address {Room 354, \\Fraser Noble Building \\ University of Aberdeen,\\ Aberdeen AB24 3UE. \\
+  email: lashorebabatunde@yahoo.com} % Your address and phone number
+%\end{center} 
+%\vfill
+
+\signature{B. Lashore} % Your name for the signature at the bottom
+\longindentation=290pt
 \begin{document}
@@
 
-\begin{letter}{Dr. Masoud Jabbari \\
-CEng MIMechE PMSAMPE AMACerS MInterPore \\
-Lead Guest Editor for Special Issue: \\
-Applied Mathematical Modelling \\
-WMG, University of Warwick \\
-Coventry, CV4 7AL}
-
-%----------------------------------------------------------------------------------------
-%	YOUR NAME & ADDRESS SECTION
-%----------------------------------------------------------------------------------------
-
-\begin{center}
-\large\bf Mr. Babatunde Lashore \\ % Your name
-%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
-Room 207, Fraser Noble Building \\ University of Aberdeen, Aberdeen AB24 3UE. \\ email: lashorebabatunde@yahoo.com % Your address and phone number
-\end{center} 
-\vfill
-
-\signature{B. Lashore} % Your name for the signature at the bottom
+\begin{letter}{Professor Johann Sienz, \\CEng FIMechE, FRAeS, CMath, \\Editor-in-Chief of the International Journal: \\Applied Mathematical Modelling \\Deputy Head of College and, \\Director of Innovation and Engagement, \\
+Swansea University, UK.}
 
@@
 
-\opening{Dear Dr. Jabbari,}
+\opening{Dear Professor Sienz,}
 
-I am submitting a manuscript to be considered for publication in the special issue of "Applied Mathematical Modelling" on "Transport in Porous Media" in relation to the $3^{rd}$ UK InterPore Conference on Porous Media and the $1^{st}$ Monash-Warwick PREFRAC Workshop on Hydraulic Fracturing.
-The abstract and presentation I made at that conference has progressed since then, and the title of my submission has changed from "A Numerical Investigation of Stochastic and Deterministic Upscaling Methods for Permeability Fields" to "A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)".
+The authors appreciate the reviewer's comments and have worked very hard to address all suggestions and comments.
 
-I hereby confirm that the research in this work has not been published elsewhere and it has not been submitted simultaneously for publication elsewhere.
-
-The manuscript presents a model for representing an upscaled permeability field using singular value decomposition.
-It compares the benefits/performance of this model to well known deterministc methods such as arithmetic and harmonic averaging techniques.
-The model is also compared with a stochastic probability density function (PDF) model.
-Then a novel control volume finite element method (CVFEM) multiphase flow simulator is used to compare simulation results from the aforementioned models.
-The manuscript presents and discusses the results before drawing conclusions.
-
-I hope you find the manuscript satisfactory and accept it for publication in the journal. I thank you for your time and I look forward to further correspondence from you.
+The revised manuscript was just submitted to the journal's portal. Also, please find below the response to the reviewer's comments , highlighting the main changes in the manuscript.
 
@@
 
-\encl{Cover Letter, Highlight.tex, Manuscript(Makefile, Stochastic\_Upscaling\_UK\_AMM\_2018.tex, article\_/figure1.tex, Pics Folder, references.bib, elsarticle.cls, elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"
+\ps{
+Editor: \\
+The bibliography is not in the required format for Applied Mathematical Modelling. Please follow the author guide.
+\url{https://www.elsevier.com/journals/applied-mathematical-modelling/0307-904x/guide-for-authors}}
+
+Reviewer \#1: \\
+The authors aim at reducing the computational cost of reservoir simulation by parameterizing the permeability field using SVD and they compare with the classical upscaling techniques.
+This very same topic has been investigated by several authors before and I do not see anything new in this presentation.
+It uses a very simplistic approach and many important questions are left in this paper.
+Moreover, the authors missed many of the important developments done in SVD-based and other forms of permeability  parameterization in recent years.
+The authors are referred to many publications listed here.\\
+The paper also lacks comparison in computational effort, which is the main objective of such parameterization. For all of these reasons I am rejecting this paper for further publication.\\
+$[1]$ Insuasty, E., Van den Hof, P.
+M.
+J., Weiland, S., \& Jansen, J.
+D.
+(2017, February 20).
+Low-Dimensional Tensor Representations for the Estimation of Petrophysical Reservoir Parameters.
+Society of Petroleum Engineers.
+doi:10.2118/182707-MS\\
+$[2]$ Jafarpour, B., \& McLaughlin, D. B. (2009, March 1). Reservoir Characterization With the Discrete Cosine Transform. Society of Petroleum Engineers. doi:10.2118/106453-PA\\
+$[3]$ Sardar Afra, Eduardo Gildin, Tensor based geology preserving reservoir parameterization with Higher Order Singular Value Decomposition (HOSVD), Computers \& Geosciences, Volume 94, 2016, Pages 110-120,\\
+$[4]$  Tavakoli, R., \& Reynolds, A.
+C.
+(2010, June 1).
+History Matching With Parametrization Based on the SVD of a Dimensionless Sensitivity Matrix.
+Society of Petroleum Engineers.
+doi:10.2118/118952-PA\\
+
+\encl{Cover\_letter\_for\_resubmission.pdf, Highlight\_revised.pdf, Manuscript\_sourceFiles(Makefile, Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.tex, article\_/figure1.tex, Pics Folder, references.bib, elsarticle.cls, elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"
 

### 2018-11-15 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Comment from both reviewers update and response to reveiwer has commenced

@@
 \usepackage{hyperref,url}
-\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=red}
+\hypersetup{colorlinks=true, urlcolor=cyan, linkcolor=blue, citecolor=red}
 %\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
@@
 
-\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
-\newcommand{\BLnote}[1]{\fbox{\parbox{\textwidth}{ \color{green} BL Note $\Rightarrow$ #1}}}
+% Margins
+\topmargin=-1in % Moves the top of the document 1 inch above the default
+\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
+\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
+\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
+
+%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
+
+\newcommand{\JGnote}[1]{\fbox{\parbox{\linewidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\BLnote}[1]{\fbox{\parbox{\linewidth}{ \color{green} BL Note $\Rightarrow$ #1}}}
 \newcommand{\red}{\textcolor{red}}
@@
 \newcommand{\st}{{\it s.t., }}
-
-% Margins
-\topmargin=-1in % Moves the top of the document 1 inch above the default
-\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
-\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
-\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
-
-%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
 
@@
 \ps{
-Editor: \\
-The bibliography is not in the required format for Applied Mathematical Modelling. Please follow the author guide.
-\url{https://www.elsevier.com/journals/applied-mathematical-modelling/0307-904x/guide-for-authors}}
+  \begin{enumerate}
+  \item Editor: \\  
+    \begin{enumerate}
+    \item The bibliography is not in the required format for Applied Mathematical Modelling.
+Please follow the author guide.\url{https://www.elsevier.com/journals/applied-mathematical-modelling/0307-904x/guide-for-authors}\\
+      \BLnote{I do not understand/I cannot see the issue the editor is referring to}
+      \end{enumerate}
 
-Reviewer \#1: \\
-The authors aim at reducing the computational cost of reservoir simulation by parameterizing the permeability field using SVD and they compare with the classical upscaling techniques.
-This very same topic has been investigated by several authors before and I do not see anything new in this presentation.
-It uses a very simplistic approach and many important questions are left in this paper.
-Moreover, the authors missed many of the important developments done in SVD-based and other forms of permeability  parameterization in recent years.
+  \item Reviewer \#1: \\
+    \begin{enumerate}
+    \item The authors aim at reducing the computational cost of reservoir simulation by parameterizing the permeability field using SVD and they compare with the classical upscaling techniques.
+This very same topic has been investigated by several authors before and I do not see anything new in this presentation.\\
+      \blue {We are thankful for the reviewer's comments and we acknowledge that the topic as well as the content of the initial presentation primarily highlights only SVD for the permeability parameterization.
+In the updated manuscript, the topic has been reprased to differentiate the work from related topics and to help clarify the novelty in the research.
+Additionally, more information has been provided in the introduction section and the sub-sections titled ``Model Order Reduction/Principal Component Space Reduction''.
+The amendments made to deal with this issue make the following contribution to the manuscript}
+      \begin{enumerate}
+      \item \blue{It introduces ``Upscaling'' in the topic, acknowledges ``Upscaling'' as a method of MOR in the body of the manuscript and goes on to differenciate between upscaling a ``single'' realization of a permeability field from other existing parameterisation techniques which apply SVD to multiple realization of of a statistical representation using feature selection or elimination.
+Essentially, the authors present a case that all ``upscaling'' cases are a form of MOR (and therefore parameterization), however not all parameterization cases are upscaling.
+Crucially, the uniqueness of the work is in the manner in which the SVD (or HOSVD) is combined with linear regression to obtain a reduction in the permeability field (Please see \ref{R_R1_Novelty_P2}, .......
+and ........), it is different from existing related works which impliment a selection or elimination concept with respect to SVD.}
+        \item \label{R_R1_Novelty_P2} \blue {next item in the list}
+      \end{enumerate}
+    \item It uses a very simplistic approach and many important questions are left in this paper.
+    \item Moreover, the authors missed many of the important developments done in SVD-based and other forms of permeability  parameterization in recent years.
 The authors are referred to many publications listed here.\\
-The paper also lacks comparison in computational effort, which is the main objective of such parameterization. For all of these reasons I am rejecting this paper for further publication.\\
 $[1]$ Insuasty, E., Van den Hof, P.
@@
 doi:10.2118/118952-PA\\
+\item The paper also lacks comparison in computational effort, which is the main objective of such parameterization. For all of these reasons I am rejecting this paper for further publication.\\
+    \end{enumerate}
+
+\item Reviewer \#2: \\
+  The manuscript looks at the problem of upscaling in flow in porous media.
+The heterogeneous properties of interest are characterised by the permeability of the porous media and a SVD-based method is used to prove that the proposed method outperforms, in terms of computational saving, other existing industry techniques.
+This topic is currently of high interest in the groundwater flow community and I think the audience of Applied Mathematical Modelling would be interested in learning about the results in the manuscript.\\
+  \begin{enumerate}
+    \item I might be overlooking something but my overall impression is that the novelty is claimed to be on the control volume finite element simulator, although later in the Introduction the authors refer the reader to an already published work [16].
+My belief is that the paper reports on an application of some already existing methodologies such as the SVD technique.
+So that, this paper does not contain any advances in model reduction methodology.
+Said that, in the spirit of reproducible research it offers an independent assessment of traditional algorithm developments such as model order reduction.
+If this is not the case and I am wrong, then, I would suggest to clarify and discuss the novelty of this research where appropriate.\\
+    \item In general, I find the manuscript well written although in some parts (e.g., in the Abstract, Introduction and Section 3) it is perhaps too general and descriptive for a journal of applied mathematical modelling.
+This latter along with the lack of novelty are my main concerns.
+I would recommend to go deeper in the technical side and bring the material into a more scientific form of presentation.
+      \item I find unbalanced the battery of figures and plots provided in the manuscript with the degree of analysis of results given in the result section.
+I would select just the most relevant plots and would focus on comment those in more details in the result section.\\
+Based on this assessment, I recommend to invite the authors to review their material and bring it into a more suitable form of presentation for a journal of applied mathematics.\\
+\item Introduction: The last part motivating what is going to be done in the following sections is too extensive. This latter is supposed to be a summary.\\
+\item Section 2: This needs a more deep explanation of the numerical formulation which was claimed earlier to be novel and how the equations are coupled and the permeability modelled.\\
+\item Section 3: I find this section too descriptive, it could be part of the Introduction.\\
+\item Section 4: The SVD technique is broadly known by mathematicians.
+I would bring that part to an appendix or just remove it.
+Section 4.2.1 has to be edited properly.
+The permeability is a tensor if one decides to model it as a tensor.
+This is misleading.
+If you are going to use a 2D geometry, I recommend to start the description from a 2D setup directly.
+The same for the rest of points, 4.2.2 and 4.2.3.
+These are known techniques, I would be better (in my opinion) to provide an algorithm (or steps) with the procedure and giving the references accordingly for the SVD and principal component spaces as done in Section 5.
+\end{enumerate}
+\end{enumerate}
+}
 

### 2018-11-15 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Initial thoughts on response completed, response to several comments is still missing

--- 2018-11-14 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
@@
 \ps{
-Editor: \\
-The bibliography is not in the required format for Applied Mathematical Modelling. Please follow the author guide.
-\url{https://www.elsevier.com/journals/applied-mathematical-modelling/0307-904x/guide-for-authors}}
-
-Reviewer \#1: \\
-The authors aim at reducing the computational cost of reservoir simulation by parameterizing the permeability field using SVD and they compare with the classical upscaling techniques.
-This very same topic has been investigated by several authors before and I do not see anything new in this presentation.
-It uses a very simplistic approach and many important questions are left in this paper.
-Moreover, the authors missed many of the important developments done in SVD-based and other forms of permeability  parameterization in recent years.
+  \begin{enumerate}
+  \item Editor:   
+    \begin{enumerate}
+    \item \label{R_E} The bibliography is not in the required format for Applied Mathematical Modelling.
+Please follow the author guide.\url{https://www.elsevier.com/journals/applied-mathematical-modelling/0307-904x/guide-for-authors}
+      \begin{enumerate}
+      \item \label{R_E_P1} \blue{....................}
+        \end{enumerate}
+      \BLnote{I do not understand/I cannot see the issue the editor is referring to here}
+      \end{enumerate}    
+  \item Reviewer \#1: 
+    \begin{enumerate}
+    \item \label{R_R1_Novelty} The authors aim at reducing the computational cost of reservoir simulation by parameterizing the permeability field using SVD and they compare with the classical upscaling techniques.
+This very same topic has been investigated by several authors before and I do not see anything new in this presentation.\\
+      \blue {We are thankful for the reviewer's comments and we acknowledge that the topic as well as the content of the initial presentation primarily highlights only SVD for the permeability parameterization.
+In the updated manuscript, the manuscript title has been reprased to differentiate the work from related topics and to help clarify the novelty in the research.
+Additionally, more information has been provided in the introduction section and the sub-sections titled ``Model Order Reduction/Principal Component Space Reduction''.
+The amendments made to deal with this issue make the following contribution to the manuscript}
+      \begin{enumerate}
+      \item \label{R_R1_Novelty_P1} \blue{It introduces ``Upscaling'' in the manuscript title, acknowledges ``Upscaling'' as a method of MOR in the body of the manuscript and goes on to differenciate between upscaling a ``single'' realization of a permeability field from other existing parameterisation techniques which apply SVD to multiple realization of of a statistical representation using feature selection or elimination.
+Essentially, the authors present a case that all ``upscaling'' cases are a form of MOR (and therefore parameterization), however not all parameterization cases are upscaling.
+Crucially, the uniqueness of the work is in the manner in which the SVD (or HOSVD) is combined with linear regression to obtain a reduction in the permeability field (Please see \ref{R_R1_Novelty_P2}, .......
+and ........), it is different from existing related works which impliment a selection or elimination concept, with respect to SVD.}
+      \item \label{R_R1_Novelty_P2} \blue {The amendment introduces ``linear regression'' in the manuscript title and substitudes interpolation for linear regression in the body of the manuscript.
+Importantly, the authors give more details on how linear regression/interpolation is used in the principal component analysis (PCA) space to achieve dimensionality reduction.}
+      \item \label{R_R1_Novelty_P3} \blue{The amendment introduces ``Principal Component Analysis Spaces'' in the manuscript title and gives it a higher level of relevance in the body of the manuscript, particularly in the introduction section.
+Additionally, the update to the manuscript highlights the fact that two techniques exist for obtaining PCA (\ie {the covariane matrix method and the SVD method}) and gives the rational for selecting the SVD method.}
+        \item \label{R_R1_Novelty_P4} \blue{The amendment to the manuscript draws a distinction between SVD and linear regression (which is simply implimented here by interpolation) in the context of parameterization}\\
+      \end{enumerate}
+      \blue{\bf{Manuscript Title before Amendment:}}
+      \begin{center}
+        \blue{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
+        \end{center}
+      \blue{\bf{Manuscript Title after Amendment:}}
+      \begin{center}
+        \blue{A Reduced Order Model for Upscaling Permeability Fields with Linear Regression in Principal Component Analysis (PCA) space using Singular Value Decomposition (SVD) or Higer Order Singular Value Decomposition (HOSVD)}
+      \end{center}
+      \blue{\bf{Manuscript body before Amendment:}}\\
+      \\
+      \\
+      \blue{\bf{Manuscript body after Amendment:}}\\
+      \\
+      \\
+    \item \label{R_R1_OverSimplification} It uses a very simplistic approach and many important questions are left in this paper.
+      \begin{enumerate}
+      \item \label{R_R1_OverSimplification_P1} \blue{The authors thank the reviewer for the comment and acknowledges that the work may be interpreted as over-simplified from the initial manuscript presented.
+A simplistic approach for presenting the work was initially favoured by the authors to avoid distraction from the main work and to simplify the findings.
+In satisfying the reviewer, more details were provided as detailed in the response to \ref{R_R1_Novelty}.
+Additionally, a set of 3-D simulations were added to the amended manuscript.
+These changes remove the simplification and the authors also hope they answered the important questions that the reviewer implied remained unanswered.
+The authors remain willing to provide a direct answer to any unanswered questions which are explicitly stated.}
+        \end{enumerate}
+    \item \label{R_R1_MissedNewDev}Moreover, the authors missed many of the important developments done in SVD-based and other forms of permeability  parameterization in recent years.
 The authors are referred to many publications listed here.\\
-The paper also lacks comparison in computational effort, which is the main objective of such parameterization. For all of these reasons I am rejecting this paper for further publication.\\
 $[1]$ Insuasty, E., Van den Hof, P.
@@
 Society of Petroleum Engineers.
-doi:10.2118/118952-PA\\
+doi:10.2118/118952-PA
+      \begin{enumerate}
+      \item \label{R_R1_MissedNewDev_P1} \blue{The authors thank the reviewers for the comment, references to the papers mentioned by the reviwer have now been included in the amended manuscript.
+Some of these papers were originally excluded from the manuscript initially because they were not related to upscaling.
+In line with the author's response at \ref{R_R1_Novelty}, the difference between the work in those papers and the authors' work are highlighted to draw out the uniqueness of the current work}
+        \end{enumerate}
+    \item \label{R_R1_CompEffort} The paper also lacks comparison in computational effort, which is the main objective of such parameterization.
+For all of these reasons I am rejecting this paper for further publication.
+      \begin{enumerate}
+      \item \label{R_R1_CompEffort} \blue{..........}
+        \end{enumerate}
+    \end{enumerate}
+
+\item Reviewer \#2: \\
+  The manuscript looks at the problem of upscaling in flow in porous media.
+The heterogeneous properties of interest are characterised by the permeability of the porous media and a SVD-based method is used to prove that the proposed method outperforms, in terms of computational saving, other existing industry techniques.
+This topic is currently of high interest in the groundwater flow community and I think the audience of Applied Mathematical Modelling would be interested in learning about the results in the manuscript.
+  \begin{enumerate}
+  \item \label{R_R2_Novelty} I might be overlooking something but my overall impression is that the novelty is claimed to be on the control volume finite element simulator, although later in the Introduction the authors refer the reader to an already published work [16].
+My belief is that the paper reports on an application of some already existing methodologies such as the SVD technique.
+So that, this paper does not contain any advances in model reduction methodology.
+Said that, in the spirit of reproducible research it offers an independent assessment of traditional algorithm developments such as model order reduction.
+If this is not the case and I am wrong, then, I would suggest to clarify and discuss the novelty of this research where appropriate.
+    \begin{enumerate}
+      \item \label{R_R2_Novelty_1} \blue{..........}
+        \end{enumerate}
+\item \label{R_R2_TooDesc} In general, I find the manuscript well written although in some parts (e.g., in the Abstract, Introduction and Section 3) it is perhaps too general and descriptive for a journal of applied mathematical modelling.
+This latter along with the lack of novelty are my main concerns.
+I would recommend to go deeper in the technical side and bring the material into a more scientific form of presentation.
+   \begin{enumerate}
+      \item \label{R_R2_TooDesc_1} \blue{..........}
+        \end{enumerate}
+      \item \label{R_R2_TooMuchFig} I find unbalanced the battery of figures and plots provided in the manuscript with the degree of analysis of results given in the result section.
+I would select just the most relevant plots and would focus on comment those in more details in the result section.\\
+        Based on this assessment, I recommend to invite the authors to review their material and bring it into a more suitable form of presentation for a journal of applied mathematics.
+         \begin{enumerate}
+      \item \label{R_R2_TooMuchFig_1} \blue{..........}
+        \end{enumerate}
+\item \label{R_R2_TooMuchSum} Introduction: The last part motivating what is going to be done in the following sections is too extensive. This latter is supposed to be a summary.
+   \begin{enumerate}
+      \item \label{R_R2_TooMuchSum_1} \blue{..........}
+        \end{enumerate}
+\item \label{R_R2_NumFormulation} Section 2: This needs a more deep explanation of the numerical formulation which was claimed earlier to be novel and how the equations are coupled and the permeability modelled.
+   \begin{enumerate}
+      \item \label{R_R2_NumFormulation_1} \blue{..........}
+        \end{enumerate}
+\item \label{R_R2_TooDesc} Section 3: I find this section too descriptive, it could be part of the Introduction.
+ \begin{enumerate}
+      \item \label{R_R2_TooDesc_1} \blue{..........}
+    \end{enumerate}
+\item \label{R_R2_SVDWellKnown} Section 4: The SVD technique is broadly known by mathematicians. I would bring that part to an appendix or just remove it.
+  \begin{enumerate}
+      \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section will be moved to the appendix}
+        \end{enumerate}
+\item \label{R_R2_TensorCorrection}Section 4.2.1 has to be edited properly. The permeability is a tensor if one decides to model it as a tensor. This is misleading.
+  \begin{enumerate}
+      \item \label{R_R2_TensorCorrection_1} \blue{The authors appreciate the reviewer's correction and apologizes for the oversight. Section 4.2.1 has now been properly edited}
+        \end{enumerate}
+  \item \label{R_R2_GeomSetupAlgorithm} If you are going to use a 2D geometry, I recommend to start the description from a 2D setup directly.
+The same for the rest of points, 4.2.2 and 4.2.3.
+These are known techniques, I would be better (in my opinion) to provide an algorithm (or steps) with the procedure and giving the references accordingly for the SVD and principal component spaces as done in Section 5.
+ \begin{enumerate}
+      \item \label{R_R2_GeomSetupAlgorithm_1} \blue{The authors thank the review for the feedback, starting the section directly on 2D simulation if only a 2D simulation is presented in the work.
+The recommended changes have been made and for completeness, some work on 3D simulations have now been included in the manuscript} \red{................response to creating algorimthm required.........}
+        \end{enumerate}
+\end{enumerate}
+\end{enumerate}
+}
 

### 2018-11-30 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
Updated response to reviewers

@@
 
-The authors appreciate the reviewer's comments and have worked very hard to address all suggestions and comments.
+The authors appreciate your comment as well as those of the reviewers, and have worked very hard to address all suggestions and comments.
 
@@
 This very same topic has been investigated by several authors before and I do not see anything new in this presentation.\\
-      \blue {We are thankful for the reviewer's comments and we acknowledge that the topic as well as the content of the initial presentation primarily highlights only SVD for the permeability parameterization.
+      \blue {We are thankful for the reviewer's comments and we acknowledge that the topic as well as the content (particularly the abstract) of the initial manuscript presented  primarily highlights only SVD for the permeability field parameterization.
+However, this does not accurately portray the work undertaken by the authors and therefore amendments have been made to correct the observed issues.
 In the updated manuscript, the manuscript title has been reprased to differentiate the work from related topics and to help clarify the novelty in the research.
@@
       \begin{enumerate}
-      \item \label{R_R1_Novelty_P1} \blue{It introduces ``Upscaling'' in the manuscript title, acknowledges ``Upscaling'' as a method of MOR in the body of the manuscript and goes on to differenciate between upscaling a ``single'' realization of a permeability field from other existing parameterisation techniques which apply SVD to multiple realization of of a statistical representation using feature selection or elimination.
-Essentially, the authors present a case that all ``upscaling'' cases are a form of MOR (and therefore parameterization), however not all parameterization cases are upscaling.
-Crucially, the uniqueness of the work is in the manner in which the SVD (or HOSVD) is combined with linear regression to obtain a reduction in the permeability field (Please see \ref{R_R1_Novelty_P2}, .......
-and ........), it is different from existing related works which impliment a selection or elimination concept, with respect to SVD.}
+      \item \label{R_R1_Novelty_P1} \blue{The amendment introduces ``Upscaling'' in the manuscript title and acknowledges ``Upscaling'' as a method of ROM in the body of the manuscript.
+The amendment goes on to differenciate "upscaling" a ``single'' realization of a permeability field from other existing parameterisation techniques which apply SVD to multiple realization of of a statistical representation.
+It is particularly noted that the existing parameterization techniques which apply SVD, implement feature selection or elimination to obtain a reduction in dimensionality.
+This implementation (\ie feature selection or elimination) was avoided by the authors in this work.
+Essentially, the authors present a case that all ``upscaling'' cases are a form of ROM (and therefore parameterization), however not all parameterization cases are upscaling.
+Crucially, the uniqueness of the work is in the manner in which the SVD or HOSVD (while implementing PCA) is combined with linear regression to obtain a reduction in the permeability field (Please see \ref{R_R1_Novelty_P2}, \ref{R_R1_Novelty_P3} and \ref{R_R2_Novelty_1}), it is different from existing related works which impliment a selection or elimination concept, with respect to SVD (or HOSVD).}
       \item \label{R_R1_Novelty_P2} \blue {The amendment introduces ``linear regression'' in the manuscript title and substitudes interpolation for linear regression in the body of the manuscript.
 Importantly, the authors give more details on how linear regression/interpolation is used in the principal component analysis (PCA) space to achieve dimensionality reduction.}
-      \item \label{R_R1_Novelty_P3} \blue{The amendment introduces ``Principal Component Analysis Spaces'' in the manuscript title and gives it a higher level of relevance in the body of the manuscript, particularly in the introduction section.
+      \item \label{R_R1_Novelty_P3} \blue{The amendment introduces ``Principal Component Analysis Spaces'' in the manuscript title and it gives and appropriate level of relevance in the body of the manuscript, particularly in the abstract.
 Additionally, the update to the manuscript highlights the fact that two techniques exist for obtaining PCA (\ie {the covariane matrix method and the SVD method}) and gives the rational for selecting the SVD method.}
@@
       \begin{center}
-        \blue{A Reduced Order Model for Upscaling Permeability Fields with Linear Regression in Principal Component Analysis (PCA) space using Singular Value Decomposition (SVD) or Higer Order Singular Value Decomposition (HOSVD)}
+        \blue{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using Singular Value Decomposition (SVD) or Higer Order Singular Value Decomposition (HOSVD): Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
       \end{center}
@@
 A simplistic approach for presenting the work was initially favoured by the authors to avoid distraction from the main work and to simplify the findings.
-In satisfying the reviewer, more details were provided as detailed in the response to \ref{R_R1_Novelty}.
-Additionally, a set of 3-D simulations were added to the amended manuscript.
+In dealing with the issue identified by the reviewer, more details were provided as detailed in the response to \ref{R_R1_Novelty}.\\
+        Additionally, a set of 3-D simulations were added to the amended manuscript.This required the introduction of HOSVD into the manuscript which also deals with the reviewer's next comment regarding recent development in SVD-based form of permeability parameterization.
+In conforming with the third reviewer's suggestion (at \ref{R_R2_SVDWellKnown_1}) to place the section on ``A brief Introduction to SVD'' in the appendix, the new section titled ``A brief Introduction to HOSVD'' has been placed in the appendix.
+\\
         These changes remove the simplification and the authors also hope they answered the important questions that the reviewer implied remained unanswered.
@@
     \begin{enumerate}
-      \item \label{R_R2_Novelty_1} \blue{..........}
+      \item \label{R_R2_Novelty_1} \blue{The authors thank the reviewer for the comments.
+While the CVFEM simulator remains relatively new, the authors acknowledge that referring to it as novel within the manuscript, tends to draw away focus from the crux of the work which is ROM.
+Therefore, corrections have been made to the manuscript to clarify that the CVFEM simulator is not the main focus of the work.\\
+Further to the explanation provided in the response at \ref{R_R1_Novelty}, while PCA (with respect to SVD or HOSVD) and linear regression are not new, the authors believe that the manner in which they (\ie PCA and linear regression) have been combined and applied to achieve dimensionality reduction for the problem at hand is novel}
         \end{enumerate}
@@
    \begin{enumerate}
-      \item \label{R_R2_TooDesc_1} \blue{..........}
+      \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment.
+The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}
         \end{enumerate}
@@
          \begin{enumerate}
-      \item \label{R_R2_TooMuchFig_1} \blue{..........}
+      \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive.
+These have been reduced from 86 to the most relevant 9 \red{update the number 9 after including figures for the 3D simulations} (which are included in the manuscript).
+Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}
         \end{enumerate}
@@
    \begin{enumerate}
-      \item \label{R_R2_TooMuchSum_1} \blue{..........}
+      \item \label{R_R2_TooMuchSum_1} \blue{The authors thank the reviewer for the comment, as advised, the latter part of the introduction has been made brief.
+Additionally, the extensive details in the introduction section which was referred to has been moved to the section on "Model Description and Simulation Setup".}
         \end{enumerate}
@@
  \begin{enumerate}
-      \item \label{R_R2_TooDesc_1} \blue{..........}
+      \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}
     \end{enumerate}
@@
   \begin{enumerate}
-      \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section will be moved to the appendix}
+      \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section has been moved to the appendix.
+Additionally, as mentioned in the response at \ref{R_R1_OverSimplification_P1}, a newly introduced section titled ``A brief Introduction to HOSVD'' was also moved to the appendix.}
         \end{enumerate}

### 2018-11-30 Papers/AppliedMaths2018/Resubmission/Highlights_resubmission.tex
Updated the file for Highlights_resubmission

\documentclass[a4paper,11pt]{article}

\newcommand{\ie}{{\it i.e., }}
% define the title
\author{B.~Lashore}
\title{Highlights}
\begin{document}
% generates the title
\maketitle
% insert the table of contents
%\tableofcontents
%\section{Some Interesting Words}

\begin{enumerate}
  \item Implemented a reduced order model (\ie{upscale}) of a permeability field by coupling linear regression with Principal Component Analysis, PCA (where PCA is obtained with singular value decomposition, SVD, for 2D cases and Higher Order Singular Value Decomposition, HOSVD, for 3D cases)
  \item For the 2D Case, benchmarked the coupled PCA (using SVD) and linear regression method by comparing with Arithmetric mean, Harmonic mean, and Probability Density Function (PDF) models, as well as the BaseCase (which is the fine grid model for the 2D case)
  \item For the 3D case, benchmarked the coupled PCA (using HOSVD) and linear regression method by comparing with the BaseCase (also known as the fine grid model for the 3D case)
  \item A high-order accurate control volume FEM multiphase flow simulator was used to perform a qualitative comparision of the simulation results from the models for both the 2D and the 3D cases
  \item The coupled PCA and linear regression model model presented a better representation compared to the other models 
\end{enumerate}
\end{document}

### 2018-12-02 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
Updated manuscript 1.5 of 7 completed

--- 2018-04-15 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
@@
 \usepackage{graphicx}
+\usepackage[mathscr]{euscript}
 %\usepackage{subfigure}
@@
 
-\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
-\author[UoA]{B. Lashore}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes\corref{cor1}}\ead{jefferson.gomes@abdn.ac.uk}
-%\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
+\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
+\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
 \cortext[cor1]{Corresponding author.}
@@
 
-In this paper, a SVD-based method was developed to reduce the order of porous media permeability field (\ie upscale).
-This method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
-It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
-Additionally, the SVD upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
+In this paper, a single realization of a permeability field was upscaled by first projecting the permeability field into a principal component analysis space (using SVD for 2D field and HOSVD for 3D fields).
+Then linear regression was employed within each of the principal component spaces to obtain approximate representations of the initial principal component.
+The new principal components are then recombined to for a new permeability field with a reduced order.
+This PCA-linear regression method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
+
+It was shown that the new upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
+Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
 
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-Singular Value Decomposition (SVD)\sep Upscaling\sep Model Order Reduction (MOR) \sep  Principal Component Spaces \sep Permeability field \sep Heterogeneity
+Principal Component Analysis (PCA) and Linear Regression \sep Singular Value Decomposition (SVD) and Higer Order Singular Value Decomposition (HOSVD) \sep Upscaling\sep Reduced Order Models (ROM), \sep Permeability field \sep Heterogeneity
 \end{keyword}
@@
 \citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998 which introduced Passive Reduced-order Interconnect Macromodeling Algorithm (PRIMA).
-Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
+Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
-In this work, upscaling is performed by SVD in principal component spaces.
+In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively.
 
@@
 Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
+Four upscaling techniques are investigated in this work and they are named Arithmetric mean, Harmonic mean, probability density function (PDF) and PCA (using SVD for 2D models and HOSVD for 3D model) coupled with linear regression.
 
-Four upscaling techniques are investigated in this work, arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
-The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case).
-The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability distribution.
-
-In Section~\ref{section:svd}, fundamental mathematics of SVD and associated properties are presented.
+In Section~\ref{section:pca_linreg}, fundamental mathematics of SVD and associated properties are presented.
 Then, the concept of spaces is explained to give the reader the understanding necessary to appreciate the transformations and projections involved in this work.
-Finally, Section~\ref{section:svd} describes model order space reduction for the permeability field within the principal component space.
-Section~\ref{section:model_simulation} starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to.
+Finally, Section~\ref{section:pca_linreg} describes the reduced order model reduction for the permeability field within the principal component space.
+Section~\ref{section:model_simulation} is dedicated to model description and simulation.
+It starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to.
 A brief summary of the pre-processing step for each of the models is also presented.
@@
 
+\subsection{Brief Overview of Upscaling}\label{section:overview_upscaling}
+
+Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+This subject of upscaling heterogenous properties has interested industries (\ie oil and gas, CCS and waste management) as well as the academic community for over $7$ decades.
+
+Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach.
+In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
+In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
+In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
+
+Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
+\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
+The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
+
+\citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields for two cases.
+Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up.
+The first case had low permeablitity in all the blocks except the bottom right block which had high permeability, while the second case employed the checkboard style described in Section~\ref{subsection:model}.
+Different conductivity ratios were also investigated for the two cases.
+The conclusion drawn was that renormalization worked fairly well for the first case, but very poorly for the second case.
+
+\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
+They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
+\citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
+
+\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
+The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.
+
 \section{Multi-Fluid Flow Model}\label{section:mathematical_model}
 
-In this work, a novel control volume finite element method (CVFEM) formulation is used to discretise and solve the set of multi-fluid flow equations.
+In this work, a control volume finite element method (CVFEM) formulation is used to discretise and solve the set of multi-fluid flow equations.
 Continuity equations are embedded into the pressure equation to enforce mass conservation and the exact force balance (extended Darcy equations).
@@
 These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{jackson_2013,Gomes_2017}).
+Although, the numerical formulation used here is relatively new, it is not the focus of this work.
+The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation.
+However, more extensive validation tests can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
 
@@
 
-\section{Brief Overview of Upscaling}\label{section:overview_upscaling}
+\section{PCA coupled with Linear Regression}\label{section:pca_linreg}
 
-Section~\ref{section:intro} briefly introduced the rational behind upscaling.
-Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-This subject of upscaling heterogenous properties has interested industries (\ie oil and gas, CCS and waste management) as well as the academic community for over $7$ decades.
+\subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
 
-Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach.
-In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
-In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
-In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
+\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
+Permeability can be represented as tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), it is assumed that permeability is a scalar quantity.
+Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.
 
-Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
-\citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
-The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
+Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
+For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed where the geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
+This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
 
-\citet{Yeo2001} discussed the accuracy of renormalization method for upscaling 2D hydraulic conductivity fields for two cases.
-Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up.
-The first case had low permeablitity in all the blocks except the bottom right block which had high permeability, while the second case employed the checkboard style described in Section~\ref{subsection:model}.
-Different conductivity ratios were also investigated for the two cases.
-The conclusion drawn was that renormalization worked fairly well for the first case, but very poorly for the second case.
+The ROM method discussed here is concerned with reducing the volume of permeability data within the permeability space.
+Consider for instance a small square which is discretized to contain four squares such that $4$ data points are defined in the middle of the four squares.
+The permeability space of $4$ can be reduced to a smaller value of $1$ through an averaging process such as arithmetic, harmonic or geometric mean.
+This type of reduction is the focus of this paper, albeit the main focus of this paper is achieving this reduction through linear regression in the principal component spaces.
 
-\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling.
-They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
-\citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
+\subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
+Essentially, the existing permeability space is transformed with SVD for 2D permeability field and HOSVD for 3D permeability fields, to principal component spaces (PCS).
+Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces.
+The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
+An algorithm which impliments the procedure described here, is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
 
-\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
-The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.
+The PCS is a bit challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
+An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
+A similar intuition can be extended to HOSVD for 3D permeability fields.
+The decomposition of a matrix into its factors using SVD  \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials.
+However, for completeness, the appendix contains a brief introduction to SVD (\ref{subsection:svd_brief}) and HOSVD (\ref{subsection:hosvd_brief}).
 
-\section{Singular Value Decomposition (SVD) and Application for Reducing the Order of Permeability Fields}\label{section:svd}
-\subsection{A Brief Introduction to SVD}\label{subsection:svd_brief}
+\subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
+For the PCA-Linear regression (PCA-LinReg) reduced order model of the permeability field, all the work is done in the principal component spaces.
+This can be completed in two steps, which is exemplified for the 2D model thus:
+\begin{enumerate}
+  \item The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+
+Note that, in the case with $z = r$, it can be assumed that step 1 has been ignored.
+However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
+The selected $z$ singular values also form a new diagonal matrix, $\mathbf{\Sigma_{new}}$ .
+
+\item The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
+The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
+
+\end{enumerate}
+
+It is trivial to show that these two steps can be replicated for a 3-D model using HOSVD to obtain the PCA space.\\
+
+Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space\cite{Tharwat_2016} , namely, the co-variance method and the SVD method.
+\citet{Tharwat_2016} goes on to describe both methods in details.
+In this work, the authors have opted to use the SVD method to obtain the PCA space.
+This is because the singular vectors which make up the PCS have a strong correlation to the coordinate axis they represent.
+This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.
+
+\subsection{Principal Component Analysis Versus Linear Regression}\label{subsection:pcs_vs_linreg}
+
+\citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure below.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{|m{1em} |m{14em} |m{14em}|} 
+ \hline
+  & PCA & Linear Regression \\ [0.5ex] 
+ \hline
+ 1 & Determines the best vector (or set of vectors) which compresses the data points by minimizing the orthogonal distance to the points & Approximates the best fit line for the points by minimizing the error \\
+ \hline
+ 2 & Essentially, it forms a projection of the original points onto the new vector space & Predicts $y$ from $x$ through a function $f(x_1,x_2,....,x_n) = y$ \\
+ \hline
+ 3 & Not used for predictions, as original feature space (\ie $x_1$ and $x_2$) give way to a new reduced dimension. Cordinates $x_1, x_2,...,x_n$ give way to $z_1,....,z_k$ where $k \leq n$ & \\[1ex]
+ \hline
+\end{tabular}
+\caption{Table comparing PCA with Linear Regression}
+\label{table:pca_vs_linreg}
+\end{table}
+
+\red{I need to plot a figure here.}
+
+\section{Model Description and Simulation Setup}\label{section:model_simulation}
+
+As previosly mentioned, four upscaling techniques are investigated in this work.
+Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
+The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case).
+The fourth upscaling technique is the crux of this research, it introduces a reduced order model which couples PCA and linear regression.
+
+\subsection{Model Description}\label{subsection:model}
+The BaseCase  (\ie fine mesh resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
+Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
+
+The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
+Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
+More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
+Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
+Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
+
+As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field.
+When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
+The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).
+
+In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
+This effectively homogenizes the permeability field in each block.
+The upscaled permeability field for the third and fourth cases are referred to as PDFCase and PCA-LinReg Case, respectively.
+And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively.
+The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
+It is appropriate to note that although these models (PDFCase and PCA-LinReg Case) are upscaled, they retain heterogeneity within the blocks.
+
+\subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
+\begin{enumerate}[1.]
+  \item A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
+  \begin{enumerate}[a)]
+    \item \textbf{K1} : $700 - 900$ mD
+    \item \textbf{K2} : $50 - 150$ mD
+    \item \textbf{K3} : $100 - 200$ mD
+    \item \textbf{K4} : $1000 - 1200$ mD
+  \end{enumerate}                                                    
+  \item The number of data points generated for each block is $1600$ and the data values are randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
+  \item Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned dataset for each block.
+This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
+\end{enumerate}
+
+\subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
+\begin{enumerate}[1.]
+  \item The datasets from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) are used to calculate mean and standard deviation for each block of the permeability field.
+  \item A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase for each of the four blocks  (\ie $400$ data points for each block).
+  \item The data values in the dataset for each block is randomly positioned within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
+  \item Finally, the structured/arranged dataset from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
+\end{enumerate}
+
+\subsubsection{2-D PCA (\ie{using SVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
+\begin{enumerate}[1.]
+  \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
+  \item A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
+(This step is optional, it is the conventional PCA dimensionality reduction)
+  \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
+(This step is necessary only if the optional step in 2 above is executed)
+  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
+These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
+  \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+It is a permeability field with a quarter of the data values in the base case and therefore a permeability field with reduced order.
+\end{enumerate}
+
+\subsubsection{3-D PCA (\ie{using HOSVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:hosvdcase_preprocess_algorithm}
+The algorithm for the 3-D case is similar to that of the 2-D case described above. However:
+\begin{enumerate}[1.]
+\item In step 1 above, HOSVD is used for factorization instead of SVD.
+Therefore, a $3 x 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$.
+  \item It goes without saying that the core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section \ref{subsubsection:svdcase_preprocess_algorithm} above.
+\end{enumerate}
+The authors found the updated Tensorly library package \cite{Tensorly_2018} helpful in implimenting and executing the algorithm for HOSVD.
+
+\subsection{Simulations}\label{subsection:simulations}
+For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
+No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
+Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
+In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
+\begin{eqnarray}
+  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
+  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
+\end{eqnarray}
+where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
+$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
+Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
+
+Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+\begin{displaymath}
+  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
+\end{displaymath}
+
+\section{Results and Discussion}\label{section:results_discussion}
+
+Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
+Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs.
+Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
+
+Figure~\ref{fig:PermFields} compares the permeability distribution for all the models.
+As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
+Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.
+
+This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and PCA-LinReg cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous.
+Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the PCA-LinReg Case give a better representation of the BaseCase.
+An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution.
+Whereas, for the PDFCase and the PCA-LinReg Case, the permeability field will change if the upgrid resolution changes.
+
+With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase.
+Meanwhile, the PCA-LinReg Case will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
+Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block.
+However, the data value at a point in the PCA-LinReg Case is directly related to the nearest data values with respect to the same point in the BaseCase, throught the interpolation which takes place in the PCS.
+
+Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case.
+However, with the PCA-LinReg Case, knowledge of blocks with similar properties is not required prior to the upscaling.
+Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation.
+The limits of the techniques used for the PCA-LinReg Case will be discussed in the author's future work.
+
+Before going on to review the results of the simulations, it is beneficial to briefly consider the Buckley-Leverett and cross-flow behaviour which are be used to validate the results from this work.
+
+\citet{buckley_1942} in 1942 derived the Buckley-Leverett equation, an analytical (albeit simplified) two phase flow equation.
+The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation.
+The equation is referred to as "simplified" because of the assumptions made while deriving it, some of which were ignored in this work.
+Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities.
+Additionally, the permeability field in each block is heterogeneous.
+However, the general validation test or expectation from Buckley-Leverett's influence on this work, is that, the injected fluid saturation in $K1$ and $K2$ is expected to have a piston-shape front within those blocks, subject some inconsistency at the boundary between the two blocks, and also within the blocks due to the heterogeneity.
+
+\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were somewhat replicated here for the simulations.
+Therefore, the work of \citet{dawe_2008} can be used to validate the resulting simulations from this work.
+In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$.
+Additionally, the cross-flow from $K1$ to $K4$ is well represented in the simulations.
+
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
+In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)).
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
+
+Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
+Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
+Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
+This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
+However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.
+
+Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
+This inconsistency is with respect to this realization of the PDFCase.
+Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
+
+\section{Conclusion}\label{section:conclusion}
+
+Upscaling is a form of reduced order model, and a method of implementing upscaling by coupling linear regression with PCA is introduced in this work.
+For a 2-D model, SVD is used to decompose the existing permeability field to obtain the PCA space, while HOSVD is used for 3-D models.
+Within, the PCA space, linear regression (or interpolation) is used to reduce the data in the PCA space.
+The reduced data in the principal component space is then recombined to form a reduced data of the permeability field.
+
+Results show that the permeability field data reduction can be specifically defined for the PDFCase and the PCA-LinReg Case but not for the ArithMeanCase and the HarmMeanCase.
+This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution.
+The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.
+This is a huge advantage as it saves time during the data pre-processing stage, because sorting and calculations for each distinct region is avoided.
+
+The author's future work will provide a quantitative analysis of the results obtained from the coupled PCA-Linear regression method.
+Additionally, future work will present other methods which follow a similar principle but also seek to optimize the quantitative results obtained.
+
+%\section{Acknowledgements}
+%Mr Babatunde Lashore
+
+\clearpage
+\appendix
+\section{\\A Brief Introduction to SVD}\label{subsection:svd_brief}
 Given a matrix $\mathbf{A}\in\mathcal{R}^{m\times n}$, the singular value decomposition (SVD) is a method for factorizing $\mathbf{A}$, such that,
@@
 \end{equation}
-where $\mathbf{U}=\left[\underline{u}_{1},\underline{u}_{2},\cdots,\underline{u}_{m}\right]\in\mathcal{R}^{m\times n}$ and $\mathbf{V}=\left[\underline{v}_{1},\underline{v}_{2},\cdots,\underline{v}_{n}\right]\in\mathcal{R}^{m\times n}$ are orthogonal but not necessarily the same.
+where $\mathbf{U}=\left[\underline{u}_{1},\underline{u}_{2},\cdots,\underline{u}_{m}\right]\in\mathcal{R}^{m\times m}$ and $\mathbf{V}=\left[\underline{v}_{1},\underline{v}_{2},\cdots,\underline{v}_{n}\right]\in\mathcal{R}^{n\times n}$ are orthogonal but not necessarily the same.
 $\Sigma$ is a diagonal matrix, \ie
@@
 
-\subsection{Principal Component Spaces and Model Order Reduction for the permeability field}\label{subsection:pcspaces}
-
-\subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
-In 3D geometry, permeability is a tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), a 2D geometry is assumed where permeability is a scalar quantity.
-Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the 2D simulation domain.
-
-Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
-For simplicity, in the remaining part of this section, it will be assumed that the $2D$ geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
-This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
-
-The model order reduction for the permeability field discussed here is concerned with reducing the volume of permeability data within the permeability space.
-Consider for instance a small square which is discretized to contain four squares such that $4$ data points are defined in the middle of the four squares.
-The permeability space of $4$ can be reduced to a smaller value of $1$ through an averaging process such as arithmetic, harmonic or geometric mean.
-This type of reduction is the focus of this paper, albeit the main focus of this paper is achieving this reduction through SVD in the principal component spaces.
-
-\subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed through SVD to principal component spaces (PCS) where traditional principal component analysis is performed before interpolation is used to implement further data reduction in the principal component spaces.
-This reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
-
-The PCS is more challenging to visualize because it usually consists of more than 3-D.
-An aid for visualizing the PCS is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{U}$) as separate PCS.
-
-\subsubsection{Model Order Reduction/Principal Component Space Reduction}\label{subsubsection:svdcase_preprocess_algorithm}
-For the SVD model order reduction of the permeability field, all the work is done in the principal component spaces.
-This can be completed in two steps: the first step is the principal component analysis (PCA) \cite{Hotelling_1933}, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
-
-In the case with $z = r$, it can be assumed that step 1 has been ignored.
-However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
-The selected $z$ singular values also form a new diagonal matrix, $\mathbf{\Sigma_{new}}$ .
-
-The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
-From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
-The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
-
-\section{Model Description and Simulation Setup}\label{section:model_simulation}
-
-\subsection{Model Description}\label{subsection:model}
-The BaseCase  (\ie fine mesh resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
-These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
-Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
-
-The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
-Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
-Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
-More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
-Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
-Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
-
-As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field.
-When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
-The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).
-
-In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
-This effectively homogenizes the permeability field in each block.
-The upscaled permeability field for the third and fourth cases are referred to as PDFCase and SVDCase, respectively.
-And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively.
-The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
-It is appropriate to note that although these models (PDFCase and SVDCase) are upscaled, they retain heterogeneity within the blocks.
-
-\subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
-  \begin{enumerate}[a)]
-    \item \textbf{K1} : $700 - 900$ mD
-    \item \textbf{K2} : $50 - 150$ mD
-    \item \textbf{K3} : $100 - 200$ mD
-    \item \textbf{K4} : $1000 - 1200$ mD
-  \end{enumerate}                                                    
-  \item The number of data points generated for each block is $1600$ and the data values are randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
-  \item Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned dataset for each block.
-This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
-\end{enumerate}
-
-\subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The datasets from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) are used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase for each of the four blocks  (\ie $400$ data points for each block).
-  \item The data values in the dataset for each block is randomly positioned within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
-  \item Finally, the structured/arranged dataset from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
-\end{enumerate}
-
-\subsubsection{SVDCase Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
-  \item A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
-  \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
-These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
-  \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
-It is a permeability field with a quarter of the data values in the base case and therefore a permeability field with reduced order.
-\end{enumerate}
-
-\subsection{Simulations}\label{subsection:simulations}
-For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
-No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
-Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
-\begin{eqnarray}
-  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
-  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
-\end{eqnarray}
-where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively.
-$\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively.
-Exponents $n_{w}$ and $n_{nw}$ are both set to 2.
-
-Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
-\begin{displaymath}
-  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
-\end{displaymath}
-
-\section{Results and Discussion}\label{section:results_discussion}
-
-Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
-Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs.
-Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
-
-Figure~\ref{fig:PermFields} compares the permeability distribution for all the models.
-As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
-Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.
-
-This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and SVDCase cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous.
-Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase.
-An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution.
-Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.
-
-With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase.
-Meanwhile, the SVDCase will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
-Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block.
-However, the data value at a point in the SVDCase is directly related to the nearest data values with respect to the same point in the BaseCase, throught the interpolation which takes place in the PCS.
-
-Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case.
-However, with the SVDCase, knowledge of blocks with similar properties is not required prior to the upscaling.
-Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation.
-The limits of the techniques used for the SVDCase will be discussed in the author's future work.
-
-Before going on to review the results of the simulations, it is beneficial to briefly consider the Buckley-Leverett and cross-flow behaviour which are be used to validate the results from this work.
-
-\citet{buckley_1942} in 1942 derived the Buckley-Leverett equation, an analytical (albeit simplified) two phase flow equation.
-The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation.
-The equation is referred to as "simplified" because of the assumptions made while deriving it, some of which were ignored in this work.
-Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities.
-Additionally, the permeability field in each block is heterogeneous.
-However, the general validation test or expectation from Buckley-Leverett's influence on this work, is that, the injected fluid saturation in $K1$ and $K2$ is expected to have a piston-shape front within those blocks, subject some inconsistency at the boundary between the two blocks, and also within the blocks due to the heterogeneity.
-
-\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were somewhat replicated here for the simulations.
-Therefore, the work of \citet{dawe_2008} can be used to validate the resulting simulations from this work.
-In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$.
-Additionally, the cross-flow from $K1$ to $K4$ is well represented in the simulations.
-
-Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
-In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
-Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)).
-Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
-
-Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
-Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
-Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
-This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
-However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.
-
-Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
-This inconsistency is with respect to this realization of the PDFCase.
-Hence, SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
-
-\section{Conclusion}\label{section:conclusion}
-
-Upscaling is a form of model order reduction, and a method of implementing upscaling using singular value decomposition, SVD, is introduced in this work.
-The SVD method of upscaling first factorizes the matrix of the permeability field and then performs interpolation within the principal component space.
-The interpolated data in the principal component space is then recombined to form a reduced matrix of the permeability field.
-
-Results show that the permeability field data reduction can be specifically defined for the PDFCase and the SVDCase but not for the ArithMeanCase and the HarmMeanCase.
-This is because the latter cases will produce the same permeabiBuckleylity field irrespective of the upgrid resolution.
-The SVDCase is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.
-
-The author's future work will provide a statistical analysis of the technique used for the SVDcase and also presents other implementations of the technique.
-
-%\section{Acknowledgements}
-%Mr William Rad\"unz would like to acknowledge the support from the Brazilian Research Council (CNPq) under the \textit{Science without Borders scholarship programme}.
-Mr Konstantinos Christou would like to acknowledge the support of the University of Aberdeen - College of Physical Science as well as the Aberdeen Formation Evaluation Society (\textit{AFES} is an SPWLA chapter).
+\section{\\A Brief introduction to HOSVD}\label{subsection:hosvd_brief}
+Using the tensor notation from \citet{Kolda_2009}, given a tensor $\mathscr{X}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$, the higher order singular value decomposition (HOSVD) is a method for factorizing $\mathscr{X}$, such that,
+\begin{equation}
+  \mathscr{X} = \mathscr{G} \times_{1} \mathbf{U}^{1}\times_{2} \mathbf{U}^{2}\times \cdots \times_{m} \mathbf{U}^{m}.
+\end{equation}
+where tensor $\mathscr{G}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$ and is normally referred to the core tensor. Sub-tensors of $\mathscr{G}$ are orthogonal and ordered.\\
+And matrices $\mathbf{U}^{m}\in\mathcal{R}^{N_{m}\times N_{m}}$ are orthogonal factor matrices which could be thought of as the principal components in each mode
 

### 2018-12-02 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
Completed the new section on latest development in SVD aka 'PCA,SVD,KLT and Reservoir Characterisation'; Also updated references

@@
 
-Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}.
+Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001}.
 \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
@@
 The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.
+
+\subsection{PCA, SVD, POD, KLT and Reservoir Characterisation}\label{section:reservoir_char}
+
+PCA, SVD and POD are closely related.
+In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as the Karhunen-Loeve Transformation (KLT) \cite{Jafarpour_2009}.
+
+A lot of the recent research in the field of petroleum engineering field which use these techniques, focus on the problem of history matching \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}.
+History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.
+It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
+
+\citet{Jafarpour_2009} compares KLT to discrete cosine transform (DCT) and goes on to state that the DCT is computationally more efficient than the KLT while being almost as accurate.
+\citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible.
+Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.
+
+Perhaps, the works of \citet{Afra_2013}, \citet{Afra_2016}, \citet{Afra_2014}, \citet{Insuasty_2017} are more closely related to the one performed here.
+However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization.
+The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same CVFEM simulator used in this work.
+However, like the work of \citet{Tavakoli_2010}, the \citeauthor{Xiao_2018} were more interested in reducing the number of variable used to describe the system.
+
+Essentially, the recent developments in the field of petroleum engineering described here make use of SVD to select the most suitable realization from multiple realizations or to reduce the representative system variables.
+However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of one of the system variable (\ie{permeability}).
 

### 2018-12-02 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
Moved Appendix to end of figures
Updated figures in article_figure1.tex and re-arranged reference list within the manuscript so that they are listed in ascending order within the manuscript

@@
 In this element-pairs velocity is represented by $n^{\rm th}$-order polynomials that are discontinuous across elements, while pressure is represented by $m^{\rm th}$-order polynomials that may be either continuous (\PN[n]{m}) or discontinuous (\PNDG[n]{m}) across elements.
-Most properties of \PNDG[n]{m} element-pairs are similar to those in the \PN[n]{m} element-pairs but allows a representation in which pressure, saturation and other solution variables (\eg temperature, concentrations etc) are discontinuous across finite element boundaries \cite{salinas_2018,adam_2016}.
+Most properties of \PNDG[n]{m} element-pairs are similar to those in the \PN[n]{m} element-pairs but allows a representation in which pressure, saturation and other solution variables (\eg temperature, concentrations etc) are discontinuous across finite element boundaries \cite{adam_2016, salinas_2018}.
 
@@
 The discretised saturation and Darcy equations are solved using a multigrid-like approach as described by \citeauthor{pavlidis2016}~\cite{pavlidis2016}.
-The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{salinas2015,adam_2016}).
-These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{jackson_2013,Gomes_2017}).
+The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}).
+These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013}).
 Although, the numerical formulation used here is relatively new, it is not the focus of this work.
@@
 \clearpage 
+%% References with bibTeX database:
+\bibliographystyle{elsarticle-harv} 
+%\bibliographystyle{elsarticle-num}
+%\bibliographystyle{apacite}
+\bibliography{references}
+
+\clearpage
+
+%\listoftables
+%\clearpage
+%\input{article_table}
+\clearpage  
+\listoffigures
+\clearpage
+\input{article_figure1}
+
+\clearpage
 \appendix
@@
 
-\clearpage 
-%% References with bibTeX database:
-\bibliographystyle{elsarticle-harv} 
-%\bibliographystyle{elsarticle-num}
-%\bibliographystyle{apacite}
-\bibliography{references}
-
-\clearpage
-
-%\listoftables
-%\clearpage
-%\input{article_table}
-\clearpage  
-\listoffigures
-\clearpage
-\input{article_figure1}
-
 \end{document}

### 2018-12-02 Papers/AppliedMaths2018/Resubmission/article_figure1.tex
Updated figures in article_figure1.tex and re-arranged reference list within the manuscript so that they are listed in ascending order within the manuscript

--- 2018-04-15 Papers/AppliedMaths2018/article_figure1.tex
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
       \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
@@
 \vspace{0.cm}
-\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{3.75cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
+\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{1.0cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
 \vspace{0.5cm}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot15.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot15.png}
       \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_dot30.png}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot15.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot15.png}
       \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_dot30.png}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot15.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot15.png}
       \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_dot30.png}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot15.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot15.png}
       \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_dot30.png}
@@
 \vbox{\vspace{-1cm}
-\hbox{\includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot15.png}
+\hspace{0.0cm} \hbox{\includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot15.png}
       \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_dot30.png}
@@
 \vbox{\vspace{-1cm}
-\hbox{\hspace{4cm} \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15withlegend.png}
+\hspace{0.0cm} \hbox{\hspace{4cm} \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15withlegend.png}
       \hspace {1.5cm} \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot15.png}}
@@
 \clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
+
+%\begin{figure}[ht] 
+%\vbox{\vspace{-1cm}
+%\centering
+%\includegraphics[width=.56\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
+%\vspace{0.cm}
+%\vspace{0.5cm}
+%}   
+%\caption{Graphical illustration of model order reduction (initially used by \citet{Schilders2008}, with graphics credited to Harvard University, Microsoft Research.)}
+%\vspace{1.5cm}
+%\label{fig:IllustrationMOR}
+%\end{figure}
+
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hbox{\includegraphics[width=.56\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_MeshOnly.png}
+      \includegraphics[width=.56\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_MeshOnly.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.05cm} (a) 3-D High Resolution Grid (BaseCase) \hspace{0.05cm} (b) 3-D Low Resolution Grid (Upscaled Cases) \hspace{3.0cm}}
+\vspace{0.5cm}
+}   
+\caption{Mesh grid used in the performed numerical 3-D simulations: (a) high-resolution and (b) upscaled cases with 2019 and 303 tetrahedral elements respectively}
+\label{fig:HiRes_LowRes_3D_Mesh}
+\end{figure}
+
+%\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hspace{0.0cm} \hbox{\includegraphics[width=.8\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_PermField_withMesh2.png}
+      \includegraphics[width=.7\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_PermField_withoutMesh.png}}
+\vspace{0.cm}
+\hbox{(a) 3-D BaseCase (overlapped with the mesh) \hspace{3.75cm} (b) 3-D BaseCase (without Mesh)}
+\vspace{0.5cm}
+\hbox{\includegraphics[width=.7\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_PermField_withMesh.png}
+      \includegraphics[width=.7\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_PermField_withoutMesh.png}}
+\vspace{0.cm}
+\hbox{(c) 3-D HOSVD Case (overlapped with the mesh) \hspace{4.75cm} (d) 3-D HOSVD Case (without Mesh)}
+\vspace{0.cm}
+}   
+\caption{Permeability field for the 3D base case as well as the HOSVD upscaled cases (Permeability legend in Fig.~\ref{fig:3D_PermFields}(a) is representative for all the other figures - \ie Fig.~\ref{fig:3D_PermFields}(b) to (d))}
+\label{fig:3D_PermFields}
+\end{figure}
+\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+\begin{landscape}
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\hspace{0.0cm} \hbox{\includegraphics[width=.6\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_Saturation_tdot18withMesh2.png}
+      \includegraphics[width=.5\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_Saturation_tdot28.png}
+      \includegraphics[width=.5\textwidth]{./Pics/3D_BaseCase/3D_BaseCase_Saturation_tdot42.png}}
+\vspace{0.cm}
+\hbox{\hspace{0.5cm} (a) 3-D BaseCase at t=0.18s \hspace{1.0cm} (b) 3-D BaseCase at t=0.28s \hspace{3.0cm} (c) 3-D BaseCase at t=0.42s}
+\vspace{0.5cm}
+\hbox{
+      \includegraphics[width=.5\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_Saturation_tdot18withMesh.png}
+      \includegraphics[width=.5\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_Saturation_tdot28.png} 
+      \includegraphics[width=.5\textwidth]{./Pics/3D_HOSVDCase/3D_HOSVDCase_Saturation_tdot42.png}}
+\vspace{0.cm}
+\hbox{ \hspace{1.5cm} (d) HOSVD Case at t=0.18s \hspace{1.0cm} (e) HOSVD Case at t=0.28s  \hspace{3.0cm} (f) HOSVD Case at t=0.42s}
+\vspace{0.cm}
+}   
+\caption{Comparing phase 1 saturation distribution for the 3-D Cases at $t=0.18, 0.28$ and $0.42$ s (Saturation legend in Fig.~\ref{fig:Saturationfield4_3DCases}(a) is representative for all the other figures - \ie Fig.~\ref{fig:Saturationfield4_3DCases}(b) to (e))}
+\label{fig:Saturationfield4_3DCases}
+\end{figure}
+\end{landscape}
+\clearpage

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

--- 2018-12-02 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
@@
 
-\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
+%\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
+\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
@@
 Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
+\red{Later}
 
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-Principal Component Analysis (PCA) and Linear Regression \sep Singular Value Decomposition (SVD) and Higer Order Singular Value Decomposition (HOSVD) \sep Upscaling\sep Reduced Order Models (ROM), \sep Permeability field \sep Heterogeneity
+Principal Component Analysis (PCA) \sep Linear Regression \sep Higher-Order Singular Value Decomposition (HOSVD) \sep Upscaling \sep Reduced Order Models (ROM) \sep Permeability.  
 \end{keyword}

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \section{Introduction}\label{section:intro}
-Naturally occuring rock formations are inherently heterogeneous, which means that rock properties such as permeability, pore spaces (\ie porosity) and pore throat vary spatially at different length scales.
+Naturally occuring rock formations are inherently heterogeneous, which means that geophysical properties, such as permeability, pore spaces (\ie porosity) and pore throat vary spatially at different length scales.
 Heterogeneity of rock formations is relevant in calculations of transport and storage of fluids in porous media (\ie multiphase flow in subsurface rocks).
@@
 It is possible to overcome these challenges by a family of techniques called {\it upscaling}.
-Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high-resolution domains with coarse descriptions (\ie low-resolution) of these properties \cite{Vereecken_2007}.
 
-Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of heterogeneous properties.
+Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of high-resolution domains give the best statistical representation of heterogeneous properties.
 There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of high-resolution domains give the best statistical representation of heterogeneous properties.
+Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of high-resolution domains give the best representation of heterogeneous properties.
 There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of high-resolution domains give the best representation of heterogeneous properties.
-There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
+Upscaling techniques which best preserve statistical geophysical and thermo-physical properties of high-resolution domains result in optimal prediction of fluid flow dynamics.
+Over the past 60 years, several upscaling techniques were developed (see \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}).
 Traditional upscaling techniques are deterministic in nature, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
-One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media and they are able to address scaling and uncertainity problems.
+One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media and they are able to address scaling and uncertainity problems.statistical
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \medskip
-{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
+{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
 Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 {\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
-Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction.
-The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}.
+Depending on the context in which MOR is used, it can be simply referred as `dimensionality reduction'.
+The definition of MOR also depends on the context in which it is used, but it suffices to state that MOR's are ale to captures essential features of a system, structure or parameter \cite{Schilders2008}.
 This implies that an original system exists with more detailed information.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998 which introduced Passive Reduced-order Interconnect Macromodeling Algorithm (PRIMA).
-Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998, which introduced the passive reduced-order interconnect macromodeling algorithm (PRIMA).
+Truncated balanced realization is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
 Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Truncated balanced realization is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
+Hankel-norm reduction \cite{Glover_1984} and proper orthogonal decompositions (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
-In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively.
 
 \bigskip
+ In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively.
 This work focuses on reducing the order of permeability distribution in porous media flow simulations.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \bigskip
- In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively.
+ In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems.
 This work focuses on reducing the order of permeability distribution in porous media flow simulations.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
  In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems.
-This work focuses on reducing the order of permeability distribution in porous media flow simulations.
+This work focuses on reducing the order of permeability distribution for porous media flow simulations.
 Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
-The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.
+The mathematical model is discretised by a high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017}.
 Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
-Four upscaling techniques are investigated in this work and they are named Arithmetric mean, Harmonic mean, probability density function (PDF) and PCA (using SVD for 2D models and HOSVD for 3D model) coupled with linear regression.
+Four upscaling techniques are investigated in this work and they are named arithmetric mean, harmonic mean, probability density function (PDF) and PCA (using SVD and HOSVD methods) coupled with linear regression.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Section~\ref{section:model_simulation} is dedicated to model description and simulation.
-It starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to.
-A brief summary of the pre-processing step for each of the models is also presented.
+It starts by describing the high-resolution problem (\ie `base case') in which the four upscaling techniques are applied to.
+A brief summary of the pre-processing steps for each of the models is also presented.
 Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 A brief summary of the pre-processing steps for each of the models is also presented.
-Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique.
-Finally, Conclusions are drawn in Section~\ref{section:conclusion}.
+Section~\ref{section:results_discussion} provides the results and further discussion of the results, it also gives further interpretation to the result obtained from the SVD upscaling technique.
+Finally, conclusions are drawn in Section~\ref{section:conclusion}.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
+\section{Upscaling}
 \subsection{Brief Overview of Upscaling}\label{section:overview_upscaling}
 
-Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-This subject of upscaling heterogenous properties has interested industries (\ie oil and gas, CCS and waste management) as well as the academic community for over $7$ decades.
+Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}.
+Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades.
+Those interested in large-scale reservoirs or groundwater generally take a two-stage geo-statistical approach.
 
-Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach.
-In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
-In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
-In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
+In the first stage, information from seismic data, well data and analogous outcrops is used to model the large-scale heterogeneities associated with facies.
+In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model rock properties of the facies \cite{Ewing_1997}.
+In addition to seismic and well data used in the previous stage, core data can be used as a source of information for the statistical properties used to determine random fields in this stage.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001}.
+A number of studies were carried out on upscaling of subsurface permeability (see \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001} for a few key references).
 \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
-The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
+The general conclusion reached from this study was that the equivalent permeability lies between harmonic and arithmetic averages.
 
@@
 \end{equation}
-are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{pavlidis_2013b}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
+are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{pavlidis_2016}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
 
@@
 %% End of tex file.
+
+%%  LocalWords:  renormalization

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Both cases employed the $4$-quadrant model (see Section~\ref{subsection:model} for details) set-up.
-The first case had low permeablitity in all the blocks except the bottom right block which had high permeability, while the second case employed the checkboard style described in Section~\ref{subsection:model}.
+The first case had low permeability in all blocks except the bottom right block which had high permeability, while the second case employed the check-board style described in Section~\ref{subsection:model}.
 Different conductivity ratios were also investigated for the two cases.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other.
-\citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
-
-\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators.
-The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.
+They also recommended to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.
+Finally, \citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding (\ie mesh coarsening) techniques of different simulators.
+The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for flow simulation models' benchmarking.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 PCA, SVD and POD are closely related.
-In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as the Karhunen-Loeve Transformation (KLT) \cite{Jafarpour_2009}.
+In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as Karhunen-Loeve Transformations (KLT) \cite{Jafarpour_2009}.
 
-A lot of the recent research in the field of petroleum engineering field which use these techniques, focus on the problem of history matching \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}.
+A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
 History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
-History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.
+History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) of a reservoir, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
 It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

--- 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
@@
 A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
-History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.
+History matching is the process of building or adjusting one or more sets of models for a reservoir, such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
 It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

--- 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
@@
 A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
-History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.
-It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
+History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
+It is important to note that reservoir configurations could be either a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
 
-\citet{Jafarpour_2009} compares KLT to discrete cosine transform (DCT) and goes on to state that the DCT is computationally more efficient than the KLT while being almost as accurate.
+\citet{Jafarpour_2009} compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate.
 \citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
+A number of recent research in reservoir engineering focus on  history matching (HM) problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
 History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
@@
 \citet{Jafarpour_2009} compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate.
-\citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible.
-Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.
+\citet{Tavakoli_2010} noted that HM calculation of sensitivities for all production data with respect to system parameters is not feasible.
+Hence, they explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matrix.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Perhaps, the works of \citet{Afra_2013}, \citet{Afra_2016}, \citet{Afra_2014}, \citet{Insuasty_2017} are more closely related to the one performed here.
+Perhaps, work performed by \citet{Afra_2013,Afra_2016,Afra_2014} and \citet{Insuasty_2017} are more closely related to the one performed here.
 However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization.
-The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same CVFEM simulator used in this work.
-However, like the work of \citet{Tavakoli_2010}, the \citeauthor{Xiao_2018} were more interested in reducing the number of variable used to describe the system.
+The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same flow simulator model used in this work.
+However, similarly to \citet{Tavakoli_2010}, \citeauthor{Xiao_2018} focused on reducing the number of variable used to describe the system.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 This work focuses on reducing the order of permeability distribution for porous media flow simulations.
+
+\bigskip
+A brief overview of current upscaling methods in reservoir simulation is described in Section~\ref{section:general_upscaling}.
 Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
@@
 Four upscaling techniques are investigated in this work and they are named arithmetric mean, harmonic mean, probability density function (PDF) and PCA (using SVD and HOSVD methods) coupled with linear regression.
-
 In Section~\ref{section:pca_linreg}, fundamental mathematics of SVD and associated properties are presented.
@@
 
-\section{Upscaling}
+\section{Upscaling}\label{section:general_upscaling}
 \subsection{Brief Overview of Upscaling}\label{section:overview_upscaling}
@@
 
-Essentially, the recent developments in the field of petroleum engineering described here make use of SVD to select the most suitable realization from multiple realizations or to reduce the representative system variables.
-However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of one of the system variable (\ie{permeability}).
+Essentially, recent developments in the field of reservoir simulation described in this section make use of SVD theory to select the most suitable realization from multiple realizations or to reduce the representative system variables.
+However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of a single system variable (\ie{permeability}).
 
@@
 Continuity equations are embedded into the pressure equation to enforce mass conservation and the exact force balance (extended Darcy equations).
-The numerical formulation employs an implicit algorithm with respect to time which is less restrictive than the traditional industry-standard implicit-pressure-explicit-saturation (IMPES) scheme \cite{aziz_1986,geiger_2004}.
+The numerical formulation employs an implicit algorithm with respect to time which is less restrictive than the traditional industry-standard implicit-pressure-explicit-saturation (IMPES) scheme \cite{aziz_1986,Chen_2007}.
 
@@
 where $\alpha$ designates a phase, $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity and $\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are phase dynamic viscosity, pressure, density and source term (which may include gravity and/or capillarity), respectively.
 $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is a function of the vector position $\mathbf{r}$, and time, $t$.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 $\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are phase dynamic viscosity, pressure, density and source term (which may include gravity and/or capillarity), respectively.
-$\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is a function of the vector position $\mathbf{r}$, and time, $t$.
+$\mathbf{K}\left(\mathbf{r}\right)$ and $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ are absolute and phase-relative permeability, respectively.
+The later is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is spatial- and time-dependent.
 
@@
 \end{equation}
-are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{pavlidis_2016}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
+are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{gomes_book_2012}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
 
@@
 The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}).
-These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013}).
+These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}).
 Although, the numerical formulation used here is relatively new, it is not the focus of this work.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation.
-However, more extensive validation tests can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
+However, extensive model and software quality assurance (\ie verification and validation tests) can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \medskip
-Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is the absolute permeability tensor of the porous medium and it is a function of the vector position $\mathbf{r}$.
-$\mathbf{K}$ is prescribed in the system of governing conservative equations, \ie it is an indepedent input variable.
-Since $\mathbf{K}$ is a petrophysical rock property that varies spatially, it cannot be determined at every spatial coordinate.
+Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is prescribed in the system of governing conservative equations, \ie it is an independent input variable.
+Since $\mathbf{K}$ is a petrophysical property of geological formations that varies spatially, it cannot be determined at every grid point (\ie spatial coordinate).
 And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations.
-This is the reason upscaling is required for processing permeability variables.
-Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($km$)\cite{ECMI_2004}.
-The upscaling discussed here is from the micro scale also known as the Darcy scale.
+This is the reason upscaling is required for processing permeability spatial variability.
+Upscaling can be performed from the continuum scale, across the micro-scale ($mm$), local- and meso-scale ($m$) to field-scale ($km$)\cite{ECMI_2004}.
+The upscaling discussed here is for micro-scale, also known as the Darcy scale.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-\section{PCA coupled with Linear Regression}\label{section:pca_linreg}
+\section{Coupled PCA and Linear Regression}\label{section:pca_linreg}
 
@@
 \subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
-Permeability can be represented as tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), it is assumed that permeability is a scalar quantity.
+Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity.
 Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity.
-Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.
-
-Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
-For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed where the geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
-This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
+In addition, in the numerical simulations performed for this work, permeability is discretised element-wise with projection to the control volume space within each element-pairs (see \cite{Christou_2018}).
+Permeability values are assigned to the centre of the FE $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
+For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed which is discretized with triangular elements (\PN[1]{2} and \PNDG[1]{1} element-pairs).
+This explanation allows one to easily visualize this permeability space because it is defined by Cartesian coordinate system.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed with SVD for 2D permeability field and HOSVD for 3D permeability fields, to principal component spaces (PCS).
+Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability fields, respectively) to principal component spaces (PCS).
 Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability fields, respectively) to principal component spaces (PCS).
+Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS).
 Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS).
-Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces.
+Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, Section~\ref{subsubsection:pca_dimred_linreg}), before interpolation is used to implement further data reduction in PCS.
 The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
-An algorithm which impliments the procedure described here, is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
+An algorithm which impliments the procedure described here is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
 
-The PCS is a bit challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
+The PCS is a slightly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
 An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-The PCS is a slightly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
+The PCS is a particularly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
 An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

--- 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
@@
 
-The PCS is a slightly challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
-An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
-A similar intuition can be extended to HOSVD for 3D permeability fields.
+The PCS is a particularly challenging to visualize as it represents projections which are embedded in SVD/HOSVD factors of the original permeability dataset.
+An aid for visualizing the PCS for a 2D permeability data is to write out $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
+A similar procedure can be extended to HOSVD for 3D permeability dataset.
 The decomposition of a matrix into its factors using SVD \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials.
-However, for completeness, the appendix contains a brief introduction to SVD (\ref{subsection:svd_brief}) and HOSVD (\ref{subsection:hosvd_brief}).
+However, for completeness, \ref{subsection:svd_brief} and \ref{subsection:hosvd_brief} contain brief overviews of SVD and HOSVD, respectively.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
-For the PCA-Linear regression (PCA-LinReg) reduced order model of the permeability field, all the work is done in the principal component spaces.
-This can be completed in two steps, which is exemplified for the 2D model thus:
-\begin{enumerate}
-  \item The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+For the PCA-Linear regression reduced order model (PCA-LinReg) of the permeability data, all work is performed in PCS. This can be conducted in two steps (for 2-D models), thus:
+\begin{description}
+  \item[Step 1:] The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
 
@@
 
-\item The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+\item[Step 2:] The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
@@
 
-\end{enumerate}
+\end{description}
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \begin{description}
-  \item[Step 1:] The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
-
-Note that, in the case with $z = r$, it can be assumed that step 1 has been ignored.
+  \item[Step 1:] Perform PCA \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+Note that, in the case with $z = r$, it can be assumed that {\it Step 1} has been ignored.
 However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
@@
 
-\item[Step 2:] The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+  \item[Step 2:] Interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) is conducted to reduce the number of data points in each column of $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-It is trivial to show that these two steps can be replicated for a 3-D model using HOSVD to obtain the PCA space.\\
+These two steps can be readily replicated for 3-D models using HOSVD to obtain the PCA space.
 
-Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space\cite{Tharwat_2016} , namely, the co-variance method and the SVD method.
-\citet{Tharwat_2016} goes on to describe both methods in details.
-In this work, the authors have opted to use the SVD method to obtain the PCA space.
-This is because the singular vectors which make up the PCS have a strong correlation to the coordinate axis they represent.
+Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space: co-variance and SVD methods (see \cite{Tharwat_2016} detailed description of both methods).
+In this work, the authors have opted to use the SVD method to obtain the PCA space, as singular vectors which make up the PCS have strong correlation to the coordinate axis they represent.
 This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
-The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure below.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure XXX.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/article_figure1.tex
Updated the PCA_is_not_LinRig figure in article_figure1.tex and appropriately reference said figure in Stochastic_Upscaling_UK_AMM_2018.tex

@@
 \centering
-\includegraphics[width=.56\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
+\includegraphics[width=.72\textwidth]{./Pics/Introduction/Graphical-illustration-of-model-order-reduction.png}
 \vspace{0.cm}
@@
 
+\begin{figure}[ht] 
+\vbox{\vspace{-1cm}
+\centering
+\includegraphics[width=.72\textwidth]{./Pics/PCA_LinReg/PCA_is_not_LinReg.png}
+\vspace{0.cm}
+\hbox{\hspace{0.25cm} (a) Linear regression \hspace{2cm} (b) PCA \hspace{3.0cm}}
+\vspace{0.5cm}
+}   
+\caption{Graphical comparision between linear regression and PCA (extracted from \citet{AndrewNg_2018})}
+\vspace{1.5cm}
+\label{fig:PCA_is_not_LinReg}
+\end{figure}
+%\end{landscape}
+\clearpage
+
+%%%%
+%%%%  FIGURE
+%%%%
+%\begin{landscape}
 \begin{figure}[ht] 
@@
 \end{figure}
-
 %\end{landscape}

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex

@@
  \hline
-  & PCA & Linear Regression \\ [0.5ex] 
+  & \begin{center}{\bf PCA}\end{center} & \begin{center}{\bf Linear Regression}\end{center} \\ [0.5ex] 
  \hline
- 1 & Determines the best vector (or set of vectors) which compresses the data points by minimizing the orthogonal distance to the points & Approximates the best fit line for the points by minimizing the error \\
+ 1 & Determines the best vector (or set of vectors) which compresses the data points by minimizing the orthogonal distance to the points & Approximates the best fit for the points by minimizing the error \\
  \hline
@@
 \end{tabular}
-\caption{Table comparing PCA with Linear Regression}
+\caption{Table comparing PCA with Linear Regression.}
 \label{table:pca_vs_linreg}

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex

@@
 Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
-The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case).
+The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie `base case').
 The fourth upscaling technique is the crux of this research, it introduces a reduced order model which couples PCA and linear regression.
@@
 \subsection{Model Description}\label{subsection:model}
-The BaseCase  (\ie fine mesh resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
-These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
+The BaseCase  (\ie high-resolution mesh) model for the permeability field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+These authors designed the permeability field for the quadrants in a checker-board style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
 Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex

@@
 \citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
-The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure below.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure~\ref{fig:PCA_is_not_LinReg}.
 
@@
 \end{table}
-
-\red{I need to plot a figure here.}
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min
updates

@@
 \subsection{Model Description}\label{subsection:model}
-The BaseCase  (\ie high-resolution mesh) model for the permeability field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
-These authors designed the permeability field for the quadrants in a checker-board style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
+The BaseCase  (\ie high-resolution mesh) configuration for the permeability dataset builds on the $2 \times 2$ block, \ie $4$ quadrant model orginally used by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+In the domain designed by these authors, permeability is represented as checker-board in which diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
 Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
@@
 Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
-More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
+More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}.
 Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

@@
 
-The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
-Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
-Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
+The BaseCase permeability model used here retains the checkerboard desgined used by these references.
+Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to).
+%, although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+Furthermore, within each block, permeability dataset varies within a pre-defined range and consists of $1600$ permeability values.
 More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}.
-Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
+Figures~\ref{fig:PermFields}a-b are pictorial representations of the permeability dataset for the base case with the mesh discretization visible and invisible, respectively.
 Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex

@@
 Furthermore, within each block, permeability dataset varies within a pre-defined range and consists of $1600$ permeability values.
-More details on the design of the permeability field for the BaseCase is described in Section~\ref{subsubsection:basecase_preprocess_algorithm}.
-Figures~\ref{fig:PermFields}a-b are pictorial representations of the permeability dataset for the base case with the mesh discretization visible and invisible, respectively.
+Details on the design of the permeability field for the BaseCase are described in Section~\ref{subsubsection:basecase_preprocess_algorithm}.
+Figures~\ref{fig:PermFields}a-b show permeability distribution for the BaseCase with the associated mesh resolution.
 Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field.
-When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
-The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).
-
-In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
-This effectively homogenizes the permeability field in each block.
-The upscaled permeability field for the third and fourth cases are referred to as PDFCase and PCA-LinReg Case, respectively.
-And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively.
-The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
-It is appropriate to note that although these models (PDFCase and PCA-LinReg Case) are upscaled, they retain heterogeneity within the blocks.
+As previously mentioned, four upscaled techniques applied to permeability dataset were obtained from the high-resolution (\ie the BaseCase) configuration.
+Prior to upscaling, mesh resolution of the BaseCase configuration was coarsened, Fig.~\ref{fig:HiRes_LowRes_Mesh}, in which the number of triangular elements was reduced from 4112 to 728.
+Arithmetic (ArithMean) and harmonic (HarmMean) averaging methods were initially applied to the BaseCase configuration.
+In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain permeability values for each block in the upscaled models.
+This effectively homogenized the permeability dataset in each block.
+Permeability dataset was also upscaled using probability density function (PDFCase) and SVD (PCA-LinReg Case).
+Description of these models are introduced in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm}-\ref{subsubsection:svdcase_preprocess_algorithm}.
+Different from ArithMean and HarmMeanand, PDFCase and PCA-LinReg Case are able to retain heterogeneity within each block.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex

@@
       \begin{enumerate}
-      \item \label{R_E_P1} \blue{....................}
+      \item \label{R_E_P1} \blue{We deduced that the comment was a request for reference list within the manuscript (where more than one reference is cited) to be rearranged in ascending and and for reference source document (\ie{reference.bib}) to contain only the materials cited.
+Both tasks have been completed, however, we remain willing to quickly correct any other issue we may have overlooked.}
         \end{enumerate}
-      \BLnote{I do not understand/I cannot see the issue the editor is referring to here}
       \end{enumerate}    
@@
       \item \label{R_R1_Novelty_P4} \blue{The amendment to the manuscript draws a distinction between SVD and linear regression (which is simply implimented here by interpolation) in the context of parameterization}\\
+        \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
    \end{enumerate}
-      \blue{\bf{Manuscript Title before Amendment:}}
-      \begin{center}
-        \blue{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
-        \end{center}
-      \blue{\bf{Manuscript Title after Amendment:}}
-      \begin{center}
-        \blue{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using Singular Value Decomposition (SVD) or Higer Order Singular Value Decomposition (HOSVD): Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
-      \end{center}
-      \blue{\bf{Manuscript body before Amendment:}}\\
-      \\
-      \\
-      \blue{\bf{Manuscript body after Amendment:}}\\
-      \\
-      \\
+      \end{enumerate}
     \item \label{R_R1_OverSimplification} It uses a very simplistic approach and many important questions are left in this paper.
@@
         These changes remove the simplification and the authors also hope they answered the important questions that the reviewer implied remained unanswered.
-The authors remain willing to provide a direct answer to any unanswered questions which are explicitly stated.}
+The authors remain willing to provide a direct answer to any unanswered questions which are explicitly stated.}\\
+        \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
 Some of these papers were originally excluded from the manuscript initially because they were not related to upscaling.
-In line with the author's response at \ref{R_R1_Novelty}, the difference between the work in those papers and the authors' work are highlighted to draw out the uniqueness of the current work}
+In line with the author's response at \ref{R_R1_Novelty}, the difference between the work in those papers and the authors' work are highlighted to draw out the uniqueness of the current work}\\
+        \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
       \begin{enumerate}
-      \item \label{R_R1_CompEffort} \blue{..........}
+      \item \label{R_R1_CompEffort} \blue{..........}\\
+        \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
 Therefore, corrections have been made to the manuscript to clarify that the CVFEM simulator is not the main focus of the work.\\
-Further to the explanation provided in the response at \ref{R_R1_Novelty}, while PCA (with respect to SVD or HOSVD) and linear regression are not new, the authors believe that the manner in which they (\ie PCA and linear regression) have been combined and applied to achieve dimensionality reduction for the problem at hand is novel}
+        Further to the explanation provided in the response at \ref{R_R1_Novelty}, while PCA (with respect to SVD or HOSVD) and linear regression are not new, the authors believe that the manner in which they (\ie PCA and linear regression) have been combined and applied to achieve dimensionality reduction for the problem at hand is novel}\\
+        \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
    \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment.
-The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}
+The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}\\
+     \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
          \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive.
-These have been reduced from 86 to the most relevant 9 \red{update the number 9 after including figures for the 3D simulations} (which are included in the manuscript).
-Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}
+These have been reduced from 86 to the most relevant 12 (which are included in the manuscript).
+Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}\\
+           \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
    \item \label{R_R2_TooMuchSum_1} \blue{The authors thank the reviewer for the comment, as advised, the latter part of the introduction has been made brief.
-Additionally, the extensive details in the introduction section which was referred to has been moved to the section on "Model Description and Simulation Setup".}
+Additionally, the extensive details in the introduction section which was referred to has been moved to the section on "Model Description and Simulation Setup".}\\
+     \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
    \begin{enumerate}
-      \item \label{R_R2_NumFormulation_1} \blue{..........}
+   \item \label{R_R2_NumFormulation_1} \blue{..........}\\
+     \blue{Please see the following sections in the tracked revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
  \begin{enumerate}
-      \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}
+ \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}\\
+   \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
     \end{enumerate}
@@
   \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section has been moved to the appendix.
-Additionally, as mentioned in the response at \ref{R_R1_OverSimplification_P1}, a newly introduced section titled ``A brief Introduction to HOSVD'' was also moved to the appendix.}
+Additionally, as mentioned in the response at \ref{R_R1_OverSimplification_P1}, a newly introduced section titled ``A brief Introduction to HOSVD'' was also moved to the appendix.}\\
+    \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
   \begin{enumerate}
-      \item \label{R_R2_TensorCorrection_1} \blue{The authors appreciate the reviewer's correction and apologizes for the oversight. Section 4.2.1 has now been properly edited}
+  \item \label{R_R2_TensorCorrection_1} \blue{The authors appreciate the reviewer's correction and apologizes for the oversight. Section 4.2.1 has now been properly edited}\\
+     \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
         \end{enumerate}
@@
  \begin{enumerate}
-      \item \label{R_R2_GeomSetupAlgorithm_1} \blue{The authors thank the review for the feedback, starting the section directly on 2D simulation if only a 2D simulation is presented in the work.
-The recommended changes have been made and for completeness, some work on 3D simulations have now been included in the manuscript} \red{................response to creating algorimthm required.........}
+ \item \label{R_R2_GeomSetupAlgorithm_1} \blue{The authors thank the review for the feedback, the recommendations with regards to the 2D geometry discussion as been made.
+And, as suggested for 4.2.2 and 4.2.3 (now 4.1.2 and 4.1.3, respectively), the subsections have been amended to provides references for SVD (and HOSVD) as well as PCA.
+Additionally, the manuscript text has been re-worded so that the section previuosly referred to as 4.2.2 refers to algorithms at 4.1.3 and 5.1.3; and Section 4.2.3 (now 4.1.3) has been written as an algorithm}\\
+   \blue{Please see the following sections in the tracked version of the revised manuscript}
+   \begin{enumerate}
+ \item \blue{.......}
+   \end{enumerate}
  \end{enumerate}
@@
 
-\encl{Cover\_letter\_for\_resubmission.pdf, Highlight\_revised.pdf, Manuscript\_sourceFiles(Makefile, Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.tex, article\_/figure1.tex, Pics Folder, references.bib, elsarticle.cls, elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"
+\encl{Cover\_letter\_for\_resubmission.pdf,\\
+  Highlight\_revised.pdf,\\
+  Stochastic\_Upscaling\_UK\_AMM\_2018\_TrackedRevision.pdf,\\
+  Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.pdf,\\
+  Manuscript\_sourceFiles(Makefile,\\
+  Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.tex,\\
+  article\_figure1.tex,\\
+  Pics Folder,\\
+  references.bib,\\
+  elsarticle.cls,\\
+  elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
+\begin{description}
+  \item[Step 1:] A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
   \begin{enumerate}[a)]
-    \item \textbf{K1} : $700 - 900$ mD
-    \item \textbf{K2} : $50 - 150$ mD
-    \item \textbf{K3} : $100 - 200$ mD
-    \item \textbf{K4} : $1000 - 1200$ mD
+    \item \textbf{K1} : $700 - 900$ mD;
+    \item \textbf{K2} : $50 - 150$ mD;
+    \item \textbf{K3} : $100 - 200$ mD;
+    \item \textbf{K4} : $1000 - 1200$ mD;
   \end{enumerate}                                                    
-  \item The number of data points generated for each block is $1600$ and the data values are randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
-  \item Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned dataset for each block.
-This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
-\end{enumerate}
+  \item[Step 2:] The number of data points generated for each block is $1600$, and data is randomly distributed within each block in a structured pattern. Albeit, the mesh is unstructured;
+  \item[Step 3:] Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' ({\it Step 1}) for the randomly positioned dataset for each block.
+This data-structure will be used by the CVFEM-based flow simulator to prescribe the permeability dataset for the BaseCase configuration.
+\end{description}
 
 \subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The datasets from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) are used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase for each of the four blocks  (\ie $400$ data points for each block).
-  \item The data values in the dataset for each block is randomly positioned within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
-  \item Finally, the structured/arranged dataset from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
-\end{enumerate}
+\begin{description}
+  \item[Step 1:] Datasets from {\it Step 1} of Section~\ref{subsubsection:basecase_preprocess_algorithm} are used to calculate mean and standard deviation for each block of permeability data;
+  \item[Step 2:] A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase configuration for each of the four blocks (\ie $400$ data points for each block);
+  \item[Step 3:] Data values in the dataset for each block is randomly positioned within each block in a structured pattern.
+Similarly to the BaseCase configuration, simulation mesh grid is also unstructured;
+  \item[Step 4:] Finally, the structured/arranged dataset from each block is combined into a single data-structure and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs (in simulations shown here, \PN[1]{2} and \PNDG[1]{1} element-pairs are used).
+\end{description}
 
-\subsubsection{2-D PCA (\ie{using SVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
-  \item A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
-(This step is optional, it is the conventional PCA dimensionality reduction)
-  \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-(This step is necessary only if the optional step in 2 above is executed)
-  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
-These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
-  \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
-It is a permeability field with a quarter of the data values in the base case and therefore a permeability field with reduced order.
-\end{enumerate}
+\subsubsection{2-D PCA (SVD) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
+\begin{description}
+  \item[Step 1:] Permeability data obtained in {\it Step 3}  of Section~\ref{subsubsection:basecase_preprocess_algorithm} is factorized using SVD method to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$;
+  \item[Step 2:] A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$ (this step is optional as it is the conventional PCA dimensionality reduction);
+  \item[Step 3:] First $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices called $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, respectively.
+This step is necessary only if the optional step in 2 above is executed;
+  \item[Step 4:] Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
+These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$;
+  \item[Step 5:] Permeability dataset used for the PCA-LinReg Case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+It is a permeability dataset with a quarter of the data values of the BaseCase, \ie a permeability dataset with reduced order.
+\end{description}
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 The algorithm for the 3-D case is similar to that of the 2-D case described above. However:
-\begin{enumerate}[1.]
-\item In step 1 above, HOSVD is used for factorization instead of SVD.
-Therefore, a $3 x 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$.
-  \item It goes without saying that the core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section \ref{subsubsection:svdcase_preprocess_algorithm} above.
-\end{enumerate}
+\begin{description}
+  \item[Step 1:] In {\it Step 1} of Section~\ref{subsubsection:svdcase_preprocess_algorithm}, HOSVD method is used for factorization instead of SVD.
+Therefore, a $3 \times 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$;
+  \item[Step 2:] The core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section~\ref{subsubsection:svdcase_preprocess_algorithm}.
+\end{description}
 The authors found the updated Tensorly library package \cite{Tensorly_2018} helpful in implimenting and executing the algorithm for HOSVD.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsubsection{3-D PCA (\ie{using HOSVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:hosvdcase_preprocess_algorithm}
-The algorithm for the 3-D case is similar to that of the 2-D case described above. However:
-\begin{description}
-  \item[Step 1:] In {\it Step 1} of Section~\ref{subsubsection:svdcase_preprocess_algorithm}, HOSVD method is used for factorization instead of SVD.
+The algorithm for 3-D case is similar to that of the 2-D case described previously. However:
+\begin{enumerate}[1.]
+  \item In {\it Step 1} of Section~\ref{subsubsection:svdcase_preprocess_algorithm}, HOSVD method is used for factorization instead of SVD.
 Therefore, a $3 \times 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$;
-  \item[Step 2:] The core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section~\ref{subsubsection:svdcase_preprocess_algorithm}.
-\end{description}
-The authors found the updated Tensorly library package \cite{Tensorly_2018} helpful in implimenting and executing the algorithm for HOSVD.
+  \item The core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section~\ref{subsubsection:svdcase_preprocess_algorithm}.
+\end{enumerate}
+The authors found that the Tensorly library package \cite{Tensorly_2018} helpful for implementation of the HOSVD algorithm.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \subsection{Simulations}\label{subsection:simulations}
-For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
-No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
-Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
+In all performed numerical simulations, the domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
+A no-flux boundary conditions were imposed on upper and lower borders of the domain, while mixed fluids left the domain from the right-hand border of the domain.
+Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations, is described in the pore rock matrix by the modified \citet{Brooks_1964} (see \citep{alpak_1999}),
 \begin{eqnarray}
@@
 
-Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+Figure~\ref{fig:PermFields} shows permeability mapping for all cases, whereas Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
 \begin{displaymath}

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
+Additionally, the number of \PN[1]{2} triangular element-pairs mesh resolution was reduced from $4112$ (BaseCase, Fig,~\ref{fig:HiRes_LowRes_Mesh}a) to $728$ (upscaled cases, Fig,~\ref{fig:HiRes_LowRes_Mesh}b), a reduction by a factor of approximately $5.6$.
+
 \section{Results and Discussion}\label{section:results_discussion}
-
-Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
-Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs.
-Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 \section{Results and Discussion}\label{section:results_discussion}
+After reduction of dimensionality of the permeability dataset using the methods described in Sections~\ref{subsection:pcspaces} and \ref{subsection:model}), numerical simulations were performed with Fluidity/IC-FERST model (see Section~\ref{section:mathematical_model} and \cite{Gomes_2017, jackson_2013,salinas_2018}).
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Figure~\ref{fig:PermFields} compares the permeability distribution for all the models.
-As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
-Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.
-
-This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and PCA-LinReg cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous.
-Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the PCA-LinReg Case give a better representation of the BaseCase.
-An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution.
-Whereas, for the PDFCase and the PCA-LinReg Case, the permeability field will change if the upgrid resolution changes.
+Figure~\ref{fig:PermFields} shows permeability distribution for all cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous.
+Given that the BaseCase is also heterogeneous, it can be stated that models for the PDFCase and PCA-LinReg Case give a qualitatively better representation of the permeability dataset within the BaseCase.
+An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the coarsening has no influence on the resulting permeability distribution.
+However, in both, PDFCase and PCA-LinReg Case, permeability distribution will change as mesh resolution is reduced.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
+\medskip
 With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase.
-Meanwhile, the PCA-LinReg Case will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
+Meanwhile, the PCA-LinReg Case will retain this specific permeability distribution (\ie Fig.~\ref{fig:PermFields}(e)) for such mesh resolution (\ie if linear interpolation is used, but this digresses from the aim of this work and it will be discussed in future publications).
 Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block.
@@
 
+\medskip
 Furthermore, prior to the pre-processing required for evaluating the ArithMeanCase, HarmMeanCase and the PDFCase it is necessary to have an understanding of the whole domain and pre-define blocks with similar properties (\ie blocks $K1,~K2,~K3$ and $K4$) in this case.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 Albeit, one has to select the upgrid resolution carefully, if the resolution is too large then there is the risk of losing relevant data in the interpolation.
-The limits of the techniques used for the PCA-LinReg Case will be discussed in the author's future work.
+The limits of the techniques used for the PCA-LinReg Case will be discussed in future work.
 
-Before going on to review the results of the simulations, it is beneficial to briefly consider the Buckley-Leverett and cross-flow behaviour which are be used to validate the results from this work.
+\medskip
+Before discuss flow simulation results with permeability distribution resulted from methods described in Sections~\ref{subsection:pcspaces} and \ref{subsection:model}), it is beneficial to briefly consider the Buckley-Leverett flow model and cross-flow behaviour which are used to validate the results from this work.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 The equation determined that a plane of constant saturation progresses uniformly through the domain during the flow simulation.
-The equation is referred to as "simplified" because of the assumptions made while deriving it, some of which were ignored in this work.
+The equation is referred to as ``simplified" because of the assumptions made while deriving it, some of which were ignored in this work.
 Principally, this work ignores the fact that the equation deals with injection into an homogeneous permeability field while this work deals injection into two blocks ($K1$ and $K2$) with different permeabilities.
@@
 
-\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were somewhat replicated here for the simulations.
-Therefore, the work of \citet{dawe_2008} can be used to validate the resulting simulations from this work.
+\citet{dawe_2008} conducted experiments to investigate cross-flow, and as previously mentioned, the permeability field for the experimental work were replicated here for the simulations.
+Therefore, the work of \citet{dawe_2008} can be used to qualitatively validate the resulting simulations from this work.
 In particular, it will be noted that the simulations matches the experiment at the boundary between $K1$ and $K2$.
@@
 Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
-In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
-Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)).
+In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}a-b, even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}c show that the fluid experiences a resistance to flow at the interface between $K1$ and $K3$ (due to lower permeability at $K2$ and $K3$) which encourages the flow into $K4$ (\ie bottom-right block, Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}d-e).
 Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
-Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
-Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
+Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all cases at $t=1.15s$.
+Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}b-c) being nearly identical.
+Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}b compared to Fig.~\ref{fig:Saturationfield@t=1.15s}c.
 This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
-However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.
+However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}b-c is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) at the top left hand-side corner of block $K2$.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

@@
 
-Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
+Figure~\ref{fig:Saturationfield@t=1.15s}d also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) where it shows phase 1 moving from block $K2$ into $K4$.
 This inconsistency is with respect to this realization of the PDFCase.
-Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
+Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}e gives the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}a.
+
+\red{HOSVD????HOSVD????HOSVD????HOSVD????HOSVD????}
 
@@
 
-Upscaling is a form of reduced order model, and a method of implementing upscaling by coupling linear regression with PCA is introduced in this work.
+Upscaling is a form of reduced order model.
+A method of implementing upscaling by coupling linear regression with PCA is introduced in this work.
 For a 2-D model, SVD is used to decompose the existing permeability field to obtain the PCA space, while HOSVD is used for 3-D models.
-Within, the PCA space, linear regression (or interpolation) is used to reduce the data in the PCA space.
-The reduced data in the principal component space is then recombined to form a reduced data of the permeability field.
+Within, the PCA space, linear regression (or interpolation) is used to reduce data in PCA space.
+The reduced data in the PCS is then recombined to form a reduced data of the permeability dataset.
 
 Results show that the permeability field data reduction can be specifically defined for the PDFCase and the PCA-LinReg Case but not for the ArithMeanCase and the HarmMeanCase.
-This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution.
-The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.
-This is a huge advantage as it saves time during the data pre-processing stage, because sorting and calculations for each distinct region is avoided.
+This is because the latter cases will produce the same permeability dataset irrespective of the coarser resolution.
+The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability distribution before upscaling.
+This is a lareg advantage as it saves time during data pre-processing stages because sorting and calculations for each distinct region is avoided.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min
Updated the results and discussion section as well as the computational saving section

@@
 %\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
-\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
+\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
@@
 \citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
-The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure XXX.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure~\ref{fig:PCA_is_not_LinReg}.
 
@@
 
-Figure~\ref{fig:PermFields} shows permeability mapping for all cases, whereas Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+Figure~\ref{fig:PermFields} shows permeability mapping for all the 2-D cases, whereas Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
 \begin{displaymath}
-  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
+  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all the 2-D cases.} 
 \end{displaymath}
@@
 
-Figure~\ref{fig:PermFields} shows permeability distribution for all cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous.
+\subsection{2-D Models and Simulations}\label{subsection:results_discussion_2d}
+Figure~\ref{fig:PermFields} shows permeability distribution for all the 2-D cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous.
 Given that the BaseCase is also heterogeneous, it can be stated that models for the PDFCase and PCA-LinReg Case give a qualitatively better representation of the permeability dataset within the BaseCase.
@@
 
-Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all cases at $t=1.15s$.
-Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}b-c) being nearly identical.
+Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the 2-D cases at $t=1.15s$.
+Generally, saturation distribution for all the 2-D cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}b-c) being nearly identical.
 Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}b compared to Fig.~\ref{fig:Saturationfield@t=1.15s}c.
@@
 
-\red{HOSVD????HOSVD????HOSVD????HOSVD????HOSVD????}
+\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
+
+Following on from the work described for the 2-D models and simulations, Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a) and (b) presents the mesh grid for building the 3-D models.
+Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case.
+While Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case.
+The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
+
+Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases.
+The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case is obtainable with HOSVD for a 3-D model.
+Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model which is in Figure~\ref{fig:3D_PermFields}(b).
+When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable.
+For example:
+\begin{enumerate}
+\item The model retains heterogeneity within each region
+\item A single realization will be obtained for the same upgrid resolution
+  \item The correlation to local heterogeniety in the base case is maintained
+\end{enumerate}
+
+Figure~\ref{fig:Saturationfield4_3DCases}(a)-(c) and Figure~\ref{fig:Saturationfield4_3DCases}(d)-(f) show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
+
+\begin{displaymath}
+  t = 0.18,~0.28\text{ and } 0.42 \text{ s.} 
+\end{displaymath}
+
+Figure~\ref{fig:Saturationfield4_3DCases}(a) and (d), which represent the phase 1 saturation distribution for the base case and the 3-D PCA-LinReg case respectively at time $t = 0.18$, retain the mesh grid to give a more details view of the flow pattern.
+Comparing, Figure~\ref{fig:Saturationfield4_3DCases}(b) and (e) as well as Figure~\ref{fig:Saturationfield4_3DCases}(c) and (f) indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
+A detailed quantitative analysis of this upscaled model will be presented in the authors' future work.
+
+\subsection{Computational Cost}\label{subsection:comp_effort}
+
+An accurate measure of the CPU cost is not available at this time, however a general note can be made regarding the savings in computational costs with respect to the upgridding resolution.
+
+The 2-D base case which had $4112$ elements was run for about $7$ hours while the upscaled 2-D case were completed under $20$ minutes.
+For the 3-D case, the base case which had $2109$ elements required about $6$ days to run while the upscaled 3-D case was completed in under $6$ hours.
 
@@
 The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability distribution before upscaling.
-This is a lareg advantage as it saves time during data pre-processing stages because sorting and calculations for each distinct region is avoided.
+This is a huge advantage as it saves time during data pre-processing stages because sorting and calculations for each distinct region is avoided.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

@@
 \subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
-
-Following on from the work described for the 2-D models and simulations, Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a) and (b) presents the mesh grid for building the 3-D models.
+Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}.
+Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations.
 Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

@@
 Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}.
-Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations.
-Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case.
-While Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case.
-The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
+Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations wich contain 2019 (BaseCase)and 303 tetrahedral \PNDG[1]{1} element-pairs (3-D PCA using HOSVD).
+The number of elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
 
 Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases.
-The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case is obtainable with HOSVD for a 3-D model.
-Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model which is in Figure~\ref{fig:3D_PermFields}(b).
+The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model.
+Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b).
 When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable.

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

@@
 \begin{enumerate}
-\item The model retains heterogeneity within each region
-\item A single realization will be obtained for the same upgrid resolution
-  \item The correlation to local heterogeniety in the base case is maintained
+  \item The model retains heterogeneity within each region;
+  \item A single realization will be obtained for the same upgrid resolution;
+  \item The correlation to local heterogeniety in the BaseCase is maintained.
 \end{enumerate}
 
-Figure~\ref{fig:Saturationfield4_3DCases}(a)-(c) and Figure~\ref{fig:Saturationfield4_3DCases}(d)-(f) show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
-
+Figures~\ref{fig:Saturationfield4_3DCases}a-c and Figs.~\ref{fig:Saturationfield4_3DCases}d-f show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
 \begin{displaymath}
@@
 
-Figure~\ref{fig:Saturationfield4_3DCases}(a) and (d), which represent the phase 1 saturation distribution for the base case and the 3-D PCA-LinReg case respectively at time $t = 0.18$, retain the mesh grid to give a more details view of the flow pattern.
-Comparing, Figure~\ref{fig:Saturationfield4_3DCases}(b) and (e) as well as Figure~\ref{fig:Saturationfield4_3DCases}(c) and (f) indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
-A detailed quantitative analysis of this upscaled model will be presented in the authors' future work.
+Figures~\ref{fig:Saturationfield4_3DCases}a,d, which represent the phase 1 saturation distribution for the BaseCase and the 3-D PCA-LinReg case, respectively at time $t = 0.18$, retain the mesh grid to give more details view of the flow pattern.
+Comparing Figs.~\ref{fig:Saturationfield4_3DCases}b,e  and Figs.~\ref{fig:Saturationfield4_3DCases}c,f, it indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
+A detailed quantitative analysis of this upscaled model will be presented in future work.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

@@
 
-Representation of heterogeneous properties (\ie permeability in this case) within a large system, is a challenge that cuts across many industries that deal with flows in porous media.
+Representation of heterogeneous petro-physical properties (\eg permeability) within a large system, is a challenge that cuts across many industries that deal with flows in porous media.
 This is because it is impossible to obtain the value of permeability at every point in realistic domains.
@@
 
-In this paper, a single realization of a permeability field was upscaled by first projecting the permeability field into a principal component analysis space (using SVD for 2D field and HOSVD for 3D fields).
+In this paper, a single realization of a permeability dataset was upscaled by first projecting the permeability field into a principal component analysis space (using SVD and HOSVD for 2- and 3-D geometries, respectively).
 Then linear regression was employed within each of the principal component spaces to obtain approximate representations of the initial principal component.
-The new principal components are then recombined to for a new permeability field with a reduced order.
+The new principal components are then recombined to form a new permeability dataset with a reduced order model.
 This PCA-linear regression method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
@@
 Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
-\red{Later}
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018_TrackedRevision.tex
Created Tracked version of updated manual

--- 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
@@
 \usepackage{comment}
+\usepackage[normalem]{ulem}
 
@@
 %\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
-\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
+\title{\red{\sout{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition}}\blue{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
@@
 \section{Introduction}\label{section:intro}
-Naturally occuring rock formations are inherently heterogeneous, which means that geophysical properties, such as permeability, pore spaces (\ie porosity) and pore throat vary spatially at different length scales.
+Naturally occuring rock formations are inherently heterogeneous, which means that \red{\sout{rock}} \blue{geophysical} properties, such as permeability, pore spaces (\ie porosity) and pore throat vary spatially at different length scales.
 Heterogeneity of rock formations is relevant in calculations of transport and storage of fluids in porous media (\ie multiphase flow in subsurface rocks).
@@
 It is possible to overcome these challenges by a family of techniques called {\it upscaling}.
-Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high-resolution domains with coarse descriptions (\ie low-resolution) of these properties \cite{Vereecken_2007}.
+Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high\blue{-}resolution domains with coarse descriptions (\ie low\blue{-}resolution) of these properties \cite{Vereecken_2007}.
 
-Upscaling techniques which best preserve statistical geophysical and thermo-physical properties of high-resolution domains result in optimal prediction of fluid flow dynamics.
-Over the past 60 years, several upscaling techniques were developed (see \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}).
+Upscaling techniques which best preserve statistical \red{\sout{and flow dynamics behaviour of the high resolution domain give the best representation of heterogeneous properties.
+There are several upscaling techniques which fall under different categories}} \blue{geophysical and thermo-physical properties of high-resolution domains result in optimal prediction of fluid flow dynamics.
+Over the past 60 years, several upscaling techniques were developed (see} \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}).
 Traditional upscaling techniques are deterministic in nature, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
@@
 \medskip
-{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
-Depending on the context in which MOR is used, it can be simply referred as `dimensionality reduction'.
-The definition of MOR also depends on the context in which it is used, but it suffices to state that MOR's are ale to captures essential features of a system, structure or parameter \cite{Schilders2008}.
+{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout \red{\sout{the}} applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
+Depending on the context in which MOR is used, it can \blue{be} simply \red{\sout{be}} referred as `dimensionality reduction'.
+The definition of MOR also depends on the context \red{\sout{it is being}} \blue{in which it is} used, but it suffices to state that \red{\sout{MOR captures}} \blue{MOR's are able to capture} the essential features of a system, structure or parameter \cite{Schilders2008}.
 This implies that an original system exists with more detailed information.
@@
 \citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998, which introduced the passive reduced-order interconnect macromodeling algorithm (PRIMA).
-Truncated balanced realization is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and proper orthogonal decompositions (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
+Truncated balanced realization is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis \blue{(PCA)} \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+Hankel-norm reduction \cite{Glover_1984} and proper orthogonal decompositions \blue{(POD)} \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
+\red{\sout{In this work, upscaling is performed by SVD in principal}}
 
 \bigskip
- In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems.
-This work focuses on reducing the order of permeability distribution for porous media flow simulations.
+ \blue{In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems.} This work focuses on reducing the order of permeability distribution for porous media flow simulations.
+
+\red{\sout{Four upscaling techniques are investigated in this work, arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
+The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie base case).
+The fourth upscaling technique is the crux of this research, it introduces singular value decomposition (SVD) as a method of upscaling using the concept of principal component space to reduce the order of the permeability distribution.}}
 
 \bigskip
-A brief overview of current upscaling methods in reservoir simulation is described in Section~\ref{section:general_upscaling}.
-Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
+\blue{A brief overview of current upscaling methods in reservoir simulation is described in Section~\ref{section:general_upscaling}.} Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
 The mathematical model is discretised by a high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017}.
@@
 
-Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}.
+\red{\sout{Section~\ref{section:intro} briefly introduced the rational behind upscaling}} Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}.
 Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades.
@@
 
-\subsection{PCA, SVD, POD, KLT and Reservoir Characterisation}\label{section:reservoir_char}
+\subsection{\blue{PCA, SVD, POD, KLT and Reservoir Characterisation}}\label{section:reservoir_char}
 
-PCA, SVD and POD are closely related.
-In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as Karhunen-Loeve Transformations (KLT) \cite{Jafarpour_2009}.
+\blue{PCA, SVD and POD are closely related.
+In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as Karhunen-Loeve Transformations (KLT)} \cite{Jafarpour_2009}.
 
-A number of recent research in reservoir engineering focus on  history matching (HM) problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
-History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
-It is important to note that reservoir configurations could be either a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
+\blue{A number of recent research in reservoir engineering focus on  history matching (HM) problems (see} \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
+\blue{History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy} \cite{Rwechungura_2011}.
+\blue{It is important to note that reservoir configurations could be either a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.}
 
-\citet{Jafarpour_2009} compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate.
-\citet{Tavakoli_2010} noted that HM calculation of sensitivities for all production data with respect to system parameters is not feasible.
-Hence, they explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matrix.
+\citet{Jafarpour_2009}\blue{ compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate.} \citet{Tavakoli_2010} \blue{noted that HM calculation of sensitivities for all production data with respect to system parameters is not feasible.
+Hence, they explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matrix.}
 
-Perhaps, work performed by \citet{Afra_2013,Afra_2016,Afra_2014} and \citet{Insuasty_2017} are more closely related to the one performed here.
-However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization.
-The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same flow simulator model used in this work.
-However, similarly to \citet{Tavakoli_2010}, \citeauthor{Xiao_2018} focused on reducing the number of variable used to describe the system.
+\blue{Perhaps, work performed by} \citet{Afra_2013,Afra_2016,Afra_2014} and \citet{Insuasty_2017}\blue{ are more closely related to the one performed here.
+However, similar to the work of} \citet{Jafarpour_2009}, \blue{they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization.
+The work o}f \citet{Xiao_2018} \blue{is also closely related to that performed here and interestingly, they used the same flow simulator model used in this work.
+However, similarly to} \citet{Tavakoli_2010}, \citeauthor{Xiao_2018} \blue{focused on reducing the number of variable used to describe the system.}
 
-Essentially, recent developments in the field of reservoir simulation described in this section make use of SVD theory to select the most suitable realization from multiple realizations or to reduce the representative system variables.
-However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of a single system variable (\ie{permeability}).
+\blue{Essentially, recent developments in the field of reservoir simulation described in this section make use of SVD theory to select the most suitable realization from multiple realizations or to reduce the representative system variables.
+However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of a single system variable (\ie{permeability}).}
 
@@
 The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}).
-These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}).
-Although, the numerical formulation used here is relatively new, it is not the focus of this work.
-The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation.
-However, extensive model and software quality assurance (\ie verification and validation tests) can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
+These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}).\blue{ Although, the numerical formulation used here is relatively new, it is not the focus of this work.
+The result and discussion section (Section} \ref{section:results_discussion}) refers to \citet{dawe_2008} \blue{for validation of the numerical formulation with respect to the 2D simulation.
+However, extensive model and software quality assurance (\ie verification and validation tests) can be found in the aforementioned references} \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
 
@@
 
-\section{Coupled PCA and Linear Regression}\label{section:pca_linreg}
+\section{\red{Singular Value Decomposition (SVD) and Application for Reducing the Order of Permeability Fields}\blue{Coupled PCA and Linear Regression}}\label{section:pca_linreg}
+
+\subsection{\red{A Brief Introduction to SVD}}
+\red{Given a matrix $\mathbf{A}\in\mathcal{R}^{m\times n}$, the singular value decomposition (SVD) is a method for factorizing $\mathbf{A}$, such that,
+\begin{equation}
+  \mathbf{A} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}^{\intercal}.
+\end{equation}}
 
@@
 \subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
-Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity.
-In addition, in the numerical simulations performed for this work, permeability is discretised element-wise with projection to the control volume space within each element-pairs (see \cite{Christou_2018}).
-Permeability values are assigned to the centre of the FE $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
+\blue{Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity.
+In addition, in the numerical simulations performed for this work, permeability is discretised element-wise with projection to the control volume space within each element-pairs (see \cite{Christou_2018}).} Permeability values are assigned to the centre of the FE $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
 For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed which is discretized with triangular elements (\PN[1]{2} and \PNDG[1]{1} element-pairs).
@@
 \subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS).
+\blue{Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS).
 Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, Section~\ref{subsubsection:pca_dimred_linreg}), before interpolation is used to implement further data reduction in PCS.
 The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
-An algorithm which impliments the procedure described here is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
+An algorithm which impliments the procedure described here is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}}
 
-The PCS is a particularly challenging to visualize as it represents projections which are embedded in SVD/HOSVD factors of the original permeability dataset.
-An aid for visualizing the PCS for a 2D permeability data is to write out $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
-A similar procedure can be extended to HOSVD for 3D permeability dataset.
-The decomposition of a matrix into its factors using SVD \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials.
+\blue{The PCS is a particularly challenging to visualize as it represents projections which are embedded in SVD/HOSVD factors of the original permeability dataset.
+An aid for visualizing the PCS for a 2D permeability data is to write out $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.\blue{ A similar procedure can be extended to HOSVD for 3D permeability dataset.
+The decomposition of a matrix into its factors using SVD} \cite{Cline_2007, Tharwat_2016} or HOSVD }\cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials.
 However, for completeness, \ref{subsection:svd_brief} and \ref{subsection:hosvd_brief} contain brief overviews of SVD and HOSVD, respectively.
@@
 \subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
-For the PCA-Linear regression reduced order model (PCA-LinReg) of the permeability data, all work is performed in PCS. This can be conducted in two steps (for 2-D models), thus:
+\blue{For the PCA-Linear regression reduced order model (PCA-LinReg) of the permeability data, all work is performed in PCS. This can be conducted in two steps (for 2-D models), thus}:
 \begin{description}
-  \item[Step 1:] Perform PCA \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+  \item[Step 1:] Perform PCA \cite{Hotelling_1933, Tharwat_2016} \blue{using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
 Note that, in the case with $z = r$, it can be assumed that {\it Step 1} has been ignored.
 However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
-The selected $z$ singular values also form a new diagonal matrix, $\mathbf{\Sigma_{new}}$ .
+The selected $z$ singular values also form a new diagonal matrix, $\mathbf{\Sigma_{new}}$ .}
 
-  \item[Step 2:] Interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) is conducted to reduce the number of data points in each column of $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+  \item[Step 2:] \blue{Interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) is conducted to reduce the number of data points in each column of $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
-The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.
+The reduced permeability field is calculated by multiplying  $\mathbf{U_{new2}}$, $\mathbf{\Sigma_{new}}$ and $\mathbf{V^{\intercal}_{new2}}$.}
 
@@
 
-These two steps can be readily replicated for 3-D models using HOSVD to obtain the PCA space.
+\blue{These two steps can be readily replicated for 3-D models using HOSVD to obtain the PCA space.}
 
-Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space: co-variance and SVD methods (see \cite{Tharwat_2016} detailed description of both methods).
+\blue{Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space: co-variance and SVD methods (see} \cite{Tharwat_2016} \blue{detailed description of both methods).
 In this work, the authors have opted to use the SVD method to obtain the PCA space, as singular vectors which make up the PCS have strong correlation to the coordinate axis they represent.
 This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.
+}
 
@@
 
-\citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
-The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure~\ref{fig:PCA_is_not_LinReg}.
-
+\citet{AndrewNg_2018} \blue{was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure~\ref{fig:PCA_is_not_LinReg}.}
+\blue{
 \begin{table}[h!]
@@
 \end{table}
+}
 
@@
 
-As previosly mentioned, four upscaling techniques are investigated in this work.
+\blue{As previosly mentioned, four upscaling techniques are investigated in this work.
 Arithmetic and harmonic means are used to obtain the first two upscaled representation and these two are classed as deterministic techniques.
 The third is a randomly generated permeability field with Gaussian distribution, prescribed by a probability density function (PDF) which was obtained from a domain discretised with high-resolution mesh with known permeability distribution (\ie `base case').
-The fourth upscaling technique is the crux of this research, it introduces a reduced order model which couples PCA and linear regression.
+The fourth upscaling technique is the crux of this research, it introduces a reduced order model which couples PCA and linear regression.}
 
@@
 
-\subsubsection{2-D PCA (SVD) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
+\subsubsection{\blue{2-D PCA (SVD) \& LinReg Case Pre-processing Algorithm}}\label{subsubsection:svdcase_preprocess_algorithm}
 \begin{description}
@@
 
-\subsubsection{3-D PCA (\ie{using HOSVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:hosvdcase_preprocess_algorithm}
-The algorithm for 3-D case is similar to that of the 2-D case described previously. However:
+\subsubsection{\blue{3-D PCA (\ie{using HOSVD}) \& LinReg Case Pre-processing Algorithm}}\label{subsubsection:hosvdcase_preprocess_algorithm}
+\blue{The algorithm for 3-D case is similar to that of the 2-D case described previously. However:
 \begin{enumerate}[1.]
@@
 \end{enumerate}
-The authors found that the Tensorly library package \cite{Tensorly_2018} helpful for implementation of the HOSVD algorithm.
+The authors found that the Tensorly library package \cite{Tensorly_2018} helpful for implementation of the HOSVD algorithm.}
 
@@
 
-Figure~\ref{fig:PermFields} shows permeability mapping for all the 2-D cases, whereas Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+Figure~\ref{fig:PermFields} \blue{shows permeability mapping for all the 2-D cases, whereas} Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} \blue{show phase saturation distribution during fluid injection for time,}
 \begin{displaymath}
@@
 
-Additionally, the number of \PN[1]{2} triangular element-pairs mesh resolution was reduced from $4112$ (BaseCase, Fig,~\ref{fig:HiRes_LowRes_Mesh}a) to $728$ (upscaled cases, Fig,~\ref{fig:HiRes_LowRes_Mesh}b), a reduction by a factor of approximately $5.6$.
+\blue{Additionally, the number of \PN[1]{2} triangular element-pairs mesh resolution was reduced from $4112$ (BaseCase}, Fig,~\ref{fig:HiRes_LowRes_Mesh}a) to $728$ (upscaled cases, Fig,~\ref{fig:HiRes_LowRes_Mesh}b), a reduction by a factor of approximately $5.6$.
 
@@
 
-\subsection{2-D Models and Simulations}\label{subsection:results_discussion_2d}
+\subsection{\blue{2-D Models and Simulations}\label{subsection:results_discussion_2d}}
 Figure~\ref{fig:PermFields} shows permeability distribution for all the 2-D cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous.
@@
 
-\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
-Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}.
-Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations wich contain 2019 (BaseCase)and 303 tetrahedral \PNDG[1]{1} element-pairs (3-D PCA using HOSVD).
-The number of elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
+\subsection{\blue{3-D Models and Simulations}\label{subsection:results_discussion_3d}}
 
-Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases.
-The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model.
-Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b).
-When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable.
+\blue{Following on from the work described for the 2-D models and simulations,} Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a) and (b) \blue{presents the mesh grid for building the 3-D models.} Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), \blue{with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case.
+While} Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), \blue{with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case.
+The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.}
+
+Figure~\ref{fig:3D_PermFields} \blue{shows the permeability distribution for the 3-D cases.
+The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case is obtainable with HOSVD for a 3-D model.
+Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model which is in} Figure~\ref{fig:3D_PermFields}(b).
+\blue{When this model is compared to the base case,} Figure~\ref{fig:3D_PermFields}(a), \blue{the same advantages of PCA-LinReg model from the 2-D case are observable.
 For example:
@@
 \end{enumerate}
-
-Figure~\ref{fig:Saturationfield4_3DCases}(a)-(c) and Figure~\ref{fig:Saturationfield4_3DCases}(d)-(f) show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
+}
+Figure~\ref{fig:Saturationfield4_3DCases}(a)-(c) and Figure~\ref{fig:Saturationfield4_3DCases}(d)-(f) \blue{show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,}
 
@@
 
-Figure~\ref{fig:Saturationfield4_3DCases}(a) and (d), which represent the phase 1 saturation distribution for the base case and the 3-D PCA-LinReg case respectively at time $t = 0.18$, retain the mesh grid to give a more details view of the flow pattern.
-Comparing, Figure~\ref{fig:Saturationfield4_3DCases}(b) and (e) as well as Figure~\ref{fig:Saturationfield4_3DCases}(c) and (f) indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
-A detailed quantitative analysis of this upscaled model will be presented in the authors' future work.
+Figure~\ref{fig:Saturationfield4_3DCases}(a) and (d), \blue{which represent the phase 1 saturation distribution for the base case and the 3-D PCA-LinReg case respectively at time $t = 0.18$, retain the mesh grid to give a more details view of the flow pattern.
+Comparing,} Figure~\ref{fig:Saturationfield4_3DCases}(b) and (e) as well as Figure~\ref{fig:Saturationfield4_3DCases}(c) and (f) \blue{indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
+A detailed quantitative analysis of this upscaled model will be presented in the authors' future work.}
 
-\subsection{Computational Cost}\label{subsection:comp_effort}
+\subsection{\blue{Computational Cost}}\label{subsection:comp_effort}
 
-An accurate measure of the CPU cost is not available at this time, however a general note can be made regarding the savings in computational costs with respect to the upgridding resolution.
+\blue{An accurate measure of the CPU cost is not available at this time, however a general note can be made regarding the savings in computational costs with respect to the upgridding resolution.}
 
-The 2-D base case which had $4112$ elements was run for about $7$ hours while the upscaled 2-D case were completed under $20$ minutes.
-For the 3-D case, the base case which had $2109$ elements required about $6$ days to run while the upscaled 3-D case was completed in under $6$ hours.
+\blue{The 2-D base case which had $4112$ elements was run for about $7$ hours while the upscaled 2-D case were completed under $20$ minutes.
+For the 3-D case, the base case which had $2109$ elements required about $6$ days to run while the upscaled 3-D case was completed in under $6$ hours.}
 
@@
 
-The author's future work will provide a quantitative analysis of the results obtained from the coupled PCA-Linear regression method.
-Additionally, future work will present other methods which follow a similar principle but also seek to optimize the quantitative results obtained.
+\blue{The author's future work will provide a quantitative analysis of the results obtained from the coupled PCA-Linear regression method.
+Additionally, future work will present other methods which follow a similar principle but also seek to optimize the quantitative results obtained.}
 
@@
 \appendix
-\section{\\A Brief Introduction to SVD}\label{subsection:svd_brief}
+\section{\\\blue{A Brief Introduction to SVD}}\label{subsection:svd_brief}
 Given a matrix $\mathbf{A}\in\mathcal{R}^{m\times n}$, the singular value decomposition (SVD) is a method for factorizing $\mathbf{A}$, such that,
@@
 
-\section{\\A Brief introduction to HOSVD}\label{subsection:hosvd_brief}
-Using the tensor notation from \citet{Kolda_2009}, given a tensor $\mathscr{X}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$, the higher order singular value decomposition (HOSVD) is a method for factorizing $\mathscr{X}$, such that,
+\section{\\\blue{A Brief introduction to HOSVD}}\label{subsection:hosvd_brief}
+\blue{Using the tensor notation from} \citet{Kolda_2009}, \blue{given a tensor $\mathscr{X}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$, the higher order singular value decomposition (HOSVD) is a method for factorizing $\mathscr{X}$, such that,}
 \begin{equation}
@@
 \end{equation}
-where tensor $\mathscr{G}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$ and is normally referred to the core tensor. Sub-tensors of $\mathscr{G}$ are orthogonal and ordered.\\
-And matrices $\mathbf{U}^{m}\in\mathcal{R}^{N_{m}\times N_{m}}$ are orthogonal factor matrices which could be thought of as the principal components in each mode
+\blue{where tensor $\mathscr{G}\in\mathcal{R}^{N_{1}\times N_{2}\times \cdots \times N_{m}}$ and is normally referred to the core tensor. Sub-tensors of $\mathscr{G}$ are orthogonal and ordered.}\\
+\blue{And matrices $\mathbf{U}^{m}\in\mathcal{R}^{N_{m}\times N_{m}}$ are orthogonal factor matrices which could be thought of as the principal components in each mode.}
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
Moved Jeff's version to replace my version

@@
 
-\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
+%\title{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
+\title{A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations}
 \author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes}
@@
 It is possible to overcome these challenges by a family of techniques called {\it upscaling}.
-Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
+Upscaling techniques solve both uncertainty and scaling problems by replacing discrete geological and fluid properties of detailed high-resolution domains with coarse descriptions (\ie low-resolution) of these properties \cite{Vereecken_2007}.
 
-Upscaling techniques which best preserve statistical properties and flow dynamics behaviour of the high resolution domain give the best representation of heterogeneous properties.
-There are several upscaling techniques which fall under different categories \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}.
+Upscaling techniques which best preserve statistical geophysical and thermo-physical properties of high-resolution domains result in optimal prediction of fluid flow dynamics.
+Over the past 60 years, several upscaling techniques were developed (see \cite{Hasting_2001, Renard_1997, Szymkiewicz_2013}).
 Traditional upscaling techniques are deterministic in nature, however over the last decade, techniques classed as stochastic have received great attention from academic and industrial porous media communities worldwide \cite{Guilleminot_2012, Ravalec-Dupin_2010, Verwoerd_2009}.
-One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media and they are able to address scaling and uncertainity problems.
+One of the reasons for this is because stochastic upscaling techniques are robust enough to handle multiphase flow in porous media and they are able to address scaling and uncertainity problems.statistical
 
 \medskip
-{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout the applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
-Depending on the context in which MOR is used, it can simply be referred as dimensionality reduction.
-The definition of MOR also depends on the context it is being used, but it suffices to state that MOR captures the essential features of a system, structure or parameter \cite{Schilders2008}.
+{\it Upscaling} is a term commonly used in the oil and gas sector and is often referred, throughout applied mathematics and engineering communities, as a form of model order reduction (or reduced order models, MOR/ROM).
+Depending on the context in which MOR is used, it can be simply referred as `dimensionality reduction'.
+The definition of MOR also depends on the context in which it is used, but it suffices to state that MOR's are able to capture the essential features of a system, structure or parameter \cite{Schilders2008}.
 This implies that an original system exists with more detailed information.
@@
 
-\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998 which introduced Passive Reduced-order Interconnect Macromodeling Algorithm (PRIMA).
-Truncated Balanced Realization  is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
-Hankel-norm reduction \cite{Glover_1984} and Proper Orthogonal Decomposition (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
+\citet{Schilders2008} provided a historical perspective on the development of Model Order Reduction, from the work of Fourier in 1807 which approximated a function with a few trigonometric terms, to the work of \citet{Odabasioglu_1998} in 1998, which introduced the passive reduced-order interconnect macromodeling algorithm (PRIMA).
+Truncated balanced realization is another MOR method developed by \citeauthor{Moore_1981}~\cite{Moore_1981}, which introduced the principal component analysis (PCA) \cite{Hotelling_1933} and \citeauthor{Golub1970}'s \cite{Golub1970} algorithm for solving singular value decomposition (SVD).
+Hankel-norm reduction \cite{Glover_1984} and proper orthogonal decompositions (POD) \cite{Sirovich_1987} are also MOR methods discussed in the references published in 1984 and 1987, respectively.
 The asymptotic waveform evaluation (AWE) \cite{Pillage_1990} was the first MOR method based on Krylov subspace technique, this method was followed by Pade-via-Lanczos method \cite{Feldmann_1995} and the PRIMA.
-In this work, upscaling is performed through linear regression in the PCA space which is obtained with SVD or HOSVD for 2D and 3D cases, respectively.
 
 \bigskip
-This work focuses on reducing the order of permeability distribution in porous media flow simulations.
+ In this work, upscaling is performed through linear regression in the PCA space which is obtained with high-order singular value decomposition (HOSVD/SVD) in 2-/3-D problems.
+This work focuses on reducing the order of permeability distribution for porous media flow simulations.
+
+\bigskip
+A brief overview of current upscaling methods in reservoir simulation is described in Section~\ref{section:general_upscaling}.
 Section~\ref{section:mathematical_model} introduces the mathematical model used to describe the relevant physics for multi-fluid flow through porous media and highlights the relevance of the permeability field.
-The mathematical model is discretised by a novel high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017} which couples both the fine resolution and upscaled representation of the permeability field.
+The mathematical model is discretised by a high-order accurate control volume finite element method (CVFEM) \cite{Gomes_2017}.
 Pre-processing statistical properties and post-simulation multiphase flow behaviour are investigated to assess the various upscaling techniques used.
-Four upscaling techniques are investigated in this work and they are named Arithmetric mean, Harmonic mean, probability density function (PDF) and PCA (using SVD for 2D models and HOSVD for 3D model) coupled with linear regression.
-
+Four upscaling techniques are investigated in this work and they are named arithmetric mean, harmonic mean, probability density function (PDF) and PCA (using SVD and HOSVD methods) coupled with linear regression.
 In Section~\ref{section:pca_linreg}, fundamental mathematics of SVD and associated properties are presented.
@@
 Section~\ref{section:model_simulation} is dedicated to model description and simulation.
-It starts by describing the high resolution (\ie base case) on which the four upscaling techniques are applied to.
-A brief summary of the pre-processing step for each of the models is also presented.
-Section~\ref{section:results_discussion} provides the results and further discussion on the results of the simulations, it also gives further interpretation to the result obtained from the SVD upscaling technique.
-Finally, Conclusions are drawn in Section~\ref{section:conclusion}.
+It starts by describing the high-resolution problem (\ie `base case') in which the four upscaling techniques are applied to.
+A brief summary of the pre-processing steps for each of the models is also presented.
+Section~\ref{section:results_discussion} provides the results and further discussion of the results, it also gives further interpretation to the result obtained from the SVD upscaling technique.
+Finally, conclusions are drawn in Section~\ref{section:conclusion}.
 
+\section{Upscaling}\label{section:general_upscaling}
 \subsection{Brief Overview of Upscaling}\label{section:overview_upscaling}
 
-Upscaling methods replace discrete geological and fluid properties of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}.
-This subject of upscaling heterogenous properties has interested industries (\ie oil and gas, CCS and waste management) as well as the academic community for over $7$ decades.
+Upscaling methods replace discrete geological and fluid properties of detailed (high-resolution) domains with coarse descriptions (low-resolution) of these properties \cite{Vereecken_2007}.
+Upscaling of heterogeneous properties has attracted the interest of several porous media flow communities (\eg oil and gas, CCS and waste management) worldwide for over $7$ decades.
+Those interested in large-scale reservoirs or groundwater generally take a two-stage geo-statistical approach.
 
-Those interested in large-scale reservoirs or ground water generally take a two-stage geostatistical approach.
-In the first stage, information from seismic data, well data and analogous outcrops is used to model the large scale heterogeneities associated with facies.
-In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model the rock properties of the facies \cite{Ewing_1997}.
-In addition to seismic and well data used in the previous stage, core data can be used as a sources of information for the statistical properties used to determine the random field in this stage.
+In the first stage, information from seismic data, well data and analogous outcrops is used to model the large-scale heterogeneities associated with facies.
+In the second stage, statistical models such as continuous multi-variate Gaussian field is used to model rock properties of the facies \cite{Ewing_1997}.
+In addition to seismic and well data used in the previous stage, core data can be used as a source of information for the statistical properties used to determine random fields in this stage.
 
-Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001}.
+A number of studies were carried out on upscaling of subsurface permeability (see \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001} for a few key references).
 \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities.
-The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.
+The general conclusion reached from this study was that the equivalent permeability lies between harmonic and arithmetic averages.
 
@@
 PCA, SVD and POD are closely related.
-In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as the Karhunen-Loeve Transformation (KLT) \cite{Jafarpour_2009}.
+In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as Karhunen-Loeve Transformations (KLT) \cite{Jafarpour_2009}.
 
-A lot of the recent research in the field of petroleum engineering field which use these techniques, focus on the problem of history matching \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}.
-History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}.
-It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
+A number of recent research in reservoir engineering focus on  history matching (HM) problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}).
+History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}.
+It is important to note that reservoir configurations could be either a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
 
-\citet{Jafarpour_2009} compares KLT to discrete cosine transform (DCT) and goes on to state that the DCT is computationally more efficient than the KLT while being almost as accurate.
-\citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible.
-Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.
+\citet{Jafarpour_2009} compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate.
+\citet{Tavakoli_2010} noted that HM calculation of sensitivities for all production data with respect to system parameters is not feasible.
+Hence, they explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matrix.
 
-Perhaps, the works of \citet{Afra_2013}, \citet{Afra_2016}, \citet{Afra_2014}, \citet{Insuasty_2017} are more closely related to the one performed here.
+Perhaps, work performed by \citet{Afra_2013,Afra_2016,Afra_2014} and \citet{Insuasty_2017} are more closely related to the one performed here.
 However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization.
-The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same CVFEM simulator used in this work.
-However, like the work of \citet{Tavakoli_2010}, the \citeauthor{Xiao_2018} were more interested in reducing the number of variable used to describe the system.
+The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same flow simulator model used in this work.
+However, similarly to \citet{Tavakoli_2010}, \citeauthor{Xiao_2018} focused on reducing the number of variable used to describe the system.
 
-Essentially, the recent developments in the field of petroleum engineering described here make use of SVD to select the most suitable realization from multiple realizations or to reduce the representative system variables.
-However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of one of the system variable (\ie{permeability}).
+Essentially, recent developments in the field of reservoir simulation described in this section make use of SVD theory to select the most suitable realization from multiple realizations or to reduce the representative system variables.
+However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of a single system variable (\ie{permeability}).
 
@@
 where $\alpha$ designates a phase, $\mathbf{q}_{\alpha}$ is the $\alpha$-th phase Darcy velocity and $\mathbf{u}_{\alpha}$ is the saturation-weighted Darcy velocity.
-$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are the phase dynamic viscosity, pressure, density and source term, which may include gravity and/or capillarity, respectively.
-$\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ is the phase relative permeability, which is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is a function of the vector position $\mathbf{r}$, and time, $t$.
+$\mu_{\alpha}$, $p_{\alpha}$, $\rho_{\alpha}$, and $\mathbf{s}_{{u}_\alpha}$ are phase dynamic viscosity, pressure, density and source term (which may include gravity and/or capillarity), respectively.
+$\mathbf{K}\left(\mathbf{r}\right)$ and $\mathcal{K}_{{r}_\alpha}\left(S_{\alpha}\right)$ are absolute and phase-relative permeability, respectively.
+The later is a function of the phase saturation $S_{\alpha}\left(\mathbf{r},t\right)$, which in turn is spatial- and time-dependent.
 
@@
 \end{equation}
-are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{pavlidis_2013b}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
+are discretised in space with CV basis functions, and in time with the $\theta$-method \cite{gomes_book_2012}. In Eqn.~\ref{saturation_equation}, $\phi$ is the porosity and $s_{cty}$ is a source term.
 
@@
 The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}).
-These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013}).
+These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}).
 Although, the numerical formulation used here is relatively new, it is not the focus of this work.
 The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation.
-However, more extensive validation tests can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
+However, extensive model and software quality assurance (\ie verification and validation tests) can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
 
 \medskip
-Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is the absolute permeability tensor of the porous medium and it is a function of the vector position $\mathbf{r}$.
-$\mathbf{K}$ is prescribed in the system of governing conservative equations, \ie it is an indepedent input variable.
-Since $\mathbf{K}$ is a petrophysical rock property that varies spatially, it cannot be determined at every spatial coordinate.
+Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is prescribed in the system of governing conservative equations, \ie it is an independent input variable.
+Since $\mathbf{K}$ is a petrophysical property of geological formations that varies spatially, it cannot be determined at every grid point (\ie spatial coordinate).
 And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations.
-This is the reason upscaling is required for processing permeability variables.
-Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($km$)\cite{ECMI_2004}.
-The upscaling discussed here is from the micro scale also known as the Darcy scale.
+This is the reason upscaling is required for processing permeability spatial variability.
+Upscaling can be performed from the continuum scale, across the micro-scale ($mm$), local- and meso-scale ($m$) to field-scale ($km$)\cite{ECMI_2004}.
+The upscaling discussed here is for micro-scale, also known as the Darcy scale.
 
-\section{PCA coupled with Linear Regression}\label{section:pca_linreg}
+\section{Coupled PCA and Linear Regression}\label{section:pca_linreg}
 
@@
 \subsubsection{Understanding the permeability space}\label{subsubsection:visualization_permspace}
-Permeability can be represented as tensor quantity, but for the purpose of the following explanation (and the remaining of this paper), it is assumed that permeability is a scalar quantity.
-Furthermore, the simulator prescribes the permeability field by assigning permeability values to the centre of element-pairs \cite{Christou_2018} which discretises the simulation domain.
-
-Permeability values assigned in the centre of the element/cell represents values of permeability for the associated element $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
-For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed where the geometry is discritized by a square grid with the value for each square element assigned in the centre of the element.
-This explanation allow one to easily visualize this permeability space because it is defined by the cartesian coordinates system.
+Permeability can be represented as either tensor or scalar quantity, however for the purpose of the following explanation (and the remaining of this work), permeability is assumed as a scalar quantity.
+In addition, in the numerical simulations performed for this work, permeability is discretised element-wise with projection to the control volume space within each element-pairs (see \cite{Christou_2018}).
+Permeability values are assigned to the centre of the FE $\left(\text{\ie P}_{0}\text{DG element-pair}\right)$.
+For simplicity, in the remaining part of this sub-section, a $2D$ geometry is assumed which is discretized with triangular elements (\PN[1]{2} and \PNDG[1]{1} element-pairs).
+This explanation allows one to easily visualize this permeability space because it is defined by Cartesian coordinate system.
 
@@
 \subsubsection{Understanding the principal component spaces}\label{subsubsection:visualization_pcspaces}
-Essentially, the existing permeability space is transformed with SVD for 2D permeability field and HOSVD for 3D permeability fields, to principal component spaces (PCS).
-Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, see Section~\ref{subsubsection:pca_dimred_linreg} for more details), before interpolation is used to implement further data reduction in the principal component spaces.
+Essentially, the existing permeability space is transformed (with SVD and HOSVD for 2- and 3-D permeability data, respectively) to principal component spaces (PCS).
+Within the PCS, traditional PCA dimensionality reduction can be optionally performed (\ie{feature selection or elimination}, Section~\ref{subsubsection:pca_dimred_linreg}), before interpolation is used to implement further data reduction in PCS.
 The reduced data in the PCS is then transformed back into the permeability space to obtain a reduced permeability space.
-An algorithm which impliments the procedure described here, is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
+An algorithm which impliments the procedure described here is presented in Section~\ref{subsubsection:svdcase_preprocess_algorithm}
 
-The PCS is a bit challenging to visualize because it represents projections which are embedded in the SVD/HOSVD factors of the original permeability field.
-An aid for visualizing the PCS for a 2D permeability field is to write out the $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
-A similar intuition can be extended to HOSVD for 3D permeability fields.
+The PCS is a particularly challenging to visualize as it represents projections which are embedded in SVD/HOSVD factors of the original permeability dataset.
+An aid for visualizing the PCS for a 2D permeability data is to write out $\mathbf{U}$, $\mathbf{\Sigma}$ and $\mathbf{V^{\intercal}}$ matrices (or SVD factors) and consider the singular vectors (\ie columns in $\mathbf{U}$ and rows in $\mathbf{V^{\intercal}}$) as separate PCS.
+A similar procedure can be extended to HOSVD for 3D permeability dataset.
 The decomposition of a matrix into its factors using SVD \cite{Cline_2007, Tharwat_2016} or HOSVD \cite{Kolda_2009, Lathauwer_2000} is covered in details in several published materials.
-However, for completeness, the appendix contains a brief introduction to SVD (\ref{subsection:svd_brief}) and HOSVD (\ref{subsection:hosvd_brief}).
+However, for completeness, \ref{subsection:svd_brief} and \ref{subsection:hosvd_brief} contain brief overviews of SVD and HOSVD, respectively.
 
 \subsubsection{Reduced Order Model/Principal Component Space Reduction}\label{subsubsection:pca_dimred_linreg}
-For the PCA-Linear regression (PCA-LinReg) reduced order model of the permeability field, all the work is done in the principal component spaces.
-This can be completed in two steps, which is exemplified for the 2D model thus:
-\begin{enumerate}
-  \item The first step is the principal component analysis (PCA) \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
-
-Note that, in the case with $z = r$, it can be assumed that step 1 has been ignored.
+For the PCA-Linear regression reduced order model (PCA-LinReg) of the permeability data, all work is performed in PCS. This can be conducted in two steps (for 2-D models), thus:
+\begin{description}
+  \item[Step 1:] Perform PCA \cite{Hotelling_1933, Tharwat_2016} using the SVD method, where the singular values are examined and, based on a pre-defined criteria, $z$ singular values are selected, starting from $\sigma_{1}$ and in a decreasing order, where $z \leq r$.
+Note that, in the case with $z = r$, it can be assumed that {\it Step 1} has been ignored.
 However, when $z < r$, the first $z$ columns of $\mathbf{U}$ and the first $z$ rows of $\mathbf{V^{\intercal}}$ are extracted from $\mathbf{U}$ and $\mathbf{V^{\intercal}}$ to form new matrices $\mathbf{U_{new}}$ and $\mathbf{V^{\intercal}_{new}}$ respectively.
@@
 
-\item The second step involves interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) to reduce the data points in each column of  $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
+  \item[Step 2:] Interpolation within each singular vector (column in $\mathbf{U}$ and row in $\mathbf{V^{\intercal}}$) is conducted to reduce the number of data points in each column of $\mathbf{U}$ and in $\mathbf{V^{\intercal}}$.
 From this step,  $\mathbf{U_{new2}}$ and $\mathbf{V^{\intercal}_{new2}}$ are obtained.
@@
 
-\end{enumerate}
+\end{description}
 
-It is trivial to show that these two steps can be replicated for a 3-D model using HOSVD to obtain the PCA space.\\
+These two steps can be readily replicated for 3-D models using HOSVD to obtain the PCA space.
 
-Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space\cite{Tharwat_2016} , namely, the co-variance method and the SVD method.
-\citet{Tharwat_2016} goes on to describe both methods in details.
-In this work, the authors have opted to use the SVD method to obtain the PCA space.
-This is because the singular vectors which make up the PCS have a strong correlation to the coordinate axis they represent.
+Finally on the PCS, it is worth noting that two methods exist for obtaining PCA space: co-variance and SVD methods (see \cite{Tharwat_2016} detailed description of both methods).
+In this work, the authors have opted to use the SVD method to obtain the PCA space, as singular vectors which make up the PCS have strong correlation to the coordinate axis they represent.
 This was exploited in making the assumption that a linear relationship exist for the data in each of the PC spaces, hence the linear regression performed to reduce the data in the PCS.
@@
 \citet{AndrewNg_2018} was quoted to have said ``PCA is not linear regression, and despite some cosmetic similarity, these are actually totally different algorithms''.
-The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} below and can also be deduced from the figure~\ref{fig:PCA_is_not_LinReg}.
+The main differences between these two mathematical methods is summarised in the Table~\ref{table:pca_vs_linreg} and can also be deduced from Figure~\ref{fig:PCA_is_not_LinReg}.
 
@@
 \subsection{Model Description}\label{subsection:model}
-The BaseCase  (\ie fine mesh resolution) model for the permeabiliy field builds on the $2 \times 2$ block, $4$ quadrant model used initially by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
-These authors designed the permeability field for the quadrants in a checkerboard style which means that diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
+The BaseCase  (\ie high-resolution mesh) configuration for the permeability dataset builds on the $2 \times 2$ block, \ie $4$ quadrant model orginally used by \citet{Cardwell_1945} and later by \citet{Yeo2001} and \citet{dawe_2008}.
+In the domain designed by these authors, permeability is represented as checker-board in which diagonally opposite blocks retained the same permeability values with one set of diagonally opposite blocks having a higher permeability value compared to the other set.
 Hence, one set of diagonally opposite blocks are referred to as high permeability blocks while the other set is referred to as low permeability blocks.
 
-The BaseCase permeability model used here retains the checkerboard desgined used by the recently named authors.
-Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to), although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
-Furthermore, within each block, the permeability field varies within a pre-defined range and consists of $1600$ permeability values.
-More details on the design of the permeability field for the BaseCase is available in section~\ref{subsubsection:basecase_preprocess_algorithm}.
-Figures~\ref{fig:PermFields}a and~\ref{fig:PermFields}b give a pictorial representation of the permeability field for the base case with the mesh discretization visible and invisible, respectively.
+The BaseCase permeability model used here retains the checkerboard desgined used by these references.
+Albeit, the permeability dataset for each block in the set of diagonally opposite blocks have similar value (\ie not exactly the same as in the papers referred to).
+%, although one set can still be referred to as a set of high permeability blocks while the other set is referred to as a set of low permeability blocks.
+Furthermore, within each block, permeability dataset varies within a pre-defined range and consists of $1600$ permeability values.
+Details on the design of the permeability field for the BaseCase are described in Section~\ref{subsubsection:basecase_preprocess_algorithm}.
+Figures~\ref{fig:PermFields}a-b show permeability distribution for the BaseCase with the associated mesh resolution.
 Using the labelling scheme used by \citet{dawe_2008}, the quadrant model block $K1,~K2,~K3$ and $K4$ are top left, bottom left, top right and bottom right, respectively.
 
-As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field.
-When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}).
-The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).
-
-In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models.
-This effectively homogenizes the permeability field in each block.
-The upscaled permeability field for the third and fourth cases are referred to as PDFCase and PCA-LinReg Case, respectively.
-And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively.
-The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively.
-It is appropriate to note that although these models (PDFCase and PCA-LinReg Case) are upscaled, they retain heterogeneity within the blocks.
+As previously mentioned, four upscaled techniques applied to permeability dataset were obtained from the high-resolution (\ie the BaseCase) configuration.
+Prior to upscaling, mesh resolution of the BaseCase configuration was coarsened, Fig.~\ref{fig:HiRes_LowRes_Mesh}, in which the number of triangular elements was reduced from 4112 to 728.
+Arithmetic (ArithMean) and harmonic (HarmMean) averaging methods were initially applied to the BaseCase configuration.
+In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain permeability values for each block in the upscaled models.
+This effectively homogenized the permeability dataset in each block.
+Permeability dataset was also upscaled using probability density function (PDFCase) and SVD (PCA-LinReg Case).
+Description of these models are introduced in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm}-\ref{subsubsection:svdcase_preprocess_algorithm}.
+Different from ArithMean and HarmMeanand, PDFCase and PCA-LinReg Case are able to retain heterogeneity within each block.
 
 \subsubsection{BaseCase Pre-processing Algorithm}\label{subsubsection:basecase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
+\begin{description}
+  \item[Step 1:] A function is used to randomly generate uniform (\ie Gaussian) dataset for each block. The range for each block is as below:
   \begin{enumerate}[a)]
-    \item \textbf{K1} : $700 - 900$ mD
-    \item \textbf{K2} : $50 - 150$ mD
-    \item \textbf{K3} : $100 - 200$ mD
-    \item \textbf{K4} : $1000 - 1200$ mD
+    \item \textbf{K1} : $700 - 900$ mD;
+    \item \textbf{K2} : $50 - 150$ mD;
+    \item \textbf{K3} : $100 - 200$ mD;
+    \item \textbf{K4} : $1000 - 1200$ mD; 
   \end{enumerate}                                                    
-  \item The number of data points generated for each block is $1600$ and the data values are randomly allocated within each block in a structured pattern. Albeit, the simulation mesh is unstructured.
-  \item Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' (in step 1 above) for the randomly positioned dataset for each block.
-This file will be used by the CVFEM-based flow simulator to prescribe the permeability field for the base case.
-\end{enumerate}
+  \item[Step 2:] The number of data points generated for each block is $1600$, and data is randomly distributed within each block in a structured pattern. Albeit, the mesh is unstructured;
+  \item[Step 3:] Merge the dataset from different blocks into a single file retaining the original ``structured pattern'' ({\it Step 1}) for the randomly positioned dataset for each block.
+This data-structure will be used by the CVFEM-based flow simulator to prescribe the permeability dataset for the BaseCase configuration.
+\end{description}
 
 \subsubsection{PDFCase Pre-processing Algorithm}\label{subsubsection:pdfcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The datasets from step one of the pre-processing algorithm for the base case (Section~\ref{subsubsection:basecase_preprocess_algorithm}) are used to calculate mean and standard deviation for each block of the permeability field.
-  \item A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase for each of the four blocks  (\ie $400$ data points for each block).
-  \item The data values in the dataset for each block is randomly positioned within each block in a structured pattern. As in the base case, the simulation grid is unstructured.
-  \item Finally, the structured/arranged dataset from each block is combined into a single file and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs.
-\end{enumerate}
+\begin{description}
+  \item[Step 1:] Datasets from {\it Step 1} of Section~\ref{subsubsection:basecase_preprocess_algorithm} are used to calculate mean and standard deviation for each block of permeability data;
+  \item[Step 2:] A function which generates a Gaussian dataset using arithmetic mean and standard deviation is used to stochastically produce a quarter of the data points from the BaseCase configuration for each of the four blocks (\ie $400$ data points for each block);
+  \item[Step 3:] Data values in the dataset for each block is randomly positioned within each block in a structured pattern.
+Similarly to the BaseCase configuration, simulation mesh grid is also unstructured;
+  \item[Step 4:] Finally, the structured/arranged dataset from each block is combined into a single data-structure and then used by the flow simulator, which merge the permeability mapping to the mesh with the appropriate element-pairs (in simulations shown here, \PN[1]{2} and \PNDG[1]{1} element-pairs are used).
+\end{description}
 
-\subsubsection{2-D PCA (\ie{using SVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
-\begin{enumerate}[1.]
-  \item The permeability field obtained in step 3 of the pre-processing algorithm for the base case is factorized using SVD to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$.
-  \item A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$.
-(This step is optional, it is the conventional PCA dimensionality reduction)
-  \item The first $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices call $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$ respectively.
-(This step is necessary only if the optional step in 2 above is executed)
-  \item Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
-These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$.
-  \item The permeability field used for the SVD case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
-It is a permeability field with a quarter of the data values in the base case and therefore a permeability field with reduced order.
-\end{enumerate}
+\subsubsection{2-D PCA (SVD) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:svdcase_preprocess_algorithm}
+\begin{description}
+  \item[Step 1:] Permeability data obtained in {\it Step 3}  of Section~\ref{subsubsection:basecase_preprocess_algorithm} is factorized using SVD method to obtain $\mathbf{U}, \Sigma,$ and $\mathbf{V}$;
+  \item[Step 2:] A selected number ($z$) of singular values are retained in decreasing order of magnitude to form a new diagonal matrix, $\Sigma_{new}$ (this step is optional as it is the conventional PCA dimensionality reduction);
+  \item[Step 3:] First $z$ columns of $\mathbf{U}$ and $\mathbf{V}$ are selected to form new truncated matrices called $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, respectively.
+This step is necessary only if the optional step in 2 above is executed;
+  \item[Step 4:] Within each column of $\mathbf{U_{new}}$ and $\mathbf{V_{new}}$, a linear interpolation is performed to form a new column with the number of data points in each column reduced to half of the original column.
+These new columns are recombined to form $\mathbf{U_{new2}}$ and $\mathbf{V_{new2}}$;
+  \item[Step 5:] Permeability dataset used for the PCA-LinReg Case is the matrix $\mathbf{A_{new2}}$, which is defined as the product of $\mathbf{U_{new2}} \mathbf{\Sigma_{new}} \mathbf{V_{new2}^{\intercal}}$.
+It is a permeability dataset with a quarter of the data values of the BaseCase, \ie a permeability dataset with reduced order.
+\end{description}
 
 \subsubsection{3-D PCA (\ie{using HOSVD}) \& LinReg Case Pre-processing Algorithm}\label{subsubsection:hosvdcase_preprocess_algorithm}
-The algorithm for the 3-D case is similar to that of the 2-D case described above. However:
+The algorithm for 3-D case is similar to that of the 2-D case described previously. However:
 \begin{enumerate}[1.]
-\item In step 1 above, HOSVD is used for factorization instead of SVD.
-Therefore, a $3 x 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$.
-  \item It goes without saying that the core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section \ref{subsubsection:svdcase_preprocess_algorithm} above.
+  \item In {\it Step 1} of Section~\ref{subsubsection:svdcase_preprocess_algorithm}, HOSVD method is used for factorization instead of SVD.
+Therefore, a $3 \times 3$ core tensor is obtained in place of the $\mathbf{\Sigma}$ term, while 3 factor matrices are obtained in place of $\mathbf{U}$ and $\mathbf{V}$;
+  \item The core tensor is treated as the $\mathbf{\Sigma}$ term, while the 3 factor matrices are treated similarly to $\mathbf{U}$ and $\mathbf{V}$ as described in Section~\ref{subsubsection:svdcase_preprocess_algorithm}.
 \end{enumerate}
-The authors found the updated Tensorly library package \cite{Tensorly_2018} helpful in implimenting and executing the algorithm for HOSVD.
+The authors found that the Tensorly library package \cite{Tensorly_2018} helpful for implementation of the HOSVD algorithm.
 
 \subsection{Simulations}\label{subsection:simulations}
-For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
-No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain.
-Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix.
-In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
+In all performed numerical simulations, the domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate.
+A no-flux boundary conditions were imposed on upper and lower borders of the domain, while mixed fluids left the domain from the right-hand border of the domain.
+Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations, is described in the pore rock matrix by the modified \citet{Brooks_1964} (see \citep{alpak_1999}),
 \begin{eqnarray}
@@
 
-Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
+Figure~\ref{fig:PermFields} shows permeability mapping for all the 2-D cases, whereas Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
 \begin{displaymath}
-  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
+  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all the 2-D cases.} 
 \end{displaymath}
 
+Additionally, the number of \PN[1]{2} triangular element-pairs mesh resolution was reduced from $4112$ (BaseCase, Fig,~\ref{fig:HiRes_LowRes_Mesh}a) to $728$ (upscaled cases, Fig,~\ref{fig:HiRes_LowRes_Mesh}b), a reduction by a factor of approximately $5.6$.
+
 \section{Results and Discussion}\label{section:results_discussion}
+After reduction of dimensionality of the permeability dataset using the methods described in Sections~\ref{subsection:pcspaces} and \ref{subsection:model}), numerical simulations were performed with Fluidity/IC-FERST model (see Section~\ref{section:mathematical_model} and \cite{Gomes_2017, jackson_2013,salinas_2018}).
 
-Mesh resolution for the the BaseCase and upscaled cases are shown in Fig,~\ref{fig:HiRes_LowRes_Mesh}.
-Domain of the BaseCase (\ie high-resolution mesh) was discretised with $4112$ \PN[1]{1} triangular element-pairs, whilst in upscaled cases the domain was discretised with $728$ \PN[1]{1} triangular element-pairs.
-Therefore the resolution for the upscaled cases is reduced by a factor of approximately $5.6$.
+\subsection{2-D Models and Simulations}\label{subsection:results_discussion_2d}
+Figure~\ref{fig:PermFields} shows permeability distribution for all the 2-D cases and highlights homogeneous representation resulting from arithmetic and harmonic averaged, Figs.~\ref{fig:PermFields}c-d, whereas PDFCase and PCA-LinReg cases (Figs.~\ref{fig:PermFields}e-f) are inherently heterogeneous.
+Given that the BaseCase is also heterogeneous, it can be stated that models for the PDFCase and PCA-LinReg Case give a qualitatively better representation of the permeability dataset within the BaseCase.
+An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the coarsening has no influence on the resulting permeability distribution.
+However, in both, PDFCase and PCA-LinReg Case, permeability distribution will change as mesh resolution is reduced.
 
-Figure~\ref{fig:PermFields} compares the permeability distribution for all the models.
-As indicated in the figure's caption, the permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)).
-Additionally, Fig.~\ref{fig:PermFields}(b) to (f) show the cases without the element edges which discretize the domain.
-
-This highlights the fact that the permeability distribution of the ArithMean and HarmMean cases, Fig.~\ref{fig:PermFields}(c) and (d), are homogeneous within each block, while PDFCase and PCA-LinReg cases, Fig.~\ref{fig:PermFields}(e) and (f), are heterogeneous.
-Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the PCA-LinReg Case give a better representation of the BaseCase.
-An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability distribution.
-Whereas, for the PDFCase and the PCA-LinReg Case, the permeability field will change if the upgrid resolution changes.
-
+\medskip
 With respect to the PDFCase and for this specific resolution, it is important to note that Fig.~\ref{fig:PermFields}(e) is only one realiztion of infinitely many possible representations of the PDFCase.
-Meanwhile, the PCA-LinReg Case will retain this specific (\ie Fig.~\ref{fig:PermFields}(e)) permeability field for this specific resolution (\ie if linear interpolation is used, but this digresses from the main point and will be discussed in future work).
+Meanwhile, the PCA-LinReg Case will retain this specific permeability distribution (\ie Fig.~\ref{fig:PermFields}(e)) for such mesh resolution (\ie if linear interpolation is used, but this digresses from the aim of this work and it will be discussed in future publications).
 Therefore, the permeability value at a specific point in the PDFCase is not directly related to the data value at the nearest point in the BaseCase because the randomly generated PDF dataset is also randomly arranged within each block.
@@
 Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases.
-In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
-Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)).
+In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}a-b, even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$.
+Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}c show that the fluid experiences a resistance to flow at the interface between $K1$ and $K3$ (due to lower permeability at $K2$ and $K3$) which encourages the flow into $K4$ (\ie bottom-right block, Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}d-e).
 Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.
 
-Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$.
-Generally, saturation distribution for all cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) being the most identical.
-Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c).
+Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the 2-D cases at $t=1.15s$.
+Generally, saturation distribution for all the 2-D cases closely resemble each other with arithmetic and harmonic mean (Figs.~\ref{fig:Saturationfield@t=1.15s}b-c) being nearly identical.
+Albeit, closer inspection will reveal that there is more displacement in Fig.~\ref{fig:Saturationfield@t=1.15s}b compared to Fig.~\ref{fig:Saturationfield@t=1.15s}c.
 This is logical giving that the block mean values calculated for arithmetic mean is higher than that for harmonic mean.
-However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$.
+However, the important feature of Figs.~\ref{fig:Saturationfield@t=1.15s}b-c is that they poorly represent the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) at the top left hand-side corner of block $K2$.
 
-Figure~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$.
+Figure~\ref{fig:Saturationfield@t=1.15s}d also shows an inconsistency with the BaseCase (Fig.~\ref{fig:Saturationfield@t=1.15s}a) where it shows phase 1 moving from block $K2$ into $K4$.
 This inconsistency is with respect to this realization of the PDFCase.
-Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)
+Hence, PCA-LinReg Case in Fig.~\ref{fig:Saturationfield@t=1.15s}e gives the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}a.
+
+\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
+Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}.
+Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations wich contain 2019 (BaseCase)and 303 tetrahedral \PNDG[1]{1} element-pairs (3-D PCA using HOSVD).
+The number of elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
+
+Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases.
+The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model.
+Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b).
+When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable.
+For example:
+\begin{enumerate}
+  \item The model retains heterogeneity within each region;
+  \item A single realization will be obtained for the same upgrid resolution;
+  \item The correlation to local heterogeniety in the BaseCase is maintained.
+\end{enumerate}
+
+Figures~\ref{fig:Saturationfield4_3DCases}a-c and Figs.~\ref{fig:Saturationfield4_3DCases}d-f show the phase 1 saturation distribution for the base case at PCA(using HOSVD)-LinReg case for time,
+\begin{displaymath}
+  t = 0.18,~0.28\text{ and } 0.42 \text{ s.} 
+\end{displaymath}
+
+Figures~\ref{fig:Saturationfield4_3DCases}a,d, which represent the phase 1 saturation distribution for the BaseCase and the 3-D PCA-LinReg case, respectively at time $t = 0.18$, retain the mesh grid to give more details view of the flow pattern.
+Comparing Figs.~\ref{fig:Saturationfield4_3DCases}b,e  and Figs.~\ref{fig:Saturationfield4_3DCases}c,f, it indicates that the 3-D PCA-LinReg model gives a good representation of the flow pattern.
+A detailed quantitative analysis of this upscaled model will be presented in future work.
+
+\subsection{Computational Cost}\label{subsection:comp_effort}
+
+An accurate measure of the CPU cost is not available at this time, however a general note can be made regarding the savings in computational costs with respect to the upgridding resolution.
+
+The 2-D base case which had $4112$ elements was run for about $7$ hours while the upscaled 2-D case were completed under $20$ minutes.
+For the 3-D case, the base case which had $2109$ elements required about $6$ days to run while the upscaled 3-D case was completed in under $6$ hours.
 
@@
 
-Upscaling is a form of reduced order model, and a method of implementing upscaling by coupling linear regression with PCA is introduced in this work.
+Upscaling is a form of reduced order model.
+A method of implementing upscaling by coupling linear regression with PCA is introduced in this work.
 For a 2-D model, SVD is used to decompose the existing permeability field to obtain the PCA space, while HOSVD is used for 3-D models.
-Within, the PCA space, linear regression (or interpolation) is used to reduce the data in the PCA space.
-The reduced data in the principal component space is then recombined to form a reduced data of the permeability field.
+Within, the PCA space, linear regression (or interpolation) is used to reduce data in PCA space.
+The reduced data in the PCS is then recombined to form a reduced data of the permeability dataset.
 
 Results show that the permeability field data reduction can be specifically defined for the PDFCase and the PCA-LinReg Case but not for the ArithMeanCase and the HarmMeanCase.
-This is because the latter cases will produce the same permeability field irrespective of the upgrid resolution.
-The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability values before upscaling.
-This is a huge advantage as it saves time during the data pre-processing stage, because sorting and calculations for each distinct region is avoided.
+This is because the latter cases will produce the same permeability dataset irrespective of the coarser resolution.
+The PCA-LinReg Case is the only technique that does not require a prior knowledge of blocks with similar permeability distribution before upscaling.
+This is a huge advantage as it saves time during data pre-processing stages because sorting and calculations for each distinct region is avoided.
 

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018_TrackedRevision.tex
Updated document to track changes in abstract

@@
 
-In this paper, a single realization of a permeability field was upscaled by first projecting the permeability field into a principal component analysis space (using SVD for 2D field and HOSVD for 3D fields).
+In this paper,\red{\sout{a SVD-based method was developed to reduce the order of porous media permeability field (\ie{upscale})}} \blue{a single realization of a permeability field was upscaled by first projecting the permeability field into a principal component analysis space (using SVD for 2D field and HOSVD for 3D fields).
 Then linear regression was employed within each of the principal component spaces to obtain approximate representations of the initial principal component.
-The new principal components are then recombined to for a new permeability field with a reduced order.
-This PCA-linear regression method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
+The new principal components are then recombined to for a new permeability field with a reduced order.} This \blue{PCA-linear regression} method was compared to traditional industry-standard upscaling techniques (\eg arithmetic and harmonic averaging) and to a stochastic-based (probability density function, PDF) method of upscaling, to highlight its benefits/performance.
 
-It was shown that the new upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
-Additionally, the upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
+It was shown that the \red{\sout{SVD}} new upscaling technique retained the heterogenous nature of the BaseCase (\ie high-resolution configuration).
+Additionally, the \red{\sout{SVD}} upscaling technique did not require {\it a priori} understanding of similar permeability blocks within the existing domain.
 
@@
 \begin{keyword} %% keywords here, in the form: keyword \sep keyword
-Principal Component Analysis (PCA) \sep Linear Regression \sep Higher-Order Singular Value Decomposition (HOSVD) \sep Upscaling \sep Reduced Order Models (ROM) \sep Permeability.  
+\blue{Principal Component Analysis (PCA)} \sep \blue{Linear Regression} \sep \blue{Higher-Order Singular Value Decomposition (HOSVD)} \sep Upscaling \sep Reduced Order Models (ROM) \sep Permeability.
 \end{keyword}

### 2018-12-06 Papers/AppliedMaths2018/Resubmission/Highlights_resubmission.tex
Updated Highlights by making the character length for each bullet point less than 125 as requested by the editor

@@
 \begin{enumerate}
-  \item Implemented a reduced order model (\ie{upscale}) of a permeability field by coupling linear regression with Principal Component Analysis, PCA (where PCA is obtained with singular value decomposition, SVD, for 2D cases and Higher Order Singular Value Decomposition, HOSVD, for 3D cases)
-  \item For the 2D Case, benchmarked the coupled PCA (using SVD) and linear regression method by comparing with Arithmetric mean, Harmonic mean, and Probability Density Function (PDF) models, as well as the BaseCase (which is the fine grid model for the 2D case)
-  \item For the 3D case, benchmarked the coupled PCA (using HOSVD) and linear regression method by comparing with the BaseCase (also known as the fine grid model for the 3D case)
-  \item A high-order accurate control volume FEM multiphase flow simulator was used to perform a qualitative comparision of the simulation results from the models for both the 2D and the 3D cases
+  \item Coupled linear regression with Principal Component Analysis, PCA, using SVD to obtain a 2D reduced order model
+  \item Benchmarked the 2D PCA and linear regression method by comparing with Arithmetric mean, Harmonic mean and PDF models
+  \item Demonstrated that the PCA-Linear regression technique can be extended to 3-D models with Higher Order SVD (HOSVD)
+  \item Performed a qualitative comparision of the models and simulation results for both the 2D and the 3D cases
   \item The coupled PCA and linear regression model model presented a better representation compared to the other models

### 2018-12-06 Papers/AppliedMaths2018/Resubmission/Highlights_resubmission.tex
Properly edited revised Highlight as per editor's request to keep character length for each bullet below 125
Corrected typo and re-committed

@@
 \begin{enumerate}
-  \item Coupled linear regression with Principal Component Analysis, PCA, using SVD to obtain a 2D reduced order model
+  \item Coupled linear regression with Principal Component Analysis (PCA) using SVD, to obtain a 2D reduced order model
   \item Benchmarked the 2D PCA and linear regression method by comparing with Arithmetric mean, Harmonic mean and PDF models
-  \item Demonstrated that the PCA-Linear regression technique can be extended to 3-D models with Higher Order SVD (HOSVD)
+  \item Demonstrated that the PCA-Linear regression technique can be extended to 3D models with Higher Order SVD (HOSVD)
   \item Performed a qualitative comparision of the models and simulation results for both the 2D and the 3D cases

### 2019-07-22 Papers/AppliedMaths2018/Resubmission/Manuscript_sourceFiles/article_figure1.tex
latest update for resubmission

--- 2018-12-03 Papers/AppliedMaths2018/Resubmission/article_figure1.tex
@@
 }   
-\caption{Graphical comparision between linear regression and PCA (extracted from \citet{AndrewNg_2018})}
+\caption{Graphical comparision between linear regression and PCA (extracted from \citet{AndrewNg_2018}).}
 \vspace{1.5cm}
@@
 }   
-\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases with 4112 and 728 triangular elements respectively}
+\caption{Mesh grid used in the performed numerical simulations: (a) high-resolution and (b) upscaled cases with 4112 and 728 triangular elements, respectively.}
 \label{fig:HiRes_LowRes_Mesh}
@@
 }   
-\caption{Permeability field for the base case as well as the upscaled cases (Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures - \ie Fig.~\ref{fig:PermFields}(b) to (f))}
+\caption{Permeability field for the BaseCase and upscaled configurations (permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures).}
 \label{fig:PermFields}

### 2019-07-22 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex
latest update for resubmission

@@
 
-The revised manuscript was just submitted to the journal's portal. Also, please find below the response to the reviewer's comments , highlighting the main changes in the manuscript.
+The revised manuscript was just submitted to the journal's portal.
+Also, please find below the response to the reviewer's comments , highlighting the main changes in the manuscript.
+As requested, a tracked pdf version of the revised manuscript is submitted along with the a clean revised manuscript.
+Text in blue in indicate new or amended text while text in red indicate deleted text.
+The latex source document form the manuscript is also provided.
+A list of the documents submitted is provided at the end of this letter.
 
@@
       \item \label{R_E_P1} \blue{We deduced that the comment was a request for reference list within the manuscript (where more than one reference is cited) to be rearranged in ascending and and for reference source document (\ie{reference.bib}) to contain only the materials cited.
-Both tasks have been completed, however, we remain willing to quickly correct any other issue we may have overlooked.}
+Both tasks have been completed, however, we remain willing to quickly correct any other issue identified by the editor.}
         \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{Manuscipt Topic}
+\item \blue{Abstract}
+\item \blue{Section 1 Introduction}
+\item \blue{Section 2.2 PCA, SVD, POD, KLT and Reservoir Characterisation}
+\item \blue{4.1.3. Understanding the principal component spaces}
+\item \blue{4.1.3. Reduced Order Model/Principal Component Space Reduction}
+\item \blue{Figure 2}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{5.1.4. 3-D PCA (i.e., using HOSVD) \& LinReg Case Pre-processing Algorithm}
+\item \blue{Figure 11 to 13}
+\item \blue{Appendix B}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+\item \blue{Section 2.2 PCA, SVD, POD, KLT and Reservoir Characterisation}
+\item \blue{5.1.4. 3-D PCA (i.e., using HOSVD) \& LinReg Case Pre-processing Algorithm}
    \end{enumerate}
@@
       \begin{enumerate}
-      \item \label{R_R1_CompEffort} \blue{..........}\\
+      \item \label{R_R1_CompEffort} \blue{The authors thank the review for the comment, a section which discusses computational effort has now been included at section 6.3}\\
         \blue{Please see the following sections in the tracked version of the revised manuscript}
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{6.3. Computational Cost}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{3. Multi-Fluid Flow Model}
    \end{enumerate}
@@
 The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}\\
-     \blue{Please see the following sections in the tracked version of the revised manuscript}
-   \begin{enumerate}
- \item \blue{.......}
-   \end{enumerate}
         \end{enumerate}
@@
          \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive.
-These have been reduced from 86 to the most relevant 12 (which are included in the manuscript).
+These have been reduced from 86 to the most relevant 13 (which are included in the manuscript).
 Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}\\
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{Figure 1 to 13}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{5. Model Description and Simulation Setup}
    \end{enumerate}
@@
    \begin{enumerate}
-   \item \label{R_R2_NumFormulation_1} \blue{..........}\\
+   \item \label{R_R2_NumFormulation_1} \blue{The manuscript has been adjusted to clarify that the numerical formulation is not the novel part of the work, however, further clarification has been provided regarding how the equations are coupled and the permeability modelled}\\
      \blue{Please see the following sections in the tracked revised manuscript}
    \begin{enumerate}
- \item \blue{.......}
+\item \blue{3. Multi-Fluid Flow Model}
+ \item \blue{5.2. Simulations}
    \end{enumerate}
@@
  \begin{enumerate}
- \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}\\
+ \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been essentially made a part of the introduction by placing at the start of the manuscript \ie{immeidately after the introduction}}\\
    \blue{Please see the following sections in the tracked version of the revised manuscript}
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{2. Upscaling}
+\item \blue{2.1. Brief Overview of Upscaling}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{Appendix A}
+\item \blue{Appendix B}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{4.1.1. Understanding the permeability space}
    \end{enumerate}
@@
    \begin{enumerate}
- \item \blue{.......}
+ \item \blue{4.1.2. Understanding the principal component spaces}
+\item \blue{4.1.3. Reduced Order Model/Principal Component Space Reduction}
    \end{enumerate}

### 2020-01-15 Papers/WCCM_ECCOMAS_2020/wccm2020-abstract.tex
Initial commit which is obtained from the abstract submitted for the UK Interpore 2018

\documentclass[12pts,a4paper,amsmath,amssymb,floatfix]{article}
\usepackage[affil-it]{authblk}
\usepackage{wrapfig}
\usepackage{epsfig,graphicx,times,psfrag}
\usepackage{enumerate}%,comment}%,enumitem}
\usepackage{pdflscape}
\usepackage{color}
\newcommand{\red}{\textcolor{red}}

\pagestyle{empty}
\def\newblock{\hskip .11em plus .33em minus .07em}

\setlength\textwidth      {16.5cm}
\setlength\textheight     {22.0cm}
\setlength\oddsidemargin  {-0.3cm}

\setlength\headheight{0in} 
\setlength\topmargin{0.cm}  
\setlength\headsep{1.cm}
\setlength\footskip{1.cm}
\setlength\parskip{0pt}

\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\chead{The Fourth UK InterPore Conference, September 10-11, 2018, The University of Aberdeen, UK}
\renewcommand{\headrulewidth}{0pt}

\title{A Machine-Learning based formulation for Upscaling Heterogeneous Permeability Fields}
\author{Babatunde Lashore, Jefferson Gomes}
\affil{School of Engineering, University of Aberdeen, UK, b.lashore@abdn.ac.uk}
\date \today
\begin{document}
\maketitle
\thispagestyle{fancy}
\begin{abstract}

The porous media community has been investigating the representation of heterogeneous petro-physical properties (

In a previous work, a technique for upscaling a permeability field using Singular Value Decomposition (SVD) was discussed \cite{Lashore_2018}. In that work, permeability was used as an example of an heterogeneous quantity (parameter), which introduced problems relating to scale and uncertainity during simulations of flow in porous media. The crux of the work, was the application of linear interpolation to singular vectors of the high resolution permeability field dataset, within the principal component space projection of the high resolution permeability field dataset. This was performed to obtain a new upscaled and upgridded permeability field representation ({\it i.e.} a Reduced Order Model, ROM) of the initial high resolution permeability field.

The investigation of the previous work concluded with qualitative observations showing that the SVD upscaling technique faired better when compared to some traditional upscaling techniques (including a Stochastic PDF upscaling technique). However, a qualitative analysis of the results was not undertaken.

The current work builds on the existing work by introducing a quadratic cost function as a metric for quantifying how well the upscaled model represents the initial high resolution model. Additionally, the current work makes use of neural networks \cite{Smola_2008, Russell_2009} for obtaining an hypothesis function for singular vectors, within the principal component space projection of the high resolution permeability field. The hypothesis function is then used to predict singular vectors with a reduced order instead of performing linear interpolation as in the previous work. Finally, the reduced order model obtained with the hypothesis function is optimized using the existing quadratic cost function.

Results show that the neural network is able to learn the permeability field and it allows the optimization of the change in resolution ({\it i.e.} upscaling), to be performed by automation, with improved results.

\end{abstract}

\begin{thebibliography}{99}
%
\bibitem{Lashore_2018} B.Lashore, K. Christou, J.L.M.A Gomes (2018) $\lq$A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)', {\it Submitted for acceptance for publication in a Special Issue of the Applied Mathematical Modelling Journal}.
%
\bibitem{Smola_2008} A. Smola, S.V.N. Vishwanathan (2008) $\lq$Introduction to Machine Learning', {\it Cambridge University Press}, ISBN 0-521-82583-0.
%
\bibitem{Russell_2009} S.J Russell, P. Norvig (2009) $\lq$Artificial Intelligence: A Modern Approach', {\it Prentice Hall} ISBN 0-13-604259-7.
%
\end{thebibliography}

\end{document}

### 2020-01-15 Papers/WCCM_ECCOMAS_2020/wccm2020-abstract.tex
First draft sent to jeff for review

@@
-\documentclass[12pts,a4paper,amsmath,amssymb,floatfix]{article}
-\usepackage[affil-it]{authblk}
-\usepackage{wrapfig}
-\usepackage{epsfig,graphicx,times,psfrag}
-\usepackage{enumerate}%,comment}%,enumitem}
-\usepackage{pdflscape}
-\usepackage{color}
+\documentclass[a4paper]{wccm2020-abstract}
+\usepackage{parskip}
+\usepackage{pslatex}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\setlength{\parskip}{5pt}
+
+\newcommand{\JGnote}[1]{\fbox{\parbox{\textwidth}{ \color{red} JG Note $\Rightarrow$ #1}}}
+\newcommand{\BLnote}[1]{\fbox{\parbox{\textwidth}{ \color{green} BL Note $\Rightarrow$ #1}}}
 \newcommand{\red}{\textcolor{red}}
+\newcommand{\blue}{\textcolor{blue}}
+\newcommand{\green}{\textcolor{green}}
+\newcommand{\yellow}{\textcolor{yellow}}
+\newcommand{\frc}{\displaystyle\frac}
+\newcommand{\PN}[2][error]{P$_{#1}$DG-P$_{#2}$}
+\newcommand{\PNDG}[2][error]{P$_{#1}$DG-P$_{#2}$DG}
+\newcommand{\eg}{{\it e.g., }} 
+\newcommand{\ie}{{\it i.e., }}
+\newcommand{\st}{{\it s.t., }}
 
-\pagestyle{empty}
-\def\newblock{\hskip .11em plus .33em minus .07em}
+\title{ABSTRACT TITLE}
 
-\setlength\textwidth      {16.5cm}
-\setlength\textheight     {22.0cm}
-\setlength\oddsidemargin  {-0.3cm}
+\author{Babatunde O. Lashore$^{1*}$, Timiloluwa A. Onimisi$^{2}$ and Jefferson LMA. Gomes$^{3}$}
 
-\setlength\headheight{0in} 
-\setlength\topmargin{0.cm}  
-\setlength\headsep{1.cm}
-\setlength\footskip{1.cm}
-\setlength\parskip{0pt}
+\address{$^{1}$ School of Engineering, University of Aberdeen, UK.,  b.lashore@abdn.ac.uk
+\and
+$^{2}$ School of Engineering, University of Aberdeen, UK., t.onimisi.19@abdn.ac.uk
+\and
+$^{3}$ School of Engineering, University of Aberdeen, UK., jefferson.gomes@abdn.ac.uk and https://www.abdn.ac.uk/engineering/people/profiles/jefferson.gomes}
 
-\usepackage{fancyhdr}
+\keywords{Multi-Fluid Flow, Upscaling, Heterogeneity, Machine Learning}
 
-\pagestyle{fancy}
-\fancyhf{}
-\chead{The Fourth UK InterPore Conference, September 10-11, 2018, The University of Aberdeen, UK}
-\renewcommand{\headrulewidth}{0pt}
+\begin{document}
+\thispagestyle{empty}
 
-\title{A Machine-Learning based formulation for Upscaling Heterogeneous Permeability Fields}
-\author{Babatunde Lashore, Jefferson Gomes}
-\affil{School of Engineering, University of Aberdeen, UK, b.lashore@abdn.ac.uk}
-\date \today
-\begin{document}
-\maketitle
-\thispagestyle{fancy}
-\begin{abstract}
+The porous media community has been investigating the challenges of appropriately representing heterogeneous petro-physical properties (\eg permeability) for decades.
+The challenges considered here are two-fold and are exemplified using permeability.
+First, it is impossible to obtain the value of permeability at every point in a field scale geological domain.
+Secondly, the large scale data set involve in running the most realistic and accurate simulations are expensive in terms of computing resources and the time required to run the simulation.
+This challenge gave birth to upscaling, a model order reduction method.
 
-The porous media community has been investigating the representation of heterogeneous petro-physical properties (
-
-In a previous work, a technique for upscaling a permeability field using Singular Value Decomposition (SVD) was discussed \cite{Lashore_2018}.
-In that work, permeability was used as an example of an heterogeneous quantity (parameter), which introduced problems relating to scale and uncertainity during simulations of flow in porous media.
-The crux of the work, was the application of linear interpolation to singular vectors of the high resolution permeability field dataset, within the principal component space projection of the high resolution permeability field dataset.
+In a previous work, a technique for upscaling a permeability field using Singular Value Decomposition (SVD) was discussed.
+The crux of that work, was the application of linear interpolation to singular vectors of the high resolution permeability field dataset, within the principal component space projection of the high resolution permeability field dataset.
 This was performed to obtain a new upscaled and upgridded permeability field representation ({\it i.e.} a Reduced Order Model, ROM) of the initial high resolution permeability field.
 
-The investigation of the previous work concluded with qualitative observations showing that the SVD upscaling technique faired better when compared to some traditional upscaling techniques (including a Stochastic PDF upscaling technique).
-However, a qualitative analysis of the results was not undertaken.
+The current work builds on the existing work by making use of neural networks \cite{Smola_2008, Russell_2009} for obtaining an hypothesis function of the singular vectors, within the principal component space projection of the high resolution permeability field.
+The hypothesis function is then used to predict singular vectors with a reduced order instead of performing linear interpolation as in the previous work.
 
-The current work builds on the existing work by introducing a quadratic cost function as a metric for quantifying how well the upscaled model represents the initial high resolution model.
-Additionally, the current work makes use of neural networks \cite{Smola_2008, Russell_2009} for obtaining an hypothesis function for singular vectors, within the principal component space projection of the high resolution permeability field.
-The hypothesis function is then used to predict singular vectors with a reduced order instead of performing linear interpolation as in the previous work.
-Finally, the reduced order model obtained with the hypothesis function is optimized using the existing quadratic cost function.
+The investigation of the previous work concluded with qualitative analysis while the new work presents a quantitative analysis in addition to the qualitative analysis of the results.
 
-Results show that the neural network is able to learn the permeability field and it allows the optimization of the change in resolution ({\it i.e.} upscaling), to be performed by automation, with improved results.
-
-\end{abstract}
+Results show that the neural network is able to learn the permeability field. This makes it possible to  automate the process of optimizing the change of resolution ({\it i.e.} upscaling).
 
 \begin{thebibliography}{99}
-%
-\bibitem{Lashore_2018} B.Lashore, K.
-Christou, J.L.M.A Gomes (2018) $\lq$A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)', {\it Submitted for acceptance for publication in a Special Issue of the Applied Mathematical Modelling Journal}.
-%
-\bibitem{Smola_2008} A. Smola, S.V.N. Vishwanathan (2008) $\lq$Introduction to Machine Learning', {\it Cambridge University Press}, ISBN 0-521-82583-0.
-%
-\bibitem{Russell_2009} S.J Russell, P. Norvig (2009) $\lq$Artificial Intelligence: A Modern Approach', {\it Prentice Hall} ISBN 0-13-604259-7.
-%
+\bibitem{Gomes_2017} Gomes, J.
+L.
+M.
+A., Pavlidis, D., Salinas, P., Xie, Z., Percival, J.
+R., Melnikova, Y., Pain, C.
+C.
+and Jackson, M.
+D.
+A force-balanced control volume finite element method for multi-phase porous media flow modelling.\textit{International Journal for Numerical Methods in Fluids} (2017), \textbf{83}: 531--445.
+\bibitem{Smola_2008} Smola, A. and Vishwanathan, S.V.N \textit{Introduction to Machine Learning}. Cambridge University Press,
+ ISBN 0-521-82583-0).
+\bibitem{Russell_2009} Russell, S.J. and Norvig, P. Artificial Intelligence: A Modern Approach. Prentice Hall.
+ISBN 0-13-604259-7.
 \end{thebibliography}

### 2020-01-15 Papers/WCCM_ECCOMAS_2020/wccm2020-abstract.tex
Abstract submitted on the 15th January 2020

@@
 
-\title{ABSTRACT TITLE}
+\title{A Machine-Learning based formulation for Upscaling Heterogeneous Permeability Fields}
 
-\author{Babatunde O. Lashore$^{1*}$, Timiloluwa A. Onimisi$^{2}$ and Jefferson LMA. Gomes$^{3}$}
+\author{Babatunde O. Lashore$^{1*}$, Temiloluwa A. Onimisi$^{2}$ and Jefferson LMA. Gomes$^{3}$}
 
@@
 First, it is impossible to obtain the value of permeability at every point in a field scale geological domain.
-Secondly, the large scale data set involve in running the most realistic and accurate simulations are expensive in terms of computing resources and the time required to run the simulation.
-This challenge gave birth to upscaling, a model order reduction method.
+Secondly, the large scale data set involved with running the most realistic and accurate simulations are expensive in terms of computing resources and the time required to run the simulation.
+These challenges gave birth to upscaling, a model order reduction method.
 
@@
 
-The current work builds on the existing work by making use of neural networks \cite{Smola_2008, Russell_2009} for obtaining an hypothesis function of the singular vectors, within the principal component space projection of the high resolution permeability field.
+The current work builds on the existing work by making use of machine learning \cite{Smola_2008, Russell_2009} for obtaining an hypothesis function of the singular vectors, within the principal component space projection of the high resolution permeability field.
 The hypothesis function is then used to predict singular vectors with a reduced order instead of performing linear interpolation as in the previous work.
 
-The investigation of the previous work concluded with qualitative analysis while the new work presents a quantitative analysis in addition to the qualitative analysis of the results.
-
-Results show that the neural network is able to learn the permeability field. This makes it possible to  automate the process of optimizing the change of resolution ({\it i.e.} upscaling).
+Results show that the coupled ROM and ML upscaling model is able to learn the permeability field.
+This makes it possible to  automate the process of optimizing the change of resolution ({\it i.e.} upscaling).
 
